### 2015-10-19 DishSimulations/paper/DishSimulationsPaper_v0.tex

\documentclass[twocolumn]{emulateapj}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{natbib}
\citestyle{aa}

\begin{document}
\title{The Hydrogen Epoch of Reionization Array Dish: Characterization with Electromagnetic Simulations}
\author{
Ewall-Wice Aaron\altaffilmark{1,2},
Bradley Richard\altaffilmark{3,4},
Jacqueline Hewitt\altaffilmark{1,2},
Ali S. Zaki\altaffilmark{5},
Bowman Judd\altaffilmark{6},
Cheng Carina\altaffilmark{5},
Neben Abraham\altaffilmark{1,2},
Parsons Aaron\altaffilmark{5},
Patra Nipanjana\altaffilmark{5},
Thyagarajan Nithyanandan\altaffilmark{6}
}

\altaffiltext{1}{MIT Kavli Institute for Cosmological Physics}
\altaffiltext{2}{MIT Dept. of Physics}
\altaffiltext{3}{National Radio Astronomy Obs., Charlottesville VA}
\altaffiltext{4}{Dept. of Astronomy, U. Virginia, Charlottesville VA}
\altaffiltext{5}{Astronomy Dept. U. California, Berkeley CA}
\altaffiltext{6}{School of Earth and Space Exploration, Arizona State U.,
Tempe AZ}
\begin{abstract}
Using electromagnetic simulations, we assess the spectral properties of the antenna element of the Hydrogen Epoch of Reionization Array (HERA) in order to both establish a specification for the degree of spectral structure that is permissible to sufficiently isolate foregrounds and allow a detection of the cosmological 21\,cm signal and verify direct laboratory measurements of the dish characteristics. We find that our simulations are in good agreement with field measurements. Using simulations of foregrounds, we find that the $\approx -40$\,dB response at 60\,ns of the HERA dish is sufficient to isolate the cosmological 21\,cm signal $\approx 0.2$\,$h$Mpc$^{-1}$ at $z\approx 8.5$ and obtain a high signal to noise detection of the power spectrum.
\end{abstract}
\section{Introduction}
Observations of the redshift 21\,cm radiation neutral hydrogen in the intergalactic medium (IGM) have the potential to illuminate the hitherto unobserved {\it dark ages} and {\it cosmic dawn}, revolutionizing our understanding of the first UV and X-ray sources in the universe and how their properties influenced galactic evolution (see \citet{Furlanetto:2006Review}, \citet{Morales:2010}, and \citet{Pritchard:2012} for reviews). As of now, two major experimental endeavors are underway to make a first detection of the 21\,cm signal with most focusing on the Epoch of Reionization (EoR) in which UV photons from early galaxies transformed the hydrogen in the universe from neutral to ionized. The first involves measuring the sky-averaged global signal and is being pursued by experiments such as EDGES \citep{Bowman:2010}, LEDA \citep{Greenhill:2012}, DARE \citep{Burns:2012}, SciHi \citep{Voytek:2014}, and BIGHORNS \citep{Sokolowski:2015} coming online in their planning stages or taking data. The second attempts to observe spatial  fluctuations in the 21\,cm emission using radio interferometers. As of now, a first generation of interferometry experiments are taking data in an attempt to make a first statistical detection of the power spectrum of 21\,cm brightness temperature fluctuations. These include the Giant Metrewave Telescope (GMRT)  \citep{Paciga:2013}, the Low Frequency ARray (LOFAR), \citep{VanHaarlem:2013}, the Murchison Widefield Array \citep{Tingay:2013} and the Precision Array for Probing the Epoch of Reionization (PAPER) \citep{Parsons:2010}.

The primary obstacle to obtaining a high redshift detection of the cosmological signal through both of these methods is the existence of foregrounds that are $\sim 10^5-10^6$ times brighter. While requiring much greater sensitivity to global-signal experiments, interferometers have the advantage that these spectrally smooth foregrounds naturally avoid a significant region of $k$-space, known as the {\it EoR window}, occupying a region known as the {\it wedge} \citep{Datta:2010,Vedantham:2012,Parsons:2012,Thyagarajan:2013,Liu:2014a,Liu:2014b}, however any structure in the frequency response of the instrument has the potential to leak foregrounds into the EoR window, masking our signal. Indeed, low level spectral structures in the analogue and digital signal chains on the initial buildout of the MWA are proving to be a significant obstacle \citep{Dillon:2015b,EwallWice:2015a,Beardsley:2015b}.

While, in principle, spectral structure in the bandpass of the instrument may be removed in calibration, simulations show that any mismodeling of emission and the primary beam, potentially below the confusion limit, will mix the significant spectral structure on long baselines into short ones, masking the signal entirely \citep{Barry:2015}. While redundant calibration \citep{Wieringa:1992,Liu:2011,Zheng:2014} is able to calibrate the independent of a detailed model of the sky, any direction-dependent chromatic structure in the primary beam of the instrument introduces additional degrees of freedom that must be modeled, potentially leading to signal loss and the introduction of spurious spectral structure due to unmodeled foregrounds in long baselines. Because of our limited knowledge of foregrounds at low-frequency and the fidelity of calibration algorithms, the only sure way of building an instrument that will guarantee a detection of the redshifted 21\,cm emission is to design it such that all spectral structure in the signal chain is limited to a finite region of delay space, well below the wedge.

The Hydrogen Epoch of Reionization Array (HERA) is an instrument currently taking first observations in the Karoo in South Africa with the ultimate goal of detecting the power spectrum of 21\,cm brightness temperature fluctuations at high signal-to-noise (SNR) \citep{Pober:2014}. A central principle in HERA's design is that it be calibration fail-safe such that a detection of the signal is guaranteed, even if the chromaticity of the instrument is not calibrated out. This paper and its companions \citep{Neben:2015b,Patra:2015,Thyagarajan:2015c} describe a multifaceted approach to establishing a stringent specification on the spectral structure permissible for HERA to be calibration fail-safe and determine to what extent its design meets these requirements. We accomplish this by establishing a spec with simulations of foregrounds \citep{Thyagarjan:2015c} and verifying that HERA primary antenna element meets this spec with reflectometry \citep{Patra:2015} and Orbcomm beam mapping \citep{Neben:2015b}. These measurements are verified with detailed electromagnetic simulations which we describe in this work.

This paper is organized as follows. In \S~\ref{sec:Formalism} we lay out our analytic framework for describing the impact of reflections and spectral structure on foreground leakage in delay-transform power spectra. In \S~\ref{sec:Simulations} we describe our electromagnetic simulations of the HERA dish element. In \S~\ref{sec:Comparison} we compare our simulation results to direct measurements of the primary dish element and in \S~\ref{sec:Foregrounds} we apply our electromagnetic simulation results to simulations of foregrounds to determine the extent that the HERA dish's chromatic structure pollutes the EoR window and their impact on HERA's overall sensitivity. We conclude in \S~\ref{sec:Conclusion}.

\section{The Impact of Reflections on Delay-Transform Power Spectra}\label{sec:Formalism}
\section{Electromagnetic Simulations of the HERA dish element}\label{sec:Simulations}
\section{Comparing Simulations Results to Measurements}
\label{sec:Comparison}
\section{The Effect of the HERA dish Chromaticity on Foreground Leakage and Sensitivity}
\label{sec:Foregrounds}
\section{Conclusions}
\label{sec:Conclusion}
\bibliographystyle{apj}
\bibliography{biblio}
\end{document}

### 2015-10-21 DishSimulations/paper/DishSimulationsPaper_v0.tex
started appendix on reflections

@@
 \bibliography{biblio}
+
+\appendix
+\section{The Effect of Reflections and Cross-Talk on Visibilities}
+In this section, we develope formalism to discuss the impact of reflections of electromagnetic waves between antennas and within the signal chain of single antennas on foreground leakage in 21\,cm experiments.
+We start with the time varying electric field from a single source with location ${\bf \widehat{k}}$ on the sky, arriving at antenna $i$ with delay $\tau_i$ and antenna $j$ with delay $\tau_j$ with respect to the electric field at the origin which we denote as $s(t)$.
+We allow for two different types of reflections: First, we allow reflections within the analogue path of each $i^{th}$ antenna which we denote as $r_i(\tau)$.
+We also allow for single reflections between any $i-j$ antenna pair which we denote as $r_{ij}(\tau')$.
+Our choice of arbitrary $\tau'$, for now, allows for multi-path propogation between antennas, though we expect it to be dominated by the geometrical delay between the antenna pair.
+The electric field at antenna $i$ is given by
+\begin{equation}
+s_i(t) = \int d \tau' s(t+\tau_i-\tau') + \sum_{j \ne i} s(t + \tau_j - \tau_{ij}) r_{ij}(\tau')
+\end{equation}  
+In an FX correlator, the electric field is sampled, Fourier transformed, and cross multipled between antenna pairs to form visibilities. The Fourier transform step leaves us with 
+\begin{equation}
+\end{equation}
+
 \end{document}

### 2015-10-24 DishMeasurements/memo/DishBeamMeasurementsMemo.tex
working on dish beam memo

%% This is a sample manuscript marked up using the
%% AASTeX v5.x LaTeX 2e macros.

%% The first piece of markup in an AASTeX v5.x document
%% is the \documentclass command. LaTeX will ignore
%% any data that comes before this command.

%% The command below calls the preprint style
%% which will produce a one-column, single-spaced document.
%% Examples of commands for other substyles follow. Use
%% whichever is most appropriate for your purposes.
%%

%\documentclass[11pt,preprint2]{aastex}
% manuscript produces a one-column, double-spaced document:
%\documentclass[manuscript]{aastex}
%% preprint2 produces a double-column, single-spaced document:

%\documentclass{emulateapj}
\documentclass[preprint]{aastex}

\usepackage{natbib}
\usepackage{amsmath}
\bibliographystyle{apj}
\usepackage{graphicx}

%% Sometimes a paper's abstract is too long to fit on the
%% title page in preprint2 mode. When that is the case,
%% use the longabstract style option.

%% \documentclass[preprint2,longabstract]{aastex}

%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
%% If you are submitting to a journal that translates manuscripts
%% into SGML, you need to follow certain guidelines when preparing
%% your macros. See the AASTeX v5.x Author Guide
%% for information.

%% You can insert a short comment on the title page using the command below.

%\slugcomment{Not to appear in Nonlearned J., 45.}

%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
%% The left head contains a list of authors,
%% usually a maximum of three (otherwise use et al.).  The right
%% head is a modified title of up to roughly 44 characters.
%% Running heads will not print in the manuscript style.

%\shorttitle{HERA Dish Beam Measurements Memo, Rev $\alpha$}
%\shortauthors{Neben}

%% This is the end of the preamble.  Indicate the beginning of the
%% paper itself with \begin{document}.

\begin{document}

\title{HERA Dish Beam Measurements Memo, Rev. $\alpha$}

%% Use \author, \affil, and the \and command to format
%% author and affiliation information.
%% Note that \email has replaced the old \authoremail command
%% from AASTeX v4.0. You can use \email to mark an email address
%% anywhere in the paper, not just in the front matter.
%% As in the title, use \\ to force line breaks.

\author{Abraham Neben, Rich Bradley, Jackie Hewitt}
%\affil{MIT Kavli Institute, Massachusetts Institute of Technology, Cambridge, MA, 02139 USA}

\author{Oct 25, 2015}
%\affil{Wasamatta U}

%% Notice that each of these authors has alternate affiliations, which
%% are identified by the \altaffilmark after each name.  Specify alternate
%% affiliation information with \altaffiltext, with one command per each
%% affiliation.

%% Mark off your abstract in the ``abstract'' environment. In the manuscript
%% style, abstract will output a Received/Accepted line after the
%% title and affiliation information. No date will appear since the author
%% does not have this information. The dates will be filled in by the
%% editorial office after submission.

\begin{abstract}
write abstract here
comment on how this expt is still a work in progress
\end{abstract}

%\keywords{instrumentation: interferometers --- techniques: interferometric --- cosmology: observations --- dark ages, reionization, first stars}

%\section{Other title ideas}
%\begin{itemize}
%\item The relationship between noise correlation and monopole sensitivity in radio interferometers
%\item The self noise of sky noise in monopole interferometers
%\item Signal and noise in global signal interferometers
%\end{itemize}

%\section{Introduction}

\section{Experimental Setup}

We review the

\begin{figure*}[h]
\includegraphics[width=6.5in]{aerial.png}
\caption{Aerial photograph of the two reference dipoles deployed in Galford Meadow at the National Radio Astronomy Observatory--Green Bank 100\,m south of the HERA dish.}
\label{fig:null3}
\end{figure*}

specify which of the three HERA dishes we are talking about

sky coverage with orbcomm experiment

\section{Beam Modeling}

\subsection{Reference antenna model}
Our power ratio measurement relies upon an accurately modeled reference dipole, and to that end we improve on the model used in \citep{neben15} by XXX

\subsection{Dish models}
\label{sec:dishmodels}

We compare measured beam patterns with a simplistic analytic model and two numerical electromagnetic models. NEED MORE DETAILS ABOUT MODELING
\begin{enumerate}
	\item Airy pattern for a 14\,m aperture
	\item CST simulation (\texttt{hera-cst/HERA\_DISH\_paper\_feed\_cyl36\_140mhz\_Y\_healpix.fits})
	\item A separate simulation run by Dave
\end{enumerate}

\section{Null Experiments}

As in \citet{neben15}, we assess systematics using a ``null experiment'' in which we use a second reference dipole as the antenna-under-test (AUT). Taking the ratio of its measured power pattern with the model beam pattern amounts to a ratio of the row power responses received by the two antennas. This test thus probes the level of environmental systematics (i.e., reflections and varying ground properties) and antenna fabrication imperfections which affect each antenna differently. This is not a probe of modeling imperfections common to both antennas, but we expect such errors to be subdominant as the physical properties of the antenna are easier to characterize, and thus simulate, than local environmental effects.

We run three null experiments with the reference dipoles deployed varying distances from the HERA dish and from each other.

\begin{itemize}
\item \texttt{null1}: reference dipoles deployed 50\,m apart on a NS line, 50\,m south of the HERA dish
\item \texttt{null3}: same as \texttt{null1} but with the south-most reference antenna moved 5\,m west
\item \texttt{null4}: same as \texttt{null1} but with 100\,m separation between both reference antennas and from the dish
\end{itemize}

Figure \ref{fig:null1} shows the results from the \texttt{null1} experiment in the form of the ratio of the power responses of the two antennas (top panel), and slices through the E an H planes of the reconstructed power patterns (bottom panel). We collected roughly 100 satellite passes. Systematics at the few percent level are observed in  within $20^\circ$ of zenith, and at the $\sim10\%$ level farther out.

The magnitude of these systematics is comparable to those observed in the two other null experiments (Figures \ref{fig:null3} and \ref{fig:null4}), an their angular distribution appears largely unchanged. This suggests that the reference dipoles differ both due to varying environmental properties and perhaps intrinsic differences. In any case, these fractional errors propagate directly into the measured beampatterns of our subsequent feed and dish measurements.

\begin{figure*}[h]
\includegraphics[width=6.5in]{null1_rel.png}
\caption{Top: ratio maps of the powers received by two reference dipoles separated by 50\,m, deployed 50\,m south of the HERA dish. Bottom: absolute beam power plots constructed by multiplying the relative power maps by a model beampattern. }
\label{fig:null1}
\end{figure*}

\begin{figure*}[h]
\includegraphics[width=6.5in]{null3_rel.png}
\caption{Same as the previous null experiment except the south reference dipole was moved 5\,m west. The systematics are largely unchanged.}
\label{fig:null3}
\end{figure*}

\begin{figure*}[h]
\includegraphics[width=6.5in]{null4_rel.png}
\caption{Same as the first null experiment except the reference dipoles are separated by 100\,m and deployed 100\,m south of the HERA dish. The systematics remain at the few percent level near zenith and increase to $\sim10\%$ farther out, with somewhat, but not entirely different angular structure. }
\label{fig:null4}
\end{figure*}

\section{Feed Measurements}

Accurate modeling of both the dish and feed will be essential for final dish modeling. To that end, we deploy the feed on the ground facing the sky (Figure \ref{fig:feedpic}), replacing the north-most reference antenna in the \texttt{null3} configuration, to isolate the feed power pattern.

Figure \ref{fig:feed0} shows the measured feed beams (top panel) and slices through the E and H planes (bottom panel). Due to intermittent connection problems to the DAQ computer, we collected only 157 high signal-to-background satellite passes over a few days. Still, the data agree very well with the CST model for $\theta<55^\circ$, outside of which the E plane response starts narrows compared to the model by up to 5\,dB at $\theta=70^\circ$. Still, the data are quite sparse in these low regions due to the connection problems, and so the usual quality control cuts are likely less effective than usual.

\begin{figure*}[h]
\includegraphics[width=5in]{feed.jpg}
\caption{Feed deployed on the ground, facing the sky, replacing the north-most reference antenna in the \texttt{null3} configuration. }
\label{fig:feedpic}
\end{figure*}

\begin{figure*}[h]
\includegraphics[width=6.5in]{feed0_abs_old_ref_model.png}
\caption{Measurements of the feed power pattern, deployed so it faces the sky. The measurements agree well with the model for $\theta<55^\circ$, but start to diverge at large zenith angles, possibly due to quality control problems due to very sparse beam sampling.}
\label{fig:feed0}
\end{figure*}

\section{Dish Characterization}

\subsection{Power pattern measurements}

Having verified the feed power pattern, we deployed feed over the dish and proceed with dish measurements. We measure the power pattern with the feed at four different heights, 4\,m, 4.5\,m, 5\,m, and 5.3\,m, chosen to probe around the nominal focus of 4.5\,m (the nominal beam) and up to the maximum height of 5.3\,m allowed by pole height and rope stresses. Heights are measured from the dish surface to the feed backplane.

Inspecting the E and H plane slices through the measured beams (bottom panels) in Figures \ref{fig:dish3}, \ref{fig:dish1}, \ref{fig:dish2}, \ref{fig:dish4}, we generally see the main lobe narrow and the sidelobe level decrease. The improvement is also seen in the yellow and red main lobe in the beam maps (top panels) which narrow and approach the expected orientations: the EW (NS) main lobe is elongated in the NS (EW) direction. The last lift produced the smallest change in the beam suggesting it is quite near the best focus.

The sky coverage in these dish measurements extends out to typically $\theta\sim50-60^\circ$. Beyond that the ORBCOMM flux is sufficiently attenuated relative to diffuse galactic emission that a power ratio measurement between the two antennas is no longer a clean probe of their gains in the direction of the satellite. At these zenith angles, the beam sidelobes are roughly -30\,dB, and seem to be trending downward at the edge of the measured region.

\begin{figure*}[h]
\includegraphics[width=6.5in]{dish3_abs_old_ref_model.png}
\caption{Dish power pattern with the feed lowered 0.5\,m below nominal focus.}
\label{fig:dish3}
\end{figure*}

\begin{figure*}[h]
\includegraphics[width=6.5in]{dish1_abs_old_ref_model.png}
\caption{Dish power pattern with the feed at the nominal focus of 4.5\,m.}
\label{fig:dish1}
\end{figure*}

\begin{figure*}[h]
\includegraphics[width=6.5in]{dish2_abs_old_ref_model.png}
\caption{Dish power pattern with the feed raised 0.5\,m above nominal focus.}
\label{fig:dish2}
\end{figure*}

\begin{figure*}[h]
\includegraphics[width=6.5in]{dish4_abs_old_ref_model.png}
\caption{Dish power pattern with the feed raised to its maximum height of 0.8\,m above nominal focus.}
\label{fig:dish4}
\end{figure*}

In order to compute beam collecting areas and assess foreground leakage we require a beam covering the entire visible sky. For each measured dish beam, we interpolate over the unmeasured cells at $\theta\lesssim60$, then extrapolate outward to the horizon. This amounts to a smooth continuation of the beam response at the same $\sim-30$\,dB level suggested by the fringes of our measurements. We take this as a first possible model of the full sky dish beam, and construct a second with a gaussian cutoff at $\theta=60^\circ$ with $\sigma=2.5^\circ$, the pair of which span the space of likely horizon responses. This procedure is depicted in Figure \ref{fig:interpbeams} where we plot the measured nominal focus beam, the beam after interpolation and extrapolation, and the beam after applying the gaussian cutoff. Figure \ref{fig:interpbeamsslice} shows the interpolated/extrapolated beam and the beam with the cutoff along with various models to illustrate the different horizon responses more clearly.

\begin{figure}[h]
\includegraphics[width=3.5in]{measbeam_raw.png}
\includegraphics[width=3.5in]{measbeam_interp.png}
\includegraphics[width=3.5in]{measbeam_interp_expcutoff.png}
\caption{We construct full sky beams as required for Section \ref{sec:sci} by starting from the nominal focus beam (top left), interpolating over unobserved cells at $\theta\lesssim60^\circ$ and extrapolating to the horizon (top right), and applying a gaussian cutoff starting at $\theta=60^\circ$ with $\sigma=2.5^\circ$ (bottom left). These last two beams span the space of likely horizon responses.}
\label{fig:interpbeams}
\end{figure}

\begin{figure}[h]
\includegraphics[width=3.5in]{ew_beams_slice.pdf}
\caption{We plot the interpolated/extrapolated measured nominal focus  beam itself (blue), and with the gaussian cutoff (cyan), along with various model beams to illustrate the varying horizon responses. }
\label{fig:interpbeamsslice}
\end{figure}

To illustrate the results of these smoothing operations we plot slices through the nominal focus dish beam along with the three model beams discussed in Sec. \ref{sec:dishmodels}. The H (E) plane slice of the main lobe is shown at the top (bottom). The plots in the left side zoom in on the main lobe, while those on the right show a zoomed out view of the entire sky pattern.

\subsection{Collecting Area}

The collecting area of the antenna is related to the power pattern by the ratio of the beam gain to its beam-weighted solid angle as
\begin{equation}
	A=\frac{\lambda^2 B(0,0)}{\int B(\theta,\phi)d\Omega}
\end{equation}
We evaluate the collecting area for four of the beams discussed above and present the numbers in Table 1. We are unable to quantify the collecting area of the beam from Dave's simulation because it was run at too coarse an angular resolution. For the measured beams, we compute the collecting area using the interpolated/extrapolated beams with and without the gaussian cutoff at $\theta=60^\circ$.

 \begin{table}[h]
 \caption{ \label{table:collectingareatable}Collecting area (m$^2$) for modeled and measured dish beams at 137\,MHz. For measured beams, we calculate the collecting area after interpolation/extrapolation, also with the $60^\circ$ gaussian cutoff (in parentheses).}
\begin{tabular}{| l | l | l |}
\hline
  Airy & 155\,  \\
  CST sim & 67.0\,  \\
  \hline
  Measured, feed at 4\,m & 42.1 (44.3) \\
  Measured, feed at 4.5\,m & 68.5 (73.6) \\ 
  Measured, feed at 5\,m & 77.1 (82.6) \\
  Measured, feed at 5.3\,m & 93.0 (97.9)\\
  \hline
\end{tabular}
\end{table}

By definition, the Airy pattern has the largest collecting area equal to the dish cross section. The others model a realistic feed with a hanging screen (the skirt or ``kilt''), effectively tapering the dish response to radiation received from its fringes to mitigate cross-coupling and crosstalk between adjacent dishes. As expected, raising the height of the feed increases the illuminated area of the dish, and thus, its collecting area. As expected, the measured collecting area matches that of the CST model at the nominal focus height of 4.5\,m.

\section{Implications for HERA Science}
\label{sec:sci}

\subsection{Foreground Leakage}
for a power spectrum analysis, note that these tests test how leakage varies as a function of the brightness of emission at different delays, not leakage due to beam frequency dependence (ie, either pattern or overall gain)

\begin{figure*}[h]
\includegraphics[width=5.5in]{LST0deg_14m_42m_EWbaselinesblackman.png}
\includegraphics[width=5.5in]{LST60deg_14m_42m_EWbaselinesblackman.png}
\caption{aeuaoeuaoeu}
\label{fig:delayspec}
\end{figure*}

\begin{figure*}[h]
\includegraphics[width=5.5in]{LST0deg_14m_42m_NSslantbaselinesblackman.png}
\includegraphics[width=5.5in]{LST0deg_14m_42m_SEslantbaselinesblackman.png}
\caption{aeuaoeuaoeu}
\label{fig:delayspec2}
\end{figure*}

\subsection{Foreground Residuals}
the accuracy of beam modeling affects the science performance in additional ways ranging from missubtraction to imperfect foreground subtraction (Neben et al. 2015b submitted). The impact of beam mismodeling on science performance is left as future work.

\section{Discussion}

As expected, the Airy patter has the largest collecting area

the beam might be narrower simply because more dish is illuminated, but not necessarily a good thing, because we want more taper at the edge

comment on how this expt is still a work in progress

%% The reference list follows the main body and any appendices.
%% Use LaTeX's thebibliography environment to mark up your reference list.
%% Note \begin{thebibliography} is followed by an empty set of
%% curly braces.  If you forget this, LaTeX will generate the error
%% "Perhaps a missing \item?".
%%
%% thebibliography produces citations in the text using \bibitem-\cite
%% cross-referencing. Each reference is preceded by a
%% \bibitem command that defines in curly braces the KEY that corresponds
%% to the KEY in the \cite commands (see the first section above).
%% Make sure that you provide a unique KEY for every \bibitem or else the
%% paper will not LaTeX. The square brackets should contain
%% the citation text that LaTeX will insert in
%% place of the \cite commands.

%% We have used macros to produce journal name abbreviations.
%% AASTeX provides a number of these for the more frequently-cited journals.
%% See the Author Guide for a list of them.

%% Note that the style of the \bibitem labels (in []) is slightly
%% different from previous examples.  The natbib system solves a host
%% of citation expression problems, but it is necessary to clearly
%% delimit the year from the author name used in the citation.
%% See the natbib documentation for more details and options.

\bibliography{DishBeamMeasurementsMemo}

\end{document}
-

### 2015-10-24 DishSimulations/paper/DishSimulationsPaper_v0.tex
some small changes

@@
 In this section, we develope formalism to discuss the impact of reflections of electromagnetic waves between antennas and within the signal chain of single antennas on foreground leakage in 21\,cm experiments.
-We start with the time varying electric field from a single source with location ${\bf \widehat{k}}$ on the sky, arriving at antenna $i$ with delay $\tau_i$ and antenna $j$ with delay $\tau_j$ with respect to the electric field at the origin which we denote as $s(t)$.
-We allow for two different types of reflections: First, we allow reflections within the analogue path of each $i^{th}$ antenna which we denote as $r_i(\tau)$.
-We also allow for single reflections between any $i-j$ antenna pair which we denote as $r_{ij}(\tau')$.
+We start with the time varying electric field from a single source with location ${\bf \widehat{k}}$ on the sky, arriving at antenna $i$ with delay $\tau_i$ and antenna $j$ with delay $\tau_j$ with respect to the electric field at the origin which we denote as $s(t,{\bf \hat{k}})$.
+We allow for two different types of reflections: First, we allow reflections within the analogue path of each $i^{th}$ antenna which we denote as $r_i(\tau,{\bf \hat{k}})$.
+We also allow for single reflections between any $i-j$ antenna pair which we denote as $r_{ij}(\tau',{\bf \hat{k}})$.
 Our choice of arbitrary $\tau'$, for now, allows for multi-path propogation between antennas, though we expect it to be dominated by the geometrical delay between the antenna pair.
@@
 \begin{equation}
-s_i(t) = \int d \tau' s(t+\tau_i-\tau') + \sum_{j \ne i} s(t + \tau_j - \tau_{ij}) r_{ij}(\tau')
+s_i(t,{\bf \hat{k}}) = \int d \tau' r_i(\tau',{\bf \hat{k}})s(t+\tau_i-\tau') + \sum_{j \ne i} \int d \tau' s(t + \tau_j - \tau_{ij}) r_{ij}(\tau',{\bf \hat{k}})
 \end{equation}  
@@
 \begin{equation}
+\widetilde{s}_i(f,{\bf \hat{k}}) = \widetilde{s}(f,{\bf \hat{k}}) \left[ \int d \tau' r_i(\tau',{\bf \hat{k}})e^{2 \pi i(\tau_i - \tau')f} + \sum_{j\ne i} \int d \tau' e^{2 \pi i(\tau_j - \tau_{ij})f} r_{ij}(\tau',{\bf \hat{k}}) \right]
+\end{equation}
+Multiplying and averaging gives us the visibility for the single source we obtain
+\begin{align}\label{eq:SingleSource}
+v_{ij}'(f,{\bf \hat{k}}) & = \langle \widetilde{s}_i(f,{\bf \widehat{k}}) \widetilde{s}_j(f,{\bf \hat{k}}) \rangle_t \nonumber \\
+&=d \Omega  I(f,{\bf \hat{k}}) g_i(f) g_j^*(f) a_i(f,{\bf \hat{k}})a_j^*(f,{\bf \hat{k}}) e^{2 \pi i{\bf u_{ij}} \cdot {\bf \hat{k}}} + d \Omega I(f,{\bf \hat{k}}) \sum_{\ell \ne j} g_i(f)a_i(f,{\bf \hat{k}}) C_{\ell j}^*(f,{\bf \hat{k}}) e^{2 \pi i {\bf u_{\ell i} \cdot {\bf \hat{k}}}} \nonumber \\
+& + d \Omega I(f,{\bf \hat{k}})\sum_{k \ne i} g_j^*(f) a_j^*(f) C_{ki}(f,{\bf \hat{k}}) e^{2 \pi i {\bf u_{kj}\cdot {\bf \hat{k}}}} + d \Omega I(f,{\bf \hat{k}}) \sum_{k\ne i}\sum_{\ell \ne j} C_{ki}(f,{\bf \hat{k}}) C_{j\ell}^*(f,{\bf \hat{k}}) e^{2 \pi i {\bf u_{k\ell}}\cdot{\bf \hat{k}}},
+\end{align}
+where $g_i(f) a_i(f,{\bf \hat{k}}) = \int d \tau r_i(\tau,{\bf \hat{k}}) e^{2 \pi i f \tau}$ is the effective direction dependent gain of the system which can be factored into a directoin dependent and direction independent function where $g_i(f)$ is the gain of the analogue signal chain after the radiation has been absorbed by the feed and $a_i(f,{\bf \hat{k}})$ describes the chromatic electric field response of the antenna.
+The first term in equation~\ref{eq:SingleSource} is an effective visibility with self-reflections.
+The two cross terms and the last term involve the mixing of visibilities complementary too the $ij$ baseline and have the potential to introduce significant chromatic features since they potentially insert visibilities on much longer basline lengths.
+Assuming propogation along a single path directly between the antennas, we may write $C_{ik}(f,{\bf \hat{k}})$ as
+\begin{equation}
+C_{ki} = a_i({\bf \hat{k}}_{ki}) \frac{1}{r_{ik}}\left[\frac{d \sigma_k}{d \Omega}({\bf \hat{k}},{\bf \hat{k}}_{ij})\right]^{1/2} e^{2 \pi i \tau_{ik} f}
 \end{equation}

### 2015-10-26 DishSimulations/paper/DishSimulationsPaper_v0.tex

--- 2015-10-19 DishSimulations/paper/DishSimulationsPaper_v0.tex
@@
 \section{The Impact of Reflections on Delay-Transform Power Spectra}\label{sec:Formalism}
+In this section, we show how reflections in the analogue signal path of an antenna lead to foreground contamination of the EoR window.
+HERA's primary antenna element consists of a sleeved dipole element suspended 5\,m above the focus of a 14\,m diameter parabolic dish (Fig.~\ref{fig:Dish}).
+
+\begin{figure}
+\includegraphics[width=.5\textwidth]{figures/DishSA.png}
+\caption{The HERA primary antenna element-one of 19 undergoing currently taking the first observations in the Karoo in South Africa.
+The antenna consists of a sleeved dipole suspended within a 2\,m diameter skirt, five meters above the ground at the focal point of a 14\,m diameter dish.}\label{fig:Dish}
+\end{figure}
+
+ We show in Appendix~\ref{app:Reflections} that if an astronomical radio signal with time dependence at the location of the feed, $s({\bf \hat{k}},t)$, experience reflections within the dish such that the voltage recorded in the feed is
+\begin{equation}
+v(t) = \sum_n r_n({\bf \hat{k}}) s({\bf \hat{k}},t - \tau_n)
+\end{equation}
+Than the resulting visibilities obtained by cross correlating antenna $i$ and antenna $j$ are given by 
+\begin{equation}
+V'_{ij}(f) = \sum_{m,n} \int d \Omega R_{mn}({\bf \hat{k}}) e^{2 \pi i \Delta \tau_{mn}f} e^{2 \pi i {\bf u}_{ij} \cdot {\bf \hat{k}}} I(f,{\bf \hat{s}}),
+\end{equation}
+where $R_{mn}({\bf \hat{s}})=r_m r_n^*$, $I(f,{\bf \hat{s}})$ is the intensity of the signal on the sky, and can be decomposed into foregrounds and signal
+\begin{equation}
+I(f,{\bf \hat{s}}) = I_{fg}(f,{\bf \hat{s}})+I_{21}(f,{\bf \hat{s}})
+\end{equation}
+While $I_{fg}$ is on the order of $10^6$ times larger than $I_{21}$, the continuum emission from foregrounds is expected to be spectrally smooth. Hence, a {\it delay transform} defined by
+\begin{equation}
+\widetilde{V}_{ij}(\tau) = \int d f e^{-2 \pi i \tau f} V_{ij}(f)
+\end{equation}
+should, in principle, separate the foregrounds from the signal with foregrounds occupying the wedge.
+However, the introduction of the chromatic $e^{2 \pi i \Delta \tau_{mn}}$ terms leads to foreground contamination being convolved out to higher delays.
+\begin{equation}
+\widetilde{V}_{ij}'(\tau) = \sum_{m,n} \widetilde{V}_{ij,FG}^{mn}(\tau - \Delta \tau_{mn}) + \widetilde{V}_{ij,21}^{mn}(\tau - \Delta \tau_{mn})
+\end{equation}
+where $V_{ij}^{mn}$ is a visibility resulting from the effective primary beam, $R_{mn}({\bf \hat{k}})$, at delay $\Delta \tau_{mn}$ induced by the reflections.
+\begin{equation}
+V_{ij}^{mn} = \int d \Omega R_{mn}({\bf \hat{s}}) I(f,{\bf \hat{s}})e^{2 \pi i {\bf u}_{ij} \cdot {\bf \hat{s}}}
+\end{equation}
+The delay transform power spectrum estimate, $\widehat{P}$, is proportional to $|\widetilde{V}_{ij}'|^2$, hence 
+\begin{align}\label{eq:Reflections}
+\widehat{P} & \propto |\widetilde{V}_{ij,FG}(\tau)|^2 + |\widetilde{V}_{ij,21}(\tau)|^2 + 2 \text{Re}(\widetilde{V}_{ij,21}(\tau)\widetilde{V}_{ij,FG}^*(\tau)) \nonumber \\
+&+ \sum_{|\Delta \tau_{mn}| > 0} 2 \text{Re} \left[   \widetilde{V}^*_{ij} (\tau) \widetilde{V}^{mn}_{ij} (\tau - \Delta \tau_{mn})  \right] \nonumber \\
+&+ \sum_{\substack{|\Delta \tau_{op}|>0\\|\Delta \tau_{mn}|>0}} \widetilde{V}^{mn}_{ij} (\tau - \Delta \tau_{mn}) \widetilde{V}^{op*}_{ij}(\tau - \Delta \tau_{op})
+\end{align}
+In the absence of reflections, only the top line of equation~\ref{eq:Reflections} would enter the delay power spectrum estimate.
+The following lines involve the translation of the signal (including foregrounds and signal) out to the delay of each reflection and weighted by the effective primary beam of the reflection.
+Since each translated visibility is intrinsically $\sim 10^6$ times brighter than the signal, any reflection with a delay large enough to place it within the EoR window, must be sufficiently attenuated by $R_{mn}({\bf \hat{k}})$.
+The precise degree of attenuation is determined in \citep{Thyagarajan:2015c} using simulations of foregrounds and noise and sets the spec for our antenna.
+In this paper, we study $R_{mn}({\bf \hat{k}})$ for the HERA antenna element to verify that it both meets the spec and agrees with direct measurements of the antenna element with refelctometry \citep{Patra:2015} and Orbcomm measurements \citep{Neben:2015b}.
+
 \section{Electromagnetic Simulations of the HERA dish element}\label{sec:Simulations}
+In Fig.~\ref{fig:SimulationSetup} we show the geometery of the electromagnetic simulation. {\bf Rich: fill in the details here}
+\begin{figure}
+
+\subsection{The Simulations}
+\includegraphics[width=.5\textwidth]{figures/One_dish_Pfeed_render_pw_0deg.png}
+\caption{A rendering of our time domain simulation at $t=0$, demonstrating the geometry and setup of our electromagnetic simulation.
+The plane wave is started just above the feed (red plane).}\label{fig:SimulationSetup}
+\end{figure}
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{figures/SimulationIllustration.png}
+\caption{An illustration of our simulation products and their origin in the HERA antenna geometry.
+A plane wave is injected from above the feed (red line).
+The amplitude of the electric field of the plane wave at output of the feed along with the voltage at the feed terminal outputs is recorded (black line).
+The feed in our simulation is situated $5$\,m above the bottom of the dish, hence there is a $\approx 30$\,ns delay between when the plane wave passes the terminal for the first time (A) and when it is first absorbed in the dipole (B), leading to the voltage response.
+Of concern to 21\,cm experiments are the subsequent reflections between the feed and the dish (C) which can lead to large delay contamination of the EoR window.}
+\label{fig:Simulation}
+\end{figure*}
+\subsection{Deconvolving the Response Function}
+In our simulation, we obtain the voltage at the feed output as a function of time which we will call $v_{out}(t)$. It is related to the input lane wave through the equation 
+\begin{equation}
+v_{out}(t) = \sum_n r_n(\theta=0) v_{in}(t - \tau_n)
+\end{equation}
+which is essentially a convolution in time of $r_n(\theta=0)$ with the input plane wave 
 \section{Comparing Simulations Results to Measurements}
@@
 \bibliography{biblio}
+
+\appendix
+\section{The Effect of Reflections and Cross-Talk on Visibilities}\label{app:Reflections}
+In this section, we develope formalism to discuss the impact of reflections of electromagnetic waves between antennas and within the signal chain of single antennas on foreground leakage in 21\,cm experiments.
+We start with the time varying electric field from a single source with location ${\bf \widehat{k}}$ on the sky, arriving at antenna $i$ with delay $\tau_i$ and antenna $j$ with delay $\tau_j$ with respect to the electric field at the origin which we denote as $s(t,{\bf \hat{s}})$.
+We allow for two different types of reflections: First, we allow reflections within the analogue path of each $i^{th}$ antenna which we denote as $r_i(\tau,{\bf \hat{s}})$.
+We also allow for single reflections between any $i-j$ antenna pair which we denote as $r_{ij}(\tau',{\bf \hat{s}})$.
+Our choice of arbitrary $\tau'$, for now, allows for multi-path propogation between antennas, though we expect it to be dominated by the geometrical delay between the antenna pair.
+The electric field at antenna $i$ is given by
+\begin{equation}
+s_i(t,{\bf \hat{s}}) = \int d \tau' r_i(\tau',{\bf \hat{s}})s(t+\tau_i-\tau') + \sum_{j \ne i} \int d \tau' s(t + \tau_j - \tau_{ij}) r_{ij}(\tau',{\bf \hat{s}})
+\end{equation}  
+In an FX correlator, the electric field is sampled, Fourier transformed, and cross multipled between antenna pairs to form visibilities. The Fourier transform step leaves us with 
+\begin{equation}
+\widetilde{s}_i(f,{\bf \hat{s}}) = \widetilde{s}(f,{\bf \hat{s}}) \left[ \int d \tau' r_i(\tau',{\bf \hat{s}})e^{2 \pi i(\tau_i - \tau')f} + \sum_{j\ne i} \int d \tau' e^{2 \pi i(\tau_j - \tau_{ij})f} r_{ij}(\tau',{\bf \hat{s}}) \right]
+\end{equation}
+Multiplying and averaging gives us the visibility for the single source we obtain
+\begin{align}\label{eq:SingleSource}
+v_{ij}'(f,{\bf \hat{s}}) & = \langle \widetilde{s}_i(f,{\bf \widehat{k}}) \widetilde{s}_j(f,{\bf \hat{s}}) \rangle_t \nonumber \\
+&=d \Omega  I(f,{\bf \hat{s}}) g_i(f) g_j^*(f) a_i(f,{\bf \hat{s}})a_j^*(f,{\bf \hat{s}}) e^{2 \pi i{\bf u_{ij}} \cdot {\bf \hat{s}}} + d \Omega I(f,{\bf \hat{s}}) \sum_{\ell \ne j} g_i(f)a_i(f,{\bf \hat{s}}) C_{\ell j}^*(f,{\bf \hat{s}}) e^{2 \pi i {\bf u_{\ell i} \cdot {\bf \hat{s}}}} \nonumber \\
+& + d \Omega I(f,{\bf \hat{s}})\sum_{k \ne i} g_j^*(f) a_j^*(f) C_{ki}(f,{\bf \hat{s}}) e^{2 \pi i {\bf u_{kj}\cdot {\bf \hat{s}}}} + d \Omega I(f,{\bf \hat{s}}) \sum_{k\ne i}\sum_{\ell \ne j} C_{ki}(f,{\bf \hat{s}}) C_{j\ell}^*(f,{\bf \hat{s}}) e^{2 \pi i {\bf u_{k\ell}}\cdot{\bf \hat{s}}},
+\end{align}
+where $g_i(f) a_i(f,{\bf \hat{s}}) = \int d \tau r_i(\tau,{\bf \hat{s}}) e^{2 \pi i f \tau}$ is the effective direction dependent gain of the system which can be factored into a directoin dependent and direction independent function where $g_i(f)$ is the gain of the analogue signal chain after the radiation has been absorbed by the feed and $a_i(f,{\bf \hat{s}})$ describes the chromatic electric field response of the antenna.
+The first term in equation~\ref{eq:SingleSource} is an effective visibility with self-reflections.
+The two cross terms and the last term involve the mixing of visibilities complementary too the $ij$ baseline and have the potential to introduce significant chromatic features since they potentially insert visibilities on much longer basline lengths.
+Assuming propogation along a single path directly between the antennas, we may write $C_{ik}(f,{\bf \hat{s}})$ as
+\begin{equation}
+C_{ki}(f,{\bf \hat{s}}) = a_i(f,{\bf \hat{s}}_{ki}) \frac{1}{r_{ik}}\left[\frac{d \sigma_k}{d \Omega}(f,{\bf \hat{s}},{\bf \hat{s}}_{ik})\right]^{1/2} e^{2 \pi i \tau_{ik} f}
+\end{equation}
+Where $r_{ik}$ is the distance between antennas $i$ and $k$, $d \sigma_k (f,{\bf \hat{s}},{\bf \hat{s}}_{ij})/ d \Omega $ is the cross-section of the antenna to scatter radiation from the ${\bf \hat{s}}$ direction to the ${\bf \hat{s}}_{ik}$ direction where ${\bf \hat{s}}_{ik}$ is the unit vector in the direction between antenna $i$ and antenna $k$.
+Integrating over the primary beam, we obtain a full expression on the effect of the foregrounds.
+\begin{align}
+V_{ij}' = \int d \Omega v_{ij}'(f,{\bf \hat{s}}) &= g_i(f) g_j(f)^* \int d \Omega A_{ij}(f,{\bf \hat{s}}) I(f,{\bf \hat{s}})e^{2 \pi i f {\bf u_{ij}} \cdot {\bf \hat{s}}} + g_i(f) \sum_{\ell \ne j} \int d \Omega  A_{i\ell j}(f,{\bf \hat{s}}) I(f,{\bf \hat{s}})e^{2 \pi i {\bf u_{\ell i} } \cdot {\bf \hat{s}} } \nonumber \\
+& + g_j^*(f) \sum_{k \ne i}  \int d \Omega A^*_{jki}(f,{\bf \hat{s}}) I({\bf \hat{s}},f) e^{2 \pi i {\bf u}_{kj} \cdot {\bf \hat{s}} } + \sum_{k \ne i} \sum_{\ell \ne j}\int d \Omega A_{k i \ell j}(f,{\bf \hat{s}}) I(f,{\bf \hat{s}})e^{2 \pi i {\bf u}_{k\ell} \cdot {\bf \hat{s}}}
+\end{align}
+which is essentially an ad-mixture of many baselines with different effective primary beams.
+We denote the effective primary beam of the $i,j$ antenna pair as $A_{ij}(f,{\bf \hat{s}})=a_i(f,{\bf \hat{s}})a_j^*(f,{\bf \hat{s}})$, the effective beam from a single reflection correlated with a direct measurement as $A_{i \ell j} = a_i(f,{\bf \hat{s}}) C^*_{\ell j}(f,{\bf \hat{s}})$ and the correlation between entirely reflected terms as experiencing an effective primary beam of $A_{k i \ell j}=C_{ki}(f,{\bf \hat{s}}) C^*_{j \ell}(f,{\bf \hat{s}})$.
+In this paper, we focus on the reflection terms within a single antenna element.
+Hence, we ignore all but the first term for now.
+Any reflection terms occurring downstream of the conversion by the feed from electromagnetic radiation to voltage are lumped into $g_i(f)$ and reflections occurring within the antenna element enter into $a_i(f,{\bf \hat{s}})$.
+While reflections within the analogue system are a potential source of contamination, HERA's post-feed analogue signal path is designed to keep all reflections under 35\,m, within the wedge.
+
+The focus of this paper and its companions is the reflection properties of the primary antenna element, so we will focus the rest of our discussion here on $a_i(f,{\bf \hat{s}})$.
+The primary elements of our dish include a feed and backplane suspended over a fourteen meter dish.
+We assume a set of discrete reflections within the dish, which without loss of generality are assumed to have frequency independent reflection coefficients\footnote{If we allow each coefficient to be frequency dependent, we can expand each frequency dependent term in a Fourier series of frequency independent terms} hence
+\begin{equation}
+a_i(f,{\bf \hat{s}}) = \sum_{n} r_n({\bf \hat{s}}) e^{2 \pi i  \tau_n f}
+\end{equation}
+Assuming all antennas are identical, we have
+\begin{equation}
+A_{ij}(f,{\bf \hat{s}}) = \sum_m \sum_n r_n({\bf \hat{s}}) r_m^*({\bf \hat{s}}) e^{2 \pi i(\tau_n-\tau_m)f} = \sum_\alpha A_\alpha({\bf \hat{s}}) e^{2 \pi i \tau_\alpha}
+\end{equation}
+where we have re-indexed $m$ and $n$ under a single greek index $\alpha$ in the second equality. The effect of internal reflections on a visibility is hence
+\begin{equation}
+V_{ij}'= \sum_\alpha \int d \Omega A_\alpha({\bf \hat{s}}) e^{2 \pi i \tau_\alpha f} e^{2 \pi i {\bf b}_{ij} \cdot {\bf \hat{s}}f/c} I(f,{\bf \hat{s}})
+\end{equation}
+Taking the delay transform, one obtains
+\begin{equation}
+\widetilde{V}_{ij}'(\tau) = \sum_\alpha \widetilde{V}_{ij}^\alpha (\tau - \tau_\alpha)
+\end{equation}
+where 
+\begin{equation}
+\widetilde{V}^\alpha_{ij}(\tau) = \int d \tau e^{-2 \pi i f \tau} \int d \Omega A_\alpha({\bf \hat{s}}) e^{2 \pi i {\bf b}_{ij} \cdot {\bf \hat{s}} f/c} I(f,{\bf \hat{s}})
+\end{equation}
+is the usual delay transform of \citet{Parsons:2012}. $\widetilde{V}_{ij}^alpha(\tau)$.
 \end{document}

### 2015-10-28 DishSimulations/paper/DishSimulationsPaper_v0.tex
progress on paper and plots

@@
 \begin{equation}
-v_{out}(t) = \sum_n r_n(\theta=0) v_{in}(t - \tau_n)
+v_{out}(t,\theta=0) = \sum_n r_n(\theta=0) v_{in}(t - \tau_n,\theta=0),
 \end{equation}
-which is essentially a convolution in time of $r_n(\theta=0)$ with the input plane wave 
-\section{Comparing Simulations Results to Measurements}
-\label{sec:Comparison}
+which is essentially a convolution in time of $r_n(\theta=0)$ with the input plane wave.
+We may undo this convolution by taking a discrete Fourier transform of both $v_{out}$ and $v_{in}$ in time, dividing them in Fourier space, and taking an inverse DFT back.
+Our simulation output is sampled at even time intervals so we may use and FFT.
+\begin{equation}
+\widehat{{\bf r}}(\theta=0) = \boldsymbol{\mathcal{F}}^{-1} \left[ \frac{\boldsymbol{\mathcal{F}} {\bf v_{out}}(\theta=0)}{{\bf v_{in}}(\theta=0)} \right] 
+\end{equation}
+where ${\bf \mathcal{F}}$ is the Fourier transform matrix for a 1d vector of length $N$. 
+\begin{equation}
+\boldsymbol{\mathcal{F}}_{mn} = e^{2 \pi i m n /N}
+\end{equation}
+In Fig.~\ref{fig:FrequencyDomain} we show the amplitude of the Fourier transform of our Gaussian input, centered at $150$\,MHz along with the voltage response.
+Since our input is band limited between $\approx 20$ and $280$\,MHz, the direct ratio of our voltage response and input wave is dominated by numerical noise outside of this range.
+We eliminate these numerical artifacts by multiplying our ratio by a Hamming window between $50$\,MHz and $250$\,MHz and set our estimate to zero elsewhere.
+From a physical standpoint, this is sensible since 21\,cm experiments only observe a limited bandwidth.
+PAPER's correlator, which will initially serve as the HERA backend samples over a $100$\,MHz instantaneous freqeuency interval.
+Hence analogue filtering is applied to limit the incoming signal within a finite bandwidth and prevent aliasing.
+
+\begin{figure}[h!]
+\includegraphics[width=.5\textwidth]{figures/frequency_domain.pdf}
+\caption{The absolute value of the discrete Fourier transform of our simulation outputs.
+We obtain the effective response function of the dish by Fourier transforming the voltage output from our dish (green line) and dividing by the Fourier transform of the input wave (blue line).
+The simple ratio is plotted as a red line.
+Since our input is limited to frequencies between $\approx 20$ and $280$\,MHz, there is significant numerical noise that will effect our result outside of this region which we see in the divergene of the red line towards the edges of the plot.
+To eliminate this noise, we multiply by a Hamming window between $50$ and $250$\,MHz and set our estimate to zero elsewhere.
+The Fourier transform of our response estimate with the filter applied is shown as a cyan line.}
+\label{fig:FrequencyDomain}
+\end{figure}
+
+\section{Results and Comparison to Reflectometry Data}\label{sec:Comparison}
+\subsection{The Delay Response at Zenith}
+In Fig.~\ref{fig:Comparison}, we show the filtered response function deconvolved from our electromagnetic simulations.
+The response of the dish rapidly dies off as a function of time.
+After $\approx90$\,ns, we observe lobed structures with a period of $\approx 30$\,ns which corresponds to the geometrical delay between the feed and the dish apex, indicating that the large $\tau$ roll off is dominated by reflections between the feed and the dish.
+
+Our simulations are intended to verify direct reflectometry measurements taken on a prototype of the HERA feed and dish in Green Bank, presented in \citep{Patra:2015}.
+For the readers convenience, we briefly explain the reflectometry measurement here before comparing them to our simulation.
+
+In the reflecometry measurement, a signal is sent from a Vector Network Analyzer (VNA) via a coaxial cable (which is calibrated out) into the back of the feed.
+The VNA than measures the ratio between returned and transmitted power as a function of frequency, $S_{11}(f)$.
+A fundamental difference between the reflectometry measurement and the delay response that we are attempting to obtain is that at zero delay, $S_{11}$ is measureing the reflection of the input wave off of the back of the feed while in the delay response of the antenna, the zero delay reflection is the fraction of the electromagnetic wave off of the sky that is accepted by the feed.
+To obtain $\boldsymbol{\widehat{\rho}}$, we must correct for this difference.
+It is shown in \citep{Patra:2015} that the correction is
+\begin{equation}
+\widehat{\rho}(f) = \frac{\Gamma_a(f)}{1-\Gamma_a(f)} \left[ S_{11}(f) - \Gamma_a(f) \right] + 1 - \Gamma_a(f).
+\end{equation}
+Applying this transformtion to $S_{11}(f)$ and taking a DFT into the time domain over a band of $100-200$\,MHz, we obtain a measurement based estimate of the dish response function at zenith which is plotted in Fig.~\ref{fig:Comparison} alongside our simulation result.
+The general trends of the two two lines are in excellent agreement though the phases of the reflections at large time scales are $\approx 10$\,ns out of phase.
+As the long term delay structure of the delay response determines to what extent foregrounds leak out of the wedge, our simulations verify our measurement of the HERA dish's key performance feature.
+\begin{figure}[h!]
+\includegraphics[width=.5\textwidth]{figures/compareSimToDataNormalized.pdf}
+\caption{The response function deconvolved from our simulation (blue line) compared to the response function estimated from reflectometry measurements described in \citep{Patra:2015}.
+Our simulations are in good agreement with the reflectometry results, dropping below $-60$\,dB at $180$\,ns.
+Since the foregrounds are $\approx 10^6$ times larger than the signal, the necessary attenuation of zenith emission is obtained after $\approx 0.1$\,$h$Mpc$^{-1}$.}
+\label{fig:Comparison}
+\end{figure}
+\subsection{The Delay Response of the Sidelobes}
+ After observing decent agreement between simulations and data, we now use our time-domain simulations to probe the side-lobe structure of the dish which are currently inaccessible to our experimental setup.
+Understanding the delay structure of the sidelobes is critical for several reasons.
+First, the sidelobes represent the largest delays occupied by foregrounds, hence the closest to the EoR window which we wish to keep foreground-free.
+While spectral leakage of sources at zenith may place them somewhere within the wedge, any spectral structure in the sidelobes is guaranteed to place these sources directly inside of the window.
+Second, the forshortening of diffuse structure near the horizon due to wide-field projection effects leads to a significant amount of foreground power entering at these delays, generally making them the most contaminated region of the wedge outside of the central lobe and leading to the so called ``pitchfork" \citep{Thyagarajan:2015a,Thyagarajan:2015b}.
+
+ We fist attempt to explore the Dish sidelobe structure by running high resolution spatial beam maps {\bf Rich fill in details of running 2D beam simulations}.
+However, comparison between individual frequency channels in both CST and FEKO indicates numerical precision errors {\bf Show a figure of an attempted beam and frequency artifacts at zenith.}
+
 \section{The Effect of the HERA dish Chromaticity on Foreground Leakage and Sensitivity}
@@
 \bibliographystyle{apj}
-\bibliography{biblio}
+\bibliography{DishSimulation_paper_v0}
 

### 2015-10-28 DishSimulations/code/cosmology.py

@@ -1,0 +1,126 @@
+#************************************************************
+#basic cosmology tools built around astropy.cosmology
+#uses Planck 2013 parameters
+#************************************************************
+import numpy as np
+import copy
+from astropy.cosmology import Planck13 as pl13
+pi=np.pi
+c=3e8 #speed of light
+f21=1.42040575177e9 #21 cm frequency
+DH=c/(pl13.H0.value*1e3)#hubble distance Mpc
+DHcm=DH*3.08567758e24#hubble distance in cm
+kb=1.38e-23
+jy=1e-26
+mH=1.6726231e-24
+#pl13.Ob0=0.022068/(pl13.H0.value/1e2)**2.
+print pl13.Ob0
+
+
+def H0_s():
+    return pl13.H0_s
+
+def get_crit():
+    return pl13.critical_density(0).value
+
+#in g cm^-3
+def baryon_density(z):
+    return get_crit()*(1+z)**3.*pl13.Ob0
+
+#in cm^-3
+def baryon_n(z):
+    return baryon_density(z)/mH
+
+def f2z(f):
+    return f21/f-1
+
+def z2f(z):
+    return f21/(z+1)
+
+def de(z):
+    return 1./np.sqrt(pl13.Om0*(1+z)**3.+1.-pl13.Om0)
+
+def dr2df(dr,z):
+    return dr/(DH*(1+z)**2.*de(z))*f21
+
+def df2dr(df,z):
+    return -df*(DH*(1+z)**2.*de(z))/f21
+
+def cMpc2deg(d,z):
+    return pl13.arcsec_per_kpc_comoving(z).value*1e3/3600.*d
+def cMpc2rad(d,z):
+    return np.radians(cMpc2deg(d,z))
+    
+
+def u2kperp(u,z):
+    return u*2.*pi/pl13.comoving_distance(z).value
+
+def eta2kpara(eta,z):
+    return (2.*pi*f21)/(DH*(1.+z)**2.*de(z))*eta
+
+def kpara2eta(kpara,z):
+    return DH*(1.+z)**2.*de(z)/(2.*pi*f21)*kpara
+
+def kperp2u(kperp,z):
+    return kperp/(2.*pi)*pl13.comoving_distance(z).value
+ 
+
+#convert from temperature to surface brightness
+def t2i(f,t):
+    return 2*(f/c)**2.*kb*t/jy
+
+def X(f):
+    z=f21/f-1
+    return pl13.comoving_distance(z).value
+def Y(f):
[…]

### 2015-10-28 DishMeasurements/memo/DishBeamMeasurementsMemo.tex

@@
 
-\title{HERA Dish Beam Measurements Memo, Rev. $\alpha$}
+\title{HERA Dish Beam Measurements Memo}
 
@@
 
-\author{Abraham Neben, Rich Bradley, Jackie Hewitt}
+\author{Abraham Neben, Rich Bradley, Jackie Hewitt, others}
 %\affil{MIT Kavli Institute, Massachusetts Institute of Technology, Cambridge, MA, 02139 USA}
 
-\author{Oct 25, 2015}
-%\affil{Wasamatta U}
+\author{Oct 26, 2015}
 
@@
 \begin{abstract}
-write abstract here
-comment on how this expt is still a work in progress
+We deploy the 137\,MHz ORBCOMM beam mapping system of \citet{neben15} at the site of the HERA prototype at NRAO--Green Bank.
+This technique measures the beam of an antenna-under-test relative to that of a well-modeled reference antenna.
+We characterize environmental systematics such as reflections and multipath effects by comparing the measured beams of different reference antennas, then measure the beam pattern of the east-most HERA dish as a function of feed height over the dish surface.
+With the feed at the nominal focus of 4.5\,m over the dish surface, the collecting area is observed to be 68.5\,m$^2$, agreeing with simulations.
+We also simulate delay spectra on baselines of different lengths and orientations at different LSTs for measured and model beams, and quantify the severity of and uncertainties in the delay space horizon brightening termed the ``pitchfork effect'' by \citet{nithya15}.
+Future measurements will study the dish beam in the presence of adjacent dishes, quantifying levels of cross-talk and cross-coupling.
 \end{abstract}
@@
 
-%\section{Other title ideas}
-%\begin{itemize}
-%\item The relationship between noise correlation and monopole sensitivity in radio interferometers
-%\item The self noise of sky noise in monopole interferometers
-%\item Signal and noise in global signal interferometers
-%\end{itemize}
+%\section{Introduction}
 
-%\section{Introduction}
+%must use frequency structure to separate FGs from signal
+%a certain amount of freq structure is imprinted onto smooth sources due to the frequency-dependent sampling function of an interferometer
+%also by faraday rotation and the bandpass (citations)
+
+%leakage is due to bandpass, frequency flagging, finite bandwidth.
+can be mitigated by subtraction in the delay spectrum (CLEAN), giving up on wedge modes, or subtraction in image space with foreground modeling, likely will have to give up on wedge modes too unless have incredible calibration and imaging fidelity, as LOFAR is attempting.
+Large risk of signal loss and calibration-induced transfer of spectral structure from long baselines to short ones
+
+%hera is pursuing two relatively orthogonal power spectrum analyses (imaging and delay transform)
+
+%the other papers in this series quantify the degree of spectral structure induced by the dish bandpass in measurement and modeling, we focus in this section on foreground leakage due to the finite bandwidth as a function of the beam response at different delays in the sky.
+Nithya discuss this is detail nithya15,nithya15b
+
+%\citet{nithya15,nithya15b} 
+%for a power spectrum analysis, note that these tests test how leakage varies as a function of the brightness of emission at different delays, not leakage due to beam frequency dependence (ie, either pattern or overall gain)
+
+\section{ORBCOMM Beam Mapping System Review}
+
+We briefly review the beam mapping system detailed by \citet{neben15}, then discuss application of system to the prototype HERA array at NRAO--Green Bank.
+The system takes advantage of the 137\,MHz communications satellites operated by ORBCOMM Inc.
+as bright point sources which, by virtue of their number ($\sim30$), short orbital periods ($\sim90$ minutes), and orbital precession cover 65\% of the visible sky in just a few days.
+The coverage is limited by the fact that the satellites' orbital inclinations are all less than $45^\circ$.
+
+In contrast to celestial source beam measurements, though, where the flux may be assumed constant over the timescale of the measurement, satellite fluxes can vary rapidly due to varying distance, orientation, and transmission power.
+To correct for this, we measure the satellite flux in each ground polarization (EW and NS) using a simple, well-modeled reference antenna.
+Comparison of this measured power with that observed in the Antenna-Under-Test (AUT) gives the AUT beam response in the direction of the satellite.
+An equivalent interpretation is that the power ratio between the AUT and the reference antenna gives the relative beam response in the satellite direction, and multiplication by the reference antenna model yields the desired AUT response.
+As discussed in \citet{neben15}, despite the fact that satellite signals are generally polarized, this procedure.
+
+In detail, we measure the dual-polarization RMS powers for each antenna in 512 2\,kHz bands across the 137--138\,MHz band.
+Each channel power is averaged over $\sim0.2$\,sec.
+There are 0--3 satellites above the horizon at any given time transmitting on different $\sim15$\,kHz wide sub-bands in 137--138\,MHz.
+By observing at many different frequencies, we probe the beam response in all these directions simultaneously.
+We compute the satellite positions using the orbital elements published by Celestrak\footnote{http://www.celestrak.com/NORAD/elements/orbcomm.txt} and the orbital integrator \texttt{predict}\footnote{http://www.qsl.net/kd2bd/predict.html}.
+However, the satellite frequencies vary occasionally to avoid interference within the constellation.
+\citet{zheng14} use interferometric phases to identify and exclude times when multiple satellites are in view.
+As our data acquisition system makes only total power measurements, we instead use an ORBCOMM interface box (typically supplied to commercial users of the network) to sync with passing satellites and record their identifier and transmission frequency.
+
+In this way, beam measurements are built up along satellite tracks over the course of several days of integration, yielding typically 200--300 satellite pass.
+Each pass is processed separately to identify and exclude times of low signal-to-background when the satellite is low in the sky or in the off state of of a pulsing sequence.
+At those times, then satellite flux no longer dominates over that of the diffuse Galactic background, and a power measurement no longer probes the response in the satellite direction.
+The beam measurements are then gridded in horizontal coordinates in HEALPix with a resolution of $1.8^\circ$ (nside=32).
+As a last quality control step to reject errant beam measurements due to RFI, for instance, we keep only the central 90\% of $\sim50$ measured beam values in each HEALPix cell.
+
+\section{Beam Modeling}
+
+\subsection{Reference Antenna Modeling}
+Our power ratio measurement relies upon an accurately modeled reference dipole.
+We are developing a more comprehensive model of the physical reference antenna and ground screen design, improving on that used in \citep{neben15}.
+As yet, this improved model yields incorrect results, so more debugging is needed.
+
+\subsection{Dish and Feed Modeling}
+\label{sec:dishmodels}
+
+We compare measured beam patterns with a simplistic analytic model and two numerical electromagnetic models.
+Briefly, the dish is constructed of overlapping mesh rectangles secured to hanging PVC pipes to form an approximately parabolic surface with diameter 14\,m.
+The feed consists of a dual-polarization dipole antenna with a circular mesh backplane and a cylindrical mesh ``skirt'' hanging down.
+The feed is suspended over the dish surface by three ropes attached to poles equally spaced around the dish.
+
+\begin{enumerate}
+	\item Airy pattern for a 14\,m aperture
+	\item CST simulation (\texttt{hera-cst/HERA\_DISH\_paper\_feed\_cyl36\_140mhz\_Y\_healpix.fits})
+	\item A separate simulation run by Dave with 68'' diameter feed backplane and 26'' skirt.
+\end{enumerate}
 
@@
 
-We review the
+A 3-element HERA engineering prototype array is being constructed at the National Radio Astronomy Observatory--Green Bank.
+We performed the beam measurements presented in this work on the first of these to be constructed, future work will characterize how its in-situ beam in the presence of the other two dishes once they are constructed.
+Figure \ref{fig:aerial} shows the west-most HERA dish next to two planned dishes in Galford Meadow.
+The two reference antennas 100\,m are positioned due south with a 100\,m separation, and the Green Bank Telescope $\sim1$\,km northwest of the dish.
+The data acquisition system is installed in the hut labeled ``Launch point'' on the image.
+
+Note that unlike the full HERA site in the Karoo Desert Radio Astronomy Reserve in South Africa, the Green Bank site has obstructions such as trees and foothills, as well as moist ground with possibly non-uniform properties.
+All these will contribute to variation of the in-situ reference antenna relative to the electromagnetic model.
+We will discuss below how we quantify these systematics with ``null experiments'' which compare the beams of the two reference antennas.
 
@@
 \caption{Aerial photograph of the two reference dipoles deployed in Galford Meadow at the National Radio Astronomy Observatory--Green Bank 100\,m south of the HERA dish.}
-\label{fig:null3}
+\label{fig:aerial}
 \end{figure*}
 
-specify which of the three HERA dishes we are talking about
-
-sky coverage with orbcomm experiment
-
-\section{Beam Modeling}
-
-\subsection{Reference antenna model}
-Our power ratio measurement relies upon an accurately modeled reference dipole, and to that end we improve on the model used in \citep{neben15} by XXX
-
-\subsection{Dish models}
-\label{sec:dishmodels}
-
-We compare measured beam patterns with a simplistic analytic model and two numerical electromagnetic models. NEED MORE DETAILS ABOUT MODELING
-\begin{enumerate}
-	\item Airy pattern for a 14\,m aperture
-	\item CST simulation (\texttt{hera-cst/HERA\_DISH\_paper\_feed\_cyl36\_140mhz\_Y\_healpix.fits})
-	\item A separate simulation run by Dave
-\end{enumerate}
-
-\section{Null Experiments}
+\section{Assessing Systematics with a Null Experiment}
 
@@
 \includegraphics[width=3.5in]{measbeam_interp_expcutoff.png}
-\caption{We construct full sky beams as required for Section \ref{sec:sci} by starting from the nominal focus beam (top left), interpolating over unobserved cells at $\theta\lesssim60^\circ$ and extrapolating to the horizon (top right), and applying a gaussian cutoff starting at $\theta=60^\circ$ with $\sigma=2.5^\circ$ (bottom left).
-These last two beams span the space of likely horizon responses.}
+\caption{We construct full sky beams as required for Section \ref{sec:foregroundleakage} by starting from the nominal focus beam (top left), interpolating over unobserved cells at $\theta\lesssim60^\circ$ and extrapolating to the horizon (top right), and applying a gaussian cutoff starting at $\theta=60^\circ$ with $\sigma=2.5^\circ$ (bottom left).
+These last two beams span the space of likely horizon responses.
+Circles denote $\theta=20^\circ,40^\circ,60^\circ,80^\circ$.}
 \label{fig:interpbeams}
@@
 
-\section{Implications for HERA Science}
-\label{sec:sci}
+Why does the collecting area increase as the feed is raised over the nominal focus?
+There are two computing effects here: (1) the reflected radiation is less well focused above the feed, decreasing the response; and (2) the tapered feed sees a larger dish as it is raised, allowing more radiation to reach the dipole as opposed to reflecting off the skirt.
+These data suggest that the second effect wins.
+Of course the reason for the skirt is to taper the feed beam in order to mitigate cross-talk and cross-coupling between the dishes.
+A larger collecting area may not be worth it in exchange for exacerbating these concerns.
 
-\subsection{Foreground Leakage}
-for a power spectrum analysis, note that these tests test how leakage varies as a function of the brightness of emission at different delays, not leakage due to beam frequency dependence (ie, either pattern or overall gain)
+\section{Foreground Leakage and Residuals}
+\label{sec:foregroundleakage}
+
+We assess the level of foreground leakage into the EOR window due to beam shape, baseline length, and LST.
+In particular, we built on the study of \citet{nithya15} of the impact of beam shape and horizon response on foreground spectral structure and containment in the wedge.
+
+We simulate delay spectra for several model and measured beams on different baseline lengths for different LSTs and baseline orientations.
+All these factors affect the level of emission horizon brightening in delay space, the ``pitchfork'' effect, and the level of foreground leakage.
+We assume a constant beam pattern over that band, with leakage due only to the finite bandwidth and choice of window function.
+Actual frequency structure imprinted onto the foregrounds by variation of the beam angular pattern or overall gain with frequency (Patra et al.)
+
+We begin by simulating visibilities over a 20\,MHz bandwidth with  400\,kHz resolution centered on 137\,MHz on two different baselines for two model beams (airy, and CST sim) and two measured beams (measured nominal focus beam, and measured nominal focus beam with $60^\circ$ cutoff).
+We use the short and maximally redundant 14\,m baseline, most useful for delay spectrum analysis, as well as a longer 42\,m baseline, more useful for imaging analysis.
+From these frequency-sequenced visibilities we calculate the delay spectrum  \citep{perbaselinetechnique} using the Blackman-Harris window following \citet{nithya15}.
+This window reduces the noise equivalent bandwidth to 10\,MHz, corresponding to $\Delta z\sim0.5$, beyond which evolution of the cosmological signal become significant.
+Larger bandwidths, though, are useful for foreground estimation and delay-space deconvolution \citep{parsonsandbacker,paper32,paper64}.
+With this caveat, our simulated delay spectra show the worst case scenario, quantifying the level of foreground isolation without estimation and deconvolution.
+
+Our sky model is comprised of a deep MWA point source survey within 20$^\circ$ of R.A.(J2000) $= 0^\text{h}\,0^\text{m}\,0^\text{s}$ and decl.(J2000) $= -30^\circ\,0'\,0''$ (Carroll et al., in prep.), the shallower but wider MWA commissioning point source survey\citep{MWACS}, the Culgoora catalog\citep{Slee1995}, and the Global Sky Model of Galactic radio emission \citep{gsm}.
+
+Figure \ref{fig:delayspec} shows the delay spectra at $0^\circ$ (top pair) and $60^\circ$ (bottom pair) LST for 14\,m (left pair) and 42\,m (right pair) EW baselines.
+For reference we plot a 1D model 21\,m power spectrum for $z\sim8$ from \citet{21cmfast}.
+Consider first the $0^\circ$ LST plots where the Galactic disk has nearly, but not completely set.
+The effect of horizon response is most visible on the longer 42\,m baseline where the measured beam (red) and CST model (yellow), both show significant brightening at the horizon delays (vertical black lines) due to roughly -30\,dB beam response near the horizon, as discussed by \citet{nithya15,nithya15}.
+In contrast, the airy model (black) and measured beam with cutoff (blue) show no significant brightening at the horizon, where they appear still to be dominated by the wings of the delay PSF from the emission closer to zero delay.
+
+We also plot (green dashed line) the delay spectrum after subtracting the visibilities computed with the $\theta\sim60^\circ$ cutoff measured beam from those using the full measured beam.
+This curve may be interpreted as the uncertainty in the ``pitchfork'' horizon brightening due to uncertainty in the beam horizon response, or equivalently as the delay spectrum residual foregrounds after subtracting foregrounds in the well modeled region of the sky.
+By construction, this subtraction leaves emission from the highest delay regions of the sky (near the horizon on opposite sides of the baseline), but also leaves some low delay emission on opposite sides of a line perpendicular to the baseline.
+However, this additional low delay emission near the horizon gets drowned out by that from near zenith where the beam is substantially stronger.
+
+On the shorter 14\,m baseline, the horizon brightening is smaller because there is roughly an order of magnitude more emission at zero delay, whose thereby stronger delay wings, which are also relatively wider compared to the narrower foreground wedge, cover up much of the edge brightening.
+At $60^\circ$ LST, effect of horizon response is much smaller as the Galactic disk is now entirely below the horizon.
+
+The level of leakage depends also on baseline orientation which sets which directions on the sky map to large delays.
+Figure \ref{fig:delayspec2} shows the delay spectra at $0^\circ$ LST on 14\,m NE (top pair) and SE (bottom pair) baselines.
+Both show increased edge brightening compared to the 14\,m EW baseline.
+\citet{nithya15} proposes to identify through modeling the baselines most susceptible to this edge brightening at any given time, and simply exclude them from the power spectrum analysis.
 
 \begin{figure*}[h]
-\includegraphics[width=5.5in]{LST0deg_14m_42m_EWbaselinesblackman.png}
-\includegraphics[width=5.5in]{LST60deg_14m_42m_EWbaselinesblackman.png}
-\caption{aeuaoeuaoeu}
+\includegraphics[width=6.7in]{LST0deg_14m_42m_EWbaselines_dish1_blackman.png}
+\includegraphics[width=6.7in]{LST60deg_14m_42m_EWbaselines_dish1_blackman.png}
+\caption{Simulated delay spectra for the GSM and point sources at $0^\circ$ (top pair) and $60^\circ$ (bottom pair) LST for EW baselines of length 14\,m (left pair) and 42\,m (right pair).
+The beams are are assumed constant over frequency.}
 \label{fig:delayspec}
@@
 \begin{figure*}[h]
-\includegraphics[width=5.5in]{LST0deg_14m_42m_NSslantbaselinesblackman.png}
-\includegraphics[width=5.5in]{LST0deg_14m_42m_SEslantbaselinesblackman.png}
-\caption{aeuaoeuaoeu}
+\includegraphics[width=6.7in]{LST0deg_14m_42m_NEslantbaselines_dish1_blackman.png}
+\includegraphics[width=6.7in]{LST0deg_14m_42m_SEslantbaselines_dish1_blackman.png}
+\caption{Simulated delay spectra for the GSM and point sources at $0^\circ$ LST for NE (top pair) and SE (bottom pair) baselines of length 14\,m (left pair) and 42\,m (right pair).
+The beams are are assumed constant over frequency.}
 \label{fig:delayspec2}
@@
 
-\subsection{Foreground Residuals}
-the accuracy of beam modeling affects the science performance in additional ways ranging from missubtraction to imperfect foreground subtraction (Neben et al.
-2015b submitted).
-The impact of beam mismodeling on science performance is left as future work.
+%\section{Discussion}
 
-\section{Discussion}
+%As expected, the Airy patter has the largest collecting area
 
-As expected, the Airy patter has the largest collecting area
+%the beam might be narrower simply because more dish is illuminated, but not necessarily a good thing, because we want more taper at the edge
 
-the beam might be narrower simply because more dish is illuminated, but not necessarily a good thing, because we want more taper at the edge
-
-comment on how this expt is still a work in progress
+%comment on how this expt is still a work in progress
 

### 2015-10-29 DishSimulations/paper/DishSimulationsPaper_v0.tex
added array simulation code

@@
 \section{The Effect of the HERA dish Chromaticity on Foreground Leakage and Sensitivity}
+
+\subsection{How Deep Can we Clean?}
+The level of foreground subtraction possible depends on the number of time steps and redundant baselines that are averaged before performing the cleaning step.
+The standard deviation on the real and imaginary part of a single delay transformed visibility is given by \citep{Morales:2004}
+\begin{equation}
+\Delta V = \frac{\sqrt{2 B} k_B T_{sys}}{A_e \sqrt{\tau}}
+\end{equation}
+where $A_e$ is the effective area of the dish, $B$ is the bandwidth, $T_{sys}$ is the system temperature, $\tau$ is the integration time, and $k_B$ is the Boltzmann constant.
+The system temperature can be calculated by assuming that $T_{sys} = 100\text{K} + T_{sky}$ where $100$\,K is the temperature of the PAPER reciever and $T_{sky} = 60 (\lambda/1\,\text{meter} )^{2.55}$ is the sky temperature \citep{Fixsen:2008}.
+For $A_e$ we use the value of $75$\,m determined in \citep{Neben:2015b}.
+If we assume that each baseline is cleaned independently and that the integration time is $\tau \approx 60$\,s, than the noise level at 150\,MHz is approximately $9.9$\,Jy\,MHz.
+In order to avoid subtracting noise, we assume that cleaning is performed down to $5\,\sigma$.
 \label{sec:Foregrounds}

### 2015-10-29 DishSimulations/code/arraytools.py

@@ -1,0 +1,66 @@
+#!/usr/bin/env python
+import numpy as np
+#************************************************************
+#Aaron Ewall-Wice
+#aaronew@mit.edu
+#October 20th 2014
+#methods to sort 2-D numpy arrays by column or row.
+#************************************************************
+#sort a 2d array of floats by a specified column
+#************************************************************
+def columnsort(a,column=0,order='desc'):
+    print a.shape
+    asorted=np.zeros(a.shape)
+    dtype=[('x',float),('y',int)]
+    sortkey=np.zeros(a.shape[0],dtype=dtype)
+    sortkey['x']=a[:,column]
+    indices=range(a.shape[0])
+    sortkey['y']=indices
+    sortkey.sort(order='x')
+    for col in range(a.shape[1]):
+        asorted[:,col]=a[sortkey['y'],col]
+    if(order=='desc'):
+        asorted=np.flipud(asorted)
+    return asorted
+        
+        
+#************************************************************
+#sort a 2d array of floats by a specified column
+#************************************************************
+def rowsort(a,row=0,order='desc'):
+    return columnsort(a.T,row,order).T
+
+
+#************************************************************
+#get unique rows of an array, courtesy bfroehle
+#https://github.com/numpy/numpy/issues/2871
+#************************************************************
+def unique_rows(A, return_index=False, return_inverse=False):
+    """
+    Similar to MATLAB's unique(A, 'rows'), this returns B, I, J
+    where B is the unique rows of A and I and J satisfy
+    A = B[J,:] and B = A[I,:]
+
+    Returns I if return_index is True
+    Returns J if return_inverse is True
+    """
+    A = np.require(A, requirements='C')
+    assert A.ndim == 2, "array must be 2-dim'l"
+
+    B = np.unique(A.view([('', A.dtype)]*A.shape[1]),
+               return_index=return_index,
+               return_inverse=return_inverse)
+
+    if return_index or return_inverse:
+        return (B[0].view(A.dtype).reshape((-1, A.shape[1]), order='C'),) \
+            + B[1:]
+    else:
+        return B.view(A.dtype).reshape((-1, A.shape[1]), order='C')
+
+#************************************************************
+#get unique columns
+#************************************************************
+#def unique_columns(A,return_index=False,return_inverse=False):
+#    if(return_index or return_inverse):
+#        
+#    unique_rows(A.T,return_index=return_index,return_inverse=return_inverse)

### 2015-10-29 DishSimulations/code/bandpass.py

@@ -1,0 +1,156 @@
+#!/usr/bin/env python
+import numpy as np
+from numpy import fft as fft
+import matplotlib.pyplot as plt
+import scipy.interpolate as interp
+#************************************************************
+#1d fft convolution
+#************************************************************
+def convFFT(x,y):
+    nx=len(x)
+    xf=np.pad(x,(nx/2,nx/2),mode='constant')
+    yf=np.pad(y,(nx/2,nx/2),mode='constant')
+    xf=(fft.fft(fft.fftshift(xf)))
+    yf=(fft.fft(fft.fftshift(yf)))
+    return fft.fftshift(np.real((fft.ifft(xf*yf))))[nx/2:3*nx/2]
+def dconvFFT(x,y):
+    nx=len(x)
+    xf=np.pad(x,(nx/2,nx/2),mode='constant')
+    yf=np.pad(y,(nx/2,nx/2),mode='constant')
+    xf=(fft.fft(fft.fftshift(xf)))
+    yf=(fft.fft(fft.fftshift(yf)))
+    return np.real(fft.fftshift(fft.ifft(xf/yf)))[nx/2:3*nx/2]
+
+#************************************************************
+#bandpass derived from Rich Bradley's simulation of inital 
+# feed design. The delay response is well modeled by a gaussian centered
+#at 40 nanoseconds with a power law tail. 
+#************************************************************
+def heraFeedDelay(tau):
+    cutoff=(80.-30.)*1e-9
+    mu=(72.-30.)*1e-9
+    vals1=np.abs(tau)<=cutoff
+    print vals1
+    vals2=np.abs(tau)>cutoff
+    pwise=np.zeros(len(tau))
+    func1=lambda x: np.exp(-(np.abs(x)-mu)**2./(2.*(7e-9)**2.))
+    func2=lambda x: func1(tau[vals1].max())*((np.abs(x)-cutoff)*1e9+1.)**-3.
+    pwise[vals1]=func1(tau[vals1])
+    pwise[vals2]=func2(tau[vals2])
+    pwise[tau<=0.]=0.
+    #plt.plot(tau*1e9,pwise)
+    #plt.xlim(1e-2,1e3)
+    #plt.yscale('log')
+    #plt.show()
+    return pwise
+          
+
+
+
+
+#def initHeraFeedBand(f,params,sRate=5e9):
+#    df=params[0]
+#    bw=params[1]
+#    fc=params[2]
[…]

### 2015-10-29 DishSimulations/code/interferometer.c

@@ -1,0 +1,105 @@
+/*************************************************************
+Aaron Ewall-Wice
+aaronew@mit.edu
+October 18th 2014
+c routines for interferometer. written at performance 
+sensitive steps to make it go faster
+************************************************************/
+#include <stdio.h>
+#include <math.h>
+#define PI (3.141592653589793)
+typedef struct {double real; double imag;} cdouble;
+typedef struct {float real; float imag;} cfloat;
+/*************************************************************
+grid data to a 2D grid stored as a vector 
+using nearest neighbor gridding
+dx,dy: grid spacing
+cxout,cyout: center values 
+************************************************************/
+void griddata_nn(long * xi, long * yi, cdouble * input, cdouble * output,long ndata, long nx, long ny)
+{
+  int m;
+  int x,y;
+  for(m=0;m<ndata;m++)
+    {
+      x=(int)xi[m];
+      y=(int)yi[m];
+      if(y<ny && x<nx && x>=0 && y>=0)
+	{
+	  output[y*nx+x].real=output[y*nx+x].real+input[m].real;
+	  output[y*nx+x].imag=output[y*nx+x].imag+input[m].imag;
+	}
+     }
+}
+/***********************************************************
+get the number uniformly gridded 
+************************************************************/
+void count_nn(long * xi, long * yi, long * counts, long ndata, long nx, long ny)
+{
+  long m,x,y;
+  for(m=0;m<ndata;m++)
+    {
+      x=xi[m];
+      y=yi[m];
+      if(y<ny && x<nx && y>=0 && x>=0)
+	{
+	  counts[y*ny+x]+=1;
+	}
+    }
+}
+
+/************************************************************
+//take differences in values of 1d array
+//n is the length of the input array
+//output array is assumed to be n*(n-1)/2 as long 
+//as output
+//only write function for doubles. must cast 
+//other data types in python
+************************************************************/
+void diffcomb(double * x, double * out, long n)
+{
+  int l,m;
+  for (l=0;l<n;l++)
+    {
+      for (m=0;m<l;m++)
+	{
+	  *out=x[l]-x[m];
+	  out++;
+	}
+    }
+}
+/************************************************************
[…]

### 2015-10-29 DishSimulations/code/interferometer.py

@@ -1,0 +1,504 @@
+#!/usr/bin/env python
+#************************************************************
+#interferometer class
+#ignore polarization for now
+#obs: an ephem observer with lon,lat,and date
+#freqs: a list of frequencies for the interferometer (Hz)
+#times: a list of ephem dates
+#assume homogenous array for now
+#************************************************************
+import matplotlib.pyplot as plt
+import astropy.wcs as wcs
+import numpy as np
+import ephem,os
+from beam import Beam
+from beam import gaussbeam,cosbeam,tophatbeam,airybeam,mwabeam
+from bandpass import Bandpass
+from bandpass import flatband
+from arraytools import unique_rows
+import ctypes as ct
+from joblib import Parallel,delayed
+import interferometer_utils as utils
+import multiprocessing,cosmology
+pi=np.pi
+c=3e8
+"""
+#test diffcomb
+bl=diffcomb(range(128))
+print bl
+#test compute visibilities
+#with an interferometer with antennae spacing of .1 lambda and a source located at m=0.5
+nuv=100
+u=np.arange(-nuv/2,nuv/2)*.1
+v=np.arange(-nuv/2,nuv/2)*.1
+ug,vg=np.meshgrid(u,v)
+u=ug.flatten()
+v=vg.flatten()
+w=np.zeros(len(u))
+uvw=np.vstack([u,v,w]).T
+ns=10
+l=np.random.rand(ns)
+lm=np.vstack([l,1-l**2.]).T
+s=np.random.rand(ns)
+print lm.shape
+#lm=np.array([[0.,.5],[0.,0.]])
+vis=computevisibilities(uvw,lm,s).reshape((nuv,nuv))
+print vis.shape
+theory=np.zeros((nuv,nuv))
+for mm in range(lm.shape[0]):
+    theory+=s[mm]/np.sqrt(1.-np.sum(lm[mm,:]**2.))*np.cos(-2*np.pi*(ug*lm[mm,0]+vg*lm[mm,1]))
+plt.imshow((np.real(vis)-theory)/theory,interpolation='nearest')
+plt.colorbar()
+plt.show()
+plt.imshow(np.real(vis),interpolation='nearest')
+plt.colorbar()
+plt.show()
+"""
+
+
+
+#************************************************************
+#change coordinates of antennae in north-south,east-west
+#at an observatory with latituded lat and local sidereal
+#time lst to coordinates with X at 0h, Y at -6h and Z 
[…]

### 2015-10-29 DishSimulations/code/prefactor.py

@@ -1,0 +1,6 @@
+#!/usr/bin/env python
+import numpy as np
+print '%e'%(1e26*np.sqrt(2.*100e6)/(75*np.sqrt(2.*60.))*(100.+60*(.21*(8.5+1))**2.55)*1.28e-23)
+
+
+

### 2015-10-29 DishSimulations/paper/DishSimulationsPaper_v0.tex
added discussion of noise limiting clean in paper and also added fisher matrix tools

@@
 
-\section{The Effect of the HERA dish Chromaticity on Foreground Leakage and Sensitivity}
+\section{The Effect of the HERA dish Chromaticity on Foreground Leakage and Sensitivity}\label{sec:Foregrounds}
+
+\subsection{Simulating Foreground Visibilities with the Spectral Structure of the HERA Dish.}
 
@@
 In order to avoid subtracting noise, we assume that cleaning is performed down to $5\,\sigma$.
-\label{sec:Foregrounds}
+In Fig.~\ref{fig:Cleaning}, we see that cleaning to $5\,\sigma$
+
+\begin{figure}
+\includegraphics[width=.5\textwidth]{figures/cleaning_noise.pdf}
+\caption{The absolute magnitude of a delay transformed 14-meter baseline (blue line) compared to the same visibility (green line) contaminated by reflections at the level observed in the HERA dish design.
+We see that the extended delay kernel smooths out structure, originating from foregrounds, within the horizon.
+For HERA, we expect to use the delay-clean to remove foregrounds.
+However, the depth of cleaning is limited by the noise level on a single baseline (black line).
+We show the foreground residuals with arising from a clean down to the $5\,\sigma$ noise level after 2 minutes of integration, seeing that cleaning at this cadence achieves $\approx$ two orders of magnitude of foreground reduction.
+The reflections in the dish lead to extensive winged structures that bleed into the EoR window and are well below the thermal noise level.
+All data in this plot are obtained from a $100$\,MHz bandwidth centered at $150$\,MHz.}
+\label{fig:Cleaning}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=.5\textwidth]{figures/resid_5sigma_compare.pdf}
+\caption{The delay transformed power spectra of foregrounds with (blue line) and without (green line) contamination from reflections in the dish.
+The residuals of these foregrounds, cleaned to $5\,\sigma$ after 2 minutes of integration, are plotted with (red dashed line) and without (cyan dashed line) dish reflections.
+We compare to the amplitude of the 21\,cm power spectrum (solid black line).
+Foreground contamination, leaked by reflections, extends out to $k_\parallel \approx 0.25$\,$h$Mpc$^{-1}$.
+The signals plummet to zero at $k=0$ is an artifact of the spatial extent of the simulation which does not probe extremely fine scales.}
+\label{fig:SignalCompare}
+\end{figure}
+
+\subsection{The Implications of Dish Reflections on EoR Sensitivity}
+Since the amplitude of the 21\,cm signal is maximal at smaller $k$ values, a loss of large scale signal out to $0.25$\,$h$Mpc$^{-1}$ will eliminate some of the power spectrum modes that HERA will have the greatest SNR on, impacting our overall sensitivity.
+We address the change in SNR and its implications on HERA's ability to place constraints on reionization parameters in this section, using the Fisher Matrix Formalism.
+
 \section{Conclusions}

### 2015-10-29 DishSimulations/code/computeW.py

@@ -1,0 +1,211 @@
+#!/usr/bin/env python
+
+import numpy as np
+import sys
+import scipy.interpolate as interp
+import re
+import scipy.optimize as op
+import matplotlib.pyplot as plt
+import cosmology as cosmo
+
+print 'cosmo=%s'%(cosmo.__file__)
+
+littleh=0.68
+config,foregrounds=sys.argv[1],sys.argv[2]
+
+def pmLogPlot(y,ymin):
+    posVals=y>0.
+    negVals=y<0.
+    
+    
+
+
+
+#numerical recipes 2nd edition page 661
+def linFit(x,y,dy):
+    s=np.sum(1./dy**2.)
+    sx=np.sum(x/dy**2.)
+    sy=np.sum(y/dy**2.)
+    sxx=np.sum(x**2./dy**2.)
+    sxy=np.sum(x*y/dy**2.)
+    delta=s*sxx-(sx)**2.
+    a=(sxx*sy-sx*sxy)/delta
+    b=(s*sxy-sx*sy)/delta
+    sa=sxx/delta
+    sb=s/delta
+    csab=-sx/delta
+    covMat=np.array([[sb,csab],[csab,sa]])
+    return np.array([b,a]),covMat
+
+
+lowInd=4
+highInd=2
+def readConfig(fileName):
+    """
+    read parser configuration file
+
+    """
+
+    # read pipeline parameters
+    print "=" * 50
+    print "Read configuration file " + fileName
+    config = {}
+    with open(fileName, "r") as cfile:
+        for line in cfile:
+            if line[0] != "#":
+                params = line.split("#")[0].split("=")  # split off comments
+                print params
+                config[params[0]] = eval(params[1])
+    return config
+
+if(foregrounds=='mod'):
+    postfix='Mod'
+elif(foregrounds=='opt'):
+    postfix='Opt'
+elif(foregrounds=='pess'):
+    postfix='Pes'
+
+config=readConfig(config)
+steps=np.array(config['STEPFRACS'])
+dStep=config['DSTEP']
+nSteps=len(steps)
+reStep=re.compile('step_[0-9]{1,2}')
+reNum=re.compile('[0-9]{1,2}')
+reGHz=re.compile('[0-9]{1,2}.[0-9]{5}')
+dirname=config['STEPPARAM']+'_Output/data/'
+plotdir=config['STEPPARAM']+'_Output/plots/'
[…]

### 2015-10-29 DishSimulations/code/computeW.sh

@@ -1,0 +1,176 @@
+#!/bin/bash
+#driver for computing the fisher matrix for a list of parameters. 
+
+#start with 1 param for now
+config=$1
+source ${config}
+thisdir=$(pwd)
+if ! [ -d "${thisdir}/${STEPPARAM}_${LABEL}_Output" ]
+then
+    mkdir ${thisdir}/${STEPPARAM}_${LABEL}_Output 
+fi
+#first determine the redshifts to compute sensitivity and power spectra at
+#than for each model, match redshifts and calculate sensitivity. 
+python redshiftFreqs.py ${ZMIN} ${ZMAX} ${DZ} ${thisdir}/${STEPPARAM}_${LABEL}_Output
+
+
+python computeDerivative.py ${config}
+#now run 21cmSense for each reshift
+#get number of steps by listing all run directories
+ls -d 21cmFAST_${STEPPARAM}_step*/>${STEPPARAM}_steplist.txt
+NSTEP=$(wc -l ${STEPPARAM}_steplist.txt | grep -o "[0-9]\{1,2\}")
+cd ${STEPPARAM}_${LABEL}_Output/data
+#now need to compute sensitivity for all steps in ps
+ #generate array file for array
+#if ! [ -f "${ARRAY}.track_${TRACK}hr_arrayfile.npz" ]
+if [ "${ARRAY}" = "mwa" ]  || [ "${ARRAY}" = "lofar" ] 
+then
+    if ! [ -f "${ARRAY}.track_6.0hr_arrayfile.npz" ]
+    then
+	if [ "${ARRAY}" = "mwa" ] 
+	then
+	    echo "using 200 max bl"
+	    python ${thisdir}/21cmSense-master/mk_array_file.py -C ${ARRAY} --bl_max 200 --track 6
+	else
+	    python ${thisdir}/21cmSense-master/mk_array_file.py -C ${ARRAY} --track 6
+	fi
+
+    fi
+else
+    if ! [ -f "${ARRAY}.drift_arrayfile.npz" ]
+    then
+
+	python ${thisdir}/21cmSense-master/mk_array_file.py -C ${ARRAY} #--track ${TRACK} #--bl_max 200.
+    fi
+fi
+
+for stepnum in `seq 0 $[${NSTEP}-1]`
+do
[…]

### 2015-10-29 DishSimulations/code/cosmology.py

@@ -13,15 +13,15 @@ DHcm=DH*3.08567758e24#hubble distance in cm
 kb=1.38e-23
 jy=1e-26
 mH=1.6726231e-24
-#pl13.Ob0=0.022068/(pl13.H0.value/1e2)**2.
-print pl13.Ob0
+pl13.Ob0=0.022068/(pl13.H0.value/1e2)**2.
+
 
 
 def H0_s():
     return pl13.H0_s
 
 def get_crit():
-    return pl13.critical_density(0).value
+    return pl13.critical_density(0)
 
 #in g cm^-3
 def baryon_density(z):

### 2015-10-29 DishSimulations/code/stepParam.sh

@@ -1,0 +1,56 @@
+#!/bin/bash
+#Aaron Ewall-Wice
+#May 12th 2015
+#script for stepping a single parameter in 21cmFAST
+#assumes init.c has already be run
+#than steps given parameter by delta, (given fiducial heating PARAM file)
+#copies directory/data cubes
+#builds programs
+#and submits grid engine jobs
+
+config=$1
+thisDir=$(pwd)
+#initialize config
+source ${config}
+#change CPU and RAM settings
+#cat 21cmFAST/Parameter_files/INIT_PARAMS.H | sed 's/NUMCORES (int) [0-9]\{1,2\}/NUMCORES (int) '${NCPU}'/' > 21cmFAST/Parameter_files/INIT_PARAMS.H
+cat 21cmFAST/Parameter_files/INIT_PARAMS_BACKUP.H | sed 's/NUMCORES (int) [0-9]\{1,2\}/NUMCORES (int) '${NCPU}'/' > 21cmFAST/Parameter_files/INIT_PARAMS.H
+#cat 21cmFAST/Parameter_files/INIT_PARAMS.H | sed 's/RAM (float) [0-9]\{2\}/NUMCORES (float) '${RAM}'/' > 21cmFAST/Parameter_files/INIT_PARAMS.H
+cat 21cmFAST/Parameter_files/INIT_PARAMS.H | sed 's/RAM (float) [0-9]\{2\}/RAM (float) '${RAM}'/' > 21cmFAST/Parameter_files/INIT_PARAMS_NEW.H
+mv 21cmFAST/Parameter_files/INIT_PARAMS_NEW.H 21cmFAST/Parameter_files/INIT_PARAMS.H
+#set TS_VERBOSE to zero, we need to conserve disk space for this. 
+cat 21cmFAST/Parameter_files/HEAT_PARAMS.H | sed 's/Ts_verbose (int) 1/Ts_verbose (int) 0/'
+#initialize DM boxes and PS will change this to qsub later
+cd 21cmFAST/Programs
+#make programs
+#make clean
+#make
+#initialize PS
+#./initOnly
+cd ${thisDir}
+#initialize step param files
+python reWriteConfig.py ${config}
+#get number of steps from number of config files
+
+#need to ajdust this to allow for multiple param files to be written. Simple Soluton: Make a directory with param files and copy everything in that
[…]

### 2015-10-29 DishSimulations/code/z2f.py

@@ -1,0 +1,7 @@
+#!/usr/bin/env python
+#convert z to frequency in GHz. 
+import sys
+z=float(sys.argv[1])
+f=1.42040575177/(z+1.)
+print '%.5f'%(f)
+

### 2015-10-29 DishSimulations/paper/DishSimulationsPaper_v0.tex
some minor edits

@@
 Cheng Carina\altaffilmark{5},
+David Deboer\altaffilmark{5},
 Neben Abraham\altaffilmark{1,2},
@@
 Patra Nipanjana\altaffilmark{5},
-Thyagarajan Nithyanandan\altaffilmark{6}
+Thyagarajan Nithyanandan\altaffilmark{6},
+and others.
 }
@@
 The precise degree of attenuation is determined in \citep{Thyagarajan:2015c} using simulations of foregrounds and noise and sets the spec for our antenna.
+
+It is instructive to examine, in more detail, the case where $r_0$ at ($\tau=0$) is significantly greater than the other coefficients. Than we can approximate
+\begin{equation}
+\widetilde{V}_{ij}'(\tau) \approx \widetilde{V}_{ij} + \sum_{m>0} \widetilde{V}_{ij}^{m0} (\tau -  \tau_m)
+\end{equation}
+
+If we make the assumption that the beam can be factored into a frequency dependent and frequency dependent term, $a_m = a({\bf \hat{k}}) r_m$ than we have
+\begin{equation}
+\widetilde{V}_{ij} \approx \widetilde{V}_{ij}(\tau) + \sum_{m>0} r_m \widetilde{V}_{ij}(\tau - \tau_m)
+\end{equation}
+ Hence, for a delay response dominated by the $0$-delay mode, as we might expect in our antenna element, the delay transformed visibilities are effectively convolved with the {\it voltage response}, not the voltage response squared as we might naively expect!
+
  In this paper, we study $R_{mn}({\bf \hat{k}})$ for the HERA antenna element to verify that it both meets the spec and agrees with direct measurements of the antenna element with refelctometry \citep{Patra:2015} and Orbcomm measurements \citep{Neben:2015b}.
@@
 
-\subsection{The Implications of Dish Reflections on EoR Sensitivity}
+\subsection{The Implications of Dish Reflections on EoR Science}
 Since the amplitude of the 21\,cm signal is maximal at smaller $k$ values, a loss of large scale signal out to $0.25$\,$h$Mpc$^{-1}$ will eliminate some of the power spectrum modes that HERA will have the greatest SNR on, impacting our overall sensitivity.

### 2015-10-29 DishSimulations/computeDerivative.py

@@ -1,0 +1,327 @@
+ #May 14th 2015
+#Aaron Ewall-Wice
+#aaronew@mit.edu
+#read config file
+#get parameter, its fiducial value and it's fractional change. 
+#for each change, select 21cmFAST run and compute power spectrum for all datacubes
+import numpy as np
+import os
+import sys
+import re
+import glob
+from joblib import Parallel, delayed
+import matplotlib.pyplot as plt
+import multiprocessing
+import powerSpectrum as power 
+import scipy.optimize as op
+import scipy.interpolate as interp
+num_cores=multiprocessing.cpu_count()
+
+#numerical recipes 2nd edition page 661
+def linFit(x,y,dy):
+    s=np.sum(1./dy**2.)
+    sx=np.sum(x/dy**2.)
+    sy=np.sum(y/dy**2.)
+    sxx=np.sum(x**2./dy**2.)
+    sxy=np.sum(x*y/dy**2.)
+    delta=s*sxx-(sx)**2.
+    a=(sxx*sy-sx*sxy)/delta
+    b=(s*sxy-sx*sy)/delta
+    sa=sxx/delta
+    sb=s/delta
+    csab=-sx/delta
+    covMat=np.array([[sb,csab],[csab,sa]])
+    return np.array([b,a]),covMat
+
+
+def readConfig(fileName):
+    """
+    read parser configuration file
+
+    """
+
+    # read pipeline parameters
+    print "=" * 50
+    print "Read configuration file " + fileName
+    config = {}
+    with open(fileName, "r") as cfile:
+        for line in cfile:
+            if line[0] != "#":
+                params = line.split("#")[0].split("=")  # split off comments
+                print params
+                config[params[0]] = eval(params[1])
+    return config
+
+#get list of data cubes 
+def getCubeNames(dirName):
+    fileList=glob.glob(dirName+'/dTb/delta_T')
+    #get redshifts form file list
+    return fileList
+        
+
+ #read in data cube,return its side length as well. 
+def readCube(cubeName):
+    print 'cubename=%s'%(cubeName)
+    #get side length from cube name
+    sideFind=re.compile('_[0-9]{2,4}_')
+    lenFind=re.compile('[0-9]{2,4}Mpc')
+    zFind=re.compile('z[0-9]{3}.[0-9]{2}')
+    nside=int(sideFind.findall(cubeName)[0][1:-1])
[…]

### 2015-10-29 DishSimulations/computeFisher.sh

@@ -1,0 +1,12 @@
+#!/bin/bash
+#compute fisher matrix from w vectors of various parameters
+#permit performing cuts in k and z and whether one wants to perform independent constraints 
+
+#config file has a list of parameters, a delta in frequency, a minimum redshift and a maximum redshift. Derive both independent constraints with each redshift interval or derive constraints from sums over redshift intervals. 
+config=$1
+
+#make directory to store outputs
+source ${config}
+echo ${DIRNAME}
+mkdir ./${DIRNAME}
+python computeFisher.py ${config}

### 2015-10-29 DishSimulations/computeOpticalDepth.py

@@ -1,0 +1,18 @@
+import numpy as np
+import scipy.interpolate as interp
+import scipy.integrate as integrate
+import cosmology as cosmo
+sigmaT=6.6524587e-25
+nfList=np.loadtxt('nfList.txt')
+zList=np.loadtxt('zList.txt')
+nfFunc=interp.interp1d(zList,nfList)
+def intFunc(x):
+    if(x<zList.min()):
+        return cosmo.baryon_n(x)*sigmaT*cosmo.DHcm*cosmo.de(x)/(1.+x)
+    elif(x>=zList.min() and x<=zList.max()):
+        return cosmo.baryon_n(x)*sigmaT*cosmo.DHcm*cosmo.de(x)/(1.+x)*(1.-nfFunc(x))
+    else:
+        return 0.
+        
+tauSum=quad(intFunc,0,zList.min())[0]+quad(intFunc,zList.min(),zList.max())[0]
+print tauSum

### 2015-10-29 DishSimulations/run_logZscroll.sh

@@ -1,0 +1,9 @@
+#!/bin/bash
+echo "running on ${HOSTNAME}"
+thisdir=$(pwd)
+folder=$1
+ssh ${HOSTNAME} "cd ${thisdir}; cd ${folder}/Programs; make clean; make; ./drive_logZscroll_Ts"
+mkdir ${thisdir}/${folder}/dTb
+mv ${thisdir}/${folder}/Boxes/delta_T* ${thisdir}/${folder}/dTb/
+#remove all boxes except for brightness temperature output
+rm -rf ${thisdir}/${folder}/Boxes/*

### 2015-10-29 DishSimulations/z2fFrac.py

@@ -1,0 +1,21 @@
+#!/usr/bin/env python
+import numpy as np
+import sys
+from scipy.integrate import quad
+f,df=float(sys.argv[1]),float(sys.argv[2])
+fL=f-df/2.
+fH=f+df/2.
+fmLow=88e6
+fmHigh=108e6
+def g(x):
+    if(x>=fmLow and x<fmHigh):
+        return 1.
+    else:
+        return 0. 
+
+def f(x):
+    if(x>=fL and x<fH):
+        return 1.
+    else:
+        return 0.
+print quad(lambda x: f(x)*g(x),fLtemp,fHtemp)[0]/(fH-fL)

### 2015-10-29 DishReflectometry/Memo copy 2.tex
First commit of all reflectometry measurements and v0 of reflectometry paper

\documentclass[12pt,preprint]{aastex}
\usepackage[margin=1in]{geometry}
\usepackage{float,amsmath}
%\usepackage{titlesec} %used to format titles
\usepackage{graphicx} %for handling figures
%\usepackage[none]{hyphenat} %disallows hyphenated words

\begin{document}

\title{HERA Dish Reflectometry} 
\author{Nipanjana Patra, Zaki Ali, Carina Cheng, Aaron Parsons}
\maketitle

\section{Introduction}

Non-ideal performance of radio telescope systems are often chromatic and manifests themselves in the measured data as systematic effects. One such non-ideality is mismatch between the impedance of free space and antenna as well as the transmission line which results in partial coupling of the sky signal into the antenna while the rest of it is reflected back into the space. In any reflector antenna, such as HERA dish antenna, this reflected signal illuminates the reflector. While most of the signal is reflected back in to the space by the reflector,  a part of it is reflected back and forth several times in between the feed and the vertex of the dish which is shadowed by the feed (red arrows in Figure \ref{fig:cartoon}). Such reflections generates multiple copies of reduced strength of the incident sky signal at various delays. This produces spurious correlation in the visibility space of the interferometric data.

 The design specification of the HERA elements are such that the amplitude of the signal that arrives at the feed at a delay of $60 \rm nS$ after multiple reflections off the dish, should be reduced by 60 dB relative to the first incident signal at the feed. We aim to verify this by carrying out Time Domain Reflectometry (TDR) at the HERA antenna prototype at the Green Bank. Understanding the nature of antenna reflections in the HERA dish is of the
utmost importance in characterising the performance of the dish. As HERA
progresses as an experiment, it is necessary to build optimal dishes that
promise to minimise the challenges of chromaticity in our quest for the Epoch
of Reionization.

\begin{figure}
\centering
\includegraphics[totalheight=0.3\textheight]{plots/reflection_cartoon.png}
\caption{The blue solid lines represent an original sky signal entering the feed. A small percentage of it (dashed blue) is reflected off the dish, and it is these reflections that we are concerned about. In our measurements however, the reflections measured contain most of the original pulse signal (solid red), so it is crucial to adjust for this difference in our analysis.}
\label{fig:cartoon}
\end{figure}

\begin{figure}
\centering
\includegraphics[totalheight=0.4\textheight]{plots/frequency_amp_phase_fullbw.png}
\caption{Amplitude and phase of the measured return loss. Colored dashed lines mark three different frequency bands: 140-160MHz, 100-200MHz, and 50-250MHz.}
\label{fig:freq}
\end{figure}

\section{Theory}{\label{sec:theory}}

In practice, a HERA dish receives signal from the sky\footnote{All astronomical
telescopes operate in this way.}. The plane waves, incident on the parabolic dish are focussed at the feed at the focal
height. For a well-designed feed, one that matches the impedance of
free space\footnote{The impedance of free space is $Z_{0} = \mu_{0}c_{0} =
\frac{1}{\epsilon_{0}c_{0}} \approx 377\Omega $.}, most of the signal will be
coupled into the system through the feed while only a small percentage will be reflected
back towards the dish for a secondary reflection into the feed (blue arrows in
Figure \ref{fig:cartoon}).  
%Therefore, the reflections we are concerned about are significantly less strong than the original signal, and it is this amount of eflection that we aim to quantify.
 In the following discussion, we consider the reflection
off the feed and the subsequent reflection off the dish as one reflection.

Quantitatively, if the incident power from the sky signal is $P_{sky}$, the feed
reflection coefficient is $\Gamma_{a}$, and the dish reflection
coefficient is $\Gamma_{d}$, then the net power entering the feed after an
$n^{th}$ reflection off the feed and the dish is:

\begin{equation}
P_{in} =  P_{sky}(1-\Gamma_{a})\Gamma_{d} [1+ \Gamma_{a}\Gamma_{d} e^{i\phi}+ (\Gamma_{a}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{d}\Gamma_{n})^{n}e^{in\phi}]
\end{equation}

where, $\phi = ({2\pi f \over c})(2l)$ is the propagation delay of a lightwave of frequency $f$ due to a reflection over a focal distance $l$. 
Therefore:
\begin{eqnarray}
{P_{in} \over P_{sky} } & = & (1-\Gamma_{a})\Gamma_{d} [1+ \Gamma_{a}\Gamma_{d} e^{i\phi}+ (\Gamma_{a}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{d}\Gamma_{n})^{n}e^{in\phi}] \nonumber\\
      & = & (1-\Gamma_{a})\Gamma_{d} {1-(\Gamma_{d}\Gamma_{a}e^{i\phi})^{n} \over 1-\Gamma_{d} \Gamma_{a} e^{i\phi} } 
\end{eqnarray}

Reflections causes the sky signal appear at various delays. We aim to measure the relative signal strength at various
delays, referred to as the ``delay spectrum" hereafter, to estimate various
levels of reflections in between the feed and the dish apex. Antenna performance is reciprocal in transmitting and receiving mode and, therefore, in order to measure the delay spectrum, we measure the complex return loss of the antenna by a Vector Network Analyser (VNA) and take the Fourier transform of the measured data. 
Since this measurement is carried out in
transmitting mode while an observation would be carried out in receiving mode,
we correct our results in order to map them to represent real observations.

%
%More specifically, our experimental set-up differs from measuring sky nal
%reflections since we send a pulse that is to be transmitted from the feed
%before receiving it again. This results in a reversed situation - most of our
%original signal is transmitted from the feed to be reflected from the dish,
%while a small percentage reflects back down the cable (red arrows in Figure
%\ref{fig:cartoon}). Therefore,

A broadband signal $P_{tr}$ is sent to the feed antenna via a 75m long cable by
a vector network analyser (VNA). A delay spectrum measurement of the system is
accomplished by measuring the return loss of the feed while keeping it at the
focal point of the dish.  When the signal is incident on the feed, part of the
incident power ($\Gamma_{a}$ ) is reflected back to the measuring device and
$(1-\Gamma_{a})$ is radiated by the feed. The signal radiated by the feed
illuminates the dish, and the signal incident at the dish apex is reflected by
the dish and returns to the feed. This incident signal is now reflected back
and forth in between the feed and the dish much like the sky signal reflection
discussed previously. Hence, if $P_{r}$ is the power incident back on the feed
for the first time then the reflected power $P_{ref}$ back into the VNA would
be:

\begin{equation}
P_{ref} =  P_{r}(1-\Gamma_{a}) [1+ \Gamma_{a}\Gamma_{d} e^{i\phi}+ (\Gamma_{a}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{d}\Gamma_{n})^{n}e^{in\phi}]
\end{equation}

Once again, we consider one reflection from the feed and its subsequent reflection from the dish as one reflection in total.

Recall that $P_{r}$ is the power incident back on the feed, which is just the feed radiated power reflected off the dish:

\begin{equation}
P_{r}= \Gamma_{d}(1-\Gamma_a) P_{tr}
\end{equation}

Also note that the first reflection of the signal sent by the VNA occurs at the antenna end. Hence the total returned power $P_{ret}$, to the VNA  would be:

\begin{eqnarray}
P_{ret} & = & \Gamma_{a}P_{tr} \nonumber\\ 
 & + &   \Gamma_{d}(1-\Gamma_a) P_{tr}(1-\Gamma_{a}) [1+ \Gamma_{a}\Gamma_{d} e^{i\phi}+  ....+ (\Gamma_{d}\Gamma_{n})^{n}e^{in\phi}]\nonumber\\
 \end{eqnarray}

Simplifying:

  \begin{eqnarray}
 {P_{ret} \over P_{tr} } & = & \Gamma_{a}
  +  \Gamma_{d}(1-\Gamma_a)^{2}  {1-(\Gamma_{d}\Gamma_{a})^{n} \over 1-\Gamma_{d} \Gamma_{a} } \nonumber\\
\end{eqnarray}

The VNA measures the magnitude and phase of the quantity ${P_{ret}\over P_{tr}}$ as a function of frequencies which is plotted in Figure \ref{fig:freq}. In our measurement set-up, the first reflection occurs at the antenna terminal $\Gamma_{a}$, so $({P_{ret} \over P_{tr} }  - \Gamma_{a}) $ gives an estimate of the delay spectrum of the sky signal. In the delay domain, the relative signal strength at zero delay represents the factor $\Gamma_{a}$ while the signal strength at any other delay represents any delayed signal that enters the feed after being reflected from the feed surroundings.

\section{Methodology}{\label{sec:methods}}

The prototype HERA dish (Figure \ref{fig:heradish} built at the NRAO site in
Green Bank, WV. is used to measure the delays associated with reflections within the dish and feed.
The dish is a 14-m parabolic reflector structurally supported
with 3 telephone poles. The reflective material is made up of wire mesh that
is attached to PVC pipes that form the parabolic shape. With the current
prototype, the feed is a PAPER dipole encased in a cylindrical cage encompassing
the backplane. The PAPER feed and the backplane (which prevents feed-to-feed
interaction between neighboring dishes) is raised and lowered by a three-pulley
system. The focal height of the dish is 4.5m ($\sim{14.76}$ft). Feed heights quoted in our measurements represent the distance from the balun to the top of the central concrete hub. Note, however, that the actual focal height of the dish represents the distance from the backplane of the feed to the dish's wire mesh, which intersects the concrete hub between the ground and the top of the hub. 
%XXX get discrepancy distance from DaveD. (1.7 ft from the bottom plate of sandwich to the top of the the cage and .26 ft from the top of the concrete hub to the middle where the parabola starts)

The following reflectometry measurements were taken on July 20-23, 2015 using a
FieldFox unit in Network Analyzer mode. A pulse is generated in the VNA
and sent through a 75ft $50\Omega$ cable that connects to the feed with a 4:1
passive balun. Magnitude and phase of the complex return loss of power is measured.
Measurements are taken for a frequency bandwidth of 50 to 500MHz. The delay spectrum is computed by taking Fourier transform of the measured data with appropriate windowing. The measurement specifications are,

\begin{itemize}
\item
Frequency bandwidth $450~MHz$ with 1024 channels i.e, frequency resolution $\Delta \nu = 0.44MHz$.
\item
For the measurement across $450~MHz$ bandwidth, resolution in the delay domain is $\Delta t = 2.22~ns$.
\item
Antenna feed focal length $4.5~m$ which corresponds to a signal propagation delay of $0.3~ns$. Hence, subsequent reflections from the dish vertex are expected to be at a delay which is integral multiple of $0.3~nS$. 
\item
Across the PAPER frequency band of $50 - 250~MHz$, the delay resolution would be $10~ns$ whereas the same over any $20MHz$ bandwidth would be $50ns$.
\end{itemize}

The signal at any other delays would be the result of signal reflection in the feed and the back place structure and the feed surroundings.

Fourier transform of a finite data series (such as the return loss over a finite bandwidth) can be interpreted as multiplication of data with a square window function, which is equivalent to convolving the Fourier transformed data with a $sinc$ function. This results in excess power at high delays due to the sidelobes in the $sinc$ function. Hence, appropriate windowing of the measurements is necessary before taking the Fourier transform. We have chosen to use a Blackman-Harris window. The effectiveness of this window function compared to a square window function is illustrated in Figure \ref{fig:window}.

\begin{figure}[H]
\centering
\includegraphics[totalheight=0.4\textheight]{plots/bh_vs_sq.png}
\caption{Fourier transform of the data shown in Figure \ref{fig:freq} using a Blackman-Harris window function as well as a square window function for the PAPER observation band between 100 to 200~MHz. The dashed lines mark the specification 60~dB - 60~ns.   }
\label{fig:window}
\end{figure}

As mentioned in Section \ref{sec:theory}, there is a mismatch in amplitude between the reflections that we measure (originating from the FieldFox pulse) and reflections produced by sky signal. The reflections that we measure (at high delays) must be lowered by a factor to represent weaker reflections that would occur after most of the sky signal is received by the feed. For our compensation, we multiply our entire delay spectrum by its DC component. We note that this correction is only accurate at high delays where our reflections of interest occur. At low delays, our spectrum amplitude should be increased to represent the original sky signal, but we do not apply this correction because it is not relevant to our analysis.

\begin{figure}
\centering
\includegraphics[trim={2cm 20cm 30cm 15cm},clip, totalheight=0.3\textheight]{plots/heradish.jpg}
\caption{HERA dish and feed at the Green Bank NRAO site.}
\label{fig:heradish}
\end{figure}

\section{Results}

Figure \ref{fig:freq} shows the return loss for a frequency bandwidth of 50 to 500MHz. This measurement was taken with the feed suspended at 12ft (distance between the balun and top of the central concrete hub). Because the return loss is the ratio of the power received to the power transmitted, higher reflections can clearly be seen outside of the PAPER bandwidth. This is not surprising, since the feed is tuned specifically for PAPER. The return loss minima are locations where our feed is well-matched to free space.

In Figure \ref{fig:3bands}, the return loss is plotted versus delay for three chosen bandwidths: the HERA bandwidth, the PAPER bandwidth, and a typical power spectra bandwidth when using a Blackman-Harris window function. It is again shown that the reflections are minimized for the PAPER bandwidth.

\begin{figure}
\centering
\includegraphics[totalheight=0.4\textheight]{plots/delay3_window.png}
\caption{Delay plots produced using a Blackman-Harris window function for 3 different frequency bandwidths: 50MHz-250MHz (``hera"), 100MHz-200MHz (``paper"), and 140MHz-160MHz (``pspec"). The black dashed lines illustrate our ``60 by 60" specification.}
\label{fig:3bands}
\end{figure}

Figure \ref{fig:elevator} is again a delay plot of the return loss, but for four different feed suspension heights. We use the PAPER bandwidth and note that the measurements are near identical at low delays, implying that low delay reflections are caused primarily by reflections within the feed cage. However, at higher delays we notice discrepancies between the different heights.

\begin{figure}
\centering
\includegraphics[totalheight=0.4\textheight]{plots/delay_heights_paper.png}
\caption{Delay plots produced using a Blackman-Harris window function for 4 different feed heights and the PAPER bandwidth. The black dashed lines illustrate our ``60 by 60" specification.}
\label{fig:elevator}
\end{figure}

Finally, Figure \ref{fig:outofthedish} presents measurements taken of the feed away from the dish. Echosorb is placed under the feed for some of the measurements, with the expectation that it will prevent any reflections off the ground. Measurements are also taken of the feed inside its metal cage in various configurations.

\begin{figure}
\centering
\includegraphics[totalheight=0.4\textheight]{plots/delay_feed.png}
\caption{Delay plots produced using a Blackman-Harris window function for different lone feed configurations and the PAPER bandwidth. The black dashed lines illustrate our ``60 by 60" specification.}
\label{fig:outofthedish}
\end{figure}

\section{Conclusion}

\end{document}

### 2015-10-29 DishReflectometry/Paper1_v0.tex
First commit of all reflectometry measurements and v0 of reflectometry paper

\documentclass[12pt,preprint]{aastex}
\usepackage{float,amsmath}
%\usepackage[margin=1in]{geometry}
%\usepackage{titlesec} %used to format titles
\usepackage{graphicx} %for handling figures
%\usepackage[none]{hyphenat} %disallows hyphenated words
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{skywalker@galaxy.far.far.away}

%\usepackage{cite}

%\citestyle{aa}
\shorttitle{HERA dish reflectometry }
\shortauthors{Patra et al.}

\begin{document}

\title{Effect of multiple reflection of the sky signal off the HERA element on the measurements of 21cm power spectrum} 
%\maketitle

\author{Nipanjana Patra\altaffilmark{1} }
\email{Contact author email: nipanjana@berkeley.edu}

\author{Zaki Ali\altaffilmark{1}, Carina Cheng\altaffilmark{1}, Dave DeBoer\altaffilmark{1}}
\author{Gilbert Hsyu\altaffilmark{2}, Tsz Kuk Leung\altaffilmark{2}, Aaron Parsons\altaffilmark{1}}

\altaffiltext{1}{University of California, Berkeley, nipanjana@berkeley.edu}
\altaffiltext{2}{To be inserted}

\begin{abstract}
\end{abstract}

\section{Introduction}
The efficacy of the techniques of foreground removal from the measured data critically limits the 21~cm power spectrum measurements. The delay transformation technique of foreground removal, introduced by  \citep{ParsonsBacker2009,Parsons2012} computes the Fourier transform of the visibility measured by an interferometer and produces a spectrum, referred to as delay spectrum hereafter, which is a function of the geometric time delay corresponding to the physical length of the baseline between two antennas. For the visibilities measured over a wide field across wide frequency bandwidth, the delay spectrum is constituted by the instrument response, the foreground signal and 21cm power spectrum, hereafter referred to as EoR signal.
%The complex visibility measured by an interferometer is a convolution of the instrument response with the true sky response in the UV plane. Therefore, when Fourier transformed, the delay spectrum is the multiplication of the sky response with the instrument response in the delay domain.
The technique exploits the smooth spectral characteristics of the foreground and for a widefield wide bandwidth visibility measurement by an interferometer with a baseline $b$, confines the foreground contribution to the computed delay spectrum within the largest possible time delay $\tau = b/c$ corresponding to the given baseline length. Such techniques also assumes a spectrally smooth instrumental response whose contribution to the measured data, much as the contribution of the smooth spectrum foreground, also has an upper bound in the delay space imposed by the largest geometric delay of the given baseline. 
Beyond this limit, for an ideal system performance, the delay spectrum would be dominated by any wideband signal across the sky with spectral and spatial fluctuation over small scale such as the EoR signal and therefore, could be detectable.\\ 
The interaction between the sky signal and instrument response can alter the relative contribution of the foreground, instrument response and the EoR signal at a given delay and thus influence the detectability of the EoR signal. Such interactions may cause the foreground and systematics to spill over at higher delays and thus push the upper limit of the foreground and systematic contaminated delay modes to much higher delays. In this process, the EoR signal over large spatial scale will be lost.

 The Hydrogen Epoch of Reionization Array (HERA) is a proposed array consisting of 568 14-m dishes in South Africa which will measure the 21~cm power spectrum between 100 to 200~MHz . In this paper, we investigate the performance of the individual HERA elements and resulting contribution of the instrument response to the delay spectrum. Reflectometry measurements  are carried out across wide bandwidth on a prototype HERA element in Green
Bank, WV (Figure \ref{fig:heradish}) and the results are interpreted in the light of delay spectrum technique. Section 2 describes the delay spectrum for the ideal and non-ideal performance of a two element interferometer. Reflectometry measurements are described in section 3. Section 4 qualifies the performance of the HERA element as an interferometer for detection of the 21~cm power spectrum.

\begin{figure}[ht!]
\centering
\includegraphics[trim={2cm 20cm 30cm 15cm},clip, totalheight=0.3\textheight]{plots/heradish.jpg}
\caption{HERA dish and feed at the Green Bank NRAO site.}
\label{fig:heradish}
\end{figure}

\section{Visibility measurements by a two element interferometer}
Consider a two element interferometer with a baseline $b$ and antenna field pattern $A(\theta, \nu)$. If we denote the sky signal at an angle $\vec \theta$ by $V_{sky}(\theta)$ and the receiver noise of each element as $V_{rec}$ then the voltage output of each antenna may be written as,  
\begin{equation}
V_{1}(\vec \theta, \nu) = V_{sky}(\vec \theta,\nu)+V_{rec1}(\nu)
\end{equation}
\begin{equation}
V_{2} (\vec \theta, \nu)= V_{sky}(\theta,\nu)exp({2\pi i \nu \vec{b}.\hat{s} \over c} )+V_{rec2}(\nu)
\end{equation}
where $\hat s$ is the unit vector along the direction of the baseline.
Hence, the time averaged complex visibility integrated over all sky as measured by the interferometer may be written as,

\begin{equation}
V e^{i\phi} = \left< \int A_{1}(\theta, \nu) V_{1}(\theta,\nu) A_{2}^{*}(\theta, \nu) V_{2}^{*} (\theta, \nu) exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right >
\end{equation}

Defining antenna power pattern as  $B(\theta,\nu)=A_{1}(\theta,\nu)A_{2}^{*}(\theta,\nu)$ and denote the sky power as  $P_{sky}=V_{sky}(\theta,\nu)V_{sky}^{*}(\theta,\nu) = |V_{sky}|^2$. Since $\left < V_{rec1}(\nu)V_{rec2}^{*}(\nu) = 0\right >$
Hence, 
\begin{eqnarray}
V e^{i\phi} & = & \int B(\vec \theta, \nu) P_{sky}(\vec \theta,\nu) exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \nonumber\\
		& = & \int B(l,m, \nu) P_{sky}(l,m,\nu) exp(2\pi i \nu \tau_{g} ) dl dm \nonumber\\
 		& = & B(\vec u,\nu) \ast P_{sky}(\vec u,\nu ) \nonumber\\
		& = & B(\nu { |\vec b| \over c} , \nu) \ast P_{sky}(\nu { |\vec b| \over c} , \nu) \nonumber\\
		& = & B(\tau_{g}, \nu) \ast P_{sky}(\tau_{g} , \nu)	
\end{eqnarray}

i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum. In other words, it is the convolution of the Fourier transform of the antenna power pattern with the Fourier transform of the sky. The complex visibility measured by an interferometer with a given baseline length has explicit dependence on frequency as well as implicit frequency dependence through the spatial frequency $\vec u = \nu { \vec b \over c}$ component. Since $\vec u $ is the

\begin{eqnarray}
\mathcal{F} \left [V e^{i\phi}\right] & = & \mathcal{F}\left [B(\vec u,\nu) \ast P_{sky}(\vec u,\nu) \right] \nonumber\\
						   & = & B(\tau)P_{sky}(\tau)\nonumber\\
						   & = & B(\nu { \vec b \over c}) 
\end{eqnarray}

For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space. Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities. If we define the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as,

\begin{eqnarray}
\mathcal{F} \left [V e^{i\phi}\right] & = & \int \left [  \int B(l,m, \nu) P_{sky}(l,m,\nu) exp[2\pi i \nu \tau_{g}] dl dm\right ] exp\left[ 2 \pi i\nu \tau \right]d\nu \nonumber\\
						   & = & \int B(\tau_{g}, \nu )\ast P_{sky}(\tau_{g}, \nu ) exp[2\pi i \nu \tau] d\nu\nonumber\\
						   & = & B(\tau+\tau_{g})P_{sky}(\tau+\tau_{g}) \nonumber	
\end{eqnarray}

Fourier transform of the

There are several different sources of instrumental chromaticity for radio
telescope systems that can result in non-ideal performances and unwanted
systematic effects in measured data. One such source is the mismatch between
the impedance of free space and the feed and transmission line, which results
in a partial coupling of the sky signal into the feed while the rest is
reflected back into the space. For any reflector telescope, such as HERA, this
signal illuminates the dish and part of it reflects back and forth several
times in between the dish feed and the vertex of the dish.  Such reflections
generate multiple reduced strength copies of the incident sky signal at various
delays, and this produces spurious correlations in the visibilities of
interferometric data.

To first order, the design specification of HERA elements requires that any
delayed signal, arriving at the feed after a multipath propagation, should be
at the level of $-60dB$ at a delay of $60ns$ relative to the first incident
signal at the feed \citep{parsons_deboer_memo}. This specification was
approximated based on the power level of the cosmological signal in relation to
foreground signals, which is estimated to be six orders of magnitude fainter
\citep{santos_et_al2005,ali_et_al2008,deoliveira2008,jelic_et_al2008,bernardi_et_al2009,bernardi_et_al2010,ghosh_et_al2011}.
Additionally, the $14m$ HERA baselines set a foreground containing
horizon-limit (the wedge) that, with some buffer, sets a delay specification of
$60ns$
\citep{parsons_et_al2012b,vedantham_et_al2012,nithya_et_al2013,liu_et_al2014a,liu_et_al2014b}.

We carry out reflectometry measurements at the HERA element prototype in Green
Bank, WV (Figure \ref{fig:heradish}) in order to understand the nature of feed
reflections in the dish and characterize its performance. As HERA progresses as
an experiment, it is necessary to build optimized dishes that aim to minimize the
challenges of chromaticity in our quest for the Epoch of Reionization.

\section{Theory}{\label{sec:theory}}
\begin{figure}[ht!]
\centering
\includegraphics[totalheight=0.35\textheight]{plots/reflection_cartoon.png}
\caption{The blue solid lines represent an original sky signal entering the
feed. A small percentage of it (dashed blue) is reflected off the dish, and it
is these reflections that we are concerned about. In our measurements however,
the reflections measured contain most of the original pulse signal (solid red),
so it is crucial to adjust for this difference in our analysis.}
\label{fig:cartoon}
\end{figure}

Plane waves incident on a parabolic dish
are focussed at the feed with focal height $l$. For a well-designed feed, one
that closely matches the impedance of free space\footnote{The impedance of free space
is $Z_{0} = \mu_{0}c_{0} = \frac{1}{\epsilon_{0}c_{0}} \approx 377\Omega $.},
most of the signal will enter the system while only
a small percentage will be reflected back towards the dish for a secondary
reflection into the feed (dashed blue arrows in Figure \ref{fig:cartoon}). In the
following discussion, we consider a reflection off the feed and the
subsequent reflection off the dish as one reflection.

Quantitatively, if the incident power from the sky signal is $P_{sky}$, the feed
reflection coefficient is $\Gamma_{f}$, and the dish reflection
coefficient is $\Gamma_{d}$, then the net power entering the feed after an
$n^{th}$ reflection off the feed and the dish is:

\begin{equation}\label{eqn:series1}
P_{in} =  P_{sky}(1-\Gamma_{f})[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
\end{equation}

where, $\phi = 2l({2\pi \over c})\nu$ is the propagation delay of a lightwave of frequency $\nu$ due to a reflection over a focal distance $l$. It is noted that upon the first incidence, the sky signal is focussed onto the feed from the entire dish and the dish reflection coefficient $\Gamma_{d}$ is $1$ for this first incidence. The subsequent back and forth reflection of the signal in between the feed and the dish, however, occurs from only the part of the dish which is shadowed by the feed. Therefore, in this case, $\Gamma_{d} < 1$.

Simplifying Equation \ref{eqn:series1}:
\begin{eqnarray}\label{eqn:ratio1}
{P_{in} \over P_{sky} } & = & (1-\Gamma_{f})[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}] \nonumber\\
      & = & (1-\Gamma_{f}) \displaystyle\sum\limits_{n=0}^{n} [\Gamma_{f}\Gamma_{d}e^{i \phi}]^{n}\nonumber\\
      & = & (1-\Gamma_{f})+(1-\Gamma_{f}) \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i \phi}]^{n}
\end{eqnarray}

The ratio in Equation \ref{eqn:ratio1} quantifies the amount of power received
with respect to the incident sky power. Realistically, the incident sky power
is not easily quantifiable, but it is a quantity we need to know to accurately
characterize reflections.  
%The right hand side of this equation consists of system parameters which are all chromatic i.e, functions of frequency.

%Reflections cause the sky signal to appear at various delays. We aim to measure
%the relative signal strength at those various delays, referred to as the
%``delay spectrum" hereafter, to estimate levels of reflections in between the
%feed and the dish apex.

%We employ the reciprocity theorem for antennas in our experimental set-up.
%More specifically, our experimental set-up differs from measuring sky signal
%reflections since we send a pulse that is to be transmitted from the feed
%before receiving it again. This results in a reversed situation - most of our
%original signal is transmitted from the feed to be reflected from the dish,
%while a small percentage reflects back down the cable (red arrows in Figure
%\ref{fig:cartoon}). Therefore, since our measurement is carried out in
%transmitting mode while an observation would be carried out in receiving mode,
%we correct our results in order to map them to represent real observations.

In our experimental set-up, instead of using sky signal, we employ
our feed as a transmitter and transmit a pulse. If the initial pulse is a broadband signal,
$P_{tr}$, sent to the feed via a $75ft$ cable by a vector network
analyser (VNA), a delay domain measurement of the system is accomplished by
taking the Fourier transform of the measured complex return loss of the feed. When the signal is incident on
the feed, part of the incident power ($\Gamma_{f}$) is reflected back to the
measuring device (dashed red arrows in Figure \ref{fig:cartoon}) and
$(1-\Gamma_{f})$ is radiated by the feed (solid red arrows in Figure
\ref{fig:cartoon}) which illuminates the dish. While most of the incident signal is reflected back into space by the dish, the reflected signal from the dish vertex returns to
the feed. This incident signal is now
reflected back and forth in between the feed and the dish much like the sky
signal reflection discussed previously.  Hence, if $P_{r}$ is the power
incident back on the feed for the first time then the reflected power, $P_{refl}$,
back into the VNA would be:

\begin{equation}\label{eqn:series2}
P_{refl} =  P_{r}(1-\Gamma_{f})[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
\end{equation}

Once again, note that we consider one reflection from the feed and its subsequent reflection from the dish as one reflection in total. Equation \ref{eqn:series2} is similar to Equation \ref{eqn:series1}, with different incident powers.

Recall that $P_{r}$ is the initial power that is incident back on the feed, which is just the feed radiated power reflected off the dish:

\begin{equation}
P_{r}= \Gamma_{d}(1-\Gamma_f)e^{i\phi} P_{tr}
\end{equation}

Also note that the first reflection of the signal sent by the VNA occurs at the feed end. Hence the total returned power $P_{ret}$, to the VNA  would be:

\begin{eqnarray}
P_{ret} & = & \Gamma_{f}P_{tr} \nonumber\\ 
 & + &   \Gamma_{d}(1-\Gamma_f)e^{i\phi} P_{tr}(1-\Gamma_{f}) [1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]\nonumber\\
 \end{eqnarray}

Simplifying:

  \begin{eqnarray}\label{eqn:ratio2}
 {P_{ret} \over P_{tr} } & = & \Gamma_{f}
  +  \Gamma_{d}(1-\Gamma_f)^{2} [e^{i\phi}+ \Gamma_{f}\Gamma_{d} e^{i2\phi}+  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{i n\phi}]\nonumber\\
  & = & \Gamma_{f} + { (1-\Gamma_f)^{2}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
   \nonumber\\
\end{eqnarray}

The ratio in Equation \ref{eqn:ratio2} is the returned power to the VNA with
respect to the transmitted power sent by the VNA. It is identical to the sky
observation case in Equation \ref{eqn:ratio1} but differs by two factors. The
first factor corresponds to an additive amplitude difference arising from
$\Gamma_{f}$, which physically accounts for the initial reflection at the feed.
The second difference is a multiplicative term which informs us about the first
reflection. Both of these terms need to be corrected for in order to relate our
measurements to real observations.
%Therefore, because our measurement is carried out in transmitting mode
%while a sky observation would be carried out in receiving mode, we correct our
%results in order to map them real observations.

The VNA measures the magnitude and phase of the quantity ${P_{ret}\over P_{tr}}$
as a function of frequency as shown in Figure \ref{fig:freq}. In our measurement
set-up, the first reflection occurs at the feed $\Gamma_{f}$, so
$({P_{ret} \over P_{tr} }  - \Gamma_{f}) $ gives an estimate of the delay
spectrum of the sky signal. In delay domain, the relative signal strength at
zero delay represents the factor $\Gamma_{f}$ while the signal strength at any
other delay represents any delayed signal that enters the feed after being
reflected from the feed surroundings.

\section{Methodology}{\label{sec:methods}}

Our reflectometry measurements are made using a prototype HERA dish at NRAO in Green Bank, WV. The dish is a $14\,m$ diameter
parabolic reflector structurally supported with 3 telephone poles. The
reflective material is made up of wire mesh that is attached to PVC
pipes, forming the parabolic shape of the dish. With the current iteration of
the HERA dish, the feed consists of a PAPER dipole encased in a cylindrical cage
encompassing the backplane. The PAPER feed and the backplane (which is aimed at
preventing feed-to-feed interaction between neighboring dishes) is raised and
lowered by a three-pulley system. The focal height of the dish is $4.5m$
($\sim{14.76}$ft).

%The heights measured in our experiment were made from
%the balun to the top of the concrete hub. However, the focal height should be
%measured from the backplane to point where the wire mesh would intersect the
%concrete hub at the vertex of the dish. To account for this height discrepency,
%we add 1.96 ft to all of our measured heights. These are the heights quoted in
%the plots.[XXX not done yet but will be done]
Our measurements are made with a FieldFox in VNA mode. In this mode, a pulse
is generated in the FieldFox and sent through a $75ft$ $50\Omega$ cable that
connects to the feed with a 4:1 passive balun. The magnitude and phase of the complex return loss is measured between 50 to $500MHz$ over 1024 frequency channels which gives a frequency resolution of 0.44MHz. The delay resolution of the measurements is $\Delta{t}=2.22ns$.
In addition, we note that the round trip of a reflection from the feed to the dish
is $9m$, which corresponds to a delay of $30ns$.

%Feed heights quoted in our measurements represent the distance from the balun to
%the top of the central concrete hub. However, the actual focal height
%of the dish represents the distance from the backplane of the feed to the dish's
%wire mesh, which intersects the concrete hub between the ground and the top of
%the hub. A 
%XXX get discrepancy distance from DaveD. (1.7 ft from the bottom plate of
%sandwich to the top of the the cage and .26 ft from the top of the concrete hub
%to the middle where the parabola starts)

%need to add in third : Antenna feed focal length 4.5 m which corresponds to a
%signal propagation delay of 0.3 ns. Hence, subsequent reflections from the dish
%vertex are expected to be at a delay which is integral multiple of 0.3 nS.
\begin{figure}[ht!]
\centering
\includegraphics[totalheight=0.4\textheight]{plots/frequency_amp_phase_fullbw.png}
\caption{Amplitude and phase of the measured return loss. Colored dashed lines
mark three different frequency bands: $140-160MHz$ (typical power spectrum bandwidth), $100-200MHz$ (PAPER bandwidth), and
$50-250MHz$ (HERA bandwidth).}
\label{fig:freq}
\end{figure}

Frequency domain data, as shown in Figure \ref{fig:freq}, can be Fourier-transformed to compute the return loss in the delay domain. Because the measured data is band-limited between $50$ to $500MHz$, it is analogous to multiply the measured data by a square window function. Then in delay domain, the response would be convolved with a $sinc$ function. This may result in excess power at high
delays due to the sidelobes of the $sinc$ function. Hence, appropriate windowing of the measured data set is necessary before taking the Fourier transform.
We have chosen a Hamming window for our analysis, and its effectiveness of this
window function compared to others is illustrated in Figure
\ref{fig:window}.

As mentioned in Section \ref{sec:theory}, there is a mismatch in amplitude
between the reflections that we measure (originating from the FieldFox pulse)
and reflections produced by sky signal. The reflections that we measure (at high
delays) must be lowered by a factor to represent weaker reflections that would
occur after most of the sky signal is received by the feed. For our
compensation, we multiply our entire delay spectrum by its DC component, which is the feed reflection coefficient $\Gamma_{f}$, and also divide by ($1-\Gamma_{f}$). In other words, these correction factors equate Equation \ref{eqn:ratio2} with Equation \ref{eqn:ratio1}. 
We note that this correction is only accurate at high delays where our
reflections of interest occur. At low delays, our spectrum amplitude should be
increased to represent the original sky signal, but we do not apply this
correction because it is not relevant to our analysis.

\begin{figure}[H]
\centering
\includegraphics[totalheight=0.41\textheight]{plots/bh_vs_sq.png}
\caption{Delay plot produced for the PAPER bandwidth ($100MHz-200MHz$) by taking the Fourier transform of the measured return loss using four different window functions: Blackman-Harris, square, Hamming, and Hanning.}
\label{fig:window}
\end{figure}

\section{Results}

Figure \ref{fig:freq} shows the return loss for a frequency bandwidth of $50$ to
$500MHz$. This measurement was taken with the feed suspended at $4.26m$, which
was our closest measurement to the actual focal height.  Because the return
loss is the ratio of the power received to the power transmitted, higher
reflections can clearly be seen outside of the PAPER bandwidth. This is not
surprising, since the feed is tuned specifically for PAPER. The return loss
minima are locations where our feed is well-matched to free space.

In Figure \ref{fig:3bands}, the return loss we measure is plotted versus delay
for three chosen bandwidths: the HERA bandwidth, the PAPER bandwidth, and a
typical power spectra bandwidth when using a Hamming window function. Two
additional measurements, using data taken in 2014 with the first prototype HERA
dish near Berkeley, CA, are also plotted using two different bandwidths. One of
the main differences between the Green Bank and Berkeley measurements is that
the feed was not encompassed in a cage for the Berkeley data (only a backplane). Additionally, the $50-1000MHz$ data taken in Berkeley was
Fourier-transformed internally by the measuring device, while the $100-200MHz$
data is analyzed post-measurement in the same way as the Green Bank data.

\begin{figure}[ht!]
\centering
\includegraphics[totalheight=0.41\textheight]{plots/delay3_window.png}
\caption{Delay plots produced using a Hamming window function for 5 different cases. Three of the cases correspond to measurements taken in Green Bank for three frequency bandwidths: $50MHz-250MHz$ (HERA bandwidth), $100MHz-200MHz$ (PAPER bandwidth), and $140MHz-160MHz$ (typical power spectrum bandwidth). Two of the cases correspond to measurements taken in 2014 of the first prototype HERA dish in Berkeley (without a feed cage). Of these, we plot data for two frequency bandwidths: $100MHz-200MHz$ (PAPER bandwidth), and $50MHz-1000MHz$ (full bandwidth used by the VNA). For the PAPER bandwidth data, we follow the same Fourier-transform analysis as the others, while the full bandwidth data is produced directly by the VNA. The black dashed lines illustrate our ``60 by 60" specification.}
\label{fig:3bands}
\end{figure}

From the plot, we see that the delay response of a feed is dependent on the band chosen for the Fourier transform.  As one might expect, in regions
where the feed return loss is low, reflections are minimized.  Thus, we cannot ignore that these measurements were performed
using a PAPER-style feed tuned for efficient operation over a $100-200MHz$ bandwidth.  Fourier transforms taken over wider bands
become dominated by the feed performance in regions outside the operating band, making the resultant delay profiles less relevant
for the power spectrum performance of the HERA instrument.  Conversely, when performing Fourier transforms over much 
narrow bands (the windowed $20MHz$ bands typical of PAPER analysis), the width of the resulting delay profile
becomes dominated by sidelobes of low delay emission interacting with the narrow bandwidth kernel.  
Although this may appear to be a relevant performance metric
for PAPER-style power spectrum analysis, such an analysis typically pre-filters out low-delay emission using wide bandwidths precisely to avoid
sidelobes from low-delay emission.  Hence, the most relevant delay-spectrum performance profile is that taken using the $100-200MHz$ band.

In the $100-200MHz$ delay profile, we see a delay response of $-50dB$ at $60ns$, which slopes down to $-60dB$ at $\sim120ns$.  Because
this does not achieve $-60dB$ attenuation at $60ns$, this indicates that the HERA system under test does not meet specification. However, we can learn additional information by evaluating
different feed components.

\begin{figure}[ht!]
\centering
\includegraphics[totalheight=0.41\textheight]{plots/delay_heights_paper.png}
\caption{Delay plots produced using a Hamming window function for 4 different feed heights and the PAPER bandwidth ($100MHz-200MHz$). The black dashed lines illustrate our ``60 by 60" specification.}
\label{fig:elevator}
\end{figure}

Figure \ref{fig:elevator} is again a delay plot of the return loss, but for
four different feed suspension heights. We use the PAPER bandwidth and note
that the measurements are near identical at low delays, implying that low delay
reflections are caused primarily by reflections within the feed cage. However,
at higher delays we notice discrepancies between the different heights.

In addition, Figure \ref{fig:outofthedish} presents measurements taken of the feed
away from the dish. Echosorb is placed under the feed for some of the
measurements, with the expectation that it will prevent any reflections off the
ground. Measurements are also taken of the feed inside its metal cage in
various configurations. It is shown that the feed performs best without the cage and with the absorber.

From these various measurements, we find that the feed itself is responsible for a significant portion of the structure up to $60ns$ and
that the cylindrical cage may be contributing up to $20ns$ to the width of the delay profile. We note that this depends strongly
on its coupling to structures around it. Structure beyond $60ns$ appears to scale
with the height of the feed above the dish, making reflections off the dish the likely culprit.

\begin{figure}[H]
\centering
\includegraphics[totalheight=0.41\textheight]{plots/delay_feed.png}
\caption{Delay plots produced using a Hamming window function for different lone feed configurations and the PAPER bandwidth ($100MHz-200MHz$). The black dashed lines illustrate our ``60 by 60" specification.}
\label{fig:outofthedish}
\end{figure}

\section{Conclusion}

The delay-domain performance of the HERA dish is central to HERA's function as a power spectrum instrument.
As we have seen, reflectometry measurements can help characterize HERA's performance in this domain, and
as Equation \ref{eqn:ratio1} shows, these measurements must be adjusted for a difference in transmission/reflection
at the first feed encounter in order to be interpreted as the delay response of a feed relative to an incident
plane wave from the sky.  We also see that the choice of windowing function is critical for accurately measuring the
antenna delay response at higher delays, where sidelobes from much higher amplitude responses at small delays can easily
dominate.  We find Hamming, Hanning, and Blackman-Harris windows to be generally adequate while square windowing functions are not.
Given the critical nature of the windowing function, we recommend that all reflectometry measurements be performed in the
frequency domain, so that the data analyst can manually implement the Fourier transform with the appropriate window.

Taken all together, we summarize that the first version of the HERA dish, with a PAPER-style feed and cylindrical cage, is close to meeting
specification, but will require additional work to fall below $-60dB$ at $60ns$.  Given that the width of the delay response is a convolution
of the feed response and the dish reflections, it is not possible to perfectly decouple the response of the feed from that of the dish.
It may be possible to achieve enough of a reduction to meet specification by modifying the feed.
Given that previous measurements using a PAPER feed with a simple backplane exhibit structure above $-60dB$ at $60ns$,
we deduce that these advances will most likely require improving the feed return loss.  We also recommend re-investigating the scattering
cone for reducing standing waves between the feed and dish.  Finally, given the proximity of our measurements to the rough 
specification that was adopted for 
HERA of $-60dB$ attenuation at $60ns$, we recommend reinvestigating this specification to determine more accurately the impact of 
the element's current delay performance on HERA science.  We suspect that, at the level of $-50dB$ at $60ns$ and $-60dB$ at $120ns$, this
performance may indeed be adequate for the delay-domain power spectrum analysis for which HERA has been optimized.

%\bibliographystyle{apj}
%\bibliography{biblio.bib}
\begin{thebibliography}{}

\bibitem[Pasrons \& Backer(2009)]{ParsonsBacker2009}
Parsons, A., \& Backer, D. 2009, \apj, 138, 219
\bibitem[Parsons et al.(2012)]{Parsons2012}
Parsons, A., \& Pober, Jonathan C., \& Aguirre, James E., \& Carilli, Christopher L., \& Jacobs, Daniel C., \& Moore, David F. 2012, \apj 756, 165
\end{thebibliography}{}

\end{document}

### 2015-10-29 DishReflectometry/plots/plot_bh_vs_sq.py

@@ -1,0 +1,56 @@
+#! /usr/bin/env python
+import numpy as n 
+import pylab as p
+import sys, csv
+import aipy as a
+
+def fromcsv(filename):
+    print 'Reading', filename
+    d = csv.reader(open(filename,'r'), delimiter=',')
+    x = n.array(list(d)[18:-1], dtype=n.float)
+    return x[:,0]/1e9, x[:,1]
+
+def take_delay(db, ph, fq, window='blackman-harris'):
+    '''Take reflectometry data in dB and phase to return delay transform.
+       Returns windowed and non windowed delay spectra for input spectrum.'''
+    d = 10**(db/20) * n.exp(2j*n.pi*ph/360)
+    tau = n.fft.fftfreq(fq.size, fq[1]-fq[0])
+    window = a.dsp.gen_window(fq.size, window)
+    _d = n.fft.ifft(d)
+    _dw = n.fft.ifft(d*window) / window.mean() #compensate for window amplitude
+    
+    if True:
+        _dw *= ( n.abs(_dw[0])/ (1- n.abs(_dw[0])))  # these should be changed to the dc bin of the windowed data.
+        _d *= ( n.abs(_d[0])/ (1- n.abs(_d[0])))  # these should be changed to the dc bin of the windowed data.
+
+    return n.fft.fftshift(_dw), n.fft.fftshift(_d), n.fft.fftshift(tau)
+
+colors = n.array([(31,119,180), (255,127,14), (44,160,44), (214,39,40), (127,127,127), (148,103,189)])/255.
+
+
+#file_base = sys.argv[1]
+file_base = '../alldata/NC41_12'
+amp = '_DB.csv'
+phs = '_P.csv'
+fq, amps = fromcsv(file_base + amp)
+fq, phs= fromcsv(file_base + phs)
+
+valid = n.where(n.logical_and(fq>.1, fq<.2))
+dw, d, tau = take_delay(amps[valid], phs[valid], fq[valid])
+dwhm, d, tau = take_delay(amps[valid], phs[valid], fq[valid], window='hamming')
+dwhn, d, tau = take_delay(amps[valid], phs[valid], fq[valid], window='hanning')
+p.plot(tau, 10*n.log10(n.abs(dw)**2), linewidth=2, label='blackman-harris', color=colors[0])
[…]

### 2015-10-29 DishReflectometry/plots/plot_frequency.py

@@ -1,0 +1,68 @@
+#! /usr/bin/env python
+import numpy as n 
+import pylab as p
+import sys, csv
+
+def fromcsv(filename):
+    print 'Reading', filename
+    d = csv.reader(open(filename,'r'), delimiter=',')
+    x = n.array(list(d)[18:-1], dtype=n.float)
+    return x[:,0]/1e9, x[:,1]
+
+colors = n.array([(31,119,180), (255,127,14), (44,160,44), (214,39,40), (127,127,127), (148,103,189)])/255.
+
+#file_base = sys.argv[1]
+file_base = '../alldata/NC41_12'
+amp = '_DB.csv'
+phs = '_P.csv'
+freqs, amps = fromcsv(file_base + amp)
+freqs, phase= fromcsv(file_base + phs)
+
+#rloss = amps * n.exp(2j*n.pi*phase/360.)
+#p.figure(figsize=(10,5))
+#p.plot(freqs, rloss.real, linewidth=3, label='real')
+#p.plot(freqs, rloss.imag, linewidth=3, label='imag')
+#p.xlabel('Frequency (GHz)' )
+#p.ylabel('Return Loss (dB)')
+#p.grid(1)
+#p.xlim(.05,.250)
+#p.ylim(-30,25)
+#p.vlines(.1, -100, 100, linestyle='--', linewidth=2)
+#p.vlines(.2, -100, 100, linestyle='--', linewidth=2)
+#p.legend()
+
+
+fig, (ax1,ax2) = p.subplots(2,1, figsize=(10,5), sharex=True)
+#ax1.plot(freqs, amps, linewidth=3, label='amplitude', color=(0,107/255.,164/255.))
+ax1.plot(freqs, amps, linewidth=3, label='amplitude', color=colors[0])
+ax1.set_ylabel('Return Loss (dB)')
+ax1.grid(1)
+#ax1.set_xlim(.05,.250)
+ax1.set_ylim(-25,25)
+#p.setp(axes[0].get_xticklabels(), visible=False)
+ax1.vlines(.1, -100, 100, linestyle='--', linewidth=2)
+ax1.vlines(.2, -100, 100, linestyle='--', linewidth=2)
+ax1.vlines(.05, -100, 100, linestyle='--', linewidth=2, color='c')
+ax1.vlines(.25, -100, 100, linestyle='--', linewidth=2, color='c')
[…]

### 2015-10-29 DishReflectometry/plots/plot_heights.py

@@ -1,0 +1,65 @@
+#! /usr/bin/env python
+
+import numpy as n
+import pylab as p
+import sys, csv
+import aipy as a
+
+def fromcsv(filename):
+    print 'Reading', filename
+    d = csv.reader(open(filename,'r'), delimiter=',')
+    x = n.array(list(d)[18:-1], dtype=n.float)
+    return x[:,0]/1e9, x[:,1]
+
+def take_delay(db, ph, fq, window='blackman-harris'):
+    '''Take reflectometry data in dB and phase to return delay transform.
+       Returns windowed and non windowed delay spectra for input spectrum.'''
+    d = 10**(db/20) * n.exp(2j*n.pi*ph/360)
+    tau = n.fft.fftfreq(fq.size, fq[1]-fq[0])
+    window = a.dsp.gen_window(fq.size, window)
+    _d = n.fft.ifft(d)
+    _dw = n.fft.ifft(d*window) / window.mean() #compensate for window amplitude
+
+    if True:
+        _dw *= ( n.abs(_dw[0])/ (1- n.abs(_dw[0])))  # these should be changed to the dc bin of the windowed data.
+        _d *= ( n.abs(_d[0])/ (1- n.abs(_d[0])))  # these should be changed to the dc bin of the windowed data.
+
+    return n.fft.fftshift(_dw), n.fft.fftshift(_d), n.fft.fftshift(tau)
+
+
+colors = n.array([(31,119,180), (255,127,14), (44,160,44), (214,39,40), (127,127,127), (148,103,189)])/255.
+
+#file_base = sys.argv[1]
+#file_base = '../alldata/NC41_'
+file_base = '../alldata/F'
+amp_end = '_DB.csv'
+phs_end = '_P.csv'
+
+#valids = [6,9,12,15]
+#valids = ['A_NC41_3','A_NC41_AB_3','C_NC41','C_NC41_AB','C_NC41_UD']
+#labels = ['feed alone 3ft above ground','feed alone 3ft above absorber','feed in cage on ground','feed in cage on absorber','feed in cage upsidedown']
+valids = ['C_NC41','C_NC41_AB']
+labels = ['feed in cage on ground','feed in cage on absorber']
+
+fig, ax = p.subplots(nrows=1,ncols=1)
+for i,v in enumerate(valids):
[…]

### 2015-10-29 DishReflectometry/plots/plot_reflectometry.py

@@ -1,0 +1,52 @@
+#! /usr/bin/env python
+
+import numpy as np, pylab as plt, aipy as a
+import sys, csv
+
+def fromcsv(filename):
+    print 'Reading', filename
+    d = csv.reader(open(filename,'r'), delimiter=',')
+    x = np.array(list(d)[18:-1], dtype=np.float)
+    return x[:,0]/1e9, x[:,1]
+
+for filename in sys.argv[1:]:
+    BASE = filename[:-len('.csv')]
+    db_file = BASE + '_DB.csv'
+    ph_file = BASE + '_P.csv'
+
+    WINDOW = 'blackman-harris'
+    #WINDOW = 'hamming'
+
+    fq,db = fromcsv(db_file)
+    fq,ph = fromcsv(ph_file)
+    #d = 10**(db/10) * np.exp(2j*np.pi*ph/360) # power
+    d = 10**(db/20) * np.exp(2j*np.pi*ph/360) # 20 to put into voltage amplitude, not power
+
+    valid = np.ones(fq.size, dtype=np.bool) # use entire sampled band
+    #valid = np.where(fq < .250) # restrict to HERA band
+    #valid = np.where(np.logical_and(fq < .2, fq > .1)) # restrict to PAPER band
+    fq, d = fq[valid], d[valid]
+    tau = np.fft.fftfreq(fq.size, fq[1]-fq[0])
+    window = a.dsp.gen_window(fq.size, WINDOW)
+    _d = np.fft.ifft(d)
+    _dw = np.fft.ifft(d*window) / window.mean() # compensate for window amplitude
+
+    if True: # approx account for 1st reflection of sky signal off of feed
+        _dw *= np.abs(_d[0])
+        _d *= np.abs(_d[0])
+
+    print np.abs(_d[0])
+    #plt.figure(1); plt.semilogy(fq, np.abs(d)**2, label=BASE)
+
+    #plt.figure(2)
+    #plt.semilogy(np.fft.fftshift(tau), np.fft.fftshift(np.abs(_d)**2))
+    #plt.semilogy(np.fft.fftshift(tau), np.fft.fftshift(np.abs(_dw)), label=BASE)
+    plt.semilogy(np.fft.fftshift(tau), np.fft.fftshift(np.abs(_dw)**2), label=BASE)
+
+#plt.figure(1); plt.legend(loc='best')
+#plt.figure(2)
+plt.xlim(-30,350)
[…]

### 2015-10-30 DishReflectometry/Paper1_v0.tex
Content updated after conversation with Aaron

@@
 Consider a two element interferometer with a baseline $b$ and antenna field pattern $A(\theta, \nu)$.
-If we denote the sky signal at an angle $\vec \theta$ by $V_{sky}(\theta)$ and the receiver noise of each element as $V_{rec}$ then the voltage output of each antenna may be written as,
+If we denote the sky signal at an angle $\vec \theta$ by $V_{sky}(\vec \theta, \nu)$ and the receiver noise of each element as $V_{rec}(\nu)$ then the voltage output of each antenna may be written as,
 \begin{equation}
-V_{1}(\vec \theta, \nu) = V_{sky}(\vec \theta,\nu)+V_{rec1}(\nu)
+V_{1}(\vec \theta, \nu) = A_{1}(\theta,\nu)V_{sky}(\vec \theta,\nu)(\nu)\nonumber\\
 \end{equation}
 \begin{equation}
-V_{2} (\vec \theta, \nu)= V_{sky}(\theta,\nu)exp({2\pi i \nu \vec{b}.\hat{s} \over c} )+V_{rec2}(\nu)
+V_{2} (\vec \theta, \nu)= A_{2}(\theta,\nu)V_{sky}(\theta,\nu)exp({2\pi i \nu \vec{b}.\hat{s} \over c} )(\nu)\nonumber\\
 \end{equation}
-where $\hat s$ is the unit vector along the direction of the baseline.
+where $\hat s$ is the unit vector along the direction of the baseline and $A_{1}(\theta,\nu)$ and $A_{2}(\theta,\nu)$ are the field pattern of the two antennas.
 Hence, the time averaged complex visibility integrated over all sky as measured by the interferometer may be written as,
@@
 \begin{equation}
-V e^{i\phi} = \left< \int A_{1}(\theta, \nu) V_{1}(\theta,\nu) A_{2}^{*}(\theta, \nu) V_{2}^{*} (\theta, \nu) exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right >
+V e^{i\phi}(\nu) =  \int  V_{1}(\theta,\nu)  V_{2}^{*} (\theta, \nu) exp(-{2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega 
+\label{eq1}
 \end{equation}
 
-Defining antenna power pattern as  $B(\theta,\nu)=A_{1}(\theta,\nu)A_{2}^{*}(\theta,\nu)$ and denote the sky power as  $P_{sky}=V_{sky}(\theta,\nu)V_{sky}^{*}(\theta,\nu) = |V_{sky}|^2$.
-Since $\left < V_{rec1}(\nu)V_{rec2}^{*}(\nu) = 0\right >$
+We define antenna cross power pattern as  $B(\theta,\nu)=A_{1}(\theta,\nu)A_{2}^{*}(\theta,\nu)$ and denote the sky power as  $V_{sky}(\theta,\nu)V_{sky}^{*}(\theta,\nu) = I_{sky}(\vec \theta, \nu)|^2$.
 Hence,
 \begin{eqnarray}
-V e^{i\phi} & = & \int B(\vec \theta, \nu) P_{sky}(\vec \theta,\nu) exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \nonumber\\
-		& = & \int B(l,m, \nu) P_{sky}(l,m,\nu) exp(2\pi i \nu \tau_{g} ) dl dm \nonumber\\
- 		& = & B(\vec u,\nu) \ast P_{sky}(\vec u,\nu ) \nonumber\\
-		& = & B(\nu { |\vec b| \over c} , \nu) \ast P_{sky}(\nu { |\vec b| \over c} , \nu) \nonumber\\
-		& = & B(\tau_{g}, \nu) \ast P_{sky}(\tau_{g} , \nu)	
+V e^{i\phi}(\nu) & = & \int B(\vec \theta, \nu) I_{sky}(\vec \theta,\nu) exp(-{2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \nonumber\\
+		& = & \int B(l,m, \nu) I_{sky}(l,m,\nu) exp(-2\pi i \nu \tau_{g} ) dl dm \nonumber\\
+ 	%	& = & B(\vec u,\nu) \ast P_{sky}(\vec u,\nu ) \nonumber\\
+	%	& = & B(\nu { |\vec b| \over c} , \nu) \ast P_{sky}(\nu { |\vec b| \over c} , \nu) \nonumber\\
+	%	& = & B(\tau_{g}, \nu) \ast P_{sky}(\tau_{g} , \nu)	
+\label{eq2}
 \end{eqnarray}
 
-i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum.
+%i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum.
 In other words, it is the convolution of the Fourier transform of the antenna power pattern with the Fourier transform of the sky.
 The complex visibility measured by an interferometer with a given baseline length has explicit dependence on frequency as well as implicit frequency dependence through the spatial frequency $\vec u = \nu { \vec b \over c}$ component.
-Since $\vec u $ is the
+Since $\vec u $ is the For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space.
+Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities.
+If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as,
+The Fourier transform of this visibility spectrum along the frequency axis results in the delay spctrum.
+\begin{eqnarray}
+\mathcal{F} \left [V e^{i\phi}\right] & = & \int \left [\int B(l,m, \nu) I_{sky}(l,m,\nu) exp(-2\pi i \nu \tau_{g} ) dl dm \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
+						%   & = & \int \left [B(\tau)\ast I_{sky}(\tau) \ast \delta(\tau+\tau_{g}) \right ] dl dm	
+\label{eq3}
+\end{eqnarray}
+
+Hence, the delay spectrum, integrated over all sky would be written as, 
+\begin{eqnarray}
+\mathcal{F} \left [V e^{i\phi}\right]   & = &  \left [B(\tau)\ast I_{sky}(\tau) \ast \delta(\tau+\tau_{g}) \right ] 	
+\label{eq4}
+\end{eqnarray}
+the convolution being carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$.
+In words, the sky delay spectrum is convoluted with the delay spectrum of the instrument and is centred at a delay $\tau_{g}$.
+The projected geometric delay $\tau_{g}$ for a given baseline can vary from 0 to $\tau_{g}$.
+Also, due to frequency dependence of the sky signal, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with delaying amplitude [Ref to the figure Parsons12].
+Sky delay spectrum $I_{sky}(\tau)$ is contributed by the foreground  $I_{fg}(\tau)$ and the 21~cm power spectrum $I_{21}(\tau)$.
+Since $I_{fg}$ is spectrally smooth, whereas $I_{21}$ contains spectral structures, for wideband measurements, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces at higher delays.
+
+\section{Effect of multiple reflections off the parabolic dish on the measured visibility}
+ Plane waves incident on a parabolic dish
+are focussed at the feed which is kept at the focal plane of the dish. The mismatch between the impedance of free space and the feed and transmission line results
+in a partial coupling of the sky signal into the feed while the rest is
+reflected off the feed.
+The reflected signal illuminates the dish and most of it is reflected back into the space.
+However, a part of it reflects back and forth several times in between the feed and the vertex of the dish which is shadowed by the feed (dashed blue arrows in Figure \ref{fig:cartoon}).
+Such reflections generate multiple copies of the incident sky signal of reduced strength at various time/phase delays and thus produces spurious correlations in the visibilities of
+interferometric data. In this section we compute the visibility of a two element interferometer accounting for the multiple reflections of the sky signal in between the feed and the dish vertex.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[totalheight=0.35\textheight]{plots/reflection_cartoon.png}
+\caption{The blue solid lines represent an original sky signal entering the
+feed. A small percentage of it (dashed blue) is reflected off the dish, and it
+is these reflections that we are concerned about. In our measurements however,
+the reflections measured contain most of the original pulse signal (solid red),
+so it is crucial to adjust for this difference in our analysis.}
+\label{fig:cartoon}
+\end{figure}
+
+We again consider a two element interferometer as described in section 2.
+Two antennas are assumed to be exactly identical so that their electrical parameters are same.
+we denote the voltage reflection coefficient of each feed by $\Gamma_{f}$.
+The voltage reflection coefficient of the reflector dish is denoted by $\Gamma_{d}$.
+Upon first incidence of the sky signal onto the dish, the entire sky signal would be reflected and focussed onto the feed.
+Hence, for first incidence $\Gamma_{d}=1$.
+Sky signal that would return to the dish after successive reflections off the feed and the dish is only reflected from a small area around the vertex of the dish and therefore, $\Gamma_{d}<1$.
+In our analysis, we consider one reflection of the sky power from the feed and subsequent reflection off the dish as one single reflection.
+If the focal length of the dish is $l$, assuming the feed is located at the focus, the roundtrip phase delay of a signal of frequency $\nu$ after first reflection will be $\Phi= 2\pi {\nu \over c } 2l$ and the corresponding time delay would be $\Delta tau$.
+
+\subsection{Visibility of a two element interferometer considering reflections to first order}
+Upon first incidence of the sky signal $V_{sky}$, $\Gamma_{f}$ fraction of the voltage is reflected off the feed while $(1-\Gamma_{f})$ fraction is coupled to the feed.
+The reflected voltage then further reflected off the dish and $(1-\Gamma_{f}) $ fraction of it reenters the feed with a phase delay $\Phi$.
+Hence, the net voltage at the output of the two antennas could be written as,
+\begin{eqnarray}
+V_{1} & = & A V_{sky}(1-\Gamma_{f}) + A V_{sky} \Gamma_{f} \Gamma_{d} e^{i\Phi} (1-\Gamma_{f})^{2}\nonumber\\
+         & = & A V_{sky} (1-\Gamma_{f}) \left [ 1+ (1-\Gamma_{a})\Gamma_{f} \Gamma_{d} e^{i\Phi} \right]\nonumber\\
+\label{eq4}
+\end{eqnarray}
+\begin{eqnarray}
+V_{2} & = & A V_{sky}(1-\Gamma_{f}) + A V_{sky} \Gamma_{f} \Gamma_{d} e^{i\Phi} (1-\Gamma_{f})^{2}exp({2\pi i \nu \vec{b}.\hat{s} \over c} )\nonumber\\
+         & = & A V_{sky} (1-\Gamma_{f}) \left [ 1+(1-\Gamma_{a}) \Gamma_{f} \Gamma_{d} e^{i\Phi} \right]exp({2\pi i \nu \vec{b}.\hat{s} \over c} )\nonumber\\
+\label{eq5}
+\end{eqnarray}
+Frequency as well as angular dependence of the quantities are not written explicitly for notational simplicity. 
+The two antennas are assumed to have identical beam pattern which is $A_{1}=A_{2} =A$.
+We also absorb the common gain term $(1-\Gamma_{f})$ with antenna response $A$ and denote them as $A_{f}= A(1-\Gamma_{f})$ here after.
+Hence, the complex visibility could be,
 
 \begin{eqnarray}
-\mathcal{F} \left [V e^{i\phi}\right] & = & \mathcal{F}\left [B(\vec u,\nu) \ast P_{sky}(\vec u,\nu) \right] \nonumber\\
-						   & = & B(\tau)P_{sky}(\tau)\nonumber\\
-						   & = & B(\nu { \vec b \over c}) 
+V e^{i\phi}(\nu) & = & \int V_{1}V_{2}^{*} d\Omega \nonumber\\
+		        & = & \int |A_{f}|^{2}|V_{sky}|^{2}\left [ 1+(1-\Gamma_{f}) \Gamma_{f} \Gamma_{d} e^{i\Phi} \right]|^{2} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega
+\label{eq6}		        
 \end{eqnarray}
 
-For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space.
-Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities.
-If we define the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as,
+ Furthermore, combining all the terms that contain instrument response we define a common instrument parameter, written as, 
+\begin{eqnarray}
+\Sigma(\vec \theta, \nu) & = & |A_{f}|^{2} |\left [ 1+ (1-\Gamma_{f}) \Gamma_{f} \Gamma_{d} e^{i\Phi} \right]|^{2}\nonumber\\
+ 	    & = &  |A_{f}|^{2}  \left[ 1+ |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} + 2 \Re \left ( (1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right) \right]
+\label{eq{7}}	    
+\end{eqnarray}
+
+First term in the square bracket represents the cross coorrelation between the two antenna outputs contributed by the sky signal upon first direct incidence.
+The second term results from the cross correlation between two reflected signals in each antenna.The last term represents the cross correlation between the first direct incident signal of one antenna and the first reflected signal from the other antenna and vice versa.
+If the dish vertex is so constructed such that the reflection from the dish vertex is negligible i.e, $\Gamma_{d}<<1\ or = 0$ then the second and the third term of the $\Sigma$ vanish. \\
+Rewriting equation \ref{eq6}, the visibility could be written as,
 
 \begin{eqnarray}
-\mathcal{F} \left [V e^{i\phi}\right] & = & \int \left [  \int B(l,m, \nu) P_{sky}(l,m,\nu) exp[2\pi i \nu \tau_{g}] dl dm\right ] exp\left[ 2 \pi i\nu \tau \right]d\nu \nonumber\\
-						   & = & \int B(\tau_{g}, \nu )\ast P_{sky}(\tau_{g}, \nu ) exp[2\pi i \nu \tau] d\nu\nonumber\\
-						   & = & B(\tau+\tau_{g})P_{sky}(\tau+\tau_{g}) \nonumber	
+V e^{i\phi}(\nu) & = & \int |A_{f}|^{2}|V_{sky}|^{2}|exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \nonumber\\
+&& +  \int |A_{f}|^{2}|V_{sky}|^{2} |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \nonumber\\
+&& + \int |A_{f}|^{2}|V_{sky}|^{2}| 2 \Re \left ((1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right)exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega
+\label{eq8}		        
 \end{eqnarray}
 
-Fourier transform of the
+Therefore, the total visibility at any frequency would be the sum of the three visibilities contributed by three sources of correlated power.
+If we assume $|\Gamma_{f}|^{2} = |\Gamma_{d}|^{2}= 10dB$,
+\subsection{Effect of multiple reflections on the delay spectrum}
+We define $B(\vec \theta, \nu) =  A^{2}(\vec \theta, \nu) $ as the beam power pattern of the interferometer and $\Sigma_{rr}(\nu), \Sigma_{dr}(\nu)$ are the correlation coefficient between the two reflected signals in each antenna and the direct signal of one antenna with the reflected signal from the other antenna in the uv plane i.e,
 
-There are several different sources of instrumental chromaticity for radio
-telescope systems that can result in non-ideal performances and unwanted
-systematic effects in measured data. One such source is the mismatch between
-the impedance of free space and the feed and transmission line, which results
-in a partial coupling of the sky signal into the feed while the rest is
-reflected back into the space. For any reflector telescope, such as HERA, this
-signal illuminates the dish and part of it reflects back and forth several
-times in between the dish feed and the vertex of the dish.  Such reflections
-generate multiple reduced strength copies of the incident sky signal at various
-delays, and this produces spurious correlations in the visibilities of
-interferometric data.
+\begin{equation}
+\Sigma_{rr}(\nu) =  \left [ |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} \right ]
+\end{equation}
+
+\begin{equation}
+\Sigma_{rr}(\nu) = \left [ 2 \Re \left ((1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right) \right]
+\end{equation}
+
+and $\Delta \tau$ is the additional delay each reflected component suffers in addition to the intrinsic geometric delay 
+$\tau_{g}$.
+
+As given in equation \ref{eq3}, the Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum.
+Hence, the all sky integrated delay spectrum could be written as,
+%\begin{eqnarray}
+%\mathcal{F} \left [V e^{i\phi}\right] & = & \int \left [\int B I_{sky}exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
+%&& + \int \left [  \int B I_{sky} \Sigma_{rr} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right] exp\left[ -2 \pi i\nu \tau \right] d\nu  \nonumber\\
+%&& +\int \left [ \int B I_{sky} \Sigma_{dr} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\	
+%&& + \int \left [  \int |A_{f}|^{2}|V_{sky}|^{2} |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right] exp\left[ -2 \pi i\nu \tau \right] d\nu  \nonumber\\
+%&& +\int \left [ \int |A_{f}|^{2}|V_{sky}|^{2} 2 \Re \left ((1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right)exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
+%			& = & \int \left [\int B I_{sky} exp({2\pi i \nu \tau_{g}} ) dl dm \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
+%&& + \int \left [  \int B I_{sky} \Sigma_{rr} exp({2\pi i \nu \tau_{g}} ) dl dm \right] exp\left[ -2 \pi i\nu \tau \right] d\nu  \nonumber\\
+%&& +\int \left [ \int B I_{sky} \Sigma_{dr} exp({2\pi i \nu \tau_{g}} ) dl dm \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
+%\label{eq9}
+%\end{eqnarray}
+%
+he all sky integrated delay spectrum could be written as, 
+\begin{eqnarray}			
+\mathcal{F} \left [V e^{i\phi}\right] & = & \left [ B(\tau)\ast I_{sky}(\tau) \right ]\ast \delta(\tau_{g}) \nonumber\\
+		&& +  \left [ B_{f}(\tau)\ast I_{sky}(\tau)* \Sigma_{rr}( \tau) \right ]\ast \delta(\tau+\tau_{g}) \nonumber\\
+		&& +  \left [B_{f}(\tau)\ast I_{sky}(\tau)* \Sigma_{dr}( \tau) \right ]\ast \delta(\tau+\tau_{g}+ \Delta \tau)\nonumber\\
+\label{eq10}
+\end{eqnarray}
+
+ In words, the Fourier transform of the visibility contributed by any two voltage components from two antennas with no mutual delay is centred at a delay $\tau = \tau_{g}$ in the delay spectrum whereas any two voltage components from two antennas components having a mutual delay of $\Delta \tau$ will be centred at $\tau +\Delta \tau$.
+
+Quantitatively, if the incident power from the sky signal is $I_{sky}$, the feed
+reflection coefficient is $\Gamma_{f}$, and the dish reflection
+coefficient is $\Gamma_{d}$, then the net power entering the feed after an
+$n^{th}$ reflection off the feed and the dish is:
 
@@
 
-\section{Theory}{\label{sec:theory}}
-\begin{figure}[ht!]
-\centering
-\includegraphics[totalheight=0.35\textheight]{plots/reflection_cartoon.png}
-\caption{The blue solid lines represent an original sky signal entering the
-feed. A small percentage of it (dashed blue) is reflected off the dish, and it
-is these reflections that we are concerned about. In our measurements however,
-the reflections measured contain most of the original pulse signal (solid red),
-so it is crucial to adjust for this difference in our analysis.}
-\label{fig:cartoon}
-\end{figure}
-
 Plane waves incident on a parabolic dish
@@
 
-Quantitatively, if the incident power from the sky signal is $P_{sky}$, the feed
+Quantitatively, if the incident power from the sky signal is $I_{sky}$, the feed
 reflection coefficient is $\Gamma_{f}$, and the dish reflection
@@
 
-\bibitem[Pasrons \& Backer(2009)]{ParsonsBacker2009}
+\bibitem[Parsons \& Backer(2009)]{ParsonsBacker2009}
 Parsons, A., \& Backer, D. 2009, \apj, 138, 219

### 2015-10-31 DishReflectometry/Paper1_v0.tex
Content updated after conversation with Aaron2

@@
 The projected geometric delay $\tau_{g}$ for a given baseline can vary from 0 to $\tau_{g}$.
-Also, due to frequency dependence of the sky signal, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with delaying amplitude [Ref to the figure Parsons12].
+Also, due to frequency dependence of the sky signal, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with decaying amplitude [Ref to the figure Parsons12].
 Sky delay spectrum $I_{sky}(\tau)$ is contributed by the foreground  $I_{fg}(\tau)$ and the 21~cm power spectrum $I_{21}(\tau)$.
-Since $I_{fg}$ is spectrally smooth, whereas $I_{21}$ contains spectral structures, for wideband measurements, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces at higher delays.
+Since $I_{fg}$ is spectrally smooth, whereas $I_{21}$ contains spectral structures, for wideband measurements, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces at higher delays and, therefore, at higher delays, the 21~cm delay spectrum is detectable.
+\textbf{[ Reference to Nithya's foreground simulation work, reference to any plots on the relative contribution of the  foreground and EoR signal.
+]}
 
-\section{Effect of multiple reflections off the parabolic dish on the measured visibility}
- Plane waves incident on a parabolic dish
-are focussed at the feed which is kept at the focal plane of the dish. The mismatch between the impedance of free space and the feed and transmission line results
-in a partial coupling of the sky signal into the feed while the rest is
-reflected off the feed.
+\section{Effects of multiple reflections of the sky signal between the parabolic dish and the feed on the measured visibility}
+ Plane waves incident on a parabolic dish are focussed at the feed which is kept at the focal plane of the dish.
+The mismatch between the impedance of free space and the feed and transmission line results in a partial coupling of the sky signal into the feed while the rest is reflected off the feed.
 The reflected signal illuminates the dish and most of it is reflected back into the space.
 However, a part of it reflects back and forth several times in between the feed and the vertex of the dish which is shadowed by the feed (dashed blue arrows in Figure \ref{fig:cartoon}).
-Such reflections generate multiple copies of the incident sky signal of reduced strength at various time/phase delays and thus produces spurious correlations in the visibilities of
-interferometric data. In this section we compute the visibility of a two element interferometer accounting for the multiple reflections of the sky signal in between the feed and the dish vertex.
+Such reflections generate multiple copies of the incident sky signal of reduced strength at various time/phase and thus produces spurious correlations in the visibilities of interferometric data.
+In this section we compute the visibility of a two element interferometer accounting for the additional reflections of the sky signal in between the feed and the dish vertex and the corresponding effects on the delay spectrum.
 
@@
 
-We again consider a two element interferometer as described in section 2.
+Consider again a two element interferometer as described in section 2.
 Two antennas are assumed to be exactly identical so that their electrical parameters are same.
-we denote the voltage reflection coefficient of each feed by $\Gamma_{f}$.
+We denote the voltage reflection coefficient of each feed by $\Gamma_{f}$.
 The voltage reflection coefficient of the reflector dish is denoted by $\Gamma_{d}$.
@@
 In our analysis, we consider one reflection of the sky power from the feed and subsequent reflection off the dish as one single reflection.
-If the focal length of the dish is $l$, assuming the feed is located at the focus, the roundtrip phase delay of a signal of frequency $\nu$ after first reflection will be $\Phi= 2\pi {\nu \over c } 2l$ and the corresponding time delay would be $\Delta tau$.
+If the focal length of the dish is $l$, assuming the feed is located at the focus, the roundtrip delay after first reflection will be $\Delta \tau = {2l \over c}$.
 
@@
 \begin{eqnarray}
-V_{1} & = & A V_{sky}(1-\Gamma_{f}) + A V_{sky} \Gamma_{f} \Gamma_{d} e^{i\Phi} (1-\Gamma_{f})^{2}\nonumber\\
-         & = & A V_{sky} (1-\Gamma_{f}) \left [ 1+ (1-\Gamma_{a})\Gamma_{f} \Gamma_{d} e^{i\Phi} \right]\nonumber\\
+V_{1} & = & A V_{sky}(1-\Gamma_{f}) + A V_{sky} \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau}  (1-\Gamma_{f})^{2}\nonumber\\
+         & = & A V_{sky} (1-\Gamma_{f}) \left [ 1+ (1-\Gamma_{a})\Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau} \right]\nonumber\\
 \label{eq4}
@@
 \begin{eqnarray}
-V_{2} & = & A V_{sky}(1-\Gamma_{f}) + A V_{sky} \Gamma_{f} \Gamma_{d} e^{i\Phi} (1-\Gamma_{f})^{2}exp({2\pi i \nu \vec{b}.\hat{s} \over c} )\nonumber\\
-         & = & A V_{sky} (1-\Gamma_{f}) \left [ 1+(1-\Gamma_{a}) \Gamma_{f} \Gamma_{d} e^{i\Phi} \right]exp({2\pi i \nu \vec{b}.\hat{s} \over c} )\nonumber\\
+V_{2} & = & A V_{sky}(1-\Gamma_{f}) + A V_{sky} \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau} (1-\Gamma_{f})^{2}exp({2\pi i \nu \vec{b}.\hat{s} \over c} )\nonumber\\
+         & = & A V_{sky} (1-\Gamma_{f}) \left [ 1+(1-\Gamma_{a}) \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau}  \right]exp({2\pi i \nu \vec{b}.\hat{s} \over c} )\nonumber\\
 \label{eq5}
@@
 V e^{i\phi}(\nu) & = & \int V_{1}V_{2}^{*} d\Omega \nonumber\\
-		        & = & \int |A_{f}|^{2}|V_{sky}|^{2}\left [ 1+(1-\Gamma_{f}) \Gamma_{f} \Gamma_{d} e^{i\Phi} \right]|^{2} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega
+		        & = & \int |A_{f}|^{2}|V_{sky}|^{2} |\left [ 1+(1-\Gamma_{f}) \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau}  \right]|^{2} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega
 \label{eq6}		        
@@
 \begin{eqnarray}
-\Sigma(\vec \theta, \nu) & = & |A_{f}|^{2} |\left [ 1+ (1-\Gamma_{f}) \Gamma_{f} \Gamma_{d} e^{i\Phi} \right]|^{2}\nonumber\\
- 	    & = &  |A_{f}|^{2}  \left[ 1+ |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} + 2 \Re \left ( (1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right) \right]
+\Sigma(\vec \theta, \nu) & = & |A_{f}|^{2} |\left [ 1+ (1-\Gamma_{f}) \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau} \right]|^{2}\nonumber\\
+ 	    & = &  |A_{f}|^{2}  \left[ 1+ |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} + 2 \Re \left ( (1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{2\pi i\nu \Delta \tau} \right) \right]
 \label{eq{7}}	    
@@
 
+Therefore, the total visibility at any frequency would be the sum of the three visibilities contributed by three sources of correlated power.
 First term in the square bracket represents the cross coorrelation between the two antenna outputs contributed by the sky signal upon first direct incidence.
@@
 If the dish vertex is so constructed such that the reflection from the dish vertex is negligible i.e, $\Gamma_{d}<<1\ or = 0$ then the second and the third term of the $\Sigma$ vanish. \\
-Rewriting equation \ref{eq6}, the visibility could be written as,
 
-\begin{eqnarray}
-V e^{i\phi}(\nu) & = & \int |A_{f}|^{2}|V_{sky}|^{2}|exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \nonumber\\
-&& +  \int |A_{f}|^{2}|V_{sky}|^{2} |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \nonumber\\
-&& + \int |A_{f}|^{2}|V_{sky}|^{2}| 2 \Re \left ((1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right)exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega
-\label{eq8}		        
-\end{eqnarray}
+%\begin{eqnarray}
+%V e^{i\phi}(\nu) & = & \int |A_{f}|^{2}|V_{sky}|^{2}|exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \nonumber\\
+%&& +  \int |A_{f}|^{2}|V_{sky}|^{2} |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \nonumber\\
+%&& + \int |A_{f}|^{2}|V_{sky}|^{2}| 2 \Re \left ((1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right)exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega
+%\label{eq8}		        
+%\end{eqnarray}
 
-Therefore, the total visibility at any frequency would be the sum of the three visibilities contributed by three sources of correlated power.
-If we assume $|\Gamma_{f}|^{2} = |\Gamma_{d}|^{2}= 10dB$,
-\subsection{Effect of multiple reflections on the delay spectrum}
+\subsection{Effect of first reflection on the delay spectrum}
 We define $B(\vec \theta, \nu) =  A^{2}(\vec \theta, \nu) $ as the beam power pattern of the interferometer and $\Sigma_{rr}(\nu), \Sigma_{dr}(\nu)$ are the correlation coefficient between the two reflected signals in each antenna and the direct signal of one antenna with the reflected signal from the other antenna in the uv plane i.e,
@@
 and $\Delta \tau$ is the additional delay each reflected component suffers in addition to the intrinsic geometric delay 
-$\tau_{g}$.
+$\tau_{g}$. Therefore, $\Sigma(\vec \theta, \nu) = B(\vec \theta, \nu) \left [ 1+\Sigma_{rr} +\Sigma_{dr} \right]$
 
@@
 %
-he all sky integrated delay spectrum could be written as, 
 \begin{eqnarray}			
-\mathcal{F} \left [V e^{i\phi}\right] & = & \left [ B(\tau)\ast I_{sky}(\tau) \right ]\ast \delta(\tau_{g}) \nonumber\\
-		&& +  \left [ B_{f}(\tau)\ast I_{sky}(\tau)* \Sigma_{rr}( \tau) \right ]\ast \delta(\tau+\tau_{g}) \nonumber\\
-		&& +  \left [B_{f}(\tau)\ast I_{sky}(\tau)* \Sigma_{dr}( \tau) \right ]\ast \delta(\tau+\tau_{g}+ \Delta \tau)\nonumber\\
+\mathcal{F} \left [V e^{i\phi}\right] & = & \left [ B(\tau)\ast I_{sky}(\tau) \right ]\ast \delta(\tau+\tau_{g}) \nonumber\\
+		&& +  \left [ B(\tau)\ast I_{sky}(\tau)* \Sigma_{rr}( \tau) \right ]\ast \delta(\tau+\tau_{g}) \nonumber\\
+		&& +  \left [B(\tau)\ast I_{sky}(\tau)* \Sigma_{dr}( \tau) \right ]\ast \delta(\tau+\tau_{g}+ \Delta \tau)\nonumber\\
 \label{eq10}

### 2015-10-31 DishReflectometry/Paper1_v0.tex
Content updated after conversation with Aaron2

@@
 The second term results from the cross correlation between two reflected signals in each antenna.The last term represents the cross correlation between the first direct incident signal of one antenna and the first reflected signal from the other antenna and vice versa.
-If the dish vertex is so constructed such that the reflection from the dish vertex is negligible i.e, $\Gamma_{d}<<1\ or = 0$ then the second and the third term of the $\Sigma$ vanish. \\
+If the dish vertex is so constructed such that the reflection from the dish vertex is negligible i.e, $\Gamma_{d}<<1\ or = 0$ then the second and the third term of the $\Sigma$ vanish.
+Also, since the net system response function changes due reflection, the delay spectrum also alters.\\
 
@@
 \subsection{Effect of first reflection on the delay spectrum}
-We define $B(\vec \theta, \nu) =  A^{2}(\vec \theta, \nu) $ as the beam power pattern of the interferometer and $\Sigma_{rr}(\nu), \Sigma_{dr}(\nu)$ are the correlation coefficient between the two reflected signals in each antenna and the direct signal of one antenna with the reflected signal from the other antenna in the uv plane i.e,
+We define $B(\vec \theta, \nu) =  A^{2}(\vec \theta, \nu) $ as the cross power pattern of the interferometer and $\Sigma_{rr}(\nu), \Sigma_{dr}(\nu)$ are the correlation coefficient between the two reflected signals in each antenna and the direct signal of one antenna with the reflected signal from the other antenna in the uv plane i.e,
 
@@
 \begin{equation}
-\Sigma_{rr}(\nu) = \left [ 2 \Re \left ((1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right) \right]
+\Sigma_{dr}(\nu) = \left [ 2 \Re \left ((1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right) \right]
 \end{equation}
@@
 
- In words, the Fourier transform of the visibility contributed by any two voltage components from two antennas with no mutual delay is centred at a delay $\tau = \tau_{g}$ in the delay spectrum whereas any two voltage components from two antennas components having a mutual delay of $\Delta \tau$ will be centred at $\tau +\Delta \tau$.
+ In words, the Fourier transform of the visibility contributed by any two voltage components from two antennas with no mutual delay is centred at a delay $\tau = \tau_{g}$ in the delay spectrum whereas any two voltage components from two antennas components having a mutual delay of $\Delta \tau$ will be centred at $\tau_{g} +\Delta \tau$.
+The correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal thus extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected.
+Also, any reflections arriving at the feed at any non-zero  value of the delay $\Delta \tau$ which could be the result of reflections from the feed structures would generate non zero delay response at those delays.
 
-Quantitatively, if the incident power from the sky signal is $I_{sky}$, the feed
-reflection coefficient is $\Gamma_{f}$, and the dish reflection
-coefficient is $\Gamma_{d}$, then the net power entering the feed after an
-$n^{th}$ reflection off the feed and the dish is:
+\subsection{Effect of higher order reflection on the delay spectrum} 
+Correlation between the higher order reflections of the signal in any antenna with the direct component of the other would result in a delay response at integral multiple of $\Delta \tau$ and vice versa.
+If $I_{sky}$ is reflected n times in between the feed and the dish, the net voltage entering the feed after an
+$n^{th}$ reflection off the feed and the dish is written as:
+\begin{equation}
+V_{1} =  A V_{sky}(1-\Gamma_{f})[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
+\end{equation}
+and,
+
+\begin{equation}
+V_{2} = A V_{sky}(1-\Gamma_{f})[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
+\end{equation}
+
+The relevant terms in the corresponding delay spectrum would be the one represents the correlation between the direct component of one antenna with the reflected components of the other resulting in higher order terms  in $\Sigma_{dr}$.
+Hence, $\Sigma_{dr}$ could be written as,
+
+\begin{equation}
+\Sigma_{dr}(\nu) = \left [ 2 \Re \left [(1-\Gamma_{f})[ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi} \right ] \right ]
+\end{equation}
+
+\begin{eqnarray}
+V e^{i\phi}(\nu) & = & \int V_{1}V_{2}^{*} d\Omega \nonumber\\
+		        & = & \int |A_{f}|^{2}|V_{sky}|^{2} |\left [ 1+(1-\Gamma_{f}) \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau}  \right]|^{2} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega
+\label{eq6}		        
+\end{eqnarray}
 

### 2015-11-02 DishReflectometry/Paper1_v0.tex
Monday update

--- 2015-10-31 DishReflectometry/Paper1_v0.tex
@@
 
-\subsection{Visibility of a two element interferometer considering reflections to first order}
+\subsection{Effect of first order reflections on visibility and delay spectrum}
 Upon first incidence of the sky signal $V_{sky}$, $\Gamma_{f}$ fraction of the voltage is reflected off the feed while $(1-\Gamma_{f})$ fraction is coupled to the feed.
-The reflected voltage then further reflected off the dish and $(1-\Gamma_{f}) $ fraction of it reenters the feed with a phase delay $\Phi$.
+The reflected voltage then further reflected off the dish and $(1-\Gamma_{f}) $ fraction of it reenters the feed with a roundtrip time delay $\Delta \tau$.
 Hence, the net voltage at the output of the two antennas could be written as,
@@
 
-Therefore, the total visibility at any frequency would be the sum of the three visibilities contributed by three sources of correlated power.
-First term in the square bracket represents the cross coorrelation between the two antenna outputs contributed by the sky signal upon first direct incidence.
+Instrumental response function acquires additional terms arising due to correlation between the directed and reflected component of the sky signal.
+The total visibility at any frequency would be the sum of the three visibilities contributed by three sources of correlated power.
+First term in the square bracket represents the cross correlation between the two antenna outputs contributed by the sky signal upon first direct incidence.
 The second term results from the cross correlation between two reflected signals in each antenna.The last term represents the cross correlation between the first direct incident signal of one antenna and the first reflected signal from the other antenna and vice versa.
-If the dish vertex is so constructed such that the reflection from the dish vertex is negligible i.e, $\Gamma_{d}<<1\ or = 0$ then the second and the third term of the $\Sigma$ vanish. \\
+
+Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum. 
+ Fourier transform of the visibility contributed by any two voltage components from two antennas with no mutual delay is centred at a delay $\tau = \tau_{g}$ in the delay spectrum whereas any two voltage components from two antennas components having a mutual delay of $\Delta \tau$ will be centred at $\tau_{g} +\Delta \tau$.
+Therefore, the correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal thus extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected.
+Also, any reflections arriving at the feed at any non-zero  value of the delay $\Delta \tau$ which could be the result of reflections from the feed structures would also generate non zero delay response at those delays.
+If the dish vertex is so constructed such that the reflection from the dish vertex is negligible i.e, $\Gamma_{d}<<1\ or = 0$ then the second and the third term of the $\Sigma$ vanish.
+Also, if we assume a $\Gamma_{a} =-10dB$ and $\Gamma_{d}= -20dB$, the second term in the expression of $\Sigma(\vec \theta, \nu)$ becomes negligible compared to the first and the third term of the expression and, therefore, can be neglected.
+\\
 
@@
 
-\subsection{Effect of first reflection on the delay spectrum}
-We define $B(\vec \theta, \nu) =  A^{2}(\vec \theta, \nu) $ as the beam power pattern of the interferometer and $\Sigma_{rr}(\nu), \Sigma_{dr}(\nu)$ are the correlation coefficient between the two reflected signals in each antenna and the direct signal of one antenna with the reflected signal from the other antenna in the uv plane i.e,
+%\subsection{Effect of first reflection on the delay spectrum}
+%We define $B(\vec \theta, \nu) =  A^{2}(\vec \theta, \nu) $ as the cross power pattern of the interferometer and $\Sigma_{rr}(\nu), \Sigma_{dr}(\nu)$ are the correlation coefficient between the two reflected signals in each antenna and the direct signal of one antenna with the reflected signal from the other antenna in the uv plane i.e,
 
-\begin{equation}
-\Sigma_{rr}(\nu) =  \left [ |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} \right ]
-\end{equation}
+%\begin{equation}
+%\Sigma_{rr}(\nu) =  \left [ |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} \right ]
+%\end{equation}
 
-\begin{equation}
-\Sigma_{rr}(\nu) = \left [ 2 \Re \left ((1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right) \right]
-\end{equation}
+%\begin{equation}
+%\Sigma_{dr}(\nu) = \left [ 2 \Re \left ((1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right) \right]
+%\end{equation}
 
-and $\Delta \tau$ is the additional delay each reflected component suffers in addition to the intrinsic geometric delay 
-$\tau_{g}$. Therefore, $\Sigma(\vec \theta, \nu) = B(\vec \theta, \nu) \left [ 1+\Sigma_{rr} +\Sigma_{dr} \right]$
+%and $\Delta \tau$ is the additional delay each reflected component suffers in addition to the intrinsic geometric delay 
+%$\tau_{g}$. Therefore, $\Sigma(\vec \theta, \nu) = B(\vec \theta, \nu) \left [ 1+\Sigma_{rr} +\Sigma_{dr} \right]$
 
-As given in equation \ref{eq3}, the Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum.
+%As given in equation \ref{eq3}, the Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum.
 Hence, the all sky integrated delay spectrum could be written as,
@@
 %
+%\begin{eqnarray}			
+%\mathcal{F} \left [V e^{i\phi}\right] & = & \left [ B(\tau)\ast I_{sky}(\tau) \right ]\ast \delta(\tau+\tau_{g}) \nonumber\\
+%		&& +  \left [ B(\tau)\ast I_{sky}(\tau)* \Sigma_{rr}( \tau) \right ]\ast \delta(\tau+\tau_{g}) \nonumber\\
+%		&& +  \left [B(\tau)\ast I_{sky}(\tau)* \Sigma_{dr}( \tau) \right ]\ast \delta(\tau+\tau_{g}+ \Delta \tau)\nonumber\\
+%\label{eq10}
+%\end{eqnarray}
+
+ %In words, the Fourier transform of the visibility contributed by any two voltage components from two antennas with no mutual delay is centred at a delay $\tau = \tau_{g}$ in the delay spectrum whereas any two voltage components from two antennas components having a mutual delay of $\Delta \tau$ will be centred at $\tau_{g} +\Delta \tau$.
+The correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal thus extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected.
+Also, any reflections arriving at the feed at any non-zero  value of the delay $\Delta \tau$ which could be the result of reflections from the feed structures would generate non zero delay response at those delays.
+
+\subsection{Effect of higher order reflection on the delay spectrum} 
+Correlation between the higher order reflections of the signal in any antenna with the direct component of the other would result in a delay response at integral multiple of $\Delta \tau$ and vice versa.
+If $I_{sky}$ is reflected n times in between the feed and the dish, the net voltage entering the feed after an
+$n^{th}$ reflection off the feed and the dish is written as:
+\begin{equation}
+V_{1} =  A V_{sky}(1-\Gamma_{f})[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
+\end{equation}
+and,
+
+\begin{equation}
+V_{2} = A V_{sky}(1-\Gamma_{f})[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
+\end{equation}
+
+where $\Phi = 2\pi\nu\Delta \tau$.
+The relevant terms in the corresponding visibility and subsequently in the delay spectrum would be the ones which represent the correlation between the direct component of one antenna with the reflected components of the other resulting in higher order terms  in $\Sigma(\vec \theta, \nu)$.
+The corresponding instrument response may be written as,
+
+\begin{equation}
+\Sigma(\vec \theta, \nu) = A_{f} \left [ 1+ 2 \Re \left [(1-\Gamma_{f})( \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}) \right ]\right ]
+\end{equation}
+
 \begin{eqnarray}
-\mathcal{F} \left [V e^{i\phi}\right] & = & \left [ B(\tau)\ast I_{sky}(\tau) \right ]\ast \delta(\tau+\tau_{g}) \nonumber\\
-		&& +  \left [ B(\tau)\ast I_{sky}(\tau)* \Sigma_{rr}( \tau) \right ]\ast \delta(\tau+\tau_{g}) \nonumber\\
-		&& +  \left [B(\tau)\ast I_{sky}(\tau)* \Sigma_{dr}( \tau) \right ]\ast \delta(\tau+\tau_{g}+ \Delta \tau)\nonumber\\
-\label{eq10}
+V e^{i\phi}(\nu) & = & \int V_{1}V_{2}^{*} d\Omega \nonumber\\
+		        & = & \int |A_{f}|^{2}|V_{sky}|^{2} |\left [ 1+(1-\Gamma_{f}) \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau}  \right]|^{2} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega
+\label{eq6}		        
 \end{eqnarray}
-
- In words, the Fourier transform of the visibility contributed by any two voltage components from two antennas with no mutual delay is centred at a delay $\tau = \tau_{g}$ in the delay spectrum whereas any two voltage components from two antennas components having a mutual delay of $\Delta \tau$ will be centred at $\tau +\Delta \tau$.
-
-Quantitatively, if the incident power from the sky signal is $I_{sky}$, the feed
-reflection coefficient is $\Gamma_{f}$, and the dish reflection
-coefficient is $\Gamma_{d}$, then the net power entering the feed after an
-$n^{th}$ reflection off the feed and the dish is:
 

### 2015-11-02 DishReflectometry/Paper1_v0.tex
Monday update2

@@
 
-\section{Effects of multiple reflections of the sky signal between the parabolic dish and the feed on the measured visibility}
+\section{Effects of additional reflections of the sky signal between the parabolic dish and the feed on the measured visibility}
  Plane waves incident on a parabolic dish are focussed at the feed which is kept at the focal plane of the dish.
@@
 
-%\begin{eqnarray}
-%V e^{i\phi}(\nu) & = & \int |A_{f}|^{2}|V_{sky}|^{2}|exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \nonumber\\
-%&& +  \int |A_{f}|^{2}|V_{sky}|^{2} |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \nonumber\\
-%&& + \int |A_{f}|^{2}|V_{sky}|^{2}| 2 \Re \left ((1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right)exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega
-%\label{eq8}		        
-%\end{eqnarray}
-
-%\subsection{Effect of first reflection on the delay spectrum}
-%We define $B(\vec \theta, \nu) =  A^{2}(\vec \theta, \nu) $ as the cross power pattern of the interferometer and $\Sigma_{rr}(\nu), \Sigma_{dr}(\nu)$ are the correlation coefficient between the two reflected signals in each antenna and the direct signal of one antenna with the reflected signal from the other antenna in the uv plane i.e,
-
-%\begin{equation}
-%\Sigma_{rr}(\nu) =  \left [ |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} \right ]
-%\end{equation}
-
-%\begin{equation}
-%\Sigma_{dr}(\nu) = \left [ 2 \Re \left ((1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right) \right]
-%\end{equation}
-
-%and $\Delta \tau$ is the additional delay each reflected component suffers in addition to the intrinsic geometric delay 
-%$\tau_{g}$. Therefore, $\Sigma(\vec \theta, \nu) = B(\vec \theta, \nu) \left [ 1+\Sigma_{rr} +\Sigma_{dr} \right]$
-
-%As given in equation \ref{eq3}, the Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum.
-Hence, the all sky integrated delay spectrum could be written as,
-%\begin{eqnarray}
-%\mathcal{F} \left [V e^{i\phi}\right] & = & \int \left [\int B I_{sky}exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
-%&& + \int \left [  \int B I_{sky} \Sigma_{rr} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right] exp\left[ -2 \pi i\nu \tau \right] d\nu  \nonumber\\
-%&& +\int \left [ \int B I_{sky} \Sigma_{dr} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\	
-%&& + \int \left [  \int |A_{f}|^{2}|V_{sky}|^{2} |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right] exp\left[ -2 \pi i\nu \tau \right] d\nu  \nonumber\\
-%&& +\int \left [ \int |A_{f}|^{2}|V_{sky}|^{2} 2 \Re \left ((1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right)exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
-%			& = & \int \left [\int B I_{sky} exp({2\pi i \nu \tau_{g}} ) dl dm \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
-%&& + \int \left [  \int B I_{sky} \Sigma_{rr} exp({2\pi i \nu \tau_{g}} ) dl dm \right] exp\left[ -2 \pi i\nu \tau \right] d\nu  \nonumber\\
-%&& +\int \left [ \int B I_{sky} \Sigma_{dr} exp({2\pi i \nu \tau_{g}} ) dl dm \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
-%\label{eq9}
-%\end{eqnarray}
-%
-%\begin{eqnarray}			
-%\mathcal{F} \left [V e^{i\phi}\right] & = & \left [ B(\tau)\ast I_{sky}(\tau) \right ]\ast \delta(\tau+\tau_{g}) \nonumber\\
-%		&& +  \left [ B(\tau)\ast I_{sky}(\tau)* \Sigma_{rr}( \tau) \right ]\ast \delta(\tau+\tau_{g}) \nonumber\\
-%		&& +  \left [B(\tau)\ast I_{sky}(\tau)* \Sigma_{dr}( \tau) \right ]\ast \delta(\tau+\tau_{g}+ \Delta \tau)\nonumber\\
-%\label{eq10}
-%\end{eqnarray}
-
- %In words, the Fourier transform of the visibility contributed by any two voltage components from two antennas with no mutual delay is centred at a delay $\tau = \tau_{g}$ in the delay spectrum whereas any two voltage components from two antennas components having a mutual delay of $\Delta \tau$ will be centred at $\tau_{g} +\Delta \tau$.
-The correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal thus extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected.
-Also, any reflections arriving at the feed at any non-zero  value of the delay $\Delta \tau$ which could be the result of reflections from the feed structures would generate non zero delay response at those delays.
-
 \subsection{Effect of higher order reflection on the delay spectrum} 
@@
 
-\begin{eqnarray}
-V e^{i\phi}(\nu) & = & \int V_{1}V_{2}^{*} d\Omega \nonumber\\
-		        & = & \int |A_{f}|^{2}|V_{sky}|^{2} |\left [ 1+(1-\Gamma_{f}) \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau}  \right]|^{2} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega
-\label{eq6}		        
-\end{eqnarray}
+and the measured visibility spectrum, integrated over all sky would be, 
+\begin{equation}\label{eqn:series1}
+V_{meas}  = I_{sky}A_{f}\Sigma( \nu)
+\end{equation}
 
-To first order, the design specification of HERA elements requires that any
-delayed signal, arriving at the feed after a multipath propagation, should be
+The design specification of HERA elements requires that any
+signal, arriving at the feed at a delay $\Delta \tau$ with respect to the direct incidence, should be
 at the level of $-60dB$ at a delay of $60ns$ relative to the first incident
@@
 foreground signals, which is estimated to be six orders of magnitude fainter
-\citep{santos_et_al2005,ali_et_al2008,deoliveira2008,jelic_et_al2008,bernardi_et_al2009,bernardi_et_al2010,ghosh_et_al2011}.
-Additionally, the $14m$ HERA baselines set a foreground containing
+\citep{santos_et_al2005,ali_et_al2008,deoliveira2008,jelic_et_al2008,bernardi_et_al2009,bernardi_et_al2010,ghosh_et_al2011}. Additionally, the $14m$ HERA baselines set a foreground containing
 horizon-limit (the wedge) that, with some buffer, sets a delay specification of
@@
 \citep{parsons_et_al2012b,vedantham_et_al2012,nithya_et_al2013,liu_et_al2014a,liu_et_al2014b}.
-
-We carry out reflectometry measurements at the HERA element prototype in Green
-Bank, WV (Figure \ref{fig:heradish}) in order to understand the nature of feed
-reflections in the dish and characterize its performance. As HERA progresses as
-an experiment, it is necessary to build optimized dishes that aim to minimize the
+Our goal is to determine the effect of the instrument response $\Sigma(\nu)$ on the delay spectrum measurement.
+\section{Measurements}
+We carried out reflectometry measurements at the HERA element prototype in Green
+Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise its performance. As HERA progresses as
+an experiment, it is necessary to build optimised dishes that aim to minimise the
 challenges of chromaticity in our quest for the Epoch of Reionization.
 
-Plane waves incident on a parabolic dish
-are focussed at the feed with focal height $l$. For a well-designed feed, one
-that closely matches the impedance of free space\footnote{The impedance of free space
-is $Z_{0} = \mu_{0}c_{0} = \frac{1}{\epsilon_{0}c_{0}} \approx 377\Omega $.},
-most of the signal will enter the system while only
-a small percentage will be reflected back towards the dish for a secondary
-reflection into the feed (dashed blue arrows in Figure \ref{fig:cartoon}). In the
-following discussion, we consider a reflection off the feed and the
-subsequent reflection off the dish as one reflection.
-
-Quantitatively, if the incident power from the sky signal is $I_{sky}$, the feed
+As given in the previous section, if the incident power from the sky signal is $I_{sky}$, the feed
 reflection coefficient is $\Gamma_{f}$, and the dish reflection
-coefficient is $\Gamma_{d}$, then the net power entering the feed after an
-$n^{th}$ reflection off the feed and the dish is:
+coefficient is $\Gamma_{d}$, then the net power entering the feed after
+$n^{th}$ reflection off the feed and the dish (i.e, the sky integrated visibility spectrum) is:
 
 \begin{equation}\label{eqn:series1}
-P_{in} =  P_{sky}(1-\Gamma_{f})[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
+I_{meas} =  I_{sky}A_{f}[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
 \end{equation}
 
-where, $\phi = 2l({2\pi \over c})\nu$ is the propagation delay of a lightwave of frequency $\nu$ due to a reflection over a focal distance $l$.
+where, $\phi = 2\pi i\nu \Delta \tau$ is the roundtrip propagation delay of a lightwave of frequency $\nu$ due to a reflection over the focal distance $l$.
 It is noted that upon the first incidence, the sky signal is focussed onto the feed from the entire dish and the dish reflection coefficient $\Gamma_{d}$ is $1$ for this first incidence.
@@
 \begin{eqnarray}\label{eqn:ratio1}
-{P_{in} \over P_{sky} } & = & (1-\Gamma_{f})[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}] \nonumber\\
-      & = & (1-\Gamma_{f}) \displaystyle\sum\limits_{n=0}^{n} [\Gamma_{f}\Gamma_{d}e^{i \phi}]^{n}\nonumber\\
-      & = & (1-\Gamma_{f})+(1-\Gamma_{f}) \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i \phi}]^{n}
+{I_{in} \over I_{sky} } & = & A_{f}[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}] \nonumber\\
+      & = & A_{f} \displaystyle\sum\limits_{n=0}^{n} [\Gamma_{f}\Gamma_{d}e^{i \phi}]^{n}\nonumber\\
+      & = & A_{f}+A_{f} \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i \phi}]^{n}
 \end{eqnarray}
 
-The ratio in Equation \ref{eqn:ratio1} quantifies the amount of power received
-with respect to the incident sky power. Realistically, the incident sky power
-is not easily quantifiable, but it is a quantity we need to know to accurately
-characterize reflections.  
-%The right hand side of this equation consists of system parameters which are all chromatic i.e, functions of frequency.
-
-%Reflections cause the sky signal to appear at various delays. We aim to measure
-%the relative signal strength at those various delays, referred to as the
-%``delay spectrum" hereafter, to estimate levels of reflections in between the
-%feed and the dish apex.
-
-%We employ the reciprocity theorem for antennas in our experimental set-up.
-%More specifically, our experimental set-up differs from measuring sky signal
-%reflections since we send a pulse that is to be transmitted from the feed
-%before receiving it again. This results in a reversed situation - most of our
-%original signal is transmitted from the feed to be reflected from the dish,
-%while a small percentage reflects back down the cable (red arrows in Figure
-%\ref{fig:cartoon}). Therefore, since our measurement is carried out in
-%transmitting mode while an observation would be carried out in receiving mode,
-%we correct our results in order to map them to represent real observations.
-
-In our experimental set-up, instead of using sky signal, we employ
-our feed as a transmitter and transmit a pulse. If the initial pulse is a broadband signal,
-$P_{tr}$, sent to the feed via a $75ft$ cable by a vector network
+In our experimental set-up, we use the feed as a transmitter and transmit a pulse. If the initial pulse is a broadband signal,
+$I_{tr}$, sent to the feed via a $75ft$ cable by a vector network
 analyser (VNA), a delay domain measurement of the system is accomplished by
-taking the Fourier transform of the measured complex return loss of the feed. When the signal is incident on
+taking the Fourier transform of the complex return loss of the feed measured by VNA. When the signal is incident on
 the feed, part of the incident power ($\Gamma_{f}$) is reflected back to the
@@
 reflected back and forth in between the feed and the dish much like the sky
-signal reflection discussed previously.  Hence, if $P_{r}$ is the power
-incident back on the feed for the first time then the reflected power, $P_{refl}$,
+signal reflection discussed previously.  Hence, if $I_{r}$ is the power
+incident back on the feed for the first time then the reflected power, $I_{refl}$,
 back into the VNA would be:
@@
 \begin{equation}\label{eqn:series2}
-P_{refl} =  P_{r}(1-\Gamma_{f})[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
+I_{refl} =  I_{r}A_{f}[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
 \end{equation}
@@
 
-Recall that $P_{r}$ is the initial power that is incident back on the feed, which is just the feed radiated power reflected off the dish:
+Recall that $I_{r}$ is the initial power that is incident back on the feed, which is just the feed radiated power reflected off the dish:
 
 \begin{equation}
-P_{r}= \Gamma_{d}(1-\Gamma_f)e^{i\phi} P_{tr}
+I_{r}= \Gamma_{d}(1-\Gamma_f)e^{i\phi} I_{tr}
 \end{equation}
@@
 \begin{eqnarray}
-P_{ret} & = & \Gamma_{f}P_{tr} \nonumber\\ 
- & + &   \Gamma_{d}(1-\Gamma_f)e^{i\phi} P_{tr}(1-\Gamma_{f}) [1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]\nonumber\\
+I_{ret} & = & \Gamma_{f}I_{tr} \nonumber\\ 
+ & + &   \Gamma_{d}(1-\Gamma_f)e^{i\phi} I_{tr}(1-\Gamma_{f}) [1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]\nonumber\\
  \end{eqnarray}
@@
   \begin{eqnarray}\label{eqn:ratio2}
- {P_{ret} \over P_{tr} } & = & \Gamma_{f}
+ {I_{ret} \over I_{tr} } & = & \Gamma_{f}
   +  \Gamma_{d}(1-\Gamma_f)^{2} [e^{i\phi}+ \Gamma_{f}\Gamma_{d} e^{i2\phi}+  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{i n\phi}]\nonumber\\
@@
 
-The VNA measures the magnitude and phase of the quantity ${P_{ret}\over P_{tr}}$
+The VNA measures the magnitude and phase of the quantity ${I_{ret}\over I_{tr}}$
 as a function of frequency as shown in Figure \ref{fig:freq}. In our measurement
 set-up, the first reflection occurs at the feed $\Gamma_{f}$, so
-$({P_{ret} \over P_{tr} }  - \Gamma_{f}) $ gives an estimate of the delay
+$({I_{ret} \over I_{tr} }  - \Gamma_{f}) $ gives an estimate of the delay
 spectrum of the sky signal. In delay domain, the relative signal strength at
@@
 \end{document}
+
+%\begin{eqnarray}
+%V e^{i\phi}(\nu) & = & \int |A_{f}|^{2}|V_{sky}|^{2}|exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \nonumber\\
+%&& +  \int |A_{f}|^{2}|V_{sky}|^{2} |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \nonumber\\
+%&& + \int |A_{f}|^{2}|V_{sky}|^{2}| 2 \Re \left ((1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right)exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega
+%\label{eq8}		        
+%\end{eqnarray}
+
+%\subsection{Effect of first reflection on the delay spectrum}
+%We define $B(\vec \theta, \nu) =  A^{2}(\vec \theta, \nu) $ as the cross power pattern of the interferometer and $\Sigma_{rr}(\nu), \Sigma_{dr}(\nu)$ are the correlation coefficient between the two reflected signals in each antenna and the direct signal of one antenna with the reflected signal from the other antenna in the uv plane i.e,
+
+%\begin{equation}
+%\Sigma_{rr}(\nu) =  \left [ |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} \right ]
+%\end{equation}
+
+%\begin{equation}
+%\Sigma_{dr}(\nu) = \left [ 2 \Re \left ((1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right) \right]
+%\end{equation}
+
+%and $\Delta \tau$ is the additional delay each reflected component suffers in addition to the intrinsic geometric delay 
+%$\tau_{g}$. Therefore, $\Sigma(\vec \theta, \nu) = B(\vec \theta, \nu) \left [ 1+\Sigma_{rr} +\Sigma_{dr} \right]$
+
+%As given in equation \ref{eq3}, the Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum.
+Hence, the all sky integrated delay spectrum could be written as,
+%\begin{eqnarray}
+%\mathcal{F} \left [V e^{i\phi}\right] & = & \int \left [\int B I_{sky}exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
+%&& + \int \left [  \int B I_{sky} \Sigma_{rr} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right] exp\left[ -2 \pi i\nu \tau \right] d\nu  \nonumber\\
+%&& +\int \left [ \int B I_{sky} \Sigma_{dr} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\	
+%&& + \int \left [  \int |A_{f}|^{2}|V_{sky}|^{2} |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right] exp\left[ -2 \pi i\nu \tau \right] d\nu  \nonumber\\
+%&& +\int \left [ \int |A_{f}|^{2}|V_{sky}|^{2} 2 \Re \left ((1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right)exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
+%			& = & \int \left [\int B I_{sky} exp({2\pi i \nu \tau_{g}} ) dl dm \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
+%&& + \int \left [  \int B I_{sky} \Sigma_{rr} exp({2\pi i \nu \tau_{g}} ) dl dm \right] exp\left[ -2 \pi i\nu \tau \right] d\nu  \nonumber\\
+%&& +\int \left [ \int B I_{sky} \Sigma_{dr} exp({2\pi i \nu \tau_{g}} ) dl dm \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
+%\label{eq9}
+%\end{eqnarray}
+%
+%\begin{eqnarray}			
+%\mathcal{F} \left [V e^{i\phi}\right] & = & \left [ B(\tau)\ast I_{sky}(\tau) \right ]\ast \delta(\tau+\tau_{g}) \nonumber\\
+%		&& +  \left [ B(\tau)\ast I_{sky}(\tau)* \Sigma_{rr}( \tau) \right ]\ast \delta(\tau+\tau_{g}) \nonumber\\
+%		&& +  \left [B(\tau)\ast I_{sky}(\tau)* \Sigma_{dr}( \tau) \right ]\ast \delta(\tau+\tau_{g}+ \Delta \tau)\nonumber\\
+%\label{eq10}
+%\end{eqnarray}
+
+ %In words, the Fourier transform of the visibility contributed by any two voltage components from two antennas with no mutual delay is centred at a delay $\tau = \tau_{g}$ in the delay spectrum whereas any two voltage components from two antennas components having a mutual delay of $\Delta \tau$ will be centred at $\tau_{g} +\Delta \tau$.
+The correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal thus extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected.
+Also, any reflections arriving at the feed at any non-zero  value of the delay $\Delta \tau$ which could be the result of reflections from the feed structures would generate non zero delay response at those delays.

### 2015-11-02 DishReflectometry/Paper1_v0.tex
Added bbl file for reflectometry paper and switched back to building bibliography
Changed notation for first three equations in S2 (eq 4 needs help)

@@
 \newcommand{\vdag}{(v)^\dagger}
+\newcommand{\volt}{{v}}
+\newcommand{\vis}{{V}}
+\newcommand{\sky}{{\rm sky}}
+\newcommand{\bmvolt}{{a}}
+\newcommand{\bm}{{A}}
+\newcommand{\thhat}{{\hat\theta}}
+\newcommand{\fngexp}{{e^{\frac{2\pi i\nu\vec{b}\cdot\thhat}{c}}}}
+\newcommand{\ifngexp}{{e^{-\frac{2\pi i\nu\vec{b}\cdot\thhat}{c}}}}
 \newcommand{\myemail}{skywalker@galaxy.far.far.away}
@@
 \section{Visibility measurements by a two element interferometer}
-Consider a two element interferometer with a baseline $b$ and antenna field pattern $A(\theta, \nu)$.
-If we denote the sky signal at an angle $\vec \theta$ by $V_{sky}(\vec \theta, \nu)$ and the receiver noise of each element as $V_{rec}(\nu)$ then the voltage output of each antenna may be written as,
+
+Consider a two element interferometer with a baseline $\vec b$ and antenna field pattern $A(\thhat, \nu)$.
+If we denote the electric field sky signal in direction $\thhat$ by $\volt_\sky(\vec \theta, \nu)$ and the receiver noise of each element as $\volt_{rec}(\nu)$ then the voltage output of each antenna may be written as,
 \begin{equation}
-V_{1}(\vec \theta, \nu) = A_{1}(\theta,\nu)V_{sky}(\vec \theta,\nu)(\nu)\nonumber\\
+\volt_{1}(\thhat, \nu) = \bmvolt_{1}(\thhat,\nu)\volt_\sky(\thhat,\nu)\nonumber\\
 \end{equation}
 \begin{equation}
-V_{2} (\vec \theta, \nu)= A_{2}(\theta,\nu)V_{sky}(\theta,\nu)exp({2\pi i \nu \vec{b}.\hat{s} \over c} )(\nu)\nonumber\\
+\volt_{2} (\thhat, \nu)= \bmvolt_{2}(\thhat,\nu)\volt_\sky(\thhat,\nu)\fngexp\nonumber\\
 \end{equation}
-where $\hat s$ is the unit vector along the direction of the baseline and $A_{1}(\theta,\nu)$ and $A_{2}(\theta,\nu)$ are the field pattern of the two antennas.
-Hence, the time averaged complex visibility integrated over all sky as measured by the interferometer may be written as,
-
+where $\bmvolt_{1}(\thhat,\nu)$ and $\bmvolt_{2}(\thhat,\nu)$ are the electric field response patterns 
+of the two antennas.
+Hence, the time averaged visibility measured by the interferometer may be written as, 
 \begin{equation}
-V e^{i\phi}(\nu) =  \int  V_{1}(\theta,\nu)  V_{2}^{*} (\theta, \nu) exp(-{2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega 
+\vis(\vec b, \nu) =  \int  \volt_{1}(\thhat,\nu)  \volt_{2}^{*} (\thhat, \nu) \ifngexp d\Omega 
 \label{eq1}
@@
 
-We define antenna cross power pattern as  $B(\theta,\nu)=A_{1}(\theta,\nu)A_{2}^{*}(\theta,\nu)$ and denote the sky power as  $V_{sky}(\theta,\nu)V_{sky}^{*}(\theta,\nu) = I_{sky}(\vec \theta, \nu)|^2$.
+We define antenna cross power pattern as  $\bm(\thhat,\nu)=\bmvolt_{1}(\thhat,\nu)\bmvolt_{2}^{*}(\thhat,\nu)$ and denote the sky intensity as  $I_\sky(\thhat,\nu)=\volt_\sky(\thhat,\nu)\volt_\sky^{*}(\thhat,\nu)$.
 Hence,
-\begin{eqnarray}
-V e^{i\phi}(\nu) & = & \int B(\vec \theta, \nu) I_{sky}(\vec \theta,\nu) exp(-{2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \nonumber\\
-		& = & \int B(l,m, \nu) I_{sky}(l,m,\nu) exp(-2\pi i \nu \tau_{g} ) dl dm \nonumber\\
+\begin{equation}
+\vis(\vec b,\nu) = \int \bm(\thhat, \nu) I_\sky(\thhat,\nu) \ifngexp d\Omega
+	%	& = & \int B(l,m, \nu) I_{sky}(l,m,\nu) exp(-2\pi i \nu \tau_{g} ) dl dm \nonumber\\
  	%	& = & B(\vec u,\nu) \ast P_{sky}(\vec u,\nu ) \nonumber\\
@@
 \label{eq2}
-\end{eqnarray}
+\end{equation}
 
@@
 If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as,
-The Fourier transform of this visibility spectrum along the frequency axis results in the delay spctrum.
-\begin{eqnarray}
-\mathcal{F} \left [V e^{i\phi}\right] & = & \int \left [\int B(l,m, \nu) I_{sky}(l,m,\nu) exp(-2\pi i \nu \tau_{g} ) dl dm \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
+In \citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
+resulting in the delay spctrum:
+\begin{equation}
+\tilde V(\vec b, \tau)  = \int\!\!\int{\bm(\thhat,\nu) I_\sky(\thhat,\nu) \ifngexp d\Omega~e^{-2\pi i\nu\tau} d\nu}
 						%   & = & \int \left [B(\tau)\ast I_{sky}(\tau) \ast \delta(\tau+\tau_{g}) \right ] dl dm	
 \label{eq3}
-\end{eqnarray}
+\end{equation}
 
@@
 \end{eqnarray}
+% XXX rethink how to express this equation (not correct about integrated over all sky)
+% XXX define tau_g
 the convolution being carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$.
@@
 
-%\bibliographystyle{apj}
-%\bibliography{biblio.bib}
-\begin{thebibliography}{}
-
-\bibitem[Parsons \& Backer(2009)]{ParsonsBacker2009}
-Parsons, A., \& Backer, D. 2009, \apj, 138, 219
-\bibitem[Parsons et al.(2012)]{Parsons2012}
-Parsons, A., \& Pober, Jonathan C., \& Aguirre, James E., \& Carilli, Christopher L., \& Jacobs, Daniel C., \& Moore, David F. 2012, \apj 756, 165
-\end{thebibliography}{}
+\bibliographystyle{apj}
+\bibliography{biblio.bib}
+%\begin{thebibliography}{}
+%
+%\bibitem[Parsons \& Backer(2009)]{ParsonsBacker2009}
+%Parsons, A., \& Backer, D. 2009, \apj, 138, 219
+%\bibitem[Parsons et al.(2012)]{Parsons2012}
+%Parsons, A., \& Pober, Jonathan C., \& Aguirre, James E., \& Carilli, Christopher L., \& Jacobs, Daniel C., \& Moore, David F. 2012, \apj 756, 165
+%\end{thebibliography}{}
 

### 2015-11-03 DishReflectometry/Paper1_v0.tex
Added 2 paragraphs to intro

@@
 \author{Gilbert Hsyu\altaffilmark{2}, Tsz Kuk Leung\altaffilmark{2}, Aaron Parsons\altaffilmark{1}}
+% XXX add all members of HERA collaboration
+% XXX suggest Patra, Parsons, Ali, DeBoer, Cheng, Leung, Hsyu, alphabetical
 
@@
 \section{Introduction}
+
+Since it was first proposed in \citet{shaver_et_al1999}, measuring 21~cm
+emission from neutral hydrogen in our early universe has gained attention as a
+powerful probe of both cosmology and astrophysics.  While the science case for
+21~cm cosmology, particularly during the Epoch of Reionization, is well
+established (see, e.g.,
+\citealt{furlanetto_et_al2006,morales_wyithe2010,furlanetto_loeb2014,pritchard_loeb2014}),
+the technical path toward measuring this signal has been more problematic.  The
+weakness of this hyperfine line keeps the 21~cm signal below opacity throughout
+cosmological history, but it also creates sensitivity and calibration
+challenges that have yet to be fully solved.  With noise temperatures dominated
+by sky noise \citep{XXX} and foregrounds four to five orders of magnitude
+brighter than the signal \citep{XXX}, 21~cm reionization experiments must
+furnish both collecting area and foreground suppression at levels significantly
+beyond anything previously achieved in radio telescopes operating below 1 GHz.
+
+One of the most problematic effects facing these experiments results form instrument
+chromaticity.  The spectral dimension of 21~cm reionization experiments is of vital
+importance; for line emission, this coordinate translates to a line-of-sight distance
+that can be used to construct three-dimensional maps (and power spectra) of emission,
+as well as probe the evolution of 21~cm emission over cosmological timescales.
+The evolving response of a radio telescope --- either a single dish
+or an interferometer --- versus spectral frequency modulates spectrally smooth foregrounds ,
+contaminating spectral modes that might
+otherwise be used to measure reionization \citep{XXX}.  Moreover, the chromaticity of
+a telescope's response pattern scales linearly with diameter, putting the
+needs of foreground suppression and signal sensitivity in direct tension with one
+another.
+
+% XXX the wedge
+
 The efficacy of the techniques of foreground removal from the measured data critically limits the 21~cm power spectrum measurements.

### 2015-11-04 DishMeasurements/memo/DishBeamMeasurementsPaper.tex
working on dish beam paper

--- 2015-10-28 DishMeasurements/memo/DishBeamMeasurementsMemo.tex
@@
 
-%\documentclass{emulateapj}
-\documentclass[preprint]{aastex}
+\documentclass{emulateapj}
+%\documentclass[preprint]{aastex}
 
@@
 
-%\shorttitle{HERA Dish Beam Measurements Memo, Rev $\alpha$}
-%\shortauthors{Neben}
+\shorttitle{The HERA Dish: Beam Measurements and Science Implications}
+\shortauthors{Neben et al.}
 
@@
 
-\title{HERA Dish Beam Measurements Memo}
+\title{The Hydrogen Epoch of Reionization Array Dish: Beam Pattern Measurements and Science Implications}
 
@@
 
-\author{Abraham Neben, Rich Bradley, Jackie Hewitt, others}
-%\affil{MIT Kavli Institute, Massachusetts Institute of Technology, Cambridge, MA, 02139 USA}
+\author{Abraham R. Neben\altaffilmark{1},
+Aaron Ewall-Wice\altaffilmark{1},
+Nipanjana Patra\altaffilmark{2},
+Nithyanandan Thyagarajan\altaffilmark{3},
+James E. Aguirre\altaffilmark{4},
+Zaki S. Ali\altaffilmark{2},
+Judd Bowman\altaffilmark{3}
+Carina Cheng\altaffilmark{2},
+David R. DeBoer\altaffilmark{2}
+Jacqueline N. Hewitt\altaffilmark{2},
+Aaron Parsons\altaffilmark{2}}
 
-\author{Oct 26, 2015}
+\affil{\altaffilmark{1}MIT Kavli Institute, Massachusetts Institute of Technology, Cambridge, MA, 02139 USA}
+\affil{\altaffilmark{2}Dept. of Astronomy, University of California, Berkeley, CA, USA}
+\affil{\altaffilmark{3}Arizona State University, School of Earth and Space Exploration, Tempe, AZ 85287, USA}
+\affil{\altaffilmark{4}Dept. of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA}
 
@@
 
-%\keywords{instrumentation: interferometers --- techniques: interferometric --- cosmology: observations --- dark ages, reionization, first stars}
+\keywords{instrumentation: interferometers --- techniques: interferometric --- cosmology: observations --- dark ages, reionization, first stars}
 
-%\section{Introduction}
+\section{Introduction}
 
-%must use frequency structure to separate FGs from signal
-%a certain amount of freq structure is imprinted onto smooth sources due to the frequency-dependent sampling function of an interferometer
-%also by faraday rotation and the bandpass (citations)
+basics of 21cm cosmology
 
-%leakage is due to bandpass, frequency flagging, finite bandwidth.
+must use frequency structure to separate FGs from signal
+a certain amount of freq structure is imprinted onto smooth sources due to the frequency-dependent sampling function of an interferometer
+also by faraday rotation and the bandpass (citations)
+
+leakage is due to bandpass, frequency flagging, finite bandwidth.
 can be mitigated by subtraction in the delay spectrum (CLEAN), giving up on wedge modes, or subtraction in image space with foreground modeling, likely will have to give up on wedge modes too unless have incredible calibration and imaging fidelity, as LOFAR is attempting.
@@
 
-%hera is pursuing two relatively orthogonal power spectrum analyses (imaging and delay transform)
+hera is pursuing two relatively orthogonal power spectrum analyses (imaging and delay transform)
 
-%the other papers in this series quantify the degree of spectral structure induced by the dish bandpass in measurement and modeling, we focus in this section on foreground leakage due to the finite bandwidth as a function of the beam response at different delays in the sky.
+the other papers in this series quantify the degree of spectral structure induced by the dish bandpass in measurement and modeling, we focus in this section on foreground leakage due to the finite bandwidth as a function of the beam response at different delays in the sky.
 Nithya discuss this is detail nithya15,nithya15b
 
-%\citet{nithya15,nithya15b} 
-%for a power spectrum analysis, note that these tests test how leakage varies as a function of the brightness of emission at different delays, not leakage due to beam frequency dependence (ie, either pattern or overall gain)
+\citet{nithya15,nithya15b} 
+for a power spectrum analysis, note that these tests test how leakage varies as a function of the brightness of emission at different delays, not leakage due to beam frequency dependence (ie, either pattern or overall gain)
 
@@
 We also plot (green dashed line) the delay spectrum after subtracting the visibilities computed with the $\theta\sim60^\circ$ cutoff measured beam from those using the full measured beam.
-This curve may be interpreted as the uncertainty in the ``pitchfork'' horizon brightening due to uncertainty in the beam horizon response, or equivalently as the delay spectrum residual foregrounds after subtracting foregrounds in the well modeled region of the sky.
+This curve may be interpreted as the uncertainty in the ``pitchfork'' horizon brightening due to uncertainty in the beam horizon response, or equivalently as the delay spectrum residual foregrounds after subtracting foregrounds in the well modeled region of the sky (Neben et al.
+2015b, submitted).
 By construction, this subtraction leaves emission from the highest delay regions of the sky (near the horizon on opposite sides of the baseline), but also leaves some low delay emission on opposite sides of a line perpendicular to the baseline.
@@
 \end{document}
--

### 2015-11-04 DishReflectometry/Memo copy.tex

\documentclass[12pt,preprint]{aastex}
\usepackage{geometry,amsmath}
\usepackage{float}
%\usepackage{titlesec} %used to format titles
\usepackage{graphicx} %for handling figures
%\usepackage[none]{hyphenat} %disallows hyphenated words

\begin{document}

\title{HERA Dish Reflectometry} 
\author{Zaki Ali, Carina Cheng, Aaron Parsons, Nipanjana Patra}
\maketitle

\section{Introduction}

There are several different sources of instrumental chromaticity for an interferometer such as HERA that each introduce unwanted systematics in data. One such source results from the antenna, which can introduce non-spectrally smooth structure in data due to delays associated with internal signal reflections. The HERA element was designed to minimize this structure - the contamination outside the foreground `wedge' - so that the expected level of the 21cm reionization signal that we are interested in still dominates this region. In order to achieve this, a chromaticity specification of -60dB at 60ns was implemented in the HERA element design, setting a constraint on the level of reflections. In other words, when a signal that originates at the feed re-enters the feed after a time delay of 60ns, it must be attenuated by at least 60dB.

Understanding the nature of antenna reflections in the HERA dish is of the utmost importance in characterizing the performance of the dish. As HERA progresses as an experiment, it is necessary to build optimal dishes that promise to minimize the challenges of chromaticity in our quest for the Epoch of Reioinization.

\section{Theory}{\label{sec:theory}}

*what is the measurement we are actually doing... S11 math stuff*

In practice, a HERA dish receives signal from the sky. Lightwaves propagate in from infinity, reflect off the dish and enter the feed. For a well-designed feed, most of the signal will be transmitted through the feed, and only a small percentage of the signal reflects off the dish a second time (blue arrows in Figure \ref{fig:cartoon}). Therefore, the reflections we are concerned about are significantly less strong than the original signal, and it is this amount of reflection that we aim to quantify.

The antenna doesn't just act as a receiver. It can also act as an emitter, which is a property we employ in our experimental set-up. Instead of measuring sky signal reflections, we are operating in a controlled environment where we send a pulse that is to be transmitted from the feed. This results in a reversed situation from before - most of our original signal is transmitted from the feed to be reflected from the dish, while a small percentage reflects back down the cable (red arrows in Figure \ref{fig:cartoon}). Therefore, the S11 parameter we measure originates from a much stronger signal than from the receiving case. This is a discrepancy we have to correct for in our analysis.

The difference between the receiving and transmitting antenna cases can be quantified by the impedance mismatch between the antenna and the sky...

*explain why the level of the measurements has to be brought down, and how this is okay for high delays... *

*WHY is the 'corrected' spectrum higher for low delays but lower for high delays?*

*WHY is the correction term related to windowing vs. unwindowing?*

\begin{figure}
\centering
\includegraphics[totalheight=0.5\textheight]{plots/reflection_cartoon.png}
\caption{The blue solid lines represent an original sky signal entering the feed. A small percentage of it (dashed blue) is reflected off the dish, and it is these reflections that we are concerned about. In our measurements however, the reflections measured contain most of the original pulse signal (solid red), so it is crucial to adjust for this difference in our analysis.}
\label{fig:cartoon}
\end{figure}

\section{Reflection of the sky signal during observation:}

\begin{figure}
\centering
\includegraphics[totalheight=0.5\textheight]{schematic.pdf}
\caption{Schematic diagram showing reflection between the dish and the feed when sky signal is incident on it. }
\label{reflection_schematic}
\end{figure}
Figure \ref{reflection_schematic} shows the schematic of the sky signal propagation path during an observation. The plane wavefront from the sky is incident on the parabolic dish and focussed at the feed. A part of this power is reflected off the feed, incidents back on the dish and comes back to the feed after further reflection from the dish. We consider one reflection off the feed and subsequent reflection off the dish as one reflection. If the incident power is $P_{sky}$, feed power reflection coefficient is $\Gamma_{a}$ and the dish reflection coefficient is $\Gamma_{d}$ then the net power entering the feed after $n$ reflection of the feed and the dish,

\begin{equation}
P_{in} =  P_{sky}(1-\Gamma_{a})\Gamma_{d} [1+ \Gamma_{a}\Gamma_{d} e^{i\phi}+ (\Gamma_{a}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{d}\Gamma_{n})^{n}e^{in\phi}]
\end{equation}

where, $\phi = ({2\pi \over c})f 2l$ is the propagation delay of the a frequency $f$ due to reflection over the focal distance $l$. 
Therefore, 
\begin{eqnarray}
{P_{in} \over P_{sky} } & = & (1-\Gamma_{a})\Gamma_{d} [1+ \Gamma_{a}\Gamma_{d} e^{i\phi}+ (\Gamma_{a}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{d}\Gamma_{n})^{n}e^{in\phi}] \nonumber\\
      & = & (1-\Gamma_{a})\Gamma_{d} {1-(\Gamma_{d}\Gamma_{a})^{n} \over 1-\Gamma_{d} \Gamma_{a} } 
\end{eqnarray}

Therefore, the input signal would have ripples of various frequencies over its passband which would manifest itself as a non-zero signal at various delays in the delay domain. We aim to measure the relative signal strength at various delays, referred to as "delay spectrum" hereafter, to estimate various level of reflections in between the feed and the dish apex.\\

 Delay spectrum measurement of the system is accomplished by measuring the return loss of the feed while keeping it at the focal point of the dish. A broadband signal $P_{tr}$ is sent to the feed antenna via a 75m long cable by the measuring instrument which is a vector network analyser (VNA). When the signal is incident on the feed, $\Gamma_{a}$ part of the incident power is reflected back to the measuring device and $(1-\Gamma_{a})$ part is radiated by the feed. The signal radiated by the feed illuminates the dish and is radiated out to the space. However, the signal incident at the dish apex is reflected by the dish and returns to the feed. This incident signal is now reflected back and forth in between the feed and the dish much like the sky signal reflection discussed previously. Hence, if $P_{r}$ is the power incident back on the feed for the first time then the reflected power $P_{ref}$ back into the measuring instrument would be,

\begin{equation}
P_{ref} =  P_{r}(1-\Gamma_{a}) [1+ \Gamma_{a}\Gamma_{d} e^{i\phi}+ (\Gamma_{a}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{d}\Gamma_{n})^{n}e^{in\phi}]
\end{equation}

Once again we consider one reflection from the feed and subsequent reflection from the dish as one reflection.

Now, $P_{r}$ is the power incident back on the feed which is the feed radiated power reflected off the dish.  
\begin{equation}
P_{r}= \Gamma_{d}(1-\Gamma_a) P_{tr}
\end{equation}
Also, the first reflection of the power sent by the measuring device occurs at the antenna end. Hence the total reflected power $P_{ret}$, returned to the measuring device would be,

\begin{eqnarray}
P_{ret} & = & \Gamma_{a}P_{tr} \nonumber\\ 
 & & +  \Gamma_{d}(1-\Gamma_a) P_{tr}(1-\Gamma_{a}) [1+ \Gamma_{a}\Gamma_{d} e^{i\phi}+  ....+ (\Gamma_{d}\Gamma_{n})^{n}e^{in\phi}]\nonumber\\
 \end{eqnarray}
 Simplifying, 
 \begin{eqnarray}
 {P_{ret} \over P_{tr} } & = & \Gamma_{a}
  +  \Gamma_{d}(1-\Gamma_a)^{2}  {1-(\Gamma_{d}\Gamma_{a})^{n} \over 1-\Gamma_{d} \Gamma_{a} } \nonumber\\
\end{eqnarray}

The VNA measures the magnitude and phase of the quantity ${P_{ret}\over P_{tr}}$ as a function of frequencies which is plotted in figure \ref{fig:freq}. Since in this measurement set up, the first reflection occurs at the antenna terminal which is represented by $\Gamma_{a}$ in the above equation, $({P_{ret} \over P_{tr} }  - \Gamma_{a}) $ gives the estimate of the delay spectrum of the sky signal. In the delay domain, the relative signal strength at zero delay represents the factor$\Gamma_{a}$ while the signal strength at any other delay represents the any delayed signal that entered the feed after being reflected from the feed surroundings.

\section{Methodology}

To measure the delays associated with reflections within the dish and feed, we
used the prototype HERA dish (Figure \ref{fig:heradish} built at the NRAO site in
Green Bank, WV. The dish is a 14-m parabolic reflector structurally supported
with 3 telephone poles. The reflective material is made up of wire mesh that
is attached to PVC pipes that form the parabolic shape. With the current
prototype, the feed is a PAPER dipole encased in a cylindrical cage encompassing
the backplane. The PAPER feed and the backplane (which prevents feed-to-feed
interaction between neighboring dishes) is raised and lowered by a three-pulley
system. The focal height of the dish is 4.5m ($\sim{14.76}$ft). Feed heights quoted in our measurements represent the distance from the balun to the top of the central concrete hub. Note, however, that the actual focal height of the dish represents the distance from the backplane of the feed to the dish's wire mesh, which intersects the concrete hub between the ground and the top of the hub. 
%XXX get discrepancy distance from DaveD.

The following reflectometry measurements were taken on July 20-23, 2015 using a
FieldFox unit in Network Analyzer mode. A pulse is generated in the FieldFox
and sent through a 75ft $50\Omega$ cable that connects to the feed with a 4:1
passive balun. The return loss as a function of frequency is saved. Both
the amplitude of the power and phase information are saved. Our
measurements are taken for a frequency bandwidth of 50 to 500MHz.

Measurements are transformed into the delay domain during post-processing so that window functions
can be used in the Fourier transform. Without a window function, taking the Fourier transform of a finite data series (such as the return loss over a finite bandwidth), which can be interpreted as a square window function, is equivalent to convolving the Fourier transformed data with a $sinc$ function. This results in excess power at high delays due to the sidelobes in the $sinc$ function. Consequently, we have chosen to use a Blackman-Harris window function when moving into the delay domain. The effectiveness of this window function compared to a square window function is illustrated in Figure \ref{fig:window}.

\begin{figure}
\centering
\includegraphics[totalheight=0.5\textheight]{plots/bh_vs_sq.png}
\caption{Delay plot produced using a Blackman-Harris window function vs. a square window function for the PAPER bandwidth.}
\label{fig:window}
\end{figure}

As mentioned in Section \ref{sec:theory}, there is a mis-match in amplitude between the reflections that we measure (originating from the FieldFox pulse) and reflections produced by sky signal. To compensate, we multiply our entire windowed delay spectrum by the DC component of the un-windowed delay spectrum.

\begin{figure}
\centering
\includegraphics[trim={2cm 20cm 30cm 15cm},clip, totalheight=0.45\textheight]{plots/heradish.jpg}
\caption{HERA dish and feed at the Green Bank NRAO site.}
\label{fig:heradish}
\end{figure}

\section{Results}

Figure \ref{fig:freq} shows the return loss for a frequency bandwidth of 50 to 500MHz. This measurement was taken with the feed suspended at 12ft (distance between the balun and top of the central concrete hub). Because the return loss is the ratio of the power received to the power transmitted, higher reflections can clearly be seen outside of the PAPER bandwidth. This is not surprising, since the feed is tuned specifically for PAPER. The return loss minima are locations where our feed is well-matched to free space.

\begin{figure}
\centering
\includegraphics[totalheight=0.4\textheight]{plots/frequency_amp_phase.png}
\caption{Amplitude and phase of the measured return loss.}
\label{fig:freq}
\end{figure}

In Figure \ref{fig:3bands}, the return loss is plotted versus delay for three chosen bandwidths: the HERA bandwidth, the PAPER bandwidth, and a typical power spectra bandwidth when using a Blackman-Harris window function. It is again shown that the reflections are minimized for the PAPER bandwidth.

\begin{figure}
\centering
\includegraphics[totalheight=0.5\textheight]{plots/delay3_window.png}
\caption{Delay plots produced using a Blackman-Harris window function for 3 different frequency bandwidths: 50MHz-250MHz (``hera"), 100MHz-200MHz (``paper"), and 140MHz-160MHz (``pspec"). The black dashed lines illustrate our ``60 by 60" specification.}
\label{fig:3bands}
\end{figure}

Figure \ref{fig:elevator} is again a delay plot of the return loss, but for four different feed suspension heights. We use the PAPER bandwidth and note that the measurements are near identical at low delays, implying that low delay reflections are caused primarily by reflections within the feed cage. However, at higher delays we notice discrepancies between the different heights.

\begin{figure}
\centering
\includegraphics[totalheight=0.5\textheight]{plots/delay_heights_paper.png}
\caption{Delay plots produced using a Blackman-Harris window function for 4 different feed heights and the PAPER bandwidth. The black dashed lines illustrate our ``60 by 60" specification.}
\label{fig:elevator}
\end{figure}

Finally, Figure \ref{fig:outofthedish} presents measurements taken of the feed away from the dish. Echosorb is placed under the feed for some of the measurements, with the expectation that it will prevent any reflections off the ground. Measurements are also taken of the feed inside its metal cage in various configurations.

\begin{figure}
\centering
\includegraphics[totalheight=0.5\textheight]{plots/delay_feed.png}
\caption{Delay plots produced using a Blackman-Harris window function for different lone feed configurations and the PAPER bandwidth. The black dashed lines illustrate our ``60 by 60" specification.}
\label{fig:outofthedish}
\end{figure}

\section{Conclusion}

\end{document}

### 2015-11-04 DishReflectometry/Memo.tex

--- 2015-11-02 DishReflectometry/Paper1_v0.tex
@@
 \documentclass[12pt,preprint]{aastex}
+\usepackage[margin=1in]{geometry}
 \usepackage{float,amsmath}
-%\usepackage[margin=1in]{geometry}
 %\usepackage{titlesec} %used to format titles
@@
 %\usepackage[none]{hyphenat} %disallows hyphenated words
-\newcommand{\vdag}{(v)^\dagger}
-\newcommand{\myemail}{skywalker@galaxy.far.far.away}
-
-%\usepackage{cite}
-
-%\citestyle{aa}
-\shorttitle{HERA dish reflectometry }
-\shortauthors{Patra et al.}
+\citestyle{aa}
 
@@
 
-\title{Effect of multiple reflection of the sky signal off the HERA element on the measurements of 21cm power spectrum} 
-%\maketitle
-
-\author{Nipanjana Patra\altaffilmark{1} }
-\email{Contact author email: nipanjana@berkeley.edu}
-
-\author{Zaki Ali\altaffilmark{1}, Carina Cheng\altaffilmark{1}, Dave DeBoer\altaffilmark{1}}
-\author{Gilbert Hsyu\altaffilmark{2}, Tsz Kuk Leung\altaffilmark{2}, Aaron Parsons\altaffilmark{1}}
-
-\altaffiltext{1}{University of California, Berkeley, nipanjana@berkeley.edu}
-\altaffiltext{2}{To be inserted}
-
-\begin{abstract}
-\end{abstract}
+\title{HERA Dish Reflectometry} 
+\author{Nipanjana Patra, Zaki Ali, Carina Cheng, Dave DeBoer, Gilbert Hsyu, Tsz Kuk Leung, Aaron Parsons}
+\maketitle
 
 \section{Introduction}
-The efficacy of the techniques of foreground removal from the measured data critically limits the 21~cm power spectrum measurements.
-The delay transformation technique of foreground removal, introduced by  \citep{ParsonsBacker2009,Parsons2012} computes the Fourier transform of the visibility measured by an interferometer and produces a spectrum, referred to as delay spectrum hereafter, which is a function of the geometric time delay corresponding to the physical length of the baseline between two antennas.
-For the visibilities measured over a wide field across wide frequency bandwidth, the delay spectrum is constituted by the instrument response, the foreground signal and 21cm power spectrum, hereafter referred to as EoR signal.
-%The complex visibility measured by an interferometer is a convolution of the instrument response with the true sky response in the UV plane.
-Therefore, when Fourier transformed, the delay spectrum is the multiplication of the sky response with the instrument response in the delay domain.
-The technique exploits the smooth spectral characteristics of the foreground and for a widefield wide bandwidth visibility measurement by an interferometer with a baseline $b$, confines the foreground contribution to the computed delay spectrum within the largest possible time delay $\tau = b/c$ corresponding to the given baseline length.
-Such techniques also assumes a spectrally smooth instrumental response whose contribution to the measured data, much as the contribution of the smooth spectrum foreground, also has an upper bound in the delay space imposed by the largest geometric delay of the given baseline.
-Beyond this limit, for an ideal system performance, the delay spectrum would be dominated by any wideband signal across the sky with spectral and spatial fluctuation over small scale such as the EoR signal and therefore, could be detectable.\\
-The interaction between the sky signal and instrument response can alter the relative contribution of the foreground, instrument response and the EoR signal at a given delay and thus influence the detectability of the EoR signal.
-Such interactions may cause the foreground and systematics to spill over at higher delays and thus push the upper limit of the foreground and systematic contaminated delay modes to much higher delays.
-In this process, the EoR signal over large spatial scale will be lost.
 
- The Hydrogen Epoch of Reionization Array (HERA) is a proposed array consisting of 568 14-m dishes in South Africa which will measure the 21~cm power spectrum between 100 to 200~MHz .
-In this paper, we investigate the performance of the individual HERA elements and resulting contribution of the instrument response to the delay spectrum.
-Reflectometry measurements  are carried out across wide bandwidth on a prototype HERA element in Green
-Bank, WV (Figure \ref{fig:heradish}) and the results are interpreted in the light of delay spectrum technique.
-Section 2 describes the delay spectrum for the ideal and non-ideal performance of a two element interferometer.
-Reflectometry measurements are described in section 3.
-Section 4 qualifies the performance of the HERA element as an interferometer for detection of the 21~cm power spectrum.
+There are several different sources of instrumental chromaticity for radio
+telescope systems that can result in non-ideal performances and unwanted
+systematic effects in measured data. One such source is the mismatch between
+the impedance of free space and the feed and transmission line, which results
+in a partial coupling of the sky signal into the feed while the rest is
+reflected back into the space. For any reflector telescope, such as HERA, this
+signal illuminates the dish and part of it reflects back and forth several
+times in between the dish feed and the vertex of the dish.  Such reflections
+generate multiple reduced strength copies of the incident sky signal at various
+delays, and this produces spurious correlations in the visibilities of
+interferometric data.
+
+To first order, the design specification of HERA elements requires that any
+delayed signal, arriving at the feed after a multipath propagation, should be
+at the level of $-60dB$ at a delay of $60ns$ relative to the first incident
+signal at the feed \citep{parsons_deboer_memo}. This specification was
+approximated based on the power level of the cosmological signal in relation to
+foreground signals, which is estimated to be six orders of magnitude fainter
+\citep{santos_et_al2005,ali_et_al2008,deoliveira2008,jelic_et_al2008,bernardi_et_al2009,bernardi_et_al2010,ghosh_et_al2011}.
+Additionally, the $14m$ HERA baselines set a foreground containing
+horizon-limit (the wedge) that, with some buffer, sets a delay specification of
+$60ns$
+\citep{parsons_et_al2012b,vedantham_et_al2012,nithya_et_al2013,liu_et_al2014a,liu_et_al2014b}.
+
+We carry out reflectometry measurements at the HERA element prototype in Green
+Bank, WV (Figure \ref{fig:heradish}) in order to understand the nature of feed
+reflections in the dish and characterize its performance. As HERA progresses as
+an experiment, it is necessary to build optimized dishes that aim to minimize the
+challenges of chromaticity in our quest for the Epoch of Reionization.
 
@@
 
-\section{Visibility measurements by a two element interferometer}
-Consider a two element interferometer with a baseline $b$ and antenna field pattern $A(\theta, \nu)$.
-If we denote the sky signal at an angle $\vec \theta$ by $V_{sky}(\vec \theta, \nu)$ and the receiver noise of each element as $V_{rec}(\nu)$ then the voltage output of each antenna may be written as,
-\begin{equation}
-V_{1}(\vec \theta, \nu) = A_{1}(\theta,\nu)V_{sky}(\vec \theta,\nu)(\nu)\nonumber\\
-\end{equation}
-\begin{equation}
-V_{2} (\vec \theta, \nu)= A_{2}(\theta,\nu)V_{sky}(\theta,\nu)exp({2\pi i \nu \vec{b}.\hat{s} \over c} )(\nu)\nonumber\\
-\end{equation}
-where $\hat s$ is the unit vector along the direction of the baseline and $A_{1}(\theta,\nu)$ and $A_{2}(\theta,\nu)$ are the field pattern of the two antennas.
-Hence, the time averaged complex visibility integrated over all sky as measured by the interferometer may be written as,
-
-\begin{equation}
-V e^{i\phi}(\nu) =  \int  V_{1}(\theta,\nu)  V_{2}^{*} (\theta, \nu) exp(-{2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega 
-\label{eq1}
-\end{equation}
-
-We define antenna cross power pattern as  $B(\theta,\nu)=A_{1}(\theta,\nu)A_{2}^{*}(\theta,\nu)$ and denote the sky power as  $V_{sky}(\theta,\nu)V_{sky}^{*}(\theta,\nu) = I_{sky}(\vec \theta, \nu)|^2$.
-Hence,
-\begin{eqnarray}
-V e^{i\phi}(\nu) & = & \int B(\vec \theta, \nu) I_{sky}(\vec \theta,\nu) exp(-{2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \nonumber\\
-		& = & \int B(l,m, \nu) I_{sky}(l,m,\nu) exp(-2\pi i \nu \tau_{g} ) dl dm \nonumber\\
- 	%	& = & B(\vec u,\nu) \ast P_{sky}(\vec u,\nu ) \nonumber\\
-	%	& = & B(\nu { |\vec b| \over c} , \nu) \ast P_{sky}(\nu { |\vec b| \over c} , \nu) \nonumber\\
-	%	& = & B(\tau_{g}, \nu) \ast P_{sky}(\tau_{g} , \nu)	
-\label{eq2}
-\end{eqnarray}
-
-%i.e, the complex visibility is the Fourier transform of the product of the antenna beam pattern with the sky angular power spectrum.
-In other words, it is the convolution of the Fourier transform of the antenna power pattern with the Fourier transform of the sky.
-The complex visibility measured by an interferometer with a given baseline length has explicit dependence on frequency as well as implicit frequency dependence through the spatial frequency $\vec u = \nu { \vec b \over c}$ component.
-Since $\vec u $ is the For a given baseline length $|\vec b|$, the visibility measured at various frequencies are not only the function of frequencies but also samples different $\vec u$ in the uv space.
-Delay transformation technique takes the visibility measurements at different frequencies and Fourier transforms the complex visibilities.
-If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as,
-The Fourier transform of this visibility spectrum along the frequency axis results in the delay spctrum.
-\begin{eqnarray}
-\mathcal{F} \left [V e^{i\phi}\right] & = & \int \left [\int B(l,m, \nu) I_{sky}(l,m,\nu) exp(-2\pi i \nu \tau_{g} ) dl dm \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
-						%   & = & \int \left [B(\tau)\ast I_{sky}(\tau) \ast \delta(\tau+\tau_{g}) \right ] dl dm	
-\label{eq3}
-\end{eqnarray}
-
-Hence, the delay spectrum, integrated over all sky would be written as, 
-\begin{eqnarray}
-\mathcal{F} \left [V e^{i\phi}\right]   & = &  \left [B(\tau)\ast I_{sky}(\tau) \ast \delta(\tau+\tau_{g}) \right ] 	
-\label{eq4}
-\end{eqnarray}
-the convolution being carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$.
-In words, the sky delay spectrum is convoluted with the delay spectrum of the instrument and is centred at a delay $\tau_{g}$.
-The projected geometric delay $\tau_{g}$ for a given baseline can vary from 0 to $\tau_{g}$.
-Also, due to frequency dependence of the sky signal, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with decaying amplitude [Ref to the figure Parsons12].
-Sky delay spectrum $I_{sky}(\tau)$ is contributed by the foreground  $I_{fg}(\tau)$ and the 21~cm power spectrum $I_{21}(\tau)$.
-Since $I_{fg}$ is spectrally smooth, whereas $I_{21}$ contains spectral structures, for wideband measurements, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces at higher delays and, therefore, at higher delays, the 21~cm delay spectrum is detectable.
-\textbf{[ Reference to Nithya's foreground simulation work, reference to any plots on the relative contribution of the  foreground and EoR signal.
-]}
-
-\section{Effects of additional reflections of the sky signal between the parabolic dish and the feed on the measured visibility}
- Plane waves incident on a parabolic dish are focussed at the feed which is kept at the focal plane of the dish.
-The mismatch between the impedance of free space and the feed and transmission line results in a partial coupling of the sky signal into the feed while the rest is reflected off the feed.
-The reflected signal illuminates the dish and most of it is reflected back into the space.
-However, a part of it reflects back and forth several times in between the feed and the vertex of the dish which is shadowed by the feed (dashed blue arrows in Figure \ref{fig:cartoon}).
-Such reflections generate multiple copies of the incident sky signal of reduced strength at various time/phase and thus produces spurious correlations in the visibilities of interferometric data.
-In this section we compute the visibility of a two element interferometer accounting for the additional reflections of the sky signal in between the feed and the dish vertex and the corresponding effects on the delay spectrum.
-
+\section{Theory}{\label{sec:theory}}
 \begin{figure}[ht!]
@@
 
-Consider again a two element interferometer as described in section 2.
-Two antennas are assumed to be exactly identical so that their electrical parameters are same.
-We denote the voltage reflection coefficient of each feed by $\Gamma_{f}$.
-The voltage reflection coefficient of the reflector dish is denoted by $\Gamma_{d}$.
-Upon first incidence of the sky signal onto the dish, the entire sky signal would be reflected and focussed onto the feed.
-Hence, for first incidence $\Gamma_{d}=1$.
-Sky signal that would return to the dish after successive reflections off the feed and the dish is only reflected from a small area around the vertex of the dish and therefore, $\Gamma_{d}<1$.
-In our analysis, we consider one reflection of the sky power from the feed and subsequent reflection off the dish as one single reflection.
-If the focal length of the dish is $l$, assuming the feed is located at the focus, the roundtrip delay after first reflection will be $\Delta \tau = {2l \over c}$.
+Plane waves incident on a parabolic dish
+are focussed at the feed with focal height $l$. For a well-designed feed, one
+that closely matches the impedance of free space\footnote{The impedance of free space
+is $Z_{0} = \mu_{0}c_{0} = \frac{1}{\epsilon_{0}c_{0}} \approx 377\Omega $.},
+most of the signal will enter the system while only
+a small percentage will be reflected back towards the dish for a secondary
+reflection into the feed (dashed blue arrows in Figure \ref{fig:cartoon}). In the
+following discussion, we consider a reflection off the feed and the
+subsequent reflection off the dish as one reflection.
 
-\subsection{Effect of first order reflections on visibility and delay spectrum}
-Upon first incidence of the sky signal $V_{sky}$, $\Gamma_{f}$ fraction of the voltage is reflected off the feed while $(1-\Gamma_{f})$ fraction is coupled to the feed.
-The reflected voltage then further reflected off the dish and $(1-\Gamma_{f}) $ fraction of it reenters the feed with a roundtrip time delay $\Delta \tau$.
-Hence, the net voltage at the output of the two antennas could be written as,
-\begin{eqnarray}
-V_{1} & = & A V_{sky}(1-\Gamma_{f}) + A V_{sky} \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau}  (1-\Gamma_{f})^{2}\nonumber\\
-         & = & A V_{sky} (1-\Gamma_{f}) \left [ 1+ (1-\Gamma_{a})\Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau} \right]\nonumber\\
-\label{eq4}
-\end{eqnarray}
-\begin{eqnarray}
-V_{2} & = & A V_{sky}(1-\Gamma_{f}) + A V_{sky} \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau} (1-\Gamma_{f})^{2}exp({2\pi i \nu \vec{b}.\hat{s} \over c} )\nonumber\\
-         & = & A V_{sky} (1-\Gamma_{f}) \left [ 1+(1-\Gamma_{a}) \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau}  \right]exp({2\pi i \nu \vec{b}.\hat{s} \over c} )\nonumber\\
-\label{eq5}
-\end{eqnarray}
-Frequency as well as angular dependence of the quantities are not written explicitly for notational simplicity. 
-The two antennas are assumed to have identical beam pattern which is $A_{1}=A_{2} =A$.
-We also absorb the common gain term $(1-\Gamma_{f})$ with antenna response $A$ and denote them as $A_{f}= A(1-\Gamma_{f})$ here after.
-Hence, the complex visibility could be,
+Quantitatively, if the incident power from the sky signal is $P_{sky}$, the feed
+reflection coefficient is $\Gamma_{f}$, and the dish reflection
+coefficient is $\Gamma_{d}$, then the net power entering the feed after an
+$n^{th}$ reflection off the feed and the dish is:
 
-\begin{eqnarray}
-V e^{i\phi}(\nu) & = & \int V_{1}V_{2}^{*} d\Omega \nonumber\\
-		        & = & \int |A_{f}|^{2}|V_{sky}|^{2} |\left [ 1+(1-\Gamma_{f}) \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau}  \right]|^{2} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega
-\label{eq6}		        
-\end{eqnarray}
-
- Furthermore, combining all the terms that contain instrument response we define a common instrument parameter, written as, 
-\begin{eqnarray}
-\Sigma(\vec \theta, \nu) & = & |A_{f}|^{2} |\left [ 1+ (1-\Gamma_{f}) \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau} \right]|^{2}\nonumber\\
- 	    & = &  |A_{f}|^{2}  \left[ 1+ |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} + 2 \Re \left ( (1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{2\pi i\nu \Delta \tau} \right) \right] 
-\label{eq{7}}	    
-\end{eqnarray}
-
-Instrumental response function acquires additional terms arising due to correlation between the directed and reflected component of the sky signal.
-The total visibility at any frequency would be the sum of the three visibilities contributed by three sources of correlated power.
-First term in the square bracket represents the cross correlation between the two antenna outputs contributed by the sky signal upon first direct incidence.
-The second term results from the cross correlation between two reflected signals in each antenna.The last term represents the cross correlation between the first direct incident signal of one antenna and the first reflected signal from the other antenna and vice versa.
-
-Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum. 
- Fourier transform of the visibility contributed by any two voltage components from two antennas with no mutual delay is centred at a delay $\tau = \tau_{g}$ in the delay spectrum whereas any two voltage components from two antennas components having a mutual delay of $\Delta \tau$ will be centred at $\tau_{g} +\Delta \tau$.
-Therefore, the correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal thus extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected.
-Also, any reflections arriving at the feed at any non-zero  value of the delay $\Delta \tau$ which could be the result of reflections from the feed structures would also generate non zero delay response at those delays.
-If the dish vertex is so constructed such that the reflection from the dish vertex is negligible i.e, $\Gamma_{d}<<1\ or = 0$ then the second and the third term of the $\Sigma$ vanish.
-Also, if we assume a $\Gamma_{a} =-10dB$ and $\Gamma_{d}= -20dB$, the second term in the expression of $\Sigma(\vec \theta, \nu)$ becomes negligible compared to the first and the third term of the expression and, therefore, can be neglected.
-\\
-
-\subsection{Effect of higher order reflection on the delay spectrum} 
-Correlation between the higher order reflections of the signal in any antenna with the direct component of the other would result in a delay response at integral multiple of $\Delta \tau$ and vice versa.
-If $I_{sky}$ is reflected n times in between the feed and the dish, the net voltage entering the feed after an
-$n^{th}$ reflection off the feed and the dish is written as:
-\begin{equation}
-V_{1} =  A V_{sky}(1-\Gamma_{f})[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
-\end{equation}
-and,
-
-\begin{equation}
-V_{2} = A V_{sky}(1-\Gamma_{f})[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
+\begin{equation}\label{eqn:series1}
+P_{in} =  P_{sky}(1-\Gamma_{f})[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
 \end{equation}
 
-where $\Phi = 2\pi\nu\Delta \tau$.
-The relevant terms in the corresponding visibility and subsequently in the delay spectrum would be the ones which represent the correlation between the direct component of one antenna with the reflected components of the other resulting in higher order terms  in $\Sigma(\vec \theta, \nu)$.
-The corresponding instrument response may be written as,
-
-\begin{equation}
-\Sigma(\vec \theta, \nu) = A_{f} \left [ 1+ 2 \Re \left [(1-\Gamma_{f})( \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}) \right ]\right ]
-\end{equation}
-
-and the measured visibility spectrum, integrated over all sky would be, 
-\begin{equation}\label{eqn:series1}
-V_{meas}  = I_{sky}A_{f}\Sigma( \nu)
-\end{equation}
-
-The design specification of HERA elements requires that any
-signal, arriving at the feed at a delay $\Delta \tau$ with respect to the direct incidence, should be
-at the level of $-60dB$ at a delay of $60ns$ relative to the first incident
-signal at the feed \citep{parsons_deboer_memo}. This specification was
-approximated based on the power level of the cosmological signal in relation to
-foreground signals, which is estimated to be six orders of magnitude fainter
-\citep{santos_et_al2005,ali_et_al2008,deoliveira2008,jelic_et_al2008,bernardi_et_al2009,bernardi_et_al2010,ghosh_et_al2011}. Additionally, the $14m$ HERA baselines set a foreground containing
-horizon-limit (the wedge) that, with some buffer, sets a delay specification of
-$60ns$
-\citep{parsons_et_al2012b,vedantham_et_al2012,nithya_et_al2013,liu_et_al2014a,liu_et_al2014b}.
-Our goal is to determine the effect of the instrument response $\Sigma(\nu)$ on the delay spectrum measurement.
-\section{Measurements}
-We carried out reflectometry measurements at the HERA element prototype in Green
-Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise its performance. As HERA progresses as
-an experiment, it is necessary to build optimised dishes that aim to minimise the
-challenges of chromaticity in our quest for the Epoch of Reionization.
-
-As given in the previous section, if the incident power from the sky signal is $I_{sky}$, the feed
-reflection coefficient is $\Gamma_{f}$, and the dish reflection
-coefficient is $\Gamma_{d}$, then the net power entering the feed after
-$n^{th}$ reflection off the feed and the dish (i.e, the sky integrated visibility spectrum) is:
-
-\begin{equation}\label{eqn:series1}
-I_{meas} =  I_{sky}A_{f}[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
-\end{equation}
-
-where, $\phi = 2\pi i\nu \Delta \tau$ is the roundtrip propagation delay of a lightwave of frequency $\nu$ due to a reflection over the focal distance $l$.
+where, $\phi = 2l({2\pi \over c})\nu$ is the propagation delay of a lightwave of frequency $\nu$ due to a reflection over a focal distance $l$.
 It is noted that upon the first incidence, the sky signal is focussed onto the feed from the entire dish and the dish reflection coefficient $\Gamma_{d}$ is $1$ for this first incidence.
@@
 \begin{eqnarray}\label{eqn:ratio1}
-{I_{in} \over I_{sky} } & = & A_{f}[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}] \nonumber\\
-      & = & A_{f} \displaystyle\sum\limits_{n=0}^{n} [\Gamma_{f}\Gamma_{d}e^{i \phi}]^{n}\nonumber\\
-      & = & A_{f}+A_{f} \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i \phi}]^{n}
+{P_{in} \over P_{sky} } & = & (1-\Gamma_{f})[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}] \nonumber\\
+      & = & (1-\Gamma_{f}) \displaystyle\sum\limits_{n=0}^{n} [\Gamma_{f}\Gamma_{d}e^{i \phi}]^{n}\nonumber\\
+      & = & (1-\Gamma_{f})+(1-\Gamma_{f}) \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i \phi}]^{n}
 \end{eqnarray}
 
-In our experimental set-up, we use the feed as a transmitter and transmit a pulse. If the initial pulse is a broadband signal,
-$I_{tr}$, sent to the feed via a $75ft$ cable by a vector network
+The ratio in Equation \ref{eqn:ratio1} quantifies the amount of power received
+with respect to the incident sky power. Realistically, the incident sky power
+is not easily quantifiable, but it is a quantity we need to know to accurately
+characterize reflections.  
+%The right hand side of this equation consists of system parameters which are all chromatic i.e, functions of frequency.
+
+%Reflections cause the sky signal to appear at various delays. We aim to measure
+%the relative signal strength at those various delays, referred to as the
+%``delay spectrum" hereafter, to estimate levels of reflections in between the
+%feed and the dish apex.
+
+%We employ the reciprocity theorem for antennas in our experimental set-up.
+%More specifically, our experimental set-up differs from measuring sky signal
+%reflections since we send a pulse that is to be transmitted from the feed
+%before receiving it again. This results in a reversed situation - most of our
+%original signal is transmitted from the feed to be reflected from the dish,
+%while a small percentage reflects back down the cable (red arrows in Figure
+%\ref{fig:cartoon}). Therefore, since our measurement is carried out in
+%transmitting mode while an observation would be carried out in receiving mode,
+%we correct our results in order to map them to represent real observations.
+
+In our experimental set-up, instead of using sky signal, we employ
+our feed as a transmitter and transmit a pulse. If the initial pulse is a broadband signal,
+$P_{tr}$, sent to the feed via a $75ft$ cable by a vector network
 analyser (VNA), a delay domain measurement of the system is accomplished by
-taking the Fourier transform of the complex return loss of the feed measured by VNA. When the signal is incident on
+taking the Fourier transform of the measured complex return loss of the feed. When the signal is incident on
 the feed, part of the incident power ($\Gamma_{f}$) is reflected back to the
@@
 reflected back and forth in between the feed and the dish much like the sky
-signal reflection discussed previously.  Hence, if $I_{r}$ is the power
-incident back on the feed for the first time then the reflected power, $I_{refl}$,
+signal reflection discussed previously.  Hence, if $P_{r}$ is the power
+incident back on the feed for the first time then the reflected power, $P_{refl}$,
 back into the VNA would be:
@@
 \begin{equation}\label{eqn:series2}
-I_{refl} =  I_{r}A_{f}[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
+P_{refl} =  P_{r}(1-\Gamma_{f})[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
 \end{equation}
@@
 
-Recall that $I_{r}$ is the initial power that is incident back on the feed, which is just the feed radiated power reflected off the dish:
+Recall that $P_{r}$ is the initial power that is incident back on the feed, which is just the feed radiated power reflected off the dish:
 
 \begin{equation}
-I_{r}= \Gamma_{d}(1-\Gamma_f)e^{i\phi} I_{tr}
+P_{r}= \Gamma_{d}(1-\Gamma_f)e^{i\phi} P_{tr}
 \end{equation}
@@
 \begin{eqnarray}
-I_{ret} & = & \Gamma_{f}I_{tr} \nonumber\\ 
- & + &   \Gamma_{d}(1-\Gamma_f)e^{i\phi} I_{tr}(1-\Gamma_{f}) [1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]\nonumber\\
+P_{ret} & = & \Gamma_{f}P_{tr} \nonumber\\ 
+ & + &   \Gamma_{d}(1-\Gamma_f)e^{i\phi} P_{tr}(1-\Gamma_{f}) [1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]\nonumber\\
  \end{eqnarray}
@@
   \begin{eqnarray}\label{eqn:ratio2}
- {I_{ret} \over I_{tr} } & = & \Gamma_{f}
+ {P_{ret} \over P_{tr} } & = & \Gamma_{f}
   +  \Gamma_{d}(1-\Gamma_f)^{2} [e^{i\phi}+ \Gamma_{f}\Gamma_{d} e^{i2\phi}+  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{i n\phi}]\nonumber\\
@@
 
-The VNA measures the magnitude and phase of the quantity ${I_{ret}\over I_{tr}}$
+The VNA measures the magnitude and phase of the quantity ${P_{ret}\over P_{tr}}$
 as a function of frequency as shown in Figure \ref{fig:freq}. In our measurement
 set-up, the first reflection occurs at the feed $\Gamma_{f}$, so
-$({I_{ret} \over I_{tr} }  - \Gamma_{f}) $ gives an estimate of the delay
+$({P_{ret} \over P_{tr} }  - \Gamma_{f}) $ gives an estimate of the delay
 spectrum of the sky signal. In delay domain, the relative signal strength at
@@
 
-%\bibliographystyle{apj}
-%\bibliography{biblio.bib}
-\begin{thebibliography}{}
-
-\bibitem[Parsons \& Backer(2009)]{ParsonsBacker2009}
-Parsons, A., \& Backer, D. 2009, \apj, 138, 219
-\bibitem[Parsons et al.(2012)]{Parsons2012}
-Parsons, A., \& Pober, Jonathan C., \& Aguirre, James E., \& Carilli, Christopher L., \& Jacobs, Daniel C., \& Moore, David F. 2012, \apj 756, 165
-\end{thebibliography}{}
+\bibliographystyle{apj}
+\bibliography{biblio}
 
 \end{document}
-
-%\begin{eqnarray}
-%V e^{i\phi}(\nu) & = & \int |A_{f}|^{2}|V_{sky}|^{2}|exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \nonumber\\
-%&& +  \int |A_{f}|^{2}|V_{sky}|^{2} |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \nonumber\\
-%&& + \int |A_{f}|^{2}|V_{sky}|^{2}| 2 \Re \left ((1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right)exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega
-%\label{eq8}		        
-%\end{eqnarray}
-
-%\subsection{Effect of first reflection on the delay spectrum}
-%We define $B(\vec \theta, \nu) =  A^{2}(\vec \theta, \nu) $ as the cross power pattern of the interferometer and $\Sigma_{rr}(\nu), \Sigma_{dr}(\nu)$ are the correlation coefficient between the two reflected signals in each antenna and the direct signal of one antenna with the reflected signal from the other antenna in the uv plane i.e,
-
-%\begin{equation}
-%\Sigma_{rr}(\nu) =  \left [ |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} \right ]
-%\end{equation}
-
-%\begin{equation}
-%\Sigma_{dr}(\nu) = \left [ 2 \Re \left ((1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right) \right]
-%\end{equation}
-
-%and $\Delta \tau$ is the additional delay each reflected component suffers in addition to the intrinsic geometric delay 
-%$\tau_{g}$. Therefore, $\Sigma(\vec \theta, \nu) = B(\vec \theta, \nu) \left [ 1+\Sigma_{rr} +\Sigma_{dr} \right]$
-
-%As given in equation \ref{eq3}, the Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum.
-Hence, the all sky integrated delay spectrum could be written as,
-%\begin{eqnarray}
-%\mathcal{F} \left [V e^{i\phi}\right] & = & \int \left [\int B I_{sky}exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
-%&& + \int \left [  \int B I_{sky} \Sigma_{rr} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right] exp\left[ -2 \pi i\nu \tau \right] d\nu  \nonumber\\
-%&& +\int \left [ \int B I_{sky} \Sigma_{dr} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\	
-%&& + \int \left [  \int |A_{f}|^{2}|V_{sky}|^{2} |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right] exp\left[ -2 \pi i\nu \tau \right] d\nu  \nonumber\\
-%&& +\int \left [ \int |A_{f}|^{2}|V_{sky}|^{2} 2 \Re \left ((1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right)exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
-%			& = & \int \left [\int B I_{sky} exp({2\pi i \nu \tau_{g}} ) dl dm \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
-%&& + \int \left [  \int B I_{sky} \Sigma_{rr} exp({2\pi i \nu \tau_{g}} ) dl dm \right] exp\left[ -2 \pi i\nu \tau \right] d\nu  \nonumber\\
-%&& +\int \left [ \int B I_{sky} \Sigma_{dr} exp({2\pi i \nu \tau_{g}} ) dl dm \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
-%\label{eq9}
-%\end{eqnarray}
-%
-%\begin{eqnarray}			
-%\mathcal{F} \left [V e^{i\phi}\right] & = & \left [ B(\tau)\ast I_{sky}(\tau) \right ]\ast \delta(\tau+\tau_{g}) \nonumber\\
-%		&& +  \left [ B(\tau)\ast I_{sky}(\tau)* \Sigma_{rr}( \tau) \right ]\ast \delta(\tau+\tau_{g}) \nonumber\\
-%		&& +  \left [B(\tau)\ast I_{sky}(\tau)* \Sigma_{dr}( \tau) \right ]\ast \delta(\tau+\tau_{g}+ \Delta \tau)\nonumber\\
-%\label{eq10}
-%\end{eqnarray}
-
- %In words, the Fourier transform of the visibility contributed by any two voltage components from two antennas with no mutual delay is centred at a delay $\tau = \tau_{g}$ in the delay spectrum whereas any two voltage components from two antennas components having a mutual delay of $\Delta \tau$ will be centred at $\tau_{g} +\Delta \tau$.
-The correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal thus extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected.
-Also, any reflections arriving at the feed at any non-zero  value of the delay $\Delta \tau$ which could be the result of reflections from the feed structures would generate non zero delay response at those delays.

### 2015-11-04 DishReflectometry/Paper1_v0.tex

@@
 by sky noise \citep{XXX} and foregrounds four to five orders of magnitude
-brighter than the signal \citep{XXX}, 21~cm reionization experiments must
+brighter than the signal \citep{XXX}, 
+sky-averaged 21~cm monopole experiments such as
+(EDGES; \citealt{XXX}),
+(BIGHORNS; \citealt{XXX}),
+(SARAS; \citealt{patra_et_al2014}),
+(SCIHI; \citealt{voytek_et_al2014}),
+(HyPerion; \citealt{presley_et_al2015})
+% XXX others?
+and 21~cm reionization power spectrum experiments such as
+the LOw Frequency ARray (LOFAR; \citealt{XXX}),
+the Murchison Widefield Array (MWA; \citealt{XXX}),
+the Giant Metre-wave Radio Telescop (GMRT; \citealt{XXX}),
+the Donald C. Backer Precision Array to Probe the Epoch of Reionization (PAPER; \citealt{parsons_et_al2010}),
+the Hydrogen Epoch of Reionization Array (HERA; \citealt{XXX}),
+and the future Square Kilometre Array (SKA; \citealt{XXX})
+must
 furnish both collecting area and foreground suppression at levels significantly
@@
 
-One of the most problematic effects facing these experiments results form instrument
+One of the most problematic effects facing these experiments is instrument
 chromaticity.  The spectral dimension of 21~cm reionization experiments is of vital
@@
 The evolving response of a radio telescope --- either a single dish
-or an interferometer --- versus spectral frequency modulates spectrally smooth foregrounds ,
+or an interferometer --- versus spectral frequency modulates spectrally smooth foregrounds,
 contaminating spectral modes that might
 otherwise be used to measure reionization \citep{XXX}.  Moreover, the chromaticity of
-a telescope's response pattern scales linearly with diameter, putting the
+a telescope's response scales linearly with diameter, putting the
 needs of foreground suppression and signal sensitivity in direct tension with one
@@
 
-% XXX the wedge
+A major step forward for the field of 21~cm cosmology has been the development
+of a mathematical description of telescope chromaticity, how it varies with
+element separation (or telescope diameter), and what it implies for distinguishing
+foreground emission from the cosmological 21~cm signal \citep{XXX}.  The ``wedge'', as it is
+colloquially known, describes a linear relationship between the separation between elements
+in an interferometric baseline and the maximum line-of-sight Fourier mode\footnote{Assuming
+a flat sky, and using appropriate
+cosmological scalars,
+the spectral axis, $\nu$, and angle on the sky, $\vec\theta$, translate to coordinates in
+a three-dimensional volume at cosmological distances.  In describing the spatial power spectrum of
+emission in this volume $P(\vec k)$, we use the three-dimensional wave vector 
+$\vec k\equiv(k_\parallel,\vec k_\perp)$, where $k_\parallel$ is aligned with the
+spectral axis $\nu$, and $\vec k_\perp$ lies in the plane of the sky.}
+that may be occupied by smooth spectrum foreground emission.  At low-order $k_\parallel$ modes
+within the limits of the wedge,
+foreground contamination may be suppressed through a combination of calibration and model 
+subtraction.  However, calibration or modeling errors rapidly re-establish the characteristic
+wedge pattern.  Outside of the wedge, foreground contamination drops rapidly 
+\citep{pober_et_al2013,thargarajan_et_al2015}, provided that the spectral responses
+of antenna elements and analog electronics are sufficiently smooth\footnote{Here, we distinguish
+the chromaticity of the elements in isolation from the chromaticity inherent to
+element separation in an interferometric baseline.}.  In promising avoidance-based
+foreground strategy employed by PAPER \citep{parsons_et_al2014,ali_et_al2015}, these modes
+may be targeted as the lowest risk path for contraining 21~cm reionization in the near term.
+
+In this paper, we examine the performance of a new prototype HERA element in the context of
+this new wedge-based framework.  In coordination with \citet{XXXsisterpapers}, we compare 
+reflectometry measurements with
+a specification for the spectral performance of an element, given models of the relative brightness of
+foreground and 21~cm reionization modes in $k$-space.  
+% XXX document map
 

### 2015-11-04 DishBeamMeasurements/paper/DishBeamMeasurementsPaper.tex

--- 2015-11-04 DishMeasurements/memo/DishBeamMeasurementsPaper.tex
@@
 
-basics of 21cm cosmology
+%- basics of 21cm cosmology
+    - shedding light on the unobserved Dark Ages and Epoch of
+      Reionization when the first luminous sources formed and reionized
+      the IGM
+    - MWA, PAPER, LOFAR, GMRT power spectrum experiments
+    - also global signal experiments like XX,YY,ZZ,
+        - the big challenge is recovering the signal below 4-5 orders of
+      magnitude brighter foregrounds and noise
+    - naive requirement is collecting area
+    - naive foreground removal is to subtract all low $k_\parallel$ modes
 
-must use frequency structure to separate FGs from signal
-a certain amount of freq structure is imprinted onto smooth sources due to the frequency-dependent sampling function of an interferometer
-also by faraday rotation and the bandpass (citations)
+%- but instrumental frequency structure has been recognized as critical
+  => wedge
+    - of course the bandpass and intrinsic smooth freq structure of
+      sources
+    - but also the freq-dependent sampling of the IFO
+    - sources at different zenith angles appear at different delays,
+      and thus different $k_\parallel$, increasing linearly with baseline length
+    - this gives rise to the “wedge” in cylindrically averaged power
+      spectra ($k_\perp$, $k_\parallel$)
 
-leakage is due to bandpass, frequency flagging, finite bandwidth.
-can be mitigated by subtraction in the delay spectrum (CLEAN), giving up on wedge modes, or subtraction in image space with foreground modeling, likely will have to give up on wedge modes too unless have incredible calibration and imaging fidelity, as LOFAR is attempting.
-Large risk of signal loss and calibration-induced transfer of spectral structure from long baselines to short ones
+%- the beam affects the wedge
+    - Nithya et al quantify the effects of antenna beam on the wedge
+    - wider beams like the dipole have large response at large zenith
+      angle, and thus large delays, wedge much more filled out, and
+      much more emission close to the EOR window, at risk of leaking in
+    - narrower beams like the airy have much narrower response, most
+      received emission is from low delays (near $k_\parallel=0$)
+    - but even there, emission is seen at the edge of the wedge,
+      interpreted as an effective brightening of the horizon due to the
+      very large solid angle it subtends 
+    - this structure (lots of emission from zero delay, and peak at the
+      horizon), was termed the pitchfork
+    - highlights importance of beam characterization across the entire
+      sky
 
-hera is pursuing two relatively orthogonal power spectrum analyses (imaging and delay transform)
+%- the design of the HERA dish
+    - small D, large N technique was enabled by moore’s law
+    - even if processing hundreds to thousands of hours of data on
+      order hundred of antennas is technically possible with parallel
+      processing and advanced data quality metrics
+    - first generation experiments are aiming for a first detection of
+      the power spectrum, even more sensitivity will be needed to
+      characterize its evolution with redshift and k, and test models
+    - HERA has thus opted for larger elements, at the expense of a
+      smaller FOV, but most of our fourier modes come from freq
+      dimension anyway
+    - a dish is preferred to a large phased array (a la SKA) as a
+      simpler antenna, with fewer degrees of freedom and reduced
+      potential for ant-to-ant variation (Neben et al)
+    - of course, elevating a feed above a dish introduces potential for
+      reflections, and thus a wigglier bandpass than that of the MWA or
+      PAPER
+    - The other papers in this series set a wiggliness spec and present
+      measurements showing it meets the spec
+    - here we focus on the angular response of the dish, ie, its beam
+      pattern
 
-the other papers in this series quantify the degree of spectral structure induced by the dish bandpass in measurement and modeling, we focus in this section on foreground leakage due to the finite bandwidth as a function of the beam response at different delays in the sky.
-Nithya discuss this is detail nithya15,nithya15b
+%- how sensitive are we to accurate beam models?
+    - what must we show about the HERA Dish to confirm that it will
+      allow us to reach the science we want?
+    - large collecting area is a given
+    - minimal sidelobes and horizon response
+    - how accurately must we verify the beam model? different analyses
+      require different levels of beam modeling fidelity
+    - HERA’s hexagonal grid permits redundant baseline calibration
+      which is agnostic to the antenna beam, as long as all are the
+      same. ant-to-ant variation adds noise to the redundant
+      calibration, likely much smaller than that incurred in MWA sky
+      model calibration 
+    - the PAPER delay spectrum technique and 1D clean is even agnostic
+      to ant-to-ant variation, as it cleans out all sky emission within
+      the horizon limits on a per baseline basis
+    - an imaging analysis (a la MWA) relies on foreground subtraction,
+      and containment of residuals in the wedge, and the subtraction
+      step is much more sensitive both to accurate modeling of the mean
+      beam and to ant-to-ant variation (Neben et al)
+    - the general questions we address in this paper
+        - the questions are: does the main lobe shape agree with the
+          model (need good model for imaging and FG subtraction)
+        - are the sidelobe levels and horizon response sufficiently
+          small to mitigate pitchfork effect and foreground leakage?
 
-\citet{nithya15,nithya15b} 
-for a power spectrum analysis, note that these tests test how leakage varies as a function of the brightness of emission at different delays, not leakage due to beam frequency dependence (ie, either pattern or overall gain)
+%- roadmap
+    - we use orbcomm to measure the dish beam pattern and calculate
+      collecting area, verify the focus
+    - then we assess the science implications in delay space, comparing
+      different models and power spectrum approaches
 
-\section{ORBCOMM Beam Mapping System Review}
+\section{Experimental Setup}
+
+\subsection{HERA--Green Bank: A three-element prototype array}
+
+A 3-element HERA engineering prototype array is being constructed at the National Radio Astronomy Observatory--Green Bank.
+We performed the beam measurements presented in this work on the first of these to be constructed, future work will characterize how its in-situ beam in the presence of the other two dishes once they are constructed.
+Figure \ref{fig:aerial} shows the west-most HERA dish next to two planned dishes in Galford Meadow.
+The two reference antennas 100\,m are positioned due south with a 100\,m separation, and the Green Bank Telescope $\sim1$\,km northwest of the dish.
+The data acquisition system is installed in the hut labeled ``Launch point'' on the image.
+
+Note that unlike the full HERA site in the Karoo Desert Radio Astronomy Reserve in South Africa, the Green Bank site has obstructions such as trees and foothills, as well as moist ground with possibly non-uniform properties.
+All these will contribute to variation of the in-situ reference antenna relative to the electromagnetic model.
+We will discuss below how we quantify these systematics with ``null experiments'' which compare the beams of the two reference antennas.
+
+%\begin{figure*}[h]
+%\includegraphics[width=6.5in]{aerial.png}
+%\caption{Aerial photograph of the two reference dipoles deployed in Galford Meadow at the National Radio Astronomy Observatory--Green Bank 100\,m south of the HERA dish.}
+%\label{fig:aerial}
+%\end{figure*}
+
+\subsection{ORBCOMM Beam Mapping System Review}
 
@@
 
-\section{Beam Modeling}
-
-\subsection{Reference Antenna Modeling}
-Our power ratio measurement relies upon an accurately modeled reference dipole.
+%Our power ratio measurement relies upon an accurately modeled reference dipole.
 We are developing a more comprehensive model of the physical reference antenna and ground screen design, improving on that used in \citep{neben15}.
@@
 
-\subsection{Dish and Feed Modeling}
+\section{Dish Design and Modeling}
+
+\subsection{Design of the HERA Dish}
+
+design principles
+tradeoffs
+description of the final design
+
+\subsection{Dish Modeling}
 \label{sec:dishmodels}
@@
 	\item Airy pattern for a 14\,m aperture
-	\item CST simulation (\texttt{hera-cst/HERA\_DISH\_paper\_feed\_cyl36\_140mhz\_Y\_healpix.fits})
+	\item CST simulation (hera-cst/HERA\_DISH\_paper \_feed\_cyl36\_140mhz\_Y\_healpix.fits)
 	\item A separate simulation run by Dave with 68'' diameter feed backplane and 26'' skirt.
@@
 
-\section{Experimental Setup}
-
-A 3-element HERA engineering prototype array is being constructed at the National Radio Astronomy Observatory--Green Bank.
-We performed the beam measurements presented in this work on the first of these to be constructed, future work will characterize how its in-situ beam in the presence of the other two dishes once they are constructed.
-Figure \ref{fig:aerial} shows the west-most HERA dish next to two planned dishes in Galford Meadow.
-The two reference antennas 100\,m are positioned due south with a 100\,m separation, and the Green Bank Telescope $\sim1$\,km northwest of the dish.
-The data acquisition system is installed in the hut labeled ``Launch point'' on the image.
-
-Note that unlike the full HERA site in the Karoo Desert Radio Astronomy Reserve in South Africa, the Green Bank site has obstructions such as trees and foothills, as well as moist ground with possibly non-uniform properties.
-All these will contribute to variation of the in-situ reference antenna relative to the electromagnetic model.
-We will discuss below how we quantify these systematics with ``null experiments'' which compare the beams of the two reference antennas.
-
-\begin{figure*}[h]
-\includegraphics[width=6.5in]{aerial.png}
-\caption{Aerial photograph of the two reference dipoles deployed in Galford Meadow at the National Radio Astronomy Observatory--Green Bank 100\,m south of the HERA dish.}
-\label{fig:aerial}
-\end{figure*}
-
-\section{Assessing Systematics with a Null Experiment}
+\section{Error Analysis}
 
@@
 
-\begin{figure*}[h]
-\includegraphics[width=6.5in]{null1_rel.png}
-\caption{Top: ratio maps of the powers received by two reference dipoles separated by 50\,m, deployed 50\,m south of the HERA dish.
+%\begin{figure*}[h]
+%\includegraphics[width=6.5in]{null1_rel.png}
+%\caption{Top: ratio maps of the powers received by two reference dipoles separated by 50\,m, deployed 50\,m south of the HERA dish.
 Bottom: absolute beam power plots constructed by multiplying the relative power maps by a model beampattern.
 }
-\label{fig:null1}
-\end{figure*}
+%\label{fig:null1}
+%\end{figure*}
 
-\begin{figure*}[h]
-\includegraphics[width=6.5in]{null3_rel.png}
-\caption{Same as the previous null experiment except the south reference dipole was moved 5\,m west. The systematics are largely unchanged.}
-\label{fig:null3}
-\end{figure*}
+%\begin{figure*}[h]
+%\includegraphics[width=6.5in]{null3_rel.png}
+%\caption{Same as the previous null experiment except the south reference dipole was moved 5\,m west. The systematics are largely unchanged.}
+%\label{fig:null3}
+%\end{figure*}
 
-\begin{figure*}[h]
-\includegraphics[width=6.5in]{null4_rel.png}
-\caption{Same as the first null experiment except the reference dipoles are separated by 100\,m and deployed 100\,m south of the HERA dish.
+%\begin{figure*}[h]
+%\includegraphics[width=6.5in]{null4_rel.png}
+%\caption{Same as the first null experiment except the reference dipoles are separated by 100\,m and deployed 100\,m south of the HERA dish.
 The systematics remain at the few percent level near zenith and increase to $\sim10\%$ farther out, with somewhat, but not entirely different angular structure.
 }
-\label{fig:null4}
-\end{figure*}
+%\label{fig:null4}
+%\end{figure*}
 
-\section{Feed Measurements}
+%\section{Feed Measurements}
 
-Accurate modeling of both the dish and feed will be essential for final dish modeling.
+%Accurate modeling of both the dish and feed will be essential for final dish modeling.
 To that end, we deploy the feed on the ground facing the sky (Figure \ref{fig:feedpic}), replacing the north-most reference antenna in the \texttt{null3} configuration, to isolate the feed power pattern.
 
-Figure \ref{fig:feed0} shows the measured feed beams (top panel) and slices through the E and H planes (bottom panel).
+%Figure \ref{fig:feed0} shows the measured feed beams (top panel) and slices through the E and H planes (bottom panel).
 Due to intermittent connection problems to the DAQ computer, we collected only 157 high signal-to-background satellite passes over a few days.
@@
 
-\begin{figure*}[h]
-\includegraphics[width=5in]{feed.jpg}
-\caption{Feed deployed on the ground, facing the sky, replacing the north-most reference antenna in the \texttt{null3} configuration. }
-\label{fig:feedpic}
-\end{figure*}
+%\begin{figure*}[h]
+%\includegraphics[width=5in]{feed.jpg}
+%\caption{Feed deployed on the ground, facing the sky, replacing the north-most reference antenna in the \texttt{null3} configuration. }
+%\label{fig:feedpic}
+%\end{figure*}
 
-\begin{figure*}[h]
-\includegraphics[width=6.5in]{feed0_abs_old_ref_model.png}
-\caption{Measurements of the feed power pattern, deployed so it faces the sky.
+%\begin{figure*}[h]
+%\includegraphics[width=6.5in]{feed0_abs_old_ref_model.png}
+%\caption{Measurements of the feed power pattern, deployed so it faces the sky.
 The measurements agree well with the model for $\theta<55^\circ$, but start to diverge at large zenith angles, possibly due to quality control problems due to very sparse beam sampling.}
-\label{fig:feed0}
-\end{figure*}
+%\label{fig:feed0}
+%\end{figure*}
 
@@
 
-\begin{figure*}[h]
-\includegraphics[width=6.5in]{dish3_abs_old_ref_model.png}
-\caption{Dish power pattern with the feed lowered 0.5\,m below nominal focus.}
-\label{fig:dish3}
-\end{figure*}
+%\begin{figure*}[h]
+%\includegraphics[width=6.5in]{dish3_abs_old_ref_model.png}
+%\caption{Dish power pattern with the feed lowered 0.5\,m below nominal focus.}
+%\label{fig:dish3}
+%\end{figure*}
 
-\begin{figure*}[h]
-\includegraphics[width=6.5in]{dish1_abs_old_ref_model.png}
-\caption{Dish power pattern with the feed at the nominal focus of 4.5\,m.}
-\label{fig:dish1}
-\end{figure*}
+%\begin{figure*}[h]
+%\includegraphics[width=6.5in]{dish1_abs_old_ref_model.png}
+%\caption{Dish power pattern with the feed at the nominal focus of 4.5\,m.}
+%\label{fig:dish1}
+%\end{figure*}
 
-\begin{figure*}[h]
-\includegraphics[width=6.5in]{dish2_abs_old_ref_model.png}
-\caption{Dish power pattern with the feed raised 0.5\,m above nominal focus.}
-\label{fig:dish2}
-\end{figure*}
+%\begin{figure*}[h]
+%\includegraphics[width=6.5in]{dish2_abs_old_ref_model.png}
+%\caption{Dish power pattern with the feed raised 0.5\,m above nominal focus.}
+%\label{fig:dish2}
+%\end{figure*}
 
-\begin{figure*}[h]
-\includegraphics[width=6.5in]{dish4_abs_old_ref_model.png}
-\caption{Dish power pattern with the feed raised to its maximum height of 0.8\,m above nominal focus.}
-\label{fig:dish4}
-\end{figure*}
+%\begin{figure*}[h]
+%\includegraphics[width=6.5in]{dish4_abs_old_ref_model.png}
+%\caption{Dish power pattern with the feed raised to its maximum height of 0.8\,m above nominal focus.}
+%\label{fig:dish4}
+%\end{figure*}
 
@@
 
-\begin{figure}[h]
-\includegraphics[width=3.5in]{measbeam_raw.png}
-\includegraphics[width=3.5in]{measbeam_interp.png}
-\includegraphics[width=3.5in]{measbeam_interp_expcutoff.png}
-\caption{We construct full sky beams as required for Section \ref{sec:foregroundleakage} by starting from the nominal focus beam (top left), interpolating over unobserved cells at $\theta\lesssim60^\circ$ and extrapolating to the horizon (top right), and applying a gaussian cutoff starting at $\theta=60^\circ$ with $\sigma=2.5^\circ$ (bottom left).
+%\begin{figure}[h]
+%\includegraphics[width=3.5in]{measbeam_raw.png}
+%\includegraphics[width=3.5in]{measbeam_interp.png}
+%\includegraphics[width=3.5in]{measbeam_interp_expcutoff.png}
+%\caption{We construct full sky beams as required for Section \ref{sec:foregroundleakage} by starting from the nominal focus beam (top left), interpolating over unobserved cells at $\theta\lesssim60^\circ$ and extrapolating to the horizon (top right), and applying a gaussian cutoff starting at $\theta=60^\circ$ with $\sigma=2.5^\circ$ (bottom left).
 These last two beams span the space of likely horizon responses.
 Circles denote $\theta=20^\circ,40^\circ,60^\circ,80^\circ$.}
-\label{fig:interpbeams}
-\end{figure}
+%\label{fig:interpbeams}
+%\end{figure}
 
-\begin{figure}[h]
-\includegraphics[width=3.5in]{ew_beams_slice.pdf}
-\caption{We plot the interpolated/extrapolated measured nominal focus  beam itself (blue), and with the gaussian cutoff (cyan), along with various model beams to illustrate the varying horizon responses.
+%\begin{figure}[h]
+%\includegraphics[width=3.5in]{ew_beams_slice.pdf}
+%\caption{We plot the interpolated/extrapolated measured nominal focus  beam itself (blue), and with the gaussian cutoff (cyan), along with various model beams to illustrate the varying horizon responses.
 }
-\label{fig:interpbeamsslice}
-\end{figure}
+%\label{fig:interpbeamsslice}
+%\end{figure}
 
@@
 
-\begin{figure*}[h]
-\includegraphics[width=6.7in]{LST0deg_14m_42m_EWbaselines_dish1_blackman.png}
-\includegraphics[width=6.7in]{LST60deg_14m_42m_EWbaselines_dish1_blackman.png}
-\caption{Simulated delay spectra for the GSM and point sources at $0^\circ$ (top pair) and $60^\circ$ (bottom pair) LST for EW baselines of length 14\,m (left pair) and 42\,m (right pair).
+%\begin{figure*}[h]
+%\includegraphics[width=6.7in]{LST0deg_14m_42m_EWbaselines_dish1_blackman.png}
+%\includegraphics[width=6.7in]{LST60deg_14m_42m_EWbaselines_dish1_blackman.png}
+%\caption{Simulated delay spectra for the GSM and point sources at $0^\circ$ (top pair) and $60^\circ$ (bottom pair) LST for EW baselines of length 14\,m (left pair) and 42\,m (right pair).
 The beams are are assumed constant over frequency.}
-\label{fig:delayspec}
-\end{figure*}
+%\label{fig:delayspec}
+%\end{figure*}
 
-\begin{figure*}[h]
-\includegraphics[width=6.7in]{LST0deg_14m_42m_NEslantbaselines_dish1_blackman.png}
-\includegraphics[width=6.7in]{LST0deg_14m_42m_SEslantbaselines_dish1_blackman.png}
-\caption{Simulated delay spectra for the GSM and point sources at $0^\circ$ LST for NE (top pair) and SE (bottom pair) baselines of length 14\,m (left pair) and 42\,m (right pair).
+%\begin{figure*}[h]
+%\includegraphics[width=6.7in]{LST0deg_14m_42m_NEslantbaselines_dish1_blackman.png}
+%\includegraphics[width=6.7in]{LST0deg_14m_42m_SEslantbaselines_dish1_blackman.png}
+%\caption{Simulated delay spectra for the GSM and point sources at $0^\circ$ LST for NE (top pair) and SE (bottom pair) baselines of length 14\,m (left pair) and 42\,m (right pair).
 The beams are are assumed constant over frequency.}
-\label{fig:delayspec2}
-\end{figure*}
+%\label{fig:delayspec2}
+%\end{figure*}
 
-%\section{Discussion}
+\section{Discussion}
 
-%As expected, the Airy patter has the largest collecting area
-
-%the beam might be narrower simply because more dish is illuminated, but not necessarily a good thing, because we want more taper at the edge
-
-%comment on how this expt is still a work in progress
+add stuff here
 

### 2015-11-04 DishSimulations/code/computeW.py
added fisher matrix calculation and plots to draft of dish simulations paper

@@ -72,8 +72,8 @@ nSteps=len(steps)
 reStep=re.compile('step_[0-9]{1,2}')
 reNum=re.compile('[0-9]{1,2}')
 reGHz=re.compile('[0-9]{1,2}.[0-9]{5}')
-dirname=config['STEPPARAM']+'_Output/data/'
-plotdir=config['STEPPARAM']+'_Output/plots/'
+dirname=config['STEPPARAM']+'_'+config['LABEL']+'_Output/data/'
+plotdir=config['STEPPARAM']+'_'+config['LABEL']+'_Output/plots/'
 trackMode=config['TRACKMODE']
 if(trackMode=='TRACK'):
     track=trackMode+config['TRACK']+'hrs'
@@ -81,9 +81,9 @@ else:
     track=trackMode
 
 senseList=dirname+'senseList'+postfix+'.txt'
-
+print senseList
 senseList=open(senseList).readlines()
-dDeltaFile=config['STEPPARAM']+'_Output/data/dDelta_'+config['STEPPARAM']+'.npz'
+dDeltaFile=config['STEPPARAM']+'_'+config['LABEL']+'_Output/data/dDelta_'+config['STEPPARAM']+'.npz'
 derivMat=np.load(dDeltaFile)
 
 zAxis=derivMat['zAxis']
@@ -98,6 +98,7 @@ wMat2=np.zeros((nZ,nK))
 errMat=np.zeros((nZ,nK))
 
 senseMat=[[ [] for nn in range(nZ)] for mm in range(nSteps)]
+
 
 #load up files
 for mm,fileName in enumerate(senseList):
@@ -143,7 +144,7 @@ for mm in range(nZ):
             if(not(np.any(np.isinf(dparams)))):
                 plt.plot(xFit,yFit,'bo',label='data')
                 plt.plot(xFit,xFit*params[0]+params[1],'-r',label='fit')
-                plt.savefig(config['STEPPARAM']+'_Output/plots/dSigma_k%d_z%d_%s_%s.png'%(nn,mm,config['ARRAY'],foregrounds))
+                plt.savefig(config['STEPPARAM']+'_'+config['LABEL']+'_Output/plots/dSigma_k%d_z%d_%s_%s.png'%(nn,mm,config['ARRAY'],foregrounds))
                 plt.close()
 #                if(np.abs(params[0])>3.*np.sqrt(dparams[0,0])):
[…]

### 2015-11-04 DishSimulations/code/computeW.sh

@@ -8,13 +8,13 @@ thisdir=$(pwd)
 if ! [ -d "${thisdir}/${STEPPARAM}_${LABEL}_Output" ]
 then
     mkdir ${thisdir}/${STEPPARAM}_${LABEL}_Output 
+    python computeDerivative.py ${config}
 fi
 #first determine the redshifts to compute sensitivity and power spectra at
 #than for each model, match redshifts and calculate sensitivity. 
 python redshiftFreqs.py ${ZMIN} ${ZMAX} ${DZ} ${thisdir}/${STEPPARAM}_${LABEL}_Output
 
 
-python computeDerivative.py ${config}
 #now run 21cmSense for each reshift
 #get number of steps by listing all run directories
 ls -d 21cmFAST_${STEPPARAM}_step*/>${STEPPARAM}_steplist.txt
@@ -60,13 +60,15 @@ do
     nchan=$(python ../../nChan.py ${bwidth} ${DF})
     echo "bwidth=${bwidth}"
     echo "nchan=${nchan}"
-    if [ "${SAMPLEV}" = "True" ]
+    if [ "${SAMPLEV}" = "False" ]
     then
-	eorFlag="--eor ${psName}"
-    else
 	eorFlag="--eor ps_zeros.txt"
+    else
+	eorFlag="--eor ${psName}"
     fi
+
     mink=$(python ../../mink.py ${z} ${MINDELAY})
+    echo "mink=${mink}"
     #generate sensitivity for pess,mod, and opt scenarios and 1 year of observing. 
     if [ "${ARRAY}" = "mwa" ]  || [ "${ARRAY}" = "lofar" ] 
     then

### 2015-11-05 DishReflectometry/Paper1_v0.tex
Tuesday update: Changed equation 4 and the text below

--- 2015-11-02 DishReflectometry/Paper1_v0.tex
@@
 resulting in the delay spctrum:
-\begin{equation}
-\tilde V(\vec b, \tau)  = \int\!\!\int{\bm(\thhat,\nu) I_\sky(\thhat,\nu) \ifngexp d\Omega~e^{-2\pi i\nu\tau} d\nu}
-						%   & = & \int \left [B(\tau)\ast I_{sky}(\tau) \ast \delta(\tau+\tau_{g}) \right ] dl dm	
+\begin{eqnarray}
+\tilde V(\vec b, \tau) & = & \int\!\!\int{\bm(\thhat,\nu) I_\sky(\thhat,\nu) \ifngexp d\Omega~e^{-2\pi i\nu\tau}d\nu}\nonumber\\	                        & = &   \int \left [ A(\vec b, \tau)\ast I_{sky}(\vec b, \tau) \ast \delta( \vec b, \tau )\right ] d\Omega
 \label{eq3}
-\end{equation}
-
-Hence, the delay spectrum, integrated over all sky would be written as, 
-\begin{eqnarray}
-\mathcal{F} \left [V e^{i\phi}\right]   & = &  \left [B(\tau)\ast I_{sky}(\tau) \ast \delta(\tau+\tau_{g}) \right ] 	
-\label{eq4}
 \end{eqnarray}
@@
 % XXX define tau_g
-the convolution being carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$.
-In words, the sky delay spectrum is convoluted with the delay spectrum of the instrument and is centred at a delay $\tau_{g}$.
+where $\tau_{g} = {\vec b \cdot \thhat \over c}$.
+The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$.
+In words, the sky delay spectrum is convoluted with the delay spectrum of the instrument.
+In the delay domain, the sky spectrum from any direction $\thhat$ would be located at $\tau = {\vec b \cdot \thhat \over c}$.
+Since the maximum geometric delay possible for a given base line would be    and is centred at a delay $\tau_{g}$.
 The projected geometric delay $\tau_{g}$ for a given baseline can vary from 0 to $\tau_{g}$.

### 2015-11-05 DishSimulations/paper/DishSimulationsPaper_v0.tex

@@
-\documentclass[twocolumn]{emulateapj}
+\documentclass[preprint]{emulateapj}
 \usepackage{amsmath}
@@
 Ewall-Wice Aaron\altaffilmark{1,2},
-Bradley Richard\altaffilmark{3,4},
+Abraham Neben\altaffilmark{1,2},
+Nipanjana Patra\altaffilmark{5},
+Thyagarajan Nithyanandan\altaffilmark{6},
+Richard Bradley\altaffilmark{3,4},
 Jacqueline Hewitt\altaffilmark{1,2},
@@
 Cheng Carina\altaffilmark{5},
-David Deboer\altaffilmark{5},
-Neben Abraham\altaffilmark{1,2},
+Deboer David\altaffilmark{5},
 Parsons Aaron\altaffilmark{5},
-Patra Nipanjana\altaffilmark{5},
-Thyagarajan Nithyanandan\altaffilmark{6},
+Venter Mariet\altaffilmark{7}
 and others.
@@
 \altaffiltext{6}{School of Earth and Space Exploration, Arizona State U.,
+\altaffiltext{7}{Stellenbosh}
 Tempe AZ}
@@
 \begin{figure}
-\includegraphics[width=.5\textwidth]{figures/DishSA.png}
+%\includegraphics[width=.5\textwidth]{figures/DishSA.png}
 \caption{The HERA primary antenna element-one of 19 undergoing currently taking the first observations in the Karoo in South Africa.
@@
 \begin{equation}
-v(t) = \sum_n r_n({\bf \hat{k}}) s({\bf \hat{k}},t - \tau_n)
+v_i(t) = \sum_n r_i({\bf \hat{k}},\tau_n) s({\bf \hat{k}},t - \tau_n)
 \end{equation}
@@
 \begin{equation}
-V'_{ij}(f) = \sum_{m,n} \int d \Omega R_{mn}({\bf \hat{k}}) e^{2 \pi i \Delta \tau_{mn}f} e^{2 \pi i {\bf u}_{ij} \cdot {\bf \hat{k}}} I(f,{\bf \hat{s}}),
+V'_{ij}(f) = \sum_{m,n} \int d \Omega R_{ij}({\bf \hat{k}},\Delta \tau_{mn}) e^{2 \pi i \Delta \tau_{mn}f} e^{2 \pi i {\bf u}_{ij} \cdot {\bf \hat{k}}} I(f,{\bf \hat{s}}),
 \end{equation}
-where $R_{mn}({\bf \hat{s}})=r_m r_n^*$, $I(f,{\bf \hat{s}})$ is the intensity of the signal on the sky, and can be decomposed into foregrounds and signal
+where $R_{ij}({\bf \hat{s}},\Delta \tau_{mn})=r_m r_n^*$, $I(f,{\bf \hat{s}})$ is the intensity of the signal on the sky, and can be decomposed into foregrounds and signal
 \begin{equation}
@@
 \end{equation}
-where $V_{ij}^{mn}$ is a visibility resulting from the effective primary beam, $R_{mn}({\bf \hat{k}})$, at delay $\Delta \tau_{mn}$ induced by the reflections.
+where $V_{ij}^{mn}$ is a visibility resulting from the effective primary beam, $R_{ij}({\bf \hat{k}},\Delta \tau_{mn})$, at delay $\Delta \tau_{mn}$ induced by the reflections.
 \begin{equation}
-V_{ij}^{mn} = \int d \Omega R_{mn}({\bf \hat{s}}) I(f,{\bf \hat{s}})e^{2 \pi i {\bf u}_{ij} \cdot {\bf \hat{s}}}
+V_{ij}^{mn} = \int d \Omega R_{ij}({\bf \hat{s}},\Delta \tau_{mn}) I(f,{\bf \hat{s}})e^{2 \pi i {\bf u}_{ij} \cdot {\bf \hat{s}}}
 \end{equation}
@@
 The following lines involve the translation of the signal (including foregrounds and signal) out to the delay of each reflection and weighted by the effective primary beam of the reflection.
-Since each translated visibility is intrinsically $\sim 10^6$ times brighter than the signal, any reflection with a delay large enough to place it within the EoR window, must be sufficiently attenuated by $R_{mn}({\bf \hat{k}})$.
-The precise degree of attenuation is determined in \citep{Thyagarajan:2015c} using simulations of foregrounds and noise and sets the spec for our antenna.
+Since each translated visibility is intrinsically $\sim 10^6$ times brighter than the signal, any reflection with a delay large enough to place it within the EoR window, must be sufficiently attenuated by $R_{ij}({\bf \hat{k}},\Delta \tau_{mn})$.% The precise degree of attenuation is determined in \citep{Thyagarajan:2015c} using simulations of foregrounds and noise and sets the spec for our antenna.
 
-It is instructive to examine, in more detail, the case where $r_0$ at ($\tau=0$) is significantly greater than the other coefficients. Than we can approximate
+To get a better idea for what spec this sets on the voltage response of our dish we examine, in more detail, the case where $r_0$ at ($\tau=0$) is significantly greater than the other coefficients as we might expect for a dish with a relatively smooth gain.
+Than we can approximate equation \ref{eq:Reflections} to linear order in $r_i$,
 \begin{equation}
@@
 
-If we make the assumption that the beam can be factored into a frequency dependent and frequency dependent term, $a_m = a({\bf \hat{k}}) r_m$ than we have
+If we make the assumption that the beam can be factored into a frequency dependent and frequency dependent term, $r_i({\bf \hat{k}},\tau) = a_i({\bf \hat{k}}) g_i(\tau)$ than we have
 \begin{equation}
-\widetilde{V}_{ij} \approx \widetilde{V}_{ij}(\tau) + \sum_{m>0} r_m \widetilde{V}_{ij}(\tau - \tau_m)
+\widetilde{V}_{ij}' \approx \widetilde{V}_{ij}(\tau) + \sum_{m>0} r_m \widetilde{V}_{ij}(\tau - \tau_m)
 \end{equation}
- Hence, for a delay response dominated by the $0$-delay mode, as we might expect in our antenna element, the delay transformed visibilities are effectively convolved with the {\it voltage response}, not the voltage response squared as we might naively expect!
+ Hence, for a delay response dominated by the $0$-delay mode, as we might expect in an antenna element with smooth gain, the delay transformed visibilities are effectively convolved with the {\it voltage response}, not the square of the voltage response as we might naively expect.
+A more compact writing the impact of the spectral structure of a separable beam on foregrounds would be
+ \begin{equation}
+ 	\widetilde{V}_{ij}'(\tau) = \left[ (g_i \star g_j^*) \star \widetilde{V}_{ij}\right](\tau)
+ \end{equation}
+ As a result, one should compare the amplitude of the voltage delay response of the antenna with the ratio between foregrounds and signal when
 
- In this paper, we study $R_{mn}({\bf \hat{k}})$ for the HERA antenna element to verify that it both meets the spec and agrees with direct measurements of the antenna element with refelctometry \citep{Patra:2015} and Orbcomm measurements \citep{Neben:2015b}.
+ In this paper, we study $r_i({\bf \hat{k}},\Delta \tau)$ for the HERA antenna element to verify that it both meets the spec and agrees with direct measurements of the antenna element with refelctometry \citep{Patra:2015} and Orbcomm measurements \citep{Neben:2015b}.
+We also explore the implications of the performance of $r_i({\bf \hat{k}},\tau)$ on the scientific bottom line for EoR experiments, using the Fisher Matrix Formalism.
 
@@
 
+\begin{figure}
+\includegraphics[width=.5\textwidth]{figures/reionization_triangle_compare.pdf}
+\caption{95\% confidence interfals with and without reflections.
+The primary effect of a large minimal delay accessible is that  the ``knee" which is the primary lever on $R_\text{mfp}$ becomes inaccessible at low redshift.
+Since the comoving minimal $k$ corresponding to a minimal delay becomes smaller at higher redshift, EoX measurements do improve constraints on $R_\text{mfp}$.
+}
+\end{figure}
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{figures/sigmaVsZ.pdf}
+\caption{Fractional Errors on reionization and heating parameters as a function of maximal observed redshift.}
+\end{figure*}
+
+\begin{figure}
+\includegraphics[width=\textwidth]{figures/triangle_hera331.pdf}
+\caption{95\% confidence regions with and without reflections assuming that observations are taken over the redshifts between 5 and 25 are observed.}
+\end{figure}
+
 \section{Conclusions}

### 2015-11-05 DishBeamMeasurements/paper/DishBeamMeasurementsPaper.tex
wrote intro

@@
 
-\title{The Hydrogen Epoch of Reionization Array Dish: Beam Pattern Measurements and Science Implications}
+\title{The Hydrogen Epoch of Reionization Array Dish I: Beam Pattern Measurements and Science Implications}
 
@@
 \begin{abstract}
+THIS WILL NEED TO BE REWRITTEN
 We deploy the 137\,MHz ORBCOMM beam mapping system of \citet{neben15} at the site of the HERA prototype at NRAO--Green Bank.
@@
 \section{Introduction}
+%- basics of 21cm cosmology
+%    - shedding light on the unobserved Dark Ages and Epoch of
+%      Reionization when the first luminous sources formed and reionized
+%      the IGM
+%    - MWA, PAPER, LOFAR, GMRT power spectrum experiments
+%    - also global signal experiments like XX,YY,ZZ,
+%        - the big challenge is recovering the signal below 4-5 orders of
+%      magnitude brighter foregrounds and noise
+%    - naive requirement is collecting area
+%    - naive foreground removal is to subtract all low $k_\parallel$ modes
 
-%- basics of 21cm cosmology
-    - shedding light on the unobserved Dark Ages and Epoch of
-      Reionization when the first luminous sources formed and reionized
-      the IGM
-    - MWA, PAPER, LOFAR, GMRT power spectrum experiments
-    - also global signal experiments like XX,YY,ZZ,
-        - the big challenge is recovering the signal below 4-5 orders of
-      magnitude brighter foregrounds and noise
-    - naive requirement is collecting area
-    - naive foreground removal is to subtract all low $k_\parallel$ modes
+A new generation of low frequency radio telescopes is coming online with the goal of
+ probing redshifted 21\,cm emission from the Cosmic Dawn. These observations will 
+ complement indirect probes of the Dark Ages and Epoch of Reionization such as quasar 
+ sightlines, deep galaxy surveys, and the CMB optical depth which leave the reionization 
+ history of the universe only loosely constrained. Sensitivity and foreground removal are 
+ the main challenges in 21\,cm observations, as the expected cosmological signal is 4--5 
+ orders of magnitude fainter than Galactic and extragalactic foregrounds. Radio 
+ interferometers such as the MWA \citep{tingay13}, PAPER \citep{ali2015}, GMRT 
+ \citep{Paciga2011}, and LOFAR \citep{lofar} are seeking a first detection of 
+ cosmological 21\,cm emission in power spectrum measurements, where the smooth 
+ frequency evolution of the foreground emission distinguishes itself from the spectrally 
+ jagged cosmological signal whose frequency dimension is a redshift axis probing the 
+ inhomogenous reionizing universe.
 
-%- but instrumental frequency structure has been recognized as critical
-  => wedge
-    - of course the bandpass and intrinsic smooth freq structure of
-      sources
-    - but also the freq-dependent sampling of the IFO
-    - sources at different zenith angles appear at different delays,
-      and thus different $k_\parallel$, increasing linearly with baseline length
-    - this gives rise to the “wedge” in cylindrically averaged power
-      spectra ($k_\perp$, $k_\parallel$)
+%%- but instrumental frequency structure has been recognized as critical
+%  => wedge
+%    - of course the bandpass and intrinsic smooth freq structure of
+%      sources
+%    - but also the freq-dependent sampling of the IFO
+%    - sources at different zenith angles appear at different delays,
+%      and thus different $k_\parallel$, increasing linearly with baseline length
+%    - this gives rise to the “wedge” in cylindrically averaged power
+%      spectra ($k_\perp$, $k_\parallel$)
 
-%- the beam affects the wedge
-    - Nithya et al quantify the effects of antenna beam on the wedge
-    - wider beams like the dipole have large response at large zenith
-      angle, and thus large delays, wedge much more filled out, and
-      much more emission close to the EOR window, at risk of leaking in
-    - narrower beams like the airy have much narrower response, most
-      received emission is from low delays (near $k_\parallel=0$)
-    - but even there, emission is seen at the edge of the wedge,
-      interpreted as an effective brightening of the horizon due to the
-      very large solid angle it subtends 
-    - this structure (lots of emission from zero delay, and peak at the
-      horizon), was termed the pitchfork
-    - highlights importance of beam characterization across the entire
-      sky
+It was initially thought that the foreground emission would be confined to the lowest few 
+line of sight Fourier modes, however it was later realized that the spectral structure of the 
+interferometer's point spread function smears foreground power into a ``wedge''-shaped 
+region in  $(k_\perp,k_\parallel)$ Fourier space. The complement of this corrupted region 
+is known as the ``EOR Window''. Here ($k_\perp,k_\parallel$) represent spatial modes 
+perpendicular and parallel to the line of sight. This effect is straightforward to understand 
+for a single baseline which measures the sky intensity weighted by the complex sky fringe 
+$e^{i \vec{k}\cdot\vec{b}}$, where $\vec{k}=\vec{k}(\theta,\phi)$ is the wave vector of 
+the incident radiation and $\vec{b}$ is the baseline vector in meters. A source at zenith 
+has $\vec{k}\perp\vec{b}$, and so appears in the visibility without any apparent 
+frequency dependence; however the visibility for a source near the horizon in line with the 
+baseline is maximally frequency dependent, and proportional to $e^{2\pi i f b/c}$.
 
-%- the design of the HERA dish
-    - small D, large N technique was enabled by moore’s law
-    - even if processing hundreds to thousands of hours of data on
-      order hundred of antennas is technically possible with parallel
-      processing and advanced data quality metrics
-    - first generation experiments are aiming for a first detection of
-      the power spectrum, even more sensitivity will be needed to
-      characterize its evolution with redshift and k, and test models
-    - HERA has thus opted for larger elements, at the expense of a
-      smaller FOV, but most of our fourier modes come from freq
-      dimension anyway
-    - a dish is preferred to a large phased array (a la SKA) as a
-      simpler antenna, with fewer degrees of freedom and reduced
-      potential for ant-to-ant variation (Neben et al)
-    - of course, elevating a feed above a dish introduces potential for
-      reflections, and thus a wigglier bandpass than that of the MWA or
-      PAPER
-    - The other papers in this series set a wiggliness spec and present
-      measurements showing it meets the spec
-    - here we focus on the angular response of the dish, ie, its beam
-      pattern
+Thus sources at different positions relative to the baseline vector manifest different 
+frequency structure despite their intrinsically smooth spectra, but are geometrically limited 
+by the baseline length so that maximum affected $k_\parallel$ mode is proportional to the 
+baseline length, and thus to $k_\perp$. It is convenient to phrase this description in terms 
+of the delay in radiation arrival at the baseline's two antennas, $\tau$, where $\tau_
+\text{max}=b/c$. The interpretation is thus that sources at low delay have little frequency 
+structure, while those near $\tau=\tau_\text{max}$ acquire the maximum frequency 
+structure given the baseline length.
 
-%- how sensitive are we to accurate beam models?
-    - what must we show about the HERA Dish to confirm that it will
-      allow us to reach the science we want?
-    - large collecting area is a given
-    - minimal sidelobes and horizon response
-    - how accurately must we verify the beam model? different analyses
-      require different levels of beam modeling fidelity
-    - HERA’s hexagonal grid permits redundant baseline calibration
-      which is agnostic to the antenna beam, as long as all are the
-      same. ant-to-ant variation adds noise to the redundant
-      calibration, likely much smaller than that incurred in MWA sky
-      model calibration 
-    - the PAPER delay spectrum technique and 1D clean is even agnostic
-      to ant-to-ant variation, as it cleans out all sky emission within
-      the horizon limits on a per baseline basis
-    - an imaging analysis (a la MWA) relies on foreground subtraction,
-      and containment of residuals in the wedge, and the subtraction
-      step is much more sensitive both to accurate modeling of the mean
-      beam and to ant-to-ant variation (Neben et al)
-    - the general questions we address in this paper
-        - the questions are: does the main lobe shape agree with the
-          model (need good model for imaging and FG subtraction)
-        - are the sidelobe levels and horizon response sufficiently
-          small to mitigate pitchfork effect and foreground leakage?
+That sources acquire frequency dependence commensurate with their position in the sky 
+tells us already that the primary beam strongly affects the apparent frequency dependence 
+of the foregrounds. The high delay regions of the sky lie near the horizon while low delay 
+regions lie closer to zenith and also perpendicular to the baseline vector. \citet{nithya15} 
+simulate the foreground contamination seen with a dipole beam, a phased array of simple 
+dipoles, and a Airy dish, and find that the latter suffers minimal foreground contamination 
+into of nonzero $k_\parallel$ model due to its narrow main lobe and minimal sidelobe 
+levels. To be sure, all are subject to the same geometric limits on foreground frequency-
+dependence, the wedge, but the emission from high delay is better suppressed using the 
+Airy dish leaving much of the wedge effectively empty.
 
-%- roadmap
-    - we use orbcomm to measure the dish beam pattern and calculate
-      collecting area, verify the focus
-    - then we assess the science implications in delay space, comparing
-      different models and power spectrum approaches
+%%- the beam affects the wedge
+%    - Nithya et al quantify the effects of antenna beam on the wedge
+%    - wider beams like the dipole have large response at large zenith
+%      angle, and thus large delays, wedge much more filled out, and
+%      much more emission close to the EOR window, at risk of leaking in
+%    - narrower beams like the airy have much narrower response, most
+%      received emission is from low delays (near $k_\parallel=0$)
+%    - but even there, emission is seen at the edge of the wedge,
+%      interpreted as an effective brightening of the horizon due to the
+%      very large solid angle it subtends 
+%    - this structure (lots of emission from zero delay, and peak at the
+%      horizon), was termed the pitchfork
+%    - highlights importance of beam characterization across the entire
+%      sky
+
+In principle, it is irrelevant how empty or full the wedge is of foreground power as it is 
+perfectly contained in it, however the finite bandwidth and imperfect frequency bandpass 
+of real instruments smear power beyond the geometrical edge of the wedge into the EOR 
+window. Sources at higher delay appear closest to the edge of the wedge, and thus are 
+most at risk of leaking into the EOR window due to these effects. In fact, 
+\citet{nithya15,nithya15b} observe that while naively we might expect minimal emission 
+at the very edge of the wedge because typical near-horizon beam responses are so small, 
+two effects cause a relative brightening of emission at those maximal delays after the 
+decline away from zero delay, creating a characteristic ``pitchfork'' shape. This horizon 
+brightening is caused by the large solid angle subtended by the near-horizon regions of the 
+sky, and the apparent shortening of baselines when viewed on axis at these elevations. 
+This second effect makes intermediate length baselines sensitive to the very bright diffuse 
+emission they would not otherwise be sensitive due to its very weak coupling to longer 
+baselines. Together, these effects can over the decline in beam sensitivity near the horizon. 
+All these considerations highlight the antenna beam as a critical design parameter for 
+21\,cm observatories
+
+%%- the design of the HERA dish
+%    - small D, large N technique was enabled by moore’s law
+%    - even if processing hundreds to thousands of hours of data on
+%      order hundred of antennas is technically possible with parallel
+%      processing and advanced data quality metrics
+%    - first generation experiments are aiming for a first detection of
+%      the power spectrum, even more sensitivity will be needed to
+%      characterize its evolution with redshift and k, and test models
+%    - HERA has thus opted for larger elements, at the expense of a
+%      smaller FOV, but most of our fourier modes come from freq
+%      dimension anyway
+%    - a dish is preferred to a large phased array (a la SKA) as a
+%      simpler antenna, with fewer degrees of freedom and reduced
+%      potential for ant-to-ant variation (Neben et al)
+%    - of course, elevating a feed above a dish introduces potential for
+%      reflections, and thus a wigglier bandpass than that of the MWA or
+%      PAPER
+%    - The other papers in this series set a wiggliness spec and present
+%      measurements showing it meets the spec
+%    - here we focus on the angular response of the dish, ie, its beam
+%      pattern
+
+This is the XXth in a series of four papers detailing the HERA element. We focus on the 
+angular response of the dish and its implications for power spectrum measurements, 
+following reflectometry measurements of the dish frequency response by Patra et al. 
+(submitted), and simulations by Ewall-Wice et al. (submitted), as well as detailed 
+foreground simulations for HERA by Thyagarajan et al. (submitted). A general description to the design of the 
+HERA experiment from an engineering point of view is given by DeBoer et al. (submitted). In essence, we 
+require a large collecting area for
+ sensitivity and minimal sidelobes and horizon response without incurring the large cost per collecting 
+area of very large dishes. A dish is preferred to a large phased array as it has fewer degrees 
+of freedom and reduced potential of antenna-to-antenna variation (Neben et al 2015b, 
+submitted). These factors naturally lead to a 14\,m diameter parabolic dish with a dipole 
+feed suspended at prime focus. The 352 dishes are positioned in a compact, hexagonal 
+array permitting redundant baseline calibration and coherent integration in $
+\vec{k}$ space \citep{omniscope,ali2015}. 
+%The smaller field of view of the HERA dish relative to that of the PAPER dipole or the MWA tile does not limit sensitivity in Fourier space as most leverage on high $k$ modes is from line of sight modes anyway \citep{PoberNextGen}.
+
+%%- roadmap
+%    - we use orbcomm to measure the dish beam pattern and calculate
+%      collecting area, verify the focus
+%    - then we assess the science implications in delay space, comparing
+%      different models and power spectrum approaches
+%%- how sensitive are we to accurate beam models?
+%    - what must we show about the HERA dish to confirm that it will
+%      allow us to reach the science we want?
+%    - large collecting area is a given
+%    - minimal sidelobes and horizon response
+%    - how accurately must we verify the beam model? different analyses
+%      require different levels of beam modeling fidelity
+%    - HERA’s hexagonal grid permits redundant baseline calibration
+%      which is agnostic to the antenna beam, as long as all are the
+%      same. ant-to-ant variation adds noise to the redundant
+%      calibration, likely much smaller than that incurred in MWA sky
+%      model calibration 
+%    - the PAPER delay spectrum technique and 1D clean is even agnostic
+%      to ant-to-ant variation, as it cleans out all sky emission within
+%      the horizon limits on a per baseline basis
+%    - an imaging analysis (a la MWA) relies on foreground subtraction,
+%      and containment of residuals in the wedge, and the subtraction
+%      step is much more sensitive both to accurate modeling of the mean
+%      beam and to ant-to-ant variation (Neben et al)
+%    - the general questions we address in this paper
+%        - the questions are: does the main lobe shape agree with the
+%          model (need good model for imaging and FG subtraction)
+%        - are the sidelobe levels and horizon response sufficiently
+%          small to mitigate pitchfork effect and foreground leakage?
+
+In this paper we first characterize the angular response of a prototype HERA dish at the National Radio 
+Astronomy Observatory--Green Bank. We use the technique data acquisition system of \citet{neben15} to 
+measure the 137\,MHz beam pattern using the ORBCOMM satellite constellation, allowing beam 
+measurements down to roughly -35dB from zenith, corresponding to an elevation roughly $30^\circ$. We 
+perform these measurements with the feed suspended at different heights above the dish, and compare the 
+observed power patterns and collecting areas with models. We consider the science implications of these 
+results by simulating visibilities with these beam models, testing different models of the sub-$30^\circ$ 
+elevation beam response unprobed by our measurements. We run these simulations for baselines of different 
+lengths and orientations at different local sidereal times to study under when the leakage out of the wedge is 
+significant, and what regions of the EOR window are affected.
+
+In detail, we discuss the experimental setup of the beam mapping experiments and their systematics, then 
+review  the ORBCOMM beam measurement system, in Section 2. We discuss the electromagnetic design and 
+modeling of the dish in Section 3, present our power pattern measurements in Section 5. We conclude with 
+discussion in Section 6.
 
@@
 
-A 3-element HERA engineering prototype array is being constructed at the National Radio Astronomy Observatory--Green Bank.
-We performed the beam measurements presented in this work on the first of these to be constructed, future work will characterize how its in-situ beam in the presence of the other two dishes once they are constructed.
-Figure \ref{fig:aerial} shows the west-most HERA dish next to two planned dishes in Galford Meadow.
-The two reference antennas 100\,m are positioned due south with a 100\,m separation, and the Green Bank Telescope $\sim1$\,km northwest of the dish.
-The data acquisition system is installed in the hut labeled ``Launch point'' on the image.
+A 3-element HERA engineering prototype array is being constructed at the National Radio 
+Astronomy Observatory--Green Bank. We performed the beam measurements presented in 
+this work on the first of these to be constructed, future work will characterize how its in-
+situ beam in the presence of the other two dishes once they are constructed. Figure 
+\ref{fig:aerial} shows the west-most HERA dish next to two planned dishes in Galford 
+Meadow. The two reference antennas 100\,m are positioned due south with a 100\,m 
+separation, and the Green Bank Telescope $\sim1$\,km northwest of the dish. The data 
+acquisition system is installed in the hut labeled ``Launch point'' on the image.
 
-Note that unlike the full HERA site in the Karoo Desert Radio Astronomy Reserve in South Africa, the Green Bank site has obstructions such as trees and foothills, as well as moist ground with possibly non-uniform properties.
-All these will contribute to variation of the in-situ reference antenna relative to the electromagnetic model.
-We will discuss below how we quantify these systematics with ``null experiments'' which compare the beams of the two reference antennas.
+Note that unlike the full HERA site in the Karoo Desert Radio Astronomy Reserve in 
+South Africa, the Green Bank site has obstructions such as trees and foothills, as well as 
+moist ground with possibly non-uniform properties. All these will contribute to variation 
+of the in-situ reference antenna relative to the electromagnetic model. We will discuss 
+below how we quantify these systematics with ``null experiments'' which compare the 
+beams of the two reference antennas.
 
@@
 
-We briefly review the beam mapping system detailed by \citet{neben15}, then discuss application of system to the prototype HERA array at NRAO--Green Bank.
-The system takes advantage of the 137\,MHz communications satellites operated by ORBCOMM Inc.
-as bright point sources which, by virtue of their number ($\sim30$), short orbital periods ($\sim90$ minutes), and orbital precession cover 65\% of the visible sky in just a few days.
-The coverage is limited by the fact that the satellites' orbital inclinations are all less than $45^\circ$.
+We briefly review the beam mapping system detailed by \citet{neben15}, then discuss 
+application of system to the prototype HERA array at NRAO--Green Bank. The system 
+takes advantage of the 137\,MHz communications satellites operated by ORBCOMM Inc. 
+as bright point sources which, by virtue of their number ($\sim30$), short orbital periods 
+($\sim90$ minutes), and orbital precession cover 65\% of the visible sky in just a few 
+days. The coverage is limited by the fact that the satellites' orbital inclinations are all less 
+than $45^\circ$.
 
-In contrast to celestial source beam measurements, though, where the flux may be assumed constant over the timescale of the measurement, satellite fluxes can vary rapidly due to varying distance, orientation, and transmission power.
-To correct for this, we measure the satellite flux in each ground polarization (EW and NS) using a simple, well-modeled reference antenna.
-Comparison of this measured power with that observed in the Antenna-Under-Test (AUT) gives the AUT beam response in the direction of the satellite.
-An equivalent interpretation is that the power ratio between the AUT and the reference antenna gives the relative beam response in the satellite direction, and multiplication by the reference antenna model yields the desired AUT response.
-As discussed in \citet{neben15}, despite the fact that satellite signals are generally polarized, this procedure.
+In contrast to celestial source beam measurements, though, where the flux may be 
+assumed constant over the timescale of the measurement, satellite fluxes can vary rapidly 
+due to varying distance, orientation, and transmission power. To correct for this, we 
+measure the satellite flux in each ground polarization (EW and NS) using a simple, well-
+modeled reference antenna. Comparison of this measured power with that observed in the 
+Antenna-Under-Test (AUT) gives the AUT beam response in the direction of the satellite. 
+An equivalent interpretation is that the power ratio between the AUT and the reference 
+antenna gives the relative beam response in the satellite direction, and multiplication by 
+the reference antenna model yields the desired AUT response. As discussed in 
+\citet{neben15}, despite the fact that satellite signals are generally polarized, this 
+procedure.
 
-In detail, we measure the dual-polarization RMS powers for each antenna in 512 2\,kHz bands across the 137--138\,MHz band.
-Each channel power is averaged over $\sim0.2$\,sec.
-There are 0--3 satellites above the horizon at any given time transmitting on different $\sim15$\,kHz wide sub-bands in 137--138\,MHz.
-By observing at many different frequencies, we probe the beam response in all these directions simultaneously.
-We compute the satellite positions using the orbital elements published by Celestrak\footnote{http://www.celestrak.com/NORAD/elements/orbcomm.txt} and the orbital integrator \texttt{predict}\footnote{http://www.qsl.net/kd2bd/predict.html}.
-However, the satellite frequencies vary occasionally to avoid interference within the constellation.
-\citet{zheng14} use interferometric phases to identify and exclude times when multiple satellites are in view.
-As our data acquisition system makes only total power measurements, we instead use an ORBCOMM interface box (typically supplied to commercial users of the network) to sync with passing satellites and record their identifier and transmission frequency.
+In detail, we measure the dual-polarization RMS powers for each antenna in 512 2\,kHz 
+bands across the 137--138\,MHz band. Each channel power is averaged over $\sim0.2$
+\,sec. There are 0--3 satellites above the horizon at any given time transmitting on different 
+$\sim15$\,kHz wide sub-bands in 137--138\,MHz. By observing at many different 
+frequencies, we probe the beam response in all these directions simultaneously. We 
+compute the satellite positions using the orbital elements published by Celestrak
+\footnote{http://www.celestrak.com/NORAD/elements/orbcomm.txt} and the orbital 
+integrator \texttt{predict}\footnote{http://www.qsl.net/kd2bd/predict.html}. However, the 
+satellite frequencies vary occasionally to avoid interference within the constellation. 
+\citet{zheng14} use interferometric phases to identify and exclude times when multiple 
+satellites are in view. As our data acquisition system makes only total power 
+measurements, we instead use an ORBCOMM interface box (typically supplied to 
+commercial users of the network) to sync with passing satellites and record their identifier 
+and transmission frequency.
 
-In this way, beam measurements are built up along satellite tracks over the course of several days of integration, yielding typically 200--300 satellite pass.
-Each pass is processed separately to identify and exclude times of low signal-to-background when the satellite is low in the sky or in the off state of of a pulsing sequence.
-At those times, then satellite flux no longer dominates over that of the diffuse Galactic background, and a power measurement no longer probes the response in the satellite direction.
-The beam measurements are then gridded in horizontal coordinates in HEALPix with a resolution of $1.8^\circ$ (nside=32).
-As a last quality control step to reject errant beam measurements due to RFI, for instance, we keep only the central 90\% of $\sim50$ measured beam values in each HEALPix cell.
+In this way, beam measurements are built up along satellite tracks over the course of 
+several days of integration, yielding typically 200--300 satellite pass. Each pass is 
+processed separately to identify and exclude times of low signal-to-background when the 
+satellite is low in the sky or in the off state of of a pulsing sequence. At those times, then 
+satellite flux no longer dominates over that of the diffuse Galactic background, and a 
+power measurement no longer probes the response in the satellite direction. The beam 
+measurements are then gridded in horizontal coordinates in HEALPix with a resolution of 
+$1.8^\circ$ (nside=32). As a last quality control step to reject errant beam measurements 
+due to RFI, for instance, we keep only the central 90\% of $\sim50$ measured beam 
+values in each HEALPix cell.
 
@@
 
-\bibliography{DishBeamMeasurementsMemo}
+\bibliography{DishBeamMeasurements}
 

### 2015-11-06 DishBeamMeasurements/paper/DishBeamMeasurementsPaper.tex
remove aarons big file, and minor beam paper updates

@@
 
-This is the XXth in a series of four papers detailing the HERA element. We focus on the 
-angular response of the dish and its implications for power spectrum measurements, 
-following reflectometry measurements of the dish frequency response by Patra et al. 
-(submitted), and simulations by Ewall-Wice et al. (submitted), as well as detailed 
-foreground simulations for HERA by Thyagarajan et al. (submitted). A general description to the design of the 
+This is the first paper in a series of four papers detailing the HERA element. We focus on the 
+angular response of the dish and its implications for power spectrum measurements. The three companion 
+papers present reflectometry measurements (Patra et al., submitted) and simulations (Ewall-Wice et al., 
+submitted) of the dish frequency response, as well as detailed 
+foreground simulations for HERA (Thyagarajan et al., submitted). A general description to the design of the 
 HERA experiment from an engineering point of view is given by DeBoer et al. (submitted). In essence, we 

### 2015-11-06 data/plot_fg.py
Added Nithya's old sim cubes to data dir, along with a script

@@ -1,0 +1,101 @@
+#! /usr/bin/env python
+import numpy as n, pylab as p, capo as C, aipy as a
+import sys, scipy, csv
+
+# 'bl' -- baseline vectors of size 30x3 for 30 baselines and three columns for x,y,z
+# 'lst' -- LST during the drift scan. There are 40 LST samples at a cadence of 36 minutes thereby covering 24 hours
+# 'fg_lags' -- delays appropriate for foreground data of size n(fg_lags)
+# 'fg_power' -- Foreground power in power spectrum units and is an array of size n(bl) x n(fg_lags) x n(lst)
+# 'eor_lags' -- delays appropriate for EoR data of size n(eor_lags)
+# 'eor_power' -- EoR power in power spectrum units and is an array of size n(bl) x n(eor_lags) x n(lst)
+
+npz = n.load(sys.argv[-1])
+
+LST = 0
+
+dk_deta = C.pspec.dk_deta(9.) 
+bls = npz['bl']
+tau1 = npz['fg_lags'] * 1e9 # ns
+tau2 = npz['eor_lags'] * 1e9 # ns
+fg = npz['fg_power'] * 1e6 # mK^2
+eor = npz['eor_power'] * 1e6 # mK^2
+
+#C.arp.waterfall(n.average(fg[:3], axis=0)); p.show()
+fg = n.average(fg[...,:25], axis=-1)
+eor = n.average(eor, axis=-1)
+
+fg = n.average(fg[:3], axis=0)
+eor = n.average(eor[:3], axis=0)
+fg_mdl = n.where(fg > 1e7, fg, 0)
+
+for kpl_cut in [0.08, 0.1, 0.12][::-1]: # h Mpc^-1
+    tau_cut = kpl_cut / dk_deta
+    tau2_cut = n.argmin(n.abs(tau2 - tau_cut))
+    SZ = eor.shape[0]
+    eor_fold = 0.5 * (eor[SZ/2:] + eor[-SZ/2::-1])
+    tau_fold = tau2[SZ/2:]
+    eori = scipy.interpolate.interp1d(tau_fold, eor_fold, bounds_error=False)
+    print tau_cut
+    tau = n.linspace(0,500,1e3)
+    resp_bound = n.ones_like(tau)
+    for j,t in enumerate(tau1):
+        if fg_mdl[j] <= 0: continue
+        resp = n.sqrt(eori(tau+t) / fg_mdl[j])
+        resp = n.where(tau+t < tau_cut, 1, resp)
[…]

### 2015-11-06 DishSimulations/computeFisher.py
cleaning up junk

@@ -1,172 +1,0 @@
-#!/usr/bin/env python
-#compute fisher matrix for optimistic, pessimistic and fiducial foregrounds scenarios using both joint redshift constraints and for each redshift independently.Invert the fisher matrix to get the covariance matrix. Plot error ellipses and write out covariance matrices to text files for each
-#redshift
-#and joint over all redshifts. 
-
-import scipy.misc as misc
-import numpy as np
-import matplotlib
-import matplotlib.pyplot as plt
-import sys
-
-
-labelIndex={'ZETA_X':'$\\frac{\\Delta \\zeta_X}{\\zeta_X}$','X_RAY_Tvir_MIN':'$\\frac{\\Delta T_{vir}}{T_{vir}}$','X_RAY_SPEC_INDEX':'$\\frac{\\Delta \\alpha}{\\alpha}$','NU_X_THRESH':'$\\frac{\\Delta \\nu_{min}}{\\nu_{min}}$'}
-def readConfig(fileName):
-    """
-    read parser configuration file
-
-    """
-
-    # read pipeline parameters
-    print "=" * 50
-    print "Read configuration file " + fileName
-    config = {}
-    with open(fileName, "r") as cfile:
-        for line in cfile:
-            if line[0] != "#":
-                params = line.split("#")[0].split("=")  # split off comments
-                config[params[0]] = eval(params[1])
-    print config
-    return config
-
-#compute the fisher matrix for a list of wMatrices
-def computeCov(wList):
-    nParams=len(wList)
-    fisherMat=np.zeros((nParams,nParams))
-#    print 'wList=%s'%wList
-    for ii in range(nParams):
-        wList[ii][np.logical_or(np.isnan(wList[ii]),np.isinf(wList[ii]))]=0.#all nans set to zero. (where do they come from?)
-        for jj in range(ii+1):
-#            print 'product = %.2e'%(np.sum((wList[ii]*wList[jj]).flatten()))
-            fisherMat[ii,jj]=np.sum((wList[ii]*wList[jj]).flatten())
-            fisherMat[jj,ii]=fisherMat[ii,jj]
-    #invert fisherMat to get covariance matrix
-#    print fisherMat
-    try:
-        covMat=np.linalg.inv(fisherMat)
-    except:
-        print 'singular'
[…]

### 2015-11-06 DishSimulations/computeFisher.sh

@@ -1,12 +1,0 @@
-#!/bin/bash
-#compute fisher matrix from w vectors of various parameters
-#permit performing cuts in k and z and whether one wants to perform independent constraints 
-
-#config file has a list of parameters, a delta in frequency, a minimum redshift and a maximum redshift. Derive both independent constraints with each redshift interval or derive constraints from sums over redshift intervals. 
-config=$1
-
-#make directory to store outputs
-source ${config}
-echo ${DIRNAME}
-mkdir ./${DIRNAME}
-python computeFisher.py ${config}

### 2015-11-06 DishSimulations/computeOpticalDepth.py

@@ -1,18 +1,0 @@
-import numpy as np
-import scipy.interpolate as interp
-import scipy.integrate as integrate
-import cosmology as cosmo
-sigmaT=6.6524587e-25
-nfList=np.loadtxt('nfList.txt')
-zList=np.loadtxt('zList.txt')
-nfFunc=interp.interp1d(zList,nfList)
-def intFunc(x):
-    if(x<zList.min()):
-        return cosmo.baryon_n(x)*sigmaT*cosmo.DHcm*cosmo.de(x)/(1.+x)
-    elif(x>=zList.min() and x<=zList.max()):
-        return cosmo.baryon_n(x)*sigmaT*cosmo.DHcm*cosmo.de(x)/(1.+x)*(1.-nfFunc(x))
-    else:
-        return 0.
-        
-tauSum=quad(intFunc,0,zList.min())[0]+quad(intFunc,zList.min(),zList.max())[0]
-print tauSum

### 2015-11-06 DishSimulations/computeW.py

@@ -1,211 +1,0 @@
-#!/usr/bin/env python
-
-import numpy as np
-import sys
-import scipy.interpolate as interp
-import re
-import scipy.optimize as op
-import matplotlib.pyplot as plt
-import cosmology as cosmo
-
-print 'cosmo=%s'%(cosmo.__file__)
-
-littleh=0.68
-config,foregrounds=sys.argv[1],sys.argv[2]
-
-def pmLogPlot(y,ymin):
-    posVals=y>0.
-    negVals=y<0.
-    
-    
-
-
-
-#numerical recipes 2nd edition page 661
-def linFit(x,y,dy):
-    s=np.sum(1./dy**2.)
-    sx=np.sum(x/dy**2.)
-    sy=np.sum(y/dy**2.)
-    sxx=np.sum(x**2./dy**2.)
-    sxy=np.sum(x*y/dy**2.)
-    delta=s*sxx-(sx)**2.
-    a=(sxx*sy-sx*sxy)/delta
-    b=(s*sxy-sx*sy)/delta
-    sa=sxx/delta
-    sb=s/delta
-    csab=-sx/delta
-    covMat=np.array([[sb,csab],[csab,sa]])
-    return np.array([b,a]),covMat
-
-
-lowInd=4
-highInd=2
-def readConfig(fileName):
-    """
-    read parser configuration file
-
-    """
-
-    # read pipeline parameters
-    print "=" * 50
-    print "Read configuration file " + fileName
-    config = {}
-    with open(fileName, "r") as cfile:
-        for line in cfile:
-            if line[0] != "#":
-                params = line.split("#")[0].split("=")  # split off comments
-                print params
-                config[params[0]] = eval(params[1])
-    return config
-
-if(foregrounds=='mod'):
-    postfix='Mod'
-elif(foregrounds=='opt'):
-    postfix='Opt'
-elif(foregrounds=='pess'):
-    postfix='Pes'
-
-config=readConfig(config)
-steps=np.array(config['STEPFRACS'])
-dStep=config['DSTEP']
-nSteps=len(steps)
-reStep=re.compile('step_[0-9]{1,2}')
-reNum=re.compile('[0-9]{1,2}')
-reGHz=re.compile('[0-9]{1,2}.[0-9]{5}')
-dirname=config['STEPPARAM']+'_Output/data/'
-plotdir=config['STEPPARAM']+'_Output/plots/'
[…]

### 2015-11-06 DishSimulations/reWriteConfig.py

@@ -1,90 +1,0 @@
-#!/usr/bin/env python
-#Aaron Ewall-Wice
-#aaronew@mit.edu
-#May 13th 2015
-#Program to parse a 21cmFAST config file and replace parameters
-import numpy as np
-import sys
-import os.path
-def readConfig(fileName):
-    """
-    read parser configuration file
-
-    """
-
-    # read pipeline parameters
-    print "=" * 50
-    print "Read configuration file " + fileName
-    config = {}
-    with open(fileName, "r") as cfile:
-        for line in cfile:
-            if line[0] != "#":
-                params = line.split("#")[0].split("=")  # split off comments
-                config[params[0]] = eval(params[1])
-    print config
-    return config
-
-#replace a parameter in 21cmFAST config with val
-def replaceParam(fileName,outName,paramName,val):
-    sVal=str(val)
-       
-    fIn=open(fileName)
-    lines=fIn.readlines()
-    fIn.close()
-    
-    for mm,line in enumerate(lines):
-        tokens=line.split(' ')
-        if(len(tokens)>=4):
-            if(tokens[1]==paramName):
-                if(tokens[3][-1]=='\n'):
-                    tokens[3]=tokens[3][:-1]
-                line=line.replace(tokens[3],'('+sVal+'*'+tokens[3]+')')
-                lines[mm]=line
-    fOut=open(outName,'w')
-    for line in lines:
-        fOut.write(line)
-    fOut.close()
-
-def getParam(fileName,paramName):
-    fIn=open(fileName)
-    lines=fIn.readlines()
-    fIn.close()
-    
-    output=0.
-    for line in lines:
-        tokens=line.split(' ')
-        if(len(tokens)>4):
-            if(tokens[1]==paramName):
-                output=float(tokens[3])
-    return output
-
-
-def stepParam(configName):
-    #make a fractional step
-    config=readConfig(configName)
-    inFile='21cmFAST/Parameter_files/%s'%(config['PARAMFILE'])
-    paramName=config['STEPPARAM']
-    steps=config['STEPFRACS']
-    stepNums=config['STEPNUMS']
-    #generate steps
-    stepVals=[1.+steps[mm] for mm in range(len(steps))]
-    for mm in range(len(steps)):
-        dirName=os.getcwd()+'/'+paramName+'_step%d_Parameter_files'%(stepNums[mm])
[…]

### 2015-11-06 DishReflectometry/Paper1_v0.tex

@@
 % XXX define tau_g
-where $\tau_{g} = {\vec b \cdot \thhat \over c}$.
 The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$.
-In words, the sky delay spectrum is convoluted with the delay spectrum of the instrument.
-In the delay domain, the sky spectrum from any direction $\thhat$ would be located at $\tau = {\vec b \cdot \thhat \over c}$.
-Since the maximum geometric delay possible for a given base line would be    and is centred at a delay $\tau_{g}$.
-The projected geometric delay $\tau_{g}$ for a given baseline can vary from 0 to $\tau_{g}$.
-Also, due to frequency dependence of the sky signal, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with decaying amplitude [Ref to the figure Parsons12].
-Sky delay spectrum $I_{sky}(\tau)$ is contributed by the foreground  $I_{fg}(\tau)$ and the 21~cm power spectrum $I_{21}(\tau)$.
-Since $I_{fg}$ is spectrally smooth, whereas $I_{21}$ contains spectral structures, for wideband measurements, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces at higher delays and, therefore, at higher delays, the 21~cm delay spectrum is detectable.
-\textbf{[ Reference to Nithya's foreground simulation work, reference to any plots on the relative contribution of the  foreground and EoR signal.
-]}
+In words, the sky delay spectrum from any direction $\thhat$ is convoluted with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ in the delay domain.
+The maximum geometric delay possible for a given base line would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$ when the phase centre is halfway in between the two antennas.
+Hence, the sky contribution from any direction would be confined within $-\tau_{g}<\tau<\tau_{g}$.
+Due to chromaticity of the sky signal, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with decaying amplitude [Ref to the figure Parsons12].
+Sky delay spectrum $I_{sky}(\tau)$ is contributed by the foreground  $I_{fg}(\tau)$  which is spectrally smooth and the 21~cm power spectrum $I_{21}(\tau)$ which contains spectral signatures.
+Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces and the 21~cm delay spectrum is detectable.
+
+\subsection{Delay spectrum: An estimate of the 21cm power spectrum}
+Add text here. 
+ \textbf{[ Reference to Nithya's foreground simulation work, reference to any plots on the relative contribution of the  foreground and EoR signal. ]}
 
@@
 The voltage reflection coefficient of the reflector dish is denoted by $\Gamma_{d}$.
-Upon first incidence of the sky signal onto the dish, the entire sky signal would be reflected and focussed onto the feed.
+Upon first incidence of the sky signal onto the dish, it is reflected from the entire dish and is focussed onto the feed.
 Hence, for first incidence $\Gamma_{d}=1$.

### 2015-11-06 DishReflectometry/Paper1_v0.tex
adding the file names of reflectometry data.

@@
 \newcommand{\ifngexp}{{e^{-\frac{2\pi i\nu\vec{b}\cdot\thhat}{c}}}}
+\newcommand{\dfngexp}{{e^{2\pi i\nu \Delta \tau}}}
 \newcommand{\myemail}{skywalker@galaxy.far.far.away}
@@
 \begin{equation}
-\volt_{2} (\thhat, \nu)= \bmvolt_{2}(\thhat,\nu)\volt_\sky(\thhat,\nu)\fngexp\nonumber\\
+\volt_{2} (\thhat, \nu)= \bmvolt_{2}(\thhat,\nu)\volt_\sky(\thhat,\nu)\dfngexp\nonumber\\
 \end{equation}
@@
 Consider again a two element interferometer as described in section 2.
-Two antennas are assumed to be exactly identical so that their electrical parameters are same.
+Two antennas are assumed to be exactly identical so that their electrical parameters and the field pattern are identical i.e, $a_{1}(\thhat,\nu) = a_{2}(\thhat,\nu)$.
 We denote the voltage reflection coefficient of each feed by $\Gamma_{f}$.
@@
 \subsection{Effect of first order reflections on visibility and delay spectrum}
-Upon first incidence of the sky signal $V_{sky}$, $\Gamma_{f}$ fraction of the voltage is reflected off the feed while $(1-\Gamma_{f})$ fraction is coupled to the feed.
+Upon first incidence of the sky signal $\volt_{sky}$, $\Gamma_{f}$ fraction of the voltage is reflected off the feed while $(1-\Gamma_{f})$ fraction is coupled to the feed.
 The reflected voltage then further reflected off the dish and $(1-\Gamma_{f}) $ fraction of it reenters the feed with a roundtrip time delay $\Delta \tau$.
@@
 \begin{eqnarray}
-V_{1} & = & A V_{sky}(1-\Gamma_{f}) + A V_{sky} \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau}  (1-\Gamma_{f})^{2}\nonumber\\
-         & = & A V_{sky} (1-\Gamma_{f}) \left [ 1+ (1-\Gamma_{a})\Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau} \right]\nonumber\\
+\volt_{1} & = & a \volt_{sky}(1-\Gamma_{f}) + a \volt_{sky} \Gamma_{f} \Gamma_{d} \dfngexp  (1-\Gamma_{f})^{2}\nonumber\\
+         & = & a \volt_{sky} (1-\Gamma_{f}) \left [ 1+ (1-\Gamma_{a})\Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau} \right]\nonumber\\
 \label{eq4}
@@
 \begin{eqnarray}
-V_{2} & = & A V_{sky}(1-\Gamma_{f}) + A V_{sky} \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau} (1-\Gamma_{f})^{2}exp({2\pi i \nu \vec{b}.\hat{s} \over c} )\nonumber\\
-         & = & A V_{sky} (1-\Gamma_{f}) \left [ 1+(1-\Gamma_{a}) \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau}  \right]exp({2\pi i \nu \vec{b}.\hat{s} \over c} )\nonumber\\
+\volt_{2} & = & \left [ a \volt_{sky}(1-\Gamma_{f}) + a \volt_{sky} \Gamma_{f} \Gamma_{d} \dfngexp (1-\Gamma_{f})^{2}\right ] \fngexp \nonumber\\
+         & = & a \volt_{sky} (1-\Gamma_{f}) \left [ 1+(1-\Gamma_{a}) \Gamma_{f} \Gamma_{d} \dfngexp  \right] \fngexp \nonumber\\
 \label{eq5}
@@
 Frequency as well as angular dependence of the quantities are not written explicitly for notational simplicity.
-The two antennas are assumed to have identical beam pattern which is $A_{1}=A_{2} =A$.
-We also absorb the common gain term $(1-\Gamma_{f})$ with antenna response $A$ and denote them as $A_{f}= A(1-\Gamma_{f})$ here after.
+We also absorb the common gain term $(1-\Gamma_{f})$ with antenna field pattern $a$ and denote them as $a_{f}= a(1-\Gamma_{f})$ here after and define the antenna cross power pattern as $\bm_{f}(\thhat,\nu)=\bmvolt_{f}(\thhat,\nu)\bmvolt_{f}^{*}(\thhat,\nu)$ .
 Hence, the complex visibility could be,
@@
 \begin{eqnarray}
-V e^{i\phi}(\nu) & = & \int V_{1}V_{2}^{*} d\Omega \nonumber\\
-		        & = & \int |A_{f}|^{2}|V_{sky}|^{2} |\left [ 1+(1-\Gamma_{f}) \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau}  \right]|^{2} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega
+\vis(\vec b, \nu) & = & \int \volt_{1}\volt_{2}^{*} d\Omega \nonumber\\
+		        & = & \int \bm_{f} \volt_{sky}|^{2} |\left [ 1+(1-\Gamma_{f}) \Gamma_{f} \Gamma_{d} \dfngexp  \right]|^{2} \fngexp  d\Omega
 \label{eq6}		        
@@
 \begin{eqnarray}
-\Sigma(\vec \theta, \nu) & = & |A_{f}|^{2} |\left [ 1+ (1-\Gamma_{f}) \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau} \right]|^{2}\nonumber\\
- 	    & = &  |A_{f}|^{2}  \left[ 1+ |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} + 2 \Re \left ( (1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{2\pi i\nu \Delta \tau} \right) \right] 
+\Sigma(\vec b, \nu) & = & \bm_{f} |\left [ 1+ (1-\Gamma_{f}) \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau} \right]|^{2}\nonumber\\
+ 	    & = &  \bm_{f}  \left[ 1+ |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} + 2 \Re \left ( (1-\Gamma_{f})\Gamma_{f}\Gamma_{d} \dfngexp \right) \right] 
 \label{eq{7}}	    
@@
 Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum. 
- Fourier transform of the visibility contributed by any two voltage components from two antennas with no mutual delay is centred at a delay $\tau = \tau_{g}$ in the delay spectrum whereas any two voltage components from two antennas components having a mutual delay of $\Delta \tau$ will be centred at $\tau_{g} +\Delta \tau$.
-Therefore, the correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal thus extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected.
-Also, any reflections arriving at the feed at any non-zero  value of the delay $\Delta \tau$ which could be the result of reflections from the feed structures would also generate non zero delay response at those delays.
+ Fourier transform of the visibility contributed by any two voltage components from two antennas with no mutual delay will be located at the same delay $\tau $ in the Fourier domain whereas any two voltage components from two antennas components having a mutual delay of $\Delta \tau$ will be centred at $\Delta \tau$.
+This additional delay extends the upper limit on the maximum geometric delay $\tau_{g}$ to $(\tau_{g}+\Delta \tau)$.
+ Thus, the correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal thus extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected.
 If the dish vertex is so constructed such that the reflection from the dish vertex is negligible i.e, $\Gamma_{d}<<1\ or = 0$ then the second and the third term of the $\Sigma$ vanish.
-Also, if we assume a $\Gamma_{a} =-10dB$ and $\Gamma_{d}= -20dB$, the second term in the expression of $\Sigma(\vec \theta, \nu)$ becomes negligible compared to the first and the third term of the expression and, therefore, can be neglected.
+Also, if we assume a $\Gamma_{a} =-10dB$ and $\Gamma_{d}= -20dB$, the second term in the expression of $\Sigma(\vec b, \nu)$ becomes negligible compared to the first and the third term of the expression and, therefore, can be neglected.
 \\
@@
 \begin{equation}
-V_{1} =  A V_{sky}(1-\Gamma_{f})[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
+\volt_{1} =  a_{f} \volt_{sky}[1+ (1-\Gamma_{f})\Gamma_{f}\Gamma_{d} \dfngexp + (1-\Gamma_{f})^{2} (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ ....+ (1-\Gamma_{f})^{n}(\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}]
 \end{equation}
@@
 
-\begin{equation}
-V_{2} = A V_{sky}(1-\Gamma_{f})[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
-\end{equation}
+\begin{eqnarray}
+\volt_{2} & = &  a_{f} \volt_{sky}[1+ (1-\Gamma_{f})\Gamma_{f}\Gamma_{d} \dfngexp + (1-\Gamma_{f})^{2} (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
+&& ....+ (1-\Gamma_{f})^{n}(\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}] \ast \fngexp 
+\end{eqnarray}
 
 where $\Phi = 2\pi\nu\Delta \tau$.
-The relevant terms in the corresponding visibility and subsequently in the delay spectrum would be the ones which represent the correlation between the direct component of one antenna with the reflected components of the other resulting in higher order terms  in $\Sigma(\vec \theta, \nu)$.
+The relevant terms in the corresponding visibility and subsequently in the delay spectrum would be the ones which represent the correlation between the direct component of one antenna with the reflected components of the other resulting in higher order terms  in $\Sigma(\vec b, \nu)$.
 The corresponding instrument response may be written as,
@@
 \begin{equation}
-\Sigma(\vec \theta, \nu) = A_{f} \left [ 1+ 2 \Re \left [(1-\Gamma_{f})( \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}) \right ]\right ]
+\Sigma(\vec b, \nu) = a_{f} \left [ 1+ 2 \Re \left [(1-\Gamma_{f}) \Gamma_{f}\Gamma_{d} e^{i\phi}+ (1-\Gamma_{f})^{2}(\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+(1-\Gamma_{f})^{n} (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi} \right ]\right ]
 \end{equation}
@@
 \begin{equation}\label{eqn:series1}
-V_{meas}  = I_{sky}A_{f}\Sigma( \nu)
+\vis(\vec b, \nu)  = \int I_{sky}\Sigma(\vec b, \nu) d\Omega
 \end{equation}

### 2015-11-06 DishSimulations/paper/DishSimulationsPaper_v0.tex
added sensitivity plot

@@
-\documentclass[preprint]{emulateapj}
+\documentclass[onecolumn]{emulateapj}
 \usepackage{amsmath}
@@
 In this section, we show how reflections in the analogue signal path of an antenna lead to foreground contamination of the EoR window.
-HERA's primary antenna element consists of a sleeved dipole element suspended 5\,m above the focus of a 14\,m diameter parabolic dish (Fig.~\ref{fig:Dish}).
+Inuitively, any reflections in the signal path introduce sinusoidal ripples in the frequency dependent gain of the instrument.
+Since reflection delay is the Fourier dual to frequency, reflections at larger delays introduce ripples at higher frequencies.
+Isolation of the 21\,cm signal from foregrounds that are over five orders of magnitude brighter depends critically on the fact that their smoothness.
+Any sinusoidal frequency structure, introduced by the antenna gain will cause these foregrounds to mimic and swamp the signal unless they are brought below a level similar to the ratio between the foregrounds and the signal itself.
+We now derive this process in formal detail.
+We assume that the intensity field on the sky is given by
+\begin{equation}\label{eq:Dirac}
+I({\bf \widehat{k}},f) \delta_D({\bf \hat{k}} - {\bf \hat{k}'})= \langle s({\bf \hat{k}},f)s^*({\bf \hat{k}'},f)  \rangle_t^2
+\end{equation}
+ where $\delta_D$ is the Dirac delta function.
+We imagine that the electric field as a function of time, $\widetilde{s}({\bf \widehat{k}},t)$ arrives at an arbitrary origin at time $t$ and at the various $i^{th}$ antenna elements of an interferometer at locations ${\bf x_i}$ at times $\tau_i={\bf x_i} \cdot {\bf \widehat{k}} /c$.
+We now consider reflections within a single dish element described by a direction dependent reflection coefficient\footnote{Ignoring reflections between multiple dish elements which we treat in Appendix~\ref{app:Reflections}}, $\widetilde{r}_i({\bf \widehat{k}},\tau)$.
+which re-introduce the signal at later times $\tau$.
+The voltage signal measured at the $i^{th}$ antenna element, $\widetilde{v}_i$, is the integral over solid angle of the convolution of the electric field entering the antenna (delayed by $\tau_i$) with $r_i({\bf \widehat{k}},\tau')$.
 
-\begin{figure}
+\begin{equation}
+\widetilde{v}_i(t) = \int d \Omega \int d \tau \widetilde{r}_i({\bf \widehat{k}},\tau') \widetilde{s}({\bf \widehat{k}},t+\tau_i - \tau)
+\end{equation}
+
+ An FX (or XF) correlator measures the time-averaged product of the fourier transform of the voltage streams between the $i^{th}$ and $j^{th}$ antenna.
+Fourier transforming the voltage stream from the $i^{th}$ antenna we obtain
+\begin{equation}
+v_i(f) = \int d \Omega \int d \tau' \widetilde{r}_i({\bf \widehat{k}},\tau') s({\bf \widehat{k}},f)e^{2 \pi i f(\tau'-\tau_i)}
+\end{equation}
+The time averaged product between the two antennas is
+\begin{equation}
+V_{ij}'(f) = \left \langle v_i(f) v_j^*(f) \right \rangle_t = \int d \Omega \int d \tau \widetilde{r}_i(\tau) d \tau' \widetilde{r}^*_j(\tau')e^{2 \pi i f (\tau'-\tau) } I({\bf \widehat{k}}, f) e^{- 2 \pi i \Delta \tau_{ij}f}
+\end{equation}
+where $\Delta \tau_{ij} = \tau_i-\tau_j = ({\bf x_i - x_j}) \cdot {\bf \widehat{k}}/c$. We eliminated one of the solid angle integrals using equation~\ref{eq:Dirac}.
+
+Defining ${\bf u}_{ij} = f ({\bf x}_i-{\bf x}_j)/c$, we obtain,
+ %HERA's primary antenna element consists of a sleeved dipole element suspended 5\,m above the focus of a 14\,m diameter parabolic dish (Fig.~\ref{fig:Dish}).
+.
+%\begin{figure}
 %\includegraphics[width=.5\textwidth]{figures/DishSA.png}
-\caption{The HERA primary antenna element-one of 19 undergoing currently taking the first observations in the Karoo in South Africa.
+%\caption{The HERA primary antenna element-one of 19 undergoing currently taking the first observations in the Karoo in South Africa.
 The antenna consists of a sleeved dipole suspended within a 2\,m diameter skirt, five meters above the ground at the focal point of a 14\,m diameter dish.}\label{fig:Dish}
-\end{figure}
+%\end{figure}
 
- We show in Appendix~\ref{app:Reflections} that if an astronomical radio signal with time dependence at the location of the feed, $s({\bf \hat{k}},t)$, experience reflections within the dish such that the voltage recorded in the feed is
-\begin{equation}
-v_i(t) = \sum_n r_i({\bf \hat{k}},\tau_n) s({\bf \hat{k}},t - \tau_n)
-\end{equation}
+% We show in Appendix~\ref{app:Reflections} that if an astronomical radio signal with time dependence at the location of the feed, $s({\bf \widehat{k}},t)$, experience reflections within the dish such that the voltage recorded in the feed is
+
 Than the resulting visibilities obtained by cross correlating antenna $i$ and antenna $j$ are given by 
 \begin{equation}
-V'_{ij}(f) = \sum_{m,n} \int d \Omega R_{ij}({\bf \hat{k}},\Delta \tau_{mn}) e^{2 \pi i \Delta \tau_{mn}f} e^{2 \pi i {\bf u}_{ij} \cdot {\bf \hat{k}}} I(f,{\bf \hat{s}}),
+V'_{ij}(f) =  \int d \Omega r_i({\bf \widehat{k}},f) r^*_j({\bf \widehat{k}},f)  I(f,{\bf \widehat{s}})e^{2 \pi i {\bf u}_{ij} \cdot {\bf \widehat{k}}},
 \end{equation}
-where $R_{ij}({\bf \hat{s}},\Delta \tau_{mn})=r_m r_n^*$, $I(f,{\bf \hat{s}})$ is the intensity of the signal on the sky, and can be decomposed into foregrounds and signal
-\begin{equation}
-I(f,{\bf \hat{s}}) = I_{fg}(f,{\bf \hat{s}})+I_{21}(f,{\bf \hat{s}})
-\end{equation}
-While $I_{fg}$ is on the order of $10^6$ times larger than $I_{21}$, the continuum emission from foregrounds is expected to be spectrally smooth. Hence, a {\it delay transform} defined by
+where ${\bf u}_{ij} = ({\bf x}_i - {\bf x}_j ) f/c$ to use the usual $uv$ notation of interferometry.
+$r_i({\bf \hat{k}},f)$ is the inverse fourier transform of the reflection response of the dish, hence we see that the reflection response is precisely the Fourier dual to the Dish's frequency domain voltage beam.
+Setting a specification on reflections is hence equivalent to setting a specification on spectral smoothness.
+
+In order to separate spectrally smooth foregrounds from our signal, we expect to use the {\it delay transform} over frequency, defined as \citep{Parsons:2012}
 \begin{equation}
@@
 \end{equation}
-should, in principle, separate the foregrounds from the signal with foregrounds occupying the wedge.
-However, the introduction of the chromatic $e^{2 \pi i \Delta \tau_{mn}}$ terms leads to foreground contamination being convolved out to higher delays.
+Applying this to equation~\ref{eq:}
 \begin{equation}
@@
 \end{equation}
-where $V_{ij}^{mn}$ is a visibility resulting from the effective primary beam, $R_{ij}({\bf \hat{k}},\Delta \tau_{mn})$, at delay $\Delta \tau_{mn}$ induced by the reflections.
+where $V_{ij}^{mn}$ is a visibility resulting from the effective primary beam, $R_{ij}({\bf \widehat{k}},\Delta \tau_{mn})$, at delay $\Delta \tau_{mn}$ induced by the reflections.
 \begin{equation}
-V_{ij}^{mn} = \int d \Omega R_{ij}({\bf \hat{s}},\Delta \tau_{mn}) I(f,{\bf \hat{s}})e^{2 \pi i {\bf u}_{ij} \cdot {\bf \hat{s}}}
+V_{ij}^{mn} = \int d \Omega R_{ij}({\bf \widehat{s}},\Delta \tau_{mn}) I(f,{\bf \widehat{s}})e^{2 \pi i {\bf u}_{ij} \cdot {\bf \widehat{s}}}
 \end{equation}
@@
 The following lines involve the translation of the signal (including foregrounds and signal) out to the delay of each reflection and weighted by the effective primary beam of the reflection.
-Since each translated visibility is intrinsically $\sim 10^6$ times brighter than the signal, any reflection with a delay large enough to place it within the EoR window, must be sufficiently attenuated by $R_{ij}({\bf \hat{k}},\Delta \tau_{mn})$.% The precise degree of attenuation is determined in \citep{Thyagarajan:2015c} using simulations of foregrounds and noise and sets the spec for our antenna.
+Since each translated visibility is intrinsically $\sim 10^6$ times brighter than the signal, any reflection with a delay large enough to place it within the EoR window, must be sufficiently attenuated by $R_{ij}({\bf \widehat{k}},\Delta \tau_{mn})$.% The precise degree of attenuation is determined in \citep{Thyagarajan:2015c} using simulations of foregrounds and noise and sets the spec for our antenna.
 
@@
 
-If we make the assumption that the beam can be factored into a frequency dependent and frequency dependent term, $r_i({\bf \hat{k}},\tau) = a_i({\bf \hat{k}}) g_i(\tau)$ than we have
+If we make the assumption that the beam can be factored into a frequency dependent and frequency dependent term, $r_i({\bf \widehat{k}},\tau) = a_i({\bf \widehat{k}}) g_i(\tau)$ than we have
 \begin{equation}
@@
 
- In this paper, we study $r_i({\bf \hat{k}},\Delta \tau)$ for the HERA antenna element to verify that it both meets the spec and agrees with direct measurements of the antenna element with refelctometry \citep{Patra:2015} and Orbcomm measurements \citep{Neben:2015b}.
-We also explore the implications of the performance of $r_i({\bf \hat{k}},\tau)$ on the scientific bottom line for EoR experiments, using the Fisher Matrix Formalism.
+ In this paper, we study $r_i({\bf \widehat{k}},\Delta \tau)$ for the HERA antenna element to verify that it both meets the spec and agrees with direct measurements of the antenna element with refelctometry \citep{Patra:2015} and Orbcomm measurements \citep{Neben:2015b}.
+We also explore the implications of the performance of $r_i({\bf \widehat{k}},\tau)$ on the scientific bottom line for EoR experiments, using the Fisher Matrix Formalism.
 
@@
 \begin{figure}
+\includegraphics[width=.5\textwidth]{figures/sensitivity_comparison.pdf}
+\caption{Comparison between sensitivities with and without reflections.}
+\end{figure}
+
+\begin{figure}
 \includegraphics[width=.5\textwidth]{figures/reionization_triangle_compare.pdf}
@@
 \section{The Effect of Reflections and Cross-Talk on Visibilities}\label{app:Reflections}
-In this section, we develope formalism to discuss the impact of reflections of electromagnetic waves between antennas and within the signal chain of single antennas on foreground leakage in 21\,cm experiments.
-We start with the time varying electric field from a single source with location ${\bf \widehat{k}}$ on the sky, arriving at antenna $i$ with delay $\tau_i$ and antenna $j$ with delay $\tau_j$ with respect to the electric field at the origin which we denote as $s(t,{\bf \hat{s}})$.
-We allow for two different types of reflections: First, we allow reflections within the analogue path of each $i^{th}$ antenna which we denote as $r_i(\tau,{\bf \hat{s}})$.
-We also allow for single reflections between any $i-j$ antenna pair which we denote as $r_{ij}(\tau',{\bf \hat{s}})$.
+In this section, we investigate, formally, the impact of reflections of electromagnetic waves between antennas and within the signal chain of single antennas on foreground leakage in 21\,cm experiments.
+We start with the time varying electric field from a single source with location ${\bf \widehat{k}}$ on the sky, arriving at antenna $i$ with delay $\tau_i$ and antenna $j$ with delay $\tau_j$ with respect to the electric field at the origin which we denote as $s(t,{\bf \widehat{s}})$.
+We allow for two different types of reflections: First, we allow reflections within the analogue path of each $i^{th}$ antenna which we denote as $r_i(\tau,{\bf \widehat{s}})$.
+We also allow for single reflections between any $i-j$ antenna pair which we denote as $r_{ij}(\tau',{\bf \widehat{s}})$.
 Our choice of arbitrary $\tau'$, for now, allows for multi-path propogation between antennas, though we expect it to be dominated by the geometrical delay between the antenna pair.
@@
 \begin{equation}
-s_i(t,{\bf \hat{s}}) = \int d \tau' r_i(\tau',{\bf \hat{s}})s(t+\tau_i-\tau') + \sum_{j \ne i} \int d \tau' s(t + \tau_j - \tau_{ij}) r_{ij}(\tau',{\bf \hat{s}})
+s_i(t,{\bf \widehat{s}}) = \int d \tau' r_i(\tau',{\bf \widehat{s}})s(t+\tau_i-\tau') + \sum_{j \ne i} \int d \tau' s(t + \tau_j - \tau_{ij}) r_{ij}(\tau',{\bf \widehat{s}})
 \end{equation}  
@@
 \begin{equation}
-\widetilde{s}_i(f,{\bf \hat{s}}) = \widetilde{s}(f,{\bf \hat{s}}) \left[ \int d \tau' r_i(\tau',{\bf \hat{s}})e^{2 \pi i(\tau_i - \tau')f} + \sum_{j\ne i} \int d \tau' e^{2 \pi i(\tau_j - \tau_{ij})f} r_{ij}(\tau',{\bf \hat{s}}) \right]
+\widetilde{s}_i(f,{\bf \widehat{s}}) = \widetilde{s}(f,{\bf \widehat{s}}) \left[ \int d \tau' r_i(\tau',{\bf \widehat{s}})e^{2 \pi i(\tau_i - \tau')f} + \sum_{j\ne i} \int d \tau' e^{2 \pi i(\tau_j - \tau_{ij})f} r_{ij}(\tau',{\bf \widehat{s}}) \right]
 \end{equation}
@@
 \begin{align}\label{eq:SingleSource}
-v_{ij}'(f,{\bf \hat{s}}) & = \langle \widetilde{s}_i(f,{\bf \widehat{k}}) \widetilde{s}_j(f,{\bf \hat{s}}) \rangle_t \nonumber \\
-&=d \Omega  I(f,{\bf \hat{s}}) g_i(f) g_j^*(f) a_i(f,{\bf \hat{s}})a_j^*(f,{\bf \hat{s}}) e^{2 \pi i{\bf u_{ij}} \cdot {\bf \hat{s}}} + d \Omega I(f,{\bf \hat{s}}) \sum_{\ell \ne j} g_i(f)a_i(f,{\bf \hat{s}}) C_{\ell j}^*(f,{\bf \hat{s}}) e^{2 \pi i {\bf u_{\ell i} \cdot {\bf \hat{s}}}} \nonumber \\
-& + d \Omega I(f,{\bf \hat{s}})\sum_{k \ne i} g_j^*(f) a_j^*(f) C_{ki}(f,{\bf \hat{s}}) e^{2 \pi i {\bf u_{kj}\cdot {\bf \hat{s}}}} + d \Omega I(f,{\bf \hat{s}}) \sum_{k\ne i}\sum_{\ell \ne j} C_{ki}(f,{\bf \hat{s}}) C_{j\ell}^*(f,{\bf \hat{s}}) e^{2 \pi i {\bf u_{k\ell}}\cdot{\bf \hat{s}}},
+v_{ij}'(f,{\bf \widehat{s}}) & = \langle \widetilde{s}_i(f,{\bf \widehat{k}}) \widetilde{s}_j(f,{\bf \widehat{s}}) \rangle_t \nonumber \\
+&=d \Omega  I(f,{\bf \widehat{s}}) g_i(f) g_j^*(f) a_i(f,{\bf \widehat{s}})a_j^*(f,{\bf \widehat{s}}) e^{2 \pi i{\bf u_{ij}} \cdot {\bf \widehat{s}}} + d \Omega I(f,{\bf \widehat{s}}) \sum_{\ell \ne j} g_i(f)a_i(f,{\bf \widehat{s}}) C_{\ell j}^*(f,{\bf \widehat{s}}) e^{2 \pi i {\bf u_{\ell i} \cdot {\bf \widehat{s}}}} \nonumber \\
+& + d \Omega I(f,{\bf \widehat{s}})\sum_{k \ne i} g_j^*(f) a_j^*(f) C_{ki}(f,{\bf \widehat{s}}) e^{2 \pi i {\bf u_{kj}\cdot {\bf \widehat{s}}}} + d \Omega I(f,{\bf \widehat{s}}) \sum_{k\ne i}\sum_{\ell \ne j} C_{ki}(f,{\bf \widehat{s}}) C_{j\ell}^*(f,{\bf \widehat{s}}) e^{2 \pi i {\bf u_{k\ell}}\cdot{\bf \widehat{s}}},
 \end{align}
-where $g_i(f) a_i(f,{\bf \hat{s}}) = \int d \tau r_i(\tau,{\bf \hat{s}}) e^{2 \pi i f \tau}$ is the effective direction dependent gain of the system which can be factored into a directoin dependent and direction independent function where $g_i(f)$ is the gain of the analogue signal chain after the radiation has been absorbed by the feed and $a_i(f,{\bf \hat{s}})$ describes the chromatic electric field response of the antenna.
+where $g_i(f) a_i(f,{\bf \widehat{s}}) = \int d \tau r_i(\tau,{\bf \widehat{s}}) e^{2 \pi i f \tau}$ is the effective direction dependent gain of the system which can be factored into a directoin dependent and direction independent function where $g_i(f)$ is the gain of the analogue signal chain after the radiation has been absorbed by the feed and $a_i(f,{\bf \widehat{s}})$ describes the chromatic electric field response of the antenna.
 The first term in equation~\ref{eq:SingleSource} is an effective visibility with self-reflections.
 The two cross terms and the last term involve the mixing of visibilities complementary too the $ij$ baseline and have the potential to introduce significant chromatic features since they potentially insert visibilities on much longer basline lengths.
-Assuming propogation along a single path directly between the antennas, we may write $C_{ik}(f,{\bf \hat{s}})$ as
+Assuming propogation along a single path directly between the antennas, we may write $C_{ik}(f,{\bf \widehat{s}})$ as
 \begin{equation}
-C_{ki}(f,{\bf \hat{s}}) = a_i(f,{\bf \hat{s}}_{ki}) \frac{1}{r_{ik}}\left[\frac{d \sigma_k}{d \Omega}(f,{\bf \hat{s}},{\bf \hat{s}}_{ik})\right]^{1/2} e^{2 \pi i \tau_{ik} f}
+C_{ki}(f,{\bf \widehat{s}}) = a_i(f,{\bf \widehat{s}}_{ki}) \frac{1}{r_{ik}}\left[\frac{d \sigma_k}{d \Omega}(f,{\bf \widehat{s}},{\bf \widehat{s}}_{ik})\right]^{1/2} e^{2 \pi i \tau_{ik} f}
 \end{equation}
-Where $r_{ik}$ is the distance between antennas $i$ and $k$, $d \sigma_k (f,{\bf \hat{s}},{\bf \hat{s}}_{ij})/ d \Omega $ is the cross-section of the antenna to scatter radiation from the ${\bf \hat{s}}$ direction to the ${\bf \hat{s}}_{ik}$ direction where ${\bf \hat{s}}_{ik}$ is the unit vector in the direction between antenna $i$ and antenna $k$.
+Where $r_{ik}$ is the distance between antennas $i$ and $k$, $d \sigma_k (f,{\bf \widehat{s}},{\bf \widehat{s}}_{ij})/ d \Omega $ is the cross-section of the antenna to scatter radiation from the ${\bf \widehat{s}}$ direction to the ${\bf \widehat{s}}_{ik}$ direction where ${\bf \widehat{s}}_{ik}$ is the unit vector in the direction between antenna $i$ and antenna $k$.
 Integrating over the primary beam, we obtain a full expression on the effect of the foregrounds.
 \begin{align}
-V_{ij}' = \int d \Omega v_{ij}'(f,{\bf \hat{s}}) &= g_i(f) g_j(f)^* \int d \Omega A_{ij}(f,{\bf \hat{s}}) I(f,{\bf \hat{s}})e^{2 \pi i f {\bf u_{ij}} \cdot {\bf \hat{s}}} + g_i(f) \sum_{\ell \ne j} \int d \Omega  A_{i\ell j}(f,{\bf \hat{s}}) I(f,{\bf \hat{s}})e^{2 \pi i {\bf u_{\ell i} } \cdot {\bf \hat{s}} } \nonumber \\
-& + g_j^*(f) \sum_{k \ne i}  \int d \Omega A^*_{jki}(f,{\bf \hat{s}}) I({\bf \hat{s}},f) e^{2 \pi i {\bf u}_{kj} \cdot {\bf \hat{s}} } + \sum_{k \ne i} \sum_{\ell \ne j}\int d \Omega A_{k i \ell j}(f,{\bf \hat{s}}) I(f,{\bf \hat{s}})e^{2 \pi i {\bf u}_{k\ell} \cdot {\bf \hat{s}}}
+V_{ij}' = \int d \Omega v_{ij}'(f,{\bf \widehat{s}}) &= g_i(f) g_j(f)^* \int d \Omega A_{ij}(f,{\bf \widehat{s}}) I(f,{\bf \widehat{s}})e^{2 \pi i f {\bf u_{ij}} \cdot {\bf \widehat{s}}} + g_i(f) \sum_{\ell \ne j} \int d \Omega  A_{i\ell j}(f,{\bf \widehat{s}}) I(f,{\bf \widehat{s}})e^{2 \pi i {\bf u_{\ell i} } \cdot {\bf \widehat{s}} } \nonumber \\
+& + g_j^*(f) \sum_{k \ne i}  \int d \Omega A^*_{jki}(f,{\bf \widehat{s}}) I({\bf \widehat{s}},f) e^{2 \pi i {\bf u}_{kj} \cdot {\bf \widehat{s}} } + \sum_{k \ne i} \sum_{\ell \ne j}\int d \Omega A_{k i \ell j}(f,{\bf \widehat{s}}) I(f,{\bf \widehat{s}})e^{2 \pi i {\bf u}_{k\ell} \cdot {\bf \widehat{s}}}
 \end{align}
 which is essentially an ad-mixture of many baselines with different effective primary beams.
-We denote the effective primary beam of the $i,j$ antenna pair as $A_{ij}(f,{\bf \hat{s}})=a_i(f,{\bf \hat{s}})a_j^*(f,{\bf \hat{s}})$, the effective beam from a single reflection correlated with a direct measurement as $A_{i \ell j} = a_i(f,{\bf \hat{s}}) C^*_{\ell j}(f,{\bf \hat{s}})$ and the correlation between entirely reflected terms as experiencing an effective primary beam of $A_{k i \ell j}=C_{ki}(f,{\bf \hat{s}}) C^*_{j \ell}(f,{\bf \hat{s}})$.
+We denote the effective primary beam of the $i,j$ antenna pair as $A_{ij}(f,{\bf \widehat{s}})=a_i(f,{\bf \widehat{s}})a_j^*(f,{\bf \widehat{s}})$, the effective beam from a single reflection correlated with a direct measurement as $A_{i \ell j} = a_i(f,{\bf \widehat{s}}) C^*_{\ell j}(f,{\bf \widehat{s}})$ and the correlation between entirely reflected terms as experiencing an effective primary beam of $A_{k i \ell j}=C_{ki}(f,{\bf \widehat{s}}) C^*_{j \ell}(f,{\bf \widehat{s}})$.
 In this paper, we focus on the reflection terms within a single antenna element.
 Hence, we ignore all but the first term for now.
-Any reflection terms occurring downstream of the conversion by the feed from electromagnetic radiation to voltage are lumped into $g_i(f)$ and reflections occurring within the antenna element enter into $a_i(f,{\bf \hat{s}})$.
+Any reflection terms occurring downstream of the conversion by the feed from electromagnetic radiation to voltage are lumped into $g_i(f)$ and reflections occurring within the antenna element enter into $a_i(f,{\bf \widehat{s}})$.
 While reflections within the analogue system are a potential source of contamination, HERA's post-feed analogue signal path is designed to keep all reflections under 35\,m, within the wedge.
 
-The focus of this paper and its companions is the reflection properties of the primary antenna element, so we will focus the rest of our discussion here on $a_i(f,{\bf \hat{s}})$.
+The focus of this paper and its companions is the reflection properties of the primary antenna element, so we will focus the rest of our discussion here on $a_i(f,{\bf \widehat{s}})$.
 The primary elements of our dish include a feed and backplane suspended over a fourteen meter dish.
@@
 \begin{equation}
-a_i(f,{\bf \hat{s}}) = \sum_{n} r_n({\bf \hat{s}}) e^{2 \pi i  \tau_n f}
+a_i(f,{\bf \widehat{s}}) = \sum_{n} r_n({\bf \widehat{s}}) e^{2 \pi i  \tau_n f}
 \end{equation}
@@
 \begin{equation}
-A_{ij}(f,{\bf \hat{s}}) = \sum_m \sum_n r_n({\bf \hat{s}}) r_m^*({\bf \hat{s}}) e^{2 \pi i(\tau_n-\tau_m)f} = \sum_\alpha A_\alpha({\bf \hat{s}}) e^{2 \pi i \tau_\alpha}
+A_{ij}(f,{\bf \widehat{s}}) = \sum_m \sum_n r_n({\bf \widehat{s}}) r_m^*({\bf \widehat{s}}) e^{2 \pi i(\tau_n-\tau_m)f} = \sum_\alpha A_\alpha({\bf \widehat{s}}) e^{2 \pi i \tau_\alpha}
 \end{equation}
@@
 \begin{equation}
-V_{ij}'= \sum_\alpha \int d \Omega A_\alpha({\bf \hat{s}}) e^{2 \pi i \tau_\alpha f} e^{2 \pi i {\bf b}_{ij} \cdot {\bf \hat{s}}f/c} I(f,{\bf \hat{s}})
+V_{ij}'= \sum_\alpha \int d \Omega A_\alpha({\bf \widehat{s}}) e^{2 \pi i \tau_\alpha f} e^{2 \pi i {\bf b}_{ij} \cdot {\bf \widehat{s}}f/c} I(f,{\bf \widehat{s}})
 \end{equation}
@@
 \begin{equation}
-\widetilde{V}^\alpha_{ij}(\tau) = \int d \tau e^{-2 \pi i f \tau} \int d \Omega A_\alpha({\bf \hat{s}}) e^{2 \pi i {\bf b}_{ij} \cdot {\bf \hat{s}} f/c} I(f,{\bf \hat{s}})
+\widetilde{V}^\alpha_{ij}(\tau) = \int d \tau e^{-2 \pi i f \tau} \int d \Omega A_\alpha({\bf \widehat{s}}) e^{2 \pi i {\bf b}_{ij} \cdot {\bf \widehat{s}} f/c} I(f,{\bf \widehat{s}})
 \end{equation}

### 2015-11-06 DishReflectometry/Paper1_v0.tex
Edited last paragraph before section 3.2.

@@
 
- The Hydrogen Epoch of Reionization Array (HERA) is a proposed array consisting of 568 14-m dishes in South Africa which will measure the 21~cm power spectrum between 100 to 200~MHz .
+The Hydrogen Epoch of Reionization Array (HERA) is a proposed array consisting of 568 14-m dishes in South Africa which will measure the 21~cm power spectrum between 100 to 200~MHz.
 In this paper, we investigate the performance of the individual HERA elements and resulting contribution of the instrument response to the delay spectrum.
@@
  If the dish vertex is so constructed such that the reflection from the dish vertex is negligible i.e, $\Gamma_{d}<<1\ or = 0$ then the second and the third term of the $\Sigma$ vanish.
-Also, if we assume a $\Gamma_{a} =-10dB$ and $\Gamma_{d}= -20dB$, the second term in the expression of $\Sigma(\vec b, \nu)$ becomes negligible compared to the first and the third term of the expression and, therefore, can be neglected.
+Also, the second term in the expression of $\Sigma(\vec b, \nu)$ is negligible compared to the first and the third term of the expression and, therefore, can be neglected.
 \\

### 2015-11-07 DishSimulations/paper/DishSimulationsPaper_v0.tex
added delay smearing cartoons

@@
 We now derive this process in formal detail.
+A simple equation for effect of direction independent reflections in the signal chain of an interferometer, downstream of the receiver, has been derived in \citep{EwallWice:2015a}, we extend this analysis in this section by considering the direction dependent reflections that can occur within the antenna element.
 We assume that the intensity field on the sky is given by
@@
 \end{equation}
- where $\delta_D$ is the Dirac delta function.
+ where $\delta_D$ is the Dirac delta function and $\langle \rangle_t$ indicates an average in time.
 We imagine that the electric field as a function of time, $\widetilde{s}({\bf \widehat{k}},t)$ arrives at an arbitrary origin at time $t$ and at the various $i^{th}$ antenna elements of an interferometer at locations ${\bf x_i}$ at times $\tau_i={\bf x_i} \cdot {\bf \widehat{k}} /c$.
@@
 Than the resulting visibilities obtained by cross correlating antenna $i$ and antenna $j$ are given by 
-\begin{equation}
-V'_{ij}(f) =  \int d \Omega r_i({\bf \widehat{k}},f) r^*_j({\bf \widehat{k}},f)  I(f,{\bf \widehat{s}})e^{2 \pi i {\bf u}_{ij} \cdot {\bf \widehat{k}}},
+\begin{equation}\label{eq:Visibility}
+V'_{ij}(f) =  \int d \Omega r_i({\bf \widehat{k}},f) r^*_j({\bf \widehat{k}},f)  I(f,{\bf \widehat{s}})e^{2 \pi i f {\bf u}_{ij} \cdot {\bf \widehat{k}}/c},
 \end{equation}
-where ${\bf u}_{ij} = ({\bf x}_i - {\bf x}_j ) f/c$ to use the usual $uv$ notation of interferometry.
+where ${\bf b}_{ij} = ({\bf x}_i - {\bf x}_j )$ to use the usual $uv$ notation of interferometry.
 $r_i({\bf \hat{k}},f)$ is the inverse fourier transform of the reflection response of the dish, hence we see that the reflection response is precisely the Fourier dual to the Dish's frequency domain voltage beam.
-Setting a specification on reflections is hence equivalent to setting a specification on spectral smoothness.
+Setting a specification on reflections is hence equivalent to setting a specification on the spectral smoothness of the voltage beam.
 
@@
 \end{equation}
-Applying this to equation~\ref{eq:}
+Applying this to equation~\ref{eq:Visibility}, we obtain
 \begin{equation}
-\widetilde{V}_{ij}'(\tau) = \sum_{m,n} \widetilde{V}_{ij,FG}^{mn}(\tau - \Delta \tau_{mn}) + \widetilde{V}_{ij,21}^{mn}(\tau - \Delta \tau_{mn})
+\widetilde{V}'_{ij}(\tau)=  \int d \Omega \int d f  r_i({\bf \widehat{k}},f) r_j^*({\bf \widehat{k}},f)  I(f,{\bf \hat{k}}) e^{2 \pi i f ( {\bf b}_{ij} \cdot {\bf \hat{k}} /c - \tau)}
 \end{equation}
+Let's examine the quantity within the angular integral.
+For each ${\bf \hat{k}}$, we see that each source is mapped to a line $\tau ={\bf b}_{ij}\cdot{\bf \hat{k}}/c$, resulting in the much discussed ``wedge" \citep{Datta:2010,Vedantham:2012,Parsons:2012,Morales:2013,Thyagarajan:2013,Liu:2014a,Liu:2014b}.
+The presence of the frequency dependent beam causes each source line to be convolved in delay with the kernel
+\begin{equation}\label{eq:Kernel}
+\widetilde{R}_{ij}({\bf \hat{k}},\tau) = \int d \tau \widetilde{r}_i({\bf \hat{k}},\tau - \Delta \tau) \widetilde{r}_j({\bf \hat{k}},\Delta \tau).
+\end{equation}
+The beam has a different delay structure in each direction, and we demonstrate the effect of foreground smearing in Fig.~\ref{fig:Smearing} for a simple model with only three sources.
+Without reflections, the sources would form lines in $b-\tau$ space.
+With the reflections, the sources are smeared out, leading to supra-horizon emission.
+\begin{figure*}[h!]
+\includegraphics[width=\textwidth]{figures/wedgeCompare.pdf}
+\caption{We demonstrate the impact on foregrounds of the frequency dependent beam.
+Left: The location of three sources in delay space assuming a frequency indepdendent beam (no reflections in the antenna element).
+Right: the presence of chromaticity due to reflections in the antenna smears the source in delay with the kernel given by equation~\ref{eq:Kernel}.
+Since the frequency response of the dish are a function of direction on the sky, the shape of the delay kernel is different for each source line.
+We see that this smearing can lead to substantial supra-horizon emission.
+Sources near zenith (low delay) tend to have a larger maximum since the beam gain is larger near zenith, but a more compact kernel (since beam bore-sights tend to have less spectral structure).
+Meanwhile, sources near the horizon have a much smaller maxima but have less compact kernels.}
+\label{fig:Smearing}
+\end{figure*}
+For the sake of pedagogy, we now consider the case where
+
 where $V_{ij}^{mn}$ is a visibility resulting from the effective primary beam, $R_{ij}({\bf \widehat{k}},\Delta \tau_{mn})$, at delay $\Delta \tau_{mn}$ induced by the reflections.

### 2015-11-07 DishBeamMeasurements/paper/DishBeamMeasurementsPaper.tex

@@
 
-\section{Dish Design and Modeling}
-
-\subsection{Design of the HERA Dish}
-
-design principles
-tradeoffs
-description of the final design
-
-\subsection{Dish Modeling}
-\label{sec:dishmodels}
-
-We compare measured beam patterns with a simplistic analytic model and two numerical electromagnetic models.
-Briefly, the dish is constructed of overlapping mesh rectangles secured to hanging PVC pipes to form an approximately parabolic surface with diameter 14\,m.
-The feed consists of a dual-polarization dipole antenna with a circular mesh backplane and a cylindrical mesh ``skirt'' hanging down.
-The feed is suspended over the dish surface by three ropes attached to poles equally spaced around the dish.
-
-\begin{enumerate}
-	\item Airy pattern for a 14\,m aperture
-	\item CST simulation (hera-cst/HERA\_DISH\_paper \_feed\_cyl36\_140mhz\_Y\_healpix.fits)
-	\item A separate simulation run by Dave with 68'' diameter feed backplane and 26'' skirt.
-\end{enumerate}
-
-\section{Error Analysis}
+\subsection{Assessing Experimental Systematics}
 
@@
 
+\section{Dish Design and Modeling}
+
+\subsection{Design of the HERA Dish}
+
+ASK DAVE DEBOER TO WRITE A TWO PARAGRAPH SUMMARY OF THE HERA ELEMENT AND HOW IT WAS DESIGNED
+
+\subsection{Dish Modeling}
+\label{sec:dishmodels}
+
+ASK DAVE OR RICH TO WRITE A ONE OR TWO PARAGRAPH SUMMARY OF THE ELECTROMAGNETIC DISH SIMULATIONS
+
 %\section{Feed Measurements}
@@
 
-\section{Dish Characterization}
+\section{Dish Measurements}
 

### 2015-11-07 DishSimulations/paper/DishSimulationsPaper_v0.tex
more edits to dish simulations paper

@@
 Using simulations of foregrounds, we find that the $\approx -40$\,dB response at 60\,ns of the HERA dish is sufficient to isolate the cosmological 21\,cm signal $\approx 0.2$\,$h$Mpc$^{-1}$ at $z\approx 8.5$ and obtain a high signal to noise detection of the power spectrum.
+At its current state, the reflections of the HERA dish design do significantly impact its ability to constrain the $R_\text{mfp}$ reionization parameter for a number of models since they prevent direct measurements of the ``knee" feature.
+This study represents the first time that direct measurements a 21\,cm interferometer design have been translated into its ability to constrain the physics of reionization.
 \end{abstract}
@@
 For each ${\bf \hat{k}}$, we see that each source is mapped to a line $\tau ={\bf b}_{ij}\cdot{\bf \hat{k}}/c$, resulting in the much discussed ``wedge" \citep{Datta:2010,Vedantham:2012,Parsons:2012,Morales:2013,Thyagarajan:2013,Liu:2014a,Liu:2014b}.
-The presence of the frequency dependent beam causes each source line to be convolved in delay with the kernel
+The presence of the frequency dependent beam causes each source line to be convolved in delay with the direction dependent kernel
 \begin{equation}\label{eq:Kernel}
@@
 \end{equation}
-The beam has a different delay structure in each direction, and we demonstrate the effect of foreground smearing in Fig.~\ref{fig:Smearing} for a simple model with only three sources.
+which itself is the convolution of the delay response of the two voltage beams, $\widetilde{r}_i({\bf \widehat{k}},\tau)$,$\widetilde{r}_j({\bf \widehat{k}},\tau)$.
+Usually, beams have a different delay structure in each direction, and we demonstrate the effect of foreground smearing in Fig.~\ref{fig:Smearing} for a simple model with only three sources.
 Without reflections, the sources would form lines in $b-\tau$ space.
@@
 \end{figure*}
-For the sake of pedagogy, we now consider the case where
+For the sake of pedagogy, we now consider the case where the beam can be factored into angular and frequency dependent components, $r_i({\bf \hat{k}},f) = g_i(f)a_i({\bf \hat{k}})$.
+For such a case, every line in Fig.~\ref{fig:Smearing} would be convolved with the same frequency dependent shape, normalized to the gain of $a_i({\bf \hat{k}})$.
 

### 2015-11-07 DishSimulations/paper/DishSimulationsPaper_v0.tex
modified notation in sec 3.2 to connect discrete simulations with continuous theory notation

@@
 For the sake of pedagogy, we now consider the case where the beam can be factored into angular and frequency dependent components, $r_i({\bf \hat{k}},f) = g_i(f)a_i({\bf \hat{k}})$.
-For such a case, every line in Fig.~\ref{fig:Smearing} would be convolved with the same frequency dependent shape, normalized to the gain of $a_i({\bf \hat{k}})$.
+For such a case, every line in Fig.~\ref{fig:Smearing} would be convolved with the same delay dependent shape, normalized to the gain of $a_i({\bf \hat{k}})$.
+In this case, we have
+\begin{equation}
+\widetilde{V}_{ij}'(\tau) = \int d\tau' \int d \tau'' \widetilde{g}_i(\tau' - \tau'')\widetilde{g}^*_j(\tau'') \widetilde{V}_{ij}(\tau-\tau')
+\end{equation}
+We can further simplify matters by assuming that $\widetilde{g}_i(\tau=0)\gg\widetilde{g}_i(\tau>0)$, which is often a good assumption at large delays for the relatively smooth bandpasses our instruments are designed to have.
+\begin{equation}\label{eq:KernelApprox}
+\widetilde{V}_{ij}'(\tau) \approx \widetilde{g}_i(0)\int d \tau' \widetilde{g}_j^*(\tau')\widetilde{V}_{ij}(\tau- \tau') + \widetilde{g}_j^*(0) \int d \tau' \widetilde{g}_i(\tau')\widetilde{V}_{ij}(\tau-\tau')
+\end{equation}
+Hence, to first order, the impact of reflections is to convolve the delay-transformed visibility with the voltage beam of the instrument, which acts as the power-kernel.
+This may be a somewhat un-intuitive result since we might naively expect for the power-kernel to be the square of the delay-response.
+This linear falloff puts exquisite requirements on the smoothness of the beam, requiring that it fall roughly six orders of magnitude in delay before the signal is accessible.
 
-where $V_{ij}^{mn}$ is a visibility resulting from the effective primary beam, $R_{ij}({\bf \widehat{k}},\Delta \tau_{mn})$, at delay $\Delta \tau_{mn}$ induced by the reflections.
-\begin{equation}
-V_{ij}^{mn} = \int d \Omega R_{ij}({\bf \widehat{s}},\Delta \tau_{mn}) I(f,{\bf \widehat{s}})e^{2 \pi i {\bf u}_{ij} \cdot {\bf \widehat{s}}}
-\end{equation}
-The delay transform power spectrum estimate, $\widehat{P}$, is proportional to $|\widetilde{V}_{ij}'|^2$, hence 
-\begin{align}\label{eq:Reflections}
-\widehat{P} & \propto |\widetilde{V}_{ij,FG}(\tau)|^2 + |\widetilde{V}_{ij,21}(\tau)|^2 + 2 \text{Re}(\widetilde{V}_{ij,21}(\tau)\widetilde{V}_{ij,FG}^*(\tau)) \nonumber \\
-&+ \sum_{|\Delta \tau_{mn}| > 0} 2 \text{Re} \left[   \widetilde{V}^*_{ij} (\tau) \widetilde{V}^{mn}_{ij} (\tau - \Delta \tau_{mn})  \right] \nonumber \\
-&+ \sum_{\substack{|\Delta \tau_{op}|>0\\|\Delta \tau_{mn}|>0}} \widetilde{V}^{mn}_{ij} (\tau - \Delta \tau_{mn}) \widetilde{V}^{op*}_{ij}(\tau - \Delta \tau_{op})
-\end{align}
-In the absence of reflections, only the top line of equation~\ref{eq:Reflections} would enter the delay power spectrum estimate.
-The following lines involve the translation of the signal (including foregrounds and signal) out to the delay of each reflection and weighted by the effective primary beam of the reflection.
-Since each translated visibility is intrinsically $\sim 10^6$ times brighter than the signal, any reflection with a delay large enough to place it within the EoR window, must be sufficiently attenuated by $R_{ij}({\bf \widehat{k}},\Delta \tau_{mn})$.% The precise degree of attenuation is determined in \citep{Thyagarajan:2015c} using simulations of foregrounds and noise and sets the spec for our antenna.
-
-To get a better idea for what spec this sets on the voltage response of our dish we examine, in more detail, the case where $r_0$ at ($\tau=0$) is significantly greater than the other coefficients as we might expect for a dish with a relatively smooth gain.
-Than we can approximate equation \ref{eq:Reflections} to linear order in $r_i$,
-\begin{equation}
-\widetilde{V}_{ij}'(\tau) \approx \widetilde{V}_{ij} + \sum_{m>0} \widetilde{V}_{ij}^{m0} (\tau -  \tau_m)
-\end{equation}
-
-If we make the assumption that the beam can be factored into a frequency dependent and frequency dependent term, $r_i({\bf \widehat{k}},\tau) = a_i({\bf \widehat{k}}) g_i(\tau)$ than we have
-\begin{equation}
-\widetilde{V}_{ij}' \approx \widetilde{V}_{ij}(\tau) + \sum_{m>0} r_m \widetilde{V}_{ij}(\tau - \tau_m)
-\end{equation}
- Hence, for a delay response dominated by the $0$-delay mode, as we might expect in an antenna element with smooth gain, the delay transformed visibilities are effectively convolved with the {\it voltage response}, not the square of the voltage response as we might naively expect.
-A more compact writing the impact of the spectral structure of a separable beam on foregrounds would be
- \begin{equation}
- 	\widetilde{V}_{ij}'(\tau) = \left[ (g_i \star g_j^*) \star \widetilde{V}_{ij}\right](\tau)
- \end{equation}
- As a result, one should compare the amplitude of the voltage delay response of the antenna with the ratio between foregrounds and signal when
-
- In this paper, we study $r_i({\bf \widehat{k}},\Delta \tau)$ for the HERA antenna element to verify that it both meets the spec and agrees with direct measurements of the antenna element with refelctometry \citep{Patra:2015} and Orbcomm measurements \citep{Neben:2015b}.
-We also explore the implications of the performance of $r_i({\bf \widehat{k}},\tau)$ on the scientific bottom line for EoR experiments, using the Fisher Matrix Formalism.
+ In this paper, we derive $\widetilde{r}_i({\bf \widehat{k}},\Delta \tau)$ for the HERA antenna element using electromagnetic simulations, in order to verify direct measurements of the antenna element with refelctometry \citep{Patra:2015} and Orbcomm measurements of the beam \citep{Neben:2015b}.
+We also explore the implications of the HERA dish's $\widetilde{r}_i({\bf \widehat{k}},\tau)$ on the scientific bottom line for EoR, using the Fisher Matrix Formalism.
 
@@
 \subsection{Deconvolving the Response Function}
-In our simulation, we obtain the voltage at the feed output as a function of time which we will call $v_{out}(t)$. It is related to the input lane wave through the equation 
+Since our simulation is sampled in finite time steps, we will adopt discretized notation for this section.
+In particular, our simulation consists of $N$ samples, evenly spaced by $d \tau$ at times $\tau_n = n \times d \tau$.
+In our simulation, we obtain the voltage at the feed output at time $\tau_n$ which we will call $\widetilde{v}_n$. It is related to the input plane wave through the discrete convolution 
 \begin{equation}
-v_{out}(t,\theta=0) = \sum_n r_n(\theta=0) v_{in}(t - \tau_n,\theta=0),
+\widetilde{v}_n({\bf \widehat{k}}) = \sum_m \widetilde{r}_m({\bf \widehat{k}}) \widetilde{s}_{n-m}({\bf \widehat{k}}),
 \end{equation}
-which is essentially a convolution in time of $r_n(\theta=0)$ with the input plane wave.
-We may undo this convolution by taking a discrete Fourier transform of both $v_{out}$ and $v_{in}$ in time, dividing them in Fourier space, and taking an inverse DFT back.
-Our simulation output is sampled at even time intervals so we may use and FFT.
+We may undo this convolution by taking a discrete Fourier transform (DFT) of both ${\bf \widetilde{v}}$ and ${\bf \widetilde{s}}$ in time, dividing them in Fourier space, and taking an inverse DFT back.
+Symbolically,
 \begin{equation}
-\widehat{{\bf r}}(\theta=0) = \boldsymbol{\mathcal{F}}^{-1} \left[ \frac{\boldsymbol{\mathcal{F}} {\bf v_{out}}(\theta=0)}{{\bf v_{in}}(\theta=0)} \right] 
+{\bf \widetilde{r}}({\bf \widehat{k}}) = \boldsymbol{\mathcal{F}}^{-1} \left[ \frac{\boldsymbol{\mathcal{F}} {\bf \widetilde{v}}({\bf \widehat{k}})}{{\bf \widetilde{s}}({\bf \widehat{k}})} \right] 
 \end{equation}
-where ${\bf \mathcal{F}}$ is the Fourier transform matrix for a 1d vector of length $N$. 
+where $\boldsymbol{\mathcal{F}}$ is the Fourier transform matrix for a 1d vector of length $N$. 
 \begin{equation}
@@
 
-\section{Results and Comparison to Reflectometry Data}\label{sec:Comparison}
+\subsection{Extrapolating the Bandpass and Power Kernel}
+We show our estimate of our delay kernel in Fig.~\ref{fig:voltageVsKernel}
+
+\begin{figure}
+\includegraphics[width=.5\textwidth]{figures/convolveCompare.pdf}
+\caption{Our estimate of $\widetilde{r}(\tau,\theta=0)$, the voltage response of the HERA dish at zenith (blue line) along with its square (green line) which falls off significantly faster with delay.
+The power kernel for identical dishes, $\widetilde{r}\star\widetilde{r}^*$, the voltage response convolved with itself, is plotted with a red line.
+Because the $\tau=0$ response of the dish is significantly larger than the reflections, linear terms in the convolution dominate the squared terms whose magnitude roughly corresponds to the green line.
+Hence, the power kernel is well approximated by $\widetilde{r}$ itself, verifying our result in equation~\ref{eq:KernelApprox}.
+}
+\end{figure}
+
+\section{Comparison to Reflectometry Data}\label{sec:Comparison}
 \subsection{The Delay Response at Zenith}

### 2015-11-09 DishSimulations/paper/DishSimulationsPaper_v0.tex
added discussion on modeling the reflection response to extrapolate to large delays relevant to EoR scales

@@
 \end{figure*}
-\subsection{Deconvolving the Response Function}
+\subsection{Deconvolving the Response Function}\label{ssec:Deconvolve}
 Since our simulation is sampled in finite time steps, we will adopt discretized notation for this section.
@@
 \subsection{Extrapolating the Bandpass and Power Kernel}
-We show our estimate of our delay kernel in Fig.~\ref{fig:voltageVsKernel}
-
+Our deconvolution gives us the time-domain voltage response of the HERA antenna element.
+We plot the absolute value of this response in Fig.~\ref{fig:KernelCompare}, seeing that it drops to $-20$\,dB after $\approx 75$\,ns.
+The power-kernel that convolves visibilities to higher delays is the convolution of $\widetilde{r}(\tau)$ with its complex conjugate, which we plot as the red line.
+The convolution is in very good agreement with the voltage response itself which is explained by the fact that second order terms of the convolution, approximately given by $|\widetilde{r}(\tau)|^2$ (green line) are over two orders of magnitude smaller above $50$\,ns.
 \begin{figure}
@@
 Hence, the power kernel is well approximated by $\widetilde{r}$ itself, verifying our result in equation~\ref{eq:KernelApprox}.
-}
+We fit a double power law model to both the power kernel (solid black line) and the voltage response(dashed black line) and find that it is a good approximation for the long-time scale behavior of both.We also plot the falloff of reflections with $Y=0.1$ in equation~\ref{eq:ReflectionModel} which is representative of the measured and simulated reflection coefficient of the feed to waves at zenith.
+The observed reflections are significantly worse.}
+\label{fig:KernelCompare}
 \end{figure}
+
+Our simulations of the Dish response only extend to $\approx 300$\,ns, however, we wish to understand the impact of reflections on the frequency dependent gain of an interferometer like HERA, which has a spectral resolution of $100$\,kHz.
+Obtaining such frequency resolution would require a calculation of the voltage response out to $100$\,$\mu$s, over two orders of magnitude beyond the time limit of our current simulation.
+Fortunately, there exists a way of extrapolating our results which is highly physically motivated.
+We first note that $\widetilde{r}(\tau)$ exhibits a pivot at around $75$\,ns, falling rapidly for the first $\sim 60$\,ns or so before leveling out and following a much shallower trend that is characterized by periodic lobed structures every $\approx 30$\,ns.
+The initial falloff is likely the intrinsic response of the feed element itself, caused by residual currents that were excited by the incident wave.
+The scalloped structures that dominate the slower, long-term fall-off is almost certainly caused by reflections between the feed element and the vertex of the dish.
+This is due to the fact that the round-trip delay between the feed and the dish, $5$\,m below, is $\approx 30$\,ns.
+This long term falloff is precisely what we must model in order to extrapolate to the very long delays required to model $100$\,kHz structures and the reflections provide us with a simple physical model for doing so.
+Adopting the notation of \citep{Patra:2015}, we let $\Gamma_d$ represent the reflection coefficient of the Dish vertex and $\Gamma_f$ represent the reflection coefficient of the feed.
+An electromagnetic wave incident on the feed, at $t=0$, is accepted with amplitude $(1-\Gamma_f)$.
+The reflected component travels back to the dish and acquires an amplitude of $(\Gamma_f \Gamma_d)$ before returning at time, $\tau_d$ later where $(1-\Gamma_f)$ will be accepted and so forth.
+The time dependent voltage at the feed from these reflections is thus
+\begin{equation}
+\widetilde{v}_r(t) = \sum_m \left( \Gamma_f \Gamma_d \right)^m \widetilde{s}(t-m \tau_d)
+\end{equation}
+Hence
+\begin{equation}
+\widetilde{r}_r(\tau) = \sum_m \left( \Gamma_f \Gamma_d \right)^m \delta_D(\tau-m\tau_d)
+\end{equation}
+Since the number of reflections, $m=t/\tau_d$, than we can write the long-term delay response in discrete form as 
+\begin{equation}
+\widetilde{r}_n \approx (\Gamma_f \Gamma_d)^{n d\tau/\tau_d}
+\end{equation}
+which is a power law.
+We thus model our discrete voltage response as a sum of two power laws, one to describe the rapid falloff at small delays from residual currents in the feed, and another at large delay to describe the reflections in the dish.
+\begin{equation}
+\widetilde{r} = A X^{(\tau/30\text{ns})} + (1-A) Y^{(\tau/30 \text{ns})}
+\end{equation}
+Strictly speaking, this equation is not correct in that it contains non-existent reflections at very small delays, however since the amplitude of these reflections is only several $\%$, the formula is still accurate here.
+We fit our voltage response function and power-kernel to this function, finding a best fit model for the voltage kernel of $A\approx0.95$,$X \approx 0.18$, and $Y\approx 0.58$.
+The large $Y$ is unrepresentative of the feed reflection coefficient which has been simulated and measured to be $\approx 0.1$ for a head-on EM wave, suggesting that the reflections are arriving from the sides and potentially involve only a small component of the dish and feed.
+Plotting the die off for the feed reflection coefficient yields dramatically better performance than what is measured.
+If the reflections are indeed originating from the sides, and a small component of the dish and feed arrangement, further suppression may be achieved through modifying this component.
 
@@
 However, comparison between individual frequency channels in both CST and FEKO indicates numerical precision errors {\bf Show a figure of an attempted beam and frequency artifacts at zenith.}
+
+Rather, we employ CST's time domain mode to simulate the response of the dish to plane waves incident off of zenith to understand the frequency dependence of the side-lobes using the same technique that was described in \S~\ref{ssec:Deconvolve}.
+In Fig.~\ref{fig:Comparison}, we show the delay structure of the sidelobe response functions we obtain on a N-S line $20^\circ$ and $30^\circ$ from zenith, which approximately correspond to the sidelobes of the beam.
 

### 2015-11-09 ForegroundSimulations/ms.tex

%%\documentclass[12pt,preprint]{aastex}

%% manuscript produces a one-column, double-spaced document:

%% \documentclass[10pt,manuscript]{aastex}

%% preprint2 produces a double-column, single-spaced document:
\documentclass[preprint2,iop,numberedappendix,twocolappendix,appendixfloats]{emulateapj}
%% \documentclass[preprint2,iop]{aastex}

%% \documentclass[preprint2,longabstract]{aastex}

%% \usepackage{ccaption}
%% \captionstyle{\raggedright}
\usepackage[caption=false]{subfig}
\usepackage{amsmath}
\usepackage{footnote}
\bibpunct{(}{)}{;}{a}{}{,} 
\captionsetup{belowskip=12pt,aboveskip=4pt}
\setlength{\textfloatsep}{10pt plus 1.0pt minus 2.0pt}
\newcommand{\dif}{\mathrm{d}}
%% \renewcommand*{\thefootnote}{\fnsymbol{footnote}}

\def\nar{{New~A~Rev.}}          % New Astronomy Review
\def\pasa{{PASA}}               % Publications of the Astron. Soc. of Australia

%% \bibliographystyle{mn2e}
%% \bibliographystyle{apj}

\shorttitle{Estimate of Foregrounds in EoR Power Spectra for HERA}
\shortauthors{Thyagarajan et~al.}

\def\ASU{\altaffilmark{1}}
\def\ASUtxt{\altaffiltext{1}{Arizona State University, School of Earth and Space Exploration, Tempe, AZ 85287, USA}}

\def\myemail{\altaffilmark{*}}
\def\myemailtxt{\altaffiltext{*}{e-mail: t\_nithyanandan@asu.edu}}

\def\UW{\altaffilmark{2}}
\def\UWtxt{\altaffiltext{2}{University of Washington, Department of Physics, Seattle, WA 98195, USA}}

\def\SKASA{\altaffilmark{3}}
\def\SKASAtxt{\altaffiltext{3}{Square Kilometre Array South Africa (SKA SA), Park Road, Pinelands 7405, South Africa}}

\def\RU{\altaffilmark{4}}
\def\RUtxt{\altaffiltext{4}{Department of Physics and Electronics, Rhodes University, Grahamstown 6140, South Africa}}

\def\CfA{\altaffilmark{5}}
\def\CfAtxt{\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA}}

\def\ANU{\altaffilmark{6}}
\def\ANUtxt{\altaffiltext{6}{Australian National University, Research School of Astronomy and Astrophysics, Canberra, ACT 2611, Australia}}

\def\CAASTRO{\altaffilmark{7}}
\def\CAASTROtxt{\altaffiltext{7}{ARC Centre of Excellence for All-sky Astrophysics (CAASTRO)}}

\def\Haystack{\altaffilmark{8}}
\def\Haystacktxt{\altaffiltext{8}{MIT Haystack Observatory, Westford, MA 01886, USA}}

\def\MIT{\altaffilmark{9}}
\def\MITtxt{\altaffiltext{9}{MIT Kavli Institute for Astrophysics and Space Research, Cambridge, MA 02139, USA}}

\def\Curtin{\altaffilmark{10}}
\def\Curtintxt{\altaffiltext{10}{International Centre for Radio Astronomy Research, Curtin University, Perth, WA 6845, Australia}}

\def\Victoria{\altaffilmark{11}}
\def\Victoriatxt{\altaffiltext{11}{Victoria University of Wellington, School of Chemical \& Physical Sciences, Wellington 6140, New Zealand}}

\def\UWisc{\altaffilmark{12}}
\def\UWisctxt{\altaffiltext{12}{University of Wisconsin--Milwaukee, Department of Physics, Milwaukee, WI 53201, USA}}

\def\UMichigan{\altaffilmark{13}}
\def\UMichigantxt{\altaffiltext{13}{University of Michigan, Department of Atmospheric, Oceanic and Space Sciences, Ann Arbor, MI 48109, USA}}

\def\UMelbourne{\altaffilmark{14}}
\def\UMelbournetxt{\altaffiltext{14}{The University of Melbourne, School of Physics, Parkville, VIC 3010, Australia}}

\def\USydney{\altaffilmark{15}}
\def\USydneytxt{\altaffiltext{15}{The University of Sydney, Sydney Institute for Astronomy, School of Physics, NSW 2006, Australia}}

\def\CASS{\altaffilmark{16}}
\def\CASStxt{\altaffiltext{16}{CSIRO Astronomy and Space Science (CASS), PO Box 76, Epping, NSW 1710, Australia}}

\def\Tata{\altaffilmark{17}}
\def\Tatatxt{\altaffiltext{17}{National Centre for Radio Astrophysics, Tata Institute for Fundamental Research, Pune 411007, India}}

\def\RRI{\altaffilmark{18}}
\def\RRItxt{\altaffiltext{18}{Raman Research Institute, Bangalore 560080, India}}

\def\NRAO{\altaffilmark{19}}
\def\NRAOtxt{\altaffiltext{19}{National Radio Astronomy Observatory, Charlottesville and Greenbank, USA}}

\def\UWA{\altaffilmark{20}}
\def\UWAtxt{\altaffiltext{20}{International Centre for Radio Astronomy Research, University of Western Australia, Crawley, WA 6009, Australia}}

%% \definenote[thanks][conversion=set 2]

\begin{document}

\title{Estimation of Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra with the Hydrogen Epoch of Reionization Array}

%% Use \author, \affil, and the \and command to format
%% author and affiliation information.
%% Note that \email has replaced the old \authoremail command
%% from AASTeX v4.0. You can use \email to mark an email address
%% anywhere in the paper, not just in the front matter.
%% As in the title, use \\ to force line breaks.

%% Author list
\author{
%% Lead Authors
Nithyanandan~Thyagarajan\ASU\myemail,
TBD
% Daniel~C.~Jacobs\ASU,
% Judd~D.~Bowman\ASU,
% N.~Barry\UW,
% A.~P.~Beardsley\UW,
% G.~Bernardi\SKASA$^,$\RU$^,$\CfA,
% F.~Briggs\ANU$^,$\CAASTRO,
% R.~J.~Cappallo\Haystack, 
% P.~Carroll\UW,
% B.~E.~Corey\Haystack, 
% % A.~A.~Deshpande\RRI, 
% A.~de~Oliveira-Costa\MIT,
% Joshua~S.~Dillon\MIT,
% D.~Emrich\Curtin,
% % B.~M.~Gaensler\USydney$^,$\CAASTRO, 
% A.~Ewall-Wice\MIT,
% L.~Feng\MIT,
% R.~Goeke\MIT,
% L.~J.~Greenhill\CfA,
% B.~J.~Hazelton\UW, 
% J.~N.~Hewitt\MIT,
% N.~Hurley-Walker\Curtin,
% M.~Johnston-Hollitt\Victoria,
% D.~L.~Kaplan\UWisc, 
% J.~C.~Kasper\UMichigan$^,$\CfA, 
% Han-Seek Kim\UMelbourne$^,$\CAASTRO,
% P.~Kittiwisit\ASU,
% E.~Kratzenberg\Haystack, 
% E.~Lenc\USydney$^,$\CAASTRO,
% J.~Line\UMelbourne$^,$\CAASTRO,
% A.~Loeb\CfA,
% C.~J.~Lonsdale\Haystack, 
% M.~J.~Lynch\Curtin, 
% B.~McKinley\UMelbourne$^,$\CAASTRO,
% S.~R.~McWhirter\Haystack,
% D.~A.~Mitchell\CASS$^,$\CAASTRO, 
% M.~F.~Morales\UW, 
% E.~Morgan\MIT, 
% A.~R.~Neben\MIT,
% D.~Oberoi\Tata, 
% A.~R.~Offringa\ANU$^,$\CAASTRO, 
% S.~M.~Ord\Curtin$^,$\CAASTRO,
% Sourabh Paul\RRI,
% B.~Pindor\UMelbourne$^,$\CAASTRO,
% J.~C.~Pober\UW,
% T.~Prabu\RRI, 
% P.~Procopio\UMelbourne$^,$\CAASTRO,
% J.~Riding\UMelbourne$^,$\CAASTRO,
% A.~E.~E.~Rogers\Haystack, 
% A.~Roshi\NRAO, 
% N.~Udaya~Shankar\RRI, 
% Shiv~K.~Sethi\RRI,
% K.~S.~Srivani\RRI, 
% R.~Subrahmanyan\RRI$^,$\CAASTRO, 
% I.~S.~Sullivan\UW,
% M.~Tegmark\MIT,
% S.~J.~Tingay\Curtin$^,$\CAASTRO, 
% C.~M.~Trott\Curtin$^,$\CAASTRO,
% M.~Waterson\Curtin$^,$\ANU,
% R.~B.~Wayth\Curtin$^,$\CAASTRO, 
% R.~L.~Webster\UMelbourne$^,$\CAASTRO, 
% A.~R.~Whitney\Haystack, 
% A.~Williams\Curtin, 
% C.~L.~Williams\MIT,
% C.~Wu\UWA,
% J.~S.~B.~Wyithe\UMelbourne$^,$\CAASTRO
}

%Institutional footnotes (typeset, then rearrange here to be in order)
\ASUtxt
% \UWtxt
% \SKASAtxt
% \RUtxt
% \CfAtxt
% \ANUtxt
% \CAASTROtxt
% \Haystacktxt
% \MITtxt
% \Curtintxt
% \Victoriatxt
% \UWisctxt
% \UMichigantxt
% \UMelbournetxt
% \USydneytxt
% \CASStxt
% \Tatatxt
% \RRItxt
% \NRAOtxt
% \UWAtxt
\myemailtxt

%% \clearpage

\begin{abstract}

\end{abstract}

\keywords{cosmology: observations --- dark ages, reionization, first stars --- large-scale structure of universe --- methods: statistical --- radio continuum: galaxies --- techniques: interferometric}

\section{Introduction}\label{intro}

Hydrogen Epoch of Reionization Array (HERA\footnote{\url{http://reionization.org/}}; DeBoer~et~al.~2015, Murchison Widefield Array \citep[MWA;][]{lon09,bow13,tin13}, Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, Low Frequency Array \citep[LOFAR;][]{van13}

Wedge papers \citep{ali08,ber09,ber10,bow09,liu09,liu14a,liu14b,dat10,liu11,gho12,mor12,par12b,tro12,dil13,dil14,pob13,thy13,thy15a,thy15b}

\section{Delay Spectrum}\label{sec:delay-spectrum}

\citep{par12b}

\section{The Wide-Field ``Pitchfork'' Effect}\label{sec:wide-field}

\citep{thy15a,thy15b}

\section{Simulations}\label{sec:sim}

We describe the instrument and foreground models used in our simulations.

\subsection{The Hydrogen Epoch of Reionization Array}\label{sec:HERA}

\subsubsection{Antenna Power Pattern}

\citep{neb15}

\subsubsection{Antenna Reflectometry}

Patra~et~al.~2015 (submitted), Ewall-Wice~et~al.~2015 (submitted)

\subsection{Foreground Model}\label{sec:foreground}

\section{Analysis of Foreground Signatures}\label{sec:FG-analysis}

\section{Summary}\label{sec:summary}

\acknowledgments

This work was supported by the U. S. National Science Foundation (NSF) through award AST-1109257. DCJ is supported by an NSF Astronomy and Astrophysics Postdoctoral Fellowship under award AST-1401708. JCP is supported by an NSF Astronomy and Astrophysics Fellowship under award AST-1302774.

% \appendix

% \par\bigskip
\bibliographystyle{apj}
\bibliography{eor}

\end{document}

### 2015-11-13 DishReflectometry/Paper1_v0.tex
Changed 3 plots and added necessary text to the plot caption.

@@
 \begin{eqnarray}
-\tilde V(\vec b, \tau) & = & \int\!\!\int{\bm(\thhat,\nu) I_\sky(\thhat,\nu) \ifngexp d\Omega~e^{-2\pi i\nu\tau}d\nu}\nonumber\\	                        & = &   \int \left [ A(\vec b, \tau)\ast I_{sky}(\vec b, \tau) \ast \delta( \vec b, \tau )\right ] d\Omega
+\tilde V(\vec b, \tau) & = & \int\!\!\int{\bm(\thhat,\nu) I_\sky(\thhat,\nu) \ifngexp d\Omega~e^{+2\pi i\nu\tau}d\nu}\nonumber\\	                        & = &   \int \left [ A(\thhat, \tau)\ast I_{sky}(\thhat, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega
 \label{eq3}
@@
 
-where $\Phi = 2\pi\nu\Delta \tau$.
 The relevant terms in the corresponding visibility and subsequently in the delay spectrum would be the ones which represent the correlation between the direct component of one antenna with the reflected components of the other resulting in higher order terms  in $\Sigma(\vec b, \nu)$.
@@
 \begin{equation}\label{eqn:series1}
-\vis(\vec b, \nu)  = \int I_{sky}\Sigma(\vec b, \nu) d\Omega
+\vis(\vec b, \nu)  = \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp d\Omega
 \end{equation}
+Corresponding delay spectrum would be, 
+\begin{eqnarray}
+\tilde V(\vec b, \tau) & = & \int \left [ \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp  d\Omega \right ]  e^{-2\pi i\nu\tau} d\nu \nonumber \\
+  			      & = & \int \left [ I_{sky}(\thhat, \nu) \ast \Sigma(\thhat, \nu) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )  \right] d\Omega
+\end{eqnarray}
 
@@
 
-\begin{figure}[H]
+\begin{figure}
 \centering
-\includegraphics[totalheight=0.41\textheight]{plots/bh_vs_sq.png}
-\caption{Delay plot produced for the PAPER bandwidth ($100MHz-200MHz$) by taking the Fourier transform of the measured return loss using four different window functions: Blackman-Harris, square, Hamming, and Hanning.}
+\includegraphics[width=1.0\linewidth]{plots1/delayspectrum.png}
+\caption{Delay transform of the transfer function of the HERA element.
+The complex return loss of the element is measured between 50 to 400~MHz when the feed is kept at the focal plane of the dish at a focal height 4.5m.
+The delay spectrum is produced by taking the Fourier transform of the magnitude of the return loss measurement after limiting the measurements between 100 to 200~MHzusing Blackman-Harris window.
+The intersection of the horizontal and vertical dashed line shows the instrument performance specification as predicted by the theory of delay transform in order to detect the 21cm power spectrum.}
 \label{fig:window}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[totalheight=0.6\linewidth]{plots1/delayspectrum_feed.png}
+\caption{Delay transform of the transfer function of the HERA feed element.
+The feed is kept on the ground downside up so that the entire radiation from the feed is radiated out.
+Once again, the measurement is done between 50 to 450 MHz and the delay spectrum is produced between $100-200$~MHz by using a Blackman-Harris window.
+The black dashed lines illustrate the instrument specification.}
+\label{fig:outofthedish}
 \end{figure}
@@
 
-\begin{figure}[ht!]
-\centering
-\includegraphics[totalheight=0.41\textheight]{plots/delay3_window.png}
-\caption{Delay plots produced using a Hamming window function for 5 different cases.
-Three of the cases correspond to measurements taken in Green Bank for three frequency bandwidths: $50MHz-250MHz$ (HERA bandwidth), $100MHz-200MHz$ (PAPER bandwidth), and $140MHz-160MHz$ (typical power spectrum bandwidth).
-Two of the cases correspond to measurements taken in 2014 of the first prototype HERA dish in Berkeley (without a feed cage).
-Of these, we plot data for two frequency bandwidths: $100MHz-200MHz$ (PAPER bandwidth), and $50MHz-1000MHz$ (full bandwidth used by the VNA).
-For the PAPER bandwidth data, we follow the same Fourier-transform analysis as the others, while the full bandwidth data is produced directly by the VNA.
-The black dashed lines illustrate our ``60 by 60" specification.}
-\label{fig:3bands}
-\end{figure}
-
 From the plot, we see that the delay response of a feed is dependent on the band chosen for the Fourier transform.  As one might expect, in regions
@@
 
-\begin{figure}[ht!]
-\centering
-\includegraphics[totalheight=0.41\textheight]{plots/delay_heights_paper.png}
-\caption{Delay plots produced using a Hamming window function for 4 different feed heights and the PAPER bandwidth ($100MHz-200MHz$). The black dashed lines illustrate our ``60 by 60" specification.}
-\label{fig:elevator}
-\end{figure}
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[width=1.0\linewidth]{plots1/delayspectrum_height.png}
+%\caption{Delay transform of the transfer function of the HERA element keeping the feed at various heights.
+Delay transform is produced by taking the Fourier transform of the measurement using Blackman-Harris window.}
+%\label{fig:elevator}
+%\end{figure}
 
@@
 with the height of the feed above the dish, making reflections off the dish the likely culprit.
-
-\begin{figure}[H]
-\centering
-\includegraphics[totalheight=0.41\textheight]{plots/delay_feed.png}
-\caption{Delay plots produced using a Hamming window function for different lone feed configurations and the PAPER bandwidth ($100MHz-200MHz$).
-The black dashed lines illustrate our ``60 by 60" specification.}
-\label{fig:outofthedish}
-\end{figure}
 

### 2015-11-13 DishBeamMeasurements/paper/DishBeamMeasurementsPaper.tex

@@
 
-In detail, we discuss the experimental setup of the beam mapping experiments and their systematics, then 
-review  the ORBCOMM beam measurement system, in Section 2. We discuss the electromagnetic design and 
-modeling of the dish in Section 3, present our power pattern measurements in Section 5. We conclude with 
-discussion in Section 6.
+In detail, we discuss the electromagnetic design and modeling of the dish in Section 3. We present the 
+experimental setup of the beam mapping experiments and discuss their systematics, then 
+review the ORBCOMM beam measurement system, in Section 3. We present our power pattern 
+measurements in Section 5. We conclude with discussion in Section 6.
+
+\section{Dish Design and Modeling}
+
+\subsection{Design of the HERA Dish}
+%- EM design
+%    - departure from large N—small D to economize data volume (mitigate
+%      data processing challenges)
+%        - easier to identify systematics, to rerun datasets, perform
+%          cross checks / jackknives
+%    - but this change must be done judiciously, one advantage of simple
+%      elements is that they have little or no frequency structure,
+%      while a dish+feed system introduces reflections in the time
+%      domain, amounting in ripples in the frequency response
+%    - how bad are these ripples and can we tune the dish to mitigate
+%      their effect in the science?
+%    - as discussed above, it is useful to think in the delay domain as
+%      the translation from frequency structure introduced by dish
+%      reflections and the foreground isolation within the horizon delay
+%      is straightforward
+%    - the smooth spectral structure of the foregrounds sets a maximum
+%      foreground isolation achievable of ~60ns with blackman-harris
+%      window
+%    - f/D =0.32 maximizes efficiency for a PAPER dipole suspended over
+%      the dish
+%    - with typical reflection dish/feed reflection coefs, attenuation
+%      after 3 round trips will be below 60dB, and 1 and 2 round trips
+%      are in wedge, isolated away from EOR window
+%    - 14m also falls near the minimum of the cost per performance model
+
+The 14\,m HERA dish design is a departure from the large N--small D approach used by 21\,cm 
+observatories like PAPER and the MWA. Both observatories are actively pursuing power 
+spectrum analyses using several year data runs, but the sheer data volume makes 
+characterization and removal of systematics, as well as repeated or complimentary analyses, 
+challenging. A larger element was chosen for HERA primarily to economize data volume. 
+The natural consequence of a larger antenna aperture is a smaller field of view, but this is a 
+small effect for 21\,cm power spectrum analyses as our leverage on $k$ modes in the 
+spherically averaged power spectrum comes primarily from $k_\parallel$ modes along the line 
+of sight (in the frequency dimension).
+
+However, such a turn from small, simpler antenna elements to larger, more complex dishes with 
+suspended feeds must be done judiciously, lest the chromatic antenna response smear otherwise 
+smooth spectrum foreground power into cosmological signal modes. For this reason the dish 
+design was carefully optimized for a foreground avoidance-based power spectrum spectrum 
+analysis, as detailed by \citet{heraMemo5} and discussed in the larger engineering context of 
+HERA by DeBoer et al (in prep).
+
+We summarize here the logic leading to a 14\,m dish with $f/D\approx0.32$. As discussed 
+above, it is useful to think in delay-space, where a source ideally appears as a delta function 
+at the delay corresponding to the difference in light travel time to two antennas in a 
+baseline. In a real instrument, finite bandwidth and intrinsic source spectral structure 
+(synchrotron sources typically have $I\propto f^{-0.85}$) smear foreground power over a 
+kernel as wide as $\sim60$\,ns. All antennas have some frequency structure as well, though 
+dipole-like elements such as sleeved dipoles and bowties may be made relative frequency 
+independent over wide bands. Suspension of a feed over a dish introduces frequency 
+structure directly due to time domain reflections between the dish and feed. We optimize the 
+HERA dish so this frequency structure extends no farther into delay space than the 60\,ns 
+intrinsic width of foregrounds. This was accomplished first through numerical modeling of 
+the beam pattern with a PAPER dipole suspended over the dish aperture, and resulted in a 
+maximum efficiency of 73\% with $f/d\approx0.32$. From there, using realistic estimates of 
+reflection loss, a 14\,m dish was observed to have the property that the signal received at the 
+feed after two bounces (round trips between the dish and feed) is above -60\,dB but 
+contained in the wedge, but all higher order reflections in the EOR window are below 
+-60\,dB, and thus an order of magnitude smaller than the expected cosmological signal.
+
+In reality, the HERA dishes are somewhat more complicated that these simple considerations 
+imply, and part of the purpose of the beam measurements presented in this paper is to 
+characterize their \textit{in situ} beam patterns. The dish is fabricated out of low cost 
+construction materials with an expected lifetime of $\sim5$ years, sufficient to detect the 21\,cm 
+power spectrum to high significance before the Square Kilometer Array builds a longer lasting 
+instrument to more fully characterize the Epoch of Reionization with imaging. The feed consists 
+of a sleeved dipole, suspended in a cage structure from from three ropes attaching to telephone 
+poles spaced around the dish.
+The dipole is mounted on a XX\,m mast over a XX\,m diameter backplane surrounded by a XX\,m long cylindrical ``skirt'' designed to reduce cross coupling with adjacent elements
+by narrowing the feed's response. The dish surface consists of 12 wire mesh strips secured to 
+60\,mm PVC pipes forming the dish skeleton. A spar at 2.4\,m elevation is added to ensure 
+approximately parabolic shape. Note that we refer to this design as a \textit{faceted parabola} 
+given that the dish surface between PVC spars is not curved, though our design ensures the 
+Ruze loss is at the percent level. A door is engineered into one of these mesh strips to facilitate 
+feed maintenance.
+
+This work presents beam pattern measurements to verify the capabilities of this new dish, in particular the 
+position of the dish focus, the shape of the main lobe, the magnitude of the dish sidelobes, the 
+degree of beam symmetry, the actual dish/feed efficiency (i.e., collecting area), and the expected level of antenna-to-antenna variation.
+
+\subsection{Dish Modeling}
+\label{sec:dishmodels}
+
+ASK DAVE OR RICH TO WRITE A ONE OR TWO PARAGRAPH SUMMARY OF THE ELECTROMAGNETIC DISH SIMULATIONS
 
@@
 %\label{fig:null4}
-%\end{figure*}
-
-\section{Dish Design and Modeling}
-
-\subsection{Design of the HERA Dish}
-
-ASK DAVE DEBOER TO WRITE A TWO PARAGRAPH SUMMARY OF THE HERA ELEMENT AND HOW IT WAS DESIGNED
-
-\subsection{Dish Modeling}
-\label{sec:dishmodels}
-
-ASK DAVE OR RICH TO WRITE A ONE OR TWO PARAGRAPH SUMMARY OF THE ELECTROMAGNETIC DISH SIMULATIONS
-
-%\section{Feed Measurements}
-
-%Accurate modeling of both the dish and feed will be essential for final dish modeling.
-To that end, we deploy the feed on the ground facing the sky (Figure \ref{fig:feedpic}), replacing the north-most reference antenna in the \texttt{null3} configuration, to isolate the feed power pattern.
-
-%Figure \ref{fig:feed0} shows the measured feed beams (top panel) and slices through the E and H planes (bottom panel).
-Due to intermittent connection problems to the DAQ computer, we collected only 157 high signal-to-background satellite passes over a few days.
-Still, the data agree very well with the CST model for $\theta<55^\circ$, outside of which the E plane response starts narrows compared to the model by up to 5\,dB at $\theta=70^\circ$.
-Still, the data are quite sparse in these low regions due to the connection problems, and so the usual quality control cuts are likely less effective than usual.
-
-%\begin{figure*}[h]
-%\includegraphics[width=5in]{feed.jpg}
-%\caption{Feed deployed on the ground, facing the sky, replacing the north-most reference antenna in the \texttt{null3} configuration. }
-%\label{fig:feedpic}
-%\end{figure*}
-
-%\begin{figure*}[h]
-%\includegraphics[width=6.5in]{feed0_abs_old_ref_model.png}
-%\caption{Measurements of the feed power pattern, deployed so it faces the sky.
-The measurements agree well with the model for $\theta<55^\circ$, but start to diverge at large zenith angles, possibly due to quality control problems due to very sparse beam sampling.}
-%\label{fig:feed0}
 %\end{figure*}

### 2015-11-18 DishReflectometry/Paper1_v0.tex

@@
 Hence, the sky contribution from any direction would be confined within $-\tau_{g}<\tau<\tau_{g}$.
-Due to chromaticity of the sky signal, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with decaying amplitude [Ref to the figure Parsons12].
+Due to chromaticity of the sky signal as well as instrument reponse, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with decaying amplitude [Ref to the figure Parsons12].
 Sky delay spectrum $I_{sky}(\tau)$ is contributed by the foreground  $I_{fg}(\tau)$  which is spectrally smooth and the 21~cm power spectrum $I_{21}(\tau)$ which contains spectral signatures.
-Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces and the 21~cm delay spectrum is detectable.
+Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces and the 21~cm delay spectrum could potentially be detectable.
 
@@
 \section{Effects of additional reflections of the sky signal between the parabolic dish and the feed on the measured visibility}
+Response of any radio telescope is chromatic and modulates the true sky signal in the spectral domain.
+This results in the convolution of the instrument response kernel with the sky signal in the delay domain.
+This fundamentally limits the detectability of a 21~cm power spectrum.
+In this section, the effect of reflections on the visibility data and corresponding effect on the delay spectrum is discussed qualitatively.
+
  Plane waves incident on a parabolic dish are focussed at the feed which is kept at the focal plane of the dish.
@@
 However, a part of it reflects back and forth several times in between the feed and the vertex of the dish which is shadowed by the feed (dashed blue arrows in Figure \ref{fig:cartoon}).
-Such reflections generate multiple copies of the incident sky signal of reduced strength at various time/phase and thus produces spurious correlations in the visibilities of interferometric data.
+Such reflections generate multiple copies of the incident sky signal of reduced strength at various delay and phase and thus produces spurious correlations in the visibilities of interferometric data.
 In this section we compute the visibility of a two element interferometer accounting for the additional reflections of the sky signal in between the feed and the dish vertex and the corresponding effects on the delay spectrum.
@@
 \includegraphics[totalheight=0.35\textheight]{plots/reflection_cartoon.png}
-\caption{The blue solid lines represent an original sky signal entering the
-feed. A small percentage of it (dashed blue) is reflected off the dish, and it
-is these reflections that we are concerned about. In our measurements however,
-the reflections measured contain most of the original pulse signal (solid red),
-so it is crucial to adjust for this difference in our analysis.}
+\caption{The propagation path of the sky signal entering the
+feed in receiving mode is shown in blue.
+Due to impedance mismatch between feed and the free space, a part of the signal (dashed blue) is reflected off the feed.
+This signal reflects off the dish apex several times and returns to the feed at multiple delays with reduced signal strength.
+The red line shows the signal path during measurements which is done in transmission mode.
+Appropriate corrections are made to derive the telescope response function during sky observation.
+}
 \label{fig:cartoon}
@@
 Hence, for first incidence $\Gamma_{d}=1$.
-Sky signal that would return to the dish after successive reflections off the feed and the dish is only reflected from a small area around the vertex of the dish and therefore, $\Gamma_{d}<1$.
+Sky signal that would return to the dish after successive reflections off the feed and the dish is reflected only from a small area around the vertex of the dish and therefore, $\Gamma_{d}<1$.
 In our analysis, we consider one reflection of the sky power from the feed and subsequent reflection off the dish as one single reflection.
@@
 Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum. 
- Fourier transform of the visibility contributed by any two voltage components from two antennas with no mutual delay will be located at the same delay $\tau $ in the Fourier domain whereas any two voltage components from two antennas components having a mutual delay of $\Delta \tau$ will be centred at $\Delta \tau$.
+ Fourier transform of the visibility contributed by any two voltage components from two antennas with no mutual delay will be located at the same delay $\tau$ in the Fourier domain whereas any two voltage components from two antennas components having a mutual delay of $\Delta \tau$ will be centred at $\tau+\Delta \tau$.
 This additional delay extends the upper limit on the maximum geometric delay $\tau_{g}$ to $(\tau_{g}+\Delta \tau)$.
- Thus, the correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal thus extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected.
- If the dish vertex is so constructed such that the reflection from the dish vertex is negligible i.e, $\Gamma_{d}<<1\ or = 0$ then the second and the third term of the $\Sigma$ vanish.
+ Thus, the correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected.
+
+ %If the dish vertex is so constructed such that the reflection from the dish vertex is negligible i.e, $\Gamma_{d}<<1\ or = 0$ then the second and the third term of the $\Sigma$ vanish.
 Also, the second term in the expression of $\Sigma(\vec b, \nu)$ is negligible compared to the first and the third term of the expression and, therefore, can be neglected.
@@
 
-\subsection{Effect of higher order reflection on the delay spectrum} 
+\subsection{Effect of multiple reflections on the delay spectrum} 
 Correlation between the higher order reflections of the signal in any antenna with the direct component of the other would result in a delay response at integral multiple of $\Delta \tau$ and vice versa.
@@
 
-\begin{equation}
-\Sigma(\vec b, \nu) = a_{f} \left [ 1+ 2 \Re \left [(1-\Gamma_{f}) \Gamma_{f}\Gamma_{d} e^{i\phi}+ (1-\Gamma_{f})^{2}(\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+(1-\Gamma_{f})^{n} (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi} \right ]\right ]
-\end{equation}
+\begin{eqnarray}
+\Sigma(\vec b, \nu) & = & a_{f}  [ 1+ 2 \Re [(1-\Gamma_{f}) \Gamma_{f}\Gamma_{d} \dfngexp+ (1-\Gamma_{f})^{2}(\Gamma_{f}\Gamma_{d})^2(\dfngexp)^{2}+ \nonumber\\
+&&  ....+(1-\Gamma_{f})^{n} (\Gamma_{f}\Gamma_{d})^{n}(\dfngexp)^{n} ] ]
+\end{eqnarray}
 
-and the measured visibility spectrum, integrated over all sky would be, 
+and the measured visibility spectrum would be, 
 \begin{equation}\label{eqn:series1}
@@
 \end{equation}
-Corresponding delay spectrum would be, 
+Taking the Fourier transform of the visibility we obtain the delay spectrum
 \begin{eqnarray}

### 2015-11-19 DishReflectometry/Paper1_v0.tex
Started rewriting section 4 and merging content of section 4 and 5.

@@
 Our goal is to determine the effect of the instrument response $\Sigma(\nu)$ on the delay spectrum measurement.
+
 \section{Measurements}
 We carried out reflectometry measurements at the HERA element prototype in Green
-Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise its performance. As HERA progresses as
-an experiment, it is necessary to build optimised dishes that aim to minimise the
-challenges of chromaticity in our quest for the Epoch of Reionization.
+Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise its performance. An HERA element consists off a $14\,m$ diameter
+parabolic reflector and a crossed-dipole pair as a feed.
+The cross dipole antenna pair is identical to the feed of the PAPER antenna which is suspended at the focal plane of the dish with the support of three vertical poles.
+HERA elements are closely spaced with centre to centre distance between two reflections being equal to the dish diameter.
+Therefore, to reduce the coupling between the adjecent dishes, the crossed dipole feed along with the back plane is encased in a cylindrical cage.
+The feed is raised and
+lowered by a three-pulley system mounted on the three poles. The focal height of the dish is $4.5m$
+($\sim{14.76}$ft).
+
+%As HERA progresses as an experiment, it is necessary to build optimised dishes that aim to minimise the
+%challenges of chromaticity in our quest for the Epoch of Reionization.
 

### 2015-11-19 ForegroundSimulations/ms.tex

@@
 
-Hydrogen Epoch of Reionization Array (HERA\footnote{\url{http://reionization.org/}}; DeBoer~et~al.~2015, Murchison Widefield Array \citep[MWA;][]{lon09,bow13,tin13}, Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, Low Frequency Array \citep[LOFAR;][]{van13}
+The period in the history of the Universe characterized by the transition of neutral hydrogen in the intergalactic medium (IGM) to a fully ionized state due to the formation of radiating objects such as the first stars and galaxies is referred to as the Epoch of Reionization (EoR).
+This is an important period of nonlinear growth of matter density perturbations and astrophysical evolution leading to the large scale structure observed currently in the Universe.
+And yet, this period in the Universe's history has remained poorly probed to date with observations.
 
-Wedge papers \citep{ali08,ber09,ber10,bow09,liu09,liu14a,liu14b,dat10,liu11,gho12,mor12,par12b,tro12,dil13,dil14,pob13,thy13,thy15a,thy15b}
+The redshifted neutral hydrogen from the IGM in this epoch has been identified to be one of the most promising and direct probes of the EoR \citep{sun72,sco90,mad97,toz00,ili02}.
+Numerous experiments using low frequency radio telescopes targeting the redshifted 21~cm line from the spin-flip transition of H{\sc i} have become operational such as the Murchison Widefield Array \citep[MWA;][]{lon09,bow13,tin13}, the Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, the Low Frequency Array \citep[LOFAR;][]{van13} and the Giant Metrewave Radio Telescope EoR experiment \citep[GMRT;][]{pac13}.
+These instruments have sufficient sensitivity for a statistical detection of the EoR signal via estimating the spatial power spectrum of the redshifted H{\sc i} temperature fluctuations \citep{bea13,thy13}.
+These instruments are intended to be precursors and pathfinders to the next generation of low frequency radio observatories such as the Hydrogen Epoch of Reionization Array\footnote{\url{http://reionization.org/}} (HERA; DeBoer~et~al.~2015) and the Square Kilometre Array\footnote{\url{https://www.skatelescope.org/}} (SKA).
+These next-generation instruments will advance the capability from a mere statistical detection of the signal to a direct three-dimensional tomographic imaging of the H{\sc i} during the EoR.
+
+The most significant challenge to low frequency EoR observations arises from the extremely bright Galactic and extragalactic foreground synchrotron emission which are $\sim 10^4$ times stronger than the desired EoR signal \citep{dim02,ali08,ber09,ber10,gho12}.
+All the current and future instruments rely on the inherent differences in spatial isotropy and spectral smoothness between the EoR signal and the foregrounds to extract the EoR power spectrum \citep[see, e.g.,][]{fur04,mor04,zal04,san05,fur06,mcq06,mor06,wan06,gle08}.
+
+When expressed in the coordinate system of power spectrum measurements described by the three-dimensional wavenumber ($k$), the foreground emission is restricted to a wedge-shaped region commonly referred to as the {\it foreground wedge} \citep{bow09,liu09,liu14a,liu14b,dat10,liu11,gho12,mor12,par12b,tro12,ved12,dil13,pob13,thy13,dil14} whereas the EoR signal has spherical symmetry due to its isotropy which appears elongated along line of sight $k$ modes due to peculiar velocity effects when dominated by matter density perturbations during early stages of reionization.
+The extreme dynamic range required to subtract foregrounds precisely demands high precision modeling of foregrounds as observed by modern wide-field instruments \citep{,thy15a,thy15b}.
 

### 2015-11-23 DishReflectometry/Paper1_v0.tex
continuing with section 4.0

@@
 Our goal is to determine the effect of the instrument response $\Sigma(\nu)$ on the delay spectrum measurement.
-
+%%%%%%%%%%%%%%%
 \section{Measurements}
@@
 The cross dipole antenna pair is identical to the feed of the PAPER antenna which is suspended at the focal plane of the dish with the support of three vertical poles.
-HERA elements are closely spaced with centre to centre distance between two reflections being equal to the dish diameter.
-Therefore, to reduce the coupling between the adjecent dishes, the crossed dipole feed along with the back plane is encased in a cylindrical cage.
+HERA elements are closely spaced with centre to centre distance between two dishes are equal to the dish diameter.
+Therefore, to reduce the coupling between the adjacent dishes, the crossed dipole feed along with the back plane is encased in a cylindrical cage.
 The feed is raised and
@@
 reflection coefficient is $\Gamma_{f}$, and the dish reflection
-coefficient is $\Gamma_{d}$, then the net power entering the feed after
-$n^{th}$ reflection off the feed and the dish (i.e, the sky integrated visibility spectrum) is:
+coefficient is $\Gamma_{d}$, then the net power entering a feed after
+$n^{th}$ reflection off the feed and the dish is:
 
-\begin{equation}\label{eqn:series1}
-I_{meas} =  I_{sky}A_{f}[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
-\end{equation}
+\begin{eqnarray}
+\tilde I_{meas}(\vec b, \nu) & = & \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp d\Omega
+\end{eqnarray}
 
-where, $\phi = 2\pi i\nu \Delta \tau$ is the roundtrip propagation delay of a lightwave of frequency $\nu$ due to a reflection over the focal distance $l$.
-It is noted that upon the first incidence, the sky signal is focussed onto the feed from the entire dish and the dish reflection coefficient $\Gamma_{d}$ is $1$ for this first incidence.
+where, $\Delta \tau$ is the roundtrip propagation delay of a frequency $\nu$ due to a reflection over the focal distance $l$.
+$I_{meas}$ is the auto correlated power obtained from a single HERA element.
+Upon our assumption that two adjacent antenna elements have identical electrical properties, this power is also a measure of the cross power or the visibility $\vis (\vec b, \nu)$ between the two antennas with a normalisation factor of $2$.
+Once again, it is to be noted that upon the first incidence, the sky signal is focussed onto the feed from the entire dish and the dish reflection coefficient $\Gamma_{d}$ is $1$ for this first incidence.
 The subsequent back and forth reflection of the signal in between the feed and the dish, however, occurs from only the part of the dish which is shadowed by the feed.
 Therefore, in this case, $\Gamma_{d} < 1$.
+For a given baseline $\vec b$, taking the ratio of the measured power and the incident power,
 
-Simplifying Equation \ref{eqn:series1}:
 \begin{eqnarray}\label{eqn:ratio1}
-{I_{in} \over I_{sky} } & = & A_{f}[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}] \nonumber\\
-      & = & A_{f} \displaystyle\sum\limits_{n=0}^{n} [\Gamma_{f}\Gamma_{d}e^{i \phi}]^{n}\nonumber\\
-      & = & A_{f}+A_{f} \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i \phi}]^{n}
+{I_{meas} \over I_{sky} } & = & \Sigma(\vec b, \nu) \nonumber\\
+      & = & a_{f}  [ 1+ 2 \Re [(1-\Gamma_{f}) \Gamma_{f}\Gamma_{d} \dfngexp+ (1-\Gamma_{f})^{2}(\Gamma_{f}\Gamma_{d})^2(\dfngexp)^{2}+ \nonumber\\
+&&  ....+(1-\Gamma_{f})^{n} (\Gamma_{f}\Gamma_{d})^{n}(\dfngexp)^{n} ] ]
 \end{eqnarray}
+
+The right hand side of this equation is the instrument response kernel of a single HERA element as well as a representative of the instrument response in the measured visibility data between a pair of antennas.
+Our goal is to measure this kernel as a function of frequency and determine its effect on the delay spectrum of the visibility.
+\subsection{Method}
 

### 2015-12-04 DishReflectometry/Paper1_v0.tex
Continued rewriting section 4

@@
 \volt_{1} & = & a \volt_{sky}(1-\Gamma_{f}) + a \volt_{sky} \Gamma_{f} \Gamma_{d} \dfngexp  (1-\Gamma_{f})^{2}\nonumber\\
-         & = & a \volt_{sky} (1-\Gamma_{f}) \left [ 1+ (1-\Gamma_{a})\Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau} \right]\nonumber\\
-\label{eq4}
+         & = & a \volt_{sky} (1-\Gamma_{f}) \left [ 1+ (1-\Gamma_{a})\Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau} \right]\nonumber
 \end{eqnarray}
@@
 \volt_{2} & = & \left [ a \volt_{sky}(1-\Gamma_{f}) + a \volt_{sky} \Gamma_{f} \Gamma_{d} \dfngexp (1-\Gamma_{f})^{2}\right ] \fngexp \nonumber\\
-         & = & a \volt_{sky} (1-\Gamma_{f}) \left [ 1+(1-\Gamma_{a}) \Gamma_{f} \Gamma_{d} \dfngexp  \right] \fngexp \nonumber\\
-\label{eq5}
+         & = & a \volt_{sky} (1-\Gamma_{f}) \left [ 1+(1-\Gamma_{a}) \Gamma_{f} \Gamma_{d} \dfngexp  \right] \fngexp \nonumber
 \end{eqnarray}
@@
 		        & = & \int \bm_{f} \volt_{sky}|^{2} |\left [ 1+(1-\Gamma_{f}) \Gamma_{f} \Gamma_{d} \dfngexp  \right]|^{2} \fngexp  d\Omega
-\label{eq6}		        
+\label{eq4}		        
 \end{eqnarray}
@@
  	    & = &  \bm_{f}  \left[ 1+ |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} + 2 \Re \left ( (1-\Gamma_{f})\Gamma_{f}\Gamma_{d} \dfngexp \right) \right] 
-\label{eq{7}}	    
+\label{eq{5}}	    
 \end{eqnarray}
@@
 $n^{th}$ reflection off the feed and the dish is written as:
-\begin{equation}
-\volt_{1} =  a_{f} \volt_{sky}[1+ (1-\Gamma_{f})\Gamma_{f}\Gamma_{d} \dfngexp + (1-\Gamma_{f})^{2} (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ ....+ (1-\Gamma_{f})^{n}(\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}]
-\end{equation}
+\begin{eqnarray}
+\volt_{1} & = &  a_{f} \volt_{sky}[1+ (1-\Gamma_{f})\Gamma_{f}\Gamma_{d} \dfngexp + (1-\Gamma_{f})^{2} (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
+&&  ....+ (1-\Gamma_{f})^{n}(\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}] \nonumber
+\end{eqnarray}
 and,
@@
 \volt_{2} & = &  a_{f} \volt_{sky}[1+ (1-\Gamma_{f})\Gamma_{f}\Gamma_{d} \dfngexp + (1-\Gamma_{f})^{2} (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
-&& ....+ (1-\Gamma_{f})^{n}(\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}] \ast \fngexp 
+&& ....+ (1-\Gamma_{f})^{n}(\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}] \ast \fngexp \nonumber
 \end{eqnarray}
@@
 \Sigma(\vec b, \nu) & = & a_{f}  [ 1+ 2 \Re [(1-\Gamma_{f}) \Gamma_{f}\Gamma_{d} \dfngexp+ (1-\Gamma_{f})^{2}(\Gamma_{f}\Gamma_{d})^2(\dfngexp)^{2}+ \nonumber\\
-&&  ....+(1-\Gamma_{f})^{n} (\Gamma_{f}\Gamma_{d})^{n}(\dfngexp)^{n} ] ]
+&&  ....+(1-\Gamma_{f})^{n} (\Gamma_{f}\Gamma_{d})^{n}(\dfngexp)^{n} ] ]\\
+& = & { a_{f}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
+   \nonumber\\
+   \label{eq6}
 \end{eqnarray}
@@
 {I_{meas} \over I_{sky} } & = & \Sigma(\vec b, \nu) \nonumber\\
-      & = & a_{f}  [ 1+ 2 \Re [(1-\Gamma_{f}) \Gamma_{f}\Gamma_{d} \dfngexp+ (1-\Gamma_{f})^{2}(\Gamma_{f}\Gamma_{d})^2(\dfngexp)^{2}+ \nonumber\\
-&&  ....+(1-\Gamma_{f})^{n} (\Gamma_{f}\Gamma_{d})^{n}(\dfngexp)^{n} ] ]
+  & = & { a_{f}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
+   \nonumber\\
 \end{eqnarray}
@@
 Our goal is to measure this kernel as a function of frequency and determine its effect on the delay spectrum of the visibility.
+
+%%%%%%%%%%%%%%%%%
 \subsection{Method}
-
-In our experimental set-up, we use the feed as a transmitter and transmit a pulse. If the initial pulse is a broadband signal,
-$I_{tr}$, sent to the feed via a $75ft$ cable by a vector network
-analyser (VNA), a delay domain measurement of the system is accomplished by
-taking the Fourier transform of the complex return loss of the feed measured by VNA. When the signal is incident on
-the feed, part of the incident power ($\Gamma_{f}$) is reflected back to the
-measuring device (dashed red arrows in Figure \ref{fig:cartoon}) and
-$(1-\Gamma_{f})$ is radiated by the feed (solid red arrows in Figure
-\ref{fig:cartoon}) which illuminates the dish. While most of the incident signal is reflected back into space by the dish, the reflected signal from the dish vertex returns to
+The instrument response kernel is measured by measuring the return loss of the antenna element at the output port of the feed using a vector network analyser.
+The vector network analyser transmits a broadband noise of known amplitude and phase via a $75ft$ cable up to the feed.
+While a part of this signal  is returns to the VNA post reflection from the feed due to mismatch between the cable and the antenna impedance resulting in the primary return loss, rest of the signal is radiated out by the antenna and illuminates the dish and radiated into the space.
+However, the reflected signal from the dish vertex returns to
 the feed. This incident signal is now
 reflected back and forth in between the feed and the dish much like the sky
-signal reflection discussed previously.  Hence, if $I_{r}$ is the power
-incident back on the feed for the first time then the reflected power, $I_{refl}$,
+signal reflection discussed previously.
+
+If $I_{tr}$ is the signal transmitted by the VNA , $\Gamma_{f}$ is the feed reflection coefficient, $I_{r}$
+is the power incident back on the feed after reflection from the dish then the reflected power, $I_{refl}$,
 back into the VNA would be:
-
 \begin{equation}\label{eqn:series2}
@@
 
-Once again, note that we consider one reflection from the feed and its subsequent reflection from the dish as one reflection in total.
+Once again, we consider one reflection from the feed and its subsequent reflection from the dish as one reflection in total.
 Equation \ref{eqn:series2} is similar to Equation \ref{eqn:series1}, with different incident powers.
 
-Recall that $I_{r}$ is the initial power that is incident back on the feed, which is just the feed radiated power reflected off the dish:
+$I_{r}$ is the power that is incident back on the feed, which is just the feed radiated power reflected off the dish:
 
@@
 
-Also note that the first reflection of the signal sent by the VNA occurs at the feed end. Hence the total returned power $P_{ret}$, to the VNA  would be:
+Hence the total returned power $P_{ret}$, to the VNA  would be:
 
@@
   +  \Gamma_{d}(1-\Gamma_f)^{2} [e^{i\phi}+ \Gamma_{f}\Gamma_{d} e^{i2\phi}+  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{i n\phi}]\nonumber\\
-  & = & \Gamma_{f} + { (1-\Gamma_f)^{2}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
+  & = & \Gamma_{f} + { (1-\Gamma_f)a_{f}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
    \nonumber\\
@@
 The VNA measures the magnitude and phase of the quantity ${I_{ret}\over I_{tr}}$
-as a function of frequency as shown in Figure \ref{fig:freq}. In our measurement
+as a function of frequency as shown in Figure \ref{fig:freq}.
+The magnitude and phase of the complex return loss is measured between 50 to 500MHz over 1024 frequency channels which gives a frequency resolution of 0.44MHz.
+The delay resolution of the measurements is ?t = 2.22ns.
+In our measurement
 set-up, the first reflection occurs at the feed $\Gamma_{f}$, so
@@
 
-\section{Methodology}{\label{sec:methods}}
+%\section{Methodology}{\label{sec:methods}}
 
-Our reflectometry measurements are made using a prototype HERA dish at NRAO in Green Bank, WV. The dish is a $14\,m$ diameter
-parabolic reflector structurally supported with 3 telephone poles. The
-reflective material is made up of wire mesh that is attached to PVC
-pipes, forming the parabolic shape of the dish. With the current iteration of
-the HERA dish, the feed consists of a PAPER dipole encased in a cylindrical cage
-encompassing the backplane. The PAPER feed and the backplane (which is aimed at
-preventing feed-to-feed interaction between neighboring dishes) is raised and
-lowered by a three-pulley system. The focal height of the dish is $4.5m$
-($\sim{14.76}$ft).
+%Our reflectometry measurements are made using a prototype HERA dish at NRAO in Green Bank, WV. The dish is a $14\,m$ diameter
+%parabolic reflector structurally supported with 3 telephone poles. The
+%reflective material is made up of wire mesh that is attached to PVC
+%pipes, forming the parabolic shape of the dish. With the current iteration of
+%the HERA dish, the feed consists of a PAPER dipole encased in a cylindrical cage
+%encompassing the backplane. The PAPER feed and the backplane (which is aimed at
+%preventing feed-to-feed interaction between neighboring dishes) is raised and
+%lowered by a three-pulley system. The focal height of the dish is $4.5m$
+%($\sim{14.76}$ft).
 
@@
 %the plots.[XXX not done yet but will be done]
-Our measurements are made with a FieldFox in VNA mode. In this mode, a pulse
-is generated in the FieldFox and sent through a $75ft$ $50\Omega$ cable that
-connects to the feed with a 4:1 passive balun.
+%Our measurements are made with a FieldFox in VNA mode. In this mode, a pulse
+%is generated in the FieldFox and sent through a $75ft$ $50\Omega$ cable that
+%connects to the feed with a 4:1 passive balun.
 The magnitude and phase of the complex return loss is measured between 50 to $500MHz$ over 1024 frequency channels which gives a frequency resolution of 0.44MHz.
 The delay resolution of the measurements is $\Delta{t}=2.22ns$.
-In addition, we note that the round trip of a reflection from the feed to the dish
-is $9m$, which corresponds to a delay of $30ns$.
+%In addition, we note that the round trip of a reflection from the feed to the dish
+%is $9m$, which corresponds to a delay of $30ns$.
 
@@
 \end{figure}
+%++++++++++++++++++++++++++++++++++++++++++++++++++++++
 
-Frequency domain data, as shown in Figure \ref{fig:freq}, can be Fourier-transformed to compute the return loss in the delay domain.
-Because the measured data is band-limited between $50$ to $500MHz$, it is analogous to multiply the measured data by a square window function.
-Then in delay domain, the response would be convolved with a $sinc$ function.
-This may result in excess power at high
-delays due to the sidelobes of the $sinc$ function. Hence, appropriate windowing of the measured data set is necessary before taking the Fourier transform.
-We have chosen a Hamming window for our analysis, and its effectiveness of this
-window function compared to others is illustrated in Figure
-\ref{fig:window}.
+\subsection{Estimation of the delay spectrum of the instrument}
+Frequency domain data, as shown in Figure \ref{fig:window}, is Fourier-transformed to compute the response of the system in the delay domain.
+The signal transmitted by the VNA is reflected first from the feed.
+In delay domain,  this appears at the zero delay bin.
+We subtract this value from the measured data and divide the the data by a factor $(1-\Gamma_{a})$ to derive the delay spectrum for the system operating in receiving mode during sky observation.
+%Because the measured data is band-limited between $50$ to $500MHz$, it is analogous to multiply the measured data by a square window function.
+%Then in delay domain, the response would be convolved with a $sinc$ function. This may result in excess power at high
+%delays due to the sidelobes of the $sinc$ function. Hence, appropriate windowing of the measured data set is necessary before taking the Fourier transform.
+%We have chosen a Hamming window for our analysis, and its effectiveness of this
+%window function compared to others is illustrated in Figure
+%\ref{fig:window}.
 

### 2015-12-06 DishReflectometry/Paper1_v0.tex
Almost all changes are done. New figures need to be made and inserted. Have to take careful look on the paper format.

@@
   			      & = & \int \left [ I_{sky}(\thhat, \nu) \ast \Sigma(\thhat, \nu) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )  \right] d\Omega
+\label{eq7}
 \end{eqnarray}
@@
    \nonumber\\
+   \label{eq8}
 \end{eqnarray}
@@
   & = & \Gamma_{f} + { (1-\Gamma_f)a_{f}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
-   \nonumber\\
+ \label{eq9}
 \end{eqnarray}
@@
 Figure \ref{fig:freq} shows the return loss for a frequency bandwidth of $50$ to
-$500MHz$. This measurement was taken with the feed suspended at $4.26m$, which
-was our closest measurement to the actual focal height.  Because the return
-loss is the ratio of the power received to the power transmitted, higher
-reflections can clearly be seen outside of the PAPER bandwidth. This is not
-surprising, since the feed is tuned specifically for PAPER. The return loss
-minima are locations where our feed is well-matched to free space.
+$500MHz$, measured when the feed is suspended at the focal plane of the parabolic dish which is at $4.26m$ from the dish vertex. 
+This measurement is Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{eq3}.
+%In Figure \ref{fig:3bands}, the return loss we measure is plotted versus delay
+%for three chosen bandwidths: the HERA bandwidth, the PAPER bandwidth, and a
+%typical power spectra bandwidth when using a Hamming window function. Two
+%additional measurements, using data taken in 2014 with the first prototype HERA
+%dish near Berkeley, CA, are also plotted using two different bandwidths. One of
+%the main differences between the Green Bank and Berkeley measurements is that
+%the feed was not encompassed in a cage for the Berkeley data (only a backplane). Additionally, the $50-1000MHz$ data taken in Berkeley was
+%Fourier-transformed internally by the measuring device, while the $100-200MHz$
+%data is analyzed post-measurement in the same way as the Green Bank data.
 
-In Figure \ref{fig:3bands}, the return loss we measure is plotted versus delay
-for three chosen bandwidths: the HERA bandwidth, the PAPER bandwidth, and a
-typical power spectra bandwidth when using a Hamming window function. Two
-additional measurements, using data taken in 2014 with the first prototype HERA
-dish near Berkeley, CA, are also plotted using two different bandwidths. One of
-the main differences between the Green Bank and Berkeley measurements is that
-the feed was not encompassed in a cage for the Berkeley data (only a backplane). Additionally, the $50-1000MHz$ data taken in Berkeley was
-Fourier-transformed internally by the measuring device, while the $100-200MHz$
-data is analyzed post-measurement in the same way as the Green Bank data.
-
-From the plot, we see that the delay response of a feed is dependent on the band chosen for the Fourier transform.  As one might expect, in regions
-where the feed return loss is low, reflections are minimized.  Thus, we cannot ignore that these measurements were performed
-using a PAPER-style feed tuned for efficient operation over a $100-200MHz$ bandwidth.  Fourier transforms taken over wider bands
-become dominated by the feed performance in regions outside the operating band, making the resultant delay profiles less relevant
+The delay response of the instrument is dependent on the band chosen for the Fourier transform.
+%As one might expect, in regions where the feed return loss is low, reflections are minimized.  Thus, we cannot ignore that these measurements were performed
+%using a PAPER-style feed tuned for efficient operation over a $100-200MHz$ bandwidth. 
+The measurement bandwidth effects the amplitude and phase of the delay spectrum. Fourier transforms taken over wider bandwidth
+become dominated by the feed sidelobes outside the operating band, making the resultant delay profiles less relevant
 for the power spectrum performance of the HERA instrument.  Conversely, when performing Fourier transforms over much 
@@
 becomes dominated by sidelobes of low delay emission interacting with the narrow bandwidth kernel.  
-Although this may appear to be a relevant performance metric
-for PAPER-style power spectrum analysis, such an analysis typically pre-filters out low-delay emission using wide bandwidths precisely to avoid
-sidelobes from low-delay emission.  Hence, the most relevant delay-spectrum performance profile is that taken using the $100-200MHz$ band.
+Although this may appear to be a relevant performance metric for PAPER power spectrum analysis, such an analysis typically pre-filters out low-delay emission using wide bandwidths precisely to avoid sidelobes from low-delay emission.
+Hence, the most relevant delay-spectrum performance profile is that taken using the $100-200MHz$ band.
+\textbf{In the $100-200MHz$ delay profile, we see a delay response of $-25dB$ at $60ns$, which slopes down to $-60dB$ at $\sim120ns$.
+WRITE AGAIN}
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=1.0\linewidth]{plots1/delayspectrum_height.png}
+\caption{Delay transform of the transfer function of the HERA element keeping the feed at various heights.
+Delay transform is produced by taking the Fourier transform of the measurement using Blackman-Harris window.}
+\label{fig:elevator}
+\end{figure}
+\begin{figure}[H]
+\centering
+\includegraphics[totalheight=0.41\textheight]{plots/delay_feed.png}
+\caption{Delay plots produced using a Hamming window function for different feed only configurations and the PAPER bandwidth ($100MHz-200MHz$).
+The black dashed lines illustrate our ``60 by 60" specification.}
+\label{fig:outofthedish}
+\end{figure}
 
-In the $100-200MHz$ delay profile, we see a delay response of $-50dB$ at $60ns$, which slopes down to $-60dB$ at $\sim120ns$.  Because
-this does not achieve $-60dB$ attenuation at $60ns$, this indicates that the HERA system under test does not meet specification. However, we can learn additional information by evaluating
-different feed components.
-
-%\begin{figure}[ht!]
-%\centering
-%\includegraphics[width=1.0\linewidth]{plots1/delayspectrum_height.png}
-%\caption{Delay transform of the transfer function of the HERA element keeping the feed at various heights.
-Delay transform is produced by taking the Fourier transform of the measurement using Blackman-Harris window.}
-%\label{fig:elevator}
-%\end{figure}
-
-Figure \ref{fig:elevator} is again a delay plot of the return loss, but for
-four different feed suspension heights. We use the PAPER bandwidth and note
-that the measurements are near identical at low delays, implying that low delay
-reflections are caused primarily by reflections within the feed cage. However,
-at higher delays we notice discrepancies between the different heights.
-
-In addition, Figure \ref{fig:outofthedish} presents measurements taken of the feed
-away from the dish. Echosorb is placed under the feed for some of the
+Figure \ref{fig:elevator} is again a delay plot of the return loss at four different feed suspension heights. 
+We use the PAPER bandwidth and note
+that the measurements are near identical at low delays, implying that low delay reflections are caused primarily by reflections within the feed cage. 
+However, at higher delays we notice discrepancies between the different heights.
+In addition, Figure \ref{fig:outofthedish} presents measurements taken of the feed only.away from the dish. Echosorb is placed under the feed for some of the
 measurements, with the expectation that it will prevent any reflections off the
-ground. Measurements are also taken of the feed inside its metal cage in
-various configurations. It is shown that the feed performs best without the cage and with the absorber.
-
-From these various measurements, we find that the feed itself is responsible for a significant portion of the structure up to $60ns$ and
-that the cylindrical cage may be contributing up to $20ns$ to the width of the delay profile. We note that this depends strongly
-on its coupling to structures around it. Structure beyond $60ns$ appears to scale
-with the height of the feed above the dish, making reflections off the dish the likely culprit.
+ground.
+ Measurements are also taken of the feed inside its metal cage in various configurations. It is shown that the feed performs best without the cage and with the absorber. 
+All these measurements are suggestive of the  fact that the feed-cage assembly itself is responsible for a significant portion of the structure up to $60ns$ and
+that the cylindrical cage may be contributing up to $20ns$ to the width of the delay profile. 
+We note that this depends stronglyon its coupling to structures around it. 
+Structure beyond $60ns$ appears to scale with the height of the feed above the dish.
 
@@
 Given the critical nature of the windowing function, we recommend that all reflectometry measurements be performed in the
-frequency domain, so that the data analyst can manually implement the Fourier transform with the appropriate window.
+frequency domain, so that the data could be Fourier transformed with the appropriate window.
 

### 2015-12-09 ForegroundSimulations/notes.tex
Add three figures and notes.tex, notes.pdf to repo
From 1ff4129 (master):
=====================

(*) Add three figures and notes.tex, notes.pdf to git repo. These
figures go into the notes and are meant to illustrate initial findings
from simulations of delay spectra of foregrounds and EoR signal. It is
meant to be used for stimulating discussions on how much we understand
our signal and foregrounds.

--- 2015-11-19 ForegroundSimulations/ms.tex
@@
 
+Figure~\ref{fig:simulated-visibilities} shows the simulated visibilities from foregrounds, the redshifted H~{\sc i} fluctuations, and residual foregrounds visibilities after deconvolution along the delay axis.
+The black curves indicate visibilities obtained with an achromatic antenna power pattern (does not change with frequency over the entire bandwidth) while the gray curves are the corresponding visibilities for a chromatic beam.
+The solid lines in black and gray denote foreground visibilities.
+The dashed curves in the same colors denote visibilities from simulated redshifted H~{\sc i} fluctuations, and the dotted-dashed lines denote the residual visibilities obtained after deconvolution of the foreground delay spectra.
+The orange curve denotes a wideband Blackman-Harris window applied to the foreground visibilities to produce delay spectra which were subsequently deconvolved to obtain the residual visibilities.
+The red, blue and green curves denote the narrowband Blackman-Harris window weights centered on 150, 160 and 170~MHz each of effective bandwidth $\simeq 10$~MHz that will be applied to the simulated EoR H~{\sc i} signal and the foregrounds (both simulated and residual visibilities).
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=\linewidth]{simulated_FG_EoR_visibilities.eps}
+\caption{Simulated EoR H~{\sc i} and foreground visibilities over 100~MHz bandwidth for a 14.6~m baseline of HERA. \label{fig:simulated-visibilities}}
+\end{figure}
+
+Figure~\ref{fig:wideband-delay_spectrum} shows the delay spectra of simulated foreground visibilities (in orange) obtained with chromatic (dashed) and achromatic (solid) beams both weighted with the wideband Blackman-Harris window functions in the spectrum, the corresponding CLEAN components in gray and the residuals in black.
+The depth of deconvolution is set by the limit at which the rms of the residuals inside the horizon limits becomes equal to that on the outside.
+It is observed that the visibilities simulated with chromatic power pattern (dashed orange) are significantly broadened in delay spectra due to the additional chromaticity.
+The delay deconvolution is restricted to the {\it foreground wedge} with three additional delay bins on either side of the wedge.
+Due to this restriction, the residuals inside the horizon delay limits are lower than those outside.
+Since the simulated visibilities obtained using the achromatic power pattern are predominantly contained well within the horizon delay limits, the delay-domain deconvolution of these delay spectra is much more effective at lowering the residuals (by $\sim 2$ orders of magnitude) than in the case of visibilities obtained with a chromatic power pattern.
+These delay spectrum residuals correspond to the visibility residuals plotted in Figure~\ref{fig:simulated-visibilities}.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=\linewidth]{wideband_simulated_FG_delay_spectrum.eps}
+\caption{. \label{fig:wideband-delay_spectrum}}
+\end{figure}
+
+Figure~\ref{fig:subband-delay_spectrum} shows the delay spectra of the simulated EoR H~{\sc i} fluctuations and the foregrounds.
+The three panels show the three different center frequencies (150, 160, and 170~MHz) around which the delay spectra were obtained using the narrow band Blackman-Harris window functions shown earlier in Figure~\ref{fig:simulated-visibilities}.
+Delay spectra obtained using chromatic and achromatic antenna power patterns are shown in black and gray colors respectively.
+The dashed lines denote delay spectra of foreground residuals obtained after complex delay-domain deconvolution under the concept of foreground removal.
+The dotted lines denote the foreground delay spectra obtained under the concept of foreground avoidance where foregrounds were not removed but simply down-weighted by the narrowband Blackman-Harris window unctions.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=\linewidth]{subband_simulated_EoR_FG_delay_spectrum.eps}
+\caption{. \label{fig:subband-delay_spectrum}}
+\end{figure}
+
+It is noticed from Figure~\ref{fig:simulated-visibilities} that the foregrounds are about 5 orders of magnitude brighter than the EoR H~{\sc i} fluctuations in the visibilities.
+From Figure~\ref{fig:subband-delay_spectrum} it is seen that the foreground visibilities under foreground avoidance and their residuals under foreground removal are still brighter than the EoR signal.
+The delay spectra of foreground residuals however are much closer in magnitude to the EoR signal (to a factor $\lesssim 10$) at $|\tau| \gtrsim 200$~ns.
+
 \section{Summary}\label{sec:summary}

### 2015-12-09 DishReflectometry/Paper1_v0.tex
Minor formatting changes,

@@
-\documentclass[12pt,preprint]{aastex}
+%\documentclass[12pt,preprint]{aastex}
+\documentclass[iop]{emulateapj}
 \usepackage{float,amsmath}
@@
 \newcommand{\bmvolt}{{a}}
-\newcommand{\bm}{{A}}
+%\newcommand{\bm}{{A}}
 \newcommand{\thhat}{{\hat\theta}}
@@
 
-\begin{figure}[ht!]
+\begin{figure*}
 \centering
@@
 \label{fig:heradish}
-\end{figure}
+\end{figure*}
 
@@
 
-\subsection{Delay spectrum: An estimate of the 21cm power spectrum}
-Add text here. 
- \textbf{[ Reference to Nithya's foreground simulation work, reference to any plots on the relative contribution of the  foreground and EoR signal. ]}
+%\subsection{Delay spectrum: An estimate of the 21cm power spectrum}
+%Add text here. 
+ %\textbf{[ Reference to Nithya's foreground simulation work, reference to any plots on the relative contribution of the  foreground and EoR signal. ]}
 
@@
 %vertex are expected to be at a delay which is integral multiple of 0.3 nS.
-\begin{figure}[ht!]
+\begin{figure*}
 \centering
-\includegraphics[totalheight=0.4\textheight]{plots/frequency_amp_phase_fullbw.png}
+\includegraphics[totalheight=0.3\textheight]{plots/frequency_amp_phase_fullbw.png}
 \caption{Amplitude and phase of the measured return loss. Colored dashed lines
-mark three different frequency bands: $140-160MHz$ (typical power spectrum bandwidth), $100-200MHz$ (PAPER bandwidth), and
+mark three different frequency bands: $140-160MHz$ (typical power spectrum bandwidth),
+$100-200MHz$ (PAPER bandwidth), and
 $50-250MHz$ (HERA bandwidth).}
 \label{fig:freq}
-\end{figure}
+\end{figure*}
 %++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 
-\begin{figure}
+\begin{figure*}
+\begin{minipage}[b]{0.5\linewidth}
 \centering
-\includegraphics[width=1.0\linewidth]{plots1/delayspectrum.png}
+\includegraphics[width=\linewidth]{plots1/delayspectrum.png}
 \caption{Delay transform of the transfer function of the HERA element.
@@
 \label{fig:window}
-\end{figure}
-
-\begin{figure}
+\end{minipage}
+\begin{minipage}[b]{0.5\linewidth}
 \centering
-\includegraphics[totalheight=0.6\linewidth]{plots1/delayspectrum_feed.png}
+\includegraphics[width=\linewidth]{plots1/delayspectrum_feed.png}
 \caption{Delay transform of the transfer function of the HERA feed element.
@@
 \label{fig:outofthedish}
-\end{figure}
+\end{minipage}
+\end{figure*}
 
@@
 WRITE AGAIN}
-\begin{figure}[ht!]
+\begin{figure}
 \centering
-\includegraphics[width=1.0\linewidth]{plots1/delayspectrum_height.png}
+\includegraphics[width=\linewidth]{plots1/delayspectrum_height.png}
 \caption{Delay transform of the transfer function of the HERA element keeping the feed at various heights.
@@
 \centering
-\includegraphics[totalheight=0.41\textheight]{plots/delay_feed.png}
+\includegraphics[width=\linewidth]{plots/delay_feed.png}
 \caption{Delay plots produced using a Hamming window function for different feed only configurations and the PAPER bandwidth ($100MHz-200MHz$).

### 2015-12-09 ForegroundSimulations/notes.tex

@@
 
-Figure~\ref{fig:wideband-delay_spectrum} shows the delay spectra of simulated foreground visibilities (in orange) obtained with chromatic (dashed) and achromatic (solid) beams both weighted with the wideband Blackman-Harris window functions in the spectrum, the corresponding CLEAN components in gray and the residuals in black.
+Figure~\ref{fig:wideband-delay_spectrum} shows the delay spectra of simulated foreground visibilities (in orange) obtained with chromatic (dashed) and achromatic (solid) beams.
+Neither of them is weighted with the wideband Blackman-Harris window functions in the spectrum.
+The corresponding CLEAN components are shown in gray and the residuals in black.
 The depth of deconvolution is set by the limit at which the rms of the residuals inside the horizon limits becomes equal to that on the outside.

### 2015-12-10 DishReflectometry/Paper1_v0.tex
Sorted out some of the references and sorting more.

@@
 
-Since it was first proposed in \citet{shaver_et_al1999}, measuring 21~cm
+Since it was first proposed in \citep{Shaver_et_al1999} measuring 21~cm
 emission from neutral hydrogen in our early universe has gained attention as a
@@
 established (see, e.g.,
-\citealt{furlanetto_et_al2006,morales_wyithe2010,furlanetto_loeb2014,pritchard_loeb2014}),
+\citep{furlanetto_et_al2006,morales_wyithe2010,pritchard_loeb2012}),
 the technical path toward measuring this signal has been more problematic.  The
@@
 \bibliography{biblio.bib}
-%\begin{thebibliography}{}
-%
-%\bibitem[Parsons \& Backer(2009)]{ParsonsBacker2009}
-%Parsons, A., \& Backer, D. 2009, \apj, 138, 219
-%\bibitem[Parsons et al.(2012)]{Parsons2012}
-%Parsons, A., \& Pober, Jonathan C., \& Aguirre, James E., \& Carilli, Christopher L., \& Jacobs, Daniel C., \& Moore, David F. 2012, \apj 756, 165
-%\end{thebibliography}{}
-
 \end{document}
-
-%\begin{eqnarray}
-%V e^{i\phi}(\nu) & = & \int |A_{f}|^{2}|V_{sky}|^{2}|exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \nonumber\\
-%&& +  \int |A_{f}|^{2}|V_{sky}|^{2} |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \nonumber\\
-%&& + \int |A_{f}|^{2}|V_{sky}|^{2}| 2 \Re \left ((1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right)exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega
-%\label{eq8}		        
-%\end{eqnarray}
-
-%\subsection{Effect of first reflection on the delay spectrum}
-%We define $B(\vec \theta, \nu) =  A^{2}(\vec \theta, \nu) $ as the cross power pattern of the interferometer and $\Sigma_{rr}(\nu), \Sigma_{dr}(\nu)$ are the correlation coefficient between the two reflected signals in each antenna and the direct signal of one antenna with the reflected signal from the other antenna in the uv plane i.e,
-
-%\begin{equation}
-%\Sigma_{rr}(\nu) =  \left [ |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} \right ]
-%\end{equation}
-
-%\begin{equation}
-%\Sigma_{dr}(\nu) = \left [ 2 \Re \left ((1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right) \right]
-%\end{equation}
-
-%and $\Delta \tau$ is the additional delay each reflected component suffers in addition to the intrinsic geometric delay 
-%$\tau_{g}$. Therefore, $\Sigma(\vec \theta, \nu) = B(\vec \theta, \nu) \left [ 1+\Sigma_{rr} +\Sigma_{dr} \right]$
-
-%As given in equation \ref{eq3}, the Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum.
-Hence, the all sky integrated delay spectrum could be written as,
-%\begin{eqnarray}
-%\mathcal{F} \left [V e^{i\phi}\right] & = & \int \left [\int B I_{sky}exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
-%&& + \int \left [  \int B I_{sky} \Sigma_{rr} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right] exp\left[ -2 \pi i\nu \tau \right] d\nu  \nonumber\\
-%&& +\int \left [ \int B I_{sky} \Sigma_{dr} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\	
-%&& + \int \left [  \int |A_{f}|^{2}|V_{sky}|^{2} |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right] exp\left[ -2 \pi i\nu \tau \right] d\nu  \nonumber\\
-%&& +\int \left [ \int |A_{f}|^{2}|V_{sky}|^{2} 2 \Re \left ((1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right)exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
-%			& = & \int \left [\int B I_{sky} exp({2\pi i \nu \tau_{g}} ) dl dm \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
-%&& + \int \left [  \int B I_{sky} \Sigma_{rr} exp({2\pi i \nu \tau_{g}} ) dl dm \right] exp\left[ -2 \pi i\nu \tau \right] d\nu  \nonumber\\
-%&& +\int \left [ \int B I_{sky} \Sigma_{dr} exp({2\pi i \nu \tau_{g}} ) dl dm \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
-%\label{eq9}
-%\end{eqnarray}
-%
-%\begin{eqnarray}			
-%\mathcal{F} \left [V e^{i\phi}\right] & = & \left [ B(\tau)\ast I_{sky}(\tau) \right ]\ast \delta(\tau+\tau_{g}) \nonumber\\
-%		&& +  \left [ B(\tau)\ast I_{sky}(\tau)* \Sigma_{rr}( \tau) \right ]\ast \delta(\tau+\tau_{g}) \nonumber\\
-%		&& +  \left [B(\tau)\ast I_{sky}(\tau)* \Sigma_{dr}( \tau) \right ]\ast \delta(\tau+\tau_{g}+ \Delta \tau)\nonumber\\
-%\label{eq10}
-%\end{eqnarray}
-
- %In words, the Fourier transform of the visibility contributed by any two voltage components from two antennas with no mutual delay is centred at a delay $\tau = \tau_{g}$ in the delay spectrum whereas any two voltage components from two antennas components having a mutual delay of $\Delta \tau$ will be centred at $\tau_{g} +\Delta \tau$.
-The correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal thus extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected.
-Also, any reflections arriving at the feed at any non-zero  value of the delay $\Delta \tau$ which could be the result of reflections from the feed structures would generate non zero delay response at those delays.

### 2015-12-10 DishSimulations/code/compare_data_reflectometry_only.py
added PAPER reflectometry data from Rich Bradley and a script to plot it

@@ -1,0 +1,186 @@
+#!/usr/bin/env python
+#************************************************************
+#Aaron Ewall-Wice
+#aaronew@mit.edu
+#November 25th 2015
+#************************************************************
+# A script that compares many different estimates of the
+# HERA dish power kernel.
+# 1) Autocorrelations
+# 2) Reflectometry measurements from UCB
+# 3) Reflectometry measurements from Rich Bradley at Green Bank
+# 4) Simulations
+#************************************************************
+import numpy as n
+import numpy.fft as fft
+import aipy as a
+import capo.arp as arp
+import matplotlib.pyplot as p
+import scipy.signal as signal
+import glob
+import csv
+#************************************************************
+#hard code directories of files for now
+#sorry :P
+#************************************************************
+autocorrDir='/Users/aaronew/Dropbox/HERA_autocorrs/' #parent directory of autocorrelations
+simDir='/Users/aaronew/Dropbox/DishPapers/DishSimulations/' #parent directory for simulations
+reflectometryDir='/Users/aaronew/Dropbox/DishPapers/DishReflectometry/'#parent directory for UCB reflectometery measurements
+reflectometryRBDir='/Users/aaronew/Dropbox/DishPapers/Reflectometry_RB/'#parent directory for Rich Bradley's reflectometery measurements
+
+#************************************************************
+#plot simulations
+#************************************************************
+
+pwFeedAndDish=n.loadtxt(simDir+'data/feedSim_500ns_pW.txt',skiprows=2) #2xntimes array with col 0 = times (ns) and col 1 = plane wave e field.
+vFeedAndDish=n.loadtxt(simDir+'data/feedSim_500ns_o1.txt',skiprows=2) #2xntimes array with col0 = times (ns) and col 1 = feed voltage output.
+ntFeedAndDish=len(pwFeedAndDish)
[…]

### 2015-12-10 DishSimulations/code/compare_data_reflectometry_only.py
some updates

@@ -94,17 +94,22 @@ responsePAPERFreqDeep=(1.-s11PAPERDeep)
 
 
 delayResponsePAPER=fft.fftshift(fft.ifft(fft.fftshift(responsePAPERFreq*windowRB_PAPER)))
+delayResponsePAPERDeep=fft.fftshift(fft.ifft(fft.fftshift(responsePAPERFreqDeep*windowRB_PAPER)))
 delayResponsePAPER[tAxisPAPER<0]=0.
+delayResponsePAPERDeep[tAxisPAPER<0]=0.
+
+
 
 
 delayKernelPAPER=signal.fftconvolve(delayResponsePAPER,n.conj(delayResponsePAPER)[::-1],mode='same')
+delayKernelPAPERDeep=signal.fftconvolve(delayResponsePAPERDeep,n.conj(delayResponsePAPERDeep)[::-1],mode='same')
 #delayKernelPAPER=fft.fftshift(fft.ifft(fft.fftshift(n.abs(responsePAPERFreq)**2.*windowRB_PAPER)))
 #delayKernelPAPERDeep=fft.fftshift(fft.ifft(fft.fftshift(n.abs(responsePAPERFreqDeep)**2.*windowRB_PAPER)))
 #delayKernelPAPERCross=fft.fftshift(fft.ifft(fft.fftshift(n.conj(responsePAPERFreqDeep)*responsePAPERFreq*windowRB_PAPER)))
 
 
 p.plot(tAxisPAPER,10.*n.log10(n.abs(delayKernelPAPER)/n.abs(delayKernelPAPER).max()),label='PAPER Reflectometry RB')
-#p.plot(tAxisPAPER,10.*n.log10(n.abs(delayKernelPAPER)/n.abs(delayKernelPAPERDeep).max()),label='PAPER Reflectometry RB Deep')
+p.plot(tAxisPAPER,10.*n.log10(n.abs(delayKernelPAPERDeep)/n.abs(delayKernelPAPERDeep).max()),label='PAPER Reflectometry RB Deep')
 #p.plot(tAxisPAPER,10.*n.log10(n.abs(delayKernelPAPER)/n.abs(delayKernelPAPERCross).max()),label='PAPER Reflectometry RB Cross')
 
 

### 2015-12-22 DishBeamMeasurements/paper/DishBeamMeasurementsPaper.tex
add new plots to repo and to paper draft

@@
 \subsection{Design of the HERA Dish}
-%- EM design
-%    - departure from large N—small D to economize data volume (mitigate
-%      data processing challenges)
-%        - easier to identify systematics, to rerun datasets, perform
-%          cross checks / jackknives
-%    - but this change must be done judiciously, one advantage of simple
-%      elements is that they have little or no frequency structure,
-%      while a dish+feed system introduces reflections in the time
-%      domain, amounting in ripples in the frequency response
-%    - how bad are these ripples and can we tune the dish to mitigate
-%      their effect in the science?
-%    - as discussed above, it is useful to think in the delay domain as
-%      the translation from frequency structure introduced by dish
-%      reflections and the foreground isolation within the horizon delay
-%      is straightforward
-%    - the smooth spectral structure of the foregrounds sets a maximum
-%      foreground isolation achievable of ~60ns with blackman-harris
-%      window
-%    - f/D =0.32 maximizes efficiency for a PAPER dipole suspended over
-%      the dish
-%    - with typical reflection dish/feed reflection coefs, attenuation
-%      after 3 round trips will be below 60dB, and 1 and 2 round trips
-%      are in wedge, isolated away from EOR window
-%    - 14m also falls near the minimum of the cost per performance model
+
+\begin{figure}[h]
+\includegraphics[width=3.4in]{IMG_0353.JPG}
+\caption{Aerial photograph of the two reference dipoles deployed in Galford Meadow at the National Radio Astronomy Observatory--Green Bank 100\,m south of the HERA dish.}
+\label{fig:dishphoto}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[width=3.4in]{feed.jpg}
+\caption{Aerial photograph of the two reference dipoles deployed in Galford Meadow at the National Radio Astronomy Observatory--Green Bank 100\,m south of the HERA dish.}
+\label{fig:dishphoto}
+\end{figure}
 
@@
 
+\begin{figure*}
+\centering
+\includegraphics[width=7in]{dave197_rich195_airy_beams.pdf}
+\caption{Simulated delay spectra for the GSM and point sources at $0^\circ$ (top pair) and $60^\circ$ (bottom pair) LST for EW baselines of length 14\,m (left pair) and 42\,m (right pair).
+The beams are are assumed constant over frequency.}
+\label{fig:delayspec}
+\end{figure*}
+
 ASK DAVE OR RICH TO WRITE A ONE OR TWO PARAGRAPH SUMMARY OF THE ELECTROMAGNETIC DISH SIMULATIONS
@@
 beams of the two reference antennas.
-
-%\begin{figure*}[h]
-%\includegraphics[width=6.5in]{aerial.png}
-%\caption{Aerial photograph of the two reference dipoles deployed in Galford Meadow at the National Radio Astronomy Observatory--Green Bank 100\,m south of the HERA dish.}
-%\label{fig:aerial}
-%\end{figure*}
 
@@
 
+\begin{figure*}[h]
+\centering
+\includegraphics[width=6.7in]{null_expt_rel_beam_maps.pdf}
+\caption{null experiment beam ratio plots}
+\label{fig:nullexptplots}
+\end{figure*}
+
 As in \citet{neben15}, we assess systematics using a ``null experiment'' in which we use a second reference dipole as the antenna-under-test (AUT).
@@
 
-%\begin{figure*}[h]
-%\includegraphics[width=6.5in]{null1_rel.png}
-%\caption{Top: ratio maps of the powers received by two reference dipoles separated by 50\,m, deployed 50\,m south of the HERA dish.
-Bottom: absolute beam power plots constructed by multiplying the relative power maps by a model beampattern.
-}
-%\label{fig:null1}
-%\end{figure*}
-
-%\begin{figure*}[h]
-%\includegraphics[width=6.5in]{null3_rel.png}
-%\caption{Same as the previous null experiment except the south reference dipole was moved 5\,m west. The systematics are largely unchanged.}
-%\label{fig:null3}
-%\end{figure*}
-
-%\begin{figure*}[h]
-%\includegraphics[width=6.5in]{null4_rel.png}
-%\caption{Same as the first null experiment except the reference dipoles are separated by 100\,m and deployed 100\,m south of the HERA dish.
-The systematics remain at the few percent level near zenith and increase to $\sim10\%$ farther out, with somewhat, but not entirely different angular structure.
-}
-%\label{fig:null4}
-%\end{figure*}
-
 \section{Dish Measurements}
@@
 
-%\begin{figure*}[h]
-%\includegraphics[width=6.5in]{dish3_abs_old_ref_model.png}
-%\caption{Dish power pattern with the feed lowered 0.5\,m below nominal focus.}
-%\label{fig:dish3}
-%\end{figure*}
+\begin{figure*}[t]
+\centering
+\includegraphics[width=6.7in]{measured_beams_and_models_maps.pdf}
+\caption{null experiment beam ratio plots}
+\label{fig:measuredbeammaps}
+\end{figure*}
 
-%\begin{figure*}[h]
-%\includegraphics[width=6.5in]{dish1_abs_old_ref_model.png}
-%\caption{Dish power pattern with the feed at the nominal focus of 4.5\,m.}
-%\label{fig:dish1}
-%\end{figure*}
-
-%\begin{figure*}[h]
-%\includegraphics[width=6.5in]{dish2_abs_old_ref_model.png}
-%\caption{Dish power pattern with the feed raised 0.5\,m above nominal focus.}
-%\label{fig:dish2}
-%\end{figure*}
-
-%\begin{figure*}[h]
-%\includegraphics[width=6.5in]{dish4_abs_old_ref_model.png}
-%\caption{Dish power pattern with the feed raised to its maximum height of 0.8\,m above nominal focus.}
-%\label{fig:dish4}
-%\end{figure*}
+\begin{figure*}[t]
+\centering
+\includegraphics[width=6.7in]{measured_beams_and_models_slices.pdf}
+\caption{null experiment beam ratio plots}
+\label{fig:measuredbeamslices}
+\end{figure*}
 
@@
  \begin{table}[h]
- \caption{ \label{table:collectingareatable}Collecting area (m$^2$) for modeled and measured dish beams at 137\,MHz.
-For measured beams, we calculate the collecting area after interpolation/extrapolation, also with the $60^\circ$ gaussian cutoff (in parentheses).}
+ \caption{ \label{table:collectingareatable}Collecting area (m$^2$) of measured 137\,MHz beams and corresponding power spectrum SNR for HERA-127.}
 \begin{tabular}{| l | l | l |}
 \hline
-  Airy & 155\,  \\
-  CST sim & 67.0\,  \\
+Beam & $A_\text{eff}$ (m$^2$) & SNR (pess, mod, opt)\\
 \hline
-  Measured, feed at 4\,m & 42.1 (44.3) \\
-  Measured, feed at 4.5\,m & 68.5 (73.6) \\ 
-  Measured, feed at 5\,m & 77.1 (82.6) \\
-  Measured, feed at 5.3\,m & 93.0 (97.9)\\
+  Airy pattern & 155 & 9.1, 11.0, 37.2  \\
+  %CST sim & 67.0 &  \\
+  %Measured, feed at 4\,m & 44.3 &  \\
+    Measured, feed at 5.3\,m & 97.9 & 8.2, 8.3, 29.2 \\
+    Measured, feed at 5\,m & 82.6 & 6.8, 6.9, 26.5 \\
+    Measured, feed at 4.5\,m & 73.6 & 6.4, 6.5, 24.8 \\ 
   \hline
@@
 
-We assess the level of foreground leakage into the EOR window due to beam shape, baseline length, and LST.
-In particular, we built on the study of \citet{nithya15} of the impact of beam shape and horizon response on foreground spectral structure and containment in the wedge.
+\begin{figure*}[h]
+\includegraphics[width=6.7in]{delay_spectra_dave_rich_airy_beams_manyLSTs.pdf}
+\caption{Simulated delay spectra for the GSM and point sources at $0^\circ$ (top pair) and $60^\circ$ (bottom pair) LST for EW baselines of length 14\,m (left pair) and 42\,m (right pair).
+The beams are are assumed constant over frequency.}
+\label{fig:delayspecmanyLSTs}
+\end{figure*}
 
-We simulate delay spectra for several model and measured beams on different baseline lengths for different LSTs and baseline orientations.
-All these factors affect the level of emission horizon brightening in delay space, the ``pitchfork'' effect, and the level of foreground leakage.
-We assume a constant beam pattern over that band, with leakage due only to the finite bandwidth and choice of window function.
-Actual frequency structure imprinted onto the foregrounds by variation of the beam angular pattern or overall gain with frequency (Patra et al.)
+\begin{figure*}[h]
+\includegraphics[width=6.7in]{gsm_kelvin_LST_2deg_and_62deg.pdf}
+\caption{Simulated delay spectra for the GSM and point sources at $0^\circ$ (top pair) and $60^\circ$ (bottom pair) LST for EW baselines of length 14\,m (left pair) and 42\,m (right pair).
+The beams are are assumed constant over frequency.}
+\label{fig:gsmplots}
+\end{figure*}
 
-We begin by simulating visibilities over a 20\,MHz bandwidth with  400\,kHz resolution centered on 137\,MHz on two different baselines for two model beams (airy, and CST sim) and two measured beams (measured nominal focus beam, and measured nominal focus beam with $60^\circ$ cutoff).
-We use the short and maximally redundant 14\,m baseline, most useful for delay spectrum analysis, as well as a longer 42\,m baseline, more useful for imaging analysis.
-From these frequency-sequenced visibilities we calculate the delay spectrum  \citep{perbaselinetechnique} using the Blackman-Harris window following \citet{nithya15}.
-This window reduces the noise equivalent bandwidth to 10\,MHz, corresponding to $\Delta z\sim0.5$, beyond which evolution of the cosmological signal become significant.
-Larger bandwidths, though, are useful for foreground estimation and delay-space deconvolution \citep{parsonsandbacker,paper32,paper64}.
-With this caveat, our simulated delay spectra show the worst case scenario, quantifying the level of foreground isolation without estimation and deconvolution.
+\begin{figure*}[h]
+\includegraphics[width=6.7in]{delay_spectra_dave_rich_airy_beams_LST2deg.pdf}
+\caption{Simulated delay spectra for the GSM and point sources at $0^\circ$ (top pair) and $60^\circ$ (bottom pair) LST for EW baselines of length 14\,m (left pair) and 42\,m (right pair).
+The beams are are assumed constant over frequency.}
+\label{fig:delayspecbadLST}
+\end{figure*}
 
-Our sky model is comprised of a deep MWA point source survey within 20$^\circ$ of R.A.(J2000) $= 0^\text{h}\,0^\text{m}\,0^\text{s}$ and decl.(J2000) $= -30^\circ\,0'\,0''$ (Carroll et al., in prep.), the shallower but wider MWA commissioning point source survey\citep{MWACS}, the Culgoora catalog\citep{Slee1995}, and the Global Sky Model of Galactic radio emission \citep{gsm}.
-
-Figure \ref{fig:delayspec} shows the delay spectra at $0^\circ$ (top pair) and $60^\circ$ (bottom pair) LST for 14\,m (left pair) and 42\,m (right pair) EW baselines.
-For reference we plot a 1D model 21\,m power spectrum for $z\sim8$ from \citet{21cmfast}.
-Consider first the $0^\circ$ LST plots where the Galactic disk has nearly, but not completely set.
-The effect of horizon response is most visible on the longer 42\,m baseline where the measured beam (red) and CST model (yellow), both show significant brightening at the horizon delays (vertical black lines) due to roughly -30\,dB beam response near the horizon, as discussed by \citet{nithya15,nithya15}.
-In contrast, the airy model (black) and measured beam with cutoff (blue) show no significant brightening at the horizon, where they appear still to be dominated by the wings of the delay PSF from the emission closer to zero delay.
-
-We also plot (green dashed line) the delay spectrum after subtracting the visibilities computed with the $\theta\sim60^\circ$ cutoff measured beam from those using the full measured beam.
-This curve may be interpreted as the uncertainty in the ``pitchfork'' horizon brightening due to uncertainty in the beam horizon response, or equivalently as the delay spectrum residual foregrounds after subtracting foregrounds in the well modeled region of the sky (Neben et al.
-2015b, submitted).
-By construction, this subtraction leaves emission from the highest delay regions of the sky (near the horizon on opposite sides of the baseline), but also leaves some low delay emission on opposite sides of a line perpendicular to the baseline.
-However, this additional low delay emission near the horizon gets drowned out by that from near zenith where the beam is substantially stronger.
-
-On the shorter 14\,m baseline, the horizon brightening is smaller because there is roughly an order of magnitude more emission at zero delay, whose thereby stronger delay wings, which are also relatively wider compared to the narrower foreground wedge, cover up much of the edge brightening.
-At $60^\circ$ LST, effect of horizon response is much smaller as the Galactic disk is now entirely below the horizon.
-
-The level of leakage depends also on baseline orientation which sets which directions on the sky map to large delays.
-Figure \ref{fig:delayspec2} shows the delay spectra at $0^\circ$ LST on 14\,m NE (top pair) and SE (bottom pair) baselines.
-Both show increased edge brightening compared to the 14\,m EW baseline.
-\citet{nithya15} proposes to identify through modeling the baselines most susceptible to this edge brightening at any given time, and simply exclude them from the power spectrum analysis.
-
-%\begin{figure*}[h]
-%\includegraphics[width=6.7in]{LST0deg_14m_42m_EWbaselines_dish1_blackman.png}
-%\includegraphics[width=6.7in]{LST60deg_14m_42m_EWbaselines_dish1_blackman.png}
-%\caption{Simulated delay spectra for the GSM and point sources at $0^\circ$ (top pair) and $60^\circ$ (bottom pair) LST for EW baselines of length 14\,m (left pair) and 42\,m (right pair).
+\begin{figure*}[h]
+\includegraphics[width=6.7in]{delay_spectra_dave_rich_airy_beams_LST62deg.pdf}
+\caption{Simulated delay spectra for the GSM and point sources at $0^\circ$ (top pair) and $60^\circ$ (bottom pair) LST for EW baselines of length 14\,m (left pair) and 42\,m (right pair).
 The beams are are assumed constant over frequency.}
-%\label{fig:delayspec}
-%\end{figure*}
-
-%\begin{figure*}[h]
-%\includegraphics[width=6.7in]{LST0deg_14m_42m_NEslantbaselines_dish1_blackman.png}
-%\includegraphics[width=6.7in]{LST0deg_14m_42m_SEslantbaselines_dish1_blackman.png}
-%\caption{Simulated delay spectra for the GSM and point sources at $0^\circ$ LST for NE (top pair) and SE (bottom pair) baselines of length 14\,m (left pair) and 42\,m (right pair).
-The beams are are assumed constant over frequency.}
-%\label{fig:delayspec2}
-%\end{figure*}
+\label{fig:delayspecgoodLST}
+\end{figure*}
 

### 2015-12-22 DishBeamMeasurements/paper/DishBeamMeasurementsPaper.tex
wrote very rough science implications section

@@
 
-\subsection{Collecting Area}
+\subsection{Collecting Area and Power Spectrum Sensitivity}
 
@@
 
-\section{Foreground Leakage and Residuals}
-\label{sec:foregroundleakage}
+\section{Implications for Foreground Suppression}
+\label{sec:foregrounds}
+
+ALSO MENTION DEPENDENCE ON BASELINE DIRECTION
+DISCUSS DELAY CLEANING TO THE 2min THERMAL NOISE LEVEL, THEN DELAY TRANSFORM AGAIN WITH REDUCED RESOLUTION, MEANING A LARGER BH WINDOW, AND THUS MORE LEAKAGE, THESE EFFECTS ARE DISCUSSED IN NITHYA'S PAPER, here we are focused on intrinsic delay distribution of foregrounds
+
+% summary of what sorts of science implications are important
+foreground separation of 21cm signal and foregrounds is the name of the game
+smooth spectrum foregrounds occupy only low k// modes, while rough 21cm signal dominates the higher higher modes
+in fact, the 21cm signal peaks at the smallest k// modes, but these 21cm modes are indistinguishable from foregrounds, so we can only detect 21cm at higher k
+thus, the better foregrounds are contained, to low k modes, the stronger the 21cm signal is
+
+% summarize again the wedge frequency structure
+foreground emission is intrinsically smooth spectrum, meaning it should live in the k//=0 mode with slight leakage into larger modes due to their smooth frequency dependence
+however, a baseline in an interferometer measures the sky multiplied by the frequency dependent fringe pattern, imprinting a frequency dependence on the source spectrum with a delay given by the light travel time between the two antennas as seen from the direction of the source
+If we fourier transform the visibility along the frequency axis we should see a peak at the delay of the source.
+Sources at high delay, near the horizon in the direction of the baseline, thus appear with more frequency structure, and sources at lower delay, perpendicular to the baseline and closer to zenith, have less.
+Sources exactly in line with the baseline have the maximum frequency dependence set by the baseline length in light travel time.
+Longer baselines have longer maximum delays, and thus larger contaminated regions of k space, this is the wedge.
+
+% pitchfork and leakage
+Understanding the primary beam is important to characterize the delay distribution of foregrounds, and thus the foreground suppression strategy that should be pursued, the expected level of leakage into the EOR window, and thus the expected sensitivity.
+Nithya et al discuss a horizon brightening effect they term the 'pitchfork'.
+if the falloff of the beam sensitivity is less than the increase in solid angle at low elevations and potentially the rebrightening of the sky due down there if the galaxy is there, emission will appear as a brightening at the horizon delay, right at the edge of the EOR window where emission is most at risk of leaking in due to frequency dependent systematics such as beam frequency dependence or miscalibration.
+
+Nithya et al discuss in detail the implications of these foreground delay spectra for suppression strategies, we are concerned here with the beam uncertainties on them
+We study these effects and their implications for foreground isolation by simulating delay spectra.
+we simulate visibilities using the GSM and point sources over 80MHz of bandwidth, the maximum delay resolution that delay CLEANing has to work with. delay CLEANing can only work within the wedge. 
+how much does our beam uncertainty affect these results? that's why we use different model beams
+only concerned with intrinsic delay spectra of the sources due to geometry, no chromatic beam patterns or gains. 
+we begin by simulating the delays for different LSTs using the HFSS beam
+as expected, the power at the horizon varies by several orders of magnitude over this range of LSTs depending on whether the center of the galaxy is just above or just below the horizon (SEE THE GSM MAPS FOR LST=2,62)
+DISCUSS THE TWO DIFFERENT BASELINE LENGTHS
+	at what k// do the FG spectra dip below the 21cm power spectra?
+	horizon brightening at short vs long baselines
+
+We plot the delay spectra for these two LSTs for both model beams, as well as for the airy beam. 
+the airy beam is an interesting comparison because Nithya's paper and sensitivity calculations assume an airy beam
+as expected, the difference between the beams is very small near zero delay, and largest when the horizon has a relative pitchfork brightening.
+If the horizon brightening is very small, the difference between the beams is correspondingly small
+NOTE THAT k// CAN BE CONVERTED TO k by adding k=0.005 or 0.02 in quadrature at z=8
 

### 2015-12-23 DishBeamMeasurements/paper/DishBeamMeasurementsPaper.tex
update to text
smaller delay range on plots, and progress in science implications section

--- 2015-12-22 DishBeamMeasurements/paper/DishBeamMeasurementsPaper.tex
@@
 
-\begin{figure}[h]
-\includegraphics[width=3.4in]{IMG_0353.JPG}
-\caption{Aerial photograph of the two reference dipoles deployed in Galford Meadow at the National Radio Astronomy Observatory--Green Bank 100\,m south of the HERA dish.}
-\label{fig:dishphoto}
-\end{figure}
-
-\begin{figure}[h]
-\includegraphics[width=3.4in]{feed.jpg}
-\caption{Aerial photograph of the two reference dipoles deployed in Galford Meadow at the National Radio Astronomy Observatory--Green Bank 100\,m south of the HERA dish.}
-\label{fig:dishphoto}
-\end{figure}
-
 The 14\,m HERA dish design is a departure from the large N--small D approach used by 21\,cm 
@@
 HERA by DeBoer et al (in prep).
+
+\begin{figure}[h]
+\includegraphics[width=3.4in]{IMG_0353.JPG}
+\caption{Aerial photograph of the two reference dipoles deployed in Galford Meadow at the National Radio Astronomy Observatory--Green Bank 100\,m south of the HERA dish.}
+\label{fig:dishphoto}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[width=3.4in]{feed.jpg}
+\caption{Aerial photograph of the two reference dipoles deployed in Galford Meadow at the National Radio Astronomy Observatory--Green Bank 100\,m south of the HERA dish.}
+\label{fig:dishphoto}
+\end{figure}
 
@@
 The beams are are assumed constant over frequency.}
-\label{fig:delayspec}
+\label{fig:modelbeams}
 \end{figure*}
@@
 \centering
-\includegraphics[width=6.7in]{null_expt_rel_beam_maps.pdf}
+\includegraphics[width=6.5in]{null_expt_rel_beam_maps.pdf}
 \caption{null experiment beam ratio plots}
@@
 
+\begin{figure*}[t]
+\centering
+\includegraphics[width=6.5in]{measured_beams_and_models_maps.pdf}
+\caption{null experiment beam ratio plots}
+\label{fig:measuredbeammaps}
+\end{figure*}
+
+\begin{figure*}[t]
+\centering
+\includegraphics[width=6.5in]{measured_beams_and_models_slices.pdf}
+\caption{null experiment beam ratio plots}
+\label{fig:measuredbeamslices}
+\end{figure*}
+
 Having verified the feed power pattern, we deployed feed over the dish and proceed with dish measurements.
@@
 At these zenith angles, the beam sidelobes are roughly -30\,dB, and seem to be trending downward at the edge of the measured region.
-
-\begin{figure*}[t]
-\centering
-\includegraphics[width=6.7in]{measured_beams_and_models_maps.pdf}
-\caption{null experiment beam ratio plots}
-\label{fig:measuredbeammaps}
-\end{figure*}
-
-\begin{figure*}[t]
-\centering
-\includegraphics[width=6.7in]{measured_beams_and_models_slices.pdf}
-\caption{null experiment beam ratio plots}
-\label{fig:measuredbeamslices}
-\end{figure*}
 
@@
 
-\subsection{Collecting Area}
+\subsection{Sensitivity}
 
@@
 \end{tabular}
-\end{table}
+\end{table}\
+
+NEED TO TALK ABOUT 21CMSENSE AND THE SNR CALCULATIONS
 
@@
 
-\section{Foreground Leakage and Residuals}
-\label{sec:foregroundleakage}
+\section{Implications for Foreground Suppression}
+\label{sec:foregrounds}
+
+ALSO MENTION DEPENDENCE ON BASELINE DIRECTION
+DISCUSS DELAY CLEANING TO THE 2min THERMAL NOISE LEVEL, THEN DELAY TRANSFORM AGAIN WITH REDUCED RESOLUTION, MEANING A LARGER BH WINDOW, AND THUS MORE LEAKAGE, THESE EFFECTS ARE DISCUSSED IN NITHYA'S PAPER, here we are focused on intrinsic delay distribution of foregrounds
+
+We simulate the power spectra of foregrounds with different primary beam models under various observing conditions.
+Broadly, beam models with more response near the horizon see smooth spectrum sources with more frequency dependence (higher delay), appearing closer to the nominally clean EOR window, making it more at risk of leaking power inside.
+We use the per-baseline approach of XX and XX, simulating visibilities measured by specific baselines as a function of frequency, then computing the Fourier transform over frequency (the delay transform) and normalizing the result into a cosmological power spectrum \citep{perbaselinetechnique}.
+
+We simulate visibilities for three beam models (HFSS, CST, and an Airy pattern for a 14\,m aperture) at various LSTs, modeling the sky as the sum of the Global Sky Model \citep{gsm} and a point source catalog (XX).
+We use a frequency spacing of 1\,MHz, sufficient to characterize delays within and just outside of the horizon limits on both baseline lengths we are concerned with, 14\,m and 42\,m.
+We use a total bandwidth of 80\,MHz (40\,MHz after applying the Blackman-Harris window) centered on 150\,MHz.
+This bandwidth is larger than the 10\,MHz thought to be safe from signal evolution over redshift, but is the bandwidth used in the power spectrum analysis of XX,XX to perform a high delay resolution empirical foreground subtraction (delay-space CLEANing) as described by XXX.
+We normalize the delay spectra into power spectra following   \citet{nithya15}.
+
+Nithya et al (submitted) detail the implications of these foreground delay spectra for suppression strategies.
+We are concerned here with the role of the beam in these predictions, in particular what our beam model and its uncertainties imply about foreground suppression strategies.
+We begin by simulating delay spectra, plotted in Figure \ref{fig:delayspec} (top panel) at various LSTs as outlined above using the nominal HFSS beam.
+As all these LSTs are high galactic latitudes far from the galactic center, the total visibility power (the level of the zero delay mode) varies by only an order of magnitude over these LSTs both on the 14\,m (left panel) and 42\,m (right panel).
+However the horizon limit at negative delay (corresponding to the western horizon) shows a peak that varies by three orders of magnitude on the 14\,m baseline and two orders of magnitude on the 42\,m baseline, showing the stark difference in pitchfork brightening when the galaxy is just above versus just below the horizon.
+
+In this figure we perform the approximate conversion from delay to k//, which we plot as a second x-axis at the top of the plot.
+For these short baselines, k// may be converted to k by adding kperp=0.005 or 0.02 in quadrature for these baselines at this redshift.
+These numbers are small compared to the range of k// plotted, and thus we interpret the k// axis as simply the k axis, and plot a 1D model power spectrum computed using 21cmFast as a dotted line for comparison.
 
 \begin{figure*}[h]
-\includegraphics[width=6.7in]{delay_spectra_dave_rich_airy_beams_manyLSTs.pdf}
+\centering
+\includegraphics[width=6in]{delay_spectra_dave_rich_airy_beams_manyLSTs.pdf}
+\includegraphics[width=6in]{delay_spectra_dave_rich_airy_beams_LST2deg.pdf}
+\includegraphics[width=6in]{delay_spectra_dave_rich_airy_beams_LST62deg.pdf}
 \caption{Simulated delay spectra for the GSM and point sources at $0^\circ$ (top pair) and $60^\circ$ (bottom pair) LST for EW baselines of length 14\,m (left pair) and 42\,m (right pair).
 The beams are are assumed constant over frequency.}
-\label{fig:delayspecmanyLSTs}
+\label{fig:delayspec}
 \end{figure*}
 
+We study the differences between our three beam models on two of these LSTs, one with maximal horizon brightening ($2^\circ$), and one with minimal horizon brightening ($62^\circ$).
+Figure \ref{fig:gsmplots} shows the sine-projected Global Sky Model in horizontal coordinates with units of Kelvin for these two LSTs.
+Dashed lines mark zenith angles 20$^\circ$, 40$^\circ$, 60$^\circ$, 80$^\circ$.
+These plots confirm that the large negative delay peak at both baseline's horizon limits at the 2 degree LST originates from the center of the galaxy being just above the horizon.
+In contrast several hours later, the galactic center is fully below the western horizon, leaving only a slight brightening near the eastern horizon due to the much weaker galactic anticenter.
+
 \begin{figure*}[h]
-\includegraphics[width=6.7in]{gsm_kelvin_LST_2deg_and_62deg.pdf}
+\centering
+\includegraphics[width=6in]{gsm_kelvin_LST_2deg_and_62deg.pdf}
 \caption{Simulated delay spectra for the GSM and point sources at $0^\circ$ (top pair) and $60^\circ$ (bottom pair) LST for EW baselines of length 14\,m (left pair) and 42\,m (right pair).
@@
 
-\begin{figure*}[h]
-\includegraphics[width=6.7in]{delay_spectra_dave_rich_airy_beams_LST2deg.pdf}
-\caption{Simulated delay spectra for the GSM and point sources at $0^\circ$ (top pair) and $60^\circ$ (bottom pair) LST for EW baselines of length 14\,m (left pair) and 42\,m (right pair).
-The beams are are assumed constant over frequency.}
-\label{fig:delayspecbadLST}
-\end{figure*}
+We turn now to the differences in foreground delay spectra in these two observing conditions with different beam models.
+Figure \ref{fig:delayspec} (middle panel) shows the delay spectra for all three beam models at $2^\circ$ LST, which has the worst horizon brightening.
+We use both numerical beam models with 5\,m feed heights, as well as the Airy pattern for a 14\,m aperture.
+The delay spectra for these beams agree out to delays of 10--20\,ns on the 14\,m baseline and 30--40\,ns on the 62m baseline.
+These limits suggest that the beams track each other fairly well out to 15--20$^\circ$ from zenith, beyond which they cease to be correlated.
+This is essentially what is observed in Figure \ref{fig:measuredbeamslices} (middle panel).
+At larger delays, especially near the negative delay horizon limit, all three model delay spectra diverge due to the significant edge brightening which effectively discriminates between these models.
+The CST, HFSS, and Airy beams reach roughly -35\,dB, -38\,dB, and -50\,dB at the horizon (Figure \ref{fig:modelbeams}), consistent with the fact that the CST beam has the largest horizon brightening, followed by the HFSS beam, and then the Airy beam.
+This is seen in the delay spectra from both baseline lengths, though the edge brightening is much more significant in the longer baseline where it is less diluted by the zero delay emission.
 
-\begin{figure*}[h]
-\includegraphics[width=6.7in]{delay_spectra_dave_rich_airy_beams_LST62deg.pdf}
-\caption{Simulated delay spectra for the GSM and point sources at $0^\circ$ (top pair) and $60^\circ$ (bottom pair) LST for EW baselines of length 14\,m (left pair) and 42\,m (right pair).
-The beams are are assumed constant over frequency.}
-\label{fig:delayspecgoodLST}
-\end{figure*}
+In contrast, all three model agree much more closely when there is little or no edge brightening as in Figure \ref{fig:measuredbeamslices} (middle panel) where we plot the delay spectra for all three beams for 62$^\circ$ LST.
+There is still a modest edge brightening observed here, a flattening off near the horizon on the short baseline and a small peak on the long baseline, both due to the increasing solid angle per zenith angle at larger zenith angles.
+However as the emission at this LST at large delays is roughly the same temperature as emission from everywhere else on the sky, washing out the difference between the three beam models.
 
@@
 
-add stuff here
+%- power spectrum analyses by first generation instruments are ongoing, but face many challenges
+%- that’s why HERA was designed to be optimized for 21cm
+
+%- in this paper we have characterized the HERA dish’s angular response
+%  down to 60deg zenith angle, -35dB from zenith
+%- confirms models to exquisite fidelity unachievable with celestial sources
+%- the level of model disagreement also gives us a handle on antenna-to-to antenna variation
+
+%- given the latest understanding of instrument chromaticity and
+%  foreground isolation (ie, Nithya), we simulate the effects of these
+%  beams on science
+ %   - taking into account uncertainties in near-horizon beam response unprobed by our measurements
+%- we make predictions for the level of horizon brightening at different LSTs, and discuss the uncertainties due to uncertain beam models (horizon brighting is an exquisite of the low elevation beam response, though an integrated statistic)
+% horizon brightening will dominated leakage into the outer window modes
+
+% frequency dependence of the beam pattern and overall gain (due to reflections) likely dominates leakage deep within the window, but the other papers in this series demonstrate that this leakage level is within our spec
+
+   % - all this highlight the need for detailed antenna characterization
+     % and simulation of the implications for science analyses  in 21cm observatories
 

### 2015-12-24 DishBeamMeasurements/paper/DishBeamMeasurementsPaper.tex
finish rough draft for me to read on the plane

@@
 
-\documentclass{emulateapj}
-%\documentclass[preprint]{aastex}
+%\documentclass{emulateapj}
+\documentclass[preprint]{aastex}
 
@@
 
-NEED TO TALK ABOUT 21CMSENSE AND THE SNR CALCULATIONS
+NEED TO TALK ABOUT 21CMSENSE\footnote{https://github.com/jpober/21cmSense} AND THE SNR CALCULATIONS
 
@@
 
-\section{Implications for Foreground Suppression}
+\section{Foreground Delay Spectra Simulations}
 \label{sec:foregrounds}
@@
 
+Power spectrum analyses by first generation 21\,cm observatories are ongoing, but are contending with challenges ranging from calibration and foreground modeling to the computing time required to process thousands of hours of data.
+HERA draws the most successful ideas from these first generation instruments, pursuing a compact and redundant array layouts, large collecting area antenna elements, and per-baseline power spectrum analysis to make advances exactly where necessary to make a first detection and characterization of the 21\,cm signal from the EOR.
+In pursuing an array of dishes rather than one of fixed dipoles, HERA turns away from the large N--small d approach used by the MWA, LOFAR, PAPER, and other first generation instruments in order to achieve sufficient sensitivity at a reasonably data processing and analysis cost.
+The papers in this series characterize the 14\,m diameter dish used as HERA's antenna element using reflectometry measurements and simulations which probe the beams gain variation with frequency, as well as beam pattern measurements and simulations which probe the beams angular variation.
+
 %- in this paper we have characterized the HERA dish’s angular response
@@
 
+We present in this paper beam pattern measurements at 137\,MHz and comparisons with beam models, as well as simulations of the foreground delay spectra using these modeled beams.
+We adapt the beam mapping system of \citet{neben15}, deploying it at the prototype three-element HERA array at the National Radio Astronomy Observatory--Green Bank.
+Only one dish had been constructed when these measurement were made.
+We present measured power patterns for three different feed heights above the dish covering much of the visible sky probing down to -30\,dB relative to the zenith response.
+The measured beams agree well with both models in the main lobe out to 10--20$^\circ$ from zenith, then roughly track the sidelobe levels at 20--30\,dB below zenith, though fail to reproduce the exact sidelobe amplitudes and locations.
+
+These deviations are larger than the $\pm1$\,dB systematics observed in the null experiments designed to probe the accuracy of the ORBCOMM beam measurement system as deployed at this location, suggesting they are accurate measurement of the in situ beam pattern of the imperfect HERA dish.
+The most likely dish non-idealities are dish surface imperfections and feed misalignment, both of which may vary from antenna to antenna in the full HERA array.
+Characterizing this antenna-to-antenna beam variation and its effects on power spectrum analyses for HERA, in the way Neben et al (submitted) do for the MWA, is left as future work.
+
+%% sensitivity
+% collecting area 
+% power spectrum SNR
+We quantify the 21\,cm power spectrum sensitivity using our measured beam patterns by first computing the collecting area at different feed heights.
+We observe a reduction of 30--50\% from that of an ideal, unobstructed Airy pattern for a 14\,m dish.
+We convert these collecting areas into effective dish sizes to predict overall power spectrum sensitivities for HERA-127 using 21cmSense, and find SNRs of 6--8 in pessimistic and moderate foreground scenarios, and 24--29 in optimistic ones, to be compared with roughly 10 and 37 using the Airy dish.
+This is a certainly a reduction, but of course an unobstructed, perfectly azimuthally symmetric Airy pattern is unachievable, every dish required polarized feeds either placed on axis where they block the primary reflector, or placed off axis where they don't get the dish's full collecting area.
+Further, the XX\,m cylinder hung from the feed backplane around the dipole mitigates cross-coupling between adjacent dishes and reduces azimuthal asymmetry, both of which facilitate analysis despite the reduced sensitivity.
+
+%% foreground delay spectrum simsulations
 %- given the latest understanding of instrument chromaticity and
@@
 % horizon brightening will dominated leakage into the outer window modes
+Beyond simply sensitivity considerations, though, different beam models affect science analyses by reweighting celestial emission in different regions of the sky which are imprinted by the interferometer with different frequency dependence.
+Understanding this ``wedge'' region in cylindrical fourier space has proved a fruitful advance in 21\,cm analyses over the past several years.
+Foregrounds acquire frequency dependence only from the changing baseline length in wavelengths with frequency, reaching a maximum fringe rate for a source at the horizon in line with the baseline.
+The complement of the wedge is the EOR window, which is where detection of the EOR signal is theoretically possible without foreground subtraction as it is nominally clear of foregrounds.
+
+However Nithya has highlighted that distribution of foregrounds within the wedge is important as well.
+The beam response at low elevations determines whether there is a brightening at the geometric, horizon limit due to the increasing solid angle and a sufficiently shallow beam gradient at low elevations.
+This produces a characteristic ``pitchfork'' shape in the delay spectrum of a single baseline, with a zero delay peak due to near-zenith emission surrounded by tines at the negative and positive horizon limits due to emission from the two horizon directions in line with the baseline.
+These horizon peaks are most at risk of corrupting the outer modes of the EOR window due to leakage from the delay point spread function.
+
+We have simulated foreground delay spectra for different baseline lengths and LSTs, finding that the level of this horizon brightening is largest when the galaxy is just above the horizon, and lowest when it is well below.
+When this pitchfork effect is large, our uncertainty in it due to beam modeling uncertainty is also large, as evidenced by the deviation of our HFSS and CST numerical beam models for these simulations.
+When the effect is small, the two beam models produce much more similar results, highlighting the delay spectrum as an exquisite probe of the challenging to measure beam response at very low elevations.
 
@@
 
-   % - all this highlight the need for detailed antenna characterization
-     % and simulation of the implications for science analyses  in 21cm observatories
+As discussed by the other papers in this series, the frequency dependence of the beam power pattern and its overall gain widen the delay kernel of a source at some delay, leaking power farther into the EOR window.
+These papers demonstrate that in the best case, a combination of bandpass calibration and delay space CLEANing can mitigate foregrounds to a manageable level, while in the worst case, HERA can still achieve a XX--XX $\sigma$ detection of the EOR parameters from the power spectrum by simply excluding a very conservative buffer at the edge of the EOR window.
+All these considerations highlight the need for precision characterization of antenna elements and their implications for 21\,cm science analyses on the part of next generation observatories if we are to have any hope of detecting making this challenging measurement.
 

### 2015-12-26 DishBeamMeasurements/paper/DishBeamMeasurementsPaper.tex
edited 3 sections, 3 more to go, you got this, Abraham

@@
  sightlines, deep galaxy surveys, and the CMB optical depth which leave the reionization 
- history of the universe only loosely constrained. Sensitivity and foreground removal are 
+ history of the universe only loosely constrained. (See \citet{FurlanettoReview, miguelreview, PritchardLoebReview, aviBook, zaroubi} for reviews) Sensitivity and foreground removal are 
  the main challenges in 21\,cm observations, as the expected cosmological signal is 4--5 
  orders of magnitude fainter than Galactic and extragalactic foregrounds. Radio 
- interferometers such as the MWA \citep{tingay13}, PAPER \citep{ali2015}, GMRT 
- \citep{Paciga2011}, and LOFAR \citep{lofar} are seeking a first detection of 
+ interferometers such as the Murchison Widefield Arry (MWA) \citep{tingay13,mwascience}, the Precision Array for Probing the Epoch of Reionization (PAPER) \citep{ali2015}, the Giant Meterwave Radio Telescope (GMRT)
+ \citep{Paciga2011}, and the Low Frequency Array (LOFAR) \citep{lofar} are seeking a first detection of 
  cosmological 21\,cm emission in power spectrum measurements, where the smooth 
- frequency evolution of the foreground emission distinguishes itself from the spectrally 
- jagged cosmological signal whose frequency dimension is a redshift axis probing the 
+ frequency evolution of the foreground emission separates from the spectrally 
+ unsmooth cosmological signal whose frequency dimension probes the a line of sight through the 
  inhomogenous reionizing universe.
+
+The Hydrogen Epoch of Reionization Array (HERA) \citep[][, deBoer et al., submitted]{PoberNextGen} is drawing on lessons learned by the MWA and PAPER to reach the calibration and foreground isolation accuracy required to make a significant detection and characterization of the cosmological signal.
+HERA uses 14\,m diameter parabolic dishes arranged in a compact, hexagonal array to achieve coherent integration on the very low surface brightness 21\,cm signal.
+Redundant baselines also permit redundant calibration techniques which solve for internal degrees of freedom with only of parameters which must be estimated from the sky \citep{zheng14}, circumventing the sky model based calibration schemes which non-redundant arrays must pursue.
+HERA is pursuing a staged deployment of 19, 127, and finally 331 elements in progressively larger hex patterns, with scattered outriggers for imaging.
+A central lesson of first generation instruments is it is essential to characterize the instrument response to foreground emission lest instrument frequency dependence smear foreground power into cosmological signal modes.
 
@@
 It was initially thought that the foreground emission would be confined to the lowest few 
-line of sight Fourier modes, however it was later realized that the spectral structure of the 
-interferometer's point spread function smears foreground power into a ``wedge''-shaped 
-region in  $(k_\perp,k_\parallel)$ Fourier space. The complement of this corrupted region 
-is known as the ``EOR Window''. Here ($k_\perp,k_\parallel$) represent spatial modes 
-perpendicular and parallel to the line of sight. This effect is straightforward to understand 
-for a single baseline which measures the sky intensity weighted by the complex sky fringe 
-$e^{i \vec{k}\cdot\vec{b}}$, where $\vec{k}=\vec{k}(\theta,\phi)$ is the wave vector of 
-the incident radiation and $\vec{b}$ is the baseline vector in meters. A source at zenith 
-has $\vec{k}\perp\vec{b}$, and so appears in the visibility without any apparent 
-frequency dependence; however the visibility for a source near the horizon in line with the 
-baseline is maximally frequency dependent, and proportional to $e^{2\pi i f b/c}$.
+line of sight Fourier modes \citep[e.g.,][]{MoralesBowmanHewittFGsub}, however it was later realized that the  
+interferometer's frequency-dependent point spread function smears foreground power into a ``wedge'' shaped 
+region in  $(k_\perp,k_\parallel)$ Fourier space \citep{Dattapowerspec,X13, PoberWedge,MoralesPSShapes, VedanthamWedge, nithya13, CathWedge, AdrianWedge1, AdrianWedge2}.
+This effect is straightforward to understand for a single baseline which measures the sky intensity weighted by the complex sky fringe
+$e^{i \vec{k}\cdot\vec{b}}$, where $\vec{k}=\vec{k}(\theta,\phi,f)$ is the wave vector of 
+the incident radiation, $\vec{b}$ is the baseline vector in meters, and $f$ is the observation frequency. Thus sources at different positions relative to the baseline vector manifest different 
+frequency structure despite their intrinsically smooth spectra, but are geometrically limited 
+by the baseline length to a maximum frequency dependence of  $e^{2\pi i f b/c}$. This limits the foreground contamination 
+to a wedge shaped region in Fourier space with $k_\parallel<a k_\perp$, where $k_\perp$ and $k_\parallel$ represent spatial modes 
+perpendicular and parallel to the line of sight, and $a$ is a constant depending on the observational frequency and cosmology. The complement of the wedge is knows as the ``EOR window''.
 
-Thus sources at different positions relative to the baseline vector manifest different 
-frequency structure despite their intrinsically smooth spectra, but are geometrically limited 
-by the baseline length so that maximum affected $k_\parallel$ mode is proportional to the 
-baseline length, and thus to $k_\perp$. It is convenient to phrase this description in terms 
+It is convenient to phrase this description in terms 
 of the delay in radiation arrival at the baseline's two antennas, $\tau$, where $\tau_
-\text{max}=b/c$. The interpretation is thus that sources at low delay have little frequency 
+\text{max}=b/c$. Sources at low delay have little frequency 
 structure, while those near $\tau=\tau_\text{max}$ acquire the maximum frequency 
@@
 
-That sources acquire frequency dependence commensurate with their position in the sky 
-tells us already that the primary beam strongly affects the apparent frequency dependence 
+The fact that sources acquire frequency dependence based on with their position on the sky 
+tells us already that the primary beam strongly affects the aggregate frequency dependence 
 of the foregrounds. The high delay regions of the sky lie near the horizon while low delay 
 regions lie closer to zenith and also perpendicular to the baseline vector. \citet{nithya15} 
-simulate the foreground contamination seen with a dipole beam, a phased array of simple 
-dipoles, and a Airy dish, and find that the latter suffers minimal foreground contamination 
-into of nonzero $k_\parallel$ model due to its narrow main lobe and minimal sidelobe 
+simulate the foreground contamination seen with a dipole beam, a phased array, and a Airy dish,
+and find that the latter suffers the least foreground leakage into
+ $k_\parallel>0$ modes due to its narrow main lobe and minimal sidelobe 
 levels. To be sure, all are subject to the same geometric limits on foreground frequency-
-dependence, the wedge, but the emission from high delay is better suppressed using the 
+dependence limiting foreground bounding foreground emission within the wedge, but the emission from high delay is better suppressed using the 
 Airy dish leaving much of the wedge effectively empty.
@@
 
-In principle, it is irrelevant how empty or full the wedge is of foreground power as it is 
-perfectly contained in it, however the finite bandwidth and imperfect frequency bandpass 
+So long as foreground emission is perfectly contained in the wedge it is irrelevant how much or 
+little of it there is, but the finite bandwidth and imperfect bandpass calibration 
 of real instruments smear power beyond the geometrical edge of the wedge into the EOR 
@@
 most at risk of leaking into the EOR window due to these effects. In fact, 
-\citet{nithya15,nithya15b} observe that while naively we might expect minimal emission 
+\citet{nithya15,nithya15b} observe in simulations and then in data that while naively we might expect minimal emission 
 at the very edge of the wedge because typical near-horizon beam responses are so small, 
-two effects cause a relative brightening of emission at those maximal delays after the 
-decline away from zero delay, creating a characteristic ``pitchfork'' shape. This horizon 
+two effects can cause a relative brightening of emission at those maximal delays, creating a characteristic ``pitchfork'' shape. This horizon 
 brightening is caused by the large solid angle subtended by the near-horizon regions of the 
-sky, and the apparent shortening of baselines when viewed on axis at these elevations. 
-This second effect makes intermediate length baselines sensitive to the very bright diffuse 
-emission they would not otherwise be sensitive due to its very weak coupling to longer 
-baselines. Together, these effects can over the decline in beam sensitivity near the horizon. 
+sky, as well as the apparent shortening of baselines when viewed nearly on axis at these elevations. 
+This second effect makes intermediate length baselines of tens to hundreds of meters sensitive to the very bright diffuse 
+emission would not see from near zenith. Together, these effects can overcome the decline in beam sensitivity near the horizon. 
 All these considerations highlight the antenna beam as a critical design parameter for 
@@
 
-This is the first paper in a series of four papers detailing the HERA element. We focus on the 
+This is the first in a series of four papers detailing the HERA element. In this work we study 
 angular response of the dish and its implications for power spectrum measurements. The three companion 
@@
 In this paper we first characterize the angular response of a prototype HERA dish at the National Radio 
-Astronomy Observatory--Green Bank. We use the technique data acquisition system of \citet{neben15} to 
-measure the 137\,MHz beam pattern using the ORBCOMM satellite constellation, allowing beam 
-measurements down to roughly -35dB from zenith, corresponding to an elevation roughly $30^\circ$. We 
-perform these measurements with the feed suspended at different heights above the dish, and compare the 
-observed power patterns and collecting areas with models. We consider the science implications of these 
-results by simulating visibilities with these beam models, testing different models of the sub-$30^\circ$ 
-elevation beam response unprobed by our measurements. We run these simulations for baselines of different 
-lengths and orientations at different local sidereal times to study under when the leakage out of the wedge is 
-significant, and what regions of the EOR window are affected.
+Astronomy Observatory--Green Bank. We use the beam mapping system of \citet{neben15} to 
+measure the 137\,MHz beam pattern using the ORBCOMM satellite constellation. We obtain beam 
+measurements out to zenith angles of $\sim60^\circ$ where the beam response is -35\,dB relative to zenith, and compare with different numerical models.
+We characterize the dish beam at various feed heights to map out the focus and study beam errors due to feed misalignment.
+We compute the collecting areas and implied EOR power spectrum sensitivities of our measured beams.
+After verifying our numerical models, we consider the science implications of these
+beam patterns by foreground delay spectra at different baseline lengths and observing conditions to study when the horizon brightening effect is strongest, and thus, when foreground are must at risk of leaking into the EOR window.
 
-In detail, we discuss the electromagnetic design and modeling of the dish in Section 3. We present the 
+In detail, we discuss the electromagnetic design and modeling of the dish in Section 2. We present the 
 experimental setup of the beam mapping experiments and discuss their systematics, then 
 review the ORBCOMM beam measurement system, in Section 3. We present our power pattern 
-measurements in Section 5. We conclude with discussion in Section 6.
+measurements in Section 4, and study the science implications of these beam measurements for foreground power spectra in Section 5, then conclude with discussion in Section 6.
 
@@
 \subsection{Design of the HERA Dish}
+NEED EDITING
 
@@
 
-\subsection{HERA--Green Bank: A three-element prototype array}
-
-A 3-element HERA engineering prototype array is being constructed at the National Radio 
-Astronomy Observatory--Green Bank. We performed the beam measurements presented in 
-this work on the first of these to be constructed, future work will characterize how its in-
-situ beam in the presence of the other two dishes once they are constructed. Figure 
-\ref{fig:aerial} shows the west-most HERA dish next to two planned dishes in Galford 
-Meadow. The two reference antennas 100\,m are positioned due south with a 100\,m 
-separation, and the Green Bank Telescope $\sim1$\,km northwest of the dish. The data 
-acquisition system is installed in the hut labeled ``Launch point'' on the image.
-
-Note that unlike the full HERA site in the Karoo Desert Radio Astronomy Reserve in 
-South Africa, the Green Bank site has obstructions such as trees and foothills, as well as 
-moist ground with possibly non-uniform properties. All these will contribute to variation 
-of the in-situ reference antenna relative to the electromagnetic model. We will discuss 
-below how we quantify these systematics with ``null experiments'' which compare the 
-beams of the two reference antennas.
-
 \subsection{ORBCOMM Beam Mapping System Review}
@@
 We briefly review the beam mapping system detailed by \citet{neben15}, then discuss 
-application of system to the prototype HERA array at NRAO--Green Bank. The system 
+application of system for HERA dish measurements. The system 
 takes advantage of the 137\,MHz communications satellites operated by ORBCOMM Inc. 
 as bright point sources which, by virtue of their number ($\sim30$), short orbital periods 
-($\sim90$ minutes), and orbital precession cover 65\% of the visible sky in just a few 
-days. The coverage is limited by the fact that the satellites' orbital inclinations are all less 
+($\sim90$ minutes), and orbital precession cover $\sim$65\% of the visible sky in just a few 
+days. The coverage from the Green Bank site is limited by the fact that the satellites' orbital inclinations are all less 
 than $45^\circ$.
 
-In contrast to celestial source beam measurements, though, where the flux may be 
+Unlike celestial source beam measurements, where the flux may be 
 assumed constant over the timescale of the measurement, satellite fluxes can vary rapidly 
-due to varying distance, orientation, and transmission power. To correct for this, we 
+due to changing distance, orientation, and transmission power. To correct for this, we 
 measure the satellite flux in each ground polarization (EW and NS) using a simple, well-
@@
 Antenna-Under-Test (AUT) gives the AUT beam response in the direction of the satellite. 
-An equivalent interpretation is that the power ratio between the AUT and the reference 
+An equivalent interpretation of the measurement is that the power ratio between the AUT and the reference 
 antenna gives the relative beam response in the satellite direction, and multiplication by 
 the reference antenna model yields the desired AUT response. As discussed in 
-\citet{neben15}, despite the fact that satellite signals are generally polarized, this 
-procedure.
+\citet{neben15}, this procedure correctly measures the response of the AUT to unpolarized radiation
+ despite the fact that satellite signals are generally polarized.
 
-In detail, we measure the dual-polarization RMS powers for each antenna in 512 2\,kHz 
-bands across the 137--138\,MHz band. Each channel power is averaged over $\sim0.2$
+In detail, we measure the dual-polarization RMS power received by each antenna in 512 2\,kHz 
+channels across the 137--138\,MHz band. Each band power is averaged over $\sim0.2$
 \,sec. There are 0--3 satellites above the horizon at any given time transmitting on different 
@@
 commercial users of the network) to sync with passing satellites and record their identifier 
-and transmission frequency.
+and transmission frequency during each pass.
 
@@
 satellite flux no longer dominates over that of the diffuse Galactic background, and a 
-power measurement no longer probes the response in the satellite direction. The beam 
-measurements are then gridded in horizontal coordinates in HEALPix with a resolution of 
+power measurement no longer probes the response in only the satellite direction. The beam 
+measurements are then gridded in horizontal coordinates in HEALPix \citep{healpix} with a resolution of 
 $1.8^\circ$ (nside=32). As a last quality control step to reject errant beam measurements 
@@
 
-%Our power ratio measurement relies upon an accurately modeled reference dipole.
-We are developing a more comprehensive model of the physical reference antenna and ground screen design, improving on that used in \citep{neben15}.
-As yet, this improved model yields incorrect results, so more debugging is needed.
+\subsection{HERA--Green Bank: A three-element prototype array}
+
+A 3-element HERA engineering prototype is being constructed at the National Radio 
+Astronomy Observatory--Green Bank. We performed the beam measurements presented in 
+this work on the first of these dishes to be constructed, future work will characterize its beam in the presence of the other two dishes once they are constructed.
+The prototype array is situated in Galford Meadow, approximately 1\,km southwest of the Green Bank Telescope.
+Note that unlike the full HERA site in the Karoo Desert Radio Astronomy Reserve in
+South Africa, the Green Bank site has trees and foothills, as well as moist ground. Our beam measurements
+are sensitive to these effects in addition to the construction imperfections of real world dishes.
+
+We use a simple dual-polarization dipole as our reference antenna.
+The dipole is constructed out of copper tubing covered by PVC for protection, mounted above a 2\,m $\times$ 2\,m ground plane.
+See \citet{neben15} for details.
+During the dish measurements the dipole is positioned 100\,m due south of the dish, though we experiment with other locations at first in our to characterize the environmental systematics of these measurements, as detailed in the next section.
 
@@
 \includegraphics[width=6.5in]{null_expt_rel_beam_maps.pdf}
-\caption{null experiment beam ratio plots}
+\caption{We characterize the accuracy of the beam measurement system through null experiments in which a second reference antenna is taken as the AUT and ratio of both reference antenna power patterns is measured for EW (left) and NS (right) polarizations.
+The reference antennas are separated by 50\,m from each other and from the HERA dish in the first experiment (top), and by 100\,m from each other and from the HERA dish in the second experiment (bottom).}
 \label{fig:nullexptplots}
@@
 As in \citet{neben15}, we assess systematics using a ``null experiment'' in which we use a second reference dipole as the antenna-under-test (AUT).
-Taking the ratio of its measured power pattern with the model beam pattern amounts to a ratio of the row power responses received by the two antennas.
-This test thus probes the level of environmental systematics (i.e., reflections and varying ground properties) and antenna fabrication imperfections which affect each antenna differently.
-This is not a probe of modeling imperfections common to both antennas, but we expect such errors to be subdominant as the physical properties of the antenna are easier to characterize, and thus simulate, than local environmental effects.
+Taking the ratio of its measured power pattern with the model beam pattern amounts to a ratio of the raw power responses received by the two antennas as a function of satellite direction.
+This probes the level of environmental systematics (i.e., reflections and varying ground properties) and antenna fabrication imperfections which affect each antenna differently.
+This is not a probe of modeling imperfections common to both antennas, but we expect such errors to be subdominant as the physical properties of the antenna are easier to characterize, and thus simulate, than misalignments and local environmental effects.
 
-We run three null experiments with the reference dipoles deployed varying distances from the HERA dish and from each other.
-
-\begin{itemize}
-\item \texttt{null1}: reference dipoles deployed 50\,m apart on a NS line, 50\,m south of the HERA dish
-\item \texttt{null3}: same as \texttt{null1} but with the south-most reference antenna moved 5\,m west
-\item \texttt{null4}: same as \texttt{null1} but with 100\,m separation between both reference antennas and from the dish
-\end{itemize}
-
-Figure \ref{fig:null1} shows the  results from the \texttt{null1} experiment in the form of the ratio of the power responses of the two antennas (top panel), and slices through the E an H planes of the reconstructed power patterns (bottom panel).
+As we are not able to replace the HERA dish with a reference antenna, we run two null experiments with both reference dipoles deployed (1) 50\,m apart on a NS line, 50\,m south of the HERA dish; and (2) 100\,m apart on a NS line, 100,m south of the HERA dish.
+Figure \ref{fig:null1} shows the  results from these experiments in the form of the ratio of the power responses of the two antennas.
 We collected roughly 100 satellite passes.
-Systematics at the few percent level are observed in  within $20^\circ$ of zenith, and at the $\sim10\%$ level farther out.
-
-The magnitude of these systematics is comparable to those observed in the two other null experiments (Figures \ref{fig:null3} and \ref{fig:null4}), an their angular distribution appears largely unchanged.
-This suggests that the reference dipoles differ both due to varying environmental properties and perhaps intrinsic differences.
-In any case, these fractional errors propagate directly into the measured beampatterns of our subsequent feed and dish measurements.
+Systematics at the few percent level are observed in  within $20^\circ$ of zenith, and at the $10--20\%$ level farther out.
+The magnitude and angular distribution of these systematics changes modestly as the separation is changed, suggesting that the reference dipoles differ largely due to intrinsic differences, with some environmental variation.
+In any case, these fractional errors propagate directly into our measured dish power patterns.
 
@@
 
-Having verified the feed power pattern, we deployed feed over the dish and proceed with dish measurements.
-We measure the power pattern with the feed at four different heights, 4\,m, 4.5\,m, 5\,m, and 5.3\,m, chosen to probe around the nominal focus of 4.5\,m (the nominal beam) and up to the maximum height of 5.3\,m allowed by pole height and rope stresses.
-Heights are measured from the dish surface to the feed backplane.
+We make three dish power pattern measurements with the feed at different heights: (1) 4.5\,m, the nominal dish focus; (2) 5.0\,m, an intermediate focus; and (3) 5.3\,m, the numerically determined focus of the dish/feed system, where all heights are measured from the dish surface to the feed back plane.
+In each configuration we collect data for 2--4 days, obtaining roughly 200 satellite passes.
+We exclude times when the received power is within 20\,dB of the background level determined at between passes, and then grid measured beam values into 1.8$^\circ$ HEALPix cells on the sky, rejecting outliers in the top or bottom 5\% in each cell as a final guard against rare satellite identification problems or ADC saturation issues.
 
-Inspecting the E and H plane slices through the measured beams (bottom panels) in Figures \ref{fig:dish3}, \ref{fig:dish1}, \ref{fig:dish2}, \ref{fig:dish4}, we generally see the main lobe narrow and the sidelobe level decrease.
-The improvement is also seen in the yellow and red main lobe in the beam maps (top panels) which narrow and approach the expected orientations: the EW (NS) main lobe is elongated in the NS (EW) direction.
-The last lift produced the smallest change in the beam suggesting it is quite near the best focus.
-
+Figure \ref{fig:measuredbeammaps} shows the measured power patterns for these three feed heights for the EW (left panel) and the NS (right panel) feed polarization.
+These maps are plotted in sine-projection with dashed circles marking zenith angles of $20^\circ$, $40^\circ$, $60^\circ$, $80^\circ$.
 The sky coverage in these dish measurements extends out to typically $\theta\sim50-60^\circ$.
 Beyond that the ORBCOMM flux is sufficiently attenuated relative to diffuse galactic emission that a power ratio measurement between the two antennas is no longer a clean probe of their gains in the direction of the satellite.
-At these zenith angles, the beam sidelobes are roughly -30\,dB, and seem to be trending downward at the edge of the measured region.
+At these zenith angles, the beam sidelobes are roughly -30\,dB, and are trending downward at the edge of the measured region.
 
-In order to compute beam collecting areas and assess foreground leakage we require a beam covering the entire visible sky.
-For each measured dish beam, we interpolate over the unmeasured cells at $\theta\lesssim60$, then extrapolate outward to the horizon.
-This amounts to a smooth continuation of the beam response at the same $\sim-30$\,dB level suggested by the fringes of our measurements.
-We take this as a first possible model of the full sky dish beam, and construct a second with a gaussian cutoff at $\theta=60^\circ$ with $\sigma=2.5^\circ$, the pair of which span the space of likely horizon responses.
-This procedure is depicted in Figure \ref{fig:interpbeams} where we plot the measured nominal focus beam, the beam after interpolation and extrapolation, and the beam after applying the gaussian cutoff.
-Figure \ref{fig:interpbeamsslice} shows the interpolated/extrapolated beam and the beam with the cutoff along with various models to illustrate the different horizon responses more clearly.
+The roughly $10^\circ$ main lobe narrows slightly as the feed is raised from 4.5\,m to 5.3\,m, and the sidelobes shrink both in size and in amplitude, confirming the numerically predicted focus of 5.3\,m.
+As expected, the EW main lobes are slightly wider in the NS direction.
+In theory, the only asymmetric part of the dish is the dipole feed, so the overall beam should have a $180^\circ$ azimuthal symmetry.
+We observe deviations from this symmetry at the few dB level in the sidelobes, suggesting dish surface and/or feed imperfections given that the systematics identified in the null experiment are smaller.
 
-%\begin{figure}[h]
-%\includegraphics[width=3.5in]{measbeam_raw.png}
-%\includegraphics[width=3.5in]{measbeam_interp.png}
-%\includegraphics[width=3.5in]{measbeam_interp_expcutoff.png}
-%\caption{We construct full sky beams as required for Section \ref{sec:foregroundleakage} by starting from the nominal focus beam (top left), interpolating over unobserved cells at $\theta\lesssim60^\circ$ and extrapolating to the horizon (top right), and applying a gaussian cutoff starting at $\theta=60^\circ$ with $\sigma=2.5^\circ$ (bottom left).
-These last two beams span the space of likely horizon responses.
-Circles denote $\theta=20^\circ,40^\circ,60^\circ,80^\circ$.}
-%\label{fig:interpbeams}
-%\end{figure}
-
-%\begin{figure}[h]
-%\includegraphics[width=3.5in]{ew_beams_slice.pdf}
-%\caption{We plot the interpolated/extrapolated measured nominal focus  beam itself (blue), and with the gaussian cutoff (cyan), along with various model beams to illustrate the varying horizon responses.
-}
-%\label{fig:interpbeamsslice}
-%\end{figure}
-
-To illustrate the results of these smoothing operations we plot slices through the nominal focus dish beam along with the three model beams discussed in Sec.
-\ref{sec:dishmodels}.
-The H (E) plane slice of the main lobe is shown at the top (bottom).
-The plots in the left side zoom in on the main lobe, while those on the right show a zoomed out view of the entire sky pattern.
+Figure \ref{fig:measuredbeamslices} shows slices through the E and H planes of these power patterns along with the HFSS and CST numerical models discussed earlier.
+As in the previous plot, the EW and NS beams are shown it the left and right panels, while the different feed heights are shown in the different rows.
+The data agree with both models to within a dB in the main lobe, but begin to diverge in the sidelobes at zenith angles of $20^\circ$ and larger.
+Here the evolution of the sidelobes as the feed is raised is again seen starkly, as is the fact that the main lobes are slightly wider along the H planes than along the E planes.
 
@@
 
-The collecting area of the antenna is related to the power pattern by the ratio of the beam gain to its beam-weighted solid angle as
+We compute the effective collecting areas of these beam patterns by first interpolating over unmeasured cells and smoothly extrapolating the power pattern to the horizon.
+These operations produce a realistically smooth beam which reaches roughly -30\,dB at the horizon, as suggested by the numerical models.
+The collecting area is related to the power pattern as
 \begin{equation}
@@
 \end{equation}
-We evaluate the collecting area for four of the beams discussed above and present the numbers in Table 1.
-We are unable to quantify the collecting area of the beam from Dave's simulation because it was run at too coarse an angular resolution.
-For the measured beams, we compute the collecting area using the interpolated/extrapolated beams with and without the gaussian cutoff at $\theta=60^\circ$.
+
+The collecting areas range are shown in Table 1 along with the maximal collecting area achieved by the Airy pattern for a 14\,m dish.
+The measured collecting areas are a 30--50\% lower than the geometric area.
+This is in line with expectations given that the Airy pattern has the largest possible collecting area, equal to the dish cross section, and the feed's backplane and cylindrical skirt reduce it.
+However we opt for this reduction over added collecting area in order to reduces the azimuthal beam asymmetry and minimize the cross-coupling between adjacent dishes.
 
@@
 \end{tabular}
-\end{table}\
+\end{table}
 
-NEED TO TALK ABOUT 21CMSENSE\footnote{https://github.com/jpober/21cmSense} AND THE SNR CALCULATIONS
+We run 21cmSense\footnote{https://github.com/jpober/21cmSense} to compute the overall SNR of a power spectrum detection with one season (6 hours per night for 180 nights) of HERA-127 data.
+To input these collecting areas into 21cmSense, we convert these measured dish collecting areas into effective dish diameters, which we input as the \texttt{dish\_size\_in\_lambda} parameter.
+We predict the SNRs with optimistic, moderate, and pessimistic foreground assumptions.
+In the optimistic case, $k$ modes inside the same $uv$ pixel are added coherently, and all modes whose frequency dependence is larger than that of source at the edge of the main lobe are used.
+In the moderate case, $k$ modes inside the same $uv$ pixel are added coherently and only modes whose frequency dependence falls outside of the horizon plus a buffer are used.
+In the pessimistic case, all baselines are added incoherently and only modes outside the horizon plus a buffer are used.
 
-By definition, the Airy pattern has the largest collecting area equal to the dish cross section.
-The others model a realistic feed with a hanging screen (the skirt or ``kilt''), effectively tapering the dish response to radiation received from its fringes to mitigate cross-coupling and crosstalk between adjacent dishes.
-As expected, raising the height of the feed increases the illuminated area of the dish, and thus, its collecting area.
-As expected, the measured collecting area matches that of the CST model at the nominal focus height of 4.5\,m.
-
-Why does the collecting area increase as the feed is raised over the nominal focus?
-There are two computing effects here: (1) the reflected radiation is less well focused above the feed, decreasing the response; and (2) the tapered feed sees a larger dish as it is raised, allowing more radiation to reach the dipole as opposed to reflecting off the skirt.
-These data suggest that the second effect wins.
-Of course the reason for the skirt is to taper the feed beam in order to mitigate cross-talk and cross-coupling between the dishes.
-A larger collecting area may not be worth it in exchange for exacerbating these concerns.
+The SNRs computed with the measured collecting areas fall from 9--11 for the Airy pattern  to 6--8 in the pessimistic and moderate cases.
+In the optimistic case, the SNR falls from 37 with the Airy pattern to 24--29 with the measured collecting areas.
+In all cases this reduction is a loss of sensitivity, but a power spectrum detection is still always very significant at the 6$\sigma$ level or better.
 
@@
 DISCUSS DELAY CLEANING TO THE 2min THERMAL NOISE LEVEL, THEN DELAY TRANSFORM AGAIN WITH REDUCED RESOLUTION, MEANING A LARGER BH WINDOW, AND THUS MORE LEAKAGE, THESE EFFECTS ARE DISCUSSED IN NITHYA'S PAPER, here we are focused on intrinsic delay distribution of foregrounds
+
+We study in this section the effects of the beam power pattern on the apparent frequency dependence of the foregrounds, and in particular the uncertainties in these predictions due to beam modeling uncertainties.
+Thyagarajan et al., (submitted)
 

### 2015-12-26 DishBeamMeasurements/paper/DishBeamMeasurementsPaper.tex
keep pushing

@@
 \section{Dish Design and Modeling}
+NEEDS TLC
 
@@
 
-ALSO MENTION DEPENDENCE ON BASELINE DIRECTION
-DISCUSS DELAY CLEANING TO THE 2min THERMAL NOISE LEVEL, THEN DELAY TRANSFORM AGAIN WITH REDUCED RESOLUTION, MEANING A LARGER BH WINDOW, AND THUS MORE LEAKAGE, THESE EFFECTS ARE DISCUSSED IN NITHYA'S PAPER, here we are focused on intrinsic delay distribution of foregrounds
+We turn in this section to the effects of the beam power pattern on the apparent frequency dependence of the foregrounds.
+Thyagarajan et al., (submitted) discuss the apparent frequency dependence of foregrounds in more detail as well as methods to mitigate to mitigate it such as delay space CLEANing.
+We focus on this section on the uncertainties in these foreground power spectrum simulations due to beam modeling uncertainties, but we must first discuss these foreground simulations themselves and their dependence on observing conditions.
 
-We study in this section the effects of the beam power pattern on the apparent frequency dependence of the foregrounds, and in particular the uncertainties in these predictions due to beam modeling uncertainties.
-Thyagarajan et al., (submitted)
+We simulate foreground power spectra using different primary beam models at various local sidereal times (LSTs).
+Given that our measured dish power patterns agree well with both numerical models (HFSS and CST) in the main lobe but deviate in the sidelobes, and that these models make somewhat different assumptions about the dish surface, we take them as a representative pair of possible dish models.
+We use a feed height of 5\,m, a compromise between larger collecting area and smaller risk of coupling to adjacent dishes.
+We also include the Airy pattern for comparison as \citet{nithya15}.
+Beam models with weaker response near the horizon (such as the Airy pattern) downweight sources in this direction of high apparent frequency dependence.
+This reduces the magnitude of emission near the edge of the EOR window, reducing the risk it leaks inside.
+We use the per-baseline approach of \citet{parsons12a,parsons12b}, simulating visibilities measured by specific baselines as a function of frequency, then computing the Fourier transform over frequency (delay transform) and normalizing the result into a cosmological power spectrum following \citet{nithya15}.
 
-We simulate the power spectra of foregrounds with different primary beam models under various observing conditions.
-Broadly, beam models with more response near the horizon see smooth spectrum sources with more frequency dependence (higher delay), appearing closer to the nominally clean EOR window, making it more at risk of leaking power inside.
-We use the per-baseline approach of XX and XX, simulating visibilities measured by specific baselines as a function of frequency, then computing the Fourier transform over frequency (the delay transform) and normalizing the result into a cosmological power spectrum \citep{perbaselinetechnique}.
+In detail, we simulate visibilities for each beam model at various LSTs, modeling the sky as the sum of the Global Sky Model \citep{gsm} and the Culgoora \citep{Slee1995} and MWA Commissioning Survey \citep{MWACS} point source catalogs.
+We use a frequency spacing of 1\,MHz, sufficient to characterize delays within and just outside of the horizon limits on both baseline lengths we are concerned with, 14\,m and 42\,m.
+We use a total bandwidth of 100\,MHz (50\,MHz after applying the Blackman-Harris window) centered on 150\,MHz.
+This bandwidth is larger than the 10\,MHz thought to be safe from signal evolution over redshift, but is the bandwidth used in the wide band delay space foreground CLEAN of \citet{paper32,paper64}.
 
-We simulate visibilities for three beam models (HFSS, CST, and an Airy pattern for a 14\,m aperture) at various LSTs, modeling the sky as the sum of the Global Sky Model \citep{gsm} and a point source catalog (XX).
-We use a frequency spacing of 1\,MHz, sufficient to characterize delays within and just outside of the horizon limits on both baseline lengths we are concerned with, 14\,m and 42\,m.
-We use a total bandwidth of 80\,MHz (40\,MHz after applying the Blackman-Harris window) centered on 150\,MHz.
-This bandwidth is larger than the 10\,MHz thought to be safe from signal evolution over redshift, but is the bandwidth used in the power spectrum analysis of XX,XX to perform a high delay resolution empirical foreground subtraction (delay-space CLEANing) as described by XXX.
-We normalize the delay spectra into power spectra following   \citet{nithya15}.
+Figure \ref{fig:delayspec} (top panel) shows simulated foreground delay spectra at various LSTs using the nominal HFSS beam.
+As all these LSTs are high galactic latitudes far from the galactic center, the total visibility power (the level of the zero delay mode) varies only by a factor of a few over these LSTs on both baseline lengths (14\,m (left panel), 42\,m (right panel)).
+However the negative delay horizon limit (corresponding to the western horizon) has a peak that varies by over three orders of magnitude on the 14\,m baseline and by two orders of magnitude on the 42\,m baseline, demonstrating the stark difference in horizon brightening when the galaxy is just above versus just below the horizon.
 
-Nithya et al (submitted) detail the implications of these foreground delay spectra for suppression strategies.
-We are concerned here with the role of the beam in these predictions, in particular what our beam model and its uncertainties imply about foreground suppression strategies.
-We begin by simulating delay spectra, plotted in Figure \ref{fig:delayspec} (top panel) at various LSTs as outlined above using the nominal HFSS beam.
-As all these LSTs are high galactic latitudes far from the galactic center, the total visibility power (the level of the zero delay mode) varies by only an order of magnitude over these LSTs both on the 14\,m (left panel) and 42\,m (right panel).
-However the horizon limit at negative delay (corresponding to the western horizon) shows a peak that varies by three orders of magnitude on the 14\,m baseline and two orders of magnitude on the 42\,m baseline, showing the stark difference in pitchfork brightening when the galaxy is just above versus just below the horizon.
-
-In this figure we perform the approximate conversion from delay to k//, which we plot as a second x-axis at the top of the plot.
-For these short baselines, k// may be converted to k by adding kperp=0.005 or 0.02 in quadrature for these baselines at this redshift.
-These numbers are small compared to the range of k// plotted, and thus we interpret the k// axis as simply the k axis, and plot a 1D model power spectrum computed using 21cmFast as a dotted line for comparison.
+In this figure we perform the approximate conversion from delay $\tau$ to $k_\parallel$, which we plot as a second $x$-axis at the top of the plot.
+For these short baselines, $k_\parallel$ may be converted to $k$ by adding $k_\perp=0.005$ for the 14\,m baseline or $k_\perp=0.02$ for the 42\,m baseline in quadrature.
+These numbers are small compared to the range of $k_\parallel$ plotted, and thus we interpret the $k_\parallel$ axis as simply the $k$ axis, and plot a 1D model power spectrum computed using 21cmFast \citep{21cmfast} as a dotted line for comparison.
 
@@
 \includegraphics[width=6in]{delay_spectra_dave_rich_airy_beams_LST62deg.pdf}
-\caption{Simulated delay spectra for the GSM and point sources at $0^\circ$ (top pair) and $60^\circ$ (bottom pair) LST for EW baselines of length 14\,m (left pair) and 42\,m (right pair).
-The beams are are assumed constant over frequency.}
+\caption{Simulated foreground delay spectra using the HFSS beam at various LSTs (top panel).
+We plot the delay spectra at two LSTs spanning the range of possible horizon brightening for three different beam models.
+The maximum horizon brightening at the negative horizon occurs at 2$^\circ$ LST (middle panel), and the three beam models thus differ markedly in their predicted delay spectra near the horizon.
+In contrast, when the horizon brightening effect is smaller at 2$^\circ$ LST, the foreground delay spectra from all three beams agree much more closely.}
 \label{fig:delayspec}
@@
 
-We study the differences between our three beam models on two of these LSTs, one with maximal horizon brightening ($2^\circ$), and one with minimal horizon brightening ($62^\circ$).
-Figure \ref{fig:gsmplots} shows the sine-projected Global Sky Model in horizontal coordinates with units of Kelvin for these two LSTs.
+To characterize the effect of beam modeling uncertainties on this horizon brightening, we select two of these LSTs, one with maximal horizon brightening ($2^\circ$), and one with minimal horizon brightening ($62^\circ$).
+Figure \ref{fig:gsmplots} shows the sine-projected Global Sky Model, which dominates the horizon brightening effect, in horizontal coordinates with units of Kelvin for both LSTs.
 Dashed lines mark zenith angles 20$^\circ$, 40$^\circ$, 60$^\circ$, 80$^\circ$.
-These plots confirm that the large negative delay peak at both baseline's horizon limits at the 2 degree LST originates from the center of the galaxy being just above the horizon.
-In contrast several hours later, the galactic center is fully below the western horizon, leaving only a slight brightening near the eastern horizon due to the much weaker galactic anticenter.
+These plots confirm that the large negative delay peak at the 2$^\circ$ LST is due to the center of the galaxy just above the horizon.
+In contrast several hours later, the galactic center is fully below the western horizon, leaving only a slight brightening near the eastern horizon due to the weaker galactic anticenter.
 
@@
 \includegraphics[width=6in]{gsm_kelvin_LST_2deg_and_62deg.pdf}
-\caption{Simulated delay spectra for the GSM and point sources at $0^\circ$ (top pair) and $60^\circ$ (bottom pair) LST for EW baselines of length 14\,m (left pair) and 42\,m (right pair).
-The beams are are assumed constant over frequency.}
+\caption{Global Sky Model \citep{gsm} in sine-projected horizontal coordinates at LST of 2$^\circ$ (left) and 62$^\circ$ right.
+The very bright emission from the center of the galaxy at the western horizon at 2$^\circ$ is seen in the delay spectra of EW baselines as a horizon brightening at negative delay.}
 \label{fig:gsmplots}
@@
 
-We turn now to the differences in foreground delay spectra in these two observing conditions with different beam models.
-Figure \ref{fig:delayspec} (middle panel) shows the delay spectra for all three beam models at $2^\circ$ LST, which has the worst horizon brightening.
-We use both numerical beam models with 5\,m feed heights, as well as the Airy pattern for a 14\,m aperture.
-The delay spectra for these beams agree out to delays of 10--20\,ns on the 14\,m baseline and 30--40\,ns on the 62m baseline.
-These limits suggest that the beams track each other fairly well out to 15--20$^\circ$ from zenith, beyond which they cease to be correlated.
-This is essentially what is observed in Figure \ref{fig:measuredbeamslices} (middle panel).
+How much do the predicted foreground power spectra differ between the three model dish power patterns?
+Figure \ref{fig:delayspec} (middle panel) shows the simulated delay spectra for all three beams at $2^\circ$ LST, when the horizon brightening is worst.
+All three delay spectra agree out to delays of 10--20\,ns on the 14\,m baseline and 30--40\,ns on the 40\,m baseline.
+These numbers suggest that the beams track each other fairly well out to 15--20$^\circ$ from zenith, beyond which they diverge.
+This is roughly what is observed in Figure \ref{fig:measuredbeamslices} (middle panel).
 At larger delays, especially near the negative delay horizon limit, all three model delay spectra diverge due to the significant edge brightening which effectively discriminates between these models.
-The CST, HFSS, and Airy beams reach roughly -35\,dB, -38\,dB, and -50\,dB at the horizon (Figure \ref{fig:modelbeams}), consistent with the fact that the CST beam has the largest horizon brightening, followed by the HFSS beam, and then the Airy beam.
-This is seen in the delay spectra from both baseline lengths, though the edge brightening is much more significant in the longer baseline where it is less diluted by the zero delay emission.
+The CST, HFSS, and Airy beams reach roughly -35\,dB, -38\,dB, and -50\,dB at the horizon (Figure \ref{fig:modelbeams}), consistent with the fact that the CST beam has the largest horizon brightening, followed by the HFSS beam, and then by the Airy beam.
+This is seen in the delay spectra for both baseline lengths, though the edge brightening is much clearer on the longer baseline where it less diluted by zero delay emission.
 
-In contrast, all three model agree much more closely when there is little or no edge brightening as in Figure \ref{fig:measuredbeamslices} (middle panel) where we plot the delay spectra for all three beams for 62$^\circ$ LST.
-There is still a modest edge brightening observed here, a flattening off near the horizon on the short baseline and a small peak on the long baseline, both due to the increasing solid angle per zenith angle at larger zenith angles.
-However as the emission at this LST at large delays is roughly the same temperature as emission from everywhere else on the sky, washing out the difference between the three beam models.
+In contrast, all three model agree much more closely when there is little or no edge brightening as in Figure \ref{fig:measuredbeamslices} (bottom panel) where we plot the delay spectra for all three beams for 62$^\circ$ LST.
+There is still a modest flattening off near the horizon on the 14\,m baseline and a slight peak on the 42\,m baseline due to the large solid angle near the horizon.
+However as the near horizon emission at this LST is roughly the same temperature as emission from everywhere else on the sky, the difference between the three beam models is greatly reduced.
 
 \section{Discussion}
-
+NEEDS TLC
 %- power spectrum analyses by first generation instruments are ongoing, but face many challenges

### 2015-12-26 DishBeamMeasurements/paper/DishBeamMeasurementsPaper.tex
getting drafty in here

@@
 \begin{abstract}
-THIS WILL NEED TO BE REWRITTEN
-We deploy the 137\,MHz ORBCOMM beam mapping system of \citet{neben15} at the site of the HERA prototype at NRAO--Green Bank.
-This technique measures the beam of an antenna-under-test relative to that of a well-modeled reference antenna.
-We characterize environmental systematics such as reflections and multipath effects by comparing the measured beams of different reference antennas, then measure the beam pattern of the east-most HERA dish as a function of feed height over the dish surface.
-With the feed at the nominal focus of 4.5\,m over the dish surface, the collecting area is observed to be 68.5\,m$^2$, agreeing with simulations.
-We also simulate delay spectra on baselines of different lengths and orientations at different LSTs for measured and model beams, and quantify the severity of and uncertainties in the delay space horizon brightening termed the ``pitchfork effect'' by \citet{nithya15}.
+The Hydrogen Epoch of Reionization Array (HERA) is a radio interferometer aiming to detect the power spectrum of 21\,cm fluctuations from neutral Hydrogen from the Epoch of Reionization.
+Drawing on lessons from the Murchison Widefield Array (MWA) and the Precision Array for Probing the Epoch of Reionization (PAPER), HERA is a hexagonal array of large (14\,m) dishes with suspended dipole feeds designed to maximize sensitivity while economizing data volume.
+This is the first of a series of four papers characterizing the frequency and angular response of the HERA dish element with simulations and measurements.
+In this work we measure the angular response at 137\,MHz using the ORBCOMM beam mapping system of \citet{neben15}.
+We measure collecting areas of 70--100\,m$^2$ and estimate power spectrum SNRs of 6--8 with one season of HERA-127 observations, making very conservative foreground assumptions.
+Lastly we simulate foreground visibilities using numerical beam models and study the foreground distribution in Fourier space as a function of LST, and the uncertainties in these predictions due to beam modeling uncertainties.
 Future measurements will study the dish beam in the presence of adjacent dishes, quantifying levels of cross-talk and cross-coupling.
@@
 \section{Dish Design and Modeling}
-NEEDS TLC
 
 \subsection{Design of the HERA Dish}
-NEED EDITING
 
+We review here the design of the HERA dish, and refer to DeBoer et al. (submitted) for details. 
 The 14\,m HERA dish design is a departure from the large N--small D approach used by 21\,cm 
@@
 challenging. A larger element was chosen for HERA primarily to economize data volume.
-The natural consequence of a larger antenna aperture is a smaller field of view, but this is a 
-small effect for 21\,cm power spectrum analyses as our leverage on $k$ modes in the 
-spherically averaged power spectrum comes primarily from $k_\parallel$ modes along the line 
-of sight (in the frequency dimension).
 
-However, such a turn from small, simpler antenna elements to larger, more complex dishes with 
-suspended feeds must be done judiciously, lest the chromatic antenna response smear otherwise 
-smooth spectrum foreground power into cosmological signal modes. For this reason the dish 
-design was carefully optimized for a foreground avoidance-based power spectrum spectrum 
-analysis, as detailed by \citet{heraMemo5} and discussed in the larger engineering context of 
-HERA by DeBoer et al (in prep).
+The HERA element is a 14\,m diameter parabolic dish ($f/D\approx0.32$) with a dual-polarized dipole feed (Fig.
+\ref{fig:feedphoto}) suspended at prime focus.
+The dish surface is formed by sheets of wire attached to PVC tubes attached to supports at the edge of the dish and to a hub at the base.
+The feed is suspended with cables attached to three telephone poles around the dish.
+For feed maintenance purposes, a door is engineered into the dish surface on one mesh panel.
+The feed stands 17\,in off a mesh back plane surrounded by a XX\,in deep cylinder.
+The nominal dish focus is at 4.5\,m from the dish surface to the feed back plane, though numerical models suggest the focus is closer to 5.3\,m.
+The feed is designed to make the beams for both polarizations more similar to each other, and also to taper the dipole beam towards the edge of the dish to mitigate dish-dish coupling.
 
-\begin{figure}[h]
-\includegraphics[width=3.4in]{IMG_0353.JPG}
-\caption{Aerial photograph of the two reference dipoles deployed in Galford Meadow at the National Radio Astronomy Observatory--Green Bank 100\,m south of the HERA dish.}
-\label{fig:dishphoto}
-\end{figure}
+Feed/dish optimization studies are ongoing and these parameters may change in the final HERA array, but in this work we use the feed with these dimensions and study the beam the feed suspended at different heights.
+We study the position of the dish focus, the shape of the main lobe, the magnitude of the dish sidelobes, the degree of beam symmetry, the actual dish/feed efficiency (i.e., collecting area), and the expected level of antenna-to-antenna variation.
 
@@
 \includegraphics[width=3.4in]{feed.jpg}
-\caption{Aerial photograph of the two reference dipoles deployed in Galford Meadow at the National Radio Astronomy Observatory--Green Bank 100\,m south of the HERA dish.}
-\label{fig:dishphoto}
+\caption{Prototype HERA feed set up outside the dish for preliminary characterization.
+This feed revision consists of a dual-polarized sleeved dipole offset 17\,in from a XX\,in diameter back plane, surrounded by a XX\,in deep cylindrical skirt.}
+\label{fig:feedphoto}
 \end{figure}
 
-We summarize here the logic leading to a 14\,m dish with $f/D\approx0.32$. As discussed 
-above, it is useful to think in delay-space, where a source ideally appears as a delta function 
-at the delay corresponding to the difference in light travel time to two antennas in a 
-baseline. In a real instrument, finite bandwidth and intrinsic source spectral structure 
-(synchrotron sources typically have $I\propto f^{-0.85}$) smear foreground power over a 
-kernel as wide as $\sim60$\,ns. All antennas have some frequency structure as well, though 
-dipole-like elements such as sleeved dipoles and bowties may be made relative frequency 
-independent over wide bands. Suspension of a feed over a dish introduces frequency 
-structure directly due to time domain reflections between the dish and feed. We optimize the 
-HERA dish so this frequency structure extends no farther into delay space than the 60\,ns 
-intrinsic width of foregrounds. This was accomplished first through numerical modeling of 
-the beam pattern with a PAPER dipole suspended over the dish aperture, and resulted in a 
-maximum efficiency of 73\% with $f/d\approx0.32$. From there, using realistic estimates of 
-reflection loss, a 14\,m dish was observed to have the property that the signal received at the 
-feed after two bounces (round trips between the dish and feed) is above -60\,dB but 
-contained in the wedge, but all higher order reflections in the EOR window are below 
--60\,dB, and thus an order of magnitude smaller than the expected cosmological signal.
-
-In reality, the HERA dishes are somewhat more complicated that these simple considerations 
-imply, and part of the purpose of the beam measurements presented in this paper is to 
-characterize their \textit{in situ} beam patterns. The dish is fabricated out of low cost 
-construction materials with an expected lifetime of $\sim5$ years, sufficient to detect the 21\,cm 
-power spectrum to high significance before the Square Kilometer Array builds a longer lasting 
-instrument to more fully characterize the Epoch of Reionization with imaging. The feed consists 
-of a sleeved dipole, suspended in a cage structure from from three ropes attaching to telephone 
-poles spaced around the dish.
-The dipole is mounted on a XX\,m mast over a XX\,m diameter backplane surrounded by a XX\,m long cylindrical ``skirt'' designed to reduce cross coupling with adjacent elements
-by narrowing the feed's response. The dish surface consists of 12 wire mesh strips secured to 
-60\,mm PVC pipes forming the dish skeleton. A spar at 2.4\,m elevation is added to ensure 
-approximately parabolic shape. Note that we refer to this design as a \textit{faceted parabola} 
-given that the dish surface between PVC spars is not curved, though our design ensures the 
-Ruze loss is at the percent level. A door is engineered into one of these mesh strips to facilitate 
-feed maintenance.
-
-This work presents beam pattern measurements to verify the capabilities of this new dish, in particular the 
-position of the dish focus, the shape of the main lobe, the magnitude of the dish sidelobes, the 
-degree of beam symmetry, the actual dish/feed efficiency (i.e., collecting area), and the expected level of antenna-to-antenna variation.
+One cost of using fewer large antenna elements is a smaller field of view, but this is a 
+small effect for 21\,cm power spectrum analyses as our leverage on $k$ modes comes primarily from $k_\parallel$ modes along the line of sight (in the frequency dimension).
+More significant is frequency structure introduced by time domain reflections between the suspended feed detailed by Ewall-Wice et al.
+(submitted) with simulations and Patra et al.
+(submitted) with zenith reflectometry measurements.
 
@@
 \includegraphics[width=7in]{dave197_rich195_airy_beams.pdf}
-\caption{Simulated delay spectra for the GSM and point sources at $0^\circ$ (top pair) and $60^\circ$ (bottom pair) LST for EW baselines of length 14\,m (left pair) and 42\,m (right pair).
-The beams are are assumed constant over frequency.}
+\caption{Simulated dish power patterns at 137\,MHz (Sec. \ref{sec:dishmodels}) using HFSS (left) and CST (middle) are shown beside an ideal Airy pattern for a 14\,m diameter dish for comparison.}
 \label{fig:modelbeams}
@@
 
-ASK DAVE OR RICH TO WRITE A ONE OR TWO PARAGRAPH SUMMARY OF THE ELECTROMAGNETIC DISH SIMULATIONS
+I EMAILED DAVE AND RICH TO ASK THEM TO WRITE A FEW SENTENCES ABOUT THE CST AND HFSS DISH MODELS
 
@@
 
+\begin{figure}[h]
+\includegraphics[width=3.4in]{IMG_0353.JPG}
+\caption{The dish with its suspended feed is seen in the back, 50\,m north of one of the reference antennas used in the null experiment to study systematics.
+The experiment is conducted in Galford Meadow at NRAO--Green Bank.}
+\label{fig:greenbankdishphoto}
+\end{figure}
+
 We use a simple dual-polarization dipole as our reference antenna.
@@
 During the dish measurements the dipole is positioned 100\,m due south of the dish, though we experiment with other locations at first in our to characterize the environmental systematics of these measurements, as detailed in the next section.
+Figure \ref{fig:greenbankdishphoto} shows the dish with suspended feed 50\,m north of one of the reference antennas.
 
@@
 
-\section{Foreground Delay Spectra Simulations}
+\section{Foreground Delay Spectrum Simulations}
 \label{sec:foregrounds}
@@
 \section{Discussion}
-NEEDS TLC
+
 %- power spectrum analyses by first generation instruments are ongoing, but face many challenges
@@
 
-Power spectrum analyses by first generation 21\,cm observatories are ongoing, but are contending with challenges ranging from calibration and foreground modeling to the computing time required to process thousands of hours of data.
-HERA draws the most successful ideas from these first generation instruments, pursuing a compact and redundant array layouts, large collecting area antenna elements, and per-baseline power spectrum analysis to make advances exactly where necessary to make a first detection and characterization of the 21\,cm signal from the EOR.
-In pursuing an array of dishes rather than one of fixed dipoles, HERA turns away from the large N--small d approach used by the MWA, LOFAR, PAPER, and other first generation instruments in order to achieve sufficient sensitivity at a reasonably data processing and analysis cost.
-The papers in this series characterize the 14\,m diameter dish used as HERA's antenna element using reflectometry measurements and simulations which probe the beams gain variation with frequency, as well as beam pattern measurements and simulations which probe the beams angular variation.
+Power spectrum analyses by first generation 21\,cm observatories are ongoing, but are contending with challenges ranging from calibration and foreground modeling to the analysis effort required to process thousands of hours of data.
+HERA draws on the most successful ideas from these first generation instruments, pursuing a compact and redundant array layout and collecting area antenna elements to minimize analysis cost.
+The hexagonal grid allows redundant calibration and coherent power spectrum integration, and the large 14\,m dish achieves sufficient sensitivity at a reasonably data processing and analysis cost.
+The papers in this series characterize the 14\,m diameter dish used as HERA's antenna element using reflectometry measurements and simulations which probe its frequency response, as well as power pattern measurement which probe its angular response.
 
@@
 
-We present in this paper beam pattern measurements at 137\,MHz and comparisons with beam models, as well as simulations of the foreground delay spectra using these modeled beams.
-We adapt the beam mapping system of \citet{neben15}, deploying it at the prototype three-element HERA array at the National Radio Astronomy Observatory--Green Bank.
-Only one dish had been constructed when these measurement were made.
-We present measured power patterns for three different feed heights above the dish covering much of the visible sky probing down to -30\,dB relative to the zenith response.
-The measured beams agree well with both models in the main lobe out to 10--20$^\circ$ from zenith, then roughly track the sidelobe levels at 20--30\,dB below zenith, though fail to reproduce the exact sidelobe amplitudes and locations.
+We present in this paper beam pattern measurements at 137\,MHz and discuss their implications for 21\,cm power spectrum analysis in terms of sensitivity and foreground isolation.
+We begin with the power pattern measurements using the beam mapping system of \citet{neben15} which we deploy at the prototype three-element HERA array at the National Radio Astronomy Observatory--Green Bank.
+Only one dish had been constructed when these measurements were made.
+We present measured power patterns for three dish configurations with the feed at different heights over the dish surface in order to characterize the focus of the system.
+The measured power patterns probe nearly two thirds of the visible sky, down to -30\,dB relative to the zenith response.
+The measured beams agree well with both models in the main lobe out to 10--20$^\circ$ from zenith, then roughly track the typical sidelobe levels at 20--30\,dB below zenith though fail to reproduce the exact sidelobe amplitudes and locations.
 
-These deviations are larger than the $\pm1$\,dB systematics observed in the null experiments designed to probe the accuracy of the ORBCOMM beam measurement system as deployed at this location, suggesting they are accurate measurement of the in situ beam pattern of the imperfect HERA dish.
+These deviations away from models and away from 180$^\circ$ azimuthal symmetry are larger than the $\pm1$\,dB systematics observed in the null experiments which probe our beam measurement accuracy, suggesting they are genuine measurements of the in situ dish beam.
 The most likely dish non-idealities are dish surface imperfections and feed misalignment, both of which may vary from antenna to antenna in the full HERA array.
-Characterizing this antenna-to-antenna beam variation and its effects on power spectrum analyses for HERA, in the way Neben et al (submitted) do for the MWA, is left as future work.
+Characterizing this antenna-to-antenna beam variation and its effects on power spectrum analyses for HERA, as Neben et al.
+(submitted) do for the MWA, is left as future work.
 
@@
 % power spectrum SNR
-We quantify the 21\,cm power spectrum sensitivity using our measured beam patterns by first computing the collecting area at different feed heights.
-We observe a reduction of 30--50\% from that of an ideal, unobstructed Airy pattern for a 14\,m dish.
-We convert these collecting areas into effective dish sizes to predict overall power spectrum sensitivities for HERA-127 using 21cmSense, and find SNRs of 6--8 in pessimistic and moderate foreground scenarios, and 24--29 in optimistic ones, to be compared with roughly 10 and 37 using the Airy dish.
-This is a certainly a reduction, but of course an unobstructed, perfectly azimuthally symmetric Airy pattern is unachievable, every dish required polarized feeds either placed on axis where they block the primary reflector, or placed off axis where they don't get the dish's full collecting area.
-Further, the XX\,m cylinder hung from the feed backplane around the dipole mitigates cross-coupling between adjacent dishes and reduces azimuthal asymmetry, both of which facilitate analysis despite the reduced sensitivity.
+We quantify HERA's 21\,cm power spectrum sensitivity given our beam measurements by first computing the collecting area of the different dish configurations.
+We observe a reduction of 30--50\% from the geometric cross section of a 14\,m dish due to the dipole feed and its cylindrical skirt which tapers the beam towards the edge of the dish to mitigate cross coupling with adjacent dishes.
+We convert these collecting areas into effective dish sizes, then use 21cmSense to predict the overall power spectrum SNR with one season of HERA-127 data.
+We find SNRs of 6--8 in pessimistic and moderate foreground scenarios, and 24--29 in optimistic ones, to be compared with SNRs of roughly 10 and 37 using full geometric collecting area.
+While certainly a reduction from the theoretical limit, these sensitivities still permit a very significant detection of the 21\,cm signal after a single observing season.
 
@@
 % horizon brightening will dominated leakage into the outer window modes
-Beyond simply sensitivity considerations, though, different beam models affect science analyses by reweighting celestial emission in different regions of the sky which are imprinted by the interferometer with different frequency dependence.
-Understanding this ``wedge'' region in cylindrical fourier space has proved a fruitful advance in 21\,cm analyses over the past several years.
-Foregrounds acquire frequency dependence only from the changing baseline length in wavelengths with frequency, reaching a maximum fringe rate for a source at the horizon in line with the baseline.
-The complement of the wedge is the EOR window, which is where detection of the EOR signal is theoretically possible without foreground subtraction as it is nominally clear of foregrounds.
+Beyond simple sensitivity considerations, though, the beam pattern affects science analyses by reweighting celestial emission in different regions of the sky, which are then imprinted with different frequency dependence by the interferometer.
+Longer baselines are proportionately more susceptible to this effect, giving rise to a ``wedge'' shaped region in 2D Fourier space.
+\citet{nithya15} has highlighted that the distribution of foregrounds \textit{within} the wedge is important as well.
+If the beam response is sufficiently shallow at low elevations, there is a brightening of emission from near the horizon in line with the baseline due in part to the large solid angle at low elevations.
+This produces a characteristic ``pitchfork'' shape in the delay spectrum of a single baseline, with a zero delay peak due to bright near-zenith emission surrounded by tines at the negative and positive horizon limits due to emission from the two horizon directions in line with the baseline.
+These horizon peaks are \textit{most} at risk of leaking foreground power into the EOR window given chromatic instrumental imperfections such as bandpass miscalibration.
 
-However Nithya has highlighted that distribution of foregrounds within the wedge is important as well.
-The beam response at low elevations determines whether there is a brightening at the geometric, horizon limit due to the increasing solid angle and a sufficiently shallow beam gradient at low elevations.
-This produces a characteristic ``pitchfork'' shape in the delay spectrum of a single baseline, with a zero delay peak due to near-zenith emission surrounded by tines at the negative and positive horizon limits due to emission from the two horizon directions in line with the baseline.
-These horizon peaks are most at risk of corrupting the outer modes of the EOR window due to leakage from the delay point spread function.
-
-We have simulated foreground delay spectra for different baseline lengths and LSTs, finding that the level of this horizon brightening is largest when the galaxy is just above the horizon, and lowest when it is well below.
-When this pitchfork effect is large, our uncertainty in it due to beam modeling uncertainty is also large, as evidenced by the deviation of our HFSS and CST numerical beam models for these simulations.
+We predict the magnitude of this effect for the HERA element as well as its dependence on beam modeling uncertainties.
+As expected, we find that the level of horizon brightening is largest when the galaxy is just above the horizon, and lowest when it is well below.
+When the pitchfork effect is large, its uncertainty is also large as seen in the deviation of the delay spectra with HFSS and CST beam models in these simulations.
 When the effect is small, the two beam models produce much more similar results, highlighting the delay spectrum as an exquisite probe of the challenging to measure beam response at very low elevations.
@@
 
-As discussed by the other papers in this series, the frequency dependence of the beam power pattern and its overall gain widen the delay kernel of a source at some delay, leaking power farther into the EOR window.
-These papers demonstrate that in the best case, a combination of bandpass calibration and delay space CLEANing can mitigate foregrounds to a manageable level, while in the worst case, HERA can still achieve a XX--XX $\sigma$ detection of the EOR parameters from the power spectrum by simply excluding a very conservative buffer at the edge of the EOR window.
+As discussed by the other papers in this series, the frequency dependence of the beam power pattern and its overall gain widen the delay kernel of a source, leaking power into the EOR window.
+These papers demonstrate that in the best case, a combination of bandpass calibration and delay space CLEANing can mitigate foregrounds to a manageable level, while in the worst case, HERA can still achieve a XX--XX $\sigma$ detection of the EOR parameters from the power spectrum by simply excluding a very conservative buffer outside the wedge.
 All these considerations highlight the need for precision characterization of antenna elements and their implications for 21\,cm science analyses on the part of next generation observatories if we are to have any hope of detecting making this challenging measurement.

### 2015-12-26 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev1.tex
finished with rev1

--- 2015-12-26 DishBeamMeasurements/paper/DishBeamMeasurementsPaper.tex
@@
 \includegraphics[width=6.5in]{measured_beams_and_models_maps.pdf}
-\caption{null experiment beam ratio plots}
+\caption{Measured dish power patterns at various feed heights for the EW (left panel) and NS (right panel) instrumental polarizations.
+The sidelobes shrink and the main lobe narrows as the feed is raised, confirming that the focus of the dish/feed system is higher than the 4.5\,m ideal focus of the parabolic dish.}
 \label{fig:measuredbeammaps}
@@
 \includegraphics[width=6.5in]{measured_beams_and_models_slices.pdf}
-\caption{null experiment beam ratio plots}
+\caption{Slices through the E and H planes through the measured dish power patterns (points) and numerical models (curves).
+The measured beams agree with both models in the main lobe out to zenith angles of 15--20$^\circ$, but begin to deviate in the sidelobes at the 0.1--0.5\% level of the beam.}
 \label{fig:measuredbeamslices}

### 2016-01-06 DishReflectometry/GB_reflectometry_part2/plot_reflectometry.py
Adding new files once again.

@@ -22,9 +22,9 @@ for filename in sys.argv[1:]:
     #d = 10**(db/10) * np.exp(2j*np.pi*ph/360) # power
     d = 10**(db/20) * np.exp(2j*np.pi*ph/360) # 20 to put into voltage amplitude, not power
 
-    valid = np.ones(fq.size, dtype=np.bool) # use entire sampled band
+    #valid = np.ones(fq.size, dtype=np.bool) # use entire sampled band
     #valid = np.where(fq < .250) # restrict to HERA band
-    #valid = np.where(np.logical_and(fq < .2, fq > .1)) # restrict to PAPER band
+    valid = np.where(np.logical_and(fq < .2, fq > .1)) # restrict to PAPER band
     fq, d = fq[valid], d[valid]
     tau = np.fft.fftfreq(fq.size, fq[1]-fq[0])
     window = a.dsp.gen_window(fq.size, WINDOW)

### 2016-01-07 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev1.tex
minor fix
update rev1 and make new plots

@@
 \author{Abraham R. Neben\altaffilmark{1},
+Richard F. Bradley\altaffilmark{2,3},
 Aaron Ewall-Wice\altaffilmark{1},
-Nipanjana Patra\altaffilmark{2},
-Nithyanandan Thyagarajan\altaffilmark{3},
-James E. Aguirre\altaffilmark{4},
-Zaki S. Ali\altaffilmark{2},
-Judd Bowman\altaffilmark{3}
-Carina Cheng\altaffilmark{2},
-David R. DeBoer\altaffilmark{2}
-Jacqueline N. Hewitt\altaffilmark{2},
-Aaron Parsons\altaffilmark{2}}
+Nipanjana Patra\altaffilmark{4},
+Nithyanandan Thyagarajan\altaffilmark{5},
+James E. Aguirre\altaffilmark{6},
+Zaki S. Ali\altaffilmark{4},
+Judd Bowman\altaffilmark{5}
+Carina Cheng\altaffilmark{4},
+David R. DeBoer\altaffilmark{4}
+Jacqueline N. Hewitt\altaffilmark{1},
+Aaron Parsons\altaffilmark{4}}
 
 \affil{\altaffilmark{1}MIT Kavli Institute, Massachusetts Institute of Technology, Cambridge, MA, 02139 USA}
-\affil{\altaffilmark{2}Dept. of Astronomy, University of California, Berkeley, CA, USA}
-\affil{\altaffilmark{3}Arizona State University, School of Earth and Space Exploration, Tempe, AZ 85287, USA}
-\affil{\altaffilmark{4}Dept. of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA}
+\affil{\altaffiltext{2}Dept. of Electrical and Computer Engineering, University of Virginia, Charlottesville, VA, 22904}
+\affil{\altaffiltext{3}National Radio Astronomy Obs., Charlottesville, VA}
+\affil{\altaffilmark{4}Dept. of Astronomy, University of California, Berkeley, CA, USA}
+\affil{\altaffilmark{5}Arizona State University, School of Earth and Space Exploration, Tempe, AZ 85287, USA}
+\affil{\altaffilmark{6}Dept. of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA}
 
@@
 In this work we measure the angular response at 137\,MHz using the ORBCOMM beam mapping system of \citet{neben15}.
-We measure collecting areas of 70--100\,m$^2$ and estimate power spectrum SNRs of 6--8 with one season of HERA-127 observations, making very conservative foreground assumptions.
+We measure collecting areas of 70--100\,m$^2$ and predict power spectrum SNRs.
+With optimistic foreground and analysis assumptions, HERA-127 should detect the EOR with an SNR of 25--30 with a single season of observations.
+Even with more pessimistic assumptions, the significance of an EOR detection remains above $5\sigma$.
 Lastly we simulate foreground visibilities using numerical beam models and study the foreground distribution in Fourier space as a function of LST, and the uncertainties in these predictions due to beam modeling uncertainties.
@@
  complement indirect probes of the Dark Ages and Epoch of Reionization such as quasar 
- sightlines, deep galaxy surveys, and the CMB optical depth which leave the reionization 
+ sightlines, and the CMB optical depth which leave the reionization 
  history of the universe only loosely constrained. (See \citet{FurlanettoReview, miguelreview, PritchardLoebReview, aviBook, zaroubi} for reviews) Sensitivity and foreground removal are 
@@
 
-So long as foreground emission is perfectly contained in the wedge it is irrelevant how much or 
+From the point of view of power spectrum estimation, so long as foreground emission is perfectly contained in the wedge it is irrelevant how much or 
 little of it there is, but the finite bandwidth and imperfect bandpass calibration 
@@
 characterization and removal of systematics, as well as repeated or complimentary analyses, 
-challenging. A larger element was chosen for HERA primarily to economize data volume.
+challenging. A larger element was chosen for HERA primarily to reduce correlation and data processing costs.
 
@@
 
-Feed/dish optimization studies are ongoing and these parameters may change in the final HERA array, but in this work we use the feed with these dimensions and study the beam the feed suspended at different heights.
+Feed/dish optimization studies are ongoing and these parameters may change in the final HERA array, but in this work we use the feed with these dimensions and study the beam with the feed suspended at different heights.
 We study the position of the dish focus, the shape of the main lobe, the magnitude of the dish sidelobes, the degree of beam symmetry, the actual dish/feed efficiency (i.e., collecting area), and the expected level of antenna-to-antenna variation.
@@
 
-I EMAILED DAVE AND RICH TO ASK THEM TO WRITE A FEW SENTENCES ABOUT THE CST AND HFSS DISH MODELS
+We numerically model the HERA dish in both HFSS and in CST, making slightly different assumptions, in order to study the dependence of the beam pattern on modeling imperfections.
+In particular, we suspect that the near horizon beam response, which sets the level of horizon brightening, is quite sensitive to modeling assumptions.
+Modeling is also useful to probe the best focus of the dish--feed system.
+The nominal focus is at 4.5\,m given that the dish has $f/D=0.32$, though the feed back plane and skirt are expected to move the focus slightly.
+
+The HFSS model uses a 14\,m paraboloid with $f/D=0.32$ as the dish, with a 1\,m hole at vertex.
+In reality the 1\,m diameter at the vertex is filled with concrete and supports the PVC pipes which suspend the mesh panels, but we effectively assume here it is perfectly absorbant.
+The feed is modeled as a PAPER dipole suspended 17\,in below a 78\,in diameter circular backplane inside a 30\,in deep skirt hanging from the backplane (DOES DAVE'S MODEL HAVE THE 0.5IN GAP BETWEEN THE BACKPLANE AND THE SKIRT??).
+All these surfaces are modeled as solid aluminum, as are the dipole ``sleeves'', circular disks just above and below the dipole plane designed to broaden its frequency response.
+The dipoles themselves is modeled as a copper pipe of diameter XX, we neglect the dielectric PVC in which the copper pipe is actually enclosed.
+In the simulations, we excite one of the dipoles using a modal port and measure the total gain response in each direction to 137.5\,MHz radiation.
+
+In the CST model we again model the dish as a 14\,m diameter solid aluminum paraboloid with $f/D=0.32$ but now neglect the 1\,m hole at zenith, effectively assuming the concrete and earth ground behind it are perfectly reflective.
+The actual material properties are somewhere in between, though difficult to predict theoretically.
+The feed model has the same dimensions as in the HFSS model.
+The simulations are done by exciting one of the dipoles with band-limited noise (100--200\,MHz).
+The beam pattern is then obtained at a given frequency using a farfield monitor after the excitation pulse energy within the structure decays to below -80\,dB.
 
@@
 We turn in this section to the effects of the beam power pattern on the apparent frequency dependence of the foregrounds.
-Thyagarajan et al., (submitted) discuss the apparent frequency dependence of foregrounds in more detail as well as methods to mitigate to mitigate it such as delay space CLEANing.
+Thyagarajan et al., (submitted) discuss the apparent frequency dependence of foregrounds in more detail as well as methods to mitigate it such as delay space CLEANing.
 We focus on this section on the uncertainties in these foreground power spectrum simulations due to beam modeling uncertainties, but we must first discuss these foreground simulations themselves and their dependence on observing conditions.
@@
 These papers demonstrate that in the best case, a combination of bandpass calibration and delay space CLEANing can mitigate foregrounds to a manageable level, while in the worst case, HERA can still achieve a XX--XX $\sigma$ detection of the EOR parameters from the power spectrum by simply excluding a very conservative buffer outside the wedge.
-All these considerations highlight the need for precision characterization of antenna elements and their implications for 21\,cm science analyses on the part of next generation observatories if we are to have any hope of detecting making this challenging measurement.
+All these considerations highlight the need for precision characterization of antenna elements and their implications for 21\,cm science analyses on the part of next generation observatories if we are to have any hope of making this challenging measurement.
 

### 2016-01-11 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev1.tex
updated dave beam models and text

@@
 In reality the 1\,m diameter at the vertex is filled with concrete and supports the PVC pipes which suspend the mesh panels, but we effectively assume here it is perfectly absorbant.
-The feed is modeled as a PAPER dipole suspended 17\,in below a 78\,in diameter circular backplane inside a 30\,in deep skirt hanging from the backplane (DOES DAVE'S MODEL HAVE THE 0.5IN GAP BETWEEN THE BACKPLANE AND THE SKIRT??).
+The feed is modeled as a PAPER dipole suspended 17\,in below a 78\,in diameter circular backplane inside a 30\,in deep skirt hanging 0.5\,in below the backplane.
 All these surfaces are modeled as solid aluminum, as are the dipole ``sleeves'', circular disks just above and below the dipole plane designed to broaden its frequency response.

### 2016-01-12 ForegroundSimulations/ms.tex
Add figures to git, reorganize section headings
From 689699b (master):
=====================

Add .eps figures to git repo

In ms.tex,

(*) Reorganize section and subsection headings

@@
 
-\shorttitle{Estimate of Foregrounds in EoR Power Spectra for HERA}
+\shorttitle{Characterization of Beam Chromaticity in EoR Power Spectra Measurements}
 \shortauthors{Thyagarajan et~al.}
@@
 
-\title{Estimation of Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra with the Hydrogen Epoch of Reionization Array}
+\title{Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra}
 
@@
 
+\section{The Hydrogen Epoch of Reionization Array}\label{sec:HERA}
+
 \section{Delay Spectrum}\label{sec:delay-spectrum}
@@
 
-\section{The Wide-Field ``Pitchfork'' Effect}\label{sec:wide-field}
+\subsection{The Wide-Field ``Pitchfork'' Effect}\label{sec:wide-field}
 
@@
 
-\subsection{The Hydrogen Epoch of Reionization Array}\label{sec:HERA}
-
-\subsubsection{Antenna Power Pattern}
+\subsection{Antenna Power Pattern}
 
@@
 
-\subsubsection{Antenna Reflectometry}
+\subsection{Foreground Model}\label{sec:foreground}
+
+\section{Chromaticity of Power Pattern}
+
+\subsection{Directional Chromaticity}
+
+\subsection{Effect on Delay Power Spectrum}
+
+\subsection{Constraints on Antenna-to-Antenna Reflections}
 
 Patra~et~al.~2015 (submitted), Ewall-Wice~et~al.~2015 (submitted)
-
-\subsection{Foreground Model}\label{sec:foreground}
-
-\section{Analysis of Foreground Signatures}\label{sec:FG-analysis}
 

### 2016-01-12 ForegroundSimulations/ms.tex
Include figures under appropriate sections
From 4deee37 (master):
=====================

In ms.tex,

(*) Include figures under appropriate sections

@@
 
+\begin{figure*}[htb]
+\centering
+\includegraphics[width=\linewidth]{off-axis_point_source_beam_chromaticity.eps}
+\caption{Chromaticity of antenna power pattern at directions off-axis. }
+\label{fig:off-axis-beam-chromaticity}
+\end{figure*}
+
 \subsection{Directional Chromaticity}
 
+\begin{figure*}[htb]
+\centering
+\includegraphics[width=\linewidth]{directional_high_delay_average_in_beam.eps}
+\caption{All-sky directional chromaticity of antenna power pattern. }
+\label{fig:directional-beam-chromaticity}
+\end{figure*}
+
 \subsection{Effect on Delay Power Spectrum}
+
+\begin{figure*}[htb]
+\centering
+\includegraphics[width=\linewidth]{asm_beam_chromaticity_subband_150_MHz.eps}
+\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra. }
+\label{fig:asm-dps-beam-chromaticity}
+\end{figure*}
 
@@
 Patra~et~al.~2015 (submitted), Ewall-Wice~et~al.~2015 (submitted)
+
+\begin{figure*}[htb]
+\centering
+\includegraphics[width=\linewidth]{spec_on_foreground_reflected_power_21cmfast.eps}
+\caption{Attenuation of foreground power (in dB) from antenna-to-antenna reflections required to keep the reflected foreground power below EoR H{\sc i} signal power.}
+\label{fig:fg-reflections}
+\end{figure*}
 

### 2016-01-12 ForegroundSimulations/ms.tex
Add simulations in .npz format under data folder
From e87f065 (master):
=====================

(*) Add simulations in .npz format from achromatic Rich and Dave beams
to git repo

In ms.tex,

(*) Add a paragraph under section "foreground model"

@@
 
+Our all-sky foreground model is the same as the one in \citet{thy15a}.
+It consists of diffuse emission \citep{deo08} and point sources.
+The latter is obtained from a combination of the NRAO VLA Sky Survey \citep[NVSS;][]{con98} at 1.4~GHz and the Sydney University Molonglo Sky Survey \citep[SUMSS;][]{boc99,mau03} at 843~MHz with a mean spectral index of -0.83.
+
 \section{Chromaticity of Power Pattern}

### 2016-01-12 ForegroundSimulations/ms.tex
Add content under section 5
From af51c8f (master):
=====================

In ms.tex,

(*) Add content under section 5

@@
 
+DeBoer~et~al.(2016)
+
 \section{Delay Spectrum}\label{sec:delay-spectrum}
@@
 
-We describe the instrument and foreground models used in our simulations.
+We simulate wide-field visibilities for 19-element HERA from all-sky antenna power pattern and foreground models using the PRISim\footnote{The Precision Radio Interferometry Simulator (PRISim) is publicly available at \href{https://github.com/nithyanandan/PRISim}{https://github.com/nithyanandan/PRISim}} software package.
+The simulations cover 24~hr of observation in {\it drift} mode consisting of 80 accumulations spanning 1080~s each.
+The total bandwidth is 100~MHz centered on 150~MHz consisting of 128 channels with 781.125~kHz frequency resolution each.
+Models of the antenna power pattern and foregrounds are described below.
 
@@
 The latter is obtained from a combination of the NRAO VLA Sky Survey \citep[NVSS;][]{con98} at 1.4~GHz and the Sydney University Molonglo Sky Survey \citep[SUMSS;][]{boc99,mau03} at 843~MHz with a mean spectral index of -0.83.
+The diffuse sky model has an angular resolution of 13\farcm 74.
 
 \section{Chromaticity of Power Pattern}
+
+The equation for delay spectrum describes the mapping between sky location of a foreground object and delay.
+The chromatic nature (variation with frequency) of the antenna power pattern results in a convolution of the geometrical mapping with the delay response of spectral chromaticity of the power pattern.
+This can result in a significant spillover of foreground power beyond the horizon delay limits especially in the case of foregrounds near the horizon.
+
+Fig.~\ref{fig:off-axis-beam-chromaticity} demonstrates the beyond-the-horizon spillover even from a flat-spectrum point source at different off-axis angles.
+The three panels correspond to delay spectra from different positions of the point source -- 0\arcdeg (left), 45\arcdeg (middle) and 89\arcdeg (right) -- from the zenith.
+The phase centers are located at the source positions and hence the delay spectra are centered on $\tau = 0$~ns.
+The response of the simulated dish power pattern (dashed line) is comapred with that from an {\it Airy} pattern resulting from a nominal uniformly illuminated circular disk (solid line).
+The gray vertical lines correspond to the horizon limits at $\pm 48.7$~ns for a 14.6~m antenna spacing.
 
@@
 \end{figure*}
+
+At 0\arcdeg off-axis, the {\it Airy} pattern has no spectral variation and thus appears as a straight vertical line centered at $\tau = 0$~ns whereas the simulated power pattern is found to exhibit some spectral variation giving rise to the wings on either side of $\tau = 0$~ns.
+As off-axis angle increases to 45\arcdeg, both the power patterns clearly exhibit chromaticity.
+They have similar magnitudes inside the horizon limits but the chromaticity of the simulated power pattern is $\sim 100$ times higher than that of an {\it Airy} pattern outside the horizon limits.
+In contrast, at 89\arcdeg off-axis, the two patterns have similar chromaticity in delay modes outside the horizon limits but the simulated power pattern has $\sim 100$ times more power inside the horizon limits indicating that the overall amplitude of the pattern at this location is higher relative to the nominal {\it Airy} pattern.
+
+It is important to note that in a generic scenario where visibilities are not phased to a specific foreground location, the chromaticity of the power pattern will imprint itself on location of the foreground objects in delay space and will give rise to significant spillover especially from foregrounds near the horizon.
+
+We investigate the effects of spectral chromaticity of the power pattern in more detail below.
 

### 2016-01-13 ForegroundSimulations/ms.tex
Add content under section 5.1
From 08b0572 (master):
=====================

In ms.tex,

(*) Add content under section 5.1

@@
 
-\subsection{Directional Chromaticity}
+\subsection{Directional Chromaticity of Power Pattern}
+
+We generalize the analysis above by computing the delay power spectrum of the power pattern along its spectral axis in every direction in an effort to study its performance as a function of angle on the sky.
+\begin{align}
+  A^\prime(l,m,\tau) &= \int A(l,m,f)\,e^{-j 2\pi f\tau} \,\dif f
+\end{align}
+
+We define the directional chromaticity of antenna power pattern as:
+\begin{align}
+  C(l,m) &= \frac{ \int\limits_{|\tau|>60\,\textrm{ns}} |A^\prime|^2 \,\dif\tau }{\int\limits_{|\tau|>60\,\textrm{ns}} \dif\tau}
+\end{align}
+where, the limit $|\tau|>60$~ns was chosen to represent a region well beyond the horizon limits ($\pm 48.7$~ns) for a 14.6~m antenna spacing.
+It thus measures the average power arising out of chromaticity in each delay mode beyond $|\tau|>60$~ns.
+
+Fig.~\ref{fig:directional-beam-chromaticity} shows the directional chromaticity, $C(l,m)$, of the power patterns of an {\it Airy} disk for reference (left) and a simulated disk (middle) on an orthographic projection onto direction cosines.
+Their color scale is shown at the top for reference.
+The chromaticity of the {\it Airy} pattern is symmetric and always below 500.
+On the other hand,  a simulated disk exhibits higher levels of chromaticity in the range 100--50,000.
+The ratio of their chromaticities is shown on the right with corresponding color scale on its right.
+The simulated disk is more chromatic than the nominal {\it Airy} disk by a factor between 100 and up to 10000.
+However, chromaticity in regions near the horizon which map to the horizon limits in the delay spectrum and have the most significant impact on spillover into the {\it EoR window} in the simulated disk are higher than that of an {\it Airy} disk only by factors $\lesssim 4$.
+Thus the simulated disk for HERA achieves reasonable control on the chromaticity near the horizon despite the very high levels near the center.
+
+Also shown are the tracks (black dots) of point sources brighter than 50~Jy in the LST range 0--12~hrs.
+The solid circle near the bottom denotes the south celestial pole.
+It is noted that there are a few bright point sources that spend a majority of time in this LST range near the northern and southern horizons which will contaminate the measured visibilities on north-south antenna spacings.
+Future simulations of the dish power pattern must take the bright foreground locations, especially near the horizon, into account.
 

### 2016-01-13 ForegroundSimulations/ms.tex
Add content under section 5.2
From 72bc820 (master):
=====================

In ms.tex,

(*) Add content under section 5.2

@@
 
+Now we consider the effect of chromaticity of the power pattern on the delay power spectrum.
+
+We simulate visibilities from our foreground model using three different models for the antenna power pattern -- {\it Airy} pattern, simulated dish, and a pattern at 150~MHz of the simulated dish assumed to be achromatic over the entire band.
+
+Fig.~\ref{fig:asm-dps-beam-chromaticity} shows the delay power spectra of foregrounds obtained with the aforementioned models for power pattern.
+In all these panels, power spectra obtained with achromatic, {\it Airy} disk and simulated disk are shown in black, red, and blue respectively.
+The vertical gray lines denote the horizon limits for a 14.6~m antenna spacing.
+The full band delay power spectra of the foregrounds measured on a 14.6~m antenna spacing oriented eastward is shown in the top left panel.
+A clear trend of broadening of spillover-wings outside the horizon limits is seen with increasing chromaticity.
+For instance, the spillover from foreground delay power spectrum obtained with simulated dish pattern extends out to $k_\parallel \approx \pm 0.14\,h$~Mpc$^{-1}$, with the {\it Airy} pattern it extends out to $k_\parallel \approx \pm 0.08\,h$~Mpc$^{-1}$, while the achromatic beam extends it only out to $k_\parallel \approx \pm 0.05\,h$~Mpc$^{-1}$.
+Thus an increase in chromaticity extends the foreground spillover into higher $k_\parallel$-modes making them inaccessible for EoR H{\sc i} signal detection.
+
+Following the foreground removal strategy, the top middle panel shows these foreground delay spectra deconvolved using the complex delay CLEAN algorithm \citep{tay99,par09,par12b}.
+The CLEAN window covers delay bins between the horizon delay limits and extends further by three delays bins on each side of the horizon limit where a delay bin is of size inverse of the bandwidth.
+The panel at the top right shows the residuals left behind after deconvolution.
+
 \begin{figure*}[htb]
@@
 
-\subsection{Constraints on Antenna-to-Antenna Reflections}
+Owing to the chromaticity of power patterns, the spillover from foregrounds extends beyond the horizon limits, most severely in the simulated disk pattern.
+As a result the residuals have significant power remaining on either side of the horizon limits since the window for deconvolution is narrower than the extent of spillover along $k_\parallel$.
+The two peaks on either side is most severe for the simulated disk pattern followed by that for the {\it Airy} disk pattern and least for an achromatic power pattern.
 
-Patra~et~al.~2015 (submitted), Ewall-Wice~et~al.~2015 (submitted)
+We investigate the effect of chromaticity of power pattern in a foreground avoidance strategy that avoids the aforementioned deconvolution of delay spectrum.
+Application of window functions with high sidelobe suppression have been discussed for mitigating foreground contamination \citep{thy13}.
+In line with the foreground avoidance strategy, the visibilities from the full band foreground simulation (whose delay power spectrum is shown on the top left) are multiplied by a Blackman-Harris window function of 10~MHz effective bandwidth.
+The delay power spectra so produced are shown in the panel on the bottom left.
+Due to the decreased effective bandwidth the resolution of the delay power spectrum appears decreased.
+Hence, only the $|k_\parallel| \gtrsim 0.14\,h$~Mpc$^{-1}$ modes remain accessible.
+Due to the overall lower amplitude of the {\it Airy} power pattern relative to the simulated dish power pattern and the achromatic pattern, the sidelobe levels of foreground delay power spectra from an {\it Airy} pattern are lower than the other models by almost two orders of magnitude.
+
+Following a delay-deconvolution based foreground removal strategy, we apply the Blackman-Harris window of effective bandwidth 10~MHz on the unsubtracted foreground residuals (top right panel) in frequency domain and obtain the delay power spectrum shown in the bottom right panel.
+It is noted that lesser the chromaticity the more effective the deconvolution process is in lowering the residuals in and around the horizon limits.
+For instance, the peak of the delay power spectrum using the achromatic beam is lowered by four orders of magnitude relative to the original peak whereas the residuals of delay power spectra with chromatic {\it Airy} and simulated power patterns is lowered only by two orders of magnitude.
+However, owing to the ineffective subtraction of the response extended beyond the horizon limits, the sidelobe levels have not been lowered significantly and are within an order of magnitude of each other.
+
+In both strategies, the EoR H{\sc i} signal power spectrum obtained by simulations with 21cmFAST (Mesinger et al. 2008) is shown for reference (dashed black lines) in the bottom panels.
+
+\subsection{Constraints on Reflections between Antennas}
+
+Patra~et~al.~2015 (submitted) and Ewall-Wice~et~al.~2015 (submitted) discuss the measured and simulated reflections between a dish and its feed.
 

### 2016-01-13 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev1.tex
change to use nithyas simulations

@@
 \centering
-\includegraphics[width=6in]{delay_spectra_dave_rich_airy_beams_manyLSTs.pdf}
-\includegraphics[width=6in]{delay_spectra_dave_rich_airy_beams_LST2deg.pdf}
-\includegraphics[width=6in]{delay_spectra_dave_rich_airy_beams_LST62deg.pdf}
+\includegraphics[width=6in]{nithya_fg_pspec_all_lst.pdf}
+\includegraphics[width=6in]{nithya_fg_pspec_lst0deg.pdf}
+\includegraphics[width=6in]{nithya_fg_pspec_lst60deg.pdf}
 \caption{Simulated foreground delay spectra using the HFSS beam at various LSTs (top panel).
@@
 
+NEED TO REVISE THIS PARAGRAPH FOR NITHYA'S SIMULATIONS, ALSO COMMENT ON THE CST-HFSS CURVE
 How much do the predicted foreground power spectra differ between the three model dish power patterns?

### 2016-01-13 DishSimulations/paper/DishSimulationsPaper_v1.tex
a long overdue update to the simulations paper

--- 2015-11-07 DishSimulations/paper/DishSimulationsPaper_v0.tex
@@
-\documentclass[onecolumn]{emulateapj}
+\documentclass[twocolumn]{emulateapj}
 \usepackage{amsmath}
@@
 Ewall-Wice Aaron\altaffilmark{1,2},
+Richard Bradley\altaffilmark{3,4},
 Abraham Neben\altaffilmark{1,2},
@@
 Thyagarajan Nithyanandan\altaffilmark{6},
-Richard Bradley\altaffilmark{3,4},
 Jacqueline Hewitt\altaffilmark{1,2},
@@
 Using simulations of foregrounds, we find that the $\approx -40$\,dB response at 60\,ns of the HERA dish is sufficient to isolate the cosmological 21\,cm signal $\approx 0.2$\,$h$Mpc$^{-1}$ at $z\approx 8.5$ and obtain a high signal to noise detection of the power spectrum.
-At its current state, the reflections of the HERA dish design do significantly impact its ability to constrain the $R_\text{mfp}$ reionization parameter for a number of models since they prevent direct measurements of the ``knee" feature.
 This study represents the first time that direct measurements a 21\,cm interferometer design have been translated into its ability to constrain the physics of reionization.
@@
 In this section, we show how reflections in the analogue signal path of an antenna lead to foreground contamination of the EoR window.
-Inuitively, any reflections in the signal path introduce sinusoidal ripples in the frequency dependent gain of the instrument.
+Intuitively, any reflections in the signal path introduce sinusoidal ripples in the frequency dependent gain of the instrument.
 Since reflection delay is the Fourier dual to frequency, reflections at larger delays introduce ripples at higher frequencies.
-Isolation of the 21\,cm signal from foregrounds that are over five orders of magnitude brighter depends critically on the fact that their smoothness.
+Isolation of the 21\,cm signal from foregrounds that are over five orders of magnitude brighter depends critically on their smoothness.
 Any sinusoidal frequency structure, introduced by the antenna gain will cause these foregrounds to mimic and swamp the signal unless they are brought below a level similar to the ratio between the foregrounds and the signal itself.
 We now derive this process in formal detail.
-A simple equation for effect of direction independent reflections in the signal chain of an interferometer, downstream of the receiver, has been derived in \citep{EwallWice:2015a}, we extend this analysis in this section by considering the direction dependent reflections that can occur within the antenna element.
+A simple equation for effect of direction independent reflections in the signal chain of an interferometer, downstream of the receiver, has been derived in \citet{EwallWice:2015a}, we extend this analysis in this section by considering the direction dependent reflections that can occur within the antenna element.
 We assume that the intensity field on the sky is given by
@@
 \begin{equation}
-\widetilde{v}_i(t) = \int d \Omega \int d \tau \widetilde{r}_i({\bf \widehat{k}},\tau') \widetilde{s}({\bf \widehat{k}},t+\tau_i - \tau)
+\widetilde{v}_i(t) = \int d \Omega \int d \tau \widetilde{r}_i({\bf \widehat{k}},\tau) \widetilde{s}({\bf \widehat{k}},t- \tau_i - \tau)
 \end{equation}
 
- An FX (or XF) correlator measures the time-averaged product of the fourier transform of the voltage streams between the $i^{th}$ and $j^{th}$ antenna.
+A correlator (FX and XF) measures the time-averaged product of the Fourier transform of the voltage streams between the $i^{th}$ and $j^{th}$ antenna.
 Fourier transforming the voltage stream from the $i^{th}$ antenna we obtain
 \begin{equation}
-v_i(f) = \int d \Omega \int d \tau' \widetilde{r}_i({\bf \widehat{k}},\tau') s({\bf \widehat{k}},f)e^{2 \pi i f(\tau'-\tau_i)}
+v_i(f) = \int d \Omega \int d \tau \widetilde{r}_i({\bf \widehat{k}},\tau) s({\bf \widehat{k}},f)e^{-2 \pi i f(\tau_i+\tau)}
 \end{equation}
@@
 \begin{equation}
-V_{ij}'(f) = \left \langle v_i(f) v_j^*(f) \right \rangle_t = \int d \Omega \int d \tau \widetilde{r}_i(\tau) d \tau' \widetilde{r}^*_j(\tau')e^{2 \pi i f (\tau'-\tau) } I({\bf \widehat{k}}, f) e^{- 2 \pi i \Delta \tau_{ij}f}
+V_{ij}'(f) = \left \langle v_i(f) v_j^*(f) \right \rangle_t = \int d \Omega \int d \tau \widetilde{r}_i(\tau) d \tau' \widetilde{r}^*_j(\tau')e^{-2 \pi i f (\tau-\tau') } I({\bf \widehat{k}}, f) e^{- 2 \pi i \Delta \tau_{ij}f}
 \end{equation}
@@
 \begin{equation}
-\widetilde{V}_{ij}(\tau) = \int d f e^{-2 \pi i \tau f} V_{ij}(f)
+\widetilde{V}_{ij}(\tau) = \int d f e^{2 \pi i \tau f} V_{ij}(f)
 \end{equation}
@@
 \begin{equation}\label{eq:Kernel}
-\widetilde{R}_{ij}({\bf \hat{k}},\tau) = \int d \tau \widetilde{r}_i({\bf \hat{k}},\tau - \Delta \tau) \widetilde{r}_j({\bf \hat{k}},\Delta \tau).
+\widetilde{R}_{ij}({\bf \hat{k}},\tau) = \int d \tau \widetilde{r}_i({\bf \widehat{k}},\tau - \Delta \tau) \widetilde{r}^*_j({\bf \widehat{k}},-\Delta \tau).
 \end{equation}
-which itself is the convolution of the delay response of the two voltage beams, $\widetilde{r}_i({\bf \widehat{k}},\tau)$,$\widetilde{r}_j({\bf \widehat{k}},\tau)$.
+which is the convolution of the delay response of voltage beam $i$ with the complex conjugate of voltage beam $j$ evaluated on a negative t-axis, $\widetilde{r}_i({\bf \widehat{k}},\tau)$,$\widetilde{r}_j({\bf \widehat{k}},\tau)$.
+Note that this is not equal to the convolution of the voltage response with its complex conjugate, which would lead to foreground power only being bled out to positive delays.
 Usually, beams have a different delay structure in each direction, and we demonstrate the effect of foreground smearing in Fig.~\ref{fig:Smearing} for a simple model with only three sources.
@@
 Since our input is band limited between $\approx 20$ and $280$\,MHz, the direct ratio of our voltage response and input wave is dominated by numerical noise outside of this range.
-We eliminate these numerical artifacts by multiplying our ratio by a Hamming window between $50$\,MHz and $250$\,MHz and set our estimate to zero elsewhere.
+We eliminate these numerical artifacts by multiplying our ratio by a Blackman-Harris window between $100$\,MHz and $200$\,MHz and set our estimate to zero elsewhere.
 From a physical standpoint, this is sensible since 21\,cm experiments only observe a limited bandwidth.
@@
 Since our input is limited to frequencies between $\approx 20$ and $280$\,MHz, there is significant numerical noise that will effect our result outside of this region which we see in the divergene of the red line towards the edges of the plot.
-To eliminate this noise, we multiply by a Hamming window between $50$ and $250$\,MHz and set our estimate to zero elsewhere.
+To eliminate this noise, we multiply by a Blackman-Harris window between $50$ and $250$\,MHz and set our estimate to zero elsewhere.
 The Fourier transform of our response estimate with the filter applied is shown as a cyan line.}
@@
 
-\subsection{Extrapolating the Bandpass and Power Kernel}
-We show our estimate of our delay kernel in Fig.~\ref{fig:voltageVsKernel}
+We plot the delay transform of the voltage response of the dish in Figure~\ref{fig:Simulations} to gauge the dynamic range of our simulations.
+Since signal at negative delays violates causality, we assume such features are sourced by numerical artifacts such as side-lobes and/or numerical precision noise.
+We see that our simulations have a dynamic range of $-60$\,dB.
+
+\begin{figure}[h!]
+\includegraphics[width=.5\textwidth]{figures/compare_simulations_paper.pdf}
+\caption{The Fourier transform of the voltage response function of our simulation for the HERA Dish (solid black line) and the PAPER antenna element (dashed black line).
+Reflections in the HERA dish element lead to significantly enhanced power above $\sim 50$\,ns.
+We show the negative delays, which should be devoid of signal, to determine the dynamic range of our technique (which is limited by sidelobes and numerical artifacts).
+We see that these contaminants exist at the $\sim-60$\,dB level.}
+\label{fig:Simulations}
+\end{figure}
 
 \begin{figure}
-\includegraphics[width=.5\textwidth]{figures/convolveCompare.pdf}
-\caption{Our estimate of $\widetilde{r}(\tau,\theta=0)$, the voltage response of the HERA dish at zenith (blue line) along with its square (green line) which falls off significantly faster with delay.
-The power kernel for identical dishes, $\widetilde{r}\star\widetilde{r}^*$, the voltage response convolved with itself, is plotted with a red line.
-Because the $\tau=0$ response of the dish is significantly larger than the reflections, linear terms in the convolution dominate the squared terms whose magnitude roughly corresponds to the green line.
-Hence, the power kernel is well approximated by $\widetilde{r}$ itself, verifying our result in equation~\ref{eq:KernelApprox}.
-}
+\includegraphics[width=.5\textwidth]{figures/compare_reflectometry_paper.pdf}
+\caption{Same as Fig.~\ref{fig:Simulations} but now including 
+ the reflectometry measurements of \citep{Patra:2015}.
+Inspecting negative delays, we see that the reflectometry measurements contain artifacts introduced by reflections and sub-reflections in the cables leading from the VNA to the feed which enter both the HERA dish and PAPER measurements at both the $-45$\,dB to $-30$\,dB level.
+The VNA measurement is noise dominated beyond $\sim 500$\,ns.}\label{fig:Reflectometry}
 \end{figure}
+
+\begin{figure}[h!]
+\includegraphics[width=.5\textwidth]{figures/compare_kernels_paper.pdf}
+\caption{The response function deconvolved from our simulations (solid lines) compared to the response function estimated from reflectometry measurements described in \citep{Patra:2015} for the HERA dish and the PAPER antenna element.
+Our simulations agree well with the reflectometry results out to $\approx 100$\,ns but disagree by $\lesssim10$\,dB beyond this.
+A potential source of the disagreement is uncalibrated structure are irregularities in the cables connecting the Vector Network Analyzer and the antenna feed which enter at the $-50$\,dB to $-30$\,dB level.}
+\label{fig:Kernels}
+\end{figure}
+
+\subsection{The Delay Response of Subbands}\label{ssec:Subbands}
+While we observe a long term falloff due to reflections between the feed and dish element, it is possible that these reflections are localized in frequency and do no effect certain sub-bands.
+To determine whether the reflections are localized in frequency, we compute the voltage delay response and power kernel for three different subbands: $100-130$\,MHz, $130-160$\,MHz, and $160-190$\,MHz.
+In order to maintain decent resolution of the kernel itself, we use frequency ranges are larger than the actual subbands that will be used for EoR power spectrum estimation $\sim 10$\,MHz which is set by the interval over which the statistics of the cosmological HI signal are expected to be stationary.
+We plot the delay transforms of the voltage gain in Fig.~\ref{fig:GainDelaySubbands} and the power kernels in Fig.~\ref{fig:KernelsSubbands}.
+The central lobe of the delay kernel is significantly wider due to the the wider window functions incurred by the reduced bandwidth, however, the shallow long-term falloff is only visible within the central $125-175$\,MHz band, indicating that long term reflections are isolated near $150$\,MHz and will not effect power spectrum measurements outside of the very center of our band.
+
+\begin{figure}[h!]
+\includegraphics[width=.5\textwidth]{figures/voltageResponseSubbands.pdf}
+\caption{The delay transform of the voltage response of the HERA dish for the full 100\,MHz bandwidth (cyan line) along with three subbands; $100-130$\,MHz, $130-160$\,MHz, and $160-190$\,MHz.
+The shallow falloff observed in \S~\ref{sec:Simulations} is most prominent in the $130-160$\,MHz subband while the falloff in the other subbands is close the the level of the sidelobes (at $\sim -50$\,dB for the lower resolution subbands).
+$k_\parallel$ values for each delay are computed at $150$\,MHz.}
+\label{fig:GainDelaySubbands}
+\end{figure}
+
+\begin{figure}[h!]
+\includegraphics[width=.5\textwidth]{figures/powerKernelSubbands.pdf}
+\caption{The power kernel for the three subbands discussed in in \S~\ref{ssec:Subbands} along with the kernel for the full bandwidth response function.
+While the long term falloff from reflections is prominent between $130-160$\,MHz, it appears at a much lower level in the other two subbands which fall below the central subband by $\sim 20$\,dB at $\sim 300$\,ns.
+$k_\parallel$ values for each delay are computed at $150$\,MHz.}
+\label{fig:KernelsSubbands}
+\end{figure}
+
+\subsection{Extrapolating the Bandpass and Power Kernel}
+Our deconvolution gives us the time-domain voltage response of the PAPER and HERA antenna elements.
+We plot the absolute value of this response in Fig.~\ref{fig:SimulationsCompare}, seeing that it drops to $-30$\,dB after $\approx 100$\,ns.
+The power-kernel that convolves visibilities to higher delays is the convolution of $\widetilde{r}(\tau)$ with its time-reversed complex conjugate, which we plot as the red line.
+The convolution is in very good agreement with the voltage response itself which is explained by the fact that second order terms of the convolution, approximately given by $|\widetilde{r}(\tau)|^2$ (green line) are over two orders of magnitude smaller above $50$\,ns.
+
+Our simulations of the Dish response only extend to $\approx 300$\,ns, however, we wish to understand the impact of reflections on the frequency dependent gain of an interferometer like HERA at comoving scales of $\approx 0.1-0.5$\,$h$Mpc$^{-1}$, corresponding to the delays between 180 and 900\,ns at $z=8$, extending beyond our simulations range.
+To extrapolate out to higher delays, we assume that the response function is dominated by reflections between the feed and the dish.
+This is due to the fact that when we extend our filter bandwidth to between $50$ and $250$\,MHz and use a hamming window (which has higher resolution), we observe lobe-like structures at delays beyond $100$\,ns with a periodicity of $30$\,ns, which corresponds to the round-trip light travel time between the feed and the dish.
+In addition, the long term falloff appears as a line on a linear-log plot (Fig.~\ref{fig:Simulations}), indicating that the kernel follows an exponential which we now show is indicative of reflections.
+We do so by adopting the notation of \citep{Patra:2015}.
+We let $\Gamma_d$ represent the reflection coefficient of the Dish vertex and $\Gamma_f$ represent the reflection coefficient of the feed.
+An electromagnetic wave incident on the feed, at $t=0$, is accepted with amplitude $(1-\Gamma_f)$.
+The reflected component travels back to the dish and acquires an amplitude of $(\Gamma_f \Gamma_d)$ before returning at time, $\tau_d$ later where $(1-\Gamma_f)$ will be accepted and so forth.
+The time dependent voltage at the feed from these reflections is thus
+\begin{equation}
+\widetilde{v}_r(t) = \sum_m \left( \Gamma_f \Gamma_d \right)^m \widetilde{s}(t-m \tau_d)
+\end{equation}
+Hence
+\begin{equation}
+\widetilde{r}_r(\tau) = \sum_m \left( \Gamma_f \Gamma_d \right)^m \delta_D(\tau-m\tau_d)
+\end{equation}
+Since the number of reflections, $m=t/\tau_d$, than we can write the long-term delay response in discrete form as 
+\begin{equation}
+\widetilde{r}_n \approx (\Gamma_f \Gamma_d)^{n d\tau/\tau_d}
+\end{equation}
+which is a power law. We thus model our discrete voltage response beyond the times sampled by our simulations as a power law
+\begin{equation}
+\widetilde{r} = A X^{(\tau/30\text{ns})} 
+\end{equation}
+We plot the best power-law fit as a dashed line inf Fig~\ref{fig:SimulationsCompare}.
+%We fit our voltage response function and power-kernel to this function, finding a best fit model for the voltage kernel of $A\approx0.95$,$X \approx 0.18$, and $Y\approx 0.58$.
+The large $Y$ is unrepresentative of the feed reflection coefficient which has been simulated and measured to be $\approx 0.1$ for a head-on EM wave, suggesting that the reflections are arriving from the sides and potentially involve only a small component of the dish and feed.
+Plotting the die off for the feed reflection coefficient yields dramatically better performance than what is measured.
+If the reflections are indeed originating from the sides, and a small component of the dish and feed arrangement, further suppression may be achieved through modifying this component.
 
@@
 \subsection{The Delay Response at Zenith}
-In Fig.~\ref{fig:Comparison}, we show the filtered response function deconvolved from our electromagnetic simulations.
+In Fig.~\ref{fig:Kernels}, we show the filtered response function deconvolved from our electromagnetic simulations.
 The response of the dish rapidly dies off as a function of time.
@@
 \end{equation}
-Applying this transformtion to $S_{11}(f)$ and taking a DFT into the time domain over a band of $100-200$\,MHz, we obtain a measurement based estimate of the dish response function at zenith which is plotted in Fig.~\ref{fig:Comparison} alongside our simulation result.
-The general trends of the two two lines are in excellent agreement though the phases of the reflections at large time scales are $\approx 10$\,ns out of phase.
+Applying this transformtion to $S_{11}(f)$ and taking a DFT into the time domain over a band of $100-200$\,MHz, we obtain a measurement based estimate of the dish response function at zenith which is plotted in Fig.~\ref{fig:Kernels} alongside our simulation result.
+The general trends of the two two lines agree within $\sim 1-3$\,dB.
 As the long term delay structure of the delay response determines to what extent foregrounds leak out of the wedge, our simulations verify our measurement of the HERA dish's key performance feature.
-\begin{figure}[h!]
-\includegraphics[width=.5\textwidth]{figures/compareSimToDataNormalized.pdf}
-\caption{The response function deconvolved from our simulation (blue line) compared to the response function estimated from reflectometry measurements described in \citep{Patra:2015}.
-Our simulations are in good agreement with the reflectometry results, dropping below $-60$\,dB at $180$\,ns.
-Since the foregrounds are $\approx 10^6$ times larger than the signal, the necessary attenuation of zenith emission is obtained after $\approx 0.1$\,$h$Mpc$^{-1}$.}
-\label{fig:Comparison}
-\end{figure}
-\subsection{The Delay Response of the Sidelobes}
- After observing decent agreement between simulations and data, we now use our time-domain simulations to probe the side-lobe structure of the dish which are currently inaccessible to our experimental setup.
-Understanding the delay structure of the sidelobes is critical for several reasons.
-First, the sidelobes represent the largest delays occupied by foregrounds, hence the closest to the EoR window which we wish to keep foreground-free.
-While spectral leakage of sources at zenith may place them somewhere within the wedge, any spectral structure in the sidelobes is guaranteed to place these sources directly inside of the window.
-Second, the forshortening of diffuse structure near the horizon due to wide-field projection effects leads to a significant amount of foreground power entering at these delays, generally making them the most contaminated region of the wedge outside of the central lobe and leading to the so called ``pitchfork" \citep{Thyagarajan:2015a,Thyagarajan:2015b}.
 
- We fist attempt to explore the Dish sidelobe structure by running high resolution spatial beam maps {\bf Rich fill in details of running 2D beam simulations}.
-However, comparison between individual frequency channels in both CST and FEKO indicates numerical precision errors {\bf Show a figure of an attempted beam and frequency artifacts at zenith.}
+\subsection{Comparison with the power kernel of the PAPER antenna element}
+We next compare the spectral characteristics of the HERA dish to the PAPER antenna element.
+The PAPER antenna consists of a sleeved dipole element element identical to the one inside of the HERA feed.
+However, rather than being suspended over a dish which greatly enhances the effective collecting area of the antenna, the dipole is placed facing upwards above a rectangular skirt structure that is designed to minimize spectral structure.
+Comparing the relative performances of these two configurations is important since by suspending the dipole upside down over a dish, HERA is potentially trading achromaticity for collecting area.
+Here we comment this tradeoff.
+In order to perform a comparison, we run an identical plane wave simulation of the PAPER dipole element and obtain the power kernel which is shown in Fig.~\ref{fig:Kernels}.
+The striking difference between the PAPER and HERA elements is that the PAPER kernel lacks the transition to a shallow falloff at $\sim 100$\,ns which we should expect given that the long term falloff is likely due to feed-dish reflections.
+{\bf I am here!}
+%\begin{figure}
+%\includegraphics[width=0.5\textwidth]{figures/compareSidelobesNormalized.pdf}
+%\caption{The modulus square of the voltage responses of the HERA dish to plane waves incident from zenith (blue line) along with $20^\circ$,$25^\circ$, and $30^\circ$ off-zenith along the NS line.
+While the sidelobes are suppressed to $\approx 20-25$\,dB at zero delay, they come within $5$\,dB of the zenith response at longer delays which can lead to the level of leakage for a soruce in the sidelobes being comparable to the leakage of a source from zenith.
+The fact that the sidelobes occupy a much larger solid angle with only moderate supression at $\sim 100$\,ns coupled with their proximity to the horizon, suggests that they will dominate supra-horizon emission.}
+%\end{figure}
 
-\section{The Effect of the HERA dish Chromaticity on Foreground Leakage and Sensitivity}\label{sec:Foregrounds}
+\section{The Effect of the HERA dish Chromaticity on Foreground Leakage and Sensitivity}\label{sec:Sensitivity}
+Having a thorough understanding of how the chromatic beam of the HERA dish leaks foregrounds into higher delays and a decent picture of the relevant voltage response of the dish itself, we are now in a position to explore the impact of the Dish's performance on the leakage of foregrounds beyond the wedge, and into the EoR window.
+Beyond the delay kernels considered in this paper and \citep{Patra:2015}, the extent of leakage will depend both on the angular structure of the primary beam, which is established in \citep{Neben:2015b} and the model of the foregrounds themselves.
+In this section, we investigate the amplitude of foreground leakage as a function of delay given an angular primary beam model and our simulation of the delay structure of the dish (\S~\ref{ssec:Leakage}).
 
-\subsection{Simulating Foreground Visibilities with the Spectral Structure of the HERA Dish.}
+Spectral leakage due to the chromaticity of the dish will cause large-scale LoS Fourier modes to be contaminated by foregrounds and hence inaccessible to the foreground filtering approach that HERA will employ.
+Since the signal-to-noise ratio is maximized at the smallest $k$ values, the loss of these modes will reduce the significance of the power spectrum detection and negatively impact the overall bottom line of the science that HERA can accomplish.
+We explore the impact of HERA's intrinsic beam chromaticity on science using the Fisher matrix formalism in \S~\ref{ssec:Science}.
 
-\subsection{How Deep Can we Clean?}
-The level of foreground subtraction possible depends on the number of time steps and redundant baselines that are averaged before performing the cleaning step.
+\subsection{The Impact of the HERA Beam Chromaticity on Foreground Contamination}\label{ssec:Leakage}
+
+Given the HERA dish chromaticity, what Fourier modes will still be accessible with the delay filtering technique?
+To answer this question, we combine our extrapolated simulations of the HERA dish's spectral structure with simulations of foregrounds.
+The foreground simulations are described fully in \citep{Thyagarajan:2015c} but for the readers convenience we briefly describe them here.
+
+Our foreground model consists of two major components: diffuse synchrotron emission from our Galaxy whose structure is described by the Global Sky Model (GSM) of \citet{deOliviaCosta:2008} and a population of point sources sourced by radio loud AGN which combines the NRAO Sky Survey (NVSS) \citep{Condon:1998} at 1.4\,GHz, the Sydney University Mologolo Sky Survey (SUMMS) \citep{Bok:1999} at 843\,MHz, and extrapolate point source fluxes to the observed $100$-$200$\,MHz band using a spectral index of $\langle \alpha \rangle=-0.83$ determined in \citet{Mauch:2003}.
+Visibilities are computed from the diffuse and point source models assuming the achromatic HERA beam computed at $150$\,MHz and described in \citep{Neben:2015c}.
+We compute two sets of visibilities: one in which the spectral structure of the dish is assumed to be completely flat, and another in which the beam is multiplied by the Dish's frequency dependent gain at zenith.
+While this model assumes incorrectly that the frequency evolution of the primary beam is identical along all lines of sight, the majority of power enters at the beams point of maximal gain (zenith) and observations of autocorrelations which reflect the angular average of the frequency dependence of all lines of sight agree well with our simulations at zenith \citep{Patra:2015}.
+
+The foreground filtering procedure employed by PAPER and HERA involves delay transforming the visibilities on a short time-scale cadence and performing a 1d delay CLEAN where the deconvolution is permitted to discover and subtract foregrounds within the horizon to horizon delay.
+Since we want to avoid CLEANing noise, the level of foreground subtraction possible by this procedure is limited by the thermal noise level on the visibility, which in terun depends on the number of time steps and redundant baselines that are averaged before performing the cleaning step.
+In this work, we assume that each visibility is cleaned independently with a two minute CLEANing cadence which corresponds approximately to the time over which HERA's short baselines are coherent.
 The standard deviation on the real and imaginary part of a single delay transformed visibility is given by \citep{Morales:2004}
@@
 In order to avoid subtracting noise, we assume that cleaning is performed down to $5\,\sigma$.
-In Fig.~\ref{fig:Cleaning}, we see that cleaning to $5\,\sigma$
+In Fig~\ref{fig:Cleaning} we compare the delay transform of visibilities before and after cleaning on a two minute cadence at the LST of 4 hours.
+While cleaning is able to remove structure within the horizon, it does not reduce any of the power associated with the foreground induced by the chromaticity of the dish.
+
+To form estimates of the 21\,cm power spectrum, we split each visibility into BlackmanHarris windowed sub-bands centered at redshift intervals of $\Delta z = 0.5$ and each with an equivalent bandwidth of $10\,MHz$, corresponding to the redshift interval over which the statistics of the brightness temperature fluctuations are expected to be stationary.
+For each windowed interval, we use the flat sky approximation and  Fourier transform in frequency, square, and multiply by a set of prefactors to obtain a power spectrum estimate \citep{Parsons:2014},
+\begin{equation}\label{eq:PS}
+\widehat{P}({\bf k}) = \left( \frac{2 k_B}{\lambda^2} \right)^2 \frac{X^2 Y}{B \Omega_{pp}} | \widetilde{V}({\bf u}) |^2.
+\end{equation}
+Here, $\lambda$ is the central wavelength of the observation, $k_B$ is the Boltzmann constant, $B$ is the bandwidth of the Fourier transform, and $\Omega_{pp}$ is the integrated solid angle of the primary beam squared.
+$X$ is a linear factor converting between $uv$ wavelengths and $k_\perp$, and $Y$ is a linear factor converting between $k_\parallel$ and the Fourier dual to frequency, $\eta$.
+
+A drift scan instrument, HERA will be capable of observing the sky at any LST within the strip declination that passes through its primary beam.
+To form a final power spectrum estimate, it is expected to perform an average over the power spectrum estimates it obtains through equation~\ref{eq:PS} for each LST independently.
+It is well documented that foreground power is maximized over certain LST ranges \citep{Thyagarajan:2015a}, hence such an estimate will either filter or weight appropriately the LSTs in which foreground power is maximized.
+\citet{Thyagarajan:2015c} focuses on the optimal weighting and selection of LST bins in forming a power spectrum estimate.
+For the purpsoes of our analysis, we focus on a single, relatively clean LST of 4 hours which includes the coldest part of the sky.
 
 \begin{figure}
-\includegraphics[width=.5\textwidth]{figures/cleaning_noise.pdf}
+\includegraphics[width=.5\textwidth]{figures/cleaning_noise_Nithya.pdf}
 \caption{The absolute magnitude of a delay transformed 14-meter baseline (blue line) compared to the same visibility (green line) contaminated by reflections at the level observed in the HERA dish design.
@@
 The reflections in the dish lead to extensive winged structures that bleed into the EoR window and are well below the thermal noise level.
-All data in this plot are obtained from a $100$\,MHz bandwidth centered at $150$\,MHz.}
+All data in this plot are obtained from a $100$\,MHz bandwidth centered at $150$\,MHz.
+Vertical dashed lines indicate the horizon delays of the baseline.}
 \label{fig:Cleaning}
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=.5\textwidth]{figures/resid_5sigma_compare.pdf}
-\caption{The delay transformed power spectra of foregrounds with (blue line) and without (green line) contamination from reflections in the dish.
-The residuals of these foregrounds, cleaned to $5\,\sigma$ after 2 minutes of integration, are plotted with (red dashed line) and without (cyan dashed line) dish reflections.
-We compare to the amplitude of the 21\,cm power spectrum (solid black line).
-Foreground contamination, leaked by reflections, extends out to $k_\parallel \approx 0.25$\,$h$Mpc$^{-1}$.
-The signals plummet to zero at $k=0$ is an artifact of the spatial extent of the simulation which does not probe extremely fine scales.}
-\label{fig:SignalCompare}
-\end{figure}
+In Fig.~\ref{fig:SignalCompare} we compare the levels of the LST averaged foregrounds and cleaning residuals with and without the chromaticity of the dish for the redshifts between $7$ and $10.5$.
+Between the redshifts of $7$ and $8.5$, the residuals with and without the chromaticity of the dish drop below the level of the 21\,cm signal below $k \approx 0.12-0.15$\,$h$Mpc$^{-1}$.
+At $z = 8.5$, at the band center, where we found the reflections to be most severe, the beam chromaticity extends foreground contamination in excess of the signal out to $k \approx 0.22$\,$h$Mpc$^{-1}$.
+As we move to progressively higher redshift, the fixed frequency interval corresponding to $\Delta z = 0.5$ decreases as $(1+z)^{-2}$ while the foregrounds themselves also become brighter.
+The power spectrum we use here also has also reached its maximum $z=8.5$ where $50\%$ reionization takes place.
+For these reasons, the $k_\parallel$ at which the foregrounds with and without beam chromaticity fall below the signal increase with redshift, falling below the between $k=0.17$ and $k=0.22$\,$h$Mpc$^{-1}$ out to $z=10.5$.
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{figures/ps_compare_nithya_lst4hr_1024ch_7p3ew_12p6ns.pdf}
+\caption{The power spectrum computed from the delay transform of a 14.6 meter baseline in equation~\ref{eq:PS} with (solid green line) and without (solid blue line) the presence of reflections in the HERA dish.
+The residuals after cleaning within the dashed black lines down to three times the level of thermal noise after 20 minutes of integration with (dashed cyan) and without (red dashed) the dish chromaticity are also plotted.
+We find that for this short baseline, clean residuals are on a similar level as the 21\,cm signal (solid black line), indicating that a redesign of the array with fewer short baselines may be necessary to maximize its sensitivity on foreground free modes.}
+\label{figure:shortBaseline}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{figures/ps_compare_nithya_lst4hr_1024ch_14p6ew_25p3ns.pdf}
+\caption{The same as Fig.~\ref{fig:shortBaseline} except now for a 29.2 meter baseline.
+We see that the level of foregrounds is down relative to our 14.6 meter baseline by two orders of magnitude, likely due to the fact that we are now outside of the region with significant contamination from the Galaxy.
+The presence of reflections tends to extend the $k_\parallel$ at which foregrounds drop below the level of the signal between $k_\parallel=0.15$\,$h$Mpc$^{-1}$ and $k_\parallel=0.22$\,$h$Mpc$^{-1}$ with the most severe contamination occurring at the $z=8.5$ subband where the reflections where observed to be worst in Fig.~\ref{fig:KernelsSubbands}.
+}
+\label{figure:shortBaseline}
+\end{figure*}
 
 \subsection{The Implications of Dish Reflections on EoR Science}
-Since the amplitude of the 21\,cm signal is maximal at smaller $k$ values, a loss of large scale signal out to $0.25$\,$h$Mpc$^{-1}$ will eliminate some of the power spectrum modes that HERA will have the greatest SNR on, impacting our overall sensitivity.
-We address the change in SNR and its implications on HERA's ability to place constraints on reionization parameters in this section, using the Fisher Matrix Formalism.
+The primary goal 21\,cm EoR observations is to obtain information about the nature of the sources that drove reionization.
+Since the amplitude of the 21\,cm signal is maximal at smaller $k$ values, a loss of large scale signal due to foreground leakage eliminates the the modes that HERA would otherwise have the greatest signal to noise detections, impacting our overall sensitivity and its ability to derive this information.
+In this section, we estimate the impact of foreground leakage on HERA's sensitivity along with its ability to determine the astrophysics of reionization.
+We do so using the Fisher Matrix formalism.
+The Fisher Matrix allows us to forecast the covariances and errors on reionization parameters given errors on power spectrum observations due to the uncertainties caused by thermal noise which is in turn determined by the $uv$ coverage and observing time of the interferometer.
+The covariance between the parameters of some model ${\bf \theta}$ is given by the inverse of the Fisher matrix, ${\bf F}$ which for Gaussian and independently determined power spectrum bins may be written approximately as \citep{Pober:2014,EwallWice:2015a},
+\begin{equation}\label{eq:Fisher}
+F_{ij} \approx \sum_{k,z} \frac{1}{\sigma^2(k,z)} \frac{\partial \Delta^2(k,z)}{\partial \theta_i} \frac{\partial \Delta^2(k,z)}{\partial \theta_j},
+\end{equation}
+where $\Delta^2(k,z)$ is the power spectrum amplitude for some $k-z$ bin and $\sigma^2(k,z)$ is the variance of the power spectrum estimate in that bin due to thermal noise and cosmic variance \citep{Beardsley:2013}.
+
+ we use the publicly available {\tt 21cmFAST} code \citep{Mesinger:2011} which generates realizations of the 21\,cm brightness temperature field using the excursion set formalism of \citet{Furlanetto:2004}.
+We employ a popular three parameter model of reionization \citep{Mesinger:2012,Pober:2014,Greig:2015,Liu:2015} with the following variables
+\begin{itemize}
+\item ${\bf \zeta}$: The ``ionization efficiency" is defined in the \citep{Furlanetto:2004} excursion formalism to be the inverse of the mass collapse fraction necessary to ionize a region and is computed from a number of other physical parameters such as the fraction of collapsed baryons that form stars and the UV photon escape fraction.
+Because $\zeta$ acts as an efficiency parameter, its primary affect is to change the timing of reionization.
+We choose a fiducial value of $\zeta=20$, though its possible values range anywhere between $5$ and $50$.
+\item ${\bf R_\text{mfp}}$: The presence of Lyman limit systems and other potential absorbers within HII regions causes UV photons to have a mean free path denoted by $R_\text{mfp}$.
+In the {\tt 21cmFAST} framework, HII regions cease to grow after reaching the radius of $R_\text{mfp}$, primarily impacting the morphology of the signal.
+We choose a fiducial value of $R_\text{mfp}=15$\,Mpc which is in line with recent simulations accounting for the subgrid physics of absorption \citep{Sobacchi:2014}.
+\item ${\bf T_\text{vir}^\text{min}}$: The minimal mass of dark matter halos that hosted ionizing sources.
+While in principle, halos with virial temperatures as small as $10^2$\,K are though, in principle, to be able to form stars, thermal and mechanical feedback have been seen to raise this limit to as high as $10^5$\,K.
+We choose a fiducial value of $T_\text{vir}^\text{min} = 1.5\times 10^4$\,K which is set by the atomic line cooling thresshold.
+\end{itemize}
+In order to account for the degeneracies in the power spectrum between heating from X-rays and reionization from UV photons, we also marginalize over three additional parameters that describe the impact of heating from early X-ray luminous sources as explored in \citep{EwallWice:2015b}.
+These are the X-ray heating efficiency $f_X$, the maximal energy of X-ray photons that are self absorbed by the ISM of early galaxies, $\nu_\text{min}$, and the spectral slope, $\alpha$ which are taken to have fiducial values of $1$,$0.3$\,keV, and $-1.2$ respectively.
+We choose to parameterize our model in terms of the fractional differences of each parameter from their fiducial values so that, for example, $\theta_\zeta = (\zeta - \zeta_\text{fid})/\zeta_\text{fid}$ and compute the derivatives in equation~\label{eq:Fisher} by performing a linear fit to realizations of the 21\,cm power spectrum calculated by {\tt 21cmFAST} at $\theta_i= \pm 10^{-2}, \pm 5\times 10^{-2}, \pm 10^{-1}$,and $ \pm 2 \times 10^{-2}$.
+
+What about $\sigma^2(k,z)$?
+$\sigma^2$ represents the noise on each 1 dimensional power spectrum estimate.
+For each measurement in the $uv$ plane, the standard deviation of a power spectrum measurement is given by the direct sum of sample variance and thermal noise \citep{McQuinn:2006} which in turn depends on the primary beam of the instrument and the time spent sampling each $uv$ cell.
+For our analysis, we assume that the $uv$ plane is sampled by circular apertures with effective areas of $75$\,m$^2$ and that $\tau({\bf k})$ is determined by by a drift scan in which baselines are integrating coherently on each $uv$ cell for $\approx 20$\,minutes.
 
@@
 
-\begin{figure}
-\includegraphics[width=.5\textwidth]{figures/reionization_triangle_compare.pdf}
-\caption{95\% confidence interfals with and without reflections.
-The primary effect of a large minimal delay accessible is that  the ``knee" which is the primary lever on $R_\text{mfp}$ becomes inaccessible at low redshift.
-Since the comoving minimal $k$ corresponding to a minimal delay becomes smaller at higher redshift, EoX measurements do improve constraints on $R_\text{mfp}$.
-}
-\end{figure}
-
-\begin{figure*}
-\includegraphics[width=\textwidth]{figures/sigmaVsZ.pdf}
+\begin{figure*}[h!]
+\includegraphics[width=\textwidth]{figures/sigmaVsZ_reionization.pdf}
 \caption{Fractional Errors on reionization and heating parameters as a function of maximal observed redshift.}
@@
 
-\begin{figure}
-\includegraphics[width=\textwidth]{figures/triangle_hera331.pdf}
+\begin{figure}[h!]
+\includegraphics[width=.5\textwidth]{figures/reionization_triangle_compare_v1.pdf}
 \caption{95\% confidence regions with and without reflections assuming that observations are taken over the redshifts between 5 and 25 are observed.}

### 2016-01-13 ForegroundSimulations/ms.tex

@@
 Patra~et~al.~2015 (submitted) and Ewall-Wice~et~al.~2015 (submitted) discuss the measured and simulated reflections between a dish and its feed.
+We provide a related discussion by estimating the attenuation in power required to keep the foreground power reflected between adjacent antennas below the expected EoR H{\sc i} signal level for the different models of power patterns used in our study.
+
+The effect of reflections it to shift the measured foreground power to higher modes in $\tau$ (or equivalently in $k_\parallel$) and thus cause further contamination in these higher $k_\parallel$ modes which are considered sensitive for EoR H{\sc i} signal detection.
+Here we estimate the attenuation required at specific $k_\parallel$ modes of interest to contain reflected foreground power between antennas below expected EoR H{\sc i} power, both corresponding to a 14.6~m antenna spacing.
+
+We define the required attenuation as the ratio: 
+\begin{align}
+  \Gamma_{k_\parallel}(\tau) &= \frac{P_\textrm{H{\sc i}}(k_\parallel)}{P_\textrm{FG}(k_\parallel - \frac{\dif k_\parallel}{\dif \tau}\,\tau)},
+\end{align}
+where, $P_\textrm{H{\sc i}}(k_\parallel)$ is the EoR H{\sc i} power spectrum for the chosen antenna spacing, $P_\textrm{FG}(k_\parallel)$ is the foreground delay power spectrum obtained with a Blackman-Harris window function applied over the full band of the three uniquely oriented 14.6~m antenna spacings further averaged over a 0--12 hr LST range and over both positive and negative $k_\parallel$ modes, $\tau$ is the delay caused by reflections, and $\dif k_\parallel/\dif \tau$ is the {\it jacobian} in the transformation of $\tau$ to $k_\parallel$.
+
+Fig.~\ref{fig:fg-reflections} shows $\Gamma_{k_\parallel}(\tau)$ (in dB) for selected $k_\parallel$ at 0.08~$h$~Mpc$^{-1}$ (left), 0.1~$h$~Mpc$^{-1}$ (middle), and 0.12~$h$~Mpc$^{-1}$ (right) as a function of delays due to reflections from other antenna spacings.
+The light, medium and dark shaded curves show $\Gamma_{k_\parallel}(\tau)$ for achromatic, {\it Airy}, and chromatic antenna power patterns respectively.
+These curves set an upper limit to the reflected foreground power below the EoR H{\sc i} signal power as a function of delays caused by antenna-to-antenna reflections.
+It is noted that a chromatic simulated power pattern sets the most severe upper limit in all three chosen $k_\parallel$ for delays $\tau < 80$~ns (left), $\tau < 120$~ns (middle), and $\tau < 160$~ns.
 
@@
 \end{figure*}
+
+The required attenuation is also a sensitive function of the chosen $k_\parallel$ mode.
+For instance, at $k_\parallel=0.08\,h$~Mpc$^{-1}$, the reflections with delays 70~ns require to be attenuated by at $\gtrsim 85$~dB for the simulated power pattern, $\gtrsim 82$~dB for the {\it Airy} pattern, and $\gtrsim 70$~dB for the achromatic pattern.
+However, at $k_\parallel=0.1\,h$~Mpc$^{-1}$ for the same delay of reflection, the requirement on attenuation is lowered to $\gtrsim 75$~dB, $\gtrsim 30$~dB and $\gtrsim 22$~dB respectively.
+If the chosen $k_\parallel$ is instead 0.12~$h$~Mpc$^{-1}$, the required attenuation is further relaxed to $\gtrsim 60$~dB, $\gtrsim 15$~dB and $\gtrsim 15$~dB respectively.
+This further reinforces the significance of reducing the chromaticity of the antenna power pattern to further relax the constraint on the system to achieve the attenuation required to contain the reflected foreground power from other antennas from contaminating the sensitive EoR H{\sc i} signal modes in the {\it EoR window}.
 

### 2016-01-13 DishSimulations/paper/DishSimulationsPaper_v1.tex
small change to paper

@@
 
-In Fig.~\ref{fig:SignalCompare} we compare the levels of the LST averaged foregrounds and cleaning residuals with and without the chromaticity of the dish for the redshifts between $7$ and $10.5$.
-Between the redshifts of $7$ and $8.5$, the residuals with and without the chromaticity of the dish drop below the level of the 21\,cm signal below $k \approx 0.12-0.15$\,$h$Mpc$^{-1}$.
-At $z = 8.5$, at the band center, where we found the reflections to be most severe, the beam chromaticity extends foreground contamination in excess of the signal out to $k \approx 0.22$\,$h$Mpc$^{-1}$.
-As we move to progressively higher redshift, the fixed frequency interval corresponding to $\Delta z = 0.5$ decreases as $(1+z)^{-2}$ while the foregrounds themselves also become brighter.
-The power spectrum we use here also has also reached its maximum $z=8.5$ where $50\%$ reionization takes place.
-For these reasons, the $k_\parallel$ at which the foregrounds with and without beam chromaticity fall below the signal increase with redshift, falling below the between $k=0.17$ and $k=0.22$\,$h$Mpc$^{-1}$ out to $z=10.5$.
+Computing the power spectrum, we inspect
 

### 2016-01-13 DishSimulations/paper/DishSimulationsPaper_v1_old.tex

--- 2016-01-13 DishSimulations/paper/DishSimulationsPaper_v1.tex
@@
 In order to avoid subtracting noise, we assume that cleaning is performed down to $5\,\sigma$.
-In Fig~\ref{fig:Cleaning} we compare the delay transform of visibilities before and after cleaning on a two minute cadence at the LST of 4 hours.
+The CLEAN is applied  independently to each LST.
+In Fig~\ref{fig:Cleaning} we compare the delay transform of visibilities before and after cleaning on a two minute cadence.
 While cleaning is able to remove structure within the horizon, it does not reduce any of the power associated with the foreground induced by the chromaticity of the dish.
 
-To form estimates of the 21\,cm power spectrum, we split each visibility into BlackmanHarris windowed sub-bands centered at redshift intervals of $\Delta z = 0.5$ and each with an equivalent bandwidth of $10\,MHz$, corresponding to the redshift interval over which the statistics of the brightness temperature fluctuations are expected to be stationary.
+To form estimates of the 21\,cm power spectrum, we split each visibility into BlackmanHarris windowed subbands centered at redshift intervals of $\Delta z = 0.5$ and each with an equivalent bandwidth of $\Delta z = 0.5$, corresponding to the redshift interval over which the statistics of the brightness temperature fluctuations are expected to be stationary.
 For each windowed interval, we use the flat sky approximation and  Fourier transform in frequency, square, and multiply by a set of prefactors to obtain a power spectrum estimate \citep{Parsons:2014},
@@
 It is well documented that foreground power is maximized over certain LST ranges \citep{Thyagarajan:2015a}, hence such an estimate will either filter or weight appropriately the LSTs in which foreground power is maximized.
-\citet{Thyagarajan:2015c} focuses on the optimal weighting and selection of LST bins in forming a power spectrum estimate.
-For the purpsoes of our analysis, we focus on a single, relatively clean LST of 4 hours which includes the coldest part of the sky.
+To determine the LSTs to be included in our power spectra, we inspect the ratio between the power spectra foreground residuals after two minutes of cleaning and a model for the power spectrum of the 21\,cm signal for several baselines as a function of LST.
+We plot the ratio for one such baseline (at 14.6 meters, one from which the majority of HERA's sensitivity will be derived) in Fig.~\ref{fig:LSTs} and see that foreground power is at its worst during the transits of the galactic centers and anti-centers between LST of 8 and 20.
+In principle, one could form an average that weights inversely by foreground amplitudes allowing for very significant reduction in the overall foreground power, however such an approach also requires precise {\it a-priori} knowledge of the foregrounds which we will not assume here.
+Instead, we take a conservative approach and form LST averaged power spectra by taking an unweighted average over all LSTs excluding the highly contaminated region between 8 and 20 hours.
 
@@
 \begin{figure*}
-\includegraphics[width=\textwidth]{figures/ps_compare_nithya_lst4hr_1024ch_7p3ew_12p6ns.pdf}
-\caption{The power spectrum computed from the delay transform of a 14.6 meter baseline in equation~\ref{eq:PS} with (solid green line) and without (solid blue line) the presence of reflections in the HERA dish.
-The residuals after cleaning within the dashed black lines down to three times the level of thermal noise after 20 minutes of integration with (dashed cyan) and without (red dashed) the dish chromaticity are also plotted.
-We find that for this short baseline, clean residuals are on a similar level as the 21\,cm signal (solid black line), indicating that a redesign of the array with fewer short baselines may be necessary to maximize its sensitivity on foreground free modes.}
-\label{figure:shortBaseline}
+\centering
+\includegraphics[width=\textwidth]{figures/snr_estimates_subBands_Nithya_comovingDF.png}
+\caption{The ratio between the foreground power spectrum and the power spectrum of 21\,cm brightness temperature fluctuations on a single $14.6$\,m baseline for several different redshift subbands assuming two minutes of foreground cleaning and chromaticity of our simulated beam.
+Significant foreground contamination enters between 8 and 20 hours, hence we form LST averaged power spectra excluding this time interval (denoted by vertical dashed red lines).}
+\label{fig:LSTs}
 \end{figure*}
@@
 \begin{figure*}
-\includegraphics[width=\textwidth]{figures/ps_compare_nithya_lst4hr_1024ch_14p6ew_25p3ns.pdf}
-\caption{The same as Fig.~\ref{fig:shortBaseline} except now for a 29.2 meter baseline.
-We see that the level of foregrounds is down relative to our 14.6 meter baseline by two orders of magnitude, likely due to the fact that we are now outside of the region with significant contamination from the Galaxy.
-The presence of reflections tends to extend the $k_\parallel$ at which foregrounds drop below the level of the signal between $k_\parallel=0.15$\,$h$Mpc$^{-1}$ and $k_\parallel=0.22$\,$h$Mpc$^{-1}$ with the most severe contamination occurring at the $z=8.5$ subband where the reflections where observed to be worst in Fig.~\ref{fig:KernelsSubbands}.
-}
-\label{figure:shortBaseline}
+\centering
+\includegraphics[width=\textwidth]{figures/PS_estimates_subBands_Nithya_comovingDF_avgMask.pdf}
+\caption{The delay transformed power spectra of foregrounds with (blue line) and without (green line) contamination from reflections in the dish.
+The residuals of these foregrounds, cleaned to $5\,\sigma$ after 2 minutes of integration, are plotted with (red dashed line) and without (cyan dashed line) dish reflections.
+The power spectra are derived from averaging over all LST excluding 8-20 hours.
+We compare to the amplitude of the 21\,cm power spectrum (solid black line).
+For each redshift, we use an equivalent bandwidth (for a BlackmanHarris window) of the frequency range corresponding to $\Delta z = 0.5$.
+We find that over most subbands, the foreground leakage extended by the chromaticity of the dish is below $0.12$-$0.15$\,$h$Mpc$^{-1}$.
+However, in the center of the band, where the reflections are significantly pronounced, the foreground leakage does not pass below $\sim 10$\% the level of the signal until  $k_\parallel \approx 0.3$\,$h$Mpc$^{-1}$.}
+\label{fig:SignalCompare}
 \end{figure*}

### 2016-01-13 DishSimulations/paper/DishSimulationsPaper_v1.tex
added clarifictation on the central lobe of Fig 9. in the Dish Simulations paper

@@
 While the long term falloff from reflections is prominent between $130-160$\,MHz, it appears at a much lower level in the other two subbands which fall below the central subband by $\sim 20$\,dB at $\sim 300$\,ns.
-$k_\parallel$ values for each delay are computed at $150$\,MHz.}
+$k_\parallel$ values for each delay are computed at $150$\,MHz.
+The wider central lobe below 150\,ns for the subband gains is an artifact of the delay resolution of a smaller bandwidth.}
 \label{fig:KernelsSubbands}
@@
 
-Computing the power spectrum, we inspect
+Computing the power spectra, we inspect the amplitude of foregrounds given the chromaticity and angular pattern of the HERA dish for several different baselines of different lengths.
 

### 2016-01-14 DishReflectometry/GB_reflectometry_part2/plot_reflectometry.py
Moved Reflectometry_RB inside GB_reflectometry, added plot_dishfeed.py

@@ -10,7 +10,7 @@ def fromcsv(filename):
     return x[:,0]/1e9, x[:,1]
 
 for filename in sys.argv[1:]:
-    BASE = filename[:-len('.csv')]
+    BASE = filename[:-len('_DB.csv')]
     db_file = BASE + '_DB.csv'
     ph_file = BASE + '_P.csv'
 
@@ -22,9 +22,9 @@ for filename in sys.argv[1:]:
     #d = 10**(db/10) * np.exp(2j*np.pi*ph/360) # power
     d = 10**(db/20) * np.exp(2j*np.pi*ph/360) # 20 to put into voltage amplitude, not power
 
-    valid = np.ones(fq.size, dtype=np.bool) # use entire sampled band
+    #valid = np.ones(fq.size, dtype=np.bool) # use entire sampled band
     #valid = np.where(fq < .250) # restrict to HERA band
-    #valid = np.where(np.logical_and(fq < .2, fq > .1)) # restrict to PAPER band
+    valid = np.where(np.logical_and(fq < .2, fq > .1)) # restrict to PAPER band
     fq, d = fq[valid], d[valid]
     tau = np.fft.fftfreq(fq.size, fq[1]-fq[0])
     window = a.dsp.gen_window(fq.size, WINDOW)

### 2016-01-14 data/plot_fg.py

@@ -10,6 +10,7 @@ import sys, scipy, csv
 # 'eor_power' -- EoR power in power spectrum units and is an array of size n(bl) x n(eor_lags) x n(lst)
 
 npz = n.load(sys.argv[-1])
+print npz.files
 
 LST = 0
 
@@ -28,7 +29,7 @@ fg = n.average(fg[:3], axis=0)
 eor = n.average(eor[:3], axis=0)
 fg_mdl = n.where(fg > 1e7, fg, 0)
 
-for kpl_cut in [0.08, 0.1, 0.12][::-1]: # h Mpc^-1
+for kpl_cut in [0.08, 0.1, 0.12, 0.15][::-1]: # h Mpc^-1
     tau_cut = kpl_cut / dk_deta
     tau2_cut = n.argmin(n.abs(tau2 - tau_cut))
     SZ = eor.shape[0]

### 2016-01-15 DishSimulations/paper/DishSimulationsPaper_v1.tex

@@
 
-Computing the power spectra, we inspect the amplitude of foregrounds given the chromaticity and angular pattern of the HERA dish for several different baselines of different lengths.
+Computing the power spectra, we inspect the amplitude of foregrounds given the chromaticity and angular pattern of the HERA dish for several different baselines.
+We first inspect a $14.6$ meter baseline in Fig.~\ref{fig:shortBaseline} and find that foregrounds contaminate a significant fraction of modes outside of the horizon for many redshifts.
+Inspecting a longer 29.2 meter baseline in Fig.~\ref{fig:longBaseline}, we find that significant regions of the visibility are foreground free.
+In both baselines, we find that the residuals after cleaning tend to be at similar levels except at the subband centered at $z=8.5$ (150\,MHz), in which foreground residuals remain above the signal level out to $k_\parallel=0.3$\,$h$Mpc$^{-1}$.
+
+To get a more global view of which baselines are significantly affected by foreground leakage, I we plot the median of the ratio between the 21\,cm power and foreground leakage between $k=0.15$\,$h$Mpc$^{-1}$ and $k=1.00$\,$h$Mpc$^{-1}$ for a subset of the short HERA baselines and plot them in Fig.~\ref{fig:Medians}.
+For all redshifts investigated, the majority of the $14.6$ meter baselines show significant contamination from diffuse foregrounds.
+Additionally, EW baselines contain a significant degree of foreground residuals as noted in \citet{Thyagarajan:2015a}.
 
@@
 We find that for this short baseline, clean residuals are on a similar level as the 21\,cm signal (solid black line), indicating that a redesign of the array with fewer short baselines may be necessary to maximize its sensitivity on foreground free modes.}
-\label{figure:shortBaseline}
+\label{fig:shortBaseline}
 \end{figure*}
@@
 \label{figure:shortBaseline}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{figures/ps_compare_nithya_lst4hr_snrVbaselineMedian.pdf}
+\caption{The median of the ratio between foreground residuals with the chromaticity of the HERA primary beam between $k_\parallel=0.15$\,$h$Mpc$^{-1}$ and $k_\parallel=1.0$\,$h$Mpc$^{-1}$, the range of k values over which HERA will derive the majority of its sensitivity.
+We see that the shortest baselines tend to have relatively low signal to foreground ratios due to the presence of high amplitude Galactic synchrotron emission.}
+\label{fig:Medians}
 \end{figure*}

### 2016-01-19 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev1.tex

@@
 In this figure we perform the approximate conversion from delay $\tau$ to $k_\parallel$, which we plot as a second $x$-axis at the top of the plot.
-For these short baselines, $k_\parallel$ may be converted to $k$ by adding $k_\perp=0.005$ for the 14\,m baseline or $k_\perp=0.02$ for the 42\,m baseline in quadrature.
+For these short baselines, $k_\parallel$ may be converted to $k$ by adding $k_\perp=0.005$ for the 14.6\,m baseline or $k_\perp=0.02$ for the 42\,m baseline in quadrature.
 These numbers are small compared to the range of $k_\parallel$ plotted, and thus we interpret the $k_\parallel$ axis as simply the $k$ axis, and plot a 1D model power spectrum computed using 21cmFast \citep{21cmfast} as a dotted line for comparison.
@@
 \caption{Simulated foreground delay spectra using the HFSS beam at various LSTs (top panel).
-We plot the delay spectra at two LSTs spanning the range of possible horizon brightening for three different beam models.
-The maximum horizon brightening at the negative horizon occurs at 2$^\circ$ LST (middle panel), and the three beam models thus differ markedly in their predicted delay spectra near the horizon.
-In contrast, when the horizon brightening effect is smaller at 2$^\circ$ LST, the foreground delay spectra from all three beams agree much more closely.}
+We also plot the delay spectra at two LSTs spanning the range of possible horizon brightening for three different beam models.
+The maximum horizon brightening at the positive horizon occurs close to 0$^\circ$ LST (middle panel), and the three beam models thus differ markedly in their predicted delay spectra near the horizon.
+In contrast, when the horizon brightening effect is smaller at 60$^\circ$ LST, the foreground delay spectra from all three beams agree much more closely.}
 \label{fig:delayspec}
@@
 Dashed lines mark zenith angles 20$^\circ$, 40$^\circ$, 60$^\circ$, 80$^\circ$.
-These plots confirm that the large negative delay peak at the 2$^\circ$ LST is due to the center of the galaxy just above the horizon.
+These plots confirm that the large negative delay peak at the 0$^\circ$ LST is due to the center of the galaxy just above the horizon.
 In contrast several hours later, the galactic center is fully below the western horizon, leaving only a slight brightening near the eastern horizon due to the weaker galactic anticenter.
@@
 
-NEED TO REVISE THIS PARAGRAPH FOR NITHYA'S SIMULATIONS, ALSO COMMENT ON THE CST-HFSS CURVE
 How much do the predicted foreground power spectra differ between the three model dish power patterns?
-Figure \ref{fig:delayspec} (middle panel) shows the simulated delay spectra for all three beams at $2^\circ$ LST, when the horizon brightening is worst.
-All three delay spectra agree out to delays of 10--20\,ns on the 14\,m baseline and 30--40\,ns on the 40\,m baseline.
-These numbers suggest that the beams track each other fairly well out to 15--20$^\circ$ from zenith, beyond which they diverge.
+Figure \ref{fig:delayspec} (middle panel) shows the simulated delay spectra for all three beams at $0^\circ$ LST, when the horizon brightening is worst.
+Both numerical models agree out to delays of roughly 20\,ns on the 14.6\,m baseline and 50\,ns on the 43.8\,m baseline.
+These numbers suggest that the beams track each other fairly well out to 25$^\circ$ from zenith, beyond which they diverge.
 This is roughly what is observed in Figure \ref{fig:measuredbeamslices} (middle panel).
-At larger delays, especially near the negative delay horizon limit, all three model delay spectra diverge due to the significant edge brightening which effectively discriminates between these models.
+At larger delays, especially near the positive delay horizon limit, all three model delay spectra diverge due to the significant edge brightening which effectively discriminates between these models.
 The CST, HFSS, and Airy beams reach roughly -35\,dB, -38\,dB, and -50\,dB at the horizon (Figure \ref{fig:modelbeams}), consistent with the fact that the CST beam has the largest horizon brightening, followed by the HFSS beam, and then by the Airy beam.
@@
 
-In contrast, all three model agree much more closely when there is little or no edge brightening as in Figure \ref{fig:measuredbeamslices} (bottom panel) where we plot the delay spectra for all three beams for 62$^\circ$ LST.
-There is still a modest flattening off near the horizon on the 14\,m baseline and a slight peak on the 42\,m baseline due to the large solid angle near the horizon.
+In contrast, all three model agree much more closely when there is little or no edge brightening as in Figure \ref{fig:measuredbeamslices} (bottom panel) where we plot the delay spectra for all three beams for 60$^\circ$ LST.
+There is still a modest flattening off near the horizon on the 14.6\,m baseline and a slight peak on the 43.8\,m baseline due to the large solid angle near the horizon.
 However as the near horizon emission at this LST is roughly the same temperature as emission from everywhere else on the sky, the difference between the three beam models is greatly reduced.

### 2016-01-20 DishSimulations/paper/DishSimulationsPaper_v1.tex
updated dish simulations paper with new Fisher matrix scenarios

--- 2016-01-13 DishSimulations/paper/DishSimulationsPaper_v1.tex
@@
 Nipanjana Patra\altaffilmark{5},
-Thyagarajan Nithyanandan\altaffilmark{6},
+Nithyanandan Thyagarajan \altaffilmark{6},
 Jacqueline Hewitt\altaffilmark{1,2},
-Ali S. Zaki\altaffilmark{5},
-Bowman Judd\altaffilmark{6},
-Cheng Carina\altaffilmark{5},
+Zaki S. Ali\altaffilmark{5},
+Judd Bowman\altaffilmark{6},
+Carina Cheng\altaffilmark{5},
 Deboer David\altaffilmark{5},
@@
 The central lobe of the delay kernel is significantly wider due to the the wider window functions incurred by the reduced bandwidth, however, the shallow long-term falloff is only visible within the central $125-175$\,MHz band, indicating that long term reflections are isolated near $150$\,MHz and will not effect power spectrum measurements outside of the very center of our band.
+To further illustrate the observed isolation of fine frequency structure in the center of the bandpass, we fit the $10$\,MHz intervals of the absolute value of the simulated gains to a sixth order polynomial and compare the residuals in Fig.~\ref{fig:Residuals}.
+We find that the gain residuals on the sixth order fit are an order of magnitude greater over the $145-155$\,MHz subband than over any other frequency interval.
 
@@
 \end{figure}
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{figures/frequency_domain_residuals.pdf}
+\caption{Residuals on the absolute value of the gain over several subbands after fitting to a sixth order polynomial.
+Consistent with our findings in Fig.~\ref{fig:KernelsSubbands}, the fine frequency residuals in the 145-155\,MHz subband are over an order of magnitude greater than those in the other subbands.}
+\label{fig:Residuals}
+\end{figure*}
 
@@
 \begin{equation}\label{eq:PS}
-\widehat{P}({\bf k}) = \left( \frac{2 k_B}{\lambda^2} \right)^2 \frac{X^2 Y}{B \Omega_{pp}} | \widetilde{V}({\bf u}) |^2.
+\widehat{P}({\bf k}) = \left( \frac{2 k_B}{\lambda^2} \right)^2 \frac{X^2 Y}{B_{pp} \Omega_{pp}} | \widetilde{V}({\bf u}) |^2.
 \end{equation}
@@
 
-Computing the power spectra, we inspect the amplitude of foregrounds given the chromaticity and angular pattern of the HERA dish for several different baselines of different lengths.
+Computing the power spectra, we inspect the amplitude of foregrounds given the chromaticity and angular pattern of the HERA dish for several different baselines.
+We first inspect a $14.6$ and $29.2$ meter baseline in Fig.~\ref{fig:BothBaselines} and find that significant regions of the visibility are foreground free.
+In both baselines, we find that the residuals after cleaning tend to be at similar levels except at the subband centered at $z=8.5$ (150\,MHz), in which foreground residuals remain above the signal level out to $k_\parallel=0.23$\,$h$Mpc$^{-1}$.
+Several other baselines especially those oriented entirely in the E-W direction, which we do not show, contain up to two orders of magnitude greater foreground contamination as is noted in \citep{Thyagarajan:2015b}.
+In a real power spectrum analysis, these baselines would be down-weighted or discarded so that they do not bias our final estimate.
+
+The level of the foregrounds in Fig.~\ref{fig:BothBaselines} was derived with no attempt to apply inverse covariance weighting \citep{Parsons:2014,Ali:2015} or fringe rate filtering \citep{Parsons:2015}.
+In order to avoid biases in a maximum likelihood analysis that determines astrophysical and cosmological parameters from our power spectra, the foregrounds should ideally be below the anticipated level of thermal noise which is shown in \citep{Pober:2014} to be on the order of a few percent the anticipated level of the cosmological signal for the full HERA deployment.
+Hence, as long as we can suppress our foregrounds below 1-10\,\% the signal level, they should not interfere significantly with a maximum likelihood analysis.
+Thus, the residuals in Fig.~\ref{fig:BothBaselines} serve as a specification for any inverse covariance weighting pipeline which will need to suppress foregrounds by between a factor of $\sim 1-10$ to bring the worst contaminated regions below the level of the signal.
+Applications of inverse covariance filters in recent PAPER observations have yielded improvements at and above this level, hence our simulations show that even with the presence of beam chromaticity, HERA will be able to isolate foregrounds below below the level of thermal noise in most of the EoR window.
 
 \begin{figure*}
-\includegraphics[width=\textwidth]{figures/ps_compare_nithya_lst4hr_1024ch_7p3ew_12p6ns.pdf}
-\caption{The power spectrum computed from the delay transform of a 14.6 meter baseline in equation~\ref{eq:PS} with (solid green line) and without (solid blue line) the presence of reflections in the HERA dish.
+\includegraphics[width=\textwidth]{figures/ps_compare_nithya_bothBaselines.pdf}
+\caption{}
+\label{fig:BothBaselines}
+\end{figure*}
+
+%\begin{figure*}
+%\includegraphics[width=\textwidth]{figures/ps_compare_nithya_lst4hr_1024ch_7p3ew_12p6ns.pdf}
+%\caption{The power spectrum computed from the delay transform of a 14.6 meter baseline in equation~\ref{eq:PS} with (solid green line) and without (solid blue line) the presence of reflections in the HERA dish.
 The residuals after cleaning within the dashed black lines down to three times the level of thermal noise after 20 minutes of integration with (dashed cyan) and without (red dashed) the dish chromaticity are also plotted.
 We find that for this short baseline, clean residuals are on a similar level as the 21\,cm signal (solid black line), indicating that a redesign of the array with fewer short baselines may be necessary to maximize its sensitivity on foreground free modes.}
-\label{figure:shortBaseline}
-\end{figure*}
+%\label{fig:shortBaseline}
+%\end{figure*}
 
-\begin{figure*}
-\includegraphics[width=\textwidth]{figures/ps_compare_nithya_lst4hr_1024ch_14p6ew_25p3ns.pdf}
-\caption{The same as Fig.~\ref{fig:shortBaseline} except now for a 29.2 meter baseline.
+%\begin{figure*}
+%\includegraphics[width=\textwidth]{figures/ps_compare_nithya_lst4hr_1024ch_14p6ew_25p3ns.pdf}
+%\caption{The same as Fig.~\ref{fig:shortBaseline} except now for a 29.2 meter baseline.
 We see that the level of foregrounds is down relative to our 14.6 meter baseline by two orders of magnitude, likely due to the fact that we are now outside of the region with significant contamination from the Galaxy.
@@
 }
-\label{figure:shortBaseline}
-\end{figure*}
+%\label{figure:shortBaseline}
+%\end{figure*}
+
+%\begin{figure*}
+%\includegraphics[width=\textwidth]{figures/ps_compare_nithya_lst4hr_snrVbaselineMedian.pdf}
+%\caption{The median of the ratio between foreground residuals with the chromaticity of the HERA primary beam between $k_\parallel=0.15$\,$h$Mpc$^{-1}$ and $k_\parallel=1.0$\,$h$Mpc$^{-1}$, the range of k values over which HERA will derive the majority of its sensitivity.
+We see that the shortest baselines tend to have relatively low signal to foreground ratios due to the presence of high amplitude Galactic synchrotron emission.}
+%\label{fig:Medians}
+%\end{figure*}
 
@@
 \begin{figure}
-\includegraphics[width=.5\textwidth]{figures/sensitivity_comparison.pdf}
-\caption{Comparison between sensitivities with and without reflections.}
+\includegraphics[width=.5\textwidth]{figures/sensitivity_comparison_v2.pdf}
+\caption{A comparison between the sensitivity achieved by HERA at redshift $8.5$ with and without the presence of beam chromaticity due to the reflections studied in this work.
+We saw in Fig.~\ref{fig:BothBaselines} that with reflections, foregrounds exceed the signal level out to $k=0.2$\,$h$Mpc$^{-1}$ at $z=8.5$ which we assume are unusable, forcing us to ignore modes out to $350$\,ns beyond the horizon, leading to the sensitivity projected in the red curve.
+The absence of these reflections allows us to work within $250$\,ns of the horizon (green curve), leading to an increase in sensitivity by a factor of $\approx 1.5$.
+}
+\label{fig:Sensitivity}
 \end{figure}
@@
 \begin{figure*}[h!]
-\includegraphics[width=\textwidth]{figures/sigmaVsZ_reionization.pdf}
-\caption{Fractional Errors on reionization and heating parameters as a function of maximal observed redshift.}
+\includegraphics[width=\textwidth]{figures/sigmaVsZ_reionization_v2.pdf}
+\caption{Fractional Errors on reionization and heating parameters as a function of maximal observed redshift out to the low end of HERA's initial observing band at $z=12$.
+The presence of strong reflections contained within a small subband at $z=8.5$ has a minimal impact on our overall constraints on reionization parameters.
+If these reflections are not localized they can lead to a factor of two loss in sensitivity to some parameters such as $T_\text{vir}^\text{min}$.}
+\label{fig:Errors}
 \end{figure*}
@@
 \begin{figure}[h!]
-\includegraphics[width=.5\textwidth]{figures/reionization_triangle_compare_v1.pdf}
-\caption{95\% confidence regions with and without reflections assuming that observations are taken over the redshifts between 5 and 25 are observed.}
+\includegraphics[width=.5\textwidth]{figures/reionization_triangle_compare_v2.pdf}
+\caption{95\% confidence regions with and without reflections assuming that observations are taken over the redshifts between 7.5 and 10.
+The presence of the reflections leads to an increase in the major axes of these confidence regions by a factor of one to two.}
+\label{fig:Confidence}
 \end{figure}
 
+We have seen in Fig.~\ref{fig:BothBaselines} that the simulated chromaticity of the dish leaks foregrounds beyond the horizon to varying degrees depending on the subband with the worst leakage occuring at $z=8.5$ centered at 150\,MHz in which foregrounds exceed the signal out to $\sim 380$\,ns which for a $14.6$\,m baseline is $\approx 330$\,ns beyond the horizon.
+At all other redshifts, the leakage due to beam chromaticity only extends to $\approx 250$\,ns beyond the horizon.
+To determine the potential impact of our observed beam chromaticity on HERA's ability to constrain the astrophysics of reionization, we consider three different scenarios for beam chromaticity that capture a range of possibilities allowed by our simulation.
+
+\begin{itemize}
+\item {\bf Optimistic: The observed reflections are an artifact of the simulation.} It is possible that the long term reflections observed in the center of our gain are artifacts of our modeling and that effects such as dissipative effects due to unmodeled non-idealities in the geometry of the disk will allow reflected radio waves to be better absorbed or escape into space, suppressing these reflections.
+In our most optimistic scenario, we assume their absence in which case the foregrounds pass below the level of the signal at $240$\,ns beyond the horizon at all redshifts between $z=7$ and $10$, consistent with what is observed in the bands where the dish chromaticity is less severe or when it is not present at all.
+We do not consider the possibility that optimal inverse covariance weighting of the foregrounds  may actually decrease the minimal delays accessible to below the $250$\,ns above the horizon observed in our simulations.
+Hence, this scenario is actually somewhat conservative and certainly more pessimistic than the ones considered in \citep{Pober:2014,Greig:2015a,EwallWice:2015b}.
+
+\item {\bf Moderate: The Simulations accurately capture the chromaticity of the dish.} In this case, we assume that the reflections cause foregrounds to pass below the level of the signal at $250$\,ns except at redshift $8.5$ where they pass below the foregrounds at $350$\,ns.
+
+\item {\bf Pessimistic: The reflections are present in all sub-bands.} In this scenario, we assume that the spectral structure observed in the neighborhood of $150$\,MHz is present throughout the entire $100$-$200$\,MHz frequency range covered by HERA.
+While more pessimistic than anything we actually observe in our simulations, this scenario serves as a reasonable upper bound.
+
+\end{itemize}
+In Fig.~\ref{fig:Sensitivity}, we compare the level of $1\sigma$ thermal noise for our optimistic and moderate scenarios at $z=8.5$ to the amplitude of the 21\,cm signal.
+While the level of thermal noise monotonically increases with $k$, there is a small upturn at the smallest $k$ values due to an increase in sample variance caused by the knee like maximum in the 21\,cm power spectrum at $k \approx 0.1$\,$h$Mpc$^{-1}$ and the shrinking number of measurements within each 1d $k$-bin.
+Despite this upturn, the smallest $k$ modes are still the highest signal to noise measurements that HERA is expected to obtain, leading to a reduction in the maximal signal to noise ratio of $\approx 1.5$ and a reduction in the number of modes that the instrument is able to measure.
+
+Folding our calculations of thermal noise and the derivatives of $\Delta^2$ into equation~\ref{eq:Fisher} and inverting, we obtain the covariance matrix for model parameters from which we calculate $95\%$ confidence regions which we plot in Fig.~\ref{fig:Confidence}.
+The presence of reflections within a limited sub-band about $z=8.5$ leads to an almost neglible increase in the extent of our confidence intervals while the presence of the reflections across the entire band causes the length and width of our confidence ellipses to increase by a factor of $\approx 2$.
+The diagonal elements of our covariance gives us error bars on each parameter which we plot in Fig.~\ref{fig:Errors}.
+We see that similar to our confidence regions, the error bars on reionization parameters for our optimistic and moderate scenarios are nearly indestinguishable.
+In our worst case where reflections of a similar level as observed in the middle of our band are present everywhere, we see an increase in our error bars by a factor of $\approx 2$.
+
+The error bars on reionization parameters, even for our most optismtic model, are a factor of a few larger than the ``moderate" errors predicted in previous works using the Fisher Matrix such as \citet{Pober:2014}, \citet{EwallWice:2015a}, and \citet{Liu:2015a,Liu:2015b}.
+There are several reasons for this.
+Firstly, in our most optimistic scenario, we assumed that foregrounds cause the signal to be inaccessible below $250$\,ns beyond the edge of the wedge while in all previous works, a comoving $k$ of $k_\text{min}=0.1$\,$h$Mpc$^{-1}$, rather than a delay was used.
+In particular, this delay corresponds to a comoving $k\approx0.15$\,$h$Mpc$^{-1}$ at $z=8.5$, in significant excess of the values used in previous works.
+However, we do not consider the potential for inverse covariance techniques to further isolate foregrounds and potentially allowing us to work closer to the wedge than a naive Fourier transform.
+Because of this, our work is significantly more conservative than previous estimates.
+Secondly, previous studies assumed a fully illuminated HERA aperture, which for a $14$\,m dish predicts and effective area of $\approx155$\,m$^2$ at $150$\,MHz.
+Electromagnetic simulations and mapping of the primary beam of the HERA dish described in \citep{Neben:2015c} indicate are in good agreement that the effective area of the antenna element is actually $\approx 98$\,m$^2$ at $150$\,MHz which leads to an increase in the overall thermal noise levels by a factor of $\approx 1.5$.
+
 \section{Conclusions}
+In this paper, we have formally described the impact of instrumental chromaticity on foreground contamination of the 21\,cm signal.
+We have also used simulations of electromagnetic waves incident from zenith on the primary antenna element on HERA to determine the extent to which reflections and other frequency dependent structure might leak foregrounds into the EoR window.
+The results of our simulations of the zenith gain of the instrument are broadly consistent with data obtained using reflectometry described in \citep{Patra:2015} and can be summarized in the following points.
+\begin{itemize}
+\item The 14-m dish and inverted dipole feed configuration introduces reflections and, as a result, spectral structure, that is in excess of that observed in the antenna design for HERA's predecessor, PAPER.
+The dish design is intended to greatly increase array collecting area over PAPER without significantly raising the number of correlated elements but we find that in doing so, some degree of spectral smoothness has been sacrificed.
+Because foreground filtering in delay space cannot distinguish between signal and foregrounds, any regions of $k$-space contaminated by these reflections are effectively unusable in a 21\,cm measurement unless they can be modeled to high fidelity and removed.
+
+\item Fortunately, these reflections appear to be contained within the central $10$\,MHz of the HERA band, indicating a resonance that, in principle can be identified in the dish design and mitigated.
+It is also possible that the  non-ideal properties of an actual antenna will allow these reflections to escape the dish after a short time or be dissipated, rather than reflecting continually to long delays.
+Because estimates of the power spectrum are obtained from sub-intervals of $\approx10$\,MHz, the reflections that we have simulated will only impact a single redshift.
+
+\item Simulating the impact of these reflections on foreground leakage using the foreground model described in \citet{Thyagarajan:2015c}, we find that the beam chromaticity extends foregrounds above the level of the cosmological signal to $\approx 350$\,ns beyond the horizon while without the reflections, foregrounds extend above the signal to $\approx 250$\,ns beyond the horizon.
+These observations are pessimistic in that no attempt to inversely weight the foregrounds by their covaranciances has been attempted.
+
+\item If the reflections are contained within a $10$\,MHz subband around $150$\,MHz, than the overall constraints that HERA will be able to place on the astrophysics of reionization are minimally impacted.
+If the reflections somehow contaminate the entire band, than our constraints on reionization parameters will suffer a factor of two increase in uncertainty but still remain on the order of $10$\%.
+\end{itemize}
+
 \label{sec:Conclusion}

### 2016-01-20 DishSimulations/paper/DishSimulationsPaper_v1.tex
updated simulations draft

@@
 Carina Cheng\altaffilmark{5},
-Deboer David\altaffilmark{5},
-Parsons Aaron\altaffilmark{5},
-Venter Mariet\altaffilmark{7}
+David Deboer\altaffilmark{5},
+Aaron Parsons\altaffilmark{5},
+Mariet Venter\altaffilmark{7}
 and others.
@@
 \item The 14-m dish and inverted dipole feed configuration introduces reflections and, as a result, spectral structure, that is in excess of that observed in the antenna design for HERA's predecessor, PAPER.
-The dish design is intended to greatly increase array collecting area over PAPER without significantly raising the number of correlated elements but we find that in doing so, some degree of spectral smoothness has been sacrificed.
+The dish design is intended to greatly increase array collecting area over PAPER without significantly raising the number of correlated elements while narrowing the angular field of view and suppressing the overall amplitude of foregrounds but we find that in achieving these ends, some degree of spectral smoothness has been sacrificed.
 Because foreground filtering in delay space cannot distinguish between signal and foregrounds, any regions of $k$-space contaminated by these reflections are effectively unusable in a 21\,cm measurement unless they can be modeled to high fidelity and removed.

### 2016-01-21 ForegroundSimulations/ms.tex
Update figures 1, 2 and corresponding text
From 01c8a7d (master):
=====================

(*) Update figures 1 and 2

In ms.tex,

(*) Change text in accordance with updated figures

@@
 The gray vertical lines correspond to the horizon limits at $\pm 48.7$~ns for a 14.6~m antenna spacing.
+In all these cases, a {\it Blackman-Harris} window function has been applied along the spectral axis.
 
@@
 
-At 0\arcdeg off-axis, the {\it Airy} pattern has no spectral variation and thus appears as a straight vertical line centered at $\tau = 0$~ns whereas the simulated power pattern is found to exhibit some spectral variation giving rise to the wings on either side of $\tau = 0$~ns.
+At 0\arcdeg off-axis, the {\it Airy} pattern has no spectral variation except that introduced by the {\it Blackman-Harris} window function and thus reproduces its Fourier response centered at $\tau = 0$~ns whereas the simulated power pattern is found to exhibit some spectral variation giving rise to the wings on either side of $\tau = 0$~ns.
 As off-axis angle increases to 45\arcdeg, both the power patterns clearly exhibit chromaticity.
-They have similar magnitudes inside the horizon limits but the chromaticity of the simulated power pattern is $\sim 100$ times higher than that of an {\it Airy} pattern outside the horizon limits.
-In contrast, at 89\arcdeg off-axis, the two patterns have similar chromaticity in delay modes outside the horizon limits but the simulated power pattern has $\sim 100$ times more power inside the horizon limits indicating that the overall amplitude of the pattern at this location is higher relative to the nominal {\it Airy} pattern.
+The simulated pattern not only has a higher magnitude inside the horizon limits (by a factor $\sim 10$) but also exhibits higher chromaticity (by many orders of magnitude) in modes beyond the horizon relative to that of an {\it Airy} pattern.
+In contrast, at 89\arcdeg off-axis, not only does the simulated pattern have higher chromaticity in high delay modes but is also two orders of magnitude higher in amplitude inside the horizon limits relative to the nominal {\it Airy} pattern.
 

### 2016-01-23 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev2.tex
rev2

--- 2016-01-19 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev1.tex
@@
 \affil{\altaffilmark{1}MIT Kavli Institute, Massachusetts Institute of Technology, Cambridge, MA, 02139 USA}
-\affil{\altaffiltext{2}Dept. of Electrical and Computer Engineering, University of Virginia, Charlottesville, VA, 22904}
-\affil{\altaffiltext{3}National Radio Astronomy Obs., Charlottesville, VA}
+\affil{\altaffilmark{2}Dept. of Electrical and Computer Engineering, University of Virginia, Charlottesville, VA 22904}
+\affil{\altaffilmark{3}National Radio Astronomy Obs., Charlottesville, VA}
 \affil{\altaffilmark{4}Dept. of Astronomy, University of California, Berkeley, CA, USA}
@@
 regions lie closer to zenith and also perpendicular to the baseline vector. \citet{nithya15} 
-simulate the foreground contamination seen with a dipole beam, a phased array, and a Airy dish,
+simulate the foreground contamination seen with a dipole beam, a phased array, and a Airy pattern,
 and find that the latter suffers the least foreground leakage into
@@
 dependence limiting foreground bounding foreground emission within the wedge, but the emission from high delay is better suppressed using the 
-Airy dish leaving much of the wedge effectively empty.
+Airy pattern leaving much of the wedge effectively empty.
 
@@
 For feed maintenance purposes, a door is engineered into the dish surface on one mesh panel.
-The feed stands 17\,in off a mesh back plane surrounded by a XX\,in deep cylinder.
-The nominal dish focus is at 4.5\,m from the dish surface to the feed back plane, though numerical models suggest the focus is closer to 5.3\,m.
+The dipole stands 17\,in below a 78\,in diameter circular mesh back plane surrounded by a 30\,in deep cylinder.
+The cylinder is offset 0.5\,in from the back plane.
 The feed is designed to make the beams for both polarizations more similar to each other, and also to taper the dipole beam towards the edge of the dish to mitigate dish-dish coupling.
+The nominal dish focus is at 4.5\,m from the dish surface, though numerical dish models including the feed predict the focus is closer to 5.3\,m.
 
@@
 \caption{Prototype HERA feed set up outside the dish for preliminary characterization.
-This feed revision consists of a dual-polarized sleeved dipole offset 17\,in from a XX\,in diameter back plane, surrounded by a XX\,in deep cylindrical skirt.}
+This feed revision consists of a dual-polarized sleeved dipole offset 17\,in from a 78\,in diameter back plane, surrounded by a 30\,in deep cylindrical skirt.}
 \label{fig:feedphoto}
@@
 Thyagarajan et al., (submitted) discuss the apparent frequency dependence of foregrounds in more detail as well as methods to mitigate it such as delay space CLEANing.
-We focus on this section on the uncertainties in these foreground power spectrum simulations due to beam modeling uncertainties, but we must first discuss these foreground simulations themselves and their dependence on observing conditions.
+We focus in this section on the uncertainties in these foreground power spectrum simulations due to beam modeling uncertainties, but we must first discuss these foreground simulations themselves and their dependence on observing conditions.
 
 We simulate foreground power spectra using different primary beam models at various local sidereal times (LSTs).
+We use frequency-independent model beams (evaluated at 137\,MHz) to isolate the interferometric foreground frequency dependence.
+The added frequency dependence of the changing overall gain and beam shape versus frequency is addressed by the other papers in this series.
 Given that our measured dish power patterns agree well with both numerical models (HFSS and CST) in the main lobe but deviate in the sidelobes, and that these models make somewhat different assumptions about the dish surface, we take them as a representative pair of possible dish models.
-We use a feed height of 5\,m, a compromise between larger collecting area and smaller risk of coupling to adjacent dishes.
-We also include the Airy pattern for comparison as \citet{nithya15}.
+We use a feed height of 5\,m, a compromise between collecting area and risk of coupling to adjacent dishes.
+We also include the Airy pattern for comparison as in \citet{nithya15}.
 Beam models with weaker response near the horizon (such as the Airy pattern) downweight sources in this direction of high apparent frequency dependence.

### 2016-01-25 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev2.tex

@@
 The Hydrogen Epoch of Reionization Array (HERA) is a radio interferometer aiming to detect the power spectrum of 21\,cm fluctuations from neutral Hydrogen from the Epoch of Reionization.
-Drawing on lessons from the Murchison Widefield Array (MWA) and the Precision Array for Probing the Epoch of Reionization (PAPER), HERA is a hexagonal array of large (14\,m) dishes with suspended dipole feeds designed to maximize sensitivity while economizing data volume.
+Drawing on lessons from the Murchison Widefield Array (MWA) and the Precision Array for Probing the Epoch of Reionization (PAPER), HERA is a hexagonal array of large (14\,m) dishes with suspended dipole feeds with element collecting area of 100\,m$^2$.
 This is the first of a series of four papers characterizing the frequency and angular response of the HERA dish element with simulations and measurements.
@@
 We measure collecting areas of 70--100\,m$^2$ and predict power spectrum SNRs.
-With optimistic foreground and analysis assumptions, HERA-127 should detect the EOR with an SNR of 25--30 with a single season of observations.
-Even with more pessimistic assumptions, the significance of an EOR detection remains above $5\sigma$.
+With optimistic foreground and analysis assumptions, HERA-127 should detect the EOR with a signal-to-noise of 25--30 with a single season of observations.
+Even pessimistically assuming that only previously demonstrated techniques are used, the significance of an EOR detection remains above $5\sigma$.
 Lastly we simulate foreground visibilities using numerical beam models and study the foreground distribution in Fourier space as a function of LST, and the uncertainties in these predictions due to beam modeling uncertainties.
-Future measurements will study the dish beam in the presence of adjacent dishes, quantifying levels of cross-talk and cross-coupling.
 \end{abstract}
@@
  complement indirect probes of the Dark Ages and Epoch of Reionization such as quasar 
- sightlines, and the CMB optical depth which leave the reionization 
+ sightlines and the CMB optical depth which leave the reionization 
  history of the universe only loosely constrained. (See \citet{FurlanettoReview, miguelreview, PritchardLoebReview, aviBook, zaroubi} for reviews) Sensitivity and foreground removal are 
@@
 HERA uses 14\,m diameter parabolic dishes arranged in a compact, hexagonal array to achieve coherent integration on the very low surface brightness 21\,cm signal.
-Redundant baselines also permit redundant calibration techniques which solve for internal degrees of freedom with only of parameters which must be estimated from the sky \citep{zheng14}, circumventing the sky model based calibration schemes which non-redundant arrays must pursue.
+Redundant baselines also permit redundant calibration techniques which solve for the relative calibration between all antennas \citep{zheng14}, and use a sky model only to set the frequency dependent flux scale.
+In contrast, non-redundant arrays are pursuing fully sky model-based calibration schemes which risk frequency-dependent calibration systematics due to sky modeling inaccuracy \citep{braun2013}.
 HERA is pursuing a staged deployment of 19, 127, and finally 331 elements in progressively larger hex patterns, with scattered outriggers for imaging.
@@
 
-It was initially thought that the foreground emission would be confined to the lowest few 
-line of sight Fourier modes \citep[e.g.,][]{MoralesBowmanHewittFGsub}, however it was later realized that the  
+In an ideal achromatic instrument the foreground emission would be confined to the lowest few 
+line of sight Fourier modes \citep[e.g.,][]{MoralesBowmanHewittFGsub}, however  the  
 interferometer's frequency-dependent point spread function smears foreground power into a ``wedge'' shaped 

### 2016-01-26 DishSimulations/paper/DishSimulationsPaper_v2.tex
latest simulations paper update

--- 2016-01-20 DishSimulations/paper/DishSimulationsPaper_v1.tex
@@
+\newcommand{\bx}{{\bf x}}
+\newcommand{\bl}{\boldsymbol{\ell}}
+\newcommand{\fts}{{\widetilde{s}}}
+\newcommand{\ftr}{{\widetilde{r}}}
+\newcommand{\ftv}{{\widetilde{v}}}
+\newcommand{\bu}{{\bf u}}
+\newcommand{\bb}{{\bf b}}
+\newcommand{\ftR}{{\widetilde{R}}}
+
 \documentclass[twocolumn]{emulateapj}
@@
 \usepackage{natbib}
+\usepackage{color}
 \citestyle{aa}
@@
 \begin{abstract}
-Using electromagnetic simulations, we assess the spectral properties of the antenna element of the Hydrogen Epoch of Reionization Array (HERA) in order to both establish a specification for the degree of spectral structure that is permissible to sufficiently isolate foregrounds and allow a detection of the cosmological 21\,cm signal and verify direct laboratory measurements of the dish characteristics.
-We find that our simulations are in good agreement with field measurements.
-Using simulations of foregrounds, we find that the $\approx -40$\,dB response at 60\,ns of the HERA dish is sufficient to isolate the cosmological 21\,cm signal $\approx 0.2$\,$h$Mpc$^{-1}$ at $z\approx 8.5$ and obtain a high signal to noise detection of the power spectrum.
-This study represents the first time that direct measurements a 21\,cm interferometer design have been translated into its ability to constrain the physics of reionization.
+We use time domain electromagnetic simulations to assess the spectral characteristics of the antenna element for the Hydrogen Epoch of Reionization Array (HERA).
+These simulations are part of a multi-faceted campaign to determine whether the dish's design is suitable for obtaining a detection of redshifted 21\,cm emission from the Epoch of Reionization.
+Our simulations show the existence of standing wave reflections in some regions of the 100-200\,MHz bandpass with an amplitude of $\approx -35$\,dB at 100\,ns which can lead to some loss of measurable modes and a modest reduction in sensitivity over a small segment of the band.
+Overall, we find that the spectral response of the dish is sufficiently smooth for proven foreground isolation methods such as delay filtering to contain foreground emission at line of sight wave numbers below $k_\parallel = 0.15-0.2$\,$h$Mpc$^{-1}$.
+Incorporating these results into a Fisher Matrix analysis, we find that the spectral structure observed in our simulations has only a small effect on the overall constraints on the astrophysics of reionization that HERA will achieve, allowing it to serve as a benchmark for the design of future instruments such as the Square Kilometer Array.
 \end{abstract}
@@
 As of now, two major experimental endeavors are underway to make a first detection of the 21\,cm signal with most focusing on the Epoch of Reionization (EoR) in which UV photons from early galaxies transformed the hydrogen in the universe from neutral to ionized.
-The first involves measuring the sky-averaged global signal and is being pursued by experiments such as EDGES \citep{Bowman:2010}, LEDA \citep{Greenhill:2012}, DARE \citep{Burns:2012}, SciHi \citep{Voytek:2014}, and BIGHORNS \citep{Sokolowski:2015} coming online in their planning stages or taking data.
+The first involves measuring the sky-averaged global signal and is being pursued by experiments such as EDGES \citep{Bowman:2010}, LEDA \citep{Greenhill:2012,Bernardi:2015}, DARE \citep{Burns:2012}, SciHi \citep{Voytek:2014}, and BIGHORNS \citep{Sokolowski:2015} either in their planning stages or already taking data.
 The second attempts to observe spatial  fluctuations in the 21\,cm emission using radio interferometers.
-As of now, a first generation of interferometry experiments are taking data in an attempt to make a first statistical detection of the power spectrum of 21\,cm brightness temperature fluctuations.
-These include the Giant Metrewave Telescope (GMRT)  \citep{Paciga:2013}, the Low Frequency ARray (LOFAR), \citep{VanHaarlem:2013}, the Murchison Widefield Array \citep{Tingay:2013} and the Precision Array for Probing the Epoch of Reionization (PAPER) \citep{Parsons:2010}.
+A first generation of such experiments are currently taking data in an attempt to make a first statistical detection of the power spectrum of 21\,cm brightness temperature fluctuations.
+These include the Giant Metrewave Telescope (GMRT)  \citep{Paciga:2013}, the Low Frequency ARray (LOFAR), \citep{VanHaarlem:2013}, the Murchison Widefield Array \citep{Tingay:2013a} and the Precision Array for Probing the Epoch of Reionization (PAPER) \citep{Parsons:2010}.
+Already, these experiments are beginning to yield upper limits on the 21\,cm signal \citep{Dillon:2013,Parsons:2014,Jacobs:2015,Dillon:2015,EwallWice:2015a} and significant scientific results.
+The most stringent measurement of $\approx 500$\,mK$^2$ \citep{Ali:2015} is able to rule out number of scenarios in which the intergalactic medium received little or no heating from X-rays \citep{Pober:2015,Greig:2015b}.
 
 The primary obstacle to obtaining a high redshift detection of the cosmological signal through both of these methods is the existence of foregrounds that are $\sim 10^5-10^6$ times brighter.
-While requiring much greater sensitivity to global-signal experiments, interferometers have the advantage that these spectrally smooth foregrounds naturally avoid a significant region of $k$-space, known as the {\it EoR window}, occupying a region known as the {\it wedge} \citep{Datta:2010,Vedantham:2012,Parsons:2012,Thyagarajan:2013,Liu:2014a,Liu:2014b}, however any structure in the frequency response of the instrument has the potential to leak foregrounds into the EoR window, masking our signal.
-Indeed, low level spectral structures in the analogue and digital signal chains on the initial buildout of the MWA are proving to be a significant obstacle \citep{Dillon:2015b,EwallWice:2015a,Beardsley:2015b}.
+While requiring much greater sensitivity than global-signal experiments, interferometers have the advantage that spectrally smooth foregrounds are naturally contained to a finite region of Fourier space, corresponding to large line of sight scales, known as the {\it wedge} \citep{Datta:2010,Vedantham:2012,Parsons:2012,Thyagarajan:2013,Liu:2014a,Liu:2014}.
+However any structure in the frequency response of the instrument is imprinted on the foregrounds and has the potential to leak power into the {\it EoR window} at small line of sight scales, masking the signal.
+Indeed, sub-percent spectral features in the analogue and digital signal chains on the initial build-out of the MWA are proving to be a significant obstacle \citep{Dillon:2015b,EwallWice:2015a,Beardsley:2015b}.
 
-While, in principle, spectral structure in the bandpass of the instrument may be removed in calibration, simulations show that any mismodeling of emission and the primary beam, potentially below the confusion limit, will mix the significant spectral structure on long baselines into short ones, masking the signal entirely \citep{Barry:2015}.
-While redundant calibration \citep{Wieringa:1992,Liu:2011,Zheng:2014} is able to calibrate the independent of a detailed model of the sky, any direction-dependent chromatic structure in the primary beam of the instrument introduces additional degrees of freedom that must be modeled, potentially leading to signal loss and the introduction of spurious spectral structure due to unmodeled foregrounds in long baselines.
-Because of our limited knowledge of foregrounds at low-frequency and the fidelity of calibration algorithms, the only sure way of building an instrument that will guarantee a detection of the redshifted 21\,cm emission is to design it such that all spectral structure in the signal chain is limited to a finite region of delay space, well below the wedge.
+While, in principle, spectral structure in the bandpass of the instrument may be removed in calibration, simulations show that any mismodeling of emission and the primary beam, potentially below the confusion limit, will mix the significant spectral structure introduced by the wedge on long baselines into short ones, masking the signal entirely \citep{Barry:2016}.
+While redundant calibration \citep{Wieringa:1992,Liu:2011,Zheng:2014} is able to solve for gains that are primarily independent of a detailed model of the sky, it is unclear how one might remove direction-dependent chromatic structure that might be present in the primary beam of the instrument.
+Because of our limited knowledge of foregrounds at low frequency and the fidelity of calibration algorithms, it is imperitive to design experiments whose spectral structure is contained, as much as possible, to low delays.
 
-The Hydrogen Epoch of Reionization Array (HERA) is an instrument currently taking first observations in the Karoo in South Africa with the ultimate goal of detecting the power spectrum of 21\,cm brightness temperature fluctuations at high signal-to-noise (SNR) \citep{Pober:2014}.
-A central principle in HERA's design is that it be calibration fail-safe such that a detection of the signal is guaranteed, even if the chromaticity of the instrument is not calibrated out.
-This paper and its companions \citep{Neben:2015b,Patra:2015,Thyagarajan:2015c} describe a multifaceted approach to establishing a stringent specification on the spectral structure permissible for HERA to be calibration fail-safe and determine to what extent its design meets these requirements.
-We accomplish this by establishing a spec with simulations of foregrounds \citep{Thyagarjan:2015c} and verifying that HERA primary antenna element meets this spec with reflectometry \citep{Patra:2015} and Orbcomm beam mapping \citep{Neben:2015b}.
-These measurements are verified with detailed electromagnetic simulations which we describe in this work.
+The Hydrogen Epoch of Reionization Array (HERA) is a next generation 21\,cm experiment designed to achieve a two-orders of magnitude improvement in sensitivity over current experiments which will allow it to make a robust detection of the 21\,cm power spectrum during the EoR \citep{Pober:2014}.
+Much of this sensitivity increase is enabled by moving the collecting area of the instrument into baselines that are located primarily inside of the EoR window and a switch from PAPER's skirted dipoles and the MWA's phased dipole arrays to an antenna element that consists of a feed suspended over a large reflecting parabolic dish.
+A central requirement for HERA's dish design is that the antenna have a response that is sufficiently smooth in frequency and centralized enough in its angular response that it leaves the EoR window free of contamination since one cannot rely on direction independent redundant calibration to remove any spectral structure that varies as a function of location on the primary beam.
+
+This paper and its companions \citep{Neben:2016,Patra:2016,Thyagarajan:2016} describe a multifaceted approach for assessing whether the HERA dish meets the requirements for isolating foregrounds within the wedge and leaving the EoR window clean.
+We accomplish this by establishing a spec with simulations of foregrounds \citep{Thyagarajan:2016} and verifying that HERA primary antenna element meets this spec with reflectometry \citep{Patra:2016} and Orbcomm beam mapping \citep{Neben:2016}.
+In this work, we present the results of time-domain electromagnetic simulations that are intended to predict the degree of spectral structure in the HERA dish, assess the impact of this spectral structure on the leakage of foregrounds into the EoR window, and to verify the reflectometry measurements taken in the field by \cite{Patra:2016}.
 
 This paper is organized as follows.
-In \S~\ref{sec:Formalism} we lay out our analytic framework for describing the impact of reflections and spectral structure on foreground leakage in delay-transform power spectra.
-In \S~\ref{sec:Simulations} we describe our electromagnetic simulations of the HERA dish element.
-In \S~\ref{sec:Comparison} we compare our simulation results to direct measurements of the primary dish element and in \S~\ref{sec:Foregrounds} we apply our electromagnetic simulation results to simulations of foregrounds to determine the extent that the HERA dish's chromatic structure pollutes the EoR window and their impact on HERA's overall sensitivity.
+In \S~\ref{sec:Formalism} we lay out our analytic framework and describe the impact of reflections and spectral structure on foreground leakage in delay-transform power spectra.
+In \S~\ref{sec:Simulations} we describe our time-domain electromagnetic simulations of the HERA dish element and how we extract the voltage response function.
+In \S~\ref{sec:SimulationResults} we describe the results and verify our simulation framework by comparing its prediction of the $S_{11}$ parameter of the HERA dish to direct field measurements described in \citep{Patra:2016}.
+In \S~\ref{sec:Foregrounds} we apply our electromagnetic simulation results to simulations of foregrounds to determine the extent that the HERA dish's chromatic structure pollutes the EoR window and their impact on HERA's overall sensitivity.
 We conclude in \S~\ref{sec:Conclusion}.
@@
 Intuitively, any reflections in the signal path introduce sinusoidal ripples in the frequency dependent gain of the instrument.
-Since reflection delay is the Fourier dual to frequency, reflections at larger delays introduce ripples at higher frequencies.
+Since time delay is the Fourier dual to frequency, reflections with larger delays introduce ripples at higher frequencies.
 Isolation of the 21\,cm signal from foregrounds that are over five orders of magnitude brighter depends critically on their smoothness.
-Any sinusoidal frequency structure, introduced by the antenna gain will cause these foregrounds to mimic and swamp the signal unless they are brought below a level similar to the ratio between the foregrounds and the signal itself.
-We now derive this process in formal detail.
-A simple equation for effect of direction independent reflections in the signal chain of an interferometer, downstream of the receiver, has been derived in \citet{EwallWice:2015a}, we extend this analysis in this section by considering the direction dependent reflections that can occur within the antenna element.
-We assume that the intensity field on the sky is given by
-\begin{equation}\label{eq:Dirac}
-I({\bf \widehat{k}},f) \delta_D({\bf \hat{k}} - {\bf \hat{k}'})= \langle s({\bf \hat{k}},f)s^*({\bf \hat{k}'},f)  \rangle_t^2
-\end{equation}
- where $\delta_D$ is the Dirac delta function and $\langle \rangle_t$ indicates an average in time.
-We imagine that the electric field as a function of time, $\widetilde{s}({\bf \widehat{k}},t)$ arrives at an arbitrary origin at time $t$ and at the various $i^{th}$ antenna elements of an interferometer at locations ${\bf x_i}$ at times $\tau_i={\bf x_i} \cdot {\bf \widehat{k}} /c$.
-We now consider reflections within a single dish element described by a direction dependent reflection coefficient\footnote{Ignoring reflections between multiple dish elements which we treat in Appendix~\ref{app:Reflections}}, $\widetilde{r}_i({\bf \widehat{k}},\tau)$.
-which re-introduce the signal at later times $\tau$.
-The voltage signal measured at the $i^{th}$ antenna element, $\widetilde{v}_i$, is the integral over solid angle of the convolution of the electric field entering the antenna (delayed by $\tau_i$) with $r_i({\bf \widehat{k}},\tau')$.
+Any sinusoidal frequency structure introduced by the reflections will cause these foregrounds to mimic and swamp the signal unless they are brought below a level similar to the ratio between the foregrounds and the signal itself.
+A simple equation describing effect of direction independent reflections in the signal chain of an interferometer, downstream of the receiver on a visibility has been derived in \citet{EwallWice:2015a}.
+We now extend this analysis by considering the direction dependent reflections that can occur within the antenna element.
+We start by denoting the electric field of radiation arriving at an $i^{th}$ antenna element at position $\bx_i$ and time $t_i = t + \bl \cdot \bx_i /c \equiv t+\tau_i$ as $\fts(\bl,\bx_i,t_i)$.
 
-\begin{equation}
-\widetilde{v}_i(t) = \int d \Omega \int d \tau \widetilde{r}_i({\bf \widehat{k}},\tau) \widetilde{s}({\bf \widehat{k}},t- \tau_i - \tau)
+Reflections within the signal chain of each antenna are most generally described by a direction dependent reflection coefficient, $\ftr_i(\bl,\tau)$.
+Its effect is to add the signal to itself multiplied by $\ftr_i$ and delayed by $\tau$.
+The voltage signal measured at the $i^{th}$ antenna element, $\widetilde{v}_i$, is the integral over solid angle of the electric fields arriving from all directions.
+The presence of the reflections introduces a convolution of the electric field entering the antenna (delayed by $\tau_i$) with $\ftr_i(\bl,\tau)$.
+
+\begin{equation}\label{eq:Voltage}
+\ftv_i(t) = \int d \Omega \int d \tau \ftr_i(\bl,\tau) \fts(\bl,t+ \tau_i - \tau)
 \end{equation}
 
-A correlator (FX and XF) measures the time-averaged product of the Fourier transform of the voltage streams between the $i^{th}$ and $j^{th}$ antenna.
+A correlator measures the time-averaged product of the Fourier transform of the voltage streams between the $i^{th}$ and $j^{th}$ antenna.
 Fourier transforming the voltage stream from the $i^{th}$ antenna we obtain
 \begin{equation}
-v_i(f) = \int d \Omega \int d \tau \widetilde{r}_i({\bf \widehat{k}},\tau) s({\bf \widehat{k}},f)e^{-2 \pi i f(\tau_i+\tau)}
+v_i(f) = \int d \Omega \int d \tau \ftr_i(\bl,\tau) s(\bl,f)e^{-2 \pi i f(\tau_i+\tau)}
 \end{equation}
 The time averaged product between the two antennas is
-\begin{equation}
-V_{ij}'(f) = \left \langle v_i(f) v_j^*(f) \right \rangle_t = \int d \Omega \int d \tau \widetilde{r}_i(\tau) d \tau' \widetilde{r}^*_j(\tau')e^{-2 \pi i f (\tau-\tau') } I({\bf \widehat{k}}, f) e^{- 2 \pi i \Delta \tau_{ij}f}
-\end{equation}
-where $\Delta \tau_{ij} = \tau_i-\tau_j = ({\bf x_i - x_j}) \cdot {\bf \widehat{k}}/c$. We eliminated one of the solid angle integrals using equation~\ref{eq:Dirac}.
+\begin{align}
+V_{ij}'(f) &= \left \langle v_i(f) v_j^*(f) \right \rangle_t \nonumber \\
+ &= \int d \Omega d \tau d \tau' \ftr_i(\tau) \ftr^*_j(\tau')e^{-2 \pi i f (\tau-\tau') } I(\bl, f) e^{- 2 \pi i \Delta \tau_{ij}f} 
+\end{align}
+where $\Delta \tau_{ij} = \tau_i-\tau_j = (\bx_i-\bx_j) \cdot \bl/c$ and $I(\bl,f)=\left \langle |s(f,\bl)|^2 \right \rangle_t$.
+Here, we have invoked the fact that electromagnetic waves arriving from different directions are incoherent.
 
-Defining ${\bf u}_{ij} = f ({\bf x}_i-{\bf x}_j)/c$, we obtain,
- %HERA's primary antenna element consists of a sleeved dipole element suspended 5\,m above the focus of a 14\,m diameter parabolic dish (Fig.~\ref{fig:Dish}).
-.
-%\begin{figure}
-%\includegraphics[width=.5\textwidth]{figures/DishSA.png}
-%\caption{The HERA primary antenna element-one of 19 undergoing currently taking the first observations in the Karoo in South Africa.
-The antenna consists of a sleeved dipole suspended within a 2\,m diameter skirt, five meters above the ground at the focal point of a 14\,m diameter dish.}\label{fig:Dish}
-%\end{figure}
-
-% We show in Appendix~\ref{app:Reflections} that if an astronomical radio signal with time dependence at the location of the feed, $s({\bf \widehat{k}},t)$, experience reflections within the dish such that the voltage recorded in the feed is
-
-Than the resulting visibilities obtained by cross correlating antenna $i$ and antenna $j$ are given by 
+Defining $\bu_{ij} = f (\bx_i-\bx_j)/c$ and performing the $\tau$ and $\tau'$ Fourier transforms, we arrive at
 \begin{equation}\label{eq:Visibility}
-V'_{ij}(f) =  \int d \Omega r_i({\bf \widehat{k}},f) r^*_j({\bf \widehat{k}},f)  I(f,{\bf \widehat{s}})e^{2 \pi i f {\bf u}_{ij} \cdot {\bf \widehat{k}}/c},
+V'_{ij}(f) =  \int d \Omega r_i(\bl,f) r^*_j(\bl,f)  I(\bl,f)e^{2 \pi i f \bu_{ij} \cdot \bl/c},
 \end{equation}
 where ${\bf b}_{ij} = ({\bf x}_i - {\bf x}_j )$ to use the usual $uv$ notation of interferometry.
-$r_i({\bf \hat{k}},f)$ is the inverse fourier transform of the reflection response of the dish, hence we see that the reflection response is precisely the Fourier dual to the Dish's frequency domain voltage beam.
-Setting a specification on reflections is hence equivalent to setting a specification on the spectral smoothness of the voltage beam.
+$r_i(\bl,f)$ is the inverse fourier transform of the reflection response of the dish, hence we see that the reflection response is precisely the Fourier dual to the Dish's frequency domain voltage beam.
+Setting a specification on reflections is hence equivalent to setting a specification on the spectral smoothness of the antenna's voltage beam.
 
-In order to separate spectrally smooth foregrounds from our signal, we expect to use the {\it delay transform} over frequency, defined as \citep{Parsons:2012}
+In order to filter spectrally smooth foregrounds from the signal,HERA is expected to employ the {\it delay transform} over frequency, defined as \citep{Parsons:2012}
 \begin{equation}
-\widetilde{V}_{ij}(\tau) = \int d f e^{2 \pi i \tau f} V_{ij}(f)
+\widetilde{V}_{ij}(\tau) = \int d f e^{2 \pi i \tau f} V_{ij}(f).
 \end{equation}
@@
 \begin{equation}
-\widetilde{V}'_{ij}(\tau)=  \int d \Omega \int d f  r_i({\bf \widehat{k}},f) r_j^*({\bf \widehat{k}},f)  I(f,{\bf \hat{k}}) e^{2 \pi i f ( {\bf b}_{ij} \cdot {\bf \hat{k}} /c - \tau)}
+\widetilde{V}'_{ij}(\tau)=  \int d \Omega \int d f  r_i(\bl,f) r_j^*(\bl,f)  I(\bl,f) e^{2 \pi i f ( \bb_{ij} \cdot \bl /c - \tau)}
 \end{equation}
 Let's examine the quantity within the angular integral.
-For each ${\bf \hat{k}}$, we see that each source is mapped to a line $\tau ={\bf b}_{ij}\cdot{\bf \hat{k}}/c$, resulting in the much discussed ``wedge" \citep{Datta:2010,Vedantham:2012,Parsons:2012,Morales:2013,Thyagarajan:2013,Liu:2014a,Liu:2014b}.
+We see that each source located at $\bl$ on the sky is mapped to a line $\tau =\bb_{ij}\cdot \bl/c$, resulting in the much discussed ``wedge" \citep{Datta:2010,Vedantham:2012,Parsons:2012,Morales:2012,Thyagarajan:2013,Liu:2014a,Liu:2014b}.
 The presence of the frequency dependent beam causes each source line to be convolved in delay with the direction dependent kernel
 \begin{equation}\label{eq:Kernel}
-\widetilde{R}_{ij}({\bf \hat{k}},\tau) = \int d \tau \widetilde{r}_i({\bf \widehat{k}},\tau - \Delta \tau) \widetilde{r}^*_j({\bf \widehat{k}},-\Delta \tau).
+\ftR_{ij}(\bl,\tau) = \int d \tau \ftr_i(\bl,\tau - \Delta \tau) \ftr^*_j(\bl,-\Delta \tau).
 \end{equation}
-which is the convolution of the delay response of voltage beam $i$ with the complex conjugate of voltage beam $j$ evaluated on a negative t-axis, $\widetilde{r}_i({\bf \widehat{k}},\tau)$,$\widetilde{r}_j({\bf \widehat{k}},\tau)$.
+which is the convolution of the delay response of the voltage beam of antenna $i$ with the time-reversed complex conjugate of voltage beam of antenna $j$.
+In the remainder of this paper, we will often refer to $\ftR$ as the {\it power kernel} applied to a visibility.
 Note that this is not equal to the convolution of the voltage response with its complex conjugate, which would lead to foreground power only being bled out to positive delays.
-Usually, beams have a different delay structure in each direction, and we demonstrate the effect of foreground smearing in Fig.~\ref{fig:Smearing} for a simple model with only three sources.
+We demonstrate the effect of foreground smearing in Fig.~\ref{fig:Smearing} for a simple model with only three sources.
 Without reflections, the sources would form lines in $b-\tau$ space.
-With the reflections, the sources are smeared out, leading to supra-horizon emission.
-\begin{figure*}[h!]
+Withthe reflections, the sources are smeared out, leading to supra-horizon emission.
+\begin{figure*}
 \includegraphics[width=\textwidth]{figures/wedgeCompare.pdf}
-\caption{We demonstrate the impact on foregrounds of the frequency dependent beam.
+\caption{A demonstration of the impact on foregrounds of the frequency dependent beam.
 Left: The location of three sources in delay space assuming a frequency indepdendent beam (no reflections in the antenna element).
@@
 \end{figure*}
-For the sake of pedagogy, we now consider the case where the beam can be factored into angular and frequency dependent components, $r_i({\bf \hat{k}},f) = g_i(f)a_i({\bf \hat{k}})$.
-For such a case, every line in Fig.~\ref{fig:Smearing} would be convolved with the same delay dependent shape, normalized to the gain of $a_i({\bf \hat{k}})$.
-In this case, we have
+For the sake of pedagogy, we now consider the case where the beam can be factored into angular and frequency independent components, $r_i(\bl,f) = g_i(f)a_i(\bl)$.
+For such a case, every line in Fig.~\ref{fig:Smearing} would be convolved with the same delay dependent shape, normalized to the gain of $a_i(\bl)$.
+In this situation, we have
 \begin{equation}
@@
 \end{equation}
-We can further simplify matters by assuming that $\widetilde{g}_i(\tau=0)\gg\widetilde{g}_i(\tau>0)$, which is often a good assumption at large delays for the relatively smooth bandpasses our instruments are designed to have.
-\begin{equation}\label{eq:KernelApprox}
-\widetilde{V}_{ij}'(\tau) \approx \widetilde{g}_i(0)\int d \tau' \widetilde{g}_j^*(\tau')\widetilde{V}_{ij}(\tau- \tau') + \widetilde{g}_j^*(0) \int d \tau' \widetilde{g}_i(\tau')\widetilde{V}_{ij}(\tau-\tau')
-\end{equation}
-Hence, to first order, the impact of reflections is to convolve the delay-transformed visibility with the voltage beam of the instrument, which acts as the power-kernel.
-This may be a somewhat un-intuitive result since we might naively expect for the power-kernel to be the square of the delay-response.
-This linear falloff puts exquisite requirements on the smoothness of the beam, requiring that it fall roughly six orders of magnitude in delay before the signal is accessible.
-
- In this paper, we derive $\widetilde{r}_i({\bf \widehat{k}},\Delta \tau)$ for the HERA antenna element using electromagnetic simulations, in order to verify direct measurements of the antenna element with refelctometry \citep{Patra:2015} and Orbcomm measurements of the beam \citep{Neben:2015b}.
-We also explore the implications of the HERA dish's $\widetilde{r}_i({\bf \widehat{k}},\tau)$ on the scientific bottom line for EoR, using the Fisher Matrix Formalism.
+where $V_{ij}$ is the visibility with the achromatic factor in the voltage patterns included. 
+We can gain further insight into the behavior of the delay kernel arising from chromaticity by assuming that $\widetilde{g}_i(\tau=0)\gg\widetilde{g}_i(\tau>0)$, which should be the case at large delays for the smooth bandpasses our instruments are designed to have.
+\begin{align}\label{eq:KernelApprox}
+\widetilde{V}_{ij}'(\tau) &\approx \widetilde{g}_i(0)\int d \tau' \widetilde{g}_j^*(\tau')\widetilde{V}_{ij}(\tau- \tau') \nonumber \\
+& + \widetilde{g}_j^*(0) \int d \tau' \widetilde{g}_i(\tau')\widetilde{V}_{ij}(\tau-\tau') 
+\end{align}
+Hence, to first order, the impact of reflections is to convolve the delay-transformed visibility with the voltage beam of the instrument.
+This may be a somewhat un-intuitive result since naive dimensional analysis might predict that the power-kernel to be proportional to the square of the delay-response.
+This linear falloff coupled with the enormous dynamic range between foregrounds and signal puts exquisite requirements on the smoothness of the beam, requiring that it fall roughly six orders of magnitude in the regions of delay space that we want to measure the signal.
 
 \section{Electromagnetic Simulations of the HERA dish element}\label{sec:Simulations}
-In Fig.~\ref{fig:SimulationSetup} we show the geometery of the electromagnetic simulation. {\bf Rich: fill in the details here}
+
+HERA \citep{DeBoer:2016} is an instrument designed to detect the power spectrum of 21\,cm brightness temperature fluctuations during the EoR at high signal-to-noise between the frequencies of 100 and 200\,MHz (redshifts 6 to 12) \citep{Pober:2014}.
+Its initial, 19-element, buildout is currently taking first observations in the Karoo in South Africa.
+HERA is meant to serve as a vast improvement in sensitivity over current efforts for only a modest increase in cost.
+It achieves this by increasing the number of correlated inputs by only a factor of $\approx 2$ while increasing the total collecting area of each correlated element by over an order of magnitude and arranging the elements in such a way as to maximize the number of short baselines that are located outside of the foreground wedge.
+Central to increasing the collecting area of each element is a switch from dipoles (used by the MWA and PAPER) to feeds suspended over large 14\,m diameter parabolic dishes.
+In Fig.~\ref{fig:AntennaComparison} we show one of the initial 19 dishes currently being deployed in South Africa at the same site as PAPER whose antenna we also show at the top of the figure.
+
+Having formally derived the impact of analogue reflections on foreground visibilities, we are now in a position to investigate their existence in the HERA dish.
+In this section, we describe the setup and parameters of our simulations (\S~\ref{ssec:Simulations}), and how we extract the voltage response function of the dish (\S~\ref{ssec:Deconvolve}).
+
 \begin{figure}
+\includegraphics[width=.5\textwidth]{figures/PAPER_HERA_compare.jpg}
+\caption{The HERA antenna element (bottom) uses a parabolic dish to achieves over an order of magnitude increase in collecting area over the PAPER antenna (top).
+The sleeved dipole in the center of the PAPER backplane is identical to the sleeved dipole being suspended under the cylindrical skirt over the vertex of the HERA dish.
+The dish geometry has the potential to introduce intra-antenna reflections which we explore in this work.}
+\label{fig:AntennaCompare}
+\end{figure}
 
-\subsection{The Simulations}
+\subsection{The Simulations}\label{ssec:Simulations}
+We perform time-domain simulations of the voltage output of the HERA feed using CST.
+{\bf \color{red} Rich: fill in the details here, describe the CST parameters and a brief overview of how it numerically solves for the voltages (citations?).
+}
+
+In Fig.~\ref{fig:SimulationSetup} we show the geometery of the electromagnetic simulation.
+A $150$\,MHz plane wave with a Gaussian envelope with FWHM of {\bf \color{red}???} is initialized {\bf \color{red} ??} meters above the dish vertex traveling in the $-z$ direction.
+It is reflected by the dish before entering the dipole feed, hidden below the cylindrical skirt in this figure.
+We record the electric field voltage of the plane wave at the feed output terminals as a function of time, plotted as a red line in Fig.~\ref{fig:SimulationOutput} along with the voltage at the feed outputs (black line).
+The delay between the primary envelopes of the plane wave and the voltage output of the feed is $\approx 30$\,ns which corresponds to the round trip travel time from the feed to the dish vertex and back.
+However, while the input plane wave, modulated by a gaussian, falls off rapidly and dies off after the first $\approx 20$\,ns after its peak, we see that the voltage output decays far more slowly with delay due to reflections within the dish-feed structure reintroducing the signal at times beyond its initial falloff.
+We are able to get a qualitative feel for the amplitude of the reflections by inspecting the falloff of the time domain voltage response and see that after $60$\,ns it reachs $\approx -25$\,dB.
+\begin{figure}
 \includegraphics[width=.5\textwidth]{figures/One_dish_Pfeed_render_pw_0deg.png}
@@
 Of concern to 21\,cm experiments are the subsequent reflections between the feed and the dish (C) which can lead to large delay contamination of the EoR window.}
-\label{fig:Simulation}
+\label{fig:SimulationOutput}
 \end{figure*}
 \subsection{Deconvolving the Response Function}\label{ssec:Deconvolve}
+
+We can do much better than this.
+From equation~\ref{eq:Voltage}, we know that the voltage output results from the convolution of the plane wave input with the voltage gain of the antenna.
+The voltage response of the dish which we are attempting to probe has been convolved with a known kernel; our input plane wave.
+Hence, a straightforward application of the Fourier convolution theorem allows us to determine the voltage response.
+
 Since our simulation is sampled in finite time steps, we will adopt discretized notation for this section.
 In particular, our simulation consists of $N$ samples, evenly spaced by $d \tau$ at times $\tau_n = n \times d \tau$.
-In our simulation, we obtain the voltage at the feed output at time $\tau_n$ which we will call $\widetilde{v}_n$. It is related to the input plane wave through the discrete convolution 
+We denote the output voltage at the feed terminals at time $\tau_n$ as $\widetilde{v}_n$. Rewriting the convolution in equation~\ref{eq:Voltage} in discrete notation, we have
 \begin{equation}
-\widetilde{v}_n({\bf \widehat{k}}) = \sum_m \widetilde{r}_m({\bf \widehat{k}}) \widetilde{s}_{n-m}({\bf \widehat{k}}),
+\ftv_n({\bf \widehat{k}}) = \sum_m \ftr_m(\bl) \fts_{n-m}(\bl).
 \end{equation}
@@
 Symbolically,
-\begin{equation}
-{\bf \widetilde{r}}({\bf \widehat{k}}) = \boldsymbol{\mathcal{F}}^{-1} \left[ \frac{\boldsymbol{\mathcal{F}} {\bf \widetilde{v}}({\bf \widehat{k}})}{{\bf \widetilde{s}}({\bf \widehat{k}})} \right] 
+\begin{equation}\label{eq:Inversion}
+\ftr(\bl) = \boldsymbol{\mathcal{F}}^{-1} \left[ \frac{\boldsymbol{\mathcal{F}} {\bf \widetilde{v}}(\bl)}{\boldsymbol{\mathcal{F}}{\fts}(\bl)} \right] 
 \end{equation}
@@
 In Fig.~\ref{fig:FrequencyDomain} we show the amplitude of the Fourier transform of our Gaussian input, centered at $150$\,MHz along with the voltage response.
-Since our input is band limited between $\approx 20$ and $280$\,MHz, the direct ratio of our voltage response and input wave is dominated by numerical noise outside of this range.
-We eliminate these numerical artifacts by multiplying our ratio by a Blackman-Harris window between $100$\,MHz and $200$\,MHz and set our estimate to zero elsewhere.
+Since our input only has support between $\approx 20$ and $280$\,MHz, the direct ratio of our voltage response and input wave is dominated by numerical noise outside of this range.
+We eliminate these artifacts by multiplying our ratio by a Blackman-Harris window between $100$\,MHz and $200$\,MHz and set our estimate to zero elsewhere.
 From a physical standpoint, this is sensible since 21\,cm experiments only observe a limited bandwidth.
@@
 The simple ratio is plotted as a red line.
+All lines are normalized to the amplitude of the input wave at $150$\,MHz.
 Since our input is limited to frequencies between $\approx 20$ and $280$\,MHz, there is significant numerical noise that will effect our result outside of this region which we see in the divergene of the red line towards the edges of the plot.
-To eliminate this noise, we multiply by a Blackman-Harris window between $50$ and $250$\,MHz and set our estimate to zero elsewhere.
+To eliminate this noise, we multiply by a Blackman-Harris window between $100$ and $200$\,MHz and set our estimate to zero elsewhere.
 The Fourier transform of our response estimate with the filter applied is shown as a cyan line.}
@@
 
-We plot the delay transform of the voltage response of the dish in Figure~\ref{fig:Simulations} to gauge the dynamic range of our simulations.
-Since signal at negative delays violates causality, we assume such features are sourced by numerical artifacts such as side-lobes and/or numerical precision noise.
-We see that our simulations have a dynamic range of $-60$\,dB.
+\section{Simulation Results}\label{sec:Results}
+
+We now discuss the results of our simulations.
+In particular, we focus on the time-domain die off of the voltage response and the resulting power kernel (\S~\ref{ssec:Kernel}), comparing it to an identical time-domain simulation of the skirted dipole antenna used by PAPER.
+In \S~\ref{ssec:Subbands} we investigate the dependence of the power kernel on frequency to determine whether specific parts of the HERA bandpass are more effected than others.
+Finally, we verify our simulation framework by performing a separate time domain simulation of a measurement of $S_{11}$ of the dish, comparing to a direct field measurement with a vector network analyzer.
+
+\subsection{The Time Domain Response of the HERA Dish}\label{ssec:Kernel}
+Applying equation~\ref{eq:Inversion} to our simulation, we obtain estimates of the time-domain voltage response of the HERA dish towards zenith which we plot in Fig.~\ref{fig:Simulations}.
+We also conduct a time-domain simulation of the voltage output in response to an identical input plane wave for the skirted dipole PAPER antenna (pictured above the HERA dish in Fig.~\ref{fig:AntennaCompare}) in order to determine whether the presence of the parabolic dish introduces reflections and spectral structure in excess of previous antenna designs for 21\,cm.
+We inspect the absolute value of $\ftv$ for both the PAPER and HERA antennas in Fig.~\ref{fig:SimulationResults}.
+Since non-zero values of $\ftv$ at negative delays violates causality, we assume such features are sourced by numerical artifacts such as side-lobes and/or numerical precision noise which set a limit on the dynamic range of our method.
+In both the PAPER and HERA simulations, the level of the voltage response at negative delays is on the order of $-60$\,dB.
+An obvious difference between the two curves is a knee in the HERA gain at $\approx 120$\,ns that is not present in PAPER, leading to a difference in gain of nearly $20$\,dB at 200\,ns.
+This is an important and perhaps not unsurprising finding: in moving from a skirted dipole to a reflecting dish in order to increase collecting area and overall sensitivity we have added additional chromatic structure.
+
+Our next step is to compute the power kernel given by      equation~\ref{eq:Kernel}.
+Since structure at negative delays in our estimate of $\ftv$ is due to numerical artifacts and sidelobes, we set the voltage response to zero at $\tau<0$ before performing a convolution with its time-reverse complex conjugate.
+In Fig.~\ref{fig:Kernels} we show the power kernel for PAPER and HERA.
+Since both voltage gains drop rapidly with increasing delay, the approximation in equation~\ref{eq:KernelApprox} holds quiet well and we see that the kernels fall off at a rate similar to the response function itself.
 
@@
 We see that these contaminants exist at the $\sim-60$\,dB level.}
-\label{fig:Simulations}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=.5\textwidth]{figures/compare_reflectometry_paper.pdf}
-\caption{Same as Fig.~\ref{fig:Simulations} but now including 
- the reflectometry measurements of \citep{Patra:2015}.
-Inspecting negative delays, we see that the reflectometry measurements contain artifacts introduced by reflections and sub-reflections in the cables leading from the VNA to the feed which enter both the HERA dish and PAPER measurements at both the $-45$\,dB to $-30$\,dB level.
-The VNA measurement is noise dominated beyond $\sim 500$\,ns.}\label{fig:Reflectometry}
+\label{fig:SimulationResults}
 \end{figure}
@@
 \includegraphics[width=.5\textwidth]{figures/compare_kernels_paper.pdf}
-\caption{The response function deconvolved from our simulations (solid lines) compared to the response function estimated from reflectometry measurements described in \citep{Patra:2015} for the HERA dish and the PAPER antenna element.
-Our simulations agree well with the reflectometry results out to $\approx 100$\,ns but disagree by $\lesssim10$\,dB beyond this.
-A potential source of the disagreement is uncalibrated structure are irregularities in the cables connecting the Vector Network Analyzer and the antenna feed which enter at the $-50$\,dB to $-30$\,dB level.}
+\caption{The absolute value of the power kernel for the HERA dish (solid black line) and for the PAPER antenna element (dashed black line) calculated using equation~\ref{eq:Kernel}.
+While an antenna can only physically have a voltage response at positive delays, the delay kernel is formed from the convolution of one antenna with the time reversed response function of the other.
+Hence, the power kernel for two identical antennas will have $\widetilde{R}(\tau) = \widetilde{R}^*(-\tau)$.}
 \label{fig:Kernels}
@@
 \subsection{The Delay Response of Subbands}\label{ssec:Subbands}
+Because the 21\,cm brightness temperature fluctuations evolve with redshift and follow roughly constant statistics over redshift intervals of $\approx 0.5$ \citep{Zaldarriaga:2004} which corresponds to a bandwidth of $8$\,MHz at $z\approx8$.
+Thus, how localized the reflections are within the HERA band will also have significant implications.
 While we observe a long term falloff due to reflections between the feed and dish element, it is possible that these reflections are localized in frequency and do no effect certain sub-bands.
 To determine whether the reflections are localized in frequency, we compute the voltage delay response and power kernel for three different subbands: $100-130$\,MHz, $130-160$\,MHz, and $160-190$\,MHz.
-In order to maintain decent resolution of the kernel itself, we use frequency ranges are larger than the actual subbands that will be used for EoR power spectrum estimation $\sim 10$\,MHz which is set by the interval over which the statistics of the cosmological HI signal are expected to be stationary.
-We plot the delay transforms of the voltage gain in Fig.~\ref{fig:GainDelaySubbands} and the power kernels in Fig.~\ref{fig:KernelsSubbands}.
-The central lobe of the delay kernel is significantly wider due to the the wider window functions incurred by the reduced bandwidth, however, the shallow long-term falloff is only visible within the central $125-175$\,MHz band, indicating that long term reflections are isolated near $150$\,MHz and will not effect power spectrum measurements outside of the very center of our band.
-To further illustrate the observed isolation of fine frequency structure in the center of the bandpass, we fit the $10$\,MHz intervals of the absolute value of the simulated gains to a sixth order polynomial and compare the residuals in Fig.~\ref{fig:Residuals}.
+In order to maintain decent resolution of the kernel itself, we use frequency ranges are larger than the actual subbands that will be used for EoR power spectrum estimation $\sim 10$\,MHz.
+We plot the resulting power kernels in Fig.~\ref{fig:KernelsSubbands}.
+The central lobe of the delay kernel is significantly wider due to the the wider window functions incurred by the reduced bandwidth.
+However, the shallow long-term falloff is only visible within the central $125-175$\,MHz band, indicating that long term reflections are isolated near $150$\,MHz and will not effect power spectrum measurements outside of the very center of our band.
+
+To further illustrate the observed isolation of fine frequency structure in the center of the bandpass and to verify that our observations are not an artifact of our reduction of the simulation outputs, we fit the $10$\,MHz intervals of the absolute value of the simulated gains to a sixth order polynomial and compare the residuals in Fig.~\ref{fig:Residuals}.
 We find that the gain residuals on the sixth order fit are an order of magnitude greater over the $145-155$\,MHz subband than over any other frequency interval.
-
-\begin{figure}[h!]
-\includegraphics[width=.5\textwidth]{figures/voltageResponseSubbands.pdf}
-\caption{The delay transform of the voltage response of the HERA dish for the full 100\,MHz bandwidth (cyan line) along with three subbands; $100-130$\,MHz, $130-160$\,MHz, and $160-190$\,MHz.
-The shallow falloff observed in \S~\ref{sec:Simulations} is most prominent in the $130-160$\,MHz subband while the falloff in the other subbands is close the the level of the sidelobes (at $\sim -50$\,dB for the lower resolution subbands).
-$k_\parallel$ values for each delay are computed at $150$\,MHz.}
-\label{fig:GainDelaySubbands}
-\end{figure}
 
@@
 
-\begin{figure*}
-\includegraphics[width=\textwidth]{figures/frequency_domain_residuals.pdf}
+\begin{figure}
+\includegraphics[width=.5\textwidth]{figures/frequency_domain_residuals.pdf}
 \caption{Residuals on the absolute value of the gain over several subbands after fitting to a sixth order polynomial.
@@
 \label{fig:Residuals}
-\end{figure*}
+\end{figure}
 
-\subsection{Extrapolating the Bandpass and Power Kernel}
+\subsection{Verifying Our Framework with $S_{11}$ Measurements and Simulations}
+
+We now attempt attempt to quantify the accuracy of our time-domain simulation framework by comparing simulations to measurements of the $S_{11}$ parameter of the HERA dish.
+Up until now, our simulations have derived the voltage response of the dish using simulations of an incoming plane wave as is the case for radio signals arriving from objects in space.
+It is possible to probe the gain of the dish using objects in the far field such as known radio sources \citep{Thyagarajan:2011,Pober:2012,Colgate:2015} or constellations of ORBCOMM satellites \citep{Neben:2015,Neben:2016}.
+However natural radio sources are too weak to probe the dish response at the $<10^{-4}$ level necessary to verify our simulations and the ORBCOMM technique can only be used to map the gain at the single frequency that the satellites transmit at, $137$\,MHz.
+Work is currently underway to use broad-band transmitters flown into the far field of the dish by drones \citep{Jacobs:2016} but this system is still under development.
+Reflectometry of the dish using a vector network analyzer is a straightforward alternative used in \citet{Patra:2016} to estimate the gains directly.
+Rather than comparing their estimate of the gain with our predicted gains (which is done in this paper), we instead set up a time domain simulation to compute the $S_{11}$ parameter of HERA antenna and compare it to direct $S_{11}$ measurements.
+\begin{figure}
+\includegraphics[width=.5\textwidth]{figures/s11_compare.pdf}
+\caption{A comparison between time-domain simulations (black lines) and measurements (grey lines) of $S_{11}$ for the HERA dish.
+We also show an $S_{11}$ measurement with the cables leading from the VNA to the feed terminated by an open circuit which allows us to probe the dynamic range of the measurement.
+We use the standard deviation of the open measurement (grey dashed line) between $100$ and $200$\,ns as our systematic floor (grey shaded region).
+We find very good agreement between our $S_{11}$ measurement and the simulation, validating the predictions of our simulations.}
+\label{fig:S11}
+\end{figure}
+For
+
+In our case, $S_{11}$ refers to the complex ratio between a voltage signal transmitted into the feed terminals and the voltage reflected back as a function of frequency, $ S_{11}(f) \equiv v_\text{trans}(f)/v_\text{recv}(f) $.
+We measure $S_{11}$ of a prototype HERA dish at the National Radio Astronomy Observatory Green Bank facility using a vector network analyzer.
+{\bf \color{red} Rich, fill in the details of the VNA measurement, discuss setup, VNA, measurement mode.
+}
+
+Because $S_{11}$ is defined as a ratio in the frequency domain in a form identical to our voltage gains, we may run time-domain simulations similar to those described in \S~\ref{ssec:Simulations} except rather than simulating an incoming plane wave, we simulate the excitation of the feed terminals by an input voltage and record output voltage as a function of time.
+We obtain $S_{11}$ in the same manner that we obtained $\ftr$ using equation~\ref{eq:Inversion} with $\ftv_\text{recv}$ taking the place of $\ftv$ in the numerator inside the Fourier transform and $\ftv_\text{trans}$ taking the place of $\fts$ in the denominator.
+
+In Fig.~\ref{fig:S11} we show the simulated amplitude of $S_{11}$ as a function of frequency for the HERA dish and the PAPER element, observing a distinctive two peaked structure before a steep die off in delay that transitions to a shallower falloff at $\approx 150$\,ns.
+The first peak is due to the reflection of the input wave off of the back of the feed while the second, roughly $35$\,ns later arises from the transmitted component of the input wave reflecting off of the dish and arriving back at the feed.
+The ensuing long term die off arises from reflections within the feed and dish structure and for reasons that will be elaborated on in \citet{Patra:2016} corresponds very closely to our simulations of the dish gain itself (compare with Fig.~\ref{fig:SimulationResults}).
+We get a sense of the dynamic range of the measurement by unhooking the SMA adapter that attaches the sleeved dipole feed to the cable from our VNA, forming an open circuit that should ideally give a reflection coefficient of $\approx 1$ at zero delay with no reflections at any other times.
+In this measurement, we find noise-like structure at $\approx -50$\,dB.
+Below $\approx 500$\,ns, we found that this structure does not integrate down upon extending the VNA integration time, leading us to conclude that it is caused by systematics, likely uncalibrated low level reflections in the VNA-feed cables.
+The level of this noise sets the systematic floor in our measurements which we show as a grey shaded region in Fig.~\ref{fig:S11}.
+We find that in the region where the $S_{11}$ measurement is above the systematics floor, there is good agreement with our simulations (within several dB) and obeying the same trends as our simulation.
+
+\section{The Effect of the HERA dish Chromaticity on Foreground Leakage and Sensitivity}\label{sec:Sensitivity}
+We are now in a position to explore the impact of the Dish's performance on the leakage of foregrounds beyond the wedge, and into the EoR window.
+Beyond the delay kernels considered in this paper and \citep{Patra:2016}, the extent of leakage will depend both on the angular structure of the primary beam, which is established through measurements and simulations in \citep{Neben:2016} and the brightness of the foregrounds themselves.
+In this section, we investigate the amplitude of foreground leakage as a function of delay given the angular primary beam model and our simulation of the delay structure of the dish.
+We start by extrapolating the delay structure observed in our simulations to match HERA's expected frequency resolution (\S~\ref{ssec:Extrapolation}).
+In \S~\ref{ssec:Leakage}, we combine this extrapolated delay response with simulations of foregrounds to determine the overall level of foreground power in HERA's visibilities.
+This leakage will cause large-scale LoS Fourier modes to be contaminated by foregrounds and hence inaccessible to the foreground filtering approach that HERA will employ.
+Since the signal-to-noise ratio is maximized at the smallest $k$ values, the loss of these modes will reduce the significance of the power spectrum detection and negatively impact the overall bottom line of the science that HERA can accomplish.
+We explore the impact of HERA's intrinsic beam chromaticity on science using the Fisher matrix formalism in \S~\ref{ssec:Science}.
+
+\subsection{Extrapolating the Bandpass and Power Kernel}\label{ssec:Extrapolation}
 Our deconvolution gives us the time-domain voltage response of the PAPER and HERA antenna elements.
@@
 In addition, the long term falloff appears as a line on a linear-log plot (Fig.~\ref{fig:Simulations}), indicating that the kernel follows an exponential which we now show is indicative of reflections.
-We do so by adopting the notation of \citep{Patra:2015}.
+We do so by adopting the notation of \citep{Patra:2016}.
 We let $\Gamma_d$ represent the reflection coefficient of the Dish vertex and $\Gamma_f$ represent the reflection coefficient of the feed.
@@
 
-\section{Comparison to Reflectometry Data}\label{sec:Comparison}
-\subsection{The Delay Response at Zenith}
-In Fig.~\ref{fig:Kernels}, we show the filtered response function deconvolved from our electromagnetic simulations.
-The response of the dish rapidly dies off as a function of time.
-After $\approx90$\,ns, we observe lobed structures with a period of $\approx 30$\,ns which corresponds to the geometrical delay between the feed and the dish apex, indicating that the large $\tau$ roll off is dominated by reflections between the feed and the dish.
-
-Our simulations are intended to verify direct reflectometry measurements taken on a prototype of the HERA feed and dish in Green Bank, presented in \citep{Patra:2015}.
-For the readers convenience, we briefly explain the reflectometry measurement here before comparing them to our simulation.
-
-In the reflecometry measurement, a signal is sent from a Vector Network Analyzer (VNA) via a coaxial cable (which is calibrated out) into the back of the feed.
-The VNA than measures the ratio between returned and transmitted power as a function of frequency, $S_{11}(f)$.
-A fundamental difference between the reflectometry measurement and the delay response that we are attempting to obtain is that at zero delay, $S_{11}$ is measureing the reflection of the input wave off of the back of the feed while in the delay response of the antenna, the zero delay reflection is the fraction of the electromagnetic wave off of the sky that is accepted by the feed.
-To obtain $\boldsymbol{\widehat{\rho}}$, we must correct for this difference.
-It is shown in \citep{Patra:2015} that the correction is
-\begin{equation}
-\widehat{\rho}(f) = \frac{\Gamma_a(f)}{1-\Gamma_a(f)} \left[ S_{11}(f) - \Gamma_a(f) \right] + 1 - \Gamma_a(f).
-\end{equation}
-Applying this transformtion to $S_{11}(f)$ and taking a DFT into the time domain over a band of $100-200$\,MHz, we obtain a measurement based estimate of the dish response function at zenith which is plotted in Fig.~\ref{fig:Kernels} alongside our simulation result.
-The general trends of the two two lines agree within $\sim 1-3$\,dB.
-As the long term delay structure of the delay response determines to what extent foregrounds leak out of the wedge, our simulations verify our measurement of the HERA dish's key performance feature.
-
-\subsection{Comparison with the power kernel of the PAPER antenna element}
-We next compare the spectral characteristics of the HERA dish to the PAPER antenna element.
-The PAPER antenna consists of a sleeved dipole element element identical to the one inside of the HERA feed.
-However, rather than being suspended over a dish which greatly enhances the effective collecting area of the antenna, the dipole is placed facing upwards above a rectangular skirt structure that is designed to minimize spectral structure.
-Comparing the relative performances of these two configurations is important since by suspending the dipole upside down over a dish, HERA is potentially trading achromaticity for collecting area.
-Here we comment this tradeoff.
-In order to perform a comparison, we run an identical plane wave simulation of the PAPER dipole element and obtain the power kernel which is shown in Fig.~\ref{fig:Kernels}.
-The striking difference between the PAPER and HERA elements is that the PAPER kernel lacks the transition to a shallow falloff at $\sim 100$\,ns which we should expect given that the long term falloff is likely due to feed-dish reflections.
-{\bf I am here!}
-%\begin{figure}
-%\includegraphics[width=0.5\textwidth]{figures/compareSidelobesNormalized.pdf}
-%\caption{The modulus square of the voltage responses of the HERA dish to plane waves incident from zenith (blue line) along with $20^\circ$,$25^\circ$, and $30^\circ$ off-zenith along the NS line.
-While the sidelobes are suppressed to $\approx 20-25$\,dB at zero delay, they come within $5$\,dB of the zenith response at longer delays which can lead to the level of leakage for a soruce in the sidelobes being comparable to the leakage of a source from zenith.
-The fact that the sidelobes occupy a much larger solid angle with only moderate supression at $\sim 100$\,ns coupled with their proximity to the horizon, suggests that they will dominate supra-horizon emission.}
-%\end{figure}
-
-\section{The Effect of the HERA dish Chromaticity on Foreground Leakage and Sensitivity}\label{sec:Sensitivity}
-Having a thorough understanding of how the chromatic beam of the HERA dish leaks foregrounds into higher delays and a decent picture of the relevant voltage response of the dish itself, we are now in a position to explore the impact of the Dish's performance on the leakage of foregrounds beyond the wedge, and into the EoR window.
-Beyond the delay kernels considered in this paper and \citep{Patra:2015}, the extent of leakage will depend both on the angular structure of the primary beam, which is established in \citep{Neben:2015b} and the model of the foregrounds themselves.
-In this section, we investigate the amplitude of foreground leakage as a function of delay given an angular primary beam model and our simulation of the delay structure of the dish (\S~\ref{ssec:Leakage}).
-
-Spectral leakage due to the chromaticity of the dish will cause large-scale LoS Fourier modes to be contaminated by foregrounds and hence inaccessible to the foreground filtering approach that HERA will employ.
-Since the signal-to-noise ratio is maximized at the smallest $k$ values, the loss of these modes will reduce the significance of the power spectrum detection and negatively impact the overall bottom line of the science that HERA can accomplish.
-We explore the impact of HERA's intrinsic beam chromaticity on science using the Fisher matrix formalism in \S~\ref{ssec:Science}.
-
 \subsection{The Impact of the HERA Beam Chromaticity on Foreground Contamination}\label{ssec:Leakage}
@@
 To answer this question, we combine our extrapolated simulations of the HERA dish's spectral structure with simulations of foregrounds.
-The foreground simulations are described fully in \citep{Thyagarajan:2015c} but for the readers convenience we briefly describe them here.
+The foreground simulations are described fully in \citep{Thyagarajan:2016} but for the readers convenience we briefly describe them here.
 
-Our foreground model consists of two major components: diffuse synchrotron emission from our Galaxy whose structure is described by the Global Sky Model (GSM) of \citet{deOliviaCosta:2008} and a population of point sources sourced by radio loud AGN which combines the NRAO Sky Survey (NVSS) \citep{Condon:1998} at 1.4\,GHz, the Sydney University Mologolo Sky Survey (SUMMS) \citep{Bok:1999} at 843\,MHz, and extrapolate point source fluxes to the observed $100$-$200$\,MHz band using a spectral index of $\langle \alpha \rangle=-0.83$ determined in \citet{Mauch:2003}.
-Visibilities are computed from the diffuse and point source models assuming the achromatic HERA beam computed at $150$\,MHz and described in \citep{Neben:2015c}.
+Our foreground model consists of two major components: diffuse synchrotron emission from our Galaxy whose structure is described by the Global Sky Model (GSM) of \citet{deOliveiraCosta:2008} and a population of point sources sourced by radio loud AGN which combines the NRAO Sky Survey (NVSS) \citep{Condon:1998} at 1.4\,GHz, the Sydney University Mologolo Sky Survey (SUMMS) \citep{Bock:1999} at 843\,MHz, and extrapolate point source fluxes to the observed $100$-$200$\,MHz band using a spectral index of $\langle \alpha \rangle=-0.83$ determined in \citet{Mauch:2003}.
+Visibilities are computed from the diffuse and point source models assuming the achromatic HERA beam computed at $150$\,MHz and described in \citep{Neben:2016}.
 We compute two sets of visibilities: one in which the spectral structure of the dish is assumed to be completely flat, and another in which the beam is multiplied by the Dish's frequency dependent gain at zenith.
-While this model assumes incorrectly that the frequency evolution of the primary beam is identical along all lines of sight, the majority of power enters at the beams point of maximal gain (zenith) and observations of autocorrelations which reflect the angular average of the frequency dependence of all lines of sight agree well with our simulations at zenith \citep{Patra:2015}.
+While this model assumes incorrectly that the frequency evolution of the primary beam is identical along all lines of sight, the majority of power enters at the beams point of maximal gain (zenith) and observations of autocorrelations which reflect the angular average of the frequency dependence of all lines of sight agree well with our simulations at zenith \citep{Patra:2016}.
 
@@
 where $A_e$ is the effective area of the dish, $B$ is the bandwidth, $T_{sys}$ is the system temperature, $\tau$ is the integration time, and $k_B$ is the Boltzmann constant.
-The system temperature can be calculated by assuming that $T_{sys} = 100\text{K} + T_{sky}$ where $100$\,K is the temperature of the PAPER reciever and $T_{sky} = 60 (\lambda/1\,\text{meter} )^{2.55}$ is the sky temperature \citep{Fixsen:2008}.
-For $A_e$ we use the value of $75$\,m determined in \citep{Neben:2015b}.
+The system temperature can be calculated by assuming that $T_{sys} = 100\text{K} + T_{sky}$ where $100$\,K is the temperature of the PAPER reciever and $T_{sky} = 60 (\lambda/1\,\text{meter} )^{2.55}$ is the sky temperature \citep{Fixsen:2011}.
+For $A_e$ we use the value of $75$\,m determined in \citep{Neben:2016}.
 If we assume that each baseline is cleaned independently and that the integration time is $\tau \approx 60$\,s, than the noise level at 150\,MHz is approximately $9.9$\,Jy\,MHz.
@@
 It is well documented that foreground power is maximized over certain LST ranges \citep{Thyagarajan:2015a}, hence such an estimate will either filter or weight appropriately the LSTs in which foreground power is maximized.
-\citet{Thyagarajan:2015c} focuses on the optimal weighting and selection of LST bins in forming a power spectrum estimate.
+\citet{Thyagarajan:2016} focuses on the optimal weighting and selection of LST bins in forming a power spectrum estimate.
 For the purpsoes of our analysis, we focus on a single, relatively clean LST of 4 hours which includes the coldest part of the sky.
@@
 
-\subsection{The Implications of Dish Reflections on EoR Science}
+\subsection{The Implications of Dish Reflections on EoR Science}\label{ssec:Science}
 The primary goal 21\,cm EoR observations is to obtain information about the nature of the sources that drove reionization.
@@
 
-\begin{figure*}[h!]
+\begin{figure*}
 \includegraphics[width=\textwidth]{figures/sigmaVsZ_reionization_v2.pdf}
@@
 Secondly, previous studies assumed a fully illuminated HERA aperture, which for a $14$\,m dish predicts and effective area of $\approx155$\,m$^2$ at $150$\,MHz.
-Electromagnetic simulations and mapping of the primary beam of the HERA dish described in \citep{Neben:2015c} indicate are in good agreement that the effective area of the antenna element is actually $\approx 98$\,m$^2$ at $150$\,MHz which leads to an increase in the overall thermal noise levels by a factor of $\approx 1.5$.
+Electromagnetic simulations and mapping of the primary beam of the HERA dish described in \citep{Neben:2016} indicate are in good agreement that the effective area of the antenna element is actually $\approx 98$\,m$^2$ at $150$\,MHz which leads to an increase in the overall thermal noise levels by a factor of $\approx 1.5$.
 
@@
 We have also used simulations of electromagnetic waves incident from zenith on the primary antenna element on HERA to determine the extent to which reflections and other frequency dependent structure might leak foregrounds into the EoR window.
-The results of our simulations of the zenith gain of the instrument are broadly consistent with data obtained using reflectometry described in \citep{Patra:2015} and can be summarized in the following points.
+The results of our simulations of the zenith gain of the instrument are broadly consistent with data obtained using reflectometry described in \citep{Patra:2016} and can be summarized in the following points.
 \begin{itemize}
@@
 
-\item Simulating the impact of these reflections on foreground leakage using the foreground model described in \citet{Thyagarajan:2015c}, we find that the beam chromaticity extends foregrounds above the level of the cosmological signal to $\approx 350$\,ns beyond the horizon while without the reflections, foregrounds extend above the signal to $\approx 250$\,ns beyond the horizon.
+\item Simulating the impact of these reflections on foreground leakage using the foreground model described in \citet{Thyagarajan:2016}, we find that the beam chromaticity extends foregrounds above the level of the cosmological signal to $\approx 350$\,ns beyond the horizon while without the reflections, foregrounds extend above the signal to $\approx 250$\,ns beyond the horizon.
 These observations are pessimistic in that no attempt to inversely weight the foregrounds by their covaranciances has been attempted.
@@
 \bibliographystyle{apj}
-\bibliography{DishSimulation_paper_v0}
-
-\appendix
-\section{The Effect of Reflections and Cross-Talk on Visibilities}\label{app:Reflections}
-In this section, we investigate, formally, the impact of reflections of electromagnetic waves between antennas and within the signal chain of single antennas on foreground leakage in 21\,cm experiments.
-We start with the time varying electric field from a single source with location ${\bf \widehat{k}}$ on the sky, arriving at antenna $i$ with delay $\tau_i$ and antenna $j$ with delay $\tau_j$ with respect to the electric field at the origin which we denote as $s(t,{\bf \widehat{s}})$.
-We allow for two different types of reflections: First, we allow reflections within the analogue path of each $i^{th}$ antenna which we denote as $r_i(\tau,{\bf \widehat{s}})$.
-We also allow for single reflections between any $i-j$ antenna pair which we denote as $r_{ij}(\tau',{\bf \widehat{s}})$.
-Our choice of arbitrary $\tau'$, for now, allows for multi-path propogation between antennas, though we expect it to be dominated by the geometrical delay between the antenna pair.
-The electric field at antenna $i$ is given by
-\begin{equation}
-s_i(t,{\bf \widehat{s}}) = \int d \tau' r_i(\tau',{\bf \widehat{s}})s(t+\tau_i-\tau') + \sum_{j \ne i} \int d \tau' s(t + \tau_j - \tau_{ij}) r_{ij}(\tau',{\bf \widehat{s}})
-\end{equation}  
-In an FX correlator, the electric field is sampled, Fourier transformed, and cross multipled between antenna pairs to form visibilities. The Fourier transform step leaves us with 
-\begin{equation}
-\widetilde{s}_i(f,{\bf \widehat{s}}) = \widetilde{s}(f,{\bf \widehat{s}}) \left[ \int d \tau' r_i(\tau',{\bf \widehat{s}})e^{2 \pi i(\tau_i - \tau')f} + \sum_{j\ne i} \int d \tau' e^{2 \pi i(\tau_j - \tau_{ij})f} r_{ij}(\tau',{\bf \widehat{s}}) \right]
-\end{equation}
-Multiplying and averaging gives us the visibility for the single source we obtain
-\begin{align}\label{eq:SingleSource}
-v_{ij}'(f,{\bf \widehat{s}}) & = \langle \widetilde{s}_i(f,{\bf \widehat{k}}) \widetilde{s}_j(f,{\bf \widehat{s}}) \rangle_t \nonumber \\
-&=d \Omega  I(f,{\bf \widehat{s}}) g_i(f) g_j^*(f) a_i(f,{\bf \widehat{s}})a_j^*(f,{\bf \widehat{s}}) e^{2 \pi i{\bf u_{ij}} \cdot {\bf \widehat{s}}} + d \Omega I(f,{\bf \widehat{s}}) \sum_{\ell \ne j} g_i(f)a_i(f,{\bf \widehat{s}}) C_{\ell j}^*(f,{\bf \widehat{s}}) e^{2 \pi i {\bf u_{\ell i} \cdot {\bf \widehat{s}}}} \nonumber \\
-& + d \Omega I(f,{\bf \widehat{s}})\sum_{k \ne i} g_j^*(f) a_j^*(f) C_{ki}(f,{\bf \widehat{s}}) e^{2 \pi i {\bf u_{kj}\cdot {\bf \widehat{s}}}} + d \Omega I(f,{\bf \widehat{s}}) \sum_{k\ne i}\sum_{\ell \ne j} C_{ki}(f,{\bf \widehat{s}}) C_{j\ell}^*(f,{\bf \widehat{s}}) e^{2 \pi i {\bf u_{k\ell}}\cdot{\bf \widehat{s}}},
-\end{align}
-where $g_i(f) a_i(f,{\bf \widehat{s}}) = \int d \tau r_i(\tau,{\bf \widehat{s}}) e^{2 \pi i f \tau}$ is the effective direction dependent gain of the system which can be factored into a directoin dependent and direction independent function where $g_i(f)$ is the gain of the analogue signal chain after the radiation has been absorbed by the feed and $a_i(f,{\bf \widehat{s}})$ describes the chromatic electric field response of the antenna.
-The first term in equation~\ref{eq:SingleSource} is an effective visibility with self-reflections.
-The two cross terms and the last term involve the mixing of visibilities complementary too the $ij$ baseline and have the potential to introduce significant chromatic features since they potentially insert visibilities on much longer basline lengths.
-Assuming propogation along a single path directly between the antennas, we may write $C_{ik}(f,{\bf \widehat{s}})$ as
-\begin{equation}
-C_{ki}(f,{\bf \widehat{s}}) = a_i(f,{\bf \widehat{s}}_{ki}) \frac{1}{r_{ik}}\left[\frac{d \sigma_k}{d \Omega}(f,{\bf \widehat{s}},{\bf \widehat{s}}_{ik})\right]^{1/2} e^{2 \pi i \tau_{ik} f}
-\end{equation}
-Where $r_{ik}$ is the distance between antennas $i$ and $k$, $d \sigma_k (f,{\bf \widehat{s}},{\bf \widehat{s}}_{ij})/ d \Omega $ is the cross-section of the antenna to scatter radiation from the ${\bf \widehat{s}}$ direction to the ${\bf \widehat{s}}_{ik}$ direction where ${\bf \widehat{s}}_{ik}$ is the unit vector in the direction between antenna $i$ and antenna $k$.
-Integrating over the primary beam, we obtain a full expression on the effect of the foregrounds.
-\begin{align}
-V_{ij}' = \int d \Omega v_{ij}'(f,{\bf \widehat{s}}) &= g_i(f) g_j(f)^* \int d \Omega A_{ij}(f,{\bf \widehat{s}}) I(f,{\bf \widehat{s}})e^{2 \pi i f {\bf u_{ij}} \cdot {\bf \widehat{s}}} + g_i(f) \sum_{\ell \ne j} \int d \Omega  A_{i\ell j}(f,{\bf \widehat{s}}) I(f,{\bf \widehat{s}})e^{2 \pi i {\bf u_{\ell i} } \cdot {\bf \widehat{s}} } \nonumber \\
-& + g_j^*(f) \sum_{k \ne i}  \int d \Omega A^*_{jki}(f,{\bf \widehat{s}}) I({\bf \widehat{s}},f) e^{2 \pi i {\bf u}_{kj} \cdot {\bf \widehat{s}} } + \sum_{k \ne i} \sum_{\ell \ne j}\int d \Omega A_{k i \ell j}(f,{\bf \widehat{s}}) I(f,{\bf \widehat{s}})e^{2 \pi i {\bf u}_{k\ell} \cdot {\bf \widehat{s}}}
-\end{align}
-which is essentially an ad-mixture of many baselines with different effective primary beams.
-We denote the effective primary beam of the $i,j$ antenna pair as $A_{ij}(f,{\bf \widehat{s}})=a_i(f,{\bf \widehat{s}})a_j^*(f,{\bf \widehat{s}})$, the effective beam from a single reflection correlated with a direct measurement as $A_{i \ell j} = a_i(f,{\bf \widehat{s}}) C^*_{\ell j}(f,{\bf \widehat{s}})$ and the correlation between entirely reflected terms as experiencing an effective primary beam of $A_{k i \ell j}=C_{ki}(f,{\bf \widehat{s}}) C^*_{j \ell}(f,{\bf \widehat{s}})$.
-In this paper, we focus on the reflection terms within a single antenna element.
-Hence, we ignore all but the first term for now.
-Any reflection terms occurring downstream of the conversion by the feed from electromagnetic radiation to voltage are lumped into $g_i(f)$ and reflections occurring within the antenna element enter into $a_i(f,{\bf \widehat{s}})$.
-While reflections within the analogue system are a potential source of contamination, HERA's post-feed analogue signal path is designed to keep all reflections under 35\,m, within the wedge.
-
-The focus of this paper and its companions is the reflection properties of the primary antenna element, so we will focus the rest of our discussion here on $a_i(f,{\bf \widehat{s}})$.
-The primary elements of our dish include a feed and backplane suspended over a fourteen meter dish.
-We assume a set of discrete reflections within the dish, which without loss of generality are assumed to have frequency independent reflection coefficients\footnote{If we allow each coefficient to be frequency dependent, we can expand each frequency dependent term in a Fourier series of frequency independent terms} hence
-\begin{equation}
-a_i(f,{\bf \widehat{s}}) = \sum_{n} r_n({\bf \widehat{s}}) e^{2 \pi i  \tau_n f}
-\end{equation}
-Assuming all antennas are identical, we have
-\begin{equation}
-A_{ij}(f,{\bf \widehat{s}}) = \sum_m \sum_n r_n({\bf \widehat{s}}) r_m^*({\bf \widehat{s}}) e^{2 \pi i(\tau_n-\tau_m)f} = \sum_\alpha A_\alpha({\bf \widehat{s}}) e^{2 \pi i \tau_\alpha}
-\end{equation}
-where we have re-indexed $m$ and $n$ under a single greek index $\alpha$ in the second equality. The effect of internal reflections on a visibility is hence
-\begin{equation}
-V_{ij}'= \sum_\alpha \int d \Omega A_\alpha({\bf \widehat{s}}) e^{2 \pi i \tau_\alpha f} e^{2 \pi i {\bf b}_{ij} \cdot {\bf \widehat{s}}f/c} I(f,{\bf \widehat{s}})
-\end{equation}
-Taking the delay transform, one obtains
-\begin{equation}
-\widetilde{V}_{ij}'(\tau) = \sum_\alpha \widetilde{V}_{ij}^\alpha (\tau - \tau_\alpha)
-\end{equation}
-where 
-\begin{equation}
-\widetilde{V}^\alpha_{ij}(\tau) = \int d \tau e^{-2 \pi i f \tau} \int d \Omega A_\alpha({\bf \widehat{s}}) e^{2 \pi i {\bf b}_{ij} \cdot {\bf \widehat{s}} f/c} I(f,{\bf \widehat{s}})
-\end{equation}
-is the usual delay transform of \citet{Parsons:2012}. $\widetilde{V}_{ij}^alpha(\tau)$.
+\bibliography{DishSimulation_paper}
 \end{document}

### 2016-01-31 DishSimulations/paper/DishSimulationsPaper_v3.tex
incorporated Rich's information into simulations paper draft. Still need to add two numbers

--- 2016-01-26 DishSimulations/paper/DishSimulationsPaper_v2.tex
@@
 \usepackage{color}
+\usepackage{hyperref}
 \citestyle{aa}
@@
 \begin{document}
-\title{The Hydrogen Epoch of Reionization Array Dish: Characterization with Electromagnetic Simulations}
+\title{The Hydrogen Epoch of Reionization Array Dish II: Characterization of Spectral Structure with Electromagnetic Simulations and their Science Implications}
 \author{
@@
 Our simulations show the existence of standing wave reflections in some regions of the 100-200\,MHz bandpass with an amplitude of $\approx -35$\,dB at 100\,ns which can lead to some loss of measurable modes and a modest reduction in sensitivity over a small segment of the band.
-Overall, we find that the spectral response of the dish is sufficiently smooth for proven foreground isolation methods such as delay filtering to contain foreground emission at line of sight wave numbers below $k_\parallel = 0.15-0.2$\,$h$Mpc$^{-1}$.
+We find that the spectral response of the dish is sufficiently smooth for proven foreground isolation methods such as delay filtering to contain foreground emission at line of sight wave numbers below $k_\parallel = 0.15-0.23$\,$h$Mpc$^{-1}$.
 Incorporating these results into a Fisher Matrix analysis, we find that the spectral structure observed in our simulations has only a small effect on the overall constraints on the astrophysics of reionization that HERA will achieve, allowing it to serve as a benchmark for the design of future instruments such as the Square Kilometer Array.
@@
 \section{Introduction}
-Observations of the redshift 21\,cm radiation neutral hydrogen in the intergalactic medium (IGM) have the potential to illuminate the hitherto unobserved {\it dark ages} and {\it cosmic dawn}, revolutionizing our understanding of the first UV and X-ray sources in the universe and how their properties influenced galactic evolution (see \citet{Furlanetto:2006Review}, \citet{Morales:2010}, and \citet{Pritchard:2012} for reviews).
-As of now, two major experimental endeavors are underway to make a first detection of the 21\,cm signal with most focusing on the Epoch of Reionization (EoR) in which UV photons from early galaxies transformed the hydrogen in the universe from neutral to ionized.
+Observations of the redshift 21\,cm radiation from neutral hydrogen in the intergalactic medium (IGM) have the potential to illuminate the hitherto unobserved {\it dark ages} and {\it cosmic dawn}, revolutionizing our understanding of the first UV and X-ray sources in the universe and how their properties influenced galactic evolution (see \citet{Furlanetto:2006Review}, \citet{Morales:2010}, and \citet{Pritchard:2012} for reviews).
+Two major experimental endeavors are underway to make a first detection of the 21\,cm signal with most focusing on the Epoch of Reionization (EoR) in which UV photons from early galaxies transformed the hydrogen in the universe from neutral to ionized.
 The first involves measuring the sky-averaged global signal and is being pursued by experiments such as EDGES \citep{Bowman:2010}, LEDA \citep{Greenhill:2012,Bernardi:2015}, DARE \citep{Burns:2012}, SciHi \citep{Voytek:2014}, and BIGHORNS \citep{Sokolowski:2015} either in their planning stages or already taking data.
@@
 The primary obstacle to obtaining a high redshift detection of the cosmological signal through both of these methods is the existence of foregrounds that are $\sim 10^5-10^6$ times brighter.
-While requiring much greater sensitivity than global-signal experiments, interferometers have the advantage that spectrally smooth foregrounds are naturally contained to a finite region of Fourier space, corresponding to large line of sight scales, known as the {\it wedge} \citep{Datta:2010,Vedantham:2012,Parsons:2012,Thyagarajan:2013,Liu:2014a,Liu:2014}.
+While requiring much greater sensitivity than global-signal experiments, interferometers have the advantage that spectrally smooth foregrounds are naturally contained to a finite region of Fourier space, corresponding to large line of sight scales, known as the {\it wedge} \citep{Datta:2010,Vedantham:2012,Parsons:2012,Thyagarajan:2013,Liu:2014a,Liu:2014b}.
 However any structure in the frequency response of the instrument is imprinted on the foregrounds and has the potential to leak power into the {\it EoR window} at small line of sight scales, masking the signal.
@@
 While, in principle, spectral structure in the bandpass of the instrument may be removed in calibration, simulations show that any mismodeling of emission and the primary beam, potentially below the confusion limit, will mix the significant spectral structure introduced by the wedge on long baselines into short ones, masking the signal entirely \citep{Barry:2016}.
-While redundant calibration \citep{Wieringa:1992,Liu:2011,Zheng:2014} is able to solve for gains that are primarily independent of a detailed model of the sky, it is unclear how one might remove direction-dependent chromatic structure that might be present in the primary beam of the instrument.
+While redundant calibration \citep{Wieringa:1992,Liu:2010,Zheng:2014} is able to solve for gains that are primarily independent of a detailed model of the sky, it is unclear how one might remove direction-dependent chromatic structure that might be present in the primary beam of the instrument without deferring to a model.
 Because of our limited knowledge of foregrounds at low frequency and the fidelity of calibration algorithms, it is imperitive to design experiments whose spectral structure is contained, as much as possible, to low delays.
@@
 Much of this sensitivity increase is enabled by moving the collecting area of the instrument into baselines that are located primarily inside of the EoR window and a switch from PAPER's skirted dipoles and the MWA's phased dipole arrays to an antenna element that consists of a feed suspended over a large reflecting parabolic dish.
-A central requirement for HERA's dish design is that the antenna have a response that is sufficiently smooth in frequency and centralized enough in its angular response that it leaves the EoR window free of contamination since one cannot rely on direction independent redundant calibration to remove any spectral structure that varies as a function of location on the primary beam.
+A central requirement for HERA's dish design is that the antenna have a response that is sufficiently smooth in frequency and centralized enough in its angular response that it leaves the EoR window free of contamination.
 
-This paper and its companions \citep{Neben:2016,Patra:2016,Thyagarajan:2016} describe a multifaceted approach for assessing whether the HERA dish meets the requirements for isolating foregrounds within the wedge and leaving the EoR window clean.
-We accomplish this by establishing a spec with simulations of foregrounds \citep{Thyagarajan:2016} and verifying that HERA primary antenna element meets this spec with reflectometry \citep{Patra:2016} and Orbcomm beam mapping \citep{Neben:2016}.
-In this work, we present the results of time-domain electromagnetic simulations that are intended to predict the degree of spectral structure in the HERA dish, assess the impact of this spectral structure on the leakage of foregrounds into the EoR window, and to verify the reflectometry measurements taken in the field by \cite{Patra:2016}.
+This paper and its companions \citep{Neben:2016,Patra:2016,Thyagarajan:2016} describe a multi-pronged campaign to assess whether the HERA dish meets the requirements for isolating foregrounds within the wedge and leaving the EoR window clean.
+We accomplish this by establishing a spec with simulations of foregrounds \citep{Thyagarajan:2016} and verifying that HERA primary antenna element meets this spec with reflectometry \citep{Patra:2016} and ORBCOMM beam mapping \citep{Neben:2016}.
+In this work, we present the results of time-domain electromagnetic simulations that are intended to predict the degree of spectral structure in the HERA dish, assess the impact of this spectral structure on the leakage of foregrounds into the EoR window, and to verify the reflectometry measurements taken in the field.
 
@@
 In \S~\ref{sec:Simulations} we describe our time-domain electromagnetic simulations of the HERA dish element and how we extract the voltage response function.
-In \S~\ref{sec:SimulationResults} we describe the results and verify our simulation framework by comparing its prediction of the $S_{11}$ parameter of the HERA dish to direct field measurements described in \citep{Patra:2016}.
-In \S~\ref{sec:Foregrounds} we apply our electromagnetic simulation results to simulations of foregrounds to determine the extent that the HERA dish's chromatic structure pollutes the EoR window and their impact on HERA's overall sensitivity.
+In \S~\ref{sec:Results} we describe the results and verify our simulation framework by comparing its prediction of the $S_{11}$ parameter of the HERA dish to direct field measurements described in \citep{Patra:2016}.
+In \S~\ref{sec:Sensitivity} we apply our electromagnetic simulation results to a foreground model to determine the extent that the HERA dish's chromatic structure pollutes the EoR window and their impact on HERA's ability to constrain reionization parameters.
 We conclude in \S~\ref{sec:Conclusion}.
@@
 Intuitively, any reflections in the signal path introduce sinusoidal ripples in the frequency dependent gain of the instrument.
-Since time delay is the Fourier dual to frequency, reflections with larger delays introduce ripples at higher frequencies.
-Isolation of the 21\,cm signal from foregrounds that are over five orders of magnitude brighter depends critically on their smoothness.
+Since time delay is the Fourier dual to frequency, reflections with larger delays introduce ripples with shorter periods.
+Isolation of the 21\,cm signal from foregrounds that are over four orders of magnitude brighter depends critically on their smoothness.
 Any sinusoidal frequency structure introduced by the reflections will cause these foregrounds to mimic and swamp the signal unless they are brought below a level similar to the ratio between the foregrounds and the signal itself.
-A simple equation describing effect of direction independent reflections in the signal chain of an interferometer, downstream of the receiver on a visibility has been derived in \citet{EwallWice:2015a}.
+A simple equation describing effect of direction independent reflections in the signal chain downstream of the feed, has been derived in \citet{EwallWice:2015a}.
 We now extend this analysis by considering the direction dependent reflections that can occur within the antenna element.
-We start by denoting the electric field of radiation arriving at an $i^{th}$ antenna element at position $\bx_i$ and time $t_i = t + \bl \cdot \bx_i /c \equiv t+\tau_i$ as $\fts(\bl,\bx_i,t_i)$.
+We start denote the electric field of radiation arriving from direction ${\bf \ell}$ at the $i^{th}$ antenna element at position $\bx_i$ and time $t_i = t + \bl \cdot \bx_i /c \equiv t+\tau_i$ as $\fts(\bl,\bx_i,t_i)$.
 
@@
 
-A correlator measures the time-averaged product of the Fourier transform of the voltage streams between the $i^{th}$ and $j^{th}$ antenna.
+The correlator of a radio interferometer records the time-averaged product of the Fourier transfored voltage streams of the $i^{th}$ and $j^{th}$ antennas.
 Fourier transforming the voltage stream from the $i^{th}$ antenna we obtain
@@
 V_{ij}'(f) &= \left \langle v_i(f) v_j^*(f) \right \rangle_t \nonumber \\
- &= \int d \Omega d \tau d \tau' \ftr_i(\tau) \ftr^*_j(\tau')e^{-2 \pi i f (\tau-\tau') } I(\bl, f) e^{- 2 \pi i \Delta \tau_{ij}f} 
+ &= \int d \Omega d \tau d \tau' \ftr_i(\bl,\tau) \ftr^*_j(\bl,\tau')e^{-2 \pi i f (\tau-\tau') } I(\bl, f) e^{- 2 \pi i \Delta \tau_{ij}f} 
 \end{align}
@@
 \end{equation}
-where ${\bf b}_{ij} = ({\bf x}_i - {\bf x}_j )$ to use the usual $uv$ notation of interferometry.
-$r_i(\bl,f)$ is the inverse fourier transform of the reflection response of the dish, hence we see that the reflection response is precisely the Fourier dual to the Dish's frequency domain voltage beam.
+where ${\bf b}_{ij} = ({\bf x}_i - {\bf x}_j )$ and $r_i(\bl,f)$ is the inverse fourier transform of the reflection response of the dish.
+From equation~\ref{eq:Visibility} we see that $r_i(\bl,f)$ is precisely the voltage beam of the antenna.
 Setting a specification on reflections is hence equivalent to setting a specification on the spectral smoothness of the antenna's voltage beam.
 
-In order to filter spectrally smooth foregrounds from the signal,HERA is expected to employ the {\it delay transform} over frequency, defined as \citep{Parsons:2012}
+In order to filter spectrally smooth foregrounds from the signal, numerous experiments expect to employ the {\it delay transform} over frequency, defined as \citep{Parsons:2012}
 \begin{equation}
@@
 Without reflections, the sources would form lines in $b-\tau$ space.
-Withthe reflections, the sources are smeared out, leading to supra-horizon emission.
+With the reflections, the sources are smeared out, leading to supra-horizon emission.
 \begin{figure*}
 \includegraphics[width=\textwidth]{figures/wedgeCompare.pdf}
-\caption{A demonstration of the impact on foregrounds of the frequency dependent beam.
+\caption{A cartoon demonstration of the impact on foregrounds of the frequency dependent beam.
 Left: The location of three sources in delay space assuming a frequency indepdendent beam (no reflections in the antenna element).
@@
 Since the frequency response of the dish are a function of direction on the sky, the shape of the delay kernel is different for each source line.
-We see that this smearing can lead to substantial supra-horizon emission.
-Sources near zenith (low delay) tend to have a larger maximum since the beam gain is larger near zenith, but a more compact kernel (since beam bore-sights tend to have less spectral structure).
-Meanwhile, sources near the horizon have a much smaller maxima but have less compact kernels.}
+We see that this smearing can lead to substantial supra-horizon emission.}
 \label{fig:Smearing}
 \end{figure*}
-For the sake of pedagogy, we now consider the case where the beam can be factored into angular and frequency independent components, $r_i(\bl,f) = g_i(f)a_i(\bl)$.
+For the sake of simplicity, we now consider the case where the beam can be factored into angular and frequency independent components, $r_i(\bl,f) = g_i(f)a_i(\bl)$.
 For such a case, every line in Fig.~\ref{fig:Smearing} would be convolved with the same delay dependent shape, normalized to the gain of $a_i(\bl)$.
@@
 \end{equation}
-where $V_{ij}$ is the visibility with the achromatic factor in the voltage patterns included. 
+where $V_{ij}$ is the visibility for the achromatic voltage pattern, $a_i(\bl)$. 
 We can gain further insight into the behavior of the delay kernel arising from chromaticity by assuming that $\widetilde{g}_i(\tau=0)\gg\widetilde{g}_i(\tau>0)$, which should be the case at large delays for the smooth bandpasses our instruments are designed to have.
@@
 Hence, to first order, the impact of reflections is to convolve the delay-transformed visibility with the voltage beam of the instrument.
-This may be a somewhat un-intuitive result since naive dimensional analysis might predict that the power-kernel to be proportional to the square of the delay-response.
-This linear falloff coupled with the enormous dynamic range between foregrounds and signal puts exquisite requirements on the smoothness of the beam, requiring that it fall roughly six orders of magnitude in the regions of delay space that we want to measure the signal.
+This may be a somewhat un-intuitive result since naive dimensional analysis might predict that the power-kernel is proportional to the square of the delay-response.
+This linear falloff coupled with the enormous dynamic range between foregrounds and signal puts exquisite requirements on the smoothness of the beam, requiring that it fall five to six orders of magnitude in the regions of delay space that we want to measure the signal.
 
@@
 
-HERA \citep{DeBoer:2016} is an instrument designed to detect the power spectrum of 21\,cm brightness temperature fluctuations during the EoR at high signal-to-noise between the frequencies of 100 and 200\,MHz (redshifts 6 to 12) \citep{Pober:2014}.
+HERA \citep{Pober:2014,DeBoer:2016} is an instrument designed to detect the power spectrum of 21\,cm brightness temperature fluctuations during the EoR at high signal-to-noise between the frequencies of 100 and 200\,MHz (redshifts 6 to 12).
 Its initial, 19-element, buildout is currently taking first observations in the Karoo in South Africa.
@@
 Central to increasing the collecting area of each element is a switch from dipoles (used by the MWA and PAPER) to feeds suspended over large 14\,m diameter parabolic dishes.
-In Fig.~\ref{fig:AntennaComparison} we show one of the initial 19 dishes currently being deployed in South Africa at the same site as PAPER whose antenna we also show at the top of the figure.
+In Fig.~\ref{fig:AntennaCompare} we show one of the initial 19 dishes currently being deployed in South Africa at the same site as PAPER whose antenna we also show at the top of the figure.
 
@@
 \includegraphics[width=.5\textwidth]{figures/PAPER_HERA_compare.jpg}
-\caption{The HERA antenna element (bottom) uses a parabolic dish to achieves over an order of magnitude increase in collecting area over the PAPER antenna (top).
+\caption{The HERA antenna element (bottom) uses a parabolic dish to achieve an order of magnitude increase in collecting area over the PAPER antenna (top).
 The sleeved dipole in the center of the PAPER backplane is identical to the sleeved dipole being suspended under the cylindrical skirt over the vertex of the HERA dish.
@@
 \subsection{The Simulations}\label{ssec:Simulations}
-We perform time-domain simulations of the voltage output of the HERA feed using CST.
-{\bf \color{red} Rich: fill in the details here, describe the CST parameters and a brief overview of how it numerically solves for the voltages (citations?).
-}
+ The time-dependent electromagnetic behavior of the antenna was modeled using Microwave Studio, a commercial numerical simulation package produced by Computer Simulation Technology (CST).
+The model consists of an idealized 14 m diameter paraboloid reflector with a feed structure placed at the focus (4.5 m above the surface).
+The feed was a dual linear polarized sleeved dipole identical to that used as an element of PAPER but with a cylindrical skirt used in place of the angled planar reflectors.
+The dipole arms were modeled as copper tubing and aluminum was assigned to the disks and reflector surfaces.
+For simulation, the entire model was encapsulated in vacuum dielectric with radiative boundaries and discrete ports of 125\,$\Omega$ impedance were defined at the terminals of the orthogonal dipoles.
+
+Microwave Studio divides the model into approximately 94 million discrete hexahedral cell,s where the field is calculated over time using Finite Integration Technique incorporating the Perfect Boundary Approximation \citep{CST} in response to a 100-200 MHz broadband pulse of about 40 ns in duration.
+The model was excited in two ways: 1) via a plane wave entering the model along the bore sight, and 2) from one of the discrete terminals (whose analysis we focus on in \S~\ref{ssec:S11}).
+The voltage responses at the terminals are monitored for these two cases over a duration of 500 ns as the excitation pulse travels throughout the model.
 
@@
 The delay between the primary envelopes of the plane wave and the voltage output of the feed is $\approx 30$\,ns which corresponds to the round trip travel time from the feed to the dish vertex and back.
-However, while the input plane wave, modulated by a gaussian, falls off rapidly and dies off after the first $\approx 20$\,ns after its peak, we see that the voltage output decays far more slowly with delay due to reflections within the dish-feed structure reintroducing the signal at times beyond its initial falloff.
+However, while the input plane wave, modulated by a gaussian, falls off rapidly and dies off after the first $\approx 20$\,ns after its peak, we see that the voltage output decays far more slowly due to reflections within the dish-feed structure.
 We are able to get a qualitative feel for the amplitude of the reflections by inspecting the falloff of the time domain voltage response and see that after $60$\,ns it reachs $\approx -25$\,dB.
@@
 \includegraphics[width=.5\textwidth]{figures/One_dish_Pfeed_render_pw_0deg.png}
-\caption{A rendering of our time domain simulation at $t=0$, demonstrating the geometry and setup of our electromagnetic simulation.
-The plane wave is started just above the feed (red plane).}\label{fig:SimulationSetup}
+\caption{A rendering of our simulation setup at $t=0$. The plane wave is started just above the feed (red plane).}\label{fig:SimulationSetup}
 \end{figure}
@@
 \caption{An illustration of our simulation products and their origin in the HERA antenna geometry.
-A plane wave is injected from above the feed (red line).
-The amplitude of the electric field of the plane wave at output of the feed along with the voltage at the feed terminal outputs is recorded (black line).
+A plane wave is injected from above the feed.
+The electric field of the plane wave at the feed terminals (red line) along with the voltage output is recorded (black line).
 The feed in our simulation is situated $5$\,m above the bottom of the dish, hence there is a $\approx 30$\,ns delay between when the plane wave passes the terminal for the first time (A) and when it is first absorbed in the dipole (B), leading to the voltage response.
@@
 From equation~\ref{eq:Voltage}, we know that the voltage output results from the convolution of the plane wave input with the voltage gain of the antenna.
-The voltage response of the dish which we are attempting to probe has been convolved with a known kernel; our input plane wave.
-Hence, a straightforward application of the Fourier convolution theorem allows us to determine the voltage response.
+Since we know the input wave, a straightforward application of the Fourier convolution theorem allows us to determine the voltage response.
 
@@
 PAPER's correlator, which will initially serve as the HERA backend samples over a $100$\,MHz instantaneous freqeuency interval.
-Hence analogue filtering is applied to limit the incoming signal within a finite bandwidth and prevent aliasing.
+Hence analogue filtering is applied to limit the incoming signal within this range to prevent aliasing.
 
@@
 \includegraphics[width=.5\textwidth]{figures/frequency_domain.pdf}
-\caption{The absolute value of the discrete Fourier transform of our simulation outputs.
-We obtain the effective response function of the dish by Fourier transforming the voltage output from our dish (green line) and dividing by the Fourier transform of the input wave (blue line).
-The simple ratio is plotted as a red line.
-All lines are normalized to the amplitude of the input wave at $150$\,MHz.
-Since our input is limited to frequencies between $\approx 20$ and $280$\,MHz, there is significant numerical noise that will effect our result outside of this region which we see in the divergene of the red line towards the edges of the plot.
-To eliminate this noise, we multiply by a Blackman-Harris window between $100$ and $200$\,MHz and set our estimate to zero elsewhere.
-The Fourier transform of our response estimate with the filter applied is shown as a cyan line.}
+\caption{The absolute value of the Fourier transform of the voltage output from our dish (green line) and the input wave (blue line), normalized to the amplitude of the input wave at $150$\,MHz.
+The ratio between input and output is plotted as a red line.
+Since our input is limited to frequencies between $\approx 20$ and $280$\,MHz, there are significant numerical artifacts in the ratio that causes divergence towards the plot edges.
+To eliminate this noise, we multiply by a Blackman-Harris window between $100$ and $200$\,MHz and set our estimate to zero elsewhere (cyan line).}
 \label{fig:FrequencyDomain}
@@
 
-\section{Simulation Results}\label{sec:Results}
+se\section{Simulation Results}\label{sec:Results}
 
@@
 In particular, we focus on the time-domain die off of the voltage response and the resulting power kernel (\S~\ref{ssec:Kernel}), comparing it to an identical time-domain simulation of the skirted dipole antenna used by PAPER.
-In \S~\ref{ssec:Subbands} we investigate the dependence of the power kernel on frequency to determine whether specific parts of the HERA bandpass are more effected than others.
-Finally, we verify our simulation framework by performing a separate time domain simulation of a measurement of $S_{11}$ of the dish, comparing to a direct field measurement with a vector network analyzer.
+In \S~\ref{ssec:Subbands} we investigate the dependence of the power kernel on frequency to determine whether specific parts of the HERA bandpass are more affected than others.
+Finally, in \S~\ref{ssec:S11} we verify our simulation framework by comparing a separate time domain simulation of $S_{11}$ of the HERA dish to a direct field measurement with a vector network analyzer (VNA).
 
 \subsection{The Time Domain Response of the HERA Dish}\label{ssec:Kernel}
-Applying equation~\ref{eq:Inversion} to our simulation, we obtain estimates of the time-domain voltage response of the HERA dish towards zenith which we plot in Fig.~\ref{fig:Simulations}.
-We also conduct a time-domain simulation of the voltage output in response to an identical input plane wave for the skirted dipole PAPER antenna (pictured above the HERA dish in Fig.~\ref{fig:AntennaCompare}) in order to determine whether the presence of the parabolic dish introduces reflections and spectral structure in excess of previous antenna designs for 21\,cm.
+Applying equation~\ref{eq:Inversion} to our simulation, we obtain estimates of the time-domain voltage response of the HERA dish towards zenith which we plot in Fig.~\ref{fig:SimulationResults}.
+We also conduct a time-domain simulation of the voltage output in response to an identical input plane wave for the skirted dipole PAPER antenna (pictured above the HERA dish in Fig.~\ref{fig:AntennaCompare}) in order to determine whether the presence of the parabolic dish introduces reflections and spectral structure in excess of previous successful antenna designs\footnote{To date, PAPER has produced the most stringent limits on the 21\,cm power spectrum leading us to use its design as a standard}.
 We inspect the absolute value of $\ftv$ for both the PAPER and HERA antennas in Fig.~\ref{fig:SimulationResults}.
-Since non-zero values of $\ftv$ at negative delays violates causality, we assume such features are sourced by numerical artifacts such as side-lobes and/or numerical precision noise which set a limit on the dynamic range of our method.
-In both the PAPER and HERA simulations, the level of the voltage response at negative delays is on the order of $-60$\,dB.
-An obvious difference between the two curves is a knee in the HERA gain at $\approx 120$\,ns that is not present in PAPER, leading to a difference in gain of nearly $20$\,dB at 200\,ns.
-This is an important and perhaps not unsurprising finding: in moving from a skirted dipole to a reflecting dish in order to increase collecting area and overall sensitivity we have added additional chromatic structure.
+Since non-zero values of $\ftv$ at negative delays violates causality, we assume such features are sourced by numerical artifacts such as side-lobes and/or numerical precision noise which sets a limit of $\approx -60$\,dB on the dynamic range of our method.
+An obvious difference between the two curves is a knee in the HERA gain at $\approx 120$\,ns that is not present in PAPER, leading to an increase in gain of nearly $20$\,dB at 200\,ns.
+This is an important and perhaps not unsurprising finding: in moving from a skirted dipole to a reflecting dish to increase collecting area and overall sensitivity we have added additional chromatic structure from reflections between the dish and the feed.
 
-Our next step is to compute the power kernel given by      equation~\ref{eq:Kernel}.
+Our next step is to compute the power kernel, $\widetilde{R}$, given by equation~\ref{eq:Kernel}.
 Since structure at negative delays in our estimate of $\ftv$ is due to numerical artifacts and sidelobes, we set the voltage response to zero at $\tau<0$ before performing a convolution with its time-reverse complex conjugate.
-In Fig.~\ref{fig:Kernels} we show the power kernel for PAPER and HERA.
+In Fig.~\ref{fig:Kernels} we show the resulting power kernel for PAPER and HERA.
 Since both voltage gains drop rapidly with increasing delay, the approximation in equation~\ref{eq:KernelApprox} holds quiet well and we see that the kernels fall off at a rate similar to the response function itself.
@@
 \includegraphics[width=.5\textwidth]{figures/compare_simulations_paper.pdf}
-\caption{The Fourier transform of the voltage response function of our simulation for the HERA Dish (solid black line) and the PAPER antenna element (dashed black line).
+\caption{The Fourier transform of the simulated voltage response of the HERA Dish (solid black line) and the PAPER antenna element (dashed black line).
 Reflections in the HERA dish element lead to significantly enhanced power above $\sim 50$\,ns.
-We show the negative delays, which should be devoid of signal, to determine the dynamic range of our technique (which is limited by sidelobes and numerical artifacts).
-We see that these contaminants exist at the $\sim-60$\,dB level.}
+Since negative delays should be devoid of signal, they allow us to determine the dynamic range of our simulations which have a numerical noise/sidelobes floor of $-60$\,dB.}
 \label{fig:SimulationResults}
@@
 \caption{The absolute value of the power kernel for the HERA dish (solid black line) and for the PAPER antenna element (dashed black line) calculated using equation~\ref{eq:Kernel}.
-While an antenna can only physically have a voltage response at positive delays, the delay kernel is formed from the convolution of one antenna with the time reversed response function of the other.
+While an antenna can only physically have a voltage response at positive delays, the delay kernel is formed from the convolution of one antenna with the time reversed conjugate response function of the other.
 Hence, the power kernel for two identical antennas will have $\widetilde{R}(\tau) = \widetilde{R}^*(-\tau)$.}
@@
 \subsection{The Delay Response of Subbands}\label{ssec:Subbands}
-Because the 21\,cm brightness temperature fluctuations evolve with redshift and follow roughly constant statistics over redshift intervals of $\approx 0.5$ \citep{Zaldarriaga:2004} which corresponds to a bandwidth of $8$\,MHz at $z\approx8$.
-Thus, how localized the reflections are within the HERA band will also have significant implications.
-While we observe a long term falloff due to reflections between the feed and dish element, it is possible that these reflections are localized in frequency and do no effect certain sub-bands.
+Because the 21\,cm brightness temperature fluctuations evolve over redshift intervals of $\Delta z \gtrsim 0.5$ \citep{Zaldarriaga:2004}, experiments will sub-divide their bands into $\approx 10$\,MHz intervals before attempting their estimates.
+Thus the localization of reflections within the HERA band will determine whether all or only a subset of redshifts are affected.
 To determine whether the reflections are localized in frequency, we compute the voltage delay response and power kernel for three different subbands: $100-130$\,MHz, $130-160$\,MHz, and $160-190$\,MHz.
-In order to maintain decent resolution of the kernel itself, we use frequency ranges are larger than the actual subbands that will be used for EoR power spectrum estimation $\sim 10$\,MHz.
-We plot the resulting power kernels in Fig.~\ref{fig:KernelsSubbands}.
-The central lobe of the delay kernel is significantly wider due to the the wider window functions incurred by the reduced bandwidth.
-However, the shallow long-term falloff is only visible within the central $125-175$\,MHz band, indicating that long term reflections are isolated near $150$\,MHz and will not effect power spectrum measurements outside of the very center of our band.
+In order to maintain decent resolution of the kernel itself, we use frequency ranges are several times larger than the actual subbands that will be used for EoR power spectrum estimation ($\approx 10$\,MHz).
+The resulting power kernels are plotted in Fig.~\ref{fig:KernelsSubbands}.
+The central lobe of the subband kernels is significantly wider due to the the wider window functions incurred by the reduced bandwidth.
+However, the shallow long-term falloff is only visible within the central $130-160$\,MHz band, indicating that long term reflections are isolated around $150$\,MHz.
 
-To further illustrate the observed isolation of fine frequency structure in the center of the bandpass and to verify that our observations are not an artifact of our reduction of the simulation outputs, we fit the $10$\,MHz intervals of the absolute value of the simulated gains to a sixth order polynomial and compare the residuals in Fig.~\ref{fig:Residuals}.
-We find that the gain residuals on the sixth order fit are an order of magnitude greater over the $145-155$\,MHz subband than over any other frequency interval.
+To further illustrate the observed isolation of fine frequency structure in the center of the bandpass and to verify that our observations are not an artifact of our reduction of the simulation outputs, we observe the reflections in frequency space by fitting $10$\,MHz intervals of the absolute value of the simulated gains to a sixth order polynomial and inspecting the residuals in Fig.~\ref{fig:Residuals}.
+We find that the gain residuals on the sixth order fit are an order of magnitude greater on the $145-155$\,MHz subband than  any other frequency interval.
+
+We note that the termination impedence used in our simulations is $100$\,$\Omega$ to which the feed is better matched towards its edges.
+Termination by a low-noise amplifier (LNA) as is the case in an actual measurement could change this situation dramatically, leading to the reflections being present across the entire band.
+We therefor consider the existence of the reflections across the entire $100$\,MHz bandpass as a realistic possibility.
 
@@
 $k_\parallel$ values for each delay are computed at $150$\,MHz.
-The wider central lobe below 150\,ns for the subband gains is an artifact of the delay resolution of a smaller bandwidth.}
+The wider central lobe below 150\,ns for the subband gains is due to the lower delay resolution from the smaller bandwidth.}
 \label{fig:KernelsSubbands}
@@
 
-\subsection{Verifying Our Framework with $S_{11}$ Measurements and Simulations}
+\subsection{Verifying Our Framework with $S_{11}$ Measurements and Simulations}\label{ssec:S11}
 
-We now attempt attempt to quantify the accuracy of our time-domain simulation framework by comparing simulations to measurements of the $S_{11}$ parameter of the HERA dish.
+We now assess the accuracy of our time-domain simulation framework by comparing simulations to measurements of the $S_{11}$ parameter of the HERA dish.
 Up until now, our simulations have derived the voltage response of the dish using simulations of an incoming plane wave as is the case for radio signals arriving from objects in space.
 It is possible to probe the gain of the dish using objects in the far field such as known radio sources \citep{Thyagarajan:2011,Pober:2012,Colgate:2015} or constellations of ORBCOMM satellites \citep{Neben:2015,Neben:2016}.
-However natural radio sources are too weak to probe the dish response at the $<10^{-4}$ level necessary to verify our simulations and the ORBCOMM technique can only be used to map the gain at the single frequency that the satellites transmit at, $137$\,MHz.
+However natural radio sources are too weak to probe the dish response at the $<10^{-4}$ level necessary to verify our simulations and the ORBCOMM technique can only be used to map the gain at the 137\,MHz ORBCOMM transmission frequency.
 Work is currently underway to use broad-band transmitters flown into the far field of the dish by drones \citep{Jacobs:2016} but this system is still under development.
-Reflectometry of the dish using a vector network analyzer is a straightforward alternative used in \citet{Patra:2016} to estimate the gains directly.
-Rather than comparing their estimate of the gain with our predicted gains (which is done in this paper), we instead set up a time domain simulation to compute the $S_{11}$ parameter of HERA antenna and compare it to direct $S_{11}$ measurements.
+Reflectometry of the dish with a VNA is a straightforward alternative used in \citet{Patra:2016} to estimate the gains directly.
+Rather than comparing their estimate of the gain with our predicted gains (which is done in their paper), we set up a time domain simulation to compute the $S_{11}$ parameter of HERA antenna and compare it to direct $S_{11}$ measurements.
 \begin{figure}
 \includegraphics[width=.5\textwidth]{figures/s11_compare.pdf}
-\caption{A comparison between time-domain simulations (black lines) and measurements (grey lines) of $S_{11}$ for the HERA dish.
+\caption{A comparison between time-domain simulations (black line) and measurements (grey line) of $S_{11}$ for the HERA dish.
 We also show an $S_{11}$ measurement with the cables leading from the VNA to the feed terminated by an open circuit which allows us to probe the dynamic range of the measurement.
-We use the standard deviation of the open measurement (grey dashed line) between $100$ and $200$\,ns as our systematic floor (grey shaded region).
+We use the standard deviation of the open measurement (grey dashed line) between $200$ and $400$\,ns as our systematic floor (grey shaded region).
 We find very good agreement between our $S_{11}$ measurement and the simulation, validating the predictions of our simulations.}
@@
 \end{figure}
-For
 
-In our case, $S_{11}$ refers to the complex ratio between a voltage signal transmitted into the feed terminals and the voltage reflected back as a function of frequency, $ S_{11}(f) \equiv v_\text{trans}(f)/v_\text{recv}(f) $.
+$S_{11}$ refers to the complex ratio between a voltage signal transmitted into the feed terminals and the voltage reflected back as a function of frequency, $ S_{11}(f) \equiv v_\text{trans}(f)/v_\text{recv}(f) $.
 We measure $S_{11}$ of a prototype HERA dish at the National Radio Astronomy Observatory Green Bank facility using a vector network analyzer.
-{\bf \color{red} Rich, fill in the details of the VNA measurement, discuss setup, VNA, measurement mode.
-}
+
+The complex reflection coefficient of the antenna was measured using an Agilent 8753D VNA.
+The VNA is connected to the antenna's balanced feed terminal via a 30.5 m length of RG-8X-LL coaxial cable and M/A Com HH-128 180 degree hybrid junction.
+The VNA was calibrated at the balanced end of the hybrid junction using a set of termination standards having SMA connectors.
+A small adapter from SMA to the post terminals on the feed was not included in the calibration.
+The VNA excites the terminals with a band-limited (100-200\,MHz) pulse, and the complex reflected voltage at the calibration plane is measured as a function of frequency.
+The reflection for the case of open terminals was measured to confirm the dynamic range and resolution of the measurement.
+While our simulations are terminated with an impedance of $125$\,$\Omega$, the VNA measurements are terminated at $100$\,$\Omega$.
 
 Because $S_{11}$ is defined as a ratio in the frequency domain in a form identical to our voltage gains, we may run time-domain simulations similar to those described in \S~\ref{ssec:Simulations} except rather than simulating an incoming plane wave, we simulate the excitation of the feed terminals by an input voltage and record output voltage as a function of time.
-We obtain $S_{11}$ in the same manner that we obtained $\ftr$ using equation~\ref{eq:Inversion} with $\ftv_\text{recv}$ taking the place of $\ftv$ in the numerator inside the Fourier transform and $\ftv_\text{trans}$ taking the place of $\fts$ in the denominator.
+We calculate $S_{11}$ from the simulation in the same manner that we obtained $\ftr$ using equation~\ref{eq:Inversion} with $\ftv_\text{recv}$ taking the place of $\ftv$ in the numerator inside the Fourier transform and $\ftv_\text{trans}$ taking the place of $\fts$ in the denominator.
 
@@
 We are now in a position to explore the impact of the Dish's performance on the leakage of foregrounds beyond the wedge, and into the EoR window.
-Beyond the delay kernels considered in this paper and \citep{Patra:2016}, the extent of leakage will depend both on the angular structure of the primary beam, which is established through measurements and simulations in \citep{Neben:2016} and the brightness of the foregrounds themselves.
+Beyond the delay kernels considered in this paper and \citet{Patra:2016}, the extent of leakage will depend both on the angular structure of the primary beam, which is established through measurements and simulations in \citet{Neben:2016} and the brightness of the foregrounds themselves.
 In this section, we investigate the amplitude of foreground leakage as a function of delay given the angular primary beam model and our simulation of the delay structure of the dish.
-We start by extrapolating the delay structure observed in our simulations to match HERA's expected frequency resolution (\S~\ref{ssec:Extrapolation}).
+We start by performing a physically motivated extrapolation of the delay structure observed in our simulations to cover the range of comoving scales relevant to power spectrum measurements (\S~\ref{ssec:Extrapolation}).
 In \S~\ref{ssec:Leakage}, we combine this extrapolated delay response with simulations of foregrounds to determine the overall level of foreground power in HERA's visibilities.
-This leakage will cause large-scale LoS Fourier modes to be contaminated by foregrounds and hence inaccessible to the foreground filtering approach that HERA will employ.
+This leakage will cause large-scale LoS Fourier modes to be contaminated by foregrounds and hence inaccessible to the foreground filtering approach.
 Since the signal-to-noise ratio is maximized at the smallest $k$ values, the loss of these modes will reduce the significance of the power spectrum detection and negatively impact the overall bottom line of the science that HERA can accomplish.
@@
 \subsection{Extrapolating the Bandpass and Power Kernel}\label{ssec:Extrapolation}
-Our deconvolution gives us the time-domain voltage response of the PAPER and HERA antenna elements.
-We plot the absolute value of this response in Fig.~\ref{fig:SimulationsCompare}, seeing that it drops to $-30$\,dB after $\approx 100$\,ns.
-The power-kernel that convolves visibilities to higher delays is the convolution of $\widetilde{r}(\tau)$ with its time-reversed complex conjugate, which we plot as the red line.
-The convolution is in very good agreement with the voltage response itself which is explained by the fact that second order terms of the convolution, approximately given by $|\widetilde{r}(\tau)|^2$ (green line) are over two orders of magnitude smaller above $50$\,ns.
 
-Our simulations of the Dish response only extend to $\approx 300$\,ns, however, we wish to understand the impact of reflections on the frequency dependent gain of an interferometer like HERA at comoving scales of $\approx 0.1-0.5$\,$h$Mpc$^{-1}$, corresponding to the delays between 180 and 900\,ns at $z=8$, extending beyond our simulations range.
-To extrapolate out to higher delays, we assume that the response function is dominated by reflections between the feed and the dish.
-This is due to the fact that when we extend our filter bandwidth to between $50$ and $250$\,MHz and use a hamming window (which has higher resolution), we observe lobe-like structures at delays beyond $100$\,ns with a periodicity of $30$\,ns, which corresponds to the round-trip light travel time between the feed and the dish.
-In addition, the long term falloff appears as a line on a linear-log plot (Fig.~\ref{fig:Simulations}), indicating that the kernel follows an exponential which we now show is indicative of reflections.
-We do so by adopting the notation of \citep{Patra:2016}.
+Our simulations of the Dish response only extend to $\approx 400$\,ns.
+However, interferometers are expected to be most sensitive to the 21\,cm power spectrum at comoving scales between $k\approx 0.1-0.5$ $h$\,Mpc$^{-1}$, corresponding to the delays between 180 and 900\,ns at $z=8$.
+To extrapolate out to the higher delays in this range, we assume that the response function is dominated by reflections between the feed and the dish.
+The long term falloff appears as a line on a linear-log plot (Fig.~\ref{fig:SimulationResults}), indicating that the voltage response follows an exponential which we now show is indicative of reflections.
 We let $\Gamma_d$ represent the reflection coefficient of the Dish vertex and $\Gamma_f$ represent the reflection coefficient of the feed.
 An electromagnetic wave incident on the feed, at $t=0$, is accepted with amplitude $(1-\Gamma_f)$.
-The reflected component travels back to the dish and acquires an amplitude of $(\Gamma_f \Gamma_d)$ before returning at time, $\tau_d$ later where $(1-\Gamma_f)$ will be accepted and so forth.
-The time dependent voltage at the feed from these reflections is thus
+The reflected component travels back to the dish and acquires an amplitude of $(\Gamma_f \Gamma_d)$ before returning at time, $\tau_d$ later where $(1-\Gamma_f)$ will be accepted and $\Gamma_f$ will be reflected back towards the dish.
+Summing the infinite series of reflections, the time dependent voltage at the feed is
 \begin{equation}
@@
 \end{equation}
-Hence
+implying that
 \begin{equation}
@@
 \end{equation}
-Since the number of reflections, $m=t/\tau_d$, than we can write the long-term delay response in discrete form as 
+Since the number of reflections is $m=t/\tau_d$, than we can write the long-term delay response in discrete form as 
 \begin{equation}
@@
 \end{equation}
-which is a power law. We thus model our discrete voltage response beyond the times sampled by our simulations as a power law
+which is an exponential in time. We thus model our discrete voltage response as an exponential
 \begin{equation}
@@
 \end{equation}
-We plot the best power-law fit as a dashed line inf Fig~\ref{fig:SimulationsCompare}.
-%We fit our voltage response function and power-kernel to this function, finding a best fit model for the voltage kernel of $A\approx0.95$,$X \approx 0.18$, and $Y\approx 0.58$.
-The large $Y$ is unrepresentative of the feed reflection coefficient which has been simulated and measured to be $\approx 0.1$ for a head-on EM wave, suggesting that the reflections are arriving from the sides and potentially involve only a small component of the dish and feed.
-Plotting the die off for the feed reflection coefficient yields dramatically better performance than what is measured.
-If the reflections are indeed originating from the sides, and a small component of the dish and feed arrangement, further suppression may be achieved through modifying this component.
+and extrapolate beyond $400$\,ns by fitting for $A$ and $X$ in our simulations between $200$ and $400$\,ns.
 
@@
 To answer this question, we combine our extrapolated simulations of the HERA dish's spectral structure with simulations of foregrounds.
-The foreground simulations are described fully in \citep{Thyagarajan:2016} but for the readers convenience we briefly describe them here.
 
-Our foreground model consists of two major components: diffuse synchrotron emission from our Galaxy whose structure is described by the Global Sky Model (GSM) of \citet{deOliveiraCosta:2008} and a population of point sources sourced by radio loud AGN which combines the NRAO Sky Survey (NVSS) \citep{Condon:1998} at 1.4\,GHz, the Sydney University Mologolo Sky Survey (SUMMS) \citep{Bock:1999} at 843\,MHz, and extrapolate point source fluxes to the observed $100$-$200$\,MHz band using a spectral index of $\langle \alpha \rangle=-0.83$ determined in \citet{Mauch:2003}.
-Visibilities are computed from the diffuse and point source models assuming the achromatic HERA beam computed at $150$\,MHz and described in \citep{Neben:2016}.
-We compute two sets of visibilities: one in which the spectral structure of the dish is assumed to be completely flat, and another in which the beam is multiplied by the Dish's frequency dependent gain at zenith.
-While this model assumes incorrectly that the frequency evolution of the primary beam is identical along all lines of sight, the majority of power enters at the beams point of maximal gain (zenith) and observations of autocorrelations which reflect the angular average of the frequency dependence of all lines of sight agree well with our simulations at zenith \citep{Patra:2016}.
+The foreground model is discussed in detail in \citet{Thyagarajan:2016} but we describe them briefly here for the readers convenience.
+It consists of two major components: diffuse synchrotron emission from our Galaxy whose structure is described by the Global Sky Model (GSM) of \citet{deOliveiraCosta:2008} and a population of point sources including objects from the NRAO Sky Survey (NVSS) \citep{Condon:1998} at 1.4\,GHz and the Sydney University Mologolo Sky Survey (SUMMS) \citep{Bock:1999} at 843\,MHz.
+Their fluxes are extrapolated to the observed $100$-$200$\,MHz band using a spectral index of $\langle \alpha \rangle=-0.83$ determined in \citet{Mauch:2003}.
+Visibilities are computed from the diffuse and point source models assuming an achromatic angular response for the HERA beam at $150$\,MHz described in \citet{Neben:2016}.
+We compute two sets of visibilities: one in which the spectral structure of the dish is assumed to be completely flat, and another in which the beam is multiplied by the frequency dependent gain at zenith determined by our simulations.
 
-The foreground filtering procedure employed by PAPER and HERA involves delay transforming the visibilities on a short time-scale cadence and performing a 1d delay CLEAN where the deconvolution is permitted to discover and subtract foregrounds within the horizon to horizon delay.
-Since we want to avoid CLEANing noise, the level of foreground subtraction possible by this procedure is limited by the thermal noise level on the visibility, which in terun depends on the number of time steps and redundant baselines that are averaged before performing the cleaning step.
-In this work, we assume that each visibility is cleaned independently with a two minute CLEANing cadence which corresponds approximately to the time over which HERA's short baselines are coherent.
-The standard deviation on the real and imaginary part of a single delay transformed visibility is given by \citep{Morales:2004}
+The foreground filtering procedure employed by PAPER and HERA involves delay transforming the visibilities and performing a 1d clean which discovers and subtract foregrounds within the horizon plus a small buffer, allowing for the suppression of foreground side-lobes in delay space.
+The level of foreground subtraction possible by this procedure is limited by the thermal noise level on the visibility, which in turn depends on the number of time steps and redundant baselines that are averaged before performing the cleaning step.
+In this work, we assume that each visibility is cleaned independently with a twenty minute cadence.
+Each baseline is coherent for $\approx 10$\,s per night so this is equivalent to each LST being integrated for $\approx 120$ nights before cleaning.
+If we were to average over redundant baselines this number would drop enormously.
+The standard deviation on the real and imaginary part of a single delay transformed visibility is \citep{Morales:2004}
 \begin{equation}
-\Delta V = \frac{\sqrt{2 B} k_B T_{sys}}{A_e \sqrt{\tau}}
+\sigma_V = \frac{\sqrt{2 B} k_B T_{sys}}{A_e \sqrt{\tau}},
 \end{equation}
 where $A_e$ is the effective area of the dish, $B$ is the bandwidth, $T_{sys}$ is the system temperature, $\tau$ is the integration time, and $k_B$ is the Boltzmann constant.
-The system temperature can be calculated by assuming that $T_{sys} = 100\text{K} + T_{sky}$ where $100$\,K is the temperature of the PAPER reciever and $T_{sky} = 60 (\lambda/1\,\text{meter} )^{2.55}$ is the sky temperature \citep{Fixsen:2011}.
-For $A_e$ we use the value of $75$\,m determined in \citep{Neben:2016}.
-If we assume that each baseline is cleaned independently and that the integration time is $\tau \approx 60$\,s, than the noise level at 150\,MHz is approximately $9.9$\,Jy\,MHz.
-In order to avoid subtracting noise, we assume that cleaning is performed down to $5\,\sigma$.
-In Fig~\ref{fig:Cleaning} we compare the delay transform of visibilities before and after cleaning on a two minute cadence at the LST of 4 hours.
-While cleaning is able to remove structure within the horizon, it does not reduce any of the power associated with the foreground induced by the chromaticity of the dish.
+For $T_{sys}$ we use the equation $T_{sys} = 100\text{K} + T_{sky}$ where $100$\,K is the temperature of the PAPER receiver and $T_{sky} = 60 (\lambda/1\,\text{meter} )^{2.55}$ is the sky temperature \citep{Fixsen:2011}.
+For $A_e$ we use the value of $98$\,m$^2$ determined in \citet{Neben:2016}.
+We clean down to five times the thermal noise level.
+In Fig~\ref{fig:Cleaning} we compare the delay transform of visibilities before and after cleaning at the LST of 4 hours.
+While cleaning is able to remove structure within the horizon, it does not reduce any of the power leaked outside of the horizon by the chromaticity of the dish.
 
-To form estimates of the 21\,cm power spectrum, we split each visibility into BlackmanHarris windowed sub-bands centered at redshift intervals of $\Delta z = 0.5$ and each with an equivalent bandwidth of $10\,MHz$, corresponding to the redshift interval over which the statistics of the brightness temperature fluctuations are expected to be stationary.
-For each windowed interval, we use the flat sky approximation and  Fourier transform in frequency, square, and multiply by a set of prefactors to obtain a power spectrum estimate \citep{Parsons:2014},
+To form estimates of the 21\,cm power spectrum, we split each visibility into Blackman-Harris windowed sub-bands centered at redshift intervals of $\Delta z = 0.5$ and each with a power equivalent bandwidth of $10$\,MHz\footnote{The end to end width of each Fourier transformed interval is 20\,MHz, however the power equivalent width of this interval (given by the integral of the bandpass squared) is only $\approx 0.5$ the full width since the Blackman-Harris window suppresses the edge channels.}.
+The flat sky approximation allows us to Fourier transform each interval in frequency, square, and multiply by a set of prefactors to obtain a power spectrum estimate \citep{Parsons:2014},
 \begin{equation}\label{eq:PS}
@@
 \end{equation}
-Here, $\lambda$ is the central wavelength of the observation, $k_B$ is the Boltzmann constant, $B$ is the bandwidth of the Fourier transform, and $\Omega_{pp}$ is the integrated solid angle of the primary beam squared.
-$X$ is a linear factor converting between $uv$ wavelengths and $k_\perp$, and $Y$ is a linear factor converting between $k_\parallel$ and the Fourier dual to frequency, $\eta$.
+Here, $\lambda$ is the central wavelength of the observation, $k_B$ is the Boltzmann constant, $B_{pp}$ is the integral of the square of the bandpass, and $\Omega_{pp}$ is the integral of the primary beam squared over solid angle.
+$X$ and $Y$ are linear factors converting between native interometry and cosmological coordinates, defined through the relation $2 \pi {\bf u}=2 \pi (u,v,\eta) = (X k_x, X k_y, Y k_z)$.
 
-A drift scan instrument, HERA will be capable of observing the sky at any LST within the strip declination that passes through its primary beam.
-To form a final power spectrum estimate, it is expected to perform an average over the power spectrum estimates it obtains through equation~\ref{eq:PS} for each LST independently.
-It is well documented that foreground power is maximized over certain LST ranges \citep{Thyagarajan:2015a}, hence such an estimate will either filter or weight appropriately the LSTs in which foreground power is maximized.
-\citet{Thyagarajan:2016} focuses on the optimal weighting and selection of LST bins in forming a power spectrum estimate.
-For the purpsoes of our analysis, we focus on a single, relatively clean LST of 4 hours which includes the coldest part of the sky.
+A drift scan instrument, HERA will observe the sky at many local sidereal times (LSTs) within the strip declination that passes through its primary beam, averaging over the power spectrum estimate at each LST.
+It is well documented that foreground power varies significantly over LST \citep{Thyagarajan:2015a}, hence such an estimate will either filter or weight LSTs in a way that minimizes the impact of the most contaminated observations.
+For our analysis, we focus on a single LST of 4 hours which points out of the galactic plane and represents a relatively clean pointing similar to those we expect for HERA to concentrate its observing time on.
 
@@
 \includegraphics[width=.5\textwidth]{figures/cleaning_noise_Nithya.pdf}
-\caption{The absolute magnitude of a delay transformed 14-meter baseline (blue line) compared to the same visibility (green line) contaminated by reflections at the level observed in the HERA dish design.
+\caption{The absolute magnitude of a  100-200\,MHz delay transformed visibility from a 14-meter baseline (blue line) compared to the same visibility (green line) contaminated by the reflections observed in our simulations of the HERA dish.
 We see that the extended delay kernel smooths out structure, originating from foregrounds, within the horizon.
@@
 However, the depth of cleaning is limited by the noise level on a single baseline (black line).
-We show the foreground residuals with arising from a clean down to the $5\,\sigma$ noise level after 2 minutes of integration, seeing that cleaning at this cadence achieves $\approx$ two orders of magnitude of foreground reduction.
-The reflections in the dish lead to extensive winged structures that bleed into the EoR window and are well below the thermal noise level.
-All data in this plot are obtained from a $100$\,MHz bandwidth centered at $150$\,MHz.
-Vertical dashed lines indicate the horizon delays of the baseline.}
+We show the foreground residuals with arising from a clean down to the $5\,\sigma$ noise level after 20 minutes of integration.
+Since cleaning cannot distinguish between foregrounds and signal, it should only be performed within a narrow region of delay-space, close to the horizon and cannot remove the broad wings leaked by the reflections unless they are accurately modeled.}
 \label{fig:Cleaning}
@@
 
-Computing the power spectra, we inspect the amplitude of foregrounds given the chromaticity and angular pattern of the HERA dish for several different baselines.
-We first inspect a $14.6$ and $29.2$ meter baseline in Fig.~\ref{fig:BothBaselines} and find that significant regions of the visibility are foreground free.
+Computing the power spectra, we inspect the amplitude of foregrounds given the chromaticity and angular pattern of the HERA dish for baselines of two different lengths in Fig.~\ref{fig:BothBaselines}.
 In both baselines, we find that the residuals after cleaning tend to be at similar levels except at the subband centered at $z=8.5$ (150\,MHz), in which foreground residuals remain above the signal level out to $k_\parallel=0.23$\,$h$Mpc$^{-1}$.
-Several other baselines especially those oriented entirely in the E-W direction, which we do not show, contain up to two orders of magnitude greater foreground contamination as is noted in \citep{Thyagarajan:2015b}.
-In a real power spectrum analysis, these baselines would be down-weighted or discarded so that they do not bias our final estimate.
+Several other baselines especially those oriented entirely in the E-W direction, which we do not show, contain up to two orders of magnitude greater galactic  contamination as is noted in \citet{Thyagarajan:2015b}.
+In an analysis, these baselines would be down-weighted or discarded so that they do not bias our final estimate.
 
-The level of the foregrounds in Fig.~\ref{fig:BothBaselines} was derived with no attempt to apply inverse covariance weighting \citep{Parsons:2014,Ali:2015} or fringe rate filtering \citep{Parsons:2015}.
-In order to avoid biases in a maximum likelihood analysis that determines astrophysical and cosmological parameters from our power spectra, the foregrounds should ideally be below the anticipated level of thermal noise which is shown in \citep{Pober:2014} to be on the order of a few percent the anticipated level of the cosmological signal for the full HERA deployment.
-Hence, as long as we can suppress our foregrounds below 1-10\,\% the signal level, they should not interfere significantly with a maximum likelihood analysis.
+The level of the foregrounds in Fig.~\ref{fig:BothBaselines} is conservative since no attempt has been made to apply inverse covariance weighting techniques \citep{Tegmark:1997a,Liu:2011,Dillon:2013,Parsons:2014,Liu:2014a,Liu:2014b,Dillon:2015a,Dillon:2015b,Trott:2016} or fringe rate filtering \citep{Parsons:2015}.
+In order to avoid biases in a maximum likelihood analysis that determines astrophysical and cosmological parameters from our power spectra, the foregrounds should ideally be below the anticipated level of thermal noise which is shown in \citet{Pober:2014} to be on the order of a few percent the anticipated level of the cosmological signal for the full HERA deployment.
+Thus, as long as we can suppress our foregrounds below $\approx 5$\% the level of the signal, they should not interfere significantly with a maximum likelihood analysis.
 Thus, the residuals in Fig.~\ref{fig:BothBaselines} serve as a specification for any inverse covariance weighting pipeline which will need to suppress foregrounds by between a factor of $\sim 1-10$ to bring the worst contaminated regions below the level of the signal.
-Applications of inverse covariance filters in recent PAPER observations have yielded improvements at and above this level, hence our simulations show that even with the presence of beam chromaticity, HERA will be able to isolate foregrounds below below the level of thermal noise in most of the EoR window.
+Applications of inverse covariance filters in recent PAPER observations have yielded improvements at and above this level {\bf \color{red} citation?}, hence our simulations show that even with the presence of beam chromaticity, HERA will be able to isolate foregrounds below the level of thermal noise in most of the EoR window.
 
@@
 \includegraphics[width=\textwidth]{figures/ps_compare_nithya_bothBaselines.pdf}
-\caption{}
+\vspace{-24pt}
+\caption{The delay transform power spectrum for different baselines over several redshifts with (green solid line) and without (blue solid line) the presence of the simulated chromaticity in the HERA dish.
+Each estimate is computed using the square of a Blackman-Harris windowed  delay transform (equation~\ref{eq:PS}) over a power equivalent bandwidth of $10$\,MHz.
+We also show the power spectra of foreground residuals after cleaning the entire $100$\,MHz band with (dashed cyan line) and without (red dashed line) the simulated spectral structure.
+For all subbands, except $z=8.5$, we find that the reflections in the HERA dish have a negligible effect on the $k_\parallel$ where the foregrounds drop below the signal level.
+This is the same subband where enhanced spectral structure due to reflections are observed in our simulations (Figs.~\ref{fig:KernelsSubbands} and \ref{fig:Residuals}).}
 \label{fig:BothBaselines}
@@
 
-%\begin{figure*}
-%\includegraphics[width=\textwidth]{figures/ps_compare_nithya_lst4hr_1024ch_7p3ew_12p6ns.pdf}
-%\caption{The power spectrum computed from the delay transform of a 14.6 meter baseline in equation~\ref{eq:PS} with (solid green line) and without (solid blue line) the presence of reflections in the HERA dish.
-The residuals after cleaning within the dashed black lines down to three times the level of thermal noise after 20 minutes of integration with (dashed cyan) and without (red dashed) the dish chromaticity are also plotted.
-We find that for this short baseline, clean residuals are on a similar level as the 21\,cm signal (solid black line), indicating that a redesign of the array with fewer short baselines may be necessary to maximize its sensitivity on foreground free modes.}
-%\label{fig:shortBaseline}
-%\end{figure*}
-
-%\begin{figure*}
-%\includegraphics[width=\textwidth]{figures/ps_compare_nithya_lst4hr_1024ch_14p6ew_25p3ns.pdf}
-%\caption{The same as Fig.~\ref{fig:shortBaseline} except now for a 29.2 meter baseline.
-We see that the level of foregrounds is down relative to our 14.6 meter baseline by two orders of magnitude, likely due to the fact that we are now outside of the region with significant contamination from the Galaxy.
-The presence of reflections tends to extend the $k_\parallel$ at which foregrounds drop below the level of the signal between $k_\parallel=0.15$\,$h$Mpc$^{-1}$ and $k_\parallel=0.22$\,$h$Mpc$^{-1}$ with the most severe contamination occurring at the $z=8.5$ subband where the reflections where observed to be worst in Fig.~\ref{fig:KernelsSubbands}.
-}
-%\label{figure:shortBaseline}
-%\end{figure*}
-
-%\begin{figure*}
-%\includegraphics[width=\textwidth]{figures/ps_compare_nithya_lst4hr_snrVbaselineMedian.pdf}
-%\caption{The median of the ratio between foreground residuals with the chromaticity of the HERA primary beam between $k_\parallel=0.15$\,$h$Mpc$^{-1}$ and $k_\parallel=1.0$\,$h$Mpc$^{-1}$, the range of k values over which HERA will derive the majority of its sensitivity.
-We see that the shortest baselines tend to have relatively low signal to foreground ratios due to the presence of high amplitude Galactic synchrotron emission.}
-%\label{fig:Medians}
-%\end{figure*}
-
 \subsection{The Implications of Dish Reflections on EoR Science}\label{ssec:Science}
-The primary goal 21\,cm EoR observations is to obtain information about the nature of the sources that drove reionization.
-Since the amplitude of the 21\,cm signal is maximal at smaller $k$ values, a loss of large scale signal due to foreground leakage eliminates the the modes that HERA would otherwise have the greatest signal to noise detections, impacting our overall sensitivity and its ability to derive this information.
-In this section, we estimate the impact of foreground leakage on HERA's sensitivity along with its ability to determine the astrophysics of reionization.
-We do so using the Fisher Matrix formalism.
-The Fisher Matrix allows us to forecast the covariances and errors on reionization parameters given errors on power spectrum observations due to the uncertainties caused by thermal noise which is in turn determined by the $uv$ coverage and observing time of the interferometer.
-The covariance between the parameters of some model ${\bf \theta}$ is given by the inverse of the Fisher matrix, ${\bf F}$ which for Gaussian and independently determined power spectrum bins may be written approximately as \citep{Pober:2014,EwallWice:2015a},
+A primary near-term goal of 21\,cm EoR observations is to obtain information about the nature of the sources that drove reionization.
+Since the amplitude of the 21\,cm signal is maximal at smaller $k$ values, a loss of large scale signal due to foreground contamination eliminates the the modes that HERA would otherwise have the greatest signal to noise detections of, reducing its overall sensitivity.
+In this section, we use the Fisher Matrix formalism to estimate the impact of foreground leakage on HERA's sensitivity along with its ability to determine the astrophysics of reionization.
+The Fisher Matrix allows us to forecast the covariances and errors on reionization parameters given errors on power spectrum observations due to the uncertainties caused by cosmic variance and thermal noise which is in turn determined by the $uv$ coverage and observing time of the interferometer.
+The covariance between the parameters, ${\bf \theta}$, of an astrophysical model is given by the inverse of the Fisher matrix, ${\bf F}$ which for Gaussian and independently determined power spectrum bins may be written approximately as \citep{Pober:2014},
 \begin{equation}\label{eq:Fisher}
@@
 \end{equation}
-where $\Delta^2(k,z)$ is the power spectrum amplitude for some $k-z$ bin and $\sigma^2(k,z)$ is the variance of the power spectrum estimate in that bin due to thermal noise and cosmic variance \citep{Beardsley:2013}.
+where $\Delta^2(k,z)$ is the power spectrum amplitude for some $k-z$ bin and $\sigma^2(k,z)$ is the variance of the power spectrum estimate.
+We write this equation as approximate since it ignores additive terms arising from the dependence of $\sigma^2(k,z)$ on model parameters due to cosmic variance which only contribute at the $\approx 1$\% level \citep{EwallWice:2015b}.
 
- we use the publicly available {\tt 21cmFAST} code \citep{Mesinger:2011} which generates realizations of the 21\,cm brightness temperature field using the excursion set formalism of \citet{Furlanetto:2004}.
-We employ a popular three parameter model of reionization \citep{Mesinger:2012,Pober:2014,Greig:2015,Liu:2015} with the following variables
+To simulate $\Delta^2$, we use the publicly available {\tt 21cmFAST}\footnote{\url{http://homepage.sns.it/mesinger/DexM___21cmFAST.html}} code \citep{Mesinger:2011} which generates realizations of the 21\,cm brightness temperature field using the excursion set formalism of \citet{Furlanetto:2004}.
+We employ a popular three parameter model of reionization \citep{Mesinger:2012} with the following variables
 \begin{itemize}
-\item ${\bf \zeta}$: The ``ionization efficiency" is defined in the \citep{Furlanetto:2004} excursion formalism to be the inverse of the mass collapse fraction necessary to ionize a region and is computed from a number of other physical parameters such as the fraction of collapsed baryons that form stars and the UV photon escape fraction.
+\item ${\bf \zeta}$: The ``ionization efficiency" is defined in the \citet{Furlanetto:2004} excursion formalism to be the inverse of the mass collapse fraction necessary to ionize a region and is computed from a number of other physical parameters including the fraction of collapsed baryons that form stars and the UV photon escape fraction.
 Because $\zeta$ acts as an efficiency parameter, its primary affect is to change the timing of reionization.
 We choose a fiducial value of $\zeta=20$, though its possible values range anywhere between $5$ and $50$.
-\item ${\bf R_\text{mfp}}$: The presence of Lyman limit systems and other potential absorbers within HII regions causes UV photons to have a mean free path denoted by $R_\text{mfp}$.
+\item ${\bf R_\text{mfp}}$: The presence of Lyman limit systems and other potential absorbers within HII regions causes UV photons to have a finite mean free path denoted by $R_\text{mfp}$.
 In the {\tt 21cmFAST} framework, HII regions cease to grow after reaching the radius of $R_\text{mfp}$, primarily impacting the morphology of the signal.
@@
 \item ${\bf T_\text{vir}^\text{min}}$: The minimal mass of dark matter halos that hosted ionizing sources.
-While in principle, halos with virial temperatures as small as $10^2$\,K are though, in principle, to be able to form stars, thermal and mechanical feedback have been seen to raise this limit to as high as $10^5$\,K.
-We choose a fiducial value of $T_\text{vir}^\text{min} = 1.5\times 10^4$\,K which is set by the atomic line cooling thresshold.
+While in principle, halos with virial temperatures as small as $10^2$\,K are thought to be able to form stars \citep{Haiman:1996a,Tegmark:1997c}, thermal and mechanical feedback have been seen to raise this limit to as high as $10^5$\,K \citep{Springel:2003,Mesinger:2008,Okamoto:2008}.
+We choose a fiducial value of $T_\text{vir}^\text{min} = 1.5\times 10^4$\,K which is set by the atomic line cooling threshold.
 \end{itemize}
 In order to account for the degeneracies in the power spectrum between heating from X-rays and reionization from UV photons, we also marginalize over three additional parameters that describe the impact of heating from early X-ray luminous sources as explored in \citep{EwallWice:2015b}.
-These are the X-ray heating efficiency $f_X$, the maximal energy of X-ray photons that are self absorbed by the ISM of early galaxies, $\nu_\text{min}$, and the spectral slope, $\alpha$ which are taken to have fiducial values of $1$,$0.3$\,keV, and $-1.2$ respectively.
-We choose to parameterize our model in terms of the fractional differences of each parameter from their fiducial values so that, for example, $\theta_\zeta = (\zeta - \zeta_\text{fid})/\zeta_\text{fid}$ and compute the derivatives in equation~\label{eq:Fisher} by performing a linear fit to realizations of the 21\,cm power spectrum calculated by {\tt 21cmFAST} at $\theta_i= \pm 10^{-2}, \pm 5\times 10^{-2}, \pm 10^{-1}$,and $ \pm 2 \times 10^{-2}$.
+These are the X-ray heating efficiency $f_X$, the maximal energy of X-ray photons that are self absorbed by the ISM of early galaxies, $\nu_\text{min}$, and the spectral slope, $\alpha$ which are taken to have fiducial values of $1$, $0.3$\,keV, and $-1.2$ respectively.
+We choose to parameterize our model in terms of the fractional difference of each variable from its fiducial value so that, for example, $\theta_\zeta = (\zeta - \zeta_\text{fid})/\zeta_\text{fid}$ and compute the derivatives in equation~\ref{eq:Fisher} by performing a linear fit to realizations of the 21\,cm power spectrum calculated by {\tt 21cmFAST} at $\theta_i= \pm 10^{-2}, \pm 5\times 10^{-2}, \pm 10^{-1}$,and $ \pm 2 \times 10^{-2}$.
 
 What about $\sigma^2(k,z)$?
-$\sigma^2$ represents the noise on each 1 dimensional power spectrum estimate.
 For each measurement in the $uv$ plane, the standard deviation of a power spectrum measurement is given by the direct sum of sample variance and thermal noise \citep{McQuinn:2006} which in turn depends on the primary beam of the instrument and the time spent sampling each $uv$ cell.
-For our analysis, we assume that the $uv$ plane is sampled by circular apertures with effective areas of $75$\,m$^2$ and that $\tau({\bf k})$ is determined by by a drift scan in which baselines are integrating coherently on each $uv$ cell for $\approx 20$\,minutes.
+For our analysis, we assume that the $uv$ plane is sampled by circular apertures with effective areas of $98$\,m$^2$ and that $\tau({\bf k})$ is determined by a drift scan in which non instantaneously redundant baselines are combined within each $uv$ cell.
+We compute standard deviation of each $(k,z)$ bin for the proposed 331-element deployment of HERA (HERA-331) using the public {\tt 21cmSense}\footnote{\url{https://github.com/jpober/21cmSense}} code \citep{Pober:2013b,Pober:2014}.
 
@@
 \includegraphics[width=.5\textwidth]{figures/sensitivity_comparison_v2.pdf}
-\caption{A comparison between the sensitivity achieved by HERA at redshift $8.5$ with and without the presence of beam chromaticity due to the reflections studied in this work.
-We saw in Fig.~\ref{fig:BothBaselines} that with reflections, foregrounds exceed the signal level out to $k=0.2$\,$h$Mpc$^{-1}$ at $z=8.5$ which we assume are unusable, forcing us to ignore modes out to $350$\,ns beyond the horizon, leading to the sensitivity projected in the red curve.
+\caption{A comparison between the sensitivity achieved by HERA-331 at redshift $8.5$ with and without the presence of beam chromaticity due to the reflections studied in this work.
+We saw in Fig.~\ref{fig:BothBaselines} that with reflections, foregrounds exceed the signal level out to $k=0.23$\,$h$Mpc$^{-1}$ at $z=8.5$ which we assume are unusable, forcing us to ignore modes out to $350$\,ns beyond the horizon, leading to the sensitivity projected in the red curve.
 The absence of these reflections allows us to work within $250$\,ns of the horizon (green curve), leading to an increase in sensitivity by a factor of $\approx 1.5$.
@@
 \includegraphics[width=\textwidth]{figures/sigmaVsZ_reionization_v2.pdf}
-\caption{Fractional Errors on reionization and heating parameters as a function of maximal observed redshift out to the low end of HERA's initial observing band at $z=12$.
+\caption{Fractional Errors on reionization and heating parameters as a function of maximal observed redshift out to the low end of HERA-331's initial observing band at $z=12$.
 The presence of strong reflections contained within a small subband at $z=8.5$ has a minimal impact on our overall constraints on reionization parameters.
@@
 \includegraphics[width=.5\textwidth]{figures/reionization_triangle_compare_v2.pdf}
-\caption{95\% confidence regions with and without reflections assuming that observations are taken over the redshifts between 7.5 and 10.
+\caption{95\% confidence regions for reionization parameters assuming $1000$ hours of observation on HERA-331 between the redshifts between 7.5 and 12.
 The presence of the reflections leads to an increase in the major axes of these confidence regions by a factor of one to two.}
@@
 At all other redshifts, the leakage due to beam chromaticity only extends to $\approx 250$\,ns beyond the horizon.
-To determine the potential impact of our observed beam chromaticity on HERA's ability to constrain the astrophysics of reionization, we consider three different scenarios for beam chromaticity that capture a range of possibilities allowed by our simulation.
+To determine the impact of our observed beam chromaticity on HERA's ability to constrain the astrophysics of reionization, we consider three different scenarios for beam chromaticity that capture a range of possibilities informed by our simulations.
 
 \begin{itemize}
-\item {\bf Optimistic: The observed reflections are an artifact of the simulation.} It is possible that the long term reflections observed in the center of our gain are artifacts of our modeling and that effects such as dissipative effects due to unmodeled non-idealities in the geometry of the disk will allow reflected radio waves to be better absorbed or escape into space, suppressing these reflections.
-In our most optimistic scenario, we assume their absence in which case the foregrounds pass below the level of the signal at $240$\,ns beyond the horizon at all redshifts between $z=7$ and $10$, consistent with what is observed in the bands where the dish chromaticity is less severe or when it is not present at all.
+\item {\bf Optimistic: The observed reflections are an artifact of the simulation.} It is possible that the long term reflections observed in the center of our gain are artifacts of our modeling such as dissipative effects due to unmodeled non-idealities in the geometry of the disk will allow reflected radio waves to be better absorbed or escape into space.
+In our most optimistic scenario, we assume their absence in which case the foregrounds pass below the level of the signal at $250$\,ns beyond the horizon at all redshifts between $z=7$ and $12$, consistent with what is observed in the bands where the dish chromaticity is less severe or when it is not present at all.
 We do not consider the possibility that optimal inverse covariance weighting of the foregrounds  may actually decrease the minimal delays accessible to below the $250$\,ns above the horizon observed in our simulations.
-Hence, this scenario is actually somewhat conservative and certainly more pessimistic than the ones considered in \citep{Pober:2014,Greig:2015a,EwallWice:2015b}.
+Hence, this scenario is actually somewhat conservative and certainly more pessimistic than the ones considered in \citet{Pober:2014,Liu:2015a,Liu:2015b,EwallWice:2015b}.
 
-\item {\bf Moderate: The Simulations accurately capture the chromaticity of the dish.} In this case, we assume that the reflections cause foregrounds to pass below the level of the signal at $250$\,ns except at redshift $8.5$ where they pass below the foregrounds at $350$\,ns.
+\item {\bf Moderate: The Simulations accurately capture the chromaticity of the dish.} In this case, we assume that the reflections cause foregrounds to pass below the level of the signal at $250$\,ns beyond the horizon except at redshift $8.5$ where they pass below the foregrounds at $350$\,ns beyond the horizon.
 
 \item {\bf Pessimistic: The reflections are present in all sub-bands.} In this scenario, we assume that the spectral structure observed in the neighborhood of $150$\,MHz is present throughout the entire $100$-$200$\,MHz frequency range covered by HERA.
-While more pessimistic than anything we actually observe in our simulations, this scenario serves as a reasonable upper bound.
+We decide to include this more pessimistic scenario since our simulations and measurements are run with a termination impedence of $\approx 100-125$\,$\Omega$ which is actually a better match to the feed at the edges of the $100-200$\,MHz band, reflecting $1-3$\% power at the edges while reflecting $\approx 10$\% power at $150$\,MHz.
+In an actual cosmological measurement, the feed is terminated by a LNA whose impedance might differ significantly, hence it is not unlikely that we find the reflections in the center of our band present across its entirety.
 
@@
 In Fig.~\ref{fig:Sensitivity}, we compare the level of $1\sigma$ thermal noise for our optimistic and moderate scenarios at $z=8.5$ to the amplitude of the 21\,cm signal.
-While the level of thermal noise monotonically increases with $k$, there is a small upturn at the smallest $k$ values due to an increase in sample variance caused by the knee like maximum in the 21\,cm power spectrum at $k \approx 0.1$\,$h$Mpc$^{-1}$ and the shrinking number of measurements within each 1d $k$-bin.
-Despite this upturn, the smallest $k$ modes are still the highest signal to noise measurements that HERA is expected to obtain, leading to a reduction in the maximal signal to noise ratio of $\approx 1.5$ and a reduction in the number of modes that the instrument is able to measure.
+The smallest $k$ modes lost to foreground contamination are the highest signal to noise measurements that HERA is expected to obtain.
+Their absence impacts sensitivity in two ways.
+By leading to a reduction in the maximal signal to noise ratio of $\approx 1.5$ and a reduction in the total number of modes that the instrument is able to measure.
 
-Folding our calculations of thermal noise and the derivatives of $\Delta^2$ into equation~\ref{eq:Fisher} and inverting, we obtain the covariance matrix for model parameters from which we calculate $95\%$ confidence regions which we plot in Fig.~\ref{fig:Confidence}.
-The presence of reflections within a limited sub-band about $z=8.5$ leads to an almost neglible increase in the extent of our confidence intervals while the presence of the reflections across the entire band causes the length and width of our confidence ellipses to increase by a factor of $\approx 2$.
-The diagonal elements of our covariance gives us error bars on each parameter which we plot in Fig.~\ref{fig:Errors}.
+Folding our calculations of thermal noise and the derivatives of $\Delta^2$ into equation~\ref{eq:Fisher} and inverting, we obtain the covariance matrix for model parameters.
+We show the 95\% confidence ellipses for the reionization parameters in Fig.~\ref{fig:Confidence}.
+The presence of reflections within a limited sub-band about $z=8.5$ leads to an almost neglible increase in the extent of our confidence intervals while the presence of the reflections across the entire band causes the lengths and widths of our confidence ellipses to increase by a factor of $\approx 2$.
+The diagonal elements of our covariance give us error bars on each parameter which we plot in Fig.~\ref{fig:Errors}.
 We see that similar to our confidence regions, the error bars on reionization parameters for our optimistic and moderate scenarios are nearly indestinguishable.
@@
 
-The error bars on reionization parameters, even for our most optismtic model, are a factor of a few larger than the ``moderate" errors predicted in previous works using the Fisher Matrix such as \citet{Pober:2014}, \citet{EwallWice:2015a}, and \citet{Liu:2015a,Liu:2015b}.
+The error bars on reionization parameters, even for our most optimistic model, are a factor of a few larger than the ``moderate" errors predicted in previous works using likelihood analyses such as \citet{Pober:2014}, \citet{Greig:2015,Greig:2015b,Greig:2015c}  \citet{EwallWice:2015b}, \citet{Liu:2015a,Liu:2015b}.
 There are several reasons for this.
-Firstly, in our most optimistic scenario, we assumed that foregrounds cause the signal to be inaccessible below $250$\,ns beyond the edge of the wedge while in all previous works, a comoving $k$ of $k_\text{min}=0.1$\,$h$Mpc$^{-1}$, rather than a delay was used.
-In particular, this delay corresponds to a comoving $k\approx0.15$\,$h$Mpc$^{-1}$ at $z=8.5$, in significant excess of the values used in previous works.
-However, we do not consider the potential for inverse covariance techniques to further isolate foregrounds and potentially allowing us to work closer to the wedge than a naive Fourier transform.
-Because of this, our work is significantly more conservative than previous estimates.
-Secondly, previous studies assumed a fully illuminated HERA aperture, which for a $14$\,m dish predicts and effective area of $\approx155$\,m$^2$ at $150$\,MHz.
-Electromagnetic simulations and mapping of the primary beam of the HERA dish described in \citep{Neben:2016} indicate are in good agreement that the effective area of the antenna element is actually $\approx 98$\,m$^2$ at $150$\,MHz which leads to an increase in the overall thermal noise levels by a factor of $\approx 1.5$.
+Firstly, in our most optimistic scenario, we assumed that foregrounds cause the signal to be inaccessible below $250$\,ns beyond the edge of the wedge which corresponds to $k_\text{min} \approx 0.15$\,$h$Mpc$^{-1}$ at $z=8.5$ while in previous works a minimal comoving $k_\text{min} \approx 0.1$\,$h$Mpc$^{-1}$ was used.
+Secondly, previous studies assumed a fully illuminated HERA aperture, which for a $14$\,m diameter dish predicts and effective area of $\approx155$\,m$^2$.
+Electromagnetic simulations and ORBCOMM mapping of the angular beam pattern of the HERA dish show that the effective area of the antenna element is actually $\approx 98$\,m$^2$ at $137$\,MHz which leads to an increase in the overall thermal noise levels by a factor of $\approx 1.5$ \citep{Neben:2016}.
 
-\section{Conclusions}
+Although conservative, our predictions bode well for the HERA design, indicating that even with the additional systematics introduced by the reflections in the Dish geometry, the array will still obtain a $\gtrsim 10 \sigma$ detection of the power spectrum and be capable of establishing precision constraints on the properties of the sources that reionized the IGM.
+
+\section{Conclusions}\label{sec:Conclusion}
 In this paper, we have formally described the impact of instrumental chromaticity on foreground contamination of the 21\,cm signal.
-We have also used simulations of electromagnetic waves incident from zenith on the primary antenna element on HERA to determine the extent to which reflections and other frequency dependent structure might leak foregrounds into the EoR window.
-The results of our simulations of the zenith gain of the instrument are broadly consistent with data obtained using reflectometry described in \citep{Patra:2016} and can be summarized in the following points.
+We have also used simulations of electromagnetic waves incident from zenith on the primary antenna element on HERA to determine the extent to which reflections and other frequency dependent structure in the dish leak foregrounds into the EoR window.
+The results of our simulations of the dish's voltage response are broadly consistent with reflectometry measurements \citep{Patra:2016} and can be summarized in the following points.
 \begin{itemize}
 \item The 14-m dish and inverted dipole feed configuration introduces reflections and, as a result, spectral structure, that is in excess of that observed in the antenna design for HERA's predecessor, PAPER.
-The dish design is intended to greatly increase array collecting area over PAPER without significantly raising the number of correlated elements while narrowing the angular field of view and suppressing the overall amplitude of foregrounds but we find that in achieving these ends, some degree of spectral smoothness has been sacrificed.
+The dish design is intended to greatly increase array collecting area over PAPER without significantly raising the number of correlated elements while narrowing the angular field of view and suppressing the overall amplitude of foregrounds.
+We find that in achieving these ends, some degree of spectral smoothness has been sacrificed.
 Because foreground filtering in delay space cannot distinguish between signal and foregrounds, any regions of $k$-space contaminated by these reflections are effectively unusable in a 21\,cm measurement unless they can be modeled to high fidelity and removed.
@@
 It is also possible that the  non-ideal properties of an actual antenna will allow these reflections to escape the dish after a short time or be dissipated, rather than reflecting continually to long delays.
-Because estimates of the power spectrum are obtained from sub-intervals of $\approx10$\,MHz, the reflections that we have simulated will only impact a single redshift.
+Because estimates of the power spectrum are obtained from sub-intervals of $\approx10$\,MHz, the reflections that we have simulated will only impact a single $\Delta z=0.5$ redshift interval.
 
-\item Simulating the impact of these reflections on foreground leakage using the foreground model described in \citet{Thyagarajan:2016}, we find that the beam chromaticity extends foregrounds above the level of the cosmological signal to $\approx 350$\,ns beyond the horizon while without the reflections, foregrounds extend above the signal to $\approx 250$\,ns beyond the horizon.
-These observations are pessimistic in that no attempt to inversely weight the foregrounds by their covaranciances has been attempted.
+\item Simulating the impact of these reflections on foreground leakage using the foreground model of \citet{Thyagarajan:2016}, we find that the beam chromaticity extends foregrounds above the level of the cosmological signal to $\approx 350$\,ns beyond the horizon while without the reflections, foregrounds extend above the signal to $\approx 250$\,ns beyond the horizon.
+These forecasts are conservative in that we do not attempt to inversely weight the foregrounds by their covariances, nor have mitigation algorithms such as delay rate filtering been applied.
 
 \item If the reflections are contained within a $10$\,MHz subband around $150$\,MHz, than the overall constraints that HERA will be able to place on the astrophysics of reionization are minimally impacted.
-If the reflections somehow contaminate the entire band, than our constraints on reionization parameters will suffer a factor of two increase in uncertainty but still remain on the order of $10$\%.
+The feed design is well matched near the band edges to the termination impedences in both our measurements and simulations which may not be the case in the field, hence we consider it a realistic possibility that these reflections contaminate the entire band.
+If this is the case, our constraints on reionization parameters will suffer a two-fold increase in uncertainty but still remain on the order of $10$\%.
+Measuring the global properties of the sources that reionized the universe to this accuracy will be an unprecedented accomplishment.
 \end{itemize}
 
-\label{sec:Conclusion}
+While we have not addressed the issue of inter-dish reflections, preliminary measurements indicate that their level is many orders of magnitude below our observations of reflections within each antenna element with a full analysis forthcoming \citep{Patra:2016}.
+Our results are very encouraging since they show that the HERA design is capable of isolating the foregrounds to sufficiently low delays to make a high significance detections of the 21\,cm power spectrum during the EoR.
+They also emphasize the importance of mitigating reflections in the analogue signal chain.
+The reflections masking our signal at $k=0.2$\,$h$Mpc$^{-1}$ are at the level of one part in $10^{-4}$, hence any interferometer designed for EoR observing must ensure that such structure is absent from the signal chain at the $10^{-5}$ level or less at $\approx 400$\,ns or be absolutely certain that their calibration strategy can faithfully remove this structure without introducing any spurious, frequency-dependent artifacts at or above this level due to foreground mismodeling or thermal noise.
+
 \bibliographystyle{apj}

### 2016-02-01 ForegroundSimulations/ms.tex

@@
 
-Fig.~\ref{fig:asm-dps-beam-chromaticity} shows the delay power spectra of foregrounds obtained with the aforementioned models for power pattern.
+Fig.~\ref{fig:asm-dps-beam-chromaticity-14.6m-baseline} shows the delay power spectra of foregrounds obtained with the aforementioned models for power pattern.
 In all these panels, power spectra obtained with achromatic, {\it Airy} disk and simulated disk are shown in black, red, and blue respectively.
@@
 \centering
-\includegraphics[width=\linewidth]{asm_beam_chromaticity_subband_150_MHz.eps}
-\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra. }
-\label{fig:asm-dps-beam-chromaticity}
+\includegraphics[width=\linewidth]{asm_beam_chromaticity_bl2_LST_3.96_hrs_subband_150.0_MHz.eps}
+\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra for a 14.6~m baseline.}
+\label{fig:asm-dps-beam-chromaticity-14.6m-baseline}
+\end{figure*}
+
+\begin{figure*}[htb]
+\centering
+\includegraphics[width=\linewidth]{asm_beam_chromaticity_bl8_LST_3.96_hrs_subband_150.0_MHz.eps}
+\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra for a 29.2~m baseline.}
+\label{fig:asm-dps-beam-chromaticity-29.2m-baseline}
 \end{figure*}

### 2016-02-02 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev3.tex
incorporating comments

--- 2016-01-25 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev2.tex
@@
 
-\shorttitle{The HERA Dish: Beam Measurements and Science Implications}
+\shorttitle{The HERA Dish I: Beam Measurements and Science Implications}
 \shortauthors{Neben et al.}
@@
 Richard F. Bradley\altaffilmark{2,3},
+Jacqueline N. Hewitt\altaffilmark{1},
+David R. DeBoer\altaffilmark{4},
+Aaron Parsons\altaffilmark{4},
 Aaron Ewall-Wice\altaffilmark{1},
@@
 Zaki S. Ali\altaffilmark{4},
-Judd Bowman\altaffilmark{5}
-Carina Cheng\altaffilmark{4},
-David R. DeBoer\altaffilmark{4}
-Jacqueline N. Hewitt\altaffilmark{1},
-Aaron Parsons\altaffilmark{4}}
+Judd Bowman\altaffilmark{5},
+Carina Cheng\altaffilmark{4}
+Saul A. Kohn\altaffilmark{6},
+Roger Dickenson\altaffilmark{3},
+Phillip Doolittle\altaffilmark{3},
+Dennis Egan\altaffilmark{3},
+Mike Hedrick\altaffilmark{3},
+Patrick Schaffner\altaffilmark{3},
+John Shelton\altaffilmark{3},
+H.A. Taylor\altaffilmark{3},
+Rusty Taylor\altaffilmark{3},
+Butch Wirt\altaffilmark{3}}
 
@@
 \begin{abstract}
-The Hydrogen Epoch of Reionization Array (HERA) is a radio interferometer aiming to detect the power spectrum of 21\,cm fluctuations from neutral Hydrogen from the Epoch of Reionization.
+The Hydrogen Epoch of Reionization Array (HERA) is a radio interferometer aiming to detect the power spectrum of 21\,cm fluctuations from neutral hydrogen from the Epoch of Reionization.
 Drawing on lessons from the Murchison Widefield Array (MWA) and the Precision Array for Probing the Epoch of Reionization (PAPER), HERA is a hexagonal array of large (14\,m) dishes with suspended dipole feeds with element collecting area of 100\,m$^2$.
-This is the first of a series of four papers characterizing the frequency and angular response of the HERA dish element with simulations and measurements.
-In this work we measure the angular response at 137\,MHz using the ORBCOMM beam mapping system of \citet{neben15}.
-We measure collecting areas of 70--100\,m$^2$ and predict power spectrum SNRs.
-With optimistic foreground and analysis assumptions, HERA-127 should detect the EOR with a signal-to-noise of 25--30 with a single season of observations.
-Even pessimistically assuming that only previously demonstrated techniques are used, the significance of an EOR detection remains above $5\sigma$.
-Lastly we simulate foreground visibilities using numerical beam models and study the foreground distribution in Fourier space as a function of LST, and the uncertainties in these predictions due to beam modeling uncertainties.
+Not only does the dish determine overall sensitivity, it determines the aggregate frequency structure of foregrounds in the interferometer.
+This is the first of a series of four papers characterizing the frequency and angular response of the with simulations and measurements.
+We focus in this paper on the angular response (i.e., power pattern), which sets the relative weighting between sky regions of high and low delay, and thus, apparent source frequency structure.
+We measure the angular response at 137\,MHz using the ORBCOMM beam mapping system of \citet{neben15}.
+We measure a collecting area of 97\,m$^2$ in the optimal dish/feed configuration, implying HERA-331 should detect the EOR with a signal-to-noise of 74 with a single season of observations, making optimistic foreground and analysis assumptions.
+Even with more pessimistic assumptions, using only previously demonstrated techniques, a HERA should achieve a signal-to-noise of 20.
+Lastly we simulate foreground visibilities using numerical beam models and study the foreground distribution in Fourier space as a function of local sidereal time, and the uncertainties in these predictions due to beam modeling uncertainties.
 \end{abstract}
@@
  the main challenges in 21\,cm observations, as the expected cosmological signal is 4--5 
- orders of magnitude fainter than Galactic and extragalactic foregrounds. Radio 
+ orders of magnitude fainter in brightness temperature than Galactic and extragalactic foregrounds. Radio 
  interferometers such as the Murchison Widefield Arry (MWA) \citep{tingay13,mwascience}, the Precision Array for Probing the Epoch of Reionization (PAPER) \citep{ali2015}, the Giant Meterwave Radio Telescope (GMRT)
@@
  frequency evolution of the foreground emission separates from the spectrally 
- unsmooth cosmological signal whose frequency dimension probes the a line of sight through the 
+ rough cosmological signal whose frequency dimension probes a line of sight through the 
  inhomogenous reionizing universe.
 
-The Hydrogen Epoch of Reionization Array (HERA) \citep[][, deBoer et al., submitted]{PoberNextGen} is drawing on lessons learned by the MWA and PAPER to reach the calibration and foreground isolation accuracy required to make a significant detection and characterization of the cosmological signal.
+The Hydrogen Epoch of Reionization Array (HERA) \citep[][deBoer et al.
+(in prep)]{PoberNextGen} is drawing on lessons learned by the MWA and PAPER to reach the calibration and foreground isolation accuracy required to make a significant detection and characterization of the cosmological signal.
 HERA uses 14\,m diameter parabolic dishes arranged in a compact, hexagonal array to achieve coherent integration on the very low surface brightness 21\,cm signal.
-Redundant baselines also permit redundant calibration techniques which solve for the relative calibration between all antennas \citep{zheng14}, and use a sky model only to set the frequency dependent flux scale.
+Redundant baselines also permit redundant calibration techniques which solve for the relative calibration between all antennas \citep{liu2010,zheng14}.
 In contrast, non-redundant arrays are pursuing fully sky model-based calibration schemes which risk frequency-dependent calibration systematics due to sky modeling inaccuracy \citep{braun2013}.
-HERA is pursuing a staged deployment of 19, 127, and finally 331 elements in progressively larger hex patterns, with scattered outriggers for imaging.
-A central lesson of first generation instruments is it is essential to characterize the instrument response to foreground emission lest instrument frequency dependence smear foreground power into cosmological signal modes.
+A central lesson from first generation instruments is that it is essential to characterize the instrument response to foreground emission lest instrument frequency dependence smear foreground power into cosmological signal modes.
 
@@
 interferometer's frequency-dependent point spread function smears foreground power into a ``wedge'' shaped 
-region in  $(k_\perp,k_\parallel)$ Fourier space \citep{Dattapowerspec,X13, PoberWedge,MoralesPSShapes, VedanthamWedge, nithya13, CathWedge, AdrianWedge1, AdrianWedge2}.
+region in  $(k_\perp,k_\parallel)$ Fourier space \citep{Dattapowerspec,X13, PoberWedge,MoralesPSShapes, VedanthamWedge, nithya13, CathWedge, AdrianWedge1, AdrianWedge2,parsons12b}.
 This effect is straightforward to understand for a single baseline which measures the sky intensity weighted by the complex sky fringe
-$e^{i \vec{k}\cdot\vec{b}}$, where $\vec{k}=\vec{k}(\theta,\phi,f)$ is the wave vector of 
-the incident radiation, $\vec{b}$ is the baseline vector in meters, and $f$ is the observation frequency. Thus sources at different positions relative to the baseline vector manifest different 
+$e^{i \vec{k}\cdot\vec{b}}$, where $\vec{k}(f)$ is the wave vector of incident radiation pointing along its direction of travel, $\vec{b}$ is the baseline vector in meters, and $f$ is the observation frequency.
+Thus sources at different positions relative to the baseline vector manifest different
 frequency structure despite their intrinsically smooth spectra, but are geometrically limited 
@@
 structure, while those near $\tau=\tau_\text{max}$ acquire the maximum frequency 
-structure given the baseline length.
+structure given the baseline length. The high delay regions of the sky lie near the horizon while low delay 
+regions lie closer to zenith and also perpendicular to the baseline vector.
 
-The fact that sources acquire frequency dependence based on with their position on the sky 
-tells us already that the primary beam strongly affects the aggregate frequency dependence 
-of the foregrounds. The high delay regions of the sky lie near the horizon while low delay 
-regions lie closer to zenith and also perpendicular to the baseline vector. \citet{nithya15} 
-simulate the foreground contamination seen with a dipole beam, a phased array, and a Airy pattern,
+So because sources acquire frequency dependence based on their position on the sky, and the primary beam weights different regions of the sky differently, we see that the primary beam (i.e., the antenna angular response) strongly affects the aggregate frequency dependence
+of the foregrounds. \citet{nithya15} simulate the foreground contamination seen with a dipole beam, a phased array, and a Airy pattern,
 and find that the latter suffers the least foreground leakage into
@@
 
-From the point of view of power spectrum estimation, so long as foreground emission is perfectly contained in the wedge it is irrelevant how much or 
-little of it there is, but the finite bandwidth and imperfect bandpass calibration 
-of real instruments smear power beyond the geometrical edge of the wedge into the EOR 
-window. Sources at higher delay appear closest to the edge of the wedge, and thus are 
-most at risk of leaking into the EOR window due to these effects. In fact, 
+For foreground avoidance-based power spectrum estimation, so long as foreground emission is perfectly contained in the wedge it is irrelevant how much or 
+little of it there is, but real world effects smear power beyond the geometrical edge of the wedge into the EOR 
+window.
+Finite bandwidth, imperfect bandpass calibration, and faraday rotation of polarized sources can all imprint slight frequency structure on otherwise spectrally smooth sources, and those appearing closest to the edge of the wedge are
+most at risk of leaking into the EOR window. In fact, 
 \citet{nithya15,nithya15b} observe in simulations and then in data that while naively we might expect minimal emission 
@@
 This second effect makes intermediate length baselines of tens to hundreds of meters sensitive to the very bright diffuse 
-emission would not see from near zenith. Together, these effects can overcome the decline in beam sensitivity near the horizon. 
+emission they would not see from near zenith. Together, these effects can overcome the decline in beam sensitivity near the horizon. 
 All these considerations highlight the antenna beam as a critical design parameter for 
-21\,cm observatories
+21\,cm observatories.
 
@@
 foreground simulations for HERA (Thyagarajan et al., submitted). A general description to the design of the 
-HERA experiment from an engineering point of view is given by DeBoer et al. (submitted). In essence, we 
+HERA experiment is given by DeBoer et al. (in prep). In essence, we 
 require a large collecting area for
@@
 of freedom and reduced potential of antenna-to-antenna variation (Neben et al 2015b, 
-submitted). These factors naturally lead to a 14\,m diameter parabolic dish with a dipole 
-feed suspended at prime focus. The 352 dishes are positioned in a compact, hexagonal 
+submitted). The 331 dishes are positioned in a compact, hexagonal 
 array permitting redundant baseline calibration and coherent integration in $
-\vec{k}$ space \citep{omniscope,ali2015}. 
+\vec{k}$ space \citep{omniscope,parsons12a}. 
 %The smaller field of view of the HERA dish relative to that of the PAPER dipole or the MWA tile does not limit sensitivity in Fourier space as most leverage on high $k$ modes is from line of sight modes anyway \citep{PoberNextGen}.
@@
 measure the 137\,MHz beam pattern using the ORBCOMM satellite constellation. We obtain beam 
-measurements out to zenith angles of $\sim60^\circ$ where the beam response is -35\,dB relative to zenith, and compare with different numerical models.
+measurements out to zenith angles of $\sim60^\circ$ where the beam response is -35\,dB relative to zenith, and compare with different numerical electromagnetic models.
 We characterize the dish beam at various feed heights to map out the focus and study beam errors due to feed misalignment.
 We compute the collecting areas and implied EOR power spectrum sensitivities of our measured beams.
-After verifying our numerical models, we consider the science implications of these
-beam patterns by foreground delay spectra at different baseline lengths and observing conditions to study when the horizon brightening effect is strongest, and thus, when foreground are must at risk of leaking into the EOR window.
+After verifying our models, we consider the science implications of these
+beam patterns by foreground delay spectra at different baseline lengths and observing conditions to study when the horizon brightening effect is strongest, and thus, when foreground are most at risk of leaking into the EOR window.
 
-In detail, we discuss the electromagnetic design and modeling of the dish in Section 2. We present the 
+We discuss the electromagnetic design and modeling of the dish in Section 2. We present the 
 experimental setup of the beam mapping experiments and discuss their systematics, then 
@@
 
-We review here the design of the HERA dish, and refer to DeBoer et al. (submitted) for details. 
+We review here the design of the HERA dish, and refer to DeBoer et al. (in prep) for details. 
 The 14\,m HERA dish design is a departure from the large N--small D approach used by 21\,cm 
@@
 
-The HERA element is a 14\,m diameter parabolic dish ($f/D\approx0.32$) with a dual-polarized dipole feed (Fig.
-\ref{fig:feedphoto}) suspended at prime focus.
+The HERA element is a 14\,m diameter parabolic dish with $f/D\approx0.32$ and dual-polarized dipole feed (Fig.
+\ref{fig:feedphoto}) suspended at prime focus, where $f/D$ is the ratio of focal length to diameter.
 The dish surface is formed by sheets of wire attached to PVC tubes attached to supports at the edge of the dish and to a hub at the base.
 The feed is suspended with cables attached to three telephone poles around the dish.
-For feed maintenance purposes, a door is engineered into the dish surface on one mesh panel.
-The dipole stands 17\,in below a 78\,in diameter circular mesh back plane surrounded by a 30\,in deep cylinder.
-The cylinder is offset 0.5\,in from the back plane.
+The dipole stands 17'' below a 78'' diameter circular mesh back plane surrounded by a 30'' deep cylinder.
+The cylinder is offset 0.5'' from the back plane.
 The feed is designed to make the beams for both polarizations more similar to each other, and also to taper the dipole beam towards the edge of the dish to mitigate dish-dish coupling.
@@
 \caption{Prototype HERA feed set up outside the dish for preliminary characterization.
-This feed revision consists of a dual-polarized sleeved dipole offset 17\,in from a 78\,in diameter back plane, surrounded by a 30\,in deep cylindrical skirt.}
+This feed revision consists of a dual-polarized sleeved dipole offset 17'' from a 78'' diameter back plane, surrounded by a 30'' deep cylindrical skirt.}
 \label{fig:feedphoto}
@@
 
-One cost of using fewer large antenna elements is a smaller field of view, but this is a 
-small effect for 21\,cm power spectrum analyses as our leverage on $k$ modes comes primarily from $k_\parallel$ modes along the line of sight (in the frequency dimension).
-More significant is frequency structure introduced by time domain reflections between the suspended feed detailed by Ewall-Wice et al.
+One cost of using fewer large antenna elements is a smaller field of view and thus fewer measured Fourier modes perpendicular to the line of sight. 
+However, this is a 
+small effect for 21\,cm power spectrum analyses as our leverage on $k$ modes comes primarily from modes along the line of sight (in the frequency dimension).
+Further, HERA's smaller field of view is actually desirable in that it drastically reduces the magnitude of emission at the edge of the wedge compared to a simple dipole element \citep{nithya15}.
+A second potential drawback is frequency structure introduced by time domain reflections between the suspended feed detailed by Ewall-Wice et al.
 (submitted) with simulations and Patra et al.
-(submitted) with zenith reflectometry measurements.
+(in prep) with zenith reflectometry measurements.
+These works demonstrate, though, that the slight frequency structure of the dish is small enough so as not to interfere with EOR science.
 
@@
 
-We numerically model the HERA dish in both HFSS and in CST, making slightly different assumptions, in order to study the dependence of the beam pattern on modeling imperfections.
+We numerically model the HERA dish in both ANSYS HFSS\footnote{http://www.ansys.com/Products/Electronics/ANSYS-HFSS} and in CST Microwave Studio\footnote{https://www.cst.com/Products/CSTMWS}, making slightly different assumptions, in order to study the dependence of the beam pattern on modeling imperfections.
 In particular, we suspect that the near horizon beam response, which sets the level of horizon brightening, is quite sensitive to modeling assumptions.
@@
 
-The HFSS model uses a 14\,m paraboloid with $f/D=0.32$ as the dish, with a 1\,m hole at vertex.
+The HFSS model (Fig.
+\ref{fig:modelbeams}, left panel) uses a 14\,m paraboloid with $f/D=0.32$ as the dish, with a 1\,m hole at the vertex.
 In reality the 1\,m diameter at the vertex is filled with concrete and supports the PVC pipes which suspend the mesh panels, but we effectively assume here it is perfectly absorbant.
-The feed is modeled as a PAPER dipole suspended 17\,in below a 78\,in diameter circular backplane inside a 30\,in deep skirt hanging 0.5\,in below the backplane.
+The feed is modeled as a PAPER dipole suspended 17'' below a 78'' diameter circular backplane inside a 30'' deep skirt hanging 0.5'' below the backplane.
 All these surfaces are modeled as solid aluminum, as are the dipole ``sleeves'', circular disks just above and below the dipole plane designed to broaden its frequency response.
-The dipoles themselves is modeled as a copper pipe of diameter XX, we neglect the dielectric PVC in which the copper pipe is actually enclosed.
+The dipoles themselves is modeled as a copper pipe of diameter XX.
 In the simulations, we excite one of the dipoles using a modal port and measure the total gain response in each direction to 137.5\,MHz radiation.
 
-In the CST model we again model the dish as a 14\,m diameter solid aluminum paraboloid with $f/D=0.32$ but now neglect the 1\,m hole at zenith, effectively assuming the concrete and earth ground behind it are perfectly reflective.
+In the CST model (Fig.
+\ref{fig:modelbeams}, middle panel) we again model the dish as a 14\,m diameter solid aluminum paraboloid with $f/D=0.32$ but now neglect the 1\,m hole at the vertex, effectively assuming the concrete and earth ground behind it are perfectly reflective.
 The actual material properties are somewhere in between, though difficult to predict theoretically.
@@
 The beam pattern is then obtained at a given frequency using a farfield monitor after the excitation pulse energy within the structure decays to below -80\,dB.
+As expected, both models have slightly stronger sidelobes and wider main lobes than the ideal Airy pattern (Fig.
+\ref{fig:modelbeams}, right panel).
 
@@
 \subsection{ORBCOMM Beam Mapping System Review}
+\label{sec:orbcommreview}
 
-We briefly review the beam mapping system detailed by \citet{neben15}, then discuss 
+We briefly review the beam mapping system detailed by \citet{neben15}, then discuss the 
 application of system for HERA dish measurements. The system 
@@
 as bright point sources which, by virtue of their number ($\sim30$), short orbital periods 
-($\sim90$ minutes), and orbital precession cover $\sim$65\% of the visible sky in just a few 
+($\sim90$ minutes), and orbital precession, cover $\sim$65\% of the visible sky in just a few 
 days. The coverage from the Green Bank site is limited by the fact that the satellites' orbital inclinations are all less 
@@
 measurements, we instead use an ORBCOMM interface box (typically supplied to 
-commercial users of the network) to sync with passing satellites and record their identifier 
+commercial users of the network) to connect to passing satellites and record their identifier 
 and transmission frequency during each pass.
@@
 power measurement no longer probes the response in only the satellite direction. The beam 
-measurements are then gridded in horizontal coordinates in HEALPix \citep{healpix} with a resolution of 
-$1.8^\circ$ (nside=32). As a last quality control step to reject errant beam measurements 
-due to RFI, for instance, we keep only the central 90\% of $\sim50$ measured beam 
-values in each HEALPix cell.
+measurements are then gridded in local Azimuth/Elevation coordinates in HEALPix \citep{healpix} as discussed in Sec. \ref{sec:orbcommreview}.
 
@@
 \begin{figure}[h]
-\includegraphics[width=3.4in]{IMG_0353.JPG}
+\includegraphics[width=3.4in]{ref_dipole_and_hera_dish.jpg}
 \caption{The dish with its suspended feed is seen in the back, 50\,m north of one of the reference antennas used in the null experiment to study systematics.
@@
 See \citet{neben15} for details.
-During the dish measurements the dipole is positioned 100\,m due south of the dish, though we experiment with other locations at first in our to characterize the environmental systematics of these measurements, as detailed in the next section.
+During the dish measurements the dipole is positioned 100\,m due south of the dish, though we experiment with other locations in order to characterize the environmental systematics of these measurements, as detailed in the next section.
 Figure \ref{fig:greenbankdishphoto} shows the dish with suspended feed 50\,m north of one of the reference antennas.
@@
 As we are not able to replace the HERA dish with a reference antenna, we run two null experiments with both reference dipoles deployed (1) 50\,m apart on a NS line, 50\,m south of the HERA dish; and (2) 100\,m apart on a NS line, 100,m south of the HERA dish.
-Figure \ref{fig:null1} shows the  results from these experiments in the form of the ratio of the power responses of the two antennas.
+Figure \ref{fig:nullexptplots} shows the results from these experiments in the form of the ratio of the power responses of the two antennas.
 We collected roughly 100 satellite passes.
-Systematics at the few percent level are observed in  within $20^\circ$ of zenith, and at the $10--20\%$ level farther out.
+Systematics at the few percent level are observed in  within $20^\circ$ of zenith, and at the 10--20\% level farther out.
 The magnitude and angular distribution of these systematics changes modestly as the separation is changed, suggesting that the reference dipoles differ largely due to intrinsic differences, with some environmental variation.
@@
 \includegraphics[width=6.5in]{measured_beams_and_models_maps.pdf}
-\caption{Measured dish power patterns at various feed heights for the EW (left panel) and NS (right panel) instrumental polarizations.
+\caption{Measured dish power patterns at various feed heights for the EW (left panel) and NS (right panel) linear instrumental polarizations.
 The sidelobes shrink and the main lobe narrows as the feed is raised, confirming that the focus of the dish/feed system is higher than the 4.5\,m ideal focus of the parabolic dish.}
@@
 In each configuration we collect data for 2--4 days, obtaining roughly 200 satellite passes.
-We exclude times when the received power is within 20\,dB of the background level determined at between passes, and then grid measured beam values into 1.8$^\circ$ HEALPix cells on the sky, rejecting outliers in the top or bottom 5\% in each cell as a final guard against rare satellite identification problems or ADC saturation issues.
+We exclude times when the received power is within 20\,dB of the background level determined between passes, and then grid measured beam values into 1.8$^\circ$ HEALPix cells on the sky, rejecting outliers in the top or bottom 5\% in each cell as a final guard against rare satellite identification problems or ADC saturation issues.
 
@@
 The roughly $10^\circ$ main lobe narrows slightly as the feed is raised from 4.5\,m to 5.3\,m, and the sidelobes shrink both in size and in amplitude, confirming the numerically predicted focus of 5.3\,m.
-As expected, the EW main lobes are slightly wider in the NS direction.
-In theory, the only asymmetric part of the dish is the dipole feed, so the overall beam should have a $180^\circ$ azimuthal symmetry.
-We observe deviations from this symmetry at the few dB level in the sidelobes, suggesting dish surface and/or feed imperfections given that the systematics identified in the null experiment are smaller.
+As the response of the dish itself is azimuthally symmetric, its response with the feed should have the 180$^\circ$ symmetry of the dipole.
+Indeed, the observed main lobes of the EW beams are slightly wider than those of the NS beams, though we observe deviations from this symmetry in the sidelobes.
+This is not surprising as the sidelobe response is very sensitive to slight dish surface and/or feed imperfections.
 
@@
 Here the evolution of the sidelobes as the feed is raised is again seen starkly, as is the fact that the main lobes are slightly wider along the H planes than along the E planes.
+We observe that both models agree with the measured beams in the main lobe but deviate differently at the few dB level in the sidelobes.
+Note that these deviations are real in that they are larger than the 0.5\,dB scale systemics identified in the null experiment.
 
@@
 These operations produce a realistically smooth beam which reaches roughly -30\,dB at the horizon, as suggested by the numerical models.
-The collecting area is related to the power pattern as
+The collecting area $A$ is related to the beam power pattern $B(\theta,\phi)$ as
 \begin{equation}
@@
  \begin{table}[h]
- \caption{ \label{table:collectingareatable}Collecting area (m$^2$) of measured 137\,MHz beams and corresponding power spectrum SNR for HERA-127.}
+ \caption{ \label{table:collectingareatable}Collecting area (m$^2$) of measured 137\,MHz beams and corresponding power spectrum SNR for HERA-331.}
 \begin{tabular}{| l | l | l |}
@@
 \hline
-  Airy pattern & 155 & 9.1, 11.0, 37.2  \\
-  %CST sim & 67.0 &  \\
-  %Measured, feed at 4\,m & 44.3 &  \\
-    Measured, feed at 5.3\,m & 97.9 & 8.2, 8.3, 29.2 \\
-    Measured, feed at 5\,m & 82.6 & 6.8, 6.9, 26.5 \\
-    Measured, feed at 4.5\,m & 73.6 & 6.4, 6.5, 24.8 \\ 
+  Airy pattern & 155 & 21.4, 25.5, 90.8  \\
+    Measured, feed at 5.3\,m & 97.9 & 18.7, 19.3, 74.3 \\
+    Measured, feed at 5\,m & 82.6 & 15.9, 16.4, 67.9 \\
+    Measured, feed at 4.5\,m & 73.6 & 15.1, 15.4, 63.9 \\ 
   \hline
@@
 
-We run 21cmSense\footnote{https://github.com/jpober/21cmSense} to compute the overall SNR of a power spectrum detection with one season (6 hours per night for 180 nights) of HERA-127 data.
-To input these collecting areas into 21cmSense, we convert these measured dish collecting areas into effective dish diameters, which we input as the \texttt{dish\_size\_in\_lambda} parameter.
-We predict the SNRs with optimistic, moderate, and pessimistic foreground assumptions.
+% To input these collecting areas into 21cmSense, we convert these measured dish collecting areas into effective dish diameters, which we input as the \texttt{dish\_size\_in\_lambda} parameter. 
+We run 21cmSense\footnote{https://github.com/jpober/21cmSense} to compute the overall SNR of a power spectrum detection with one season (6 hours per night for 180 nights) of HERA-331 data.We predict the SNRs with optimistic, moderate, and pessimistic foreground assumptions.
 In the optimistic case, $k$ modes inside the same $uv$ pixel are added coherently, and all modes whose frequency dependence is larger than that of source at the edge of the main lobe are used.
@@
 
-The SNRs computed with the measured collecting areas fall from 9--11 for the Airy pattern  to 6--8 in the pessimistic and moderate cases.
-In the optimistic case, the SNR falls from 37 with the Airy pattern to 24--29 with the measured collecting areas.
-In all cases this reduction is a loss of sensitivity, but a power spectrum detection is still always very significant at the 6$\sigma$ level or better.
+The SNRs computed with the measured collecting areas are 15-20 in the pessimistic and moderate cases compared with 20-25 for the Airy pattern.
+In the optimistic case, the SNR falls from 90 with the Airy pattern to 60-75 with the measured collecting areas.
+In all cases this reduction is a loss of sensitivity, but a power spectrum detection is still always very significant at the 15$\sigma$ level or better.
 
@@
 
-We turn in this section to the effects of the beam power pattern on the apparent frequency dependence of the foregrounds.
+We consider now the effects of the beam power pattern on the apparent frequency dependence of the foregrounds.
 Thyagarajan et al., (submitted) discuss the apparent frequency dependence of foregrounds in more detail as well as methods to mitigate it such as delay space CLEANing.
-We focus in this section on the uncertainties in these foreground power spectrum simulations due to beam modeling uncertainties, but we must first discuss these foreground simulations themselves and their dependence on observing conditions.
+We focus in this section on the uncertainties in these foreground power spectrum simulations due to beam modeling uncertainties, but first discuss these foreground simulations themselves and their dependence on observing conditions.
 
@@
 
-In detail, we simulate visibilities for each beam model at various LSTs, modeling the sky as the sum of the Global Sky Model \citep{gsm} and the Culgoora \citep{Slee1995} and MWA Commissioning Survey \citep{MWACS} point source catalogs.
-We use a frequency spacing of 1\,MHz, sufficient to characterize delays within and just outside of the horizon limits on both baseline lengths we are concerned with, 14\,m and 42\,m.
+In detail, we simulate visibilities for each beam model at various LSTs, modeling the sky as the sum of the Global Sky Model \citep{gsm} and the Culgoora \citep{Slee1995} and MWA Commissioning Survey \citep{MWACS} point source catalogs, all evaluated at 150\,MHz.
+We use a frequency spacing of 1\,MHz, sufficient to characterize delays within and just outside of the horizon limits on both baseline lengths we are concerned with, 14.6\,m and 43.8\,m.
 We use a total bandwidth of 100\,MHz (50\,MHz after applying the Blackman-Harris window) centered on 150\,MHz.
-This bandwidth is larger than the 10\,MHz thought to be safe from signal evolution over redshift, but is the bandwidth used in the wide band delay space foreground CLEAN of \citet{paper32,paper64}.
+This bandwidth is larger than the 10\,MHz thought to be safe from signal evolution over redshift, but is the bandwidth used in the wide band delay space foreground filter of \citet{paper32,paper64}.
 
 Figure \ref{fig:delayspec} (top panel) shows simulated foreground delay spectra at various LSTs using the nominal HFSS beam.
-As all these LSTs are high galactic latitudes far from the galactic center, the total visibility power (the level of the zero delay mode) varies only by a factor of a few over these LSTs on both baseline lengths (14\,m (left panel), 42\,m (right panel)).
-However the negative delay horizon limit (corresponding to the western horizon) has a peak that varies by over three orders of magnitude on the 14\,m baseline and by two orders of magnitude on the 42\,m baseline, demonstrating the stark difference in horizon brightening when the galaxy is just above versus just below the horizon.
+As all these LSTs are high galactic latitudes far from the galactic center, the total visibility power (the level of the zero delay mode) varies only by a factor of a few over these LSTs on both baseline lengths (14.6\,m (left panel), 43.8\,m (right panel)).
+However the positive delay horizon limit (corresponding to the western horizon) has a peak that varies by over 1.5 orders of magnitude on both baseline, demonstrating the stark difference in horizon brightening when the galaxy is just above versus just below the horizon.
 
-In this figure we perform the approximate conversion from delay $\tau$ to $k_\parallel$, which we plot as a second $x$-axis at the top of the plot.
-For these short baselines, $k_\parallel$ may be converted to $k$ by adding $k_\perp=0.005$ for the 14.6\,m baseline or $k_\perp=0.02$ for the 42\,m baseline in quadrature.
-These numbers are small compared to the range of $k_\parallel$ plotted, and thus we interpret the $k_\parallel$ axis as simply the $k$ axis, and plot a 1D model power spectrum computed using 21cmFast \citep{21cmfast} as a dotted line for comparison.
-
+In this figure we perform the approximate conversion from delay $\tau$ to $k_\parallel$ at $z=8$, which we plot as a second $x$-axis at the top of the plot.
+For these short baselines it is a good approximation to interpret $k_\parallel$ as $k$, and we thus plot a 1D model power spectrum computed using 21cmFast \citep{21cmfast} as a dotted line for comparison.
+Ftop panel
 \begin{figure*}[h]
@@
 \caption{Simulated foreground delay spectra using the HFSS beam at various LSTs (top panel).
-We also plot the delay spectra at two LSTs spanning the range of possible horizon brightening for three different beam models.
+We then plot the delay spectra at two LSTs spanning the range of possible horizon brightening for three different beam models.
 The maximum horizon brightening at the positive horizon occurs close to 0$^\circ$ LST (middle panel), and the three beam models thus differ markedly in their predicted delay spectra near the horizon.
+The horizon is shown in all panels as a vertical line at the baseline's maximum delay seen by radiation from the horizon in line with the baseline.
 In contrast, when the horizon brightening effect is smaller at 60$^\circ$ LST, the foreground delay spectra from all three beams agree much more closely.}
@@
 To characterize the effect of beam modeling uncertainties on this horizon brightening, we select two of these LSTs, one with maximal horizon brightening ($2^\circ$), and one with minimal horizon brightening ($62^\circ$).
-Figure \ref{fig:gsmplots} shows the sine-projected Global Sky Model, which dominates the horizon brightening effect, in horizontal coordinates with units of Kelvin for both LSTs.
+Figure \ref{fig:gsmplots} shows the sine-projected Global Sky Model at 150\,MHz, which dominates the horizon brightening effect, in local Azimuth/Elevation coordinates with units of Kelvin for both LSTs.
 Dashed lines mark zenith angles 20$^\circ$, 40$^\circ$, 60$^\circ$, 80$^\circ$.
@@
 Power spectrum analyses by first generation 21\,cm observatories are ongoing, but are contending with challenges ranging from calibration and foreground modeling to the analysis effort required to process thousands of hours of data.
-HERA draws on the most successful ideas from these first generation instruments, pursuing a compact and redundant array layout and collecting area antenna elements to minimize analysis cost.
-The hexagonal grid allows redundant calibration and coherent power spectrum integration, and the large 14\,m dish achieves sufficient sensitivity at a reasonably data processing and analysis cost.
+HERA draws on the most successful ideas from these first generation instruments, pursuing a compact and redundant array layout and large collecting area antenna elements.
+The hexagonal grid allows redundant calibration and coherent power spectrum integration, and the large 14\,m dish achieves sufficient sensitivity at a reasonable data processing and analysis cost.
 The papers in this series characterize the 14\,m diameter dish used as HERA's antenna element using reflectometry measurements and simulations which probe its frequency response, as well as power pattern measurement which probe its angular response.
@@
 We begin with the power pattern measurements using the beam mapping system of \citet{neben15} which we deploy at the prototype three-element HERA array at the National Radio Astronomy Observatory--Green Bank.
-Only one dish had been constructed when these measurements were made.
 We present measured power patterns for three dish configurations with the feed at different heights over the dish surface in order to characterize the focus of the system.
@@
 We observe a reduction of 30--50\% from the geometric cross section of a 14\,m dish due to the dipole feed and its cylindrical skirt which tapers the beam towards the edge of the dish to mitigate cross coupling with adjacent dishes.
-We convert these collecting areas into effective dish sizes, then use 21cmSense to predict the overall power spectrum SNR with one season of HERA-127 data.
-We find SNRs of 6--8 in pessimistic and moderate foreground scenarios, and 24--29 in optimistic ones, to be compared with SNRs of roughly 10 and 37 using full geometric collecting area.
-While certainly a reduction from the theoretical limit, these sensitivities still permit a very significant detection of the 21\,cm signal after a single observing season.
+We convert these collecting areas into effective dish sizes, then use 21cmSense to predict the overall power spectrum SNR with one season of HERA-331 data.
+We find SNRs of 18.7, 19.3, and 74.3 in the pessimistic, and moderate, and optimistic foreground scenarios with the feed at optimal focus.
+While a reduction from the theoretical limit of an unobstructed 14\,m aperture, these sensitivities still permit a very significant detection of the 21\,cm signal after a single observing season.
 
@@
 This produces a characteristic ``pitchfork'' shape in the delay spectrum of a single baseline, with a zero delay peak due to bright near-zenith emission surrounded by tines at the negative and positive horizon limits due to emission from the two horizon directions in line with the baseline.
-These horizon peaks are \textit{most} at risk of leaking foreground power into the EOR window given chromatic instrumental imperfections such as bandpass miscalibration.
+These horizon peaks are \textit{most} at risk of leaking foreground power into the EOR window given chromatic instrumental responses such as bandpass miscalibration, though techniques are being developed to suppress emission from near the horizon \citep{parsonsoptimalfringeratefiltering}.
 
@@
 These papers demonstrate that in the best case, a combination of bandpass calibration and delay space CLEANing can mitigate foregrounds to a manageable level, while in the worst case, HERA can still achieve a XX--XX $\sigma$ detection of the EOR parameters from the power spectrum by simply excluding a very conservative buffer outside the wedge.
-All these considerations highlight the need for precision characterization of antenna elements and their implications for 21\,cm science analyses on the part of next generation observatories if we are to have any hope of making this challenging measurement.
+All these considerations highlight the need for precision characterization of antenna elements and their implications for 21\,cm science analyses on the part of next generation observatories.
 

### 2016-02-03 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev3.tex
added dish figure, working on power pattern measurement text updates

@@
  sensitivity and minimal sidelobes and horizon response without incurring the large cost per collecting 
-area of very large dishes. A dish is preferred to a large phased array as it has fewer degrees 
-of freedom and reduced potential of antenna-to-antenna variation (Neben et al 2015b, 
-submitted). The 331 dishes are positioned in a compact, hexagonal 
+area of very large dishes.
+A dish is preferred to a large phased array as it has a less complex beampattern and reduced potential for antenna-to-antenna variation (Neben et al, submitted).
+The 331 dishes are positioned in a compact, hexagonal
 array permitting redundant baseline calibration and coherent integration in $
@@
 
-We review here the design of the HERA dish, and refer to DeBoer et al. (in prep) for details. 
-The 14\,m HERA dish design is a departure from the large N--small D approach used by 21\,cm 
-observatories like PAPER and the MWA. Both observatories are actively pursuing power 
-spectrum analyses using several year data runs, but the sheer data volume makes 
-characterization and removal of systematics, as well as repeated or complimentary analyses, 
-challenging. A larger element was chosen for HERA primarily to reduce correlation and data processing costs.
+The HERA element (Fig.
+\ref{fig:feeddiagram}) is a 14\,m diameter faceted parabolic dish ($f\#=0.32$) with a dual-polarized dipole feed suspended at prime focus.
+The dish surface is formed by wire mesh sheets (i.e., facets) mounted on PVC tubes which run from the lip of the dish to the hub at the vertex.
+The feed consists of a dual linear polarization PAPER sleeved dipole mounted 17'' below a 78'' diameter wire mesh back plane surrounded by a 30'' deep cylinder, suspended from cables attached to each the three telephone poles around the dish.
+The dipole ``sleeves'' are circular disks just above and below the dipole designed to broaden its frequency response.
+The cylinder is offset 0.5'' from the back plane, and is designed to make the beams for both linear polarizations more similar, and also to taper the dipole beam towards the edge of the dish to mitigate dish-dish coupling.
+Fig.
+\ref{fig:feedphoto} shows the feed as deployed on the ground for early testing.
+The nominal dish focus is $f=(f\#)D=4.48$\,m, though our numerical electromagnetic models suggest the actual focus is slightly higher due to the feed geometry.
+In this work we study the dish beam pattern at feed heights of 4.5\,m, 5.0\,m, and 5.3\,m, measured from dish surface to feed plane.
+These height measurements are uncertain at the $\pm5\%$ level in this study.
+For more details on the dish design and construction see DeBoer et al.
+(in prep).
+Also note that feed/dish optimization studies are ongoing and the values of these parameters may change in the full HERA array.
 
-The HERA element is a 14\,m diameter parabolic dish with $f/D\approx0.32$ and dual-polarized dipole feed (Fig.
-\ref{fig:feedphoto}) suspended at prime focus, where $f/D$ is the ratio of focal length to diameter.
-The dish surface is formed by sheets of wire attached to PVC tubes attached to supports at the edge of the dish and to a hub at the base.
-The feed is suspended with cables attached to three telephone poles around the dish.
-The dipole stands 17'' below a 78'' diameter circular mesh back plane surrounded by a 30'' deep cylinder.
-The cylinder is offset 0.5'' from the back plane.
-The feed is designed to make the beams for both polarizations more similar to each other, and also to taper the dipole beam towards the edge of the dish to mitigate dish-dish coupling.
-The nominal dish focus is at 4.5\,m from the dish surface, though numerical dish models including the feed predict the focus is closer to 5.3\,m.
-
-Feed/dish optimization studies are ongoing and these parameters may change in the final HERA array, but in this work we use the feed with these dimensions and study the beam with the feed suspended at different heights.
-We study the position of the dish focus, the shape of the main lobe, the magnitude of the dish sidelobes, the degree of beam symmetry, the actual dish/feed efficiency (i.e., collecting area), and the expected level of antenna-to-antenna variation.
+\begin{figure}[h]
+\includegraphics[width=3.4in]{dish_and_feed_diagram.pdf}
+\caption{some stuff here}
+\label{fig:feeddiagram}
+\end{figure}
 
@@
 
-One cost of using fewer large antenna elements is a smaller field of view and thus fewer measured Fourier modes perpendicular to the line of sight. 
+As the HERA element is larger than the MWA or PAPER antenna elements, one might worry about the  smaller field of view and thus smaller number of measured Fourier modes perpendicular to the line of sight.
 However, this is a
@@
 (in prep) with zenith reflectometry measurements.
-These works demonstrate, though, that the slight frequency structure of the dish is small enough so as not to interfere with EOR science.
-
+These works demonstrate, though, that the slight frequency structure of the dish is sufficiently small to not interfere with EOR science.
+\\
 \subsection{Dish Modeling}
@@
 \includegraphics[width=7in]{dave197_rich195_airy_beams.pdf}
-\caption{Simulated dish power patterns at 137\,MHz (Sec. \ref{sec:dishmodels}) using HFSS (left) and CST (middle) are shown beside an ideal Airy pattern for a 14\,m diameter dish for comparison.}
+\caption{Simulated dish power patterns at 137\,MHz (Sec.
+\ref{sec:dishmodels}) with $h_\text{feed}=5$\,m using HFSS (left) and CST (middle) are shown beside an ideal Airy pattern for a 14\,m diameter dish for comparison.}
 \label{fig:modelbeams}
@@
 We numerically model the HERA dish in both ANSYS HFSS\footnote{http://www.ansys.com/Products/Electronics/ANSYS-HFSS} and in CST Microwave Studio\footnote{https://www.cst.com/Products/CSTMWS}, making slightly different assumptions, in order to study the dependence of the beam pattern on modeling imperfections.
-In particular, we suspect that the near horizon beam response, which sets the level of horizon brightening, is quite sensitive to modeling assumptions.
-Modeling is also useful to probe the best focus of the dish--feed system.
-The nominal focus is at 4.5\,m given that the dish has $f/D=0.32$, though the feed back plane and skirt are expected to move the focus slightly.
+In particular, the near horizon beam response, which sets the level of horizon brightening in the delay spectrum, is quite sensitive to modeling assumptions.
+Modeling also probes the best focus of the dish--feed system.
 
-The HFSS model (Fig.
-\ref{fig:modelbeams}, left panel) uses a 14\,m paraboloid with $f/D=0.32$ as the dish, with a 1\,m hole at the vertex.
-In reality the 1\,m diameter at the vertex is filled with concrete and supports the PVC pipes which suspend the mesh panels, but we effectively assume here it is perfectly absorbant.
-The feed is modeled as a PAPER dipole suspended 17'' below a 78'' diameter circular backplane inside a 30'' deep skirt hanging 0.5'' below the backplane.
-All these surfaces are modeled as solid aluminum, as are the dipole ``sleeves'', circular disks just above and below the dipole plane designed to broaden its frequency response.
-The dipoles themselves is modeled as a copper pipe of diameter XX.
+The HFSS beam model (Fig.
+\ref{fig:modelbeams}, left panel) assumes a solid 14\,m parabolic dish ($f\#=0.32$) with a 1\,m hole at the vertex.
+In reality a 1\,m diameter circle at the vertex is filled with concrete and supports the PVC pipes which suspend the mesh panels, but we effectively assume here it is perfectly absorbant.
+The feed is modeled as sleeved dipole with a solid metal back plane and cylinder with the dimensions given above.
+Copper is used for the dipole itself, and aluminum for all reflecting surfaces.
 In the simulations, we excite one of the dipoles using a modal port and measure the total gain response in each direction to 137.5\,MHz radiation.
 
-In the CST model (Fig.
-\ref{fig:modelbeams}, middle panel) we again model the dish as a 14\,m diameter solid aluminum paraboloid with $f/D=0.32$ but now neglect the 1\,m hole at the vertex, effectively assuming the concrete and earth ground behind it are perfectly reflective.
-The actual material properties are somewhere in between, though difficult to predict theoretically.
-The feed model has the same dimensions as in the HFSS model.
-The simulations are done by exciting one of the dipoles with band-limited noise (100--200\,MHz).
-The beam pattern is then obtained at a given frequency using a farfield monitor after the excitation pulse energy within the structure decays to below -80\,dB.
+The CST beam model (Fig.
+\ref{fig:modelbeams}, middle panel) again assumes a 14\,m parabolic diameter solid aluminum paraboloid with $f/D=0.32$ but neglects the 1\,m hole at the vertex, effectively assuming the concrete and earth ground behind it are perfectly reflective.
+The actual material properties are somewhere between fully reflective and fully absorbant, and thus, between these two models.
+The feed model has the same dimensions and properties as in the HFSS model.
+These simulations are done by exciting one of the dipoles with band-limited noise (100--200\,MHz), then measuring the farfield radiation in each direction after the excitation pulse energy within the structure decays to below -80\,dB.
 As expected, both models have slightly stronger sidelobes and wider main lobes than the ideal Airy pattern (Fig.
 \ref{fig:modelbeams}, right panel).
+In both models, the best focus is found to be close to 5.3\,m with this feed geometry, slightly larger than the nominal focus of 4.5\,m, as expected.
 
@@
 \includegraphics[width=6.5in]{measured_beams_and_models_maps.pdf}
-\caption{Measured dish power patterns at various feed heights for the EW (left panel) and NS (right panel) linear instrumental polarizations.
-The sidelobes shrink and the main lobe narrows as the feed is raised, confirming that the focus of the dish/feed system is higher than the 4.5\,m ideal focus of the parabolic dish.}
+\caption{Measured dish power patterns with three feed heights for the EW (left panel) and NS (right panel) linear instrumental polarizations.
+The sidelobes shrink and the main lobe narrows as the feed is raised, confirming that the best focus of the dish/feed system is close to $h_\text{feed}=5.3$\,m.}
 \label{fig:measuredbeammaps}
@@
 \caption{Slices through the E and H planes through the measured dish power patterns (points) and numerical models (curves).
-The measured beams agree with both models in the main lobe out to zenith angles of 15--20$^\circ$, but begin to deviate in the sidelobes at the 0.1--0.5\% level of the beam.}
+The measured beams agree with both models in the main lobe out to zenith angles of 15--20$^\circ$, but begin to deviate in the sidelobes where the beam response is 25-30\,dB down from zenith.}
 \label{fig:measuredbeamslices}
@@
 
-We make three dish power pattern measurements with the feed at different heights: (1) 4.5\,m, the nominal dish focus; (2) 5.0\,m, an intermediate focus; and (3) 5.3\,m, the numerically determined focus of the dish/feed system, where all heights are measured from the dish surface to the feed back plane.
+feed misalignment vs surface imperfections (different across different feed heights)
+risk of cross-coupling
+tie-downs
+
+We make dish power pattern measurements with the feed at 4.5\,m, 5.0\,m, and 5.3\,m height above the dish surface (see Fig. \ref{fig:feeddiagram}).
+
 In each configuration we collect data for 2--4 days, obtaining roughly 200 satellite passes.
@@
   Airy pattern & 155 & 21.4, 25.5, 90.8  \\
-    Measured, feed at 5.3\,m & 97.9 & 18.7, 19.3, 74.3 \\
-    Measured, feed at 5\,m & 82.6 & 15.9, 16.4, 67.9 \\
-    Measured, feed at 4.5\,m & 73.6 & 15.1, 15.4, 63.9 \\ 
+    Measured, feed at 5.3\,m & 93.0 & 18.7, 19.3, 74.3 \\
+    Measured, feed at 5\,m & 77.1 & 15.9, 16.4, 67.9 \\
+    Measured, feed at 4.5\,m & 68.5 & 15.1, 15.4, 63.9 \\ 
   \hline
@@
 % To input these collecting areas into 21cmSense, we convert these measured dish collecting areas into effective dish diameters, which we input as the \texttt{dish\_size\_in\_lambda} parameter. 
-We run 21cmSense\footnote{https://github.com/jpober/21cmSense} to compute the overall SNR of a power spectrum detection with one season (6 hours per night for 180 nights) of HERA-331 data.We predict the SNRs with optimistic, moderate, and pessimistic foreground assumptions.
+We run 21cmSense\footnote{https://github.com/jpober/21cmSense} to compute the overall SNR of a power spectrum detection with one season (6 hours per night for 180 nights) of HERA-331 data.
+We predict the SNRs with optimistic, moderate, and pessimistic foreground assumptions assuming a fiducial Epoch of Reionization model generated with 21cmFast \citep{21cmfast}.
+This model assumes $\zeta=31.5$ for the ionizing efficiency, $T_\mathrm{vir}=1.5\times10^4$\,K for the minimum virial temperature of halos producing ionizing photons, and $R_\text{mfp}=30$\,Mpc for the mean free path of ionizing photons, and reaches 50\% ionization at $z \sim 9.5$ and complete ionization at $z \sim 7$, and is consistent with most current observations \citep[e.g.][]{PoberNextGen}.
 In the optimistic case, $k$ modes inside the same $uv$ pixel are added coherently, and all modes whose frequency dependence is larger than that of source at the edge of the main lobe are used.
-In the moderate case, $k$ modes inside the same $uv$ pixel are added coherently and only modes whose frequency dependence falls outside of the horizon plus a buffer are used.
-In the pessimistic case, all baselines are added incoherently and only modes outside the horizon plus a buffer are used.
+In the moderate case, $k$ modes inside the same $uv$ pixel are added coherently and only modes whose frequency dependence falls outside of the horizon plus a buffer of $\Delta k_\parallel=0.1\,\mathrm{h}\,\mathrm{Mpc}^{-1}$ are used.
+In the pessimistic case, all baselines are added incoherently and only modes outside the horizon plus the same buffer are used.
 
@@
 
+As discussed by the other papers in this series, the frequency dependence of both the beam's angular response and its overall gain widen the delay kernel of a source, leaking power into the EOR window out to $k_\parallel=$0.15-0.23h\,Mpc$^{-1}$.
+This is well inside the wedge plus buffer assumed in the moderate and pessimistic cases considered above.
+The optimistic case requires calibrating out the instrument frequency response enough to begin to access cosmological modes within the wedge.
+This is much more challenging, but the sensitivity gains are enormous as those signal modes are thought to be the strongest.
+
 %% foreground delay spectrum simsulations
@@
 When the pitchfork effect is large, its uncertainty is also large as seen in the deviation of the delay spectra with HFSS and CST beam models in these simulations.
-When the effect is small, the two beam models produce much more similar results, highlighting the delay spectrum as an exquisite probe of the challenging to measure beam response at very low elevations.
-
-% frequency dependence of the beam pattern and overall gain (due to reflections) likely dominates leakage deep within the window, but the other papers in this series demonstrate that this leakage level is within our spec
-
-As discussed by the other papers in this series, the frequency dependence of the beam power pattern and its overall gain widen the delay kernel of a source, leaking power into the EOR window.
-These papers demonstrate that in the best case, a combination of bandpass calibration and delay space CLEANing can mitigate foregrounds to a manageable level, while in the worst case, HERA can still achieve a XX--XX $\sigma$ detection of the EOR parameters from the power spectrum by simply excluding a very conservative buffer outside the wedge.
-All these considerations highlight the need for precision characterization of antenna elements and their implications for 21\,cm science analyses on the part of next generation observatories.
+When the effect is small, the two beam models produce much more similar results, highlighting the delay spectrum as an exquisite probe of the difficult-to-measure beam response at very low elevations.
 

### 2016-02-03 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev3.tex
various updates

@@
 We measure the angular response at 137\,MHz using the ORBCOMM beam mapping system of \citet{neben15}.
-We measure a collecting area of 97\,m$^2$ in the optimal dish/feed configuration, implying HERA-331 should detect the EOR with a signal-to-noise of 74 with a single season of observations, making optimistic foreground and analysis assumptions.
-Even with more pessimistic assumptions, using only previously demonstrated techniques, a HERA should achieve a signal-to-noise of 20.
-Lastly we simulate foreground visibilities using numerical beam models and study the foreground distribution in Fourier space as a function of local sidereal time, and the uncertainties in these predictions due to beam modeling uncertainties.
+We measure a collecting area of 97\,m$^2$ in the optimal dish/feed configuration, implying HERA-331 should detect the EOR power spectrum with a signal-to-noise ratio of 74 with a single season of observations, making optimistic foreground and analysis assumptions.
+Even with more pessimistic assumptions, using only previously demonstrated techniques, a HERA should detect the power spectrum with at least $18\sigma$ significance.
+Lastly we study the impact of these beam measurements on the distribution of foregrounds in Fourier space.
 \end{abstract}
@@
 Redundant baselines also permit redundant calibration techniques which solve for the relative calibration between all antennas \citep{liu2010,zheng14}.
-In contrast, non-redundant arrays are pursuing fully sky model-based calibration schemes which risk frequency-dependent calibration systematics due to sky modeling inaccuracy \citep{braun2013}.
 A central lesson from first generation instruments is that it is essential to characterize the instrument response to foreground emission lest instrument frequency dependence smear foreground power into cosmological signal modes.
@@
 This effect is straightforward to understand for a single baseline which measures the sky intensity weighted by the complex sky fringe
-$e^{i \vec{k}\cdot\vec{b}}$, where $\vec{k}(f)$ is the wave vector of incident radiation pointing along its direction of travel, $\vec{b}$ is the baseline vector in meters, and $f$ is the observation frequency.
+$e^{i \vec{k}\cdot\vec{b}}$, where $\vec{k}(\nu)$ is the wave vector of incident radiation pointing along its direction of travel, $\vec{b}$ is the baseline vector in meters, and $\nu$ is the observation frequency.
 Thus sources at different positions relative to the baseline vector manifest different
 frequency structure despite their intrinsically smooth spectra, but are geometrically limited 
-by the baseline length to a maximum frequency dependence of  $e^{2\pi i f b/c}$. This limits the foreground contamination 
+by the baseline length to a maximum frequency dependence of  $e^{2\pi i \nu \tau_g}$, where $\tau_g=\vec{b}\cdot\hat{k}/c$ is the delay in radiation arrival time between the two antennas in the baseline.
+This limits the foreground contamination
 to a wedge shaped region in Fourier space with $k_\parallel<a k_\perp$, where $k_\perp$ and $k_\parallel$ represent spatial modes 
@@
 window.
-Finite bandwidth, imperfect bandpass calibration, and faraday rotation of polarized sources can all imprint slight frequency structure on otherwise spectrally smooth sources, and those appearing closest to the edge of the wedge are
+Finite bandwidth, imperfect bandpass calibration, and faraday rotation \citep{jelic2010,moore2013,giannisurvey, moore2013,moore2015,asad2015} of polarized sources can all imprint slight frequency structure on otherwise spectrally smooth sources, and those appearing closest to the edge of the wedge are
 most at risk of leaking into the EOR window. In fact, 
@@
 The CST beam model (Fig.
-\ref{fig:modelbeams}, middle panel) again assumes a 14\,m parabolic diameter solid aluminum paraboloid with $f/D=0.32$ but neglects the 1\,m hole at the vertex, effectively assuming the concrete and earth ground behind it are perfectly reflective.
+\ref{fig:modelbeams}, middle panel) again assumes a 14\,m parabolic diameter solid aluminum paraboloid with $f\#=0.32$ but neglects the 1\,m hole at the vertex, effectively assuming the concrete and earth ground behind it are perfectly reflective.
 The actual material properties are somewhere between fully reflective and fully absorbant, and thus, between these two models.
@@
 
-We make dish power pattern measurements with the feed at 4.5\,m, 5.0\,m, and 5.3\,m height above the dish surface (see Fig. \ref{fig:feeddiagram}).
-
+We make dish power pattern measurements at 137\,MHz as described in Sec.
+\ref{sec:orbcommreview} with the feed at 4.5\,m, 5.0\,m, and 5.3\,m height above the dish surface (see Fig.
+\ref{fig:feeddiagram}).
 In each configuration we collect data for 2--4 days, obtaining roughly 200 satellite passes.
@@
 
-Figure \ref{fig:measuredbeammaps} shows the measured power patterns for these three feed heights for the EW (left panel) and the NS (right panel) feed polarization.
+Fig.
+\ref{fig:measuredbeammaps} shows the measured power patterns for these three feed heights for the EW (left panel) and the NS (right panel) feed polarization.
 These maps are plotted in sine-projection with dashed circles marking zenith angles of $20^\circ$, $40^\circ$, $60^\circ$, $80^\circ$.
-The sky coverage in these dish measurements extends out to typically $\theta\sim50-60^\circ$.
-Beyond that the ORBCOMM flux is sufficiently attenuated relative to diffuse galactic emission that a power ratio measurement between the two antennas is no longer a clean probe of their gains in the direction of the satellite.
-At these zenith angles, the beam sidelobes are roughly -30\,dB, and are trending downward at the edge of the measured region.
+The sky coverage in these dish measurements extends out to typically $\theta\sim60^\circ$, beyond which the ORBCOMM flux is sufficiently attenuated relative to diffuse galactic emission that power measurements are no longer  clean probes of the antenna gains in the direction of the satellite.
+At these largest measurable zenith angles the beam sidelobes are roughly -30\,dB and trending downward.
 
-The roughly $10^\circ$ main lobe narrows slightly as the feed is raised from 4.5\,m to 5.3\,m, and the sidelobes shrink both in size and in amplitude, confirming the numerically predicted focus of 5.3\,m.
+The roughly $10^\circ$ main lobe narrows slightly as the feed is raised from 4.5\,m to 5.3\,m, and the sidelobes shrink both in size and in amplitude, confirming that the focus is closer to 5.3\,m.
 As the response of the dish itself is azimuthally symmetric, its response with the feed should have the 180$^\circ$ symmetry of the dipole.
-Indeed, the observed main lobes of the EW beams are slightly wider than those of the NS beams, though we observe deviations from this symmetry in the sidelobes.
-This is not surprising as the sidelobe response is very sensitive to slight dish surface and/or feed imperfections.
+Indeed, the observed main lobes of the EW (NS) beams are slightly wider in the NS (EW), especially in the 5.3\,m feed height beam as it is most in focus.
+Unsurprisingly, we observe deviations from this symmetry in the sidelobes, which are very sensitive to slight dish/feed imperfections.
 
@@
 Here the evolution of the sidelobes as the feed is raised is again seen starkly, as is the fact that the main lobes are slightly wider along the H planes than along the E planes.
-We observe that both models agree with the measured beams in the main lobe but deviate differently at the few dB level in the sidelobes.
-Note that these deviations are real in that they are larger than the 0.5\,dB scale systemics identified in the null experiment.
+We observe that both models agree with the measured beams in the main lobe but deviate differently at the 1--5 dB level in the sidelobes.
+
+We emphasize that the model deviations observed in the measured beams are real in that they are larger than the 0.5\,dB systematics observed in the null experiments (Fig.
+\ref{fig:nullexptplots}).
+Those experiments bound the impact of environmental reflections and reference dipole mismodeling to the 10\% level or smaller across the whole sky.
+The observed dish beam asymmetries and sidelobe mismodeling are likely due to imperfections in dish construction such as surface imperfections or feed misalignment.
+As the observed sidelobe asymmetries in Fig.
+\ref{fig:measuredbeammaps} change over the three beam measurements, they are more likely to result from feed mis-centering over the dish.
+The feed is suspended by rope from three telephone poles spaced around the dish, and is raised by pulling all three ropes to a new length.
+Each time this is done the feed centering is slightly disturbed.
+Feed mis-leveling and mis-alignment will also disturb the beampattern, but these effects would persist across changes of the feed height.
+In mitigate these errors, the feeds in the full HERA array will be tied down to the dish surface.
 
@@
 
-%- power spectrum analyses by first generation instruments are ongoing, but face many challenges
-%- that’s why HERA was designed to be optimized for 21cm
-
 Power spectrum analyses by first generation 21\,cm observatories are ongoing, but are contending with challenges ranging from calibration and foreground modeling to the analysis effort required to process thousands of hours of data.
@@
 The papers in this series characterize the 14\,m diameter dish used as HERA's antenna element using reflectometry measurements and simulations which probe its frequency response, as well as power pattern measurement which probe its angular response.
-
-%- in this paper we have characterized the HERA dish’s angular response
-%  down to 60deg zenith angle, -35dB from zenith
-%- confirms models to exquisite fidelity unachievable with celestial sources
-%- the level of model disagreement also gives us a handle on antenna-to-to antenna variation
 
@@
 
-%% sensitivity
-% collecting area 
-% power spectrum SNR
 We quantify HERA's 21\,cm power spectrum sensitivity given our beam measurements by first computing the collecting area of the different dish configurations.
@@
 
-As discussed by the other papers in this series, the frequency dependence of both the beam's angular response and its overall gain widen the delay kernel of a source, leaking power into the EOR window out to $k_\parallel=$0.15-0.23h\,Mpc$^{-1}$.
-This is well inside the wedge plus buffer assumed in the moderate and pessimistic cases considered above.
-The optimistic case requires calibrating out the instrument frequency response enough to begin to access cosmological modes within the wedge.
-This is much more challenging, but the sensitivity gains are enormous as those signal modes are thought to be the strongest.
-
-%% foreground delay spectrum simsulations
-%- given the latest understanding of instrument chromaticity and
-%  foreground isolation (ie, Nithya), we simulate the effects of these
-%  beams on science
- %   - taking into account uncertainties in near-horizon beam response unprobed by our measurements
-%- we make predictions for the level of horizon brightening at different LSTs, and discuss the uncertainties due to uncertain beam models (horizon brighting is an exquisite of the low elevation beam response, though an integrated statistic)
-% horizon brightening will dominated leakage into the outer window modes
 Beyond simple sensitivity considerations, though, the beam pattern affects science analyses by reweighting celestial emission in different regions of the sky, which are then imprinted with different frequency dependence by the interferometer.
@@
 When the effect is small, the two beam models produce much more similar results, highlighting the delay spectrum as an exquisite probe of the difficult-to-measure beam response at very low elevations.
+
+As discussed by the other papers in this series, the frequency dependence of both the beam's angular response and its overall gain widen the delay kernel of a source, leaking power into the EOR window out to $k_\parallel=$0.15-0.23h\,Mpc$^{-1}$.
+This is well inside the wedge plus buffer assumed in the moderate and pessimistic cases considered above.
+The optimistic case requires calibrating out the instrument frequency response enough to begin to access cosmological modes within the wedge.
+This is much more challenging, but the sensitivity gains are enormous as those signal modes are thought to be the strongest.
+Even in the pessimistic case, though, assuming only previously demonstrated analysis techniques, we project a $18\sigma$ detection of the EOR power spectrum which would provide begin to probe reionization models in detail and shed light on our cosmic dawn.
 

### 2016-02-04 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev3.tex
done with rev3

@@
 Aaron Parsons\altaffilmark{4},
+James E. Aguirre\altaffilmark{6},
 Aaron Ewall-Wice\altaffilmark{1},
@@
 Nithyanandan Thyagarajan\altaffilmark{5},
-James E. Aguirre\altaffilmark{6},
 Zaki S. Ali\altaffilmark{4},
 Judd Bowman\altaffilmark{5},
-Carina Cheng\altaffilmark{4}
-Saul A. Kohn\altaffilmark{6},
+Carina Cheng\altaffilmark{4},
 Roger Dickenson\altaffilmark{3},
@@
 Mike Hedrick\altaffilmark{3},
+Saul A. Kohn\altaffilmark{6},
+Benjamin R.B. Saliwanchik\altaffilmark{7},
 Patrick Schaffner\altaffilmark{3},
@@
 Rusty Taylor\altaffilmark{3},
-Butch Wirt\altaffilmark{3}}
+Butch Wirt\altaffilmark{3},
+Jeff Zheng\altaffilmark{1}}
 
@@
 \affil{\altaffilmark{6}Dept. of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA}
+\affil{\altaffilmark{7}Astrophysics and Cosmology Research Unit, University of KwaZulu-Natal, Durban, South Africa}
 
@@
 The Hydrogen Epoch of Reionization Array (HERA) is a radio interferometer aiming to detect the power spectrum of 21\,cm fluctuations from neutral hydrogen from the Epoch of Reionization.
-Drawing on lessons from the Murchison Widefield Array (MWA) and the Precision Array for Probing the Epoch of Reionization (PAPER), HERA is a hexagonal array of large (14\,m) dishes with suspended dipole feeds with element collecting area of 100\,m$^2$.
+Drawing on lessons from the Murchison Widefield Array (MWA) and the Precision Array for Probing the Epoch of Reionization (PAPER), HERA is a hexagonal array of large (14\,m diameter) dishes with suspended dipole feeds with element collecting area of 100\,m$^2$.
 Not only does the dish determine overall sensitivity, it determines the aggregate frequency structure of foregrounds in the interferometer.
@@
 We measure the angular response at 137\,MHz using the ORBCOMM beam mapping system of \citet{neben15}.
-We measure a collecting area of 97\,m$^2$ in the optimal dish/feed configuration, implying HERA-331 should detect the EOR power spectrum with a signal-to-noise ratio of 74 with a single season of observations, making optimistic foreground and analysis assumptions.
-Even with more pessimistic assumptions, using only previously demonstrated techniques, a HERA should detect the power spectrum with at least $18\sigma$ significance.
+We measure a collecting area of 93\,m$^2$ in the optimal dish/feed configuration, implying HERA-331 should detect the EOR power spectrum with a signal-to-noise ratio of 19.3 using a foreground avoidance approach, and 74.3 using a foreground subtraction approach.
 Lastly we study the impact of these beam measurements on the distribution of foregrounds in Fourier space.
@@
 (in prep)]{PoberNextGen} is drawing on lessons learned by the MWA and PAPER to reach the calibration and foreground isolation accuracy required to make a significant detection and characterization of the cosmological signal.
-HERA uses 14\,m diameter parabolic dishes arranged in a compact, hexagonal array to achieve coherent integration on the very low surface brightness 21\,cm signal.
+HERA uses 14\,m diameter parabolic dishes arranged in a compact, hexagonal array to achieve coherent integration of the very low surface brightness 21\,cm signal.
 Redundant baselines also permit redundant calibration techniques which solve for the relative calibration between all antennas \citep{liu2010,zheng14}.
@@
 to a wedge shaped region in Fourier space with $k_\parallel<a k_\perp$, where $k_\perp$ and $k_\parallel$ represent spatial modes 
-perpendicular and parallel to the line of sight, and $a$ is a constant depending on the observational frequency and cosmology. The complement of the wedge is knows as the ``EOR window''.
+perpendicular and parallel to the line of sight, and $a$ is a constant depending on the observational frequency and cosmology. The complement of the wedge is known as the ``EOR window''.
 
@@
 levels. To be sure, all are subject to the same geometric limits on foreground frequency-
-dependence limiting foreground bounding foreground emission within the wedge, but the emission from high delay is better suppressed using the 
+dependence which limit foreground bounding foreground emission within the wedge, but the emission from high delay is better suppressed using the 
 Airy pattern leaving much of the wedge effectively empty.
@@
 This is the first in a series of four papers detailing the HERA element. In this work we study 
-angular response of the dish and its implications for power spectrum measurements. The three companion 
+the angular response of the dish and its implications for power spectrum measurements. The three companion 
 papers present reflectometry measurements (Patra et al., submitted) and simulations (Ewall-Wice et al., 
@@
 experimental setup of the beam mapping experiments and discuss their systematics, then 
-review the ORBCOMM beam measurement system, in Section 3. We present our power pattern 
+review the ORBCOMM beam measurement system in Section 3. We present our power pattern 
 measurements in Section 4, and study the science implications of these beam measurements for foreground power spectra in Section 5, then conclude with discussion in Section 6.
@@
 The nominal dish focus is $f=(f\#)D=4.48$\,m, though our numerical electromagnetic models suggest the actual focus is slightly higher due to the feed geometry.
-In this work we study the dish beam pattern at feed heights of 4.5\,m, 5.0\,m, and 5.3\,m, measured from dish surface to feed plane.
+In this work we study the dish beam pattern at feed heights of 4.5\,m, 5.0\,m, and 5.3\,m, measured from dish surface to feed plane, the last height being the maximum height we can achieve with the feed suspension system installed on the dish.
 These height measurements are uncertain at the $\pm5\%$ level in this study.
@@
 (in prep).
-Also note that feed/dish optimization studies are ongoing and the values of these parameters may change in the full HERA array.
+Feed/dish optimization studies are ongoing and the values of these parameters may change in the full HERA array.
 
@@
 Further, HERA's smaller field of view is actually desirable in that it drastically reduces the magnitude of emission at the edge of the wedge compared to a simple dipole element \citep{nithya15}.
-A second potential drawback is frequency structure introduced by time domain reflections between the suspended feed detailed by Ewall-Wice et al.
+A second potential drawback is frequency structure introduced by time domain reflections between the dish and feed detailed by Ewall-Wice et al.
 (submitted) with simulations and Patra et al.
@@
 \includegraphics[width=7in]{dave197_rich195_airy_beams.pdf}
-\caption{Simulated dish power patterns at 137\,MHz (Sec.
+\caption{Simulated dish power patterns (NS polarization) at 137\,MHz (see Sec.
 \ref{sec:dishmodels}) with $h_\text{feed}=5$\,m using HFSS (left) and CST (middle) are shown beside an ideal Airy pattern for a 14\,m diameter dish for comparison.}
@@
 
-We numerically model the HERA dish in both ANSYS HFSS\footnote{http://www.ansys.com/Products/Electronics/ANSYS-HFSS} and in CST Microwave Studio\footnote{https://www.cst.com/Products/CSTMWS}, making slightly different assumptions, in order to study the dependence of the beam pattern on modeling imperfections.
+We numerically model the HERA dish in both ANSYS HFSS\footnote{http://www.ansys.com/Products/Electronics/ANSYS-HFSS} and in CST Microwave Studio\footnote{https://www.cst.com/Products/CSTMWS}, making slightly different assumptions, in order to study the dependence of the beam pattern on modeling inaccuracies and material uncertainties.
 In particular, the near horizon beam response, which sets the level of horizon brightening in the delay spectrum, is quite sensitive to modeling assumptions.
@@
 
-The HFSS beam model (Fig.
-\ref{fig:modelbeams}, left panel) assumes a solid 14\,m parabolic dish ($f\#=0.32$) with a 1\,m hole at the vertex.
+The HFSS model assumes a solid 14\,m parabolic dish ($f\#=0.32$) with a 1\,m hole at the vertex.
 In reality a 1\,m diameter circle at the vertex is filled with concrete and supports the PVC pipes which suspend the mesh panels, but we effectively assume here it is perfectly absorbant.
@@
 
-The CST beam model (Fig.
-\ref{fig:modelbeams}, middle panel) again assumes a 14\,m parabolic diameter solid aluminum paraboloid with $f\#=0.32$ but neglects the 1\,m hole at the vertex, effectively assuming the concrete and earth ground behind it are perfectly reflective.
+The CST model again assumes a 14\,m parabolic diameter solid aluminum paraboloid with $f\#=0.32$ but neglects the 1\,m hole at the vertex, effectively assuming the concrete and earth ground behind it are perfectly reflective.
 The actual material properties are somewhere between fully reflective and fully absorbant, and thus, between these two models.
@@
 These simulations are done by exciting one of the dipoles with band-limited noise (100--200\,MHz), then measuring the farfield radiation in each direction after the excitation pulse energy within the structure decays to below -80\,dB.
-As expected, both models have slightly stronger sidelobes and wider main lobes than the ideal Airy pattern (Fig.
-\ref{fig:modelbeams}, right panel).
-In both models, the best focus is found to be close to 5.3\,m with this feed geometry, slightly larger than the nominal focus of 4.5\,m, as expected.
+
+The simulated HFSS and CST beams for the NS dipole are plotted in Fig.
+\ref{fig:modelbeams} (left and center panel) along with an Airy pattern for comparison.
+As expected, both model beams have slightly stronger sidelobes and wider main lobes than the ideal Airy pattern.
+The dipole sleeve (circular pieces in Fig.
+\ref{fig:feedphoto}) and skirt result in a feed beam which is slightly elongated in the E plane and slightly compressed in the H plane, opposite to the behavior of a simple dipole.
+This wider dish illumination in the NS direction by the NS feed dipole results in a narrower dish beam in the NS direction.
+Similarly, the EW dish beam is narrower in the EW direction.
+Lastly, we note that in both models, the best focus is found to be close to 5.23\,m with this feed geometry, slightly larger than the nominal focus of 4.5\,m, as expected.
 
@@
 We briefly review the beam mapping system detailed by \citet{neben15}, then discuss the 
-application of system for HERA dish measurements. The system 
+application of the system for HERA dish measurements. The system 
 takes advantage of the 137\,MHz communications satellites operated by ORBCOMM Inc. 
@@
 In this way, beam measurements are built up along satellite tracks over the course of 
-several days of integration, yielding typically 200--300 satellite pass. Each pass is 
+several days of integration, yielding typically 200--300 satellite passes. Each pass is 
 processed separately to identify and exclude times of low signal-to-background when the 
-satellite is low in the sky or in the off state of of a pulsing sequence. At those times, then 
+satellite is low in the sky or in the off state of a pulsing sequence. At those times, then 
 satellite flux no longer dominates over that of the diffuse Galactic background, and a 
@@
 
-As we are not able to replace the HERA dish with a reference antenna, we run two null experiments with both reference dipoles deployed (1) 50\,m apart on a NS line, 50\,m south of the HERA dish; and (2) 100\,m apart on a NS line, 100,m south of the HERA dish.
+As we are not able to replace the HERA dish with a reference antenna, we run two null experiments with both reference dipoles deployed (1) 50\,m apart on a NS line, 50\,m south of the HERA dish; and (2) 100\,m apart on a NS line, 100\,m south of the HERA dish.
 Figure \ref{fig:nullexptplots} shows the results from these experiments in the form of the ratio of the power responses of the two antennas.
@@
 Fig.
-\ref{fig:measuredbeammaps} shows the measured power patterns for these three feed heights for the EW (left panel) and the NS (right panel) feed polarization.
-These maps are plotted in sine-projection with dashed circles marking zenith angles of $20^\circ$, $40^\circ$, $60^\circ$, $80^\circ$.
+\ref{fig:measuredbeammaps} shows the measured power patterns for these three feed heights for the EW (left panel) and the NS (right panel) feed polarizations.
+These maps are plotted in sine-projection with dashed circles marking zenith angles of $20^\circ$, $40^\circ$, $60^\circ$, and $80^\circ$.
 The sky coverage in these dish measurements extends out to typically $\theta\sim60^\circ$, beyond which the ORBCOMM flux is sufficiently attenuated relative to diffuse galactic emission that power measurements are no longer  clean probes of the antenna gains in the direction of the satellite.
@@
 As in the previous plot, the EW and NS beams are shown it the left and right panels, while the different feed heights are shown in the different rows.
-The data agree with both models to within a dB in the main lobe, but begin to diverge in the sidelobes at zenith angles of $20^\circ$ and larger.
+The data agree with both models to within 1\,dB in the main lobe, though often appear slightly shifted so they are not quite centered on zenith.
+The data diverge further in the sidelobes at zenith angles of $20^\circ$ and larger.
 Here the evolution of the sidelobes as the feed is raised is again seen starkly, as is the fact that the main lobes are slightly wider along the H planes than along the E planes.
@@
 \ref{fig:nullexptplots}).
-Those experiments bound the impact of environmental reflections and reference dipole mismodeling to the 10\% level or smaller across the whole sky.
-The observed dish beam asymmetries and sidelobe mismodeling are likely due to imperfections in dish construction such as surface imperfections or feed misalignment.
-As the observed sidelobe asymmetries in Fig.
-\ref{fig:measuredbeammaps} change over the three beam measurements, they are more likely to result from feed mis-centering over the dish.
+Those experiments bound the impact of environmental reflections and reference dipole mismodeling to the ma 10\% level or smaller across the whole sky.
+The observed dish beam asymmetries, model deviations in sidelobes, and slight shifts of the main lobes all suggest feed centering errors.
 The feed is suspended by rope from three telephone poles spaced around the dish, and is raised by pulling all three ropes to a new length.
-Each time this is done the feed centering is slightly disturbed.
-Feed mis-leveling and mis-alignment will also disturb the beampattern, but these effects would persist across changes of the feed height.
-In mitigate these errors, the feeds in the full HERA array will be tied down to the dish surface.
+Each time this is done the feed centering is slightly disturbed because all three ropes must be pulled to the exact same length to center the feed.
+If feed tilt/rotation errors or dish surface imperfections were significant, then the beam errors at different feed heights would look similar because these errors persist when the feed is raised or lowered.
+The fact that they change over the three beam measurements suggests that feed centering errors are most significant because they change when the feed height is changed.
+To mitigate these errors, the feeds in the full HERA array will be tied down to the dish surface.
 
@@
 
-The collecting areas range are shown in Table 1 along with the maximal collecting area achieved by the Airy pattern for a 14\,m dish.
-The measured collecting areas are a 30--50\% lower than the geometric area.
+The collecting areas are shown in Table 1 along with the maximal collecting area achieved by the Airy pattern for a 14\,m dish.
+The measured collecting areas are 30--50\% lower than the geometric area.
 This is in line with expectations given that the Airy pattern has the largest possible collecting area, equal to the dish cross section, and the feed's backplane and cylindrical skirt reduce it.
@@
  \begin{table}[h]
- \caption{ \label{table:collectingareatable}Collecting area (m$^2$) of measured 137\,MHz beams and corresponding power spectrum SNR for HERA-331.}
+ \caption{ \label{table:collectingareatable}Collecting area (m$^2$) of measured 137\,MHz beams and corresponding power spectrum SNR for HERA-331 using either foreground avoidance or foreground subtraction.}
 \begin{tabular}{| l | l | l |}
 \hline
-Beam & $A_\text{eff}$ (m$^2$) & SNR (pess, mod, opt)\\
+Beam & $A_\text{eff}$ (m$^2$) & SNR (avoidance, subtraction)\\
 \hline
-  Airy pattern & 155 & 21.4, 25.5, 90.8  \\
-    Measured, feed at 5.3\,m & 93.0 & 18.7, 19.3, 74.3 \\
-    Measured, feed at 5\,m & 77.1 & 15.9, 16.4, 67.9 \\
-    Measured, feed at 4.5\,m & 68.5 & 15.1, 15.4, 63.9 \\ 
+  Airy pattern & 155 & 25.5, 90.8  \\
+    Measured, feed at 5.3\,m & 93.0 & 19.3, 74.3 \\
+    Measured, feed at 5\,m & 77.1 &  16.4, 67.9 \\
+    Measured, feed at 4.5\,m & 68.5 &  15.4, 63.9 \\ 
   \hline
@@
 We run 21cmSense\footnote{https://github.com/jpober/21cmSense} to compute the overall SNR of a power spectrum detection with one season (6 hours per night for 180 nights) of HERA-331 data.
-We predict the SNRs with optimistic, moderate, and pessimistic foreground assumptions assuming a fiducial Epoch of Reionization model generated with 21cmFast \citep{21cmfast}.
+We use a fiducial Epoch of Reionization model generated with 21cmFast \citep{21cmfast}.
 This model assumes $\zeta=31.5$ for the ionizing efficiency, $T_\mathrm{vir}=1.5\times10^4$\,K for the minimum virial temperature of halos producing ionizing photons, and $R_\text{mfp}=30$\,Mpc for the mean free path of ionizing photons, and reaches 50\% ionization at $z \sim 9.5$ and complete ionization at $z \sim 7$, and is consistent with most current observations \citep[e.g.][]{PoberNextGen}.
-In the optimistic case, $k$ modes inside the same $uv$ pixel are added coherently, and all modes whose frequency dependence is larger than that of source at the edge of the main lobe are used.
-In the moderate case, $k$ modes inside the same $uv$ pixel are added coherently and only modes whose frequency dependence falls outside of the horizon plus a buffer of $\Delta k_\parallel=0.1\,\mathrm{h}\,\mathrm{Mpc}^{-1}$ are used.
-In the pessimistic case, all baselines are added incoherently and only modes outside the horizon plus the same buffer are used.
+We predict SNRs first for a foreground \textit{avoidance} approach where only modes outside of the wedge plus a buffer of $\Delta k_\parallel=0.1\,\mathrm{h}\,\mathrm{Mpc}^{-1}$ are used.
+These modes have frequency dependence larger than that of any source on the sky.
+We also predict SNRs for a foreground \textit{subtraction} approach using all modes whose instrumental frequency dependence is larger than that of a source at the edge of the main lobe.
 
-The SNRs computed with the measured collecting areas are 15-20 in the pessimistic and moderate cases compared with 20-25 for the Airy pattern.
-In the optimistic case, the SNR falls from 90 with the Airy pattern to 60-75 with the measured collecting areas.
+The SNRs computed with the measured collecting areas are 15-20 with foreground avoidance compared with 25 for the Airy pattern.
+With foreground subtraction, the SNR falls from 90 with the Airy pattern to 60-75 with the measured collecting areas.
 In all cases this reduction is a loss of sensitivity, but a power spectrum detection is still always very significant at the 15$\sigma$ level or better.
@@
 The horizon is shown in all panels as a vertical line at the baseline's maximum delay seen by radiation from the horizon in line with the baseline.
-In contrast, when the horizon brightening effect is smaller at 60$^\circ$ LST, the foreground delay spectra from all three beams agree much more closely.}
+In contrast, when the horizon brightening effect is smaller at 60$^\circ$ LST, the foreground delay spectra from all three beams agree.}
 \label{fig:delayspec}
@@
 Figure \ref{fig:gsmplots} shows the sine-projected Global Sky Model at 150\,MHz, which dominates the horizon brightening effect, in local Azimuth/Elevation coordinates with units of Kelvin for both LSTs.
-Dashed lines mark zenith angles 20$^\circ$, 40$^\circ$, 60$^\circ$, 80$^\circ$.
+Dashed lines mark zenith angles 20$^\circ$, 40$^\circ$, 60$^\circ$, and 80$^\circ$.
 These plots confirm that the large negative delay peak at the 0$^\circ$ LST is due to the center of the galaxy just above the horizon.
-In contrast several hours later, the galactic center is fully below the western horizon, leaving only a slight brightening near the eastern horizon due to the weaker galactic anticenter.
+In contrast, several hours later, the galactic center is fully below the western horizon, leaving only a slight brightening near the eastern horizon due to the weaker galactic anticenter.
 
-\begin{figure*}[h]
+\begin{figure*}[t]
 \centering
@@
 The measured power patterns probe nearly two thirds of the visible sky, down to -30\,dB relative to the zenith response.
-The measured beams agree well with both models in the main lobe out to 10--20$^\circ$ from zenith, then roughly track the typical sidelobe levels at 20--30\,dB below zenith though fail to reproduce the exact sidelobe amplitudes and locations.
+The measured beams agree well with both models in the main lobe out to 10--20$^\circ$ from zenith, then roughly track the typical sidelobe levels at 20--30\,dB below zenith, deviating at the 1--5\,dB level.
 
@@
 
-As discussed by the other papers in this series, the frequency dependence of both the beam's angular response and its overall gain widen the delay kernel of a source, leaking power into the EOR window out to $k_\parallel=$0.15-0.23h\,Mpc$^{-1}$.
+As discussed by the other papers in this series (Ewall-Wice et al., in prep, Patra et al., in prep, Thyagarajan et al., in prep), the frequency dependence of both the beam's angular response and its overall gain widen the delay kernel of a source, leaking power into the EOR window out to $k_\parallel=$0.15-0.23h\,Mpc$^{-1}$.
 This is well inside the wedge plus buffer assumed in the moderate and pessimistic cases considered above.

### 2016-02-04 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev3b.tex
rev3b

--- 2016-02-04 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev3.tex
@@
 array permitting redundant baseline calibration and coherent integration in $
-\vec{k}$ space \citep{omniscope,parsons12a}. 
+\vec{k}$ space \citep{zheng14,parsons12a}. 
 %The smaller field of view of the HERA dish relative to that of the PAPER dipole or the MWA tile does not limit sensitivity in Fourier space as most leverage on high $k$ modes is from line of sight modes anyway \citep{PoberNextGen}.
@@
 \includegraphics[width=3.4in]{dish_and_feed_diagram.pdf}
-\caption{some stuff here}
+\caption{Diagram showing the dimensions and layout of the HERA dish and suspended feed.}
 \label{fig:feeddiagram}
@@
 
-feed misalignment vs surface imperfections (different across different feed heights)
-risk of cross-coupling
-tie-downs
-
 We make dish power pattern measurements at 137\,MHz as described in Sec.
@@
 We use a total bandwidth of 100\,MHz (50\,MHz after applying the Blackman-Harris window) centered on 150\,MHz.
-This bandwidth is larger than the 10\,MHz thought to be safe from signal evolution over redshift, but is the bandwidth used in the wide band delay space foreground filter of \citet{paper32,paper64}.
+This bandwidth is larger than the 10\,MHz thought to be safe from signal evolution over redshift, but is the bandwidth used in the wide band delay space foreground filter of \citet{paper32,ali2015}.
 
@@
 We convert these collecting areas into effective dish sizes, then use 21cmSense to predict the overall power spectrum SNR with one season of HERA-331 data.
-We find SNRs of 18.7, 19.3, and 74.3 in the pessimistic, and moderate, and optimistic foreground scenarios with the feed at optimal focus.
+We find SNRs of 19.3 and 74.3 using foreground avoidance and subtraction respectively, with the feed at optimal focus.
 While a reduction from the theoretical limit of an unobstructed 14\,m aperture, these sensitivities still permit a very significant detection of the 21\,cm signal after a single observing season.
@@
 As discussed by the other papers in this series (Ewall-Wice et al., in prep, Patra et al., in prep, Thyagarajan et al., in prep), the frequency dependence of both the beam's angular response and its overall gain widen the delay kernel of a source, leaking power into the EOR window out to $k_\parallel=$0.15-0.23h\,Mpc$^{-1}$.
-This is well inside the wedge plus buffer assumed in the moderate and pessimistic cases considered above.
-The optimistic case requires calibrating out the instrument frequency response enough to begin to access cosmological modes within the wedge.
+This is well inside the wedge plus buffer used in a foreground avoidance analysis.
+Foreground subtraction requires calibrating out the instrument frequency response enough to begin to access cosmological modes within the wedge.
 This is much more challenging, but the sensitivity gains are enormous as those signal modes are thought to be the strongest.
-Even in the pessimistic case, though, assuming only previously demonstrated analysis techniques, we project a $18\sigma$ detection of the EOR power spectrum which would provide begin to probe reionization models in detail and shed light on our cosmic dawn.
+Even with only foreground avoidance, though, assuming only previously demonstrated analysis techniques, we project a $18\sigma$ detection of the EOR power spectrum which would provide begin to probe reionization models in detail and shed light on our cosmic dawn.
 

### 2016-02-06 ForegroundSimulations/ms.tex
Update Introduction section
From c14f775 (master):
=====================

In ms.tex,

(*) Update Introduction section

--- 2016-01-21 ForegroundSimulations/ms.tex
@@
 
-\shorttitle{Characterization of Beam Chromaticity in EoR Power Spectra Measurements}
+\shorttitle{Effects of Beam Chromaticity in EoR Power Spectra Measurements}
 \shortauthors{Thyagarajan et~al.}
@@
 When expressed in the coordinate system of power spectrum measurements described by the three-dimensional wavenumber ($k$), the foreground emission is restricted to a wedge-shaped region commonly referred to as the {\it foreground wedge} \citep{bow09,liu09,liu14a,liu14b,dat10,liu11,gho12,mor12,par12b,tro12,ved12,dil13,pob13,thy13,dil14} whereas the EoR signal has spherical symmetry due to its isotropy which appears elongated along line of sight $k$ modes due to peculiar velocity effects when dominated by matter density perturbations during early stages of reionization.
-The extreme dynamic range required to subtract foregrounds precisely demands high precision modeling of foregrounds as observed by modern wide-field instruments \citep{,thy15a,thy15b}.
+
+The extreme dynamic range required to subtract foregrounds precisely demands high precision modeling of foregrounds as observed by modern wide-field instruments \citep{thy15a,thy15b}.
+Their studies of effects of wide-field measurements of EoR power spectra have demonstrated the {\it pitchfork} effect wherein foreshortening of baselines causes a prominent enhancement of foreground power near the horizon limits of the {\it foreground wedge} as well in the contamination beyond.
+In this paper, we explore yet another phenomenon that inherently extends foreground power beyond the {\it wedge}, namely, that arising from the chromaticity of the antenna power pattern.
+% We specifically use the current design of 14~m dish of HERA as an example in our study.
+
+This paper is organized as follows.
+\S\ref{sec:HERA} introduces the HERA instrument.
+A brief summary of the delay spectrum technique used extensively in this analysis and the recently confirmed {\it pitchfork} effect are presented in \S\ref{sec:delay-spectrum}.
+\S\ref{sec:sim} describes foreground simulations including antenna beam pattern and all-sky foreground models.
+\S\ref{sec:beam-chromaticity} investigates the effects of chromaticity of antenna beam on the resulting delay power spectrum and the cosmologically motivated constraints it places on dish reflectometry.
+Our findings are summarized in \S\ref{sec:summary}.
 
@@
 
-\section{Chromaticity of Power Pattern}
+\section{Chromaticity of Power Pattern}\label{sec:beam-chromaticity}
 
@@
 
-\subsection{Directional Chromaticity of Power Pattern}
+\subsection{Directional Chromaticity of Power Pattern}\label{sec:directional-chromaticity}
 
@@
 
-\subsection{Effect on Delay Power Spectrum}
+\subsection{Effect on Delay Power Spectrum}\label{sec:chromaticity-delay-spectrum}
 
@@
 
-Fig.~\ref{fig:asm-dps-beam-chromaticity} shows the delay power spectra of foregrounds obtained with the aforementioned models for power pattern.
+Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines} shows the delay power spectra of foregrounds obtained with the aforementioned models for power pattern.
 In all these panels, power spectra obtained with achromatic, {\it Airy} disk and simulated disk are shown in black, red, and blue respectively.
@@
 
+% \begin{figure*}[htb]
+% \centering
+% \includegraphics[width=\linewidth]{asm_beam_chromaticity_bl2_LST_3.96_hrs_subband_150.0_MHz.eps}
+% \caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra for a 14.6~m baseline.}
+% \label{fig:asm-dps-beam-chromaticity-14.6m-baseline}
+% \end{figure*}
+
+% \begin{figure*}[htb]
+% \centering
+% \includegraphics[width=\linewidth]{asm_beam_chromaticity_bl8_LST_3.96_hrs_subband_150.0_MHz.eps}
+% \caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra for a 29.2~m baseline.}
+% \label{fig:asm-dps-beam-chromaticity-29.2m-baseline}
+% \end{figure*}
+
 \begin{figure*}[htb]
 \centering
-\includegraphics[width=\linewidth]{asm_beam_chromaticity_subband_150_MHz.eps}
-\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra. }
-\label{fig:asm-dps-beam-chromaticity}
+\includegraphics[width=\linewidth]{asm_foreground_eor_beam_chromaticity_fullband.eps}
+\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra for different baselines.}
+\label{fig:asm-dps-beam-chromaticity-baselines}
+\end{figure*}
+
+\begin{figure*}[htb]
+\centering
+\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_150.0_MHz_subband.eps}
+\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra obtained from the 150~MHz subband for different baseline lengths.}
+\label{fig:asm-dps-beam-chromaticity-baselines-150-subband}
+\end{figure*}
+
+\begin{figure*}[htb]
+\centering
+\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_170.0_MHz_subband.eps}
+\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra obtained from the 170~MHz subband for different baseline lengths.}
+\label{fig:asm-dps-beam-chromaticity-baselines-170-subband}
 \end{figure*}
@@
 
-\subsection{Constraints on Reflections between Antennas}
+\subsection{Constraints on Reflections between Antennas}\label{sec:reflectometry}
 
@@
 \centering
-\includegraphics[width=\linewidth]{spec_on_foreground_reflected_power_21cmfast.eps}
+\includegraphics[width=\linewidth]{spec_on_foreground_reflected_power_21cmfast_14.6m_150.0_MHz_subband_v2.eps}
 \caption{Attenuation of foreground power (in dB) from antenna-to-antenna reflections required to keep the reflected foreground power below EoR H{\sc i} signal power.}

### 2016-02-06 ForegroundSimulations/ms.tex
Update section 2
From 5193a76 (master):
=====================

In ms.tex,

(*) Update section 2

@@
 
-\citep{par12b}
+A brief description of the delay spectrum technique \citep{par12a,par12b} is provided here. We borrow the notation used in \citet{thy15a}.
+
+{\it Visibilities} measured by an interferometer are given by \citep{van34,zer38,tho01}:
+\begin{align}\label{eqn:obsvis}
+  V_b(f) &= \iint\limits_\textrm{sky} A(\hat{\boldsymbol{s}},f)\,I(\hat{\boldsymbol{s}},f)\,e^{-i2\pi f\frac{\boldsymbol{b}\cdot\hat{\boldsymbol{s}}}{c}}\,\dif\Omega,
+\end{align}
+where, $\boldsymbol{b}$ is the vector joining antenna pairs (commonly referred to as the baseline vector), $\hat{\boldsymbol{s}}$ is the unit vector denoting direction on the sky, $f$ denotes frequency, $c$ is the speed of light, $\dif\Omega$ is the solid angle element to which $\hat{\boldsymbol{s}}$ is the unit normal vector, $I(\hat{\boldsymbol{s}},f)$ and $A(\hat{\boldsymbol{s}},f)$ are the sky brightness and antenna's directional power pattern, respectively, as a function of $\hat{\boldsymbol{s}}$ and $f$.
+The {\it delay spectrum}, $\tilde{V}_b(\tau)$, is defined as the inverse Fourier transform of $V_b(f)$ along the frequency coordinate:
+\begin{align}\label{eqn:delay-transform}
+  \tilde{V}_b(\tau) &\equiv \int V_b(f)\,W(f)\,e^{i2\pi f\tau}\,\dif f,
+\end{align}
+where, $W(f)$ is a spectral weighting function which can be chosen to control the quality of the delay spectrum \citep{ved12,thy13}, and $\tau$ represents the signal delay between antenna pairs:
+\begin{equation}\label{eqn:delay}
+  \tau = \frac{\boldsymbol{b}\cdot\hat{\boldsymbol{s}}}{c}.
+\end{equation}
+
+The delay spectrum has a close resemblance to cosmological H~{\sc i} spatial power spectrum. Thus, the delay power spectrum is defined as:
+\begin{align}\label{eqn:delay-power-spectrum}
+  P_\textrm{d}(\boldsymbol{k}_\perp,k_\parallel) &\equiv |\tilde{V}_b(\tau)|^2\left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2,
+\end{align}
+with
+\begin{align}
+  \boldsymbol{k}_\perp &\equiv \frac{2\pi(\frac{\boldsymbol{b}}{\lambda})}{D}, \\
+  k_\parallel &\equiv \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, 
+\end{align}
+where, $\Delta B$ is the bandwidth, $\lambda$ is the wavelength of the band center, $k_\textrm{B}$ is the Boltzmann constant, $f_{21}$ is the rest frame frequency of the 21~cm spin flip transition of H~{\sc i}, $z$ is the redshift, $D\equiv D(z)$ is the transverse comoving distance, $\Delta D$ is the comoving depth along the line of sight corresponding to $\Delta B$, and $h$, $H_0$ and $E(z)\equiv [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ are standard terms in cosmology, and following \citet{par14},
+\begin{align}
+  \Omega\Delta B &= \iint \left|A(\hat{\boldsymbol{s}},f)\,W(f)\right|^2\,\dif\Omega\,\dif f.
+\end{align}
+
+In this paper, we use $\Omega_\textrm{M}=0.27$, $\Omega_\Lambda=0.73$, $\Omega_\textrm{K}=1-\Omega_\textrm{M}-\Omega_\Lambda$, $H_0=100\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P_\textrm{d}(\boldsymbol{k}_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.
 

### 2016-02-07 ForegroundSimulations/ms.tex
Add discussion about pitchfork effect in section 3
From ace91c7 (master):
=====================

In ms.tex,

(*) Add discussion about pitchfork effect in section 3

@@
 
-\subsection{The Wide-Field ``Pitchfork'' Effect}\label{sec:wide-field}
+It was recently discovered that in wide-field measurements diffuse foreground emission from wide off-axis angles appear enhanced in the delay spectrum near the edges of the {\it foreground wedge} even on wide antenna spacings \citep{thy15a}.
+Called the {\it pitchfork} effect, this arises due to severe foreshortening of baseline vectors towards the horizon along joining the antenna pairs thereby enhancing their sensitivity to large scale structures in these directions.
+Since delay spectrum maps directions on the sky to delay bins, the emission from large scales near the horizon appears enhanced in delay bins near the horizon limits of the {\it foreground wedge}.
+Since these delay modes lie adjacent to those considered sensitive to the EoR signal, they cause a significant contamination of line-of-sight modes critical for EoR signal detection.
+These findings were confirmed in MWA observations \citep{thy15b}.
 
-\citep{thy15a,thy15b}
+It was also demonstrated in these studies that design of antenna power pattern, specifically its amplitude near the horizon, is an important tool in mitigating foreground contamination caused by these wide-field effects.
+A dish characterized by a nominal {\it Airy} pattern was found to mitigate this contamination by over four and two orders of magnitude relative to a dipole and a phased array of dipoles respectively.
+HERA has significantly based its antenna design principles on these findings in choosing its antenna geometry while paying close attention to the properties of the resulting antenna power pattern.
+
+In this paper, we investigate the spectral properties of the proposed dish design through their effects on the resultant foreground delay power spectrum and the constraints they place on attenuation required to suppress reflections between the dish-receiver assembly to within tolerable limits.
 
@@
 The simulations cover 24~hr of observation in {\it drift} mode consisting of 80 accumulations spanning 1080~s each.
-The total bandwidth is 100~MHz centered on 150~MHz consisting of 128 channels with 781.125~kHz frequency resolution each.
+The total bandwidth is 100~MHz centered on 150~MHz consisting of 256 channels with 390.625~kHz frequency resolution.
 Models of the antenna power pattern and foregrounds are described below.

### 2016-02-07 ForegroundSimulations/ms.tex
Add description of antenna models in section 4.1
From b2391d0 (master):
=====================

In ms.tex,

(*) Add description of antenna models in section 4.1

@@
 
-\subsection{Antenna Power Pattern}
+\subsection{Antenna Power Pattern}\label{sec:beam-model}
 
-\citep{neb15}
+The High Frequency Structural Simulator (HFSS) was used to model the dish and its angular response used in this study.
+The HFSS model used prime focus optics with a 14~m faceted parabola with a spar f/D ratio of 0.32.
+The model has a 1~m central hole in the aluminum surface which is filled with a dielectric material similar to dry soil.
+The feed used a full PAPER dipole inside of a cylindrical backplane, the backplane is modeled as an aluminum surface.
+For the metal parts of the dipole, the discs were modeled as aluminum at the actual size, and the arms and terminals were modeled as copper.
+Dielectric stand-offs and supporting members were included.
+For the calculations, one pair of arms was excited using a modal port.
+These models cover a frequency range of 100--200~MHz in intervals of 1~MHz.
+Please refer to DeBoer~et~al.~(2016) for a complete description of the dish model.
+
+For reference, we use two other models for the antenna power pattern.
+The first is a nominal {\it Airy} pattern corresponding to a uniformly illuminated circular aperture of 14~m diameter and the second is an achromatic model where the response of the design at 150~MHz of the HFSS model described above was fixed as the hypothetical response at all frequencies covering the entire band.
+This frequency independent model will be used to isolate the effects of spectral structures in the antenna power pattern (or beam chromaticity) on foreground delay power spectra.
+
+In a related series of papers, Neben et~al.
+(2016; submitted) discuss the agreement of these model antenna beam patterns with actual measurements and Ewall-Wice et~al.
+(2016; submitted) model the reflections and return loss expected in the proposed antenna-receiver assembly.
+Our focus in this paper is to investigate chromaticity of antenna power patterns from the point of view of their impact on foreground contamination in delay power spectra.
 
@@
 The latter is obtained from a combination of the NRAO VLA Sky Survey \citep[NVSS;][]{con98} at 1.4~GHz and the Sydney University Molonglo Sky Survey \citep[SUMSS;][]{boc99,mau03} at 843~MHz with a mean spectral index of -0.83.
-The diffuse sky model has an angular resolution of 13\farcm 74.
+The diffuse sky model has an angular resolution of 13\farcm 74 and a spectral index estimated for every pixel.
 

### 2016-02-08 DishReflectometry/Paper1_v1.tex
Edited section 3.

--- 2015-12-10 DishReflectometry/Paper1_v0.tex
@@
 
-\title{Effect of multiple reflection of the sky signal off the HERA element on the measurements of 21cm power spectrum} 
+\title{THE HYDROGEN EPOCH OF REIONIZATION ARRAY DISH: CHARACTERIZATION OF  THE INSTRUMENTAL RESPONSE WITH REFLECTOMETRY MEASUREMENTS AND ITS IMPLICATIONS ON THE MEASUREMENT OF 21CM POWER SPECTRUM. } 
 %\maketitle
@@
 \email{Contact author email: nipanjana@berkeley.edu}
-
 \author{Zaki Ali\altaffilmark{1}, Carina Cheng\altaffilmark{1}, Dave DeBoer\altaffilmark{1}}
 \author{Gilbert Hsyu\altaffilmark{2}, Tsz Kuk Leung\altaffilmark{2}, Aaron Parsons\altaffilmark{1}}
-% XXX add all members of HERA collaboration
-% XXX suggest Patra, Parsons, Ali, DeBoer, Cheng, Leung, Hsyu, alphabetical
-
 \altaffiltext{1}{University of California, Berkeley, nipanjana@berkeley.edu}
@@
 \citep{furlanetto_et_al2006,morales_wyithe2010,pritchard_loeb2012}),
-the technical path toward measuring this signal has been more problematic.  The
+the technical path toward measuring this signal has been extremely challenging.  The
 weakness of this hyperfine line keeps the 21~cm signal below opacity throughout
 cosmological history, but it also creates sensitivity and calibration
-challenges that have yet to be fully solved.  With noise temperatures dominated
+challenges that are yet to be fully solved.  With noise temperatures dominated
 by sky noise \citep{XXX} and foregrounds four to five orders of magnitude
@@
 
-\section{Visibility measurements by a two element interferometer}
+\section{Visibility measurements by a two element interferometer and the delay spectrum}
 
@@
 
-\section{Effects of additional reflections of the sky signal between the parabolic dish and the feed on the measured visibility}
+\section{Effects of multiple reflections on visibility and delay spectrum}
 Response of any radio telescope is chromatic and modulates the true sky signal in the spectral domain.
@@
 
+The Hydrogen Epoch of Reionization Array consists of parabolic dishes which provide increased collecting area per array element compared to its predecessor experiment PAPER.
 Plane waves incident on a parabolic dish are focussed at the feed which is kept at the focal plane of the dish.
@@
 Such reflections generate multiple copies of the incident sky signal of reduced strength at various delay and phase and thus produces spurious correlations in the visibilities of interferometric data.
+Identical spurious visibilities could be resulted due to reflections internal to the system causing delay space distortion.
+Therefore, it is necessary to measure and understand the instrument delay spectrum in order to qualify the system for the measurement of 21cm power spectrum.
 In this section we compute the visibility of a two element interferometer accounting for the additional reflections of the sky signal in between the feed and the dish vertex and the corresponding effects on the delay spectrum.

### 2016-02-08 ForegroundSimulations/ms.tex

@@
 These models cover a frequency range of 100--200~MHz in intervals of 1~MHz.
-Please refer to DeBoer~et~al.~(2016) for a complete description of the dish model.
+Refer to DeBoer~et~al.~(2016) for a complete description of the dish model.
 
@@
 
+\subsection{Directional Chromaticity of Power Pattern}\label{sec:directional-chromaticity}
+
 Fig.~\ref{fig:off-axis-beam-chromaticity} demonstrates the beyond-the-horizon spillover even from a flat-spectrum point source at different off-axis angles.
@@
 It is important to note that in a generic scenario where visibilities are not phased to a specific foreground location, the chromaticity of the power pattern will imprint itself on location of the foreground objects in delay space and will give rise to significant spillover especially from foregrounds near the horizon.
-
-We investigate the effects of spectral chromaticity of the power pattern in more detail below.
-
-\subsection{Directional Chromaticity of Power Pattern}\label{sec:directional-chromaticity}
 
@@
 It is noted that there are a few bright point sources that spend a majority of time in this LST range near the northern and southern horizons which will contaminate the measured visibilities on north-south antenna spacings.
-Future simulations of the dish power pattern must take the bright foreground locations, especially near the horizon, into account.
+Simulations of the antenna power pattern must take the bright foreground locations, especially near the horizon, into account.
 
@@
 
-We simulate visibilities from our foreground model using three different models for the antenna power pattern -- {\it Airy} pattern, simulated dish, and a pattern at 150~MHz of the simulated dish assumed to be achromatic over the entire band.
-
-Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines} shows the delay power spectra of foregrounds obtained with the aforementioned models for power pattern.
-In all these panels, power spectra obtained with achromatic, {\it Airy} disk and simulated disk are shown in black, red, and blue respectively.
-The vertical gray lines denote the horizon limits for a 14.6~m antenna spacing.
-The full band delay power spectra of the foregrounds measured on a 14.6~m antenna spacing oriented eastward is shown in the top left panel.
+In HERA-19 array layout configuration, there are 30 unique baseline vectors and 8 unique baseline lengths.
+Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines} shows the delay power spectra of foregrounds on the 8 unique baseline lengths obtained with the aforementioned models for power pattern.
+In all these panels, the full-band foreground delay power spectra obtained with achromatic, {\it Airy} and chromatic beam patterns are shown in black, red, and blue respectively.
+The vertical dotted lines denote the horizon limits for baseline lengths indicated in each panel.
 A clear trend of broadening of spillover-wings outside the horizon limits is seen with increasing chromaticity.
-For instance, the spillover from foreground delay power spectrum obtained with simulated dish pattern extends out to $k_\parallel \approx \pm 0.14\,h$~Mpc$^{-1}$, with the {\it Airy} pattern it extends out to $k_\parallel \approx \pm 0.08\,h$~Mpc$^{-1}$, while the achromatic beam extends it only out to $k_\parallel \approx \pm 0.05\,h$~Mpc$^{-1}$.
+For instance, the spillover from foreground delay power spectrum obtained with chromatic beam pattern is restricted to $|k_\parallel| \lesssim 0.2\,h$~Mpc$^{-1}$, with the {\it Airy} pattern it is restricted to $|k_\parallel| \lesssim 0.15\,h$~Mpc$^{-1}$, while with the achromatic beam it is restricted to $|k_\parallel| \lesssim 0.12\,h$~Mpc$^{-1}$ even on longest baseline lengths.
 Thus an increase in chromaticity extends the foreground spillover into higher $k_\parallel$-modes making them inaccessible for EoR H{\sc i} signal detection.
 
-Following the foreground removal strategy, the top middle panel shows these foreground delay spectra deconvolved using the complex delay CLEAN algorithm \citep{tay99,par09,par12b}.
-The CLEAN window covers delay bins between the horizon delay limits and extends further by three delays bins on each side of the horizon limit where a delay bin is of size inverse of the bandwidth.
-The panel at the top right shows the residuals left behind after deconvolution.
-
-% \begin{figure*}[htb]
-% \centering
-% \includegraphics[width=\linewidth]{asm_beam_chromaticity_bl2_LST_3.96_hrs_subband_150.0_MHz.eps}
-% \caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra for a 14.6~m baseline.}
-% \label{fig:asm-dps-beam-chromaticity-14.6m-baseline}
-% \end{figure*}
-
-% \begin{figure*}[htb]
-% \centering
-% \includegraphics[width=\linewidth]{asm_beam_chromaticity_bl8_LST_3.96_hrs_subband_150.0_MHz.eps}
-% \caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra for a 29.2~m baseline.}
-% \label{fig:asm-dps-beam-chromaticity-29.2m-baseline}
-% \end{figure*}
+Hence it is clearly demonstrated that higher the beam chromaticity, the farther the foreground contamination inherently extends beyond the horizon limits of the {\it foreground wedge}.
+The {\it Airy} pattern typically creates one secondary peak whereas the chromatic beam is found to produce multiple secondary peaks outside the {\it foreground wedge} on each side.
 
@@
 
+It must be emphasized that such a significant spillover is not limited by the horizon limits of the {\it foreground wedge} because this is caused by spectral structure in the antenna beam pattern in addition to that caused by position-dependent geometric phase in the visibility spectra.
+As a result delay-based complex deconvolution techniques such as CLEAN \citep{tay99,par09,par12b} that rely on smoothness of foreground spectra and only spectral window shape will not have adequate information to accurately deconvolve intrinsic supra-horizon spillover arising from the chromaticity of the antenna beam.
+Thus, we leave delay power spectrum estimation using {\it foreground removal} strategy to future work and use {\it foreground avoidance} approach in this study.
+
+We investigate the effect of chromaticity of power pattern in a {\it foreground avoidance} strategy that avoids the aforementioned deconvolution of delay spectrum.
+Application of window functions with high sidelobe suppression have been discussed for mitigating foreground contamination \citep{thy13}.
+In line with the {\it foreground avoidance} strategy, Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-150-subband} shows delay spectra after applying a {\it Blackman-Harris} window function extending 10~MHz on each side centered on 150~MHz with effective bandwidth of 10~MHz.
+The 8 panels correspond to those shown in Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines}.
+As a result of narrowed subband, the resolution in delay space (and $k_\parallel$) has coarsened.
+The cyan and gray lines denote power spectra of two EoR models, namely, those obtained from 21cmFAST \citep{mes11} and \citet{lid08} respectively.
+These models will be denoted hereafter as AM and AL respectively.
+
 \begin{figure*}[htb]
@@
 \end{figure*}
+
+Firstly, it is noted that the coarsening of delay resolution significantly absorbs the distinct differences caused by beams of different chromaticities as seen in the full band foreground delay spectra outside the {\it foreground wedge} in Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines}.
+Secondly, it is also found that barring the shortest baselines ($|\boldsymbol{b}| \leq $~29.2~m), which have the most severe foreground contamination especially from diffuse emission, foreground contamination on baselines longer than $\gtrsim 29.2$~m is lesser than EoR signal power for $|k_\parallel| \gtrsim 0.22\,h$~Mpc$^{-1}$ in either of the models.
+
+Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-170-subband} is similar to Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-150-subband} except it is obtained with a subband {\it Blackman-Harris} window function centered on 170~MHz.
+In this subband relative to that centered on 150~MHz, the ratio of powers of the EoR signal and foregrounds is even higher outside the wedge thus indicating a stronger potential for direct detectability without the use of sophisticated power spectrum estimation techniques on almost all baseline lengths.
 
@@
 
-Owing to the chromaticity of power patterns, the spillover from foregrounds extends beyond the horizon limits, most severely in the simulated disk pattern.
+It must be emphasized that these are obtained only with windowing techniques and do not represent the best sensitivity achievable with sophisticated tools such as optimal covariance-based weighting schemes \citep{liu14a,liu14b,ali15,dil15}.
+Thus assuming the data is limited by foregrounds and not by thermal noise, this demonstrates that even with no sophistication in power spectrum estimation, a direct detection based on simple windowing and delay spectrum technique is possible on a majority of HERA baselines and will further allow distinguishing between different EoR models.
+This finding holds even in the most conservative scenario where the modeled beam pattern with most severe chromaticity inherently results in significant and inherent foreground contamination outside the {\it foreground wedge}.
+
+% Owing to the chromaticity of power patterns, the spillover from foregrounds extends beyond the horizon limits, most severely in the simulated disk pattern.
 As a result the residuals have significant power remaining on either side of the horizon limits since the window for deconvolution is narrower than the extent of spillover along $k_\parallel$.
@@
 
-We investigate the effect of chromaticity of power pattern in a foreground avoidance strategy that avoids the aforementioned deconvolution of delay spectrum.
+% We investigate the effect of chromaticity of power pattern in a foreground avoidance strategy that avoids the aforementioned deconvolution of delay spectrum.
 Application of window functions with high sidelobe suppression have been discussed for mitigating foreground contamination \citep{thy13}.
@@
 
-Following a delay-deconvolution based foreground removal strategy, we apply the Blackman-Harris window of effective bandwidth 10~MHz on the unsubtracted foreground residuals (top right panel) in frequency domain and obtain the delay power spectrum shown in the bottom right panel.
+% Following a delay-deconvolution based foreground removal strategy, we apply the Blackman-Harris window of effective bandwidth 10~MHz on the unsubtracted foreground residuals (top right panel) in frequency domain and obtain the delay power spectrum shown in the bottom right panel.
 It is noted that lesser the chromaticity the more effective the deconvolution process is in lowering the residuals in and around the horizon limits.
@@
 
-In both strategies, the EoR H{\sc i} signal power spectrum obtained by simulations with 21cmFAST (Mesinger et al. 2008) is shown for reference (dashed black lines) in the bottom panels.
+% In both strategies, the EoR H{\sc i} signal power spectrum obtained by simulations with 21cmFAST (Mesinger et al. 2008) is shown for reference (dashed black lines) in the bottom panels.
 

### 2016-02-08 ForegroundSimulations/ms.tex

@@
 \usepackage{footnote}
+\usepackage{url}
 \bibpunct{(}{)}{;}{a}{}{,} 
@@
 The most significant challenge to low frequency EoR observations arises from the extremely bright Galactic and extragalactic foreground synchrotron emission which are $\sim 10^4$ times stronger than the desired EoR signal \citep{dim02,ali08,ber09,ber10,gho12}.
-All the current and future instruments rely on the inherent differences in spatial isotropy and spectral smoothness between the EoR signal and the foregrounds to extract the EoR power spectrum \citep[see, e.g.,][]{fur04,mor04,zal04,san05,fur06,mcq06,mor06,wan06,gle08}.
+All the current and future instruments rely on the inherent differences in spatial isotropy and spectral smoothness between the EoR signal and the foregrounds to extract the EoR power spectrum \citep[see, e.g.,][]{fur04b,mor04,zal04,san05,fur06,mcq06,mor06,wan06,gle08}.
 
@@
 
-We simulate wide-field visibilities for 19-element HERA from all-sky antenna power pattern and foreground models using the PRISim\footnote{The Precision Radio Interferometry Simulator (PRISim) is publicly available at \href{https://github.com/nithyanandan/PRISim}{https://github.com/nithyanandan/PRISim}} software package.
+We simulate wide-field visibilities for 19-element HERA from all-sky antenna power pattern and foreground models using the PRISim\footnote{The Precision Radio Interferometry Simulator (PRISim) is publicly available at \url{https://github.com/nithyanandan/PRISim}} software package.
 The simulations cover 24~hr of observation in {\it drift} mode consisting of 80 accumulations spanning 1080~s each.
@@
 The diffuse sky model has an angular resolution of 13\farcm 74 and a spectral index estimated for every pixel.
+
+\subsection{EoR Model}\label{sec:EoR-model}
+
+For reference, we use two models of EoR.
+In the first, simulations of the H{\sc i} signal were created using the publically available 21cmFAST\footnote{\url{http://homepage.sns.it/mesinger/DexM\_\_\_21cmFAST.html}} code described in \citet{mes11}.
+The code uses the excursion set formalism of \citet{fur04a} to generate ionization and 21cm brightness fields for numerous redshifts.
+The model shown in this paper assumes the same fiducial values of $T_\text{vir}^\text{min} = 2 \times 10^4$~K (virial temperature of minimum mass of dark matter halos that host ionizing sources), $\zeta = 20$ (ionization efficiency), and $R_\text{mfp}=15$~Mpc (mean free path of UV photons) which predicts the redshift of 50\% ionization (and hence a peak in the power spectrum signal) to be at $z=8.5$ as in Ewall-Wice~et~al.(2016; submitted).
+The second model is borrowed from the simulations described in detail in \citet{lid08}.
+Hereafter, we refer to these two as EoR models 1 and 2 respectively.
 
@@
 As a result of narrowed subband, the resolution in delay space (and $k_\parallel$) has coarsened.
-The cyan and gray lines denote power spectra of two EoR models, namely, those obtained from 21cmFAST \citep{mes11} and \citet{lid08} respectively.
-These models will be denoted hereafter as AM and AL respectively.
+The cyan and gray lines denote power spectra of EoR models 1 and 2 respectively.
 
@@
 Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-170-subband} is similar to Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-150-subband} except it is obtained with a subband {\it Blackman-Harris} window function centered on 170~MHz.
-In this subband relative to that centered on 150~MHz, the ratio of powers of the EoR signal and foregrounds is even higher outside the wedge thus indicating a stronger potential for direct detectability without the use of sophisticated power spectrum estimation techniques on almost all baseline lengths.
+In this subband relative to that centered on 150~MHz, the ratio of powers of the EoR signal and foregrounds is even higher outside the wedge thus indicating a stronger potential for direct detectability without the use of optimal power spectrum estimation techniques on almost all baseline lengths.
 

### 2016-02-08 DishReflectometry/Paper1_v1.tex
Edited section 3. Third attempt to push.

@@
 \newcommand{\bmvolt}{{a}}
-%\newcommand{\bm}{{A}}
+\newcommand{\beam}{{A}}
 \newcommand{\thhat}{{\hat\theta}}
@@
 
-\subsection{Effect of first order reflections on visibility and delay spectrum}
+\subsection{Visibility and delay spectrum computation considering multiple reflections}
 Upon first incidence of the sky signal $\volt_{sky}$, $\Gamma_{f}$ fraction of the voltage is reflected off the feed while $(1-\Gamma_{f})$ fraction is coupled to the feed.
 The reflected voltage then further reflected off the dish and $(1-\Gamma_{f}) $ fraction of it reenters the feed with a roundtrip time delay $\Delta \tau$.
-Hence, the net voltage at the output of the two antennas could be written as,
+Hence, if $I_{sky}$ is reflected n times in between the feed and the dish, the net voltage entering the feed after an
+$n^{th}$ reflection off the feed and the dish is written as:
 \begin{eqnarray}
-\volt_{1} & = & a \volt_{sky}(1-\Gamma_{f}) + a \volt_{sky} \Gamma_{f} \Gamma_{d} \dfngexp  (1-\Gamma_{f})^{2}\nonumber\\
-         & = & a \volt_{sky} (1-\Gamma_{f}) \left [ 1+ (1-\Gamma_{a})\Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau} \right]\nonumber
+\volt_{1} & = &  a_{f} \volt_{sky}[1+ (1-\Gamma_{f})\Gamma_{f}\Gamma_{d} \dfngexp \nonumber \\
+	&& + (1-\Gamma_{f})^{2} (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
+&&  ....+ (1-\Gamma_{f})^{n}(\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}] \nonumber
 \end{eqnarray}
+and,
+
 \begin{eqnarray}
-\volt_{2} & = & \left [ a \volt_{sky}(1-\Gamma_{f}) + a \volt_{sky} \Gamma_{f} \Gamma_{d} \dfngexp (1-\Gamma_{f})^{2}\right ] \fngexp \nonumber\\
-         & = & a \volt_{sky} (1-\Gamma_{f}) \left [ 1+(1-\Gamma_{a}) \Gamma_{f} \Gamma_{d} \dfngexp  \right] \fngexp \nonumber
+\volt_{2} & = &  a_{f} \volt_{sky}[1+ (1-\Gamma_{f})\Gamma_{f}\Gamma_{d} \dfngexp \nonumber\\
+&&+ (1-\Gamma_{f})^{2} (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
+&& ....+ (1-\Gamma_{f})^{n}(\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}] \ast \fngexp \nonumber
 \end{eqnarray}
+
+%\begin{eqnarray}
+%\volt_{1} & = & a \volt_{sky}(1-\Gamma_{f}) + a \volt_{sky} \Gamma_{f} \Gamma_{d} \dfngexp  (1-\Gamma_{f})^{2}\nonumber\\
+   %      & = & a \volt_{sky} (1-\Gamma_{f}) \left [ 1+ (1-\Gamma_{a})\Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau} \right]\nonumber
+%\end{eqnarray}
+%\begin{eqnarray}
+%\volt_{2} & = & \left [ a \volt_{sky}(1-\Gamma_{f}) + a \volt_{sky} \Gamma_{f} \Gamma_{d} \dfngexp (1-\Gamma_{f})^{2}\right ] \fngexp \nonumber\\
+   %      & = & a \volt_{sky} (1-\Gamma_{f}) \left [ 1+(1-\Gamma_{a}) \Gamma_{f} \Gamma_{d} \dfngexp  \right] \fngexp \nonumber
+%\end{eqnarray}
 Frequency as well as angular dependence of the quantities are not written explicitly for notational simplicity.
-We also absorb the common gain term $(1-\Gamma_{f})$ with antenna field pattern $a$ and denote them as $a_{f}= a(1-\Gamma_{f})$ here after and define the antenna cross power pattern as $\bm_{f}(\thhat,\nu)=\bmvolt_{f}(\thhat,\nu)\bmvolt_{f}^{*}(\thhat,\nu)$ .
+We also absorb the common gain term $(1-\Gamma_{f})$ with antenna field pattern $a$ and denote them as $a_{f}= a(1-\Gamma_{f})$ here after and define the antenna cross power pattern as $\beam_{f}(\thhat,\nu)=\bmvolt_{f}(\thhat,\nu)\bmvolt_{f}^{*}(\thhat,\nu)$ .
 Hence, the complex visibility could be,
 
-\begin{eqnarray}
-\vis(\vec b, \nu) & = & \int \volt_{1}\volt_{2}^{*} d\Omega \nonumber\\
-		        & = & \int \bm_{f} \volt_{sky}|^{2} |\left [ 1+(1-\Gamma_{f}) \Gamma_{f} \Gamma_{d} \dfngexp  \right]|^{2} \fngexp  d\Omega
-\label{eq4}		        
-\end{eqnarray}
+%\begin{eqnarray}
+%\vis(\vec b, \nu) & = & \int \volt_{1}\volt_{2}^{*} d\Omega \nonumber\\
+%		        & = & \int \beam_{f} \volt_{sky}|^{2} |\left [ 1+(1-\Gamma_{f}) \Gamma_{f} \Gamma_{d} \dfngexp  \right]|^{2} \fngexp  d\Omega
+%\label{eq4}		        
+%\end{eqnarray}
 
@@
 Correlation between the higher order reflections of the signal in any antenna with the direct component of the other would result in a delay response at integral multiple of $\Delta \tau$ and vice versa.
-If $I_{sky}$ is reflected n times in between the feed and the dish, the net voltage entering the feed after an
-$n^{th}$ reflection off the feed and the dish is written as:
-\begin{eqnarray}
-\volt_{1} & = &  a_{f} \volt_{sky}[1+ (1-\Gamma_{f})\Gamma_{f}\Gamma_{d} \dfngexp + (1-\Gamma_{f})^{2} (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
-&&  ....+ (1-\Gamma_{f})^{n}(\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}] \nonumber
-\end{eqnarray}
-and,
-
-\begin{eqnarray}
-\volt_{2} & = &  a_{f} \volt_{sky}[1+ (1-\Gamma_{f})\Gamma_{f}\Gamma_{d} \dfngexp + (1-\Gamma_{f})^{2} (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
-&& ....+ (1-\Gamma_{f})^{n}(\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}] \ast \fngexp \nonumber
-\end{eqnarray}
-
+-----
 The relevant terms in the corresponding visibility and subsequently in the delay spectrum would be the ones which represent the correlation between the direct component of one antenna with the reflected components of the other resulting in higher order terms  in $\Sigma(\vec b, \nu)$.

### 2016-02-10 data/quadratic_estimator.py
Add quadratic estimator script and plotter for foreground pspecs.

@@ -1,0 +1,170 @@
+#! /usr/bin/env python
+import numpy as n, pylab as p, aipy as a
+import sys, optparse, capo
+
+o = optparse.OptionParser()
+opts,args = o.parse_args(sys.argv[1:])
+
+WINDOW='none'
+PLOT=True
+
+
+def cov(m):
+    '''Because numpy.cov is stupid and casts as float.'''
+    #return n.cov(m)
+    X = n.array(m, ndmin=2, dtype=n.complex)
+    X -= X.mean(axis=1)[(slice(None),n.newaxis)]
+    N = X.shape[1]
+    fact = float(N - 1)
+    return (n.dot(X, X.T.conj()) / fact).squeeze()
+
+def get_Q(mode, n_k):
+    _m = n.zeros((n_k,), dtype=n.complex)
+    _m[mode] = 1.
+    m = n.fft.fft(n.fft.ifftshift(_m)) * a.dsp.gen_window(nchan, WINDOW)
+    Q = n.einsum('i,j', m, m.conj())
+    return Q
+
+def read_npz(f):
+    '''Return dictionary with keys [bl][cent] = vis'''
+    data = {}
+    subdata = {}
+    datawind = {}
+    npz = n.load(f)
+    bls = npz['bl'] #30X3, 20 bls by x,y,z
+    freq = npz['freq'] #256, in hz
+    lst = npz['lst']*12/180. #len = 80, in hours
+    subcent = npz['subbands'] #3 centers of the subbands.
+    fwgts = npz['freq_wts'] #3X256 window functions for reach subband.
+    vis = npz['skyvis_freq'] #30bls x 256 chs x 80 times
+    bandvis = npz['subband_skyvis_freq'] #30bls x 3 bands x256 chs x 80 times
+    for i,(x,y,z) in enumerate(bls):
+        data[i] = {}
+        subdata[i] = {}
+        datawind[i] = {}
+        data[i]=  vis[i,:,:]
+        for k,midch in enumerate(subcent):
+            mask = n.where(fwgts[k]>0.0)
+            subdata[i][midch] = bandvis[i,k,mask,:]
+            datawind[i][midch] = vis[i,mask,:]
+    return data, datawind, subdata, lst, freq, bls, fwgts
+
+def delay_filter(data, bl, nchan, sdf):
+    bin_dly = 1./(nchan*sdf)
+#    return bls, freq, lst, subcent, fwgts, vis, bandvis
+
[…]

### 2016-02-10 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev2.tex

@@
 Richard F. Bradley\altaffilmark{2,3},
+Aaron Parsons\altaffilmark{4},
+Jacqueline N. Hewitt\altaffilmark{1},
+David R. DeBoer\altaffilmark{4}
 Aaron Ewall-Wice\altaffilmark{1},
@@
 Zaki S. Ali\altaffilmark{4},
-Judd Bowman\altaffilmark{5}
-Carina Cheng\altaffilmark{4},
-David R. DeBoer\altaffilmark{4}
-Jacqueline N. Hewitt\altaffilmark{1},
-Aaron Parsons\altaffilmark{4}}
+Judd Bowman\altaffilmark{5},
+Carina Cheng\altaffilmark{4}}
 
@@
 With optimistic foreground and analysis assumptions, HERA-127 should detect the EOR with a signal-to-noise of 25--30 with a single season of observations.
-Even pessimistically assuming that only previously demonstrated techniques are used, the significance of an EOR detection remains above $5\sigma$.
+Even with more pessimistic assumptions, using only previously demonstrated techniques, the significance of an EOR detection remains above $5\sigma$.
 Lastly we simulate foreground visibilities using numerical beam models and study the foreground distribution in Fourier space as a function of LST, and the uncertainties in these predictions due to beam modeling uncertainties.

### 2016-02-11 DishReflectometry/Paper1_v1.tex

@@
 We also absorb the common gain term $(1-\Gamma_{f})$ with antenna field pattern $a$ and denote them as $a_{f}= a(1-\Gamma_{f})$ here after and define the antenna cross power pattern as $\beam_{f}(\thhat,\nu)=\bmvolt_{f}(\thhat,\nu)\bmvolt_{f}^{*}(\thhat,\nu)$ .
-Hence, the complex visibility could be,
 
@@
  Furthermore, combining all the terms that contain instrument response we define a common instrument parameter, written as,
+
  \begin{eqnarray}
-\Sigma(\vec b, \nu) & = & \bm_{f} |\left [ 1+ (1-\Gamma_{f}) \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau} \right]|^{2}\nonumber\\
- 	    & = &  \bm_{f}  \left[ 1+ |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} + 2 \Re \left ( (1-\Gamma_{f})\Gamma_{f}\Gamma_{d} \dfngexp \right) \right] 
-\label{eq{5}}	    
+\Sigma(\vec b, \nu) & = & a_{f}  [ 1+ 2 \Re [(1-\Gamma_{f}) \Gamma_{f}\Gamma_{d} \dfngexp \nonumber\\
+&& + (1-\Gamma_{f})^{2}(\Gamma_{f}\Gamma_{d})^2(\dfngexp)^{2}+ \nonumber\\
+&&  ....+(1-\Gamma_{f})^{n} (\Gamma_{f}\Gamma_{d})^{n}(\dfngexp)^{n} ] ]\\
+& = & { a_{f}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
+   \nonumber\\
+   \label{eq6}
 \end{eqnarray}
 
-Instrumental response function acquires additional terms arising due to correlation between the directed and reflected component of the sky signal.
-The total visibility at any frequency would be the sum of the three visibilities contributed by three sources of correlated power.
-First term in the square bracket represents the cross correlation between the two antenna outputs contributed by the sky signal upon first direct incidence.
-The second term results from the cross correlation between two reflected signals in each antenna.The last term represents the cross correlation between the first direct incident signal of one antenna and the first reflected signal from the other antenna and vice versa.
+%\begin{eqnarray}
+%\Sigma(\vec b, \nu) & = & \bm_{f} |\left [ 1+ (1-\Gamma_{f}) \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau} \right]|^{2}\nonumber\\
+ %	    & = &  \bm_{f}  \left[ 1+ |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} + 2 \Re \left ( (1-\Gamma_{f})\Gamma_{f}\Gamma_{d} \dfngexp \right) \right] 
+%\label{eq{5}}	    
+%\end{eqnarray}
 
+Instrumental response function acquires additional terms arising due to correlation between the direct and reflected component of the sky signal.
 Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum.
- Fourier transform of the visibility contributed by any two voltage components from two antennas with no mutual delay will be located at the same delay $\tau$ in the Fourier domain whereas any two voltage components from two antennas components having a mutual delay of $\Delta \tau$ will be centred at $\tau+\Delta \tau$.
+Fourier transform of the visibility contributed by any two voltage components from two antennas with no mutual delay will be located at the same delay $\tau = 0$ in the Fourier domain whereas any two voltage components from two antennas components having a mutual delay of $\Delta \tau$ will be centred at $\tau+\Delta \tau$.
 This additional delay extends the upper limit on the maximum geometric delay $\tau_{g}$ to $(\tau_{g}+\Delta \tau)$.
@@
 \\
+%===================================
 
-\subsection{Effect of multiple reflections on the delay spectrum} 
-Correlation between the higher order reflections of the signal in any antenna with the direct component of the other would result in a delay response at integral multiple of $\Delta \tau$ and vice versa.
------
-The relevant terms in the corresponding visibility and subsequently in the delay spectrum would be the ones which represent the correlation between the direct component of one antenna with the reflected components of the other resulting in higher order terms  in $\Sigma(\vec b, \nu)$.
-The corresponding instrument response may be written as,
-
-\begin{eqnarray}
-\Sigma(\vec b, \nu) & = & a_{f}  [ 1+ 2 \Re [(1-\Gamma_{f}) \Gamma_{f}\Gamma_{d} \dfngexp+ (1-\Gamma_{f})^{2}(\Gamma_{f}\Gamma_{d})^2(\dfngexp)^{2}+ \nonumber\\
-&&  ....+(1-\Gamma_{f})^{n} (\Gamma_{f}\Gamma_{d})^{n}(\dfngexp)^{n} ] ]\\
-& = & { a_{f}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
-   \nonumber\\
-   \label{eq6}
-\end{eqnarray}
-
-and the measured visibility spectrum would be, 
+The respective visibility as well as the dealy spectrum would be, 
 \begin{equation}\label{eqn:series1}
@@
 \end{equation}
-Taking the Fourier transform of the visibility we obtain the delay spectrum
 \begin{eqnarray}
-\tilde V(\vec b, \tau) & = & \int \left [ \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp  d\Omega \right ]  e^{-2\pi i\nu\tau} d\nu \nonumber \\
-  			      & = & \int \left [ I_{sky}(\thhat, \nu) \ast \Sigma(\thhat, \nu) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )  \right] d\Omega
+%\tilde V(\vec b, \tau) & = & \int \left [ \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp  d\Omega \right ]  e^{-2\pi i\nu\tau} d\nu \nonumber \\
+\tilde V(\vec b, \tau) & = & \int \left [ I_{sky}(\thhat, \nu) \ast \Sigma(\thhat, \nu) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )  \right] d\Omega
 \label{eq7}
@@
 \citep{parsons_et_al2012b,vedantham_et_al2012,nithya_et_al2013,liu_et_al2014a,liu_et_al2014b}.
-Our goal is to determine the effect of the instrument response $\Sigma(\nu)$ on the delay spectrum measurement.
+Our goal is to measure the instrument response $\Sigma(\nu)$ and its effect on the power spectrum measurements.
 %%%%%%%%%%%%%%%

### 2016-02-11 DishReflectometry/Paper1_v1.tex
Added feed figure.

@@
 \includegraphics[trim={2cm 20cm 30cm 15cm},clip, totalheight=0.3\textheight]{plots/heradish.jpg}
-\caption{HERA dish and feed at the Green Bank NRAO site.}
+\caption{HERA dish feed at the Green Bank NRAO site.}
 \label{fig:heradish}
@@
 
+ The respective visibility as well as the dealy spectrum would be, 
+\begin{equation}\label{eqn:series1}
+\vis(\vec b, \nu)  = \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp d\Omega
+\end{equation}
+\begin{eqnarray}
+%\tilde V(\vec b, \tau) & = & \int \left [ \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp  d\Omega \right ]  e^{-2\pi i\nu\tau} d\nu \nonumber \\
+\tilde V(\vec b, \tau) & = & \int \left [ I_{sky}(\thhat, \nu) \ast \Sigma(\thhat, \nu) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )  \right] d\Omega
+\label{eq7}
+\end{eqnarray}
+
 %\begin{eqnarray}
@@
 
-The respective visibility as well as the dealy spectrum would be, 
-\begin{equation}\label{eqn:series1}
-\vis(\vec b, \nu)  = \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp d\Omega
-\end{equation}
-\begin{eqnarray}
-%\tilde V(\vec b, \tau) & = & \int \left [ \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp  d\Omega \right ]  e^{-2\pi i\nu\tau} d\nu \nonumber \\
-\tilde V(\vec b, \tau) & = & \int \left [ I_{sky}(\thhat, \nu) \ast \Sigma(\thhat, \nu) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )  \right] d\Omega
-\label{eq7}
-\end{eqnarray}
-
 The design specification of HERA elements requires that any
@@
 \section{Measurements}
+\begin{figure*}
+\centering
+\includegraphics[trim={2cm 10cm 20cm 5cm},clip, totalheight=0.3\textheight]{plots/herafeed.jpg}
+\vspace{1.0 em}
+\caption{HERA feed consists of a pair of crossed dipole ove xxx mt diameter backplane made of wire mesh.
+The backplane is surrounded by xxx m wire mesh around the edge resulting in encasing the cross dipole in a cylindrical cage.}
+\label{fig:herafeed}
+\end{figure*}
+
 We carried out reflectometry measurements at the HERA element prototype in Green
@@
 
-where, $\Delta \tau$ is the roundtrip propagation delay of a frequency $\nu$ due to a reflection over the focal distance $l$.
+%where, $\Delta \tau$ is the roundtrip propagation delay of a frequency $\nu$ due to a reflection over the focal distance $l$.
+
 $I_{meas}$ is the auto correlated power obtained from a single HERA element.
@@
 {I_{meas} \over I_{sky} } & = & \Sigma(\vec b, \nu) \nonumber\\
-  & = & { a_{f}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
+  & = & { a_{f}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}\fngexp]^{n}
    \nonumber\\
@@
 \subsection{Method}
-The instrument response kernel is measured by measuring the return loss of the antenna element at the output port of the feed using a vector network analyser.
-The vector network analyser transmits a broadband noise of known amplitude and phase via a $75ft$ cable up to the feed.
+The instrument response kernel is measured by measuring the return loss of the HERA element at the output port of the feed using a vector network analyser.
+The vector network analyser transmits a broadband noise of known amplitude and phase via a $50ft$ cable up to the feed.
 While a part of this signal  is returns to the VNA post reflection from the feed due to mismatch between the cable and the antenna impedance resulting in the primary return loss, rest of the signal is radiated out by the antenna and illuminates the dish and radiated into the space.
@@
 
-If $I_{tr}$ is the signal transmitted by the VNA , $\Gamma_{f}$ is the feed reflection coefficient, $I_{r}$
-is the power incident back on the feed after reflection from the dish then the reflected power, $I_{refl}$,
+If $I_{tr}$ is the signal transmitted by the VNA and $\Gamma_{f}$ is the feed reflection coefficient, $\Gamma_{f}$ fraction of this transmitted power would be reflected back to the VNA while $\(1-\Gamma_{f})$ fraction would be radiated.
+This radiated power will be reflected back and forth in between the feed and the dish with partial coupling of the signal into the feed at each reflection.
+If  $I_{r}$ is the
+is the total reflected power incident back on the feed after n reflection from the dish then the total reflected power, $I_{refl}$,
 back into the VNA would be:
-\begin{equation}\label{eqn:series2}
-I_{refl} =  I_{r}A_{f}[1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+ (\Gamma_{f}\Gamma_{d})^2e^{i2\phi}+ ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]
-\end{equation}
+\begin{eqnarray}\label{eqn:series2}
+I_{refl} & = &  I_{r}A_{f}[1+ \Gamma_{f}\Gamma_{d} \fngexp + (\Gamma_{f}\Gamma_{d})^2 (\fngexp)^{2}\nonumber\\
+&&+ ....+ (\Gamma_{f}\Gamma_{d})^{n}(\fngexp)^{2}]
+\end{eqnarray}
 
@@
 \begin{equation}
-I_{r}= \Gamma_{d}(1-\Gamma_f)e^{i\phi} I_{tr}
+I_{r}= \Gamma_{d}(1-\Gamma_f)\fngexp I_{tr}
 \end{equation}
@@
 I_{ret} & = & \Gamma_{f}I_{tr} \nonumber\\ 
- & + &   \Gamma_{d}(1-\Gamma_f)e^{i\phi} I_{tr}(1-\Gamma_{f}) [1+ \Gamma_{f}\Gamma_{d} e^{i\phi}+  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{in\phi}]\nonumber\\
+ &&  + \Gamma_{d}(1-\Gamma_f)\fngexp I_{tr}(1-\Gamma_{f}) [1+ \Gamma_{f}\Gamma_{d}\fngexp \nonumber\\
+&& +  ....+ (\Gamma_{f}\Gamma_{d})^{n}(\fngexp)^{n}]\nonumber\\
  \end{eqnarray}

### 2016-02-12 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev4.tex

--- 2016-02-04 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev3b.tex
@@
 
-\author{Abraham R. Neben\altaffilmark{1},
-Richard F. Bradley\altaffilmark{2,3},
-Jacqueline N. Hewitt\altaffilmark{1},
-David R. DeBoer\altaffilmark{4},
-Aaron Parsons\altaffilmark{4},
-James E. Aguirre\altaffilmark{6},
-Aaron Ewall-Wice\altaffilmark{1},
-Nipanjana Patra\altaffilmark{4},
-Nithyanandan Thyagarajan\altaffilmark{5},
-Zaki S. Ali\altaffilmark{4},
-Judd Bowman\altaffilmark{5},
-Carina Cheng\altaffilmark{4},
-Roger Dickenson\altaffilmark{3},
-Phillip Doolittle\altaffilmark{3},
-Dennis Egan\altaffilmark{3},
-Mike Hedrick\altaffilmark{3},
-Saul A. Kohn\altaffilmark{6},
-Benjamin R.B. Saliwanchik\altaffilmark{7},
-Patrick Schaffner\altaffilmark{3},
-John Shelton\altaffilmark{3},
-H.A. Taylor\altaffilmark{3},
-Rusty Taylor\altaffilmark{3},
-Butch Wirt\altaffilmark{3},
-Jeff Zheng\altaffilmark{1}}
+\author{Abraham R. Neben\altaffilmark{1,2},
+Richard F. Bradley\altaffilmark{3,4},
+Jacqueline N. Hewitt\altaffilmark{1,2},
+David R. DeBoer\altaffilmark{5},
+Aaron R. Parsons\altaffilmark{5},
+James E. Aguirre\altaffilmark{7},
+Zaki S. Ali\altaffilmark{5},
+Carina Cheng\altaffilmark{5},
+Aaron Ewall-Wice\altaffilmark{1,2},
+Nipanjana Patra\altaffilmark{5},
+Nithyanandan Thyagarajan\altaffilmark{6},
+Judd Bowman\altaffilmark{6},
+Roger Dickenson\altaffilmark{4},
+Joshua S. Dillon\altaffilmark{5},
+Phillip Doolittle\altaffilmark{4},
+Dennis Egan\altaffilmark{4},
+Mike Hedrick\altaffilmark{4},
+Daniel C. Jacobs\altaffilmark{6},
+Saul A. Kohn\altaffilmark{7},
+Patricia J. Klima\altaffilmark{4},
+Kavilan Moodley\altaffilmark{8},
+Benjamin R.B. Saliwanchik\altaffilmark{8},
+Patrick Schaffner\altaffilmark{4},
+John Shelton\altaffilmark{4},
+H.A. Taylor\altaffilmark{4},
+Rusty Taylor\altaffilmark{4},
+Butch Wirt\altaffilmark{4},
+Haoxuan Zheng\altaffilmark{1,2}}
 
 \affil{\altaffilmark{1}MIT Kavli Institute, Massachusetts Institute of Technology, Cambridge, MA, 02139 USA}
-\affil{\altaffilmark{2}Dept. of Electrical and Computer Engineering, University of Virginia, Charlottesville, VA 22904}
-\affil{\altaffilmark{3}National Radio Astronomy Obs., Charlottesville, VA}
-\affil{\altaffilmark{4}Dept. of Astronomy, University of California, Berkeley, CA, USA}
-\affil{\altaffilmark{5}Arizona State University, School of Earth and Space Exploration, Tempe, AZ 85287, USA}
-\affil{\altaffilmark{6}Dept. of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA}
-\affil{\altaffilmark{7}Astrophysics and Cosmology Research Unit, University of KwaZulu-Natal, Durban, South Africa}
+\affil{\altaffilmark{2}Dept. of Physics, Massachusetts Institute of Technology, Cambridge, MA, 02139 USA}
+\affil{\altaffilmark{3}Dept. of Electrical and Computer Engineering, University of Virginia, Charlottesville, VA 22904}
+\affil{\altaffilmark{4}National Radio Astronomy Obs., Charlottesville, VA}
+\affil{\altaffilmark{5}Dept. of Astronomy, University of California, Berkeley, CA, USA}
+\affil{\altaffilmark{6}Arizona State University, School of Earth and Space Exploration, Tempe, AZ 85287, USA}
+\affil{\altaffilmark{7}Dept. of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA}
+\affil{\altaffilmark{8}Astrophysics and Cosmology Research Unit, University of KwaZulu-Natal, Durban, South Africa}
 
@@
 \begin{abstract}
-The Hydrogen Epoch of Reionization Array (HERA) is a radio interferometer aiming to detect the power spectrum of 21\,cm fluctuations from neutral hydrogen from the Epoch of Reionization.
-Drawing on lessons from the Murchison Widefield Array (MWA) and the Precision Array for Probing the Epoch of Reionization (PAPER), HERA is a hexagonal array of large (14\,m diameter) dishes with suspended dipole feeds with element collecting area of 100\,m$^2$.
-Not only does the dish determine overall sensitivity, it determines the aggregate frequency structure of foregrounds in the interferometer.
-This is the first of a series of four papers characterizing the frequency and angular response of the with simulations and measurements.
+The Hydrogen Epoch of Reionization Array (HERA) is a radio interferometer aiming to detect the power spectrum of 21\,cm fluctuations from neutral hydrogen from the Epoch of Reionization (EOR).
+Drawing on lessons from the Murchison Widefield Array (MWA) and the Precision Array for Probing the Epoch of Reionization (PAPER), HERA is a hexagonal array of large (14\,m diameter) dishes with suspended dipole feeds.
+Not only does the dish determine overall sensitivity, it affects the observed frequency structure of foregrounds in the interferometer.
+This is the first of a series of four papers characterizing the frequency and angular response of the dish with simulations and measurements.
 We focus in this paper on the angular response (i.e., power pattern), which sets the relative weighting between sky regions of high and low delay, and thus, apparent source frequency structure.
 We measure the angular response at 137\,MHz using the ORBCOMM beam mapping system of \citet{neben15}.
-We measure a collecting area of 93\,m$^2$ in the optimal dish/feed configuration, implying HERA-331 should detect the EOR power spectrum with a signal-to-noise ratio of 19.3 using a foreground avoidance approach, and 74.3 using a foreground subtraction approach.
+We measure a collecting area of 93\,m$^2$ in the optimal dish/feed configuration, implying HERA-320 should detect the EOR power spectrum at $z\sim9$ with a signal-to-noise ratio of 19.3 using a foreground avoidance approach, and 74.3 using a foreground subtraction approach.
 Lastly we study the impact of these beam measurements on the distribution of foregrounds in Fourier space.
@@
 
-\keywords{instrumentation: interferometers --- techniques: interferometric --- cosmology: observations --- dark ages, reionization, first stars}
+\keywords{instrumentation: interferometers --- cosmology: observations --- reionization, first stars}
 
@@
  probing redshifted 21\,cm emission from the Cosmic Dawn. These observations will 
- complement indirect probes of the Dark Ages and Epoch of Reionization such as quasar 
- sightlines and the CMB optical depth which leave the reionization 
- history of the universe only loosely constrained. (See \citet{FurlanettoReview, miguelreview, PritchardLoebReview, aviBook, zaroubi} for reviews) Sensitivity and foreground removal are 
+ complement indirect probes of the Epoch of Reionization such as quasar 
+ sightlines and the CMB optical depth, which leave the reionization 
+ history of the universe only loosely constrained.
+(See \citet{FurlanettoReview, miguelreview, PritchardLoebReview, aviBook, zaroubi} for reviews) In the longer term, 21\,cm observations are expected to improve constraints on cosmology \citep[e.g.,][]{mao08, liu15a,liu15b}.
+Sensitivity and foreground removal are
  the main challenges in 21\,cm observations, as the expected cosmological signal is 4--5 
  orders of magnitude fainter in brightness temperature than Galactic and extragalactic foregrounds. Radio 
- interferometers such as the Murchison Widefield Arry (MWA) \citep{tingay13,mwascience}, the Precision Array for Probing the Epoch of Reionization (PAPER) \citep{ali2015}, the Giant Meterwave Radio Telescope (GMRT)
+ interferometers such as the Murchison Widefield Array (MWA) \citep{lonsdale09,tingay13,mwascience}, the Precision Array for Probing the Epoch of Reionization (PAPER) \citep{parsons10,parsons14,ali2015}, the Giant Meterwave Radio Telescope (GMRT)
  \citep{Paciga2011}, and the Low Frequency Array (LOFAR) \citep{lofar} are seeking a first detection of 
- cosmological 21\,cm emission in power spectrum measurements, where the smooth 
- frequency evolution of the foreground emission separates from the spectrally 
+ cosmological 21\,cm emission in power spectrum measurements. In the power spectrum, the spectrally smooth foreground emission separates from the spectrally 
  rough cosmological signal whose frequency dimension probes a line of sight through the 
@@
 
-The Hydrogen Epoch of Reionization Array (HERA) \citep[][deBoer et al.
-(in prep)]{PoberNextGen} is drawing on lessons learned by the MWA and PAPER to reach the calibration and foreground isolation accuracy required to make a significant detection and characterization of the cosmological signal.
+The Hydrogen Epoch of Reionization Array (HERA) \citep{PoberNextGen,deboer16} is drawing on lessons learned by the MWA and PAPER to reach the calibration and foreground isolation accuracy required to make a significant detection and characterization of the cosmological signal.
 HERA uses 14\,m diameter parabolic dishes arranged in a compact, hexagonal array to achieve coherent integration of the very low surface brightness 21\,cm signal.
-Redundant baselines also permit redundant calibration techniques which solve for the relative calibration between all antennas \citep{liu2010,zheng14}.
+Redundant baselines also permit redundant calibration techniques which solve for the relative calibration between all antennas \citep{redundant3, redundant4, liu2010,zheng14}.
 A central lesson from first generation instruments is that it is essential to characterize the instrument response to foreground emission lest instrument frequency dependence smear foreground power into cosmological signal modes.
@@
 interferometer's frequency-dependent point spread function smears foreground power into a ``wedge'' shaped 
-region in  $(k_\perp,k_\parallel)$ Fourier space \citep{Dattapowerspec,X13, PoberWedge,MoralesPSShapes, VedanthamWedge, nithya13, CathWedge, AdrianWedge1, AdrianWedge2,parsons12b}.
+region in $(k_\perp,k_\parallel)$ Fourier space \citep{Dattapowerspec,X13, PoberWedge,MoralesPSShapes, VedanthamWedge, nithya13, CathWedge, AdrianWedge1, AdrianWedge2,parsons12b}, where $k_\parallel$ modes are along the line of sight and $k_\perp$ modes are perpendicular to it.
 This effect is straightforward to understand for a single baseline which measures the sky intensity weighted by the complex sky fringe
-$e^{i \vec{k}\cdot\vec{b}}$, where $\vec{k}(\nu)$ is the wave vector of incident radiation pointing along its direction of travel, $\vec{b}$ is the baseline vector in meters, and $\nu$ is the observation frequency.
-Thus sources at different positions relative to the baseline vector manifest different
-frequency structure despite their intrinsically smooth spectra, but are geometrically limited 
-by the baseline length to a maximum frequency dependence of  $e^{2\pi i \nu \tau_g}$, where $\tau_g=\vec{b}\cdot\hat{k}/c$ is the delay in radiation arrival time between the two antennas in the baseline.
+$e^{2\pi i \nu \tau_g}$, where $\tau_g=\vec{b}\cdot\hat{s}/c$ is the delay in radiation arrival time at the second antenna relative to the first antenna of the baseline.
+Here $\nu$ is the observation frequency, $\vec{b}$ is the baseline vector, and $\hat{s}$ is the direction of the source.
+ Thus sources at different positions relative to the baseline vector appear with different 
+frequency structure despite their intrinsically smooth spectra. However, this instrumental frequency structure is limited 
+by the baseline length to a maximum frequency dependence of  $e^{2\pi i \nu b/c}$ for sources at maximum delay, near the horizon in line with the baseline vector.
 This limits the foreground contamination
@@
 perpendicular and parallel to the line of sight, and $a$ is a constant depending on the observational frequency and cosmology. The complement of the wedge is known as the ``EOR window''.
-
-It is convenient to phrase this description in terms 
-of the delay in radiation arrival at the baseline's two antennas, $\tau$, where $\tau_
-\text{max}=b/c$. Sources at low delay have little frequency 
-structure, while those near $\tau=\tau_\text{max}$ acquire the maximum frequency 
-structure given the baseline length. The high delay regions of the sky lie near the horizon while low delay 
-regions lie closer to zenith and also perpendicular to the baseline vector.
 
@@
 window.
-Finite bandwidth, imperfect bandpass calibration, and faraday rotation \citep{jelic2010,moore2013,giannisurvey, moore2013,moore2015,asad2015} of polarized sources can all imprint slight frequency structure on otherwise spectrally smooth sources, and those appearing closest to the edge of the wedge are
+Finite bandwidth, imperfect bandpass calibration, and faraday rotation of polarized sources can all imprint slight frequency structure on otherwise spectrally smooth sources \citep{jelic2010,giannisurvey, moore2013,moore2015,asad2015,newburgh14,shaw15}, and those closest to the edge of the wedge are
 most at risk of leaking into the EOR window. In fact, 
@@
 the angular response of the dish and its implications for power spectrum measurements. The three companion 
-papers present reflectometry measurements (Patra et al., submitted) and simulations (Ewall-Wice et al., 
-submitted) of the dish frequency response, as well as detailed 
-foreground simulations for HERA (Thyagarajan et al., submitted). A general description to the design of the 
-HERA experiment is given by DeBoer et al. (in prep). In essence, we 
+papers present reflectometry measurements \citep{patra16} and simulations \citep{ewallwice16} of the dish frequency response, as well as detailed 
+foreground simulations for HERA \citep{nithya16}. A general description of the design of the 
+HERA experiment is given by DeBoer et al. \citep{deboer16}. In essence, we 
 require a large collecting area for
- sensitivity and minimal sidelobes and horizon response without incurring the large cost per collecting 
+ sensitivity, and minimal sidelobes and horizon response without incurring the large cost per collecting 
 area of very large dishes.
-A dish is preferred to a large phased array as it has a less complex beampattern and reduced potential for antenna-to-antenna variation (Neben et al, submitted).
-The 331 dishes are positioned in a compact, hexagonal
-array permitting redundant baseline calibration and coherent integration in $
-\vec{k}$ space \citep{zheng14,parsons12a}. 
+A dish is preferred to a large phased array as it has a less complex beampattern and reduced potential for antenna-to-antenna variation \citep{neben16}.
+The core array consists of 320 dishes positioned on a compact, hexagonal
+grid \citep{dillonparsons16} permitting redundant baseline calibration and coherent integration in $
+\vec{k}$ space \citep{zheng14,parsons12a}. Improved imaging is permitted by 30 outriggers, but these do not appreciably affect power spectrum sensitivity.
 %The smaller field of view of the HERA dish relative to that of the PAPER dipole or the MWA tile does not limit sensitivity in Fourier space as most leverage on high $k$ modes is from line of sight modes anyway \citep{PoberNextGen}.
@@
 After verifying our models, we consider the science implications of these
-beam patterns by foreground delay spectra at different baseline lengths and observing conditions to study when the horizon brightening effect is strongest, and thus, when foreground are most at risk of leaking into the EOR window.
+beam patterns by foreground delay spectra at different baseline lengths and observing conditions to study when the horizon brightening effect is strongest, and thus, when foregrounds are most at risk of leaking into the EOR window.
 
@@
 The HERA element (Fig.
-\ref{fig:feeddiagram}) is a 14\,m diameter faceted parabolic dish ($f\#=0.32$) with a dual-polarized dipole feed suspended at prime focus.
+\ref{fig:feeddiagram}) is a 14\,m diameter faceted parabolic dish ($ f/D=0.32$) with a dual-polarized dipole feed suspended at prime focus \citep{dishmemo}.
+Here $f$ is the focal length of the dish and $D$ is the dish diameter.
 The dish surface is formed by wire mesh sheets (i.e., facets) mounted on PVC tubes which run from the lip of the dish to the hub at the vertex.
-The feed consists of a dual linear polarization PAPER sleeved dipole mounted 17'' below a 78'' diameter wire mesh back plane surrounded by a 30'' deep cylinder, suspended from cables attached to each the three telephone poles around the dish.
+For these tests, the feed consists of a dual linear polarization PAPER sleeved dipole mounted 17'' below a 78'' diameter wire mesh back plane surrounded by a 30'' deep cylinder, suspended from cables attached to each of the three telephone poles around the dish.
 The dipole ``sleeves'' are circular disks just above and below the dipole designed to broaden its frequency response.
-The cylinder is offset 0.5'' from the back plane, and is designed to make the beams for both linear polarizations more similar, and also to taper the dipole beam towards the edge of the dish to mitigate dish-dish coupling.
+The cylinder is offset 0.5'' from the back plane, and is designed to make the beams for both linear polarizations more similar.
 Fig.
 \ref{fig:feedphoto} shows the feed as deployed on the ground for early testing.
-The nominal dish focus is $f=(f\#)D=4.48$\,m, though our numerical electromagnetic models suggest the actual focus is slightly higher due to the feed geometry.
-In this work we study the dish beam pattern at feed heights of 4.5\,m, 5.0\,m, and 5.3\,m, measured from dish surface to feed plane, the last height being the maximum height we can achieve with the feed suspension system installed on the dish.
+The nominal dish focus is $f=(f/d)D=4.48$\,m, though given its faceted design, the dish does not have a single focus.
+Our numerical electromagnetic models suggest the best focus is slightly higher due to the feed geometry.
+In this work we study the dish beam pattern at rigging heights of 4.5\,m, 5.0\,m, and 5.3\,m, measured from dish surface to feed plane, the last height being the maximum height we can achieve with the feed suspension system installed on the dish.
 These height measurements are uncertain at the $\pm5\%$ level in this study.
-For more details on the dish design and construction see DeBoer et al.
-(in prep).
-Feed/dish optimization studies are ongoing and the values of these parameters may change in the full HERA array.
+For more details on the dish design and construction see \citet{deboer16}.
+Feed/dish optimization studies are ongoing and the values of these parameters may change in the full HERA array \citep{feedoptimizationmemo}.
 
@@
 \includegraphics[width=3.4in]{dish_and_feed_diagram.pdf}
-\caption{Diagram showing the dimensions and layout of the HERA dish and suspended feed.}
+\caption{Diagram showing the dimensions and layout of the parabolic HERA dish and suspended feed.}
 \label{fig:feeddiagram}
@@
 \includegraphics[width=3.4in]{feed.jpg}
-\caption{Prototype HERA feed set up outside the dish for preliminary characterization.
+\caption{Prototype HERA feed seen here outside the dish and upside-down for preliminary characterization.
 This feed revision consists of a dual-polarized sleeved dipole offset 17'' from a 78'' diameter back plane, surrounded by a 30'' deep cylindrical skirt.}
@@
 
-As the HERA element is larger than the MWA or PAPER antenna elements, one might worry about the  smaller field of view and thus smaller number of measured Fourier modes perpendicular to the line of sight.
+As the HERA element is larger than the MWA or PAPER antenna elements, one might worry about the  smaller field of view and thus smaller range of Fourier space probed perpendicular to the line of sight.
 However, this is a
@@
 A second potential drawback is frequency structure introduced by time domain reflections between the dish and feed detailed by Ewall-Wice et al.
-(submitted) with simulations and Patra et al.
-(in prep) with zenith reflectometry measurements.
+\citep{ewallwice16} with simulations and \citep{patra16} with zenith reflectometry measurements.
 These works demonstrate, though, that the slight frequency structure of the dish is sufficiently small to not interfere with EOR science.
-\\
+
 \subsection{Dish Modeling}
@@
 \centering
-\includegraphics[width=7in]{dave197_rich195_airy_beams.pdf}
+\includegraphics[width=7in]{dave195_rich195_airy_beams.pdf}
 \caption{Simulated dish power patterns (NS polarization) at 137\,MHz (see Sec.
-\ref{sec:dishmodels}) with $h_\text{feed}=5$\,m using HFSS (left) and CST (middle) are shown beside an ideal Airy pattern for a 14\,m diameter dish for comparison.}
+\ref{sec:dishmodels}) with $h_\text{feed}=5$\,m using HFSS (left) and CST (middle) are shown beside an ideal Airy pattern for a 14\,m diameter dish for comparison.
+Dased lines mark zenith angles of 20$^\circ$, 40$^\circ$, 60$^\circ$, and 80$^\circ$.}
 \label{fig:modelbeams}
@@
 
-We numerically model the HERA dish in both ANSYS HFSS\footnote{http://www.ansys.com/Products/Electronics/ANSYS-HFSS} and in CST Microwave Studio\footnote{https://www.cst.com/Products/CSTMWS}, making slightly different assumptions, in order to study the dependence of the beam pattern on modeling inaccuracies and material uncertainties.
+We numerically model the HERA dish in both ANSYS HFSS\footnote{http://www.ansys.com/Products/Electronics/ANSYS-HFSS} and in CST Microwave Studio\footnote{https://www.cst.com/Products/CSTMWS}, making slightly different assumptions, in order to study the range of realistic beams given modeling inaccuracies and material imperfections.
 In particular, the near horizon beam response, which sets the level of horizon brightening in the delay spectrum, is quite sensitive to modeling assumptions.
-Modeling also probes the best focus of the dish--feed system.
 
-The HFSS model assumes a solid 14\,m parabolic dish ($f\#=0.32$) with a 1\,m hole at the vertex.
+The HFSS model uses a realistic faceted dish \citep{deboer16} ($f/D=0.32$) with a 1\,m diameter dielectric similar to dry soil at the vertex.
 In reality a 1\,m diameter circle at the vertex is filled with concrete and supports the PVC pipes which suspend the mesh panels, but we effectively assume here it is perfectly absorbant.
-The feed is modeled as sleeved dipole with a solid metal back plane and cylinder with the dimensions given above.
+The feed is modeled as a sleeved dipole with a solid metal back plane and cylinder with the dimensions given above.
 Copper is used for the dipole itself, and aluminum for all reflecting surfaces.
@@
 
-The CST model again assumes a 14\,m parabolic diameter solid aluminum paraboloid with $f\#=0.32$ but neglects the 1\,m hole at the vertex, effectively assuming the concrete and earth ground behind it are perfectly reflective.
-The actual material properties are somewhere between fully reflective and fully absorbant, and thus, between these two models.
+The CST model assumes a 14\,m diameter perfect paraboloid of solid aluminum with $f/D=0.32$ but neglects the 1\,m hole at the vertex, effectively assuming the concrete and earth ground behind it are perfectly reflective.
 The feed model has the same dimensions and properties as in the HFSS model.
@@
 Similarly, the EW dish beam is narrower in the EW direction.
-Lastly, we note that in both models, the best focus is found to be close to 5.23\,m with this feed geometry, slightly larger than the nominal focus of 4.5\,m, as expected.
+Lastly, we note that in both models, the best focus is found to be close to 5.23\,m with this feed geometry.
 
@@
 due to changing distance, orientation, and transmission power. To correct for this, we 
-measure the satellite flux in each ground polarization (EW and NS) using a simple, well-
+measure the satellite flux in each ground polarization (East-West (EW) and North-South (NS)) using a simple, well-
 modeled reference antenna. Comparison of this measured power with that observed in the 
@@
 the reference antenna model yields the desired AUT response. As discussed in 
-\citet{neben15}, this procedure correctly measures the response of the AUT to unpolarized radiation
- despite the fact that satellite signals are generally polarized.
+\citet{neben15}, this procedure correctly measures the desired response of the AUT to unpolarized radiation despite the fact that satellite signals are generally polarized.
 
@@
 frequencies, we probe the beam response in all these directions simultaneously. We 
-compute the satellite positions using the orbital elements published by Celestrak
-\footnote{http://www.celestrak.com/NORAD/elements/orbcomm.txt} and the orbital 
+compute the satellite positions using the orbital elements published by Celestrak\footnote{http://www.celestrak.com/NORAD/elements/orbcomm.txt} and the orbital 
 integrator \texttt{predict}\footnote{http://www.qsl.net/kd2bd/predict.html}. However, the 
@@
 processed separately to identify and exclude times of low signal-to-background when the 
-satellite is low in the sky or in the off state of a pulsing sequence. At those times, then 
+satellite is low in the sky or in the off state of a pulsing sequence. At those times, the 
 satellite flux no longer dominates over that of the diffuse Galactic background, and a 
@@
 We collected roughly 100 satellite passes.
-Systematics at the few percent level are observed in  within $20^\circ$ of zenith, and at the 10--20\% level farther out.
+Systematics at the few percent level are observed within $20^\circ$ of zenith, and at the 10--20\% level farther out.
 The magnitude and angular distribution of these systematics changes modestly as the separation is changed, suggesting that the reference dipoles differ largely due to intrinsic differences, with some environmental variation.
@@
 \subsection{Power pattern measurements}
+\label{sec:powerpatternmeasurements}
 
@@
 \includegraphics[width=6.5in]{measured_beams_and_models_maps.pdf}
-\caption{Measured dish power patterns with three feed heights for the EW (left panel) and NS (right panel) linear instrumental polarizations.
-The sidelobes shrink and the main lobe narrows as the feed is raised, confirming that the best focus of the dish/feed system is close to $h_\text{feed}=5.3$\,m.}
+\caption{Measured dish power patterns at three feed rigging heights (Fig.
+\ref{fig:feeddiagram}) for the EW (left panel) and NS (right panel) instrumental polarizations.
+The sidelobes shrink and the main lobe narrows as the feed is raised, confirming that the best focus is close to $h_\text{rig}=5.3$\,m.}
 \label{fig:measuredbeammaps}
@@
 \includegraphics[width=6.5in]{measured_beams_and_models_slices.pdf}
-\caption{Slices through the E and H planes through the measured dish power patterns (points) and numerical models (curves).
-The measured beams agree with both models in the main lobe out to zenith angles of 15--20$^\circ$, but begin to deviate in the sidelobes where the beam response is 25-30\,dB down from zenith.}
+\caption{Slices through the E (red) and H (cyan) planes through the measured dish power patterns (points) and numerical models (curves).
+The measured beams agree with both models in the main lobe out to zenith angles of 15--20$^\circ$ up to slight main lobe tilts, but begin to deviate in the sidelobes where the beam response is 25-30\,dB down from zenith.
+The measured beams typically differ more from both model beams than the models differ from each other, suggesting that real world effects are more significant that the slightly different assumptions used in the CST and HFSS simulations.
+In particular, the most likely systematic is mis-centering of the feed over the dish (see Sec.
+\ref{sec:powerpatternmeasurements}).}
 \label{fig:measuredbeamslices}
@@
 We make dish power pattern measurements at 137\,MHz as described in Sec.
-\ref{sec:orbcommreview} with the feed at 4.5\,m, 5.0\,m, and 5.3\,m height above the dish surface (see Fig.
+\ref{sec:orbcommreview} with feed rigging heights of 4.5\,m, 5.0\,m, and 5.3\,m above the dish surface (see Fig.
 \ref{fig:feeddiagram}).
@@
 These maps are plotted in sine-projection with dashed circles marking zenith angles of $20^\circ$, $40^\circ$, $60^\circ$, and $80^\circ$.
-The sky coverage in these dish measurements extends out to typically $\theta\sim60^\circ$, beyond which the ORBCOMM flux is sufficiently attenuated relative to diffuse galactic emission that power measurements are no longer  clean probes of the antenna gains in the direction of the satellite.
-At these largest measurable zenith angles the beam sidelobes are roughly -30\,dB and trending downward.
+The sky coverage in these dish measurements extends out to typically zenith angles of $\theta\sim60^\circ$, beyond which the ORBCOMM flux is sufficiently attenuated relative to diffuse galactic emission that a power measurements is no longer a clean probe of the antenna gain in the direction of the satellite.
+At these largest measurable zenith angles the beam sidelobes are roughly -30\,dB down from the zenith boresight gain, and trending downward.
 
-The roughly $10^\circ$ main lobe narrows slightly as the feed is raised from 4.5\,m to 5.3\,m, and the sidelobes shrink both in size and in amplitude, confirming that the focus is closer to 5.3\,m.
-As the response of the dish itself is azimuthally symmetric, its response with the feed should have the 180$^\circ$ symmetry of the dipole.
+The roughly $10^\circ$ full-width-at-half-max main lobe narrows slightly as the feed is raised from 4.5\,m to 5.3\,m, and the sidelobes shrink in size and amplitude, confirming that the best focus is closer to 5.3\,m.
+As discussed in Sec.
+\ref{sec:dishmodels}, the dish beam should be narrower in the E plane and wider in the H plane, with an overall 180$^\circ$ symmetry.
 Indeed, the observed main lobes of the EW (NS) beams are slightly wider in the NS (EW), especially in the 5.3\,m feed height beam as it is most in focus.
-Unsurprisingly, we observe deviations from this symmetry in the sidelobes, which are very sensitive to slight dish/feed imperfections.
+We observe deviations from this symmetry in the sidelobes, which are very sensitive to slight dish/feed imperfections.
 
 Figure \ref{fig:measuredbeamslices} shows slices through the E and H planes of these power patterns along with the HFSS and CST numerical models discussed earlier.
-As in the previous plot, the EW and NS beams are shown it the left and right panels, while the different feed heights are shown in the different rows.
-The data agree with both models to within 1\,dB in the main lobe, though often appear slightly shifted so they are not quite centered on zenith.
+As in the previous plot, the EW and NS beams are shown in the left and right panels, while the different feed heights are shown in the different rows.
+The data agree with both models to within 1\,dB in the main lobe, though in several cases appear slightly shifted so they are not quite centered on zenith.
 The data diverge further in the sidelobes at zenith angles of $20^\circ$ and larger.
 Here the evolution of the sidelobes as the feed is raised is again seen starkly, as is the fact that the main lobes are slightly wider along the H planes than along the E planes.
-We observe that both models agree with the measured beams in the main lobe but deviate differently at the 1--5 dB level in the sidelobes.
+We observe that both models agree with the measured beams in the main lobe but deviate from the data in different ways at the 1--5 dB level in the sidelobes.
+Neither model looks consistently better, suggesting that the as-built HERA dish deviates from both numerical models more significantly than the models deviate from each other due to their slightly different assumptions.
 
-We emphasize that the model deviations observed in the measured beams are real in that they are larger than the 0.5\,dB systematics observed in the null experiments (Fig.
+We emphasize that the model deviations observed in the measured beams are real in that they are larger than the 0.5\,dB scale systematics observed in the null experiments (Fig.
 \ref{fig:nullexptplots}).
-Those experiments bound the impact of environmental reflections and reference dipole mismodeling to the ma 10\% level or smaller across the whole sky.
+Those experiments bound the impact of environmental reflections and reference dipole mismodeling to the 10\% level or smaller across the whole sky.
 The observed dish beam asymmetries, model deviations in sidelobes, and slight shifts of the main lobes all suggest feed centering errors.
@@
 If feed tilt/rotation errors or dish surface imperfections were significant, then the beam errors at different feed heights would look similar because these errors persist when the feed is raised or lowered.
-The fact that they change over the three beam measurements suggests that feed centering errors are most significant because they change when the feed height is changed.
-To mitigate these errors, the feeds in the full HERA array will be tied down to the dish surface.
+All three ropes are tied to a single location on the feed, so rope length errors affect on the feed centering, not its rotation or tilt.
+The fact that the observed model deviations change over the three beam measurements suggests that feed centering errors are most significant because they are the only ones which change when the feed height is changed.
+To mitigate these errors, the feeds in the full HERA array will be tied down to the dish surface at several points.
 
@@
 This is in line with expectations given that the Airy pattern has the largest possible collecting area, equal to the dish cross section, and the feed's backplane and cylindrical skirt reduce it.
-However we opt for this reduction over added collecting area in order to reduces the azimuthal beam asymmetry and minimize the cross-coupling between adjacent dishes.
+However we opt for this reduction over added collecting area in order to reduces the azimuthal beam asymmetry.
 
  \begin{table}[h]
- \caption{ \label{table:collectingareatable}Collecting area (m$^2$) of measured 137\,MHz beams and corresponding power spectrum SNR for HERA-331 using either foreground avoidance or foreground subtraction.}
+ \caption{ \label{table:collectingareatable}Collecting area (m$^2$) of measured 137\,MHz beams and corresponding power spectrum SNR for HERA-320 using either foreground avoidance or foreground subtraction.}
 \begin{tabular}{| l | l | l |}
 \hline
-Beam & $A_\text{eff}$ (m$^2$) & SNR (avoidance, subtraction)\\
+Beam & $A_\text{eff}$ (m$^2$) & SNR ($\sigma$)\\
+&& (avoidance, subtraction)\\
 \hline
@@
 % To input these collecting areas into 21cmSense, we convert these measured dish collecting areas into effective dish diameters, which we input as the \texttt{dish\_size\_in\_lambda} parameter. 
-We run 21cmSense\footnote{https://github.com/jpober/21cmSense} to compute the overall SNR of a power spectrum detection with one season (6 hours per night for 180 nights) of HERA-331 data.
+We run 21cmSense\footnote{https://github.com/jpober/21cmSense} to compute the overall SNR of a power spectrum detection with one season (6 hours per night for 180 nights) of HERA-320 data.
 We use a fiducial Epoch of Reionization model generated with 21cmFast \citep{21cmfast}.
@@
 We consider now the effects of the beam power pattern on the apparent frequency dependence of the foregrounds.
-Thyagarajan et al., (submitted) discuss the apparent frequency dependence of foregrounds in more detail as well as methods to mitigate it such as delay space CLEANing.
+\citet{nithya16} discuss the apparent frequency dependence of foregrounds in more detail as well as the contribution from the beam frequency dependence.
 We focus in this section on the uncertainties in these foreground power spectrum simulations due to beam modeling uncertainties, but first discuss these foreground simulations themselves and their dependence on observing conditions.
@@
 We use frequency-independent model beams (evaluated at 137\,MHz) to isolate the interferometric foreground frequency dependence.
-The added frequency dependence of the changing overall gain and beam shape versus frequency is addressed by the other papers in this series.
+The added frequency dependence of the changing overall gain and beam shape with frequency is addressed by the other papers in this series.
 Given that our measured dish power patterns agree well with both numerical models (HFSS and CST) in the main lobe but deviate in the sidelobes, and that these models make somewhat different assumptions about the dish surface, we take them as a representative pair of possible dish models.
-We use a feed height of 5\,m, a compromise between collecting area and risk of coupling to adjacent dishes.
+We use the empirically best feed height of 5.3\,m.
 We also include the Airy pattern for comparison as in \citet{nithya15}.
@@
 This reduces the magnitude of emission near the edge of the EOR window, reducing the risk it leaks inside.
-We use the per-baseline approach of \citet{parsons12a,parsons12b}, simulating visibilities measured by specific baselines as a function of frequency, then computing the Fourier transform over frequency (delay transform) and normalizing the result into a cosmological power spectrum following \citet{nithya15}.
+We use the per-baseline approach of \citet{parsons12a,parsons12b} by first simulating visibilities measured by specific baselines as a function of frequency, then computing the Fourier transform over frequency (delay transform), and lastly normalizing the result into a cosmological power spectrum following \citet{nithya15}.
 
-In detail, we simulate visibilities for each beam model at various LSTs, modeling the sky as the sum of the Global Sky Model \citep{gsm} and the Culgoora \citep{Slee1995} and MWA Commissioning Survey \citep{MWACS} point source catalogs, all evaluated at 150\,MHz.
-We use a frequency spacing of 1\,MHz, sufficient to characterize delays within and just outside of the horizon limits on both baseline lengths we are concerned with, 14.6\,m and 43.8\,m.
-We use a total bandwidth of 100\,MHz (50\,MHz after applying the Blackman-Harris window) centered on 150\,MHz.
-This bandwidth is larger than the 10\,MHz thought to be safe from signal evolution over redshift, but is the bandwidth used in the wide band delay space foreground filter of \citet{paper32,ali2015}.
+In detail, we simulate visibilities using PRISim\footnote{https://github.com/nithyanandan/PRISim} for each beam model at various LSTs, modeling the sky as the sum of the Global Sky Model \citep{gsm} and the NVSS \citep{nvss} and SUMSS \citep{sumss,sumss2} point source catalogs.
+We use a frequency spacing of 781\,kHz, sufficient to characterize delays within and just outside of the horizon limits on both baseline lengths considered, 14.6\,m and 43.8\,m.
+We use a total bandwidth of 100\,MHz (effectively reduced to 50\,MHz after applying the Blackman-Harris window) centered on 150\,MHz.
+This bandwidth is larger than the 10\,MHz thought to be safe from signal evolution with redshift, but is the bandwidth used in the wide band delay space foreground filter of \citet{paper32,ali2015}.
 
 Figure \ref{fig:delayspec} (top panel) shows simulated foreground delay spectra at various LSTs using the nominal HFSS beam.
-As all these LSTs are high galactic latitudes far from the galactic center, the total visibility power (the level of the zero delay mode) varies only by a factor of a few over these LSTs on both baseline lengths (14.6\,m (left panel), 43.8\,m (right panel)).
-However the positive delay horizon limit (corresponding to the western horizon) has a peak that varies by over 1.5 orders of magnitude on both baseline, demonstrating the stark difference in horizon brightening when the galaxy is just above versus just below the horizon.
+As all these LSTs correspond to high galactic latitudes far from the galactic center, the total visibility power (the level of the zero delay mode) varies only by a factor of a few over these LSTs on both baseline lengths (14.6\,m (left panel), 43.8\,m (right panel)).
+However the positive delay horizon limit (corresponding to the western horizon) has a peak that varies by over 1.5 orders of magnitude on both baselines, demonstrating the stark difference in horizon brightening when the galaxy is just above versus just below the horizon.
+In this figure we perform the approximate conversion from delay $\tau$ to $k_\parallel$ at $z=8$, which we plot as a second $x$-axis at the top of the plot.
 
-In this figure we perform the approximate conversion from delay $\tau$ to $k_\parallel$ at $z=8$, which we plot as a second $x$-axis at the top of the plot.
-For these short baselines it is a good approximation to interpret $k_\parallel$ as $k$, and we thus plot a 1D model power spectrum computed using 21cmFast \citep{21cmfast} as a dotted line for comparison.
-Ftop panel
 \begin{figure*}[h]
@@
 \includegraphics[width=6in]{nithya_fg_pspec_lst60deg.pdf}
-\caption{Simulated foreground delay spectra using the HFSS beam at various LSTs (top panel).
-We then plot the delay spectra at two LSTs spanning the range of possible horizon brightening for three different beam models.
-The maximum horizon brightening at the positive horizon occurs close to 0$^\circ$ LST (middle panel), and the three beam models thus differ markedly in their predicted delay spectra near the horizon.
-The horizon is shown in all panels as a vertical line at the baseline's maximum delay seen by radiation from the horizon in line with the baseline.
-In contrast, when the horizon brightening effect is smaller at 60$^\circ$ LST, the foreground delay spectra from all three beams agree.}
+\caption{We plot simulated foreground delay spectra using the HFSS beam at various LSTs (top panel).
+The maximum horizon brightening at the positive horizon occurs close to 0$^\circ$ LST.
+At this LST, the simulated foreground delay spectra for the three beam models differ markedly near the positive horizon, plotted as a vertical line at the baseline's maximum delay.
+In contrast, when the horizon brightening effect is smaller at 60$^\circ$ LST (bottom panel), the foreground delay spectra from all three beams agree better.}
 \label{fig:delayspec}
@@
 
-To characterize the effect of beam modeling uncertainties on this horizon brightening, we select two of these LSTs, one with maximal horizon brightening ($2^\circ$), and one with minimal horizon brightening ($62^\circ$).
+To characterize the effect of beam modeling uncertainties on this horizon brightening, we select two of these LSTs, one with maximal horizon brightening ($0^\circ$), and one with minimal horizon brightening ($60^\circ$).
 Figure \ref{fig:gsmplots} shows the sine-projected Global Sky Model at 150\,MHz, which dominates the horizon brightening effect, in local Azimuth/Elevation coordinates with units of Kelvin for both LSTs.
-Dashed lines mark zenith angles 20$^\circ$, 40$^\circ$, 60$^\circ$, and 80$^\circ$.
-These plots confirm that the large negative delay peak at the 0$^\circ$ LST is due to the center of the galaxy just above the horizon.
-In contrast, several hours later, the galactic center is fully below the western horizon, leaving only a slight brightening near the eastern horizon due to the weaker galactic anticenter.
+These plots confirm that the large positive delay peak at the 0$^\circ$ LST is due to the center of the galaxy just above the western horizon.
+In contrast, several hours later, the galactic center is fully below the horizon, leaving only a slight brightening near the eastern horizon due to the weaker galactic anticenter.
 
@@
 \includegraphics[width=6in]{gsm_kelvin_LST_2deg_and_62deg.pdf}
-\caption{Global Sky Model \citep{gsm} in sine-projected horizontal coordinates at LST of 2$^\circ$ (left) and 62$^\circ$ right.
-The very bright emission from the center of the galaxy at the western horizon at 2$^\circ$ is seen in the delay spectra of EW baselines as a horizon brightening at negative delay.}
+\caption{Global Sky Model \citep{gsm} in sine-projected horizontal coordinates at LST of 2$^\circ$ (left) and 60$^\circ$ right.
+The very bright emission from the center of the galaxy at the western horizon at 0$^\circ$ is seen in the delay spectra of EW baselines as a horizon brightening at negative delay.}
 \label{fig:gsmplots}
@@
 Both numerical models agree out to delays of roughly 20\,ns on the 14.6\,m baseline and 50\,ns on the 43.8\,m baseline.
-These numbers suggest that the beams track each other fairly well out to 25$^\circ$ from zenith, beyond which they diverge.
-This is roughly what is observed in Figure \ref{fig:measuredbeamslices} (middle panel).
+These numbers suggest that the beams track each other fairly well out to roughly 25$^\circ$ from zenith, beyond which they diverge.
+This is roughly what is observed in Figure \ref{fig:measuredbeamslices}.
 At larger delays, especially near the positive delay horizon limit, all three model delay spectra diverge due to the significant edge brightening which effectively discriminates between these models.
-The CST, HFSS, and Airy beams reach roughly -35\,dB, -38\,dB, and -50\,dB at the horizon (Figure \ref{fig:modelbeams}), consistent with the fact that the CST beam has the largest horizon brightening, followed by the HFSS beam, and then by the Airy beam.
+The CST and HFSS beams reach roughly -32\,dB and -38\,dB at $80^\circ$ zenith angle (Figure \ref{fig:modelbeams}), consistent with the fact that the CST beam has a larger horizon brightening than the HFSS beam.
 This is seen in the delay spectra for both baseline lengths, though the edge brightening is much clearer on the longer baseline where it less diluted by zero delay emission.
 
-In contrast, all three model agree much more closely when there is little or no edge brightening as in Figure \ref{fig:measuredbeamslices} (bottom panel) where we plot the delay spectra for all three beams for 60$^\circ$ LST.
+In contrast, all three models agree better when there is little or no edge brightening as in Figure \ref{fig:delayspec} (bottom panel) where we plot the delay spectra for all three beams for 60$^\circ$ LST.
 There is still a modest flattening off near the horizon on the 14.6\,m baseline and a slight peak on the 43.8\,m baseline due to the large solid angle near the horizon.
@@
 Power spectrum analyses by first generation 21\,cm observatories are ongoing, but are contending with challenges ranging from calibration and foreground modeling to the analysis effort required to process thousands of hours of data.
-HERA draws on the most successful ideas from these first generation instruments, pursuing a compact and redundant array layout and large collecting area antenna elements.
+HERA draws on the most successful ideas from these first generation instruments, pursuing a compact and redundant array layout with large antenna elements.
 The hexagonal grid allows redundant calibration and coherent power spectrum integration, and the large 14\,m dish achieves sufficient sensitivity at a reasonable data processing and analysis cost.
-The papers in this series characterize the 14\,m diameter dish used as HERA's antenna element using reflectometry measurements and simulations which probe its frequency response, as well as power pattern measurement which probe its angular response.
+The papers in this series characterize HERA's 14\,m diameter dish element using reflectometry measurements and simulations, which probe its frequency response, as well as power pattern measurements probing its angular response.
 
-We present in this paper beam pattern measurements at 137\,MHz and discuss their implications for 21\,cm power spectrum analysis in terms of sensitivity and foreground isolation.
-We begin with the power pattern measurements using the beam mapping system of \citet{neben15} which we deploy at the prototype three-element HERA array at the National Radio Astronomy Observatory--Green Bank.
-We present measured power patterns for three dish configurations with the feed at different heights over the dish surface in order to characterize the focus of the system.
-The measured power patterns probe nearly two thirds of the visible sky, down to -30\,dB relative to the zenith response.
-The measured beams agree well with both models in the main lobe out to 10--20$^\circ$ from zenith, then roughly track the typical sidelobe levels at 20--30\,dB below zenith, deviating at the 1--5\,dB level.
+We have presented beam pattern measurements at 137\,MHz, and discussed their implications for 21\,cm power spectrum analyses in terms of sensitivity and foreground isolation.
+We begun with power pattern measurements made using the beam mapping system of \citet{neben15} which we deployed at the prototype three-element HERA array at the National Radio Astronomy Observatory--Green Bank.
+We measured the dish power pattern with the feed at different heights over the dish surface and found that the best focus is at a feed rigging height of 5.3\,m, though this may change for different feed designs being explored\citep{feedoptimizationmemo}.
+The measured beams probe nearly two thirds of the visible sky down to -30\,dB relative to boresight, and agree well with both models in the main lobe out to 10--20$^\circ$ from zenith.
+The measured beams roughly track the predicted sidelobe levels at 20--30\,dB below zenith, deviating at the 1--5\,dB level.
 
-These deviations away from models and away from 180$^\circ$ azimuthal symmetry are larger than the $\pm1$\,dB systematics observed in the null experiments which probe our beam measurement accuracy, suggesting they are genuine measurements of the in situ dish beam.
-The most likely dish non-idealities are dish surface imperfections and feed misalignment, both of which may vary from antenna to antenna in the full HERA array.
-Characterizing this antenna-to-antenna beam variation and its effects on power spectrum analyses for HERA, as Neben et al.
-(submitted) do for the MWA, is left as future work.
+These deviations away from models and away from 180$^\circ$ azimuthal symmetry are larger than the $\pm0.5$\,dB systematics observed in our null experiments which probe the accuracy of our beam measurement system, suggesting they are genuine measurements of the in situ dish beam.
+The most likely culprit is feed mis-centering which shifts and distorts the main lobe sidelobes.
+In the full HERA array, the suspended feeds will be tied to the dish surface at several points to level and center them.
+Characterizing the level of antenna-to-antenna beam variation in the full HERA array and its effects on power spectrum analyses, as Neben et al.
+(in press) do for the MWA, is left as future work.
 
-We quantify HERA's 21\,cm power spectrum sensitivity given our beam measurements by first computing the collecting area of the different dish configurations.
-We observe a reduction of 30--50\% from the geometric cross section of a 14\,m dish due to the dipole feed and its cylindrical skirt which tapers the beam towards the edge of the dish to mitigate cross coupling with adjacent dishes.
-We convert these collecting areas into effective dish sizes, then use 21cmSense to predict the overall power spectrum SNR with one season of HERA-331 data.
-We find SNRs of 19.3 and 74.3 using foreground avoidance and subtraction respectively, with the feed at optimal focus.
-While a reduction from the theoretical limit of an unobstructed 14\,m aperture, these sensitivities still permit a very significant detection of the 21\,cm signal after a single observing season.
+We quantify HERA's sensitivity to the 21\,cm power spectrum given our beam measurements by first computing the collecting area of the measured beams at the different feed rigging heights, finding 93\,m$^2$ at the best focus.
+We observe a reduction of 30--50\% from the geometric cross section of a 14\,m dish due to feed blockage and under-illumination of the dish.
+We convert our measured collecting areas into effective dish sizes, then use 21cmSense to predict the overall power spectrum SNR at $z\sim9.5$ with one season of HERA-320 data.
+We predict SNRs of 19.3 and 74.3 using foreground avoidance and subtraction approaches respectively, compared with SNRs of 25.5 and 90.8 using an ideal unobstructed 14\,m aperture (Airy pattern).
+Still, these sensitivities permit a very significant detection of the 21\,cm signal after a single observing season.
 
 Beyond simple sensitivity considerations, though, the beam pattern affects science analyses by reweighting celestial emission in different regions of the sky, which are then imprinted with different frequency dependence by the interferometer.
-Longer baselines are proportionately more susceptible to this effect, giving rise to a ``wedge'' shaped region in 2D Fourier space.
+Longer baselines are more susceptible to this effect, giving rise to a ``wedge'' shaped region in 2D Fourier space.
 \citet{nithya15} has highlighted that the distribution of foregrounds \textit{within} the wedge is important as well.
-If the beam response is sufficiently shallow at low elevations, there is a brightening of emission from near the horizon in line with the baseline due in part to the large solid angle at low elevations.
+If the beam falloff is sufficiently shallow at low elevations, there is a relative brightening of emission from near the horizon in line with the baseline due in part to the large solid angle at low elevations.
 This produces a characteristic ``pitchfork'' shape in the delay spectrum of a single baseline, with a zero delay peak due to bright near-zenith emission surrounded by tines at the negative and positive horizon limits due to emission from the two horizon directions in line with the baseline.
@@
 As expected, we find that the level of horizon brightening is largest when the galaxy is just above the horizon, and lowest when it is well below.
-When the pitchfork effect is large, its uncertainty is also large as seen in the deviation of the delay spectra with HFSS and CST beam models in these simulations.
+When this pitchfork effect is large, we find that the uncertainty in its predicted amplitude is also large, as seen in the differences between the delay spectra calculated using HFSS and CST beam models.
 When the effect is small, the two beam models produce much more similar results, highlighting the delay spectrum as an exquisite probe of the difficult-to-measure beam response at very low elevations.
 
-As discussed by the other papers in this series (Ewall-Wice et al., in prep, Patra et al., in prep, Thyagarajan et al., in prep), the frequency dependence of both the beam's angular response and its overall gain widen the delay kernel of a source, leaking power into the EOR window out to $k_\parallel=$0.15-0.23h\,Mpc$^{-1}$.
+As discussed by the other papers in this series \citep{ewallwice16,patra16,nithya16}, the frequency dependence of both the beam's angular response and its overall gain widen the delay kernel of a source, leaking power into the EOR window out to $k_\parallel=$0.15-0.23h\,Mpc$^{-1}$.
 This is well inside the wedge plus buffer used in a foreground avoidance analysis.
-Foreground subtraction requires calibrating out the instrument frequency response enough to begin to access cosmological modes within the wedge.
+Foreground subtraction, however, requires calibrating out the instrument frequency response well enough to begin to access cosmological modes within the wedge.
 This is much more challenging, but the sensitivity gains are enormous as those signal modes are thought to be the strongest.
-Even with only foreground avoidance, though, assuming only previously demonstrated analysis techniques, we project a $18\sigma$ detection of the EOR power spectrum which would provide begin to probe reionization models in detail and shed light on our cosmic dawn.
+Even with only foreground avoidance, though, assuming only previously demonstrated analysis techniques, we project a $19.3\sigma$ detection of the EOR power spectrum with a single observing season which would provide begin to probe reionization models in detail and shed light on our cosmic dawn.
+
+\begin{acknowledgments}
+We thank Jonathan Pober, Gianni Bernardi, and Eloy de Lera Acedo for helpful comments on our manuscript.
+This work was supported by NSF grant AST-1440343, the Marble Astrophysics Fund, and the MIT School of Science.
+ARP acknowledges support from NSF CAREER award 1352519.
+AEW acknowledges support from an NSF Graduate Research Fellowship under Grant No.
+1122374.
+DJC acknowledges support from NSF grant AST-1401708.
+\end{acknowledgments}
 

### 2016-02-12 DishReflectometry/Paper1_v1.tex
Corrected notations.

@@
 
-Consider a two element interferometer with a baseline $\vec b$ and antenna field pattern $A(\thhat, \nu)$.
+Consider a two element interferometer with a baseline $\vec b$ and antenna field pattern $\bmvolt(\thhat, \nu)$.
 If we denote the electric field sky signal in direction $\thhat$ by $\volt_\sky(\vec \theta, \nu)$ and the receiver noise of each element as $\volt_{rec}(\nu)$ then the voltage output of each antenna may be written as,
@@
 
-We define antenna cross power pattern as  $\bm(\thhat,\nu)=\bmvolt_{1}(\thhat,\nu)\bmvolt_{2}^{*}(\thhat,\nu)$ and denote the sky intensity as  $I_\sky(\thhat,\nu)=\volt_\sky(\thhat,\nu)\volt_\sky^{*}(\thhat,\nu)$.
+We define antenna cross power pattern as  $\beam(\thhat,\nu)=\bmvolt_{1}(\thhat,\nu)\bmvolt_{2}^{*}(\thhat,\nu)$ and denote the sky intensity as  $I_\sky(\thhat,\nu)=\volt_\sky(\thhat,\nu)\volt_\sky^{*}(\thhat,\nu)$.
 Hence,
 \begin{equation}
-\vis(\vec b,\nu) = \int \bm(\thhat, \nu) I_\sky(\thhat,\nu) \ifngexp d\Omega
+\vis(\vec b,\nu) = \int \beam(\thhat, \nu) I_\sky(\thhat,\nu) \ifngexp d\Omega
 	%	& = & \int B(l,m, \nu) I_{sky}(l,m,\nu) exp(-2\pi i \nu \tau_{g} ) dl dm \nonumber\\
@@
 \begin{eqnarray}
-\tilde V(\vec b, \tau) & = & \int\!\!\int{\bm(\thhat,\nu) I_\sky(\thhat,\nu) \ifngexp d\Omega~e^{+2\pi i\nu\tau}d\nu}\nonumber\\	                        & = &   \int \left [ A(\thhat, \tau)\ast I_{sky}(\thhat, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega
+\tilde V(\vec b, \tau) & = & \int\!\!\int{\beam(\thhat,\nu) I_\sky(\thhat,\nu) \ifngexp d\Omega~e^{+2\pi i\nu\tau}d\nu}\nonumber\\	                        & = &   \int \left [ A(\thhat, \tau)\ast I_{sky}(\thhat, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega
 \label{eq3}
@@
 Consider again a two element interferometer as described in section 2.
-Two antennas are assumed to be exactly identical so that their electrical parameters and the field pattern are identical i.e, $a_{1}(\thhat,\nu) = a_{2}(\thhat,\nu)$.
+Two antennas are assumed to be exactly identical so that their electrical parameters and the field pattern are identical i.e, $a_{1}(\thhat,\nu) = a_{2}(\thhat,\nu) = a(\thhat, \nu)$.
 We denote the voltage reflection coefficient of each feed by $\Gamma_{f}$.
@@
 \begin{eqnarray}
-\volt_{1} & = &  a_{f} \volt_{sky}[1+ (1-\Gamma_{f})\Gamma_{f}\Gamma_{d} \dfngexp \nonumber \\
-	&& + (1-\Gamma_{f})^{2} (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
-&&  ....+ (1-\Gamma_{f})^{n}(\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}] \nonumber
+\volt_{1} & = &  \bmvolt (1-\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber \\
+	&& + (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
+&&  ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}] \nonumber
 \end{eqnarray}
 and, 
-
 \begin{eqnarray}
-\volt_{2} & = &  a_{f} \volt_{sky}[1+ (1-\Gamma_{f})\Gamma_{f}\Gamma_{d} \dfngexp \nonumber\\
-&&+ (1-\Gamma_{f})^{2} (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
-&& ....+ (1-\Gamma_{f})^{n}(\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}] \ast \fngexp \nonumber
+\volt_{2} & = &  \bmvolt (1-\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber\\
+&&+  (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
+&& ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}] \ast \fngexp \nonumber
 \end{eqnarray}
-
 %\begin{eqnarray}
@@
 Frequency as well as angular dependence of the quantities are not written explicitly for notational simplicity.
-We also absorb the common gain term $(1-\Gamma_{f})$ with antenna field pattern $a$ and denote them as $a_{f}= a(1-\Gamma_{f})$ here after and define the antenna cross power pattern as $\beam_{f}(\thhat,\nu)=\bmvolt_{f}(\thhat,\nu)\bmvolt_{f}^{*}(\thhat,\nu)$ .
+We also absorb the common gain term $(1-\Gamma_{f})$ with antenna field pattern $a$ and denote them as $\bmvolt_{f}= \bmvolt(1-\Gamma_{f})$ here after.
+The cross power generated by $v_{1}$ and $v_{2}$ would have spurious visibility response due to mutual correlation between multiply reflected voltages.
+Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum.
+In the delay domain, visibility contributed by any two voltage components from two antennas with no mutual delay will be located at the delay $\tau = 0$ whereas any two voltage components from two antennas components having a mutual delay of $n\Delta \tau$ will be centred at $n\Delta \tau$.
+These will broaden the width of the delay spectrum which finally interferes with the 21cm power spectrum detection.
+Combining these terms, the expression of visibility will be,
 
-%\begin{eqnarray}
-%\vis(\vec b, \nu) & = & \int \volt_{1}\volt_{2}^{*} d\Omega \nonumber\\
-%		        & = & \int \beam_{f} \volt_{sky}|^{2} |\left [ 1+(1-\Gamma_{f}) \Gamma_{f} \Gamma_{d} \dfngexp  \right]|^{2} \fngexp  d\Omega
-%\label{eq4}		        
-%\end{eqnarray}
+\begin{eqnarray}\label{eqn:series1}
+\vis(\vec b, \nu) & = & \int \volt_{1}\volt_{2}^{*} d\Omega \nonumber\\
+			& = & \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp d\Omega
+\end{eqnarray}
 
- Furthermore, combining all the terms that contain instrument response we define a common instrument parameter, written as,
-
+where we define a combined common instrument parameter, written as, 
  \begin{eqnarray}
-\Sigma(\vec b, \nu) & = & a_{f}  [ 1+ 2 \Re [(1-\Gamma_{f}) \Gamma_{f}\Gamma_{d} \dfngexp \nonumber\\
-&& + (1-\Gamma_{f})^{2}(\Gamma_{f}\Gamma_{d})^2(\dfngexp)^{2}+ \nonumber\\
-&&  ....+(1-\Gamma_{f})^{n} (\Gamma_{f}\Gamma_{d})^{n}(\dfngexp)^{n} ] ]\\
-& = & { a_{f}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
+\Sigma(\vec b, \nu) & = & \beam_{f}  [ 1+  \Gamma_{f}\Gamma_{d} \dfngexp \nonumber\\
+&& + (\Gamma_{f}\Gamma_{d})^2(\dfngexp)^{2}+ \nonumber\\
+&&  ....+(\Gamma_{f}\Gamma_{d})^{n}(\dfngexp)^{n}  ]\\
+& = & \beam_{f}\displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
    \nonumber\\
@@
 \end{eqnarray}
-
- The respective visibility as well as the dealy spectrum would be, 
-\begin{equation}\label{eqn:series1}
-\vis(\vec b, \nu)  = \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp d\Omega
-\end{equation}
+where, $\beam_{f}=\bmvolt_{f}\bmvolt_{f}^{*}$ is the antenna cross power pattern.
+and the delay spectrum would be, 
 \begin{eqnarray}
@@
 
-Instrumental response function acquires additional terms arising due to correlation between the direct and reflected component of the sky signal.
+%Instrumental response function acquires additional terms arising due to correlation between the direct and reflected component of the sky signal.
 Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum.
-Fourier transform of the visibility contributed by any two voltage components from two antennas with no mutual delay will be located at the same delay $\tau = 0$ in the Fourier domain whereas any two voltage components from two antennas components having a mutual delay of $\Delta \tau$ will be centred at $\tau+\Delta \tau$.
+%Fourier transform of the visibility contributed by any two voltage components from two antennas with no mutual delay will be located at the same delay $\tau = 0$ in the Fourier domain whereas any two voltage components from two antennas components having a mutual delay of $\Delta \tau$ will be centred at $\tau+\Delta \tau$.
 This additional delay extends the upper limit on the maximum geometric delay $\tau_{g}$ to $(\tau_{g}+\Delta \tau)$.
@@
 {I_{meas} \over I_{sky} } & = & \Sigma(\vec b, \nu) \nonumber\\
-  & = & { a_{f}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}\fngexp]^{n}
+  & = & \beam_{f} \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}\fngexp]^{n}
    \nonumber\\
@@
 The vector network analyser transmits a broadband noise of known amplitude and phase via a $50ft$ cable up to the feed.
-While a part of this signal  is returns to the VNA post reflection from the feed due to mismatch between the cable and the antenna impedance resulting in the primary return loss, rest of the signal is radiated out by the antenna and illuminates the dish and radiated into the space.
+While a part of this signal  returns to the VNA post reflection from the feed due to mismatch between the cable and the antenna impedance resulting in the primary return loss, rest of the signal is radiated out by the antenna and illuminates the dish and radiated into the space.
 However, the reflected signal from the dish vertex returns to
@@
 
-If $I_{tr}$ is the signal transmitted by the VNA and $\Gamma_{f}$ is the feed reflection coefficient, $\Gamma_{f}$ fraction of this transmitted power would be reflected back to the VNA while $\(1-\Gamma_{f})$ fraction would be radiated.
-This radiated power will be reflected back and forth in between the feed and the dish with partial coupling of the signal into the feed at each reflection.
-If  $I_{r}$ is the
-is the total reflected power incident back on the feed after n reflection from the dish then the total reflected power, $I_{refl}$,
-back into the VNA would be:
+If $I_{tr}$ is the signal transmitted by the VNA and $\Gamma_{f}$ is the feed reflection coefficient, $\Gamma_{f}$ fraction of this transmitted power would be reflected back to the VNA while $(1-\Gamma_{f})$ fraction would be radiated.
+$\Gamma_{d}$ fraction of this radiated power will be reflected back and forth in between the feed and the dish with partial coupling of the signal into the feed at each reflection.
+The power radiated out of the feed, denoted by $I_{r}$ is ,
+\begin{equation}
+I_{r}= \beam_{f} I_{tr}
+\end{equation}
+
+The total reflected power, returned to the VNA, denoted byt $I_{ret}$ would be:
 \begin{eqnarray}\label{eqn:series2}
-I_{refl} & = &  I_{r}A_{f}[1+ \Gamma_{f}\Gamma_{d} \fngexp + (\Gamma_{f}\Gamma_{d})^2 (\fngexp)^{2}\nonumber\\
-&&+ ....+ (\Gamma_{f}\Gamma_{d})^{n}(\fngexp)^{2}]
+I_{ret} & = & \Gamma_{f}I_{tr}+ I_{r}(1-\Gamma_{f}) [\Gamma_{d} \fngexp + \Gamma_{f}\Gamma_{d}^{2} (\fngexp)^{2}\nonumber\\
+&&+ ....+ \Gamma_{f}^{(n-1)}\Gamma_{d})^{n}(\fngexp)^{n}]
 \end{eqnarray}
 
-Once again, we consider one reflection from the feed and its subsequent reflection from the dish as one reflection in total.
+%Once again, we consider one reflection from the feed and its subsequent reflection from the dish as one reflection in total.
 Equation \ref{eqn:series2} is similar to Equation \ref{eqn:series1}, with different incident powers.
 
-$I_{r}$ is the power that is incident back on the feed, which is just the feed radiated power reflected off the dish:
+%$I_{r}$ is the power that is incident back on the feed, which is just the feed radiated power reflected off the dish:
 
-\begin{equation}
-I_{r}= \Gamma_{d}(1-\Gamma_f)\fngexp I_{tr}
-\end{equation}
+%Hence the total returned power $P_{ret}$, to the VNA  would be:
 
-Hence the total returned power $P_{ret}$, to the VNA  would be:
+%\begin{eqnarray}
+%I_{ret} & = & \Gamma_{f}I_{tr} \nonumber\\ 
+ %&&  + \Gamma_{d}(1-\Gamma_f)\fngexp I_{tr}(1-\Gamma_{f}) [1+ \Gamma_{f}\Gamma_{d}\fngexp \nonumber\\
+%&& +  ....+ (\Gamma_{f}\Gamma_{d})^{n}(\fngexp)^{n}]\nonumber\\
+ %\end{eqnarray}
 
-\begin{eqnarray}
-I_{ret} & = & \Gamma_{f}I_{tr} \nonumber\\ 
- &&  + \Gamma_{d}(1-\Gamma_f)\fngexp I_{tr}(1-\Gamma_{f}) [1+ \Gamma_{f}\Gamma_{d}\fngexp \nonumber\\
-&& +  ....+ (\Gamma_{f}\Gamma_{d})^{n}(\fngexp)^{n}]\nonumber\\
- \end{eqnarray}
-
-Simplifying:
+Using the value of $I_{r}$ and simplifying:
 
@@
  {I_{ret} \over I_{tr} } & = & \Gamma_{f}
-  +  \Gamma_{d}(1-\Gamma_f)^{2} [e^{i\phi}+ \Gamma_{f}\Gamma_{d} e^{i2\phi}+  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{i n\phi}]\nonumber\\
-  & = & \Gamma_{f} + { (1-\Gamma_f)a_{f}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
+  +  \Gamma_{d}(1-\Gamma_f) \beam_{f} I_{tr} [e^{i\phi}+ \Gamma_{f}\Gamma_{d} e^{i2\phi}+  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{i n\phi}]\nonumber\\
+  & = & \Gamma_{f} + { (1-\Gamma_f)\beam_{f}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
  \label{eq9}

### 2016-02-15 DishReflectometry/Paper1_v1.tex
reorganized sections

@@
 &&  ....+(\Gamma_{f}\Gamma_{d})^{n}(\dfngexp)^{n}  ]\\
-& = & \beam_{f}\displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
+& = & \beam_{f}\displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
    \nonumber\\
@@
 \begin{eqnarray}
-\tilde I_{meas}(\vec b, \nu) & = & \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp d\Omega
+\tilde I_{meas}(\vec b, \nu) & = & \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \dfngexp d\Omega
 \end{eqnarray}
@@
 {I_{meas} \over I_{sky} } & = & \Sigma(\vec b, \nu) \nonumber\\
-  & = & \beam_{f} \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}\fngexp]^{n}
+  & = & \beam_{f} \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
    \nonumber\\
@@
 \begin{eqnarray}\label{eqn:series2}
-I_{ret} & = & \Gamma_{f}I_{tr}+ I_{r}(1-\Gamma_{f}) [\Gamma_{d} \fngexp + \Gamma_{f}\Gamma_{d}^{2} (\fngexp)^{2}\nonumber\\
-&&+ ....+ \Gamma_{f}^{(n-1)}\Gamma_{d})^{n}(\fngexp)^{n}]
+I_{ret} & = & \Gamma_{f}I_{tr}+ I_{r}(1-\Gamma_{f}) [\Gamma_{d} \dfngexp + \Gamma_{f}\Gamma_{d}^{2} (\dfngexp)^{2}\nonumber\\
+&&+ ....+ \Gamma_{f}^{n-1}\Gamma_{d})^{n}(\dfngexp)^{n}]
 \end{eqnarray}
-
-%Once again, we consider one reflection from the feed and its subsequent reflection from the dish as one reflection in total.
-Equation \ref{eqn:series2} is similar to Equation \ref{eqn:series1}, with different incident powers.
-
-%$I_{r}$ is the power that is incident back on the feed, which is just the feed radiated power reflected off the dish:
-
-%Hence the total returned power $P_{ret}$, to the VNA  would be:
-
-%\begin{eqnarray}
-%I_{ret} & = & \Gamma_{f}I_{tr} \nonumber\\ 
- %&&  + \Gamma_{d}(1-\Gamma_f)\fngexp I_{tr}(1-\Gamma_{f}) [1+ \Gamma_{f}\Gamma_{d}\fngexp \nonumber\\
-%&& +  ....+ (\Gamma_{f}\Gamma_{d})^{n}(\fngexp)^{n}]\nonumber\\
- %\end{eqnarray}
 
@@
  {I_{ret} \over I_{tr} } & = & \Gamma_{f}
-  +  \Gamma_{d}(1-\Gamma_f) \beam_{f} I_{tr} [e^{i\phi}+ \Gamma_{f}\Gamma_{d} e^{i2\phi}+  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{i n\phi}]\nonumber\\
+  +  \Gamma_{d}(1-\Gamma_f) \beam_{f} I_{tr} [e^{i\phi}+ \Gamma_{f}\Gamma_{d} e^{i2\phi}\nonumber\\ 
+  && +  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{i n\phi}]\nonumber\\
   & = & \Gamma_{f} + { (1-\Gamma_f)\beam_{f}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
@@
 
-The ratio in Equation \ref{eqn:ratio2} is the returned power to the VNA with
-respect to the transmitted power sent by the VNA. It is identical to the sky
-observation case in Equation \ref{eqn:ratio1} but differs by two factors. The
+The ratio in Equation \ref{eqn:ratio2} is identical to the ratio in the sky
+observation in Equation \ref{eqn:ratio1} except in two factors. The
 first factor corresponds to an additive amplitude difference arising from
 $\Gamma_{f}$, which physically accounts for the initial reflection at the feed.
-The second difference is a multiplicative term which informs us about the first
-reflection. Both of these terms need to be corrected for in order to relate our
-measurements to real observations.
-%Therefore, because our measurement is carried out in transmitting mode
-%while a sky observation would be carried out in receiving mode, we correct our
-%results in order to map them real observations.
+The second difference is the multiplicative ${ (1-\Gamma_f)\over \Gamma_{f} }$.
+Our measurement is corrected  for these two terms to map the instrument response measurements from transmission mode in which the measurement is taken to receiving mode in which the sky observation is done.
 
-The VNA measures the magnitude and phase of the quantity ${I_{ret}\over I_{tr}}$
-as a function of frequency as shown in Figure \ref{fig:freq}.
-The magnitude and phase of the complex return loss is measured between 50 to 500MHz over 1024 frequency channels which gives a frequency resolution of 0.44MHz.
-The delay resolution of the measurements is ?t = 2.22ns.
-In our measurement
-set-up, the first reflection occurs at the feed $\Gamma_{f}$, so
-$({I_{ret} \over I_{tr} }  - \Gamma_{f}) $ gives an estimate of the delay
-spectrum of the sky signal. In delay domain, the relative signal strength at
-zero delay represents the factor $\Gamma_{f}$ while the signal strength at any
-other delay represents any delayed signal that enters the feed after being
-reflected from the feed surroundings.
-
-%\section{Methodology}{\label{sec:methods}}
-
-%Our reflectometry measurements are made using a prototype HERA dish at NRAO in Green Bank, WV. The dish is a $14\,m$ diameter
-%parabolic reflector structurally supported with 3 telephone poles. The
-%reflective material is made up of wire mesh that is attached to PVC
-%pipes, forming the parabolic shape of the dish. With the current iteration of
-%the HERA dish, the feed consists of a PAPER dipole encased in a cylindrical cage
-%encompassing the backplane. The PAPER feed and the backplane (which is aimed at
-%preventing feed-to-feed interaction between neighboring dishes) is raised and
-%lowered by a three-pulley system. The focal height of the dish is $4.5m$
-%($\sim{14.76}$ft).
-
-%The heights measured in our experiment were made from
-%the balun to the top of the concrete hub. However, the focal height should be
-%measured from the backplane to point where the wire mesh would intersect the
-%concrete hub at the vertex of the dish. To account for this height discrepency,
-%we add 1.96 ft to all of our measured heights. These are the heights quoted in
-%the plots.[XXX not done yet but will be done]
-%Our measurements are made with a FieldFox in VNA mode. In this mode, a pulse
-%is generated in the FieldFox and sent through a $75ft$ $50\Omega$ cable that
-%connects to the feed with a 4:1 passive balun.
-The magnitude and phase of the complex return loss is measured between 50 to $500MHz$ over 1024 frequency channels which gives a frequency resolution of 0.44MHz.
-The delay resolution of the measurements is $\Delta{t}=2.22ns$.
-%In addition, we note that the round trip of a reflection from the feed to the dish
-%is $9m$, which corresponds to a delay of $30ns$.
-
-%Feed heights quoted in our measurements represent the distance from the balun to
-%the top of the central concrete hub. However, the actual focal height
-%of the dish represents the distance from the backplane of the feed to the dish's
-%wire mesh, which intersects the concrete hub between the ground and the top of
-%the hub. A 
-%XXX get discrepancy distance from DaveD. (1.7 ft from the bottom plate of
-%sandwich to the top of the the cage and .26 ft from the top of the concrete hub
-%to the middle where the parabola starts)
-
-%need to add in third : Antenna feed focal length 4.5 m which corresponds to a
-%signal propagation delay of 0.3 ns. Hence, subsequent reflections from the dish
-%vertex are expected to be at a delay which is integral multiple of 0.3 nS.
-\begin{figure*}
-\centering
-\includegraphics[totalheight=0.3\textheight]{plots/frequency_amp_phase_fullbw.png}
-\caption{Amplitude and phase of the measured return loss. Colored dashed lines
-mark three different frequency bands: $140-160MHz$ (typical power spectrum bandwidth),
-$100-200MHz$ (PAPER bandwidth), and
-$50-250MHz$ (HERA bandwidth).}
-\label{fig:freq}
-\end{figure*}
 %++++++++++++++++++++++++++++++++++++++++++++++++++++++
@@
 \section{Results}
+\begin{figure*}
+\centering
+\includegraphics[totalheight=0.3\textheight]{plots/frequency_amp_phase_fullbw.png}
+\caption{Amplitude and phase of the measured return loss. Colored dashed lines
+mark three different frequency bands: $140-160MHz$ (typical power spectrum bandwidth),
+$100-200MHz$ (PAPER bandwidth), and
+$50-250MHz$ (HERA bandwidth).}
+\label{fig:freq}
+\end{figure*}
 
-Figure \ref{fig:freq} shows the return loss for a frequency bandwidth of $50$ to
-$500MHz$, measured when the feed is suspended at the focal plane of the parabolic dish which is at $4.26m$ from the dish vertex. 
+Figure \ref{fig:freq} shows the return loss measured between $50$ to
+$500MHz$, measured when the feed is suspended at the focal plane of the parabolic dish which is at $5m$ from the dish vertex. 
 This measurement is Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{eq3}.
-%In Figure \ref{fig:3bands}, the return loss we measure is plotted versus delay
-%for three chosen bandwidths: the HERA bandwidth, the PAPER bandwidth, and a
-%typical power spectra bandwidth when using a Hamming window function. Two
-%additional measurements, using data taken in 2014 with the first prototype HERA
-%dish near Berkeley, CA, are also plotted using two different bandwidths. One of
-%the main differences between the Green Bank and Berkeley measurements is that
-%the feed was not encompassed in a cage for the Berkeley data (only a backplane). Additionally, the $50-1000MHz$ data taken in Berkeley was
-%Fourier-transformed internally by the measuring device, while the $100-200MHz$
-%data is analyzed post-measurement in the same way as the Green Bank data.
 
 The delay response of the instrument is dependent on the band chosen for the Fourier transform.
-%As one might expect, in regions where the feed return loss is low, reflections are minimized.  Thus, we cannot ignore that these measurements were performed
-%using a PAPER-style feed tuned for efficient operation over a $100-200MHz$ bandwidth. 
 The measurement bandwidth effects the amplitude and phase of the delay spectrum. Fourier transforms taken over wider bandwidth

### 2016-02-16 DishReflectometry/Paper1_v1.tex
Added figure 4,5 from new measurements and rewriting the result section

@@
-%\documentclass[12pt,preprint]{aastex}
-\documentclass[iop]{emulateapj}
+\documentclass[twocolumn]{emulateapj}
 \usepackage{float,amsmath}
-%\usepackage[margin=1in]{geometry}
-%\usepackage{titlesec} %used to format titles
-\usepackage{graphicx} %for handling figures
-%\usepackage[none]{hyphenat} %disallows hyphenated words
+\usepackage{graphicx}
+\usepackage{natbib}
+\usepackage{color}
+\usepackage{hyperref}
+\citestyle{aa}
+
 \newcommand{\vdag}{(v)^\dagger}
@@
 
-%\usepackage{cite}
-
-%\citestyle{aa}
 \shorttitle{HERA dish reflectometry }
@@
 
-\subsection{Visibility and delay spectrum computation considering multiple reflections}
+%\subsection{Visibility and delay spectrum computation considering multiple reflections}
 Upon first incidence of the sky signal $\volt_{sky}$, $\Gamma_{f}$ fraction of the voltage is reflected off the feed while $(1-\Gamma_{f})$ fraction is coupled to the feed.
@@
 \end{eqnarray}
-%\begin{eqnarray}
-%\volt_{1} & = & a \volt_{sky}(1-\Gamma_{f}) + a \volt_{sky} \Gamma_{f} \Gamma_{d} \dfngexp  (1-\Gamma_{f})^{2}\nonumber\\
-   %      & = & a \volt_{sky} (1-\Gamma_{f}) \left [ 1+ (1-\Gamma_{a})\Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau} \right]\nonumber
-%\end{eqnarray}
-%\begin{eqnarray}
-%\volt_{2} & = & \left [ a \volt_{sky}(1-\Gamma_{f}) + a \volt_{sky} \Gamma_{f} \Gamma_{d} \dfngexp (1-\Gamma_{f})^{2}\right ] \fngexp \nonumber\\
-   %      & = & a \volt_{sky} (1-\Gamma_{f}) \left [ 1+(1-\Gamma_{a}) \Gamma_{f} \Gamma_{d} \dfngexp  \right] \fngexp \nonumber
-%\end{eqnarray}
 Frequency as well as angular dependence of the quantities are not written explicitly for notational simplicity.
@@
 
-%\begin{eqnarray}
-%\Sigma(\vec b, \nu) & = & \bm_{f} |\left [ 1+ (1-\Gamma_{f}) \Gamma_{f} \Gamma_{d} e^{2\pi i\nu \Delta \tau} \right]|^{2}\nonumber\\
- %	    & = &  \bm_{f}  \left[ 1+ |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} + 2 \Re \left ( (1-\Gamma_{f})\Gamma_{f}\Gamma_{d} \dfngexp \right) \right] 
-%\label{eq{5}}	    
-%\end{eqnarray}
-
-%Instrumental response function acquires additional terms arising due to correlation between the direct and reflected component of the sky signal.
-Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum.
-%Fourier transform of the visibility contributed by any two voltage components from two antennas with no mutual delay will be located at the same delay $\tau = 0$ in the Fourier domain whereas any two voltage components from two antennas components having a mutual delay of $\Delta \tau$ will be centred at $\tau+\Delta \tau$.
-This additional delay extends the upper limit on the maximum geometric delay $\tau_{g}$ to $(\tau_{g}+\Delta \tau)$.
  Thus, the correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected.
-
- %If the dish vertex is so constructed such that the reflection from the dish vertex is negligible i.e, $\Gamma_{d}<<1\ or = 0$ then the second and the third term of the $\Sigma$ vanish.
-Also, the second term in the expression of $\Sigma(\vec b, \nu)$ is negligible compared to the first and the third term of the expression and, therefore, can be neglected.
 \\
-%===================================
-
 The design specification of HERA elements requires that any
@@
 Our goal is to measure the instrument response $\Sigma(\nu)$ and its effect on the power spectrum measurements.
-%%%%%%%%%%%%%%%
-\section{Measurements}
+%++++++++++++++++++++++++++++++++++++++++++++++++++++++
+\section{Reflectometry measurements}
 \begin{figure*}
@@
 \end{figure*}
-
 We carried out reflectometry measurements at the HERA element prototype in Green
@@
 The feed is raised and
-lowered by a three-pulley system mounted on the three poles. The focal height of the dish is $4.5m$
-($\sim{14.76}$ft).
-
-%As HERA progresses as an experiment, it is necessary to build optimised dishes that aim to minimise the
-%challenges of chromaticity in our quest for the Epoch of Reionization.
-
+lowered by a three-pulley system mounted on the three poles. The focal height of the dish is $5m$.  
 As given in the previous section, if the incident power from the sky signal is $I_{sky}$, the feed
@@
 \end{eqnarray}
-
-%where, $\Delta \tau$ is the roundtrip propagation delay of a frequency $\nu$ due to a reflection over the focal distance $l$.
 
@@
 %%%%%%%%%%%%%%%%%
-\subsection{Method}
+\subsection{Measurement equations}
 The instrument response kernel is measured by measuring the return loss of the HERA element at the output port of the feed using a vector network analyser.
@@
 %++++++++++++++++++++++++++++++++++++++++++++++++++++++
-
-\subsection{Estimation of the delay spectrum of the instrument}
-Frequency domain data, as shown in Figure \ref{fig:window}, is Fourier-transformed to compute the response of the system in the delay domain.
-The signal transmitted by the VNA is reflected first from the feed.
-In delay domain,  this appears at the zero delay bin.
-We subtract this value from the measured data and divide the the data by a factor $(1-\Gamma_{a})$ to derive the delay spectrum for the system operating in receiving mode during sky observation.
-%Because the measured data is band-limited between $50$ to $500MHz$, it is analogous to multiply the measured data by a square window function.
-%Then in delay domain, the response would be convolved with a $sinc$ function. This may result in excess power at high
-%delays due to the sidelobes of the $sinc$ function. Hence, appropriate windowing of the measured data set is necessary before taking the Fourier transform.
-%We have chosen a Hamming window for our analysis, and its effectiveness of this
-%window function compared to others is illustrated in Figure
-%\ref{fig:window}.
-
-As mentioned in Section \ref{sec:theory}, there is a mismatch in amplitude
-between the reflections that we measure (originating from the FieldFox pulse)
-and reflections produced by sky signal. The reflections that we measure (at high
-delays) must be lowered by a factor to represent weaker reflections that would
-occur after most of the sky signal is received by the feed. For our
-compensation, we multiply our entire delay spectrum by its DC component, which is the feed reflection coefficient $\Gamma_{f}$, and also divide by ($1-\Gamma_{f}$).
-In other words, these correction factors equate Equation \ref{eqn:ratio2} with Equation \ref{eqn:ratio1}.
-We note that this correction is only accurate at high delays where our
-reflections of interest occur. At low delays, our spectrum amplitude should be
-increased to represent the original sky signal, but we do not apply this
-correction because it is not relevant to our analysis.
-
-\begin{figure*}
+\section{Results}
+\begin{figure*}[ht]
 \begin{minipage}[b]{0.5\linewidth}
 \centering
-\includegraphics[width=\linewidth]{plots1/delayspectrum.png}
-\caption{Delay transform of the transfer function of the HERA element.
-The complex return loss of the element is measured between 50 to 400~MHz when the feed is kept at the focal plane of the dish at a focal height 4.5m.
-The delay spectrum is produced by taking the Fourier transform of the magnitude of the return loss measurement after limiting the measurements between 100 to 200~MHzusing Blackman-Harris window.
-The intersection of the horizontal and vertical dashed line shows the instrument performance specification as predicted by the theory of delay transform in order to detect the 21cm power spectrum.}
-\label{fig:window}
+\includegraphics[angle=0, width=\linewidth]{plots/s11_mag_fullband.png}
 \end{minipage}
+\hspace{0.1cm}
 \begin{minipage}[b]{0.5\linewidth}
 \centering
-\includegraphics[width=\linewidth]{plots1/delayspectrum_feed.png}
-\caption{Delay transform of the transfer function of the HERA feed element.
-The feed is kept on the ground downside up so that the entire radiation from the feed is radiated out.
-Once again, the measurement is done between 50 to 450 MHz and the delay spectrum is produced between $100-200$~MHz by using a Blackman-Harris window.
-The black dashed lines illustrate the instrument specification.}
-\label{fig:outofthedish}
+\includegraphics[angle=0, width=\linewidth]{plots/s11_ph_fullband.png}
 \end{minipage}
-\end{figure*}
-
-\section{Results}
-\begin{figure*}
-\centering
-\includegraphics[totalheight=0.3\textheight]{plots/frequency_amp_phase_fullbw.png}
-\caption{Amplitude and phase of the measured return loss. Colored dashed lines
-mark three different frequency bands: $140-160MHz$ (typical power spectrum bandwidth),
-$100-200MHz$ (PAPER bandwidth), and
-$50-250MHz$ (HERA bandwidth).}
+\caption{Left: Magnitude of the return loss of power measured in between 50 to 500 MHz using vector network analyser. Right panel shows the corresponding phase.}
 \label{fig:freq}       
@@
 Figure \ref{fig:freq} shows the return loss measured between $50$ to
-$500MHz$, measured when the feed is suspended at the focal plane of the parabolic dish which is at $5m$ from the dish vertex. 
+$500MHz$ when the feed is suspended at the focal plane of the parabolic dish which is at $5m$ from the dish vertex.
 This measurement is Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{eq3}.
+Measurement bandwidth is kept much larger than the bandwidth of operation to achieve higher delay resolution.
+
+\subsection{Estimation of the delay spectrum of the instrument}
+At first, the frequency domain data is Fourier-transformed to compute the response of the system in the delay domain.
+The signal transmitted by the VNA is reflected first from the feed.
+In delay domain, this appears at the zero delay bin.
+In a second iteration , we subtract this value from the measured data and divide the the data by a factor ${(1-\Gamma_{a})\over \Gamma_{f}}$ to map the delay spectrum of the system from transmitting mode to receiving mode during sky observation.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{plots/delay_spectrum_50_500_blackmanHarris.png}
+\caption{Delay spectrum of the HERA element computed by taking the Fourier transform of the measured return loss of power at the feed output.
+The complex return loss of the element is measured between 50 to 500~MHz when the feed is kept at the focal plane of the dish at a focal height 5m.}
+\label{fig:window}
+\end{figure}
+
+\subsubsection{Effect of dish and the feed on delay spectrum estimation}
+\subsubsection{Effect of feed height on delay spectrum estimation}
+\subsubsection{Effect of frequency bandwidth on delay spectrum estimation}
+\subsection{Comparison with PAPER antenna}
+\section{Comparison with simulations}
+\section{Effect of instrument delay spectrum on 21cm power spectrum measurements }
 

### 2016-02-17 DishReflectometry/Paper1_v1.tex
added section 5.1.1,5.1.2 and figure 5,6,7

@@
 In delay domain, this appears at the zero delay bin.
-In a second iteration , we subtract this value from the measured data and divide the the data by a factor ${(1-\Gamma_{a})\over \Gamma_{f}}$ to map the delay spectrum of the system from transmitting mode to receiving mode during sky observation.
+In a second iteration , we subtract this value from the measured data and divide the the data by a factor ${(1-\Gamma_{f})\over \Gamma_{f}}$ to map the delay spectrum of the system from transmitting mode to receiving mode during sky observation.
 
@@
 \centering
-\includegraphics[width=\linewidth]{plots/delay_spectrum_50_500_blackmanHarris.png}
+\includegraphics[width=\linewidth]{plots/delay_spectrum_100_200_blackman_Harris.png}
 \caption{Delay spectrum of the HERA element computed by taking the Fourier transform of the measured return loss of power at the feed output.
@@
 
+\subsubsection{Effect of antenna beam pattern and feed return loss on delay spectrum estimation}
+The return loss $\Gamma_{f}$ determines the amount of power coupled to the system via the feed antenna.
+Additionally, with each reflections, the power coupled to the system reduces by a factor of $\Gamma_{f}^{2}$.
+Since reflected signal results in system response in higher delay, mutiple reflections of the signal off the feed and the dish would result in an exponential envelope in the delay spectrum.
+The return loss of power results from the antenna impedance mismatch with the free space as well as the transmission line.
+The complex feed antenna impedance is shown in the figure \ref{fig:feed_impedance}.
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{plots/Feed_impedance.png}
+\caption{Complex antenna impedance of the HERA feed element.}
+\label{fig:feed_impedance}
+\end{figure} 
+While antenna beam pattern $A_{f}$ is a smooth function of frequency and should have its imprint confined to lower delays, the return loss $\Gamma_{f}$ broadens the delay spectrum.
+However, a smaller return loss will result in vertical shift of the delay spectrum at lower values and therefore can make the higher order reflections insignificant.
+Given the antenna impedance and the 50 Ohm transmission line the measurements are done using the passive balun with a 2:1 impedance ratio providing a net retrun loss of power between the sky, the antenna and the transmission line shown in the figure \ref{fig:freq}.
+This provides the maximum impedance matching.
+\\
+\subsubsection{Effect of frequency bandwidth on delay spectrum estimation}
+Estimation of the delay spectrum by taking the Fourier transform of the measured return loss is sensitive to the frequency bandwidth of operation.
+Since the measurements are done in the spectral domain, measurement between two frequencies is analogous to windowing the frequency domain data by a square window function.
+In the delay domain, Fourier transform of this would result in multiple side lobes at higher delays.
+Therefore, appropriate windowing of the data is  necessary prior to taking the Fourier transform of the measured data.
+Figure \ref{fig:window} shows the delay spectrum estimated from the measured data using a square window as well as Blackman Harris window.
+Windowing the data prior to Fourier transform significantlu reduces the system response higher delays.
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{plots/window.png}
+\caption{Effect of finite bandwidth on estimation of delay spectrum: Blue line shows the delay spectrum of the HERA element computed from the measured data which is band limited between 100 to 200MHz.
+Green line shows the delay spectrum estimated from the same data set after multiplying the data by a Blackman Harris window.
+The delay spectrum of the windowed data set shows significant reduction in the instrument response at higher delays.}
+\label{fig:window}
+\end{figure}
+
 \subsubsection{Effect of dish and the feed on delay spectrum estimation}
+The delay spectrum of the instrument is the combined response due to the dish and the feed reflections.
+Any additional reflections also contributes to the measured return loss and thus contributed to the delay spectrum at various delays.
+Figure \ref{fig:feed_only} shows the delay spectrum of the feed alone while the feed is kept upside down on the ground.
 \subsubsection{Effect of feed height on delay spectrum estimation}
-\subsubsection{Effect of frequency bandwidth on delay spectrum estimation}
 \subsection{Comparison with PAPER antenna}

### 2016-02-17 DishReflectometry/Paper1_v1.tex
added section 5.1.3 and continuing.

@@
 \subsubsection{Effect of dish and the feed on delay spectrum estimation}
-The delay spectrum of the instrument is the combined response due to the dish and the feed reflections.
+Measurement equations shows the effects of mutiple reflections of the sky signal between the feed and the dish.
+Any other reflections off the feed structure and/or any other part of the dish-feed assembly would appear at arbitrary delays.
+The estimated delay spectrum of the instrument is collectively contributed by all the reflections.
+We measure the return loss of the feed alone keeping it on the ground facing the sky shown in the Figure \ref{fig:freq}.
+Delay spectrum estimated from this measurement provides the lowest limit of the delay spectrum of the instrument considering there is no significant multiple reflections in between the feed and the dish.
  Any additional reflections also contributes to the measured return loss and thus contributed to the delay spectrum at various delays.

### 2016-02-19 DishReflectometry/Paper1_v1.tex
New plots

@@
 \email{Contact author email: nipanjana@berkeley.edu}
-\author{Zaki Ali\altaffilmark{1}, Carina Cheng\altaffilmark{1}, Dave DeBoer\altaffilmark{1}}
-\author{Gilbert Hsyu\altaffilmark{2}, Tsz Kuk Leung\altaffilmark{2}, Aaron Parsons\altaffilmark{1}}
+\author{Aaron Parsons\altaffilmark{1}, Dave DeBoer, Zaki Ali\altaffilmark{1}, Cherie Day\altaffilmark{1}, Carina Cheng\altaffilmark{1}}
+\author{Gilbert Hsyu\altaffilmark{2}, Tsz Kuk Leung\altaffilmark{2}}
 \altaffiltext{1}{University of California, Berkeley, nipanjana@berkeley.edu}
@@
 \centering
-\includegraphics[angle=0, width=\linewidth]{plots/s11_mag_fullband.png}
+\includegraphics[angle=0, width=\linewidth]{plots/s11_HERA_feed_PAPER_mag.png}
 \end{minipage}
@@
 \centering
-\includegraphics[angle=0, width=\linewidth]{plots/s11_ph_fullband.png}
+\includegraphics[angle=0, width=\linewidth]{plots/s11_HERA_feed_PAPER_ph.png}
 \end{minipage}
-\caption{Left: Magnitude of the return loss of power measured in between 50 to 500 MHz using vector network analyser. Right panel shows the corresponding phase.}
+\caption{Left: Magnitude of the return loss of power measured in between 100 to 200 MHz using vector network analyser.
+Right panel shows the corresponding phase.HERA feed design is derived from modified PAPER antenna and therefore the return loss closely relates to the PAPER antenna response with slight frequency shift.
+The return loss measured when the HERA feed is suspended over the dish is, however, show deviation from the feed performance.
+}
 \label{fig:freq}       
@@
 
-Figure \ref{fig:freq} shows the return loss measured between $50$ to
-$500MHz$ when the feed is suspended at the focal plane of the parabolic dish which is at $5m$ from the dish vertex.
+Figure \ref{fig:freq} shows the return loss measured between $100$ to
+$200MHz$ when the feed is suspended at the focal plane of the parabolic dish which is at $5m$ from the dish vertex.
 This measurement is Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{eq3}.
@@
 \centering
-\includegraphics[width=\linewidth]{plots/delay_spectrum_100_200_blackman_Harris.png}
-\caption{Delay spectrum of the HERA element computed by taking the Fourier transform of the measured return loss of power at the feed output.
-The complex return loss of the element is measured between 50 to 500~MHz when the feed is kept at the focal plane of the dish at a focal height 5m.}
-\label{fig:window}
+\includegraphics[width=\linewidth]{plots/delay_spectrum_100_200_BH.png}
+\caption{Delay spectrum of the HERA element, the PAPER element and the HERA feed estimated by taking the Fourier transform of the measured return loss of power at the feed output.
+HERA feed design is driven by the PAPER element with improved response at all delays.
+The feed, when suspended on the dish results in a more complex return loss and corresponding delay response is shown in the figure.}
+\label{fig:delay_spectrum}
 \end{figure}
@@
 \end{figure} 
-
 \subsubsection{Effect of dish and the feed on delay spectrum estimation}
-Measurement equations shows the effects of mutiple reflections of the sky signal between the feed and the dish.
+Measurement equations shows the effects of multiple reflections of the sky signal between the feed and the dish.
 Any other reflections off the feed structure and/or any other part of the dish-feed assembly would appear at arbitrary delays.
@@
 We measure the return loss of the feed alone keeping it on the ground facing the sky shown in the Figure \ref{fig:freq}.
-Delay spectrum estimated from this measurement provides the lowest limit of the delay spectrum of the instrument considering there is no significant multiple reflections in between the feed and the dish.
+Delay spectrum estimated from this measurement provides the lowest limit of the delay spectrum of the instrument considering there is no multiple reflections in between the feed and the dish.
  Any additional reflections also contributes to the measured return loss and thus contributed to the delay spectrum at various delays.
-Figure \ref{fig:feed_only} shows the delay spectrum of the feed alone while the feed is kept upside down on the ground.
-\subsubsection{Effect of feed height on delay spectrum estimation}
-\subsection{Comparison with PAPER antenna}
-\section{Comparison with simulations}
+Figure \ref{fig:delay_spectrum} shows the delay spectrum of the feed while it is kept upside down on the ground in green, as well as that of a HERA antenna with the feed suspended at the focal plane in blue.
+Red line shows shows the delay spectrum of the PAPER antenna in comparison with the HERA element.
+%\subsubsection{Effect of feed height on delay spectrum estimation}
+\subsubsection{Comparison of performance of HERA with PAPER}
+While PAPER has established the till date the most stringent upper limit on the 21cm power spectrum measurement, the need to increase the measurement sensitivity called for increased collecting area per PAPER antenna.
+This has driven to the parabolic reflector antenna based design of the PAPER successor HERA where essentially the PAPER antenna with minor modification of the ground plane-side plane assembly works as the feed and thus having larger collecting area per element.
+Figure \ref{fig:freq} shows the return loss measurement of power of the PAPER antenna and figure \ref{fig:delay_spectrum} shows (red line) the corresponding delay spectrum.
+The feed element shows improved delay response compared to the PAPER element across all delays $>50~ns$ with marginal improvement at delays $<50~ns$.
+The delay response of the HERA element degrades marginally as the feed is suspended over the dish due to multiple reflections between the feed and the dish.
+It is evident that majority of the response at lower delays are contributed due to the feed and its supporting structure at lower delays which is somewhat common to all three measurements.
+At the lower delays, the structures in the delay response remains unaltered even with the variation of the feed height relative to the dish vertex.
+It is essentially these structures set lower limits on the $k_{||}$ that could be probed and any redshift $z$ above the instrument footprint.
+
+\subsubsection{Comparison with simulations}
 \section{Effect of instrument delay spectrum on 21cm power spectrum measurements }
@@
 WRITE AGAIN}
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{plots1/delayspectrum_height.png}
-\caption{Delay transform of the transfer function of the HERA element keeping the feed at various heights.
-Delay transform is produced by taking the Fourier transform of the measurement using Blackman-Harris window.}
-\label{fig:elevator}
-\end{figure}
-\begin{figure}[H]
-\centering
-\includegraphics[width=\linewidth]{plots/delay_feed.png}
-\caption{Delay plots produced using a Hamming window function for different feed only configurations and the PAPER bandwidth ($100MHz-200MHz$).
-The black dashed lines illustrate our ``60 by 60" specification.}
-\label{fig:outofthedish}
-\end{figure}
 

### 2016-02-19 DishSimulations/memo/aarondefns.tex
Stuck in merge conflict  Please enter the commit message for your changes. Lines starting

\def\BCCP{$^2$}
\def\BCCPtxt{$^2$Berkeley Center for Cosmological Physics, University of California, Berkeley, Berkeley, California 94720, USA }

\def\ASU{$^7$}
\def\ASUtxt{$^7$Arizona State University, School of Earth and Space Exploration, Tempe, AZ 85287, USA}

\def\myemail{\altaffilmark{*}}
\def\myemailtxt{\altaffiltext{*}{aaronew@mit.edu}}

\def\UW{$^6$}
\def\UWtxt{$^6$University of Washington, Department of Physics, Seattle, WA 98195, USA}

\def\SKASA{$^8$}
\def\SKASAtxt{$^8$Square Kilometre Array South Africa (SKA SA), Park Road, Pinelands 7405, South Africa}

\def\RU{$^9$}
\def\RUtxt{$^9$Department of Physics and Electronics, Rhodes University, Grahamstown 6140, South Africa}

\def\CfA{$^3$}
\def\CfAtxt{$^3$Harvard-Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA}

\def\ANU{$^{10}$}
\def\ANUtxt{$^{10}$Australian National University, Research School of Astronomy and Astrophysics, Canberra, ACT 2611, Australia}

\def\CAASTRO{$^{11}$}
\def\CAASTROtxt{$^{11}$ARC Centre of Excellence for All-sky Astrophysics (CAASTRO)}

\def\Haystack{$^{12}$}
\def\Haystacktxt{$^{12}$MIT Haystack Observatory, Westford, MA 01886, USA}

\def\MIT{$^1$}
\def\MITtxt{$^1$MIT Kavli Institute for Astrophysics and Space Research, Cambridge, MA 02139, USA}

\def\Curtin{$^{13}$}
\def\Curtintxt{$^{13}$International Centre for Radio Astronomy Research, Curtin University, Perth, WA 6845, Australia}

\def\Victoria{$^{16}$}
\def\Victoriatxt{$^{16}$Victoria University of Wellington, School of Chemical \& Physical Sciences, Wellington 6140, New Zealand}

\def\UWisc{$^{17}$}
\def\UWisctxt{$^{17}$University of Wisconsin--Milwaukee, Department of Physics, Milwaukee, WI 53201, USA}

\def\UMichigan{$^{18}$}
\def\UMichigantxt{$^{18}$University of Michigan, Department of Atmospheric, Oceanic and Space Sciences, Ann Arbor, MI 48109, USA}

\def\UMelbourne{$^{19}$}
\def\UMelbournetxt{$^{19}$The University of Melbourne, School of Physics, Parkville, VIC 3010, Australia}

\def\USydney{$^{14}$}
\def\USydneytxt{$^{14}$The University of Sydney, Sydney Institute for Astronomy, School of Physics, NSW 2006, Australia}

\def\CASS{$^{20}$}
\def\CASStxt{$^{20}$CSIRO Astronomy and Space Science (CASS), PO Box 76, Epping, NSW 1710, Australia}

\def\Tata{$^{21}$}
\def\Tatatxt{$^{21}$National Centre for Radio Astrophysics, Tata Institute for Fundamental Research, Pune 411007, India}

\def\RRI{$^{22}$}
\def\RRItxt{$^{22}$Raman Research Institute, Bangalore 560080, India}

\def\NRAO{$^{23}$}
\def\NRAOtxt{$^{23}$National Radio Astronomy Observatory, Charlottesville and Greenbank, USA}

\def\UWA{$^{24}$}
\def\UWAtxt{$^{24}$International Centre for Radio Astronomy Research, University of Western Australia, Crawley, WA 6009, Australia}

\def\ASTRON{$^5$}
\def\ASTRONtxt{$^5$Netherlands Institute for Radio Astronomy (ASTRON), PO Box 2, 7990 AA Dwingeloo, The Netherlands}

\def\Dunlap{$^{15}$}
\def\Dunlaptxt{$^{15}$Dunlap Institute for Astronomy and Astrophysics, University of Toronto, ON M5S 3H4, Canada}

\def\SNS{$^4$}
\def\SNStxt{$^4$Scuola Normale Superiore, Piazza dei Cavalieri 7, I-56126 Pisa, Italy}

\newcommand{\dtb}{T_b}
\newcommand{\Mpci}{\text{ Mpc}^{-1}}
\newcommand{\Mpc}{\text{ Mpc}}
\newcommand{\MHz}{\text{ MHz}}
\newcommand{\GHz}{\text{ GHz}}
\newcommand{\mJy}{\text{ mJy}}
\newcommand{\muJy}{ \text{ } \mu \text{Jy}}
\newcommand{\nJy}{\text{ nJy}}
\newcommand{\Msun}{ M_{\odot}}
\newcommand{\ssection}{$\S$}
\newcommand{\erg}{\text{ erg}}
\newcommand{\second}{\text{ sec}}
\newcommand{\yr}{\text{ yr}}
\newcommand{\degree}{^{\circ}}
\newcommand{\kperp}{k_\perp}
\newcommand{\kpara}{k_\parallel}
\newcommand{\mto}{$\to$}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\trans}{\mathsf{T}}
\newcommand{\mK}{\text{ mK}}
\newcommand{\K}{\text{ K}}
\newcommand{\meter}{\text{ m}}
\newcommand{\km}{\text{km}}
\newcommand{\hfine}{21\,cm}

\def\Let@{\def\\{\notag\math@cr}}

### 2016-02-19 DishSimulations/paper/DishSimulationsPaper_v0.tex
Stuck in merge conflict  Please enter the commit message for your changes. Lines starting

@@
 \begin{equation}
-\widetilde{v}_i(t) = \int d \Omega \int d \tau \widetilde{r}_i({\bf \widehat{k}},\tau') \widetilde{s}({\bf \widehat{k}},t+\tau_i - \tau)
+\widetilde{v}_i(t) = \int d \Omega \int d \tau \widetilde{r}_i({\bf \widehat{k}},\tau) \widetilde{s}({\bf \widehat{k}},t- \tau_i - \tau)
 \end{equation}
@@
 \begin{equation}
-v_i(f) = \int d \Omega \int d \tau' \widetilde{r}_i({\bf \widehat{k}},\tau') s({\bf \widehat{k}},f)e^{2 \pi i f(\tau'-\tau_i)}
+v_i(f) = \int d \Omega \int d \tau \widetilde{r}_i({\bf \widehat{k}},\tau) s({\bf \widehat{k}},f)e^{-2 \pi i f(\tau_i+\tau)}
 \end{equation}
@@
 Rather, we employ CST's time domain mode to simulate the response of the dish to plane waves incident off of zenith to understand the frequency dependence of the side-lobes using the same technique that was described in \S~\ref{ssec:Deconvolve}.
-In Fig.~\ref{fig:Comparison}, we show the delay structure of the sidelobe response functions we obtain on a N-S line $20^\circ$ and $30^\circ$ from zenith, which approximately correspond to the sidelobes of the beam.
+In Fig.~\ref{fig:Sidelobes}, we show the delay structure of the sidelobe response functions we obtain on a N-S line $20^\circ$ and $30^\circ$ from zenith, which approximately corresponds to the first two nulls of the beam.
+Each response is normalized to the voltage response at zero delay and zenith.
+We see that at zero delay, the sidelobes are $\approx 20-25$\,dB down.
+However, at larger delays, $\approx 100$\,ns, the difference with the $20^\circ$ sidelobe is only $\approx 5-10$\,dB while the $30^\circ$ sidelobe maintains $\approx 15-20$\,dB separation with the zenith response.
+This behavior indicates that while the overall amplitude of the sidelobes is reduced at zero-delay, the enhanced frequency structure over the sidelobes can mitigate this advantage at high delays, leading for the brightness of sidelobe foregrounds, leaked at $\gtrsim 100$\,ns to appear just as bright as the leakage of foregrounds from zenith at $\gtrsim 100$\,ns.
 
-\section{The Effect of the HERA dish Chromaticity on Foreground Leakage and Sensitivity}\label{sec:Foregrounds}
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figures/compareSidelobesNormalized.pdf}
+\caption{The modulus square of the voltage responses of the HERA dish to plane waves incident from zenith (blue line) along with $20^\circ$,$25^\circ$, and $30^\circ$ off-zenith along the NS line.
+While the sidelobes are suppressed to $\approx 20-25$\,dB at zero delay, they come within $5$\,dB of the zenith response at longer delays which can lead to the level of leakage for a soruce in the sidelobes being comparable to the leakage of a source from zenith.
+The fact that the sidelobes occupy a much larger solid angle with only moderate supression at $\sim 100$\,ns coupled with their proximity to the horizon, suggests that they will dominate supra-horizon emission.}
+\end{figure}
+
+\section{The Effect of the HERA dish Chromaticity on Foreground Leakage and Sensitivity}
+Having a thorough understanding of how the chromatic beam of the HERA dish leaks foregrounds into higher delays and a decent picture of the relevant voltage response of the dish itself, we are now in a position to explore the impact of the Dish's performance on the leakage of foregrounds beyond the wedge, and into the EoR window.
+Beyond the delay kernels considered in this paper and \citep{Patra:2015}, the extent of leakage will depend both on the angular structure of the primary beam, which is established in \citep{Neben:2015b} and the model of the foregrounds themselves.
+In this section, we investigate the amplitude of foreground leakage as a function of delay given an angular primary beam model and two models of the delay structure of the dish: one in which the frequency structure is constant in all directions, and another in which we take into account the increased spectral structure that we observed in \S~\ref{ssec:Sidelobes}.
 
@@
 \end{figure}
+
+\subsection{The Impact of Delay-Rate Filtering.}
 

### 2016-02-19 DishSimulations/paper/DishSimulationsPaper_v6.tex

--- 2016-01-31 DishSimulations/paper/DishSimulationsPaper_v3.tex
@@
 \newcommand{\bx}{{\bf x}}
-\newcommand{\bl}{\boldsymbol{\ell}}
+\newcommand{\bl}{\widehat{\bf r}}
 \newcommand{\fts}{{\widetilde{s}}}
@@
 \usepackage{hyperref}
+\usepackage{comment}
 \citestyle{aa}
@@
 \begin{document}
-\title{The Hydrogen Epoch of Reionization Array Dish II: Characterization of Spectral Structure with Electromagnetic Simulations and their Science Implications}
+\title{The Hydrogen Epoch of Reionization Array Dish II: Characterization of Spectral Structure with Electromagnetic  Simulations and its science Implications.}
 \author{
-Ewall-Wice Aaron\altaffilmark{1,2},
+Aaron Ewall-Wice \altaffilmark{1,2},
 Richard Bradley\altaffilmark{3,4},
+David Deboer\altaffilmark{5},
+Jacqueline Hewitt\altaffilmark{1,2},
+Aaron Parsons\altaffilmark{5},
+James Aguirre\altaffilmark{6},
+Zaki S. Ali\altaffilmark{5},
+Carina Cheng\altaffilmark{5},
 Abraham Neben\altaffilmark{1,2},
 Nipanjana Patra\altaffilmark{5},
-Nithyanandan Thyagarajan \altaffilmark{6},
-Jacqueline Hewitt\altaffilmark{1,2},
-Zaki S. Ali\altaffilmark{5},
+Nithyanandan Thyagarajan \altaffilmark{7},
+Mariet Venter\altaffilmark{8},
 Judd Bowman\altaffilmark{6},
-Carina Cheng\altaffilmark{5},
-David Deboer\altaffilmark{5},
-Aaron Parsons\altaffilmark{5},
-Mariet Venter\altaffilmark{7}
-and others.
+Eloy de Lera Acedo\altaffilmark{9},
+Roger Dickenson\altaffilmark{3},
+Phillip Doolittle\altaffilmark{3},
+Dennis Egan\altaffilmark{3},
+Mike Hedrick\altaffilmark{3},
+Saul Kohn\altaffilmark{6},
+Patrick Schaffner\altaffilmark{3},
+John Shelton\altaffilmark{3},
+Benjamin Saliwanchik\altaffilmark{10},
+Max Tegmark\altaffilmark{1,2}
+H.A. Taylor\altaffilmark{3},
+Rusty Taylor\altaffilmark{3},
+Butch Wirt\altaffilmark{3},
 }
@@
 \altaffiltext{5}{Astronomy Dept. U. California, Berkeley CA}
-\altaffiltext{6}{School of Earth and Space Exploration, Arizona State U.,
-\altaffiltext{7}{Stellenbosh}
-Tempe AZ}
+\altaffiltext{6}{Dept. of Physics and Astronomy, University of Pennsylvania, Philidelphia, PA}
+\altaffiltext{7}{School of Earth and Space Exploration, Arizona State U.Tempe AZ}
+\altaffiltext{8}{Cavendish Laboratory, University of Cambridge, Cambridge, UK}
+\altaffiltext{9}{SKA South Africa, Cape Town, SA}
+\altaffiltext{10}{University of KwaZulu-Natal, Durban, SA}
 \begin{abstract}
-We use time domain electromagnetic simulations to assess the spectral characteristics of the antenna element for the Hydrogen Epoch of Reionization Array (HERA).
-These simulations are part of a multi-faceted campaign to determine whether the dish's design is suitable for obtaining a detection of redshifted 21\,cm emission from the Epoch of Reionization.
-Our simulations show the existence of standing wave reflections in some regions of the 100-200\,MHz bandpass with an amplitude of $\approx -35$\,dB at 100\,ns which can lead to some loss of measurable modes and a modest reduction in sensitivity over a small segment of the band.
-We find that the spectral response of the dish is sufficiently smooth for proven foreground isolation methods such as delay filtering to contain foreground emission at line of sight wave numbers below $k_\parallel = 0.15-0.23$\,$h$Mpc$^{-1}$.
-Incorporating these results into a Fisher Matrix analysis, we find that the spectral structure observed in our simulations has only a small effect on the overall constraints on the astrophysics of reionization that HERA will achieve, allowing it to serve as a benchmark for the design of future instruments such as the Square Kilometer Array.
+We use time domain electromagnetic simulations to assess the spectral characteristics of the dish antenna for the Hydrogen Epoch of Reionization Array (HERA).
+These simulations are part of a multi-faceted campaign to determine whether the dish design is suitable for obtaining a detection of redshifted 21\,cm emission from the Epoch of Reionization.
+Our simulations show the existence of reflections in some regions of the 100-200\,MHz bandpass with an amplitude of $\approx -35$\,dB at 100\,ns which can lead to some loss of measurable modes and a modest reduction in sensitivity.
+Even in the presence of this structure, we find that the spectral response of the dish is sufficiently smooth for proven foreground isolation methods such as delay filtering to contain foreground emission at line of sight wave numbers below $k_\parallel = 0.15-0.23$\,$h$Mpc$^{-1}$.
+Incorporating these results into a Fisher Matrix analysis, we find that the spectral structure observed in our simulations has only a small effect on the overall constraints on the astrophysics of reionization that HERA will achieve, allowing it to serve as a benchmark for the design of future instruments.%such as the Square Kilometer Array.
 \end{abstract}
 \section{Introduction}
-Observations of the redshift 21\,cm radiation from neutral hydrogen in the intergalactic medium (IGM) have the potential to illuminate the hitherto unobserved {\it dark ages} and {\it cosmic dawn}, revolutionizing our understanding of the first UV and X-ray sources in the universe and how their properties influenced galactic evolution (see \citet{Furlanetto:2006Review}, \citet{Morales:2010}, and \citet{Pritchard:2012} for reviews).
-Two major experimental endeavors are underway to make a first detection of the 21\,cm signal with most focusing on the Epoch of Reionization (EoR) in which UV photons from early galaxies transformed the hydrogen in the universe from neutral to ionized.
+Observations of the redshifted 21\,cm radiation from neutral hydrogen in the intergalactic medium (IGM) have the potential to illuminate the hitherto unobserved {\it dark ages} and {\it cosmic dawn}, revolutionizing our understanding of the first UV and X-ray sources in the universe and how their properties influenced galactic evolution (see \citet{Furlanetto:2006Review}, \citet{Morales:2010}, and \citet{Pritchard:2012} for reviews).
+Two major experimental endeavors are underway to detect the 21\,cm signal, with most focusing on the Epoch of Reionization (EoR) in which UV photons from early galaxies transformed the hydrogen in the universe from neutral to ionized.
 The first involves measuring the sky-averaged global signal and is being pursued by experiments such as EDGES \citep{Bowman:2010}, LEDA \citep{Greenhill:2012,Bernardi:2015}, DARE \citep{Burns:2012}, SciHi \citep{Voytek:2014}, and BIGHORNS \citep{Sokolowski:2015} either in their planning stages or already taking data.
@@
 A first generation of such experiments are currently taking data in an attempt to make a first statistical detection of the power spectrum of 21\,cm brightness temperature fluctuations.
-These include the Giant Metrewave Telescope (GMRT)  \citep{Paciga:2013}, the Low Frequency ARray (LOFAR), \citep{VanHaarlem:2013}, the Murchison Widefield Array \citep{Tingay:2013a} and the Precision Array for Probing the Epoch of Reionization (PAPER) \citep{Parsons:2010}.
-Already, these experiments are beginning to yield upper limits on the 21\,cm signal \citep{Dillon:2013,Parsons:2014,Jacobs:2015,Dillon:2015,EwallWice:2015a} and significant scientific results.
+These include the Giant Metrewave Telescope (GMRT)  \citep{Paciga:2013}, the Low Frequency ARray (LOFAR), \citep{VanHaarlem:2013}, the Murchison Widefield Array \citep{Tingay:2013a}, the MIT Epoch of Reionization Experiment (MITEoR) \citep{Zheng:2013}, and the Precision Array for Probing the Epoch of Reionization (PAPER) \citep{Parsons:2010}.
+Already, many of these experiments are beginning to yield upper limits on the 21\,cm signal \citep{Dillon:2013,Parsons:2014,Jacobs:2015,Dillon:2015} and significant scientific results.
 The most stringent measurement of $\approx 500$\,mK$^2$ \citep{Ali:2015} is able to rule out number of scenarios in which the intergalactic medium received little or no heating from X-rays \citep{Pober:2015,Greig:2015b}.
 
-The primary obstacle to obtaining a high redshift detection of the cosmological signal through both of these methods is the existence of foregrounds that are $\sim 10^5-10^6$ times brighter.
+The primary challenge to obtaining a high redshift detection of the cosmological signal through both of these methods is the existence of foregrounds that are $\sim 10^5-10^6$ times brighter \citep{Bernardi:2009,Pober:2013a,Dillon:2014}.
 While requiring much greater sensitivity than global-signal experiments, interferometers have the advantage that spectrally smooth foregrounds are naturally contained to a finite region of Fourier space, corresponding to large line of sight scales, known as the {\it wedge} \citep{Datta:2010,Vedantham:2012,Parsons:2012,Thyagarajan:2013,Liu:2014a,Liu:2014b}.
-However any structure in the frequency response of the instrument is imprinted on the foregrounds and has the potential to leak power into the {\it EoR window} at small line of sight scales, masking the signal.
-Indeed, sub-percent spectral features in the analogue and digital signal chains on the initial build-out of the MWA are proving to be a significant obstacle \citep{Dillon:2015b,EwallWice:2015a,Beardsley:2015b}.
+Since the location of each foreground on the sky determines its position in the wedge, with sources near the horizon being introduced at line of sight scales closest to the {\it EoR window}, the angular response of an instruments beam pattern has significant implications on the amount of side-lobe power that is leaked into the EoR window \citep{Thyagarajan:2015a,Thyagarajan:2015b,Pober:2016}.
 
-While, in principle, spectral structure in the bandpass of the instrument may be removed in calibration, simulations show that any mismodeling of emission and the primary beam, potentially below the confusion limit, will mix the significant spectral structure introduced by the wedge on long baselines into short ones, masking the signal entirely \citep{Barry:2016}.
-While redundant calibration \citep{Wieringa:1992,Liu:2010,Zheng:2014} is able to solve for gains that are primarily independent of a detailed model of the sky, it is unclear how one might remove direction-dependent chromatic structure that might be present in the primary beam of the instrument without deferring to a model.
-Because of our limited knowledge of foregrounds at low frequency and the fidelity of calibration algorithms, it is imperitive to design experiments whose spectral structure is contained, as much as possible, to low delays.
+Beyond leakage from wedge side-lobes, any structure in the frequency response of the instrument is imprinted on the foregrounds and has the potential to leak power into the EoR window at small line of sight scales, masking the signal.
+Indeed, sub-percent spectral features in the analogue and digital signal chains on the initial build-out of the MWA are proving to be a significant calibration challenge \citep{Dillon:2015b,EwallWice:2015a,Beardsley:2015b}.
 
-The Hydrogen Epoch of Reionization Array (HERA) is a next generation 21\,cm experiment designed to achieve a two-orders of magnitude improvement in sensitivity over current experiments which will allow it to make a robust detection of the 21\,cm power spectrum during the EoR \citep{Pober:2014}.
+While, in principle, spectral structure in the bandpass of the instrument may be removed in calibration, it is being investigated whether any mismodeling of emission and the primary beam will mix the significant spectral structure introduced by the wedge on long baselines into short ones, masking the signal entirely \citep{Barry:2016}.
+While redundant calibration \citep{Wieringa:1992,Liu:2010,Zheng:2014} is able to solve for gains that are primarily independent of a detailed model of the sky, antenna elements with significant direction dependent chromaticity that varies from element to element might break the assumptions of redundancy that such calibration relies upon and pose a significant obstacle.
+Because of our limited knowledge of foregrounds at low frequency and the fidelity of calibration algorithms, it is imperative to design experiments whose band-passes are as devoid of spectral structure as possible.
+
+Drawing off of the lessons of the PAPER, MWA, and MITEoR experiments, the Hydrogen Epoch of Reionization Array (HERA) \citep{Pober:2014,DeBoer:2016} is a next generation 21\,cm experiment designed to achieve a two-orders of magnitude improvement in sensitivity over current experiments which will allow it to make a robust detection of the 21\,cm power spectrum during the EoR.
 Much of this sensitivity increase is enabled by moving the collecting area of the instrument into baselines that are located primarily inside of the EoR window and a switch from PAPER's skirted dipoles and the MWA's phased dipole arrays to an antenna element that consists of a feed suspended over a large reflecting parabolic dish.
-A central requirement for HERA's dish design is that the antenna have a response that is sufficiently smooth in frequency and centralized enough in its angular response that it leaves the EoR window free of contamination.
+A central requirement for HERA's dish design is that the antenna have a response that is sufficiently smooth in frequency and centralized enough in its angular response that it leaves the EoR window free of the side-lobe contamination observed in \citep{Thyagarajan:2015a,Thyagarajan:2015b,Pober:2016}.
+Central to increasing the collecting area of each element on HERA is a switch from dipoles (used by the MWA and PAPER) to feeds suspended over large 14\,m diameter parabolic dishes.
+In Fig.~\ref{fig:AntennaCompare} we show one of the initial 19 dishes currently being deployed in South Africa at the same site as PAPER whose antenna we also show at the top of the figure.
+
+\begin{figure}
+\includegraphics[width=.5\textwidth]{figures/PAPER_HERA_compare.jpg}
+\caption{The HERA antenna element (bottom) uses a parabolic dish to achieve an order of magnitude increase in collecting area over the PAPER antenna (top).
+The sleeved dipole in the center of the PAPER backplane is identical to the sleeved dipole being suspended under the cylindrical skirt over the vertex of the HERA dish.
+The suspended feed arrangement has the potential to introduce intra-antenna reflections which we explore in this work.}
+\label{fig:AntennaCompare}
+\end{figure}
 
 This paper and its companions \citep{Neben:2016,Patra:2016,Thyagarajan:2016} describe a multi-pronged campaign to assess whether the HERA dish meets the requirements for isolating foregrounds within the wedge and leaving the EoR window clean.
-We accomplish this by establishing a spec with simulations of foregrounds \citep{Thyagarajan:2016} and verifying that HERA primary antenna element meets this spec with reflectometry \citep{Patra:2016} and ORBCOMM beam mapping \citep{Neben:2016}.
+We accomplish this by establishing antenna specifications with simulations of foregrounds \citep{Thyagarajan:2016} and verifying that the HERA primary antenna element meets these specifications with reflectometry \citep{Patra:2016} and ORBCOMM beam mapping \citep{Neben:2016}.
 In this work, we present the results of time-domain electromagnetic simulations that are intended to predict the degree of spectral structure in the HERA dish, assess the impact of this spectral structure on the leakage of foregrounds into the EoR window, and to verify the reflectometry measurements taken in the field.
@@
 In \S~\ref{sec:Results} we describe the results and verify our simulation framework by comparing its prediction of the $S_{11}$ parameter of the HERA dish to direct field measurements described in \citep{Patra:2016}.
-In \S~\ref{sec:Sensitivity} we apply our electromagnetic simulation results to a foreground model to determine the extent that the HERA dish's chromatic structure pollutes the EoR window and their impact on HERA's ability to constrain reionization parameters.
-We conclude in \S~\ref{sec:Conclusion}.
+In \S~\ref{sec:Sensitivity} we apply our electromagnetic simulation results to a foreground model to determine the extent that the HERA dish's chromatic structure pollutes the EoR window and the impact on HERA's ability to constrain reionization parameters.
+We summarize our conclusions in \S~\ref{sec:Conclusion}.
 
@@
 Any sinusoidal frequency structure introduced by the reflections will cause these foregrounds to mimic and swamp the signal unless they are brought below a level similar to the ratio between the foregrounds and the signal itself.
-A simple equation describing effect of direction independent reflections in the signal chain downstream of the feed, has been derived in \citet{EwallWice:2015a}.
+A simple equation describing the effect of direction independent reflections in the signal chain downstream of the feed has been derived in \citet{EwallWice:2015a}.
 We now extend this analysis by considering the direction dependent reflections that can occur within the antenna element.
-We start denote the electric field of radiation arriving from direction ${\bf \ell}$ at the $i^{th}$ antenna element at position $\bx_i$ and time $t_i = t + \bl \cdot \bx_i /c \equiv t+\tau_i$ as $\fts(\bl,\bx_i,t_i)$.
+We start by denoting the electric field of radiation arriving from direction ${\bf \ell}$ at the $i^{th}$ antenna element at position $\bx_i$ and time $t_i = t + \bl \cdot \bx_i /c \equiv t+\tau_i$ as $\fts(\bl,\bx_i,t_i)$.
 
@@
 The voltage signal measured at the $i^{th}$ antenna element, $\widetilde{v}_i$, is the integral over solid angle of the electric fields arriving from all directions.
-The presence of the reflections introduces a convolution of the electric field entering the antenna (delayed by $\tau_i$) with $\ftr_i(\bl,\tau)$.
+The presence of reflections introduces a convolution of the electric field entering the antenna (delayed by $\tau_i$) with $\ftr_i(\bl,\tau)$:
 
 \begin{equation}\label{eq:Voltage}
-\ftv_i(t) = \int d \Omega \int d \tau \ftr_i(\bl,\tau) \fts(\bl,t+ \tau_i - \tau)
+\ftv_i(t) = \int d \Omega \int d \tau \ftr_i(\bl,\tau) \fts(\bl,t- \tau_i - \tau).
+\end{equation}
+Applying the Fourier convolution theorem, the Fourier transform of this equation gives $v_i(\omega)$ as the simple angular integral of the product of $s_i(\bl,\omega)$ and $r_i(\bl,\omega)$, where $\omega=$ is the angular frequency of electromagnetic radiation.
+\begin{equation}
+v_i(\omega) = \int d \Omega  r_i(\bl,\omega) s(\bl,\omega) e^{-i \omega \tau_i}.
 \end{equation}
@@
 The correlator of a radio interferometer records the time-averaged product of the Fourier transfored voltage streams of the $i^{th}$ and $j^{th}$ antennas. 
+\begin{comment}
 Fourier transforming the voltage stream from the $i^{th}$ antenna we obtain
 \begin{equation}
-v_i(f) = \int d \Omega \int d \tau \ftr_i(\bl,\tau) s(\bl,f)e^{-2 \pi i f(\tau_i+\tau)}
+v_i(\omega) = \int d \Omega \int d \tau \ftr_i(\bl,\tau) s(\bl,\omega)e^{-i \omega (\tau_i+\tau)}.
 \end{equation}
-The time averaged product between the two antennas is
-\begin{align}
-V_{ij}'(f) &= \left \langle v_i(f) v_j^*(f) \right \rangle_t \nonumber \\
- &= \int d \Omega d \tau d \tau' \ftr_i(\bl,\tau) \ftr^*_j(\bl,\tau')e^{-2 \pi i f (\tau-\tau') } I(\bl, f) e^{- 2 \pi i \Delta \tau_{ij}f} 
+\end{comment}
+The time averaged product of the Fourier transform between the two antennas is
+\begin{align}\label{eq:Visibility}
+V_{ij}'(\omega) &= \left \langle v_i(\omega) v_j^*(\omega) \right \rangle_t \nonumber \\
+ &= \int d \Omega r_i(\bl,\omega) r_j^*(\bl,\omega) I(\bl, \omega) e^{- i\omega\Delta \tau_{ij}} \nonumber \\
+ & = \int d \Omega r_i(\bl,\omega) r^*_j(\bl,\omega)  I(\bl,\omega)e^{-i\omega \bb_{ij} \cdot \bl/c},
 \end{align}
-where $\Delta \tau_{ij} = \tau_i-\tau_j = (\bx_i-\bx_j) \cdot \bl/c$ and $I(\bl,f)=\left \langle |s(f,\bl)|^2 \right \rangle_t$.
+where $\Delta \tau_{ij} = \tau_i-\tau_j = (\bx_i-\bx_j) \cdot \bl/c$, $I(\bl,\omega)=\left \langle |s(\bl,\omega)|^2 \right \rangle_t$, and $\bb_{ij} = (\bx_i-\bx_j)$.
 Here, we have invoked the fact that electromagnetic waves arriving from different directions are incoherent.
-
-Defining $\bu_{ij} = f (\bx_i-\bx_j)/c$ and performing the $\tau$ and $\tau'$ Fourier transforms, we arrive at
-\begin{equation}\label{eq:Visibility}
-V'_{ij}(f) =  \int d \Omega r_i(\bl,f) r^*_j(\bl,f)  I(\bl,f)e^{2 \pi i f \bu_{ij} \cdot \bl/c},
-\end{equation}
-where ${\bf b}_{ij} = ({\bf x}_i - {\bf x}_j )$ and $r_i(\bl,f)$ is the inverse fourier transform of the reflection response of the dish.
-From equation~\ref{eq:Visibility} we see that $r_i(\bl,f)$ is precisely the voltage beam of the antenna.
+This equation leaves us with the familiar interferometry equation \citep{Thompson:1986}, allowing us to see that $r_i(\bl,\omega)$ equivalent to the voltage beam of the antenna.
 Setting a specification on reflections is hence equivalent to setting a specification on the spectral smoothness of the antenna's voltage beam.
@@
 \begin{equation}
-\widetilde{V}_{ij}(\tau) = \int d f e^{2 \pi i \tau f} V_{ij}(f).
+\widetilde{V}_{ij}(\tau) = \frac{1}{2 \pi} \int d \omega V_{ij}(\omega) e^{i \omega \tau }.
 \end{equation}
@@
 \begin{equation}
-\widetilde{V}'_{ij}(\tau)=  \int d \Omega \int d f  r_i(\bl,f) r_j^*(\bl,f)  I(\bl,f) e^{2 \pi i f ( \bb_{ij} \cdot \bl /c - \tau)}
+\widetilde{V}_{ij}(\tau)= \frac{1}{2\pi} \int d \Omega \int d \omega r_i(\bl,\omega) r_j^*(\bl,\omega)  I(\bl,\omega) e^{-i \omega ( \bb_{ij} \cdot \bl /c - \tau)}.
 \end{equation}
@@
 We see that each source located at $\bl$ on the sky is mapped to a line $\tau =\bb_{ij}\cdot \bl/c$, resulting in the much discussed ``wedge" \citep{Datta:2010,Vedantham:2012,Parsons:2012,Morales:2012,Thyagarajan:2013,Liu:2014a,Liu:2014b}.
-The presence of the frequency dependent beam causes each source line to be convolved in delay with the direction dependent kernel
+The presence of the frequency dependent beam causes each source line to be convolved in delay with the direction dependent kernel,
 \begin{equation}\label{eq:Kernel}
-\ftR_{ij}(\bl,\tau) = \int d \tau \ftr_i(\bl,\tau - \Delta \tau) \ftr^*_j(\bl,-\Delta \tau).
+\ftR_{ij}(\bl,\tau) = \int d  \tau' \ftr_i(\bl,\tau - \tau') \ftr^*_j(\bl,-\tau'),
 \end{equation}
@@
 We demonstrate the effect of foreground smearing in Fig.~\ref{fig:Smearing} for a simple model with only three sources.
-Without reflections, the sources would form lines in $b-\tau$ space.
+Without reflections, the sources would form lines intersecting zero in the two dimensional space with the baseline length, $b$ on the x-axis and the delay, $\tau$ on the y-axis.
 With the reflections, the sources are smeared out, leading to supra-horizon emission.
@@
 Right: the presence of chromaticity due to reflections in the antenna smears the source in delay with the kernel given by equation~\ref{eq:Kernel}.
-Since the frequency response of the dish are a function of direction on the sky, the shape of the delay kernel is different for each source line.
+Since the frequency response of the dish is a function of direction on the sky, the shape of the delay kernel is different for each source line.
 We see that this smearing can lead to substantial supra-horizon emission.}
@@
 \begin{equation}
-\widetilde{V}_{ij}'(\tau) = \int d\tau' \int d \tau'' \widetilde{g}_i(\tau' - \tau'')\widetilde{g}^*_j(\tau'') \widetilde{V}_{ij}(\tau-\tau')
+\widetilde{V}_{ij}(\tau) = \int d\tau' \int d \tau'' \widetilde{g}_i(\tau' - \tau'')\widetilde{g}^*_j(-\tau'') \widetilde{V}_{ij}^a(\tau-\tau'),
 \end{equation}
-where $V_{ij}$ is the visibility for the achromatic voltage pattern, $a_i(\bl)$. 
+where $V_{ij}^a$ is the visibility for the achromatic voltage pattern, $a_i(\bl)$. 
 We can gain further insight into the behavior of the delay kernel arising from chromaticity by assuming that $\widetilde{g}_i(\tau=0)\gg\widetilde{g}_i(\tau>0)$, which should be the case at large delays for the smooth bandpasses our instruments are designed to have.
 \begin{align}\label{eq:KernelApprox}
-\widetilde{V}_{ij}'(\tau) &\approx \widetilde{g}_i(0)\int d \tau' \widetilde{g}_j^*(\tau')\widetilde{V}_{ij}(\tau- \tau') \nonumber \\
-& + \widetilde{g}_j^*(0) \int d \tau' \widetilde{g}_i(\tau')\widetilde{V}_{ij}(\tau-\tau') 
+\widetilde{V}_{ij}(\tau) &\approx \widetilde{g}_i(0)\int d \tau' \widetilde{g}_j^*(-\tau')\widetilde{V}^a_{ij}(\tau- \tau') \nonumber \\
+& + \widetilde{g}_j^*(0) \int d \tau' \widetilde{g}_i(\tau')\widetilde{V}^a_{ij}(\tau-\tau').
 \end{align}
@@
 \section{Electromagnetic Simulations of the HERA dish element}\label{sec:Simulations}
-
-HERA \citep{Pober:2014,DeBoer:2016} is an instrument designed to detect the power spectrum of 21\,cm brightness temperature fluctuations during the EoR at high signal-to-noise between the frequencies of 100 and 200\,MHz (redshifts 6 to 12).
+%HERA \citep{Pober:2014,DeBoer:2016} is an instrument designed to detect the power spectrum of 21\,cm brightness temperature fluctuations during the EoR at high signal-to-noise between the frequencies of 100 and 200\,MHz (redshifts 6 to 12).
 Its initial, 19-element, buildout is currently taking first observations in the Karoo in South Africa.
@@
 It achieves this by increasing the number of correlated inputs by only a factor of $\approx 2$ while increasing the total collecting area of each correlated element by over an order of magnitude and arranging the elements in such a way as to maximize the number of short baselines that are located outside of the foreground wedge.
-Central to increasing the collecting area of each element is a switch from dipoles (used by the MWA and PAPER) to feeds suspended over large 14\,m diameter parabolic dishes.
-In Fig.~\ref{fig:AntennaCompare} we show one of the initial 19 dishes currently being deployed in South Africa at the same site as PAPER whose antenna we also show at the top of the figure.
 
@@
 In this section, we describe the setup and parameters of our simulations (\S~\ref{ssec:Simulations}), and how we extract the voltage response function of the dish (\S~\ref{ssec:Deconvolve}).
-
-\begin{figure}
-\includegraphics[width=.5\textwidth]{figures/PAPER_HERA_compare.jpg}
-\caption{The HERA antenna element (bottom) uses a parabolic dish to achieve an order of magnitude increase in collecting area over the PAPER antenna (top).
-The sleeved dipole in the center of the PAPER backplane is identical to the sleeved dipole being suspended under the cylindrical skirt over the vertex of the HERA dish.
-The dish geometry has the potential to introduce intra-antenna reflections which we explore in this work.}
-\label{fig:AntennaCompare}
-\end{figure}
 
@@
 For simulation, the entire model was encapsulated in vacuum dielectric with radiative boundaries and discrete ports of 125\,$\Omega$ impedance were defined at the terminals of the orthogonal dipoles.
+The simulated is conducted in a box encapsulating the dish geometry plus three wavelengths (at 150\,MHz) on all sides with open boundary conditions.
 
-Microwave Studio divides the model into approximately 94 million discrete hexahedral cell,s where the field is calculated over time using Finite Integration Technique incorporating the Perfect Boundary Approximation \citep{CST} in response to a 100-200 MHz broadband pulse of about 40 ns in duration.
-The model was excited in two ways: 1) via a plane wave entering the model along the bore sight, and 2) from one of the discrete terminals (whose analysis we focus on in \S~\ref{ssec:S11}).
+Microwave Studio divides the model into approximately 94 million discrete hexahedral cells where the field is calculated over time using Finite Integration Technique incorporating the Perfect Boundary Approximation\footnote{This proprietary technique is used by CST to reduce the number of simulation cells and should not be confused with PEC periodic boundary conditions.}  \citetext{Workflow and Solver Overflow Document, CST Microwave Studio, 2015, Chapter 3.} in response to a 100-200 MHz broadband pulse of about 40 ns in duration.
+The model was excited in two ways: 1) via a E-W polarized plane wave entering the model along the bore sight, and 2) from one of the discrete terminals (whose analysis we focus on in \S~\ref{ssec:S11}).
 The voltage responses at the terminals are monitored for these two cases over a duration of 500 ns as the excitation pulse travels throughout the model.
 
-In Fig.~\ref{fig:SimulationSetup} we show the geometery of the electromagnetic simulation.
-A $150$\,MHz plane wave with a Gaussian envelope with FWHM of {\bf \color{red}???} is initialized {\bf \color{red} ??} meters above the dish vertex traveling in the $-z$ direction.
+In Fig.~\ref{fig:SimulationSetup} we show the geometry of the electromagnetic simulation.
+A $150$\,MHz plane wave with a Gaussian envelope is initialized above the dish vertex traveling in the $-z$ direction.
 It is reflected by the dish before entering the dipole feed, hidden below the cylindrical skirt in this figure.
-We record the electric field voltage of the plane wave at the feed output terminals as a function of time, plotted as a red line in Fig.~\ref{fig:SimulationOutput} along with the voltage at the feed outputs (black line).
+We record the electric field voltage of the plane wave at the feed output terminals as a function of time, plotted as a red line in Fig.~\ref{fig:SimulationOutput} along with the output voltage at the terminals for the feed polarized parallel to the plan wave (black line).
 The delay between the primary envelopes of the plane wave and the voltage output of the feed is $\approx 30$\,ns which corresponds to the round trip travel time from the feed to the dish vertex and back.
 However, while the input plane wave, modulated by a gaussian, falls off rapidly and dies off after the first $\approx 20$\,ns after its peak, we see that the voltage output decays far more slowly due to reflections within the dish-feed structure.
-We are able to get a qualitative feel for the amplitude of the reflections by inspecting the falloff of the time domain voltage response and see that after $60$\,ns it reachs $\approx -25$\,dB.
+We are able to get a qualitative feel for the amplitude of the reflections by inspecting the falloff of the time domain voltage response and see that after $60$\,ns it reaches $\approx -25$\,dB.
 \begin{figure}
@@
 \begin{equation}\label{eq:Inversion}
-\ftr(\bl) = \boldsymbol{\mathcal{F}}^{-1} \left[ \frac{\boldsymbol{\mathcal{F}} {\bf \widetilde{v}}(\bl)}{\boldsymbol{\mathcal{F}}{\fts}(\bl)} \right] 
+\ftr(\bl) = \boldsymbol{\mathcal{F}}^{-1} \left[ \frac{\boldsymbol{\mathcal{F}} {\bf \widetilde{v}}(\bl)}{\boldsymbol{\mathcal{F}}{\fts}(\bl)} \right] ,
 \end{equation}
@@
 \begin{equation}
-\boldsymbol{\mathcal{F}}_{mn} = e^{2 \pi i m n /N}
+\boldsymbol{\mathcal{F}}_{mn} = e^{-2 \pi i m n /N}.
 \end{equation}
@@
 
-se\section{Simulation Results}\label{sec:Results}
+\section{Simulation Results}\label{sec:Results}
 
@@
 In particular, we focus on the time-domain die off of the voltage response and the resulting power kernel (\S~\ref{ssec:Kernel}), comparing it to an identical time-domain simulation of the skirted dipole antenna used by PAPER.
-In \S~\ref{ssec:Subbands} we investigate the dependence of the power kernel on frequency to determine whether specific parts of the HERA bandpass are more affected than others.
+In \S~\ref{ssec:Subbands} we investigate the dependence of the power kernel on frequency to determine whether specific parts of the HERA bandpass are more affected by reflections than others.
 Finally, in \S~\ref{ssec:S11} we verify our simulation framework by comparing a separate time domain simulation of $S_{11}$ of the HERA dish to a direct field measurement with a vector network analyzer (VNA).
@@
 \subsection{The Delay Response of Subbands}\label{ssec:Subbands}
-Because the 21\,cm brightness temperature fluctuations evolve over redshift intervals of $\Delta z \gtrsim 0.5$ \citep{Zaldarriaga:2004}, experiments will sub-divide their bands into $\approx 10$\,MHz intervals before attempting their estimates.
+Because the 21\,cm brightness temperature fluctuations evolve over redshift intervals of $\Delta z \gtrsim 0.5$ \citep{Zaldarriaga:2004}, experiments will sub-divide their bands into $\approx 10$\,MHz intervals for power spectrum estimates at multiple redshifts.
 Thus the localization of reflections within the HERA band will determine whether all or only a subset of redshifts are affected.
 To determine whether the reflections are localized in frequency, we compute the voltage delay response and power kernel for three different subbands: $100-130$\,MHz, $130-160$\,MHz, and $160-190$\,MHz.
-In order to maintain decent resolution of the kernel itself, we use frequency ranges are several times larger than the actual subbands that will be used for EoR power spectrum estimation ($\approx 10$\,MHz).
+In order to maintain decent resolution of the kernel itself, we use frequency ranges that are several times larger than the actual subbands that will be used for EoR power spectrum estimation ($\approx 10$\,MHz).
 The resulting power kernels are plotted in Fig.~\ref{fig:KernelsSubbands}.
@@
 
-We note that the termination impedence used in our simulations is $100$\,$\Omega$ to which the feed is better matched towards its edges.
+We note that the termination impedence used in our simulations is $125$\,$\Omega$ to which the feed is better matched towards its edges.
 Termination by a low-noise amplifier (LNA) as is the case in an actual measurement could change this situation dramatically, leading to the reflections being present across the entire band.
-We therefor consider the existence of the reflections across the entire $100$\,MHz bandpass as a realistic possibility.
+We therefore consider the existence of the reflections across the entire $100$\,MHz bandpass as a realistic possibility.
 
@@
 \includegraphics[width=.5\textwidth]{figures/powerKernelSubbands.pdf}
-\caption{The power kernel for the three subbands discussed in in \S~\ref{ssec:Subbands} along with the kernel for the full bandwidth response function.
+\caption{The power kernel for the three subbands discussed in \S~\ref{ssec:Subbands} along with the kernel for the full bandwidth response function.
 While the long term falloff from reflections is prominent between $130-160$\,MHz, it appears at a much lower level in the other two subbands which fall below the central subband by $\sim 20$\,dB at $\sim 300$\,ns.
@@
 \begin{figure}
-\includegraphics[width=.5\textwidth]{figures/frequency_domain_residuals.pdf}
+\includegraphics[width=.5\textwidth]{figures/frequency_domain_residuals_single.pdf}
 \caption{Residuals on the absolute value of the gain over several subbands after fitting to a sixth order polynomial.
@@
 We now assess the accuracy of our time-domain simulation framework by comparing simulations to measurements of the $S_{11}$ parameter of the HERA dish.
-Up until now, our simulations have derived the voltage response of the dish using simulations of an incoming plane wave as is the case for radio signals arriving from objects in space.
+Up until now, our simulations have derived the voltage response of the dish using simulations of an incoming plane wave as is the case for radio signals arriving from objects at cosmological distances.
 It is possible to probe the gain of the dish using objects in the far field such as known radio sources \citep{Thyagarajan:2011,Pober:2012,Colgate:2015} or constellations of ORBCOMM satellites \citep{Neben:2015,Neben:2016}.
@@
 We use the standard deviation of the open measurement (grey dashed line) between $200$ and $400$\,ns as our systematic floor (grey shaded region).
-We find very good agreement between our $S_{11}$ measurement and the simulation, validating the predictions of our simulations.}
+We find very good agreement between our $S_{11}$ measurement and the simulation, validating the predictions of our simulations.
+Both the simulations and measurements in this figure were derived from delay transforms over 100\,MHz.}
 \label{fig:S11}
@@
 $S_{11}$ refers to the complex ratio between a voltage signal transmitted into the feed terminals and the voltage reflected back as a function of frequency, $ S_{11}(f) \equiv v_\text{trans}(f)/v_\text{recv}(f) $.
-We measure $S_{11}$ of a prototype HERA dish at the National Radio Astronomy Observatory Green Bank facility using a vector network analyzer.
-
-The complex reflection coefficient of the antenna was measured using an Agilent 8753D VNA.
+We measure $S_{11}$ of a prototype HERA dish at the National Radio Astronomy Observatory Green Bank facility using an Agilent 8753D VNA.
 The VNA is connected to the antenna's balanced feed terminal via a 30.5 m length of RG-8X-LL coaxial cable and M/A Com HH-128 180 degree hybrid junction.
@@
 
-Because $S_{11}$ is defined as a ratio in the frequency domain in a form identical to our voltage gains, we may run time-domain simulations similar to those described in \S~\ref{ssec:Simulations} except rather than simulating an incoming plane wave, we simulate the excitation of the feed terminals by an input voltage and record output voltage as a function of time.
+Because $S_{11}$ is defined as a ratio in the frequency domain in a form identical to our voltage gains, we may run time-domain simulations similar to those described in \S~\ref{ssec:Simulations} except rather than simulating an incoming plane wave, we simulate the excitation of the feed terminals by a delta-gap impedance port and record output voltage as a function of time.
 We calculate $S_{11}$ from the simulation in the same manner that we obtained $\ftr$ using equation~\ref{eq:Inversion} with $\ftv_\text{recv}$ taking the place of $\ftv$ in the numerator inside the Fourier transform and $\ftv_\text{trans}$ taking the place of $\fts$ in the denominator.
@@
 In this measurement, we find noise-like structure at $\approx -50$\,dB.
-Below $\approx 500$\,ns, we found that this structure does not integrate down upon extending the VNA integration time, leading us to conclude that it is caused by systematics, likely uncalibrated low level reflections in the VNA-feed cables.
+Below $\approx 500$\,ns, we found that this structure does not integrate down with time, leading us to conclude that it is caused by systematics, likely uncalibrated low level reflections in the VNA-feed cables.
 The level of this noise sets the systematic floor in our measurements which we show as a grey shaded region in Fig.~\ref{fig:S11}.
@@
 \section{The Effect of the HERA dish Chromaticity on Foreground Leakage and Sensitivity}\label{sec:Sensitivity}
-We are now in a position to explore the impact of the Dish's performance on the leakage of foregrounds beyond the wedge, and into the EoR window.
+We are now in a position to explore the impact of the dish's performance on the leakage of foregrounds beyond the wedge, and into the EoR window.
 Beyond the delay kernels considered in this paper and \citet{Patra:2016}, the extent of leakage will depend both on the angular structure of the primary beam, which is established through measurements and simulations in \citet{Neben:2016} and the brightness of the foregrounds themselves.
@@
 The long term falloff appears as a line on a linear-log plot (Fig.~\ref{fig:SimulationResults}), indicating that the voltage response follows an exponential which we now show is indicative of reflections.
-We let $\Gamma_d$ represent the reflection coefficient of the Dish vertex and $\Gamma_f$ represent the reflection coefficient of the feed.
+We let $\Gamma_d$ represent the reflection coefficient of the Dish vertex and $\Gamma_f$ represent the reflection coefficient of the feed in the presence of each-other.
 An electromagnetic wave incident on the feed, at $t=0$, is accepted with amplitude $(1-\Gamma_f)$.
@@
 \begin{equation}
-\widetilde{v}_r(t) = \sum_m \left( \Gamma_f \Gamma_d \right)^m \widetilde{s}(t-m \tau_d)
+\widetilde{v}_r(t) = \sum_m \left( \Gamma_f \Gamma_d \right)^m \widetilde{s}(t-m \tau_d),
 \end{equation}
-implying that
-\begin{equation}
-\widetilde{r}_r(\tau) = \sum_m \left( \Gamma_f \Gamma_d \right)^m \delta_D(\tau-m\tau_d)
+which implies that
+\begin{equation}\label{eq:deltaSeries}
+\widetilde{r}_r(\tau) = \sum_m \left( \Gamma_f \Gamma_d \right)^m \delta_D(\tau-m\tau_d).
 \end{equation}
@@
 which is an exponential in time. We thus model our discrete voltage response as an exponential
-\begin{equation}
+\begin{equation}\label{eq:RefModel}
 \widetilde{r} = A X^{(\tau/30\text{ns})} 
 \end{equation}
-and extrapolate beyond $400$\,ns by fitting for $A$ and $X$ in our simulations between $200$ and $400$\,ns.
+to extrapolate beyond $400$\,ns by fitting for $A$ and $X$ in our simulations between $200$ and $400$\,ns.
+In this pedagogical treatment, we have assumed that the reflection coefficients are frequency independent which is not the case in real life.
+The impact of frequency dependent reflection coefficients is to replace the summands in equation~\ref{eq:deltaSeries} with the Fourier transform of $(\Gamma_f\Gamma_d)^m$ evaluated at $t=(\tau - m \tau_d)$.
+As long as $(\Gamma_f\Gamma_d)^m$ is compact in delay space, which is the case if the reflection coefficients evolve smoothly with frequency, than our pedagogical approximation still yields the power law in equation~\ref{eq:RefModel}.
 
@@
 
-The foreground filtering procedure employed by PAPER and HERA involves delay transforming the visibilities and performing a 1d clean which discovers and subtract foregrounds within the horizon plus a small buffer, allowing for the suppression of foreground side-lobes in delay space.
+The foreground filtering procedure employed by PAPER and HERA involves delay transforming the visibilities and performing a 1d clean \citep{Parsons:2009,Parsons:2012} which discovers and subtracts foregrounds within the horizon plus a small buffer, allowing for the suppression of foreground side-lobes in delay space.
 The level of foreground subtraction possible by this procedure is limited by the thermal noise level on the visibility, which in turn depends on the number of time steps and redundant baselines that are averaged before performing the cleaning step.
 In this work, we assume that each visibility is cleaned independently with a twenty minute cadence.
-Each baseline is coherent for $\approx 10$\,s per night so this is equivalent to each LST being integrated for $\approx 120$ nights before cleaning.
+Each baseline is coherent for $\approx 10$\,s per night so this is equivalent to each local Sidereal time (LST) being integrated for $\approx 120$ nights before cleaning.
 If we were to average over redundant baselines this number would drop enormously.
@@
 We clean down to five times the thermal noise level.
+Subtracting a model of the sky is an alternative to cleaning but also assumes a priori knowledge of the foregrounds and the instrumental response.
 In Fig~\ref{fig:Cleaning} we compare the delay transform of visibilities before and after cleaning at the LST of 4 hours.
 While cleaning is able to remove structure within the horizon, it does not reduce any of the power leaked outside of the horizon by the chromaticity of the dish.
+If we knew the spectral response of the dish perfectly, than we might be able to clean with this kernel and remove the supra-horizon structure.
+However, our design goal is for us to not require such precise instrumental knowledge (which would need to be less than one part in $10^{-4}$ to not be necessary).
 
@@
 Here, $\lambda$ is the central wavelength of the observation, $k_B$ is the Boltzmann constant, $B_{pp}$ is the integral of the square of the bandpass, and $\Omega_{pp}$ is the integral of the primary beam squared over solid angle.
-$X$ and $Y$ are linear factors converting between native interometry and cosmological coordinates, defined through the relation $2 \pi {\bf u}=2 \pi (u,v,\eta) = (X k_x, X k_y, Y k_z)$.
+$X$ and $Y$ are linear factors converting between native interferometry and cosmological coordinates, defined through the relation $2 \pi {\bf u}=2 \pi (u,v,\eta) = (X k_x, X k_y, Y k_z)$.
 
-A drift scan instrument, HERA will observe the sky at many local sidereal times (LSTs) within the strip declination that passes through its primary beam, averaging over the power spectrum estimate at each LST.
+A drift scan instrument, HERA will observe the sky at many LSTs within the strip declination that passes through its primary beam, averaging over the power spectrum estimate at each LST.
 It is well documented that foreground power varies significantly over LST \citep{Thyagarajan:2015a}, hence such an estimate will either filter or weight LSTs in a way that minimizes the impact of the most contaminated observations.
@@
 However, the depth of cleaning is limited by the noise level on a single baseline (black line).
-We show the foreground residuals with arising from a clean down to the $5\,\sigma$ noise level after 20 minutes of integration.
+We show the foreground residuals from a clean down to the $5\,\sigma$ noise level after 20 minutes of integration.
 Since cleaning cannot distinguish between foregrounds and signal, it should only be performed within a narrow region of delay-space, close to the horizon and cannot remove the broad wings leaked by the reflections unless they are accurately modeled.}
@@
 The level of the foregrounds in Fig.~\ref{fig:BothBaselines} is conservative since no attempt has been made to apply inverse covariance weighting techniques \citep{Tegmark:1997a,Liu:2011,Dillon:2013,Parsons:2014,Liu:2014a,Liu:2014b,Dillon:2015a,Dillon:2015b,Trott:2016} or fringe rate filtering \citep{Parsons:2015}.
-In order to avoid biases in a maximum likelihood analysis that determines astrophysical and cosmological parameters from our power spectra, the foregrounds should ideally be below the anticipated level of thermal noise which is shown in \citet{Pober:2014} to be on the order of a few percent the anticipated level of the cosmological signal for the full HERA deployment.
-Thus, as long as we can suppress our foregrounds below $\approx 5$\% the level of the signal, they should not interfere significantly with a maximum likelihood analysis.
-Thus, the residuals in Fig.~\ref{fig:BothBaselines} serve as a specification for any inverse covariance weighting pipeline which will need to suppress foregrounds by between a factor of $\sim 1-10$ to bring the worst contaminated regions below the level of the signal.
-Applications of inverse covariance filters in recent PAPER observations have yielded improvements at and above this level {\bf \color{red} citation?}, hence our simulations show that even with the presence of beam chromaticity, HERA will be able to isolate foregrounds below the level of thermal noise in most of the EoR window.
+Applications of inverse covariance filters in recent PAPER observations have yielded reductions in foreground power by greater than an order of magnitud \citep{Ali:2015}, hence our simulations show that even with the presence of beam chromaticity, HERA will be able to isolate foregrounds below the level of thermal noise in most of the EoR window.
 
@@
 A primary near-term goal of 21\,cm EoR observations is to obtain information about the nature of the sources that drove reionization.
-Since the amplitude of the 21\,cm signal is maximal at smaller $k$ values, a loss of large scale signal due to foreground contamination eliminates the the modes that HERA would otherwise have the greatest signal to noise detections of, reducing its overall sensitivity.
+Since the amplitude of the 21\,cm signal is maximal at smaller $k$ values, a loss of large scale signal due to foreground contamination eliminates the modes that HERA would otherwise have the greatest signal to noise detections of, reducing its overall sensitivity.
 In this section, we use the Fisher Matrix formalism to estimate the impact of foreground leakage on HERA's sensitivity along with its ability to determine the astrophysics of reionization.
@@
 \item ${\bf \zeta}$: The ``ionization efficiency" is defined in the \citet{Furlanetto:2004} excursion formalism to be the inverse of the mass collapse fraction necessary to ionize a region and is computed from a number of other physical parameters including the fraction of collapsed baryons that form stars and the UV photon escape fraction.
-Because $\zeta$ acts as an efficiency parameter, its primary affect is to change the timing of reionization.
+Because $\zeta$ acts as an efficiency parameter, its primary effect is to change the timing of reionization.
 We choose a fiducial value of $\zeta=20$, though its possible values range anywhere between $5$ and $50$.
@@
 \end{itemize}
-In order to account for the degeneracies in the power spectrum between heating from X-rays and reionization from UV photons, we also marginalize over three additional parameters that describe the impact of heating from early X-ray luminous sources as explored in \citep{EwallWice:2015b}.
-These are the X-ray heating efficiency $f_X$, the maximal energy of X-ray photons that are self absorbed by the ISM of early galaxies, $\nu_\text{min}$, and the spectral slope, $\alpha$ which are taken to have fiducial values of $1$, $0.3$\,keV, and $-1.2$ respectively.
+In order to account for the degeneracies in the power spectrum between heating from X-rays and reionization from UV photons, we also marginalize over three additional parameters that describe the impact of heating from early X-ray sources as explored in \citep{EwallWice:2015b}.
+These are the X-ray heating efficiency, $f_X$; the maximal energy of X-ray photons that are self absorbed by the ISM of early galaxies, $\nu_\text{min}$; and the spectral slope, $\alpha$ which are taken to have fiducial values of $1$, $0.3$\,keV, and $-1.2$ respectively.
 We choose to parameterize our model in terms of the fractional difference of each variable from its fiducial value so that, for example, $\theta_\zeta = (\zeta - \zeta_\text{fid})/\zeta_\text{fid}$ and compute the derivatives in equation~\ref{eq:Fisher} by performing a linear fit to realizations of the 21\,cm power spectrum calculated by {\tt 21cmFAST} at $\theta_i= \pm 10^{-2}, \pm 5\times 10^{-2}, \pm 10^{-1}$,and $ \pm 2 \times 10^{-2}$.
 
-What about $\sigma^2(k,z)$?
-For each measurement in the $uv$ plane, the standard deviation of a power spectrum measurement is given by the direct sum of sample variance and thermal noise \citep{McQuinn:2006} which in turn depends on the primary beam of the instrument and the time spent sampling each $uv$ cell.
-For our analysis, we assume that the $uv$ plane is sampled by circular apertures with effective areas of $98$\,m$^2$ and that $\tau({\bf k})$ is determined by a drift scan in which non instantaneously redundant baselines are combined within each $uv$ cell.
-We compute standard deviation of each $(k,z)$ bin for the proposed 331-element deployment of HERA (HERA-331) using the public {\tt 21cmSense}\footnote{\url{https://github.com/jpober/21cmSense}} code \citep{Pober:2013b,Pober:2014}.
+For each measurement in the $uv$ plane, the standard deviation of a power spectrum measurement ($\sigma^2(k,z)$) is given by the direct sum of sample variance and thermal noise \citep{McQuinn:2006} which in turn depends on the primary beam of the instrument and the time spent sampling each $uv$ cell.
+For our analysis, we assume that the $uv$ plane is sampled by circular apertures with effective areas of $98$\,m$^2$ and that $\tau({\bf k})$ is determined by a drift scan in which non-instantaneously redundant baselines are combined within each $uv$ cell.
+We compute the standard deviation of each $(k,z)$ bin for the proposed 350-element deployment of HERA (HERA-350) using the public {\tt 21cmSense}\footnote{\url{https://github.com/jpober/21cmSense}} code \citep{Pober:2013b,Pober:2014}.
 
@@
 \includegraphics[width=.5\textwidth]{figures/sensitivity_comparison_v2.pdf}
-\caption{A comparison between the sensitivity achieved by HERA-331 at redshift $8.5$ with and without the presence of beam chromaticity due to the reflections studied in this work.
+\caption{The $1\sigma$ thermal noise levels achieved by HERA-350 at redshift $8.5$ with (red line) and without (green line) the presence of beam chromaticity due to the reflections studied in this work.
 We saw in Fig.~\ref{fig:BothBaselines} that with reflections, foregrounds exceed the signal level out to $k=0.23$\,$h$Mpc$^{-1}$ at $z=8.5$ which we assume are unusable, forcing us to ignore modes out to $350$\,ns beyond the horizon, leading to the sensitivity projected in the red curve.
@@
 
-\begin{figure*}
-\includegraphics[width=\textwidth]{figures/sigmaVsZ_reionization_v2.pdf}
-\caption{Fractional Errors on reionization and heating parameters as a function of maximal observed redshift out to the low end of HERA-331's initial observing band at $z=12$.
-The presence of strong reflections contained within a small subband at $z=8.5$ has a minimal impact on our overall constraints on reionization parameters.
-If these reflections are not localized they can lead to a factor of two loss in sensitivity to some parameters such as $T_\text{vir}^\text{min}$.}
-\label{fig:Errors}
-\end{figure*}
-
 \begin{figure}[h!]
 \includegraphics[width=.5\textwidth]{figures/reionization_triangle_compare_v2.pdf}
-\caption{95\% confidence regions for reionization parameters assuming $1000$ hours of observation on HERA-331 between the redshifts between 7.5 and 12.
+\caption{95\% confidence regions for reionization parameters assuming $1000$ hours of observation on HERA-350 between the redshifts between 7.5 and 12.
 The presence of the reflections leads to an increase in the major axes of these confidence regions by a factor of one to two.}
@@
 
-We have seen in Fig.~\ref{fig:BothBaselines} that the simulated chromaticity of the dish leaks foregrounds beyond the horizon to varying degrees depending on the subband with the worst leakage occuring at $z=8.5$ centered at 150\,MHz in which foregrounds exceed the signal out to $\sim 380$\,ns which for a $14.6$\,m baseline is $\approx 330$\,ns beyond the horizon.
+\begin{figure*}
+\includegraphics[width=\textwidth]{figures/sigmaVsZ_reionization_v2.pdf}
+\caption{Fractional Errors on reionization and heating parameters as a function of maximal observed redshift out to the low end of HERA-350's initial observing band at $z=12$.
+The presence of strong reflections contained within a small subband at $z=8.5$ has a minimal impact on our overall constraints on reionization parameters.
+If these reflections are not localized they can worsen our sensitivity to some parameters such as $T_\text{vir}^\text{min}$ by a factor of two.}
+\label{fig:Errors}
+\end{figure*}
+
+We have seen in Fig.~\ref{fig:BothBaselines} that the simulated chromaticity of the dish leaks foregrounds beyond the horizon to varying degrees depending on the subband with the worst leakage occuring at $z=8.5$ centered at 150\,MHz.
+In this subband, foregrounds exceed the signal out to $\sim 380$\,ns which for a $14.6$\,m baseline is $\approx 330$\,ns beyond the horizon.
 At all other redshifts, the leakage due to beam chromaticity only extends to $\approx 250$\,ns beyond the horizon.
@@
 \begin{itemize}
-\item {\bf Optimistic: The observed reflections are an artifact of the simulation.} It is possible that the long term reflections observed in the center of our gain are artifacts of our modeling such as dissipative effects due to unmodeled non-idealities in the geometry of the disk will allow reflected radio waves to be better absorbed or escape into space.
+\item {\bf Optimistic: The observed reflections are an artifact of the simulation.} It is possible that the long term reflections observed in the center of our gain are artifacts of our modeling.
+Dissipative effects due to unmodeled non-idealities in the geometry of the dish may allow reflected radio waves to be better absorbed or escape into space.
 In our most optimistic scenario, we assume their absence in which case the foregrounds pass below the level of the signal at $250$\,ns beyond the horizon at all redshifts between $z=7$ and $12$, consistent with what is observed in the bands where the dish chromaticity is less severe or when it is not present at all.
 We do not consider the possibility that optimal inverse covariance weighting of the foregrounds  may actually decrease the minimal delays accessible to below the $250$\,ns above the horizon observed in our simulations.
-Hence, this scenario is actually somewhat conservative and certainly more pessimistic than the ones considered in \citet{Pober:2014,Liu:2015a,Liu:2015b,EwallWice:2015b}.
+Hence, this scenario is actually somewhat conservative and certainly more pessimistic than previous Fisher analyses \citet{Pober:2014,Liu:2015a,Liu:2015b,EwallWice:2015b}.
 
@@
 We decide to include this more pessimistic scenario since our simulations and measurements are run with a termination impedence of $\approx 100-125$\,$\Omega$ which is actually a better match to the feed at the edges of the $100-200$\,MHz band, reflecting $1-3$\% power at the edges while reflecting $\approx 10$\% power at $150$\,MHz.
-In an actual cosmological measurement, the feed is terminated by a LNA whose impedance might differ significantly, hence it is not unlikely that we find the reflections in the center of our band present across its entirety.
+In an actual cosmological measurement, the feed is terminated by an LNA whose impedance may not be perfectly matched at all frequencies despite the best efforts of its designers, hence it is possible that we will find the reflections across the entirety of the 100\,MHz band.
 
@@
 Firstly, in our most optimistic scenario, we assumed that foregrounds cause the signal to be inaccessible below $250$\,ns beyond the edge of the wedge which corresponds to $k_\text{min} \approx 0.15$\,$h$Mpc$^{-1}$ at $z=8.5$ while in previous works a minimal comoving $k_\text{min} \approx 0.1$\,$h$Mpc$^{-1}$ was used.
-Secondly, previous studies assumed a fully illuminated HERA aperture, which for a $14$\,m diameter dish predicts and effective area of $\approx155$\,m$^2$.
+Secondly, previous studies assumed a fully illuminated HERA aperture, which for a $14$\,m diameter dish predicts an effective area of $\approx155$\,m$^2$.
 Electromagnetic simulations and ORBCOMM mapping of the angular beam pattern of the HERA dish show that the effective area of the antenna element is actually $\approx 98$\,m$^2$ at $137$\,MHz which leads to an increase in the overall thermal noise levels by a factor of $\approx 1.5$ \citep{Neben:2016}.
 
-Although conservative, our predictions bode well for the HERA design, indicating that even with the additional systematics introduced by the reflections in the Dish geometry, the array will still obtain a $\gtrsim 10 \sigma$ detection of the power spectrum and be capable of establishing precision constraints on the properties of the sources that reionized the IGM.
+Although conservative, our analysis shows that the level of chromaticity present in the HERA beams is not yeat an insurmountable obstacle for the 21\,cm power spectrum measurement.
+Even with the additional systematics introduced by the reflections in the Dish geometry, the array will still obtain a $\gtrsim 10 \sigma$ detection of the power spectrum and be capable of establishing precision constraints on the properties of the sources that reionized the IGM.
 
@@
 
-\item Fortunately, these reflections appear to be contained within the central $10$\,MHz of the HERA band, indicating a resonance that, in principle can be identified in the dish design and mitigated.
+\item These reflections appear to be contained within the central $10$\,MHz of the HERA band.
+This is likely due to a better impedance match at the band edges between the feed and the terminals which may not exist in an actual deployment.
 It is also possible that the  non-ideal properties of an actual antenna will allow these reflections to escape the dish after a short time or be dissipated, rather than reflecting continually to long delays.
@@
 
-While we have not addressed the issue of inter-dish reflections, preliminary measurements indicate that their level is many orders of magnitude below our observations of reflections within each antenna element with a full analysis forthcoming \citep{Patra:2016}.
-Our results are very encouraging since they show that the HERA design is capable of isolating the foregrounds to sufficiently low delays to make a high significance detections of the 21\,cm power spectrum during the EoR.
-They also emphasize the importance of mitigating reflections in the analogue signal chain.
-The reflections masking our signal at $k=0.2$\,$h$Mpc$^{-1}$ are at the level of one part in $10^{-4}$, hence any interferometer designed for EoR observing must ensure that such structure is absent from the signal chain at the $10^{-5}$ level or less at $\approx 400$\,ns or be absolutely certain that their calibration strategy can faithfully remove this structure without introducing any spurious, frequency-dependent artifacts at or above this level due to foreground mismodeling or thermal noise.
+%While we have not addressed the issue of inter-dish reflections, measurements of cross coupling are currently underway with a full analysis forthcoming \citep{Patra:2016}.
+
+Our results are very encouraging since they show that the HERA design is capable of isolating the foregrounds to sufficiently low delays to make a high significance detection of the 21\,cm power spectrum during the EoR.
+They also emphasize the importance of mitigating spectral structure in the analogue signal chain.
+The reflections masking our signal at $k=0.2$\,$h$Mpc$^{-1}$ are at the level of one part in $10^{-4}$ and are mathematically identical to Fourier modes introduced by any instrumental spectral structure and the requirement that spectral structure be smaller than $10^{-4}$\,dB at $\approx 350$\,ns to be below the signal is applicable to all steps in the signal chain beyond the dish.
+A full statement of such a specifications for spectral structure to observe the EoR power spectrum at different $k$ values will be given in \citet{Thyagarajan:2016}.
+Hence any interferometer designed for EoR observing should ensure that such structure is absent from the signal chain at the $\sim10^{-5}$ level or less at $\approx 350$\,ns or be absolutely certain that their calibration strategy can faithfully remove this structure without introducing any spurious, frequency-dependent artifacts at or above this level due to foreground mismodeling or thermal noise.
+
+%\section*{acknoledgments}
+%We would like to thank Jonathan Pober and Eloy de Lera Acedo for their helpful comments. AEW acknowledges support from a National Science Foundation Graduate Research Fellowship (grant number
 

### 2016-02-22 DishReflectometry/Paper1_v1.tex

@@
 
-Since it was first proposed in \citep{Shaver_et_al1999} measuring 21~cm
+Since it was first proposed in ~\citep{Shaver_et_al1999} measuring 21~cm
 emission from neutral hydrogen in our early universe has gained attention as a
@@
 established (see, e.g.,
-\citep{furlanetto_et_al2006,morales_wyithe2010,pritchard_loeb2012}),
+~\citep{furlanetto_et_al2006,morales_wyithe2010,pritchard_loeb2012}),
 the technical path toward measuring this signal has been extremely challenging.  The
@@
 challenges that are yet to be fully solved.  With noise temperatures dominated
-by sky noise \citep{XXX} and foregrounds four to five orders of magnitude
-brighter than the signal \citep{XXX}, 
+by sky noise ~\citep{XXX} and foregrounds four to five orders of magnitude
+brighter than the signal ~\citep{XXX}, 
 sky-averaged 21~cm monopole experiments such as
-(EDGES; \citealt{XXX}),
-(BIGHORNS; \citealt{XXX}),
-(SARAS; \citealt{patra_et_al2014}),
-(SCIHI; \citealt{voytek_et_al2014}),
-(HyPerion; \citealt{presley_et_al2015})
+(EDGES; ~\citealt{XXX}),
+(BIGHORNS; ~\citealt{XXX}),
+(SARAS; ~\citealt{patra_et_al2014}),
+(SCIHI; ~\citealt{voytek_et_al2014}),
+(HYPERION; ~\citealt{presley_et_al2015})
 % XXX others?
 and 21~cm reionization power spectrum experiments such as
-the LOw Frequency ARray (LOFAR; \citealt{XXX}),
-the Murchison Widefield Array (MWA; \citealt{XXX}),
-the Giant Metre-wave Radio Telescop (GMRT; \citealt{XXX}),
-the Donald C. Backer Precision Array to Probe the Epoch of Reionization (PAPER; \citealt{parsons_et_al2010}),
-the Hydrogen Epoch of Reionization Array (HERA; \citealt{XXX}),
-and the future Square Kilometre Array (SKA; \citealt{XXX})
+the LOw Frequency ARray (LOFAR; ~\citealt{XXX}),
+the Murchison Widefield Array (MWA; ~\citealt{XXX}),
+the Giant Metre-wave Radio Telescop (GMRT; ~\citealt{XXX}),
+the Donald C. Backer Precision Array to Probe the Epoch of Reionization (PAPER; ~\citealt{parsons_et_al2010}),
+the Hydrogen Epoch of Reionization Array (HERA; ~\citealt{XXX}),
+and the future Square Kilometre Array (SKA; ~\citealt{XXX})
 must
@@
 contaminating spectral modes that might
-otherwise be used to measure reionization \citep{XXX}.  Moreover, the chromaticity of
+otherwise be used to measure reionization ~\citep{XXX}.  Moreover, the chromaticity of
 a telescope's response scales linearly with diameter, putting the
@@
 element separation (or telescope diameter), and what it implies for distinguishing
-foreground emission from the cosmological 21~cm signal \citep{XXX}.  The ``wedge'', as it is
+foreground emission from the cosmological 21~cm signal ~\citep{XXX}.  The ``wedge'', as it is
 colloquially known, describes a linear relationship between the separation between elements
@@
 wedge pattern.  Outside of the wedge, foreground contamination drops rapidly 
-\citep{pober_et_al2013,thargarajan_et_al2015}, provided that the spectral responses
+~\citep{pober_et_al2013,thargarajan_et_al2015}, provided that the spectral responses
 of antenna elements and analog electronics are sufficiently smooth\footnote{Here, we distinguish
@@
 element separation in an interferometric baseline.}.  In promising avoidance-based
-foreground strategy employed by PAPER \citep{parsons_et_al2014,ali_et_al2015}, these modes
+foreground strategy employed by PAPER ~\citep{parsons_et_al2014,ali_et_al2015}, these modes
 may be targeted as the lowest risk path for contraining 21~cm reionization in the near term.
@@
 In this paper, we examine the performance of a new prototype HERA element in the context of
-this new wedge-based framework.  In coordination with \citet{XXXsisterpapers}, we compare 
+this new wedge-based framework.  In coordination with ~\citet{XXXsisterpapers}, we compare 
 reflectometry measurements with
@@
 The efficacy of the techniques of foreground removal from the measured data critically limits the 21~cm power spectrum measurements.
-The delay transformation technique of foreground removal, introduced by  \citep{ParsonsBacker2009,Parsons2012} computes the Fourier transform of the visibility measured by an interferometer and produces a spectrum, referred to as delay spectrum hereafter, which is a function of the geometric time delay corresponding to the physical length of the baseline between two antennas.
+The delay transformation technique of foreground removal, introduced by  ~\citep{ParsonsBacker2009,Parsons2012} computes the Fourier transform of the visibility measured by an interferometer and produces a spectrum, referred to as delay spectrum hereafter, which is a function of the geometric time delay corresponding to the physical length of the baseline between two antennas.
 For the visibilities measured over a wide field across wide frequency bandwidth, the delay spectrum is constituted by the instrument response, the foreground signal and 21cm power spectrum, hereafter referred to as EoR signal.
@@
 If we defineI_{sky} the Fourier conjugate of the frequency axis as $\tau$ then the equation could be written as,
-In \citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
+In ~\citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
 resulting in the delay spctrum:
@@
 at the level of $-60dB$ at a delay of $60ns$ relative to the first incident
-signal at the feed \citep{parsons_deboer_memo}. This specification was
+signal at the feed ~\citep{parsons_deboer_memo}. This specification was
 approximated based on the power level of the cosmological signal in relation to
-foreground signals, which is estimated to be six orders of magnitude fainter
-\citep{santos_et_al2005,ali_et_al2008,deoliveira2008,jelic_et_al2008,bernardi_et_al2009,bernardi_et_al2010,ghosh_et_al2011}. Additionally, the $14m$ HERA baselines set a foreground containing
+foreground signals, which is estimated to be six orders of magnitude fainter ~\citep{santos_et_al2005,ali_et_al2008,deoliveira2008,jelic_et_al2008,bernardi_et_al2009,bernardi_et_al2010,ghosh_et_al2011}.
+Additionally, the $14m$ HERA baselines set a foreground containing
 horizon-limit (the wedge) that, with some buffer, sets a delay specification of
 $60ns$
-\citep{parsons_et_al2012b,vedantham_et_al2012,nithya_et_al2013,liu_et_al2014a,liu_et_al2014b}.
+~\citep{parsons_et_al2012b,vedantham_et_al2012,nithya_et_al2013,liu_et_al2014a,liu_et_al2014b}.
 Our goal is to measure the instrument response $\Sigma(\nu)$ and its effect on the power spectrum measurements.
@@
 Figure \ref{fig:window} shows the delay spectrum estimated from the measured data using a square window as well as Blackman Harris window.
-Windowing the data prior to Fourier transform significantlu reduces the system response higher delays.
+Windowing the data prior to Fourier transform significantly reduces the system response higher delays.
 \begin{figure}
@@
 
+\bibliography{biblio.bib}{}
 \bibliographystyle{apj}
-\bibliography{biblio.bib}
 \end{document}

### 2016-02-23 DishReflectometry/Paper1_v1.tex
minor changes after changes made my Cherie are put in place.

@@
 (SCIHI; ~\citealt{voytek_et_al2014}),
-(HYPERION; ~\citealt{presley_et_al2015})
+(HyPerion; ~\citealt{presley_et_al2015})
 % XXX others?
@@
 \begin{equation}
-\volt_{2} (\thhat, \nu)= \bmvolt_{2}(\thhat,\nu)\volt_\sky(\thhat,\nu)\dfngexp\nonumber\\
+\volt_{2} (\thhat, \nu)= \bmvolt_{2}(\thhat,\nu)\volt_\sky(\thhat,\nu)\fngexp\nonumber\\
 \end{equation}
@@
 The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$.
-In words, the sky delay spectrum from any direction $\thhat$ is convoluted with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ in the delay domain.
+In words, the sky delay spectrum from any direction $\thhat$ is convolved with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ in the delay domain.
 The maximum geometric delay possible for a given base line would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$ when the phase centre is halfway in between the two antennas.
@@
 approximated based on the power level of the cosmological signal in relation to
-foreground signals, which is estimated to be six orders of magnitude fainter ~\citep{santos_et_al2005,ali_et_al2008,deoliveira2008,jelic_et_al2008,bernardi_et_al2009,bernardi_et_al2010,ghosh_et_al2011}.
-Additionally, the $14m$ HERA baselines set a foreground containing
+foreground signals, which is estimated to be six orders of magnitude fainter
+~\citep{santos_et_al2005,ali_et_al2008,deoliveira2008,jelic_et_al2008,bernardi_et_al2009,bernardi_et_al2010,ghosh_et_al2011}. Additionally, the $14m$ HERA baselines set a foreground containing
 horizon-limit (the wedge) that, with some buffer, sets a delay specification of
@@
 Figure \ref{fig:window} shows the delay spectrum estimated from the measured data using a square window as well as Blackman Harris window.
-Windowing the data prior to Fourier transform significantly reduces the system response higher delays.
+Windowing the data prior to Fourier transform significantlu reduces the system response higher delays.
 \begin{figure}

### 2016-02-23 data/quadratic_estimator.py
changes to quadratic_estimator.py script
-change complex -> complex128
-add in threshold to turn imaginary parts into be completely zero. hitting numerical errors.
-add ntimes to reading data so we can ut time samples.
- add in some more plotting.
-make necessary changes to array sizes for ^ to work

@@ -1,6 +1,7 @@
 #! /usr/bin/env python
 import numpy as n, pylab as p, aipy as a
 import sys, optparse, capo
+import ipdb as db
 
 o = optparse.OptionParser()
 opts,args = o.parse_args(sys.argv[1:])
@@ -10,11 +11,17 @@ WINDOW='none'
 PLOT=True
 HALF=True
 
+def Formatter(object):
+    def __init__(self, im):
+        self.im = im
+    def __call__(self, x, y):
+        z = self.im.get_array()[int(y), int(x)]
+        return 'x={:1e-10f},y={:1e-10f},z={:1e-10f}'.format(x,y,z)
 
 def cov(m):
     '''Because numpy.cov is stupid and casts as float.'''
     #return n.cov(m)
-    X = n.array(m, ndmin=2, dtype=n.complex)
+    X = n.array(m, ndmin=2, dtype=n.complex128)
     X -= X.mean(axis=1)[(slice(None),n.newaxis)]
     N = X.shape[1]
     fact = float(N - 1)
@@ -23,13 +30,17 @@ def cov(m):
 def get_Q(mode, n_k):
     '''Gets the Q matrix in the quadratic estimator formalism. 
        See Ali et. al. eq.12'''
-    _m = n.zeros((n_k,), dtype=n.complex)
+    _m = n.zeros((n_k,), dtype=n.complex128)
     _m[mode] = 1.
     m = n.fft.fft(n.fft.ifftshift(_m)) * a.dsp.gen_window(nchan, WINDOW)
-    Q = n.einsum('i,j', m, m.conj())
+    Q = n.einsum('i,j', m.conj(), m)
+    print n.diag(Q)
+#    capo.arp.waterfall(Q, mode='phs')
+#    p.colorbar(shrink=.5)
+#    p.show()
     return Q
 
-def read_npz(f, half=HALF):
+def read_npz(f, half=HALF,ntimes=None):
     '''Return dictionary with keys [bl][cent] = vis'''
     data = {} # full visibility data (all chans)
     subdata = {} #a subset of the channels corresponding to the windowed channels but no window applied.
@@ -48,27 +59,26 @@ def read_npz(f, half=HALF):
         data[i] = {}
         subdata[i] = {}
         datawind[i] = {}
-        data[i]=  vis[i,:,:]
+        data[i]=  vis[i,:,:ntimes]
         for k,midch in enumerate(subcent):
[…]

### 2016-02-23 DishBeamMeasurements/memo/DishBeamMeasurementsMemo_oct26_2015.tex

--- 2015-10-28 DishMeasurements/memo/DishBeamMeasurementsMemo.tex
@@
 
-\title{HERA Dish Beam Measurements Memo}
+\title{HERA Dish Beam Measurements Memo Draft}
 
@@
 
-\author{Abraham Neben, Rich Bradley, Jackie Hewitt, others}
+\author{Abraham Neben, Rich Bradley, Jackie Hewitt, James Aguirre, Pat Klima, others?}
 %\affil{MIT Kavli Institute, Massachusetts Institute of Technology, Cambridge, MA, 02139 USA}

### 2016-02-23 DishSimulations/memo/memo.tex

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{amsmath,graphicx,bm,amsbsy,aas_macros,url,array,amssymb,breqn,aas_macros,todonotes,graphicx,comment}
\RequirePackage{fixltx2e}
\include{aarondefns}
\bibliographystyle{mn2e}

\title{Simulations of the delay response of the HERA dish and implications for EoR power spectrum measurements.}
\author[A Ewall-Wice et al.]{A.~Ewall-Wice,\thanks{E-mail: aaronew@mit.edu}~
Jacqueline~N.~Hewitt,~
Richard~Bradley,~
Mariet~Venter,~
}

\begin{document}

\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
\voffset=-.6in

\begin{abstract}
Numerical simulations of the spectral response of the PAPER feed+Dish+skirt antenna are performed. We find that the time-domain response of this arrangement misses the -60\,dB, 60\,ns spec by $\approx 25$\,dB. Simple calculations of foreground residual leakage into the EoR window are also carried out. After subtracting a perfect foreground model that does not include the antenna response, we find that the spectral structure extrapolated from the simulation causes foreground residuals to exceed the level of the cosmological signal $\sim 0.25h$Mpc$^{-1}$ beyond the wedge. Residuals for an antenna that meets the spec exactly are limited to $\sim 0.1h$Mpc$^{-1}$ beyond the wedge. While definitive conclusions about the overall contamination of the power spectrum should not be drawn from this analysis, we hope that it will motivate firmly established measurements of the HERA dish's performance and more thorough studies of the actual impact on foreground contamination in a full power spectrum pipeline analysis.
\end{abstract}

\section{CST time domain simulations.}
In this note, we simulate the effect of the time response function of the HERA dish power spectrum measurements. We run a 500\,ns CST simulation of the voltage response of the reciever to a 150\,MHz plane wave with a finite pulse envelope, incoming from zenith (${\bf v}_{in}$) and record the time domain voltage response at the receiver output (${\bf v}_{out}$).

\begin{figure*}
\includegraphics[width=\textwidth]{figures/voltage.pdf}
\caption{The power in the voltage output as a function of time (green line normalized to 1 at $t=0$) in response to the power of our input plane wave (blue line) from our simulation. At 60\,ns, the power has only reached -35dB, significantly above the HERA spec.}
\label{fig:voltageResponse}
\end{figure*}

In Figure~\ref{fig:voltageResponse} we show the power (normalized to $t=0$) in the input wave and the voltage response. By 60\,ns, the power level has only fallen by $\approx -35$ dB. Since the input wave packet falls very steeply after $\sim 10$\,ns, we do not think that it is from the instantaneous reaction of the system to the falling plane wave. We can, of course, obtain the response function directly from the simulation by deconvolving the plane wave out of the total voltage output in a calculation that we now describe.

\section{Deconvolving the response function}
The voltage a the receiver output terminals, $v_{out}$, may be expressed as the convolution of the antenna response function, $R(\tau)$ with the intput signal, $v_{in}$.

\begin{equation}
v_{out}(t) = \int d \tau R(\tau) v_{in}(t - \tau) .
\end{equation}

Using the Fourier convolution theorem, we may undue this convolution by Fourier transforming, dividing the output by the plane wave, and fourier transforming back. Our estimate of the response, $\widehat{R}(t)$ may be expressed mathematically as 
\begin{equation}\label{eq:ftResponse}
\widehat{R}(t) = \boldsymbol{\mathcal{F}}^{-1}\left[ \frac{\boldsymbol{\mathcal{F}}{\bf v}_{out}}{\boldsymbol{\mathcal{F}}{\bf v}_{in}}\right]
\end{equation}
where
\begin{equation}
\boldsymbol{\mathcal{F}}_{kj} = e^{-2 \pi i kj /N}
\end{equation}
and
\begin{equation}
\frac{1}{N} \boldsymbol{\mathcal{F}}_{kj} = e^{2 \pi i kj /N}
\end{equation}

In Figure \ref{fig:tSim} we show the 500\,ns simulation of a plane wave incident on the HERA dish from zenith along with the voltage response. We also show the estimated response function out to $250$\,ns computed from equation \ref{eq:ftResponse}. Notable in the response function itself is very fine time scale structure that reaches positive and negative values but goes down very slowly as a function of delay. This noisy structure originates from the fact that our input plane wave is significantly smoother than time-resolution of the simulation and hence has compact support in the frequency domain. In Fig.~\ref{fig:freqDomain} we show the magnitude of the Fourier transform of the input plane wave (blue line) and see that it occupies a limited region of the frequency axis, centered at $150$\,MHz.  The voltage response (green line) is also primarily centered at the frequencies of the input wave (after all, it is effectively a multiplication of the input in the frequency domain) with significant numerical noise at frequencies away from the lobes and at the zero frequency region as well. The ratio of the unfiltered signals introduces significant high frequency noise power (red line). To eliminate the high frequeny noise, we multiply the frequency domain ratio of the voltage response and input wave by a $2$\,GHz FWHM Blackman-Harris window (cyan). After applying this first filter, the response function appears as the magenta line in the frequency domain. We show this noise filtered response function in Fig.~\ref{fig:tSimFiltered}. Even though significant modifications have been made in the frequency domain, the convolution of this response function with the input plane wave still well reproduces the voltage output. Another filter is ultimately applied to simulate the 100\,MHz instrumental bandpass and our final frequency-domain response is shown in Fig.~\ref{fig:finalFilter}.
%/Users/anguta/Documents/science/data/HERA_feed/reflectionGain.ipynb
\begin{figure*}
\includegraphics[width=\textwidth]{figures/deconvolution.pdf}
\caption{Simulated voltage levels from an input plane wave (blue line) as a function of time. The voltage response at the feed output (green line) is effectively the convolution of the input wave with the time-domain response function of the dish. We recover this response function by dividing the FFT of the voltage response with the FFT of the input plane wave and take the inverse transform to light red curve. We note that the measured response function only goes out to 250\,ns since an FFT deconvolution determines the response function between $-\tau/2$ and $\tau/2$ for a $\tau$ lenght simulation. In order to check our measured response function, we perform a direct convolution of the response with the input plane wave and recover the red points.}
\label{fig:tSim}
\end{figure*}

%/Users/anguta/Documents/science/data/HERA_feed/reflectionGainFix.ipynb
\begin{figure*}
\includegraphics[width=\textwidth]{figures/freq_domain.pdf}
\caption{The absolute value of the fourier transform of our input plane wave (blue line) and the voltage response (green line). The 150\,MHz plane wave, modulated by a gaussian only probes a finite region of frequency space while the voltage response outside of this region is dominated by numerical noise above $\sim 1$\,GHz. It is this numerical noise that leads to the fine time-scale structure in the unfiltered response function in Fig.~\ref{fig:tSim}. To remove this noise, we multiply the ratio of the voltage output to the plane wave intput (red line) by a Blackman-Harris window (cyan line) to obtain the filtered response function (black line).}
\label{fig:freqDomain}
\end{figure*}

\begin{figure}
\includegraphics[width=.48\textwidth]{figures/response_fft.pdf}
\caption{The absolute value of the Fourier transform of the response function convolved with a 100\,MHz Blackman-Harris window to simulate the actual HERA bandpass.}
\label{fig:finalFilter}
\end{figure}

\begin{figure*}
\includegraphics[width=\textwidth]{figures/deconvolution_filtered.pdf}
\caption{Same as Fig.~\ref{fig:tSim} except now the Fourier domain ratio between the voltage response and input plane wave is multiplied by a 2 GHz Blackman-Harris window. }
\label{fig:tSimFiltered}
\end{figure*}

\section{Considerations of filtering and sampling and the affect on the visibility.}
We have obtained an estimate of the response function from our simulations. However, the signal undergoes filtering and sampling, the effects of which we will consider here.

Before being sampled, the signal is subjected to high and low-pass filtering to prevent aliasing. For HERA, the bandpass is centered at $\approx 150$\,MHz with a bandwidth of $\approx 100$\,MHz. The frequency response of the antenna after the analogue filtering step, $\widetilde{F}$ is 
\begin{equation}
\widetilde{v}_{out}(f) = \widetilde{R}(f) \widetilde{v}_{in}(f) \widetilde{F}(f)
\end{equation}
Sampling may be represented as multiplying the time-stream by a sampling function $s(t)$, 
\begin{equation}
s(t) = \sum_{m=-\infty}^{\infty} \delta_D(t-m \Delta t).
\end{equation}
Which corresponds to convolving with a Shah function in the Fourier domain. 
\begin{equation}
\widetilde{s}(f) =  \frac{1}{\Delta t} \sum_{m=-\infty}^{\infty} \delta_D \left(f - \frac{m}{\Delta t} \right)
\end{equation}
The F-step of the correlator takes place over a finite time interval which we will call $\tau$, leading to a convolution in the $f$ domain by a window function $\widetilde{W}_\tau(f)$. This window function is often quite narrow thanks to the employment of polyphase filtering. The output from the F-stage of the correlator, for the $i^{th}$ antenna, which we denote as $v_i$ is the input signal, multiplied by the antenna/analogue response function and the filter function and convolved with the sampling (shah) and the DFT window function. We assume in this note that all antenna have the same filter, sampling, and DFT window. 
\begin{equation}\label{eq:freqFull}
\widetilde{v}_i(f) = (( \widetilde{v}_{in}(f) \widetilde{R}(f) \widetilde{F}(f) ) \star \widetilde{s}(f) ) \star \widetilde{W}_\tau(f)
\end{equation}
For this analysis, we will assume that the analogue filter is sufficiently compact to prevent any aliasing and that the input spectrum $\widetilde{v}(f)$ along with the bandpass  is a constant over the width of $\widetilde{W}_\tau$. These two assumptions allow us to discard the convolutions in equation~\ref{eq:freqFull}
\begin{equation}
\widetilde{v}(f) \approx \widetilde{v}_{in}(f) \left[ \left( \widetilde{F} \widetilde{R} \right) \right](f) \equiv \widetilde{v}_{in}(f) \widetilde{g}
\end{equation}
Where $\widetilde{g}$ denotes the effective gain. If we assume that all antennas have the same response function, than the visibility formed from the product of two Fourier transformed voltage streams is
\begin{equation}\label{eq:vis}
v_{ij} = \widetilde{v}_i \widetilde{v}_j^* |\widetilde{F} \widetilde{R}|^2
\end{equation}
Strictly speaking, the delay response from the antenna element is a function of direction, and actually gives the frequency dependent beam in the direction of each source. 
\begin{equation}
v_{ij} = \int d \Omega I e^{2 \pi i {\bf b}_{ij} \cdot {\bf \hat{s}} } |\widetilde{F}|^2 A(f,{\bf \hat{s}})
\end{equation}
Where $|\widetilde{R}(f,{\bf \hat{s}})|^2$ is the beam of the antenna. In our analysis here, we are only considering the delay response to a plane-wave from zenith, so in predicting visibilities from this response, we are assuming that the antenna has the same frequency structure in all directions which is not in fact true. We are still in the process of simulating full beams and have run up against numerical precision issues.

For now, we assume $\widetilde{R}(f)$ is independent of direction and identical to the delay response function computed here. For $\widetilde{F}(f)$, we employ two Blackman-Harris windows with widths of $100$\,MHz centered at $150$\,MHz and $-150$\,MHz. This effectively eliminates any low frequency noise that may be present in our estimate of the response function as well. In Fig.~\ref{fig:dBresponse} we show the response function power level as a function of delay after applying this filter function. We see that it resembles a falling envelope multiplied by a $\sim$150\,MHz sinusoid. As we might expect from the voltage output in Fig.~\ref{fig:voltageResponse}, the power reaches $-35$\,dB at $\approx 60$\,ns. We also see that after $\approx 60$\,ns, the structure is dominated by lobed reflection structures that are spaced by $\approx 30$\,ns which corresponds to the round trip travel time between the feed and the bottom of the dish (which are separated by $\approx 5$\,m).

\begin{figure*}
\includegraphics[width=\textwidth]{figures/responses_db.pdf}
\caption{The time-domain power response function of the PAPER feed with a 100 MHz blackman Harris window centered at 150 MHz applied. The response functions have been shifted $\approx 30$\,ns to the left to account for the initial propogation time for the input wave packet to arrive at the feed. We have drawn a dashed black line at 60\,ns to ephasize the HERA spec of -60dB at 60\,ns. We find ourselves at $\approx -35$\,dB at 60\,ns.}
\label{fig:dBresponse}
\end{figure*}

\section{Implications for Power Spectrum measurements}

Our analysis of CST simulations indicates that the HERA dish+PAPER dipole+skirt does not meet the -60dB at 60\,ns spec. In this section we try to address the implications on our ability to isolate foregrounds within the wedge and measure the 21\,cm power spectrum. To do this, we use a bandpass derived from the response function in our CST simulations and compute foreground visibilities with the reflections using equation \ref{eq:vis}.

\subsection{Extrapolating the Response Function}

A critical limitation of our simulations is the limited extent of 250\,ns in the time domain. HERA is expected to have a frequency resolution of $\sim 100$\,kHz. To fully simulate the antenna gain to this resolution would require a simulation run on the order of $10^4$\,ns long, 40 times longer than its current length. As a result, we are forced to extrapolate the response function beyond $200$\,ns. While there is obviously enormous uncertainty in this extrapolation, the fact that the structure beyond $\approx 70$\,ns appears to be dominated by reflections provides us with a physically motivated framework for performing such an extrapolation; a wave having undergone $m$ reflections will decay in amplitude as $r^m$ where $r$ is the reflection coefficient. The number of reflections is proportional to delay, hence we  expect an exponential decay of the form
\begin{equation}\label{eq:pLaw}
R(\tau) \sim A r^\tau,
\end{equation}
for large $\tau$. We extrapolate the response function by tiling two reflection lobes from within the 250\,ns simulation span multiplied by a fit of equation \ref{eq:pLaw} to  the envelope for $t>70$\,ns. Interestingly enough, the best fit $r$ in our simulations for a 30\,ns reflection is quite large, $\approx 0.60$. In order to test the robustness of our extrapolation results, we also generate a response function with a time constant that is three times smaller than the fitted value, significantly accelerating the rate of reflection die off predicted by the simulaton. We also investigate whether the existing spec of -60\,dB at 60\,ns is sufficient in our simulations by scaling the simulated response function over 250\,ns by a power law that forces it to exactly exactly meet the spec and extrapolate as before. We show the extrapolated response functions for these three approaches in Fig.~\ref{fig:extrapolated}. We note that the extrapolated power law in the response function that meets the spec is less steep than the steep extrapolated power law.

\begin{figure*}
\includegraphics[width=.33\textwidth]{figures/response_extrapolated.pdf}
\includegraphics[width=.33\textwidth]{figures/response_steep_extrapolated.pdf}
\includegraphics[width=.33\textwidth]{figures/response_spec_extrapolated.pdf}
\caption{Here we show the envelope of the magnitude of the response function convolved with a Blackman-Harris filter with FWHM $100$\,MHz centered at $150$\,MHz (blue points). We extend the simulation to arbitrary delays by copying the reflection structure from the simulation multiplied by an exponential (thick black line) to get the red line. We test the robustness of our predictions by decreasing the time constant by a factor of 3 (middle) and also scaling the simulated magnitudes by a power law so that they exactly meet the -60dB at 60\,ns spec (right).}
\label{fig:extrapolated}
\end{figure*}

\subsection{Simulations of Foreground Power Spectra}

From the extrapolated response function, we obtain an effective bandpass for the instrument by Fourier transforming into the frequency domain. We show the amplitude and phase of the effective bandpass in our fiducial extrapolation in \ref{fig:extBandpass}.

\begin{figure*}
\includegraphics[width=\textwidth]{figures/bandpass.pdf}
\caption{The bandpass between 100 and 200\,MHz calculated by taking the FFT of the 100\,MHz Blackman-Harris filtered response function extrapolated to $100\mu$s. }
\label{fig:extBandpass}
\end{figure*}

 We simulate visibilities with foregrounds in equation~\ref{eq:vis} by combining point sources from the MWACS catalogue \citep{HurleyWalker:2014} with the desourced Haslam map \citep{Remazeilles:2015} extrapolated to low frequency using a spectral index of $-0.5$. For the angular beam, we use an Airy function with a 14-m aperture. We generate visibilities for an E-W line 19 antennas phased to zenith with an LST of 4 hours and lat of -27 degrees, corresponding to the MWA EoR-01 field viewed from the MRO. We show our beam pattern and diffuse foregrounds in Fig.~\ref{fig:foregrounds}.

\begin{figure*}
\includegraphics[width=.48\textwidth]{figures/beam.png}
\includegraphics[width=.48\textwidth]{figures/diffuse.png}
\caption{The Airy primary beam used in these simulations (left) along with the diffuse foregrounds (right).}
\label{fig:foregrounds}
\end{figure*}

From these visibilities, we generate delay power spectra a-la \citep{Parsons:2014} using the formula
\begin{equation}
\widehat{P}(k) = \left( \frac{\lambda^2}{2 k_B} \right)^2 \frac{X^2 Y}{\Omega B} \left| \widetilde{V}(u,v,\tau) \right|^2,
\end{equation}
where $\lambda$ is the wavelength, $k_B$ is the Boltzmann constant, $\Omega$ is the effective beam solid angle given by $\Omega = \int A d\Omega$, $B$ is the bandwidth. $\widetilde{V}$ is the delay-transform of each visibility in frequency. 
\begin{equation}
\widetilde{V}(u,v,\eta) = \int d f V( {\bf b}f_0/c = {\bf u},f)e^{-2 \pi i f \tau}
\end{equation}
where $f_0$ is the center frequency of the band over which the delay transform is being taken. We perform the simulation over 16\,MHz centered at $150$\,MHz with a Blackman-Harris window applied to the DFT.  We show the foreground power spectra compared to 21cmFAST signal at $z=8$ In Fig.~\ref{fig:visPS} compared with the level of foregrounds for a flat bandpass smallest HERA baseline at $u_\lambda = 7.4$. To get a sense of how foreground subtraction without knowledge of the antenna spectral response might preform, we also form a power spectrum from the difference between visibilities with the spectral response of the antenna and a flat spectral response. We find that for the spectral response extrapolations that do not meet the HERA spec, the foreground residual is significantly above the level of the signal out to $k_\parallel \approx 0.2-0.25h$Mpc$^{-1}$.

\begin{figure*}
\includegraphics[width=.33\textwidth]{figures/delay_response_compare.pdf}
\includegraphics[width=.33\textwidth]{figures/delay_response_compare_steep.pdf}
\includegraphics[width=.33\textwidth]{figures/delay_response_compare_spec.pdf}
\caption{The foreground power spectrum for the smallest HERA baseline with a flat bandpass (solid blue line) and the antenna response function (solid green line). The horizon + a 0.1 $h$Mpc$^{-1}$ buffer is denoted by the vertical black line. The residual visibility obtained from subtracting the foreground visibiliteis with a flat response function (as we might expect from model subraction) (red dashed line) is shown for our extrapolated response function (left), the steep response function (middle) and the response function forced to meet spec (right). For the response functions that do not meet the HERA spec, residuals after foreground subtraction remain above the signal level out to $k_\| \approx 0.2-0.25 h$Mpc$^{-1}$. In the response function that does meet the spec, residuals pass below the signal at $k_\| \approx 0.2 h$Mpc$^{-1}$.  }
\label{fig:visPS}
\end{figure*}

We next bin spherically to obtain 1d power spectra from our foreground subtracted visibilities, excluding the wedge plus a 0.07 $h$Mpc$^{-1}$ buffer. As we might expect from our smallest $u_\perp$ power spectrum, the spherical power spectra of foreground residuals with the response functions that do not meet the -60dB at 60\,ns spec exceed the signal at $k\gtrsim 0.2h$Mpc$^{-1}$ and only falling below $10\times$ the signal level at $0.25-0.30h$Mpc$^{-1}$ (Fig.~\ref{fig:ps1d}).

\begin{figure*}
\includegraphics[width=.33\textwidth]{figures/hera_1dPower_EoR_feed.pdf}
\includegraphics[width=.33\textwidth]{figures/hera_1dPower_EoR_feed_steep.pdf}
\includegraphics[width=.33\textwidth]{figures/hera_1dPower_EoR_feed_spec.pdf}
\caption{Spherically binned power spectra excluding the wedge plus a 0.07 $h$Mpc$^{-1}$ buffer of the 21\,cm signal (black line) and the visibilities resulting from the subtraction of a foreground model without the delay response of the instrument (blue line). In the left panel, we show the residuals for the delay response extrapolated by an exponential, in the middle an exponential with a steep ($\times 3$ time constant, and the right, the response function scaled by a power law so that it meets the -60\,dB at 60\,ns spec.}
\label{fig:ps1d}
\end{figure*}

\section{The Efficacy of Delay Cleaning in the Presence of Reflections.}
In the previous sections, we considered the subtraction of a perfect foreground model with no knowledge of the Dish's spectral response. Since it is unlikely that a sub-percent accurate foreground model will exist in the near future, this assumption is highly unrealistic. We begin to replicate the expected foreground leakage in an actual analysis by simulating the foreground cleaning analysis employed bye PAPER. This work is ongoing and we describe some initial steps in this section.

Foregrounds are simulated over a wide bandpass between 100 and 200\,MHz. Visibilities are Fourier transformed into delay space with a Blackman-Harris window function. The {\tt aipy.deconv.clean} method is used to clean with a delta function kernel within a clean box equal to the wedge plus a $0.1 h$\,Mpc$^{-1}$ buffer. The residuals are transformed back into frequency space and delay power spectra are formed from a 150-158\,MHz subband.

\begin{figure*}
\includegraphics[width=.48\textwidth]{figures/delay_response_compare_cleaned.pdf}
\includegraphics[width=.48\textwidth]{figures/delay_response_compare_cleaned_deep.pdf}
\caption{Left: The foregrounds power spectrum formed from a $150-158$\,MHz subband. Blue and Green lines denote the Foregrounds with and without the delay response of the dish respectively. The Dashed red line shows the power spectrum residual of the foregrounds while the cyan line shows the power spectrum residuals with the antenna response. Cleaning was performed with a tolerance of $10^{-3}$. We see that at $10^{-3}$ tolerance, the region of Fourier space that is foreground free is identical with and without the reflections but extends to $k \approx 0.3$\,$h$Mpc$^{-1}$. Right: The same as the left except cleaning is performed with a tolerance of $10^{-5}$. When cleaning much deeper, one is able to remove foregrounds to lower $k_\parallel$ however the reflections continue to contaminate out to $0.3$\,$h$Mpc$^{-1}$ regardless of the clean depth. }
\label{fig:PSCleaned}
\end{figure*}

 In Figure~\ref{fig:PSCleaned} we compare the residuals from cleaning with and without the delay response of the dish included. We find that the extent to wich the delay response matters depend heavily on the clean depth which will in turn depend on the level of integration performed before cleaning. If cleaning occurs with a tolerance of $10^{-3}$ then foregrounds, with or without the reflections, dominate the signal out to $k_\parallel \approx 0.3$\,$h$Mpc$^{-1}$. If cleaning with a tolerance of $10^{-5}$ occurs, than the foregrounds is performed, than without the reflection, the region of Fourier space down to $k_\parallel \approx 0.2$\,$h$Mpc$^{-1}$ opens up. We note that this requires the score difference between clean steps to be within an order of magnitude of the signal which is not expected to occur on a single baseline, even a redundant one. Integrating deeply enough on a single redundant baseline to perform such a clean may be a driver for expanding beyond HERA-331, even if the additional antennas do not directly add much sensitivity.

\section{Conclusions and Caveats.}

Our numerical results show that the delay response of the HERA dish misses the -60\,dB at 60\,ns spec by a factor of $\sim 10^3$. While the choice of filtering function has a significant impact on our estimate of the response function, we have chosen a fairly conservative Blackman-Harris window and the actual voltage stream in response to the plane-wave input (Fig.~\ref{fig:voltageResponse}) agrees with our $-35$\,dB at 60\,ns estimate quite well.

What is far more uncertain is the actual impact on the power spectrum. Our extrapolation framework is physically sensible and our predictions do not appear to change much with significant modifications to our extrapolation time constant, hence we consider our predictions robust against this degree of freedom. Our prediction of foreground contamination on the other hand, incorporates a very specific subtraction analysis that assumes perfect knowledge of the foregrounds and no knowledge of the frequency dependent gain; both incorrect assumptions for a real measurement. On the other hand, we have only considered the spectral response of the dish towards zenith and ignored the angular variation in the spectral structure of the beam which is likely to be more significant in the side-lobes (and closer to the edge of the wedge), leading us to believe that the projections here may actually be overly optimistic.

\begin{comment}

We attempt to model the the full angular dependence of the frequency dependent gain in the next section, however the numerical resolution issues in CST's beam estimation lead us to be somewhat wary of these results.

\section{CST simulations of the primary beam.}\label{sec:beamSim}

We investigate the full chromaticity of the PAPER feed+dish+skirt arrangement by computing the directivity of the X-polarized dipole arms in CST. The directivity is computed at spacings of 1 degree in polar coordinates $\theta$ and $\phi$ with 100\,kHz spectral resolution between 145 and 155\,MHz. Due to numerical precision issues, the frequency dependent gains computed in CST are found to have step-like structures on the order of several\,kHz wide. To circumvent this problem, we interpolate between beam slices that are 1\,MHz apart using both polynomial fitting (to 7th order) and cubic spline interpolation. Since the resolution issue can shift the beam values up to several hundred kHz, there may still be resolution-induced structure in the gains. In Fig.~\ref{fig:beamPlot} we illustrate the frequency structure of different lines of sight through the beam. After being fit to cubic-spline interpolated functions and 7th order polynomials, the delay transform of the frequency dependences does appear to exceed the level of a flat Blackman-Harris window by $\approx 20$\,dB at $k \approx 0.2$\,hMpc$^{-1}$, the region where we expect to obtain maximal EoR sensitivity.

A significant problem with this calculation beyond the deficiency in frequency resolution and need for interpolation is the use of nearest neighbor interpolation of the primary beam in the angular direction. Since the delay transform mixes angular structure into frequency (which is a staircase in nearest neighbors), this could also cause nasty artifacts.

\begin{figure*}
\includegraphics[width=\textwidth]{figures/beam_plot.pdf}
\caption{Left Column: line of sight cuts through simulations of the HERA XX-polarized primary beam derived using CST. The original simulations were run at 100\,kHz resolution, however the decimal point precision forces us to use interpolation between 1\,MHz slices. The dots show simulation points, solid lines indicate cubic spline interpolation and dashed lines denote 7th order polynomial fits which tend to have several \% residuals. In the middle column, we show the delay kernel of the LoS cuts. The thick black line indicates the enveloping Blackman-Harris window function. The polynomial and cubic-spline fits tend to produce excess power above 0.4 h/Mpc. In the right column we show the locations of our frequency cuts on the primary beam. }
\label{fig:beamPlot}
\end{figure*}

\begin{figure*}
\includegraphics[width=.48\textwidth]{figures/beam_poly_compare.pdf}
\includegraphics[width=.48\textwidth]{figures/beam_interp_compare.pdf}
\caption{(left): The power spectrum on the smallest HERA baseline for the polynomial interpolated beam (in frequency). (Right): The power spectrum on a single visibility with the cubic spline interpolated beam}
\label{fig:visBeam}
\end{figure*}
\end{comment}

\bibliography{ms}

\end{document}

### 2016-02-23 DishSimulations/paper/DishSimulationsPaper_v2.tex

@@
 \includegraphics[width=.5\textwidth]{figures/s11_compare.pdf}
-\caption{A comparison between time-domain simulations (black lines) and measurements (grey lines) of $S_{11}$ for the HERA dish.
+\caption{A comparison between time-domain simulations (black line) and measurements (grey line) of $S_{11}$ for the HERA dish.
 We also show an $S_{11}$ measurement with the cables leading from the VNA to the feed terminated by an open circuit which allows us to probe the dynamic range of the measurement.
@@
 \subsection{Extrapolating the Bandpass and Power Kernel}\label{ssec:Extrapolation}
-Our deconvolution gives us the time-domain voltage response of the PAPER and HERA antenna elements.
-We plot the absolute value of this response in Fig.~\ref{fig:SimulationsCompare}, seeing that it drops to $-30$\,dB after $\approx 100$\,ns.
-The power-kernel that convolves visibilities to higher delays is the convolution of $\widetilde{r}(\tau)$ with its time-reversed complex conjugate, which we plot as the red line.
-The convolution is in very good agreement with the voltage response itself which is explained by the fact that second order terms of the convolution, approximately given by $|\widetilde{r}(\tau)|^2$ (green line) are over two orders of magnitude smaller above $50$\,ns.
 
-Our simulations of the Dish response only extend to $\approx 300$\,ns, however, we wish to understand the impact of reflections on the frequency dependent gain of an interferometer like HERA at comoving scales of $\approx 0.1-0.5$\,$h$Mpc$^{-1}$, corresponding to the delays between 180 and 900\,ns at $z=8$, extending beyond our simulations range.
+Our simulations of the Dish response only extend to $\approx 400$\,ns, however, we wish to understand the impact of reflections on the frequency dependent gain of an interferometer like HERA at comoving scales of $\approx 0.1-0.5$\,$h$Mpc$^{-1}$, corresponding to the delays between 180 and 900\,ns at $z=8$.
 To extrapolate out to higher delays, we assume that the response function is dominated by reflections between the feed and the dish.
-This is due to the fact that when we extend our filter bandwidth to between $50$ and $250$\,MHz and use a hamming window (which has higher resolution), we observe lobe-like structures at delays beyond $100$\,ns with a periodicity of $30$\,ns, which corresponds to the round-trip light travel time between the feed and the dish.
-In addition, the long term falloff appears as a line on a linear-log plot (Fig.~\ref{fig:Simulations}), indicating that the kernel follows an exponential which we now show is indicative of reflections.
-We do so by adopting the notation of \citep{Patra:2016}.
-We let $\Gamma_d$ represent the reflection coefficient of the Dish vertex and $\Gamma_f$ represent the reflection coefficient of the feed.
+The long term falloff appears as a line on a linear-log plot (Fig.~\ref{fig:SimulationResults}), indicating that the voltage response follows an exponential which we now show is indicative of reflections.
+We do so by adopting the notation of \citet{Patra:2016}, letting $\Gamma_d$ represent the reflection coefficient of the Dish vertex and $\Gamma_f$ represent the reflection coefficient of the feed.
 An electromagnetic wave incident on the feed, at $t=0$, is accepted with amplitude $(1-\Gamma_f)$.
-The reflected component travels back to the dish and acquires an amplitude of $(\Gamma_f \Gamma_d)$ before returning at time, $\tau_d$ later where $(1-\Gamma_f)$ will be accepted and so forth.
-The time dependent voltage at the feed from these reflections is thus
+The reflected component travels back to the dish and acquires an amplitude of $(\Gamma_f \Gamma_d)$ before returning at time, $\tau_d$ later where $(1-\Gamma_f)$ will be accepted and $\Gamma_f$ will be reflected back towards the dish.
+Summing the infinite series of reflections, the time dependent voltage at the feed is
 \begin{equation}
@@
 \end{equation}
-which is a power law. We thus model our discrete voltage response beyond the times sampled by our simulations as a power law
+which is an exponential in time. We thus model our discrete voltage response beyond the times sampled by our simulations as an exponential
 \begin{equation}
@@
 \end{equation}
-We plot the best power-law fit as a dashed line inf Fig~\ref{fig:SimulationsCompare}.
-%We fit our voltage response function and power-kernel to this function, finding a best fit model for the voltage kernel of $A\approx0.95$,$X \approx 0.18$, and $Y\approx 0.58$.
-The large $Y$ is unrepresentative of the feed reflection coefficient which has been simulated and measured to be $\approx 0.1$ for a head-on EM wave, suggesting that the reflections are arriving from the sides and potentially involve only a small component of the dish and feed.
-Plotting the die off for the feed reflection coefficient yields dramatically better performance than what is measured.
-If the reflections are indeed originating from the sides, and a small component of the dish and feed arrangement, further suppression may be achieved through modifying this component.
+and extrapolate the time-domain voltage response of the dish by fitting for $A$ and $X$ in our simulations between 200 and 400\,ns.
 
@@
 To answer this question, we combine our extrapolated simulations of the HERA dish's spectral structure with simulations of foregrounds.
-The foreground simulations are described fully in \citep{Thyagarajan:2016} but for the readers convenience we briefly describe them here.
 
-Our foreground model consists of two major components: diffuse synchrotron emission from our Galaxy whose structure is described by the Global Sky Model (GSM) of \citet{deOliveiraCosta:2008} and a population of point sources sourced by radio loud AGN which combines the NRAO Sky Survey (NVSS) \citep{Condon:1998} at 1.4\,GHz, the Sydney University Mologolo Sky Survey (SUMMS) \citep{Bock:1999} at 843\,MHz, and extrapolate point source fluxes to the observed $100$-$200$\,MHz band using a spectral index of $\langle \alpha \rangle=-0.83$ determined in \citet{Mauch:2003}.
-Visibilities are computed from the diffuse and point source models assuming the achromatic HERA beam computed at $150$\,MHz and described in \citep{Neben:2016}.
-We compute two sets of visibilities: one in which the spectral structure of the dish is assumed to be completely flat, and another in which the beam is multiplied by the Dish's frequency dependent gain at zenith.
-While this model assumes incorrectly that the frequency evolution of the primary beam is identical along all lines of sight, the majority of power enters at the beams point of maximal gain (zenith) and observations of autocorrelations which reflect the angular average of the frequency dependence of all lines of sight agree well with our simulations at zenith \citep{Patra:2016}.
+The foreground model is discussed in detail in \citet{Thyagarajan:2016} but we describe them briefly here for the readers convenience.
+It consists of two major components: diffuse synchrotron emission from our Galaxy whose structure is described by the Global Sky Model (GSM) of \citet{deOliveiraCosta:2008} and a population of point sources sourced by radio loud AGN.
+The point sources include those observed in both the NRAO Sky Survey (NVSS) \citep{Condon:1998} at 1.4\,GHz and the Sydney University Mologolo Sky Survey (SUMMS) \citep{Bock:1999} at 843\,MHz.
+Their fluxes are extrapolated to the observed $100$-$200$\,MHz band using a spectral index of $\langle \alpha \rangle=-0.83$ determined in \citet{Mauch:2003}.
+Visibilities are computed from the diffuse and point source models assuming an achromatic angular response for the HERA beam computed at $150$\,MHz described in \citet{Neben:2016}.
+We compute two sets of visibilities: one in which the spectral structure of the dish is assumed to be completely flat, and another in which the beam is multiplied by the frequency dependent gain at zenith determined by our simulations.
+While this model assumes incorrectly that the frequency evolution of the primary beam is identical along all lines of sight, the majority of power enters at the beams point of maximal gain and observations of autocorrelations which reflect the angular average of the frequency dependence of all lines of sight agree well with our simulations at zenith \citep{Patra:2016}.
 
-The foreground filtering procedure employed by PAPER and HERA involves delay transforming the visibilities on a short time-scale cadence and performing a 1d delay CLEAN where the deconvolution is permitted to discover and subtract foregrounds within the horizon to horizon delay.
-Since we want to avoid CLEANing noise, the level of foreground subtraction possible by this procedure is limited by the thermal noise level on the visibility, which in terun depends on the number of time steps and redundant baselines that are averaged before performing the cleaning step.
-In this work, we assume that each visibility is cleaned independently with a two minute CLEANing cadence which corresponds approximately to the time over which HERA's short baselines are coherent.
-The standard deviation on the real and imaginary part of a single delay transformed visibility is given by \citep{Morales:2004}
+The foreground filtering procedure employed by PAPER and HERA involves delay transforming the visibilities and performing a 1d clean which discovers and subtract foregrounds within the horizon plus a small buffer, allowing for the suppression of foreground side-lobes in delay space.
+The level of foreground subtraction possible by this procedure is limited by the thermal noise level on the visibility, which in turn depends on the number of time steps and redundant baselines that are averaged before performing the cleaning step.
+In this work, we assume that each visibility is cleaned independently with a twenty minute cadence.
+Each baseline is coherent for $\approx 10$\,s per night, hence we assume that each baseline and LST is being integrated for $\approx 120$\,nights before cleaning although if we were to average over redundant baselines this number would drop enormously.
+The standard deviation on the real and imaginary part of a single delay transformed visibility is \citep{Morales:2004}
 \begin{equation}
-\Delta V = \frac{\sqrt{2 B} k_B T_{sys}}{A_e \sqrt{\tau}}
+\sigma_V = \frac{\sqrt{2 B} k_B T_{sys}}{A_e \sqrt{\tau}},
 \end{equation}
 where $A_e$ is the effective area of the dish, $B$ is the bandwidth, $T_{sys}$ is the system temperature, $\tau$ is the integration time, and $k_B$ is the Boltzmann constant.
-The system temperature can be calculated by assuming that $T_{sys} = 100\text{K} + T_{sky}$ where $100$\,K is the temperature of the PAPER reciever and $T_{sky} = 60 (\lambda/1\,\text{meter} )^{2.55}$ is the sky temperature \citep{Fixsen:2011}.
-For $A_e$ we use the value of $75$\,m determined in \citep{Neben:2016}.
-If we assume that each baseline is cleaned independently and that the integration time is $\tau \approx 60$\,s, than the noise level at 150\,MHz is approximately $9.9$\,Jy\,MHz.
-In order to avoid subtracting noise, we assume that cleaning is performed down to $5\,\sigma$.
-In Fig~\ref{fig:Cleaning} we compare the delay transform of visibilities before and after cleaning on a two minute cadence at the LST of 4 hours.
-While cleaning is able to remove structure within the horizon, it does not reduce any of the power associated with the foreground induced by the chromaticity of the dish.
+For $T_{sys}$ we use the equation $T_{sys} = 100\text{K} + T_{sky}$ where $100$\,K is the temperature of the PAPER receiver and $T_{sky} = 60 (\lambda/1\,\text{meter} )^{2.55}$ is the sky temperature \citep{Fixsen:2011}.
+For $A_e$ we use the value of $98$\,m$^2$ determined in \citet{Neben:2016}.
+We assume that cleaning is performed down to five times the thermal noise level.
+In Fig~\ref{fig:Cleaning} we compare the delay transform of visibilities before and after cleaning at the LST of 4 hours.
+While cleaning is able to remove structure within the horizon, it does not reduce any of the power leaked outside of the horizon by the chromaticity of the dish.
 
-To form estimates of the 21\,cm power spectrum, we split each visibility into BlackmanHarris windowed sub-bands centered at redshift intervals of $\Delta z = 0.5$ and each with an equivalent bandwidth of $10\,MHz$, corresponding to the redshift interval over which the statistics of the brightness temperature fluctuations are expected to be stationary.
-For each windowed interval, we use the flat sky approximation and  Fourier transform in frequency, square, and multiply by a set of prefactors to obtain a power spectrum estimate \citep{Parsons:2014},
+To form estimates of the 21\,cm power spectrum, we split each visibility into Blackman-Harris windowed sub-bands centered at redshift intervals of $\Delta z = 0.5$ and each with a power equivalent bandwidth of $10$\,MHz\footnote{The end to end width of each Fourier transformed interval is 20\,MHz, however the effective width of this interval is only $\approx 0.5$ the full width since the Blackman-Harris window supresses the edge channels.}, corresponding to the redshift interval over which the statistics of the brightness temperature fluctuations are expected to be stationary.
+The flat sky approximation allows us to Fourier transform each interval in frequency, square, and multiply by a set of prefactors to obtain a power spectrum estimate \citep{Parsons:2014},
 \begin{equation}\label{eq:PS}
@@
 \end{equation}
-Here, $\lambda$ is the central wavelength of the observation, $k_B$ is the Boltzmann constant, $B$ is the bandwidth of the Fourier transform, and $\Omega_{pp}$ is the integrated solid angle of the primary beam squared.
-$X$ is a linear factor converting between $uv$ wavelengths and $k_\perp$, and $Y$ is a linear factor converting between $k_\parallel$ and the Fourier dual to frequency, $\eta$.
+Here, $\lambda$ is the central wavelength of the observation, $k_B$ is the Boltzmann constant, $B_{pp}$ is the integral of the square of the bandpass, and $\Omega_{pp}$ is the integral of the primary beam squared over solid angle.
+$X$ and $Y$ are linear factors converting between native interometry and cosmological coordinates, defined through the relation $2 \pi {\bf u}=2 \pi (u,v,\eta) = (X k_x, X k_y, Y k_z)$.
 
 A drift scan instrument, HERA will be capable of observing the sky at any LST within the strip declination that passes through its primary beam.
-To form a final power spectrum estimate, it is expected to perform an average over the power spectrum estimates it obtains through equation~\ref{eq:PS} for each LST independently.
-It is well documented that foreground power is maximized over certain LST ranges \citep{Thyagarajan:2015a}, hence such an estimate will either filter or weight appropriately the LSTs in which foreground power is maximized.
-\citet{Thyagarajan:2016} focuses on the optimal weighting and selection of LST bins in forming a power spectrum estimate.
-For the purpsoes of our analysis, we focus on a single, relatively clean LST of 4 hours which includes the coldest part of the sky.
+To form a final power spectrum estimate, it is expected to perform an average over the power spectrum estimates for each LST.
+It is well documented that foreground power varies significantly over LST \citep{Thyagarajan:2015a}, hence such an estimate will either filter or weight LSTS in a way that minimizes the impact of the most contaminated observations.
+For our analysis, we focus on a single LST of 4 hours which points out of the galactic plane and represents a relatively clean pointing similar to those we expect for HERA to concentrate its observing time on.
 
@@
 
-Computing the power spectra, we inspect the amplitude of foregrounds given the chromaticity and angular pattern of the HERA dish for several different baselines.
-We first inspect a $14.6$ and $29.2$ meter baseline in Fig.~\ref{fig:BothBaselines} and find that significant regions of the visibility are foreground free.
+Computing the power spectra, we inspect the amplitude of foregrounds given the chromaticity and angular pattern of the HERA dish for baselines of two different lengths in Fig.~\ref{fig:BothBaselines}.
 In both baselines, we find that the residuals after cleaning tend to be at similar levels except at the subband centered at $z=8.5$ (150\,MHz), in which foreground residuals remain above the signal level out to $k_\parallel=0.23$\,$h$Mpc$^{-1}$.
-Several other baselines especially those oriented entirely in the E-W direction, which we do not show, contain up to two orders of magnitude greater foreground contamination as is noted in \citep{Thyagarajan:2015b}.
-In a real power spectrum analysis, these baselines would be down-weighted or discarded so that they do not bias our final estimate.
+Several other baselines especially those oriented entirely in the E-W direction, which we do not show, contain up to two orders of magnitude greater galactic  contamination as is noted in \citet{Thyagarajan:2015b}.
+In an analysis, these baselines would be down-weighted or discarded so that they do not bias our final estimate.
 
-The level of the foregrounds in Fig.~\ref{fig:BothBaselines} was derived with no attempt to apply inverse covariance weighting \citep{Parsons:2014,Ali:2015} or fringe rate filtering \citep{Parsons:2015}.
-In order to avoid biases in a maximum likelihood analysis that determines astrophysical and cosmological parameters from our power spectra, the foregrounds should ideally be below the anticipated level of thermal noise which is shown in \citep{Pober:2014} to be on the order of a few percent the anticipated level of the cosmological signal for the full HERA deployment.
-Hence, as long as we can suppress our foregrounds below 1-10\,\% the signal level, they should not interfere significantly with a maximum likelihood analysis.
+The level of the foregrounds in Fig.~\ref{fig:BothBaselines} is conservative since no attempt has been made to apply inverse covariance weighting techniques \citep{Tegmark:1997a,Liu:2011,Dillon:2013,Parsons:2014,Liu:2014a,Liu:2014b,Dillon:2015a,Dillon:2015b,Trott:2016} or fringe rate filtering \citep{Parsons:2015}.
+In order to avoid biases in a maximum likelihood analysis that determines astrophysical and cosmological parameters from our power spectra, the foregrounds should ideally be below the anticipated level of thermal noise which is shown in \citet{Pober:2014} to be on the order of a few percent the anticipated level of the cosmological signal for the full HERA deployment.
+Hence, as long as we can suppress our foregrounds below $\approx 1$\% the level of the signal, they should not interfere significantly with a maximum likelihood analysis.
 Thus, the residuals in Fig.~\ref{fig:BothBaselines} serve as a specification for any inverse covariance weighting pipeline which will need to suppress foregrounds by between a factor of $\sim 1-10$ to bring the worst contaminated regions below the level of the signal.
-Applications of inverse covariance filters in recent PAPER observations have yielded improvements at and above this level, hence our simulations show that even with the presence of beam chromaticity, HERA will be able to isolate foregrounds below below the level of thermal noise in most of the EoR window.
+Applications of inverse covariance filters in recent PAPER observations have yielded improvements at and above this level {\bf \color{red} citation?}, hence our simulations show that even with the presence of beam chromaticity, HERA will be able to isolate foregrounds below the level of thermal noise in most of the EoR window.
 
@@
 \includegraphics[width=\textwidth]{figures/ps_compare_nithya_bothBaselines.pdf}
-\caption{}
+\vspace{-24pt}
+\caption{The delay transform power spectrum for different baselines over several redshifts with (green solid line) and without (blue solid line) the presence of the simulated chromaticity in the HERA dish.
+Each estimate is computed using the square of a Blackman-Harris windowed  delay transform (equation~\ref{eq:PS})) over an equivalent power bandwidth of $10$\,MHz.
+We also show the power spectra of foreground residuals after cleaning the entire $100$\,MHz band with (dashed cyan line) and without (red dashed line) the beam spectral structure.
+For all subbands except $z=8.5$, we find that the reflections in the HERA dish have a negligible effect on the $k_\parallel$ where the foregrounds drop below the signal level.
+This is the same subband where enhanced spectral structure due to reflections are observed in our simulations (Figs.~\ref{fig:KernelsSubbands} and \ref{fig:Residuals}).}
 \label{fig:BothBaselines}
@@
 
-%\begin{figure*}
-%\includegraphics[width=\textwidth]{figures/ps_compare_nithya_lst4hr_1024ch_7p3ew_12p6ns.pdf}
-%\caption{The power spectrum computed from the delay transform of a 14.6 meter baseline in equation~\ref{eq:PS} with (solid green line) and without (solid blue line) the presence of reflections in the HERA dish.
-The residuals after cleaning within the dashed black lines down to three times the level of thermal noise after 20 minutes of integration with (dashed cyan) and without (red dashed) the dish chromaticity are also plotted.
-We find that for this short baseline, clean residuals are on a similar level as the 21\,cm signal (solid black line), indicating that a redesign of the array with fewer short baselines may be necessary to maximize its sensitivity on foreground free modes.}
-%\label{fig:shortBaseline}
-%\end{figure*}
-
-%\begin{figure*}
-%\includegraphics[width=\textwidth]{figures/ps_compare_nithya_lst4hr_1024ch_14p6ew_25p3ns.pdf}
-%\caption{The same as Fig.~\ref{fig:shortBaseline} except now for a 29.2 meter baseline.
-We see that the level of foregrounds is down relative to our 14.6 meter baseline by two orders of magnitude, likely due to the fact that we are now outside of the region with significant contamination from the Galaxy.
-The presence of reflections tends to extend the $k_\parallel$ at which foregrounds drop below the level of the signal between $k_\parallel=0.15$\,$h$Mpc$^{-1}$ and $k_\parallel=0.22$\,$h$Mpc$^{-1}$ with the most severe contamination occurring at the $z=8.5$ subband where the reflections where observed to be worst in Fig.~\ref{fig:KernelsSubbands}.
-}
-%\label{figure:shortBaseline}
-%\end{figure*}
-
-%\begin{figure*}
-%\includegraphics[width=\textwidth]{figures/ps_compare_nithya_lst4hr_snrVbaselineMedian.pdf}
-%\caption{The median of the ratio between foreground residuals with the chromaticity of the HERA primary beam between $k_\parallel=0.15$\,$h$Mpc$^{-1}$ and $k_\parallel=1.0$\,$h$Mpc$^{-1}$, the range of k values over which HERA will derive the majority of its sensitivity.
-We see that the shortest baselines tend to have relatively low signal to foreground ratios due to the presence of high amplitude Galactic synchrotron emission.}
-%\label{fig:Medians}
-%\end{figure*}
-
 \subsection{The Implications of Dish Reflections on EoR Science}\label{ssec:Science}
-The primary goal 21\,cm EoR observations is to obtain information about the nature of the sources that drove reionization.
-Since the amplitude of the 21\,cm signal is maximal at smaller $k$ values, a loss of large scale signal due to foreground leakage eliminates the the modes that HERA would otherwise have the greatest signal to noise detections, impacting our overall sensitivity and its ability to derive this information.
-In this section, we estimate the impact of foreground leakage on HERA's sensitivity along with its ability to determine the astrophysics of reionization.
-We do so using the Fisher Matrix formalism.
-The Fisher Matrix allows us to forecast the covariances and errors on reionization parameters given errors on power spectrum observations due to the uncertainties caused by thermal noise which is in turn determined by the $uv$ coverage and observing time of the interferometer.
-The covariance between the parameters of some model ${\bf \theta}$ is given by the inverse of the Fisher matrix, ${\bf F}$ which for Gaussian and independently determined power spectrum bins may be written approximately as \citep{Pober:2014,EwallWice:2015a},
+A primary near-term goal of 21\,cm EoR observations is to obtain information about the nature of the sources that drove reionization.
+Since the amplitude of the 21\,cm signal is maximal at smaller $k$ values, a loss of large scale signal due to foreground contamination eliminates the the modes that HERA would otherwise have the greatest signal to noise detections of, reducing its overall sensitivity.
+In this section, we use the Fisher Matrix formalism to estimate the impact of foreground leakage on HERA's sensitivity along with its ability to determine the astrophysics of reionization.
+The Fisher Matrix allows us to forecast the covariances and errors on reionization parameters given errors on power spectrum observations due to the uncertainties caused by cosmic variance and thermal noise which is in turn determined by the $uv$ coverage and observing time of the interferometer.
+The covariance between the parameters of some model ${\bf \theta}$ is given by the inverse of the Fisher matrix, ${\bf F}$ which for Gaussian and independently determined power spectrum bins may be written approximately as \citep{Pober:2014},
 \begin{equation}\label{eq:Fisher}
@@
 where $\Delta^2(k,z)$ is the power spectrum amplitude for some $k-z$ bin and $\sigma^2(k,z)$ is the variance of the power spectrum estimate in that bin due to thermal noise and cosmic variance \citep{Beardsley:2013}.
+We write this equation as approximate since it ignores terms arising from the dependence of $\sigma^2(k,z)$ on model parameters due to cosmic variance but only contribute at the $\approx 1$\% level \citep{EwallWice:2015b}.
 
- we use the publicly available {\tt 21cmFAST} code \citep{Mesinger:2011} which generates realizations of the 21\,cm brightness temperature field using the excursion set formalism of \citet{Furlanetto:2004}.
-We employ a popular three parameter model of reionization \citep{Mesinger:2012,Pober:2014,Greig:2015,Liu:2015} with the following variables
+To simulate $\Delta^2$, we use the publicly available {\tt 21cmFAST}\footnote{\url{http://homepage.sns.it/mesinger/DexM___21cmFAST.html}} code \citep{Mesinger:2011} which generates realizations of the 21\,cm brightness temperature field using the excursion set formalism of \citet{Furlanetto:2004}.
+We employ a popular three parameter model of reionization \citep{Mesinger:2012} with the following variables
 \begin{itemize}
-\item ${\bf \zeta}$: The ``ionization efficiency" is defined in the \citep{Furlanetto:2004} excursion formalism to be the inverse of the mass collapse fraction necessary to ionize a region and is computed from a number of other physical parameters such as the fraction of collapsed baryons that form stars and the UV photon escape fraction.
+\item ${\bf \zeta}$: The ``ionization efficiency" is defined in the \citet{Furlanetto:2004} excursion formalism to be the inverse of the mass collapse fraction necessary to ionize a region and is computed from a number of other physical parameters including the fraction of collapsed baryons that form stars and the UV photon escape fraction.
 Because $\zeta$ acts as an efficiency parameter, its primary affect is to change the timing of reionization.
@@
 \item ${\bf T_\text{vir}^\text{min}}$: The minimal mass of dark matter halos that hosted ionizing sources.
-While in principle, halos with virial temperatures as small as $10^2$\,K are though, in principle, to be able to form stars, thermal and mechanical feedback have been seen to raise this limit to as high as $10^5$\,K.
-We choose a fiducial value of $T_\text{vir}^\text{min} = 1.5\times 10^4$\,K which is set by the atomic line cooling thresshold.
+While in principle, halos with virial temperatures as small as $10^2$\,K are thought to be able to form stars \citep{Haiman:1996a,Tegmark:1997c}, thermal and mechanical feedback have been seen to raise this limit to as high as $10^5$\,K \citep{Springel:2003,Mesinger:2008,Okamoto:2008}.
+We choose a fiducial value of $T_\text{vir}^\text{min} = 1.5\times 10^4$\,K which is set by the atomic line cooling threshold.
 \end{itemize}
 In order to account for the degeneracies in the power spectrum between heating from X-rays and reionization from UV photons, we also marginalize over three additional parameters that describe the impact of heating from early X-ray luminous sources as explored in \citep{EwallWice:2015b}.
-These are the X-ray heating efficiency $f_X$, the maximal energy of X-ray photons that are self absorbed by the ISM of early galaxies, $\nu_\text{min}$, and the spectral slope, $\alpha$ which are taken to have fiducial values of $1$,$0.3$\,keV, and $-1.2$ respectively.
-We choose to parameterize our model in terms of the fractional differences of each parameter from their fiducial values so that, for example, $\theta_\zeta = (\zeta - \zeta_\text{fid})/\zeta_\text{fid}$ and compute the derivatives in equation~\label{eq:Fisher} by performing a linear fit to realizations of the 21\,cm power spectrum calculated by {\tt 21cmFAST} at $\theta_i= \pm 10^{-2}, \pm 5\times 10^{-2}, \pm 10^{-1}$,and $ \pm 2 \times 10^{-2}$.
+These are the X-ray heating efficiency $f_X$, the maximal energy of X-ray photons that are self absorbed by the ISM of early galaxies, $\nu_\text{min}$, and the spectral slope, $\alpha$ which are taken to have fiducial values of $1$, $0.3$\,keV, and $-1.2$ respectively.
+We choose to parameterize our model in terms of the fractional differences of each parameter from their fiducial values so that, for example, $\theta_\zeta = (\zeta - \zeta_\text{fid})/\zeta_\text{fid}$ and compute the derivatives in equation~\ref{eq:Fisher} by performing a linear fit to realizations of the 21\,cm power spectrum calculated by {\tt 21cmFAST} at $\theta_i= \pm 10^{-2}, \pm 5\times 10^{-2}, \pm 10^{-1}$,and $ \pm 2 \times 10^{-2}$.
 
 What about $\sigma^2(k,z)$?
-$\sigma^2$ represents the noise on each 1 dimensional power spectrum estimate.
 For each measurement in the $uv$ plane, the standard deviation of a power spectrum measurement is given by the direct sum of sample variance and thermal noise \citep{McQuinn:2006} which in turn depends on the primary beam of the instrument and the time spent sampling each $uv$ cell.
-For our analysis, we assume that the $uv$ plane is sampled by circular apertures with effective areas of $75$\,m$^2$ and that $\tau({\bf k})$ is determined by by a drift scan in which baselines are integrating coherently on each $uv$ cell for $\approx 20$\,minutes.
+For our analysis, we assume that the $uv$ plane is sampled by circular apertures with effective areas of $98$\,m$^2$ and that $\tau({\bf k})$ is determined by a drift scan in which non instantaneously redundant baselines are combined within each $uv$ cell.
+We compute the sensitivity for the proposed 331-element hexagonally packed deployment of HERA (HERA-331).
 
@@
 At all other redshifts, the leakage due to beam chromaticity only extends to $\approx 250$\,ns beyond the horizon.
-To determine the potential impact of our observed beam chromaticity on HERA's ability to constrain the astrophysics of reionization, we consider three different scenarios for beam chromaticity that capture a range of possibilities allowed by our simulation.
+To determine the impact of our observed beam chromaticity on HERA's ability to constrain the astrophysics of reionization, we consider three different scenarios for beam chromaticity that capture a range of possibilities informed by our simulations.
 
 \begin{itemize}
-\item {\bf Optimistic: The observed reflections are an artifact of the simulation.} It is possible that the long term reflections observed in the center of our gain are artifacts of our modeling and that effects such as dissipative effects due to unmodeled non-idealities in the geometry of the disk will allow reflected radio waves to be better absorbed or escape into space, suppressing these reflections.
-In our most optimistic scenario, we assume their absence in which case the foregrounds pass below the level of the signal at $240$\,ns beyond the horizon at all redshifts between $z=7$ and $10$, consistent with what is observed in the bands where the dish chromaticity is less severe or when it is not present at all.
+\item {\bf Optimistic: The observed reflections are an artifact of the simulation.} It is possible that the long term reflections observed in the center of our gain are artifacts of our modeling such as dissipative effects due to unmodeled non-idealities in the geometry of the disk will allow reflected radio waves to be better absorbed or escape into space.
+In our most optimistic scenario, we assume their absence in which case the foregrounds pass below the level of the signal at $250$\,ns beyond the horizon at all redshifts between $z=7$ and $12$, consistent with what is observed in the bands where the dish chromaticity is less severe or when it is not present at all.
 We do not consider the possibility that optimal inverse covariance weighting of the foregrounds  may actually decrease the minimal delays accessible to below the $250$\,ns above the horizon observed in our simulations.
-Hence, this scenario is actually somewhat conservative and certainly more pessimistic than the ones considered in \citep{Pober:2014,Greig:2015a,EwallWice:2015b}.
+Hence, this scenario is actually somewhat conservative and certainly more pessimistic than the ones considered in \citet{Pober:2014,Liu:2015a,Liu:2015b,EwallWice:2015b}.
 
-\item {\bf Moderate: The Simulations accurately capture the chromaticity of the dish.} In this case, we assume that the reflections cause foregrounds to pass below the level of the signal at $250$\,ns except at redshift $8.5$ where they pass below the foregrounds at $350$\,ns.
+\item {\bf Moderate: The Simulations accurately capture the chromaticity of the dish.} In this case, we assume that the reflections cause foregrounds to pass below the level of the signal at $250$\,ns beyond the horizon except at redshift $8.5$ where they pass below the foregrounds at $350$\,ns beyond the horizon.
 
 \item {\bf Pessimistic: The reflections are present in all sub-bands.} In this scenario, we assume that the spectral structure observed in the neighborhood of $150$\,MHz is present throughout the entire $100$-$200$\,MHz frequency range covered by HERA.
-While more pessimistic than anything we actually observe in our simulations, this scenario serves as a reasonable upper bound.
+While more pessimistic than anything we actually observe in our simulations, this scenario serves as a reasonable upper bound on the reflections we expect given our simulations.
 
@@
 
-Folding our calculations of thermal noise and the derivatives of $\Delta^2$ into equation~\ref{eq:Fisher} and inverting, we obtain the covariance matrix for model parameters from which we calculate $95\%$ confidence regions which we plot in Fig.~\ref{fig:Confidence}.
+Folding our calculations of thermal noise and the derivatives of $\Delta^2$ into equation~\ref{eq:Fisher} and inverting, we obtain the covariance matrix for model parameters.
+We show the 95\% confidence ellipses for the reionization parameters in Fig.~\ref{fig:Confidence}.
 The presence of reflections within a limited sub-band about $z=8.5$ leads to an almost neglible increase in the extent of our confidence intervals while the presence of the reflections across the entire band causes the length and width of our confidence ellipses to increase by a factor of $\approx 2$.
@@
 
-The error bars on reionization parameters, even for our most optismtic model, are a factor of a few larger than the ``moderate" errors predicted in previous works using the Fisher Matrix such as \citet{Pober:2014}, \citet{EwallWice:2015a}, and \citet{Liu:2015a,Liu:2015b}.
+The error bars on reionization parameters, even for our most optismtic model, are a factor of a few larger than the ``moderate" errors predicted in previous works using likelihood analyses such as \citet{Pober:2014}, \citet{Greig:2015,Greig:2015b,Greig:2015c}  \citet{EwallWice:2015b}, \citet{Liu:2015a,Liu:2015b}.
 There are several reasons for this.
 Firstly, in our most optimistic scenario, we assumed that foregrounds cause the signal to be inaccessible below $250$\,ns beyond the edge of the wedge while in all previous works, a comoving $k$ of $k_\text{min}=0.1$\,$h$Mpc$^{-1}$, rather than a delay was used.
-In particular, this delay corresponds to a comoving $k\approx0.15$\,$h$Mpc$^{-1}$ at $z=8.5$, in significant excess of the values used in previous works.
-However, we do not consider the potential for inverse covariance techniques to further isolate foregrounds and potentially allowing us to work closer to the wedge than a naive Fourier transform.
-Because of this, our work is significantly more conservative than previous estimates.
-Secondly, previous studies assumed a fully illuminated HERA aperture, which for a $14$\,m dish predicts and effective area of $\approx155$\,m$^2$ at $150$\,MHz.
-Electromagnetic simulations and mapping of the primary beam of the HERA dish described in \citep{Neben:2016} indicate are in good agreement that the effective area of the antenna element is actually $\approx 98$\,m$^2$ at $150$\,MHz which leads to an increase in the overall thermal noise levels by a factor of $\approx 1.5$.
+This delay corresponds to a larger comoving wave number of $k\approx0.15$\,$h$Mpc$^{-1}$ at $z=8.5$.
+Secondly, previous studies assumed a fully illuminated HERA aperture, which for a $14$\,m dish predicts and effective area of $\approx155$\,m$^2$.
+Electromagnetic simulations and ORBCOMM mapping of the angular beam pattern of the HERA dish show that the effective area of the antenna element is actually $\approx 98$\,m$^2$ at $137$\,MHz which leads to an increase in the overall thermal noise levels by a factor of $\approx 1.5$ \citep{Neben:2016}.
 
-\section{Conclusions}
+Although conservative, our predictions bode well for the HERA design, indicating that even with the additional systematics introduced by the Dish geometry, the array will still obtain a $\gtrsim 10 \sigma$ detection of the power spectrum and be capable of establishing precision constraints on the properties of reionization galaxies.
+
+\section{Conclusions}\label{sec:Conclusion}
 In this paper, we have formally described the impact of instrumental chromaticity on foreground contamination of the 21\,cm signal.
-We have also used simulations of electromagnetic waves incident from zenith on the primary antenna element on HERA to determine the extent to which reflections and other frequency dependent structure might leak foregrounds into the EoR window.
-The results of our simulations of the zenith gain of the instrument are broadly consistent with data obtained using reflectometry described in \citep{Patra:2016} and can be summarized in the following points.
+We have also used simulations of electromagnetic waves incident from zenith on the primary antenna element on HERA to determine the extent to which reflections and other frequency dependent structure in the dish that might leak foregrounds into the EoR window.
+The results of our simulations of the dish's voltage response are broadly consistent with reflectometry measurements \citep{Patra:2016} and can be summarized in the following points.
 \begin{itemize}
 \item The 14-m dish and inverted dipole feed configuration introduces reflections and, as a result, spectral structure, that is in excess of that observed in the antenna design for HERA's predecessor, PAPER.
-The dish design is intended to greatly increase array collecting area over PAPER without significantly raising the number of correlated elements while narrowing the angular field of view and suppressing the overall amplitude of foregrounds but we find that in achieving these ends, some degree of spectral smoothness has been sacrificed.
+The dish design is intended to greatly increase array collecting area over PAPER without significantly raising the number of correlated elements while narrowing the angular field of view and suppressing the overall amplitude of foregrounds.
+We find that in achieving these ends, some degree of spectral smoothness has been sacrificed.
 Because foreground filtering in delay space cannot distinguish between signal and foregrounds, any regions of $k$-space contaminated by these reflections are effectively unusable in a 21\,cm measurement unless they can be modeled to high fidelity and removed.
@@
 It is also possible that the  non-ideal properties of an actual antenna will allow these reflections to escape the dish after a short time or be dissipated, rather than reflecting continually to long delays.
-Because estimates of the power spectrum are obtained from sub-intervals of $\approx10$\,MHz, the reflections that we have simulated will only impact a single redshift.
+Because estimates of the power spectrum are obtained from sub-intervals of $\approx10$\,MHz, the reflections that we have simulated will only impact a single $\Delta z=0.5$ redshift interval.
 
-\item Simulating the impact of these reflections on foreground leakage using the foreground model described in \citet{Thyagarajan:2016}, we find that the beam chromaticity extends foregrounds above the level of the cosmological signal to $\approx 350$\,ns beyond the horizon while without the reflections, foregrounds extend above the signal to $\approx 250$\,ns beyond the horizon.
-These observations are pessimistic in that no attempt to inversely weight the foregrounds by their covaranciances has been attempted.
+\item Simulating the impact of these reflections on foreground leakage using the foreground model of \citet{Thyagarajan:2016}, we find that the beam chromaticity extends foregrounds above the level of the cosmological signal to $\approx 350$\,ns beyond the horizon while without the reflections, foregrounds extend above the signal to $\approx 250$\,ns beyond the horizon.
+These observations are pessimistic in that no attempt to inversely weight the foregrounds by the foreground covaranciances has been attempted, nor have mitigation algorithms such as delay rate filtering been applied, putting our forecasts on the conservative side.
 
 \item If the reflections are contained within a $10$\,MHz subband around $150$\,MHz, than the overall constraints that HERA will be able to place on the astrophysics of reionization are minimally impacted.
-If the reflections somehow contaminate the entire band, than our constraints on reionization parameters will suffer a factor of two increase in uncertainty but still remain on the order of $10$\%.
+If the reflections somehow contaminate the entire band, than our constraints on reionization parameters will suffer a two-fold increase in uncertainty but still remain on the order of $10$\%.
+Measuring the global properties of the sources that reionized the universe to this accuracy will be an unprecedented accomplishment.
 \end{itemize}
 
-\label{sec:Conclusion}
+While we have not addressed the issue of inter-dish reflections, preliminary measurements indicate that their level is many orders of magnitude below our observations of reflections within each antenna element with a full analysis forthcoming \citep{Patra:2016}.
+Our results are very encouraging since they show that the HERA design is capable of isolating the foregrounds to sufficiently low delays to make a high significance detections of the 21\,cm power spectrum during the EoR.
+They also emphasize the importance of mitigating reflections in the analogue signal chain.
+The reflections masking our signal at $k=0.2$\,$h$Mpc$^{-1}$ are at the level of one part in $10^{-4}$, hence any interferometer designed for EoR observing must ensure that such structure is absent from the signal chain at the $10^{-5}$ level or less at $\approx 400$\,ns or be absolutely certain that their calibration strategy can faithfully remove this structure without introducing any spurious, frequency-dependent artifacts at or above this level due to foreground mismodeling or thermal noise.
+Such a feat that has yet to be demonstrated in the literature of widefield 21\,cm interferometry experiments but whose extraordinary difficulty is illustrated in \citet{Barry:2016}.
+
 \bibliographystyle{apj}

### 2016-02-23 DishSimulations/paper/delay_response.tex

\documentclass{article}
\usepackage{amsmath,amssymb,graphicx}
\begin{document}
\title{Computing the Delay Response from Reflectometry}
\author{Aaron Ewall-Wice}
\date{January 13th 2015}
\maketitle
Here is a brief description of how I compute the delay response of the HERA dish from reflectometry measurements.

According to Nipanjana's memo, the reflection coefficient measured by the VNA is given by 
\begin{equation}
S_{11}(f)=\Gamma_f(f) + \frac{(1-\Gamma_f(f))^2}{\Gamma_f(f)} \sum_{n=1} \left[ \Gamma_f(f) \Gamma_d(f) e^{2 \pi i f \tau} \right]^n
\end{equation}
where $\Gamma_f(f)$ is the frequency dependent reflection coefficient of the feed and $\Gamma_d(f)$ is the reflection coefficient of the dish, and $\tau$ is the round trip delay between the feed and the dish. Because the terms in the sum are all multiplied by at least a factor of $e^{2 \pi i \tau}$ which translates them to $\tau \approx 30$\,ns in delay space, only the $\Gamma_f(f)$ out front adds significant power to the zero delay modes.

Meanwhile, the voltage gain of the antenna, which we are trying to measure is given by 
\begin{equation}
G(f) = (1-\Gamma_f(f)) + (1-\Gamma_f(f)) \sum_{n=1} \left[\Gamma_f(f) \Gamma_d(f) e^{2 \pi i f \tau} \right]^n
\end{equation}
In the reflectometry measurement of the feed only, we measure $\Gamma_f(f)$ directly, e.g.
\begin{equation}
S_{11}^f = \Gamma_f(f)
\end{equation}
We can than obtain $\widehat{G}(f)$ through the following transformation in the frequency domain
\begin{equation}\label{eq:estimate:YesZ}
\widehat{G}(f) = \frac{\Gamma_f(f)}{1-\Gamma_f(f)} \left[S_{11}(f) - \Gamma_f(f) \right] + \left[1-\Gamma_f(f) \right]
\end{equation},
where $\Gamma_f$ is supplied directly by the feed only reflectometry measurement, $S_{11}^f$. 
Since the 
At zero delay, the amplitude of $\widetilde{G}(\tau)$ should be $\sim (1-\widetilde{\Gamma}_f(\tau))$ which we have accounted for in our calculation. In delay space, we should therefor normalize all $\tau>0$ measurements to this value.

One can also ignore the zero delay contribution and obtain a very similar estimate where $(1-\Gamma_f(f))$ has not been added back in. We refer to this as "nz", short for "no zero".

\begin{equation}\label{eq:estimateNoZ}
\widehat{G}_{nz}(f) = \frac{\Gamma_f(f)}{(1-\Gamma_f(f))} \left[ S_{11}(f) - \Gamma_f(f) \right]
\end{equation}

This is a fine approximation for $\tau\gtrsim 30\,$ns if one is simply looking at the delay spectrum of the voltage response but, as we will explain below, neglecting the zero delay will bias the power kernel by multiplying by an incorrect normalization factor as we will explain below. First, let's see what the data looks like.

In Fig.~\ref{fig:Reflectometry}, we plot the We note that both the feed only measurement and the feed and dish measurement level off at a similar level above  $125$\,ns, indicating that either the large time scale shallow falloff in the measurements is an intrinsic property of the feed (and not associated with feed-dish reflections) or is associated with some measurement systematic (such as reflections within the cable. We also see that the zero delay peak in the $S_{11}$ measurement of the feed and dish corresponds with the peak of the $S_{11}$ measurement of the feed only due to the fact that the first peak in both measurements arises from the reflection of the reflectometry pulse off the back of the back of the feed.

Because the measurement of the feed only has large delay structure that is comparable to the structure in the measurement of the feed and dish, added $(1-\Gamma_f(f))$ does cause $\widehat{G}$ to be several dB larger than $\widehat{G}_{nz}$ at a few of places at large delay but the differences are not terribly dramatic.

\begin{figure}
\includegraphics[width=\textwidth]{figures/GB_reflectometry.pdf}
\caption{A comparison between the one dimensional delay transform of various reflectometry measurements. The raw measurements are given by $S_{11}$ of the feed only (black dashed line) and $S_{11}$ of the feed and dish (grey dashed line). We also plot $\widehat{G}$  (solid grey line) and $\widehat{G}_{nz}$ (solid black line).  }
\label{fig:Reflectometry}
\end{figure}

 The significant disagreement between $\widehat{G}$ and $\widehat{G}_{nz}$ at zero delay, which might seem inconsequential, becomes important when one attempts to measure the power kernel. The power kernel is given by
 \begin{equation}
 \widehat{K}(\tau) = \int d \Delta \tau \widehat{G}(\Delta \tau) \widehat{G}^*(-\tau + \Delta \tau) 
 \end{equation}
Because $G(\tau)$ is a function that decreases rapidly from its maximum value at $\tau=0$, this convolution can be approximated to first order as
\begin{equation}
\widehat{K}(\tau) \approx \widehat{G}(0) \widehat{G}^*(-\tau)
\end{equation}
Hence, our estimate of $\widehat{G}(0)$ sets the overall amplitude of our estimate of $\widehat{K}(\tau)$. Because $\widehat{G}_{nz}$ does not attempt to make an accurate estimate of the zero delay mode and has subtracted it from the data, this suppresses the amplitude of $\widehat{K}_{nz}(\tau)$ by a factor of $-15$\,dB, the amplitude of $\widehat{G}_{nz}(0)$.

\begin{figure}
\includegraphics[width=\textwidth]{figures/GB_kernels.pdf}
\caption{A comparison between the power kernels computed with and without the inclusion of power at zero delay before performing the convolution. While the 1-dimensional voltage responses are at similar levels in Fig.~\ref{fig:Reflectometry}, they differ dramatically (by 15\,dB) in the power kernel. This is due to the difference in normalization in the convolution caused by misestimating the zero delay power.}
\label{fig:Reflectometry}
\end{figure}

\end{document}

### 2016-02-23 data/plot_pspecs.py
added in data files for quad est with 50 time samples.
updated plotting script and quad_est.py save file names

@@ -5,7 +5,8 @@ import pylab as p
 #In plots dashed curves are delay power spectra with a blackman harris window across the subband. solid curves are power spectra attained via oqe formalism.
 
 #names = ['pspecs_achrmbeam_sbinfo.npz', 'pspecs_chrmbeam_sbinfo.npz', 'pspecs_funcbeam_sbinfo.npz']
-names = ['pspecs_chrmbeam_sbinfo.npz']
+#50names = ['pspecs_achrmbeam_sbinfo.npz', 'pspecs_chrmbeam_sbinfo.npz', 'pspecs_funcbeam_sbinfo.npz']
+names = ['pspecs_achrmbeam_sbinfo.npz', 'pspecs_achrmbeam_sbinfo.npz_50.npz']
 files = [ n.load(k) for k in names ]
 
 #shape of pC and pI is (3,30,49) = (subband, bl, ks)
@@ -17,9 +18,10 @@ colors = ['k', 'c', 'm']
 for b,bl in enumerate(files[0]['bls']):
     print b, bl
     for k,f in enumerate(files):
+        print f
         p.subplot(111)
-        p.semilogy(f['hetas'][k],n.abs(f['pCnorm'][sband,b,:,12]), colors[k], label=names[k].split('_')[1])
-        p.semilogy(f['wetas'][k],n.abs(f['pInorm'][sband,b,:,12]),'--'+colors[k])
+        p.semilogy(f['hetas'][k],n.abs(f['pCnorm'][sband,b,:,12]), colors[k], label=names[k])
+        p.semilogy(f['wetas'][k],n.abs(f['pInorm'][sband,b,:,12]),'--'+colors[k], label=names[k])
     
     p.suptitle('[ '+', '.join(map(str,bl)) + ' ]')
     p.legend()

### 2016-02-23 data/quadratic_estimator.py

@@ -244,7 +244,7 @@ for f in files:
 
             hetas[bb] = etas(freq[hfreqs[band]])
             wetas[bb] = etas(freq[wfreqs[band]])
-            if PLOT and 1 :
+            if PLOT and 0:
                 p.subplot(111); p.semilogy(etas(freq[hfreqs[band]]),n.abs(banddataC[bb][bl][:,12]),color='c')
                 p.subplot(111); p.semilogy(etas(freq[hfreqs[band]]),n.abs(banddataC_norm[bb][bl][:,12]), color='k')
                 p.subplot(111); p.semilogy(etas(freq[wfreqs[band]]),n.abs(banddataI[bb][bl][:,12]), color='g')
@@ -254,4 +254,4 @@ for f in files:
 
             
 
-    n.savez('pspecs_'+f.split('/')[-1], bls=bls, pC=banddataC, pI=banddataI, pCnorm=banddataC_norm, pInorm=banddataI_norm, hetas=hetas, wetas=wetas)
+    n.savez('pspecs_'+f.split('/')[-1]+'_%d'%ntimes, bls=bls, pC=banddataC, pI=banddataI, pCnorm=banddataC_norm, pInorm=banddataI_norm, hetas=hetas, wetas=wetas)

### 2016-02-23 DishReflectometry/Paper1_v1.tex
Fixed some spelling issues

--- 2016-02-22 DishReflectometry/Paper1_v1.tex
@@
 \email{Contact author email: nipanjana@berkeley.edu}
-\author{Aaron Parsons\altaffilmark{1}, Dave DeBoer, Zaki Ali\altaffilmark{1}, Cherie Day\altaffilmark{1}, Carina Cheng\altaffilmark{1}}
+\author{Aaron Parsons\altaffilmark{1}, Dave DeBoer, Zaki S. Ali\altaffilmark{1}, Cherie Day\altaffilmark{1}, Carina Cheng\altaffilmark{1}}
 \author{Gilbert Hsyu\altaffilmark{2}, Tsz Kuk Leung\altaffilmark{2}}
@@
 The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$.
-In words, the sky delay spectrum from any direction $\thhat$ is convoluted with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ in the delay domain.
+In words, the sky delay spectrum from any direction $\thhat$ is convoluted with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ %defined this differently earlier
+ in the delay domain.
 The maximum geometric delay possible for a given base line would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$ when the phase centre is halfway in between the two antennas.
+%The phase center is elsewhere defined as being at the center of one of the antennas.
  Hence, the sky contribution from any direction would be confined within $-\tau_{g}<\tau<\tau_{g}$.
@@
 
-The total reflected power, returned to the VNA, denoted byt $I_{ret}$ would be:
+The total reflected power, returned to the VNA, denoted by $I_{ret}$ would be:
 \begin{eqnarray}\label{eqn:series2}
@@
 Additionally, with each reflections, the power coupled to the system reduces by a factor of $\Gamma_{f}^{2}$.
-Since reflected signal results in system response in higher delay, mutiple reflections of the signal off the feed and the dish would result in an exponential envelope in the delay spectrum.
+Since reflected signal results in system response in higher delay, multiple reflections of the signal off the feed and the dish would result in an exponential envelope in the delay spectrum.
 The return loss of power results from the antenna impedance mismatch with the free space as well as the transmission line.
@@
 However, a smaller return loss will result in vertical shift of the delay spectrum at lower values and therefore can make the higher order reflections insignificant.
-Given the antenna impedance and the 50 Ohm transmission line the measurements are done using the passive balun with a 2:1 impedance ratio providing a net retrun loss of power between the sky, the antenna and the transmission line shown in the figure \ref{fig:freq}.
+Given the antenna impedance and the 50 Ohm transmission line the measurements are done using the passive balun with a 2:1 impedance ratio providing a net return loss of power between the sky, the antenna and the transmission line shown in the figure \ref{fig:freq}.
 This provides the maximum impedance matching.

### 2016-02-24 DishReflectometry/GB_reflectometry_part2/plot_reflectometry.py
Adding the script for plotting subbands.

@@ -21,11 +21,28 @@ for filename in sys.argv[1:]:
     fq,ph = fromcsv(ph_file)
     #d = 10**(db/10) * np.exp(2j*np.pi*ph/360) # power
     d = 10**(db/20) * np.exp(2j*np.pi*ph/360) # 20 to put into voltage amplitude, not power
+    valids = {
+          '100- 130 MHz'  : np.where(np.logical_and(fq>.100 ,fq<.130)), 
+          '130 - 160 MHz' : np.where(np.logical_and(fq>.130 ,fq<.160)), 
+          '160 - 190 MHz' : np.where(np.logical_and(fq>.160 ,fq<.190)),
+          }
+          
+
+for i,v in enumerate(valids.keys()):
 
     #valid = np.ones(fq.size, dtype=np.bool) # use entire sampled band
     #valid = np.where(fq < .250) # restrict to HERA band
-    valid = np.where(np.logical_and(fq < .170, fq > .130)) # restrict to PAPER band
-    fq, d, db, ph = fq[valid], d[valid], db[valid], ph[valid]
+    if v == '100-130 MHz': 
+    #valid1 = np.where(np.logical_and(fq < .130, fq > .100)) # restrict to PAPER band
+    #valid2 = np.where(np.logical_and(fq < .160, fq > .130)) # restrict to PAPER band
+    #valid3 = np.where(np.logical_and(fq < .190, fq > .160))
+#if i==0:
+      fq, d, db, ph = fq[valid[v]], d[valid[v]], db[valid[v]], ph[valid[v]]
+#elif i==1:
+ #   fq, d, db, ph = fq[valid2], d[valid2], db[valid2], ph[valid2]
+#elif i==2:    
+  #  fq, d, db, ph = fq[valid3], d[valid3], db[valid3], ph[valid3]
+    
     tau = np.fft.fftfreq(fq.size, fq[1]-fq[0])
     window = a.dsp.gen_window(fq.size, WINDOW)
     
@@ -67,13 +84,14 @@ for filename in sys.argv[1:]:
    #plt.plot(np.fft.fftshift(tau), 10.0*np.log10(np.fft.fftshift(np.abs(_d))), linewidth=2.5, label= 'Square Window')
     plt.plot(np.fft.fftshift(tau), 10.0*np.log10(np.fft.fftshift(np.abs(_dww))), linewidth=2.5, label=BASE.replace('_', ' '))
     
[…]

### 2016-02-24 DishReflectometry/GB_reflectometry_part2/plot_reflectometry.py
Corrected equations 6,12

@@ -38,8 +38,8 @@ for i,v in enumerate(valids.keys()):
     #valid3 = np.where(np.logical_and(fq < .190, fq > .160))
 #if i==0:
       fq, d, db, ph = fq[valid[v]], d[valid[v]], db[valid[v]], ph[valid[v]]
-#elif i==1:
- #   fq, d, db, ph = fq[valid2], d[valid2], db[valid2], ph[valid2]
+    elif v == '130-160 MHz':
+      fq, d, db, ph = fq[valid2], d[valid2], db[valid2], ph[valid2]
 #elif i==2:    
   #  fq, d, db, ph = fq[valid3], d[valid3], db[valid3], ph[valid3]
     

### 2016-02-25 DishReflectometry/Paper1_v1.tex
Changed equation 3

@@
 the Murchison Widefield Array (MWA; ~\citealt{XXX}),
-the Giant Metre-wave Radio Telescop (GMRT; ~\citealt{XXX}),
+the Giant Metre-wave Radio Telescope (GMRT; ~\citealt{XXX}),
 the Donald C. Backer Precision Array to Probe the Epoch of Reionization (PAPER; ~\citealt{parsons_et_al2010}),
@@
 \begin{eqnarray}
-\tilde V(\vec b, \tau) & = & \int\!\!\int{\beam(\thhat,\nu) I_\sky(\thhat,\nu) \ifngexp d\Omega~e^{+2\pi i\nu\tau}d\nu}\nonumber\\	                        & = &   \int \left [ A(\thhat, \tau)\ast I_{sky}(\thhat, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega
+\tilde V(\vec b, \tau) & = & \int\!\![{\beam(\vec b,\nu)*I_\sky(\vec b,\nu)] ~e^{-2\pi i\nu\tau}d\nu}\nonumber\\	                        %& = &   \left [ A(\vec b, \tau)\ast I_{sky}(\vec b, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega
 \label{eq3}
@@
 %The phase center is elsewhere defined as being at the center of one of the antennas.
+ Hence, the sky contribution from any direction would be confined within $-\tau_{g}<\tau<\tau_{g}$.
+Due to chromaticity of the sky signal as well as instrument reponse, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with decaying amplitude [Ref to the figure Parsons12].
+Sky delay spectrum $I_{sky}(\tau)$ is contributed by the foreground  $I_{fg}(\tau)$  which is spectrally smooth and the 21~cm power spectrum $I_{21}(\tau)$ which contains spectral signatures.
+Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces and the 21~cm delay spectrum could potentially be detectable.
+The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$.
+In words, the sky delay spectrum from any direction $\thhat$ is convolved with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ in the delay domain.
+The maximum geometric delay possible for a given base line would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$ when the phase centre is halfway in between the two antennas.
 Hence, the sky contribution from any direction would be confined within $-\tau_{g}<\tau<\tau_{g}$.
@@
 &&+  (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
-&& ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}] \ast \fngexp \nonumber
+&& ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}] \fngexp \nonumber
 \end{eqnarray}
@@
 \vis(\vec b, \nu) & = & \int \volt_{1}\volt_{2}^{*} d\Omega \nonumber\\
-			& = & \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp d\Omega
+			& = & \int I_{sky}(\vec b, \nu)\Sigma(\nu) \fngexp d\Omega
 \end{eqnarray}
@@
  \begin{eqnarray}
-\Sigma(\vec b, \nu) & = & \beam_{f}  [ 1+  \Gamma_{f}\Gamma_{d} \dfngexp \nonumber\\
+\Sigma( \nu) & = & \beam_{f}  [ 1+  \Gamma_{f}\Gamma_{d} \dfngexp \nonumber\\
 && + (\Gamma_{f}\Gamma_{d})^2(\dfngexp)^{2}+ \nonumber\\
 &&  ....+(\Gamma_{f}\Gamma_{d})^{n}(\dfngexp)^{n}  ]\\
-& = & \beam_{f}\displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
+& = & \beam_{f}+\beam_{f} \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
    \nonumber\\ 
@@
 \end{eqnarray}
-where, $\beam_{f}=\bmvolt_{f}\bmvolt_{f}^{*}$ is the antenna cross power pattern.
+where, $\beam_{f}=\bmvolt_{f}\bmvolt_{f}^{*}= |a(1-\Gamma_{f})|^{2}$ is the antenna cross power pattern.
 and the delay spectrum would be, 
@@
 approximated based on the power level of the cosmological signal in relation to
-foreground signals, which is estimated to be six orders of magnitude fainter ~\citep{santos_et_al2005,ali_et_al2008,deoliveira2008,jelic_et_al2008,bernardi_et_al2009,bernardi_et_al2010,ghosh_et_al2011}.
+foreground signals, which is estimated to be six orders of magnitude fainter
+~\citep{santos_et_al2005,  ali_et_al2008,deoliveira2008, jelic_et_al2008, bernardi_et_al2009,bernardi_et_al2010, ghosh_et_al2011}. Additionally, the $14m$ HERA baselines set a foreground containing
 Additionally, the $14m$ HERA baselines set a foreground containing
@@
 {I_{meas} \over I_{sky} } & = & \Sigma(\vec b, \nu) \nonumber\\
-  & = & \beam_{f} \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
+  & = & \beam_{f}+ \beam_{f} \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
    \nonumber\\
@@
 
-The total reflected power, returned to the VNA, denoted by $I_{ret}$ would be:
+The total reflected power returned to the VNA, as measured by the VNA would be:
 \begin{eqnarray}\label{eqn:series2}
-I_{ret} & = & \Gamma_{f}I_{tr}+ I_{r}(1-\Gamma_{f}) [\Gamma_{d} \dfngexp + \Gamma_{f}\Gamma_{d}^{2} (\dfngexp)^{2}\nonumber\\
+I_{meas} & = & \Gamma_{f}I_{tr}+ I_{r}(1-\Gamma_{f}) [\Gamma_{d} \dfngexp + \Gamma_{f}\Gamma_{d}^{2} (\dfngexp)^{2}\nonumber\\
 &&+ ....+ \Gamma_{f}^{n-1}\Gamma_{d})^{n}(\dfngexp)^{n}]
@@
   \begin{eqnarray}\label{eqn:ratio2}
- {I_{ret} \over I_{tr} } & = & \Gamma_{f}
+ {I_{meas} \over I_{tr} } & = & \Gamma_{f}
   +  \Gamma_{d}(1-\Gamma_f) \beam_{f} I_{tr} [e^{i\phi}+ \Gamma_{f}\Gamma_{d} e^{i2\phi}\nonumber\\ 
@@
 The ratio in Equation \ref{eqn:ratio2} is identical to the ratio in the sky
-observation in Equation \ref{eqn:ratio1} except in two factors. The
+observation in Equation \ref{eqn:ratio1} except in three factors. The
 first factor corresponds to an additive amplitude difference arising from
@@
 The second difference is the multiplicative ${ (1-\Gamma_f)\over \Gamma_{f} }$.
-Our measurement is corrected  for these two terms to map the instrument response measurements from transmission mode in which the measurement is taken to receiving mode in which the sky observation is done.
-
+In addition, in order to estimate the true response of the system to the sky signal in the receiving mode, we add the term $A_{f}$.
+These corrections map the measured instrument response from transmission mode in which the measurement is taken to receiving mode in which the sky observation is done.
+The corrected measurement could be written as
+ \begin{eqnarray}\label{eqn:ratio2}
+ \left[{I_{meas} \over I_{tr}}-\Gamma_{f}\right]{ \Gamma_{f} \over (1-\Gamma_{f})} + \beam_{f}  & = & \beam_{f}+ \beam_{f} \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}\nonumber\\
+ & = & {I_{meas} \over I_{sky} }
+ \label{eq9}
+\end{eqnarray}
 %++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2016-02-25 DishReflectometry/GB_reflectometry_part2/check.py
Adding all new processing and plots

@@ -1,0 +1,16 @@
+#! /usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+	
+	
+fig = plt.figure()
+ax1 = fig.add_subplot(111)
+ax2 = ax1.twiny()
+
+a = np.cos(2*np.pi*np.linspace(0, 1, 60.))
+
+ax1.plot(range(60), a)
+ax2.plot(range(100), np.ones(100)) # Create a dummy plot
+ax2.cla()
+plt.show()

### 2016-02-25 DishReflectometry/GB_reflectometry_part2/plot_reflectometry.py

@@ -3,6 +3,11 @@
 import numpy as np, pylab as plt, aipy as a
 import sys, csv
 
+def fromcsv1(filename):
+    print 'Reading', filename
+    d = csv.reader(open(filename,'r'), delimiter=',')
+    x = np.array(list(d)[18:-1], dtype=np.float)
+    return x[:,0]/1e3, x[:,1]
 def fromcsv(filename):
     print 'Reading', filename
     d = csv.reader(open(filename,'r'), delimiter=',')
@@ -16,50 +21,63 @@ for filename in sys.argv[1:]:
 
     WINDOW = 'blackman-harris'
     #WINDOW = 'hamming'
-
-    fq,db = fromcsv(db_file)
-    fq,ph = fromcsv(ph_file)
+    
+    fq,db = fromcsv(db_file) # Reading the magnitude and the phase of the datafile to be processed
+    fq,ph = fromcsv(ph_file) 
+    fq_rb,db_rb = fromcsv1('measurement_dishAndFeed_DB.csv')
+    fq_rb,ph_rb = fromcsv1('measurement_dishAndFeed_P.csv')
+    d_rb = 10**(db_rb/20) * np.exp(2j*np.pi*ph_rb/360) # 20 to put into voltage amplitude, not power 
+    
+    fq_f,db_f = fromcsv('HERA_FEED_DB.csv') # Reading the magnitude and phase of the feed only datafile to calibrate for the zero point/ 
+    fq_f,ph_f = fromcsv('HERA_FEED_P.csv')
     #d = 10**(db/10) * np.exp(2j*np.pi*ph/360) # power
     d = 10**(db/20) * np.exp(2j*np.pi*ph/360) # 20 to put into voltage amplitude, not power
-    valids = {
-          '100- 130 MHz'  : np.where(np.logical_and(fq>.100 ,fq<.130)), 
-          '130 - 160 MHz' : np.where(np.logical_and(fq>.130 ,fq<.160)), 
-          '160 - 190 MHz' : np.where(np.logical_and(fq>.160 ,fq<.190)),
-          }
+    d_f = 10**(db_f/20) * np.exp(2j*np.pi*ph_f/360) # 20 to put into voltage amplitude, not power
+    
+#    valids = {
+#          '100- 130 MHz'  : np.where(np.logical_and(fq>.100 ,fq<.130)), 
[…]

### 2016-02-25 DishReflectometry/GB_reflectometry_part2/plot_reflectometry_subband.py

@@ -1,0 +1,114 @@
+#! /usr/bin/env python
+
+import numpy as np, pylab as plt, aipy as a
+import sys, csv
+
+def fromcsv(filename):
+    print 'Reading', filename
+    d = csv.reader(open(filename,'r'), delimiter=',')
+    x = np.array(list(d)[18:-1], dtype=np.float)
+    return x[:,0]/1e9, x[:,1]
+    #d = 10**(db/10) * np.exp(2j*np.pi*ph/360) # power
+    
+
+def take_delay(db, db_f, ph, ph_f, fq, window='blackman-harris'):
+    '''Take reflectometry data in dB and phase to return delay transform.
+       Returns windowed and non windowed delay spectra for input spectrum.'''    
+    d = 10**(db/20) * np.exp(2j*np.pi*ph/360) # 20 to put into voltage amplitude, not power
+    d_f = 10**(db_f/20) * np.exp(2j*np.pi*ph_f/360) # 20 to put into voltage amplitude, not power
+    d1 = d
+    #d1 = (np.abs(d)-np.abs(d_f))
+    #d1 = (np.abs(d)-np.abs(d_f))*np.abs(d_f)/(1-np.abs(d_f))+ (1-np.abs(d_f))
+    tau = np.fft.fftfreq(fq.size, fq[1]-fq[0])
+    window = a.dsp.gen_window(fq.size, window)
+    _d = np.fft.ifft(np.abs(d1)**2.0)
+    _dw = np.fft.ifft(np.abs(d1)**2.0*window) / window.mean() #compensate for window amplitude
+    
+    if True:
+    #if False:
+        
+        _dw *= ( np.abs(_dw[0])/ (1- np.abs(_dw[0])))  # these should be changed to the dc bin of the windowed data.
+        _d *= ( np.abs(_d[0])/ (1- np.abs(_d[0])))  # these should be changed to the dc bin of the windowed data.
+
+    return np.fft.fftshift(_dw), np.fft.fftshift(_d), np.fft.fftshift(tau)
+
+colors = np.array([(31,119,180), (255,127,14), (44,160,44), (214,39,40), (148,103,189)])/255.
+
+for filename in sys.argv[1:]:
+    BASE = filename[:-len('.csv')]
+    db_file = BASE + '_DB.csv'
+    ph_file = BASE + '_P.csv'
+
+    WINDOW = 'blackman-harris'
+    #WINDOW = 'hamming'
+    
[…]

### 2016-02-25 DishReflectometry/Reflectometry_RB/data_conversion.py
Adding processed data from Rich's measurements

@@ -1,0 +1,19 @@
+import numpy as np, pylab as plt, aipy as a
+import sys, csv
+
+def fromcsv1(filename):
+    print 'Reading', filename
+    d = csv.reader(open(filename,'r'), delimiter=',')
+    x = np.array(list(d)[18:-1], dtype=np.float)
+    return x[:,0], x[:,1]
+    
+    fq_rb,db_rb = fromcsv1('measurement_dishAndFeed_DB.csv')
+    fq_rb,ph_rb = fromcsv1('measurement_dishAndFeed_P.csv')
+    
+    fq_rb = fq_rb*1000000
+    
+    with open('measurement_dishAndFeed1_DB.csv', 'wb') as csvfile:
+    spamwriter = csv.writer(csvfile, delimiter=' ',
+                            quotechar='|', quoting=csv.QUOTE_MINIMAL)
+    spamwriter.writerow(['Spam'] * 5 + ['Baked Beans'])
+    spamwriter.writerow(['Spam', 'Lovely Spam', 'Wonderful Spam'])

### 2016-02-25 DishReflectometry/Reflectometry_RB/plot_reflectometry.py

@@ -7,7 +7,7 @@ def fromcsv(filename):
     print 'Reading', filename
     d = csv.reader(open(filename,'r'), delimiter=',')
     x = np.array(list(d)[18:-1], dtype=np.float)
-    return x[:,0]/1e3, x[:,1]
+    return x[:,0]/1e9, x[:,1]
 
 for filename in sys.argv[1:]:
     BASE = filename[:-len('.csv')]
@@ -16,16 +16,37 @@ for filename in sys.argv[1:]:
 
     WINDOW = 'blackman-harris'
     #WINDOW = 'hamming'
-
-    fq,db = fromcsv(db_file)
-    fq,ph = fromcsv(ph_file)
+    
+    fq,db = fromcsv(db_file) # Reading the magnitude and the phase of the datafile to be processed
+    fq,ph = fromcsv(ph_file) 
+    
+    fq_f,db_f = fromcsv('HERA_FEED_DB.csv') # Reading the magnitude and phase of the feed only datafile to calibrate for the zero point/ 
+    fq_f,ph_f = fromcsv('HERA_FEED_P.csv')
     #d = 10**(db/10) * np.exp(2j*np.pi*ph/360) # power
     d = 10**(db/20) * np.exp(2j*np.pi*ph/360) # 20 to put into voltage amplitude, not power
+    d_f = 10**(db_f/20) * np.exp(2j*np.pi*ph_f/360) # 20 to put into voltage amplitude, not power
+    
+#    valids = {
+#          '100- 130 MHz'  : np.where(np.logical_and(fq>.100 ,fq<.130)), 
+#          '130 - 160 MHz' : np.where(np.logical_and(fq>.130 ,fq<.160)), 
+#          '160 - 190 MHz' : np.where(np.logical_and(fq>.160 ,fq<.190)),
+#          }
+          
+
+#for i,v in enumerate(valids.keys()):
 
     #valid = np.ones(fq.size, dtype=np.bool) # use entire sampled band
     #valid = np.where(fq < .250) # restrict to HERA band
+#    if v == '100-130 MHz': 
     valid = np.where(np.logical_and(fq < .200, fq > .100)) # restrict to PAPER band
-    fq, d, db, ph = fq[valid], d[valid], db[valid], ph[valid]
+    
[…]

### 2016-02-26 DishReflectometry/GB_reflectometry_part2/plot_reflectometry.py
New correction for transmission coefficient.

@@ -24,15 +24,23 @@ for filename in sys.argv[1:]:
     
     fq,db = fromcsv(db_file) # Reading the magnitude and the phase of the datafile to be processed
     fq,ph = fromcsv(ph_file) 
-    fq_rb,db_rb = fromcsv1('measurement_dishAndFeed_DB.csv')
-    fq_rb,ph_rb = fromcsv1('measurement_dishAndFeed_P.csv')
-    d_rb = 10**(db_rb/20) * np.exp(2j*np.pi*ph_rb/360) # 20 to put into voltage amplitude, not power 
     
     fq_f,db_f = fromcsv('HERA_FEED_DB.csv') # Reading the magnitude and phase of the feed only datafile to calibrate for the zero point/ 
     fq_f,ph_f = fromcsv('HERA_FEED_P.csv')
-    #d = 10**(db/10) * np.exp(2j*np.pi*ph/360) # power
+    
     d = 10**(db/20) * np.exp(2j*np.pi*ph/360) # 20 to put into voltage amplitude, not power
     d_f = 10**(db_f/20) * np.exp(2j*np.pi*ph_f/360) # 20 to put into voltage amplitude, not power
+    
+    fq_rb,db_rb = fromcsv1('measurement_dishAndFeed_DB.csv')# Reading Rich's dish+feed measurements magnitude and phase file.
+    fq_rb,ph_rb = fromcsv1('measurement_dishAndFeed_P.csv')
+    
+    fq_rb_f,db_rb_f = fromcsv1('measurement_FeedOnly_DB.csv')#Reading Rich's feed only file to do the zero delay corrections.
+    fq_rb_f,ph_rb_f = fromcsv1('measurement_FeedOnly_P.csv')
+    
+    d_rb = 10**(db_rb/20) * np.exp(2j*np.pi*ph_rb/360) # 20 to put into voltage amplitude, not power 
+    d_rb_f = 10**(db_rb_f/20) * np.exp(2j*np.pi*ph_rb_f/360) # 20 to put into voltage amplitude, not power 
+    
+    
     
 #    valids = {
 #          '100- 130 MHz'  : np.where(np.logical_and(fq>.100 ,fq<.130)), 
@@ -49,7 +57,7 @@ for filename in sys.argv[1:]:
[…]

### 2016-02-29 DishReflectometry/Paper1_v1.tex
added section before 2-element to introduce reception with multiple reflections

@@
 \end{figure*}
+
+\section{Antenna Reception With Multiple Reflections}
+To examine the performance of an antenna and feed in the presence of multiple reflections, think of the system as a screen at a distance $F$ from a feed (see Fig.
+\ref{fig:sys}), noting that this does ignore the sky pattern of the feed itself.
+The screen reflects voltage as $\Gamma_d$ and transmits $(1+\Gamma_d)$ (see, {\em e.g.} Pozar).
+Similarly, the feed reflects $\Gamma_f$ and transmits $(1+\Gamma_f)$.
+The voltage pattern $\volt_{sky}$ is incident onto that system and  $(1+\Gamma_{d})(1+\Gamma_{f})$ is coupled into the cable leading from the feed.
+Additionally however, the voltage pattern is reflected off the feed ($\Gamma_f$), then the dish ($\Gamma_d$) and subsequently $(1+\Gamma_{f})$ of it reenters the feed with a roundtrip time delay $\Delta \tau=2F/c$.
+Hence, if $v_{sky}$ is reflected $n$ times in between the feed and the dish, the net voltage entering the feed after the
+$n^{th}$ reflection may be written as:
+\begin{eqnarray}
+\volt_{rec} & = &  (1+\Gamma_d) (1+\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber \\
+	&& + (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
+&&  ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}]
+\end{eqnarray}
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{microsys.pdf}
+\caption{System}
+\label{fig:sys}
+\end{figure}
+
+\noindent
+Defining $\Sigma_{\nu}=\volt_{rec}/\volt_{sky}$ and we see that 
+ \begin{equation}
+\Sigma_{\nu}  =   (1+\Gamma_d)(1+\Gamma_{f}) \displaystyle\sum\limits_{n=0}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
+   \label{eq:Sigma}
+\end{equation}
+Note that $n=0$ is when the initial wave enters the cable at the feed (where we assume we have set our reference plane).
+We may identify $(1+\Gamma_d)$ as the voltage reception pattern of the antenna, denoted $p_n(\theta,\phi)$, which is a function of angle on the sky.
+Additionally, $(1+\Gamma_f$) is the voltage efficiency for the feed (not a function of angle), denoted $\eta_f$.
+
+(As an aside, note that the sum in Eq. \ref{eq:Sigma} equals:
+\begin{equation}
+\Sigma_{\nu} =  (1+\Gamma_d)(1+\Gamma_{f})\frac{1+\Gamma_{f}^{N+1}\Gamma_{d}^{N+1}e^{(N+1)i\theta}}{1+\Gamma_{f}\Gamma_{d}e^{i\theta}} \nonumber
+\end{equation}
+which, in the limit becomes:
+\begin{equation}
+\Sigma_{\nu} = \frac{ (1+\Gamma_d)(1+\Gamma_{f})}{1+\Gamma_{f}\Gamma_{d}e^{i\theta}} \nonumber
+\end{equation} 
+since $|\Gamma_d|$ and $|\Gamma_f|$ are less than one.)
+
+To measure this quantity, we may connect a vector network analyzer (VNA) to the feed, calibrate it to the end of the cable at the feed and measure. 
+In this case, we ignore $\volt_{sky}$, and we see that $\Gamma_f \volt_{trans}$ gets reflected back from the feed connection and $(1+\Gamma_f)\volt_{trans}$ is emitted, where $\volt_{trans}$ is the signal from the VNA.
+$\Gamma_d$ of that is reflected back towards the feed and $(1+\Gamma_f)$ is received by the VNA suitably delayed.
+The received voltage after $n$ reflections (where again $n=0$ is the first reflected signal at the reference plane) is therefore:
+
+\begin{eqnarray}
+\volt_{rec} & = &  \Gamma_f \volt_{trans} \nonumber \\
+         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp \nonumber \\
+         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp \Gamma_d\Gamma_f\dfngexp \nonumber \\
+         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp (\Gamma_d\Gamma_f\dfngexp)^2 \nonumber \\
+&&  ....+ \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp (\Gamma_d\Gamma_f\dfngexp)^n
+\end{eqnarray}
+Defining $s_{11}=\volt_{rec}/\volt_{trans}$ (the VNA measured quantity), this may be factored to yield
+\begin{equation}
+s_{11} = \Gamma_f + \frac{(1+\Gamma_f)^2}{\Gamma_{f}} \displaystyle\sum\limits_{n=1}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
+\end{equation}
+Adding in the zeroth term and rearranging, we have
+\begin{equation}
+s_{11} +\frac{(1+\Gamma_f)^2}{\Gamma_f}-\Gamma_f = \frac{(1+\Gamma_f)^2}{\Gamma_{f}} \displaystyle\sum\limits_{n=0}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
+\end{equation}
+Comparing to Eq. \ref{eq:Sigma} and we find that
+\begin{equation}
+\Sigma_{\nu} = (1+\Gamma_d)\frac{\Gamma_f}{(1+\Gamma_{f})}\left(s_{11} + \frac{(1+\Gamma_f)^2}{\Gamma_f}- \Gamma_f\right)
+\end{equation}
+After rearranging and plugging in for $p_n(\theta,\phi)$ and $\eta_f$ we find
+\begin{equation}
+\Sigma_{\nu} = p_n(\theta,\phi)\left[\frac{\Gamma_f}{\eta_f}\left(s_{11} - \Gamma_f\right) + \eta_f\right]
+\end{equation}
+By measuring the feed separately, we may use that result for $\Gamma_f = s_{11,f}$ and $\eta_f = 1 + s_{11,f}$.
+
+For power, we want the squared magnitude, or:
+\begin{equation}
+\raggedright
+|\Sigma_{\nu}|^2 =  P_n(\theta,\phi)\times ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\nonumber
+\end{equation}
+\begin{equation}
+             \left[\epsilon_f +  2\operatorname{Re}\left(\frac{\Gamma_f}{\eta_f}(s_{11} - \Gamma_f)\right) 
+                              + \frac{|\Gamma_f|^2}{\epsilon_{f}}|s_{11} - \Gamma_f|^2 \right]
+\end{equation}
+where $P_n(\theta,\phi)= |p_n(\theta,\phi)|^2$ is the normalized power pattern, and $\epsilon_f=|\eta_f|^2$ is the feed efficiency.
 

### 2016-02-29 DishReflectometry/Paper1_v1.tex
updated section 3

@@
 \noindent
-Defining $\Sigma_{\nu}=\volt_{rec}/\volt_{sky}$ and we see that 
+Defining $a=\volt_{rec}/\volt_{sky}$ and we see that 
  \begin{equation}
-\Sigma_{\nu}  =   (1+\Gamma_d)(1+\Gamma_{f}) \displaystyle\sum\limits_{n=0}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
+a  =   (1+\Gamma_d)(1+\Gamma_{f}) \displaystyle\sum\limits_{n=0}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
    \label{eq:Sigma}
@@
 Note that $n=0$ is when the initial wave enters the cable at the feed (where we assume we have set our reference plane).
-We may identify $(1+\Gamma_d)$ as the voltage reception pattern of the antenna, denoted $p_n(\theta,\phi)$, which is a function of angle on the sky.
+We may identify $(1+\Gamma_d)$ as the voltage reception pattern of the antenna, denoted $p_n(\hat{\theta})$, which is a function of angle on the sky.
 Additionally, $(1+\Gamma_f$) is the voltage efficiency for the feed (not a function of angle), denoted $\eta_f$.
 
-(As an aside, note that the sum in Eq. \ref{eq:Sigma} equals:
+As an aside, note that the sum in Eq. \ref{eq:Sigma} may be evaluated we may rewrite
 \begin{equation}
-\Sigma_{\nu} =  (1+\Gamma_d)(1+\Gamma_{f})\frac{1+\Gamma_{f}^{N+1}\Gamma_{d}^{N+1}e^{(N+1)i\theta}}{1+\Gamma_{f}\Gamma_{d}e^{i\theta}} \nonumber
+a =  (1+\Gamma_d)(1+\Gamma_{f})\frac{1+\Gamma_{f}^{N+1}\Gamma_{d}^{N+1}(\dfngexp)^{N+1}}{1+\Gamma_{f}\Gamma_{d}\dfngexp} \nonumber
 \end{equation}
@@
 \begin{equation}
-\Sigma_{\nu} = \frac{ (1+\Gamma_d)(1+\Gamma_{f})}{1+\Gamma_{f}\Gamma_{d}e^{i\theta}} \nonumber
+a = \frac{ (1+\Gamma_d)(1+\Gamma_{f})}{1+\Gamma_{f}\Gamma_{d}\dfngexp} \nonumber
 \end{equation} 
-since $|\Gamma_d|$ and $|\Gamma_f|$ are less than one.)
+since $|\Gamma_d|$ and $|\Gamma_f|$ are less than one.
 
@@
 \begin{equation}
-\Sigma_{\nu} = (1+\Gamma_d)\frac{\Gamma_f}{(1+\Gamma_{f})}\left(s_{11} + \frac{(1+\Gamma_f)^2}{\Gamma_f}- \Gamma_f\right)
+a = (1+\Gamma_d)\frac{\Gamma_f}{(1+\Gamma_{f})}\left(s_{11} + \frac{(1+\Gamma_f)^2}{\Gamma_f}- \Gamma_f\right)
 \end{equation}
-After rearranging and plugging in for $p_n(\theta,\phi)$ and $\eta_f$ we find
+After rearranging and plugging in for $p_n(\hat{\theta})$ and $\eta_f$ we find
 \begin{equation}
-\Sigma_{\nu} = p_n(\theta,\phi)\left[\frac{\Gamma_f}{\eta_f}\left(s_{11} - \Gamma_f\right) + \eta_f\right]
+a = p_n(\hat{\theta})\left[\eta_f + \frac{\Gamma_f}{\eta_f}\left(s_{11} - \Gamma_f\right)\right]
 \end{equation}
@@
 \raggedright
-|\Sigma_{\nu}|^2 =  P_n(\theta,\phi)\times ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\nonumber
+A(\hat{\theta}) = |aa^*|^2 =  P_n(\hat{\theta})\times ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\nonumber
 \end{equation}
@@
 \end{equation}
-where $P_n(\theta,\phi)= |p_n(\theta,\phi)|^2$ is the normalized power pattern, and $\epsilon_f=|\eta_f|^2$ is the feed efficiency.
+where $P_n(\hat{\theta})= |p_n(\hat{\theta})|^2$ is the normalized power pattern, and $\epsilon_f=|\eta_f|^2$ is the feed efficiency.
 
 \section{Visibility measurements by a two element interferometer and the delay spectrum}
-
-Consider a two element interferometer with a baseline $\vec b$ and antenna field pattern $\bmvolt(\thhat, \nu)$.
-If we denote the electric field sky signal in direction $\thhat$ by $\volt_\sky(\vec \theta, \nu)$ and the receiver noise of each element as $\volt_{rec}(\nu)$ then the voltage output of each antenna may be written as,
+Now consider a two element interferometer with a baseline $\vec b$.
+If we denote the electric field sky signal in direction $\thhat$ by $\volt_\sky(\vec \theta, \nu)$  then the voltage output of each antenna may be written as,
 \begin{equation}
@@
 \end{equation}
-where $\bmvolt_{1}(\thhat,\nu)$ and $\bmvolt_{2}(\thhat,\nu)$ are the electric field response patterns 
-of the two antennas.
 Hence, the time averaged visibility measured by the interferometer may be written as, 

### 2016-02-29 DishReflectometry/Paper1_v1.tex
Corrected citation
first (incomplete) pass at updating the next few sections (primarily %%% commenting out of material already now covered earlier

@@
 \section{Antenna Reception With Multiple Reflections}
+\label{sec:multiple}
 To examine the performance of an antenna and feed in the presence of multiple reflections, think of the system as a screen at a distance $F$ from a feed (see Fig.
@@
 Therefore, it is necessary to measure and understand the instrument delay spectrum in order to qualify the system for the measurement of 21cm power spectrum.
-In this section we compute the visibility of a two element interferometer accounting for the additional reflections of the sky signal in between the feed and the dish vertex and the corresponding effects on the delay spectrum.
+In this section we compute the visibility of a two element interferometer accounting for the additional reflections of the sky signal in between the feed and the dish vertex and the corresponding effects on the delay spectrum, using the multiple reflection formulation of Sec.
+\ref{sec:multiple}.
 
-\begin{figure}[ht!]
-\centering
-\includegraphics[totalheight=0.35\textheight]{plots/reflection_cartoon.png}
-\caption{The propagation path of the sky signal entering the
-feed in receiving mode is shown in blue.
+%%%\begin{figure}[ht!]
+%%%\centering
+%%%\includegraphics[totalheight=0.35\textheight]{plots/reflection_cartoon.png}
+%%%\caption{The propagation path of the sky signal entering the
+%%%feed in receiving mode is shown in blue.
 Due to impedance mismatch between feed and the free space, a part of the signal (dashed blue) is reflected off the feed.
@@
 }
-\label{fig:cartoon}
-\end{figure}
-
-Consider again a two element interferometer as described in section 2.
+%%%\label{fig:cartoon}
+%%%\end{figure}
+%%%
+%%%Consider again a two element interferometer as described in section 2.
 Two antennas are assumed to be exactly identical so that their electrical parameters and the field pattern are identical i.e, $a_{1}(\thhat,\nu) = a_{2}(\thhat,\nu) = a(\thhat, \nu)$.
@@
 If the focal length of the dish is $l$, assuming the feed is located at the focus, the roundtrip delay after first reflection will be $\Delta \tau = {2l \over c}$.
-
-%\subsection{Visibility and delay spectrum computation considering multiple reflections}
-Upon first incidence of the sky signal $\volt_{sky}$, $\Gamma_{f}$ fraction of the voltage is reflected off the feed while $(1-\Gamma_{f})$ fraction is coupled to the feed.
+%%%
+%%%%\subsection{Visibility and delay spectrum computation considering multiple reflections}
+%%%Upon first incidence of the sky signal $\volt_{sky}$, $\Gamma_{f}$ fraction of the voltage is reflected off the feed while $(1-\Gamma_{f})$ fraction is coupled to the feed.
 The reflected voltage then further reflected off the dish and $(1-\Gamma_{f}) $ fraction of it reenters the feed with a roundtrip time delay $\Delta \tau$.
 Hence, if $I_{sky}$ is reflected n times in between the feed and the dish, the net voltage entering the feed after an
-$n^{th}$ reflection off the feed and the dish is written as:
-\begin{eqnarray}
-\volt_{1} & = &  \bmvolt (1-\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber \\
-	&& + (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
-&&  ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}] \nonumber
-\end{eqnarray}
-and, 
-\begin{eqnarray}
-\volt_{2} & = &  \bmvolt (1-\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber\\
-&&+  (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
-&& ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}] \fngexp \nonumber
-\end{eqnarray}
-Frequency as well as angular dependence of the quantities are not written explicitly for notational simplicity.
+%%%$n^{th}$ reflection off the feed and the dish is written as:
+%%%\begin{eqnarray}
+%%%\volt_{1} & = &  \bmvolt (1-\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber \\
+%%%	&& + (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
+%%%&&  ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}] \nonumber
+%%%\end{eqnarray}
+%%%and, 
+%%%\begin{eqnarray}
+%%%\volt_{2} & = &  \bmvolt (1-\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber\\
+%%%&&+  (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
+%%%&& ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}] \fngexp \nonumber
+%%%\end{eqnarray}
+%%%Frequency as well as angular dependence of the quantities are not written explicitly for notational simplicity.
 We also absorb the common gain term $(1-\Gamma_{f})$ with antenna field pattern $a$ and denote them as $\bmvolt_{f}= \bmvolt(1-\Gamma_{f})$ here after.
+
 The cross power generated by $v_{1}$ and $v_{2}$ would have spurious visibility response due to mutual correlation between multiply reflected voltages.
@@
 \vis(\vec b, \nu) & = & \int \volt_{1}\volt_{2}^{*} d\Omega \nonumber\\
-			& = & \int I_{sky}(\vec b, \nu)\Sigma(\nu) \fngexp d\Omega
+			& = & \int I_{sky}(\vec b, \nu)A(\thhat,\nu) \ifngexp d\Omega
 \end{eqnarray}
-
-where we define a combined common instrument parameter, written as, 
- \begin{eqnarray}
-\Sigma( \nu) & = & \beam_{f}  [ 1+  \Gamma_{f}\Gamma_{d} \dfngexp \nonumber\\
-&& + (\Gamma_{f}\Gamma_{d})^2(\dfngexp)^{2}+ \nonumber\\
-&&  ....+(\Gamma_{f}\Gamma_{d})^{n}(\dfngexp)^{n}  ]\\
-& = & \beam_{f}+\beam_{f} \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
-   \nonumber\\ 
-   \label{eq6}
-\end{eqnarray}
-where, $\beam_{f}=\bmvolt_{f}\bmvolt_{f}^{*}= |a(1-\Gamma_{f})|^{2}$ is the antenna cross power pattern.
+%%%where we define a combined common instrument parameter, written as, 
+%%% \begin{eqnarray}
+%%%\Sigma(\thhat, \nu) & = & \beam_{f}  [ 1+  \Gamma_{f}\Gamma_{d} \dfngexp \nonumber\\
+%%%&& + (\Gamma_{f}\Gamma_{d})^2(\dfngexp)^{2}+ \nonumber\\
+%%%&&  ....+(\Gamma_{f}\Gamma_{d})^{n}(\dfngexp)^{n}  ]\\
+%%%& = & \beam_{f}+\beam_{f} \displaystyle\sum\limits_{n=1}^{n} [2\Re( \Gamma_{f}\Gamma_{d}\dfngexp)]^{n}
+%%%   \nonumber\\ 
+%%%   \label{eq6}
+%%%\end{eqnarray}
+%%%where, $\beam_{f}=\bmvolt_{f}\bmvolt_{f}^{*}= |a(1-\Gamma_{f})|^{2}$ is the antenna cross power pattern.
 and the delay spectrum would be, 
@@
 %\tilde V(\vec b, \tau) & = & \int \left [ \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp  d\Omega \right ]  e^{-2\pi i\nu\tau} d\nu \nonumber \\
-\tilde V(\vec b, \tau) & = & \int \left [ I_{sky}(\thhat, \nu) \ast \Sigma(\thhat, \nu) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )  \right] d\Omega
+\tilde V(\vec b, \tau) & = & \int \left [ I_{sky}(\vec b, \nu) \ast A(\vec b, \nu) \right]\dfngexp d\Omega
 \label{eq7}
@@
 \begin{eqnarray}
-\tilde I_{meas}(\vec b, \nu) & = & \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \dfngexp d\Omega
+\tilde I_{meas}(\vec b, \nu) & = & \int I_{sky}(\vec b, \nu)A(\vec b, \nu) \dfngexp d\Omega
 \end{eqnarray}
@@
 Upon our assumption that two adjacent antenna elements have identical electrical properties, this power is also a measure of the cross power or the visibility $\vis (\vec b, \nu)$ between the two antennas with a normalisation factor of $2$.
-Once again, it is to be noted that upon the first incidence, the sky signal is focussed onto the feed from the entire dish and the dish reflection coefficient $\Gamma_{d}$ is $1$ for this first incidence.
+
+%%%Once again, it is to be noted that upon the first incidence, the sky signal is focussed onto the feed from the entire dish and the dish reflection coefficient $\Gamma_{d}$ is $1$ for this first incidence.
 The subsequent back and forth reflection of the signal in between the feed and the dish, however, occurs from only the part of the dish which is shadowed by the feed.
@@
 For a given baseline $\vec b$, taking the ratio of the measured power and the incident power,
-
-\begin{eqnarray}\label{eqn:ratio1}
-{I_{meas} \over I_{sky} } & = & \Sigma(\vec b, \nu) \nonumber\\
-  & = & \beam_{f}+ \beam_{f} \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
-   \nonumber\\
-   \label{eq8}
-\end{eqnarray}
-
-The right hand side of this equation is the instrument response kernel of a single HERA element as well as a representative of the instrument response in the measured visibility data between a pair of antennas.
+%%%
+%%%\begin{eqnarray}\label{eqn:ratio1}
+%%%{I_{meas} \over I_{sky} } & = & \Sigma(\vec b, \nu) \nonumber\\
+%%%  & = & \beam_{f}+ \beam_{f} \displaystyle\sum\limits_{n=1}^{n} [2\Re(\Gamma_{f}\Gamma_{d}\dfngexp)]^{n}
+%%%   \nonumber\\
+%%%   \label{eq8}
+%%%\end{eqnarray}
+%%%
+%%%The right hand side of this equation is the instrument response kernel of a single HERA element as well as a representative of the instrument response in the measured visibility data between a pair of antennas.
 Our goal is to measure this kernel as a function of frequency and determine its effect on the delay spectrum of the visibility.
-
-%%%%%%%%%%%%%%%%%
-\subsection{Measurement equations}
-The instrument response kernel is measured by measuring the return loss of the HERA element at the output port of the feed using a vector network analyser.
+%%%
+%%%%%%%%%%%%%%%%%%%%
+%%%\subsection{Measurement equations}
+%%%The instrument response kernel is measured by measuring the return loss of the HERA element at the output port of the feed using a vector network analyser.
 The vector network analyser transmits a broadband noise of known amplitude and phase via a $50ft$ cable up to the feed.
@@
 However, the reflected signal from the dish vertex returns to
-the feed. This incident signal is now
-reflected back and forth in between the feed and the dish much like the sky
-signal reflection discussed previously.
-
-If $I_{tr}$ is the signal transmitted by the VNA and $\Gamma_{f}$ is the feed reflection coefficient, $\Gamma_{f}$ fraction of this transmitted power would be reflected back to the VNA while $(1-\Gamma_{f})$ fraction would be radiated.
+%%%the feed. This incident signal is now
+%%%reflected back and forth in between the feed and the dish much like the sky
+%%%signal reflection discussed previously.
+%%%
+%%%If $I_{tr}$ is the signal transmitted by the VNA and $\Gamma_{f}$ is the feed reflection coefficient, $\Gamma_{f}$ fraction of this transmitted power would be reflected back to the VNA while $(1-\Gamma_{f})$ fraction would be radiated.
 $\Gamma_{d}$ fraction of this radiated power will be reflected back and forth in between the feed and the dish with partial coupling of the signal into the feed at each reflection.
 The power radiated out of the feed, denoted by $I_{r}$ is ,
-\begin{equation}
-I_{r}= \beam_{f} I_{tr}
-\end{equation}
-
-The total reflected power returned to the VNA, as measured by the VNA would be:
-\begin{eqnarray}\label{eqn:series2}
-I_{meas} & = & \Gamma_{f}I_{tr}+ I_{r}(1-\Gamma_{f}) [\Gamma_{d} \dfngexp + \Gamma_{f}\Gamma_{d}^{2} (\dfngexp)^{2}\nonumber\\
-&&+ ....+ \Gamma_{f}^{n-1}\Gamma_{d})^{n}(\dfngexp)^{n}]
-\end{eqnarray}
-
-Using the value of $I_{r}$ and simplifying:
-
-  \begin{eqnarray}\label{eqn:ratio2}
- {I_{meas} \over I_{tr} } & = & \Gamma_{f}
-  +  \Gamma_{d}(1-\Gamma_f) \beam_{f} I_{tr} [e^{i\phi}+ \Gamma_{f}\Gamma_{d} e^{i2\phi}\nonumber\\ 
-  && +  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{i n\phi}]\nonumber\\
-  & = & \Gamma_{f} + { (1-\Gamma_f)\beam_{f}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
- \label{eq9}
-\end{eqnarray}
-
-The ratio in Equation \ref{eqn:ratio2} is identical to the ratio in the sky
-observation in Equation \ref{eqn:ratio1} except in three factors. The
-first factor corresponds to an additive amplitude difference arising from
-$\Gamma_{f}$, which physically accounts for the initial reflection at the feed.
-The second difference is the multiplicative ${ (1-\Gamma_f)\over \Gamma_{f} }$.
+%%%\begin{equation}
+%%%I_{r}= \beam_{f} I_{tr}
+%%%\end{equation}
+%%%
+%%%The total reflected power returned to the VNA, as measured by the VNA would be:
+%%%\begin{eqnarray}\label{eqn:series2}
+%%%I_{meas} & = & \Gamma_{f}I_{tr}+ I_{r}(1-\Gamma_{f}) [\Gamma_{d} \dfngexp + \Gamma_{f}\Gamma_{d}^{2} (\dfngexp)^{2}\nonumber\\
+%%%&&+ ....+ \Gamma_{f}^{n-1}\Gamma_{d}^{n}(\dfngexp)^{n}]
+%%%\end{eqnarray}
+%%%
+%%%Using the value of $I_{r}$ and simplifying:
+%%% 
+%%%  \begin{eqnarray}\label{eqn:ratio2}
+%%% {I_{meas} \over I_{tr} } & = & \Gamma_{f}
+%%%  +  \Gamma_{d}(1-\Gamma_f) \beam_{f} I_{tr} [e^{i\phi}+ \Gamma_{f}\Gamma_{d} e^{i2\phi}\nonumber\\ 
+%%%  && +  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{i n\phi}]\nonumber\\
+%%%  & = & \Gamma_{f} + { (1-\Gamma_f)\beam_{f}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
+%%% \label{eq9}
+%%%\end{eqnarray}
+%%%
+%%%The ratio in Equation \ref{eqn:ratio2} is identical to the ratio in the sky
+%%%observation in Equation \ref{eqn:ratio1} except in three factors. The
+%%%first factor corresponds to an additive amplitude difference arising from
+%%%$\Gamma_{f}$, which physically accounts for the initial reflection at the feed.
+%%%The second difference is the multiplicative ${ (1-\Gamma_f)\over \Gamma_{f} }$.
 In addition, in order to estimate the true response of the system to the sky signal in the receiving mode, we add the term $A_{f}$.
@@
 The corrected measurement could be written as
- \begin{eqnarray}\label{eqn:ratio2}
- \left[{I_{meas} \over I_{tr}}-\Gamma_{f}\right]{ \Gamma_{f} \over (1-\Gamma_{f})} + \beam_{f}  & = & \beam_{f}+ \beam_{f} \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}\nonumber\\
- & = & {I_{meas} \over I_{sky} }
- \label{eq9}
-\end{eqnarray}
+%%% \begin{eqnarray}\label{eqn:ratio2}
+%%% \left[{I_{meas} \over I_{tr}}-\Gamma_{f}\right]{ \Gamma_{f} \over (1-\Gamma_{f})} + \beam_{f}  & = & \beam_{f}+ \beam_{f} \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}\nonumber\\
+%%% & = & {I_{meas} \over I_{sky} }
+%%% \label{eq9}
+%%%\end{eqnarray}
 %++++++++++++++++++++++++++++++++++++++++++++++++++++++

### 2016-02-29 DishReflectometry/Paper1_v1.tex
moved system plot over to plots directory
got rid of eta and epsilon

@@
 \centering
-\includegraphics[width=0.5\textwidth]{microsys.pdf}
+\includegraphics[width=0.5\textwidth]{plots/microsys.pdf}
 \caption{System}
@@
 We may identify $(1+\Gamma_d)$ as the voltage reception pattern of the antenna, denoted $p_n(\hat{\theta})$, which is a function of angle on the sky.
-Additionally, $(1+\Gamma_f$) is the voltage efficiency for the feed (not a function of angle), denoted $\eta_f$.
+Additionally, $(1+\Gamma_f$) is the voltage efficiency for the feed (not a function of angle).
 
@@
 \end{equation}
-After rearranging and plugging in for $p_n(\hat{\theta})$ and $\eta_f$ we find
+After rearranging and plugging in for $p_n(\hat{\theta})$ we find
 \begin{equation}
-a = p_n(\hat{\theta})\left[\eta_f + \frac{\Gamma_f}{\eta_f}\left(s_{11} - \Gamma_f\right)\right]
+a = p_n(\hat{\theta})\left[(1+\Gamma_f) + \frac{\Gamma_f}{(1+\Gamma_f)}\left(s_{11} - \Gamma_f\right)\right]
 \end{equation}
-By measuring the feed separately, we may use that result for $\Gamma_f = s_{11,f}$ and $\eta_f = 1 + s_{11,f}$.
+By measuring the feed separately, we may use that result for $\Gamma_f = s_{11,f}$.
 
@@
 \begin{equation}
-             \left[\epsilon_f +  2\operatorname{Re}\left(\frac{\Gamma_f}{\eta_f}(s_{11} - \Gamma_f)\right) 
-                              + \frac{|\Gamma_f|^2}{\epsilon_{f}}|s_{11} - \Gamma_f|^2 \right]
+             \left[|1+\Gamma_f|^2 +  2\operatorname{Re}\left(\frac{\Gamma_f}{(1+\Gamma_f)}(s_{11} - \Gamma_f)\right) 
+                              + \frac{|\Gamma_f|^2}{|1+\Gamma_{f}|^2}|s_{11} - \Gamma_f|^2 \right]
 \end{equation}
-where $P_n(\hat{\theta})= |p_n(\hat{\theta})|^2$ is the normalized power pattern, and $\epsilon_f=|\eta_f|^2$ is the feed efficiency.
+where $P_n(\hat{\theta})= |p_n(\hat{\theta})|^2$ is the normalized power pattern.  Note that $|1+\Gamma_f|^2$ is the feed efficiency ($\epsilon_f$).
 

### 2016-03-01 ForegroundSimulations/ms.tex
Update figures
From e0b14ff (master):
=====================

(*) Add and update figures

In ms.tex,

(*) Update figures

@@
 \centering
-\includegraphics[width=\linewidth]{asm_foreground_eor_beam_chromaticity_fullband.eps}
+\includegraphics[width=\linewidth]{asm_foreground_eor_beam_chromaticity_fullband_bhw2.0.eps}
 \caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra for different baselines.}
@@
 Thus, we leave delay power spectrum estimation using {\it foreground removal} strategy to future work and use {\it foreground avoidance} approach in this study.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=\linewidth]{spec_on_achrmbeam_foreground_reflected_power_21cmfast_14.6m_150.0_MHz_subband_v2.eps}
+\caption{Attenuation of foreground power (in dB) from antenna-to-antenna reflections required to keep the reflected foreground power below EoR H{\sc i} signal power.}
+\label{fig:fg-reflections-achrmbeam}
+\end{figure}
+
+\begin{figure*}[htb]
+\centering
+\includegraphics[width=\linewidth]{spec_on_foreground_reflected_power_21cmfast_14.6m_150.0_MHz_subband_v2.eps}
+\caption{Attenuation of foreground power (in dB) from antenna-to-antenna reflections required to keep the reflected foreground power below EoR H{\sc i} signal power.}
+\label{fig:fg-reflections}
+\end{figure*}
 
@@
 \centering
-\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_150.0_MHz_subband.eps}
+\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_150.0_MHz_subband_win_method_bhw2.0.eps}
 \caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra obtained from the 150~MHz subband for different baseline lengths.}
@@
 \centering
-\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_170.0_MHz_subband.eps}
+\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_170.0_MHz_subband_win_method_bhw2.0.eps}
 \caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra obtained from the 170~MHz subband for different baseline lengths.}
@@
 This finding holds even in the most conservative scenario where the modeled beam pattern with most severe chromaticity inherently results in significant and inherent foreground contamination outside the {\it foreground wedge}.
+
+\begin{figure*}[htb]
+\centering
+\subfloat[][Power patterns]{\label{fig:21cmfast-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_150.0_MHz_subband.eps}}
+\subfloat[][Power patterns]{\label{fig:lidz-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_150.0_MHz_subband.eps}} \\
+\subfloat[][Power patterns]{\label{fig:21cmfast-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_170.0_MHz_subband.eps}}
+\subfloat[][Power patterns]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_170.0_MHz_subband.eps}}
+\caption{}
+\label{fig:eor-fg-ratios}
+\end{figure*}
 
@@
 
-\begin{figure*}[htb]
-\centering
-\includegraphics[width=\linewidth]{spec_on_foreground_reflected_power_21cmfast_14.6m_150.0_MHz_subband_v2.eps}
-\caption{Attenuation of foreground power (in dB) from antenna-to-antenna reflections required to keep the reflected foreground power below EoR H{\sc i} signal power.}
-\label{fig:fg-reflections}
-\end{figure*}
-
 The required attenuation is also a sensitive function of the chosen $k_\parallel$ mode.

### 2016-03-01 ForegroundSimulations/ms.tex
Rearrange section and subsection titles
From 508edb8 (restructure):
==========================

In eor.bib,

(*) Add an entry for Harris (1978) on window functions

In ms.tex,

(*) Rearrange section and subsection titles
(*) Add couple of paragraphs on new spectral window function

@@
 
-\subsection{Directional Chromaticity of Power Pattern}\label{sec:directional-chromaticity}
+\subsection{Effects on Foreground Contamination}\label{sec:effects-fgdps}
 
-Fig.~\ref{fig:off-axis-beam-chromaticity} demonstrates the beyond-the-horizon spillover even from a flat-spectrum point source at different off-axis angles.
+In the estimation of power spectrum, specific choices for spectral weighting function, $W(f)$, has been found to be effective in reducing foreground contamination by many orders of magnitude \citep{thy13} and is regularly used in EoR data analysis \citep{par12a}.
+For instance, a {\it Blackman-Harris} function \citep{har78} has a dynamic range of $\sim$100 -- 120~dB in delay power spectrum and a reduced effective bandwidth, where, we define effective bandwidth as:
+\begin{align}
+  B_\textrm{eff} &= \int_{-B/2}^{+B/2} |W(f)|^2\,\dif f.
+\end{align}
+For a {\it Blackman-Harris} window function denoted by $W_\textrm{BH}(f)$, $B_\textrm{eff} \approx B/2$.
+Hence, the window spans a total of $2N$ frequency channels each of width $\Delta f$ to have $B_\textrm{eff} \approx N\,\Delta f$.
+
+Considering that the dynamic range required to suppress foreground contamination in the {\it EoR window} may be even higher than that provided by a {\it Blackman-Harris} window function, we use a modified version given by the convolution of a {\it Blackman-Harris} window with itself:
+\begin{align}
+  W(f) &= W_\textrm{BH}(f) \ast W_\textrm{BH}(f).
+\end{align}
+In delay spectrum, this window has a response that is obtained by squaring of the {\it Blackman-Harris} window response and thus improves the dynamic range further in the response by another 100 -- 120~dB.
+
+\subsection{Constraints on Reflections in the Instrument}\label{sec:constraints-reflectometry}
+
+% \subsection{Directional Chromaticity of Power Pattern}\label{sec:directional-chromaticity}
+
+% Fig.~\ref{fig:off-axis-beam-chromaticity} demonstrates the beyond-the-horizon spillover even from a flat-spectrum point source at different off-axis angles.
 The three panels correspond to delay spectra from different positions of the point source -- 0\arcdeg (left), 45\arcdeg (middle) and 89\arcdeg (right) -- from the zenith.
@@
 
-\begin{figure*}[htb]
-\centering
-\includegraphics[width=\linewidth]{off-axis_point_source_beam_chromaticity.eps}
-\caption{Chromaticity of antenna power pattern at directions off-axis. }
-\label{fig:off-axis-beam-chromaticity}
-\end{figure*}
+% \begin{figure*}[htb]
+% \centering
+% \includegraphics[width=\linewidth]{off-axis_point_source_beam_chromaticity.eps}
+% \caption{Chromaticity of antenna power pattern at directions off-axis. }
+% \label{fig:off-axis-beam-chromaticity}
+% \end{figure*}
 
-At 0\arcdeg off-axis, the {\it Airy} pattern has no spectral variation except that introduced by the {\it Blackman-Harris} window function and thus reproduces its Fourier response centered at $\tau = 0$~ns whereas the simulated power pattern is found to exhibit some spectral variation giving rise to the wings on either side of $\tau = 0$~ns.
+% At 0\arcdeg off-axis, the {\it Airy} pattern has no spectral variation except that introduced by the {\it Blackman-Harris} window function and thus reproduces its Fourier response centered at $\tau = 0$~ns whereas the simulated power pattern is found to exhibit some spectral variation giving rise to the wings on either side of $\tau = 0$~ns.
 As off-axis angle increases to 45\arcdeg, both the power patterns clearly exhibit chromaticity.
@@
 
-It is important to note that in a generic scenario where visibilities are not phased to a specific foreground location, the chromaticity of the power pattern will imprint itself on location of the foreground objects in delay space and will give rise to significant spillover especially from foregrounds near the horizon.
+% It is important to note that in a generic scenario where visibilities are not phased to a specific foreground location, the chromaticity of the power pattern will imprint itself on location of the foreground objects in delay space and will give rise to significant spillover especially from foregrounds near the horizon.
 
-We generalize the analysis above by computing the delay power spectrum of the power pattern along its spectral axis in every direction in an effort to study its performance as a function of angle on the sky.
-\begin{align}
-  A^\prime(l,m,\tau) &= \int A(l,m,f)\,e^{-j 2\pi f\tau} \,\dif f
-\end{align}
+% We generalize the analysis above by computing the delay power spectrum of the power pattern along its spectral axis in every direction in an effort to study its performance as a function of angle on the sky.
+% \begin{align}
+%   A^\prime(l,m,\tau) &= \int A(l,m,f)\,e^{-j 2\pi f\tau} \,\dif f
+% \end{align}
 
-We define the directional chromaticity of antenna power pattern as:
-\begin{align}
-  C(l,m) &= \frac{ \int\limits_{|\tau|>60\,\textrm{ns}} |A^\prime|^2 \,\dif\tau }{\int\limits_{|\tau|>60\,\textrm{ns}} \dif\tau}
-\end{align}
-where, the limit $|\tau|>60$~ns was chosen to represent a region well beyond the horizon limits ($\pm 48.7$~ns) for a 14.6~m antenna spacing.
+% We define the directional chromaticity of antenna power pattern as:
+% \begin{align}
+%   C(l,m) &= \frac{ \int\limits_{|\tau|>60\,\textrm{ns}} |A^\prime|^2 \,\dif\tau }{\int\limits_{|\tau|>60\,\textrm{ns}} \dif\tau}
+% \end{align}
+% where, the limit $|\tau|>60$~ns was chosen to represent a region well beyond the horizon limits ($\pm 48.7$~ns) for a 14.6~m antenna spacing.
 It thus measures the average power arising out of chromaticity in each delay mode beyond $|\tau|>60$~ns.
 
-Fig.~\ref{fig:directional-beam-chromaticity} shows the directional chromaticity, $C(l,m)$, of the power patterns of an {\it Airy} disk for reference (left) and a simulated disk (middle) on an orthographic projection onto direction cosines.
+% Fig.~\ref{fig:directional-beam-chromaticity} shows the directional chromaticity, $C(l,m)$, of the power patterns of an {\it Airy} disk for reference (left) and a simulated disk (middle) on an orthographic projection onto direction cosines.
 Their color scale is shown at the top for reference.
@@
 
-Also shown are the tracks (black dots) of point sources brighter than 50~Jy in the LST range 0--12~hrs.
+% Also shown are the tracks (black dots) of point sources brighter than 50~Jy in the LST range 0--12~hrs.
 The solid circle near the bottom denotes the south celestial pole.
@@
 
-\begin{figure*}[htb]
-\centering
-\includegraphics[width=\linewidth]{directional_high_delay_average_in_beam.eps}
-\caption{All-sky directional chromaticity of antenna power pattern. }
-\label{fig:directional-beam-chromaticity}
-\end{figure*}
+% \begin{figure*}[htb]
+% \centering
+% \includegraphics[width=\linewidth]{directional_high_delay_average_in_beam.eps}
+% \caption{All-sky directional chromaticity of antenna power pattern. }
+% \label{fig:directional-beam-chromaticity}
+% \end{figure*}
 
@@
 
+\section{EoR Sensitivity}\label{sec:eor-sensitivity}
+
 \section{Summary}\label{sec:summary}

### 2016-03-02 ForegroundSimulations/ms.tex
Add and update figures, and edit section 5.1
From a653e3f (restructure):
==========================

(*) Update foreground delay power spectrum figures
(*) Add spectral weghting function figure to git repo

In ms.tex,

(*) Use updated foreground delay power spectrum figures
(*) Major changes to section 5.1 - introduce spectral weighting
functions and text on effects of beam chromaticity on foreground
delay spectra

@@
 
-In this paper, we investigate the spectral properties of the proposed dish design through their effects on the resultant foreground delay power spectrum and the constraints they place on attenuation required to suppress reflections between the dish-receiver assembly to within tolerable limits.
+In this paper, we investigate the spectral properties of the proposed dish design through their effects on the resultant foreground delay power spectrum and the constraints they place on attenuation required to suppress reflections between the dish-receiver assembly and antenna pairs to within tolerable limits.
 
@@
 This frequency independent model will be used to isolate the effects of spectral structures in the antenna power pattern (or beam chromaticity) on foreground delay power spectra.
+Hereafter, we refer to these three beams as `simulated', `{\it Airy}' and `achromatic' models.
 
 In a related series of papers, Neben et~al.
-(2016; submitted) discuss the agreement of these model antenna beam patterns with actual measurements and Ewall-Wice et~al.
+(2016; submitted) discuss the agreement of these simulated antenna beam patterns with actual measurements and Ewall-Wice et~al.
 (2016; submitted) model the reflections and return loss expected in the proposed antenna-receiver assembly.
@@
 
-\subsection{Effects on Foreground Contamination}\label{sec:effects-fgdps}
+\subsection{Effect on Foreground Contamination}\label{sec:effects-fgdps}
 
-In the estimation of power spectrum, specific choices for spectral weighting function, $W(f)$, has been found to be effective in reducing foreground contamination by many orders of magnitude \citep{thy13} and is regularly used in EoR data analysis \citep{par12a}.
-For instance, a {\it Blackman-Harris} function \citep{har78} has a dynamic range of $\sim$100 -- 120~dB in delay power spectrum and a reduced effective bandwidth, where, we define effective bandwidth as:
-\begin{align}
-  B_\textrm{eff} &= \int_{-B/2}^{+B/2} |W(f)|^2\,\dif f.
+Since our aim in this paper is to quantify foreground contamination and EoR sensitivity without employing any sophisticated {\it foreground removal} techniques, we turn out attention to {\it foreground avoidance} strategy that employs spectral weighting technique.
+In such an estimation of power spectrum, specific choices for spectral weighting function, $W(f)$, have been found to be effective in reducing foreground contamination by many orders of magnitude \citep{thy13} and is regularly used in EoR data analysis \citep{par12a}.
+For instance, a {\it Blackman-Harris} function \citep{har78} has a dynamic range of $\sim$100 -- 120~dB in delay power spectrum and a reduced effective bandwidth, with:
+\begin{align}\label{eqn:Beff}
+  \epsilon &= \frac{1}{B} \int_{-B/2}^{+B/2} |W(f)|^2\,\dif f, \\
+  \textrm{and,}\quad B_\textrm{eff} &= \epsilon\,B,
+  % B_\textrm{eff} &= \int_{-B/2}^{+B/2} |W(f)|^2\,\dif f.
 \end{align}
-For a {\it Blackman-Harris} window function denoted by $W_\textrm{BH}(f)$, $B_\textrm{eff} \approx B/2$.
+where, $1-\epsilon$ is the loss in overall spectral sensitivity and $B_\textrm{eff}$ is the effective bandwidth.
+For a {\it Blackman-Harris} window function denoted by $W_\textrm{BH}(f)$, $\epsilon \approx 50\%$.
 Hence, the window spans a total of $2N$ frequency channels each of width $\Delta f$ to have $B_\textrm{eff} \approx N\,\Delta f$.
 
-Considering that the dynamic range required to suppress foreground contamination in the {\it EoR window} may be even higher than that provided by a {\it Blackman-Harris} window function, we use a modified version given by the convolution of a {\it Blackman-Harris} window with itself:
-\begin{align}
+Considering that the dynamic range required to suppress foreground contamination in the {\it EoR window} may probably be even higher than that provided by a {\it Blackman-Harris} window function, we use a modified version given by the convolution of a {\it Blackman-Harris} window with itself:
+\begin{align}\label{eqn:bhw2}
   W(f) &= W_\textrm{BH}(f) \ast W_\textrm{BH}(f).
 \end{align}
-In delay spectrum, this window has a response that is obtained by squaring of the {\it Blackman-Harris} window response and thus improves the dynamic range further in the response by another 100 -- 120~dB.
+In its Fourier domain, this window has a response that is obtained by squaring of the {\it Blackman-Harris} window response and thus improves the dynamic range further in the power response by another 100 -- 120~dB while $\epsilon\approx 42\%$.
+This is an enormous gain in sidelobe characteristics for a negligible loss in over sensitivity relative to a simple {\it Blackman-Harris} weighting.
+This will ensure that the contamination resulting from spillover of foregrounds along the line-of-sight $k$-modes are limited by intrinsic spectral structures in the foregrounds and the beam patterns and not by sidelobes from spectral weighting.
+In this paper, we apply this modified spectral weighting function defined in equation~\ref{eqn:bhw2} whenever foregrounds are represented in the Fourier delay domain.
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=\linewidth]{window_function_modifications.eps}
+  \caption{Choices for spectral weighting functions, $W(f)$ ({\it top}) and their delay power spectrum responses, $|\widetilde{W}(\tau)|^2$ ({\it bottom}).
+The gray curves correspond to a {\it Blackman-Harris} window while those in black correspond to a {\it Blackman-Harris} window convolved with itself.
+The overall sensitivity of the former is $\epsilon \approx 50\%$ of a rectangular window while that of the latter is $\epsilon \approx 42\%$.
+Hence, the latter is narrower than the former.
+As a result, the main lobe of the convolved window function response is wider than that of a {\it Blackman-Harris} window.
+However, the sidelobes from the convolved window function are suppressed by more than ten orders of magnitude relative to that of a nominal {\it Blackman-Harris} window for only a slight loss of resolution.}
+  \label{fig:window-functions}
+\end{figure}
+
+In HERA-19 array layout, there are 30 unique baseline vectors and 8 unique baseline lengths.
+Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines} shows the delay power spectra of foregrounds on the 8 unique baseline lengths obtained with the aforementioned models for power pattern.
+In all these panels, the full-band spectrally weighted foreground delay power spectra obtained with achromatic, {\it Airy} and fully chromatic simulated beam patterns are shown in black, red, and blue respectively.
+The brightening of foreground power near the horizon limits (vertical dotted lines) due to the {\it pitchfork} effect \citep{thy15a,thy15b} is prominently seen in all cases.
+A clear trend of broadening of spillover-wings outside the horizon limits is seen with increasing chromaticity as the beam is changed from the achromatic to the {\it Airy} to the chromatic simulated model.
+For instance, the spillover from foreground delay power spectrum obtained with chromatic beam pattern is restricted to $|k_\parallel| \lesssim 0.2\,h$~Mpc$^{-1}$, with the {\it Airy} pattern it is restricted to $|k_\parallel| \lesssim 0.15\,h$~Mpc$^{-1}$, while with the achromatic beam it is restricted to $|k_\parallel| \lesssim 0.12\,h$~Mpc$^{-1}$ even on longest baseline lengths.
+It is also noted that despite the extreme dynamic range of the employed spectral weighting function, the tail of the foreground spillover at $|k_\parallel| \gtrsim 0.2\,h$~Mpc$^{-1}$ with an {\it Airy} beam pattern is many orders of magnitude higher than that using an achromatic beam while that from the simulated chromatic beam is even higher than from an {\it Airy} pattern by a few orders of magnitude.
+This signals that the foreground spillover shown are truly limited by intrinsic spectral features in the antenna beam patterns.
+
+\begin{figure*}[htb]
+  \centering
+  \includegraphics[width=\linewidth]{asm_foreground_eor_beam_chromaticity_fullband_bhw2.0.eps}
+  \caption{Foreground delay power spectra on unique baseline lengths of HERA-19 at arbitrary local sidereal times (LST).
+The baseline length and orientation (anti-clockwise from East) are annotated at the top right corner of each panel.
+Black, red and blue curves correspond to delay power spectra obtained with achromatic, {\it Airy} and chromatic simulated antenna beams respectively.
+The achromatic beam has no spectral structure, the simulated chromatic beam has maximum chromaticity while a nominal {\it Airy} pattern has intermediate level of chromaticity.
+The {\it pitchfork} effect is clearly visible as peaks around the horizon limits.
+With increase in chromaticity of the antenna beam the foreground spillover beyond the {\it foreground wedge} becomes progressively worse - the extent of foreground-spillover wings beyond the horizon limits (vertical dotted lines) and the amplitude of spillover beyond $k_\parallel\gtrsim 0.2\,h$~Mpc$^{-1}$ is most severe for the chromatic simulated beam, intermediate for an {\it Airy} pattern and negligible for an achromatic beam.}
+  \label{fig:asm-dps-beam-chromaticity-baselines}
+\end{figure*}
+
+It is clearly demonstrated that higher the beam chromaticity, the farther the foreground contamination inherently extends along $k_\parallel$.
+Thus, the chromaticity of antenna beam needs to be carefully controlled in EoR experiments in order to not allow sensitive $k_\parallel$-modes to become inaccessible for EoR H{\sc i} signal detection.
+
+It must be emphasized that such a significant spillover is not limited by the horizon limits of the {\it foreground wedge} because this is caused by spectral structure in the antenna beam pattern in addition to that caused by position-dependent geometric phase in the visibility spectra.
+As a result delay-based complex deconvolution techniques such as CLEAN \citep{tay99,par09,par12b} that rely on smoothness of foreground spectra and only spectral window shape will not have adequate information to accurately deconvolve intrinsic supra-horizon spillover arising from the chromaticity of the antenna beam.
+We leave delay power spectrum estimation using {\it foreground removal} strategy that accounts for direction-dependent and beam chromaticity-dependent effects to future work and use only simple {\it foreground avoidance} approach in this study.
 
@@
 
-Now we consider the effect of chromaticity of the power pattern on the delay power spectrum.
-
-In HERA-19 array layout configuration, there are 30 unique baseline vectors and 8 unique baseline lengths.
-Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines} shows the delay power spectra of foregrounds on the 8 unique baseline lengths obtained with the aforementioned models for power pattern.
-In all these panels, the full-band foreground delay power spectra obtained with achromatic, {\it Airy} and chromatic beam patterns are shown in black, red, and blue respectively.
-The vertical dotted lines denote the horizon limits for baseline lengths indicated in each panel.
-A clear trend of broadening of spillover-wings outside the horizon limits is seen with increasing chromaticity.
-For instance, the spillover from foreground delay power spectrum obtained with chromatic beam pattern is restricted to $|k_\parallel| \lesssim 0.2\,h$~Mpc$^{-1}$, with the {\it Airy} pattern it is restricted to $|k_\parallel| \lesssim 0.15\,h$~Mpc$^{-1}$, while with the achromatic beam it is restricted to $|k_\parallel| \lesssim 0.12\,h$~Mpc$^{-1}$ even on longest baseline lengths.
-Thus an increase in chromaticity extends the foreground spillover into higher $k_\parallel$-modes making them inaccessible for EoR H{\sc i} signal detection.
-
-Hence it is clearly demonstrated that higher the beam chromaticity, the farther the foreground contamination inherently extends beyond the horizon limits of the {\it foreground wedge}.
-The {\it Airy} pattern typically creates one secondary peak whereas the chromatic beam is found to produce multiple secondary peaks outside the {\it foreground wedge} on each side.
-
-\begin{figure*}[htb]
-\centering
-\includegraphics[width=\linewidth]{asm_foreground_eor_beam_chromaticity_fullband_bhw2.0.eps}
-\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra for different baselines.}
-\label{fig:asm-dps-beam-chromaticity-baselines}
-\end{figure*}
-
-It must be emphasized that such a significant spillover is not limited by the horizon limits of the {\it foreground wedge} because this is caused by spectral structure in the antenna beam pattern in addition to that caused by position-dependent geometric phase in the visibility spectra.
-As a result delay-based complex deconvolution techniques such as CLEAN \citep{tay99,par09,par12b} that rely on smoothness of foreground spectra and only spectral window shape will not have adequate information to accurately deconvolve intrinsic supra-horizon spillover arising from the chromaticity of the antenna beam.
-Thus, we leave delay power spectrum estimation using {\it foreground removal} strategy to future work and use {\it foreground avoidance} approach in this study.
-
 \begin{figure}[htb]
@@
 \centering
-\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_150.0_MHz_subband_win_method_bhw2.0.eps}
-\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra obtained from the 150~MHz subband for different baseline lengths.}
-\label{fig:asm-dps-beam-chromaticity-baselines-150-subband}
+\subfloat[][Power patterns]{\label{fig:asm-dps-beam-chromaticity-baselines-150-subband}\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_150.0_MHz_subband_win_method_bhw2.0.eps}} \\
+\subfloat[][Power patterns]{\label{fig:asm-dps-beam-chromaticity-baselines-170-subband}\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_170.0_MHz_subband_win_method_bhw2.0.eps}}
+\label{fig:subbands}
 \end{figure*}
+
+% \begin{figure*}[htb]
+% \centering
+% \includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_150.0_MHz_subband_win_method_bhw2.0.eps}
+% \caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra obtained from the 150~MHz subband for different baseline lengths.}
+% \label{fig:asm-dps-beam-chromaticity-baselines-150-subband}
+% \end{figure*}
 
@@
 
-\begin{figure*}[htb]
-\centering
-\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_170.0_MHz_subband_win_method_bhw2.0.eps}
-\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra obtained from the 170~MHz subband for different baseline lengths.}
-\label{fig:asm-dps-beam-chromaticity-baselines-170-subband}
-\end{figure*}
+% \begin{figure*}[htb]
+% \centering
+% \includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_170.0_MHz_subband_win_method_bhw2.0.eps}
+% \caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra obtained from the 170~MHz subband for different baseline lengths.}
+% \label{fig:asm-dps-beam-chromaticity-baselines-170-subband}
+% \end{figure*}
 

### 2016-03-02 ForegroundSimulations/ms.tex
Add two references to bioliography file
From 0e115e5 (restructure):
==========================

In eor.bib,

(*) Add references to Neben et al.(2016) and Ewall-Wice et al.(2016)

@@
 
-In a related series of papers, Neben et~al.
-(2016; submitted) discuss the agreement of these simulated antenna beam patterns with actual measurements and Ewall-Wice et~al.
-(2016; submitted) model the reflections and return loss expected in the proposed antenna-receiver assembly.
+In a related series of papers, \citet{neb16} discuss the agreement of these simulated antenna beam patterns with actual measurements and \citet{ewa16} model the reflections and return loss expected in the proposed antenna-receiver assembly.
 Our focus in this paper is to investigate chromaticity of antenna power patterns from the point of view of their impact on foreground contamination in delay power spectra.

### 2016-03-03 ForegroundSimulations/ms.tex
Update figures on reflection specs
From 9ba1a46 (restructure):
==========================

(*) Update figures on reflection specs

@@
 
+Patra~et~al.~2015 (submitted) and \citet{ewa16} discuss the measured and simulated reflections between a dish and its feed.
+We provide a related discussion by estimating the attenuation in power required to keep the foreground power reflected between adjacent antennas below the expected EoR H{\sc i} signal level for the different models of power patterns used in our study.
+
+The effect of reflections it to shift the measured foreground power to higher modes in $\tau$ (or equivalently in $k_\parallel$) and thus cause further contamination in these higher $k_\parallel$ modes which are considered sensitive for EoR H{\sc i} signal detection.
+Here we estimate the attenuation required at specific $k_\parallel$ modes of interest to contain reflected foreground power between antennas below expected EoR H{\sc i} power, both corresponding to a 14.6~m antenna spacing.
+
+We define the required attenuation as the ratio: 
+\begin{align}
+  \Gamma_{k_\parallel}(\tau) &= \frac{P_\textrm{H{\sc i}}(k_\parallel)}{P_\textrm{FG}(k_\parallel - \frac{\dif k_\parallel}{\dif \tau}\,\tau)},
+\end{align}
+where, $P_\textrm{H{\sc i}}(k_\parallel)$ is the EoR H{\sc i} power spectrum for the chosen antenna spacing, $P_\textrm{FG}(k_\parallel)$ is the foreground delay power spectrum obtained with a Blackman-Harris window function applied over the full band of the three uniquely oriented 14.6~m antenna spacings further averaged over a 0--12 hr LST range and over both positive and negative $k_\parallel$ modes, $\tau$ is the delay caused by reflections, and $\dif k_\parallel/\dif \tau$ is the {\it jacobian} in the transformation of $\tau$ to $k_\parallel$.
+
+Fig.~\ref{fig:fg-reflections} shows $\Gamma_{k_\parallel}(\tau)$ (in dB) for selected $k_\parallel$ at 0.08~$h$~Mpc$^{-1}$ (left), 0.1~$h$~Mpc$^{-1}$ (middle), and 0.12~$h$~Mpc$^{-1}$ (right) as a function of delays due to reflections from other antenna spacings.
+The light, medium and dark shaded curves show $\Gamma_{k_\parallel}(\tau)$ for achromatic, {\it Airy}, and chromatic antenna power patterns respectively.
+These curves set an upper limit to the reflected foreground power below the EoR H{\sc i} signal power as a function of delays caused by antenna-to-antenna reflections.
+It is noted that a chromatic simulated power pattern sets the most severe upper limit in all three chosen $k_\parallel$ for delays $\tau < 80$~ns (left), $\tau < 120$~ns (middle), and $\tau < 160$~ns.
+
+The required attenuation is also a sensitive function of the chosen $k_\parallel$ mode.
+For instance, at $k_\parallel=0.08\,h$~Mpc$^{-1}$, the reflections with delays 70~ns require to be attenuated by at $\gtrsim 85$~dB for the simulated power pattern, $\gtrsim 82$~dB for the {\it Airy} pattern, and $\gtrsim 70$~dB for the achromatic pattern.
+However, at $k_\parallel=0.1\,h$~Mpc$^{-1}$ for the same delay of reflection, the requirement on attenuation is lowered to $\gtrsim 75$~dB, $\gtrsim 30$~dB and $\gtrsim 22$~dB respectively.
+If the chosen $k_\parallel$ is instead 0.12~$h$~Mpc$^{-1}$, the required attenuation is further relaxed to $\gtrsim 60$~dB, $\gtrsim 15$~dB and $\gtrsim 15$~dB respectively.
+This further reinforces the significance of reducing the chromaticity of the antenna power pattern to further relax the constraint on the system to achieve the attenuation required to contain the reflected foreground power from other antennas from contaminating the sensitive EoR H{\sc i} signal modes in the {\it EoR window}.
+
 % \subsection{Directional Chromaticity of Power Pattern}\label{sec:directional-chromaticity}
@@
 
-\subsection{Constraints on Reflections between Antennas}\label{sec:reflectometry}
-
-Patra~et~al.~2015 (submitted) and Ewall-Wice~et~al.~2015 (submitted) discuss the measured and simulated reflections between a dish and its feed.
-We provide a related discussion by estimating the attenuation in power required to keep the foreground power reflected between adjacent antennas below the expected EoR H{\sc i} signal level for the different models of power patterns used in our study.
-
-The effect of reflections it to shift the measured foreground power to higher modes in $\tau$ (or equivalently in $k_\parallel$) and thus cause further contamination in these higher $k_\parallel$ modes which are considered sensitive for EoR H{\sc i} signal detection.
-Here we estimate the attenuation required at specific $k_\parallel$ modes of interest to contain reflected foreground power between antennas below expected EoR H{\sc i} power, both corresponding to a 14.6~m antenna spacing.
-
-We define the required attenuation as the ratio: 
-\begin{align}
-  \Gamma_{k_\parallel}(\tau) &= \frac{P_\textrm{H{\sc i}}(k_\parallel)}{P_\textrm{FG}(k_\parallel - \frac{\dif k_\parallel}{\dif \tau}\,\tau)},
-\end{align}
-where, $P_\textrm{H{\sc i}}(k_\parallel)$ is the EoR H{\sc i} power spectrum for the chosen antenna spacing, $P_\textrm{FG}(k_\parallel)$ is the foreground delay power spectrum obtained with a Blackman-Harris window function applied over the full band of the three uniquely oriented 14.6~m antenna spacings further averaged over a 0--12 hr LST range and over both positive and negative $k_\parallel$ modes, $\tau$ is the delay caused by reflections, and $\dif k_\parallel/\dif \tau$ is the {\it jacobian} in the transformation of $\tau$ to $k_\parallel$.
-
-Fig.~\ref{fig:fg-reflections} shows $\Gamma_{k_\parallel}(\tau)$ (in dB) for selected $k_\parallel$ at 0.08~$h$~Mpc$^{-1}$ (left), 0.1~$h$~Mpc$^{-1}$ (middle), and 0.12~$h$~Mpc$^{-1}$ (right) as a function of delays due to reflections from other antenna spacings.
-The light, medium and dark shaded curves show $\Gamma_{k_\parallel}(\tau)$ for achromatic, {\it Airy}, and chromatic antenna power patterns respectively.
-These curves set an upper limit to the reflected foreground power below the EoR H{\sc i} signal power as a function of delays caused by antenna-to-antenna reflections.
-It is noted that a chromatic simulated power pattern sets the most severe upper limit in all three chosen $k_\parallel$ for delays $\tau < 80$~ns (left), $\tau < 120$~ns (middle), and $\tau < 160$~ns.
-
-The required attenuation is also a sensitive function of the chosen $k_\parallel$ mode.
-For instance, at $k_\parallel=0.08\,h$~Mpc$^{-1}$, the reflections with delays 70~ns require to be attenuated by at $\gtrsim 85$~dB for the simulated power pattern, $\gtrsim 82$~dB for the {\it Airy} pattern, and $\gtrsim 70$~dB for the achromatic pattern.
-However, at $k_\parallel=0.1\,h$~Mpc$^{-1}$ for the same delay of reflection, the requirement on attenuation is lowered to $\gtrsim 75$~dB, $\gtrsim 30$~dB and $\gtrsim 22$~dB respectively.
-If the chosen $k_\parallel$ is instead 0.12~$h$~Mpc$^{-1}$, the required attenuation is further relaxed to $\gtrsim 60$~dB, $\gtrsim 15$~dB and $\gtrsim 15$~dB respectively.
-This further reinforces the significance of reducing the chromaticity of the antenna power pattern to further relax the constraint on the system to achieve the attenuation required to contain the reflected foreground power from other antennas from contaminating the sensitive EoR H{\sc i} signal modes in the {\it EoR window}.
-
 \section{EoR Sensitivity}\label{sec:eor-sensitivity}

### 2016-03-03 ForegroundSimulations/ms.tex
Update subsection 5.2 on reflectometry specs
From 4497f7b (restructure):
==========================

In ms.tex,

(*) Update subsection 5.2 on reflectometry specs

@@
 \begin{align}
-  \boldsymbol{k}_\perp &\equiv \frac{2\pi(\frac{\boldsymbol{b}}{\lambda})}{D}, \\
-  k_\parallel &\equiv \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, 
+  \boldsymbol{k}_\perp &\equiv \frac{2\pi(\frac{\boldsymbol{b}}{\lambda})}{D}, \label{eqn:kperp-baseline}\\
+  k_\parallel &\equiv \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, \label{eqn:kprll-delay}
 \end{align}
@@
 
-Patra~et~al.~2015 (submitted) and \citet{ewa16} discuss the measured and simulated reflections between a dish and its feed.
-We provide a related discussion by estimating the attenuation in power required to keep the foreground power reflected between adjacent antennas below the expected EoR H{\sc i} signal level for the different models of power patterns used in our study.
+One of the primary causes for spectral structure in antenna power patterns is reflections in the instrument.
+Patra~et~al.~2015 (in preparation) and \citet{ewa16} discuss the measured and simulated reflections respectively between a dish and its feed.
+Reflection between structures and signal paths from different antennas also causes chromaticity in the antenna beam.
+In this section, we provide cosmologically motivated upper limits on instrument systematics caused by these two types of reflections.
+% a related discussion by estimating the attenuation in power required to keep the foreground power reflected between adjacent antennas below the expected EoR H{\sc i} signal level for the different models of power patterns used in our study.
 
 The effect of reflections it to shift the measured foreground power to higher modes in $\tau$ (or equivalently in $k_\parallel$) and thus cause further contamination in these higher $k_\parallel$ modes which are considered sensitive for EoR H{\sc i} signal detection.
-Here we estimate the attenuation required at specific $k_\parallel$ modes of interest to contain reflected foreground power between antennas below expected EoR H{\sc i} power, both corresponding to a 14.6~m antenna spacing.
+Equivalently, these delay shifts introduce ripples in the spectrum.
+The net chromaticity in the measurements is the product of spectral structure arising out of the intrinsic nature of foreground emission, the baseline-dependent frequency structure of the fringes, the spectral features in the antenna power pattern besides any other spectral structures in the instrument unaccounted for.
+Equivalently, in the Fourier domain these factors have a convolving effect.
+In order to isolate the requirements on beam chromaticity from other sources of chromaticity, we start with an antenna beam in which those spectral structures are absent but the intrinsic chromaticity of foregrounds and the baseline fringes are included.
 
-We define the required attenuation as the ratio: 
-\begin{align}
-  \Gamma_{k_\parallel}(\tau) &= \frac{P_\textrm{H{\sc i}}(k_\parallel)}{P_\textrm{FG}(k_\parallel - \frac{\dif k_\parallel}{\dif \tau}\,\tau)},
+% We estimate the attenuation required at specific modes of interest $|k_\parallel|>k_\textrm{p}$ to contain reflected foreground power between antennas below expected EoR H{\sc i} power, both corresponding to a 14.6~m antenna spacing.
+
+We define the required attenuation on the reflected foreground power as the ratio: 
+\begin{align}\label{eqn:attenuation}
+  \Gamma_{k_\textrm{p}}(\tau) \geq \min_{|k_\parallel|>k_\textrm{p}}\left\{\frac{P_\textrm{FG}(k_\parallel - \frac{\dif k_\parallel}{\dif \tau}\,\tau)}{P_\textrm{H{\sc i}}(k_\parallel)}\right\}^{1/2},
 \end{align}
-where, $P_\textrm{H{\sc i}}(k_\parallel)$ is the EoR H{\sc i} power spectrum for the chosen antenna spacing, $P_\textrm{FG}(k_\parallel)$ is the foreground delay power spectrum obtained with a Blackman-Harris window function applied over the full band of the three uniquely oriented 14.6~m antenna spacings further averaged over a 0--12 hr LST range and over both positive and negative $k_\parallel$ modes, $\tau$ is the delay caused by reflections, and $\dif k_\parallel/\dif \tau$ is the {\it jacobian} in the transformation of $\tau$ to $k_\parallel$.
+where, $P_\textrm{H{\sc i}}(k_\parallel)$ is the EoR H{\sc i} power spectrum for the chosen antenna spacing, $P_\textrm{FG}(k_\parallel)$ is the foreground delay power spectrum obtained with the spectral weighting function applied over the full band of the three uniquely oriented 14.6~m antenna spacings further averaged over a 0--12 hr LST range and over both positive and negative $k_\parallel$ modes, $\tau$ is the delay caused by reflections, and $\dif k_\parallel/\dif \tau$ is the {\it jacobian} in the transformation of $\tau$ to $k_\parallel$ (see equation~\ref{eqn:kprll-delay}).
+Equivalently, $\Gamma_{k_\textrm{p}}(\tau)$ is determined by the requirement that the reflected foreground power obtained by shifting in delay is below the EoR H{\sc i} signal power in line-of-sight spatial scales of interest given by $|k_\parallel|>k_\textrm{p}$.
+For this analysis constraining reflections, we use the 21cmFAST model at 150~MHz ($z\approx 8.47$) for $P_\textrm{H{\sc i}}(k_\parallel)$.
 
-Fig.~\ref{fig:fg-reflections} shows $\Gamma_{k_\parallel}(\tau)$ (in dB) for selected $k_\parallel$ at 0.08~$h$~Mpc$^{-1}$ (left), 0.1~$h$~Mpc$^{-1}$ (middle), and 0.12~$h$~Mpc$^{-1}$ (right) as a function of delays due to reflections from other antenna spacings.
-The light, medium and dark shaded curves show $\Gamma_{k_\parallel}(\tau)$ for achromatic, {\it Airy}, and chromatic antenna power patterns respectively.
-These curves set an upper limit to the reflected foreground power below the EoR H{\sc i} signal power as a function of delays caused by antenna-to-antenna reflections.
-It is noted that a chromatic simulated power pattern sets the most severe upper limit in all three chosen $k_\parallel$ for delays $\tau < 80$~ns (left), $\tau < 120$~ns (middle), and $\tau < 160$~ns.
-
-The required attenuation is also a sensitive function of the chosen $k_\parallel$ mode.
-For instance, at $k_\parallel=0.08\,h$~Mpc$^{-1}$, the reflections with delays 70~ns require to be attenuated by at $\gtrsim 85$~dB for the simulated power pattern, $\gtrsim 82$~dB for the {\it Airy} pattern, and $\gtrsim 70$~dB for the achromatic pattern.
-However, at $k_\parallel=0.1\,h$~Mpc$^{-1}$ for the same delay of reflection, the requirement on attenuation is lowered to $\gtrsim 75$~dB, $\gtrsim 30$~dB and $\gtrsim 22$~dB respectively.
-If the chosen $k_\parallel$ is instead 0.12~$h$~Mpc$^{-1}$, the required attenuation is further relaxed to $\gtrsim 60$~dB, $\gtrsim 15$~dB and $\gtrsim 15$~dB respectively.
-This further reinforces the significance of reducing the chromaticity of the antenna power pattern to further relax the constraint on the system to achieve the attenuation required to contain the reflected foreground power from other antennas from contaminating the sensitive EoR H{\sc i} signal modes in the {\it EoR window}.
-
-% \subsection{Directional Chromaticity of Power Pattern}\label{sec:directional-chromaticity}
-
-% Fig.~\ref{fig:off-axis-beam-chromaticity} demonstrates the beyond-the-horizon spillover even from a flat-spectrum point source at different off-axis angles.
-The three panels correspond to delay spectra from different positions of the point source -- 0\arcdeg (left), 45\arcdeg (middle) and 89\arcdeg (right) -- from the zenith.
-The phase centers are located at the source positions and hence the delay spectra are centered on $\tau = 0$~ns.
-The response of the simulated dish power pattern (dashed line) is comapred with that from an {\it Airy} pattern resulting from a nominal uniformly illuminated circular disk (solid line).
-The gray vertical lines correspond to the horizon limits at $\pm 48.7$~ns for a 14.6~m antenna spacing.
-In all these cases, a {\it Blackman-Harris} window function has been applied along the spectral axis.
-
-% \begin{figure*}[htb]
-% \centering
-% \includegraphics[width=\linewidth]{off-axis_point_source_beam_chromaticity.eps}
-% \caption{Chromaticity of antenna power pattern at directions off-axis. }
-% \label{fig:off-axis-beam-chromaticity}
-% \end{figure*}
-
-% At 0\arcdeg off-axis, the {\it Airy} pattern has no spectral variation except that introduced by the {\it Blackman-Harris} window function and thus reproduces its Fourier response centered at $\tau = 0$~ns whereas the simulated power pattern is found to exhibit some spectral variation giving rise to the wings on either side of $\tau = 0$~ns.
-As off-axis angle increases to 45\arcdeg, both the power patterns clearly exhibit chromaticity.
-The simulated pattern not only has a higher magnitude inside the horizon limits (by a factor $\sim 10$) but also exhibits higher chromaticity (by many orders of magnitude) in modes beyond the horizon relative to that of an {\it Airy} pattern.
-In contrast, at 89\arcdeg off-axis, not only does the simulated pattern have higher chromaticity in high delay modes but is also two orders of magnitude higher in amplitude inside the horizon limits relative to the nominal {\it Airy} pattern.
-
-% It is important to note that in a generic scenario where visibilities are not phased to a specific foreground location, the chromaticity of the power pattern will imprint itself on location of the foreground objects in delay space and will give rise to significant spillover especially from foregrounds near the horizon.
-
-% We generalize the analysis above by computing the delay power spectrum of the power pattern along its spectral axis in every direction in an effort to study its performance as a function of angle on the sky.
-% \begin{align}
-%   A^\prime(l,m,\tau) &= \int A(l,m,f)\,e^{-j 2\pi f\tau} \,\dif f
-% \end{align}
-
-% We define the directional chromaticity of antenna power pattern as:
-% \begin{align}
-%   C(l,m) &= \frac{ \int\limits_{|\tau|>60\,\textrm{ns}} |A^\prime|^2 \,\dif\tau }{\int\limits_{|\tau|>60\,\textrm{ns}} \dif\tau}
-% \end{align}
-% where, the limit $|\tau|>60$~ns was chosen to represent a region well beyond the horizon limits ($\pm 48.7$~ns) for a 14.6~m antenna spacing.
-It thus measures the average power arising out of chromaticity in each delay mode beyond $|\tau|>60$~ns.
-
-% Fig.~\ref{fig:directional-beam-chromaticity} shows the directional chromaticity, $C(l,m)$, of the power patterns of an {\it Airy} disk for reference (left) and a simulated disk (middle) on an orthographic projection onto direction cosines.
-Their color scale is shown at the top for reference.
-The chromaticity of the {\it Airy} pattern is symmetric and always below 500.
-On the other hand,  a simulated disk exhibits higher levels of chromaticity in the range 100--50,000.
-The ratio of their chromaticities is shown on the right with corresponding color scale on its right.
-The simulated disk is more chromatic than the nominal {\it Airy} disk by a factor between 100 and up to 10000.
-However, chromaticity in regions near the horizon which map to the horizon limits in the delay spectrum and have the most significant impact on spillover into the {\it EoR window} in the simulated disk are higher than that of an {\it Airy} disk only by factors $\lesssim 4$.
-Thus the simulated disk for HERA achieves reasonable control on the chromaticity near the horizon despite the very high levels near the center.
-
-% Also shown are the tracks (black dots) of point sources brighter than 50~Jy in the LST range 0--12~hrs.
-The solid circle near the bottom denotes the south celestial pole.
-It is noted that there are a few bright point sources that spend a majority of time in this LST range near the northern and southern horizons which will contaminate the measured visibilities on north-south antenna spacings.
-Simulations of the antenna power pattern must take the bright foreground locations, especially near the horizon, into account.
-
-% \begin{figure*}[htb]
-% \centering
-% \includegraphics[width=\linewidth]{directional_high_delay_average_in_beam.eps}
-% \caption{All-sky directional chromaticity of antenna power pattern. }
-% \label{fig:directional-beam-chromaticity}
-% \end{figure*}
-
-\subsection{Effect on Delay Power Spectrum}\label{sec:chromaticity-delay-spectrum}
+For reflections caused by dish-feed assembly, we use $P_\textrm{FG}(k_\parallel)$ obtained with the achromatic beam model on a 14.6~m baseline in equation~\ref{eqn:attenuation}.
+Fig.~\ref{fig:fg-reflections-achrmbeam} shows $\Gamma_{k_\textrm{p}}(\tau)$ (in dB) for $k_\textrm{p}$ chosen to be 0.1~$h$~Mpc$^{-1}$ (solid), 0.15~$h$~Mpc$^{-1}$ (dashed), and 0.2~$h$~Mpc$^{-1}$ (dotted).
+These curves set an upper limit to the reflected foreground power below the EoR H{\sc i} signal power as a function of delays caused by dish-feed reflections.
+In other words, it implies that if reflections in the dish-feed assembly are attenuated to levels that lie in the regions below the different shaded regions, such spectral systematics in the instrument will not hinder detection of EoR in those corresponding $k_\parallel$ modes of interest.
 
@@
 \includegraphics[width=\linewidth]{spec_on_achrmbeam_foreground_reflected_power_21cmfast_14.6m_150.0_MHz_subband_v2.eps}
-\caption{Attenuation of foreground power (in dB) from antenna-to-antenna reflections required to keep the reflected foreground power below EoR H{\sc i} signal power.}
+\caption{Lower limit on attenuation of reflected foreground power (in dB) from dish-feed reflections required to keep the reflected foreground power below EoR H{\sc i} signal power for all $k_\parallel$-modes greater than $0.1\,h$~Mpc$^{-1}$ (solid), $0.15\,h$~Mpc$^{-1}$ (dashed) and $0.2\,h$~Mpc$^{-1}$ (dotted).
+This is obtained on 14.6~m antenna spacing for a 21cmFAST EoR model at 150~MHz ($z\approx 8.47$) and foreground power obtained with an achromatic antenna beam model.
+When the attenuation on dish-feed reflections is higher than these limits (outside the shaded regions), EoR will be detectable in respective $k_\parallel$-modes despite these reflections.}
 \label{fig:fg-reflections-achrmbeam}
 \end{figure}
+
+The elbow-shaped turnover is a measure of the most severe requirement on attenuation of reflections.
+This depends sensitively on the chosen $k_\parallel$ modes.
+For instance, the attenuation required is $\gtrsim 54$~dB at $\sim 200$~ns for $k_\textrm{p}=0.1\,h$~Mpc$^{-1}$, $\gtrsim 56$~dB at $\sim 300$~ns for $k_\textrm{p}=0.15\,h$~Mpc$^{-1}$ and $\gtrsim 58$~dB at $\sim 400$~ns for $k_\textrm{p}=0.2\,h$~Mpc$^{-1}$.
+Measurements by Patra et al.
+(2016) for HERA dish-feed assembly show that the return losses lie well within the regions excluded by the shaded regions thus implying that the attenuation is well above the lower limit and hence will not prevent EoR detection.
+
+Similarly, for reflections arising out of structures and interfaces across different antennas, we use $P_\textrm{FG}(k_\parallel)$ obtained with the simulated chromatic and {\it Airy} antenna beams on 14.6~m baselines.
+These beams do not include spectral features from antenna-to-antenna reflections.
+Thus $\Gamma_{k_\textrm{p}}(\tau)$ provides lower limit for attenuation of antenna-to-antenna reflections.
+Fig.~\ref{fig:fg-reflections} is similar to Fig.~\ref{fig:fg-reflections-achrmbeam} with constraints for values of $k_\textrm{p}$ chosen to be 0.1~$h$~Mpc$^{-1}$ (left), 0.15~$h$~Mpc$^{-1}$ (middle), and 0.2~$h$~Mpc$^{-1}$ (right).
+Lower limits are estimated for {\it Airy} (dashed lines) and simulated chromatic beams (solid lines).
 
@@
 \includegraphics[width=\linewidth]{spec_on_foreground_reflected_power_21cmfast_14.6m_150.0_MHz_subband_v2.eps}
-\caption{Attenuation of foreground power (in dB) from antenna-to-antenna reflections required to keep the reflected foreground power below EoR H{\sc i} signal power.}
+\caption{Lower limit on attenuation of reflected foreground power (in dB) from antenna-to-antenna reflections required to keep the reflected foreground power below EoR H{\sc i} signal power for all $k_\parallel$-modes greater than $0.1\,h$~Mpc$^{-1}$ (left), $0.15\,h$~Mpc$^{-1}$ (middle) and $0.2\,h$~Mpc$^{-1}$ (right).
+This is obtained on 14.6~m antenna spacing for a 21cmFAST EoR model at 150~MHz ($z\approx 8.47$) and foreground power obtained with an {\it Airy} (dashed) and simulated chromatic (solid) antenna beam models.
+Regions excluding shaded regions indicate EoR will be detectable in respective $k_\parallel$-modes despite these reflections.
+Increase in beam chromaticity makes the requirement on attenuation more severe.
+For instance, $k_\parallel > 0.1\,h$~Mpc$^{-1}$ modes will be inaccessible with the simulated chromatic beam if these reflections are taken into account.
+However, for the same beam the instrument will enjoy a much higher tolerance despite these reflections if the modes of interest are $k_\parallel > 0.2\,h$~Mpc$^{-1}$ for EoR detection.
+Owing to lower chromaticity, an {\it Airy} beam offers higher tolerance to reflections compared to the simulated chromatic beam.}
 \label{fig:fg-reflections}
 \end{figure*}
+
+Increase in beam chromaticity makes the lower limits on attenuating reflections more severe relative to that from an achromatic beam.
+For instance, for $k_\textrm{p}=0.1\,h$~Mpc$^{-1}$ there is no delay at which the required attenuation is unconstrained to the left of the elbow-shaped turnover, including at $\tau=0$.
+This means that when additional chromaticity from antenna-to-antenna reflections is taken into account, the requirement that all $k_\parallel$-modes with $k_\parallel > 0.1\,h$~Mpc$^{-1}$ be accessible for EoR signal detection will not be satisfied with the currently simulated chromatic beam for HERA.
+For $k_\textrm{p}=0.15\,h$~Mpc$^{-1}$, there is a narrow range of allowed attenuation which is unconstrained for $\tau \lesssim 50$~ns.
+However, for $k_\parallel > 0.2\,h$~Mpc$^{-1}$, the foreground power spectrum using simulated chromatic dish beam will have enough room to be effective for EoR signal detection despite additional chromaticity arising from antenna-to-antenna reflections.
+
+It may be noted here that designing a dish whose antenna beam closely resembles a nominal {\it Airy} pattern will have a significantly higher ceiling of tolerance for allowing antenna-to-antenna reflections and yet remain very effective for EoR signal detection.
+The HERA collaboration is actively pursuing constant improvement of its dish design to keep minimize limitations from such chromatic systematics.
+
+\subsection{Effect on Delay Power Spectrum}\label{sec:chromaticity-delay-spectrum}
 
@@
 
-This work was supported by the U.
-S.
-National Science Foundation (NSF) through award AST-1109257.
-DCJ is supported by an NSF Astronomy and Astrophysics Postdoctoral Fellowship under award AST-1401708.
-JCP is supported by an NSF Astronomy and Astrophysics Fellowship under award AST-1302774.
+This work was supported by the U. S. National Science Foundation (NSF) through award AST-1109257. DCJ is supported by an NSF Astronomy and Astrophysics Postdoctoral Fellowship under award AST-1401708.
 

### 2016-03-03 ForegroundSimulations/ms.tex
Make minor changes to EoR sensitivity section
From 3e3495b (restructure):
==========================

In ms.tex,

(*) Make minor changes to EoR sensitivity section

@@
 
-\subsection{Effect on Delay Power Spectrum}\label{sec:chromaticity-delay-spectrum}
+\section{EoR Sensitivity}\label{sec:eor-sensitivity}
 
-We investigate the effect of chromaticity of power pattern in a {\it foreground avoidance} strategy that avoids the aforementioned deconvolution of delay spectrum.
-Application of window functions with high sidelobe suppression have been discussed for mitigating foreground contamination \citep{thy13}.
-In line with the {\it foreground avoidance} strategy, Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-150-subband} shows delay spectra after applying a {\it Blackman-Harris} window function extending 10~MHz on each side centered on 150~MHz with effective bandwidth of 10~MHz.
+In line with the {\it foreground avoidance} strategy, Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-150-subband} shows delay spectra after applying a {\it Blackman-Harris} spectral weighting function defined in equation~\ref{eqn:bhw2} with $B_\textrm{eff}=10$~MHz.
 The 8 panels correspond to those shown in Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines}.
@@
 
-\section{EoR Sensitivity}\label{sec:eor-sensitivity}
-
 \section{Summary}\label{sec:summary}

### 2016-03-03 ForegroundSimulations/ms.tex
Comment some lines in EoR sensitivity section
From e4fc215 (restructure):
==========================

In ms.tex,

(*) Comment some lines in EoR sensitivity section

@@
 
-Firstly, it is noted that the coarsening of delay resolution significantly absorbs the distinct differences caused by beams of different chromaticities as seen in the full band foreground delay spectra outside the {\it foreground wedge} in Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines}.
+% Firstly, it is noted that the coarsening of delay resolution significantly absorbs the distinct differences caused by beams of different chromaticities as seen in the full band foreground delay spectra outside the {\it foreground wedge} in Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines}.
 Secondly, it is also found that barring the shortest baselines ($|\boldsymbol{b}| \leq $~29.2~m), which have the most severe foreground contamination especially from diffuse emission, foreground contamination on baselines longer than $\gtrsim 29.2$~m is lesser than EoR signal power for $|k_\parallel| \gtrsim 0.22\,h$~Mpc$^{-1}$ in either of the models.
 
-Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-170-subband} is similar to Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-150-subband} except it is obtained with a subband {\it Blackman-Harris} window function centered on 170~MHz.
+% Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-170-subband} is similar to Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-150-subband} except it is obtained with a subband {\it Blackman-Harris} window function centered on 170~MHz.
 In this subband relative to that centered on 150~MHz, the ratio of powers of the EoR signal and foregrounds is even higher outside the wedge thus indicating a stronger potential for direct detectability without the use of optimal power spectrum estimation techniques on almost all baseline lengths.
 
-% \begin{figure*}[htb]
-% \centering
-% \includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_170.0_MHz_subband_win_method_bhw2.0.eps}
-% \caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra obtained from the 170~MHz subband for different baseline lengths.}
-% \label{fig:asm-dps-beam-chromaticity-baselines-170-subband}
-% \end{figure*}
+% % \begin{figure*}[htb]
+% % \centering
+% % \includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_170.0_MHz_subband_win_method_bhw2.0.eps}
+% % \caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra obtained from the 170~MHz subband for different baseline lengths.}
+% % \label{fig:asm-dps-beam-chromaticity-baselines-170-subband}
+% % \end{figure*}
 
-It must be emphasized that these are obtained only with windowing techniques and do not represent the best sensitivity achievable with sophisticated tools such as optimal covariance-based weighting schemes \citep{liu14a,liu14b,ali15,dil15}.
+% It must be emphasized that these are obtained only with windowing techniques and do not represent the best sensitivity achievable with sophisticated tools such as optimal covariance-based weighting schemes \citep{liu14a,liu14b,ali15,dil15}.
 Thus assuming the data is limited by foregrounds and not by thermal noise, this demonstrates that even with no sophistication in power spectrum estimation, a direct detection based on simple windowing and delay spectrum technique is possible on a majority of HERA baselines and will further allow distinguishing between different EoR models.

### 2016-03-04 ForegroundSimulations/ms.tex
Update figure, add content under section 6
From fe435fa (fgsim):
====================

(*) Update 150 MHz subband delay spectra figure

In ms.tex,

(*) Add content to section 6

--- 2016-03-03 ForegroundSimulations/ms.tex
@@
 In HERA-19 array layout, there are 30 unique baseline vectors and 8 unique baseline lengths.
-Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines} shows the delay power spectra of foregrounds on the 8 unique baseline lengths obtained with the aforementioned models for power pattern.
+Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines} shows the delay power spectra of foregrounds on the 8 unique baseline lengths obtained with the aforementioned models for power pattern at arbitrary local sidereal times (LST).
 In all these panels, the full-band spectrally weighted foreground delay power spectra obtained with achromatic, {\it Airy} and fully chromatic simulated beam patterns are shown in black, red, and blue respectively.
@@
   \includegraphics[width=\linewidth]{asm_foreground_eor_beam_chromaticity_fullband_bhw2.0.eps}
-  \caption{Foreground delay power spectra on unique baseline lengths of HERA-19 at arbitrary local sidereal times (LST).
+  \caption{Foreground delay power spectra in units of K$^2 (h^{-1}$~Mpc$)^3$ on unique baseline lengths of HERA-19 at arbitrary LST.
 The baseline length and orientation (anti-clockwise from East) are annotated at the top right corner of each panel.
@@
 
-In line with the {\it foreground avoidance} strategy, Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-150-subband} shows delay spectra after applying a {\it Blackman-Harris} spectral weighting function defined in equation~\ref{eqn:bhw2} with $B_\textrm{eff}=10$~MHz.
-The 8 panels correspond to those shown in Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines}.
-As a result of narrowed subband, the resolution in delay space (and $k_\parallel$) has coarsened.
-The cyan and gray lines denote power spectra of EoR models 1 and 2 respectively.
+Here our goal is to estimate sensitivity for EoR detection in the presence of antenna beam chromaticity, using HERA as an example.
+As stated earlier, we estimate sensitivity of HERA in the most conservative scenario where we consider only {\it foreground avoidance} under simple spectral weighting scheme.
+We emphasize that other strategies involving {\it foreground removal} and inverse covariance-based weighting schemes will produce more optimal results than presented here.
+
+In order to avoid signal evolution across the entire bandwidth, we use subbands in which EoR signal evolution is not expected to be significant.
+These subbands with $B_\textrm{eff}=10$~MHz are defined by spectral weights obtained by convolution of {\it Blackman-Harris} window with itself.
+These subbands are centered at 150~MHz and 170~MHz to estimate sensitivity at $z \approx 8.47$ and $z \approx 7.36$.
+We use independent EoR models 1 and 2 to reduce the dependence of this analysis on any single EoR model.
+
+\subsection{Sensitivity on Baseline-$k_\parallel$ Parameter Space}\label{sec:baseline-kprll}
+
+We present the sensitivity of HERA against foregrounds obtained with three antenna beams of different chromaticities in two-dimensional parameter space of baseline lengths (transverse spatial scales) and $k_\parallel$ (line-of-sight spatial scales).
+Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-150-subband} and \ref{fig:asm-dps-beam-chromaticity-baselines-170-subband} show the EoR signal and foreground power in 150~MHz and 170~MHz subbands respectively.
+EoR models 1 and 2 are shown in cyan and gray respectively.
+The foreground delay power spectra obtained with achromatic, {\it Airy} and simulated chromatic antenna patterns are shown in black, red, and blue respectively.
+Each panel corresponds to a unique baseline vector, same as in Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines}.
 
@@
 \centering
-\subfloat[][Power patterns]{\label{fig:asm-dps-beam-chromaticity-baselines-150-subband}\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_150.0_MHz_subband_win_method_bhw2.0.eps}} \\
-\subfloat[][Power patterns]{\label{fig:asm-dps-beam-chromaticity-baselines-170-subband}\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_170.0_MHz_subband_win_method_bhw2.0.eps}}
+\subfloat[][150~MHz subband ($z \approx 8.47$)]{\label{fig:asm-dps-beam-chromaticity-baselines-150-subband}\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_150.0_MHz_subband_win_method_bhw2.0.eps}} \\
+\subfloat[][170~MHz subband ($z \approx 7.36$)]{\label{fig:asm-dps-beam-chromaticity-baselines-170-subband}\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_170.0_MHz_subband_win_method_bhw2.0.eps}}
+\caption{EoR signal and foreground delay power spectrum in units of K$^2 (h^{-1}$~Mpc$)^3$ in 150~MHz (top) and 170~MHz (bottom) subbands ($B_\textrm{eff}=10$~MHz) on eight unique baseline lengths of HERA-19 at arbitrary LST.
+The length and orientation of the baseline vector corresponding to each panel is annotated on the top right corner.
+EoR models 1 and 2 are shown in cyan and gray respectively.
+The foregrounds obtained with achromatic, {\it Airy} and simulated chromatic antenna beams are shown in black, red and blue respectively.
+EoR detection sensitivity is highest for antenna beam with least chromaticity and vice versa.
+Even for the simulated chromatic antenna beam pattern, which has the highest chromaticity among the antenna beam models considered, foreground power will be lower than two independent EoR models by more than two orders of magnitude for $|k_\parallel| \gtrsim 0.2\,h$~Mpc$^{-1}$ on all HERA baselines.}
 \label{fig:subbands}
@@
 
-% \begin{figure*}[htb]
-% \centering
-% \includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_150.0_MHz_subband_win_method_bhw2.0.eps}
-% \caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra obtained from the 150~MHz subband for different baseline lengths.}
-% \label{fig:asm-dps-beam-chromaticity-baselines-150-subband}
-% \end{figure*}
+Due to narrower subbands, the resolution of the foreground delay spectrum is coarser and the central region of foreground contamination extends to $|k_\parallel| \lesssim 0.2\,h$~Mpc$^{-1}$.
+The coarsening of delay resolution significantly absorbs the distinct differences caused by beams of different chromaticities as seen in the full band foreground delay spectra outside the {\it foreground wedge} in Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines}.
+In other words, the foreground spillover wings that extend beyond the horizon even in the case of full-band simulated chromatic beam are on spectral scales larger than the 10~MHz effective bandwidth of the subbands.
+Hence, this results in an EoR signal-foreground crossover at $|k_\parallel| \gtrsim 0.2\,h$~Mpc$^{-1}$ independent of different antenna beam chromaticities used in this analysis.
 
-Firstly, it is noted that the coarsening of delay resolution significantly absorbs the distinct differences caused by beams of different chromaticities as seen in the full band foreground delay spectra outside the {\it foreground wedge} in Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines}.
-Secondly, it is also found that barring the shortest baselines ($|\boldsymbol{b}| \leq $~29.2~m), which have the most severe foreground contamination especially from diffuse emission, foreground contamination on baselines longer than $\gtrsim 29.2$~m is lesser than EoR signal power for $|k_\parallel| \gtrsim 0.22\,h$~Mpc$^{-1}$ in either of the models.
+From Fig.~\ref{fig:subbands}, it is clearly demonstrated that HERA has significant sensitivity on all baselines in both subbands to detect EoR by more than two orders of magnitude above foreground contamination obtained with any level of antenna beam chromaticity.
+While this clearly includes foregrounds obtained with the currently simulated chromatic beam pattern, the sensitivity against foregrounds obtained with achromatic and {\it Airy} antenna power patterns are even higher by many orders of magnitude.
+This only further reiterates that efforts to keep lowering systematic spectral effects in the antenna beam must be undertaken continuously, as is the case with HERA.
 
-Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-170-subband} is similar to Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-150-subband} except it is obtained with a subband {\it Blackman-Harris} window function centered on 170~MHz.
-In this subband relative to that centered on 150~MHz, the ratio of powers of the EoR signal and foregrounds is even higher outside the wedge thus indicating a stronger potential for direct detectability without the use of optimal power spectrum estimation techniques on almost all baseline lengths.
-
-% \begin{figure*}[htb]
-% \centering
-% \includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_170.0_MHz_subband_win_method_bhw2.0.eps}
-% \caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra obtained from the 170~MHz subband for different baseline lengths.}
-% \label{fig:asm-dps-beam-chromaticity-baselines-170-subband}
-% \end{figure*}
-
-It must be emphasized that these are obtained only with windowing techniques and do not represent the best sensitivity achievable with sophisticated tools such as optimal covariance-based weighting schemes \citep{liu14a,liu14b,ali15,dil15}.
-Thus assuming the data is limited by foregrounds and not by thermal noise, this demonstrates that even with no sophistication in power spectrum estimation, a direct detection based on simple windowing and delay spectrum technique is possible on a majority of HERA baselines and will further allow distinguishing between different EoR models.
-This finding holds even in the most conservative scenario where the modeled beam pattern with most severe chromaticity inherently results in significant and inherent foreground contamination outside the {\it foreground wedge}.
+\subsection{Sensitivity on Baseline-RA Parameter Space}\label{sec:baseline-LST}
 

### 2016-03-04 ForegroundSimulations/ms.tex
Update section 6.2 under EoR sensitivity
From d4fc481 (fgsim):
====================

In ms.tex,

(*) Update section 6.2 under EoR sensitivity

@@
 In this section, we provide cosmologically motivated upper limits on instrument systematics caused by these two types of reflections.
-% a related discussion by estimating the attenuation in power required to keep the foreground power reflected between adjacent antennas below the expected EoR H{\sc i} signal level for the different models of power patterns used in our study.
 
@@
 In order to isolate the requirements on beam chromaticity from other sources of chromaticity, we start with an antenna beam in which those spectral structures are absent but the intrinsic chromaticity of foregrounds and the baseline fringes are included.
-
-% We estimate the attenuation required at specific modes of interest $|k_\parallel|>k_\textrm{p}$ to contain reflected foreground power between antennas below expected EoR H{\sc i} power, both corresponding to a 14.6~m antenna spacing.
 
@@
 
+We investigate the EoR sensitivity in two dimensional parameter space formed by baselines and pointings in Right Ascension (RA$\equiv\alpha$) to highlight capabilities of HERA and provide clues for the best observing window.
+
+In this section, we assume that the H{\sc i} power spectrum is isotropic (no sample variance) and hence, independent of $\alpha$.
+However, it is dependent on the center of the subband, $f_0$, where $f_0 = f_{21}/(1+z)$.
+The foreground delay power spectra depends on both $f_0$ and $\alpha$.
+Thus, we rewrite the EoR H{\sc i} and foreground delay power spectra explicitly as a function of these quantities as $P_\textrm{H{\sc i}}(|\boldsymbol{b}|,k_\parallel,f_0)$ and $P_\textrm{FG}(\boldsymbol{b},k_\parallel,f_0,\alpha)$ respectively.
+
+We define baseline-dependent $k_\parallel$-modes of interest for {\it foreground avoidance} as $|k_\parallel| > k_\parallel^\textrm{FA}(\boldsymbol{b})$, with:
+\begin{align}
+  k_\parallel^\textrm{FA}(\boldsymbol{b}) &= \frac{2\pi\,f_{21}H_0\,E(z)}{c(1+z)^2}\,\left(\frac{|\boldsymbol{b}|}{c} + \frac{\zeta}{B_\textrm{eff}}\right), \label{eqn:kprll-limit}
+\end{align}
+where, the first term inside the parenthesis denotes the horizon limit, the second relates to the resolution due to subband bandwidth, $B_\textrm{eff}$, and $\zeta$ denotes a buffer to ensure $k_\parallel^\textrm{FA}(|\boldsymbol{b}|)$ threshold ``avoids'' the main lobe of foreground power.
+
+We estimate the worst case sensitivity in the $\boldsymbol{b}$--$\alpha$ parameter space as:
+\begin{align}
+  \rho(\boldsymbol{b},f_0,\alpha) &= \min_{|k_\parallel|>k_\parallel^\textrm{FA}(|\boldsymbol{b}|)}\left\{\frac{P_\textrm{H{\sc i}}(|\boldsymbol{b}|,k_\parallel,f_0)}{P_\textrm{FG}(\boldsymbol{b},k_\parallel,f_0,\alpha)}\right\}
+\end{align}
+We consider the foreground power spectrum obtained with the simulated chromatic antenna beam, and EoR models 1 and 2, in each of the 150~MHz and 170~MHz subbands.
+Fig.~\ref{fig:eor-fg-ratios} shows the worst case sensitivity, $\rho(\boldsymbol{b},f_0,\alpha)$, for all 30 unique HERA baselines over 24 hours of $\alpha$ for the two EoR models and two subbands used in this study.
+
 \begin{figure*}[htb]
 \centering
-\subfloat[][Power patterns]{\label{fig:21cmfast-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_150.0_MHz_subband.eps}}
-\subfloat[][Power patterns]{\label{fig:lidz-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_150.0_MHz_subband.eps}} \\
-\subfloat[][Power patterns]{\label{fig:21cmfast-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_170.0_MHz_subband.eps}}
-\subfloat[][Power patterns]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_170.0_MHz_subband.eps}}
+\subfloat[][EoR model 1, 150~MHz subband ]{\label{fig:21cmfast-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_150.0_MHz_subband.eps}}
+\subfloat[][EoR model 2, 150~MHz subband ]{\label{fig:lidz-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_150.0_MHz_subband.eps}} \\
+\subfloat[][EoR model 1, 170~MHz subband ]{\label{fig:21cmfast-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_170.0_MHz_subband.eps}}
+\subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_170.0_MHz_subband.eps}}
 \caption{}
@@
 
-% Owing to the chromaticity of power patterns, the spillover from foregrounds extends beyond the horizon limits, most severely in the simulated disk pattern.
-As a result the residuals have significant power remaining on either side of the horizon limits since the window for deconvolution is narrower than the extent of spillover along $k_\parallel$.
-The two peaks on either side is most severe for the simulated disk pattern followed by that for the {\it Airy} disk pattern and least for an achromatic power pattern.
+In general, sensitivity increases with longer baselines.
+We attribute this to the much steeper dependence of foreground emission on baseline length than that of EoR H{\sc i} power.
+This is also confirmed from Fig.~\ref{fig:subbands} where the peak and sidelobe levels of foreground power obtained with the simulated chromatic antenna beam on the 14.6~m baseline, which is sensitive to diffuse emission, progressively drops by two orders of magnitude on the 58.4~m baseline where diffuse emission is not as dominant.
+Hence, from a foreground contamination standpoint, the shortest baselines are less sensitive than the longer ones in the HERA-19 layout.
 
-% We investigate the effect of chromaticity of power pattern in a foreground avoidance strategy that avoids the aforementioned deconvolution of delay spectrum.
-Application of window functions with high sidelobe suppression have been discussed for mitigating foreground contamination \citep{thy13}.
-In line with the foreground avoidance strategy, the visibilities from the full band foreground simulation (whose delay power spectrum is shown on the top left) are multiplied by a Blackman-Harris window function of 10~MHz effective bandwidth.
-The delay power spectra so produced are shown in the panel on the bottom left.
-Due to the decreased effective bandwidth the resolution of the delay power spectrum appears decreased.
-Hence, only the $|k_\parallel| \gtrsim 0.14\,h$~Mpc$^{-1}$ modes remain accessible.
-Due to the overall lower amplitude of the {\it Airy} power pattern relative to the simulated dish power pattern and the achromatic pattern, the sidelobe levels of foreground delay power spectra from an {\it Airy} pattern are lower than the other models by almost two orders of magnitude.
+However, in all four cases considered here, the worst case signal-noise ratio lies above unity in most of this parameter space.
+It demonstrates that HERA will detect the EoR signal with a very high signal-noise ratio on all baselines in a vast majority of the pointings.
 
-% Following a delay-deconvolution based foreground removal strategy, we apply the Blackman-Harris window of effective bandwidth 10~MHz on the unsubtracted foreground residuals (top right panel) in frequency domain and obtain the delay power spectrum shown in the bottom right panel.
-It is noted that lesser the chromaticity the more effective the deconvolution process is in lowering the residuals in and around the horizon limits.
-For instance, the peak of the delay power spectrum using the achromatic beam is lowered by four orders of magnitude relative to the original peak whereas the residuals of delay power spectra with chromatic {\it Airy} and simulated power patterns is lowered only by two orders of magnitude.
-However, owing to the ineffective subtraction of the response extended beyond the horizon limits, the sidelobe levels have not been lowered significantly and are within an order of magnitude of each other.
-
-% In both strategies, the EoR H{\sc i} signal power spectrum obtained by simulations with 21cmFAST (Mesinger et al. 2008) is shown for reference (dashed black lines) in the bottom panels.
+We reiterate that these estimates are obtained from a conservative scenario wherein only simple spectral weighting technique in the {\it foreground avoidance} limit is used, without any foreground removal or sophisticated weighting strategies using inverse-covariance.
+Further, these estimates represent worst-case lower limits demonstrating that HERA-19 and its successors will be extremely sensitive for EoR experiments and will benefit even further with more optimal foreground suppression strategies.
 
@@
 
-This work was supported by the U. S. National Science Foundation (NSF) through award AST-1109257. DCJ is supported by an NSF Astronomy and Astrophysics Postdoctoral Fellowship under award AST-1401708.
+This work was supported by the U. S. National Science Foundation (NSF) through award AST-1109257.
 

### 2016-03-04 ForegroundSimulations/ms.tex
Add paragraph in Delay Spectrum section
From 9e6a4f7 (fgsim):
====================

In ms.tex,

(*) Add paragraph in Delay Spectrum section

@@
 \end{align}
+
+We note that these visibilities and delay power spectra are dependent on right ascension (RA) of the pointing as well as the center of the frequency band.
+We defer expressing visibilities and delay power spectra explicitly as a function of pointing or center frequency (or redshift) to later sections where it is necessitated.
 

### 2016-03-04 ForegroundSimulations/ms.tex
Update Introduction, add citations to bibliography
From d6a3635 (fgsim):
====================

In eor.bib,

(*) Add two references - Pober et al.(2015, 2016)

In ms.tex,

(*) Update Introduction section

@@
 
-The extreme dynamic range required to subtract foregrounds precisely demands high precision modeling of foregrounds as observed by modern wide-field instruments \citep{thy15a,thy15b}.
-Their studies of effects of wide-field measurements of EoR power spectra have demonstrated the {\it pitchfork} effect wherein foreshortening of baselines causes a prominent enhancement of foreground power near the horizon limits of the {\it foreground wedge} as well in the contamination beyond.
+However, despite attempts to exploit this knowledge about differences in spectral and spatial symmetry in lengthy observations, analysis from the first-generation experiments has at best only led to weak constraints on reionization models \citep{ali15,dil15,pob15}.
+This is because their sensitivity is primarily limited by instrumental and foreground systematics.
+The extreme dynamic range required to suppress foreground and instrument systematics demands high precision modeling of foregrounds as observed by modern wide-field instruments.
+One such study was undertaken by \citet{thy15a,thy15b}.
+Their studies of effects of wide-field measurements of EoR power spectra have demonstrated the {\it pitchfork} effect wherein foreshortening of baselines causes a prominent enhancement of foreground power near the horizon limits of the {\it foreground wedge} as well as in the contamination beyond.
+It highlighted the importance of controlling the response of wide-field instruments near the horizon.
+The need of precise subtraction of foregrounds in wide-field measurements was also highlighted in \citet{pob16}.
+
 In this paper, we explore yet another phenomenon that inherently extends foreground power beyond the {\it wedge}, namely, that arising from the chromaticity of the antenna power pattern.
-% We specifically use the current design of 14~m dish of HERA as an example in our study.
+While highlighting the significance of such instrumental systematics on future EoR experiments, we demonstrate that the current HERA instrument design will exceed these specifications to detect the EoR signal with high significance, when data is limited by foregrounds and systematics, even in the most conservative scenario which involves neither foreground subtraction nor optimal analysis techniques but only relies on a simple spectral weighting scheme.
 
@@
 \S\ref{sec:sim} describes foreground simulations including antenna beam pattern and all-sky foreground models.
-\S\ref{sec:beam-chromaticity} investigates the effects of chromaticity of antenna beam on the resulting delay power spectrum and the cosmologically motivated constraints it places on dish reflectometry.
+\S\ref{sec:beam-chromaticity} investigates the effects of chromaticity of antenna beam on the resulting delay power spectrum and the cosmologically motivated constraints it places on reflections in the instrument.
+Lower limits on sensitivity of HERA under conservative conditions are demonstrated in \S\ref{sec:eor-sensitivity}.
 Our findings are summarized in \S\ref{sec:summary}.
@@
 
-We reiterate that these estimates are obtained from a conservative scenario wherein only simple spectral weighting technique in the {\it foreground avoidance} limit is used, without any foreground removal or sophisticated weighting strategies using inverse-covariance.
+We reiterate that these estimates are obtained in a conservative scenario wherein only simple spectral weighting technique in the {\it foreground avoidance} limit is used, without any foreground removal or sophisticated weighting strategies using inverse-covariance.
 Further, these estimates represent worst-case lower limits demonstrating that HERA-19 and its successors will be extremely sensitive for EoR experiments and will benefit even further with more optimal foreground suppression strategies.

### 2016-03-04 ForegroundSimulations/ms.tex
Update HERA section, add citations
From ff20950 (fgsim):
====================

In eor.bib,

(*) Add few more references

In ms.tex,

(*) Update section 2 on HERA Instrument

@@
 The redshifted neutral hydrogen from the IGM in this epoch has been identified to be one of the most promising and direct probes of the EoR \citep{sun72,sco90,mad97,toz00,ili02}.
-Numerous experiments using low frequency radio telescopes targeting the redshifted 21~cm line from the spin-flip transition of H{\sc i} have become operational such as the Murchison Widefield Array \citep[MWA;][]{lon09,bow13,tin13}, the Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, the Low Frequency Array \citep[LOFAR;][]{van13} and the Giant Metrewave Radio Telescope EoR experiment \citep[GMRT;][]{pac13}.
+Numerous experiments using low frequency radio telescopes targeting the redshifted 21~cm line from the spin-flip transition of H{\sc i} have become operational such as the Murchison Widefield Array \citep[MWA;][]{lon09,bow13,tin13}, the Donald~C.~Backer Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, the Low Frequency Array \citep[LOFAR;][]{van13} and the Giant Metrewave Radio Telescope EoR experiment \citep[GMRT;][]{pac13}.
 These instruments have sufficient sensitivity for a statistical detection of the EoR signal via estimating the spatial power spectrum of the redshifted H{\sc i} temperature fluctuations \citep{bea13,thy13}.
-These instruments are intended to be precursors and pathfinders to the next generation of low frequency radio observatories such as the Hydrogen Epoch of Reionization Array\footnote{\url{http://reionization.org/}} (HERA; DeBoer~et~al.~2015) and the Square Kilometre Array\footnote{\url{https://www.skatelescope.org/}} (SKA).
+These instruments are intended to be precursors and pathfinders to the next generation of low frequency radio observatories such as the Hydrogen Epoch of Reionization Array\footnote{\url{http://reionization.org/}} \citep[HERA;][]{deb16} and the Square Kilometre Array\footnote{\url{https://www.skatelescope.org/}} (SKA).
 These next-generation instruments will advance the capability from a mere statistical detection of the signal to a direct three-dimensional tomographic imaging of the H{\sc i} during the EoR.
@@
 
-DeBoer~et~al.(2016)
+\citet{deb16} describe the HERA instrument in detail. Here, we provide a brief summary.
+
+The primary science goal of HERA is to widen our understanding of the first stars, galaxies, and black holes, and their role in driving reionization.
+Through power-spectral measurements of the redshifted 21cm line of H{\sc i} in the primordial IGM, HERA aims to directly constrain the topology and evolution of reionization, opening a unique window into the complex astrophysical interplay between the first luminous objects and their environments.
+HERA builds on the advances of first-generation 21cm EoR experiments, particularly PAPER, MWA, the MIT EoR experiment \citep[MITEoR;][]{zhe14} and the Experiment to Detect the Global EoR Step \citep[EDGES;][]{bow10}.
+
+HERA will deploy 14~m fixed zenith-pointing parabolic dishes that strike an optimal balance between sensitivity and systematics.
+The large collecting area of a HERA element yields $\approx 5$ times the sensitivity of an MWA tile and more than 20 times that of a PAPER element.
+
+320 core elements of HERA will be arranged in a compact hexagonal grid, split into three displaced segments to cover the $uv$-plane with sub-element sampling density.
+The core will be supplemented by 30 additional outrigger elements to tile the $uv$-plane with instantaneously complete sub-aperture sampling out to $250\lambda$ and complete aperture-scale sampling out to $350\lambda$ (at 150~MHz).
+The layout and its advantages are discussed in \citet{dil16}.
+
+In this study, we use the HERA-19 hexagonal array layout, a small subset of the planned layout.
+Without loss of generality, the analysis and results in this paper will apply to the full proposed layout as well.
 
@@
 These models cover a frequency range of 100--200~MHz in intervals of 1~MHz.
-Refer to DeBoer~et~al.~(2016) for a complete description of the dish model.
+Refer to \citet{deb16} for a complete description of the dish model.
 
@@
 One of the primary causes for spectral structure in antenna power patterns is reflections in the instrument.
-Patra~et~al.~2015 (in preparation) and \citet{ewa16} discuss the measured and simulated reflections respectively between a dish and its feed.
+\citet{pat16} and \citet{ewa16} discuss the measured and simulated reflections respectively between a dish and its feed.
 Reflection between structures and signal paths from different antennas also causes chromaticity in the antenna beam.
@@
 For instance, the attenuation required is $\gtrsim 54$~dB at $\sim 200$~ns for $k_\textrm{p}=0.1\,h$~Mpc$^{-1}$, $\gtrsim 56$~dB at $\sim 300$~ns for $k_\textrm{p}=0.15\,h$~Mpc$^{-1}$ and $\gtrsim 58$~dB at $\sim 400$~ns for $k_\textrm{p}=0.2\,h$~Mpc$^{-1}$.
-Measurements by Patra et al.
-(2016) for HERA dish-feed assembly show that the return losses lie well within the regions excluded by the shaded regions thus implying that the attenuation is well above the lower limit and hence will not prevent EoR detection.
+Measurements by \citet{pat16} for HERA dish-feed assembly show that the return losses lie well within the regions excluded by the shaded regions thus implying that the attenuation is well above the lower limit and hence will not prevent EoR detection.
 

### 2016-03-05 ForegroundSimulations/ms.tex
Update Summary section
From d67699b (fgsim):
====================

In ms.tex,

(*) Update Summary section

@@
 
-\acknowledgments
+First-generation EoR experiments such as the MWA, PAPER and LOFAR have made enormous progress in the field of 21~cm cosmology.
+However, they are currently limited by the systematics due to the extremely bright foregrounds and the instrument.
+Hence, characterizing the foregrounds and the instrument to a very high level of precision is critical for the success of next-generation EoR experiments.
+In this paper, we highlight the importance of a key systematic feature of the instrument -- the spectral structure of the antenna power pattern -- and its impact on EoR signal contamination, using HERA as an example.
 
-This work was supported by the U. S. National Science Foundation (NSF) through award AST-1109257.
+Using a new high dynamic range spectral weighting function obtained by convolving a {\it Blackman-Harris} window with itself, we isolate the effects of beam chromaticity on foreground delay power spectrum.
+We use three antenna beam models of varying chromaticity (achromatic, {\it Airy} and simulated chromatic) and show that increase in chromaticity extends the foreground spillover well beyond the horizon limits of the {\it foreground wedge} into the clean {\it EoR window} considered sensitive for EoR signal detection.
+The level of foreground spillover in the simulated chromatic beam is a few orders of magnitude worse than that from a nominal {\it Airy} disk pattern, which in turn is many orders of magnitude worse than that from an achromatic beam with no spectral structure.
+
+We note that the inevitable reflections in the antenna-feed assembly and between reflecting structures across multiple antennas are also significant factors that contaminate the cosmological signal in high $k_\parallel$-modes inside the {\it EoR window}.
+Using a novel approach, we provide a formalism to set cosmologically-motivated constraints directly on the level of suppression required on these reflections in the instrument.
+Ongoing reflectometry studies clearly indicate HERA will exceed the cosmologically-motivated lower limits prescribed here.
+
+Taking into account the effects of these instrumental systematics, if data is not limited by thermal noise, we demonstrate that HERA will detect EoR with high significance with s simple spectral weighting even under a conservative analysis criterion which does not involve any {\it foreground removal} strategies.
+All baselines of HERA-19 will not only detect but also help in filtering highly likely EoR models.
+
+We are also investigating advanced strategies for foreground removal that will robustly eliminate these systematics further.
+More optimal analysis techniques and further design improvements will make HERA not only clear the obstacles limiting first-generation experiments but also become transformational for next-generation low frequency cosmology experiments.
+
+% \acknowledgments
+
+% This work was supported by the U. S. National Science Foundation (NSF) through award AST-1109257.
 

### 2016-03-05 ForegroundSimulations/ms.tex
Update acknowledgements
From 475858c (fgsim):
====================

In ms.tex,

(*) Update acknowledgements
Add caption to figure 6
From 0f8f59c (fgsim):
====================

In ms.tex,

(*) Add caption to figure 6

@@
 \subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_170.0_MHz_subband.eps}}
-\caption{}
+\caption{Lower limits on EoR sensitivity, $\rho(\boldsymbol{b},f_0,\alpha)$, in {\it foreground avoidance} modes for different HERA-19 baselines as a function of RA ($\alpha$) of pointing on the sky.
+Each panel corresponds to the EoR model and subband indicated.
+The baseline vector is specified by its length (in m) and orientation (in degrees) at the bottom and top of the $x$-axis respectively.
+The color scale is logarithmic.
+Even with worst-case sensitivity, clearly HERA will be able detect EoR drawn from independent models on all baselines for a large fraction of a full 24~hour sky transit cycle.}
 \label{fig:eor-fg-ratios}
@@
 
-% \acknowledgments
+\acknowledgments
 
-% This work was supported by the U. S. National Science Foundation (NSF) through award AST-1109257.
+We thank Zaki Ali, Adam Beardsley, and Daniel Jacobs for their valuable inputs during the preparation of this manuscript.
 

### 2016-03-05 ForegroundSimulations/ms.tex
Add Abstract, and minor edits
From f3ce757 (fgsim):
====================

In ms.tex,

(*) Add Abstract
(*) Update caption of figure 6
(*) Minor edits throughout

@@
 
+Unaccounted systematics from foregrounds and instruments prevent present day experiments from detecting redshifted 21~cm signal from the Epoch of Reionization (EoR).
+In-depth understanding of these effects is critical for the success of such experiments.
+We identify spectral structures (chromaticity) in the antenna power pattern as one such systematic that significantly affects all EoR measurements.
+Increase in chromaticity of the antenna beam causes the already bright foreground power to leak well beyond ideal limits and contaminate the otherwise clean EoR signal modes.
+A primary source of this chromaticity is reflections in the antenna-feed assembly and between structures in neighboring antennas.
+Using precise foreground simulations taking wide-field effects into account, we provide a framework to set cosmologically-motivated upper limits on these reflections to prevent further EoR signal degradation.
+We use the Hydrogen Epoch of Reionization Array (HERA) as an example.
+Using a simple and yet high dynamic range spectral weighting scheme, we demonstrate that EoR detection using HERA will not be impeded by such spectral systematics even in a conservative scenario that does not require removal of foregrounds.
+We also show that all baselines in a 19-element HERA layout are capable of detecting EoR over a substantial observing window on the sky.
+
 \end{abstract}
@@
 These instruments are intended to be precursors and pathfinders to the next generation of low frequency radio observatories such as the Hydrogen Epoch of Reionization Array\footnote{\url{http://reionization.org/}} \citep[HERA;][]{deb16} and the Square Kilometre Array\footnote{\url{https://www.skatelescope.org/}} (SKA).
-These next-generation instruments will advance the capability from a mere statistical detection of the signal to a direct three-dimensional tomographic imaging of the H{\sc i} during the EoR.
+These next-generation instruments will advance the capability from a mere statistical detection of the signal to a direct three-dimensional tomographic imaging of the H{\sc i} from the EoR.
 
@@
 
-We note that these visibilities and delay power spectra are dependent on right ascension (RA) of the pointing as well as the center of the frequency band.
-We defer expressing visibilities and delay power spectra explicitly as a function of pointing or center frequency (or redshift) to later sections where it is necessitated.
+In this paper, we use $\Omega_\textrm{M}=0.27$, $\Omega_\Lambda=0.73$, $\Omega_\textrm{K}=1-\Omega_\textrm{M}-\Omega_\Lambda$, $H_0=100\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P_\textrm{d}(\boldsymbol{k}_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.
 
-In this paper, we use $\Omega_\textrm{M}=0.27$, $\Omega_\Lambda=0.73$, $\Omega_\textrm{K}=1-\Omega_\textrm{M}-\Omega_\Lambda$, $H_0=100\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P_\textrm{d}(\boldsymbol{k}_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.
+We note that these visibilities and delay power spectra are dependent on right ascension (RA) of the pointing as well as the frequency band.
+We defer expressing visibilities and delay power spectra explicitly as a function of pointing or center frequency (or redshift) to later sections where it becomes necessary.
 
@@
 \end{align}
-In its Fourier domain, this window has a response that is obtained by squaring of the {\it Blackman-Harris} window response and thus improves the dynamic range further in the power response by another 100 -- 120~dB while $\epsilon\approx 42\%$.
+In its Fourier domain, this window has a response obtained by squaring the {\it Blackman-Harris} window response and thus increases the dynamic range further in the power response by another 100 -- 120~dB while $\epsilon\approx 42\%$.
 This is an enormous gain in sidelobe characteristics for a negligible loss in over sensitivity relative to a simple {\it Blackman-Harris} weighting.
@@
 The color scale is logarithmic.
-Even with worst-case sensitivity, clearly HERA will be able detect EoR drawn from independent models on all baselines for a large fraction of a full 24~hour sky transit cycle.}
+Even with worst-case sensitivity, clearly HERA will be able detect EoR drawn from independent models on all baselines for a large fraction of a full 24~hour sky transit cycle.
+The sensitivity is seen to increase with increasing baseline length.
+This is because the loss in sensitivity to diffuse foreground power with increase in antenna spacings is faster than in the case of the EoR signal.}
 \label{fig:eor-fg-ratios}

### 2016-03-05 ForegroundSimulations/ms.tex
Update title, authors list, affiliations, keywords
From f2cbdf8 (fgsim):
====================

In ms.tex,

(*) Update title, authors list, affiliations and keywords

@@
 
-\shorttitle{Effects of Beam Chromaticity in EoR Power Spectra Measurements}
+\shorttitle{Effects of Beam Chromaticity on EoR Power Spectra Measurements}
 \shortauthors{Thyagarajan et~al.}
@@
 \def\ASU{\altaffilmark{1}}
-\def\ASUtxt{\altaffiltext{1}{Arizona State University, School of Earth and Space Exploration, Tempe, AZ 85287, USA}}
+\def\ASUtxt{\affil{\altaffilmark{1}Arizona State University, School of Earth and Space Exploration, Tempe, AZ 85287, USA}}
 
-\def\myemail{\altaffilmark{*}}
-\def\myemailtxt{\altaffiltext{*}{e-mail: t\_nithyanandan@asu.edu}}
+\def\UCB{\altaffilmark{2}}
+\def\UCBtxt{\affil{\altaffilmark{2}Dept. of Astronomy, University of California, Berkeley, CA, USA}}
 
-\def\UW{\altaffilmark{2}}
-\def\UWtxt{\altaffiltext{2}{University of Washington, Department of Physics, Seattle, WA 98195, USA}}
+\def\MIT{\altaffilmark{3}}
+\def\MITtxt{\affil{\altaffilmark{3}MIT Kavli Institute for Astrophysics and Space Research, Cambridge, MA 02139, USA}}
 
-\def\SKASA{\altaffilmark{3}}
-\def\SKASAtxt{\altaffiltext{3}{Square Kilometre Array South Africa (SKA SA), Park Road, Pinelands 7405, South Africa}}
+% \def\ASU{\altaffilmark{1}}
+% \def\ASUtxt{\altaffiltext{1}{Arizona State University, School of Earth and Space Exploration, Tempe, AZ 85287, USA}}
 
-\def\RU{\altaffilmark{4}}
-\def\RUtxt{\altaffiltext{4}{Department of Physics and Electronics, Rhodes University, Grahamstown 6140, South Africa}}
+% \def\UCB{\altaffilmark{2}}
+% \def\UCBtxt{\altaffiltext{2}{Dept. of Astronomy, University of California, Berkeley, CA, USA}}
 
-\def\CfA{\altaffilmark{5}}
-\def\CfAtxt{\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA}}
+% \def\MIT{\altaffilmark{3}}
+% \def\MITtxt{\altaffiltext{3}{MIT Kavli Institute for Astrophysics and Space Research, Cambridge, MA 02139, USA}}
 
-\def\ANU{\altaffilmark{6}}
-\def\ANUtxt{\altaffiltext{6}{Australian National University, Research School of Astronomy and Astrophysics, Canberra, ACT 2611, Australia}}
-
-\def\CAASTRO{\altaffilmark{7}}
-\def\CAASTROtxt{\altaffiltext{7}{ARC Centre of Excellence for All-sky Astrophysics (CAASTRO)}}
-
-\def\Haystack{\altaffilmark{8}}
-\def\Haystacktxt{\altaffiltext{8}{MIT Haystack Observatory, Westford, MA 01886, USA}}
-
-\def\MIT{\altaffilmark{9}}
-\def\MITtxt{\altaffiltext{9}{MIT Kavli Institute for Astrophysics and Space Research, Cambridge, MA 02139, USA}}
-
-\def\Curtin{\altaffilmark{10}}
-\def\Curtintxt{\altaffiltext{10}{International Centre for Radio Astronomy Research, Curtin University, Perth, WA 6845, Australia}}
-
-\def\Victoria{\altaffilmark{11}}
-\def\Victoriatxt{\altaffiltext{11}{Victoria University of Wellington, School of Chemical \& Physical Sciences, Wellington 6140, New Zealand}}
-
-\def\UWisc{\altaffilmark{12}}
-\def\UWisctxt{\altaffiltext{12}{University of Wisconsin--Milwaukee, Department of Physics, Milwaukee, WI 53201, USA}}
-
-\def\UMichigan{\altaffilmark{13}}
-\def\UMichigantxt{\altaffiltext{13}{University of Michigan, Department of Atmospheric, Oceanic and Space Sciences, Ann Arbor, MI 48109, USA}}
-
-\def\UMelbourne{\altaffilmark{14}}
-\def\UMelbournetxt{\altaffiltext{14}{The University of Melbourne, School of Physics, Parkville, VIC 3010, Australia}}
-
-\def\USydney{\altaffilmark{15}}
-\def\USydneytxt{\altaffiltext{15}{The University of Sydney, Sydney Institute for Astronomy, School of Physics, NSW 2006, Australia}}
-
-\def\CASS{\altaffilmark{16}}
-\def\CASStxt{\altaffiltext{16}{CSIRO Astronomy and Space Science (CASS), PO Box 76, Epping, NSW 1710, Australia}}
-
-\def\Tata{\altaffilmark{17}}
-\def\Tatatxt{\altaffiltext{17}{National Centre for Radio Astrophysics, Tata Institute for Fundamental Research, Pune 411007, India}}
-
-\def\RRI{\altaffilmark{18}}
-\def\RRItxt{\altaffiltext{18}{Raman Research Institute, Bangalore 560080, India}}
-
-\def\NRAO{\altaffilmark{19}}
-\def\NRAOtxt{\altaffiltext{19}{National Radio Astronomy Observatory, Charlottesville and Greenbank, USA}}
-
-\def\UWA{\altaffilmark{20}}
-\def\UWAtxt{\altaffiltext{20}{International Centre for Radio Astronomy Research, University of Western Australia, Crawley, WA 6009, Australia}}
+\def\myemail{\altaffilmark{$\dagger$}}
+\def\myemailtxt{\altaffiltext{$\dagger$}{e-mail: t\_nithyanandan@asu.edu}}
 
@@
 
-\title{Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra}
+\title{Effects of Antenna Beam Chromaticity on Redshifted 21~cm Power Spectrum and Implications for Hydrogen Epoch of Reionization Array}
+% \title{Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra}
 
@@
 Nithyanandan~Thyagarajan\ASU\myemail,
-TBD
-% Daniel~C.~Jacobs\ASU,
-% Judd~D.~Bowman\ASU,
-% N.~Barry\UW,
-% A.~P.~Beardsley\UW,
-% G.~Bernardi\SKASA$^,$\RU$^,$\CfA,
-% F.~Briggs\ANU$^,$\CAASTRO,
-% R.~J.~Cappallo\Haystack, 
-% P.~Carroll\UW,
-% B.~E.~Corey\Haystack, 
-% % A.~A.~Deshpande\RRI, 
-% A.~de~Oliveira-Costa\MIT,
-% Joshua~S.~Dillon\MIT,
-% D.~Emrich\Curtin,
-% % B.~M.~Gaensler\USydney$^,$\CAASTRO, 
-% A.~Ewall-Wice\MIT,
-% L.~Feng\MIT,
-% R.~Goeke\MIT,
-% L.~J.~Greenhill\CfA,
-% B.~J.~Hazelton\UW, 
-% J.~N.~Hewitt\MIT,
-% N.~Hurley-Walker\Curtin,
-% M.~Johnston-Hollitt\Victoria,
-% D.~L.~Kaplan\UWisc, 
-% J.~C.~Kasper\UMichigan$^,$\CfA, 
-% Han-Seek Kim\UMelbourne$^,$\CAASTRO,
-% P.~Kittiwisit\ASU,
-% E.~Kratzenberg\Haystack, 
-% E.~Lenc\USydney$^,$\CAASTRO,
-% J.~Line\UMelbourne$^,$\CAASTRO,
-% A.~Loeb\CfA,
-% C.~J.~Lonsdale\Haystack, 
-% M.~J.~Lynch\Curtin, 
-% B.~McKinley\UMelbourne$^,$\CAASTRO,
-% S.~R.~McWhirter\Haystack,
-% D.~A.~Mitchell\CASS$^,$\CAASTRO, 
-% M.~F.~Morales\UW, 
-% E.~Morgan\MIT, 
-% A.~R.~Neben\MIT,
-% D.~Oberoi\Tata, 
-% A.~R.~Offringa\ANU$^,$\CAASTRO, 
-% S.~M.~Ord\Curtin$^,$\CAASTRO,
-% Sourabh Paul\RRI,
-% B.~Pindor\UMelbourne$^,$\CAASTRO,
-% J.~C.~Pober\UW,
-% T.~Prabu\RRI, 
-% P.~Procopio\UMelbourne$^,$\CAASTRO,
-% J.~Riding\UMelbourne$^,$\CAASTRO,
-% A.~E.~E.~Rogers\Haystack, 
-% A.~Roshi\NRAO, 
-% N.~Udaya~Shankar\RRI, 
-% Shiv~K.~Sethi\RRI,
-% K.~S.~Srivani\RRI, 
-% R.~Subrahmanyan\RRI$^,$\CAASTRO, 
-% I.~S.~Sullivan\UW,
-% M.~Tegmark\MIT,
-% S.~J.~Tingay\Curtin$^,$\CAASTRO, 
-% C.~M.~Trott\Curtin$^,$\CAASTRO,
-% M.~Waterson\Curtin$^,$\ANU,
-% R.~B.~Wayth\Curtin$^,$\CAASTRO, 
-% R.~L.~Webster\UMelbourne$^,$\CAASTRO, 
-% A.~R.~Whitney\Haystack, 
-% A.~Williams\Curtin, 
-% C.~L.~Williams\MIT,
-% C.~Wu\UWA,
-% J.~S.~B.~Wyithe\UMelbourne$^,$\CAASTRO
+Aaron~R.~Parsons\UCB,
+David~R.~DeBoer\UCB,
+Judd~D.~Bowman\ASU,
+%% Co-authors
+Nipanjana~Patra\UCB,
+Aaron~M.~Ewall-Wice\MIT,
+Abraham~R.~Neben\MIT
 }
@@
 \ASUtxt
-% \UWtxt
-% \SKASAtxt
-% \RUtxt
-% \CfAtxt
-% \ANUtxt
-% \CAASTROtxt
-% \Haystacktxt
-% \MITtxt
-% \Curtintxt
-% \Victoriatxt
-% \UWisctxt
-% \UMichigantxt
-% \UMelbournetxt
-% \USydneytxt
-% \CASStxt
-% \Tatatxt
-% \RRItxt
-% \NRAOtxt
-% \UWAtxt
+\UCBtxt
+\MITtxt
 \myemailtxt
@@
 
-\keywords{cosmology: observations --- dark ages, reionization, first stars --- large-scale structure of universe --- methods: statistical --- radio continuum: galaxies --- techniques: interferometric}
+\keywords{cosmology: observations --- dark ages, reionization, first stars --- instrumentation: interferometers --- large-scale structure of universe --- radio continuum: galaxies --- techniques: interferometric}
 
@@
 
-\subsection{EoR Model}\label{sec:EoR-model}
+\subsection{EoR Models}\label{sec:EoR-model}
 
@@
 
-It must be emphasized that such a significant spillover is not limited by the horizon limits of the {\it foreground wedge} because this is caused by spectral structure in the antenna beam pattern in addition to that caused by position-dependent geometric phase in the visibility spectra.
+It must be emphasized that such a significant spillover is not bound by the horizon limits of the {\it foreground wedge} because this is caused by spectral structure in the antenna beam pattern in addition to that caused by position-dependent geometric phase in the visibility spectra.
 As a result delay-based complex deconvolution techniques such as CLEAN \citep{tay99,par09,par12b} that rely on smoothness of foreground spectra and only spectral window shape will not have adequate information to accurately deconvolve intrinsic supra-horizon spillover arising from the chromaticity of the antenna beam.

### 2016-03-06 ForegroundSimulations/ms.tex
Update sensitivity figures, minor text edits
From ed32dfb (fgsim):
====================

(*) Update sensitivity figures

In ms.tex,

(*) Minor edits throughout
(*) Use updated sensitivity figures

@@
 
-\shorttitle{Effects of Beam Chromaticity on EoR Power Spectra Measurements}
+\shorttitle{Effects of Beam Chromaticity on EoR H{\sc i} Power Spectra Measurements}
 \shortauthors{Thyagarajan et~al.}
@@
 Unaccounted systematics from foregrounds and instruments prevent present day experiments from detecting redshifted 21~cm signal from the Epoch of Reionization (EoR).
-In-depth understanding of these effects is critical for the success of such experiments.
+In-depth understanding of these effects is critical for such experiments to succeed.
 We identify spectral structures (chromaticity) in the antenna power pattern as one such systematic that significantly affects all EoR measurements.
@@
 This is an important period of nonlinear growth of matter density perturbations and astrophysical evolution leading to the large scale structure observed currently in the Universe.
-And yet, this period in the Universe's history has remained poorly probed to date with observations.
+And yet, this period in the Universe's history has remained poorly probed to date.
 
@@
 Numerous experiments using low frequency radio telescopes targeting the redshifted 21~cm line from the spin-flip transition of H{\sc i} have become operational such as the Murchison Widefield Array \citep[MWA;][]{lon09,bow13,tin13}, the Donald~C.~Backer Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, the Low Frequency Array \citep[LOFAR;][]{van13} and the Giant Metrewave Radio Telescope EoR experiment \citep[GMRT;][]{pac13}.
-These instruments have sufficient sensitivity for a statistical detection of the EoR signal via estimating the spatial power spectrum of the redshifted H{\sc i} temperature fluctuations \citep{bea13,thy13}.
+Many of these instruments have sufficient sensitivity for a statistical detection of the EoR signal by estimating the spatial power spectrum of the redshifted H{\sc i} spin temperature fluctuations \citep{bea13,thy13}.
 These instruments are intended to be precursors and pathfinders to the next generation of low frequency radio observatories such as the Hydrogen Epoch of Reionization Array\footnote{\url{http://reionization.org/}} \citep[HERA;][]{deb16} and the Square Kilometre Array\footnote{\url{https://www.skatelescope.org/}} (SKA).
-These next-generation instruments will advance the capability from a mere statistical detection of the signal to a direct three-dimensional tomographic imaging of the H{\sc i} from the EoR.
+These next-generation instruments will advance the capability from a mere statistical detection of the signal to a direct three-dimensional tomographic imaging of H{\sc i} from the EoR.
 
@@
 
-When expressed in the coordinate system of power spectrum measurements described by the three-dimensional wavenumber ($k$), the foreground emission is restricted to a wedge-shaped region commonly referred to as the {\it foreground wedge} \citep{bow09,liu09,liu14a,liu14b,dat10,liu11,gho12,mor12,par12b,tro12,ved12,dil13,pob13,thy13,dil14} whereas the EoR signal has spherical symmetry due to its isotropy which appears elongated along line of sight $k$ modes due to peculiar velocity effects when dominated by matter density perturbations during early stages of reionization.
+When expressed in the coordinate system of power spectrum measurements described by the three-dimensional wavenumber ($k$), the foreground emission is restricted to a wedge-shaped region commonly referred to as the {\it foreground wedge} \citep{bow09,liu09,liu14a,liu14b,dat10,liu11,gho12,mor12,par12b,tro12,ved12,dil13,pob13,thy13,dil14}, whereas the EoR signal has spherical symmetry due to its isotropy which appears elongated along line of sight $k$ modes due to peculiar velocity effects when dominated by matter density perturbations during early stages of reionization.
 
@@
 It highlighted the importance of controlling the response of wide-field instruments near the horizon.
-The need of precise subtraction of foregrounds in wide-field measurements was also highlighted in \citet{pob16}.
+The need for precise subtraction of foregrounds in wide-field measurements was also highlighted in \citet{pob16}.
 
 In this paper, we explore yet another phenomenon that inherently extends foreground power beyond the {\it wedge}, namely, that arising from the chromaticity of the antenna power pattern.
-While highlighting the significance of such instrumental systematics on future EoR experiments, we demonstrate that the current HERA instrument design will exceed these specifications to detect the EoR signal with high significance, when data is limited by foregrounds and systematics, even in the most conservative scenario which involves neither foreground subtraction nor optimal analysis techniques but only relies on a simple spectral weighting scheme.
+While highlighting the importance of such instrumental systematics on future EoR experiments, we demonstrate that the current HERA instrument design will exceed these specifications to detect the EoR signal with high significance.
+This will hold when data is limited by foregrounds and systematics even in the most conservative scenario which involves neither foreground subtraction nor optimal analysis techniques but only relies on a simple spectral weighting scheme.
 
@@
 A brief summary of the delay spectrum technique used extensively in this analysis and the recently confirmed {\it pitchfork} effect are presented in \S\ref{sec:delay-spectrum}.
-\S\ref{sec:sim} describes foreground simulations including antenna beam pattern and all-sky foreground models.
+\S\ref{sec:sim} describes foreground simulations including antenna beam pattern, all-sky foreground models and two independent EoR models.
 \S\ref{sec:beam-chromaticity} investigates the effects of chromaticity of antenna beam on the resulting delay power spectrum and the cosmologically motivated constraints it places on reflections in the instrument.
-Lower limits on sensitivity of HERA under conservative conditions are demonstrated in \S\ref{sec:eor-sensitivity}.
+Lower limits on sensitivity of HERA under simple {\it foreground avoidance} criteria are demonstrated in \S\ref{sec:eor-sensitivity}.
 Our findings are summarized in \S\ref{sec:summary}.
@@
 
-The delay spectrum has a close resemblance to cosmological H~{\sc i} spatial power spectrum. Thus, the delay power spectrum is defined as:
+The delay spectrum has a close resemblance to cosmological H~{\sc i} spatial power spectrum and is defined as:
 \begin{align}\label{eqn:delay-power-spectrum}
@@
 We note that these visibilities and delay power spectra are dependent on right ascension (RA) of the pointing as well as the frequency band.
-We defer expressing visibilities and delay power spectra explicitly as a function of pointing or center frequency (or redshift) to later sections where it becomes necessary.
+However, we defer expressing them explicitly as a function of pointing and center frequency (or redshift) to later sections where it becomes necessary.
 
@@
 A dish characterized by a nominal {\it Airy} pattern was found to mitigate this contamination by over four and two orders of magnitude relative to a dipole and a phased array of dipoles respectively.
-HERA has significantly based its antenna design principles on these findings in choosing its antenna geometry while paying close attention to the properties of the resulting antenna power pattern.
+HERA has significantly based its antenna design principles on these findings in choosing its antenna geometry.
 
-In this paper, we investigate the spectral properties of the proposed dish design through their effects on the resultant foreground delay power spectrum and the constraints they place on attenuation required to suppress reflections between the dish-receiver assembly and antenna pairs to within tolerable limits.
+In this paper, we investigate the spectral properties of the proposed dish design through their effects on the resultant foreground delay power spectrum and the constraints they place on attenuation required to suppress reflections between the antenna-feed assembly and antenna pairs to within tolerable limits.
 
@@
 
-In a related series of papers, \citet{neb16} discuss the agreement of these simulated antenna beam patterns with actual measurements and \citet{ewa16} model the reflections and return loss expected in the proposed antenna-receiver assembly.
+In a related series of papers, \citet{neb16} discuss the agreement of these simulated antenna beam patterns with actual measurements and \citet{ewa16} model the reflections and return loss expected in the proposed antenna-feed assembly.
 Our focus in this paper is to investigate chromaticity of antenna power patterns from the point of view of their impact on foreground contamination in delay power spectra.
@@
 The code uses the excursion set formalism of \citet{fur04a} to generate ionization and 21cm brightness fields for numerous redshifts.
-The model shown in this paper assumes the same fiducial values of $T_\text{vir}^\text{min} = 2 \times 10^4$~K (virial temperature of minimum mass of dark matter halos that host ionizing sources), $\zeta = 20$ (ionization efficiency), and $R_\text{mfp}=15$~Mpc (mean free path of UV photons) which predicts the redshift of 50\% ionization (and hence a peak in the power spectrum signal) to be at $z=8.5$ as in Ewall-Wice~et~al.(2016; submitted).
-The second model is borrowed from the simulations described in detail in \citet{lid08}.
+The model shown in this paper assumes the same fiducial values as in \citet{ewa16}: $T_\text{vir}^\text{min} = 2 \times 10^4$~K (virial temperature of minimum mass of dark matter halos that host ionizing sources), $\zeta = 20$ (ionization efficiency), and $R_\text{mfp}=15$~Mpc (mean free path of UV photons) which predicts the redshift of 50\% ionization (and hence a peak in the power spectrum signal) to be at $z=8.5$.
+The second EoR model is borrowed from the simulations described in detail in \citet{lid08}.
 Hereafter, we refer to these two as EoR models 1 and 2 respectively.
@@
 The chromatic nature (variation with frequency) of the antenna power pattern results in a convolution of the geometrical mapping with the delay response of spectral chromaticity of the power pattern.
-This can result in a significant spillover of foreground power beyond the horizon delay limits especially in the case of foregrounds near the horizon.
+We discuss the resulting spillover of foreground power beyond the horizon delay limits.
 
@@
 Since our aim in this paper is to quantify foreground contamination and EoR sensitivity without employing any sophisticated {\it foreground removal} techniques, we turn out attention to {\it foreground avoidance} strategy that employs spectral weighting technique.
-In such an estimation of power spectrum, specific choices for spectral weighting function, $W(f)$, have been found to be effective in reducing foreground contamination by many orders of magnitude \citep{thy13} and is regularly used in EoR data analysis \citep{par12a}.
+In such a scheme, specific choices for spectral weighting function, $W(f)$, have been found to be effective in reducing foreground contamination by many orders of magnitude \citep{thy13} and is regularly used in EoR data analysis \citep{par12a}.
 For instance, a {\it Blackman-Harris} function \citep{har78} has a dynamic range of $\sim$100 -- 120~dB in delay power spectrum and a reduced effective bandwidth, with:
@@
 For a {\it Blackman-Harris} window function denoted by $W_\textrm{BH}(f)$, $\epsilon \approx 50\%$.
-Hence, the window spans a total of $2N$ frequency channels each of width $\Delta f$ to have $B_\textrm{eff} \approx N\,\Delta f$.
+% Hence, the window spans a total of $2N$ frequency channels each of width $\Delta f$ to have $B_\textrm{eff} \approx N\,\Delta f$.
 
@@
 \end{align}
-In its Fourier domain, this window has a response obtained by squaring the {\it Blackman-Harris} window response and thus increases the dynamic range further in the power response by another 100 -- 120~dB while $\epsilon\approx 42\%$.
-This is an enormous gain in sidelobe characteristics for a negligible loss in over sensitivity relative to a simple {\it Blackman-Harris} weighting.
-This will ensure that the contamination resulting from spillover of foregrounds along the line-of-sight $k$-modes are limited by intrinsic spectral structures in the foregrounds and the beam patterns and not by sidelobes from spectral weighting.
-In this paper, we apply this modified spectral weighting function defined in equation~\ref{eqn:bhw2} whenever foregrounds are represented in the Fourier delay domain.
+
+Fig.~\ref{fig:window-functions} shows the {\it Blackman-Harris} window (gray) and  the window in equation~\ref{eqn:bhw2} (black) in frequency (top) and their power responses in delay (bottom).
+In its Fourier domain, this window has a response obtained by squaring the {\it Blackman-Harris} window response and thus increases the dynamic range further in the power response by another 100 -- 120~dB with $\epsilon\approx 42\%$.
 
@@
 The overall sensitivity of the former is $\epsilon \approx 50\%$ of a rectangular window while that of the latter is $\epsilon \approx 42\%$.
-Hence, the latter is narrower than the former.
-As a result, the main lobe of the convolved window function response is wider than that of a {\it Blackman-Harris} window.
-However, the sidelobes from the convolved window function are suppressed by more than ten orders of magnitude relative to that of a nominal {\it Blackman-Harris} window for only a slight loss of resolution.}
+As a result, the main lobe of the convolved window function response is slightly wider than that of a {\it Blackman-Harris} window.
+However, the sidelobes from the convolved window function are suppressed by more than ten orders of magnitude relative to that of a nominal {\it Blackman-Harris} window.}
   \label{fig:window-functions}
@@
 
+This is an enormous gain in sidelobe characteristics for a negligible loss of sensitivity relative to a simple {\it Blackman-Harris} weighting.
+This will ensure that the contamination resulting from spillover of foregrounds along the line-of-sight $k$-modes are limited only by intrinsic spectral structures in the foregrounds and the beam patterns and not by sidelobes from spectral weighting.
+In this paper, we apply this modified spectral weighting function defined in equation~\ref{eqn:bhw2} whenever foregrounds are represented in the Fourier delay domain.
+
 In HERA-19 array layout, there are 30 unique baseline vectors and 8 unique baseline lengths.
-Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines} shows the delay power spectra of foregrounds on the 8 unique baseline lengths obtained with the aforementioned models for power pattern at arbitrary local sidereal times (LST).
+Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines} shows the delay power spectra of foregrounds on the 8 unique baseline lengths obtained with the aforementioned models for power pattern at arbitrary pointings on the sky.
 In all these panels, the full-band spectrally weighted foreground delay power spectra obtained with achromatic, {\it Airy} and fully chromatic simulated beam patterns are shown in black, red, and blue respectively.
@@
   \includegraphics[width=\linewidth]{asm_foreground_eor_beam_chromaticity_fullband_bhw2.0.eps}
-  \caption{Foreground delay power spectra in units of K$^2 (h^{-1}$~Mpc$)^3$ on unique baseline lengths of HERA-19 at arbitrary LST.
+  \caption{Foreground delay power spectra in units of K$^2 (h^{-1}$~Mpc$)^3$ on unique baseline lengths of HERA-19 at arbitrary sky pointings.
 The baseline length and orientation (anti-clockwise from East) are annotated at the top right corner of each panel.
@@
 
-It must be emphasized that such a significant spillover is not bound by the horizon limits of the {\it foreground wedge} because this is caused by spectral structure in the antenna beam pattern in addition to that caused by position-dependent geometric phase in the visibility spectra.
+It must be emphasized that such a significant spillover is not bound by the horizon limits of the {\it foreground wedge} because this is caused by spectral structure in the antenna beam pattern which is independent of the position-dependent geometric delays.
 As a result delay-based complex deconvolution techniques such as CLEAN \citep{tay99,par09,par12b} that rely on smoothness of foreground spectra and only spectral window shape will not have adequate information to accurately deconvolve intrinsic supra-horizon spillover arising from the chromaticity of the antenna beam.
-We leave delay power spectrum estimation using {\it foreground removal} strategy that accounts for direction-dependent and beam chromaticity-dependent effects to future work and use only simple {\it foreground avoidance} approach in this study.
+We leave delay power spectrum estimation using {\it foreground removal} strategy that accounts for direction-dependent and beam chromaticity-dependent effects to future work.
 
@@
 
-The effect of reflections it to shift the measured foreground power to higher modes in $\tau$ (or equivalently in $k_\parallel$) and thus cause further contamination in these higher $k_\parallel$ modes which are considered sensitive for EoR H{\sc i} signal detection.
+The effect of reflections it to shift the measured foreground power to higher modes in $\tau$ (or equivalently in $k_\parallel$) and thus cause further contamination in these higher $k_\parallel$-modes which are considered sensitive for EoR H{\sc i} signal detection.
 Equivalently, these delay shifts introduce ripples in the spectrum.
-The net chromaticity in the measurements is the product of spectral structure arising out of the intrinsic nature of foreground emission, the baseline-dependent frequency structure of the fringes, the spectral features in the antenna power pattern besides any other spectral structures in the instrument unaccounted for.
+The net chromaticity in the measurements is the product of spectral structure arising out of the intrinsic nature of foreground emission, the baseline- and position-dependent frequency structure of the fringes, the spectral features in the antenna power pattern besides any other spectral structures in the instrument unaccounted for.
 Equivalently, in the Fourier domain these factors have a convolving effect.
@@
 \end{align}
-where, $P_\textrm{H{\sc i}}(k_\parallel)$ is the EoR H{\sc i} power spectrum for the chosen antenna spacing, $P_\textrm{FG}(k_\parallel)$ is the foreground delay power spectrum obtained with the spectral weighting function applied over the full band of the three uniquely oriented 14.6~m antenna spacings further averaged over a 0--12 hr LST range and over both positive and negative $k_\parallel$ modes, $\tau$ is the delay caused by reflections, and $\dif k_\parallel/\dif \tau$ is the {\it jacobian} in the transformation of $\tau$ to $k_\parallel$ (see equation~\ref{eqn:kprll-delay}).
+where, $P_\textrm{H{\sc i}}(k_\parallel)$ is the EoR H{\sc i} power spectrum for the chosen antenna spacing, $P_\textrm{FG}(k_\parallel)$ is the foreground delay power spectrum obtained with the spectral weighting function applied over the full band of the three uniquely oriented 14.6~m antenna spacings further averaged over a 0--12 hr local sidereal time (LST) range and over both positive and negative $k_\parallel$-modes, $\tau$ is the delay caused by reflections, and $\dif k_\parallel/\dif \tau$ is the {\it jacobian} in the transformation of $\tau$ to $k_\parallel$ (see equation~\ref{eqn:kprll-delay}).
 Equivalently, $\Gamma_{k_\textrm{p}}(\tau)$ is determined by the requirement that the reflected foreground power obtained by shifting in delay is below the EoR H{\sc i} signal power in line-of-sight spatial scales of interest given by $|k_\parallel|>k_\textrm{p}$.
-For this analysis constraining reflections, we use the 21cmFAST model at 150~MHz ($z\approx 8.47$) for $P_\textrm{H{\sc i}}(k_\parallel)$.
+For this analysis constraining reflections, we use EoR model 1 at 150~MHz ($z\approx 8.47$).
 
@@
 Fig.~\ref{fig:fg-reflections-achrmbeam} shows $\Gamma_{k_\textrm{p}}(\tau)$ (in dB) for $k_\textrm{p}$ chosen to be 0.1~$h$~Mpc$^{-1}$ (solid), 0.15~$h$~Mpc$^{-1}$ (dashed), and 0.2~$h$~Mpc$^{-1}$ (dotted).
-These curves set an upper limit to the reflected foreground power below the EoR H{\sc i} signal power as a function of delays caused by dish-feed reflections.
+These curves set an upper limit for the reflected foreground power to lie below the EoR H{\sc i} signal power as a function of delays caused by dish-feed reflections.
 In other words, it implies that if reflections in the dish-feed assembly are attenuated to levels that lie in the regions below the different shaded regions, such spectral systematics in the instrument will not hinder detection of EoR in those corresponding $k_\parallel$ modes of interest.
@@
 \caption{Lower limit on attenuation of reflected foreground power (in dB) from dish-feed reflections required to keep the reflected foreground power below EoR H{\sc i} signal power for all $k_\parallel$-modes greater than $0.1\,h$~Mpc$^{-1}$ (solid), $0.15\,h$~Mpc$^{-1}$ (dashed) and $0.2\,h$~Mpc$^{-1}$ (dotted).
-This is obtained on 14.6~m antenna spacing for a 21cmFAST EoR model at 150~MHz ($z\approx 8.47$) and foreground power obtained with an achromatic antenna beam model.
+This is obtained on 14.6~m antenna spacing for EoR model 1 at 150~MHz ($z\approx 8.47$) and foreground power obtained with an achromatic antenna beam model.
 When the attenuation on dish-feed reflections is higher than these limits (outside the shaded regions), EoR will be detectable in respective $k_\parallel$-modes despite these reflections.}
@@
 \caption{Lower limit on attenuation of reflected foreground power (in dB) from antenna-to-antenna reflections required to keep the reflected foreground power below EoR H{\sc i} signal power for all $k_\parallel$-modes greater than $0.1\,h$~Mpc$^{-1}$ (left), $0.15\,h$~Mpc$^{-1}$ (middle) and $0.2\,h$~Mpc$^{-1}$ (right).
-This is obtained on 14.6~m antenna spacing for a 21cmFAST EoR model at 150~MHz ($z\approx 8.47$) and foreground power obtained with an {\it Airy} (dashed) and simulated chromatic (solid) antenna beam models.
+This is obtained on 14.6~m antenna spacing for EoR model 1 at 150~MHz ($z\approx 8.47$) and foreground power obtained with an {\it Airy} (dashed) and simulated chromatic (solid) antenna beam models.
 Regions excluding shaded regions indicate EoR will be detectable in respective $k_\parallel$-modes despite these reflections.
@@
 For instance, $k_\parallel > 0.1\,h$~Mpc$^{-1}$ modes will be inaccessible with the simulated chromatic beam if these reflections are taken into account.
-However, for the same beam the instrument will enjoy a much higher tolerance despite these reflections if the modes of interest are $k_\parallel > 0.2\,h$~Mpc$^{-1}$ for EoR detection.
-Owing to lower chromaticity, an {\it Airy} beam offers higher tolerance to reflections compared to the simulated chromatic beam.}
+However, for the same beam the instrument will have much higher tolerance despite these reflections if the modes of interest are $k_\parallel > 0.2\,h$~Mpc$^{-1}$.
+Due to lower chromaticity, an {\it Airy} beam offers more tolerance to reflections than the simulated chromatic beam.}
 \label{fig:fg-reflections}
@@
 
-It may be noted here that designing a dish whose antenna beam closely resembles a nominal {\it Airy} pattern will have a significantly higher ceiling of tolerance for allowing antenna-to-antenna reflections and yet remain very effective for EoR signal detection.
-The HERA collaboration is actively pursuing constant improvement of its dish design to keep minimize limitations from such chromatic systematics.
+It may be noted here that designing a dish whose antenna beam closely resembles a nominal {\it Airy} pattern will have a significantly higher tolerance for allowing antenna-to-antenna reflections and yet remain very effective for EoR signal detection.
+The HERA collaboration constantly pursues improvement of its dish design to keep minimize limitations from such chromatic systematics.
 
@@
 These subbands with $B_\textrm{eff}=10$~MHz are defined by spectral weights obtained by convolution of {\it Blackman-Harris} window with itself.
-These subbands are centered at 150~MHz and 170~MHz to estimate sensitivity at $z \approx 8.47$ and $z \approx 7.36$.
-We use independent EoR models 1 and 2 to reduce the dependence of this analysis on any single EoR model.
+These subbands are centered at 150~MHz and 170~MHz to estimate sensitivity at $z \approx 8.47$ and $z \approx 7.36$ respectively.
+We use both EoR models 1 and 2 to reduce the dependence of this analysis on any single EoR model.
 
@@
 \subfloat[][170~MHz subband ($z \approx 7.36$)]{\label{fig:asm-dps-beam-chromaticity-baselines-170-subband}\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_170.0_MHz_subband_win_method_bhw2.0.eps}}
-\caption{EoR signal and foreground delay power spectrum in units of K$^2 (h^{-1}$~Mpc$)^3$ in 150~MHz (top) and 170~MHz (bottom) subbands ($B_\textrm{eff}=10$~MHz) on eight unique baseline lengths of HERA-19 at arbitrary LST.
+\caption{EoR signal and foreground delay power spectrum in units of K$^2 (h^{-1}$~Mpc$)^3$ in 150~MHz (top) and 170~MHz (bottom) subbands ($B_\textrm{eff}=10$~MHz) on eight unique baseline lengths of HERA-19 at arbitrary sky pointings.
 The length and orientation of the baseline vector corresponding to each panel is annotated on the top right corner.
@@
 The foregrounds obtained with achromatic, {\it Airy} and simulated chromatic antenna beams are shown in black, red and blue respectively.
-EoR detection sensitivity is highest for antenna beam with least chromaticity and vice versa.
-Even for the simulated chromatic antenna beam pattern, which has the highest chromaticity among the antenna beam models considered, foreground power will be lower than two independent EoR models by more than two orders of magnitude for $|k_\parallel| \gtrsim 0.2\,h$~Mpc$^{-1}$ on all HERA baselines.}
+EoR sensitivity is highest for antenna beam with least chromaticity and vice versa.
+Even for the simulated chromatic antenna beam pattern, which has the highest chromaticity among the antenna beam models considered, foreground power will be lower than signal power from the two independent EoR models by more than two orders of magnitude for $|k_\parallel| \gtrsim 0.2\,h$~Mpc$^{-1}$ on all HERA baselines.}
 \label{fig:subbands}
@@
 
-\subsection{Sensitivity on Baseline-RA Parameter Space}\label{sec:baseline-LST}
+\subsection{Sensitivity on Baseline-RA Parameter Space}\label{sec:baseline-RA}
 
@@
 \end{align}
-where, the first term inside the parenthesis denotes the horizon limit, the second relates to the resolution due to subband bandwidth, $B_\textrm{eff}$, and $\zeta$ denotes a buffer to ensure $k_\parallel^\textrm{FA}(|\boldsymbol{b}|)$ threshold ``avoids'' the main lobe of foreground power.
+where, the first term inside the parenthesis denotes the horizon limit, the second relates to the resolution due to subband bandwidth, $B_\textrm{eff}$, and $\zeta$ denotes a buffer to ensure $k_\parallel^\textrm{FA}(|\boldsymbol{b}|)$ threshold ``safely'' avoids the main lobe of foreground power.
 
@@
 First-generation EoR experiments such as the MWA, PAPER and LOFAR have made enormous progress in the field of 21~cm cosmology.
-However, they are currently limited by the systematics due to the extremely bright foregrounds and the instrument.
-Hence, characterizing the foregrounds and the instrument to a very high level of precision is critical for the success of next-generation EoR experiments.
+However, they are currently limited by the systematics due to extremely bright foregrounds and the instrument.
+Hence, characterizing these to a very high level of precision is critical for the success of next-generation EoR experiments.
 In this paper, we highlight the importance of a key systematic feature of the instrument -- the spectral structure of the antenna power pattern -- and its impact on EoR signal contamination, using HERA as an example.
@@
 Using a novel approach, we provide a formalism to set cosmologically-motivated constraints directly on the level of suppression required on these reflections in the instrument.
-Ongoing reflectometry studies clearly indicate HERA will exceed the cosmologically-motivated lower limits prescribed here.
+Ongoing reflectometry studies clearly indicate HERA will exceed the lower limits prescribed here.
 
-Taking into account the effects of these instrumental systematics, if data is not limited by thermal noise, we demonstrate that HERA will detect EoR with high significance with s simple spectral weighting even under a conservative analysis criterion which does not involve any {\it foreground removal} strategies.
+Taking into account the effects of these instrumental systematics, if data is not limited by thermal noise, we demonstrate that HERA will detect EoR with high significance with s simple spectral weighting even under a conservative analysis criterion which does not involve {\it foreground removal} strategies.
 All baselines of HERA-19 will not only detect but also help in filtering highly likely EoR models.

### 2016-03-06 ForegroundSimulations/ms.tex
Correct typos
From 3f81d66 (fgsim):
====================

In ms.tex,

(*) Correct typos

@@
 For reference, we use two models of EoR.
-In the first, simulations of the H{\sc i} signal were created using the publically available 21cmFAST\footnote{\url{http://homepage.sns.it/mesinger/DexM\_\_\_21cmFAST.html}} code described in \citet{mes11}.
+In the first, simulations of the H{\sc i} signal were created using the publicly available 21cmFAST\footnote{\url{http://homepage.sns.it/mesinger/DexM\_\_\_21cmFAST.html}} code described in \citet{mes11}.
 The code uses the excursion set formalism of \citet{fur04a} to generate ionization and 21cm brightness fields for numerous redshifts.

### 2016-03-11 ForegroundSimulations/ms.tex
Incorporate comments from Dave DeBoer
From 50bc153 (fgsim):
====================

In ms.tex,

(*) Incorporate comments from Dave DeBoer

@@
 
-When expressed in the coordinate system of power spectrum measurements described by the three-dimensional wavenumber ($k$), the foreground emission is restricted to a wedge-shaped region commonly referred to as the {\it foreground wedge} \citep{bow09,liu09,liu14a,liu14b,dat10,liu11,gho12,mor12,par12b,tro12,ved12,dil13,pob13,thy13,dil14}, whereas the EoR signal has spherical symmetry due to its isotropy which appears elongated along line of sight $k$ modes due to peculiar velocity effects when dominated by matter density perturbations during early stages of reionization.
+When expressed in the coordinate system of power spectrum measurements described by the three-dimensional wavenumber ($k$), the foreground emission is restricted to a wedge-shaped region commonly referred to as the {\it foreground wedge} \citep{bow09,liu09,liu14a,liu14b,dat10,liu11,gho12,mor12,par12b,tro12,ved12,dil13,pob13,thy13,dil14} bounded by the horizon limits \citep{par12b}, whereas the EoR signal has spherical symmetry due to its isotropy which appears elongated along line of sight $k$ modes due to peculiar velocity effects when dominated by matter density perturbations during early stages of reionization.
+The region of $k$-space excluding the {\it foreground wedge} is commonly referred to as the {\it EoR window} since it is expected to be relatively free of foreground contamination.
 
@@
 
-\citet{deb16} describe the HERA instrument in detail. Here, we provide a brief summary.
+\citet{deb16} describe the HERA instrument in detail. Here, we provide a brief summary of the telescope currently under construction on the South African SKA site.
 
@@
 
-In this study, we use the HERA-19 hexagonal array layout, a small subset of the planned layout.
+In this study, we use the HERA-19 hexagonal array layout, a small subset of the planned layout that are currently in use.
 Without loss of generality, the analysis and results in this paper will apply to the full proposed layout as well.
@@
 \end{align}
-where, $\Delta B$ is the bandwidth, $\lambda$ is the wavelength of the band center, $k_\textrm{B}$ is the Boltzmann constant, $f_{21}$ is the rest frame frequency of the 21~cm spin flip transition of H~{\sc i}, $z$ is the redshift, $D\equiv D(z)$ is the transverse comoving distance, $\Delta D$ is the comoving depth along the line of sight corresponding to $\Delta B$, and $h$, $H_0$ and $E(z)\equiv [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ are standard terms in cosmology, and following \citet{par14},
+where, $\Delta B$ is the bandwidth, $\lambda$ is the wavelength of the band center, $k_\textrm{B}$ is the Boltzmann constant, $\boldsymbol{k}_\perp$ and $k_\parallel$ are the transverse (on the sky) and line-of-sight (into the sky) wavenumbers respectively, $f_{21}$ is the rest frame frequency of the 21~cm spin flip transition of H~{\sc i}, $z$ is the redshift, $D\equiv D(z)$ is the transverse comoving distance, $\Delta D$ is the comoving depth along the line of sight corresponding to $\Delta B$, and $h$, $H_0$ and $E(z)\equiv [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ are standard terms in cosmology, and following \citet{par14},
 \begin{align}
-  \Omega\Delta B &= \iint \left|A(\hat{\boldsymbol{s}},f)\,W(f)\right|^2\,\dif\Omega\,\dif f.
+  \Omega\Delta B &= \iint \left|A(\hat{\boldsymbol{s}},f)\,W(f)\right|^2\,\dif\Omega\,\dif f,
 \end{align}
+which is related to the cosmic volume probed by the instrument.
 
@@
 For the calculations, one pair of arms was excited using a modal port.
-These models cover a frequency range of 100--200~MHz in intervals of 1~MHz.
-Refer to \citet{deb16} for a complete description of the dish model.
+These models cover a frequency range of 90--210~MHz in intervals of 1~MHz \citep{deb16}.
 
@@
 
-In a related series of papers, \citet{neb16} discuss the agreement of these simulated antenna beam patterns with actual measurements and \citet{ewa16} model the reflections and return loss expected in the proposed antenna-feed assembly.
+In a related series of papers, \citet{neb16} discuss the agreement of these simulated antenna beam patterns with actual measurements, \citet{ewa16} model the reflections and return loss expected in the proposed antenna-feed assembly, and \citet{pat16} present measurements quantifying the reflections.
 Our focus in this paper is to investigate chromaticity of antenna power patterns from the point of view of their impact on foreground contamination in delay power spectra.
@@
 However, in all four cases considered here, the worst case signal-noise ratio lies above unity in most of this parameter space.
-It demonstrates that HERA will detect the EoR signal with a very high signal-noise ratio on all baselines in a vast majority of the pointings.
+It demonstrates that HERA should detect the EoR signal with a very high signal-noise ratio on all baselines in a vast majority of the pointings.
 
@@
 
-Taking into account the effects of these instrumental systematics, if data is not limited by thermal noise, we demonstrate that HERA will detect EoR with high significance with s simple spectral weighting even under a conservative analysis criterion which does not involve {\it foreground removal} strategies.
+Taking into account the effects of these instrumental systematics, if data is not limited by thermal noise, we demonstrate that HERA should detect EoR with high significance with s simple spectral weighting even under a conservative analysis criterion which does not involve {\it foreground removal} strategies.
 All baselines of HERA-19 will not only detect but also help in filtering highly likely EoR models.

### 2016-03-12 ForegroundSimulations/ms.tex
Address Judd's comments, Sort reference order
From ea7bb98 (fgsim):
====================

In ms.tex,

(*) Incorporate comments from Judd
(*) Fix some math errors

In eor.bib,

(*) Sort Thyagarajan et al. (2015a,b)

@@
 \newcommand{\dif}{\mathrm{d}}
+\newcommand{\bibsortorder}[1]{}
 %% \renewcommand*{\thefootnote}{\fnsymbol{footnote}}
@@
 
-Unaccounted systematics from foregrounds and instruments prevent present day experiments from detecting redshifted 21~cm signal from the Epoch of Reionization (EoR).
+Unaccounted systematics from foregrounds and instruments prevent current experiments from detecting redshifted 21~cm signal from the Epoch of Reionization (EoR).
 In-depth understanding of these effects is critical for such experiments to succeed.
@@
 A primary source of this chromaticity is reflections in the antenna-feed assembly and between structures in neighboring antennas.
-Using precise foreground simulations taking wide-field effects into account, we provide a framework to set cosmologically-motivated upper limits on these reflections to prevent further EoR signal degradation.
+Using precise foreground simulations taking wide-field effects into account, we provide a framework to set cosmologically-motivated design specifications on these reflections to prevent further EoR signal degradation.
 We use the Hydrogen Epoch of Reionization Array (HERA) as an example.
-Using a simple and yet high dynamic range spectral weighting scheme, we demonstrate that EoR detection using HERA will not be impeded by such spectral systematics even in a conservative scenario that does not require removal of foregrounds.
+Using a simple and yet high dynamic range spectral weighting scheme, we demonstrate that EoR detection using HERA will not be impeded by such spectral systematics even in a conservative scenario that does not perform removal of foregrounds.
 We also show that all baselines in a 19-element HERA layout are capable of detecting EoR over a substantial observing window on the sky.
@@
 
-When expressed in the coordinate system of power spectrum measurements described by the three-dimensional wavenumber ($k$), the foreground emission is restricted to a wedge-shaped region commonly referred to as the {\it foreground wedge} \citep{bow09,liu09,liu14a,liu14b,dat10,liu11,gho12,mor12,par12b,tro12,ved12,dil13,pob13,thy13,dil14} bounded by the horizon limits \citep{par12b}, whereas the EoR signal has spherical symmetry due to its isotropy which appears elongated along line of sight $k$ modes due to peculiar velocity effects when dominated by matter density perturbations during early stages of reionization.
+When expressed in the coordinate system of power spectrum measurements described by the three-dimensional wavenumber ($k$), the foreground emission is restricted to a wedge-shaped region commonly referred to as the {\it foreground wedge} \citep{bow09,liu09,liu14a,liu14b,dat10,liu11,gho12,mor12,par12b,tro12,ved12,dil13,pob13,thy13,dil14} bounded by the horizon limits \citep{par12b}, whereas the EoR signal has spherical symmetry due to its isotropy which appears elongated along line-of-sight $k$-modes due to peculiar velocity effects when dominated by matter density perturbations during early stages of reionization.
 The region of $k$-space excluding the {\it foreground wedge} is commonly referred to as the {\it EoR window} since it is expected to be relatively free of foreground contamination.
@@
 \S\ref{sec:beam-chromaticity} investigates the effects of chromaticity of antenna beam on the resulting delay power spectrum and the cosmologically motivated constraints it places on reflections in the instrument.
-Lower limits on sensitivity of HERA under simple {\it foreground avoidance} criteria are demonstrated in \S\ref{sec:eor-sensitivity}.
+Foreground-limited sensitivity of HERA under simple {\it foreground avoidance} criteria are demonstrated in \S\ref{sec:eor-sensitivity}.
 Our findings are summarized in \S\ref{sec:summary}.
@@
 \end{align}
-where, $\Delta B$ is the bandwidth, $\lambda$ is the wavelength of the band center, $k_\textrm{B}$ is the Boltzmann constant, $\boldsymbol{k}_\perp$ and $k_\parallel$ are the transverse (on the sky) and line-of-sight (into the sky) wavenumbers respectively, $f_{21}$ is the rest frame frequency of the 21~cm spin flip transition of H~{\sc i}, $z$ is the redshift, $D\equiv D(z)$ is the transverse comoving distance, $\Delta D$ is the comoving depth along the line of sight corresponding to $\Delta B$, and $h$, $H_0$ and $E(z)\equiv [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ are standard terms in cosmology, and following \citet{par14},
+where, $\Delta B$ is the bandwidth, $\lambda$ is the wavelength of the band center, $k_\textrm{B}$ is the Boltzmann constant, $\boldsymbol{k}_\perp$ and $k_\parallel$ are the transverse (on the sky) and line-of-sight (into the sky) wavenumbers respectively, $f_{21}$ is the rest frame frequency of the 21~cm spin-flip transition of H~{\sc i}, $z$ is the redshift, $D\equiv D(z)$ is the transverse comoving distance, $\Delta D$ is the comoving depth along the line of sight corresponding to $\Delta B$, and $h$, $H_0$ and $E(z)\equiv [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ are standard terms in cosmology.
+Following \citet{par14},
 \begin{align}
@@
 which is related to the cosmic volume probed by the instrument.
-
 In this paper, we use $\Omega_\textrm{M}=0.27$, $\Omega_\Lambda=0.73$, $\Omega_\textrm{K}=1-\Omega_\textrm{M}-\Omega_\Lambda$, $H_0=100\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P_\textrm{d}(\boldsymbol{k}_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.
@@
 
-It was recently discovered that in wide-field measurements diffuse foreground emission from wide off-axis angles appear enhanced in the delay spectrum near the edges of the {\it foreground wedge} even on wide antenna spacings \citep{thy15a}.
+It was recently discovered that in wide-field measurements diffuse foreground emission from wide off-axis angles appears enhanced in the delay spectrum near the edges of the {\it foreground wedge} even on wide antenna spacings \citep{thy15a}.
 Called the {\it pitchfork} effect, this arises due to severe foreshortening of baseline vectors towards the horizon along joining the antenna pairs thereby enhancing their sensitivity to large scale structures in these directions.
@@
 
-For reference, we use two models of EoR.
+We use two models of EoR.
 In the first, simulations of the H{\sc i} signal were created using the publicly available 21cmFAST\footnote{\url{http://homepage.sns.it/mesinger/DexM\_\_\_21cmFAST.html}} code described in \citet{mes11}.
@@
 The model shown in this paper assumes the same fiducial values as in \citet{ewa16}: $T_\text{vir}^\text{min} = 2 \times 10^4$~K (virial temperature of minimum mass of dark matter halos that host ionizing sources), $\zeta = 20$ (ionization efficiency), and $R_\text{mfp}=15$~Mpc (mean free path of UV photons) which predicts the redshift of 50\% ionization (and hence a peak in the power spectrum signal) to be at $z=8.5$.
-The second EoR model is borrowed from the simulations described in detail in \citet{lid08}.
+The second EoR model is from the simulations described in detail in \citet{lid08}.
 Hereafter, we refer to these two as EoR models 1 and 2 respectively.
@@
 The equation for delay spectrum describes the mapping between sky location of a foreground object and delay.
-The chromatic nature (variation with frequency) of the antenna power pattern results in a convolution of the geometrical mapping with the delay response of spectral chromaticity of the power pattern.
+The chromatic nature (variation with frequency) of the antenna power pattern appears multiplicatively in the frequency axis and thus results in convolving its delay response with that of the foregrounds and the geometric phases measured by the baseline vector.
 We discuss the resulting spillover of foreground power beyond the horizon delay limits.
@@
 
-Since our aim in this paper is to quantify foreground contamination and EoR sensitivity without employing any sophisticated {\it foreground removal} techniques, we turn out attention to {\it foreground avoidance} strategy that employs spectral weighting technique.
+Since our aim in this paper is to quantify EoR-foreground power ratio without employing any sophisticated {\it foreground removal} techniques, we turn our attention to {\it foreground avoidance} strategy that employs spectral weighting technique.
 In such a scheme, specific choices for spectral weighting function, $W(f)$, have been found to be effective in reducing foreground contamination by many orders of magnitude \citep{thy13} and is regularly used in EoR data analysis \citep{par12a}.
@@
 
-This is an enormous gain in sidelobe characteristics for a negligible loss of sensitivity relative to a simple {\it Blackman-Harris} weighting.
-This will ensure that the contamination resulting from spillover of foregrounds along the line-of-sight $k$-modes are limited only by intrinsic spectral structures in the foregrounds and the beam patterns and not by sidelobes from spectral weighting.
+This is an enormous gain in sidelobe characteristics for a small loss of sensitivity relative to a simple {\it Blackman-Harris} weighting.
+This will ensure that the contamination resulting from spillover of foregrounds along the line-of-sight $k$-modes are limited only by intrinsic spectral structures in the foregrounds or beam patterns and not by sidelobes from spectral weighting.
 In this paper, we apply this modified spectral weighting function defined in equation~\ref{eqn:bhw2} whenever foregrounds are represented in the Fourier delay domain.
@@
 The brightening of foreground power near the horizon limits (vertical dotted lines) due to the {\it pitchfork} effect \citep{thy15a,thy15b} is prominently seen in all cases.
-A clear trend of broadening of spillover-wings outside the horizon limits is seen with increasing chromaticity as the beam is changed from the achromatic to the {\it Airy} to the chromatic simulated model.
+A clear broadening of spillover-wings outside the horizon limits is seen with increasing chromaticity as the beam is changed from the achromatic to the {\it Airy} to the chromatic simulated model.
 For instance, the spillover from foreground delay power spectrum obtained with chromatic beam pattern is restricted to $|k_\parallel| \lesssim 0.2\,h$~Mpc$^{-1}$, with the {\it Airy} pattern it is restricted to $|k_\parallel| \lesssim 0.15\,h$~Mpc$^{-1}$, while with the achromatic beam it is restricted to $|k_\parallel| \lesssim 0.12\,h$~Mpc$^{-1}$ even on longest baseline lengths.
-It is also noted that despite the extreme dynamic range of the employed spectral weighting function, the tail of the foreground spillover at $|k_\parallel| \gtrsim 0.2\,h$~Mpc$^{-1}$ with an {\it Airy} beam pattern is many orders of magnitude higher than that using an achromatic beam while that from the simulated chromatic beam is even higher than from an {\it Airy} pattern by a few orders of magnitude.
+It is also noted that despite the extreme dynamic range of the spectral weighting function employed, the tail of the foreground spillover at $|k_\parallel| \gtrsim 0.2\,h$~Mpc$^{-1}$ with an {\it Airy} beam pattern is many orders of magnitude higher than that using an achromatic beam while that from the simulated chromatic beam is even higher than from an {\it Airy} pattern by a few orders of magnitude.
 This signals that the foreground spillover shown are truly limited by intrinsic spectral features in the antenna beam patterns.
@@
 
-It is clearly demonstrated that higher the beam chromaticity, the farther the foreground contamination inherently extends along $k_\parallel$.
-Thus, the chromaticity of antenna beam needs to be carefully controlled in EoR experiments in order to not allow sensitive $k_\parallel$-modes to become inaccessible for EoR H{\sc i} signal detection.
+This clearly demonstrates that higher the beam chromaticity, the farther the foreground contamination inherently extends along $k_\parallel$.
+Thus, the chromaticity of antenna beam needs to be carefully controlled in EoR experiments in order to keep the foreground systematics sufficiently low.
 
-It must be emphasized that such a significant spillover is not bound by the horizon limits of the {\it foreground wedge} because this is caused by spectral structure in the antenna beam pattern which is independent of the position-dependent geometric delays.
+Such a significant spillover is not bound by the horizon limits of the {\it foreground wedge} because this is caused by spectral structure in the antenna beam pattern which is independent of the position-dependent geometric delays.
 As a result delay-based complex deconvolution techniques such as CLEAN \citep{tay99,par09,par12b} that rely on smoothness of foreground spectra and only spectral window shape will not have adequate information to accurately deconvolve intrinsic supra-horizon spillover arising from the chromaticity of the antenna beam.
-We leave delay power spectrum estimation using {\it foreground removal} strategy that accounts for direction-dependent and beam chromaticity-dependent effects to future work.
+While delay power spectrum estimation using {\it foreground removal} strategy that accounts for direction- and beam chromaticity-dependent effects is possible, we leave it for future work.
 
@@
 Reflection between structures and signal paths from different antennas also causes chromaticity in the antenna beam.
-In this section, we provide cosmologically motivated upper limits on instrument systematics caused by these two types of reflections.
+In this section, we provide cosmologically motivated design specifications on instrument systematics caused by these two types of reflections.
 
-The effect of reflections it to shift the measured foreground power to higher modes in $\tau$ (or equivalently in $k_\parallel$) and thus cause further contamination in these higher $k_\parallel$-modes which are considered sensitive for EoR H{\sc i} signal detection.
-Equivalently, these delay shifts introduce ripples in the spectrum.
-The net chromaticity in the measurements is the product of spectral structure arising out of the intrinsic nature of foreground emission, the baseline- and position-dependent frequency structure of the fringes, the spectral features in the antenna power pattern besides any other spectral structures in the instrument unaccounted for.
-Equivalently, in the Fourier domain these factors have a convolving effect.
-In order to isolate the requirements on beam chromaticity from other sources of chromaticity, we start with an antenna beam in which those spectral structures are absent but the intrinsic chromaticity of foregrounds and the baseline fringes are included.
+The effect of reflections it to shift the measured foreground power to higher modes in $\tau$ (or in $k_\parallel$) and thus cause further contamination in these higher $k_\parallel$-modes which are considered sensitive for EoR H{\sc i} signal detection.
+These delay shifts introduce ripples in the spectrum.
+The net chromaticity in the measurements is the product of spectral structure arising out of the intrinsic nature of foreground emission, the baseline- and position-dependent frequency structure of the geometric phases, the spectral features in the antenna power pattern besides any other spectral structures in the instrument unaccounted for.
+In the Fourier domain these factors have a convolving effect.
+In order to isolate the requirements on beam chromaticity from other sources of chromaticity, we start with an antenna beam in which those spectral structures are absent but the intrinsic chromaticity of foregrounds and the geometric phases of baselines are included.
 
@@
 \begin{align}\label{eqn:attenuation}
-  \Gamma_{k_\textrm{p}}(\tau) \geq \min_{|k_\parallel|>k_\textrm{p}}\left\{\frac{P_\textrm{FG}(k_\parallel - \frac{\dif k_\parallel}{\dif \tau}\,\tau)}{P_\textrm{H{\sc i}}(k_\parallel)}\right\}^{1/2},
+  \Gamma_{k_\textrm{p}}(\tau) \geq \max_{|k_\parallel|>k_\textrm{p}}\left\{\frac{P_\textrm{FG}(k_\parallel - \frac{\dif k_\parallel}{\dif \tau}\,\tau)}{P_\textrm{H{\sc i}}(k_\parallel)}\right\}^{1/2},
 \end{align}
-where, $P_\textrm{H{\sc i}}(k_\parallel)$ is the EoR H{\sc i} power spectrum for the chosen antenna spacing, $P_\textrm{FG}(k_\parallel)$ is the foreground delay power spectrum obtained with the spectral weighting function applied over the full band of the three uniquely oriented 14.6~m antenna spacings further averaged over a 0--12 hr local sidereal time (LST) range and over both positive and negative $k_\parallel$-modes, $\tau$ is the delay caused by reflections, and $\dif k_\parallel/\dif \tau$ is the {\it jacobian} in the transformation of $\tau$ to $k_\parallel$ (see equation~\ref{eqn:kprll-delay}).
-Equivalently, $\Gamma_{k_\textrm{p}}(\tau)$ is determined by the requirement that the reflected foreground power obtained by shifting in delay is below the EoR H{\sc i} signal power in line-of-sight spatial scales of interest given by $|k_\parallel|>k_\textrm{p}$.
-For this analysis constraining reflections, we use EoR model 1 at 150~MHz ($z\approx 8.47$).
+where, $P_\textrm{H{\sc i}}(k_\parallel)$ is the EoR H{\sc i} power spectrum for the chosen antenna spacing, $P_\textrm{FG}(k_\parallel)$ is the foreground delay power spectrum obtained with the spectral weighting function applied over the full-band of the three uniquely oriented 14.6~m antenna spacings further averaged over a 0--12 hr local sidereal time (LST) range and over both positive and negative $k_\parallel$-modes, $\tau$ is the delay caused by reflections, and $\dif k_\parallel/\dif \tau$ is the {\it jacobian} in the transformation of $\tau$ to $k_\parallel$ (see equation~\ref{eqn:kprll-delay}).
+Thus, $\Gamma_{k_\textrm{p}}(\tau)$ is determined by the requirement that the reflected foreground power obtained by shifting in delay is below the EoR H{\sc i} signal power in line-of-sight spatial scales of interest given by $|k_\parallel|>k_\textrm{p}$.
+
+Both EoR models were used separately in this analysis to reduce the dependence of design specifications for reflections on any single model.
+However, we found similar results except for minor differences caused by small amplitude differences between the two EoR models.
+Hence, we only use results from using EoR model 1 at 150~MHz ($z\approx 8.47$).
+
+\subsubsection{Reflections in Dish-Feed Assembly}\label{sec:dish-feed-reflections}
 
@@
 These curves set an upper limit for the reflected foreground power to lie below the EoR H{\sc i} signal power as a function of delays caused by dish-feed reflections.
-In other words, it implies that if reflections in the dish-feed assembly are attenuated to levels that lie in the regions below the different shaded regions, such spectral systematics in the instrument will not hinder detection of EoR in those corresponding $k_\parallel$ modes of interest.
+It implies that if reflections in the dish-feed assembly are attenuated to levels that lie in the regions below the different shaded regions, such spectral systematics in the instrument will not hinder detection of EoR in those corresponding $k_\parallel$-modes of interest.
 
@@
 \includegraphics[width=\linewidth]{spec_on_achrmbeam_foreground_reflected_power_21cmfast_14.6m_150.0_MHz_subband_v2.eps}
-\caption{Lower limit on attenuation of reflected foreground power (in dB) from dish-feed reflections required to keep the reflected foreground power below EoR H{\sc i} signal power for all $k_\parallel$-modes greater than $0.1\,h$~Mpc$^{-1}$ (solid), $0.15\,h$~Mpc$^{-1}$ (dashed) and $0.2\,h$~Mpc$^{-1}$ (dotted).
+\caption{Minimum required attenuation (in dB) for internal dish-feed reflections required to keep the reflected foreground power below EoR H{\sc i} signal power for all $k_\parallel$-modes greater than $0.1\,h$~Mpc$^{-1}$ (solid), $0.15\,h$~Mpc$^{-1}$ (dashed) and $0.2\,h$~Mpc$^{-1}$ (dotted).
 This is obtained on 14.6~m antenna spacing for EoR model 1 at 150~MHz ($z\approx 8.47$) and foreground power obtained with an achromatic antenna beam model.
@@
 
+\subsubsection{Antenna-to-Antenna Reflections}\label{sec:antenna-antenna-reflections}
+
 Similarly, for reflections arising out of structures and interfaces across different antennas, we use $P_\textrm{FG}(k_\parallel)$ obtained with the simulated chromatic and {\it Airy} antenna beams on 14.6~m baselines.
@@
 \includegraphics[width=\linewidth]{spec_on_foreground_reflected_power_21cmfast_14.6m_150.0_MHz_subband_v2.eps}
-\caption{Lower limit on attenuation of reflected foreground power (in dB) from antenna-to-antenna reflections required to keep the reflected foreground power below EoR H{\sc i} signal power for all $k_\parallel$-modes greater than $0.1\,h$~Mpc$^{-1}$ (left), $0.15\,h$~Mpc$^{-1}$ (middle) and $0.2\,h$~Mpc$^{-1}$ (right).
+\caption{Minimum required attenuation (in dB) for antenna-to-antenna reflections to keep reflected foreground power below EoR H{\sc i} signal power for all $k_\parallel$-modes greater than $0.1\,h$~Mpc$^{-1}$ (left), $0.15\,h$~Mpc$^{-1}$ (middle) and $0.2\,h$~Mpc$^{-1}$ (right).
 This is obtained on 14.6~m antenna spacing for EoR model 1 at 150~MHz ($z\approx 8.47$) and foreground power obtained with an {\it Airy} (dashed) and simulated chromatic (solid) antenna beam models.
@@
 
-It may be noted here that designing a dish whose antenna beam closely resembles a nominal {\it Airy} pattern will have a significantly higher tolerance for allowing antenna-to-antenna reflections and yet remain very effective for EoR signal detection.
-The HERA collaboration constantly pursues improvement of its dish design to keep minimize limitations from such chromatic systematics.
+We note here that designing a dish whose antenna beam closely resembles a nominal {\it Airy} pattern will have a significantly higher tolerance for allowing antenna-to-antenna reflections and yet remain very effective for EoR signal detection.
+The HERA collaboration constantly pursues improvement of its dish design to minimize limitations from such chromatic systematics.
 
-\section{EoR Sensitivity}\label{sec:eor-sensitivity}
+In both types of reflections discussed, similar design limits on reflections on various antenna spacings were also studied.
+With increase in baseline length, the amplitude of foreground power decreases but the {\it foreground window} also widens.
+This means the amplitude of reflections required to be suppressed is lower but there is lesser room along delay axis before the reflected foreground modes shift to and contaminate the $k_\parallel$-modes of interest.
+As a result, the elbow-shaped design constraints shift upward and leftward.
+For instance, in the presence of dish-feed reflections, it will still be feasible to probe $k_\parallel > 0.15\,h$~Mpc$^{-1}$ with the 58.4~m baselines but not other larger scales.
 
-Here our goal is to estimate sensitivity for EoR detection in the presence of antenna beam chromaticity, using HERA as an example.
-As stated earlier, we estimate sensitivity of HERA in the most conservative scenario where we consider only {\it foreground avoidance} under simple spectral weighting scheme.
+\section{Foreground-limited EoR Sensitivity}\label{sec:eor-sensitivity}
+
+Here our goal is to estimate the foreground-limited sensitivity (ratio of EoR signal power to foreground power) in the presence of antenna beam chromaticity, using HERA as an example.
+As stated earlier, we estimate this ratio for HERA in the most conservative scenario where we consider only {\it foreground avoidance} under simple spectral weighting scheme.
 We emphasize that other strategies involving {\it foreground removal} and inverse covariance-based weighting schemes will produce more optimal results than presented here.
@@
 These subbands with $B_\textrm{eff}=10$~MHz are defined by spectral weights obtained by convolution of {\it Blackman-Harris} window with itself.
-These subbands are centered at 150~MHz and 170~MHz to estimate sensitivity at $z \approx 8.47$ and $z \approx 7.36$ respectively.
+These subbands are centered at 150~MHz and 170~MHz to estimate EoR-foreground power ratio at $z \approx 8.47$ and $z \approx 7.36$ respectively.
 We use both EoR models 1 and 2 to reduce the dependence of this analysis on any single EoR model.
 
-\subsection{Sensitivity on Baseline-$k_\parallel$ Parameter Space}\label{sec:baseline-kprll}
+\subsection{Dependence on Baseline-$k_\parallel$ Parameter Space}\label{sec:baseline-kprll}
 
-We present the sensitivity of HERA against foregrounds obtained with three antenna beams of different chromaticities in two-dimensional parameter space of baseline lengths (transverse spatial scales) and $k_\parallel$ (line-of-sight spatial scales).
+We estimate the ratio of EoR signal and foreground powers for HERA, where the latter is obtained with three antenna beams of different chromaticities.
 Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-150-subband} and \ref{fig:asm-dps-beam-chromaticity-baselines-170-subband} show the EoR signal and foreground power in 150~MHz and 170~MHz subbands respectively.
@@
 The foregrounds obtained with achromatic, {\it Airy} and simulated chromatic antenna beams are shown in black, red and blue respectively.
-EoR sensitivity is highest for antenna beam with least chromaticity and vice versa.
+EoR-foreground power ratio is highest for antenna beam with least chromaticity and vice versa.
 Even for the simulated chromatic antenna beam pattern, which has the highest chromaticity among the antenna beam models considered, foreground power will be lower than signal power from the two independent EoR models by more than two orders of magnitude for $|k_\parallel| \gtrsim 0.2\,h$~Mpc$^{-1}$ on all HERA baselines.}
@@
 Due to narrower subbands, the resolution of the foreground delay spectrum is coarser and the central region of foreground contamination extends to $|k_\parallel| \lesssim 0.2\,h$~Mpc$^{-1}$.
-The coarsening of delay resolution significantly absorbs the distinct differences caused by beams of different chromaticities as seen in the full band foreground delay spectra outside the {\it foreground wedge} in Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines}.
-In other words, the foreground spillover wings that extend beyond the horizon even in the case of full-band simulated chromatic beam are on spectral scales larger than the 10~MHz effective bandwidth of the subbands.
+The coarsening of delay resolution significantly absorbs the distinct differences caused by beams of different chromaticities as seen in the full-band foreground delay spectra outside the {\it foreground wedge} in Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines}.
+This means the foreground spillover wings that extend beyond the horizon even in the case of simulated chromatic beam are on spectral scales larger than the 10~MHz effective bandwidth of the subbands.
 Hence, this results in an EoR signal-foreground crossover at $|k_\parallel| \gtrsim 0.2\,h$~Mpc$^{-1}$ independent of different antenna beam chromaticities used in this analysis.
 
-From Fig.~\ref{fig:subbands}, it is clearly demonstrated that HERA has significant sensitivity on all baselines in both subbands to detect EoR by more than two orders of magnitude above foreground contamination obtained with any level of antenna beam chromaticity.
-While this clearly includes foregrounds obtained with the currently simulated chromatic beam pattern, the sensitivity against foregrounds obtained with achromatic and {\it Airy} antenna power patterns are even higher by many orders of magnitude.
+From Fig.~\ref{fig:subbands}, it is clearly demonstrated that across all baselines and subbands, HERA should detect EoR by more than two orders of magnitude above foreground contamination obtained with any level of antenna beam chromaticity.
+% While this clearly includes foregrounds obtained with the currently simulated chromatic beam pattern, the sensitivity against foregrounds obtained with achromatic and {\it Airy} antenna power patterns are even higher by many orders of magnitude.
 This only further reiterates that efforts to keep lowering systematic spectral effects in the antenna beam must be undertaken continuously, as is the case with HERA.
 
-\subsection{Sensitivity on Baseline-RA Parameter Space}\label{sec:baseline-RA}
+\subsection{Dependence on Baseline-RA Parameter Space}\label{sec:baseline-RA}
 
-We investigate the EoR sensitivity in two dimensional parameter space formed by baselines and pointings in Right Ascension (RA$\equiv\alpha$) to highlight capabilities of HERA and provide clues for the best observing window.
+We investigate the EoR-foreground power ratio in two dimensional parameter space formed by baselines and pointings in Right Ascension (RA$\equiv\alpha$) to highlight capabilities of HERA and provide clues for the best observing window.
 
-In this section, we assume that the H{\sc i} power spectrum is isotropic (no sample variance) and hence, independent of $\alpha$.
+Due to the assumed isotropy of the redshifted H{\sc i} power spectrum, it is independent of $\alpha$.
 However, it is dependent on the center of the subband, $f_0$, where $f_0 = f_{21}/(1+z)$.
@@
 \end{align}
-where, the first term inside the parenthesis denotes the horizon limit, the second relates to the resolution due to subband bandwidth, $B_\textrm{eff}$, and $\zeta$ denotes a buffer to ensure $k_\parallel^\textrm{FA}(|\boldsymbol{b}|)$ threshold ``safely'' avoids the main lobe of foreground power.
+where, the first term inside the parenthesis denotes the horizon limit, the second relates to the resolution due to subband bandwidth, $B_\textrm{eff}$, and $\zeta$ denotes a buffer to ensure the $k_\parallel^\textrm{FA}(|\boldsymbol{b}|)$ threshold ``safely'' avoids the main lobe of foreground power.
 
-We estimate the worst case sensitivity in the $\boldsymbol{b}$--$\alpha$ parameter space as:
+We estimate the worst case EoR-foreground power ratio in the $\boldsymbol{b}$--$\alpha$ parameter space as:
 \begin{align}
-  \rho(\boldsymbol{b},f_0,\alpha) &= \min_{|k_\parallel|>k_\parallel^\textrm{FA}(|\boldsymbol{b}|)}\left\{\frac{P_\textrm{H{\sc i}}(|\boldsymbol{b}|,k_\parallel,f_0)}{P_\textrm{FG}(\boldsymbol{b},k_\parallel,f_0,\alpha)}\right\}
+  \rho(\boldsymbol{b},f_0,\alpha) &= \min_{|k_\parallel|>k_\parallel^\textrm{FA}(|\boldsymbol{b}|)}\left\{\frac{P_\textrm{H{\sc i}}(|\boldsymbol{b}|,k_\parallel,f_0)}{P_\textrm{FG}(\boldsymbol{b},k_\parallel,f_0,\alpha)}\right\}.
 \end{align}
+This denotes the minimum EoR-foreground power ratio in $k_\parallel$-modes of interest for {\it foreground avoidance}, $|k_\parallel| > k_\parallel^\textrm{FA}(\boldsymbol{b})$, for each baseline vector ($\boldsymbol{b}$), subband ($f_0$), and sky pointing ($\alpha$).
+
 We consider the foreground power spectrum obtained with the simulated chromatic antenna beam, and EoR models 1 and 2, in each of the 150~MHz and 170~MHz subbands.
-Fig.~\ref{fig:eor-fg-ratios} shows the worst case sensitivity, $\rho(\boldsymbol{b},f_0,\alpha)$, for all 30 unique HERA baselines over 24 hours of $\alpha$ for the two EoR models and two subbands used in this study.
+Fig.~\ref{fig:eor-fg-ratios} shows $\rho(\boldsymbol{b},f_0,\alpha)$ for all 30 unique HERA baselines over 24 hours of $\alpha$ for the two EoR models and two subbands used in this study.
 
@@
 \subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_170.0_MHz_subband.eps}}
-\caption{Lower limits on EoR sensitivity, $\rho(\boldsymbol{b},f_0,\alpha)$, in {\it foreground avoidance} modes for different HERA-19 baselines as a function of RA ($\alpha$) of pointing on the sky.
+\caption{Worst case EoR-foreground power ratio, $\rho(\boldsymbol{b},f_0,\alpha)$, in {\it foreground avoidance} modes for different HERA-19 baselines as a function of RA ($\alpha$) of pointing on the sky.
 Each panel corresponds to the EoR model and subband indicated.
@@
 The color scale is logarithmic.
-Even with worst-case sensitivity, clearly HERA will be able detect EoR drawn from independent models on all baselines for a large fraction of a full 24~hour sky transit cycle.
-The sensitivity is seen to increase with increasing baseline length.
+Even in the worst case, HERA will be able detect EoR drawn from independent models on all baselines for a large fraction of a full 24~hour sky transit cycle.
+$\rho(\boldsymbol{b},f_0,\alpha)$ is seen to increase with increasing baseline length.
 This is because the loss in sensitivity to diffuse foreground power with increase in antenna spacings is faster than in the case of the EoR signal.}
@@
 
-In general, sensitivity increases with longer baselines.
+For the baselines considered, $\rho(\boldsymbol{b},f_0,\alpha)$ increases with longer baselines.
 We attribute this to the much steeper dependence of foreground emission on baseline length than that of EoR H{\sc i} power.
@@
 
-However, in all four cases considered here, the worst case signal-noise ratio lies above unity in most of this parameter space.
-It demonstrates that HERA should detect the EoR signal with a very high signal-noise ratio on all baselines in a vast majority of the pointings.
+However, in all four cases considered here, except when the Galactic center appears overhead in the RA range roughly in the range 16-19 hr, the worst case signal-foreground ratio lies above unity in most of this parameter space.
+It demonstrates that HERA should detect the EoR signal with a very high signal-foreground ratio on all baselines in a vast majority of the pointings.
 
 We reiterate that these estimates are obtained in a conservative scenario wherein only simple spectral weighting technique in the {\it foreground avoidance} limit is used, without any foreground removal or sophisticated weighting strategies using inverse-covariance.
-Further, these estimates represent worst-case lower limits demonstrating that HERA-19 and its successors will be extremely sensitive for EoR experiments and will benefit even further with more optimal foreground suppression strategies.
+Further, these estimates represent worst-case limits demonstrating that HERA-19 and its successors will be extremely sensitive for EoR experiments and will benefit even further with more optimal foreground suppression strategies.
 
@@
 We note that the inevitable reflections in the antenna-feed assembly and between reflecting structures across multiple antennas are also significant factors that contaminate the cosmological signal in high $k_\parallel$-modes inside the {\it EoR window}.
-Using a novel approach, we provide a formalism to set cosmologically-motivated constraints directly on the level of suppression required on these reflections in the instrument.
-Ongoing reflectometry studies clearly indicate HERA will exceed the lower limits prescribed here.
+Using a novel approach, we provide a formalism to set cosmologically-motivated design requirements directly on the level of suppression required on these reflections in the instrument.
+Ongoing reflectometry studies clearly indicate HERA will comfortably achieve the design limits prescribed here.
 
-Taking into account the effects of these instrumental systematics, if data is not limited by thermal noise, we demonstrate that HERA should detect EoR with high significance with s simple spectral weighting even under a conservative analysis criterion which does not involve {\it foreground removal} strategies.
+Taking into account the effects of these instrumental systematics, if data is not limited by thermal noise, we demonstrate that HERA should detect EoR with high significance with a simple spectral weighting even under a conservative analysis criterion which does not involve {\it foreground removal} strategies.
 All baselines of HERA-19 will not only detect but also help in filtering highly likely EoR models.

### 2016-03-15 ForegroundSimulations/ms.tex
Replace use of "sensitivity" with "dynamic range"
From 10a4726 (fgsim):
====================

In ms.tex,

(*) Replace usage of "sensitivity" with "dynamic range" throughout

@@
 \S\ref{sec:beam-chromaticity} investigates the effects of chromaticity of antenna beam on the resulting delay power spectrum and the cosmologically motivated constraints it places on reflections in the instrument.
-Foreground-limited sensitivity of HERA under simple {\it foreground avoidance} criteria are demonstrated in \S\ref{sec:eor-sensitivity}.
+EoR-foreground dynamic range of HERA under simple {\it foreground avoidance} criteria are demonstrated in \S\ref{sec:eor-sensitivity}.
 Our findings are summarized in \S\ref{sec:summary}.
@@
 
-\section{Foreground-limited EoR Sensitivity}\label{sec:eor-sensitivity}
+\section{EoR-Foreground Dynamic Range}\label{sec:eor-sensitivity}
 
-Here our goal is to estimate the foreground-limited sensitivity (ratio of EoR signal power to foreground power) in the presence of antenna beam chromaticity, using HERA as an example.
+Here our goal is to estimate the EoR-foreground dynamic range (ratio of EoR signal power to foreground power) in the presence of antenna beam chromaticity, using HERA as an example.
 As stated earlier, we estimate this ratio for HERA in the most conservative scenario where we consider only {\it foreground avoidance} under simple spectral weighting scheme.
@@
 These subbands with $B_\textrm{eff}=10$~MHz are defined by spectral weights obtained by convolution of {\it Blackman-Harris} window with itself.
-These subbands are centered at 150~MHz and 170~MHz to estimate EoR-foreground power ratio at $z \approx 8.47$ and $z \approx 7.36$ respectively.
+These subbands are centered at 150~MHz and 170~MHz to estimate EoR-foreground dynamic range at $z \approx 8.47$ and $z \approx 7.36$ respectively.
 We use both EoR models 1 and 2 to reduce the dependence of this analysis on any single EoR model.
@@
 The foregrounds obtained with achromatic, {\it Airy} and simulated chromatic antenna beams are shown in black, red and blue respectively.
-EoR-foreground power ratio is highest for antenna beam with least chromaticity and vice versa.
+EoR-foreground dynamic range is highest for antenna beam with least chromaticity and vice versa.
 Even for the simulated chromatic antenna beam pattern, which has the highest chromaticity among the antenna beam models considered, foreground power will be lower than signal power from the two independent EoR models by more than two orders of magnitude for $|k_\parallel| \gtrsim 0.2\,h$~Mpc$^{-1}$ on all HERA baselines.}
@@
 
-We investigate the EoR-foreground power ratio in two dimensional parameter space formed by baselines and pointings in Right Ascension (RA$\equiv\alpha$) to highlight capabilities of HERA and provide clues for the best observing window.
+We investigate the EoR-foreground dynamic range in two dimensional parameter space formed by baselines and pointings in Right Ascension (RA$\equiv\alpha$) to highlight capabilities of HERA and provide clues for the best observing window.
 
@@
 
-We estimate the worst case EoR-foreground power ratio in the $\boldsymbol{b}$--$\alpha$ parameter space as:
+We estimate the worst case EoR-foreground dynamic range in the $\boldsymbol{b}$--$\alpha$ parameter space as:
 \begin{align}
@@
 \end{align}
-This denotes the minimum EoR-foreground power ratio in $k_\parallel$-modes of interest for {\it foreground avoidance}, $|k_\parallel| > k_\parallel^\textrm{FA}(\boldsymbol{b})$, for each baseline vector ($\boldsymbol{b}$), subband ($f_0$), and sky pointing ($\alpha$).
+This denotes the minimum EoR-foreground dynamic range in $k_\parallel$-modes of interest for {\it foreground avoidance}, $|k_\parallel| > k_\parallel^\textrm{FA}(\boldsymbol{b})$, for each baseline vector ($\boldsymbol{b}$), subband ($f_0$), and sky pointing ($\alpha$).
 
@@
 \subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_170.0_MHz_subband.eps}}
-\caption{Worst case EoR-foreground power ratio, $\rho(\boldsymbol{b},f_0,\alpha)$, in {\it foreground avoidance} modes for different HERA-19 baselines as a function of RA ($\alpha$) of pointing on the sky.
+\caption{Worst case EoR-foreground dynamic range, $\rho(\boldsymbol{b},f_0,\alpha)$, in {\it foreground avoidance} modes for different HERA-19 baselines as a function of RA ($\alpha$) of pointing on the sky.
 Each panel corresponds to the EoR model and subband indicated.

### 2016-03-15 ForegroundSimulations/ms.tex
Minor adjustment in section 5.2.1
From 1caedff (fgsim):
====================

In ms.tex,

(*) Minor adjustment in section 5.2.1

@@
 Fig.~\ref{fig:fg-reflections-achrmbeam} shows $\Gamma_{k_\textrm{p}}(\tau)$ (in dB) for $k_\textrm{p}$ chosen to be 0.1~$h$~Mpc$^{-1}$ (solid), 0.15~$h$~Mpc$^{-1}$ (dashed), and 0.2~$h$~Mpc$^{-1}$ (dotted).
-These curves set an upper limit for the reflected foreground power to lie below the EoR H{\sc i} signal power as a function of delays caused by dish-feed reflections.
-It implies that if reflections in the dish-feed assembly are attenuated to levels that lie in the regions below the different shaded regions, such spectral systematics in the instrument will not hinder detection of EoR in those corresponding $k_\parallel$-modes of interest.
+These curves set an upper limit for the reflected foreground power to lie below the EoR H{\sc i} signal power as a function of delays.
+These reflections are primarily caused in the dish-feed assembly and to some extent in other subsystems not accounted for.
+It implies that if these reflections are attenuated to levels that lie in the regions below the different shaded regions, such spectral systematics in the instrument will not hinder detection of EoR in those corresponding $k_\parallel$-modes of interest.
 
@@
 For instance, the attenuation required is $\gtrsim 54$~dB at $\sim 200$~ns for $k_\textrm{p}=0.1\,h$~Mpc$^{-1}$, $\gtrsim 56$~dB at $\sim 300$~ns for $k_\textrm{p}=0.15\,h$~Mpc$^{-1}$ and $\gtrsim 58$~dB at $\sim 400$~ns for $k_\textrm{p}=0.2\,h$~Mpc$^{-1}$.
-Measurements by \citet{pat16} for HERA dish-feed assembly show that the return losses lie well within the regions excluded by the shaded regions thus implying that the attenuation is well above the lower limit and hence will not prevent EoR detection.
+Measurements by \citet{pat16} show that the return losses for HERA lie well within the regions excluded by the shaded regions thus implying that the attenuation is well above the lower limit and hence will not prevent EoR detection.
 

### 2016-03-15 ForegroundSimulations/ms.tex
Trim text in Abstract and Introduction
From cbfc31c (fgsim):
====================

In ms.tex,

(*) Trim text in Abstract and Introduction

@@
 Unaccounted systematics from foregrounds and instruments prevent current experiments from detecting redshifted 21~cm signal from the Epoch of Reionization (EoR).
-In-depth understanding of these effects is critical for such experiments to succeed.
 We identify spectral structures (chromaticity) in the antenna power pattern as one such systematic that significantly affects all EoR measurements.
@@
 
-The period in the history of the Universe characterized by the transition of neutral hydrogen in the intergalactic medium (IGM) to a fully ionized state due to the formation of radiating objects such as the first stars and galaxies is referred to as the Epoch of Reionization (EoR).
+% The period in the history of the Universe characterized by the transition of neutral hydrogen in the intergalactic medium (IGM) to a fully ionized state due to the formation of radiating objects such as the first stars and galaxies is referred to as the Epoch of Reionization (EoR).
 This is an important period of nonlinear growth of matter density perturbations and astrophysical evolution leading to the large scale structure observed currently in the Universe.
@@
 
+The Epoch of Reionization (EoR) is an important period of nonlinear growth of matter density perturbations and astrophysical evolution leading to the large scale structure observed currently in the Universe.
 The redshifted neutral hydrogen from the IGM in this epoch has been identified to be one of the most promising and direct probes of the EoR \citep{sun72,sco90,mad97,toz00,ili02}.
-Numerous experiments using low frequency radio telescopes targeting the redshifted 21~cm line from the spin-flip transition of H{\sc i} have become operational such as the Murchison Widefield Array \citep[MWA;][]{lon09,bow13,tin13}, the Donald~C.~Backer Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, the Low Frequency Array \citep[LOFAR;][]{van13} and the Giant Metrewave Radio Telescope EoR experiment \citep[GMRT;][]{pac13}.
+
+Numerous experiments using low frequency radio telescopes targeting the redshifted 21~cm line from the spin-flip transition of H{\sc i} in this epoch have become operational such as the Murchison Widefield Array \citep[MWA;][]{lon09,bow13,tin13}, the Donald~C.~Backer Precision Array for Probing the Epoch of Reionization \citep[PAPER;][]{par10}, the Low Frequency Array \citep[LOFAR;][]{van13} and the Giant Metrewave Radio Telescope EoR experiment \citep[GMRT;][]{pac13}.
 Many of these instruments have sufficient sensitivity for a statistical detection of the EoR signal by estimating the spatial power spectrum of the redshifted H{\sc i} spin temperature fluctuations \citep{bea13,thy13}.
@@
 The most significant challenge to low frequency EoR observations arises from the extremely bright Galactic and extragalactic foreground synchrotron emission which are $\sim 10^4$ times stronger than the desired EoR signal \citep{dim02,ali08,ber09,ber10,gho12}.
-All the current and future instruments rely on the inherent differences in spatial isotropy and spectral smoothness between the EoR signal and the foregrounds to extract the EoR power spectrum \citep[see, e.g.,][]{fur04b,mor04,zal04,san05,fur06,mcq06,mor06,wan06,gle08}.
+However, there are inherent differences in spatial isotropy and spectral smoothness between the EoR signal and the foregrounds \citep[see, e.g.,][]{fur04b,mor04,zal04,san05,fur06,mcq06,mor06,wan06,gle08}.
+% All the current and future instruments rely on the inherent differences in spatial isotropy and spectral smoothness between the EoR signal and the foregrounds to extract the EoR power spectrum \citep[see, e.g.,][]{fur04b,mor04,zal04,san05,fur06,mcq06,mor06,wan06,gle08}.
 
-When expressed in the coordinate system of power spectrum measurements described by the three-dimensional wavenumber ($k$), the foreground emission is restricted to a wedge-shaped region commonly referred to as the {\it foreground wedge} \citep{bow09,liu09,liu14a,liu14b,dat10,liu11,gho12,mor12,par12b,tro12,ved12,dil13,pob13,thy13,dil14} bounded by the horizon limits \citep{par12b}, whereas the EoR signal has spherical symmetry due to its isotropy which appears elongated along line-of-sight $k$-modes due to peculiar velocity effects when dominated by matter density perturbations during early stages of reionization.
+When expressed in the coordinate system of power spectrum measurements described by the three-dimensional wavenumber ($k$), the foreground emission is restricted to a wedge-shaped region commonly referred to as the {\it foreground wedge} \citep{bow09,liu09,liu14a,liu14b,dat10,liu11,gho12,mor12,par12b,tro12,ved12,dil13,pob13,thy13,dil14} bounded by the horizon limits \citep{par12b}, whereas the EoR signal has spherical symmetry due to its isotropy.
+% which appears elongated along line-of-sight $k$-modes due to peculiar velocity effects when dominated by matter density perturbations during early stages of reionization.
 The region of $k$-space excluding the {\it foreground wedge} is commonly referred to as the {\it EoR window} since it is expected to be relatively free of foreground contamination.
 
-However, despite attempts to exploit this knowledge about differences in spectral and spatial symmetry in lengthy observations, analysis from the first-generation experiments has at best only led to weak constraints on reionization models \citep{ali15,dil15,pob15}.
+Despite attempts to exploit this knowledge about differences in spectral and spatial symmetry, first-generation experiments have at best only led to weak constraints on reionization models \citep{ali15,dil15,pob15}.
 This is because their sensitivity is primarily limited by instrumental and foreground systematics.
 The extreme dynamic range required to suppress foreground and instrument systematics demands high precision modeling of foregrounds as observed by modern wide-field instruments.
-One such study was undertaken by \citet{thy15a,thy15b}.
+
+% One such study was undertaken by \citet{thy15a,thy15b}.
 Their studies of effects of wide-field measurements of EoR power spectra have demonstrated the {\it pitchfork} effect wherein foreshortening of baselines causes a prominent enhancement of foreground power near the horizon limits of the {\it foreground wedge} as well as in the contamination beyond.
@@
 
-In this paper, we explore yet another phenomenon that inherently extends foreground power beyond the {\it wedge}, namely, that arising from the chromaticity of the antenna power pattern.
+In this paper, we explore a phenomenon that inherently extends foreground power beyond the {\it wedge}, namely, that arising from the chromaticity of the antenna power pattern.
 While highlighting the importance of such instrumental systematics on future EoR experiments, we demonstrate that the current HERA instrument design will exceed these specifications to detect the EoR signal with high significance.
-This will hold when data is limited by foregrounds and systematics even in the most conservative scenario which involves neither foreground subtraction nor optimal analysis techniques but only relies on a simple spectral weighting scheme.
+This will hold true when data is limited by foregrounds and systematics even in the most conservative scenario which involves neither foreground subtraction nor optimal analysis techniques but only relies on a simple spectral weighting scheme.
 
 This paper is organized as follows.
-\S\ref{sec:HERA} introduces the HERA instrument.
-A brief summary of the delay spectrum technique used extensively in this analysis and the recently confirmed {\it pitchfork} effect are presented in \S\ref{sec:delay-spectrum}.
+\S\ref{sec:HERA} describes the HERA instrument.
+A brief summary of the delay spectrum technique used extensively in this analysis and the recently confirmed wide-field instrument effects are presented in \S\ref{sec:delay-spectrum}.
 \S\ref{sec:sim} describes foreground simulations including antenna beam pattern, all-sky foreground models and two independent EoR models.

### 2016-03-15 ForegroundSimulations/ms.tex
Trim text throughout
From 3b0f6bb (fgsim):
====================

In ms.tex,

(*) Trim text throughout

@@
 \end{align}
-where, $\Delta B$ is the bandwidth, $\lambda$ is the wavelength of the band center, $k_\textrm{B}$ is the Boltzmann constant, $\boldsymbol{k}_\perp$ and $k_\parallel$ are the transverse (on the sky) and line-of-sight (into the sky) wavenumbers respectively, $f_{21}$ is the rest frame frequency of the 21~cm spin-flip transition of H~{\sc i}, $z$ is the redshift, $D\equiv D(z)$ is the transverse comoving distance, $\Delta D$ is the comoving depth along the line of sight corresponding to $\Delta B$, and $h$, $H_0$ and $E(z)\equiv [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ are standard terms in cosmology.
+where, $\Delta B$ is the bandwidth, $\lambda$ is the wavelength of the band center, $k_\textrm{B}$ is the Boltzmann constant, $\boldsymbol{k}_\perp$ and $k_\parallel$ are the transverse (on the sky) and line-of-sight (into the sky) wavenumbers respectively, $f_{21}$ is the rest-frame frequency of the 21~cm spin-flip transition of H~{\sc i}, $z$ is the redshift, $D\equiv D(z)$ is the transverse comoving distance, $\Delta D$ is the comoving depth along the line of sight corresponding to $\Delta B$, and $h$, $H_0$ and $E(z)\equiv [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ are standard terms in cosmology.
 Following \citet{par14},
@@
 
-In this paper, we investigate the spectral properties of the proposed dish design through their effects on the resultant foreground delay power spectrum and the constraints they place on attenuation required to suppress reflections between the antenna-feed assembly and antenna pairs to within tolerable limits.
+In this paper, we investigate the spectral properties of the proposed dish design through their effects on the resultant foreground delay power spectrum and the constraints they place on attenuation required to suppress reflections in the instrument.
 
@@
 The total bandwidth is 100~MHz centered on 150~MHz consisting of 256 channels with 390.625~kHz frequency resolution.
-Models of the antenna power pattern and foregrounds are described below.
+The models used are described below.
 
@@
 Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines} shows the delay power spectra of foregrounds on the 8 unique baseline lengths obtained with the aforementioned models for power pattern at arbitrary pointings on the sky.
-In all these panels, the full-band spectrally weighted foreground delay power spectra obtained with achromatic, {\it Airy} and fully chromatic simulated beam patterns are shown in black, red, and blue respectively.
+In all these panels, the full-band foreground delay power spectra obtained with achromatic, {\it Airy} and fully chromatic simulated beam patterns are shown in black, red, and blue respectively.
 The brightening of foreground power near the horizon limits (vertical dotted lines) due to the {\it pitchfork} effect \citep{thy15a,thy15b} is prominently seen in all cases.
@@
 Here our goal is to estimate the EoR-foreground dynamic range (ratio of EoR signal power to foreground power) in the presence of antenna beam chromaticity, using HERA as an example.
-As stated earlier, we estimate this ratio for HERA in the most conservative scenario where we consider only {\it foreground avoidance} under simple spectral weighting scheme.
+% As stated earlier, we estimate this ratio for HERA in the most conservative scenario where we consider only {\it foreground avoidance} under simple spectral weighting scheme.
 We emphasize that other strategies involving {\it foreground removal} and inverse covariance-based weighting schemes will produce more optimal results than presented here.
-
 In order to avoid signal evolution across the entire bandwidth, we use subbands in which EoR signal evolution is not expected to be significant.
@@
 where, the first term inside the parenthesis denotes the horizon limit, the second relates to the resolution due to subband bandwidth, $B_\textrm{eff}$, and $\zeta$ denotes a buffer to ensure the $k_\parallel^\textrm{FA}(|\boldsymbol{b}|)$ threshold ``safely'' avoids the main lobe of foreground power.
+In this study, we use $\zeta=3.5$.
 
@@
 
-We reiterate that these estimates are obtained in a conservative scenario wherein only simple spectral weighting technique in the {\it foreground avoidance} limit is used, without any foreground removal or sophisticated weighting strategies using inverse-covariance.
+% We reiterate that these estimates are obtained in a conservative scenario wherein only simple spectral weighting technique in the {\it foreground avoidance} limit is used, without any foreground removal or sophisticated weighting strategies using inverse-covariance.
 Further, these estimates represent worst-case limits demonstrating that HERA-19 and its successors will be extremely sensitive for EoR experiments and will benefit even further with more optimal foreground suppression strategies.

### 2016-03-22 ForegroundSimulations/ms.tex
Change in author ordering, Abstract and Intro
From b8ea8c2 (fgsim):
====================

In ms.tex,

(*) Minor changes in Abstract and Introduction.
(*) Change in author ordering

@@
 %% Co-authors
-Nipanjana~Patra\UCB,
 Aaron~M.~Ewall-Wice\MIT,
-Abraham~R.~Neben\MIT
+Abraham~R.~Neben\MIT,
+Nipanjana~Patra\UCB
 }
@@
 Unaccounted systematics from foregrounds and instruments prevent current experiments from detecting redshifted 21~cm signal from the Epoch of Reionization (EoR).
-We identify spectral structures (chromaticity) in the antenna power pattern as one such systematic that significantly affects all EoR measurements.
+We identify spectral structures (chromaticity) in the antenna power pattern as one such systematic that significantly affects all EoR experiments.
 Increase in chromaticity of the antenna beam causes the already bright foreground power to leak well beyond ideal limits and contaminate the otherwise clean EoR signal modes.
@@
 Using a simple and yet high dynamic range spectral weighting scheme, we demonstrate that EoR detection using HERA will not be impeded by such spectral systematics even in a conservative scenario that does not perform removal of foregrounds.
-We also show that all baselines in a 19-element HERA layout are capable of detecting EoR over a substantial observing window on the sky.
+All baselines in a 19-element HERA layout are capable of detecting EoR over a substantial observing window on the sky.
 
@@
 The Epoch of Reionization (EoR) is an important period of nonlinear growth of matter density perturbations and astrophysical evolution leading to the large scale structure observed currently in the Universe.
-The redshifted neutral hydrogen from the IGM in this epoch has been identified to be one of the most promising and direct probes of the EoR \citep{sun72,sco90,mad97,toz00,ili02}.
+The redshifted neutral hydrogen in this epoch has been identified to be one of the most promising and direct probes of the EoR \citep{sun72,sco90,mad97,toz00,ili02}.
 

### 2016-03-23 ForegroundSimulations/ms.tex
Minor changes throughout
From ffe0557 (fgsim):
====================

In ms.tex,

(*) Minor changes throughout

@@
 
-\citet{deb16} describe the HERA instrument in detail. Here, we provide a brief summary of the telescope currently under construction on the South African SKA site.
+\citet{deb16} describe the HERA instrument in detail. We provide a summary of the instrument currently under construction on the South African SKA site.
 
@@
 The core will be supplemented by 30 additional outrigger elements to tile the $uv$-plane with instantaneously complete sub-aperture sampling out to $250\lambda$ and complete aperture-scale sampling out to $350\lambda$ (at 150~MHz).
-The layout and its advantages are discussed in \citet{dil16}.
+The layout is discussed in \citet{dil16}.
 
@@
 
-A brief description of the delay spectrum technique \citep{par12a,par12b} is provided here. We borrow the notation used in \citet{thy15a}.
+The delay spectrum technique \citep{par12a,par12b} is briefly described here. We borrow the notation used in \citet{thy15a}.
 
@@
 \begin{align}\label{eqn:obsvis}
-  V_b(f) &= \iint\limits_\textrm{sky} A(\hat{\boldsymbol{s}},f)\,I(\hat{\boldsymbol{s}},f)\,e^{-i2\pi f\frac{\boldsymbol{b}\cdot\hat{\boldsymbol{s}}}{c}}\,\dif\Omega,
+  V_b(f) &= \int\limits_\textrm{sky} A(\hat{\boldsymbol{s}},f)\,I(\hat{\boldsymbol{s}},f)\,e^{-i2\pi f\frac{\boldsymbol{b}\cdot\hat{\boldsymbol{s}}}{c}}\,\dif\Omega,
 \end{align}
@@
 
-The delay spectrum has a close resemblance to cosmological H~{\sc i} spatial power spectrum and is defined as:
+The delay spectrum has a close resemblance to cosmological H{\sc i} spatial power spectrum and is defined as:
 \begin{align}\label{eqn:delay-power-spectrum}
-  P_\textrm{d}(\boldsymbol{k}_\perp,k_\parallel) &\equiv |\tilde{V}_b(\tau)|^2\left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2,
+  P(\boldsymbol{b},k_\parallel) &\equiv |\tilde{V}_b(\tau)|^2\left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2,
 \end{align}
@@
   \boldsymbol{k}_\perp &\equiv \frac{2\pi(\frac{\boldsymbol{b}}{\lambda})}{D}, \label{eqn:kperp-baseline}\\
-  k_\parallel &\equiv \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, \label{eqn:kprll-delay}
+  k_\parallel &\equiv \frac{2\pi\,f_{21}H_0\,E(z)}{c(1+z)^2}\,\tau, \label{eqn:kprll-delay}
 \end{align}
-where, $\Delta B$ is the bandwidth, $\lambda$ is the wavelength of the band center, $k_\textrm{B}$ is the Boltzmann constant, $\boldsymbol{k}_\perp$ and $k_\parallel$ are the transverse (on the sky) and line-of-sight (into the sky) wavenumbers respectively, $f_{21}$ is the rest-frame frequency of the 21~cm spin-flip transition of H~{\sc i}, $z$ is the redshift, $D\equiv D(z)$ is the transverse comoving distance, $\Delta D$ is the comoving depth along the line of sight corresponding to $\Delta B$, and $h$, $H_0$ and $E(z)\equiv [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ are standard terms in cosmology.
-Following \citet{par14},
+where, $\Delta B$ is the bandwidth, $\lambda$ is the wavelength of the band center, $k_\textrm{B}$ is the Boltzmann constant, $\boldsymbol{k}_\perp$ and $k_\parallel$ are the transverse (on the sky) and line-of-sight (into the sky) wavenumbers respectively, $f_{21}$ is the rest-frame frequency of the 21~cm spin-flip transition of H{\sc i}, $z$ is the redshift, $D\equiv D(z)$ is the transverse comoving distance, $\Delta D$ is the comoving depth along the line of sight corresponding to $\Delta B$, and $h$, $H_0$ and $E(z)\equiv [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ are standard terms in cosmology.
+$P(\boldsymbol{b},k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.
+In this paper, we use $\Omega_\textrm{M}=0.27$, $\Omega_\Lambda=0.73$, $\Omega_\textrm{K}=1-\Omega_\textrm{M}-\Omega_\Lambda$, $H_0=100\,$km$\,$s$^{-1}\,$Mpc$^{-1}$.
 \begin{align}
@@
 \end{align}
-which is related to the cosmic volume probed by the instrument.
-In this paper, we use $\Omega_\textrm{M}=0.27$, $\Omega_\Lambda=0.73$, $\Omega_\textrm{K}=1-\Omega_\textrm{M}-\Omega_\Lambda$, $H_0=100\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P_\textrm{d}(\boldsymbol{k}_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.
+is related to the cosmic volume probed by the instrument \citet{par14}.
 
 We note that these visibilities and delay power spectra are dependent on right ascension (RA) of the pointing as well as the frequency band.
-However, we defer expressing them explicitly as a function of pointing and center frequency (or redshift) to later sections where it becomes necessary.
+However, we defer expressing them explicitly as a function of pointing and frequency band (or redshift) to later sections where necessary.
 
@@
 
-In this paper, we investigate the spectral properties of the proposed dish design through their effects on the resultant foreground delay power spectrum and the constraints they place on attenuation required to suppress reflections in the instrument.
+In this paper, we investigate the spectral properties of the proposed dish design from a foreground contamination standpoint and the constraints they place on attenuation required to suppress reflections in the instrument.
 
@@
 In a related series of papers, \citet{neb16} discuss the agreement of these simulated antenna beam patterns with actual measurements, \citet{ewa16} model the reflections and return loss expected in the proposed antenna-feed assembly, and \citet{pat16} present measurements quantifying the reflections.
-Our focus in this paper is to investigate chromaticity of antenna power patterns from the point of view of their impact on foreground contamination in delay power spectra.
+Our focus in this paper is to investigate chromaticity of antenna power patterns from the point of view of their impact on foreground contamination.
 
@@
 Since our aim in this paper is to quantify EoR-foreground power ratio without employing any sophisticated {\it foreground removal} techniques, we turn our attention to {\it foreground avoidance} strategy that employs spectral weighting technique.
-In such a scheme, specific choices for spectral weighting function, $W(f)$, have been found to be effective in reducing foreground contamination by many orders of magnitude \citep{thy13} and is regularly used in EoR data analysis \citep{par12a}.
+Specific choices for spectral weighting function, $W(f)$, have been found to be effective in reducing foreground contamination by many orders of magnitude \citep{thy13} and is regularly used in EoR data analysis \citep{par12a}.
 For instance, a {\it Blackman-Harris} function \citep{har78} has a dynamic range of $\sim$100 -- 120~dB in delay power spectrum and a reduced effective bandwidth, with:
@@
 \end{align}
-where, $1-\epsilon$ is the loss in overall spectral sensitivity and $B_\textrm{eff}$ is the effective bandwidth.
+where, $B$ denotes the end-to-end range of the observing band, $1-\epsilon$ is the loss in overall spectral sensitivity and $B_\textrm{eff}$ is the effective bandwidth.
 For a {\it Blackman-Harris} window function denoted by $W_\textrm{BH}(f)$, $\epsilon \approx 50\%$.
@@
 
-Considering that the dynamic range required to suppress foreground contamination in the {\it EoR window} may probably be even higher than that provided by a {\it Blackman-Harris} window function, we use a modified version given by the convolution of a {\it Blackman-Harris} window with itself:
+As the dynamic range required to suppress foreground contamination in the {\it EoR window} may probably be even higher than that provided by a {\it Blackman-Harris} window function, we use a modified version given by convolving a {\it Blackman-Harris} window with itself:
 \begin{align}\label{eqn:bhw2}
@@
 
-This is an enormous gain in sidelobe characteristics for a small loss of sensitivity relative to a simple {\it Blackman-Harris} weighting.
+This is an enormous gain in sidelobe characteristics for a small loss of sensitivity relative to a {\it Blackman-Harris} weighting.
 This will ensure that the contamination resulting from spillover of foregrounds along the line-of-sight $k$-modes are limited only by intrinsic spectral structures in the foregrounds or beam patterns and not by sidelobes from spectral weighting.
@@
 Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines} shows the delay power spectra of foregrounds on the 8 unique baseline lengths obtained with the aforementioned models for power pattern at arbitrary pointings on the sky.
-In all these panels, the full-band foreground delay power spectra obtained with achromatic, {\it Airy} and fully chromatic simulated beam patterns are shown in black, red, and blue respectively.
+In all these panels, the full-band foreground delay power spectra obtained with achromatic, {\it Airy} and chromatic simulated beam patterns are shown in black, red, and blue respectively.
 The brightening of foreground power near the horizon limits (vertical dotted lines) due to the {\it pitchfork} effect \citep{thy15a,thy15b} is prominently seen in all cases.
@@
 It is also noted that despite the extreme dynamic range of the spectral weighting function employed, the tail of the foreground spillover at $|k_\parallel| \gtrsim 0.2\,h$~Mpc$^{-1}$ with an {\it Airy} beam pattern is many orders of magnitude higher than that using an achromatic beam while that from the simulated chromatic beam is even higher than from an {\it Airy} pattern by a few orders of magnitude.
-This signals that the foreground spillover shown are truly limited by intrinsic spectral features in the antenna beam patterns.
+Thus, the foreground spillover shown is truly limited by intrinsic spectral features in the antenna beam patterns.
 
@@
 This clearly demonstrates that higher the beam chromaticity, the farther the foreground contamination inherently extends along $k_\parallel$.
-Thus, the chromaticity of antenna beam needs to be carefully controlled in EoR experiments in order to keep the foreground systematics sufficiently low.
+Thus, the chromaticity of antenna beam needs to be controlled in EoR experiments to keep the foreground systematics sufficiently low.
 
-Such a significant spillover is not bound by the horizon limits of the {\it foreground wedge} because this is caused by spectral structure in the antenna beam pattern which is independent of the position-dependent geometric delays.
-As a result delay-based complex deconvolution techniques such as CLEAN \citep{tay99,par09,par12b} that rely on smoothness of foreground spectra and only spectral window shape will not have adequate information to accurately deconvolve intrinsic supra-horizon spillover arising from the chromaticity of the antenna beam.
+Such a significant spillover is not bound by the horizon limits as this is caused by spectral structure in the antenna beam pattern and is independent of geometric phases.
+Hence, delay-based complex deconvolution techniques \citep{par09,par12b} that rely on smoothness of foreground spectra and only spectral window shape will not have adequate information to accurately deconvolve intrinsic supra-horizon spillover arising from the chromaticity of the antenna beam.
 While delay power spectrum estimation using {\it foreground removal} strategy that accounts for direction- and beam chromaticity-dependent effects is possible, we leave it for future work.
@@
 
-One of the primary causes for spectral structure in antenna power patterns is reflections in the instrument.
-\citet{pat16} and \citet{ewa16} discuss the measured and simulated reflections respectively between a dish and its feed.
-Reflection between structures and signal paths from different antennas also causes chromaticity in the antenna beam.
+A primary cause for spectral structure in antenna power patterns is reflections in the instrument.
+\citet{pat16} and \citet{ewa16} discuss the measured and simulated reflections respectively between a dish and its feed for HERA.
+Reflections between different antennas also causes chromaticity in the antenna beam.
 In this section, we provide cosmologically motivated design specifications on instrument systematics caused by these two types of reflections.
 
-The effect of reflections it to shift the measured foreground power to higher modes in $\tau$ (or in $k_\parallel$) and thus cause further contamination in these higher $k_\parallel$-modes which are considered sensitive for EoR H{\sc i} signal detection.
+Reflections shift the measured foreground power to higher modes in $\tau$ (or in $k_\parallel$) and thus cause further contamination in these critical higher $k_\parallel$-modes.
 These delay shifts introduce ripples in the spectrum.
@@
 \begin{align}\label{eqn:attenuation}
-  \Gamma_{k_\textrm{p}}(\tau) \geq \max_{|k_\parallel|>k_\textrm{p}}\left\{\frac{P_\textrm{FG}(k_\parallel - \frac{\dif k_\parallel}{\dif \tau}\,\tau)}{P_\textrm{H{\sc i}}(k_\parallel)}\right\}^{1/2},
+  \Gamma_{k_\textrm{p}}(\boldsymbol{b},\tau) \geq \max_{|k_\parallel|>k_\textrm{p}}\left\{\frac{\left\langle P_\textrm{FG}(\boldsymbol{b},k_\parallel - \frac{\dif k_\parallel}{\dif \tau}\,\tau)\right\rangle}{P_\textrm{H{\sc i}}(|\boldsymbol{b}|,k_\parallel)}\right\}^{1/2},
 \end{align}
-where, $P_\textrm{H{\sc i}}(k_\parallel)$ is the EoR H{\sc i} power spectrum for the chosen antenna spacing, $P_\textrm{FG}(k_\parallel)$ is the foreground delay power spectrum obtained with the spectral weighting function applied over the full-band of the three uniquely oriented 14.6~m antenna spacings further averaged over a 0--12 hr local sidereal time (LST) range and over both positive and negative $k_\parallel$-modes, $\tau$ is the delay caused by reflections, and $\dif k_\parallel/\dif \tau$ is the {\it jacobian} in the transformation of $\tau$ to $k_\parallel$ (see equation~\ref{eqn:kprll-delay}).
-Thus, $\Gamma_{k_\textrm{p}}(\tau)$ is determined by the requirement that the reflected foreground power obtained by shifting in delay is below the EoR H{\sc i} signal power in line-of-sight spatial scales of interest given by $|k_\parallel|>k_\textrm{p}$.
+where, $\tau$ is the delay caused by reflections, and $\dif k_\parallel/\dif \tau$ is the {\it jacobian} in the transformation of $\tau$ to $k_\parallel$ (see equation~\ref{eqn:kprll-delay}).
+$P_\textrm{H{\sc i}}(|\boldsymbol{b}|,k_\parallel)$ is the EoR H{\sc i} delay power spectrum.
+$P_\textrm{FG}(\boldsymbol{b},k_\parallel)$ is the full-band foreground delay power spectrum.
+The angular brackets denote averaging over baseline vectors of the specified length, and a local sidereal time (LST) range.
+Thus, $\Gamma_{k_\textrm{p}}(\tau)$ is determined by the requirement that the reflected foreground power obtained by shifting in delay lies below the EoR H{\sc i} signal power in line-of-sight spatial scales of interest, $|k_\parallel|>k_\textrm{p}$.
 
-Both EoR models were used separately in this analysis to reduce the dependence of design specifications for reflections on any single model.
+Both EoR models were employed in this analysis to reduce the dependence of design specifications on any single model.
 However, we found similar results except for minor differences caused by small amplitude differences between the two EoR models.
-Hence, we only use results from using EoR model 1 at 150~MHz ($z\approx 8.47$).
+Hence, we only present results from using EoR model 1 at 150~MHz.
 
@@
 
-For reflections caused by dish-feed assembly, we use $P_\textrm{FG}(k_\parallel)$ obtained with the achromatic beam model on a 14.6~m baseline in equation~\ref{eqn:attenuation}.
+For reflections caused by dish-feed assembly, we use $P_\textrm{FG}(k_\parallel)$ obtained with the achromatic beam model on 14.6~m baselines in a 0--12 hr LST range.
 Fig.~\ref{fig:fg-reflections-achrmbeam} shows $\Gamma_{k_\textrm{p}}(\tau)$ (in dB) for $k_\textrm{p}$ chosen to be 0.1~$h$~Mpc$^{-1}$ (solid), 0.15~$h$~Mpc$^{-1}$ (dashed), and 0.2~$h$~Mpc$^{-1}$ (dotted).
@@
 These reflections are primarily caused in the dish-feed assembly and to some extent in other subsystems not accounted for.
-It implies that if these reflections are attenuated to levels that lie in the regions below the different shaded regions, such spectral systematics in the instrument will not hinder detection of EoR in those corresponding $k_\parallel$-modes of interest.
+It implies that if attenuated to levels that lie in the regions below the different shaded regions, such spectral systematics in the instrument will not hinder detection of EoR in those corresponding $k_\parallel$-modes of interest.
 
@@
 This is obtained on 14.6~m antenna spacing for EoR model 1 at 150~MHz ($z\approx 8.47$) and foreground power obtained with an achromatic antenna beam model.
-When the attenuation on dish-feed reflections is higher than these limits (outside the shaded regions), EoR will be detectable in respective $k_\parallel$-modes despite these reflections.}
+For EoR to be detectable in respective $k_\parallel$-modes despite these systematics, the attenuation of reflections must exceed these limits (outside the shaded regions).}
 \label{fig:fg-reflections-achrmbeam}
@@
 The elbow-shaped turnover is a measure of the most severe requirement on attenuation of reflections.
-This depends sensitively on the chosen $k_\parallel$ modes.
+This depends sensitively on the choice of $k_p$.
 For instance, the attenuation required is $\gtrsim 54$~dB at $\sim 200$~ns for $k_\textrm{p}=0.1\,h$~Mpc$^{-1}$, $\gtrsim 56$~dB at $\sim 300$~ns for $k_\textrm{p}=0.15\,h$~Mpc$^{-1}$ and $\gtrsim 58$~dB at $\sim 400$~ns for $k_\textrm{p}=0.2\,h$~Mpc$^{-1}$.
-Measurements by \citet{pat16} show that the return losses for HERA lie well within the regions excluded by the shaded regions thus implying that the attenuation is well above the lower limit and hence will not prevent EoR detection.
+Measurements are underway \citep{pat16} to confirm that the return losses in the HERA design lie well within the regions excluded by the shaded regions.
 
@@
 
-In both types of reflections discussed, similar design limits on reflections on various antenna spacings were also studied.
+Similar design limits on reflections on various antenna spacings were also studied.
 With increase in baseline length, the amplitude of foreground power decreases but the {\it foreground window} also widens.
@@
 
-Here our goal is to estimate the EoR-foreground dynamic range (ratio of EoR signal power to foreground power) in the presence of antenna beam chromaticity, using HERA as an example.
+We estimate the EoR-foreground dynamic range (ratio of EoR signal and foreground powers) for both EoR models in the presence of antenna beam chromaticity, using HERA as an example.
 % As stated earlier, we estimate this ratio for HERA in the most conservative scenario where we consider only {\it foreground avoidance} under simple spectral weighting scheme.
 We emphasize that other strategies involving {\it foreground removal} and inverse covariance-based weighting schemes will produce more optimal results than presented here.
-In order to avoid signal evolution across the entire bandwidth, we use subbands in which EoR signal evolution is not expected to be significant.
-These subbands with $B_\textrm{eff}=10$~MHz are defined by spectral weights obtained by convolution of {\it Blackman-Harris} window with itself.
+In order to avoid signal evolution across the entire band, we use subbands in which EoR signal evolution is not expected to be significant.
+These subbands with $B_\textrm{eff}=10$~MHz are defined by spectral weights in equation~\ref{eqn:bhw2}.
 These subbands are centered at 150~MHz and 170~MHz to estimate EoR-foreground dynamic range at $z \approx 8.47$ and $z \approx 7.36$ respectively.
-We use both EoR models 1 and 2 to reduce the dependence of this analysis on any single EoR model.
 
@@
 
-We estimate the ratio of EoR signal and foreground powers for HERA, where the latter is obtained with three antenna beams of different chromaticities.
+We estimate EoR-foreground dynamic range for HERA using antenna beams of different chromaticities.
 Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-150-subband} and \ref{fig:asm-dps-beam-chromaticity-baselines-170-subband} show the EoR signal and foreground power in 150~MHz and 170~MHz subbands respectively.
@@
 The foreground delay power spectra obtained with achromatic, {\it Airy} and simulated chromatic antenna patterns are shown in black, red, and blue respectively.
-Each panel corresponds to a unique baseline vector, same as in Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines}.
+Each panel corresponds to a baseline vector, same as in Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines}.
 
@@
 The coarsening of delay resolution significantly absorbs the distinct differences caused by beams of different chromaticities as seen in the full-band foreground delay spectra outside the {\it foreground wedge} in Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines}.
-This means the foreground spillover wings that extend beyond the horizon even in the case of simulated chromatic beam are on spectral scales larger than the 10~MHz effective bandwidth of the subbands.
+This means the foreground spillover wings that extend beyond the horizon even in the case of simulated chromatic beam are on spectral scales larger than the 10~MHz effective bandwidth.
 Hence, this results in an EoR signal-foreground crossover at $|k_\parallel| \gtrsim 0.2\,h$~Mpc$^{-1}$ independent of different antenna beam chromaticities used in this analysis.
@@
 \begin{align}
-  \rho(\boldsymbol{b},f_0,\alpha) &= \min_{|k_\parallel|>k_\parallel^\textrm{FA}(|\boldsymbol{b}|)}\left\{\frac{P_\textrm{H{\sc i}}(|\boldsymbol{b}|,k_\parallel,f_0)}{P_\textrm{FG}(\boldsymbol{b},k_\parallel,f_0,\alpha)}\right\}.
+  \rho(\boldsymbol{b},f_0,\alpha) &= \min_{|k_\parallel|>k_\parallel^\textrm{FA}(\boldsymbol{b})}\left\{\frac{P_\textrm{H{\sc i}}(|\boldsymbol{b}|,k_\parallel,f_0)}{P_\textrm{FG}(\boldsymbol{b},k_\parallel,f_0,\alpha)}\right\}.
 \end{align}
@@
 
-For the baselines considered, $\rho(\boldsymbol{b},f_0,\alpha)$ increases with longer baselines.
-We attribute this to the much steeper dependence of foreground emission on baseline length than that of EoR H{\sc i} power.
-This is also confirmed from Fig.~\ref{fig:subbands} where the peak and sidelobe levels of foreground power obtained with the simulated chromatic antenna beam on the 14.6~m baseline, which is sensitive to diffuse emission, progressively drops by two orders of magnitude on the 58.4~m baseline where diffuse emission is not as dominant.
-Hence, from a foreground contamination standpoint, the shortest baselines are less sensitive than the longer ones in the HERA-19 layout.
+For the baselines considered, $\rho(\boldsymbol{b},f_0,\alpha)$ increases with baseline length.
+We attribute this to the much steeper dependence of foreground emission (predominantly diffuse emission) on baseline length than that of EoR H{\sc i} power.
+This is also confirmed from Fig.~\ref{fig:subbands} where the peak and sidelobe levels of foreground power obtained with the simulated chromatic antenna beam on the 14.6~m baseline, progressively drops by two orders of magnitude on the 58.4~m baseline.
+Hence, from a foreground contamination standpoint, the shortest baselines are less sensitive than longer ones in HERA-19 layout.
 
 However, in all four cases considered here, except when the Galactic center appears overhead in the RA range roughly in the range 16-19 hr, the worst case signal-foreground ratio lies above unity in most of this parameter space.
-It demonstrates that HERA should detect the EoR signal with a very high signal-foreground ratio on all baselines in a vast majority of the pointings.
+It demonstrates that HERA should detect the EoR signal with a very high signal-foreground ratio on all baselines over a majority of the pointings.
 
@@
 
-We note that the inevitable reflections in the antenna-feed assembly and between reflecting structures across multiple antennas are also significant factors that contaminate the cosmological signal in high $k_\parallel$-modes inside the {\it EoR window}.
+We note that the inevitable reflections in the antenna-feed assembly and between reflecting structures across multiple antennas are also significant factors that contaminate the cosmological signal in $k_\parallel$-modes in the {\it EoR window}.
 Using a novel approach, we provide a formalism to set cosmologically-motivated design requirements directly on the level of suppression required on these reflections in the instrument.
-Ongoing reflectometry studies clearly indicate HERA will comfortably achieve the design limits prescribed here.
+% Ongoing reflectometry studies clearly indicate HERA will comfortably achieve the design limits prescribed here.
 
-Taking into account the effects of these instrumental systematics, if data is not limited by thermal noise, we demonstrate that HERA should detect EoR with high significance with a simple spectral weighting even under a conservative analysis criterion which does not involve {\it foreground removal} strategies.
+By accounting for these instrumental systematics, if data is not limited by thermal noise, we demonstrate that HERA should detect EoR with high significance with a simple spectral weighting even under a conservative analysis criterion that does not involve {\it foreground removal} strategies.
 All baselines of HERA-19 will not only detect but also help in filtering highly likely EoR models.
@@
 We are also investigating advanced strategies for foreground removal that will robustly eliminate these systematics further.
-More optimal analysis techniques and further design improvements will make HERA not only clear the obstacles limiting first-generation experiments but also become transformational for next-generation low frequency cosmology experiments.
+More optimal analysis techniques and further design improvements will make HERA not only clear the obstacles limiting first-generation experiments but also become transformational for next generation of low-frequency cosmology experiments.
 

### 2016-03-23 ForegroundSimulations/ms.tex
Append bibliography in tex file for arXiv
From bbb5b82 (fgsim-arxiv):
==========================

In ms.tex,

(*) Append contents of ms.bbl in bibliography to be compatible to
arXiv

@@
 Aaron~M.~Ewall-Wice\MIT,
-Abraham~R.~Neben\MIT,
+Abraham~R.~Neben\MIT, and
 Nipanjana~Patra\UCB
@@
 
-% \par\bigskip
 \bibliographystyle{apj}
-\bibliography{eor}
+% \bibliography{eor}
+\begin{thebibliography}{}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Ali} {et~al.}(2008){Ali}, {Bharadwaj}, \& {Chengalur}}]{ali08}
+{Ali}, S.~S., {Bharadwaj}, S., \& {Chengalur}, J.~N. 2008, \mnras, 385, 2166
+
+\bibitem[{{Ali} {et~al.}(2015){Ali}, {Parsons}, {Zheng}, {Pober}, {Liu},
+  {Aguirre}, {Bradley}, {Bernardi}, {Carilli}, {Cheng}, {DeBoer}, {Dexter},
+  {Grobbelaar}, {Horrell}, {Jacobs}, {Klima}, {MacMahon}, {Maree}, {Moore},
+  {Razavi}, {Stefan}, {Walbrugh}, \& {Walker}}]{ali15}
+{Ali}, Z.~S., {Parsons}, A.~R., {Zheng}, H., {et~al.} 2015, \apj, 809, 61
+
+\bibitem[{{Beardsley} {et~al.}(2013){Beardsley}, {Hazelton}, {Morales},
+  {Arcus}, {Barnes}, {Bernardi}, {Bowman}, {Briggs}, {Bunton}, {Cappallo},
+  {Corey}, {Deshpande}, {deSouza}, {Emrich}, {Gaensler}, {Goeke}, {Greenhill},
+  {Herne}, {Hewitt}, {Johnston-Hollitt}, {Kaplan}, {Kasper}, {Kincaid},
+  {Koenig}, {Kratzenberg}, {Lonsdale}, {Lynch}, {McWhirter}, {Mitchell},
+  {Morgan}, {Oberoi}, {Ord}, {Pathikulangara}, {Prabu}, {Remillard}, {Rogers},
+  {Roshi}, {Salah}, {Sault}, {Udaya}, {Srivani}, {Stevens}, {Subrahmanyan},
+  {Tingay}, {Wayth}, {Waterson}, {Webster}, {Whitney}, {Williams}, {Williams},
+  \& {Wyithe}}]{bea13}
+{Beardsley}, A.~P., {Hazelton}, B.~J., {Morales}, M.~F., {et~al.} 2013, \mnras,
+  429, L5
+
+\bibitem[{{Bernardi} {et~al.}(2009){Bernardi}, {de Bruyn}, {Brentjens},
+  {Ciardi}, {Harker}, {Jeli{\'c}}, {Koopmans}, {Labropoulos}, {Offringa},
+  {Pandey}, {Schaye}, {Thomas}, {Yatawatta}, \& {Zaroubi}}]{ber09}
+{Bernardi}, G., {de Bruyn}, A.~G., {Brentjens}, M.~A., {et~al.} 2009, \aap,
+  500, 965
+
+\bibitem[{{Bernardi} {et~al.}(2010){Bernardi}, {de Bruyn}, {Harker},
+  {Brentjens}, {Ciardi}, {Jeli{\'c}}, {Koopmans}, {Labropoulos}, {Offringa},
+  {Pandey}, {Schaye}, {Thomas}, {Yatawatta}, \& {Zaroubi}}]{ber10}
+{Bernardi}, G., {de Bruyn}, A.~G., {Harker}, G., {et~al.} 2010, \aap, 522, A67
+
+\bibitem[{{Bock} {et~al.}(1999){Bock}, {Large}, \& {Sadler}}]{boc99}
+{Bock}, D.~C.-J., {Large}, M.~I., \& {Sadler}, E.~M. 1999, \aj, 117, 1578
+
+\bibitem[{{Bowman} {et~al.}(2009){Bowman}, {Morales}, \& {Hewitt}}]{bow09}
+{Bowman}, J.~D., {Morales}, M.~F., \& {Hewitt}, J.~N. 2009, \apj, 695, 183
+
+\bibitem[{{Bowman} \& {Rogers}(2010)}]{bow10}
+{Bowman}, J.~D., \& {Rogers}, A.~E.~E. 2010, \nat, 468, 796
+
+\bibitem[{{Bowman} {et~al.}(2013){Bowman}, {Cairns}, {Kaplan}, {Murphy},
+  {Oberoi}, {Staveley-Smith}, {Arcus}, {Barnes}, {Bernardi}, {Briggs}, {Brown},
+  {Bunton}, {Burgasser}, {Cappallo}, {Chatterjee}, {Corey}, {Coster},
+  {Deshpande}, {deSouza}, {Emrich}, {Erickson}, {Goeke}, {Gaensler},
+  {Greenhill}, {Harvey-Smith}, {Hazelton}, {Herne}, {Hewitt},
+  {Johnston-Hollitt}, {Kasper}, {Kincaid}, {Koenig}, {Kratzenberg}, {Lonsdale},
+  {Lynch}, {Matthews}, {McWhirter}, {Mitchell}, {Morales}, {Morgan}, {Ord},
+  {Pathikulangara}, {Prabu}, {Remillard}, {Robishaw}, {Rogers}, {Roshi},
+  {Salah}, {Sault}, {Shankar}, {Srivani}, {Stevens}, {Subrahmanyan}, {Tingay},
+  {Wayth}, {Waterson}, {Webster}, {Whitney}, {Williams}, {Williams}, \&
+  {Wyithe}}]{bow13}
+{Bowman}, J.~D., {Cairns}, I., {Kaplan}, D.~L., {et~al.} 2013, \pasa, 30, 31
+
+\bibitem[{{Condon} {et~al.}(1998){Condon}, {Cotton}, {Greisen}, {Yin},
+  {Perley}, {Taylor}, \& {Broderick}}]{con98}
+{Condon}, J.~J., {Cotton}, W.~D., {Greisen}, E.~W., {et~al.} 1998, \aj, 115,
+  1693
+
+\bibitem[{{Datta} {et~al.}(2010){Datta}, {Bowman}, \& {Carilli}}]{dat10}
+{Datta}, A., {Bowman}, J.~D., \& {Carilli}, C.~L. 2010, \apj, 724, 526
+
+\bibitem[{{de Oliveira-Costa} {et~al.}(2008){de Oliveira-Costa}, {Tegmark},
+  {Gaensler}, {Jonas}, {Landecker}, \& {Reich}}]{deo08}
+{de Oliveira-Costa}, A., {Tegmark}, M., {Gaensler}, B.~M., {et~al.} 2008,
+  \mnras, 388, 247
+
+\bibitem[{DeBoer {et~al.}(2016)}]{deb16}
+DeBoer, D., {et~al.} 2016, in preparation
+
+\bibitem[{{Di Matteo} {et~al.}(2002){Di Matteo}, {Perna}, {Abel}, \&
+  {Rees}}]{dim02}
+{Di Matteo}, T., {Perna}, R., {Abel}, T., \& {Rees}, M.~J. 2002, \apj, 564, 576
+
+\bibitem[{Dillon {et~al.}(2013)Dillon, Liu, \& Tegmark}]{dil13}
+Dillon, J.~S., Liu, A., \& Tegmark, M. 2013, Phys. Rev. D, 87, 043005
+
+\bibitem[{{Dillon} \& {Parsons}(2016)}]{dil16}
+{Dillon}, J.~S., \& {Parsons}, A.~R. 2016, ArXiv e-prints, arXiv:1602.06259
+
+\bibitem[{{Dillon} {et~al.}(2014){Dillon}, {Liu}, {Williams}, {Hewitt},
+  {Tegmark}, {Morgan}, {Levine}, {Morales}, {Tingay}, {Bernardi}, {Bowman},
+  {Briggs}, {Cappallo}, {Emrich}, {Mitchell}, {Oberoi}, {Prabu}, {Wayth}, \&
+  {Webster}}]{dil14}
+{Dillon}, J.~S., {Liu}, A., {Williams}, C.~L., {et~al.} 2014, \prd, 89, 023002
+
+\bibitem[{{Dillon} {et~al.}(2015){Dillon}, {Neben}, {Hewitt}, {Tegmark},
+  {Barry}, {Beardsley}, {Bowman}, {Briggs}, {Carroll}, {de Oliveira-Costa},
+  {Ewall-Wice}, {Feng}, {Greenhill}, {Hazelton}, {Hernquist}, {Hurley-Walker},
+  {Jacobs}, {Kim}, {Kittiwisit}, {Lenc}, {Line}, {Loeb}, {McKinley},
+  {Mitchell}, {Morales}, {Offringa}, {Paul}, {Pindor}, {Pober}, {Procopio},
+  {Riding}, {Sethi}, {Shankar}, {Subrahmanyan}, {Sullivan}, {Thyagarajan},
+  {Tingay}, {Trott}, {Wayth}, {Webster}, {Wyithe}, {Bernardi}, {Cappallo},
+  {Deshpande}, {Johnston-Hollitt}, {Kaplan}, {Lonsdale}, {McWhirter}, {Morgan},
+  {Oberoi}, {Ord}, {Prabu}, {Srivani}, {Williams}, \& {Williams}}]{dil15}
+{Dillon}, J.~S., {Neben}, A.~R., {Hewitt}, J.~N., {et~al.} 2015, \prd, 91,
+  123011
+
+\bibitem[{{Ewall-Wice} {et~al.}(2016){Ewall-Wice}, {Bradley}, {DeBoer},
+  {Hewitt}, {Parsons}, {Aguirre}, {Ali}, {Bowman}, {Cheng}, {Neben}, {Patra},
+  {Thyagarajan}, {Venter}, {de Lera Acedo}, {Dillon}, {Doolittle}, {Egan},
+  {Hendrick}, {Klima}, {Kohn}, {Schaffner}, {Shelton}, {Saliwanchik},
+  {Tegmark}, {Taylor}, {Taylor}, \& {Wirt}}]{ewa16}
+{Ewall-Wice}, A., {Bradley}, R., {DeBoer}, D., {et~al.} 2016, ArXiv e-prints,
+  arXiv:1602.06277
+
+\bibitem[{{Furlanetto} \& {Briggs}(2004)}]{fur04b}
+{Furlanetto}, S.~R., \& {Briggs}, F.~H. 2004, \nar, 48, 1039
+
+\bibitem[{{Furlanetto} {et~al.}(2006){Furlanetto}, {Oh}, \& {Briggs}}]{fur06}
+{Furlanetto}, S.~R., {Oh}, S.~P., \& {Briggs}, F.~H. 2006, \physrep, 433, 181
+
+\bibitem[{{Furlanetto} {et~al.}(2004){Furlanetto}, {Zaldarriaga}, \&
+  {Hernquist}}]{fur04a}
+{Furlanetto}, S.~R., {Zaldarriaga}, M., \& {Hernquist}, L. 2004, \apj, 613, 1
+
+\bibitem[{{Ghosh} {et~al.}(2012){Ghosh}, {Prasad}, {Bharadwaj}, {Ali}, \&
+  {Chengalur}}]{gho12}
+{Ghosh}, A., {Prasad}, J., {Bharadwaj}, S., {Ali}, S.~S., \& {Chengalur}, J.~N.
+  2012, \mnras, 426, 3295
+
+\bibitem[{{Gleser} {et~al.}(2008){Gleser}, {Nusser}, \& {Benson}}]{gle08}
+{Gleser}, L., {Nusser}, A., \& {Benson}, A.~J. 2008, \mnras, 391, 383
+
+\bibitem[{{Harris}(1978)}]{har78}
+{Harris}, F.~J. 1978, IEEE Proceedings, 66, 51
+
+\bibitem[{{Iliev} {et~al.}(2002){Iliev}, {Shapiro}, {Ferrara}, \&
+  {Martel}}]{ili02}
+{Iliev}, I.~T., {Shapiro}, P.~R., {Ferrara}, A., \& {Martel}, H. 2002, \apjl,
+  572, L123
+
+\bibitem[{{Lidz} {et~al.}(2008){Lidz}, {Zahn}, {McQuinn}, {Zaldarriaga}, \&
+  {Hernquist}}]{lid08}
+{Lidz}, A., {Zahn}, O., {McQuinn}, M., {Zaldarriaga}, M., \& {Hernquist}, L.
+  2008, \apj, 680, 962
+
+\bibitem[{{Liu} {et~al.}(2014{\natexlab{a}}){Liu}, {Parsons}, \&
+  {Trott}}]{liu14a}
+{Liu}, A., {Parsons}, A.~R., \& {Trott}, C.~M. 2014{\natexlab{a}}, \prd, 90,
+  023018
+
+\bibitem[{{Liu} {et~al.}(2014{\natexlab{b}}){Liu}, {Parsons}, \&
+  {Trott}}]{liu14b}
+---. 2014{\natexlab{b}}, \prd, 90, 023019
+
+\bibitem[{{Liu} \& {Tegmark}(2011)}]{liu11}
+{Liu}, A., \& {Tegmark}, M. 2011, \prd, 83, 103006
+
+\bibitem[{{Liu} {et~al.}(2009){Liu}, {Tegmark}, {Bowman}, {Hewitt}, \&
+  {Zaldarriaga}}]{liu09}
+{Liu}, A., {Tegmark}, M., {Bowman}, J., {Hewitt}, J., \& {Zaldarriaga}, M.
+  2009, \mnras, 398, 401
+
+\bibitem[{{Lonsdale} {et~al.}(2009){Lonsdale}, {Cappallo}, {Morales}, {Briggs},
+  {Benkevitch}, {Bowman}, {Bunton}, {Burns}, {Corey}, {Desouza}, {Doeleman},
+  {Derome}, {Deshpande}, {Gopala}, {Greenhill}, {Herne}, {Hewitt}, {Kamini},
+  {Kasper}, {Kincaid}, {Kocz}, {Kowald}, {Kratzenberg}, {Kumar}, {Lynch},
+  {Madhavi}, {Matejek}, {Mitchell}, {Morgan}, {Oberoi}, {Ord},
+  {Pathikulangara}, {Prabu}, {Rogers}, {Roshi}, {Salah}, {Sault}, {Shankar},
+  {Srivani}, {Stevens}, {Tingay}, {Vaccarella}, {Waterson}, {Wayth}, {Webster},
+  {Whitney}, {Williams}, \& {Williams}}]{lon09}
+{Lonsdale}, C.~J., {Cappallo}, R.~J., {Morales}, M.~F., {et~al.} 2009, IEEE
+  Proceedings, 97, 1497
+
+\bibitem[{{Madau} {et~al.}(1997){Madau}, {Meiksin}, \& {Rees}}]{mad97}
+{Madau}, P., {Meiksin}, A., \& {Rees}, M.~J. 1997, \apj, 475, 429
+
+\bibitem[{{Mauch} {et~al.}(2003){Mauch}, {Murphy}, {Buttery}, {Curran},
+  {Hunstead}, {Piestrzynski}, {Robertson}, \& {Sadler}}]{mau03}
+{Mauch}, T., {Murphy}, T., {Buttery}, H.~J., {et~al.} 2003, \mnras, 342, 1117
+
+\bibitem[{{McQuinn} {et~al.}(2006){McQuinn}, {Zahn}, {Zaldarriaga},
+  {Hernquist}, \& {Furlanetto}}]{mcq06}
+{McQuinn}, M., {Zahn}, O., {Zaldarriaga}, M., {Hernquist}, L., \& {Furlanetto},
+  S.~R. 2006, \apj, 653, 815
+
+\bibitem[{{Mesinger} {et~al.}(2011){Mesinger}, {Furlanetto}, \& {Cen}}]{mes11}
+{Mesinger}, A., {Furlanetto}, S., \& {Cen}, R. 2011, \mnras, 411, 955
+
+\bibitem[{{Morales} {et~al.}(2006){Morales}, {Bowman}, \& {Hewitt}}]{mor06}
+{Morales}, M.~F., {Bowman}, J.~D., \& {Hewitt}, J.~N. 2006, \apj, 648, 767
+
+\bibitem[{{Morales} {et~al.}(2012){Morales}, {Hazelton}, {Sullivan}, \&
+  {Beardsley}}]{mor12}
+{Morales}, M.~F., {Hazelton}, B., {Sullivan}, I., \& {Beardsley}, A. 2012,
+  \apj, 752, 137
+
+\bibitem[{{Morales} \& {Hewitt}(2004)}]{mor04}
+{Morales}, M.~F., \& {Hewitt}, J. 2004, \apj, 615, 7
+
+\bibitem[{{Neben} {et~al.}(2016){Neben}, {Bradley}, {Hewitt}, {DeBoer},
+  {Parsons}, {Aguirre}, {Ali}, {Cheng}, {Ewall-Wice}, {Patra}, {Thyagarajan},
+  {Bowman}, {Dickenson}, {Dillon}, {Doolittle}, {Egan}, {Hedrick}, {Jacobs},
+  {Kohn}, {Klima}, {Moodley}, {Saliwanchik}, {Schaffner}, {Shelton}, {Taylor},
+  {Taylor}, {Tegmark}, {Wirt}, \& {Zheng}}]{neb16}
+{Neben}, A.~R., {Bradley}, R.~F., {Hewitt}, J.~N., {et~al.} 2016, ArXiv
+  e-prints, arXiv:1602.03887
+
+\bibitem[{{Paciga} {et~al.}(2013){Paciga}, {Albert}, {Bandura}, {Chang},
+  {Gupta}, {Hirata}, {Odegova}, {Pen}, {Peterson}, {Roy}, {Shaw}, {Sigurdson},
+  \& {Voytek}}]{pac13}
+{Paciga}, G., {Albert}, J.~G., {Bandura}, K., {et~al.} 2013, \mnras, 433, 639
+
+\bibitem[{{Parsons} {et~al.}(2012{\natexlab{a}}){Parsons}, {Pober}, {McQuinn},
+  {Jacobs}, \& {Aguirre}}]{par12a}
+{Parsons}, A., {Pober}, J., {McQuinn}, M., {Jacobs}, D., \& {Aguirre}, J.
+  2012{\natexlab{a}}, \apj, 753, 81
+
+\bibitem[{{Parsons} \& {Backer}(2009)}]{par09}
+{Parsons}, A.~R., \& {Backer}, D.~C. 2009, \aj, 138, 219
+
+\bibitem[{{Parsons} {et~al.}(2012{\natexlab{b}}){Parsons}, {Pober}, {Aguirre},
+  {Carilli}, {Jacobs}, \& {Moore}}]{par12b}
+{Parsons}, A.~R., {Pober}, J.~C., {Aguirre}, J.~E., {et~al.}
+  2012{\natexlab{b}}, \apj, 756, 165
+
+\bibitem[{{Parsons} {et~al.}(2010){Parsons}, {Backer}, {Foster}, {Wright},
+  {Bradley}, {Gugliucci}, {Parashare}, {Benoit}, {Aguirre}, {Jacobs},
+  {Carilli}, {Herne}, {Lynch}, {Manley}, \& {Werthimer}}]{par10}
+{Parsons}, A.~R., {Backer}, D.~C., {Foster}, G.~S., {et~al.} 2010, \aj, 139,
+  1468
+
+\bibitem[{{Parsons} {et~al.}(2014){Parsons}, {Liu}, {Aguirre}, {Ali},
+  {Bradley}, {Carilli}, {DeBoer}, {Dexter}, {Gugliucci}, {Jacobs}, {Klima},
+  {MacMahon}, {Manley}, {Moore}, {Pober}, {Stefan}, \& {Walbrugh}}]{par14}
+{Parsons}, A.~R., {Liu}, A., {Aguirre}, J.~E., {et~al.} 2014, \apj, 788, 106
+
+\bibitem[{Patra {et~al.}(2016)}]{pat16}
+Patra, N., {et~al.} 2016, in preparation
+
+\bibitem[{{Pober} {et~al.}(2013){Pober}, {Parsons}, {Aguirre}, {Ali},
+  {Bradley}, {Carilli}, {DeBoer}, {Dexter}, {Gugliucci}, {Jacobs}, {Klima},
+  {MacMahon}, {Manley}, {Moore}, {Stefan}, \& {Walbrugh}}]{pob13}
+{Pober}, J.~C., {Parsons}, A.~R., {Aguirre}, J.~E., {et~al.} 2013, \apjl, 768,
+  L36
+
+\bibitem[{{Pober} {et~al.}(2015){Pober}, {Ali}, {Parsons}, {McQuinn},
+  {Aguirre}, {Bernardi}, {Bradley}, {Carilli}, {Cheng}, {DeBoer}, {Dexter},
+  {Furlanetto}, {Grobbelaar}, {Horrell}, {Jacobs}, {Klima}, {Kohn}, {Liu},
+  {MacMahon}, {Maree}, {Mesinger}, {Moore}, {Razavi-Ghods}, {Stefan},
+  {Walbrugh}, {Walker}, \& {Zheng}}]{pob15}
+{Pober}, J.~C., {Ali}, Z.~S., {Parsons}, A.~R., {et~al.} 2015, \apj, 809, 62
+
+\bibitem[{{Santos} {et~al.}(2005){Santos}, {Cooray}, \& {Knox}}]{san05}
+{Santos}, M.~G., {Cooray}, A., \& {Knox}, L. 2005, \apj, 625, 575
+
+\bibitem[{{Scott} \& {Rees}(1990)}]{sco90}
+{Scott}, D., \& {Rees}, M.~J. 1990, \mnras, 247, 510
+
+\bibitem[{{Sunyaev} \& {Zeldovich}(1972)}]{sun72}
+{Sunyaev}, R.~A., \& {Zeldovich}, Y.~B. 1972, \aap, 20, 189
+
+\bibitem[{{Thompson} {et~al.}(2001){Thompson}, {Moran}, \& {Swenson}}]{tho01}
+{Thompson}, A.~R., {Moran}, J.~M., \& {Swenson}, Jr., G.~W. 2001,
+  {Interferometry and Synthesis in Radio Astronomy, 2nd Edition} (Wiley)
+
+\bibitem[{{Thyagarajan} {et~al.}(2013){Thyagarajan}, {Udaya Shankar},
+  {Subrahmanyan}, {Arcus}, {Bernardi}, {Bowman}, {Briggs}, {Bunton},
+  {Cappallo}, {Corey}, {deSouza}, {Emrich}, {Gaensler}, {Goeke}, {Greenhill},
+  {Hazelton}, {Herne}, {Hewitt}, {Johnston-Hollitt}, {Kaplan}, {Kasper},
+  {Kincaid}, {Koenig}, {Kratzenberg}, {Lonsdale}, {Lynch}, {McWhirter},
+  {Mitchell}, {Morales}, {Morgan}, {Oberoi}, {Ord}, {Pathikulangara},
+  {Remillard}, {Rogers}, {Anish Roshi}, {Salah}, {Sault}, {Srivani}, {Stevens},
+  {Thiagaraj}, {Tingay}, {Wayth}, {Waterson}, {Webster}, {Whitney}, {Williams},
+  {Williams}, \& {Wyithe}}]{thy13}
+{Thyagarajan}, N., {Udaya Shankar}, N., {Subrahmanyan}, R., {et~al.} 2013,
+  \apj, 776, 6
+
+\bibitem[{{Thyagarajan} {et~al.}(2015{\natexlab{a}}){Thyagarajan}, {Jacobs},
+  {Bowman}, {Barry}, {Beardsley}, {Bernardi}, {Briggs}, {Cappallo}, {Carroll},
+  {Corey}, {de Oliveira-Costa}, {Dillon}, {Emrich}, {Ewall-Wice}, {Feng},
+  {Goeke}, {Greenhill}, {Hazelton}, {Hewitt}, {Hurley-Walker},
+  {Johnston-Hollitt}, {Kaplan}, {Kasper}, {Kim}, {Kittiwisit}, {Kratzenberg},
+  {Lenc}, {Line}, {Loeb}, {Lonsdale}, {Lynch}, {McKinley}, {McWhirter},
+  {Mitchell}, {Morales}, {Morgan}, {Neben}, {Oberoi}, {Offringa}, {Ord},
+  {Paul}, {Pindor}, {Pober}, {Prabu}, {Procopio}, {Riding}, {Rogers}, {Roshi},
+  {Udaya Shankar}, {Sethi}, {Srivani}, {Subrahmanyan}, {Sullivan}, {Tegmark},
+  {Tingay}, {Trott}, {Waterson}, {Wayth}, {Webster}, {Whitney}, {Williams},
+  {Williams}, {Wu}, \& {Wyithe}}]{thy15a}
+{Thyagarajan}, N., {Jacobs}, D.~C., {Bowman}, J.~D., {et~al.}
+  2015{\natexlab{a}}, \apj, 804, 14
+
+\bibitem[{{Thyagarajan} {et~al.}(2015{\natexlab{b}}){Thyagarajan}, {Jacobs},
+  {Bowman}, {Barry}, {Beardsley}, {Bernardi}, {Briggs}, {Cappallo}, {Carroll},
+  {Deshpande}, {de Oliveira-Costa}, {Dillon}, {Ewall-Wice}, {Feng},
+  {Greenhill}, {Hazelton}, {Hernquist}, {Hewitt}, {Hurley-Walker},
+  {Johnston-Hollitt}, {Kaplan}, {Kim}, {Kittiwisit}, {Lenc}, {Line}, {Loeb},
+  {Lonsdale}, {McKinley}, {McWhirter}, {Mitchell}, {Morales}, {Morgan},
+  {Neben}, {Oberoi}, {Offringa}, {Ord}, {Paul}, {Pindor}, {Pober}, {Prabu},
+  {Procopio}, {Riding}, {Udaya Shankar}, {Sethi}, {Srivani}, {Subrahmanyan},
+  {Sullivan}, {Tegmark}, {Tingay}, {Trott}, {Wayth}, {Webster}, {Williams},
+  {Williams}, \& {Wyithe}}]{thy15b}
+---. 2015{\natexlab{b}}, \apjl, 807, L28
+
+\bibitem[{{Tingay} {et~al.}(2013){Tingay}, {Goeke}, {Bowman}, {Emrich}, {Ord},
+  {Mitchell}, {Morales}, {Booler}, {Crosse}, {Wayth}, {Lonsdale}, {Tremblay},
+  {Pallot}, {Colegate}, {Wicenec}, {Kudryavtseva}, {Arcus}, {Barnes},
+  {Bernardi}, {Briggs}, {Burns}, {Bunton}, {Cappallo}, {Corey}, {Deshpande},
+  {Desouza}, {Gaensler}, {Greenhill}, {Hall}, {Hazelton}, {Herne}, {Hewitt},
+  {Johnston-Hollitt}, {Kaplan}, {Kasper}, {Kincaid}, {Koenig}, {Kratzenberg},
+  {Lynch}, {Mckinley}, {Mcwhirter}, {Morgan}, {Oberoi}, {Pathikulangara},
+  {Prabu}, {Remillard}, {Rogers}, {Roshi}, {Salah}, {Sault}, {Udaya-Shankar},
+  {Schlagenhaufer}, {Srivani}, {Stevens}, {Subrahmanyan}, {Waterson},
+  {Webster}, {Whitney}, {Williams}, {Williams}, \& {Wyithe}}]{tin13}
+{Tingay}, S.~J., {Goeke}, R., {Bowman}, J.~D., {et~al.} 2013, \pasa, 30, 7
+
+\bibitem[{{Tozzi} {et~al.}(2000){Tozzi}, {Madau}, {Meiksin}, \& {Rees}}]{toz00}
+{Tozzi}, P., {Madau}, P., {Meiksin}, A., \& {Rees}, M.~J. 2000, \apj, 528, 597
+
+\bibitem[{{Trott} {et~al.}(2012){Trott}, {Wayth}, \& {Tingay}}]{tro12}
+{Trott}, C.~M., {Wayth}, R.~B., \& {Tingay}, S.~J. 2012, \apj, 757, 101
+
+\bibitem[{{van Cittert}(1934)}]{van34}
+{van Cittert}, P.~H. 1934, Physica, 1, 201
+
+\bibitem[{{van Haarlem} {et~al.}(2013){van Haarlem}, {Wise}, {Gunst}, {Heald},
+  {McKean}, {Hessels}, {de Bruyn}, {Nijboer}, {Swinbank}, {Fallows},
+  {Brentjens}, {Nelles}, {Beck}, {Falcke}, {Fender}, {H{\"o}randel},
+  {Koopmans}, {Mann}, {Miley}, {R{\"o}ttgering}, {Stappers}, {Wijers},
+  {Zaroubi}, {van den Akker}, {Alexov}, {Anderson}, {Anderson}, {van Ardenne},
+  {Arts}, {Asgekar}, {Avruch}, {Batejat}, {B{\"a}hren}, {Bell}, {Bell}, {van
+  Bemmel}, {Bennema}, {Bentum}, {Bernardi}, {Best}, {B{\^i}rzan}, {Bonafede},
+  {Boonstra}, {Braun}, {Bregman}, {Breitling}, {van de Brink}, {Broderick},
+  {Broekema}, {Brouw}, {Br{\"u}ggen}, {Butcher}, {van Cappellen}, {Ciardi},
+  {Coenen}, {Conway}, {Coolen}, {Corstanje}, {Damstra}, {Davies}, {Deller},
+  {Dettmar}, {van Diepen}, {Dijkstra}, {Donker}, {Doorduin}, {Dromer}, {Drost},
+  {van Duin}, {Eisl{\"o}ffel}, {van Enst}, {Ferrari}, {Frieswijk}, {Gankema},
+  {Garrett}, {de Gasparin}, {Gerbers}, {de Geus}, {Grie{\ss}meier}, {Grit},
+  {Gruppen}, {Hamaker}, {Hassall}, {Hoeft}, {Holties}, {Horneffer}, {van der
+  Horst}, {van Houwelingen}, {Huijgen}, {Iacobelli}, {Intema}, {Jackson},
+  {Jelic}, {de Jong}, {Kant}, {Karastergiou}, {Koers}, {Kollen}, {Kondratiev},
+  {Kooistra}, {Koopman}, {Koster}, {Kuniyoshi}, {Kramer}, {Kuper},
+  {Lambropoulos}, {Law}, {van Leeuwen}, {Lemaitre}, {Loose}, {Maat}, {Macario},
+  {Markoff}, {Masters}, {McFadden}, {McKay-Bukowski}, {Meijering}, {Meulman},
+  {Mevius}, {Millenaar}, {Miller-Jones}, {Mohan}, {Mol}, {Morawietz},
+  {Morganti}, {Mulcahy}, {Mulder}, {Munk}, {Nieuwenhuis}, {van Nieuwpoort},
+  {Noordam}, {Norden}, {Noutsos}, {Offringa}, {Olofsson}, {Omar}, {Orr{\'u}},
+  {Overeem}, {Paas}, {Pandey-Pommier}, {Pandey}, {Pizzo}, {Polatidis},
+  {Rafferty}, {Rawlings}, {Reich}, {de Reijer}, {Reitsma}, {Renting},
+  {Riemers}, {Rol}, {Romein}, {Roosjen}, {Ruiter}, {Scaife}, {van der Schaaf},
+  {Scheers}, {Schellart}, {Schoenmakers}, {Schoonderbeek}, {Serylak},
+  {Shulevski}, {Sluman}, {Smirnov}, {Sobey}, {Spreeuw}, {Steinmetz}, {Sterks},
+  {Stiepel}, {Stuurwold}, {Tagger}, {Tang}, {Tasse}, {Thomas}, {Thoudam},
+  {Toribio}, {van der Tol}, {Usov}, {van Veelen}, {van der Veen}, {ter Veen},
+  {Verbiest}, {Vermeulen}, {Vermaas}, {Vocks}, {Vogt}, {de Vos}, {van der Wal},
+  {van Weeren}, {Weggemans}, {Weltevrede}, {White}, {Wijnholds}, {Wilhelmsson},
+  {Wucknitz}, {Yatawatta}, {Zarka}, {Zensus}, \& {van Zwieten}}]{van13}
+{van Haarlem}, M.~P., {Wise}, M.~W., {Gunst}, A.~W., {et~al.} 2013, \aap, 556,
+  A2
+
+\bibitem[{{Vedantham} {et~al.}(2012){Vedantham}, {Udaya Shankar}, \&
+  {Subrahmanyan}}]{ved12}
+{Vedantham}, H., {Udaya Shankar}, N., \& {Subrahmanyan}, R. 2012, \apj, 745,
+  176
+
+\bibitem[{{Wang} {et~al.}(2006){Wang}, {Tegmark}, {Santos}, \& {Knox}}]{wan06}
+{Wang}, X., {Tegmark}, M., {Santos}, M.~G., \& {Knox}, L. 2006, \apj, 650, 529
+
+\bibitem[{{Zaldarriaga} {et~al.}(2004){Zaldarriaga}, {Furlanetto}, \&
+  {Hernquist}}]{zal04}
+{Zaldarriaga}, M., {Furlanetto}, S.~R., \& {Hernquist}, L. 2004, \apj, 608, 622
+
+\bibitem[{{Zernike}(1938)}]{zer38}
+{Zernike}, F. 1938, Physica, 5, 785
+
+\bibitem[{{Zheng} {et~al.}(2014){Zheng}, {Tegmark}, {Buza}, {Dillon},
+  {Gharibyan}, {Hickish}, {Kunz}, {Liu}, {Losh}, {Lutomirski}, {Morrison},
+  {Narayanan}, {Perko}, {Rosner}, {Sanchez}, {Schutz}, {Tribiano}, {Valdez},
+  {Yang}, {Adami}, {Zelko}, {Zheng}, {Armstrong}, {Bradley}, {Dexter},
+  {Ewall-Wice}, {Magro}, {Matejek}, {Morgan}, {Neben}, {Pan}, {Penna},
+  {Peterson}, {Su}, {Villasenor}, {Williams}, \& {Zhu}}]{zhe14}
+{Zheng}, H., {Tegmark}, M., {Buza}, V., {et~al.} 2014, \mnras, 445, 1084
+
+\end{thebibliography}
 

### 2016-03-25 ForegroundSimulations/ms.tex
Make updates suggested by Aaron Parsons
From bbb5b82 (fgsim):
====================

In eor.bib,

(*) Add WMAP9 and Planck references for cosmological parameters

In ms.tex,

(*) Make updates suggested by Aaron Parsons

--- 2016-03-23 ForegroundSimulations/ms.tex
@@
 
-Unaccounted systematics from foregrounds and instruments prevent current experiments from detecting redshifted 21~cm signal from the Epoch of Reionization (EoR).
-We identify spectral structures (chromaticity) in the antenna power pattern as one such systematic that significantly affects all EoR experiments.
-Increase in chromaticity of the antenna beam causes the already bright foreground power to leak well beyond ideal limits and contaminate the otherwise clean EoR signal modes.
+Unaccounted systematics from foregrounds and instruments limit sensitivity of current experiments from detecting redshifted 21~cm signal from the Epoch of Reionization (EoR).
+Upcoming experiments are faced with a challenge to deliver more collecting area per antenna element without degrading the data with systematics.
+This paper and its companions show that dishes are viable for achieving this balance using the Hydrogen Epoch of Reionization Array (HERA) as an example.
+In this paper, we specifically identify spectral systematics associated with the antenna power pattern as a significant detriment affecting all EoR experiments.
+Chromaticity of the antenna beam causes the already bright foreground power to leak well beyond ideal limits and contaminate the otherwise clean EoR signal modes.
 A primary source of this chromaticity is reflections in the antenna-feed assembly and between structures in neighboring antennas.
-Using precise foreground simulations taking wide-field effects into account, we provide a framework to set cosmologically-motivated design specifications on these reflections to prevent further EoR signal degradation.
-We use the Hydrogen Epoch of Reionization Array (HERA) as an example.
-Using a simple and yet high dynamic range spectral weighting scheme, we demonstrate that EoR detection using HERA will not be impeded by such spectral systematics even in a conservative scenario that does not perform removal of foregrounds.
+Using precise foreground simulations taking wide-field effects into account, we provide a framework to set cosmologically-motivated design specifications on these reflections to prevent further EoR signal degradation and show HERA will not be impeded by such spectral systematics.
+Using a simple and yet high dynamic range spectral weighting scheme, we demonstrate that even in a conservative scenario that does not perform removal of foregrounds, HERA will detect EoR signal in line-of-sight $k$-modes, $k_\parallel \gtrsim 0.2\,h$~Mpc$^{-1}$, with high significance.
 All baselines in a 19-element HERA layout are capable of detecting EoR over a substantial observing window on the sky.
@@
 Many of these instruments have sufficient sensitivity for a statistical detection of the EoR signal by estimating the spatial power spectrum of the redshifted H{\sc i} spin temperature fluctuations \citep{bea13,thy13}.
-These instruments are intended to be precursors and pathfinders to the next generation of low frequency radio observatories such as the Hydrogen Epoch of Reionization Array\footnote{\url{http://reionization.org/}} \citep[HERA;][]{deb16} and the Square Kilometre Array\footnote{\url{https://www.skatelescope.org/}} (SKA).
-These next-generation instruments will advance the capability from a mere statistical detection of the signal to a direct three-dimensional tomographic imaging of H{\sc i} from the EoR.
+These instruments are precursors and pathfinders to the next generation of low frequency radio observatories such as the Hydrogen Epoch of Reionization Array\footnote{\url{http://reionization.org/}} \citep[HERA;][]{deb16} and the Square Kilometre Array\footnote{\url{https://www.skatelescope.org/}} (SKA).
+These next-generation instruments will advance the capability from a statistical detection of the signal to a direct three-dimensional tomographic imaging of H{\sc i} from the EoR.
 
@@
 
-Despite attempts to exploit this knowledge about differences in spectral and spatial symmetry, first-generation experiments have at best only led to weak constraints on reionization models \citep{ali15,dil15,pob15}.
+% Despite attempts to exploit this knowledge about differences in spectral and spatial symmetry, first-generation experiments have at best only led to weak constraints on reionization models \citep{ali15,dil15,pob15}.
 This is because their sensitivity is primarily limited by instrumental and foreground systematics.
+The extreme dynamic range required to suppress foreground and instrument systematics demands high precision modeling of foregrounds as observed by modern wide-field instruments.
+
+Using this knowledge, experiments have begun constraining reionization models \citep{par14,ali15,pob15}.
+While this progress is encouraging, efforts are slowed by struggles to increase collecting area while contending with foreground and instrumental systematics.
 The extreme dynamic range required to suppress foreground and instrument systematics demands high precision modeling of foregrounds as observed by modern wide-field instruments.
@@
 
-In this paper, we explore a phenomenon that inherently extends foreground power beyond the {\it wedge}, namely, that arising from the chromaticity of the antenna power pattern.
+Along with companion papers \citep{ewa16,neb16,pat16}, we focus on determining whether larger antenna elements can be viable for EoR experiments.
+In this paper, we explore the impact of chromaticity in the antenna power pattern on extending foreground power beyond the {\it wedge}.
 While highlighting the importance of such instrumental systematics on future EoR experiments, we demonstrate that the current HERA instrument design will exceed these specifications to detect the EoR signal with high significance.
@@
 
-\citet{deb16} describe the HERA instrument in detail. We provide a summary of the instrument currently under construction on the South African SKA site.
+\citet{deb16} describe the instrument in detail while \citet{pob14} explored the range of astrophysical parameters that can be probed with HERA.
+We provide a summary of the instrument currently under construction on the South African SKA site.
 
@@
 
-HERA will deploy 14~m fixed zenith-pointing parabolic dishes that strike an optimal balance between sensitivity and systematics.
+HERA is deploying 14~m fixed zenith-pointing parabolic dishes that strike an optimal balance between sensitivity and systematics \citep[][and this paper]{ewa16,neb16,pat16}.
 The large collecting area of a HERA element yields $\approx 5$ times the sensitivity of an MWA tile and more than 20 times that of a PAPER element.
@@
 $P(\boldsymbol{b},k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.
-In this paper, we use $\Omega_\textrm{M}=0.27$, $\Omega_\Lambda=0.73$, $\Omega_\textrm{K}=1-\Omega_\textrm{M}-\Omega_\Lambda$, $H_0=100\,$km$\,$s$^{-1}\,$Mpc$^{-1}$.
+In this paper, we use $\Omega_\textrm{M}=0.27$, $\Omega_\Lambda=0.73$, $\Omega_\textrm{K}=1-\Omega_\textrm{M}-\Omega_\Lambda$, $H_0=100\,h\,$km$\,$s$^{-1}\,$Mpc$^{-1}$ \citep{wmap9cosmo}.
 \begin{align}
@@
 \end{align}
-is related to the cosmic volume probed by the instrument \citet{par14}.
+is related to the cosmic volume probed by the instrument \citep[see appendix of][]{par14}.
 
@@
 
-The equation for delay spectrum describes the mapping between sky location of a foreground object and delay.
+The equation for delay spectrum defines the interplay between foregrounds and antenna power pattern, and the mapping between geometric phases of baselines and delays.
+We discuss the spillover of foreground power beyond the horizon delay limits caused by the chromatic nature of the antenna power pattern.
+
+% The equation for delay spectrum describes the mapping between sky location of a foreground object and delay.
 The chromatic nature (variation with frequency) of the antenna power pattern appears multiplicatively in the frequency axis and thus results in convolving its delay response with that of the foregrounds and the geometric phases measured by the baseline vector.
@@
 Since our aim in this paper is to quantify EoR-foreground power ratio without employing any sophisticated {\it foreground removal} techniques, we turn our attention to {\it foreground avoidance} strategy that employs spectral weighting technique.
-Specific choices for spectral weighting function, $W(f)$, have been found to be effective in reducing foreground contamination by many orders of magnitude \citep{thy13} and is regularly used in EoR data analysis \citep{par12a}.
+Specific choices for spectral weighting function, $W(f)$, have been found to be effective in reducing foreground contamination by many orders of magnitude \citep{thy13} and is regularly used in redshifted 21~cm data analysis \citep{par12a,par12b}.
 For instance, a {\it Blackman-Harris} function \citep{har78} has a dynamic range of $\sim$100 -- 120~dB in delay power spectrum and a reduced effective bandwidth, with:
@@
 where, $B$ denotes the end-to-end range of the observing band, $1-\epsilon$ is the loss in overall spectral sensitivity and $B_\textrm{eff}$ is the effective bandwidth.
-For a {\it Blackman-Harris} window function denoted by $W_\textrm{BH}(f)$, $\epsilon \approx 50\%$.
+The {\it noise equivalent width} is defined as $w_\textrm{ne}\equiv \sum_i |\widetilde{W}(\tau_i)|^2 / |\widetilde{W}(0)|^2$.
+For a {\it Blackman-Harris} window function denoted by $W_\textrm{BH}(f)$, $\epsilon \approx 50\%$ and $w_\textrm{ne} \approx 2$.
 % Hence, the window spans a total of $2N$ frequency channels each of width $\Delta f$ to have $B_\textrm{eff} \approx N\,\Delta f$.
@@
 Fig.~\ref{fig:window-functions} shows the {\it Blackman-Harris} window (gray) and  the window in equation~\ref{eqn:bhw2} (black) in frequency (top) and their power responses in delay (bottom).
-In its Fourier domain, this window has a response obtained by squaring the {\it Blackman-Harris} window response and thus increases the dynamic range further in the power response by another 100 -- 120~dB with $\epsilon\approx 42\%$.
+In its Fourier domain, this window has a response obtained by squaring the {\it Blackman-Harris} window response and thus increases the dynamic range further in the power response by another 100 -- 120~dB with $\epsilon\approx 42\%$ and $w_\textrm{ne} \approx 2.88$.
 
@@
 
-This clearly demonstrates that higher the beam chromaticity, the farther the foreground contamination inherently extends along $k_\parallel$.
+This clearly demonstrates that with increasing beam chromaticity, the foreground contamination inherently extends farther along $k_\parallel$.
 Thus, the chromaticity of antenna beam needs to be controlled in EoR experiments to keep the foreground systematics sufficiently low.
@@
 These delay shifts introduce ripples in the spectrum.
-The net chromaticity in the measurements is the product of spectral structure arising out of the intrinsic nature of foreground emission, the baseline- and position-dependent frequency structure of the geometric phases, the spectral features in the antenna power pattern besides any other spectral structures in the instrument unaccounted for.
-In the Fourier domain these factors have a convolving effect.
-In order to isolate the requirements on beam chromaticity from other sources of chromaticity, we start with an antenna beam in which those spectral structures are absent but the intrinsic chromaticity of foregrounds and the geometric phases of baselines are included.
+The net chromaticity in the measurements is the product of spectral structure arising out of the intrinsic nature of foreground emission, $I(\hat{\boldsymbol{s}},f)$, the baseline- and position-dependent frequency structure of the geometric phases, $e^{-i2\pi f\frac{\boldsymbol{b}\cdot\hat{\boldsymbol{s}}}{c}}$, the spectral features in the antenna power pattern, $A(\hat{\boldsymbol{s}},f)$, besides any other spectral structures in the instrument unaccounted for.
+In $P(\boldsymbol{b},k_\parallel)$ defined in the Fourier domain, these factors have a convolving effect.
+
+From these factors, we isolate here the effects of chromaticity in the antenna power pattern caused by reflections in antenna structures and signal paths.
+And, we devise a cosmologically-motivated method to set design requirements on suppressing reflections in the instrument.
 
@@
 The angular brackets denote averaging over baseline vectors of the specified length, and a local sidereal time (LST) range.
-Thus, $\Gamma_{k_\textrm{p}}(\tau)$ is determined by the requirement that the reflected foreground power obtained by shifting in delay lies below the EoR H{\sc i} signal power in line-of-sight spatial scales of interest, $|k_\parallel|>k_\textrm{p}$.
+
+We assume the interpretation that reflections cause additional spectral structures in the antenna power pattern in which they would be absent otherwise.
+Thus, we use an antenna power pattern in which those spectral structures from reflections which we are interested in addressing are absent but the intrinsic chromaticity of foregrounds and the geometric phases of baselines are included.
+$\Gamma_{k_\textrm{p}}(\tau)$ is determined by the requirement that the reflected foreground power so obtained, after shifting in delay, lies below the EoR H{\sc i} signal power in line-of-sight spatial scales of interest, $|k_\parallel|>k_\textrm{p}$.
+Thus, by disentangling spectral systematics inherent in the antenna power pattern from the overall EoR-foreground dynamic range, a design requirement that sets a limit on that systematic is obtained.
 
@@
 For reflections caused by dish-feed assembly, we use $P_\textrm{FG}(k_\parallel)$ obtained with the achromatic beam model on 14.6~m baselines in a 0--12 hr LST range.
+In this instance, we assume dish-feed reflections predominantly imprint chromaticity in an otherwise achromatic antenna power pattern and $\Gamma_{k_\textrm{p}}(\tau)$ is interpreted as the design goal for attenuating these reflections.
+These reflections are primarily caused in the dish-feed assembly and to some extent in other subsystems not accounted for.
 Fig.~\ref{fig:fg-reflections-achrmbeam} shows $\Gamma_{k_\textrm{p}}(\tau)$ (in dB) for $k_\textrm{p}$ chosen to be 0.1~$h$~Mpc$^{-1}$ (solid), 0.15~$h$~Mpc$^{-1}$ (dashed), and 0.2~$h$~Mpc$^{-1}$ (dotted).
 These curves set an upper limit for the reflected foreground power to lie below the EoR H{\sc i} signal power as a function of delays.
-These reflections are primarily caused in the dish-feed assembly and to some extent in other subsystems not accounted for.
 It implies that if attenuated to levels that lie in the regions below the different shaded regions, such spectral systematics in the instrument will not hinder detection of EoR in those corresponding $k_\parallel$-modes of interest.
@@
 For instance, the attenuation required is $\gtrsim 54$~dB at $\sim 200$~ns for $k_\textrm{p}=0.1\,h$~Mpc$^{-1}$, $\gtrsim 56$~dB at $\sim 300$~ns for $k_\textrm{p}=0.15\,h$~Mpc$^{-1}$ and $\gtrsim 58$~dB at $\sim 400$~ns for $k_\textrm{p}=0.2\,h$~Mpc$^{-1}$.
-Measurements are underway \citep{pat16} to confirm that the return losses in the HERA design lie well within the regions excluded by the shaded regions.
+Measurements are underway \citep{pat16} to confirm that the return losses in the HERA design lie within the regions excluded by the shaded regions.
 
@@
 Similarly, for reflections arising out of structures and interfaces across different antennas, we use $P_\textrm{FG}(k_\parallel)$ obtained with the simulated chromatic and {\it Airy} antenna beams on 14.6~m baselines.
-These beams do not include spectral features from antenna-to-antenna reflections.
-Thus $\Gamma_{k_\textrm{p}}(\tau)$ provides lower limit for attenuation of antenna-to-antenna reflections.
+The simulated chromatic pattern in fact includes explicit simulations of reflections between structures within an antenna subsystem while the {\it Airy} pattern is assumed to include these effects.
+But both these beams do not include spectral features from antenna-to-antenna reflections.
+Thus $\Gamma_{k_\textrm{p}}(\tau)$ provides lower limit for attenuation of such antenna-to-antenna reflections.
 Fig.~\ref{fig:fg-reflections} is similar to Fig.~\ref{fig:fg-reflections-achrmbeam} with constraints for values of $k_\textrm{p}$ chosen to be 0.1~$h$~Mpc$^{-1}$ (left), 0.15~$h$~Mpc$^{-1}$ (middle), and 0.2~$h$~Mpc$^{-1}$ (right).
@@
 As a result, the elbow-shaped design constraints shift upward and leftward.
-For instance, in the presence of dish-feed reflections, it will still be feasible to probe $k_\parallel > 0.15\,h$~Mpc$^{-1}$ with the 58.4~m baselines but not other larger scales.
+For instance, in the presence of dish-feed reflections, it will still be feasible to probe only $k_\parallel > 0.15\,h$~Mpc$^{-1}$ with the 58.4~m baselines.
 
@@
 
-We note that the inevitable reflections in the antenna-feed assembly and between reflecting structures across multiple antennas are also significant factors that contaminate the cosmological signal in $k_\parallel$-modes in the {\it EoR window}.
+We note that inevitable reflections in the antenna-feed assembly and between reflecting structures across multiple antennas are also significant factors that contaminate the cosmological signal in $k_\parallel$-modes in the {\it EoR window}.
 Using a novel approach, we provide a formalism to set cosmologically-motivated design requirements directly on the level of suppression required on these reflections in the instrument.
-% Ongoing reflectometry studies clearly indicate HERA will comfortably achieve the design limits prescribed here.
+This provides a way to set goals on antenna performance and evaluate antenna designs that deliver larger collecting area per antenna.
 
-By accounting for these instrumental systematics, if data is not limited by thermal noise, we demonstrate that HERA should detect EoR with high significance with a simple spectral weighting even under a conservative analysis criterion that does not involve {\it foreground removal} strategies.
+By accounting for these instrumental systematics, if data is not limited by thermal noise, we demonstrate that HERA should detect EoR in $k_\parallel\gtrsim 0.2\,h$~Mpc$^{-1}$ with high significance with a simple spectral weighting even under a conservative analysis criterion that does not involve {\it foreground removal} strategies.
 All baselines of HERA-19 will not only detect but also help in filtering highly likely EoR models.
@@
 We are also investigating advanced strategies for foreground removal that will robustly eliminate these systematics further.
+Advances in calibration, foreground modeling and subtraction will improve the performance listed here.
 More optimal analysis techniques and further design improvements will make HERA not only clear the obstacles limiting first-generation experiments but also become transformational for next generation of low-frequency cosmology experiments.
@@
 We thank Zaki Ali, Adam Beardsley, and Daniel Jacobs for their valuable inputs during the preparation of this manuscript.
+This work was supported by the U.S.
+National Science Foundation (NSF) through awards AST-1440343 and AST-1410719.
+ARP acknowledges support from NSF CAREER award 1352519.
+AEW acknowledges support from NSF Graduate Research Fellowship under grant 1122374.
 

### 2016-03-26 ForegroundSimulations/ms.tex
Incorporate Judd's suggestions in Abstract
From 4b3c3b1 (fgsim):
====================

In ms.tex,

(*) Incorporate Judd's suggestions in Abstract

@@
 
-Unaccounted systematics from foregrounds and instruments limit sensitivity of current experiments from detecting redshifted 21~cm signal from the Epoch of Reionization (EoR).
+Unaccounted for systematics from foregrounds and instruments limit the sensitivity of current experiments from detecting redshifted 21~cm signals from the Epoch of Reionization (EoR).
 Upcoming experiments are faced with a challenge to deliver more collecting area per antenna element without degrading the data with systematics.
 This paper and its companions show that dishes are viable for achieving this balance using the Hydrogen Epoch of Reionization Array (HERA) as an example.
-In this paper, we specifically identify spectral systematics associated with the antenna power pattern as a significant detriment affecting all EoR experiments.
-Chromaticity of the antenna beam causes the already bright foreground power to leak well beyond ideal limits and contaminate the otherwise clean EoR signal modes.
+Here, we specifically identify spectral systematics associated with the antenna power pattern as a significant detriment to all EoR experiments which causes the already bright foreground power to leak well beyond ideal limits and contaminate the otherwise clean EoR signal modes.
 A primary source of this chromaticity is reflections in the antenna-feed assembly and between structures in neighboring antennas.
-Using precise foreground simulations taking wide-field effects into account, we provide a framework to set cosmologically-motivated design specifications on these reflections to prevent further EoR signal degradation and show HERA will not be impeded by such spectral systematics.
-Using a simple and yet high dynamic range spectral weighting scheme, we demonstrate that even in a conservative scenario that does not perform removal of foregrounds, HERA will detect EoR signal in line-of-sight $k$-modes, $k_\parallel \gtrsim 0.2\,h$~Mpc$^{-1}$, with high significance.
+Using precise foreground simulations taking wide-field effects into account, we provide a framework to set cosmologically-motivated design specifications on these reflections to prevent further EoR signal degradation.
+We show HERA will not be impeded by such spectral systematics and demonstrate that even in a conservative scenario that does not perform removal of foregrounds, HERA will detect EoR signal in line-of-sight $k$-modes, $k_\parallel \gtrsim 0.2\,h$~Mpc$^{-1}$, with high significance.
 All baselines in a 19-element HERA layout are capable of detecting EoR over a substantial observing window on the sky.
@@
 
-\citet{deb16} describe the instrument in detail while \citet{pob14} explored the range of astrophysical parameters that can be probed with HERA.
+\citet{deb16} describe the HERA instrument in detail while \citet{pob14} explored the range of astrophysical parameters that HERA can probe.
 We provide a summary of the instrument currently under construction on the South African SKA site.
@@
 
-We assume the interpretation that reflections cause additional spectral structures in the antenna power pattern in which they would be absent otherwise.
+We adopt the interpretation that reflections cause additional spectral structures in the antenna power pattern in which they would be absent otherwise.
 Thus, we use an antenna power pattern in which those spectral structures from reflections which we are interested in addressing are absent but the intrinsic chromaticity of foregrounds and the geometric phases of baselines are included.
@@
 Similarly, for reflections arising out of structures and interfaces across different antennas, we use $P_\textrm{FG}(k_\parallel)$ obtained with the simulated chromatic and {\it Airy} antenna beams on 14.6~m baselines.
-The simulated chromatic pattern in fact includes explicit simulations of reflections between structures within an antenna subsystem while the {\it Airy} pattern is assumed to include these effects.
+The simulated chromatic pattern in fact includes explicit simulations of reflections between structures within an antenna subsystem.
+We assume the same is true for the {\it Airy} pattern as well.
 But both these beams do not include spectral features from antenna-to-antenna reflections.

### 2016-03-28 ForegroundSimulations/ms.tex
Incorporate Aaron EW's comments in Abstract
From dbd4f78 (fgsim):
====================

In ms.tex,

(*) Incorporate Aaron EW's comments in Abstract

@@
 
-Unaccounted for systematics from foregrounds and instruments limit the sensitivity of current experiments from detecting redshifted 21~cm signals from the Epoch of Reionization (EoR).
+Unaccounted for systematics from foregrounds and instruments can severely limit the sensitivity of current experiments from detecting redshifted 21~cm signals from the Epoch of Reionization (EoR).
 Upcoming experiments are faced with a challenge to deliver more collecting area per antenna element without degrading the data with systematics.

### 2016-03-29 ForegroundSimulations/ms.tex
Add numbered figures to repo
From ce9972b (fgsim):
====================

(*) Add numbered figures to repo

In ms.tex,

(*) Add commented lines for numbered figures

@@
   \centering
-  \includegraphics[width=\linewidth]{window_function_modifications.eps}
+  % \includegraphics[width=\linewidth]{window_function_modifications.eps}
+  \includegraphics[width=\linewidth]{f1.eps}
   \caption{Choices for spectral weighting functions, $W(f)$ ({\it top}) and their delay power spectrum responses, $|\widetilde{W}(\tau)|^2$ ({\it bottom}).
@@
   \centering
-  \includegraphics[width=\linewidth]{asm_foreground_eor_beam_chromaticity_fullband_bhw2.0.eps}
+  % \includegraphics[width=\linewidth]{asm_foreground_eor_beam_chromaticity_fullband_bhw2.0.eps}
+  \includegraphics[width=\linewidth]{f2.eps}
   \caption{Foreground delay power spectra in units of K$^2 (h^{-1}$~Mpc$)^3$ on unique baseline lengths of HERA-19 at arbitrary sky pointings.
@@
   \centering
-\includegraphics[width=\linewidth]{spec_on_achrmbeam_foreground_reflected_power_21cmfast_14.6m_150.0_MHz_subband_v2.eps}
+  % \includegraphics[width=\linewidth]{spec_on_achrmbeam_foreground_reflected_power_21cmfast_14.6m_150.0_MHz_subband_v2.eps}
+  \includegraphics[width=\linewidth]{f3.eps}
   \caption{Minimum required attenuation (in dB) for internal dish-feed reflections required to keep the reflected foreground power below EoR H{\sc i} signal power for all $k_\parallel$-modes greater than $0.1\,h$~Mpc$^{-1}$ (solid), $0.15\,h$~Mpc$^{-1}$ (dashed) and $0.2\,h$~Mpc$^{-1}$ (dotted).
@@
   \centering
-\includegraphics[width=\linewidth]{spec_on_foreground_reflected_power_21cmfast_14.6m_150.0_MHz_subband_v2.eps}
+  % \includegraphics[width=\linewidth]{spec_on_foreground_reflected_power_21cmfast_14.6m_150.0_MHz_subband_v2.eps}
+  \includegraphics[width=\linewidth]{f4.eps}
   \caption{Minimum required attenuation (in dB) for antenna-to-antenna reflections to keep reflected foreground power below EoR H{\sc i} signal power for all $k_\parallel$-modes greater than $0.1\,h$~Mpc$^{-1}$ (left), $0.15\,h$~Mpc$^{-1}$ (middle) and $0.2\,h$~Mpc$^{-1}$ (right).
@@
   \centering
-\subfloat[][150~MHz subband ($z \approx 8.47$)]{\label{fig:asm-dps-beam-chromaticity-baselines-150-subband}\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_150.0_MHz_subband_win_method_bhw2.0.eps}} \\
-\subfloat[][170~MHz subband ($z \approx 7.36$)]{\label{fig:asm-dps-beam-chromaticity-baselines-170-subband}\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_170.0_MHz_subband_win_method_bhw2.0.eps}}
+  % \subfloat[][150~MHz subband ($z \approx 8.47$)]{\label{fig:asm-dps-beam-chromaticity-baselines-150-subband}\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_150.0_MHz_subband_win_method_bhw2.0.eps}} \\
+  % \subfloat[][170~MHz subband ($z \approx 7.36$)]{\label{fig:asm-dps-beam-chromaticity-baselines-170-subband}\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_170.0_MHz_subband_win_method_bhw2.0.eps}}
+  \subfloat[][150~MHz subband ($z \approx 8.47$)]{\label{fig:asm-dps-beam-chromaticity-baselines-150-subband}\includegraphics[width=\linewidth]{f5a.eps}} \\
+  \subfloat[][170~MHz subband ($z \approx 7.36$)]{\label{fig:asm-dps-beam-chromaticity-baselines-170-subband}\includegraphics[width=\linewidth]{f5b.eps}}
   \caption{EoR signal and foreground delay power spectrum in units of K$^2 (h^{-1}$~Mpc$)^3$ in 150~MHz (top) and 170~MHz (bottom) subbands ($B_\textrm{eff}=10$~MHz) on eight unique baseline lengths of HERA-19 at arbitrary sky pointings.
@@
   \centering
-\subfloat[][EoR model 1, 150~MHz subband ]{\label{fig:21cmfast-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_150.0_MHz_subband.eps}}
-\subfloat[][EoR model 2, 150~MHz subband ]{\label{fig:lidz-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_150.0_MHz_subband.eps}} \\
-\subfloat[][EoR model 1, 170~MHz subband ]{\label{fig:21cmfast-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_170.0_MHz_subband.eps}}
-\subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_170.0_MHz_subband.eps}}
+  % \subfloat[][EoR model 1, 150~MHz subband ]{\label{fig:21cmfast-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_150.0_MHz_subband.eps}}
+  % \subfloat[][EoR model 2, 150~MHz subband ]{\label{fig:lidz-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_150.0_MHz_subband.eps}} \\
+  % \subfloat[][EoR model 1, 170~MHz subband ]{\label{fig:21cmfast-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_170.0_MHz_subband.eps}}
+  % \subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_170.0_MHz_subband.eps}}
+  \subfloat[][EoR model 1, 150~MHz subband ]{\label{fig:21cmfast-fg-ratio-150}\includegraphics[width=0.45\linewidth]{f6a.eps}}
+  \subfloat[][EoR model 2, 150~MHz subband ]{\label{fig:lidz-fg-ratio-150}\includegraphics[width=0.45\linewidth]{f6b.eps}} \\
+  \subfloat[][EoR model 1, 170~MHz subband ]{\label{fig:21cmfast-fg-ratio-170}\includegraphics[width=0.45\linewidth]{f6c.eps}}
+  \subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{f6d.eps}}
   \caption{Worst case EoR-foreground dynamic range, $\rho(\boldsymbol{b},f_0,\alpha)$, in {\it foreground avoidance} modes for different HERA-19 baselines as a function of RA ($\alpha$) of pointing on the sky.
@@
 
-% \par\bigskip
 \bibliographystyle{apj}
-\bibliography{eor}
+% \bibliography{eor}
+\begin{thebibliography}{}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Ali} {et~al.}(2008){Ali}, {Bharadwaj}, \& {Chengalur}}]{ali08}
+{Ali}, S.~S., {Bharadwaj}, S., \& {Chengalur}, J.~N. 2008, \mnras, 385, 2166
+
+\bibitem[{{Ali} {et~al.}(2015){Ali}, {Parsons}, {Zheng}, {Pober}, {Liu},
+  {Aguirre}, {Bradley}, {Bernardi}, {Carilli}, {Cheng}, {DeBoer}, {Dexter},
+  {Grobbelaar}, {Horrell}, {Jacobs}, {Klima}, {MacMahon}, {Maree}, {Moore},
+  {Razavi}, {Stefan}, {Walbrugh}, \& {Walker}}]{ali15}
+{Ali}, Z.~S., {Parsons}, A.~R., {Zheng}, H., {et~al.} 2015, \apj, 809, 61
+
+\bibitem[{{Beardsley} {et~al.}(2013){Beardsley}, {Hazelton}, {Morales},
+  {Arcus}, {Barnes}, {Bernardi}, {Bowman}, {Briggs}, {Bunton}, {Cappallo},
+  {Corey}, {Deshpande}, {deSouza}, {Emrich}, {Gaensler}, {Goeke}, {Greenhill},
+  {Herne}, {Hewitt}, {Johnston-Hollitt}, {Kaplan}, {Kasper}, {Kincaid},
+  {Koenig}, {Kratzenberg}, {Lonsdale}, {Lynch}, {McWhirter}, {Mitchell},
+  {Morgan}, {Oberoi}, {Ord}, {Pathikulangara}, {Prabu}, {Remillard}, {Rogers},
+  {Roshi}, {Salah}, {Sault}, {Udaya}, {Srivani}, {Stevens}, {Subrahmanyan},
+  {Tingay}, {Wayth}, {Waterson}, {Webster}, {Whitney}, {Williams}, {Williams},
+  \& {Wyithe}}]{bea13}
+{Beardsley}, A.~P., {Hazelton}, B.~J., {Morales}, M.~F., {et~al.} 2013, \mnras,
+  429, L5
+
+\bibitem[{{Bernardi} {et~al.}(2009){Bernardi}, {de Bruyn}, {Brentjens},
+  {Ciardi}, {Harker}, {Jeli{\'c}}, {Koopmans}, {Labropoulos}, {Offringa},
+  {Pandey}, {Schaye}, {Thomas}, {Yatawatta}, \& {Zaroubi}}]{ber09}
+{Bernardi}, G., {de Bruyn}, A.~G., {Brentjens}, M.~A., {et~al.} 2009, \aap,
+  500, 965
+
+\bibitem[{{Bernardi} {et~al.}(2010){Bernardi}, {de Bruyn}, {Harker},
+  {Brentjens}, {Ciardi}, {Jeli{\'c}}, {Koopmans}, {Labropoulos}, {Offringa},
+  {Pandey}, {Schaye}, {Thomas}, {Yatawatta}, \& {Zaroubi}}]{ber10}
+{Bernardi}, G., {de Bruyn}, A.~G., {Harker}, G., {et~al.} 2010, \aap, 522, A67
+
+\bibitem[{{Bock} {et~al.}(1999){Bock}, {Large}, \& {Sadler}}]{boc99}
+{Bock}, D.~C.-J., {Large}, M.~I., \& {Sadler}, E.~M. 1999, \aj, 117, 1578
+
+\bibitem[{{Bowman} {et~al.}(2009){Bowman}, {Morales}, \& {Hewitt}}]{bow09}
+{Bowman}, J.~D., {Morales}, M.~F., \& {Hewitt}, J.~N. 2009, \apj, 695, 183
+
+\bibitem[{{Bowman} \& {Rogers}(2010)}]{bow10}
+{Bowman}, J.~D., \& {Rogers}, A.~E.~E. 2010, \nat, 468, 796
+
+\bibitem[{{Bowman} {et~al.}(2013){Bowman}, {Cairns}, {Kaplan}, {Murphy},
+  {Oberoi}, {Staveley-Smith}, {Arcus}, {Barnes}, {Bernardi}, {Briggs}, {Brown},
+  {Bunton}, {Burgasser}, {Cappallo}, {Chatterjee}, {Corey}, {Coster},
+  {Deshpande}, {deSouza}, {Emrich}, {Erickson}, {Goeke}, {Gaensler},
+  {Greenhill}, {Harvey-Smith}, {Hazelton}, {Herne}, {Hewitt},
+  {Johnston-Hollitt}, {Kasper}, {Kincaid}, {Koenig}, {Kratzenberg}, {Lonsdale},
+  {Lynch}, {Matthews}, {McWhirter}, {Mitchell}, {Morales}, {Morgan}, {Ord},
+  {Pathikulangara}, {Prabu}, {Remillard}, {Robishaw}, {Rogers}, {Roshi},
+  {Salah}, {Sault}, {Shankar}, {Srivani}, {Stevens}, {Subrahmanyan}, {Tingay},
+  {Wayth}, {Waterson}, {Webster}, {Whitney}, {Williams}, {Williams}, \&
+  {Wyithe}}]{bow13}
+{Bowman}, J.~D., {Cairns}, I., {Kaplan}, D.~L., {et~al.} 2013, \pasa, 30, 31
+
+\bibitem[{{Condon} {et~al.}(1998){Condon}, {Cotton}, {Greisen}, {Yin},
+  {Perley}, {Taylor}, \& {Broderick}}]{con98}
+{Condon}, J.~J., {Cotton}, W.~D., {Greisen}, E.~W., {et~al.} 1998, \aj, 115,
+  1693
+
+\bibitem[{{Datta} {et~al.}(2010){Datta}, {Bowman}, \& {Carilli}}]{dat10}
+{Datta}, A., {Bowman}, J.~D., \& {Carilli}, C.~L. 2010, \apj, 724, 526
+
+\bibitem[{{de Oliveira-Costa} {et~al.}(2008){de Oliveira-Costa}, {Tegmark},
+  {Gaensler}, {Jonas}, {Landecker}, \& {Reich}}]{deo08}
+{de Oliveira-Costa}, A., {Tegmark}, M., {Gaensler}, B.~M., {et~al.} 2008,
+  \mnras, 388, 247
+
+\bibitem[{DeBoer {et~al.}(2016)}]{deb16}
+DeBoer, D., {et~al.} 2016, in preparation
+
+\bibitem[{{Di Matteo} {et~al.}(2002){Di Matteo}, {Perna}, {Abel}, \&
+  {Rees}}]{dim02}
+{Di Matteo}, T., {Perna}, R., {Abel}, T., \& {Rees}, M.~J. 2002, \apj, 564, 576
+
+\bibitem[{Dillon {et~al.}(2013)Dillon, Liu, \& Tegmark}]{dil13}
+Dillon, J.~S., Liu, A., \& Tegmark, M. 2013, Phys. Rev. D, 87, 043005
+
+\bibitem[{{Dillon} \& {Parsons}(2016)}]{dil16}
+{Dillon}, J.~S., \& {Parsons}, A.~R. 2016, ArXiv e-prints, arXiv:1602.06259
+
+\bibitem[{{Dillon} {et~al.}(2014){Dillon}, {Liu}, {Williams}, {Hewitt},
+  {Tegmark}, {Morgan}, {Levine}, {Morales}, {Tingay}, {Bernardi}, {Bowman},
+  {Briggs}, {Cappallo}, {Emrich}, {Mitchell}, {Oberoi}, {Prabu}, {Wayth}, \&
+  {Webster}}]{dil14}
+{Dillon}, J.~S., {Liu}, A., {Williams}, C.~L., {et~al.} 2014, \prd, 89, 023002
+
+\bibitem[{{Ewall-Wice} {et~al.}(2016){Ewall-Wice}, {Bradley}, {DeBoer},
+  {Hewitt}, {Parsons}, {Aguirre}, {Ali}, {Bowman}, {Cheng}, {Neben}, {Patra},
+  {Thyagarajan}, {Venter}, {de Lera Acedo}, {Dillon}, {Doolittle}, {Egan},
+  {Hendrick}, {Klima}, {Kohn}, {Schaffner}, {Shelton}, {Saliwanchik},
+  {Tegmark}, {Taylor}, {Taylor}, \& {Wirt}}]{ewa16}
+{Ewall-Wice}, A., {Bradley}, R., {DeBoer}, D., {et~al.} 2016, ArXiv e-prints,
+  arXiv:1602.06277
+
+\bibitem[{{Furlanetto} \& {Briggs}(2004)}]{fur04b}
+{Furlanetto}, S.~R., \& {Briggs}, F.~H. 2004, \nar, 48, 1039
+
+\bibitem[{{Furlanetto} {et~al.}(2006){Furlanetto}, {Oh}, \& {Briggs}}]{fur06}
+{Furlanetto}, S.~R., {Oh}, S.~P., \& {Briggs}, F.~H. 2006, \physrep, 433, 181
+
+\bibitem[{{Furlanetto} {et~al.}(2004){Furlanetto}, {Zaldarriaga}, \&
+  {Hernquist}}]{fur04a}
+{Furlanetto}, S.~R., {Zaldarriaga}, M., \& {Hernquist}, L. 2004, \apj, 613, 1
+
+\bibitem[{{Ghosh} {et~al.}(2012){Ghosh}, {Prasad}, {Bharadwaj}, {Ali}, \&
+  {Chengalur}}]{gho12}
+{Ghosh}, A., {Prasad}, J., {Bharadwaj}, S., {Ali}, S.~S., \& {Chengalur}, J.~N.
+  2012, \mnras, 426, 3295
+
+\bibitem[{{Gleser} {et~al.}(2008){Gleser}, {Nusser}, \& {Benson}}]{gle08}
+{Gleser}, L., {Nusser}, A., \& {Benson}, A.~J. 2008, \mnras, 391, 383
+
+\bibitem[{{Harris}(1978)}]{har78}
+{Harris}, F.~J. 1978, IEEE Proceedings, 66, 51
+
+\bibitem[{{Hinshaw} {et~al.}(2013){Hinshaw}, {Larson}, {Komatsu}, {Spergel},
+  {Bennett}, {Dunkley}, {Nolta}, {Halpern}, {Hill}, {Odegard}, {Page}, {Smith},
+  {Weiland}, {Gold}, {Jarosik}, {Kogut}, {Limon}, {Meyer}, {Tucker}, {Wollack},
+  \& {Wright}}]{wmap9cosmo}
+{Hinshaw}, G., {Larson}, D., {Komatsu}, E., {et~al.} 2013, \apjs, 208, 19
+
+\bibitem[{{Iliev} {et~al.}(2002){Iliev}, {Shapiro}, {Ferrara}, \&
+  {Martel}}]{ili02}
+{Iliev}, I.~T., {Shapiro}, P.~R., {Ferrara}, A., \& {Martel}, H. 2002, \apjl,
+  572, L123
+
+\bibitem[{{Lidz} {et~al.}(2008){Lidz}, {Zahn}, {McQuinn}, {Zaldarriaga}, \&
+  {Hernquist}}]{lid08}
+{Lidz}, A., {Zahn}, O., {McQuinn}, M., {Zaldarriaga}, M., \& {Hernquist}, L.
+  2008, \apj, 680, 962
+
+\bibitem[{{Liu} {et~al.}(2014{\natexlab{a}}){Liu}, {Parsons}, \&
+  {Trott}}]{liu14a}
+{Liu}, A., {Parsons}, A.~R., \& {Trott}, C.~M. 2014{\natexlab{a}}, \prd, 90,
+  023018
+
+\bibitem[{{Liu} {et~al.}(2014{\natexlab{b}}){Liu}, {Parsons}, \&
+  {Trott}}]{liu14b}
+---. 2014{\natexlab{b}}, \prd, 90, 023019
+
+\bibitem[{{Liu} \& {Tegmark}(2011)}]{liu11}
+{Liu}, A., \& {Tegmark}, M. 2011, \prd, 83, 103006
+
+\bibitem[{{Liu} {et~al.}(2009){Liu}, {Tegmark}, {Bowman}, {Hewitt}, \&
+  {Zaldarriaga}}]{liu09}
+{Liu}, A., {Tegmark}, M., {Bowman}, J., {Hewitt}, J., \& {Zaldarriaga}, M.
+  2009, \mnras, 398, 401
+
+\bibitem[{{Lonsdale} {et~al.}(2009){Lonsdale}, {Cappallo}, {Morales}, {Briggs},
+  {Benkevitch}, {Bowman}, {Bunton}, {Burns}, {Corey}, {Desouza}, {Doeleman},
+  {Derome}, {Deshpande}, {Gopala}, {Greenhill}, {Herne}, {Hewitt}, {Kamini},
+  {Kasper}, {Kincaid}, {Kocz}, {Kowald}, {Kratzenberg}, {Kumar}, {Lynch},
+  {Madhavi}, {Matejek}, {Mitchell}, {Morgan}, {Oberoi}, {Ord},
+  {Pathikulangara}, {Prabu}, {Rogers}, {Roshi}, {Salah}, {Sault}, {Shankar},
+  {Srivani}, {Stevens}, {Tingay}, {Vaccarella}, {Waterson}, {Wayth}, {Webster},
+  {Whitney}, {Williams}, \& {Williams}}]{lon09}
+{Lonsdale}, C.~J., {Cappallo}, R.~J., {Morales}, M.~F., {et~al.} 2009, IEEE
+  Proceedings, 97, 1497
+
+\bibitem[{{Madau} {et~al.}(1997){Madau}, {Meiksin}, \& {Rees}}]{mad97}
+{Madau}, P., {Meiksin}, A., \& {Rees}, M.~J. 1997, \apj, 475, 429
+
+\bibitem[{{Mauch} {et~al.}(2003){Mauch}, {Murphy}, {Buttery}, {Curran},
+  {Hunstead}, {Piestrzynski}, {Robertson}, \& {Sadler}}]{mau03}
+{Mauch}, T., {Murphy}, T., {Buttery}, H.~J., {et~al.} 2003, \mnras, 342, 1117
+
+\bibitem[{{McQuinn} {et~al.}(2006){McQuinn}, {Zahn}, {Zaldarriaga},
+  {Hernquist}, \& {Furlanetto}}]{mcq06}
+{McQuinn}, M., {Zahn}, O., {Zaldarriaga}, M., {Hernquist}, L., \& {Furlanetto},
+  S.~R. 2006, \apj, 653, 815
+
+\bibitem[{{Mesinger} {et~al.}(2011){Mesinger}, {Furlanetto}, \& {Cen}}]{mes11}
+{Mesinger}, A., {Furlanetto}, S., \& {Cen}, R. 2011, \mnras, 411, 955
+
+\bibitem[{{Morales} {et~al.}(2006){Morales}, {Bowman}, \& {Hewitt}}]{mor06}
+{Morales}, M.~F., {Bowman}, J.~D., \& {Hewitt}, J.~N. 2006, \apj, 648, 767
+
+\bibitem[{{Morales} {et~al.}(2012){Morales}, {Hazelton}, {Sullivan}, \&
+  {Beardsley}}]{mor12}
+{Morales}, M.~F., {Hazelton}, B., {Sullivan}, I., \& {Beardsley}, A. 2012,
+  \apj, 752, 137
+
+\bibitem[{{Morales} \& {Hewitt}(2004)}]{mor04}
+{Morales}, M.~F., \& {Hewitt}, J. 2004, \apj, 615, 7
+
+\bibitem[{{Neben} {et~al.}(2016){Neben}, {Bradley}, {Hewitt}, {DeBoer},
+  {Parsons}, {Aguirre}, {Ali}, {Cheng}, {Ewall-Wice}, {Patra}, {Thyagarajan},
+  {Bowman}, {Dickenson}, {Dillon}, {Doolittle}, {Egan}, {Hedrick}, {Jacobs},
+  {Kohn}, {Klima}, {Moodley}, {Saliwanchik}, {Schaffner}, {Shelton}, {Taylor},
+  {Taylor}, {Tegmark}, {Wirt}, \& {Zheng}}]{neb16}
+{Neben}, A.~R., {Bradley}, R.~F., {Hewitt}, J.~N., {et~al.} 2016, ArXiv
+  e-prints, arXiv:1602.03887
+
+\bibitem[{{Paciga} {et~al.}(2013){Paciga}, {Albert}, {Bandura}, {Chang},
+  {Gupta}, {Hirata}, {Odegova}, {Pen}, {Peterson}, {Roy}, {Shaw}, {Sigurdson},
+  \& {Voytek}}]{pac13}
+{Paciga}, G., {Albert}, J.~G., {Bandura}, K., {et~al.} 2013, \mnras, 433, 639
+
+\bibitem[{{Parsons} {et~al.}(2012{\natexlab{a}}){Parsons}, {Pober}, {McQuinn},
+  {Jacobs}, \& {Aguirre}}]{par12a}
+{Parsons}, A., {Pober}, J., {McQuinn}, M., {Jacobs}, D., \& {Aguirre}, J.
+  2012{\natexlab{a}}, \apj, 753, 81
+
+\bibitem[{{Parsons} \& {Backer}(2009)}]{par09}
+{Parsons}, A.~R., \& {Backer}, D.~C. 2009, \aj, 138, 219
+
+\bibitem[{{Parsons} {et~al.}(2012{\natexlab{b}}){Parsons}, {Pober}, {Aguirre},
+  {Carilli}, {Jacobs}, \& {Moore}}]{par12b}
+{Parsons}, A.~R., {Pober}, J.~C., {Aguirre}, J.~E., {et~al.}
+  2012{\natexlab{b}}, \apj, 756, 165
+
+\bibitem[{{Parsons} {et~al.}(2010){Parsons}, {Backer}, {Foster}, {Wright},
+  {Bradley}, {Gugliucci}, {Parashare}, {Benoit}, {Aguirre}, {Jacobs},
+  {Carilli}, {Herne}, {Lynch}, {Manley}, \& {Werthimer}}]{par10}
+{Parsons}, A.~R., {Backer}, D.~C., {Foster}, G.~S., {et~al.} 2010, \aj, 139,
+  1468
+
+\bibitem[{{Parsons} {et~al.}(2014){Parsons}, {Liu}, {Aguirre}, {Ali},
+  {Bradley}, {Carilli}, {DeBoer}, {Dexter}, {Gugliucci}, {Jacobs}, {Klima},
+  {MacMahon}, {Manley}, {Moore}, {Pober}, {Stefan}, \& {Walbrugh}}]{par14}
+{Parsons}, A.~R., {Liu}, A., {Aguirre}, J.~E., {et~al.} 2014, \apj, 788, 106
+
+\bibitem[{Patra {et~al.}(2016)}]{pat16}
+Patra, N., {et~al.} 2016, in preparation
+
+\bibitem[{{Pober} {et~al.}(2013){Pober}, {Parsons}, {Aguirre}, {Ali},
+  {Bradley}, {Carilli}, {DeBoer}, {Dexter}, {Gugliucci}, {Jacobs}, {Klima},
+  {MacMahon}, {Manley}, {Moore}, {Stefan}, \& {Walbrugh}}]{pob13}
+{Pober}, J.~C., {Parsons}, A.~R., {Aguirre}, J.~E., {et~al.} 2013, \apjl, 768,
+  L36
+
+\bibitem[{{Pober} {et~al.}(2014){Pober}, {Liu}, {Dillon}, {Aguirre}, {Bowman},
+  {Bradley}, {Carilli}, {DeBoer}, {Hewitt}, {Jacobs}, {McQuinn}, {Morales},
+  {Parsons}, {Tegmark}, \& {Werthimer}}]{pob14}
+{Pober}, J.~C., {Liu}, A., {Dillon}, J.~S., {et~al.} 2014, \apj, 782, 66
+
+\bibitem[{{Pober} {et~al.}(2015){Pober}, {Ali}, {Parsons}, {McQuinn},
+  {Aguirre}, {Bernardi}, {Bradley}, {Carilli}, {Cheng}, {DeBoer}, {Dexter},
+  {Furlanetto}, {Grobbelaar}, {Horrell}, {Jacobs}, {Klima}, {Kohn}, {Liu},
+  {MacMahon}, {Maree}, {Mesinger}, {Moore}, {Razavi-Ghods}, {Stefan},
+  {Walbrugh}, {Walker}, \& {Zheng}}]{pob15}
+{Pober}, J.~C., {Ali}, Z.~S., {Parsons}, A.~R., {et~al.} 2015, \apj, 809, 62
+
+\bibitem[{{Santos} {et~al.}(2005){Santos}, {Cooray}, \& {Knox}}]{san05}
+{Santos}, M.~G., {Cooray}, A., \& {Knox}, L. 2005, \apj, 625, 575
+
+\bibitem[{{Scott} \& {Rees}(1990)}]{sco90}
+{Scott}, D., \& {Rees}, M.~J. 1990, \mnras, 247, 510
+
+\bibitem[{{Sunyaev} \& {Zeldovich}(1972)}]{sun72}
+{Sunyaev}, R.~A., \& {Zeldovich}, Y.~B. 1972, \aap, 20, 189
+
+\bibitem[{{Thompson} {et~al.}(2001){Thompson}, {Moran}, \& {Swenson}}]{tho01}
+{Thompson}, A.~R., {Moran}, J.~M., \& {Swenson}, Jr., G.~W. 2001,
+  {Interferometry and Synthesis in Radio Astronomy, 2nd Edition} (Wiley)
+
+\bibitem[{{Thyagarajan} {et~al.}(2013){Thyagarajan}, {Udaya Shankar},
+  {Subrahmanyan}, {Arcus}, {Bernardi}, {Bowman}, {Briggs}, {Bunton},
+  {Cappallo}, {Corey}, {deSouza}, {Emrich}, {Gaensler}, {Goeke}, {Greenhill},
+  {Hazelton}, {Herne}, {Hewitt}, {Johnston-Hollitt}, {Kaplan}, {Kasper},
+  {Kincaid}, {Koenig}, {Kratzenberg}, {Lonsdale}, {Lynch}, {McWhirter},
+  {Mitchell}, {Morales}, {Morgan}, {Oberoi}, {Ord}, {Pathikulangara},
+  {Remillard}, {Rogers}, {Anish Roshi}, {Salah}, {Sault}, {Srivani}, {Stevens},
+  {Thiagaraj}, {Tingay}, {Wayth}, {Waterson}, {Webster}, {Whitney}, {Williams},
+  {Williams}, \& {Wyithe}}]{thy13}
+{Thyagarajan}, N., {Udaya Shankar}, N., {Subrahmanyan}, R., {et~al.} 2013,
+  \apj, 776, 6
+
+\bibitem[{{Thyagarajan} {et~al.}(2015{\natexlab{a}}){Thyagarajan}, {Jacobs},
+  {Bowman}, {Barry}, {Beardsley}, {Bernardi}, {Briggs}, {Cappallo}, {Carroll},
+  {Corey}, {de Oliveira-Costa}, {Dillon}, {Emrich}, {Ewall-Wice}, {Feng},
+  {Goeke}, {Greenhill}, {Hazelton}, {Hewitt}, {Hurley-Walker},
+  {Johnston-Hollitt}, {Kaplan}, {Kasper}, {Kim}, {Kittiwisit}, {Kratzenberg},
+  {Lenc}, {Line}, {Loeb}, {Lonsdale}, {Lynch}, {McKinley}, {McWhirter},
+  {Mitchell}, {Morales}, {Morgan}, {Neben}, {Oberoi}, {Offringa}, {Ord},
+  {Paul}, {Pindor}, {Pober}, {Prabu}, {Procopio}, {Riding}, {Rogers}, {Roshi},
+  {Udaya Shankar}, {Sethi}, {Srivani}, {Subrahmanyan}, {Sullivan}, {Tegmark},
+  {Tingay}, {Trott}, {Waterson}, {Wayth}, {Webster}, {Whitney}, {Williams},
+  {Williams}, {Wu}, \& {Wyithe}}]{thy15a}
+{Thyagarajan}, N., {Jacobs}, D.~C., {Bowman}, J.~D., {et~al.}
+  2015{\natexlab{a}}, \apj, 804, 14
+
+\bibitem[{{Thyagarajan} {et~al.}(2015{\natexlab{b}}){Thyagarajan}, {Jacobs},
+  {Bowman}, {Barry}, {Beardsley}, {Bernardi}, {Briggs}, {Cappallo}, {Carroll},
+  {Deshpande}, {de Oliveira-Costa}, {Dillon}, {Ewall-Wice}, {Feng},
+  {Greenhill}, {Hazelton}, {Hernquist}, {Hewitt}, {Hurley-Walker},
+  {Johnston-Hollitt}, {Kaplan}, {Kim}, {Kittiwisit}, {Lenc}, {Line}, {Loeb},
+  {Lonsdale}, {McKinley}, {McWhirter}, {Mitchell}, {Morales}, {Morgan},
+  {Neben}, {Oberoi}, {Offringa}, {Ord}, {Paul}, {Pindor}, {Pober}, {Prabu},
+  {Procopio}, {Riding}, {Udaya Shankar}, {Sethi}, {Srivani}, {Subrahmanyan},
+  {Sullivan}, {Tegmark}, {Tingay}, {Trott}, {Wayth}, {Webster}, {Williams},
+  {Williams}, \& {Wyithe}}]{thy15b}
+---. 2015{\natexlab{b}}, \apjl, 807, L28
+
+\bibitem[{{Tingay} {et~al.}(2013){Tingay}, {Goeke}, {Bowman}, {Emrich}, {Ord},
+  {Mitchell}, {Morales}, {Booler}, {Crosse}, {Wayth}, {Lonsdale}, {Tremblay},
+  {Pallot}, {Colegate}, {Wicenec}, {Kudryavtseva}, {Arcus}, {Barnes},
+  {Bernardi}, {Briggs}, {Burns}, {Bunton}, {Cappallo}, {Corey}, {Deshpande},
+  {Desouza}, {Gaensler}, {Greenhill}, {Hall}, {Hazelton}, {Herne}, {Hewitt},
+  {Johnston-Hollitt}, {Kaplan}, {Kasper}, {Kincaid}, {Koenig}, {Kratzenberg},
+  {Lynch}, {Mckinley}, {Mcwhirter}, {Morgan}, {Oberoi}, {Pathikulangara},
+  {Prabu}, {Remillard}, {Rogers}, {Roshi}, {Salah}, {Sault}, {Udaya-Shankar},
+  {Schlagenhaufer}, {Srivani}, {Stevens}, {Subrahmanyan}, {Waterson},
+  {Webster}, {Whitney}, {Williams}, {Williams}, \& {Wyithe}}]{tin13}
+{Tingay}, S.~J., {Goeke}, R., {Bowman}, J.~D., {et~al.} 2013, \pasa, 30, 7
+
+\bibitem[{{Tozzi} {et~al.}(2000){Tozzi}, {Madau}, {Meiksin}, \& {Rees}}]{toz00}
+{Tozzi}, P., {Madau}, P., {Meiksin}, A., \& {Rees}, M.~J. 2000, \apj, 528, 597
+
+\bibitem[{{Trott} {et~al.}(2012){Trott}, {Wayth}, \& {Tingay}}]{tro12}
+{Trott}, C.~M., {Wayth}, R.~B., \& {Tingay}, S.~J. 2012, \apj, 757, 101
+
+\bibitem[{{van Cittert}(1934)}]{van34}
+{van Cittert}, P.~H. 1934, Physica, 1, 201
+
+\bibitem[{{van Haarlem} {et~al.}(2013){van Haarlem}, {Wise}, {Gunst}, {Heald},
+  {McKean}, {Hessels}, {de Bruyn}, {Nijboer}, {Swinbank}, {Fallows},
+  {Brentjens}, {Nelles}, {Beck}, {Falcke}, {Fender}, {H{\"o}randel},
+  {Koopmans}, {Mann}, {Miley}, {R{\"o}ttgering}, {Stappers}, {Wijers},
+  {Zaroubi}, {van den Akker}, {Alexov}, {Anderson}, {Anderson}, {van Ardenne},
+  {Arts}, {Asgekar}, {Avruch}, {Batejat}, {B{\"a}hren}, {Bell}, {Bell}, {van
+  Bemmel}, {Bennema}, {Bentum}, {Bernardi}, {Best}, {B{\^i}rzan}, {Bonafede},
+  {Boonstra}, {Braun}, {Bregman}, {Breitling}, {van de Brink}, {Broderick},
+  {Broekema}, {Brouw}, {Br{\"u}ggen}, {Butcher}, {van Cappellen}, {Ciardi},
+  {Coenen}, {Conway}, {Coolen}, {Corstanje}, {Damstra}, {Davies}, {Deller},
+  {Dettmar}, {van Diepen}, {Dijkstra}, {Donker}, {Doorduin}, {Dromer}, {Drost},
+  {van Duin}, {Eisl{\"o}ffel}, {van Enst}, {Ferrari}, {Frieswijk}, {Gankema},
+  {Garrett}, {de Gasparin}, {Gerbers}, {de Geus}, {Grie{\ss}meier}, {Grit},
+  {Gruppen}, {Hamaker}, {Hassall}, {Hoeft}, {Holties}, {Horneffer}, {van der
+  Horst}, {van Houwelingen}, {Huijgen}, {Iacobelli}, {Intema}, {Jackson},
+  {Jelic}, {de Jong}, {Kant}, {Karastergiou}, {Koers}, {Kollen}, {Kondratiev},
+  {Kooistra}, {Koopman}, {Koster}, {Kuniyoshi}, {Kramer}, {Kuper},
+  {Lambropoulos}, {Law}, {van Leeuwen}, {Lemaitre}, {Loose}, {Maat}, {Macario},
+  {Markoff}, {Masters}, {McFadden}, {McKay-Bukowski}, {Meijering}, {Meulman},
+  {Mevius}, {Millenaar}, {Miller-Jones}, {Mohan}, {Mol}, {Morawietz},
+  {Morganti}, {Mulcahy}, {Mulder}, {Munk}, {Nieuwenhuis}, {van Nieuwpoort},
+  {Noordam}, {Norden}, {Noutsos}, {Offringa}, {Olofsson}, {Omar}, {Orr{\'u}},
+  {Overeem}, {Paas}, {Pandey-Pommier}, {Pandey}, {Pizzo}, {Polatidis},
+  {Rafferty}, {Rawlings}, {Reich}, {de Reijer}, {Reitsma}, {Renting},
+  {Riemers}, {Rol}, {Romein}, {Roosjen}, {Ruiter}, {Scaife}, {van der Schaaf},
+  {Scheers}, {Schellart}, {Schoenmakers}, {Schoonderbeek}, {Serylak},
+  {Shulevski}, {Sluman}, {Smirnov}, {Sobey}, {Spreeuw}, {Steinmetz}, {Sterks},
+  {Stiepel}, {Stuurwold}, {Tagger}, {Tang}, {Tasse}, {Thomas}, {Thoudam},
+  {Toribio}, {van der Tol}, {Usov}, {van Veelen}, {van der Veen}, {ter Veen},
+  {Verbiest}, {Vermeulen}, {Vermaas}, {Vocks}, {Vogt}, {de Vos}, {van der Wal},
+  {van Weeren}, {Weggemans}, {Weltevrede}, {White}, {Wijnholds}, {Wilhelmsson},
+  {Wucknitz}, {Yatawatta}, {Zarka}, {Zensus}, \& {van Zwieten}}]{van13}
+{van Haarlem}, M.~P., {Wise}, M.~W., {Gunst}, A.~W., {et~al.} 2013, \aap, 556,
+  A2
+
+\bibitem[{{Vedantham} {et~al.}(2012){Vedantham}, {Udaya Shankar}, \&
+  {Subrahmanyan}}]{ved12}
+{Vedantham}, H., {Udaya Shankar}, N., \& {Subrahmanyan}, R. 2012, \apj, 745,
+  176
+
+\bibitem[{{Wang} {et~al.}(2006){Wang}, {Tegmark}, {Santos}, \& {Knox}}]{wan06}
+{Wang}, X., {Tegmark}, M., {Santos}, M.~G., \& {Knox}, L. 2006, \apj, 650, 529
+
+\bibitem[{{Zaldarriaga} {et~al.}(2004){Zaldarriaga}, {Furlanetto}, \&
+  {Hernquist}}]{zal04}
+{Zaldarriaga}, M., {Furlanetto}, S.~R., \& {Hernquist}, L. 2004, \apj, 608, 622
+
+\bibitem[{{Zernike}(1938)}]{zer38}
+{Zernike}, F. 1938, Physica, 5, 785
+
+\bibitem[{{Zheng} {et~al.}(2014){Zheng}, {Tegmark}, {Buza}, {Dillon},
+  {Gharibyan}, {Hickish}, {Kunz}, {Liu}, {Losh}, {Lutomirski}, {Morrison},
+  {Narayanan}, {Perko}, {Rosner}, {Sanchez}, {Schutz}, {Tribiano}, {Valdez},
+  {Yang}, {Adami}, {Zelko}, {Zheng}, {Armstrong}, {Bradley}, {Dexter},
+  {Ewall-Wice}, {Magro}, {Matejek}, {Morgan}, {Neben}, {Pan}, {Penna},
+  {Peterson}, {Su}, {Villasenor}, {Williams}, \& {Zhu}}]{zhe14}
+{Zheng}, H., {Tegmark}, M., {Buza}, V., {et~al.} 2014, \mnras, 445, 1084
+
+\end{thebibliography}
 

### 2016-03-29 ForegroundSimulations/ms.tex
Remove commented lines
From 1c12a9b (fgsim-arxiv):
==========================

In ms.tex,

(*) Remove commented lines

@@
 
-% The period in the history of the Universe characterized by the transition of neutral hydrogen in the intergalactic medium (IGM) to a fully ionized state due to the formation of radiating objects such as the first stars and galaxies is referred to as the Epoch of Reionization (EoR).
-This is an important period of nonlinear growth of matter density perturbations and astrophysical evolution leading to the large scale structure observed currently in the Universe.
-And yet, this period in the Universe's history has remained poorly probed to date.
-
 The Epoch of Reionization (EoR) is an important period of nonlinear growth of matter density perturbations and astrophysical evolution leading to the large scale structure observed currently in the Universe.
@@
 However, there are inherent differences in spatial isotropy and spectral smoothness between the EoR signal and the foregrounds \citep[see, e.g.,][]{fur04b,mor04,zal04,san05,fur06,mcq06,mor06,wan06,gle08}.
-% All the current and future instruments rely on the inherent differences in spatial isotropy and spectral smoothness between the EoR signal and the foregrounds to extract the EoR power spectrum \citep[see, e.g.,][]{fur04b,mor04,zal04,san05,fur06,mcq06,mor06,wan06,gle08}.
 
 When expressed in the coordinate system of power spectrum measurements described by the three-dimensional wavenumber ($k$), the foreground emission is restricted to a wedge-shaped region commonly referred to as the {\it foreground wedge} \citep{bow09,liu09,liu14a,liu14b,dat10,liu11,gho12,mor12,par12b,tro12,ved12,dil13,pob13,thy13,dil14} bounded by the horizon limits \citep{par12b}, whereas the EoR signal has spherical symmetry due to its isotropy.
-% which appears elongated along line-of-sight $k$-modes due to peculiar velocity effects when dominated by matter density perturbations during early stages of reionization.
 The region of $k$-space excluding the {\it foreground wedge} is commonly referred to as the {\it EoR window} since it is expected to be relatively free of foreground contamination.
-
-% Despite attempts to exploit this knowledge about differences in spectral and spatial symmetry, first-generation experiments have at best only led to weak constraints on reionization models \citep{ali15,dil15,pob15}.
-This is because their sensitivity is primarily limited by instrumental and foreground systematics.
-The extreme dynamic range required to suppress foreground and instrument systematics demands high precision modeling of foregrounds as observed by modern wide-field instruments.
 
@@
 The extreme dynamic range required to suppress foreground and instrument systematics demands high precision modeling of foregrounds as observed by modern wide-field instruments.
-
-% One such study was undertaken by \citet{thy15a,thy15b}.
-Their studies of effects of wide-field measurements of EoR power spectra have demonstrated the {\it pitchfork} effect wherein foreshortening of baselines causes a prominent enhancement of foreground power near the horizon limits of the {\it foreground wedge} as well as in the contamination beyond.
-It highlighted the importance of controlling the response of wide-field instruments near the horizon.
-The need for precise subtraction of foregrounds in wide-field measurements was also highlighted in \citet{pob16}.
 
@@
 
-% The equation for delay spectrum describes the mapping between sky location of a foreground object and delay.
-The chromatic nature (variation with frequency) of the antenna power pattern appears multiplicatively in the frequency axis and thus results in convolving its delay response with that of the foregrounds and the geometric phases measured by the baseline vector.
-We discuss the resulting spillover of foreground power beyond the horizon delay limits.
-
 \subsection{Effect on Foreground Contamination}\label{sec:effects-fgdps}
@@
 For a {\it Blackman-Harris} window function denoted by $W_\textrm{BH}(f)$, $\epsilon \approx 50\%$ and $w_\textrm{ne} \approx 2$.
-% Hence, the window spans a total of $2N$ frequency channels each of width $\Delta f$ to have $B_\textrm{eff} \approx N\,\Delta f$.
 
@@
 We estimate the EoR-foreground dynamic range (ratio of EoR signal and foreground powers) for both EoR models in the presence of antenna beam chromaticity, using HERA as an example.
-% As stated earlier, we estimate this ratio for HERA in the most conservative scenario where we consider only {\it foreground avoidance} under simple spectral weighting scheme.
-We emphasize that other strategies involving {\it foreground removal} and inverse covariance-based weighting schemes will produce more optimal results than presented here.
 In order to avoid signal evolution across the entire band, we use subbands in which EoR signal evolution is not expected to be significant.
@@
 From Fig.~\ref{fig:subbands}, it is clearly demonstrated that across all baselines and subbands, HERA should detect EoR by more than two orders of magnitude above foreground contamination obtained with any level of antenna beam chromaticity.
-% While this clearly includes foregrounds obtained with the currently simulated chromatic beam pattern, the sensitivity against foregrounds obtained with achromatic and {\it Airy} antenna power patterns are even higher by many orders of magnitude.
-This only further reiterates that efforts to keep lowering systematic spectral effects in the antenna beam must be undertaken continuously, as is the case with HERA.
 
@@
 It demonstrates that HERA should detect the EoR signal with a very high signal-foreground ratio on all baselines over a majority of the pointings.
-
-% We reiterate that these estimates are obtained in a conservative scenario wherein only simple spectral weighting technique in the {\it foreground avoidance} limit is used, without any foreground removal or sophisticated weighting strategies using inverse-covariance.
-Further, these estimates represent worst-case limits demonstrating that HERA-19 and its successors will be extremely sensitive for EoR experiments and will benefit even further with more optimal foreground suppression strategies.
 

### 2016-03-29 ForegroundSimulations/ms.tex
Remove commented lines
From d4fb025 (fgsim):
====================

In ms.tex,

(*) Remove commented lines

--- 2016-03-28 ForegroundSimulations/ms.tex
@@
   \textrm{and,}\quad B_\textrm{eff} &= \epsilon\,B,
-  % B_\textrm{eff} &= \int_{-B/2}^{+B/2} |W(f)|^2\,\dif f.
 \end{align}
@@
 \begin{figure*}[htb]
-\centering
-\subfloat[][EoR model 1, 150~MHz subband ]{\label{fig:21cmfast-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_150.0_MHz_subband.eps}}
-\subfloat[][EoR model 2, 150~MHz subband ]{\label{fig:lidz-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_150.0_MHz_subband.eps}} \\
-\subfloat[][EoR model 1, 170~MHz subband ]{\label{fig:21cmfast-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_170.0_MHz_subband.eps}}
-\subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_170.0_MHz_subband.eps}}
+  % \centering
+  % \subfloat[][EoR model 1, 150~MHz subband ]{\label{fig:21cmfast-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_150.0_MHz_subband.eps}}
+  % \subfloat[][EoR model 2, 150~MHz subband ]{\label{fig:lidz-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_150.0_MHz_subband.eps}} \\
+  % \subfloat[][EoR model 1, 170~MHz subband ]{\label{fig:21cmfast-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_170.0_MHz_subband.eps}}
+  % \subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_170.0_MHz_subband.eps}}
+  \subfloat[][EoR model 1, 150~MHz subband ]{\label{fig:21cmfast-fg-ratio-150}\includegraphics[width=0.45\linewidth]{f6a.eps}}
+  \subfloat[][EoR model 2, 150~MHz subband ]{\label{fig:lidz-fg-ratio-150}\includegraphics[width=0.45\linewidth]{f6b.eps}} \\
+  \subfloat[][EoR model 1, 170~MHz subband ]{\label{fig:21cmfast-fg-ratio-170}\includegraphics[width=0.45\linewidth]{f6c.eps}}
+  \subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{f6d.eps}}
   \caption{Worst case EoR-foreground dynamic range, $\rho(\boldsymbol{b},f_0,\alpha)$, in {\it foreground avoidance} modes for different HERA-19 baselines as a function of RA ($\alpha$) of pointing on the sky.

### 2016-04-05 DishReflectometry/Paper1_v1.tex
First iteration of the draft for Aaron to read: From section 1 to section 3

@@
 needs of foreground suppression and signal sensitivity in direct tension with one
-another.
+another. In addition to that, systematic effects are unique to each instruments and their manifestation 
+is different in each dataset.
 
@@
 
-In this paper, we examine the performance of a new prototype HERA element in the context of
-this new wedge-based framework.  In coordination with ~\citet{XXXsisterpapers}, we compare 
-reflectometry measurements with
-a specification for the spectral performance of an element, given models of the relative brightness of
-foreground and 21~cm reionization modes in $k$-space.  
 % XXX document map
-
 The efficacy of the techniques of foreground removal from the measured data critically limits the 21~cm power spectrum measurements.
@@
 The Hydrogen Epoch of Reionization Array (HERA) is a proposed array consisting of 568 14-m dishes in South Africa which will measure the 21~cm power spectrum between 100 to 200~MHz.
-In this paper, we investigate the performance of the individual HERA elements and resulting contribution of the instrument response to the delay spectrum.
+In this paper, we investigate the performance of an individual HERA element and resulting contribution of the instrument response to the delay spectrum.
  Reflectometry measurements  are carried out across wide bandwidth on a prototype HERA element in Green
@@
 Reflectometry measurements are described in section 3.
-Section 4 qualifies the performance of the HERA element as an interferometer for detection of the 21~cm power spectrum.
+Section 4 describes the performance of the HERA element as an interferometer for detection of the 21~cm power spectrum.
+In coordination with ~\citet{XXXsisterpapers}, we compare 
+reflectometry measurements with
+a specification for the spectral performance of an element, given models of the relative brightness of
+foreground and 21~cm reionization modes in $k$-space in section 5.
 
@@
 
-\section{Antenna Reception With Multiple Reflections}
-\label{sec:multiple}
-To examine the performance of an antenna and feed in the presence of multiple reflections, think of the system as a screen at a distance $F$ from a feed (see Fig.
-\ref{fig:sys}), noting that this does ignore the sky pattern of the feed itself.
-The screen reflects voltage as $\Gamma_d$ and transmits $(1+\Gamma_d)$ (see, {\em e.g.} Pozar).
-Similarly, the feed reflects $\Gamma_f$ and transmits $(1+\Gamma_f)$.
-The voltage pattern $\volt_{sky}$ is incident onto that system and  $(1+\Gamma_{d})(1+\Gamma_{f})$ is coupled into the cable leading from the feed.
-Additionally however, the voltage pattern is reflected off the feed ($\Gamma_f$), then the dish ($\Gamma_d$) and subsequently $(1+\Gamma_{f})$ of it reenters the feed with a roundtrip time delay $\Delta \tau=2F/c$.
-Hence, if $v_{sky}$ is reflected $n$ times in between the feed and the dish, the net voltage entering the feed after the
-$n^{th}$ reflection may be written as:
-\begin{eqnarray}
-\volt_{rec} & = &  (1+\Gamma_d) (1+\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber \\
-	&& + (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
-&&  ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}]
-\end{eqnarray}
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{plots/microsys.pdf}
-\caption{System}
-\label{fig:sys}
-\end{figure}
-
-\noindent
-Defining $a=\volt_{rec}/\volt_{sky}$ and we see that 
- \begin{equation}
-a  =   (1+\Gamma_d)(1+\Gamma_{f}) \displaystyle\sum\limits_{n=0}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
-   \label{eq:Sigma}
-\end{equation}
-Note that $n=0$ is when the initial wave enters the cable at the feed (where we assume we have set our reference plane).
-We may identify $(1+\Gamma_d)$ as the voltage reception pattern of the antenna, denoted $p_n(\hat{\theta})$, which is a function of angle on the sky.
-Additionally, $(1+\Gamma_f$) is the voltage efficiency for the feed (not a function of angle).
-
-As an aside, note that the sum in Eq. \ref{eq:Sigma} may be evaluated we may rewrite
-\begin{equation}
-a =  (1+\Gamma_d)(1+\Gamma_{f})\frac{1+\Gamma_{f}^{N+1}\Gamma_{d}^{N+1}(\dfngexp)^{N+1}}{1+\Gamma_{f}\Gamma_{d}\dfngexp} \nonumber
-\end{equation}
-which, in the limit becomes:
-\begin{equation}
-a = \frac{ (1+\Gamma_d)(1+\Gamma_{f})}{1+\Gamma_{f}\Gamma_{d}\dfngexp} \nonumber
-\end{equation} 
-since $|\Gamma_d|$ and $|\Gamma_f|$ are less than one.
-
-To measure this quantity, we may connect a vector network analyzer (VNA) to the feed, calibrate it to the end of the cable at the feed and measure. 
-In this case, we ignore $\volt_{sky}$, and we see that $\Gamma_f \volt_{trans}$ gets reflected back from the feed connection and $(1+\Gamma_f)\volt_{trans}$ is emitted, where $\volt_{trans}$ is the signal from the VNA.
-$\Gamma_d$ of that is reflected back towards the feed and $(1+\Gamma_f)$ is received by the VNA suitably delayed.
-The received voltage after $n$ reflections (where again $n=0$ is the first reflected signal at the reference plane) is therefore:
-
-\begin{eqnarray}
-\volt_{rec} & = &  \Gamma_f \volt_{trans} \nonumber \\
-         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp \nonumber \\
-         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp \Gamma_d\Gamma_f\dfngexp \nonumber \\
-         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp (\Gamma_d\Gamma_f\dfngexp)^2 \nonumber \\
-&&  ....+ \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp (\Gamma_d\Gamma_f\dfngexp)^n
-\end{eqnarray}
-Defining $s_{11}=\volt_{rec}/\volt_{trans}$ (the VNA measured quantity), this may be factored to yield
-\begin{equation}
-s_{11} = \Gamma_f + \frac{(1+\Gamma_f)^2}{\Gamma_{f}} \displaystyle\sum\limits_{n=1}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
-\end{equation}
-Adding in the zeroth term and rearranging, we have
-\begin{equation}
-s_{11} +\frac{(1+\Gamma_f)^2}{\Gamma_f}-\Gamma_f = \frac{(1+\Gamma_f)^2}{\Gamma_{f}} \displaystyle\sum\limits_{n=0}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
-\end{equation}
-Comparing to Eq. \ref{eq:Sigma} and we find that
-\begin{equation}
-a = (1+\Gamma_d)\frac{\Gamma_f}{(1+\Gamma_{f})}\left(s_{11} + \frac{(1+\Gamma_f)^2}{\Gamma_f}- \Gamma_f\right)
-\end{equation}
-After rearranging and plugging in for $p_n(\hat{\theta})$ we find
-\begin{equation}
-a = p_n(\hat{\theta})\left[(1+\Gamma_f) + \frac{\Gamma_f}{(1+\Gamma_f)}\left(s_{11} - \Gamma_f\right)\right]
-\end{equation}
-By measuring the feed separately, we may use that result for $\Gamma_f = s_{11,f}$.
-
-For power, we want the squared magnitude, or:
-\begin{equation}
-\raggedright
-A(\hat{\theta}) = |aa^*|^2 =  P_n(\hat{\theta})\times ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\nonumber
-\end{equation}
-\begin{equation}
-             \left[|1+\Gamma_f|^2 +  2\operatorname{Re}\left(\frac{\Gamma_f}{(1+\Gamma_f)}(s_{11} - \Gamma_f)\right) 
-                              + \frac{|\Gamma_f|^2}{|1+\Gamma_{f}|^2}|s_{11} - \Gamma_f|^2 \right]
-\end{equation}
-where $P_n(\hat{\theta})= |p_n(\hat{\theta})|^2$ is the normalized power pattern.  Note that $|1+\Gamma_f|^2$ is the feed efficiency ($\epsilon_f$).
-
 \section{Visibility measurements by a two element interferometer and the delay spectrum}
-Now consider a two element interferometer with a baseline $\vec b$.
+Consider a two element interferometer with a baseline $\vec b$.
 If we denote the electric field sky signal in direction $\thhat$ by $\volt_\sky(\vec \theta, \nu)$  then the voltage output of each antenna may be written as,
@@
 The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. 
-In words, the sky delay spectrum from any direction $\thhat$ is convoluted with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ %defined this differently earlier
+The redshifted 21 cm spatial power spectrum is defined as
+\begin{equation}
+  P(k_\perp,k_\parallel) = |\tilde V(\vec b, \tau)|^{2} \left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2,
+\label{eq:delay-power-spectrum}
+\end{equation}
+where
+\begin{equation}
+  k_\perp = \frac{2\pi f}{D}({b\over c}), \\
+  k_\parallel = \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, 
+\end{equation}
+The power spectrum is a function of cosmological as well as instrumental parameters which are:\\
+$f_{21}$:rest frame frequency of the 21~cm radiation.\\
+$f$: observation frequency.\\
+$z$: cosmological redshift corresponding to frequency of observation.\\
+ $\Delta B$: bandwidth centered at the observation frequency.\\
+ $k_\textrm{B}$: Boltzmann constant.\\
+ $D\equiv D(z)$ comoving distance along the line of sight\\
+ $\Delta D$ the comoving distance along the line of sight corresponding to bandwidth of observation $\Delta B$.\\
+$E(z)= [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ \\
+
+In this paper, we use $\Omega_{M}=0.27$, $\Omega_{\Lambda}=0.73$, $\Omega_{K}=1-\Omega_{M}-\Omega_{\Lambda}$, $H_0=100\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P_\textrm{d}(k_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.
+
+Since both $k_{\perp}$ and $k_{\parallel}$ are functions of the delay $\tau$ corresponding to the given baseline length, the redshifted 21 cm power spectrum could be estimated from the measurement of delay spectrum of visibility by an interferometer.
+Sky delay spectrum from any direction $\thhat$ is convolved with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ %defined this differently earlier
  in the delay domain.
@@
 Due to chromaticity of the sky signal as well as instrument reponse, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with decaying amplitude [Ref to the figure Parsons12].
-Sky delay spectrum $I_{sky}(\tau)$ is contributed by the foreground  $I_{fg}(\tau)$  which is spectrally smooth and the 21~cm power spectrum $I_{21}(\tau)$ which contains spectral signatures.
-Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces and the 21~cm delay spectrum could potentially be detectable.
-The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$.
-In words, the sky delay spectrum from any direction $\thhat$ is convolved with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ in the delay domain.
+Sky delay spectrum $P_{sky}(\tau)$ is contributed by the foreground  $P_{fg}(\tau)$  which is spectrally smooth and the 21~cm power spectrum $P_{21}(\tau)$ which contains spectral signatures.Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces and the 21~cm delay spectrum could be detectable.
+
+ %In words, the sky delay spectrum from any direction $\thhat$ is convolved with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ in the delay domain.
 The maximum geometric delay possible for a given base line would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$ when the phase centre is halfway in between the two antennas.
@@
 \section{Effects of multiple reflections on visibility and delay spectrum}
-Response of any radio telescope is chromatic and modulates the true sky signal in the spectral domain.
-This results in the convolution of the instrument response kernel with the sky signal in the delay domain.
-This fundamentally limits the detectability of a 21~cm power spectrum.
-In this section, the effect of reflections on the visibility data and corresponding effect on the delay spectrum is discussed qualitatively.
-
 The Hydrogen Epoch of Reionization Array consists of parabolic dishes which provide increased collecting area per array element compared to its predecessor experiment PAPER.
@@
 \ref{sec:multiple}.
+In this section, the effect of reflections on the visibility data and corresponding effect on the delay spectrum is discussed in detail.
+We assume two antennas with identical geometry and electrical parameters i.e, $\bmvolt_{1}(\thhat,\nu)=\bmvolt_{2}(\thhat,\nu) = \bmvolt(\thhat,\nu)$.
+ \subsection{Antenna Reception With Multiple Reflections}
+\label{sec:multiple}
+To examine the performance of an antenna and feed in the presence of multiple reflections, think of the system as a screen at a distance $F$ from a feed (see Fig.
+\ref{fig:sys}), noting that this does ignore the sky pattern of the feed itself.
+The screen reflects voltage as $\Gamma_d$ and transmits $(1+\Gamma_d)$ (see, {\em e.g.} Pozar).
+Similarly, the feed reflects $\Gamma_f$ and transmits $(1+\Gamma_f)$.
+The voltage pattern $\volt_{sky}$ is incident onto that system and  $(1+\Gamma_{d})(1+\Gamma_{f})$ is coupled into the cable leading from the feed.
+Additionally however, the voltage pattern is reflected off the feed ($\Gamma_f$), then the dish ($\Gamma_d$) and subsequently $(1+\Gamma_{f})$ of it reenters the feed with a roundtrip time delay $\Delta \tau=2F/c$.
+Hence, if $v_{sky}$ is reflected $n$ times in between the feed and the dish, the net voltage entering the feed after the
+$n^{th}$ reflection may be written as:
+\begin{eqnarray}
+\volt_{rec} & = &  (1+\Gamma_d) (1+\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber \\
+	&& + (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
+&&  ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}]
+\end{eqnarray}
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{plots/microsys.pdf}
+\caption{System}
+\label{fig:sys}
+\end{figure}
 
-%%%\begin{figure}[ht!]
-%%%\centering
-%%%\includegraphics[totalheight=0.35\textheight]{plots/reflection_cartoon.png}
-%%%\caption{The propagation path of the sky signal entering the
-%%%feed in receiving mode is shown in blue.
-Due to impedance mismatch between feed and the free space, a part of the signal (dashed blue) is reflected off the feed.
-This signal reflects off the dish apex several times and returns to the feed at multiple delays with reduced signal strength.
-The red line shows the signal path during measurements which is done in transmission mode.
-Appropriate corrections are made to derive the telescope response function during sky observation.
-}
-%%%\label{fig:cartoon}
-%%%\end{figure}
-%%%
-%%%Consider again a two element interferometer as described in section 2.
-Two antennas are assumed to be exactly identical so that their electrical parameters and the field pattern are identical i.e, $a_{1}(\thhat,\nu) = a_{2}(\thhat,\nu) = a(\thhat, \nu)$.
-We denote the voltage reflection coefficient of each feed by $\Gamma_{f}$.
-The voltage reflection coefficient of the reflector dish is denoted by $\Gamma_{d}$.
-Upon first incidence of the sky signal onto the dish, it is reflected from the entire dish and is focussed onto the feed.
-Hence, for first incidence $\Gamma_{d}=1$.
-Sky signal that would return to the dish after successive reflections off the feed and the dish is reflected only from a small area around the vertex of the dish and therefore, $\Gamma_{d}<1$.
-In our analysis, we consider one reflection of the sky power from the feed and subsequent reflection off the dish as one single reflection.
-If the focal length of the dish is $l$, assuming the feed is located at the focus, the roundtrip delay after first reflection will be $\Delta \tau = {2l \over c}$.
-%%%
-%%%%\subsection{Visibility and delay spectrum computation considering multiple reflections}
-%%%Upon first incidence of the sky signal $\volt_{sky}$, $\Gamma_{f}$ fraction of the voltage is reflected off the feed while $(1-\Gamma_{f})$ fraction is coupled to the feed.
-The reflected voltage then further reflected off the dish and $(1-\Gamma_{f}) $ fraction of it reenters the feed with a roundtrip time delay $\Delta \tau$.
-Hence, if $I_{sky}$ is reflected n times in between the feed and the dish, the net voltage entering the feed after an
-%%%$n^{th}$ reflection off the feed and the dish is written as:
-%%%\begin{eqnarray}
-%%%\volt_{1} & = &  \bmvolt (1-\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber \\
-%%%	&& + (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
-%%%&&  ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}] \nonumber
-%%%\end{eqnarray}
-%%%and, 
-%%%\begin{eqnarray}
-%%%\volt_{2} & = &  \bmvolt (1-\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber\\
-%%%&&+  (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
-%%%&& ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}] \fngexp \nonumber
-%%%\end{eqnarray}
-%%%Frequency as well as angular dependence of the quantities are not written explicitly for notational simplicity.
-We also absorb the common gain term $(1-\Gamma_{f})$ with antenna field pattern $a$ and denote them as $\bmvolt_{f}= \bmvolt(1-\Gamma_{f})$ here after.
+\noindent
+%Defining $a=\volt_{rec}/\volt_{sky}$ and we see that 
+Hence,
+ \begin{eqnarray}
+{\volt_{rec}\over \volt_{sky} } & = &   (1+\Gamma_d)(1+\Gamma_{f}) \displaystyle\sum\limits_{n=0}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}\nonumber\\
+& = & \frac{ (1+\Gamma_d)(1+\Gamma_{f})}{1+\Gamma_{f}\Gamma_{d}\dfngexp} 
+ \label{eq:Sigma}
+\end{eqnarray}
+Note that $n=0$ is when the initial wave enters the cable at the feed (where we assume we have set our reference plane).
+We may identify $(1+\Gamma_d)(1+\Gamma_{a})$ as the voltage reception pattern of the antenna, denoted $\bmvolt(\thhat,\nu)$, which is a function of angle on the sky.
+Additionally, $(1+\Gamma_f$) is the voltage efficiency for the feed (not a function of angle).
 
-The cross power generated by $v_{1}$ and $v_{2}$ would have spurious visibility response due to mutual correlation between multiply reflected voltages.
+%As an aside, note that the sum in Eq. \ref{eq:Sigma} may be evaluated we may rewrite
+%\begin{equation}
+%{\volt_{rec}\over \volt_{sky} } =  (1+\Gamma_d)(1+\Gamma_{f})\frac{1+\Gamma_{f}^{N+1}\Gamma_{d}^{N+1}(\dfngexp)^{N+1}}{1+\Gamma_{f}%\Gamma_{d}\dfngexp} \nonumber
+%\end{equation}
+%which, in the limit becomes:
+%\begin{equation}
+%{\volt_{rec}\over \volt_{sky} } = \frac{ (1+\Gamma_d)(1+\Gamma_{f})}{1+\Gamma_{f}\Gamma_{d}\dfngexp} \nonumber
+%\end{equation} 
+%since $|\Gamma_d|$ and $|\Gamma_f|$ are less than one.
+
+Accurate measurement of this quantity requires receiving the $v_{sky}$ from a well calibrated wideband source in the sky in the far field of the HERA antenna element with significant isotropic emission.
+While this condition is hard to achieve in practice, due to reciprocity of the antenna performance in the transmission and reception mode, the right hand side of the equation \ref{eq:Sigma} could be measured using the returnloss measurement technique with a vector network analyser.
+A vector network analyzer (VNA) is connected to the HERA element via a 50 feet long cable.
+The VNA transmit a broadband noise voltage  $\volt_{trans}$.
+$(1+\Gamma_f)$ fraction of this voltage is radiated by the feed while the fraction $\Gamma_{f}$ returns to the VNA.
+While the radiated signal illuminated the dish and most of it is radiated into the space,  $\Gamma_d$ fraction of this signal is reflected back towards the feed and $(1+\Gamma_f)$ is received by the VNA.
+The received voltage after $n$ reflections between the dish and the feed, (where again $n=0$ is the first reflected signal at the reference plane) is therefore:
+
+\begin{eqnarray}
+\volt_{rec} & = &  \Gamma_f \volt_{trans} \nonumber \\
+         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp \nonumber \\
+         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp \Gamma_d\Gamma_f\dfngexp \nonumber \\
+         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp (\Gamma_d\Gamma_f\dfngexp)^2 \nonumber \\
+&&  ....+ \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp (\Gamma_d\Gamma_f\dfngexp)^n
+\end{eqnarray}
+Therefore, 
+\begin{equation}
+{\volt_{rec}\over \volt_{trans} } = \Gamma_f + \frac{(1+\Gamma_f)^2}{\Gamma_{f}} \displaystyle\sum\limits_{n=1}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
+\label{eq:s11}
+\end{equation}
+The VNA measures the quantity $\volt_{rec}/\volt_{trans}=s_{11}$ which is the voltage reflection coefficient of the HERA element.
+The fundamental difference between the righ hand side of the equation \ref{eq:Sigma} and \ref{eq:s11} are the $n=0$ term and the multiplicative factor in front of the convergent series $\displaystyle\sum\limits_{n=1}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}$ that represents the contribution of the delayed voltage components at the VNA input arising due to multiple signal reflection between the feed and the dish.
+Finally, writing $\volt_{rec}/\volt_{trans}=s_{11}$, equation \ref{eq:s11} could be written as,
+\begin{equation}
+s_{11} +\frac{(1+\Gamma_f)^2}{\Gamma_f}-\Gamma_f = \frac{(1+\Gamma_f)^2}{\Gamma_{f}} \displaystyle\sum\limits_{n=0}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
+\end{equation}
+Comparing to Eq. \ref{eq:Sigma} and we find that
+\begin{eqnarray}
+{\volt_{rec}\over \volt_{sky} } & = & (1+\Gamma_d)\left[(1+\Gamma_f) + \frac{\Gamma_f}{(1+\Gamma_f)}\left(s_{11} - \Gamma_f\right)\right] \nonumber\\
+ & = & \bmvolt(\thhat,\nu) \left[(1+\Gamma_f) + \frac{\Gamma_f}{(1+\Gamma_f)}\left(s_{11} - \Gamma_f\right)\right]
+\end{eqnarray}
+When the feed return loss is measured separately, all the higher order terms of the equation \ref{eq:s11} does not exist.
+In this case $\Gamma_f = s_{11}^{f}$.
+Using this measurements and VNA measurement of $s11$, the quantity $v_{rec}\over v_{sky}$ is estimated.
+
+From this, for a two element interferometer with identical antenna elements, the ratio of the received sky intensity to true sky intensity will be, 
+\begin{eqnarray}
+{I_{rec}\over I_{sky} } & = & |{\volt_{rec}\over \volt_{sky} }|^2 =  \beam(\thhat,\nu)\times \nonumber\\
+             && \left[|1+\Gamma_f|^2 +  2\operatorname{Re}\left(\frac{\Gamma_f}{(1+\Gamma_f)}(s_{11} - \Gamma_f)\right)\right] + \nonumber\\ 
+             &&  \left[ \frac{|\Gamma_f|^2}{|1+\Gamma_{f}|^2}|s_{11} - \Gamma_f|^2  \right]  \nonumber\\
+\label{eq:power_ratio}             
+\end{eqnarray}
+
+In terms of visibility, the same could be written as,  
+\begin{eqnarray}
+\vis^{mul}(\vec b,\nu) & = & \int \beam(\thhat,\nu)\times \nonumber\\
+             && \left[|1+\Gamma_f|^2 +  2\operatorname{Re}\left(\frac{\Gamma_f}{(1+\Gamma_f)}(s_{11} - \Gamma_f)\right)\right] + \nonumber\\ 
+             &&  \left[ \frac{|\Gamma_f|^2}{|1+\Gamma_{f}|^2}|s_{11} - \Gamma_f|^2  \right]  I_{sky} \ifngexp d\Omega
+\label{visibility_mul}
+\end{eqnarray}
+
+Comparing eq \ref{eq:power_ratio} with \ref{eq2}, the cross power generated by $v_{1}$ and $v_{2}$ would have spurious visibility response due to mutual correlation between multiply reflected voltages represented by the second and the third term of the right hand side of the equation \ref{eq:power_ratio}.
+In ideal case, $\Gamma_{f}=0$ in which case equation \ref{eq:power_ratio} results in equation \ref{eq2}.
 Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum.
@@
 These will broaden the width of the delay spectrum which finally interferes with the 21cm power spectrum detection.
-Combining these terms, the expression of visibility will be,
+% Combining these terms, the expression of visibility will be,
 
-\begin{eqnarray}\label{eqn:series1}
-\vis(\vec b, \nu) & = & \int \volt_{1}\volt_{2}^{*} d\Omega \nonumber\\
-			& = & \int I_{sky}(\vec b, \nu)A(\thhat,\nu) \ifngexp d\Omega
-\end{eqnarray}
+%\begin{eqnarray}\label{eqn:series1}
+%\vis(\vec b, \nu) & = & \int \volt_{1}\volt_{2}^{*} d\Omega \nonumber\\
+%			& = & \int I_{sky}(\vec b, \nu)A(\thhat,\nu) \ifngexp d\Omega
+%\end{eqnarray}
 %%%where we define a combined common instrument parameter, written as, 
@@
 %%%where, $\beam_{f}=\bmvolt_{f}\bmvolt_{f}^{*}= |a(1-\Gamma_{f})|^{2}$ is the antenna cross power pattern.
-and the delay spectrum would be, 
-\begin{eqnarray}
+%and the delay spectrum would be, 
+%\begin{eqnarray}
 %\tilde V(\vec b, \tau) & = & \int \left [ \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp  d\Omega \right ]  e^{-2\pi i\nu\tau} d\nu \nonumber \\
-\tilde V(\vec b, \tau) & = & \int \left [ I_{sky}(\vec b, \nu) \ast A(\vec b, \nu) \right]\dfngexp d\Omega
-\label{eq7}
-\end{eqnarray}
+%\tilde V(\vec b, \tau) & = & \int \left [ I_{sky}(\vec b, \nu) \ast A(\vec b, \nu) \right]\dfngexp d\Omega
+%\label{eq7}
+%\end{eqnarray}
 
- Thus, the correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected.
+% Thus, the correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected.
 \\
-The design specification of HERA elements requires that any
-signal, arriving at the feed at a delay $\Delta \tau$ with respect to the direct incidence, should be
-at the level of $-60dB$ at a delay of $60ns$ relative to the first incident
-signal at the feed ~\citep{parsons_deboer_memo}. This specification was
-approximated based on the power level of the cosmological signal in relation to
-foreground signals, which is estimated to be six orders of magnitude fainter
-~\citep{santos_et_al2005,  ali_et_al2008,deoliveira2008, jelic_et_al2008, bernardi_et_al2009,bernardi_et_al2010, ghosh_et_al2011}. Additionally, the $14m$ HERA baselines set a foreground containing
-Additionally, the $14m$ HERA baselines set a foreground containing
-horizon-limit (the wedge) that, with some buffer, sets a delay specification of
-$60ns$
-~\citep{parsons_et_al2012b,vedantham_et_al2012,nithya_et_al2013,liu_et_al2014a,liu_et_al2014b}.
+In a related series of papers, (Thyagarajan et al 2016) has shown the detailed sensitivity calculations of HERA is using a comprehensive foreground as well as model for EoR power spectrum for various simulated antenna element response (\ref{fig:sim_limit_delay}) From this simulations, the figure \ref{fig:sim_limit_delay} (Thyagarajan et al) shows the level of attenuation required for the multiple reflected sky signal in order to reduce the foreground contaminations at the delay modes significant for power spectrum measurements.
+Ewall-Wice et al 2016 has simulated the time domain response of the HERA element considering multiple reflections between the feed and the dish.
+Figure \ref{fig:sim_limit_delay} shows the simulated cross-power response of a pair of HERA antenna as a function of time(Ewall-wice et al).
+These simulations set up the performance criterion for the HERA antenna element.
+ \begin{figure*}[ht]
+\begin{minipage}[b]{0.5\linewidth}
+\centering
+\includegraphics[angle=0, width=\linewidth]{plots/sim_limit.jpg}
+\end{minipage}
+\hspace{0.1cm}
+\begin{minipage}[b]{0.5\linewidth}
+\centering
+\includegraphics[angle=0, width=\linewidth]{plots/sim_delay.jpg}
+\end{minipage}
+\caption{Left: Signal attenuation required for the reflected sky power arriving at the feed at higher delay as estimated from the simulated antenna beam and froeground models (Thyagarajan et al).
+The three different contour shows three different system performance requirements set based on the simulated response of HERA element for a measurement frequency of 150MHz corresponding to the redshift of $z=8.47$ and a 14.5m baseline.
+The instrumental requirements become extremely stringent for the detection of the smaller $k_\parallel$ values corresponding to very large spatial scales.
+Right: The simulated cross power response kernel for HERA.
+The simulation assumes and achromatic beam with the chromaticity attributed entirely by the multiple reflections between the dish and the feed.
+This shows the levels to which the multiple reflections at the higher delays is expected to be reduced following the dish and the feed design.}
+\label{fig:sim_limit_delay}       
+\end{figure*}
+
+%signal, arriving at the feed at a delay $\Delta \tau$ with respect to the direct incidence, should be
+%at the level of $-60dB$ at a delay of $60ns$ relative to the first incident
+%signal at the feed ~\citep{parsons_deboer_memo}. This specification was
+%approximated based on the power level of the cosmological signal in relation to
+%foreground signals, which is estimated to be six orders of magnitude fainter
+%~\citep{santos_et_al2005,  ali_et_al2008,deoliveira2008, jelic_et_al2008, bernardi_et_al2009,bernardi_et_al2010, ghosh_et_al2011}. Additionally, the $14m$ HERA baselines set a foreground containing
+%Additionally, the $14m$ HERA baselines set a foreground containing
+%horizon-limit (the wedge) that, with some buffer, sets a delay specification of
+%$60ns$
+%~\citep{parsons_et_al2012b,vedantham_et_al2012,nithya_et_al2013,liu_et_al2014a,liu_et_al2014b}.
 Our goal is to measure the instrument response $\Sigma(\nu)$ and its effect on the power spectrum measurements.
@@
 \end{figure*}
-We carried out reflectometry measurements at the HERA element prototype in Green
-Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise its performance. An HERA element consists off a $14\,m$ diameter
+Reflectometry measurements are carried out at the HERA element prototype in Green
+Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise the performance.  HERA element consists off a $14\,m$ diameter
 parabolic reflector and a crossed-dipole pair as a feed.
@@
 The feed is raised and
-lowered by a three-pulley system mounted on the three poles. The focal height of the dish is $5m$.  
-As given in the previous section, if the incident power from the sky signal is $I_{sky}$, the feed
-reflection coefficient is $\Gamma_{f}$, and the dish reflection
-coefficient is $\Gamma_{d}$, then the net power entering a feed after
-$n^{th}$ reflection off the feed and the dish is:
+lowered by a three-pulley system mounted on the three poles.
+The focal height of the dish is $5m$.
+The detail geometry and electromagnetic design of of the feed is presented in deBoer et al 2016 (in prep).
+\\
+A vector network analyser is connected via a 50feet long cable at the feed output of the HERA element and the return loss $(s_{11})$ of the HERA element is measured as a function of frequencies while the feed is suspended at the focal plane of the dish.
+This measurement is
+Section 3 laid the mathematical framework of how the delay spectrum is estimated from the return loss measurement. 
+%, if the incident power from the sky signal is $I_{sky}$, the feed
+%reflection coefficient is $\Gamma_{f}$, and the dish reflection
+%coefficient is $\Gamma_{d}$, then the net power entering a feed after
+%$n^{th}$ reflection off the feed and the dish is:
 
-\begin{eqnarray}
-\tilde I_{meas}(\vec b, \nu) & = & \int I_{sky}(\vec b, \nu)A(\vec b, \nu) \dfngexp d\Omega
-\end{eqnarray}
+%\begin{eqnarray}
+%\tilde I_{meas}(\vec b, \nu) & = & \int I_{sky}(\vec b, \nu)A(\vec b, \nu) \dfngexp d\Omega
+%\end{eqnarray}
 
-$I_{meas}$ is the auto correlated power obtained from a single HERA element.
-Upon our assumption that two adjacent antenna elements have identical electrical properties, this power is also a measure of the cross power or the visibility $\vis (\vec b, \nu)$ between the two antennas with a normalisation factor of $2$.
-
-%%%Once again, it is to be noted that upon the first incidence, the sky signal is focussed onto the feed from the entire dish and the dish reflection coefficient $\Gamma_{d}$ is $1$ for this first incidence.
-The subsequent back and forth reflection of the signal in between the feed and the dish, however, occurs from only the part of the dish which is shadowed by the feed.
-Therefore, in this case, $\Gamma_{d} < 1$.
-For a given baseline $\vec b$, taking the ratio of the measured power and the incident power,
-%%%
-%%%\begin{eqnarray}\label{eqn:ratio1}
-%%%{I_{meas} \over I_{sky} } & = & \Sigma(\vec b, \nu) \nonumber\\
-%%%  & = & \beam_{f}+ \beam_{f} \displaystyle\sum\limits_{n=1}^{n} [2\Re(\Gamma_{f}\Gamma_{d}\dfngexp)]^{n}
-%%%   \nonumber\\
-%%%   \label{eq8}
-%%%\end{eqnarray}
-%%%
-%%%The right hand side of this equation is the instrument response kernel of a single HERA element as well as a representative of the instrument response in the measured visibility data between a pair of antennas.
-Our goal is to measure this kernel as a function of frequency and determine its effect on the delay spectrum of the visibility.
-%%%
-%%%%%%%%%%%%%%%%%%%%
-%%%\subsection{Measurement equations}
-%%%The instrument response kernel is measured by measuring the return loss of the HERA element at the output port of the feed using a vector network analyser.
-The vector network analyser transmits a broadband noise of known amplitude and phase via a $50ft$ cable up to the feed.
-While a part of this signal  returns to the VNA post reflection from the feed due to mismatch between the cable and the antenna impedance resulting in the primary return loss, rest of the signal is radiated out by the antenna and illuminates the dish and radiated into the space.
-However, the reflected signal from the dish vertex returns to
-%%%the feed. This incident signal is now
-%%%reflected back and forth in between the feed and the dish much like the sky
-%%%signal reflection discussed previously.
-%%%
-%%%If $I_{tr}$ is the signal transmitted by the VNA and $\Gamma_{f}$ is the feed reflection coefficient, $\Gamma_{f}$ fraction of this transmitted power would be reflected back to the VNA while $(1-\Gamma_{f})$ fraction would be radiated.
-$\Gamma_{d}$ fraction of this radiated power will be reflected back and forth in between the feed and the dish with partial coupling of the signal into the feed at each reflection.
-The power radiated out of the feed, denoted by $I_{r}$ is ,
-%%%\begin{equation}
-%%%I_{r}= \beam_{f} I_{tr}
-%%%\end{equation}
-%%%
-%%%The total reflected power returned to the VNA, as measured by the VNA would be:
-%%%\begin{eqnarray}\label{eqn:series2}
-%%%I_{meas} & = & \Gamma_{f}I_{tr}+ I_{r}(1-\Gamma_{f}) [\Gamma_{d} \dfngexp + \Gamma_{f}\Gamma_{d}^{2} (\dfngexp)^{2}\nonumber\\
-%%%&&+ ....+ \Gamma_{f}^{n-1}\Gamma_{d}^{n}(\dfngexp)^{n}]
-%%%\end{eqnarray}
-%%%
-%%%Using the value of $I_{r}$ and simplifying:
-%%% 
-%%%  \begin{eqnarray}\label{eqn:ratio2}
-%%% {I_{meas} \over I_{tr} } & = & \Gamma_{f}
-%%%  +  \Gamma_{d}(1-\Gamma_f) \beam_{f} I_{tr} [e^{i\phi}+ \Gamma_{f}\Gamma_{d} e^{i2\phi}\nonumber\\ 
-%%%  && +  ....+ (\Gamma_{f}\Gamma_{d})^{n}e^{i n\phi}]\nonumber\\
-%%%  & = & \Gamma_{f} + { (1-\Gamma_f)\beam_{f}\over \Gamma_{f} } \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}
-%%% \label{eq9}
-%%%\end{eqnarray}
-%%%
-%%%The ratio in Equation \ref{eqn:ratio2} is identical to the ratio in the sky
-%%%observation in Equation \ref{eqn:ratio1} except in three factors. The
-%%%first factor corresponds to an additive amplitude difference arising from
-%%%$\Gamma_{f}$, which physically accounts for the initial reflection at the feed.
-%%%The second difference is the multiplicative ${ (1-\Gamma_f)\over \Gamma_{f} }$.
-In addition, in order to estimate the true response of the system to the sky signal in the receiving mode, we add the term $A_{f}$.
-These corrections map the measured instrument response from transmission mode in which the measurement is taken to receiving mode in which the sky observation is done.
-The corrected measurement could be written as
-%%% \begin{eqnarray}\label{eqn:ratio2}
-%%% \left[{I_{meas} \over I_{tr}}-\Gamma_{f}\right]{ \Gamma_{f} \over (1-\Gamma_{f})} + \beam_{f}  & = & \beam_{f}+ \beam_{f} \displaystyle\sum\limits_{n=1}^{n} [\Gamma_{f}\Gamma_{d}e^{i\phi}]^{n}\nonumber\\
-%%% & = & {I_{meas} \over I_{sky} }
-%%% \label{eq9}
-%%%\end{eqnarray}
-%++++++++++++++++++++++++++++++++++++++++++++++++++++++
+Return loss measurements are similar to auto correlation measurement from a single HERA element.
+Upon our assumption that two adjacent antenna elements have identical design parameters and electrical properties, this power is also a measure of the cross power or the visibility $\vis (\vec b, \nu)$ between the two antennas with a normalisation factor of $2$.
 \section{Results}
@@
 Measurement bandwidth is kept much larger than the bandwidth of operation to achieve higher delay resolution.
+A number of systematic effects as well as mathematical artefacts that are critical to this measurements are taken in to account in determination of the delay spectrum and described below.
 
 \subsection{Estimation of the delay spectrum of the instrument}
-At first, the frequency domain data is Fourier-transformed to compute the response of the system in the delay domain.
-The signal transmitted by the VNA is reflected first from the feed.
+%At first, the frequency domain measurement of s11 is Fourier-transformed to compute the response of the system in the delay domain.
+
+While measuring the return loss of the dish-feed assembly, the signal transmitted by the VNA is reflected first off the feed.
+This essentially represents a mismatch in between the feed and the 50 Ohm transmission line.
 In delay domain, this appears at the zero delay bin.
-In a second iteration , we subtract this value from the measured data and divide the the data by a factor ${(1-\Gamma_{f})\over \Gamma_{f}}$ to map the delay spectrum of the system from transmitting mode to receiving mode during sky observation.
+The for the feed, the zero delay response is identical whether or not the feed is suspended on the dish and  Therefore, we measure this response by measuring the feed return loss alone while the feed is kept on the ground facing the sky.
+This results in feed response alone including the feed cage structure but excluding the dish response.
+The using the return loss measurement of the feed $(\Gamma_{f})$, the return loss measurement $s_{11}$ of the dish and feed assembly is corrected via equation \ref{eq:power_ratio} and the quantity of interest ${I_{rec}\overI_{sky}}$ is estimated.
 

### 2016-04-05 DishReflectometry/GB_reflectometry_part2/Simulation/plot_reflectometry_41.py
Adding the data-code directory

@@ -83,85 +83,10 @@ for filename in sys.argv[1:]:
         d1 = ((d-d_f)*d_f/d_t ) # Reflections corrected to produce system bandpass in the receiving mode 
         d2 = d1+d_t # Zero term added for final correction
 
-        _d = np.fft.ifft((d2)**2*window)/window.mean()
-        _dww = np.fft.ifft(np.abs(d2)**2*window) /window.mean()# compensate for window amplitude
-        #print np.fft.fftshift(tau)
-        
+        _d = np.fft.ifft((d_f)**2*window)/window.mean()
+        _dww = np.fft.ifft((d2)**2*window) /window.mean()# compensate for window amplitude
         #_dww_rb = np.fft.ifft((d2_rb)**2*window2) / window2.mean() # compensate for window amplitude
-
-    #import IPython; IPython.embed()
-    plt.plot(fq_f,np.abs(d_f),linewidth=2.5,label='Transmission UCB(real)')
-    plt.plot(fq_f,np.abs(d2),linewidth=2.5,label='Transmission UCB(real)')
-    plt.show()
-    #plt.plot(fq,d_t.imag,linewidth=2.5,label='Transmission UCB (imag)')
-    #plt.plot(fq,10.0*np.log10(np.abs(d2)),linewidth=2.5,label='Corrected measurements UCB (abs mag)')
-    #plt.plot(fq_rb_f,d_rb_t.real,linewidth=2.5,label='Transmission RB (real)')
-    #plt.plot(fq_rb_f,d_rb_t.imag,linewidth=2.5,label='Transmission RB (imag)')
-    #plt.plot(fq_rb_f,10.0*np.log10(np.abs(d2_rb)),linewidth=2.5,label='Corrected measurements RB (abs mag)')
     
-    
-   #plt.plot(np.fft.fftshift(tau), 10.0*np.log10(np.fft.fftshift(np.abs(_d))), linewidth=2.5, label= 'Square Window')
-    #plt.plot(np.fft.fftshift(tau), 10.0*np.log10(np.fft.fftshift(np.abs(_d))), linewidth=2.5, label='Feed only (measurement)')
-    #plt.plot(np.fft.fftshift(tau), 10.0*np.log10(np.fft.fftshift(np.abs(_dww))), linewidth=2.5, label='current balun')
-    
-    
-    db = db-30.0
[…]

### 2016-04-05 DishReflectometry/GB_reflectometry_part2/Simulation/plot_simulation.py

@@ -1,0 +1,99 @@
+#! /usr/bin/env python
+
+import numpy as np, pylab as plt, aipy as a
+import sys, csv
+
+
+def fromcsv(filename):
+    print 'Reading', filename
+    d = csv.reader(open(filename,'r'), delimiter=',')
+    x = np.array(list(d)[18:-1], dtype=np.float)
+    #print d[0]
+    return x[:,0]/1e3, x[:,1]
+
+for filename in sys.argv[1:]:
+    BASE = filename[:-len('.csv')]
+    db_file = BASE + '_DB.csv'
+    ph_file = BASE + '_P.csv'
+
+    WINDOW = 'blackman-harris'
+    #WINDOW = 'hamming'
+    
+    fq,db = fromcsv(db_file) # Reading the magnitude and the phase of the datafile to be processed
+    fq,ph = fromcsv(ph_file) 
+    
+    fq_f,db_f = fromcsv('simulation_feeds11_DB.csv') # Reading the magnitude and phase of the feed only datafile to calibrate for the zero point/ 
+    fq_f,ph_f = fromcsv('simulation_feeds11_P.csv')
+    
+    d = 10**(db/20) * np.exp(2j*np.pi*ph/360) # 20 to put into voltage amplitude, not power
+    d_f = 10**(db_f/20) * np.exp(2j*np.pi*ph_f/360) # 20 to put into voltage amplitude, not power
+    
+    valid = np.where(np.logical_and(fq < .200, fq > .090)) # restrict to PAPER band
+    
+    fq, d, db, ph, fq_f,d_f, db_f, ph_f = fq[valid], d[valid], db[valid], ph[valid],fq_f[valid], d_f[valid], db_f[valid],ph_f[valid]
+    
+    
+    tau = np.fft.fftfreq(fq.size, fq[1]-fq[0])
+    window = a.dsp.gen_window(fq.size, WINDOW)
+   
+
+    if True: # approx account for 1st reflection of sky signal off of feed
+        
+        d_t =1+d_f # Transmission coefficient
+        d1 = ((d-d_f)*d_f/d_t ) # Reflections corrected to produce system bandpass in the receiving mode 
+        d2 = d1+d_t # Zero term added for final correction
+
+        _d = np.fft.ifft((d_f)**2*window)/window.mean()
+        _dw = np.fft.ifft((d)**2*window)/window.mean()
[…]

### 2016-04-05 DishReflectometry/GB_reflectometry_part2/final_plot_reflectometry.py

@@ -1,0 +1,153 @@
+#! /usr/bin/env python
+
+import numpy as np, pylab as plt, aipy as a
+import sys, csv
+
+
+def fromcsv(filename):
+    print 'Reading', filename
+    d = csv.reader(open(filename,'r'), delimiter=',')
+    x = np.array(list(d)[18:-1], dtype=np.float)
+    return x[:,0]/1e9, x[:,1]
+
+def lin(db,ph): # Converting the magnitude and phase of the measurements into complex returnloss in voltage ratio.
+    return 10**(db/20) * np.exp(2j*np.pi*ph/360)
+
+def pwr(d): # Computing the absolute magnitude of power in db. 
+    return 10*np.log10(np.abs(d)**2)
+    
+def vna_open(db_open,ph_open,fq):
+    cable_phse = (2*np.pi*fq*30.48)/(0.81*0.3)
+    ph_open_cable = ph_open+cable_phse
+    d_open = lin(db_open,ph_open)
+    meas = lin(db_open,ph_open_cable)
+    gamma2 = (d_open-1)/(meas+1)
+    return gamma2
+    
+def vna_short(db_open,ph_open,fq):
+    cable_phse = (2*np.pi*fq*30.48)/(0.85*0.3)
+    ph_open_cable = ph_open+cable_phse
+    d_open = lin(db_open,ph_open)
+    meas = lin(db_open,ph_open_cable)
+    gamma2 = (d_open+1)/(meas-1)
+    return gamma2
+
+for filename in sys.argv[1:]:
+    BASE = filename[:-len('.csv')]
+    db_file = BASE + '_DB.csv'
+    ph_file = BASE + '_P.csv'
+    
+    fq,db = fromcsv(db_file) # Reading the magnitude and the phase of the datafile to be processed
+    fq,ph = fromcsv(ph_file) 
+    
+    fq_f,db_f = fromcsv('HERA_FEED_DB.csv') # Reading the magnitude and phase of the feed only datafile to calibrate for the zero point/ 
+    fq_f,ph_f = fromcsv('HERA_FEED_P.csv')
+    
+    fq_open,db_open = fromcsv('Calibration/OPENNN_DB.csv')# Reading the open file to calibrate for the multiple signal reflections in the 50 feet long cable
+    fq_open,ph_open = fromcsv('Calibration/OPENNN_P.csv')
+    
[…]

### 2016-04-05 DishReflectometry/GB_reflectometry_part2/plot_calibration.py

@@ -1,0 +1,94 @@
+#! /usr/bin/env python
+
+import numpy as np, pylab as plt, aipy as a
+import sys, csv
+
+    
+def fromcsv(filename):
+    print 'Reading', filename
+    d = csv.reader(open(filename,'r'), delimiter=',')
+    x = np.array(list(d)[18:-1], dtype=np.float)
+    return x[:,0]/1e9, x[:,1]
+
+for filename in sys.argv[1:]:
+    BASE = filename[:-len('.csv')]
+    db_file = BASE + '_DB.csv'
+    ph_file = BASE + '_P.csv'
+
+    WINDOW = 'blackman-harris'
+    #WINDOW = 'hamming'
+    
+    fq,db = fromcsv(db_file) # Reading the magnitude and the phase of the datafile to be processed
+    fq,ph = fromcsv(ph_file) 
+    d = 10**(db/20) * np.exp(2j*np.pi*ph/360) # Converting the data to linear date. 20 to put into voltage amplitude, not power
+
+
+    valid = np.where(np.logical_and(fq < .200, fq > .100)) # restrict to PAPER band
+    
+    fq, d, db, ph = fq[valid],d[valid], db[valid], ph[valid]
+
+    tau = np.fft.fftfreq(fq.size, fq[1]-fq[0])
+    window = a.dsp.gen_window(fq.size, WINDOW)
+   
+
+    if True: # approx account for 1st reflection of sky signal off of feed
+        #_dw *= np.abs(_d[0])
+        #_d *= np.abs(_d[0])
+        
+        #d -= np.abs(_d[0])
+        #d1 = (np.abs(d)-np.abs(d_f))*np.abs(d_f)/(1-np.abs(d_f))+ (1-np.abs(d_f))
+        #d_t = 1+d_f
+        #d1 = (d-d_f)
+        #d2 = d1*d_f
+        #d3 = d2/d_t
+        
+        _dw1 = np.fft.ifft((d)**2*window) /window.mean()# compensate for window amplitude
+        #_dw2 = np.fft.ifft((d_f)**2*window) /window.mean()# compensate for window amplitude
+        #_dw3 = np.fft.ifft((d1)**2*window) /window.mean()# compensate for window amplitude
[…]

### 2016-04-05 DishReflectometry/GB_reflectometry_part2/plot_reflec_cal.py

@@ -1,0 +1,116 @@
+#! /usr/bin/env python
+
+import numpy as np, pylab as plt, aipy as a
+import sys, csv
+
+def fromcsv2(filename):
+    print 'Reading', filename
+    d = csv.reader(open(filename,'r'), delimiter=',')
+    x = np.array(list(d)[18:-1], dtype=np.float)
+    return x[:,0]/1e3, x[:,1]
+def fromcsv1(filename):
+    print 'Reading', filename
+    d = csv.reader(open(filename,'r'), delimiter=',')
+    x = np.array(list(d)[18:-1], dtype=np.float)
+    return x[:,0]/1e3, x[:,1]
+def fromcsv(filename):
+    print 'Reading', filename
+    d = csv.reader(open(filename,'r'), delimiter=',')
+    x = np.array(list(d)[18:-1], dtype=np.float)
+    return x[:,0]/1e9, x[:,1]
+
+for filename in sys.argv[1:]:
+    BASE = filename[:-len('.csv')]
+    db_file = BASE + '_DB.csv'
+    ph_file = BASE + '_P.csv'
+
+    WINDOW = 'blackman-harris'
+    #WINDOW = 'hamming'
+    
+    fq,db = fromcsv(db_file) # Reading the magnitude and the phase of the datafile to be processed
+    fq,ph = fromcsv(ph_file) 
+    
+    fq_f,db_f = fromcsv('HERA_FEED_DB.csv') # Reading the magnitude and phase of the feed only datafile to calibrate for the zero point/ 
+    fq_f,ph_f = fromcsv('HERA_FEED_P.csv')
+    
+    d = 10**(db/20) * np.exp(2j*np.pi*ph/360) # 20 to put into voltage amplitude, not power
+    d_f = 10**(db_f/20) * np.exp(2j*np.pi*ph_f/360) # 20 to put into voltage amplitude, not power
+    
+    fq_cal,db_cal = fromcsv('Calibration/CALIBR_DB.csv')# Reading Rich's dish+feed measurements magnitude and phase file.
+    fq_cal,ph_cal = fromcsv('Calibration/CALIBR_P.csv')
+    
+    d_cal = 10**(db_cal/20) * np.exp(2j*np.pi*ph_cal/360) # 20 to put into voltage amplitude, not power 
+    
+
[…]

### 2016-04-05 DishReflectometry/GB_reflectometry_part2/plot_reflectometry_cablecal.py

@@ -1,0 +1,155 @@
+#! /usr/bin/env python
+
+import numpy as np, pylab as plt, aipy as a
+import sys, csv
+
+def fromcsv2(filename):
+    print 'Reading', filename
+    d = csv.reader(open(filename,'r'), delimiter=',')
+    x = np.array(list(d)[18:-1], dtype=np.float)
+    return x[:,0]/1e3, x[:,1]
+def fromcsv1(filename):
+    print 'Reading', filename
+    d = csv.reader(open(filename,'r'), delimiter=',')
+    x = np.array(list(d)[18:-1], dtype=np.float)
+    return x[:,0]/1e3, x[:,1]
+def fromcsv(filename):
+    print 'Reading', filename
+    d = csv.reader(open(filename,'r'), delimiter=',')
+    x = np.array(list(d)[18:-1], dtype=np.float)
+    return x[:,0]/1e9, x[:,1]
+
+for filename in sys.argv[1:]:
+    BASE = filename[:-len('.csv')]
+    db_file = BASE + '_DB.csv'
+    ph_file = BASE + '_P.csv'
+
+    WINDOW = 'blackman-harris'
+    #WINDOW = 'hamming'
+    
+    fq,db = fromcsv(db_file) # Reading the magnitude and the phase of the datafile to be processed
+    fq,ph = fromcsv(ph_file) 
+    
+    fq_f,db_f = fromcsv('HERA_FEED_DB.csv') # Reading the magnitude and phase of the feed only datafile to calibrate for the zero point/ 
+    fq_f,ph_f = fromcsv('HERA_FEED_P.csv')
+    
+    d = 10**(db/20) * np.exp(2j*np.pi*ph/360) # 20 to put into voltage amplitude, not power
+    d_f = 10**(db_f/20) * np.exp(2j*np.pi*ph_f/360) # 20 to put into voltage amplitude, not power
+    
+    
+    fq_rb_f,db_rb_f = fromcsv('Calibration/OPENN_DB.csv')#Reading Rich's feed only file to do the zero delay corrections.
+    fq_rb_f,ph_rb_f = fromcsv('Calibration/OPENN_P.csv')
+    
+    d_rb_f = 10**(db_rb_f/20) * np.exp(2j*np.pi*ph_rb_f/360) # 20 to put into voltage amplitude, not power 
+    
+
[…]

### 2016-04-05 DishReflectometry/GB_reflectometry_part2/plot_reflectometry_rb.py

@@ -1,0 +1,106 @@
+#! /usr/bin/env python
+
+import numpy as np, pylab as plt, aipy as a
+import sys, csv
+
+    
+def fromcsv(filename):
+    print 'Reading', filename
+    d = csv.reader(open(filename,'r'), delimiter=',')
+    x = np.array(list(d)[18:-1], dtype=np.float)
+    return x[:,0]/1e3, x[:,1]
+
+for filename in sys.argv[1:]:
+    BASE = filename[:-len('.csv')]
+    db_file = BASE + '_DB.csv'
+    ph_file = BASE + '_P.csv'
+
+    WINDOW = 'blackman-harris'
+    #WINDOW = 'hamming'
+    
+    fq,db = fromcsv(db_file) # Reading the magnitude and the phase of the datafile to be processed
+    fq,ph = fromcsv(ph_file) 
+    d = 10**(db/20) * np.exp(2j*np.pi*ph/360) # Converting the data to linear date. 20 to put into voltage amplitude, not power
+
+    fq_f,db_f = fromcsv('measurement_FeedOnly_DB.csv')#Reading Rich's feed only file to do the zero delay corrections.
+    fq_f,ph_f = fromcsv('measurement_FeedOnly_P.csv')
+    d_f = 10**(db_f/20) * np.exp(2j*np.pi*ph_f/360) # Converting the data to linear date. 20 to put into voltage amplitude, not power
+
+    
+    valid = np.where(np.logical_and(fq < .200, fq > .100)) # restrict to PAPER band
+    
+    fq, fq_f, d, db, ph, d_f, db_f, ph_f = fq[valid], fq_f[valid],d[valid], db[valid], ph[valid], d_f[valid], db_f[valid],ph_f[valid]
+
+    tau = np.fft.fftfreq(fq.size, fq[1]-fq[0])
+    window = a.dsp.gen_window(fq.size, WINDOW)
+   
+
+    if True: # approx account for 1st reflection of sky signal off of feed
+        #_dw *= np.abs(_d[0])
+        #_d *= np.abs(_d[0])
+        
+        #d -= np.abs(_d[0])
+        #d1 = (np.abs(d)-np.abs(d_f))*np.abs(d_f)/(1-np.abs(d_f))+ (1-np.abs(d_f))
+        d_t = 1+d_f
[…]

### 2016-04-06 DishReflectometry/GB_reflectometry_part2/final_plot_reflectometry.py
Adding data again with new processing

@@ -94,16 +94,16 @@ for filename in sys.argv[1:]:
 
         _d = np.fft.ifft(np.abs(d)**2*window)/window.mean()
         _df = np.fft.ifft(np.abs(d_f)**2*window)/window.mean() #Take the Fourier transform of the SQUARE of the absolute MAGNITUDE of the voltage return loss of the feed.
-        _dt = np.fft.ifft(np.abs(d_t)**2*window)/window.mean() #Take the Fourier transform of the SQUARE of the absolute MAGNITUDE of the voltage return loss of the feed.
-        _dopen = np.fft.ifft(np.abs(d_open)**2*window)/window.mean() #Take the Fourier transform of the SQUARE of the absolute magnitude of the voltage return loss of the feed.
-        _dgamma2 = np.fft.ifft(np.abs(gamma_vna_open)**2*window)/window.mean() #Take the Fourier transform of the SQUARE of the absolute magnitude of the voltage return loss of the feed.
+        _dt = np.fft.ifft(np.abs(d_t)**2*window)/window.mean() #Take the Fourier transform of the SQUARE of the absolute MAGNITUDE of the voltage transmission of the feed.
+        _dopen = np.fft.ifft(np.abs(d_open)**2*window)/window.mean() #Take the Fourier transform of the SQUARE of the absolute magnitude of the voltage return loss of the open.
+        _dgamma2 = np.fft.ifft(np.abs(gamma_vna_open)**2*window)/window.mean() #Take the Fourier transform of the SQUARE of the absolute magnitude of the voltage return loss of the vna input.
         _dH = np.fft.ifft(np.abs(d2)**2*window) /window.mean()#Take the Fourier transform of the SQUARE of the absolute magnitude of the voltage return loss  of the HERA element.
         
         #_dopen[[np.where((np.fft.fftshift(tau) <= -90) & (np.fft.fftshift(tau) >= -170))]]=0.0
         
     	#plt.plot(np.fft.fftshift(tau),pwr(np.fft.fftshift(np.abs(_d))),linewidth=2.5,label='feed')
-    	plt.plot(np.fft.fftshift(tau),pwr(np.fft.fftshift(np.abs(_dt))),linewidth=2.5,label='gammaopen')
[…]

### 2016-04-06 DishReflectometry/plots/plot_heights.py
Adding new plots

@@ -47,10 +47,10 @@ for i,v in enumerate(valids):
     fq,phs = fromcsv(file_base + str(v) + phs_end)
     #bandwidth = n.where(n.logical_and(fq>.05 ,fq<.25)) #HERA bandwidth
     #bandwidth = n.where(n.logical_and(fq>.1,fq<.2)) #PAPER bandwidth
-    bandwidth = n.where(n.logical_and(fq>.05,fq<.5)) #full bandwidth
+    bandwidth = n.where(n.logical_and(fq>.100,fq<.200)) #full bandwidth
     dw, d, tau = take_delay(amps[bandwidth], phs[bandwidth], fq[bandwidth])
-#    p.plot(tau, 10*n.log10(n.abs(dw)**2), linewidth=2, label=('%s'%v)+'ft', color=colors[i])
-    ax.plot(tau, 10*n.log10(n.abs(dw)**2), linewidth=2, label=labels[i], color=colors[i])
+    #p.plot(fq, dw, linewidth=2, label=('%s'%v)+'ft', color=colors[i])
+    ax.plot(tau, (dw)**1, linewidth=2, label=labels[i], color=colors[i])
 p.xlim(-30,350)
 p.ylim(-100, 1)
 p.vlines(60, -100,100, linestyle='--', linewidth=2)

### 2016-04-06 DishReflectometry/plots/plot_reflectometry.py

@@ -1,4 +1,4 @@
-#! /usr/bin/env python
+ls#! /usr/bin/env python
 
 import numpy as np, pylab as plt, aipy as a
 import sys, csv

### 2016-04-06 DishReflectometry/Paper1_v1.tex
First draft completed up to section 3

@@
 \centering
-\includegraphics[angle=0, width=\linewidth]{plots/s11_HERA_feed_PAPER_mag.png}
+\includegraphics[angle=0, width=\linewidth]{plots/RL_mag.png}
 \end{minipage}
@@
 \centering
-\includegraphics[angle=0, width=\linewidth]{plots/s11_HERA_feed_PAPER_ph.png}
+\includegraphics[angle=0, width=\linewidth]{plots/RL_phse.png}
 \end{minipage}
 \caption{Left: Magnitude of the return loss of power measured in between 100 to 200 MHz using vector network analyser.
-Right panel shows the corresponding phase.HERA feed design is derived from modified PAPER antenna and therefore the return loss closely relates to the PAPER antenna response with slight frequency shift.
+Right panel shows the corresponding phase.
+Return loss of the feed alone is shown in green while the same for the feed+dish assembly is shown in blue.
+Finally, the quantity of interest ${I_{rec}\over I_{sky}}$ is shown in red.
+In ideal condition 100\% of the sky power is to be received and ${I_{rec}\over I_{sky}} = 1$ or 0dB.
+Finite return loss at the antenna input deviate this quantity from its ideal value and ${I_{rec}\over I_{sky}} < 1$.
+Also, frequency dependence of the feed and the dish as well as the multiple reflections introduces the small scale fluctuations as shown in the red curve.
+}
+% HERA feed design is derived from modified PAPER antenna and therefore the return loss closely relates to the PAPER antenna response with slight frequency shift.
 The return loss measured when the HERA feed is suspended over the dish is, however, show deviation from the feed performance.
@@
 Measurement bandwidth is kept much larger than the bandwidth of operation to achieve higher delay resolution.
-A number of systematic effects as well as mathematical artefacts that are critical to this measurements are taken in to account in determination of the delay spectrum and described below.
+A number of systematic effects as well as mathematical artefacts that are critical to this measurements and corresponding estimation of the delay spectrum are taken in to account in determination of the delay spectrum and described below.
 
-\subsection{Estimation of the delay spectrum of the instrument}
+\subsection{Feed effect:zero delay correction}
 %At first, the frequency domain measurement of s11 is Fourier-transformed to compute the response of the system in the delay domain.
@@
 While measuring the return loss of the dish-feed assembly, the signal transmitted by the VNA is reflected first off the feed.
+This is represented by $\Gamma_{f}$ in equation \ref{eq:power_ratio}.
 This essentially represents a mismatch in between the feed and the 50 Ohm transmission line.
 In delay domain, this appears at the zero delay bin.
-The for the feed, the zero delay response is identical whether or not the feed is suspended on the dish and  Therefore, we measure this response by measuring the feed return loss alone while the feed is kept on the ground facing the sky.
-This results in feed response alone including the feed cage structure but excluding the dish response.
-The using the return loss measurement of the feed $(\Gamma_{f})$, the return loss measurement $s_{11}$ of the dish and feed assembly is corrected via equation \ref{eq:power_ratio} and the quantity of interest ${I_{rec}\overI_{sky}}$ is estimated.
+The zero delay response is identical whether or not the feed is suspended on the dish and  Therefore, we measure this response by measuring the feed return loss alone while the feed is kept on the ground facing the sky.
+This results in feed return loss alone including the surrounding cage structure but excluding the dish response.
+While $\Gamma_{f}$ fraction of power is reflected off the feed, $1+\Gamma_{f}$ fraction of the power gets transmitted.
+In receiving mode, upon initial incidence, $\Gamma_{f}$ fraction of voltage is reflected back in to the space while $1+\Gamma_{f}$ voltage enters the feed.
+In receiving mode, in delay domain, this appears at the zero delay bin.
+The using the return loss measurement of the feed $(\Gamma_{f})$, the return loss measurement $s_{11}$ of the dish and feed assembly is corrected via equation \ref{eq:power_ratio} for the zero delay component and the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated.
 

### 2016-04-14 DishReflectometry/Paper1_v1.tex
Proofreading and sharping
Basic proofreading, grammer checking, and sharping of sentence structure.

--- 2016-04-05 DishReflectometry/Paper1_v1.tex
@@
 needs of foreground suppression and signal sensitivity in direct tension with one
-another. In addition to that, systematic effects are unique to each instruments and their manifestation 
+another. In addition to that, systematic effects are unique to each instrument and their manifestation 
 is different in each dataset.
@@
 in an interferometric baseline and the maximum line-of-sight Fourier mode\footnote{Assuming
-a flat sky, and using appropriate
+a flat sky and using appropriate
 cosmological scalars,
@@
 $\vec k\equiv(k_\parallel,\vec k_\perp)$, where $k_\parallel$ is aligned with the
-spectral axis $\nu$, and $\vec k_\perp$ lies in the plane of the sky.}
+spectral axis, $\nu$, and $\vec k_\perp$ lies in the plane of the sky.}
 that may be occupied by smooth spectrum foreground emission.  At low-order $k_\parallel$ modes
@@
 the chromaticity of the elements in isolation from the chromaticity inherent to
-element separation in an interferometric baseline.}.  In promising avoidance-based
+element separation in an interferometric baseline.}.  In the promising, avoidance-based
 foreground strategy employed by PAPER ~\citep{parsons_et_al2014,ali_et_al2015}, these modes
-may be targeted as the lowest risk path for contraining 21~cm reionization in the near term.
+may be targeted as the lowest risk path for constraining 21~cm reionization in the near term.
 
@@
 The efficacy of the techniques of foreground removal from the measured data critically limits the 21~cm power spectrum measurements.
-The delay transformation technique of foreground removal, introduced by  ~\citep{ParsonsBacker2009,Parsons2012} computes the Fourier transform of the visibility measured by an interferometer and produces a spectrum, referred to as delay spectrum hereafter, which is a function of the geometric time delay corresponding to the physical length of the baseline between two antennas.
-For the visibilities measured over a wide field across wide frequency bandwidth, the delay spectrum is constituted by the instrument response, the foreground signal and 21cm power spectrum, hereafter referred to as EoR signal.
+The delay transformation technique of foreground removal, introduced by  ~\cite{ParsonsBacker2009,Parsons2012}, computes the Fourier transform of the visibility measured by an interferometer and produces a spectrum, referred to as the delay spectrum hereafter, which is a function of the geometric time delay corresponding to the physical length of the baseline between two antennas.
+For the visibilities measured over a wide field across a wide frequency bandwidth, the delay spectrum consists of the instrument response, the foreground signal, and the 21cm power spectrum, hereafter referred to as the EoR signal.
 %The complex visibility measured by an interferometer is a convolution of the instrument response with the true sky response in the UV plane.
 Therefore, when Fourier transformed, the delay spectrum is the multiplication of the sky response with the instrument response in the delay domain.
-The technique exploits the smooth spectral characteristics of the foreground and for a widefield wide bandwidth visibility measurement by an interferometer with a baseline $b$, confines the foreground contribution to the computed delay spectrum within the largest possible time delay $\tau = b/c$ corresponding to the given baseline length.
-Such techniques also assumes a spectrally smooth instrumental response whose contribution to the measured data, much as the contribution of the smooth spectrum foreground, also has an upper bound in the delay space imposed by the largest geometric delay of the given baseline.
-Beyond this limit, for an ideal system performance, the delay spectrum would be dominated by any wideband signal across the sky with spectral and spatial fluctuation over small scale such as the EoR signal and therefore, could be detectable.\\
-The interaction between the sky signal and instrument response can alter the relative contribution of the foreground, instrument response and the EoR signal at a given delay and thus influence the detectability of the EoR signal.
-Such interactions may cause the foreground and systematics to spill over at higher delays and thus push the upper limit of the foreground and systematic contaminated delay modes to much higher delays.
-In this process, the EoR signal over large spatial scale will be lost.
-
-The Hydrogen Epoch of Reionization Array (HERA) is a proposed array consisting of 568 14-m dishes in South Africa which will measure the 21~cm power spectrum between 100 to 200~MHz.
-In this paper, we investigate the performance of an individual HERA element and resulting contribution of the instrument response to the delay spectrum.
- Reflectometry measurements  are carried out across wide bandwidth on a prototype HERA element in Green
-Bank, WV (Figure \ref{fig:heradish}) and the results are interpreted in the light of delay spectrum technique.
+The technique exploits the smooth spectral characteristics of the foreground and for a widefield wide bandwidth visibility measurement by an interferometer with a baseline $b$, confines the foreground contribution to the computed delay spectrum within the largest possible time delay, $\tau = b/c$, corresponding to the given baseline length.
+Such techniques also assume a spectrally smooth instrumental response whose contribution to the measured data, much as the contribution of the smooth spectrum foreground, also has an upper bound in the delay space imposed by the largest geometric delay of the given baseline.
+Beyond this limit, for an ideal system performance, the delay spectrum would be dominated by any wideband signal across the sky with spectral and spatial fluctuations over small scales, such as the EoR signal, and therefore, could be detectable.\\
+\indent The interaction between the sky signal and instrument response can alter the relative contribution of the foreground, instrument response and the EoR signal at a given delay and, thus, influence the detectability of the EoR signal.
+Such interactions may cause the foreground and systematics to spill over into higher delays and, thus, push the upper limit of the foreground and systematics contaminated delay modes to much higher delays.
+In this process, the EoR signal over large spatial scales will be lost.
+\\
+\indent The Hydrogen Epoch of Reionization Array (HERA) is a proposed array consisting of 568 14-m dishes in South Africa which will measure the 21~cm power spectrum between 100 to 200~MHz.
+In this paper, we investigate the performance of an individual HERA element and the resulting contribution of the instrument response to the delay spectrum.
+ Reflectometry measurements  are carried out across a wide bandwidth on a prototype HERA element in Green Bank, WV (Figure \ref{fig:heradish}), and the results are interpreted in light of the delay spectrum technique.
 Section 2 describes the delay spectrum for the ideal and non-ideal performance of a two element interferometer.
@@
 Consider a two element interferometer with a baseline $\vec b$.
-If we denote the electric field sky signal in direction $\thhat$ by $\volt_\sky(\vec \theta, \nu)$  then the voltage output of each antenna may be written as,
+If we denote the electric field sky signal in the direction $\thhat$ by $\volt_\sky(\vec \theta, \nu)$, then the voltage output of each antenna may be written as,
 \begin{equation}
@@
 
-We define antenna cross power pattern as  $\beam(\thhat,\nu)=\bmvolt_{1}(\thhat,\nu)\bmvolt_{2}^{*}(\thhat,\nu)$ and denote the sky intensity as  $I_\sky(\thhat,\nu)=\volt_\sky(\thhat,\nu)\volt_\sky^{*}(\thhat,\nu)$.
+We define the antenna cross power pattern as  $\beam(\thhat,\nu)=\bmvolt_{1}(\thhat,\nu)\bmvolt_{2}^{*}(\thhat,\nu)$ and denote the sky intensity as  $I_\sky(\thhat,\nu)=\volt_\sky(\thhat,\nu)\volt_\sky^{*}(\thhat,\nu)$.
 Hence,
@@
 In ~\citet{parsons_et_al2012a}, the Fourier transform of the visibility along the frequency axis was introduced,
-resulting in the delay spctrum:
+resulting in the delay spectrum:
 \begin{eqnarray}
-\tilde V(\vec b, \tau) & = & \int\!\![{\beam(\vec b,\nu)*I_\sky(\vec b,\nu)] ~e^{-2\pi i\nu\tau}d\nu}\nonumber\\	                        %& = &   \left [ A(\vec b, \tau)\ast I_{sky}(\vec b, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega
+\tilde V(\vec b, \tau) & = & \int\!\![{\beam(\vec b,\nu)*I_\sky(\vec b,\nu)] ~e^{-2\pi i\nu\tau}d\nu}%\nonumber\\	                        %& = &   \left [ A(\vec b, \tau)\ast I_{sky}(\vec b, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega
 \label{eq3}
@@
 \begin{equation}
-  P(k_\perp,k_\parallel) = |\tilde V(\vec b, \tau)|^{2} \left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2,
+  P(k_\perp,k_\parallel) = (|\tilde V(\vec b, \tau)|^{2} \left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2 ,
 \label{eq:delay-power-spectrum}
@@
 \begin{equation}
-  k_\perp = \frac{2\pi f}{D}({b\over c}), \\
+  k_\perp = \frac{2\pi f}{D}\Bigg({b\over c}\Bigg), \text{ }
   k_\parallel = \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, 
@@
 $f$: observation frequency.\\
-$z$: cosmological redshift corresponding to frequency of observation.\\
+$z$: cosmological redshift corresponding to the frequency of observation.\\
  $\Delta B$: bandwidth centered at the observation frequency.\\
@@
 $E(z)= [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ \\
+\indent In this paper, we use $\Omega_{M}=0.27$, $\Omega_{\Lambda}=0.73$, $\Omega_{K}=1-\Omega_{M}-\Omega_{\Lambda}$, $H_0=100 h^{-1}\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P(k_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.
 
-In this paper, we use $\Omega_{M}=0.27$, $\Omega_{\Lambda}=0.73$, $\Omega_{K}=1-\Omega_{M}-\Omega_{\Lambda}$, $H_0=100\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P_\textrm{d}(k_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.
-
-Since both $k_{\perp}$ and $k_{\parallel}$ are functions of the delay $\tau$ corresponding to the given baseline length, the redshifted 21 cm power spectrum could be estimated from the measurement of delay spectrum of visibility by an interferometer.
-Sky delay spectrum from any direction $\thhat$ is convolved with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ %defined this differently earlier
+\indent Since both $k_{\perp}$ and $k_{\parallel}$ are functions of the delay $\tau$, corresponding to the given baseline length, the redshifted 21 cm power spectrum could be estimated from the delay spectrum of the visibility measured by an interferometer.
+The sky delay spectrum from any direction $\thhat$ is convolved with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ %defined this differently earlier
  in the delay domain.
-The maximum geometric delay possible for a given base line would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$ when the phase centre is halfway in between the two antennas.
+The maximum geometric delay possible for a given baseline would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$, when the phase centre is halfway in between the two antennas.
 %The phase center is elsewhere defined as being at the center of one of the antennas.
  Hence, the sky contribution from any direction would be confined within $-\tau_{g}<\tau<\tau_{g}$.
-Due to chromaticity of the sky signal as well as instrument reponse, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with decaying amplitude [Ref to the figure Parsons12].
-Sky delay spectrum $P_{sky}(\tau)$ is contributed by the foreground  $P_{fg}(\tau)$  which is spectrally smooth and the 21~cm power spectrum $P_{21}(\tau)$ which contains spectral signatures.Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground with respect to the delay spectrum of the $I_{21}$ reduces and the 21~cm delay spectrum could be detectable.
+Due to the chromaticity of the sky signal as well as the instrument response, the delay spectrum of the sky spills over into delays with $\tau> \tau_{g}$, with a decaying amplitude [Ref to the Figure Parsons12].
+The foreground, $P_{fg}(\tau)$, which is spectrally smooth, and the 21~cm power spectrum, $P_{21}(\tau)$, which contains spectral signatures, contribute to the sky delay spectrum, $P_{sky}(\tau)$.Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground, with respect to the delay spectrum of the $I_{21}$, reduces and the 21cm delay spectrum could be detectable.
 
@@
 Hence, the sky contribution from any direction would be confined within $-\tau_{g}<\tau<\tau_{g}$.
-Due to chromaticity of the sky signal as well as instrument reponse, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with decaying amplitude [Ref to the figure Parsons12].
+Due to chromaticity of the sky signal as well as instrument reponse, the delay spectrum of the sky spills over the delay $\tau> \tau_{g}$ with decaying amplitude [Ref to the Figure Parsons12].
 Sky delay spectrum $I_{sky}(\tau)$ is contributed by the foreground  $I_{fg}(\tau)$  which is spectrally smooth and the 21~cm power spectrum $I_{21}(\tau)$ which contains spectral signatures.
@@
 \section{Effects of multiple reflections on visibility and delay spectrum}
-The Hydrogen Epoch of Reionization Array consists of parabolic dishes which provide increased collecting area per array element compared to its predecessor experiment PAPER.
-Plane waves incident on a parabolic dish are focussed at the feed which is kept at the focal plane of the dish.
+The Hydrogen Epoch of Reionization Array consists of parabolic dishes which provide increased collecting area per array element compared to its predecessor experiment, PAPER.
+Plane waves incident on a parabolic dish are focussed at the feed, which is kept at the focal plane of the dish.
 The mismatch between the impedance of free space and the feed and transmission line results in a partial coupling of the sky signal into the feed while the rest is reflected off the feed. 
-The reflected signal illuminates the dish and most of it is reflected back into the space.
-However, a part of it reflects back and forth several times in between the feed and the vertex of the dish which is shadowed by the feed (dashed blue arrows in Figure \ref{fig:cartoon}).
-Such reflections generate multiple copies of the incident sky signal of reduced strength at various delay and phase and thus produces spurious correlations in the visibilities of interferometric data.
-Identical spurious visibilities could be resulted due to reflections internal to the system causing delay space distortion.
-Therefore, it is necessary to measure and understand the instrument delay spectrum in order to qualify the system for the measurement of 21cm power spectrum.
-In this section we compute the visibility of a two element interferometer accounting for the additional reflections of the sky signal in between the feed and the dish vertex and the corresponding effects on the delay spectrum, using the multiple reflection formulation of Sec.
+The reflected signal illuminates the dish and most of it reflects back into free space.
+However, a part of it is reflected back and forth several times in between the feed and the vertex of the dish, which is shadowed by the feed.
+%No longer an included figure (dashed blue arrows in Figure \ref{fig:cartoon}).
+Such reflections generate multiple copies of the incident sky signal of reduced strength at various delays and phases and, thus, produce spurious correlations in the visibilities of interferometric data.
+Identical spurious visibilities could result from reflections internal to the system causing delay space distortion.
+Therefore, it is necessary to measure and understand the instrument delay spectrum in order to qualify the system for the measurement of the 21cm power spectrum.
+\\
+\indent In this section, we compute the visibility of a two element interferometer accounting for the additional reflections of the sky signal in between the feed and the dish vertex and the corresponding affects on the delay spectrum, using the multiple reflection formulation of Sec.
 \ref{sec:multiple}.
-In this section, the effect of reflections on the visibility data and corresponding effect on the delay spectrum is discussed in detail.
-We assume two antennas with identical geometry and electrical parameters i.e, $\bmvolt_{1}(\thhat,\nu)=\bmvolt_{2}(\thhat,\nu) = \bmvolt(\thhat,\nu)$.
+We also examine, in detail, the affect of reflections on the visibility data and the corresponding affect on the delay spectrum.
+We assume two antennas with identical geometry and electrical parameters, i.e, $\bmvolt_{1}(\thhat,\nu)=\bmvolt_{2}(\thhat,\nu) = \bmvolt(\thhat,\nu)$.
  \subsection{Antenna Reception With Multiple Reflections}
 \label{sec:multiple}
-To examine the performance of an antenna and feed in the presence of multiple reflections, think of the system as a screen at a distance $F$ from a feed (see Fig.
-\ref{fig:sys}), noting that this does ignore the sky pattern of the feed itself.
-The screen reflects voltage as $\Gamma_d$ and transmits $(1+\Gamma_d)$ (see, {\em e.g.} Pozar).
+To examine the performance of an antenna and feed in the presence of multiple reflections, we can think of the system as a screen at a distance $F$ from a feed (see Figure \ref{fig:sys}), noting that this does ignore the sky pattern of the feed itself.
+The screen reflects a factor, $\Gamma_d$, of the voltage and transmits $(1+\Gamma_d)$ (see, {\em e.g.} Pozar).
 Similarly, the feed reflects $\Gamma_f$ and transmits $(1+\Gamma_f)$.
 The voltage pattern $\volt_{sky}$ is incident onto that system and  $(1+\Gamma_{d})(1+\Gamma_{f})$ is coupled into the cable leading from the feed.
-Additionally however, the voltage pattern is reflected off the feed ($\Gamma_f$), then the dish ($\Gamma_d$) and subsequently $(1+\Gamma_{f})$ of it reenters the feed with a roundtrip time delay $\Delta \tau=2F/c$.
+Additionally, however, the voltage pattern is reflected off the feed ($\Gamma_f$), then the dish ($\Gamma_d$) and subsequently $(1+\Gamma_{f})$ of it reenters the feed with a roundtrip time delay $\Delta \tau=2F/c$.
 Hence, if $v_{sky}$ is reflected $n$ times in between the feed and the dish, the net voltage entering the feed after the
@@
 Note that $n=0$ is when the initial wave enters the cable at the feed (where we assume we have set our reference plane).
-We may identify $(1+\Gamma_d)(1+\Gamma_{a})$ as the voltage reception pattern of the antenna, denoted $\bmvolt(\thhat,\nu)$, which is a function of angle on the sky.
+We may identify $(1+\Gamma_d)(1+\Gamma_{a})$ \textbf{Shouldn't have $\mathbf{(1+\Gamma_a)}$?} as the voltage reception pattern of the antenna, denoted $\bmvolt(\thhat,\nu)$, which is a function of angle on the sky.
 Additionally, $(1+\Gamma_f$) is the voltage efficiency for the feed (not a function of angle).
@@
 
-Accurate measurement of this quantity requires receiving the $v_{sky}$ from a well calibrated wideband source in the sky in the far field of the HERA antenna element with significant isotropic emission.
-While this condition is hard to achieve in practice, due to reciprocity of the antenna performance in the transmission and reception mode, the right hand side of the equation \ref{eq:Sigma} could be measured using the returnloss measurement technique with a vector network analyser.
-A vector network analyzer (VNA) is connected to the HERA element via a 50 feet long cable.
-The VNA transmit a broadband noise voltage  $\volt_{trans}$.
-$(1+\Gamma_f)$ fraction of this voltage is radiated by the feed while the fraction $\Gamma_{f}$ returns to the VNA.
-While the radiated signal illuminated the dish and most of it is radiated into the space,  $\Gamma_d$ fraction of this signal is reflected back towards the feed and $(1+\Gamma_f)$ is received by the VNA.
-The received voltage after $n$ reflections between the dish and the feed, (where again $n=0$ is the first reflected signal at the reference plane) is therefore:
+An accurate measurement of this quantity requires receiving $v_{sky}$ from a well calibrated, wideband source in the sky in the far field of the HERA antenna element with significant isotropic emission.
+While this condition is hard to achieve in practice, due to the reciprocity of the antenna performance in the transmission and reception mode, the right hand side of equation \ref{eq:Sigma} could be measured using the return loss measurement technique with a vector network analyzer (VNA).
+\\
+\indent A VNA is connected to the HERA element via a 50-foot cable.
+It then transmits a broadband noise voltage, $\volt_{trans}$, and a factor $(1+\Gamma_f)$ of this voltage is radiated by the feed while the fraction $\Gamma_{f}$ returns to the VNA.
+Although the radiated signal illuminates the dish and most of it is radiated into free space, a fraction $\Gamma_d$ of this signal is reflected back towards the feed, and $(1+\Gamma_f)$ is received by the VNA.
+The received voltage, after $n$ reflections between the dish and the feed (where again $n=0$ is the first reflected signal at the reference plane), is therefore:
 
@@
          && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp (\Gamma_d\Gamma_f\dfngexp)^2 \nonumber \\
-&&  ....+ \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp (\Gamma_d\Gamma_f\dfngexp)^n
+&&  ....+ \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp (\Gamma_d\Gamma_f\dfngexp)^n \nonumber \\
 \end{eqnarray}
@@
 The VNA measures the quantity $\volt_{rec}/\volt_{trans}=s_{11}$ which is the voltage reflection coefficient of the HERA element.
-The fundamental difference between the righ hand side of the equation \ref{eq:Sigma} and \ref{eq:s11} are the $n=0$ term and the multiplicative factor in front of the convergent series $\displaystyle\sum\limits_{n=1}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}$ that represents the contribution of the delayed voltage components at the VNA input arising due to multiple signal reflection between the feed and the dish.
-Finally, writing $\volt_{rec}/\volt_{trans}=s_{11}$, equation \ref{eq:s11} could be written as,
+The fundamental differences between the right hand side of equations \ref{eq:Sigma} and \ref{eq:s11} are the $n=0$ term and the multiplicative factor in front of the convergent series $\displaystyle\sum\limits_{n=1}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}$ that represents the contribution of the delayed voltage components at the VNA input, arising due to multiple signal reflections between the feed and the dish.
+Finally, writing $\volt_{rec}/\volt_{trans}=s_{11}$, equation \ref{eq:s11} can be written as,
 \begin{equation}
@@
 \end{eqnarray}
-When the feed return loss is measured separately, all the higher order terms of the equation \ref{eq:s11} does not exist.
-In this case $\Gamma_f = s_{11}^{f}$.
-Using this measurements and VNA measurement of $s11$, the quantity $v_{rec}\over v_{sky}$ is estimated.
-
-From this, for a two element interferometer with identical antenna elements, the ratio of the received sky intensity to true sky intensity will be, 
+When the feed return loss is measured separately, all the higher order terms of equation \ref{eq:s11} do not exist.
+In this case, $\Gamma_f = s_{11}^{f}$.
+Using this measurement and the VNA measurement of $s11$, the quantity $v_{rec}\over v_{sky}$ is estimated.
+\\
+%
+\indent From this, for a two element interferometer with identical antenna elements, the ratio of the received sky intensity to true sky intensity will be, 
 \begin{eqnarray}
-{I_{rec}\over I_{sky} } & = & |{\volt_{rec}\over \volt_{sky} }|^2 =  \beam(\thhat,\nu)\times \nonumber\\
+{I_{rec}\over I_{sky} } & = & \Bigg|{\volt_{rec}\over \volt_{sky} }\Bigg|^2 =  \beam(\thhat,\nu)\times \nonumber\\
              && \left[|1+\Gamma_f|^2 +  2\operatorname{Re}\left(\frac{\Gamma_f}{(1+\Gamma_f)}(s_{11} - \Gamma_f)\right)\right] + \nonumber\\ 
@@
 
-Comparing eq \ref{eq:power_ratio} with \ref{eq2}, the cross power generated by $v_{1}$ and $v_{2}$ would have spurious visibility response due to mutual correlation between multiply reflected voltages represented by the second and the third term of the right hand side of the equation \ref{eq:power_ratio}.
-In ideal case, $\Gamma_{f}=0$ in which case equation \ref{eq:power_ratio} results in equation \ref{eq2}.
-Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum.
-In the delay domain, visibility contributed by any two voltage components from two antennas with no mutual delay will be located at the delay $\tau = 0$ whereas any two voltage components from two antennas components having a mutual delay of $n\Delta \tau$ will be centred at $n\Delta \tau$.
-These will broaden the width of the delay spectrum which finally interferes with the 21cm power spectrum detection.
+Comparing equations \ref{eq:power_ratio} and \ref{eq2}, the cross power generated by $v_{1}$ and $v_{2}$ would have a spurious visibility response due to the mutual correlation between multiply reflected voltages represented by the second and the third term of the right hand side of equation \ref{eq:power_ratio}.
+In the ideal case, $\Gamma_{f}=0$, in which case equation \ref{eq:power_ratio} results in equation \ref{eq2}.
+The Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum.
+In the delay domain, visibilities contributed to by any two voltage components from two antennas with no mutual delay will be located at the delay $\tau = 0$ whereas any two voltage components from two antennas having a mutual delay of $n\Delta \tau$ will be centred at $n\Delta \tau$.
+These will broaden the width of the delay spectrum, which ultimately interferes with the 21cm power spectrum detection.
 % Combining these terms, the expression of visibility will be,
@@
 \\
-In a related series of papers, (Thyagarajan et al 2016) has shown the detailed sensitivity calculations of HERA is using a comprehensive foreground as well as model for EoR power spectrum for various simulated antenna element response (\ref{fig:sim_limit_delay}) From this simulations, the figure \ref{fig:sim_limit_delay} (Thyagarajan et al) shows the level of attenuation required for the multiple reflected sky signal in order to reduce the foreground contaminations at the delay modes significant for power spectrum measurements.
-Ewall-Wice et al 2016 has simulated the time domain response of the HERA element considering multiple reflections between the feed and the dish.
-Figure \ref{fig:sim_limit_delay} shows the simulated cross-power response of a pair of HERA antenna as a function of time(Ewall-wice et al).
+In a related series of papers, Thyagarajan et al.
+(2016) have shown the simulated sensitivity calculations of HERA for various antenna element responses (Figure \ref{fig:sim_limit_delay}) using a comprehensive foreground model as well as a model for the EoR power spectrum.
+From these simulations, Figure \ref{fig:sim_limit_delay} (Thyagarajan et al.) shows the level of attenuation required for the multiply reflected sky signal in order to reduce the foreground contaminations at the delay modes significant for power spectrum measurements.
+Ewall-Wice et al.
+(2016) has simulated the time domain response of the HERA element considering multiple reflections between the feed and the dish.
+Figure \ref{fig:sim_limit_delay} shows the simulated cross-power response of a pair of HERA antennas as a function of time (Ewall-wice et al.).
 These simulations set up the performance criterion for the HERA antenna element.
@@
 \end{minipage}
-\caption{Left: Signal attenuation required for the reflected sky power arriving at the feed at higher delay as estimated from the simulated antenna beam and froeground models (Thyagarajan et al).
-The three different contour shows three different system performance requirements set based on the simulated response of HERA element for a measurement frequency of 150MHz corresponding to the redshift of $z=8.47$ and a 14.5m baseline.
-The instrumental requirements become extremely stringent for the detection of the smaller $k_\parallel$ values corresponding to very large spatial scales.
+\caption{Left: Signal attenuation required for the reflected sky power arriving at the feed at higher delays, as estimated from the simulated antenna beam and foreground models (Thyagarajan et al.).
+The three different contours show three different system performance requirements based on the simulated response of the HERA element for a measurement frequency of 150MHz, corresponding to the redshift of $z=8.47$, and a 14.5m baseline.
+The instrumental requirements become extremely stringent for the detection of the smaller $k_\parallel$ values, corresponding to very large spatial scales.
 Right: The simulated cross power response kernel for HERA.
-The simulation assumes and achromatic beam with the chromaticity attributed entirely by the multiple reflections between the dish and the feed.
-This shows the levels to which the multiple reflections at the higher delays is expected to be reduced following the dish and the feed design.}
+The simulation assumes an achromatic beam with the chromaticity attributed entirely to the multiple reflections between the dish and the feed.
+This shows the level to which the multiple reflections at the higher delays is expected to be reduced following the dish and feed designs.} %Some explanation of the left hand axis of the right panel figure would be really nice in here since this is the only mention of R(tau), and it's new notation compared to the rest of the paper.
 \label{fig:sim_limit_delay}       
@@
 \vspace{1.0 em}
-\caption{HERA feed consists of a pair of crossed dipole ove xxx mt diameter backplane made of wire mesh.
-The backplane is surrounded by xxx m wire mesh around the edge resulting in encasing the cross dipole in a cylindrical cage.}
+\caption{The HERA feed consists of a pair of crossed-dipoles ove xxx mt diameter backplane made of wire mesh.
+The backplane is surrounded by xxx m wire mesh around the edge resulting in encasing the crossed-dipoles in a cylindrical cage.}
 \label{fig:herafeed}
 \end{figure*}
-Reflectometry measurements are carried out at the HERA element prototype in Green
-Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise the performance.  HERA element consists off a $14\,m$ diameter
-parabolic reflector and a crossed-dipole pair as a feed.
-The cross dipole antenna pair is identical to the feed of the PAPER antenna which is suspended at the focal plane of the dish with the support of three vertical poles.
-HERA elements are closely spaced with centre to centre distance between two dishes are equal to the dish diameter.
-Therefore, to reduce the coupling between the adjacent dishes, the crossed dipole feed along with the back plane is encased in a cylindrical cage.
-The feed is raised and
-lowered by a three-pulley system mounted on the three poles.
-The focal height of the dish is $5m$.
-The detail geometry and electromagnetic design of of the feed is presented in deBoer et al 2016 (in prep).
+Reflectometry measurements were carried out on the prototype HERA element in Green
+Bank, WV, (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise the performance. The HERA element consists of a $14\,m$ diameter
+parabolic reflector and a crossed-dipole pair -- identical to the feed of the PAPER antenna -- as a feed, which is suspended at the focal plane of the dish, where the focal height is $5m$, with the support of three vertical poles.
+The HERA elements are closely spaced, with the centre-to-centre distance between two dishes equal to the dish diameter.
+Therefore, to reduce the coupling between the adjacent dishes, the crossed-dipole feed and the back plane are encased in a cylindrical cage.
+The feed is raised and lowered by a three-pulley system mounted on the three poles.
+The detailed geometry and electromagnetic design of the feed is presented in deBoer et al.
+2016 (in prep).
 \\
-A vector network analyser is connected via a 50feet long cable at the feed output of the HERA element and the return loss $(s_{11})$ of the HERA element is measured as a function of frequencies while the feed is suspended at the focal plane of the dish.
-This measurement is
-Section 3 laid the mathematical framework of how the delay spectrum is estimated from the return loss measurement. 
+\indent A VNA is connected via a 50-ft cable at the feed output of the HERA element, and the return loss $(s_{11})$ is measured as a function of frequency while the feed is suspended at the focal plane of the dish.
+Section 3 laid the mathematical framework for how the delay spectrum is estimated from the return loss measurement.
 %, if the incident power from the sky signal is $I_{sky}$, the feed
@@
 %\end{eqnarray}
-
-Return loss measurements are similar to auto correlation measurement from a single HERA element.
-Upon our assumption that two adjacent antenna elements have identical design parameters and electrical properties, this power is also a measure of the cross power or the visibility $\vis (\vec b, \nu)$ between the two antennas with a normalisation factor of $2$.
+%
+Return loss measurements are similar to auto correlation measurements from a single HERA element.
+Given our assumption that two adjacent antenna elements have identical design parameters and electrical properties, this power is also a measure of the cross power, or the visibility $\vis (\vec b, \nu)$, between the two antennas with a normalization factor of $2$.
+%
 \section{Results}
@@
 \centering
-\includegraphics[angle=0, width=\linewidth]{plots/s11_HERA_feed_PAPER_ph.png}
+\includegraphics[angle=0, width=\linewidth]{plots/RL_phse.png}
 \end{minipage}
-\caption{Left: Magnitude of the return loss of power measured in between 100 to 200 MHz using vector network analyser.
-Right panel shows the corresponding phase.HERA feed design is derived from modified PAPER antenna and therefore the return loss closely relates to the PAPER antenna response with slight frequency shift.
-The return loss measured when the HERA feed is suspended over the dish is, however, show deviation from the feed performance.
+\caption{Left: Magnitude of the return loss of power measured between 100 to 200 MHz using the vector network analyzer.
+Right: The corresponding phase.
+The return loss of the feed alone is shown in green while the same for the feed+dish assembly is shown in blue.
+Finally, the quantity of interest ${I_{rec}\over I_{sky}}$ is shown in red.
+Ideally, 100\% of the sky power is received, and ${I_{rec}\over I_{sky}} = 1$, or 0dB.
+A finite return loss at the antenna input causes deviations in this quantity from its ideal value, and ${I_{rec}\over I_{sky}} < 1$.
+Also, the frequency dependence of the feed and dish, as well as the multiple reflections, introduces the small scale fluctuations shown in the red curve.
+}
+% The HERA feed design is derived from a modified PAPER antenna, and, therefore, the return loss closely relates to the PAPER antenna response with a slight frequency shift.
+The return loss measured when the HERA feed is suspended over the dish, however, shows deviations from the feed performance.
 }
@@
 Figure \ref{fig:freq} shows the return loss measured between $100$ to
-$200MHz$ when the feed is suspended at the focal plane of the parabolic dish which is at $5m$ from the dish vertex.
+$200$ MHz when the feed is suspended at the focal plane of the parabolic dish -- $5m$ from the dish vertex.
 This measurement is Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{eq3}.
-Measurement bandwidth is kept much larger than the bandwidth of operation to achieve higher delay resolution.
-A number of systematic effects as well as mathematical artefacts that are critical to this measurements are taken in to account in determination of the delay spectrum and described below.
+The measurement bandwidth is kept much larger than the bandwidth of operation to achieve a higher delay resolution.
+A number of systematic effects, as well as mathematical artifacts critical to these measurements and the corresponding estimation of the delay spectrum, are taken in to account in determining the delay spectrum and are described below.
 
-\subsection{Estimation of the delay spectrum of the instrument}
+\subsection{Feed effect: zero delay correction}
 %At first, the frequency domain measurement of s11 is Fourier-transformed to compute the response of the system in the delay domain.
@@
 While measuring the return loss of the dish-feed assembly, the signal transmitted by the VNA is reflected first off the feed.
-This essentially represents a mismatch in between the feed and the 50 Ohm transmission line.
-In delay domain, this appears at the zero delay bin.
-The for the feed, the zero delay response is identical whether or not the feed is suspended on the dish and  Therefore, we measure this response by measuring the feed return loss alone while the feed is kept on the ground facing the sky.
-This results in feed response alone including the feed cage structure but excluding the dish response.
-The using the return loss measurement of the feed $(\Gamma_{f})$, the return loss measurement $s_{11}$ of the dish and feed assembly is corrected via equation \ref{eq:power_ratio} and the quantity of interest ${I_{rec}\overI_{sky}}$ is estimated.
-
+This is represented by $\Gamma_{f}$ in equation \ref{eq:power_ratio}.
+This essentially represents a mismatched impedance between the feed and the 50 Ohm transmission line.
+In the delay domain, this appears at the zero delay bin.
+This response is identical whether or not the feed is suspended on the dish.
+We can, therefore, quantify this response by measuring the feed return loss while the feed is kept on the ground facing the sky.
+This results in a feed return loss including the surrounding cage structure but excluding the dish response.
+While a fraction, $\Gamma_{f}$, of the power is reflected off the feed, $1+\Gamma_{f}$ gets transmitted.
+In the receiving mode, upon initial incidence, $\Gamma_{f}$ of the voltage is reflected back into free space while $1+\Gamma_{f}$ enters the feed, and, in the delay domain, this appears at the zero delay bin.
+Using the return loss measurement of the feed $(\Gamma_{f})$ and the return loss measurement, $s_{11}$, of the dish, the feed assembly is corrected via equation \ref{eq:power_ratio} for the zero delay component, and the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated.
+%
+%
 \begin{figure}
@@
 \includegraphics[width=\linewidth]{plots/delay_spectrum_100_200_BH.png}
-\caption{Delay spectrum of the HERA element, the PAPER element and the HERA feed estimated by taking the Fourier transform of the measured return loss of power at the feed output.
-HERA feed design is driven by the PAPER element with improved response at all delays.
-The feed, when suspended on the dish results in a more complex return loss and corresponding delay response is shown in the figure.}
+\caption{Delay spectrum of the HERA element, the PAPER element, and the HERA feed estimated by taking the Fourier transform of the measured return loss of power at the feed output.
+The HERA feed design is driven by the PAPER element with an improved response at all delays.
+The feed, when suspended on the dish, results in a more complex return loss, and the corresponding delay response is shown in the figure.} %Delay units are incorrect!!!!
+Should be ns not GHz!!!!
 \label{fig:delay_spectrum}
 \end{figure}
-
+%
 \subsubsection{Effect of antenna beam pattern and feed return loss on delay spectrum estimation}
-The return loss $\Gamma_{f}$ determines the amount of power coupled to the system via the feed antenna.
-Additionally, with each reflections, the power coupled to the system reduces by a factor of $\Gamma_{f}^{2}$.
-Since reflected signal results in system response in higher delay, multiple reflections of the signal off the feed and the dish would result in an exponential envelope in the delay spectrum.
-The return loss of power results from the antenna impedance mismatch with the free space as well as the transmission line.
-The complex feed antenna impedance is shown in the figure \ref{fig:feed_impedance}.
+The return loss $\Gamma_{f}$ determines the amount of power coupled to the system via the feed.
+Additionally, with each reflection, the power coupled to the system reduces by a factor of $\Gamma_{f}^{2}$.
+Since the reflected signal results in a system response at a higher delay, multiple reflections of the signal off the feed and the dish would result in an exponential envelope in the delay spectrum.
+The return loss of power results from the antenna impedance mismatch with free space as well as the transmission line.
+The complex antenna impedance is shown in Figure \ref{fig:feed_impedance}.
 \begin{figure}
@@
 \includegraphics[width=\linewidth]{plots/Feed_impedance.png}
-\caption{Complex antenna impedance of the HERA feed element.}
+\caption{Complex antenna impedance of the HERA feed element.} %Some indication of which line is which on the plot would be really helpful here.
 \label{fig:feed_impedance}
 \end{figure} 
-While antenna beam pattern $A_{f}$ is a smooth function of frequency and should have its imprint confined to lower delays, the return loss $\Gamma_{f}$ broadens the delay spectrum.
-However, a smaller return loss will result in vertical shift of the delay spectrum at lower values and therefore can make the higher order reflections insignificant.
-Given the antenna impedance and the 50 Ohm transmission line the measurements are done using the passive balun with a 2:1 impedance ratio providing a net return loss of power between the sky, the antenna and the transmission line shown in the figure \ref{fig:freq}.
+%
+While the antenna beam pattern, $A_{f}$, is a smooth function of frequency and should have its imprint confined to lower delays, the return loss, $\Gamma_{f}$, broadens the delay spectrum.
+However, a smaller return loss will result in a vertical shift of the delay spectrum at lower values and, therefore, can make the higher order reflections insignificant.
+Given the antenna impedance and the 50 Ohm transmission line, the measurements are done using a passive balun with a 2:1 impedance ratio, providing a net return loss of power between the sky, the antenna, and the transmission line shown in Figure \ref{fig:freq}.
 This provides the maximum impedance matching.
@@
 \subsubsection{Effect of frequency bandwidth on delay spectrum estimation}
-Estimation of the delay spectrum by taking the Fourier transform of the measured return loss is sensitive to the frequency bandwidth of operation.
-Since the measurements are done in the spectral domain, measurement between two frequencies is analogous to windowing the frequency domain data by a square window function.
-In the delay domain, Fourier transform of this would result in multiple side lobes at higher delays.
+The estimation of the delay spectrum by taking the Fourier transform of the measured return loss is sensitive to the frequency bandwidth of operation.
+Since the measurements are done in the spectral domain, a measurement between two frequencies is analogous to windowing the frequency domain data by a square window function.
+In the delay domain, the Fourier transform of this would result in multiple side lobes at higher delays.
 Therefore, appropriate windowing of the data is necessary prior to taking the Fourier transform of the measured data.
-Figure \ref{fig:window} shows the delay spectrum estimated from the measured data using a square window as well as Blackman Harris window.
-Windowing the data prior to Fourier transform significantly reduces the system response higher delays.
+Figure \ref{fig:window} shows the delay spectrum estimated from the measured data using a square window as well as a Blackman Harris window.
+Windowing prior to Fourier transforming the data significantly reduces the system response at higher delays.
 \begin{figure}
@@
 \includegraphics[width=\linewidth]{plots/window.png}
-\caption{Effect of finite bandwidth on estimation of delay spectrum: Blue line shows the delay spectrum of the HERA element computed from the measured data which is band limited between 100 to 200MHz.
-Green line shows the delay spectrum estimated from the same data set after multiplying the data by a Blackman Harris window.
-The delay spectrum of the windowed data set shows significant reduction in the instrument response at higher delays.}
+\caption{The affect of a finite bandwidth on the estimation of the delay spectrum: The blue line shows the delay spectrum of the HERA element computed from the measured data, which is band limited between 100 to 200MHz.
+The green line shows the delay spectrum estimated from the same data set after multiplying the data by a Blackman Harris window.
+The delay spectrum of the windowed data set shows a significant reduction in the instrument response at higher delays.}
 \label{fig:window}
 \end{figure} 
-\subsubsection{Effect of dish and the feed on delay spectrum estimation}
-Measurement equations shows the effects of multiple reflections of the sky signal between the feed and the dish.
+\subsubsection{Effect of the dish and feed on the delay spectrum estimation}
+The measurement equations show the effects of multiple reflections of the sky signal between the feed and the dish.
 Any other reflections off the feed structure and/or any other part of the dish-feed assembly would appear at arbitrary delays.
-The estimated delay spectrum of the instrument is collectively contributed by all the reflections.
-We measure the return loss of the feed alone keeping it on the ground facing the sky shown in the Figure \ref{fig:freq}.
-Delay spectrum estimated from this measurement provides the lowest limit of the delay spectrum of the instrument considering there is no multiple reflections in between the feed and the dish.
- Any additional reflections also contributes to the measured return loss and thus contributed to the delay spectrum at various delays.
-Figure \ref{fig:delay_spectrum} shows the delay spectrum of the feed while it is kept upside down on the ground in green, as well as that of a HERA antenna with the feed suspended at the focal plane in blue.
-Red line shows shows the delay spectrum of the PAPER antenna in comparison with the HERA element.
+The estimated delay spectrum of the instrument is collectively contributed to by all the reflections.
+We measure the return loss of the feed alone, keeping it on the ground facing the sky (Figure \ref{fig:freq}).
+The delay spectrum estimated from this measurement provides the lowest limit of the delay spectrum of the instrument, considering there are not multiple reflections between the feed and the dish.
+ Any additional reflections also contribute to the measured return loss and, thus, the delay spectrum at various delays.
+Figure \ref{fig:delay_spectrum} shows the delay spectrum of the feed while it is kept upside down on the ground (in green), as well as that of a HERA antenna with the feed suspended at the focal plane (in blue).
+The red line shows the delay spectrum of the PAPER antenna for comparison with the HERA element.
 %\subsubsection{Effect of feed height on delay spectrum estimation}
-\subsubsection{Comparison of performance of HERA with PAPER}
-While PAPER has established the till date the most stringent upper limit on the 21cm power spectrum measurement, the need to increase the measurement sensitivity called for increased collecting area per PAPER antenna.
-This has driven to the parabolic reflector antenna based design of the PAPER successor HERA where essentially the PAPER antenna with minor modification of the ground plane-side plane assembly works as the feed and thus having larger collecting area per element.
-Figure \ref{fig:freq} shows the return loss measurement of power of the PAPER antenna and figure \ref{fig:delay_spectrum} shows (red line) the corresponding delay spectrum.
-The feed element shows improved delay response compared to the PAPER element across all delays $>50~ns$ with marginal improvement at delays $<50~ns$.
+\subsubsection{Performance Comparison: HERA vs. PAPER}
+While PAPER has established the, to date, most stringent upper limit on the 21cm power spectrum measurement, the need to increase the measurement sensitivity called for increased collecting area per PAPER antenna.
+This has driven the parabolic reflector antenna design of the PAPER successor, HERA, where essentially the PAPER antenna, with minor modifications of the ground plane-side plane assembly, works as the feed and, thus, in combination with the dish, yields a larger collecting area per element.
+Figure \ref{fig:freq} shows the return loss measurement for the PAPER antenna, and Figure \ref{fig:delay_spectrum} shows the corresponding delay spectrum (red line).
+The HERA feed element shows an improved delay response compared to the PAPER element across all delays $>50~ns$, with marginal improvement at delays $<50~ns$.
 The delay response of the HERA element degrades marginally as the feed is suspended over the dish due to multiple reflections between the feed and the dish.
-It is evident that majority of the response at lower delays are contributed due to the feed and its supporting structure at lower delays which is somewhat common to all three measurements.
-At the lower delays, the structures in the delay response remains unaltered even with the variation of the feed height relative to the dish vertex.
-It is essentially these structures set lower limits on the $k_{||}$ that could be probed and any redshift $z$ above the instrument footprint.
+The majority of structure in the response at lower delays is due to the feed and its supporting structure, evidenced by those features common to all three measurements.
+At the lower delays, the structures in the delay response remain unaltered even with the variation of the feed height relative to the dish vertex.
+Essentially these structures set lower limits on the $k_{||}$ values that could be probed, and since redshift $z$ maps to frequency (and, thus, $k_{||}$), any redshift above the instrument footprint could likewise be probed.
+%Check for accuracy....
 

### 2016-04-15 DishReflectometry/GB_reflectometry_part2/Simulation/datacopy_ddboer.c
updated up to section 5. New processed data added in data folder

@@ -1,0 +1,58 @@
+#include<stdio.h>
+#include<math.h>
+#include<stdlib.h>
+#define Nsample 102
+main()
+{
+int i;
+float freq[Nsample];
+float feed_DB[Nsample],feed_P[Nsample];
+float HERA_DB[Nsample],HERA_P[Nsample];
+FILE *fp1=NULL;
+FILE *fp2=NULL; 
+FILE *fp3=NULL;
+FILE *fp4=NULL;
+FILE *fp5=NULL;
+FILE *fp6=NULL;
+
+fp1= fopen("fig7_hera_data.txt","r");
+if(fp1==NULL)
+printf("Can't open the file");
+fp2= fopen("simulation_aaron.csv","w");
+if(fp2==NULL)
+printf("Can't open the file");
+//fp3= fopen("simulation_feeds11_P.csv","w");
+//if(fp3==NULL)
+//printf("Can't open the file");
+
+
+//fp4= fopen("useHERAs11.csv","r");
+//if(fp4==NULL)
+//printf("Can't open the file");
+//fp5= fopen("simulation_HERAs11_DB.csv","w");
+//if(fp5==NULL)
+//printf("Can't open the file");
+//fp6= fopen("simulation_HERAs11_P.csv","w");
+//if(fp6==NULL)
+//printf("Can't open the file");
+
+
+
+for(i=0;i<Nsample;i++)
+{
+fscanf(fp1,"%f\t\t%f\n",&freq[i],&feed_DB[i]);
+fprintf(fp2,"%f,%f\n", freq[i],feed_DB[i]);
+//fprintf(fp3,"%f,%f\n", freq[i],feed_P[i]);
+//fprintf(fp5,"%f,%f\n", freq[i],HERA_DB[i]);
+//fprintf(fp6,"%f,%f\n", freq[i],HERA_P[i]);
+
+//printf("Its running it new\n");
+//printf("%d,%f\n", i,0.0);
+}
+fclose(fp1);
+fclose(fp2);
+//fclose(fp3);
+//fclose(fp4);
+//fclose(fp5);
+//fclose(fp6);
+}

### 2016-04-15 DishReflectometry/GB_reflectometry_part2/Simulation/plot_simulation.py

@@ -11,6 +11,35 @@ def fromcsv(filename):
     #print d[0]
     return x[:,0]/1e3, x[:,1]
 
+def fromcsv1(filename):
+    print 'Reading', filename
+    d = csv.reader(open(filename,'r'), delimiter=',')
+    x = np.array(list(d)[18:-1], dtype=np.float)
+    #print d[0]
+    return x[:,0]/1e9, x[:,1]
+    
+def lin(db,ph): # Converting the magnitude and phase of the measurements into complex returnloss in voltage ratio
+    return 10**(db/20) * np.exp(2j*np.pi*ph/360)
+
+def pwr(d): # Computing the absolute magnitude of power in db. 
+    return 10*np.log10(np.abs(d)**2)
+def pwr1(d): # Computing the absolute magnitude of power in db. 
+    return 10*np.log10(np.abs(d)**1)
+    
+def k_parallel(tau):
+    f21 = 1.42 #In GHz
+    z = (1.42/0.15 -1) 
+    Omega_M = 0.27
+    Omega_L = 0.73
+    Omega_K = 1-Omega_M-Omega_L
+    H0 = 100*1000 #m per sec h per Mpc
+    
+    E = (Omega_M*(1+z)**3+Omega_K*(1+z)**2+Omega_L)**0.5
+    
+    k_ll = 2*np.pi*tau*f21*H0*E/((3*10**8)*(1+z)**2)    
+    
+    return k_ll
+
 for filename in sys.argv[1:]:
     BASE = filename[:-len('.csv')]
     db_file = BASE + '_DB.csv'
@@ -25,53 +54,162 @@ for filename in sys.argv[1:]:
     fq_f,db_f = fromcsv('simulation_feeds11_DB.csv') # Reading the magnitude and phase of the feed only datafile to calibrate for the zero point/ 
     fq_f,ph_f = fromcsv('simulation_feeds11_P.csv')
     
-    d = 10**(db/20) * np.exp(2j*np.pi*ph/360) # 20 to put into voltage amplitude, not power
-    d_f = 10**(db_f/20) * np.exp(2j*np.pi*ph_f/360) # 20 to put into voltage amplitude, not power
     
-    valid = np.where(np.logical_and(fq < .200, fq > .090)) # restrict to PAPER band
[…]

### 2016-04-15 DishReflectometry/GB_reflectometry_part2/final_plot_reflectometry.py

@@ -1,6 +1,6 @@
 #! /usr/bin/env python
 
-import numpy as np, pylab as plt, aipy as a
+import numpy as np, pylab as plt, aipy as a, scipy as sp
 import sys, csv
 
 
@@ -31,6 +31,30 @@ def vna_short(db_open,ph_open,fq):
     meas = lin(db_open,ph_open_cable)
     gamma2 = (d_open+1)/(meas-1)
     return gamma2
+    
+def k_parallel(tau):
+    f21 = 1.42 #In GHz
+    z = (1.42/0.15 -1)
+    Omega_M = 0.27
+    Omega_L = 0.73
+    Omega_K = 1-Omega_M-Omega_L
+    H0 = 100*1000 #m per sec h per Mpc
+    E = (Omega_M*(1+z)**3+Omega_K*(1+z)**2+Omega_L)**0.5
+    k_ll = 2*np.pi*tau*H0*E/(3*10**8)*(1+z)**2    
+    return k_ll
+    
+def multiy(x,y1,y2):
+    fig, ax1 = plt.subplots()
+    ax1.plot(x,y1, color = 'k', linewidth=2.5)
+    ax1.set_xlabel('Freq (GHz)')
+    ax1.set_ylabel('Magnitude (dB)')
+    ax2 = ax1.twinx()
+    ax2.plot(x,y2,linewidth=2.5)
+    ax2.set_ylabel('Phase (Deg)')
+    ax2.set_ylabel('exp', color='b')
+    for tl in ax2.get_yticklabels():
+    	tl.set_color('b')
+    
 
 for filename in sys.argv[1:]:
     BASE = filename[:-len('.csv')]
@@ -43,20 +67,29 @@ for filename in sys.argv[1:]:
     fq_f,db_f = fromcsv('HERA_FEED_DB.csv') # Reading the magnitude and phase of the feed only datafile to calibrate for the zero point/ 
     fq_f,ph_f = fromcsv('HERA_FEED_P.csv')
     
+    
+    fq_p,db_p = fromcsv('PAPER1_DB.csv') # Reading the magnitude and phase of the feed only datafile to calibrate for the zero point/ 
+    fq_p,ph_p = fromcsv('PAPER1_P.csv')
+    
     fq_open,db_open = fromcsv('Calibration/OPENNN_DB.csv')# Reading the open file to calibrate for the multiple signal reflections in the 50 feet long cable
     fq_open,ph_open = fromcsv('Calibration/OPENNN_P.csv')
     
[…]

### 2016-04-15 DishReflectometry/GB_reflectometry_part2/plot_reflectometry_subband.py

@@ -16,21 +16,23 @@ def take_delay(db, db_f, ph, ph_f, fq, window='blackman-harris'):
        Returns windowed and non windowed delay spectra for input spectrum.'''    
     d = 10**(db/20) * np.exp(2j*np.pi*ph/360) # 20 to put into voltage amplitude, not power
     d_f = 10**(db_f/20) * np.exp(2j*np.pi*ph_f/360) # 20 to put into voltage amplitude, not power
-    d1 = d
+    d_t =1+d_f # Computing the transmission coefficient
+    d1 = ((d-d_f)*d_f/d_t ) # Reflections corrected to produce system bandpass in the receiving mode 
+    d2 = d1+d_t # Zero term added for final correction
     #d1 = (np.abs(d)-np.abs(d_f))
     #d1 = (np.abs(d)-np.abs(d_f))*np.abs(d_f)/(1-np.abs(d_f))+ (1-np.abs(d_f))
     tau = np.fft.fftfreq(fq.size, fq[1]-fq[0])
     window = a.dsp.gen_window(fq.size, window)
-    _d = np.fft.ifft(np.abs(d1)**2.0)
-    _dw = np.fft.ifft(np.abs(d1)**2.0*window) / window.mean() #compensate for window amplitude
+    _d = np.fft.ifft(np.abs(d2)**2.0)
+    _dw = np.fft.ifft(np.abs(d2)**2.0*window) / window.mean() #compensate for window amplitude
     
     if True:
     #if False:
         
-        _dw *= ( np.abs(_dw[0])/ (1- np.abs(_dw[0])))  # these should be changed to the dc bin of the windowed data.
-        _d *= ( np.abs(_d[0])/ (1- np.abs(_d[0])))  # these should be changed to the dc bin of the windowed data.
+        #_dw *= ( np.abs(_dw[0])/ (1- np.abs(_dw[0])))  # these should be changed to the dc bin of the windowed data.
+        #_d *= ( np.abs(_d[0])/ (1- np.abs(_d[0])))  # these should be changed to the dc bin of the windowed data.
 
-    return np.fft.fftshift(_dw), np.fft.fftshift(_d), np.fft.fftshift(tau)
+     return np.fft.fftshift(_dw), np.fft.fftshift(_d), np.fft.fftshift(tau)
 
[…]

### 2016-04-15 DishReflectometry/Paper1_v1.tex
Paper updated up to section 5

--- 2016-04-06 DishReflectometry/Paper1_v1.tex
@@
 
-\section{Introduction}
+\section{\textbf{Introduction}}
 
@@
 
-\section{Visibility measurements by a two element interferometer and the delay spectrum}
+\section{\textbf{Visibility measurements by a two element interferometer and the delay spectrum}}
 Consider a two element interferometer with a baseline $\vec b$.
@@
 
-\section{Effects of multiple reflections on visibility and delay spectrum}
+\section{\textbf{Effects of multiple reflections on visibility and delay spectrum}}
 The Hydrogen Epoch of Reionization Array consists of parabolic dishes which provide increased collecting area per array element compared to its predecessor experiment PAPER.
@@
 We assume two antennas with identical geometry and electrical parameters i.e, $\bmvolt_{1}(\thhat,\nu)=\bmvolt_{2}(\thhat,\nu) = \bmvolt(\thhat,\nu)$.
- \subsection{Antenna Reception With Multiple Reflections}
+ \subsection{\textbf{Antenna Reception With Multiple Reflections}}
 \label{sec:multiple}
@@
 \\
-In a related series of papers, (Thyagarajan et al 2016) has shown the detailed sensitivity calculations of HERA is using a comprehensive foreground as well as model for EoR power spectrum for various simulated antenna element response (\ref{fig:sim_limit_delay}) From this simulations, the figure \ref{fig:sim_limit_delay} (Thyagarajan et al) shows the level of attenuation required for the multiple reflected sky signal in order to reduce the foreground contaminations at the delay modes significant for power spectrum measurements.
-Ewall-Wice et al 2016 has simulated the time domain response of the HERA element considering multiple reflections between the feed and the dish.
-Figure \ref{fig:sim_limit_delay} shows the simulated cross-power response of a pair of HERA antenna as a function of time(Ewall-wice et al).
-These simulations set up the performance criterion for the HERA antenna element.
- \begin{figure*}[ht]
-\begin{minipage}[b]{0.5\linewidth}
-\centering
-\includegraphics[angle=0, width=\linewidth]{plots/sim_limit.jpg}
-\end{minipage}
-\hspace{0.1cm}
-\begin{minipage}[b]{0.5\linewidth}
-\centering
-\includegraphics[angle=0, width=\linewidth]{plots/sim_delay.jpg}
-\end{minipage}
-\caption{Left: Signal attenuation required for the reflected sky power arriving at the feed at higher delay as estimated from the simulated antenna beam and froeground models (Thyagarajan et al).
-The three different contour shows three different system performance requirements set based on the simulated response of HERA element for a measurement frequency of 150MHz corresponding to the redshift of $z=8.47$ and a 14.5m baseline.
-The instrumental requirements become extremely stringent for the detection of the smaller $k_\parallel$ values corresponding to very large spatial scales.
-Right: The simulated cross power response kernel for HERA.
-The simulation assumes and achromatic beam with the chromaticity attributed entirely by the multiple reflections between the dish and the feed.
-This shows the levels to which the multiple reflections at the higher delays is expected to be reduced following the dish and the feed design.}
-\label{fig:sim_limit_delay}       
-\end{figure*}
 
@@
 %++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{Reflectometry measurements}
+\section{\textbf{Reflectometry measurements}}
 \begin{figure*}
@@
 Section 3 laid the mathematical framework of how the delay spectrum is estimated from the return loss measurement.
+The return loss of the feed while  facing up the sky as well as while suspended on the dish and ${I_{rec}\over I_{sky}}$  is shown in figure \ref{fig:all_RL}.
 %, if the incident power from the sky signal is $I_{sky}$, the feed
@@
 Upon our assumption that two adjacent antenna elements have identical design parameters and electrical properties, this power is also a measure of the cross power or the visibility $\vis (\vec b, \nu)$ between the two antennas with a normalisation factor of $2$.
-\section{Results}
-\begin{figure*}[ht]
-\begin{minipage}[b]{0.5\linewidth}
+\section{\textbf{Results}}
+\begin{figure}[ht]
+\begin{minipage}[b]{\linewidth}
 \centering
@@
 \end{minipage}
-\hspace{0.1cm}
-\begin{minipage}[b]{0.5\linewidth}
+\vspace{0.1cm}
+\begin{minipage}[b]{\linewidth}
 \centering
@@
 Finite return loss at the antenna input deviate this quantity from its ideal value and ${I_{rec}\over I_{sky}} < 1$.
-Also, frequency dependence of the feed and the dish as well as the multiple reflections introduces the small scale fluctuations as shown in the red curve.
+Also, frequency dependence of the feed and the dish as well as the multiple reflections introduces the small scale fluctuations as seen in the red curve.
 }
@@
 }
-\label{fig:freq}       
-\end{figure*}
+\label{fig:all_RL}
+\end{figure}
+\begin{figure}       
+\centering
+\includegraphics[width=\linewidth]{plots/H_dish_feed.png}
+\caption{Delay spectrum of the HERA element (blue) the HERA feed (green) estimated by taking the Fourier transform of the measured return loss of power at the feed output.
+The feed, when suspended on the dish results in a more complex return loss and corresponding delay response is shown in the figure.
+After correcting the measurements from the transmission mode to reception mode by equation \ref{eq:power_ratio} the delay spectrum in the receiving mode is estimated (red).
+}
+\label{fig:delay_spectrum}
+\end{figure}
 
-Figure \ref{fig:freq} shows the return loss measured between $100$ to
+Figure \ref{fig:all_RL} shows the return loss measured between $100$ to
 $200MHz$ when the feed is suspended at the focal plane of the parabolic dish which is at $5m$ from the dish vertex.
@@
 
-\subsection{Feed effect:zero delay correction}
+\subsection{\textbf{Feed effect:zero delay correction}}
 %At first, the frequency domain measurement of s11 is Fourier-transformed to compute the response of the system in the delay domain.
@@
 In receiving mode, in delay domain, this appears at the zero delay bin.
-The using the return loss measurement of the feed $(\Gamma_{f})$, the return loss measurement $s_{11}$ of the dish and feed assembly is corrected via equation \ref{eq:power_ratio} for the zero delay component and the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated.
+The using the return loss measurement of the feed $(\Gamma_{f})$, the return loss measurement $s_{11}$ of the dish and feed assembly is corrected via equation \ref{eq:power_ratio} and the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated.
+Magnitude and phase of $\Gamma_{f}$ , $s_{11}$ and ${I_{rec}\over I_{sky}}$ is shown in figure \ref{fig:all_RL}.
 
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{plots/delay_spectrum_100_200_BH.png}
-\caption{Delay spectrum of the HERA element, the PAPER element and the HERA feed estimated by taking the Fourier transform of the measured return loss of power at the feed output.
-HERA feed design is driven by the PAPER element with improved response at all delays.
-The feed, when suspended on the dish results in a more complex return loss and corresponding delay response is shown in the figure.}
-\label{fig:delay_spectrum}
-\end{figure}
-
-\subsubsection{Effect of antenna beam pattern and feed return loss on delay spectrum estimation}
+\subsubsection{\textbf{Effect of antenna beam pattern and feed return loss}}
 The return loss $\Gamma_{f}$ determines the amount of power coupled to the system via the feed antenna.
@@
 The complex feed antenna impedance is shown in the figure \ref{fig:feed_impedance}.
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{plots/Feed_impedance.png}
-\caption{Complex antenna impedance of the HERA feed element.}
-\label{fig:feed_impedance}
-\end{figure} 
 While antenna beam pattern $A_{f}$ is a smooth function of frequency and should have its imprint confined to lower delays, the return loss $\Gamma_{f}$ broadens the delay spectrum.
 However, a smaller return loss will result in vertical shift of the delay spectrum at lower values and therefore can make the higher order reflections insignificant.
-Given the antenna impedance and the 50 Ohm transmission line the measurements are done using the passive balun with a 2:1 impedance ratio providing a net return loss of power between the sky, the antenna and the transmission line shown in the figure \ref{fig:freq}.
-This provides the maximum impedance matching.
-\\
-\subsubsection{Effect of frequency bandwidth on delay spectrum estimation}
-Estimation of the delay spectrum by taking the Fourier transform of the measured return loss is sensitive to the frequency bandwidth of operation.
+During observation, each HERA element is connected to an active balun similar to the ones used in the PAPER antenna (need reference) which provides greater than 10dB return loss of power at the feed output.These baluns are under further design improvements aiming at 10 to 20dB better imepedance match between the feed and the balun than the measurements presented here.
+Our measurement is done using a vector network analyser for which the active balun has been replaced by a passive balun.Given the antenna impedance and the 50 Ohm transmission line the measurements are done using the passive balun with a 2:1 impedance ratio providing a net return loss of power between the sky, the antenna and the transmission line shown in the figure \ref{fig:all_RL}.
+This measurements are conservative estimate  for both $\Gamma_{f}$ and $s_{11}$.
+
+\subsubsection{\textbf{Effect of measurement bandwidth and window function}}
+Estimation of the delay spectrum by taking the Fourier transform of the measured return loss is sensitive to the bandwidth of measurements.
 Since the measurements are done in the spectral domain, measurement between two frequencies is analogous to windowing the frequency domain data by a square window function.
@@
 \centering
-\includegraphics[width=\linewidth]{plots/window.png}
+\includegraphics[width=\linewidth]{plots/window_effect.png}
 \caption{Effect of finite bandwidth on estimation of delay spectrum: Blue line shows the delay spectrum of the HERA element computed from the measured data which is band limited between 100 to 200MHz.
@@
 \end{figure} 
-\subsubsection{Effect of dish and the feed on delay spectrum estimation}
+%\subsubsection{\textbf{Delay spectrum of subbands}} 
+%The red shifted 21cm power spectrum measurements could be divided into sub-bands around multiple frequencies corresponding to various redshifts.
+Assuming that the power spectrum evolved over the redshift range $\Delta z \>0.5$ (Zaldarriaga 2004, ) corresponding to a $5~MHz$ band width at $150~MHz$.
+
+\subsubsection{\textbf{Effect of dish reflections}}
 Measurement equations shows the effects of multiple reflections of the sky signal between the feed and the dish.
@@
 The estimated delay spectrum of the instrument is collectively contributed by all the reflections.
-We measure the return loss of the feed alone keeping it on the ground facing the sky shown in the Figure \ref{fig:freq}.
+We measure the return loss of the feed alone keeping it on the ground facing the sky shown in the Figure \ref{fig:all_RL}.
 Delay spectrum estimated from this measurement provides the lowest limit of the delay spectrum of the instrument considering there is no multiple reflections in between the feed and the dish.
@@
 Figure \ref{fig:delay_spectrum} shows the delay spectrum of the feed while it is kept upside down on the ground in green, as well as that of a HERA antenna with the feed suspended at the focal plane in blue.
-Red line shows shows the delay spectrum of the PAPER antenna in comparison with the HERA element.
+At lower delays, the reflections are dominated by the feed structure.
+Therefore, the delay spectrum in both the cases follow each other.
+Since the distance between the feed and the dish is 5 m, the roundtrip delay between the dish and the feed as about $30~ns$ around which these two delay spectrum starts to deviate.
+At delays $\> 50nS$ the dish reflections starts to dominate over the reflections from the feed structure and the two delay spectrum deviates from each other.
 %\subsubsection{Effect of feed height on delay spectrum estimation}
-\subsubsection{Comparison of performance of HERA with PAPER}
+\subsubsection{\textbf{Effect of multiple reflection between the feed and the backend.}}
+Multiple reflections of the sky signal between the feed and the dish broadens the delay response of the instrument resulting in spill over of the smooth foreground power sky at higher delays.
+Another effect that have exact similar impact on the delay spectrum is the multiple reflection of the received signal between the feed output and the input of the analog backend and correlators.
+In our measurements, the feed output is connected to the VNA via a 50 feet long LMR 400 cable.
+This length correspond to a delay of $\approx 120~nS$ for the signals travelling through the cable.
+The delay spectrum of both feed and feed-dish assembly shows an enhanced feature at this delay indicating a reflection from the VNA input.
+We measure the VNA input reflections by disconnecting the feed and connecting an open load at the feed input of the cable.
+The measured return loss is shown in the figure \ref{fig:open_RL}.
+Since the electromagnetic wave travelling through a transmission line undergoes a $100\%$ reflections from an open ended transmission line, we compute the combined effect of the VNA input return loss along with the cable resistive loss from this measurement as shown in fiigure \ref{VNA_RL}.
+This results an important system design criterion for HERA.
+The VNA input return loss is found to be at a level of $-14$ to $-30dB$ across the measurement band.
+This is consistent with the matched provided by the commercially available RF connectors that are commonly used.
+This manifests itself in a peak in the delay spectrum which is $50~dB$ above the measurement noise floor.
+The delays at which this effect becomes dominant depends on the length of the cable.
+Due to finite return loss at the input of the backends, this effect will be present in all the observations and thus would impact the instrument delay spectrum.
+However, its effect could be reduced below the level where the foreground  achieving a return loss at the backend input is greater than at least $-30~dB$.
+
+\begin{figure*}[ht]
+\begin{minipage}[b]{0.5\linewidth}
+\centering
+\includegraphics[angle=0, width=\linewidth]{plots/open_RL.png}
+\end{minipage}
+\hspace{0.1cm}
+\begin{minipage}[b]{0.5\linewidth}
+\centering
+\includegraphics[angle=0, width=\linewidth]{plots/open_delay.png}
+\end{minipage}
+\caption{Left: Magnitude and phase of the return loss measured when the open load is connected at the feed input of the cable.
+Ideally, for an open load, the electromagnetic wave travelling through the transmission cable undergoes a $100\%$ reflections and magnitude of the return loss is $0dB$.
+However, due to the resistive loss in the cable, the a small part of the signal is dissipated in the cable resulting a smaller return loss.
+Right: Delay spectrum of the open load that shows the multiple reflections at the VNA input.
+The delay spectrum of the feed and the feed-dish assembly is also plotted for comparison.}
+\label{fig:open_RL}       
+\end{figure*}
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{plots/VNA_RL.png}
+\caption{Magnitude and phase of the combined effects of the return loss at the VNA input alone with the cable resistive loss as computed from the return loss measurement of the open load at the feed input of the cable.
+This is consistent with the specifications of the RF connectors which is commonly used at low frequencies }
+\label{fig:window}
+\end{figure}
+
+\subsubsection{\textbf{Comparison with simulations}}
+\begin{itemize}
+\item 
+\textbf{Comparison with electromagnetic simulation:}\\
+%\begin{figure}
+%\centering
+%\includegraphics[width=\linewidth]{plots/Feed_impedance.png}
+%\caption{Complex antenna impedance of the HERA feed element.}
+%\label{fig:feed_impedance}
+% d\end{figure} 
+The simultated and measureded return loss of the feed as well as the HERA element is shown in figure \ref{meas_sim_RL_feed} and figure \ref{meas_sim_RL_HERA}.
+\begin{figure}[ht]
+\begin{minipage}[b]{\linewidth}
+\centering
+\includegraphics[angle=0, width=\linewidth]{plots/feed_meas_sim_mag.png}
+\end{minipage}
+\vspace{0.1cm}
+\begin{minipage}[b]{\linewidth}
+\centering
+\includegraphics[angle=0, width=\linewidth]{plots/feed_meas_sim_ph.png}
+\end{minipage}
+\caption{Magnitude and phase of the return loss of the feed as simulated and measured.
+While both the measurement and the simulation shows similar resonance around $120~MHz$, the simulation shows a better matching to a 50 Ohm transmission line compared to the measurements.
+The measurement also has some small scale fluctuation due to multiple reflection of the signal at the VNA input.
+}
+\label{meas_sim_RL_feed}
+\end{figure}
+\begin{figure}[ht]
+\begin{minipage}[b]{\linewidth}
+\centering
+\includegraphics[angle=0, width=\linewidth]{plots/HERA_meas_sim_mag.png}
+\end{minipage}
+\vspace{0.1cm}
+\begin{minipage}[b]{\linewidth}
+\centering
+\includegraphics[angle=0, width=\linewidth]{plots/HERA_meas_sim_ph.png}
+\end{minipage}
+\caption{Magnitude and phase of the return loss of the HERA element as simulated and measured.
+In this case, both measurement and simulation shows similar level of return loss across the band with marginally better return loss at the high frequency end of the band.
+}
+\label{meas_sim_RL_HERA}
+\end{figure}
+
+The delay spectrum estimated from the simulated and measured return loss is shown in the figure \ref{fig:sim_em}.
+The two delay spectrum are in good agreement with each other upto around $60~ns$ up to which the structures in the delay domain are mostly caused due to signal reflections in the feed structure.
+Since the simulated return loss shows a better match of the antenna to the 50 Ohm transmission line.
+At zero delay , in case of simulation, almost $100\%$ of the sky signal is received whereas in case of measurements, this match is found to be less than $5~dB$ resulting in partial coupling of the sky signal to the system.
+Given all the reflections unaltered, if the matching in between the feed and the transmission line is improved by about $10~dB$, which is achievable in reality, the delay spectrum would improve substantially.
+This is plotted in grey.
+The work is currently under progress to improve the feed return loss at least by  $10dB$ (Eloy et al 2016 in prep?).
+Beyond $60~nS$ other multiple reflections manifests themselves at higher delays and the delay spectrum of the measurement and simulations begin to deviate from each other.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{plots/delay_sim_meas.png}
+\caption{Comparison between delay spectrum of HERA element estimated from the electromagnetic simulation of the feed return loss (dave deBoer 2016) and measurements by a vector network analyser.}
+\label{fig:sim_em}
+\end{figure}
+
+\item
+\textbf{Comparison with time domain simulation: }\\
+In a related series of papers, (Ewall-Wice et al 2016) has shown the simulated power kernel of the HERA element which considers the electromagnetic simulations of the HERA feed and multiple reflection in between the dish and the feed vertex.
+Our measurements, in comparison to the simulations, shows a much complex structure in the delay spectrum.
+This results from various multiple reflections within and around the feed as well as in the cable connecting the feed output to the vector network analyser.
+Once again, keeping all other reflections within the system unchanged, a simple $~10dB$ improvement in the feed impedance match could match the simulations with measurements.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{plots/delay_power.png}
+\caption{Comparison between delay spectrum of HERA element estimated from the simulation of the multiple reflections between the feed and the dish and reflectometry measurements by a vector network analyser.}
+\label{fig:sim_pk}
+\end{figure}
+
+\item
+\textbf{Comparison with foreground simulation}
+In a related series of papers, (Thyagarajan et al 2016) has presented the detailed sensitivity calculations of HERA is using a comprehensive foreground as well as model for EoR power spectrum for various simulated antenna element response.
+The theoretical limits for the level of signal attenuation required in order to reduce the foreground contaminations at the delay modes significant for power spectrum measurements are shown for three different lower limits of $k_\parallel$ values.
+The requirements for the reduced instrument response at higher delays are more stringent for the detection of lower $k_\parallel$ modes.
+The response is computed for the redshift of $z=8.47$ at frequency $150~MHz$.
+The yellow and cyan curves shows the improvement on the instrument delay spectrum that could be achieved by improving the feed return loss by $20, 30db$ respectively.
+With a $30dB$ improvement in return loss, for power spectrum at $k_{\parallel}>0.15$, the foreground contaminations at higher delays could potentially be limited to only a few delay modes.
+Achieving a $30~dB$ improvement at the feed is extremely challenging.
+However, since multiple reflections results in multiplication of the feed return loss as well as the input return loss at the backend, a $20~dB$ improvement in the feed and another $~20dB$ improvement in the mismatch between the cable and the backend input could establish the same.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{plots/meas_forground.png}
+\caption{Delay spectrum of HERA element estimated from the reflectometry measurements by a vector network analyser compared to the limits of foreground simulation (Thyagarajan et al).}
+\label{fig:sim_fg}
+\end{figure}
+
+\end{itemize}
+
+\subsubsection{\textbf{Comparison of performance of HERA with PAPER}}
 While PAPER has established the till date the most stringent upper limit on the 21cm power spectrum measurement, the need to increase the measurement sensitivity called for increased collecting area per PAPER antenna.
@@
 
-\subsubsection{Comparison with simulations}
-\section{Effect of instrument delay spectrum on 21cm power spectrum measurements }
-
-The delay response of the instrument is dependent on the band chosen for the Fourier transform.
-The measurement bandwidth effects the amplitude and phase of the delay spectrum. Fourier transforms taken over wider bandwidth
-become dominated by the feed sidelobes outside the operating band, making the resultant delay profiles less relevant
-for the power spectrum performance of the HERA instrument.  Conversely, when performing Fourier transforms over much 
-narrow bands (the windowed $20MHz$ bands typical of PAPER analysis), the width of the resulting delay profile
-becomes dominated by sidelobes of low delay emission interacting with the narrow bandwidth kernel.  
-Although this may appear to be a relevant performance metric for PAPER power spectrum analysis, such an analysis typically pre-filters out low-delay emission using wide bandwidths precisely to avoid sidelobes from low-delay emission.
+%\section{\textbf{Effect of instrument delay spectrum on 21cm power spectrum measurements} }
+%The delay response of the instrument is dependent on the band chosen for the Fourier transform.
+%The measurement bandwidth effects the amplitude and phase of the delay spectrum. Fourier transforms taken over wider bandwidth
+%become dominated by the feed sidelobes outside the operating band, making the resultant delay profiles less relevant
+%for the power spectrum performance of the HERA instrument.  Conversely, when performing Fourier transforms over much 
+%narrow bands (the windowed $20MHz$ bands typical of PAPER analysis), the width of the resulting delay profile
+%becomes dominated by sidelobes of low delay emission interacting with the narrow bandwidth kernel.  
+%Although this may appear to be a relevant performance metric for PAPER power spectrum analysis, such an analysis typically pre-filters out low-delay emission using wide bandwidths precisely to avoid sidelobes from low-delay emission.
 Hence, the most relevant delay-spectrum performance profile is that taken using the $100-200MHz$ band.
@@
 
-Figure \ref{fig:elevator} is again a delay plot of the return loss at four different feed suspension heights. 
-We use the PAPER bandwidth and note
-that the measurements are near identical at low delays, implying that low delay reflections are caused primarily by reflections within the feed cage. 
-However, at higher delays we notice discrepancies between the different heights.
-In addition, Figure \ref{fig:outofthedish} presents measurements taken of the feed only.away from the dish. Echosorb is placed under the feed for some of the
-measurements, with the expectation that it will prevent any reflections off the
-ground.
- Measurements are also taken of the feed inside its metal cage in various configurations. It is shown that the feed performs best without the cage and with the absorber. 
-All these measurements are suggestive of the  fact that the feed-cage assembly itself is responsible for a significant portion of the structure up to $60ns$ and
-that the cylindrical cage may be contributing up to $20ns$ to the width of the delay profile. 
-We note that this depends stronglyon its coupling to structures around it. 
-Structure beyond $60ns$ appears to scale with the height of the feed above the dish.
+%Figure \ref{fig:elevator} is again a delay plot of the return loss at four different feed suspension heights. 
+%We use the PAPER bandwidth and note
+%that the measurements are near identical at low delays, implying that low delay reflections are caused primarily by reflections within the feed cage. 
+%However, at higher delays we notice discrepancies between the different heights.
+%In addition, Figure \ref{fig:outofthedish} presents measurements taken of the feed only.away from the dish. Echosorb is placed under the feed for some of the
+%measurements, with the expectation that it will prevent any reflections off the
+%ground.
+% Measurements are also taken of the feed inside its metal cage in various configurations. It is shown that the feed performs best without the cage and with the absorber. 
+%All these measurements are suggestive of the  fact that the feed-cage assembly itself is responsible for a significant portion of the structure up to $60ns$ and
+%that the cylindrical cage may be contributing up to $20ns$ to the width of the delay profile. 
+%We note that this depends stronglyon its coupling to structures around it. 
+%Structure beyond $60ns$ appears to scale with the height of the feed above the dish.
 
-\section{Conclusion}
+\section{\textbf{Conclusion}}
 

### 2016-04-19 DishReflectometry/Paper1_v1.tex

--- 2016-04-14 DishReflectometry/Paper1_v1.tex
@@
 
-\section{Visibility measurements by a two element interferometer and the delay spectrum}
+\section{\textbf{Visibility measurements by a two element interferometer and the delay spectrum}}
 Consider a two element interferometer with a baseline $\vec b$.
 If we denote the electric field sky signal in the direction $\thhat$ by $\volt_\sky(\vec \theta, \nu)$, then the voltage output of each antenna may be written as,
+
 \begin{equation}
@@
 
-\section{Effects of multiple reflections on visibility and delay spectrum}
-The Hydrogen Epoch of Reionization Array consists of parabolic dishes which provide increased collecting area per array element compared to its predecessor experiment, PAPER.
-Plane waves incident on a parabolic dish are focussed at the feed, which is kept at the focal plane of the dish.
+\section{\textbf{Effects of multiple reflections on visibility and delay spectrum}}
+The Hydrogen Epoch of Reionization Array consists of parabolic dishes which provide increased collecting area per array element compared to its predecessor experiment PAPER.
+Plane waves incident on a parabolic dish are focussed at the feed which is kept at the focal plane of the dish.
 The mismatch between the impedance of free space and the feed and transmission line results in a partial coupling of the sky signal into the feed while the rest is reflected off the feed. 
-The reflected signal illuminates the dish and most of it reflects back into free space.
-However, a part of it is reflected back and forth several times in between the feed and the vertex of the dish, which is shadowed by the feed.
-%No longer an included figure (dashed blue arrows in Figure \ref{fig:cartoon}).
-Such reflections generate multiple copies of the incident sky signal of reduced strength at various delays and phases and, thus, produce spurious correlations in the visibilities of interferometric data.
-Identical spurious visibilities could result from reflections internal to the system causing delay space distortion.
-Therefore, it is necessary to measure and understand the instrument delay spectrum in order to qualify the system for the measurement of the 21cm power spectrum.
-\\
-\indent In this section, we compute the visibility of a two element interferometer accounting for the additional reflections of the sky signal in between the feed and the dish vertex and the corresponding affects on the delay spectrum, using the multiple reflection formulation of Sec.
+The reflected signal illuminates the dish and most of it is reflected back into the space.
+However, a part of it reflects back and forth several times in between the feed and the vertex of the dish which is shadowed by the feed (dashed blue arrows in Figure \ref{fig:cartoon}).
+Such reflections generate multiple copies of the incident sky signal of reduced strength at various delay and phase and thus produces spurious correlations in the visibilities of interferometric data.
+Identical spurious visibilities could be resulted due to reflections internal to the system causing delay space distortion.
+Therefore, it is necessary to measure and understand the instrument delay spectrum in order to qualify the system for the measurement of 21cm power spectrum.
+In this section we compute the visibility of a two element interferometer accounting for the additional reflections of the sky signal in between the feed and the dish vertex and the corresponding effects on the delay spectrum, using the multiple reflection formulation of Sec.
 \ref{sec:multiple}.
-We also examine, in detail, the affect of reflections on the visibility data and the corresponding affect on the delay spectrum.
-We assume two antennas with identical geometry and electrical parameters, i.e, $\bmvolt_{1}(\thhat,\nu)=\bmvolt_{2}(\thhat,\nu) = \bmvolt(\thhat,\nu)$.
- \subsection{Antenna Reception With Multiple Reflections}
+In this section, the effect of reflections on the visibility data and corresponding effect on the delay spectrum is discussed in detail.
+We assume two antennas with identical geometry and electrical parameters i.e, $\bmvolt_{1}(\thhat,\nu)=\bmvolt_{2}(\thhat,\nu) = \bmvolt(\thhat,\nu)$.
+ \subsection{\textbf{Antenna Reception With Multiple Reflections}}
 \label{sec:multiple}
@@
 Note that $n=0$ is when the initial wave enters the cable at the feed (where we assume we have set our reference plane).
-We may identify $(1+\Gamma_d)(1+\Gamma_{a})$ \textbf{Shouldn't have $\mathbf{(1+\Gamma_a)}$?} as the voltage reception pattern of the antenna, denoted $\bmvolt(\thhat,\nu)$, which is a function of angle on the sky.
+We may identify $(1+\Gamma_d)$ as the voltage reception pattern of the antenna, denoted $\bmvolt(\thhat,\nu)$, which is a function of angle on the sky.
 Additionally, $(1+\Gamma_f$) is the voltage efficiency for the feed (not a function of angle).
@@
 \\
-In a related series of papers, Thyagarajan et al.
+
+%In a related series of papers, Thyagarajan et al.
 (2016) have shown the simulated sensitivity calculations of HERA for various antenna element responses (Figure \ref{fig:sim_limit_delay}) using a comprehensive foreground model as well as a model for the EoR power spectrum.
@@
 These simulations set up the performance criterion for the HERA antenna element.
- \begin{figure*}[ht]
-\begin{minipage}[b]{0.5\linewidth}
-\centering
-\includegraphics[angle=0, width=\linewidth]{plots/sim_limit.jpg}
-\end{minipage}
-\hspace{0.1cm}
-\begin{minipage}[b]{0.5\linewidth}
-\centering
-\includegraphics[angle=0, width=\linewidth]{plots/sim_delay.jpg}
-\end{minipage}
-\caption{Left: Signal attenuation required for the reflected sky power arriving at the feed at higher delays, as estimated from the simulated antenna beam and foreground models (Thyagarajan et al.).
+% \begin{figure*}[ht]
+%\begin{minipage}[b]{0.5\linewidth}
+%\centering
+%\includegraphics[angle=0, width=\linewidth]{plots/sim_limit.jpg}
+%\end{minipage}
+%\hspace{0.1cm}
+%\begin{minipage}[b]{0.5\linewidth}
+%\centering
+%\includegraphics[angle=0, width=\linewidth]{plots/sim_delay.jpg}
+%\end{minipage}
+%\caption{Left: Signal attenuation required for the reflected sky power arriving at the feed at higher delays, as estimated from the simulated antenna beam and foreground models (Thyagarajan et al.).
 The three different contours show three different system performance requirements based on the simulated response of the HERA element for a measurement frequency of 150MHz, corresponding to the redshift of $z=8.47$, and a 14.5m baseline.
@@
 This shows the level to which the multiple reflections at the higher delays is expected to be reduced following the dish and feed designs.} %Some explanation of the left hand axis of the right panel figure would be really nice in here since this is the only mention of R(tau), and it's new notation compared to the rest of the paper.
-\label{fig:sim_limit_delay}       
-\end{figure*}
+%\label{fig:sim_limit_delay}       
+%\end{figure*}
 
@@
 \end{figure*}
+
+Reflectometry measurements are carried out at the HERA element prototype in Green
+Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise the performance.  HERA element consists off a $14\,m$ diameter
+parabolic reflector and a crossed-dipole pair as a feed.
+The cross dipole antenna pair is identical to the feed of the PAPER antenna which is suspended at the focal plane of the dish with the support of three vertical poles.
+HERA elements are closely spaced with centre to centre distance between two dishes are equal to the dish diameter.
+Therefore, to reduce the coupling between the adjacent dishes, the crossed dipole feed along with the back plane is encased in a cylindrical cage.
+The feed is raised and
+lowered by a three-pulley system mounted on the three poles.
+The focal height of the dish is $5m$.
+The detail geometry and electromagnetic design of of the feed is presented in deBoer et al 2016 (in prep).
+\\
+A vector network analyser is connected via a 50feet long cable at the feed output of the HERA element and the return loss $(s_{11})$ of the HERA element is measured as a function of frequencies while the feed is suspended at the focal plane of the dish.
+This measurement is
+Section 3 laid the mathematical framework of how the delay spectrum is estimated from the return loss measurement.
+The return loss of the feed while  facing up the sky as well as while suspended on the dish and ${I_{rec}\over I_{sky}}$  is shown in figure \ref{fig:all_RL}.
+
 Reflectometry measurements were carried out on the prototype HERA element in Green
@@
 Section 3 laid the mathematical framework for how the delay spectrum is estimated from the return loss measurement.
+
 %, if the incident power from the sky signal is $I_{sky}$, the feed
@@
 %\end{eqnarray}
+
+Return loss measurements are similar to auto correlation measurement from a single HERA element.
+Upon our assumption that two adjacent antenna elements have identical design parameters and electrical properties, this power is also a measure of the cross power or the visibility $\vis (\vec b, \nu)$ between the two antennas with a normalisation factor of $2$.
+
 %
@@
 \section{Results}
-\begin{figure*}[ht]
-\begin{minipage}[b]{0.5\linewidth}
+\begin{figure}[ht]
+\begin{minipage}[b]{\linewidth}
 \centering
@@
 \end{minipage}
-\caption{Left: Magnitude of the return loss of power measured between 100 to 200 MHz using the vector network analyzer.
-Right: The corresponding phase.
-The return loss of the feed alone is shown in green while the same for the feed+dish assembly is shown in blue.
+\caption{Left: Magnitude of the return loss of power measured in between 100 to 200 MHz using vector network analyser.
+Right panel shows the corresponding phase.
+Return loss of the feed alone is shown in green while the same for the feed+dish assembly is shown in blue.
 Finally, the quantity of interest ${I_{rec}\over I_{sky}}$ is shown in red.
-Ideally, 100\% of the sky power is received, and ${I_{rec}\over I_{sky}} = 1$, or 0dB.
-A finite return loss at the antenna input causes deviations in this quantity from its ideal value, and ${I_{rec}\over I_{sky}} < 1$.
-Also, the frequency dependence of the feed and dish, as well as the multiple reflections, introduces the small scale fluctuations shown in the red curve.
+In ideal condition 100\% of the sky power is to be received and ${I_{rec}\over I_{sky}} = 1$ or 0dB.
+Finite return loss at the antenna input deviate this quantity from its ideal value and ${I_{rec}\over I_{sky}} < 1$.
+Also, frequency dependence of the feed and the dish as well as the multiple reflections introduces the small scale fluctuations as seen in the red curve.
 }
-% The HERA feed design is derived from a modified PAPER antenna, and, therefore, the return loss closely relates to the PAPER antenna response with a slight frequency shift.
-The return loss measured when the HERA feed is suspended over the dish, however, shows deviations from the feed performance.
+% HERA feed design is derived from modified PAPER antenna and therefore the return loss closely relates to the PAPER antenna response with slight frequency shift.
+The return loss measured when the HERA feed is suspended over the dish is, however, show deviation from the feed performance.
 }
-\label{fig:freq}       
-\end{figure*}
+\label{fig:all_RL}
+\end{figure}
+\begin{figure}       
+\centering
+\includegraphics[width=\linewidth]{plots/H_dish_feed.png}
+\caption{Delay spectrum of the HERA element (blue) the HERA feed (green) estimated by taking the Fourier transform of the measured return loss of power at the feed output.
+The feed, when suspended on the dish results in a more complex return loss and corresponding delay response is shown in the figure.
+After correcting the measurements from the transmission mode to reception mode by equation \ref{eq:power_ratio} the delay spectrum in the receiving mode is estimated (red).
+}
+\label{fig:delay_spectrum}
+\end{figure}
+
+Figure \ref{fig:all_RL} shows the return loss measured between $100$ to
+$200MHz$ when the feed is suspended at the focal plane of the parabolic dish which is at $5m$ from the dish vertex.
+This measurement is Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{eq3}.
+Measurement bandwidth is kept much larger than the bandwidth of operation to achieve higher delay resolution.
+A number of systematic effects as well as mathematical artefacts that are critical to this measurements and corresponding estimation of the delay spectrum are taken in to account in determination of the delay spectrum and described below.
+
+\subsection{\textbf{Feed effect:zero delay correction}}
+%At first, the frequency domain measurement of s11 is Fourier-transformed to compute the response of the system in the delay domain.
+
+While measuring the return loss of the dish-feed assembly, the signal transmitted by the VNA is reflected first off the feed.
+This is represented by $\Gamma_{f}$ in equation \ref{eq:power_ratio}.
+This essentially represents a mismatch in between the feed and the 50 Ohm transmission line.
+In delay domain, this appears at the zero delay bin.
+The zero delay response is identical whether or not the feed is suspended on the dish and  Therefore, we measure this response by measuring the feed return loss alone while the feed is kept on the ground facing the sky.
+This results in feed return loss alone including the surrounding cage structure but excluding the dish response.
+While $\Gamma_{f}$ fraction of power is reflected off the feed, $1+\Gamma_{f}$ fraction of the power gets transmitted.
+In receiving mode, upon initial incidence, $\Gamma_{f}$ fraction of voltage is reflected back in to the space while $1+\Gamma_{f}$ voltage enters the feed.
+In receiving mode, in delay domain, this appears at the zero delay bin.
+The using the return loss measurement of the feed $(\Gamma_{f})$, the return loss measurement $s_{11}$ of the dish and feed assembly is corrected via equation \ref{eq:power_ratio} and the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated.
+Magnitude and phase of $\Gamma_{f}$ , $s_{11}$ and ${I_{rec}\over I_{sky}}$ is shown in figure \ref{fig:all_RL}.
 
@@
 %At first, the frequency domain measurement of s11 is Fourier-transformed to compute the response of the system in the delay domain.
+
+\subsubsection{\textbf{Effect of antenna beam pattern and feed return loss}}
+The return loss $\Gamma_{f}$ determines the amount of power coupled to the system via the feed antenna.
+Additionally, with each reflections, the power coupled to the system reduces by a factor of $\Gamma_{f}^{2}$.
+Since reflected signal results in system response in higher delay, multiple reflections of the signal off the feed and the dish would result in an exponential envelope in the delay spectrum.
+The return loss of power results from the antenna impedance mismatch with the free space as well as the transmission line.
+The complex feed antenna impedance is shown in the figure \ref{fig:feed_impedance}.
+While antenna beam pattern $A_{f}$ is a smooth function of frequency and should have its imprint confined to lower delays, the return loss $\Gamma_{f}$ broadens the delay spectrum.
+However, a smaller return loss will result in vertical shift of the delay spectrum at lower values and therefore can make the higher order reflections insignificant.
+During observation, each HERA element is connected to an active balun similar to the ones used in the PAPER antenna (need reference) which provides greater than 10dB return loss of power at the feed output.These baluns are under further design improvements aiming at 10 to 20dB better imepedance match between the feed and the balun than the measurements presented here.
+Our measurement is done using a vector network analyser for which the active balun has been replaced by a passive balun.Given the antenna impedance and the 50 Ohm transmission line the measurements are done using the passive balun with a 2:1 impedance ratio providing a net return loss of power between the sky, the antenna and the transmission line shown in the figure \ref{fig:all_RL}.
+This measurements are conservative estimate  for both $\Gamma_{f}$ and $s_{11}$.
+
+\subsubsection{\textbf{Effect of measurement bandwidth and window function}}
+Estimation of the delay spectrum by taking the Fourier transform of the measured return loss is sensitive to the bandwidth of measurements.
+Since the measurements are done in the spectral domain, measurement between two frequencies is analogous to windowing the frequency domain data by a square window function.
+In the delay domain, Fourier transform of this would result in multiple side lobes at higher delays.
+Therefore, appropriate windowing of the data is  necessary prior to taking the Fourier transform of the measured data.
+Figure \ref{fig:window} shows the delay spectrum estimated from the measured data using a square window as well as Blackman Harris window.
+Windowing the data prior to Fourier transform significantly reduces the system response higher delays.
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{plots/window_effect.png}
+\caption{Effect of finite bandwidth on estimation of delay spectrum: Blue line shows the delay spectrum of the HERA element computed from the measured data which is band limited between 100 to 200MHz.
+Green line shows the delay spectrum estimated from the same data set after multiplying the data by a Blackman Harris window.
+The delay spectrum of the windowed data set shows significant reduction in the instrument response at higher delays.}
+\label{fig:window}
+\end{figure} 
+%\subsubsection{\textbf{Delay spectrum of subbands}} 
+%The red shifted 21cm power spectrum measurements could be divided into sub-bands around multiple frequencies corresponding to various redshifts.
+Assuming that the power spectrum evolved over the redshift range $\Delta z \>0.5$ (Zaldarriaga 2004, ) corresponding to a $5~MHz$ band width at $150~MHz$.
+
+\subsubsection{\textbf{Effect of dish reflections}}
+Measurement equations shows the effects of multiple reflections of the sky signal between the feed and the dish.
+Any other reflections off the feed structure and/or any other part of the dish-feed assembly would appear at arbitrary delays.
+The estimated delay spectrum of the instrument is collectively contributed by all the reflections.
+We measure the return loss of the feed alone keeping it on the ground facing the sky shown in the Figure \ref{fig:all_RL}.
+Delay spectrum estimated from this measurement provides the lowest limit of the delay spectrum of the instrument considering there is no multiple reflections in between the feed and the dish.
+ Any additional reflections also contributes to the measured return loss and thus contributed to the delay spectrum at various delays.
+Figure \ref{fig:delay_spectrum} shows the delay spectrum of the feed while it is kept upside down on the ground in green, as well as that of a HERA antenna with the feed suspended at the focal plane in blue.
+At lower delays, the reflections are dominated by the feed structure.
+Therefore, the delay spectrum in both the cases follow each other.
+Since the distance between the feed and the dish is 5 m, the roundtrip delay between the dish and the feed as about $30~ns$ around which these two delay spectrum starts to deviate.
+At delays $\> 50nS$ the dish reflections starts to dominate over the reflections from the feed structure and the two delay spectrum deviates from each other.
+%\subsubsection{Effect of feed height on delay spectrum estimation}
+\subsubsection{\textbf{Effect of multiple reflection between the feed and the backend.}}
+Multiple reflections of the sky signal between the feed and the dish broadens the delay response of the instrument resulting in spill over of the smooth foreground power sky at higher delays.
+Another effect that have exact similar impact on the delay spectrum is the multiple reflection of the received signal between the feed output and the input of the analog backend and correlators.
+In our measurements, the feed output is connected to the VNA via a 50 feet long LMR 400 cable.
+This length correspond to a delay of $\approx 120~nS$ for the signals travelling through the cable.
+The delay spectrum of both feed and feed-dish assembly shows an enhanced feature at this delay indicating a reflection from the VNA input.
+We measure the VNA input reflections by disconnecting the feed and connecting an open load at the feed input of the cable.
+The measured return loss is shown in the figure \ref{fig:open_RL}.
+Since the electromagnetic wave travelling through a transmission line undergoes a $100\%$ reflections from an open ended transmission line, we compute the combined effect of the VNA input return loss along with the cable resistive loss from this measurement as shown in fiigure \ref{VNA_RL}.
+This results an important system design criterion for HERA.
+The VNA input return loss is found to be at a level of $-14$ to $-30dB$ across the measurement band.
+This is consistent with the matched provided by the commercially available RF connectors that are commonly used.
+This manifests itself in a peak in the delay spectrum which is $50~dB$ above the measurement noise floor.
+The delays at which this effect becomes dominant depends on the length of the cable.
+Due to finite return loss at the input of the backends, this effect will be present in all the observations and thus would impact the instrument delay spectrum.
+However, its effect could be reduced below the level where the foreground  achieving a return loss at the backend input is greater than at least $-30~dB$.
+
+\begin{figure*}[ht]
+\begin{minipage}[b]{0.5\linewidth}
+\centering
+\includegraphics[angle=0, width=\linewidth]{plots/open_RL.png}
+\end{minipage}
+\hspace{0.1cm}
+\begin{minipage}[b]{0.5\linewidth}
+\centering
+\includegraphics[angle=0, width=\linewidth]{plots/open_delay.png}
+\end{minipage}
+\caption{Left: Magnitude and phase of the return loss measured when the open load is connected at the feed input of the cable.
+Ideally, for an open load, the electromagnetic wave travelling through the transmission cable undergoes a $100\%$ reflections and magnitude of the return loss is $0dB$.
+However, due to the resistive loss in the cable, the a small part of the signal is dissipated in the cable resulting a smaller return loss.
+Right: Delay spectrum of the open load that shows the multiple reflections at the VNA input.
+The delay spectrum of the feed and the feed-dish assembly is also plotted for comparison.}
+\label{fig:open_RL}       
+\end{figure*}
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{plots/VNA_RL.png}
+\caption{Magnitude and phase of the combined effects of the return loss at the VNA input alone with the cable resistive loss as computed from the return loss measurement of the open load at the feed input of the cable.
+This is consistent with the specifications of the RF connectors which is commonly used at low frequencies }
+\label{fig:window}
+\end{figure}
 
@@
 
-\subsubsection{Comparison with simulations}
-\section{Effect of instrument delay spectrum on 21cm power spectrum measurements }
+\subsubsection{\textbf{Comparison with simulations}}
+\begin{itemize}
+\item 
+\textbf{Comparison with electromagnetic simulation:}\\
+%\begin{figure}
+%\centering
+%\includegraphics[width=\linewidth]{plots/Feed_impedance.png}
+%\caption{Complex antenna impedance of the HERA feed element.}
+%\label{fig:feed_impedance}
+% d\end{figure} 
+The simultated and measureded return loss of the feed as well as the HERA element is shown in figure \ref{meas_sim_RL_feed} and figure \ref{meas_sim_RL_HERA}.
+\begin{figure}[ht]
+\begin{minipage}[b]{\linewidth}
+\centering
+\includegraphics[angle=0, width=\linewidth]{plots/feed_meas_sim_mag.png}
+\end{minipage}
+\vspace{0.1cm}
+\begin{minipage}[b]{\linewidth}
+\centering
+\includegraphics[angle=0, width=\linewidth]{plots/feed_meas_sim_ph.png}
+\end{minipage}
+\caption{Magnitude and phase of the return loss of the feed as simulated and measured.
+While both the measurement and the simulation shows similar resonance around $120~MHz$, the simulation shows a better matching to a 50 Ohm transmission line compared to the measurements.
+The measurement also has some small scale fluctuation due to multiple reflection of the signal at the VNA input.
+}
+\label{meas_sim_RL_feed}
+\end{figure}
 
-The delay response of the instrument is dependent on the band chosen for the Fourier transform.
-The measurement bandwidth effects the amplitude and phase of the delay spectrum. Fourier transforms taken over wider bandwidth
-become dominated by the feed sidelobes outside the operating band, making the resultant delay profiles less relevant
-for the power spectrum performance of the HERA instrument.  Conversely, when performing Fourier transforms over much 
-narrow bands (the windowed $20MHz$ bands typical of PAPER analysis), the width of the resulting delay profile
-becomes dominated by sidelobes of low delay emission interacting with the narrow bandwidth kernel.  
-Although this may appear to be a relevant performance metric for PAPER power spectrum analysis, such an analysis typically pre-filters out low-delay emission using wide bandwidths precisely to avoid sidelobes from low-delay emission.
+\begin{figure}[ht]
+\begin{minipage}[b]{\linewidth}
+\centering
+\includegraphics[angle=0, width=\linewidth]{plots/HERA_meas_sim_mag.png}
+\end{minipage}
+\vspace{0.1cm}
+\begin{minipage}[b]{\linewidth}
+\centering
+\includegraphics[angle=0, width=\linewidth]{plots/HERA_meas_sim_ph.png}
+\end{minipage}
+\caption{Magnitude and phase of the return loss of the HERA element as simulated and measured.
+In this case, both measurement and simulation shows similar level of return loss across the band with marginally better return loss at the high frequency end of the band.
+}
+\label{meas_sim_RL_HERA}
+\end{figure}
+
+The delay spectrum estimated from the simulated and measured return loss is shown in the figure \ref{fig:sim_em}.
+The two delay spectrum are in good agreement with each other upto around $60~ns$ up to which the structures in the delay domain are mostly caused due to signal reflections in the feed structure.
+Since the simulated return loss shows a better match of the antenna to the 50 Ohm transmission line.
+At zero delay , in case of simulation, almost $100\%$ of the sky signal is received whereas in case of measurements, this match is found to be less than $5~dB$ resulting in partial coupling of the sky signal to the system.
+Given all the reflections unaltered, if the matching in between the feed and the transmission line is improved by about $10~dB$, which is achievable in reality, the delay spectrum would improve substantially.
+This is plotted in grey.
+The work is currently under progress to improve the feed return loss at least by  $10dB$ (Eloy et al 2016 in prep?).
+Beyond $60~nS$ other multiple reflections manifests themselves at higher delays and the delay spectrum of the measurement and simulations begin to deviate from each other.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{plots/delay_sim_meas.png}
+\caption{Comparison between delay spectrum of HERA element estimated from the electromagnetic simulation of the feed return loss (dave deBoer 2016) and measurements by a vector network analyser.}
+\label{fig:sim_em}
+\end{figure}
+
+\item
+\textbf{Comparison with time domain simulation: }\\
+In a related series of papers, (Ewall-Wice et al 2016) has shown the simulated power kernel of the HERA element which considers the electromagnetic simulations of the HERA feed and multiple reflection in between the dish and the feed vertex.
+Our measurements, in comparison to the simulations, shows a much complex structure in the delay spectrum.
+This results from various multiple reflections within and around the feed as well as in the cable connecting the feed output to the vector network analyser.
+Once again, keeping all other reflections within the system unchanged, a simple $~10dB$ improvement in the feed impedance match could match the simulations with measurements.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{plots/delay_power.png}
+\caption{Comparison between delay spectrum of HERA element estimated from the simulation of the multiple reflections between the feed and the dish and reflectometry measurements by a vector network analyser.}
+\label{fig:sim_pk}
+\end{figure}
+
+\item
+\textbf{Comparison with foreground simulation}
+In a related series of papers, (Thyagarajan et al 2016) has presented the detailed sensitivity calculations of HERA is using a comprehensive foreground as well as model for EoR power spectrum for various simulated antenna element response.
+The theoretical limits for the level of signal attenuation required in order to reduce the foreground contaminations at the delay modes significant for power spectrum measurements are shown for three different lower limits of $k_\parallel$ values.
+The requirements for the reduced instrument response at higher delays are more stringent for the detection of lower $k_\parallel$ modes.
+The response is computed for the redshift of $z=8.47$ at frequency $150~MHz$.
+The yellow and cyan curves shows the improvement on the instrument delay spectrum that could be achieved by improving the feed return loss by $20, 30db$ respectively.
+With a $30dB$ improvement in return loss, for power spectrum at $k_{\parallel}>0.15$, the foreground contaminations at higher delays could potentially be limited to only a few delay modes.
+Achieving a $30~dB$ improvement at the feed is extremely challenging.
+However, since multiple reflections results in multiplication of the feed return loss as well as the input return loss at the backend, a $20~dB$ improvement in the feed and another $~20dB$ improvement in the mismatch between the cable and the backend input could establish the same.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{plots/meas_forground.png}
+\caption{Delay spectrum of HERA element estimated from the reflectometry measurements by a vector network analyser compared to the limits of foreground simulation (Thyagarajan et al).}
+\label{fig:sim_fg}
+\end{figure}
+
+\end{itemize}
+
+\subsubsection{\textbf{Comparison of performance of HERA with PAPER}}
+While PAPER has established the till date the most stringent upper limit on the 21cm power spectrum measurement, the need to increase the measurement sensitivity called for increased collecting area per PAPER antenna.
+This has driven to the parabolic reflector antenna based design of the PAPER successor HERA where essentially the PAPER antenna with minor modification of the ground plane-side plane assembly works as the feed and thus having larger collecting area per element.
+Figure \ref{fig:freq} shows the return loss measurement of power of the PAPER antenna and figure \ref{fig:delay_spectrum} shows (red line) the corresponding delay spectrum.
+The feed element shows improved delay response compared to the PAPER element across all delays $>50~ns$ with marginal improvement at delays $<50~ns$.
+The delay response of the HERA element degrades marginally as the feed is suspended over the dish due to multiple reflections between the feed and the dish.
+It is evident that majority of the response at lower delays are contributed due to the feed and its supporting structure at lower delays which is somewhat common to all three measurements.
+At the lower delays, the structures in the delay response remains unaltered even with the variation of the feed height relative to the dish vertex.
+It is essentially these structures set lower limits on the $k_{||}$ that could be probed and any redshift $z$ above the instrument footprint.
+
+%\section{\textbf{Effect of instrument delay spectrum on 21cm power spectrum measurements} }
+%The delay response of the instrument is dependent on the band chosen for the Fourier transform.
+%The measurement bandwidth effects the amplitude and phase of the delay spectrum. Fourier transforms taken over wider bandwidth
+%become dominated by the feed sidelobes outside the operating band, making the resultant delay profiles less relevant
+%for the power spectrum performance of the HERA instrument.  Conversely, when performing Fourier transforms over much 
+%narrow bands (the windowed $20MHz$ bands typical of PAPER analysis), the width of the resulting delay profile
+%becomes dominated by sidelobes of low delay emission interacting with the narrow bandwidth kernel.  
+%Although this may appear to be a relevant performance metric for PAPER power spectrum analysis, such an analysis typically pre-filters out low-delay emission using wide bandwidths precisely to avoid sidelobes from low-delay emission.
 Hence, the most relevant delay-spectrum performance profile is that taken using the $100-200MHz$ band.

### 2016-04-19 DishReflectometry/plots/plot_foreground_meas.py
Adding script to produce plot 16

@@ -1,0 +1,211 @@
+#! /usr/bin/env python
+
+import numpy as np, pylab as plt, aipy as a
+import sys, csv
+
+
+#def fromcsv(filename):
+ #   print 'Reading', filename
+  #  d = csv.reader(open(filename,'r'), delimiter=',')
+   # x = np.array(list(d)[18:-1], dtype=np.float)
+    #print d[0]
+    #return x[:,0]/1e3, x[:,1]
+
+def fromcsv1(filename):
+    print 'Reading', filename
+    d = csv.reader(open(filename,'r'), delimiter=',')
+    x = np.array(list(d)[18:-1], dtype=np.float)
+    #print d[0]
+    return x[:,0]/1e9, x[:,1]
+    
+def lin(db,ph): # Converting the magnitude and phase of the measurements into complex returnloss in voltage ratio
+    return 10**(db/20) * np.exp(2j*np.pi*ph/360)
+
+def pwr(d): # Computing the absolute magnitude of power in db. 
+    return 10*np.log10(np.abs(d)**2)
+def pwr1(d): # Computing the absolute magnitude of power in db. 
+    return 10*np.log10(np.abs(d)**1)
+    
+def k_parallel(tau):
+    f21 = 1.42 #In GHz
+    z = (1.42/0.15 -1) 
+    Omega_M = 0.27
+    Omega_L = 0.73
+    Omega_K = 1-Omega_M-Omega_L
+    H0 = 100*1000 #m per sec h per Mpc
+    
+    E = (Omega_M*(1+z)**3+Omega_K*(1+z)**2+Omega_L)**0.5
+    
+    k_ll = 2*np.pi*tau*f21*H0*E/((3*10**8)*(1+z)**2)    
+    
+    return k_ll
+if True:
+#for filename in sys.argv[1:]:
+ #   BASE = filename[:-len('.csv')]
+  #  db_file = BASE + '_DB.csv'
+   # ph_file = BASE + '_P.csv'
+
+    WINDOW = 'blackman-harris'
+    #WINDOW = 'hamming'
+    
+    #fq,db = fromcsv(db_file) # Reading the magnitude and the phase of the datafile to be processed
+    #fq,ph = fromcsv(ph_file) 
+    
+    
[…]

### 2016-04-19 DishReflectometry/plots/plot_s11sim_meas.py
Adding script for fig 15

@@ -1,0 +1,137 @@
+#! /usr/bin/env python
+
+import numpy as np, pylab as plt, aipy as a
+import sys, csv
+
+
+def fromcsv(filename):
+    print 'Reading', filename
+    d = csv.reader(open(filename,'r'), delimiter=',')
+    x = np.array(list(d)[18:-1], dtype=np.float)
+    #print d[0]
+    return x[:,0]/1e3, x[:,1]
+
+def fromcsv1(filename):
+    print 'Reading', filename
+    d = csv.reader(open(filename,'r'), delimiter=',')
+    x = np.array(list(d)[18:-1], dtype=np.float)
+    #print d[0]
+    return x[:,0]/1e9, x[:,1]
+    
+def lin(db,ph): # Converting the magnitude and phase of the measurements into complex returnloss in voltage ratio
+    return 10**(db/20) * np.exp(2j*np.pi*ph/360)
+
+def pwr(d): # Computing the absolute magnitude of power in db. 
+    return 10*np.log10(np.abs(d)**2)
+def pwr1(d): # Computing the absolute magnitude of power in db. 
+    return 10*np.log10(np.abs(d)**1)
+    
+def k_parallel(tau):
+    f21 = 1.42 #In GHz
+    z = (1.42/0.15 -1) 
+    Omega_M = 0.27
+    Omega_L = 0.73
+    Omega_K = 1-Omega_M-Omega_L
+    H0 = 100*1000 #m per sec h per Mpc
+    
+    E = (Omega_M*(1+z)**3+Omega_K*(1+z)**2+Omega_L)**0.5
+    
+    k_ll = 2*np.pi*tau*f21*H0*E/((3*10**8)*(1+z)**2)    
+    
+    return k_ll
+
+if True:
+
+    WINDOW = 'blackman-harris'
+    #WINDOW = 'hamming'
+     
+    fq,db = fromcsv('/Users/Punthipatra/WORKAREA1/DATA_Area/Project_HERA/DishPapers/DishReflectometry/GB_reflectometry_part2/Simulation/simulation_HERAs11_DB.csv') # Reading the magnitude and phase of the feed only datafile to calibrate for the zero point/ 
+    fq,ph = fromcsv('/Users/Punthipatra/WORKAREA1/DATA_Area/Project_HERA/DishPapers/DishReflectometry/GB_reflectometry_part2/Simulation/simulation_HERAs11_P.csv')
+    
[…]

### 2016-05-04 ForegroundSimulations/reply_to_referee_report.txt
Make most of the changes suggested by referee
From 9e3f5a4 (master):
=====================

In ms.tex,

(*) Make most of the changes suggested by referee

In eor.bib,

(*) Add citation to HERA memo

Referee Report

Reviewer's Comments:

While 21cm cosmology promises a tremendous amount of new information in both astrophysics and cosmology, the weakness of the signal combined with the dominance of foregrounds poses daunting requirements on instrument characterization. The work presented in this manuscript directly addresses some of the most urgent yet poorly understood aspects of 21 cm instruments, so it is highly valuable to the field and timely for the deployment and future expansion of the HERA project. Therefore, I recommend this work for publication, with minor modifications to address my comments below:

Major comments:

1) It is not clear if the design of HERA dish is good enough or not. In sections 2 and 6, the authors convey the message that HERA dish design is good enough (even "optimal"), whereas in section 5 it is clear that more dish measurements and possible design tweaks are needed. It is important to present a more coherent picture on this front.

Response: The intention of this paper and companion papers is to illustrate that HERA is basing its design after comprehensive analysis of its effects on detectability of the EoR signal. Though many parameters of the HERA design are close to being final, efforts are ongoing to fine-tune the instrument based on measurements. I have rephrased statements to emphasize this picture.

2) Section 4.1 needs to be more explicit regarding the assumptions and limitations in the HFSS simulation, especially those related to effects investigated in this work. For example, does the HFSS consider multiple reflections between the feed and the dish? How about between dishes?

Response: Added a sentence at the end of first paragraph under section 4.1 that the models include mutiple reflections between the dish and the feed but not those between dishes.

3) The choice of arbitrary pointing in section 5.1 undermines the credibility of this work. I understand that the choice of pointing may not be very important here, but an arbitrary choice with no further explanation is not acceptable. Fig. 6 seems to suggest certain sky directions (around RA hour 17) can have very different impacts on the results.

Response: I have now noted in section 5.1 that choice of pointing is immaterial for HERA as long as pointings that have the Galactic plane overhead (in RA range 16-19 hours) are avoided. In fact, no one specific pointing was chosen only to demonstrate that HERA is robust to all pointings except for a narrow range in RA.

4) For figures 2 and 5, it seems that presenting curves for all 8 baseline lengths conveys little more information than presenting just the shortest and longest baselines. Maybe less can be more in this case?

Response: I have noted in section 5.1 that foreground contamination depends on baseline length, orientation, pointing direction and spatial structure of emitting source. Hence, I chose a range of baseline lengths and orientations. I used all unique baseline lengths to demonstrate that all baselines individually will be sensitive to the EoR signal.

Minor comments:

Abstract:
1) "with high significance": this sounds vague. Is there a sigma value or a signal-to-noise ratio (SNR) to quote?

Response: Unless thermal noise is included it is difficult to quote a SNR. Here I have assumed data is not thermal noise limited but only limited by foregrounds and systematics studied in this paper. In such a scenario the significance of detection again varies anywhere from 10 to more than 1000.

2) "All baselines...are capable": does this mean each baseline individually can make the detection, or all of them combined? Since this work focuses on beam chromaticity and just assumes sufficient SNR, it is not clear if such statement regarding detection is truly justifiable in the scope of this work.

Response: It is meant to imply all baselines individually can make the detection as long as they are not thermal-noise limited but only limited by foreground and instrumental systematics studied here. Hence the sentence is now prefixed with "Under these conditions" which refers to data that is limited by foregrounds and such systematics discussed in this paper.

Section 1:
1) "there are inherent differences in spatial isotropy and spectral smoothness between the EoR signal and the foregrounds": explicitly describe the difference in one sentence?

Response: Added a sentence as suggested.

2) "whereas the EoR signal has spherical symmetry due to its isotropy": two issues here. First, the 'whereas' is a strange transition. The wedge bounded by horizon limits versus the isotropy of EoR signal do not prove any point as far as I can tell. The wedge is there even if the foreground were also isotropic, and EoR signal is subject to the horizon limits just like the foreground. Second, EoR signal is statistically isotropic, so saying the signal is spherically symmetric might be misleading for readers not familiar with the subject.

Response: Reworded to indicate foregrounds are inside the wedge due to the horizon limits and smooth spectrum while the EoR power spectrum is spherically symmetric due to statistical isotropy and fluctuating in its spectrum.

Section 2:

1) "currently under construction on the South African SKA site": nit-picking here (everywhere?), but it might sound confusing why HERA is built on the SKA site. Maybe just omit the SKA site information since it is not relevant?

Response: Replaced SKA site with "South African Karoo Radio Astronomy Reserve".

2) "strike an optimal balance between sensitivity and systematics": this is directly related to my major comments #1. First of all, even if that were the case, it is not quite appropriate to state it as a matter of fact in the introduction, since it is what this work is setting out to prove. Secondly, it seems clear in this work that the dish design has not truly achieved the optimum. Sections 5.2.1 and 5.2.2 explicitly state that 'measurements are under way" and "the HERA collaboration constantly pursues improvement of its dish design".

Response: Removed the word "optimal". The balance between sensitivity and systematics was initially studied in DeBoer and Parsons (2015) - a HERA memo - to which a citation has now been added. This study was specific to choice of dish size and preliminary estimates of specifications for dish based on sensitivity and systematics. Our current work along with companion papers are a much more comprehensive effort to further reinforce findings of that preliminary study. It is in this context that sentence was used. It is true that the dish design is not finalized yet and is still being fine-tuned for optimum performance. Hence, removal of the word "optimum" is consistent with other statements about measurements and fine-tuning of the dish design.

3) I think it is never explained in this section that HERA 19 is already built, and full HERA with 320 elements is being proposed?

Response: The last paragraph in section 2 does mention this.

Section 4:
1) It would be helpful to explain in half a sentence what kind of software HFSS is. Is it a commercial simulation software, or a customized HERA software?

Response: Added a brief description

2) The authors go into great detail as to what the materials are used in simulation, which leaves the reader wondering: are they the same as what are actually used in the dish? For example, "the backplane is modeled as an aluminum surface", but is it actually an aluminum surface? A nice picture of an actual HERA dish may help here.

Response: TBD

3) Can the authors briefly comment on the relative importance of point sources versus the diffuse emission in the simulation? Are the point sources relevant for the 14 m baselines? What about the 60 m ones?

Response: TBD

Section 5:
1) "The equation for delay spectrum": explicit \eqref (that is, identify the equation)

Response: Explicitly refer to equations 1 and 2 as suggested

2) "by convolving a Blackman-Harris window with itself": I might be wrong here, but Fig. 1 looks like a multiplication in frequency and convolution in delay domain? If it is squared in the delay domain, where do the ripples come from in the BH*BH curve in the delay domain since the BH curve is smooth?

Response: It is definitely a multiplication in delay domain as equation 10 indicates. This is what leads to the squaring and increase in dynamic range in delay domain. However, it is not a squaring of the same exact BH delay domain curve (gray) shown in figure 1 (bottom). This is because after convolving in frequency the resultant window must fit in a 100 MHz band end-to-end. An auto-convolution of the BH curve shown in figure 1 (which already already occupies 100 MHz end-to-end) will result in a curve that takes up 200 MHz end-to-end. Hence a new BH curve with appropriate width is chosen such that after auto-convolution, the resultant curve occupies 100 MHz. In other words, the black curve in top panel is not obtained by convolving gray curve with itself but from a slightly different BH curve of different (smaller) width with itself. This is the reason the null-like dips in delay domain are not aligned between the two. I have added a few sentences to describe this subtlety.

The ripples seen could be because of the aforementioned adjustments in frequency domain. Also being at the level of 10**-8 to 10**-5 they are insignificant compared to the overall dynamic range. In other words, even if the gray curve had ripples at this level, in a log scale plot they will not appear as ripples when superimposed on the tail which is at the level of 10 to 10**4. Thus it will not be surprising that the gray curve will still appear smooth despite these ripples.

3) If the square of the Blackman-Harris window works so much better, why not the third or fourth power?

Response: With higher order powers of the delay domain response, they start getting broader in delay and narrower in frequency. This results in loss of thermal noise senstivity due to loss of effective bandwidth. And viewing from a Fourier domain perspective, due to loss of delay resolution, sensitivity to large scale structure will reduce. In conclusion, it is possible to use higher order powers but depending on the application, this may result in loss of sensitivity especially on large scales. In this paper, we found that squaring was sufficient to achieve the dynamic range required for our purposes. I have added a small note highlighting this trade-off.

4) Fig 1: the axis labels for the top plot have non math mode fonts, which are inconsistent with all other plots.

Response: Corrected as suggested

5) Fig 1: 'as a result' is a strange transition since the previous sentence is talking about epsilon.

Response: Removed the phrase "As a result"

6) "cause further contamination": it is not clear what 'further' is being compared to. What is the original contamination?

Response: Added a sentence to indicate this contamination is in addition to that due to other spectral structures in the foregrounds and the instrument.

7) "small amplitude differences": Fig. 5 (a) seems to show as much as 2 orders of magnitude difference between the two EoR models?

Response: Qualified as relatively small differences when only the relevant modes $k_\parallel > k_p$ are considered.

Section 6:
1) The transition between sections 5 and 6 can use a few more sentences. It is not very clear how the dynamic range relates to the dish's reflectometry.

Response: Added a transition sentence at the beginning of the first paragraph in section 6.

2) Fig. 6: comment on the dark stripe around RA hour 17?

Response: The last paragraph in section 6 discusses this. I have also added a sentence describing it in the caption of figure 6.

Section 7:
1) "robustly eliminate these systematics further": robustly and further sound strange together.

Response: Changed to "effectively reduce these systematics further"

### 2016-05-04 ForegroundSimulations/ms.tex
Make most of the changes suggested by referee
From 9e3f5a4 (master):
=====================

In ms.tex,

(*) Make most of the changes suggested by referee

In eor.bib,

(*) Add citation to HERA memo

@@
 We show HERA will not be impeded by such spectral systematics and demonstrate that even in a conservative scenario that does not perform removal of foregrounds, HERA will detect EoR signal in line-of-sight $k$-modes, $k_\parallel \gtrsim 0.2\,h$~Mpc$^{-1}$, with high significance.
-All baselines in a 19-element HERA layout are capable of detecting EoR over a substantial observing window on the sky.
+{\bf Under these conditions,} all baselines in a 19-element HERA layout are capable of detecting EoR over a substantial observing window on the sky.
 
@@
 However, there are inherent differences in spatial isotropy and spectral smoothness between the EoR signal and the foregrounds \citep[see, e.g.,][]{fur04b,mor04,zal04,san05,fur06,mcq06,mor06,wan06,gle08}.
+{\bf For instance, the foregrounds have smooth spectrum and are not isotropic, whereas the EoR signal manifests with a fluctuating spectrum and statistical isotropy.}
 
-When expressed in the coordinate system of power spectrum measurements described by the three-dimensional wavenumber ($k$), the foreground emission is restricted to a wedge-shaped region commonly referred to as the {\it foreground wedge} \citep{bow09,liu09,liu14a,liu14b,dat10,liu11,gho12,mor12,par12b,tro12,ved12,dil13,pob13,thy13,dil14} bounded by the horizon limits \citep{par12b}, whereas the EoR signal has spherical symmetry due to its isotropy.
+When expressed in the coordinate system of power spectrum measurements described by the three-dimensional wavenumber ($k$), the foreground emission is restricted to a wedge-shaped region commonly referred to as the {\it foreground wedge} \citep{bow09,liu09,liu14a,liu14b,dat10,liu11,gho12,mor12,par12b,tro12,ved12,dil13,pob13,thy13,dil14} bounded by the horizon limits \citep{par12b}, {\bf owing to its smooth spectrum}.
+{\bf On the other hand, the EoR power spectrum has spherical symmetry due to statistical isotropy and non-smooth spectrum}.
 The region of $k$-space excluding the {\it foreground wedge} is commonly referred to as the {\it EoR window} since it is expected to be relatively free of foreground contamination.
@@
 In this paper, we explore the impact of chromaticity in the antenna power pattern on extending foreground power beyond the {\it wedge}.
-While highlighting the importance of such instrumental systematics on future EoR experiments, we demonstrate that the current HERA instrument design will exceed these specifications to detect the EoR signal with high significance.
+While highlighting the importance of such instrumental systematics on future EoR experiments, we demonstrate that the HERA instrument design {\bf planned} will detect the EoR signal with high significance.
 This will hold true when data is limited by foregrounds and systematics even in the most conservative scenario which involves neither foreground subtraction nor optimal analysis techniques but only relies on a simple spectral weighting scheme.
@@
 \citet{deb16} describe the HERA instrument in detail while \citet{pob14} explored the range of astrophysical parameters that HERA can probe.
-We provide a summary of the instrument currently under construction on the South African SKA site.
+We provide a summary of the instrument currently under construction {\bf in the South African Karoo Radio Astronomy Reserve}.
 
@@
 
-HERA is deploying 14~m fixed zenith-pointing parabolic dishes that strike an optimal balance between sensitivity and systematics \citep[][and this paper]{ewa16,neb16,pat16}.
-The large collecting area of a HERA element yields $\approx 5$ times the sensitivity of an MWA tile and more than 20 times that of a PAPER element.
+HERA is deploying 14~m fixed zenith-pointing parabolic dishes that {\bf aim to} strike a balance between sensitivity and systematics \citep[][and this paper]{deb15,ewa16,neb16,pat16}.
+The large collecting area of a HERA element {\bf will yield} $\approx 5$ times the sensitivity of an MWA tile and more than 20 times that of a PAPER element.
 
@@
 
-In this study, we use the HERA-19 hexagonal array layout, a small subset of the planned layout that are currently in use.
+In this study, we use the HERA-19 hexagonal array layout, a small subset of the planned layout that {\bf is} currently in use.
 Without loss of generality, the analysis and results in this paper will apply to the full proposed layout as well.
@@
 
-The High Frequency Structural Simulator (HFSS) was used to model the dish and its angular response used in this study.
+The High Frequency Structural Simulator (HFSS), {\bf a commercial finite element method solver for electromagnetic structures from Ansys,} was used to model the dish and its angular response used in this study.
 The HFSS model used prime focus optics with a 14~m faceted parabola with a spar f/D ratio of 0.32.
@@
 For the calculations, one pair of arms was excited using a modal port.
-These models cover a frequency range of 90--210~MHz in intervals of 1~MHz \citep{deb16}.
+These models cover a frequency range of 90--210~MHz in intervals of 1~MHz {\bf and include multiple reflections between the dish and the feed but not those between dishes} \citep{deb16}.
 
@@
 
-Our all-sky foreground model is the same as the one in \citet{thy15a}.
-It consists of diffuse emission \citep{deo08} and point sources.
-The latter is obtained from a combination of the NRAO VLA Sky Survey \citep[NVSS;][]{con98} at 1.4~GHz and the Sydney University Molonglo Sky Survey \citep[SUMSS;][]{boc99,mau03} at 843~MHz with a mean spectral index of -0.83.
+{\bf We use the foreground model of \citet{thy15a} wherein diffuse and point sources were shown to affect foreground contamination differently.
+The model for diffuse emission is obtained from \citet{deo08} and that for point sources} is obtained from a combination of the NRAO VLA Sky Survey \citep[NVSS;][]{con98} at 1.4~GHz and the Sydney University Molonglo Sky Survey \citep[SUMSS;][]{boc99,mau03} at 843~MHz with a mean spectral index of -0.83.
 The diffuse sky model has an angular resolution of 13\farcm 74 and a spectral index estimated for every pixel.
@@
 
-The equation for delay spectrum defines the interplay between foregrounds and antenna power pattern, and the mapping between geometric phases of baselines and delays.
+{\bf Equations~\ref{eqn:obsvis} and \ref{eqn:delay-transform} define} the interplay between foregrounds and antenna power pattern, and the mapping between geometric phases of baselines and delays.
 We discuss the spillover of foreground power beyond the horizon delay limits caused by the chromatic nature of the antenna power pattern.
@@
 Fig.~\ref{fig:window-functions} shows the {\it Blackman-Harris} window (gray) and  the window in equation~\ref{eqn:bhw2} (black) in frequency (top) and their power responses in delay (bottom).
-In its Fourier domain, this window has a response obtained by squaring the {\it Blackman-Harris} window response and thus increases the dynamic range further in the power response by another 100 -- 120~dB with $\epsilon\approx 42\%$ and $w_\textrm{ne} \approx 2.88$.
+In its Fourier domain, this window has a response obtained by squaring {\bf a} {\it Blackman-Harris} window response and thus increases the dynamic range further in the power response by another 100 -- 120~dB with $\epsilon\approx 42\%$ and $w_\textrm{ne} \approx 2.88$.
 
@@
 The overall sensitivity of the former is $\epsilon \approx 50\%$ of a rectangular window while that of the latter is $\epsilon \approx 42\%$.
-As a result, the main lobe of the convolved window function response is slightly wider than that of a {\it Blackman-Harris} window.
+The main lobe of the convolved window function response is slightly wider than that of a {\it Blackman-Harris} window.
 However, the sidelobes from the convolved window function are suppressed by more than ten orders of magnitude relative to that of a nominal {\it Blackman-Harris} window.}
@@
 
+{\bf It must be noted that in order to obtain this modified window function over a band of 100~MHz after convolution, the original {\it Blackman-Harris} window used in the convolution must occupy a band narrower than 100~MHz.
+This is why the modified window has a wider response in delay domain.
+This loss of delay-domain resolution, or equivalently, narrower effective bandwidth results in a slight reduction of sensitivity towards noise as well as small $k$-modes.
+While higher order powers could be used instead of the squared response we employ, there is a trade-off between the dynamic range and sensitivity.
+A squared response was found to be sufficient for our purposes.}
+
 In HERA-19 array layout, there are 30 unique baseline vectors and 8 unique baseline lengths.
-Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines} shows the delay power spectra of foregrounds on the 8 unique baseline lengths obtained with the aforementioned models for power pattern at arbitrary pointings on the sky.
+{\bf \citet{thy15a} showed that foreground contamination depends not only on the baseline length but also on its orientation, pointing direction on the sky, and whether the source of emission is diffuse or compact}.
+Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines} shows the delay power spectra of foregrounds on the 8 unique baseline lengths obtained with the aforementioned models for power pattern at {\bf certain chosen} pointings on the sky.
+{\bf It will be shown later in \S\ref{sec:baseline-RA} that choice of pointing is immaterial for HERA as long as pointings with the Galactic plane overhead are avoided}.
 In all these panels, the full-band foreground delay power spectra obtained with achromatic, {\it Airy} and chromatic simulated beam patterns are shown in black, red, and blue respectively.
@@
   \includegraphics[width=\linewidth]{f2.eps}
-  \caption{Foreground delay power spectra in units of K$^2 (h^{-1}$~Mpc$)^3$ on unique baseline lengths of HERA-19 at arbitrary sky pointings.
+  \caption{Foreground delay power spectra in units of K$^2 (h^{-1}$~Mpc$)^3$ on unique baseline lengths of HERA-19 at {\bf certain chosen} sky pointings.
 The baseline length and orientation (anti-clockwise from East) are annotated at the top right corner of each panel.
@@
 
-Reflections shift the measured foreground power to higher modes in $\tau$ (or in $k_\parallel$) and thus cause further contamination in these critical higher $k_\parallel$-modes.
+Reflections shift the measured foreground power to higher modes in $\tau$ (or in $k_\parallel$) and thus cause contamination in these critical $k_\parallel$-modes {\bf which is in addition to that already present due to spectral structures in the foregrounds and the instrument}.
 These delay shifts introduce ripples in the spectrum.
@@
 Both EoR models were employed in this analysis to reduce the dependence of design specifications on any single model.
-However, we found similar results except for minor differences caused by small amplitude differences between the two EoR models.
+However, we found similar results except for minor differences caused by {\bf relatively} small amplitude differences between the two EoR models {\bf for $|k_\parallel|>k_\textrm{p}$}.
 Hence, we only present results from using EoR model 1 at 150~MHz.
@@
 
-We estimate the EoR-foreground dynamic range (ratio of EoR signal and foreground powers) for both EoR models in the presence of antenna beam chromaticity, using HERA as an example.
+{\bf The HERA antenna beam model used accounts for chromaticity introduced due to reflections between the dish and the feed but not between dishes.
+Assuming the latter is insignificant,} we estimate the EoR-foreground dynamic range (ratio of EoR signal and foreground powers) {\bf achievable with HERA} for both EoR models in the presence of antenna beam chromaticity.
 In order to avoid signal evolution across the entire band, we use subbands in which EoR signal evolution is not expected to be significant.
@@
   \subfloat[][170~MHz subband ($z \approx 7.36$)]{\label{fig:asm-dps-beam-chromaticity-baselines-170-subband}\includegraphics[width=\linewidth]{f5b.eps}}
-  \caption{EoR signal and foreground delay power spectrum in units of K$^2 (h^{-1}$~Mpc$)^3$ in 150~MHz (top) and 170~MHz (bottom) subbands ($B_\textrm{eff}=10$~MHz) on eight unique baseline lengths of HERA-19 at arbitrary sky pointings.
+  \caption{EoR signal and foreground delay power spectrum in units of K$^2 (h^{-1}$~Mpc$)^3$ in 150~MHz (top) and 170~MHz (bottom) subbands ($B_\textrm{eff}=10$~MHz) on eight unique baseline lengths of HERA-19 at {\bf certain chosen} sky pointings.
 The length and orientation of the baseline vector corresponding to each panel is annotated on the top right corner.
@@
 The color scale is logarithmic.
-Even in the worst case, HERA will be able detect EoR drawn from independent models on all baselines for a large fraction of a full 24~hour sky transit cycle.
+Even in the worst case, HERA will be able detect EoR drawn from independent models on all baselines for a large fraction of a full 24~hour sky transit cycle {\bf except during the transit of the Galactic plane seen at 16--19 hours of RA}.
 $\rho(\boldsymbol{b},f_0,\alpha)$ is seen to increase with increasing baseline length.
@@
 
-However, in all four cases considered here, except when the Galactic center appears overhead in the RA range roughly in the range 16-19 hr, the worst case signal-foreground ratio lies above unity in most of this parameter space.
+However, in all four cases considered here, except when the Galactic {\bf plane} appears overhead {\bf roughly between 16 and 19 hours of RA}, the worst case signal-foreground ratio lies above unity in most of this parameter space.
 It demonstrates that HERA should detect the EoR signal with a very high signal-foreground ratio on all baselines over a majority of the pointings.
@@
 By accounting for these instrumental systematics, if data is not limited by thermal noise, we demonstrate that HERA should detect EoR in $k_\parallel\gtrsim 0.2\,h$~Mpc$^{-1}$ with high significance with a simple spectral weighting even under a conservative analysis criterion that does not involve {\it foreground removal} strategies.
-All baselines of HERA-19 will not only detect but also help in filtering highly likely EoR models.
+All baselines of HERA-19 will not only {\bf individually} detect but also help in filtering highly likely EoR models.
 
-We are also investigating advanced strategies for foreground removal that will robustly eliminate these systematics further.
+We are also investigating advanced strategies for foreground removal that will {\bf effectively reduce} these systematics further.
 Advances in calibration, foreground modeling and subtraction will improve the performance listed here.

### 2016-05-06 ForegroundSimulations/reply_to_referee_report.txt
Address relative importance of emission type
From 31e2ef7 (fgsim):
====================

In ms.tex,

(*) Change "dish design" to "element design"
(*) Add some sentences to indicate relative significance of diffuse
and point source emission

In reply_to_referee_report.txt,

(*) Address referee comment on relative significance of diffuse and
point source emission

@@
 I have rephrased statements to emphasize this picture.
+It must also be noted that the dish design is close to final while efforts are ongoing to obtain an optimal feed design.
 
@@
 In such a scenario the significance of detection again varies anywhere from 10 to more than 1000.
+The exact detection significance will depend on the analysis methods and weighting schemes used.
 
@@
 Response: It is meant to imply all baselines individually can make the detection as long as they are not thermal-noise limited but only limited by foreground and instrumental systematics studied here.
-Hence the sentence is now prefixed with "Under these conditions" which refers to data that is limited by foregrounds and such systematics discussed in this paper.
+Hence the sentence is now prefixed/qualified with "Under these conditions" which refers to data that is limited by foregrounds and such systematics discussed in this paper.
 
@@
 It is in this context that sentence was used.
-It is true that the dish design is not finalized yet and is still being fine-tuned for optimum performance.
-Hence, removal of the word "optimum" is consistent with other statements about measurements and fine-tuning of the dish design.
+Unlike the dish design, it is true that the feed design is not finalized yet and is still being fine-tuned for optimum performance.
+Hence, removal of the word "optimum" is consistent with other statements about measurements and fine-tuning of the HERA element (dish and feed together) design.
 
@@
 
-Response: The last paragraph in section 2 does mention this.
+Response: The last paragraph in section 2 mentions this.
 
@@
 
-Response: TBD
+Response: For the HERA-19 layout the diffuse emission has a dominant effect.
+This can be seen from how the foreground emission peak drops with increasing baseline length and how the dynamic range in figure 6 increases with baseline length.
+I have added a sentence in the penultimate paragraph of section 6.2 to highlight this.
 

### 2016-05-06 ForegroundSimulations/ms.tex
Address relative importance of emission type
From 31e2ef7 (fgsim):
====================

In ms.tex,

(*) Change "dish design" to "element design"
(*) Add some sentences to indicate relative significance of diffuse
and point source emission

In reply_to_referee_report.txt,

(*) Address referee comment on relative significance of diffuse and
point source emission

@@
 
-In this paper, we investigate the spectral properties of the proposed dish design from a foreground contamination standpoint and the constraints they place on attenuation required to suppress reflections in the instrument.
+In this paper, we investigate the spectral properties of the proposed HERA {\bf element (dish and feed)} design from a foreground contamination standpoint and the constraints they place on attenuation required to suppress reflections in the instrument.
 
@@
 For $k_\textrm{p}=0.15\,h$~Mpc$^{-1}$, there is a narrow range of allowed attenuation which is unconstrained for $\tau \lesssim 50$~ns.
-However, for $k_\parallel > 0.2\,h$~Mpc$^{-1}$, the foreground power spectrum using simulated chromatic dish beam will have enough room to be effective for EoR signal detection despite additional chromaticity arising from antenna-to-antenna reflections.
+However, for $k_\parallel > 0.2\,h$~Mpc$^{-1}$, the foreground power spectrum using simulated chromatic beam will have enough room to be effective for EoR signal detection despite additional chromaticity arising from antenna-to-antenna reflections.
 
-We note here that designing a dish whose antenna beam closely resembles a nominal {\it Airy} pattern will have a significantly higher tolerance for allowing antenna-to-antenna reflections and yet remain very effective for EoR signal detection.
-The HERA collaboration constantly pursues improvement of its dish design to minimize limitations from such chromatic systematics.
+We note here that designing {\bf an antenna element whose beam} closely resembles a nominal {\it Airy} pattern will have a significantly higher tolerance for allowing antenna-to-antenna reflections and yet remain very effective for EoR signal detection.
+The HERA collaboration constantly pursues improvement of its {\bf antenna element} design to minimize limitations from such chromatic systematics.
 
@@
 \end{align}
-where, the first term inside the parenthesis denotes the horizon limit, the second relates to the resolution due to subband bandwidth, $B_\textrm{eff}$, and $\zeta$ denotes a buffer to ensure the $k_\parallel^\textrm{FA}(|\boldsymbol{b}|)$ threshold ``safely'' avoids the main lobe of foreground power.
+where, the first term inside the parenthesis denotes the horizon limit, the second relates to the resolution due to subband bandwidth, $B_\textrm{eff}$, and $\zeta$ denotes a buffer to ensure the $k_\parallel^\textrm{FA}(|\boldsymbol{b}|)$ threshold ``safely'' avoids the main lobe of foreground power \citep{thy13}.
 In this study, we use $\zeta=3.5$.
@@
 For the baselines considered, $\rho(\boldsymbol{b},f_0,\alpha)$ increases with baseline length.
-We attribute this to the much steeper dependence of foreground emission (predominantly diffuse emission) on baseline length than that of EoR H{\sc i} power.
+We attribute this to the much steeper dependence of foreground emission on baseline length than that of EoR H{\sc i} power.
+{\bf This trend demonstrates that it is predominantly due to diffuse emission}.
 This is also confirmed from Fig.~\ref{fig:subbands} where the peak and sidelobe levels of foreground power obtained with the simulated chromatic antenna beam on the 14.6~m baseline, progressively drops by two orders of magnitude on the 58.4~m baseline.
 Hence, from a foreground contamination standpoint, the shortest baselines are less sensitive than longer ones in HERA-19 layout.
+% {\bf With the full proposed layout emission from point sources may become significant on longer baselines}.
 
-However, in all four cases considered here, except when the Galactic {\bf plane} appears overhead {\bf roughly between 16 and 19 hours of RA}, the worst case signal-foreground ratio lies above unity in most of this parameter space.
+In all four cases considered here, except when the Galactic {\bf plane} appears overhead {\bf roughly between 16 and 19 hours of RA}, the worst case signal-foreground ratio lies above unity in most of this parameter space.
 It demonstrates that HERA should detect the EoR signal with a very high signal-foreground ratio on all baselines over a majority of the pointings.

### 2016-05-06 ForegroundSimulations/reply_to_referee_report.txt
Address referee comment on HFSS modeling details
From 83d99a7 (fgsim):
====================

(*) Add hera19.eps and hfssHERA.eps to git repo

In ms.tex,

(*) Address referee comment on HFSS modeling details
(*) Include HERA-19 layout and HFSS schematic figures with
corresponding texts

@@
 In fact, no one specific pointing was chosen only to demonstrate that HERA is robust to all pointings except for a narrow range in RA.
+Figure 6 is now renumbered as figure 8.
 
@@
 I used all unique baseline lengths to demonstrate that all baselines individually will be sensitive to the EoR signal.
+Figures 2 and 5 are now renumbered as 4 and 7 respectively.
 
@@
 
-Response: Unless thermal noise is included it is difficult to quote a SNR.
+Response: Unless thermal noise is included it is hard to quote a SNR.
 Here I have assumed data is not thermal noise limited but only limited by foregrounds and systematics studied in this paper.
@@
 
-Response: The last paragraph in section 2 mentions this.
+Response: The last paragraph in section 2 mentions this. A figure (now numbered 1) has been introduced to show the actual HERA-19 layout built on site.
 
@@
 
-Response: TBD
+Response: A picture has been added (now figure 2).
+The dipoles are modeled using the actual materials used.
+The dish and backplane are made of meshed surfaces which are computationally hard to model with HFSS.
+Instead they have been modeled as aluminum surfaces.
+At these frequencies, the cross-welded mesh electrical properties are well modeled as a good conductor like aluminum.
+A paragraph has been added in section 4.1 that describes these details.
 
@@
 This is what leads to the squaring and increase in dynamic range in delay domain.
-However, it is not a squaring of the same exact BH delay domain curve (gray) shown in figure 1 (bottom).
+However, it is not a squaring of the same exact BH delay domain curve (gray) shown in the bottom of figure 1 (now fig.
+3).
 This is because after convolving in frequency the resultant window must fit in a 100 MHz band end-to-end.
-An auto-convolution of the BH curve shown in figure 1 (which already already occupies 100 MHz end-to-end) will result in a curve that takes up 200 MHz end-to-end.
+An auto-convolution of the BH curve shown in the figure (which already already occupies 100 MHz end-to-end) will result in a curve that takes up 200 MHz end-to-end.
 Hence a new BH curve with appropriate width is chosen such that after auto-convolution, the resultant curve occupies 100 MHz.
@@
 This results in loss of thermal noise senstivity due to loss of effective bandwidth.
-And viewing from a Fourier domain perspective, due to loss of delay resolution, sensitivity to large scale structure will reduce.
+And viewing from a Fourier domain perspective, due to loss of delay resolution, sensitivity to large scale structure will reduce slightly.
 In conclusion, it is possible to use higher order powers but depending on the application, this may result in loss of sensitivity especially on large scales.
@@
 
-Response: Corrected as suggested
+Response: Corrected as suggested. Now figure 3.
 
@@
 
-Response: Removed the phrase "As a result"
+Response: Removed the phrase "As a result" in what is now figure 3.
 
@@
 
-Response: The last paragraph in section 6 discusses this. I have also added a sentence describing it in the caption of figure 6.
+Response: The last paragraph in section 6 discusses this. I have also added a sentence describing it in the caption of figure (now #8).
 

### 2016-05-06 ForegroundSimulations/ms.tex
Address referee comment on HFSS modeling details
From 83d99a7 (fgsim):
====================

(*) Add hera19.eps and hfssHERA.eps to git repo

In ms.tex,

(*) Address referee comment on HFSS modeling details
(*) Include HERA-19 layout and HFSS schematic figures with
corresponding texts

@@
 
-In this study, we use the HERA-19 hexagonal array layout, a small subset of the planned layout that {\bf is} currently in use.
+In this study, we use the HERA-19 hexagonal array layout, a small subset of the planned layout that {\bf is} currently in use {\bf (see Figure~\ref{fig:HERA-19})}.
 Without loss of generality, the analysis and results in this paper will apply to the full proposed layout as well.
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=\linewidth]{hera19.eps}
+  \caption{{\bf 19-element HERA layout used in this study, a subset of the full proposed layout. It is located in the South African Karoo Radio Astronomy Reserve.}}
+  \label{fig:HERA-19}
+\end{figure}
 
@@
 The High Frequency Structural Simulator (HFSS), {\bf a commercial finite element method solver for electromagnetic structures from Ansys,} was used to model the dish and its angular response used in this study.
-The HFSS model used prime focus optics with a 14~m faceted parabola with a spar f/D ratio of 0.32.
-The model has a 1~m central hole in the aluminum surface which is filled with a dielectric material similar to dry soil.
-The feed used a full PAPER dipole inside of a cylindrical backplane, the backplane is modeled as an aluminum surface.
-For the metal parts of the dipole, the discs were modeled as aluminum at the actual size, and the arms and terminals were modeled as copper.
+The HFSS model used prime focus optics with a 14~m faceted parabola with a spar $f/D$ ratio of 0.32.
+The model has a 1~m central hole in the surface which is filled with a dielectric material similar to dry soil.
+The feed used a full PAPER dipole inside a cylindrical backplane.
 Dielectric stand-offs and supporting members were included.
 For the calculations, one pair of arms was excited using a modal port.
+
+{\bf The dipoles were modeled with the actual materials used -- aluminum for the discs and copper for the arms and terminals.
+The dish and the backplane are actually meshed surfaces.
+For computational feasibility, they were modeled as aluminum surfaces in HFSS.
+At these frequencies, the cross-welded mesh electrical properties are well modeled as a good conductor like aluminum.}
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=\linewidth]{hfssHERA.eps}
+  \caption{{\bf Schematic representation of the HERA dish-feed assembly used in the HFSS model.
+The dish surface is modeled as a 14~m faceted parabola.
+The feed uses a PAPER dipole surrounded by a cylindrical backplane.
+A $f/D$ ratio of 0.32 is used.
+A length scale of 200~inches ($\approx 5$~m) is shown at the bottom for reference.}}
+  \label{fig:HFSS-HERA}
+\end{figure}
+
 These models cover a frequency range of 90--210~MHz in intervals of 1~MHz {\bf and include multiple reflections between the dish and the feed but not those between dishes} \citep{deb16}.

### 2016-05-06 ForegroundSimulations/reply_to_referee_report.txt
Rename and renumber figures
From 1ab992f (fgsim):
====================

(*) Rename and renumber figures

In reply_to_referee_report.txt,

(*) Fine-tune response to referee report

In ms.tex,

(*) Minor changes throughout

@@
+We thank the reviewer for a thorough review of our paper whose comments have helped improve the quality of the manuscript tremendously.
+We are delighted to hear from the reviewer that this paper is interesting and merits timely publication.
+My response (on behalf) of the authors is provided below.
+
+Some overall changes in the manuscript not covered by the specific queries of the reviewer are:
+1) changes are highlighted in bold face
+2) two new figures have been added illustrating the HERA-19 layout and the HFSS model schematic for HERA dish-feed assembly.
+
+Please find below my responses to all the specific concerns raised by the reviewer.
+
 Referee Report
@@
 
-Response: A picture has been added (now figure 2).
+Response: A picture has been added (now figure 2) that shows a schematic view of the HFSS model.
+The newly added figure 1 shows the actual dishes and the layout.
 The dipoles are modeled using the actual materials used.
@@
 
-The ripples seen could be because of the aforementioned adjustments in frequency domain.
+The ripples seen could be due to the aforementioned adjustments in frequency domain.
 Also being at the level of 10**-8 to 10**-5 they are insignificant compared to the overall dynamic range.

### 2016-05-06 ForegroundSimulations/ms.tex
Rename and renumber figures
From 1ab992f (fgsim):
====================

(*) Rename and renumber figures

In reply_to_referee_report.txt,

(*) Fine-tune response to referee report

In ms.tex,

(*) Minor changes throughout

@@
   \centering
-  \includegraphics[width=\linewidth]{hera19.eps}
-  \caption{{\bf 19-element HERA layout used in this study, a subset of the full proposed layout. It is located in the South African Karoo Radio Astronomy Reserve.}}
+  \includegraphics[width=\linewidth]{f1.eps}
+  \caption{{\bf 19-element HERA layout used in this study, a subset of the full proposed 350-element layout. It is located in the South African Karoo Radio Astronomy Reserve.}}
   \label{fig:HERA-19}
@@
 For the calculations, one pair of arms was excited using a modal port.
+{\bf Fig.~\ref{fig:HFSS-model} shows a schematic view of the dish-feed assembly modeled using HFSS.}
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=\linewidth]{f2.eps}
+  \caption{{\bf Schematic view of the HERA dish-feed assembly used in the HFSS model.
+The dish surface is modeled as a 14~m faceted parabola.
+The feed uses a PAPER dipole surrounded by a cylindrical backplane.
+A $f/D$ ratio of 0.32 is used.
+A length scale of 200~inches ($\approx 5$~m) is shown at the bottom for reference.}}
+  \label{fig:HFSS-model}
+\end{figure}
 
@@
 
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=\linewidth]{hfssHERA.eps}
-  \caption{{\bf Schematic representation of the HERA dish-feed assembly used in the HFSS model.
-The dish surface is modeled as a 14~m faceted parabola.
-The feed uses a PAPER dipole surrounded by a cylindrical backplane.
-A $f/D$ ratio of 0.32 is used.
-A length scale of 200~inches ($\approx 5$~m) is shown at the bottom for reference.}}
-  \label{fig:HFSS-HERA}
-\end{figure}
-
-These models cover a frequency range of 90--210~MHz in intervals of 1~MHz {\bf and include multiple reflections between the dish and the feed but not those between dishes} \citep{deb16}.
+These models cover a frequency range of 90--210~MHz in intervals of 1~MHz. {\bf They include multiple reflections between the dish and the feed but not those between dishes} \citep{deb16}.
 
@@
   % \includegraphics[width=\linewidth]{window_function_modifications.eps}
-  \includegraphics[width=\linewidth]{f1.eps}
+  \includegraphics[width=\linewidth]{f3.eps}
   \caption{Choices for spectral weighting functions, $W(f)$ ({\it top}) and their delay power spectrum responses, $|\widetilde{W}(\tau)|^2$ ({\it bottom}).
@@
 This is why the modified window has a wider response in delay domain.
-This loss of delay-domain resolution, or equivalently, narrower effective bandwidth results in a slight reduction of sensitivity towards noise as well as small $k$-modes.
-While higher order powers could be used instead of the squared response we employ, there is a trade-off between the dynamic range and sensitivity.
+This loss of delay-domain resolution, or equivalently, narrower effective bandwidth results in a slight reduction of noise sensitivity and delay resolution.
+While higher order powers could be used instead of the squared response we employ, there is a trade-off between the dynamic range, delay resolution, and sensitivity.
 A squared response was found to be sufficient for our purposes.}
@@
 {\bf It will be shown later in \S\ref{sec:baseline-RA} that choice of pointing is immaterial for HERA as long as pointings with the Galactic plane overhead are avoided}.
+
 In all these panels, the full-band foreground delay power spectra obtained with achromatic, {\it Airy} and chromatic simulated beam patterns are shown in black, red, and blue respectively.
@@
   % \includegraphics[width=\linewidth]{asm_foreground_eor_beam_chromaticity_fullband_bhw2.0.eps}
-  \includegraphics[width=\linewidth]{f2.eps}
+  \includegraphics[width=\linewidth]{f4.eps}
   \caption{Foreground delay power spectra in units of K$^2 (h^{-1}$~Mpc$)^3$ on unique baseline lengths of HERA-19 at {\bf certain chosen} sky pointings.
@@
   % \includegraphics[width=\linewidth]{spec_on_achrmbeam_foreground_reflected_power_21cmfast_14.6m_150.0_MHz_subband_v2.eps}
-  \includegraphics[width=\linewidth]{f3.eps}
+  \includegraphics[width=\linewidth]{f5.eps}
   \caption{Minimum required attenuation (in dB) for internal dish-feed reflections required to keep the reflected foreground power below EoR H{\sc i} signal power for all $k_\parallel$-modes greater than $0.1\,h$~Mpc$^{-1}$ (solid), $0.15\,h$~Mpc$^{-1}$ (dashed) and $0.2\,h$~Mpc$^{-1}$ (dotted).
@@
   % \includegraphics[width=\linewidth]{spec_on_foreground_reflected_power_21cmfast_14.6m_150.0_MHz_subband_v2.eps}
-  \includegraphics[width=\linewidth]{f4.eps}
+  \includegraphics[width=\linewidth]{f6.eps}
   \caption{Minimum required attenuation (in dB) for antenna-to-antenna reflections to keep reflected foreground power below EoR H{\sc i} signal power for all $k_\parallel$-modes greater than $0.1\,h$~Mpc$^{-1}$ (left), $0.15\,h$~Mpc$^{-1}$ (middle) and $0.2\,h$~Mpc$^{-1}$ (right).
@@
 As a result, the elbow-shaped design constraints shift upward and leftward.
-For instance, in the presence of dish-feed reflections, it will still be feasible to probe only $k_\parallel > 0.15\,h$~Mpc$^{-1}$ with the 58.4~m baselines.
+For instance, in the presence of dish-feed reflections, it will be feasible to probe only $k_\parallel > 0.15\,h$~Mpc$^{-1}$ with the 58.4~m baselines.
 
@@
 {\bf The HERA antenna beam model used accounts for chromaticity introduced due to reflections between the dish and the feed but not between dishes.
-Assuming the latter is insignificant,} we estimate the EoR-foreground dynamic range (ratio of EoR signal and foreground powers) {\bf achievable with HERA} for both EoR models in the presence of antenna beam chromaticity.
+Ignoring the latter,} we estimate the EoR-foreground dynamic range (ratio of EoR signal and foreground powers) {\bf achievable with HERA} for both EoR models in the presence of antenna beam chromaticity.
 In order to avoid signal evolution across the entire band, we use subbands in which EoR signal evolution is not expected to be significant.
@@
   % \subfloat[][170~MHz subband ($z \approx 7.36$)]{\label{fig:asm-dps-beam-chromaticity-baselines-170-subband}\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_170.0_MHz_subband_win_method_bhw2.0.eps}}
-  \subfloat[][150~MHz subband ($z \approx 8.47$)]{\label{fig:asm-dps-beam-chromaticity-baselines-150-subband}\includegraphics[width=\linewidth]{f5a.eps}} \\
-  \subfloat[][170~MHz subband ($z \approx 7.36$)]{\label{fig:asm-dps-beam-chromaticity-baselines-170-subband}\includegraphics[width=\linewidth]{f5b.eps}}
+  \subfloat[][150~MHz subband ($z \approx 8.47$)]{\label{fig:asm-dps-beam-chromaticity-baselines-150-subband}\includegraphics[width=\linewidth]{f7a.eps}} \\
+  \subfloat[][170~MHz subband ($z \approx 7.36$)]{\label{fig:asm-dps-beam-chromaticity-baselines-170-subband}\includegraphics[width=\linewidth]{f7b.eps}}
   \caption{EoR signal and foreground delay power spectrum in units of K$^2 (h^{-1}$~Mpc$)^3$ in 150~MHz (top) and 170~MHz (bottom) subbands ($B_\textrm{eff}=10$~MHz) on eight unique baseline lengths of HERA-19 at {\bf certain chosen} sky pointings.
@@
   % \subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_170.0_MHz_subband.eps}}
-  \subfloat[][EoR model 1, 150~MHz subband ]{\label{fig:21cmfast-fg-ratio-150}\includegraphics[width=0.45\linewidth]{f6a.eps}}
-  \subfloat[][EoR model 2, 150~MHz subband ]{\label{fig:lidz-fg-ratio-150}\includegraphics[width=0.45\linewidth]{f6b.eps}} \\
-  \subfloat[][EoR model 1, 170~MHz subband ]{\label{fig:21cmfast-fg-ratio-170}\includegraphics[width=0.45\linewidth]{f6c.eps}}
-  \subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{f6d.eps}}
+  \subfloat[][EoR model 1, 150~MHz subband ]{\label{fig:21cmfast-fg-ratio-150}\includegraphics[width=0.45\linewidth]{f8a.eps}}
+  \subfloat[][EoR model 2, 150~MHz subband ]{\label{fig:lidz-fg-ratio-150}\includegraphics[width=0.45\linewidth]{f8b.eps}} \\
+  \subfloat[][EoR model 1, 170~MHz subband ]{\label{fig:21cmfast-fg-ratio-170}\includegraphics[width=0.45\linewidth]{f8c.eps}}
+  \subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{f8d.eps}}
   \caption{Worst case EoR-foreground dynamic range, $\rho(\boldsymbol{b},f_0,\alpha)$, in {\it foreground avoidance} modes for different HERA-19 baselines as a function of RA ($\alpha$) of pointing on the sky.

### 2016-05-09 ForegroundSimulations/ms.tex
Minor edits to ms.tex and response to referee
From d2876cc (fgsim):
====================

(*) coverletter.txt to git repo

In ms.tex,

(*) make minor corrections

In reply_to_referee_report.tex,

(*) Fine-tune response to referee report

@@
   \includegraphics[width=\linewidth]{f1.eps}
-  \caption{{\bf 19-element HERA layout used in this study, a subset of the full proposed 350-element layout. It is located in the South African Karoo Radio Astronomy Reserve.}}
+  \caption{{\bf 19-element HERA layout used in this study, a subset of the full proposed 350-element layout.
+It is located in the South African Karoo Radio Astronomy Reserve.
+Each dish is 14~m across.
+The relative physical scale is illustrated by the group of people in this picture.}}
   \label{fig:HERA-19}
@@
 
-{\bf Equations~\ref{eqn:obsvis} and \ref{eqn:delay-transform} define} the interplay between foregrounds and antenna power pattern, and the mapping between geometric phases of baselines and delays.
+{\bf Equations~\ref{eqn:obsvis} and \ref{eqn:delay-transform} define} the interplay between foregrounds, {\bf the} antenna power pattern, and the mapping between geometric phases of baselines and delays.
 We discuss the spillover of foreground power beyond the horizon delay limits caused by the chromatic nature of the antenna power pattern.
@@
 
-We estimate the worst case EoR-foreground dynamic range in the $\boldsymbol{b}$--$\alpha$ parameter space as:
+We estimate the worst-case EoR-foreground dynamic range in the $\boldsymbol{b}$--$\alpha$ parameter space as:
 \begin{align}
@@
   \subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{f8d.eps}}
-  \caption{Worst case EoR-foreground dynamic range, $\rho(\boldsymbol{b},f_0,\alpha)$, in {\it foreground avoidance} modes for different HERA-19 baselines as a function of RA ($\alpha$) of pointing on the sky.
+  \caption{Worst-case EoR-foreground dynamic range, $\rho(\boldsymbol{b},f_0,\alpha)$, in {\it foreground avoidance} modes for different HERA-19 baselines as a function of RA ($\alpha$) of pointing on the sky.
 Each panel corresponds to the EoR model and subband indicated.
@@
 
-In all four cases considered here, except when the Galactic {\bf plane} appears overhead {\bf roughly between 16 and 19 hours of RA}, the worst case signal-foreground ratio lies above unity in most of this parameter space.
+In all four cases considered here, except when the Galactic {\bf plane} appears overhead {\bf roughly between 16 and 19 hours of RA}, the worst-case signal-foreground ratio lies above unity in most of this parameter space.
 It demonstrates that HERA should detect the EoR signal with a very high signal-foreground ratio on all baselines over a majority of the pointings.

### 2016-05-17 ForegroundSimulations/ms.tex
Bold highlights to normal font, minor edits
From 314d0d4 (fgsim):
====================

In ms.tex,

(*) Revert bold font highlighting to normal font
(*) Change \tilde to \widetilde

@@
 We show HERA will not be impeded by such spectral systematics and demonstrate that even in a conservative scenario that does not perform removal of foregrounds, HERA will detect EoR signal in line-of-sight $k$-modes, $k_\parallel \gtrsim 0.2\,h$~Mpc$^{-1}$, with high significance.
-{\bf Under these conditions,} all baselines in a 19-element HERA layout are capable of detecting EoR over a substantial observing window on the sky.
+Under these conditions, all baselines in a 19-element HERA layout are capable of detecting EoR over a substantial observing window on the sky.
 
@@
 However, there are inherent differences in spatial isotropy and spectral smoothness between the EoR signal and the foregrounds \citep[see, e.g.,][]{fur04b,mor04,zal04,san05,fur06,mcq06,mor06,wan06,gle08}.
-{\bf For instance, the foregrounds have smooth spectrum and are not isotropic, whereas the EoR signal manifests with a fluctuating spectrum and statistical isotropy.}
+For instance, the foregrounds have smooth spectrum and are not isotropic, whereas the EoR signal manifests with a fluctuating spectrum and statistical isotropy.
 
-When expressed in the coordinate system of power spectrum measurements described by the three-dimensional wavenumber ($k$), the foreground emission is restricted to a wedge-shaped region commonly referred to as the {\it foreground wedge} \citep{bow09,liu09,liu14a,liu14b,dat10,liu11,gho12,mor12,par12b,tro12,ved12,dil13,pob13,thy13,dil14} bounded by the horizon limits \citep{par12b}, {\bf owing to its smooth spectrum}.
-{\bf On the other hand, the EoR power spectrum has spherical symmetry due to statistical isotropy and non-smooth spectrum}.
+When expressed in the coordinate system of power spectrum measurements described by the three-dimensional wavenumber ($k$), the foreground emission is restricted to a wedge-shaped region commonly referred to as the {\it foreground wedge} \citep{bow09,liu09,liu14a,liu14b,dat10,liu11,gho12,mor12,par12b,tro12,ved12,dil13,pob13,thy13,dil14} bounded by the horizon limits \citep{par12b}, owing to its smooth spectrum.
+On the other hand, the EoR power spectrum has spherical symmetry due to statistical isotropy and non-smooth spectrum.
 The region of $k$-space excluding the {\it foreground wedge} is commonly referred to as the {\it EoR window} since it is expected to be relatively free of foreground contamination.
@@
 In this paper, we explore the impact of chromaticity in the antenna power pattern on extending foreground power beyond the {\it wedge}.
-While highlighting the importance of such instrumental systematics on future EoR experiments, we demonstrate that the HERA instrument design {\bf planned} will detect the EoR signal with high significance.
+While highlighting the importance of such instrumental systematics on future EoR experiments, we demonstrate that the HERA instrument design planned will detect the EoR signal with high significance.
 This will hold true when data is limited by foregrounds and systematics even in the most conservative scenario which involves neither foreground subtraction nor optimal analysis techniques but only relies on a simple spectral weighting scheme.
@@
 \citet{deb16} describe the HERA instrument in detail while \citet{pob14} explored the range of astrophysical parameters that HERA can probe.
-We provide a summary of the instrument currently under construction {\bf in the South African Karoo Radio Astronomy Reserve}.
+We provide a summary of the instrument currently under construction in the South African Karoo Radio Astronomy Reserve.
 
@@
 
-HERA is deploying 14~m fixed zenith-pointing parabolic dishes that {\bf aim to} strike a balance between sensitivity and systematics \citep[][and this paper]{deb15,ewa16,neb16,pat16}.
-The large collecting area of a HERA element {\bf will yield} $\approx 5$ times the sensitivity of an MWA tile and more than 20 times that of a PAPER element.
+HERA is deploying 14~m fixed zenith-pointing parabolic dishes that aim to strike a balance between sensitivity and systematics \citep[][and this paper]{deb15,ewa16,neb16,pat16}.
+The large collecting area of a HERA element will yield $\approx 5$ times the sensitivity of an MWA tile and more than 20 times that of a PAPER element.
 
@@
 
-In this study, we use the HERA-19 hexagonal array layout, a small subset of the planned layout that {\bf is} currently in use {\bf (see Figure~\ref{fig:HERA-19})}.
+In this study, we use the HERA-19 hexagonal array layout, a small subset of the planned layout that is currently in use (see Figure~\ref{fig:HERA-19}).
 Without loss of generality, the analysis and results in this paper will apply to the full proposed layout as well.
@@
   \includegraphics[width=\linewidth]{f1.eps}
-  \caption{{\bf 19-element HERA layout used in this study, a subset of the full proposed 350-element layout.
+  \caption{19-element HERA layout used in this study, a subset of the full proposed 350-element layout.
 It is located in the South African Karoo Radio Astronomy Reserve.
 Each dish is 14~m across.
-The relative physical scale is illustrated by the group of people in this picture.}}
+The relative physical scale is illustrated by the group of people in this picture.}
   \label{fig:HERA-19}
@@
 where, $\boldsymbol{b}$ is the vector joining antenna pairs (commonly referred to as the baseline vector), $\hat{\boldsymbol{s}}$ is the unit vector denoting direction on the sky, $f$ denotes frequency, $c$ is the speed of light, $\dif\Omega$ is the solid angle element to which $\hat{\boldsymbol{s}}$ is the unit normal vector, $I(\hat{\boldsymbol{s}},f)$ and $A(\hat{\boldsymbol{s}},f)$ are the sky brightness and antenna's directional power pattern, respectively, as a function of $\hat{\boldsymbol{s}}$ and $f$.
-The {\it delay spectrum}, $\tilde{V}_b(\tau)$, is defined as the inverse Fourier transform of $V_b(f)$ along the frequency coordinate:
+The {\it delay spectrum}, $\widetilde{V}_b(\tau)$, is defined as the inverse Fourier transform of $V_b(f)$ along the frequency coordinate:
 \begin{align}\label{eqn:delay-transform}
-  \tilde{V}_b(\tau) &\equiv \int V_b(f)\,W(f)\,e^{i2\pi f\tau}\,\dif f,
+  \widetilde{V}_b(\tau) &\equiv \int V_b(f)\,W(f)\,e^{i2\pi f\tau}\,\dif f,
 \end{align}
@@
 \begin{align}\label{eqn:delay-power-spectrum}
-  P(\boldsymbol{b},k_\parallel) &\equiv |\tilde{V}_b(\tau)|^2\left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2,
+  P(\boldsymbol{b},k_\parallel) &\equiv |\widetilde{V}_b(\tau)|^2\left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2,
 \end{align}
@@
 
-In this paper, we investigate the spectral properties of the proposed HERA {\bf element (dish and feed)} design from a foreground contamination standpoint and the constraints they place on attenuation required to suppress reflections in the instrument.
+In this paper, we investigate the spectral properties of the proposed HERA element (dish and feed) design from a foreground contamination standpoint and the constraints they place on attenuation required to suppress reflections in the instrument.
 
@@
 
-The High Frequency Structural Simulator (HFSS), {\bf a commercial finite element method solver for electromagnetic structures from Ansys,} was used to model the dish and its angular response used in this study.
+The High Frequency Structural Simulator (HFSS), a commercial finite element method solver for electromagnetic structures from Ansys, was used to model the dish and its angular response used in this study.
 The HFSS model used prime focus optics with a 14~m faceted parabola with a spar $f/D$ ratio of 0.32.
@@
 For the calculations, one pair of arms was excited using a modal port.
-{\bf Fig.~\ref{fig:HFSS-model} shows a schematic view of the dish-feed assembly modeled using HFSS.}
+Fig.~\ref{fig:HFSS-model} shows a schematic view of the dish-feed assembly modeled using HFSS.
 
@@
   \includegraphics[width=\linewidth]{f2.eps}
-  \caption{{\bf Schematic view of the HERA dish-feed assembly used in the HFSS model.
+  \caption{Schematic view of the HERA dish-feed assembly used in the HFSS model.
 The dish surface is modeled as a 14~m faceted parabola.
@@
 A $f/D$ ratio of 0.32 is used.
-A length scale of 200~inches ($\approx 5$~m) is shown at the bottom for reference.}}
+A length scale of 200~inches ($\approx 5$~m) is shown at the bottom for reference.}
   \label{fig:HFSS-model}
@@
 
-{\bf The dipoles were modeled with the actual materials used -- aluminum for the discs and copper for the arms and terminals.
+The dipoles were modeled with the actual materials used -- aluminum for the discs and copper for the arms and terminals.
 The dish and the backplane are actually meshed surfaces.
 For computational feasibility, they were modeled as aluminum surfaces in HFSS.
-At these frequencies, the cross-welded mesh electrical properties are well modeled as a good conductor like aluminum.}
+At these frequencies, the cross-welded mesh electrical properties are well modeled as a good conductor like aluminum.
 
-These models cover a frequency range of 90--210~MHz in intervals of 1~MHz. {\bf They include multiple reflections between the dish and the feed but not those between dishes} \citep{deb16}.
+These models cover a frequency range of 90--210~MHz in intervals of 1~MHz. They include multiple reflections between the dish and the feed but not those between dishes \citep{deb16}.
 
@@
 
-{\bf We use the foreground model of \citet{thy15a} wherein diffuse and point sources were shown to affect foreground contamination differently.
-The model for diffuse emission is obtained from \citet{deo08} and that for point sources} is obtained from a combination of the NRAO VLA Sky Survey \citep[NVSS;][]{con98} at 1.4~GHz and the Sydney University Molonglo Sky Survey \citep[SUMSS;][]{boc99,mau03} at 843~MHz with a mean spectral index of -0.83.
+We use the foreground model of \citet{thy15a} wherein diffuse and point sources were shown to affect foreground contamination differently.
+The model for diffuse emission is obtained from \citet{deo08} and that for point sources is obtained from a combination of the NRAO VLA Sky Survey \citep[NVSS;][]{con98} at 1.4~GHz and the Sydney University Molonglo Sky Survey \citep[SUMSS;][]{boc99,mau03} at 843~MHz with a mean spectral index of -0.83.
 The diffuse sky model has an angular resolution of 13\farcm 74 and a spectral index estimated for every pixel.
@@
 The second EoR model is from the simulations described in detail in \citet{lid08}.
-Hereafter, we refer to these two as EoR models 1 and 2 respectively.
+Hereafter, we refer to these two as EoR models~1 and 2 respectively.
 
@@
 
-{\bf Equations~\ref{eqn:obsvis} and \ref{eqn:delay-transform} define} the interplay between foregrounds, {\bf the} antenna power pattern, and the mapping between geometric phases of baselines and delays.
+Equations~\ref{eqn:obsvis} and \ref{eqn:delay-transform} define the interplay between foregrounds, the antenna power pattern, and the mapping between geometric phases of baselines and delays.
 We discuss the spillover of foreground power beyond the horizon delay limits caused by the chromatic nature of the antenna power pattern.
@@
 Fig.~\ref{fig:window-functions} shows the {\it Blackman-Harris} window (gray) and  the window in equation~\ref{eqn:bhw2} (black) in frequency (top) and their power responses in delay (bottom).
-In its Fourier domain, this window has a response obtained by squaring {\bf a} {\it Blackman-Harris} window response and thus increases the dynamic range further in the power response by another 100 -- 120~dB with $\epsilon\approx 42\%$ and $w_\textrm{ne} \approx 2.88$.
+In its Fourier domain, this window has a response obtained by squaring a {\it Blackman-Harris} window response and thus increases the dynamic range further in the power response by another 100 -- 120~dB with $\epsilon\approx 42\%$ and $w_\textrm{ne} \approx 2.88$.
 
@@
 
-{\bf It must be noted that in order to obtain this modified window function over a band of 100~MHz after convolution, the original {\it Blackman-Harris} window used in the convolution must occupy a band narrower than 100~MHz.
+It must be noted that in order to obtain this modified window function over a band of 100~MHz after convolution, the original {\it Blackman-Harris} window used in the convolution must occupy a band narrower than 100~MHz.
 This is why the modified window has a wider response in delay domain.
@@
 While higher order powers could be used instead of the squared response we employ, there is a trade-off between the dynamic range, delay resolution, and sensitivity.
-A squared response was found to be sufficient for our purposes.}
+A squared response was found to be sufficient for our purposes.
 
 In HERA-19 array layout, there are 30 unique baseline vectors and 8 unique baseline lengths.
-{\bf \citet{thy15a} showed that foreground contamination depends not only on the baseline length but also on its orientation, pointing direction on the sky, and whether the source of emission is diffuse or compact}.
-Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines} shows the delay power spectra of foregrounds on the 8 unique baseline lengths obtained with the aforementioned models for power pattern at {\bf certain chosen} pointings on the sky.
-{\bf It will be shown later in \S\ref{sec:baseline-RA} that choice of pointing is immaterial for HERA as long as pointings with the Galactic plane overhead are avoided}.
+\citet{thy15a} showed that foreground contamination depends not only on the baseline length but also on its orientation, pointing direction on the sky, and whether the source of emission is diffuse or compact.
+Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines} shows the delay power spectra of foregrounds on the 8 unique baseline lengths obtained with the aforementioned models for power pattern at certain chosen pointings on the sky.
+It will be shown later in \S\ref{sec:baseline-RA} that choice of pointing is immaterial for HERA as long as pointings with the Galactic plane overhead are avoided.
 
@@
   \includegraphics[width=\linewidth]{f4.eps}
-  \caption{Foreground delay power spectra in units of K$^2 (h^{-1}$~Mpc$)^3$ on unique baseline lengths of HERA-19 at {\bf certain chosen} sky pointings.
+  \caption{Foreground delay power spectra in units of K$^2 (h^{-1}$~Mpc$)^3$ on unique baseline lengths of HERA-19 at certain chosen sky pointings.
 The baseline length and orientation (anti-clockwise from East) are annotated at the top right corner of each panel.
@@
 
-Reflections shift the measured foreground power to higher modes in $\tau$ (or in $k_\parallel$) and thus cause contamination in these critical $k_\parallel$-modes {\bf which is in addition to that already present due to spectral structures in the foregrounds and the instrument}.
+Reflections shift the measured foreground power to higher modes in $\tau$ (or in $k_\parallel$) and thus cause contamination in these critical $k_\parallel$-modes which is in addition to that already present due to spectral structures in the foregrounds and the instrument.
 These delay shifts introduce ripples in the spectrum.
@@
 Both EoR models were employed in this analysis to reduce the dependence of design specifications on any single model.
-However, we found similar results except for minor differences caused by {\bf relatively} small amplitude differences between the two EoR models {\bf for $|k_\parallel|>k_\textrm{p}$}.
-Hence, we only present results from using EoR model 1 at 150~MHz.
+However, we found similar results except for minor differences caused by relatively small amplitude differences between the two EoR models at $|k_\parallel|>k_\textrm{p}$.
+Hence, we only present results from using EoR model~1 at 150~MHz.
 
@@
   \caption{Minimum required attenuation (in dB) for internal dish-feed reflections required to keep the reflected foreground power below EoR H{\sc i} signal power for all $k_\parallel$-modes greater than $0.1\,h$~Mpc$^{-1}$ (solid), $0.15\,h$~Mpc$^{-1}$ (dashed) and $0.2\,h$~Mpc$^{-1}$ (dotted).
-This is obtained on 14.6~m antenna spacing for EoR model 1 at 150~MHz ($z\approx 8.47$) and foreground power obtained with an achromatic antenna beam model.
+This is obtained on 14.6~m antenna spacing for EoR model~1 at 150~MHz ($z\approx 8.47$) and foreground power obtained with an achromatic antenna beam model.
 For EoR to be detectable in respective $k_\parallel$-modes despite these systematics, the attenuation of reflections must exceed these limits (outside the shaded regions).}
@@
   \caption{Minimum required attenuation (in dB) for antenna-to-antenna reflections to keep reflected foreground power below EoR H{\sc i} signal power for all $k_\parallel$-modes greater than $0.1\,h$~Mpc$^{-1}$ (left), $0.15\,h$~Mpc$^{-1}$ (middle) and $0.2\,h$~Mpc$^{-1}$ (right).
-This is obtained on 14.6~m antenna spacing for EoR model 1 at 150~MHz ($z\approx 8.47$) and foreground power obtained with an {\it Airy} (dashed) and simulated chromatic (solid) antenna beam models.
+This is obtained on 14.6~m antenna spacing for EoR model~1 at 150~MHz ($z\approx 8.47$) and foreground power obtained with an {\it Airy} (dashed) and simulated chromatic (solid) antenna beam models.
 Regions excluding shaded regions indicate EoR will be detectable in respective $k_\parallel$-modes despite these reflections.
@@
 
-We note here that designing {\bf an antenna element whose beam} closely resembles a nominal {\it Airy} pattern will have a significantly higher tolerance for allowing antenna-to-antenna reflections and yet remain very effective for EoR signal detection.
-The HERA collaboration constantly pursues improvement of its {\bf antenna element} design to minimize limitations from such chromatic systematics.
+We note here that designing an antenna element whose beam closely resembles a nominal {\it Airy} pattern will have a significantly higher tolerance for allowing antenna-to-antenna reflections and yet remain very effective for EoR signal detection.
+The HERA collaboration constantly pursues improvement of its antenna element design to minimize limitations from such chromatic systematics.
 
@@
 
-{\bf The HERA antenna beam model used accounts for chromaticity introduced due to reflections between the dish and the feed but not between dishes.
-Ignoring the latter,} we estimate the EoR-foreground dynamic range (ratio of EoR signal and foreground powers) {\bf achievable with HERA} for both EoR models in the presence of antenna beam chromaticity.
+The HERA antenna beam model used accounts for chromaticity introduced due to reflections between the dish and the feed but not between dishes.
+Ignoring the latter, we estimate the EoR-foreground dynamic range (ratio of EoR signal and foreground powers) achievable with HERA for both EoR models in the presence of antenna beam chromaticity.
 In order to avoid signal evolution across the entire band, we use subbands in which EoR signal evolution is not expected to be significant.
@@
 Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-150-subband} and \ref{fig:asm-dps-beam-chromaticity-baselines-170-subband} show the EoR signal and foreground power in 150~MHz and 170~MHz subbands respectively.
-EoR models 1 and 2 are shown in cyan and gray respectively.
+EoR models~1 and 2 are shown in cyan and gray respectively.
 The foreground delay power spectra obtained with achromatic, {\it Airy} and simulated chromatic antenna patterns are shown in black, red, and blue respectively.
@@
   \subfloat[][170~MHz subband ($z \approx 7.36$)]{\label{fig:asm-dps-beam-chromaticity-baselines-170-subband}\includegraphics[width=\linewidth]{f7b.eps}}
-  \caption{EoR signal and foreground delay power spectrum in units of K$^2 (h^{-1}$~Mpc$)^3$ in 150~MHz (top) and 170~MHz (bottom) subbands ($B_\textrm{eff}=10$~MHz) on eight unique baseline lengths of HERA-19 at {\bf certain chosen} sky pointings.
+  \caption{EoR signal and foreground delay power spectrum in units of K$^2 (h^{-1}$~Mpc$)^3$ in 150~MHz (top) and 170~MHz (bottom) subbands ($B_\textrm{eff}=10$~MHz) on eight unique baseline lengths of HERA-19 at certain chosen sky pointings.
 The length and orientation of the baseline vector corresponding to each panel is annotated on the top right corner.
-EoR models 1 and 2 are shown in cyan and gray respectively.
+EoR models~1 and 2 are shown in cyan and gray respectively.
 The foregrounds obtained with achromatic, {\it Airy} and simulated chromatic antenna beams are shown in black, red and blue respectively.
@@
 
-We consider the foreground power spectrum obtained with the simulated chromatic antenna beam, and EoR models 1 and 2, in each of the 150~MHz and 170~MHz subbands.
+We consider the foreground power spectrum obtained with the simulated chromatic antenna beam, and EoR models~1 and 2, in each of the 150~MHz and 170~MHz subbands.
 Fig.~\ref{fig:eor-fg-ratios} shows $\rho(\boldsymbol{b},f_0,\alpha)$ for all 30 unique HERA baselines over 24 hours of $\alpha$ for the two EoR models and two subbands used in this study.
@@
   % \subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_170.0_MHz_subband.eps}}
-  \subfloat[][EoR model 1, 150~MHz subband ]{\label{fig:21cmfast-fg-ratio-150}\includegraphics[width=0.45\linewidth]{f8a.eps}}
-  \subfloat[][EoR model 2, 150~MHz subband ]{\label{fig:lidz-fg-ratio-150}\includegraphics[width=0.45\linewidth]{f8b.eps}} \\
-  \subfloat[][EoR model 1, 170~MHz subband ]{\label{fig:21cmfast-fg-ratio-170}\includegraphics[width=0.45\linewidth]{f8c.eps}}
-  \subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{f8d.eps}}
+  \subfloat[][EoR model~1, 150~MHz subband ]{\label{fig:21cmfast-fg-ratio-150}\includegraphics[width=0.45\linewidth]{f8a.eps}}
+  \subfloat[][EoR model~2, 150~MHz subband ]{\label{fig:lidz-fg-ratio-150}\includegraphics[width=0.45\linewidth]{f8b.eps}} \\
+  \subfloat[][EoR model~1, 170~MHz subband ]{\label{fig:21cmfast-fg-ratio-170}\includegraphics[width=0.45\linewidth]{f8c.eps}}
+  \subfloat[][EoR model~2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{f8d.eps}}
   \caption{Worst-case EoR-foreground dynamic range, $\rho(\boldsymbol{b},f_0,\alpha)$, in {\it foreground avoidance} modes for different HERA-19 baselines as a function of RA ($\alpha$) of pointing on the sky.
@@
 The color scale is logarithmic.
-Even in the worst case, HERA will be able detect EoR drawn from independent models on all baselines for a large fraction of a full 24~hour sky transit cycle {\bf except during the transit of the Galactic plane seen at 16--19 hours of RA}.
+Even in the worst case, HERA will be able detect EoR drawn from independent models on all baselines for a large fraction of a full 24~hour sky transit cycle except during the transit of the Galactic plane seen at 16--19 hours of RA.
 $\rho(\boldsymbol{b},f_0,\alpha)$ is seen to increase with increasing baseline length.
@@
 We attribute this to the much steeper dependence of foreground emission on baseline length than that of EoR H{\sc i} power.
-{\bf This trend demonstrates that it is predominantly due to diffuse emission}.
+This trend demonstrates that it is predominantly due to diffuse emission.
 This is also confirmed from Fig.~\ref{fig:subbands} where the peak and sidelobe levels of foreground power obtained with the simulated chromatic antenna beam on the 14.6~m baseline, progressively drops by two orders of magnitude on the 58.4~m baseline.
 Hence, from a foreground contamination standpoint, the shortest baselines are less sensitive than longer ones in HERA-19 layout.
-% {\bf With the full proposed layout emission from point sources may become significant on longer baselines}.
 
-In all four cases considered here, except when the Galactic {\bf plane} appears overhead {\bf roughly between 16 and 19 hours of RA}, the worst-case signal-foreground ratio lies above unity in most of this parameter space.
+In all four cases considered here, except when the Galactic plane appears overhead roughly between 16 and 19 hours of RA, the worst-case signal-foreground ratio lies above unity in most of this parameter space.
 It demonstrates that HERA should detect the EoR signal with a very high signal-foreground ratio on all baselines over a majority of the pointings.
@@
 By accounting for these instrumental systematics, if data is not limited by thermal noise, we demonstrate that HERA should detect EoR in $k_\parallel\gtrsim 0.2\,h$~Mpc$^{-1}$ with high significance with a simple spectral weighting even under a conservative analysis criterion that does not involve {\it foreground removal} strategies.
-All baselines of HERA-19 will not only {\bf individually} detect but also help in filtering highly likely EoR models.
+All baselines of HERA-19 will not only individually detect but also help in filtering highly likely EoR models.
 
-We are also investigating advanced strategies for foreground removal that will {\bf effectively reduce} these systematics further.
+We are also investigating advanced strategies for foreground removal that will effectively reduce these systematics further.
 Advances in calibration, foreground modeling and subtraction will improve the performance listed here.

### 2016-06-27 DishReflectometry/GB_reflectometry_part2/Simulation/delayplot/delayplot.py
dding all the changes done from June 15-June 26th

@@ -1,0 +1,94 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import aipy as ap
+
+######Read in data#####
+ant_file = 'useHERAs11.csv'
+feed_file= 'useHERA_feeds11.csv'
+def readfile(fn):
+    fp = open(fn,'r')
+    i=0
+    freq=[]
+    s11_mag_dB=[]
+    s11_phase_deg=[]
+    s11 = []
+    for line in fp:
+        #print line,
+        if i>0 and len(line)>2:
+            data = line.split(',')
+            freq.append(float(data[0]))
+            m = np.power(10.0,float(data[1])/20.0)
+            s11_mag_dB.append(float(data[1]))
+            p = np.pi*float(data[2])/180.0
+            s11_phase_deg.append(float(data[2]))
+            s11.append(m*np.exp(1j*p))
+        i+=1
+    fp.close()
+    freq = np.array(freq)
+    s11_mag_dB = np.array(s11_mag_dB)
+    s11_phase_deg = np.array(s11_phase_deg)
+    s11=np.array(s11)
+    return freq,s11_mag_dB,s11_phase_deg, s11
+    
+fa,ma,pa,S11=readfile(ant_file)
+ff,mf,pf,Gf=readfile(feed_file)
+Ef = 1.0 + Gf
+
+plt.figure('S11')
+plt.plot(fa,ma,label='antenna')
+plt.plot(ff,mf,label='feed')
+plt.legend()
+
+def csq(c):
+    cc = c*c.conjugate()
+    return np.real(cc.real)
+
+#####Compute Sigma#####
+plt.figure('Sigma_f')
+#####       S     #####
+S = Gf*(S11-Gf)/Ef + Ef
+plt.plot(fa,csq(S))
+
+#####Analytical |S|^2#####
+t1 = csq(Ef)
+_t = Gf*(S11-Gf)/Ef
+t2 = 2.0*np.real(_t.real)
+t3 = csq(Gf)*csq(S11-Gf)/csq(Ef)
+
+#S2 = t1 + t2 + t3
+S2 = csq(S)
+#S2 = S2*S2.conjugate()
+plt.plot(fa,S2)
+
+#####Get delay spectrum version#####
+#####    Change type here     #####
+S2use = 'square'  # 'linear' or 'square'
+####################################
+if S2use[0] == 'l':
+    use_S = S
[…]

### 2016-06-27 DishReflectometry/GB_reflectometry_part2/Simulation/plot_simulation.py

@@ -2,7 +2,7 @@
 
 import numpy as np, pylab as plt, aipy as a
 import sys, csv
-
+from matplotlib import colors
 
 def fromcsv(filename):
     print 'Reading', filename
@@ -61,6 +61,13 @@ for filename in sys.argv[1:]:
     fq_H,db_H = fromcsv1('/Users/Punthipatra/WORKAREA1/DATA_Area/Project_HERA/DishPapers/DishReflectometry/GB_reflectometry_part2/HERA_DB.csv') # Reading the magnitude and phase of the feed only datafile to calibrate for the zero point/ 
     fq_H,ph_H = fromcsv1('/Users/Punthipatra/WORKAREA1/DATA_Area/Project_HERA/DishPapers/DishReflectometry/GB_reflectometry_part2/HERA_P.csv')
     
+    #fq_feed =fq_f
+    #db_feed =db_f
+    #ph_feed =ph_f
+    #fq_H = fq
+    #db_H = db
+    #ph_H = ph
+    
     delay,delay_spectrum = fromcsv('simulation_aaron.csv') # Reading the magnitude and phase of the feed only datafile to calibrate for the zero point/ 
     
     
@@ -73,7 +80,7 @@ for filename in sys.argv[1:]:
     d_H = lin(db_H,ph_H)
     
     
-    valid = np.where(np.logical_and(fq < .200, fq > .100)) # restrict to PAPER band
+    valid = np.where(np.logical_and(fq < .200, fq > .10)) # restrict to PAPER band
     valid1 = np.where(np.logical_and(fq_H < .200, fq_H > .100)) # restrict to PAPER band
     
     fq, db, ph, d = fq[valid], db[valid], ph[valid], d[valid]
@@ -116,11 +123,13 @@ for filename in sys.argv[1:]:
         #plt.plot(fq_f,180*np.arctan2(np.imag(d_f),np.real(d_f))/np.pi,linewidth=2.5,label='return loss HERA element (simulation)' )
         #plt.plot(fq_feed,ph_feed,linewidth=2.5,label='return loss HERA element (measured)' )
         
-        #plt.plot(fq,pwr(d2),linewidth=2.5,label='return loss feed (simulation)' )
+        #plt.plot(fq,db,linewidth=2.5,label='return loss feed (simulation)' )
+        #plt.show()
[…]

### 2016-06-27 DishReflectometry/GB_reflectometry_part2/plot_reflectometry.py

@@ -90,9 +90,9 @@ for filename in sys.argv[1:]:
         #_dww_rb = np.fft.ifft((d2_rb)**2*window2) / window2.mean() # compensate for window amplitude
 
     #import IPython; IPython.embed()
-    plt.plot(fq_f,np.abs(d_f),linewidth=2.5,label='Transmission UCB(real)')
-    plt.plot(fq_f,np.abs(d2),linewidth=2.5,label='Transmission UCB(real)')
-    plt.show()
+    #plt.plot(fq_f,np.abs(d_f),linewidth=2.5,label='Transmission UCB(real)')
+    #plt.plot(fq_f,np.abs(d2),linewidth=2.5,label='Transmission UCB(real)')
+    #plt.show()
     #plt.plot(fq,d_t.imag,linewidth=2.5,label='Transmission UCB (imag)')
     #plt.plot(fq,10.0*np.log10(np.abs(d2)),linewidth=2.5,label='Corrected measurements UCB (abs mag)')
     #plt.plot(fq_rb_f,d_rb_t.real,linewidth=2.5,label='Transmission RB (real)')

### 2016-06-28 DishReflectometry/GB_reflectometry_part2/dly_resp_cov_wgt.py
Uploadint Aaron's code for analysis.

@@ -1,0 +1,234 @@
+#! /usr/bin/env python
+import numpy as np, pylab as plt
+import capo, aipy, scipy.interpolate, random
+import capo.oqe as oqe
+import sys
+
+HERA_BM_EFF_150 = 0.0905 # at 150 MHz, from beam_area.py X4Y2_490_150.hmap for \Omega_eff
+HERA_BM_NOS_150 = 0.0401 # at 150 MHz, from beam_area.py X4Y2_490_150.hmap for \Omega_eff
+
+#CH0,NCHAN = 30, 61
+CH0,NCHAN = 98, 61
+
+def jy2T(fq, bm=HERA_BM_NOS_150):
+    '''Return [mK] / [Jy] for a beam size (in sr) and frequency (in GHz).'''
+    lam = aipy.const.c / (fq * 1e9)
+    return 1e-23 * lam**2 / (2 * aipy.const.k * bm) * 1e3
+
+def gen_eor_mdl(ks, Pk, shape, fq_axis=1, fq0=.1, fq1=.2, bm_eff=HERA_BM_EFF_150, bm_nos=HERA_BM_NOS_150, kpr=.06):
+    fqs = np.linspace(fq0,fq1,shape[fq_axis]) # GHz
+    B = fq1 - fq0 # GHz
+    z = capo.pspec.f2z(np.average(fqs))
+    scalar = capo.pspec.X2Y(z) * bm_eff * B
+    mdl = scipy.interpolate.interp1d(ks, Pk, bounds_error=False, fill_value=0)
+    etas = np.fft.fftfreq(fqs.size, fqs[1]-fqs[0])
+    kpls = etas * capo.pspec.dk_deta(z)
+    ks = np.sqrt(kpls**2 + kpr**2)
+    Pk = mdl(ks)
+    dspec_amp = np.sqrt(Pk / scalar)
+    sh = [1] * len(shape); sh[fq_axis] = -1
+    dspec_amp.shape = sh
+    jy2mK_HERA = jy2T(fqs, bm=bm_nos); jy2mK_HERA.shape = sh
+    vis = oqe.noise(shape).astype(np.complex128) * dspec_amp
+    vis_mK = np.fft.fft(vis, axis=fq_axis)
+    vis_Jy = vis_mK / jy2mK_HERA
+    return vis_Jy
+
+def gen_constraint(tau, achr, eor, tcut=200.):
+    mn = {}
+    for i,ti in enumerate(tau):
+        for j,tj in enumerate(tau):
[…]

### 2016-06-28 DishReflectometry/Paper1_v2.tex

--- 2016-04-19 DishReflectometry/Paper1_v1.tex
@@
 Due to the chromaticity of the sky signal as well as the instrument response, the delay spectrum of the sky spills over into delays with $\tau> \tau_{g}$, with a decaying amplitude [Ref to the Figure Parsons12].
-The foreground, $P_{fg}(\tau)$, which is spectrally smooth, and the 21~cm power spectrum, $P_{21}(\tau)$, which contains spectral signatures, contribute to the sky delay spectrum, $P_{sky}(\tau)$.Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground, with respect to the delay spectrum of the $I_{21}$, reduces and the 21cm delay spectrum could be detectable.
+The foreground, $P_{fg}(\tau)$, which is spectrally smooth, and the 21~cm power spectrum, $P_{21}(\tau)$, which contains spectral signatures, contribute to the sky delay spectrum $P_{sky}(\tau)$.Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground, with respect to the delay spectrum of the $I_{21}$, reduces and the 21cm delay spectrum could be detectable.
 
@@
 
-\subsection{Feed effect: zero delay correction}
-%At first, the frequency domain measurement of s11 is Fourier-transformed to compute the response of the system in the delay domain.
-
 \subsubsection{\textbf{Effect of antenna beam pattern and feed return loss}}
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{plots/VNA_RL.png}
-\caption{Magnitude and phase of the combined effects of the return loss at the VNA input alone with the cable resistive loss as computed from the return loss measurement of the open load at the feed input of the cable.
+%\begin{figure}
+%\centering
+%\includegraphics[width=\linewidth]{plots/VNA_RL.png}
+%\caption{Magnitude and phase of the combined effects of the return loss at the VNA input alone with the cable resistive loss as computed from the return loss measurement of the open load at the feed input of the cable.
 This is consistent with the specifications of the RF connectors which is commonly used at low frequencies }
-\label{fig:window}
-\end{figure}
+%\label{fig:window}
+%\end{figure}
 

### 2016-06-29 DishReflectometry/Paper1_v2.tex
Edditing to incorporate Aaron's analysis.

@@
+%\documentclass[12pt,preprint]{aastex}
 \documentclass[twocolumn]{emulateapj}
@@
 established (see, e.g.,
-~\citep{furlanetto_et_al2006,morales_wyithe2010,pritchard_loeb2012}),
+~\cite{furlanetto_et_al2006, morales_wyithe2010, pritchard_loeb2012}),
 the technical path toward measuring this signal has been extremely challenging.  The
@@
 challenges that are yet to be fully solved.  With noise temperatures dominated
-by sky noise ~\citep{XXX} and foregrounds four to five orders of magnitude
-brighter than the signal ~\citep{XXX}, 
+by sky noise and foregrounds four to five orders of magnitude
+brighter than the signal ~\citep{2015ApJ...801..138P}, 
 sky-averaged 21~cm monopole experiments such as
-(EDGES; ~\citealt{XXX}),
-(BIGHORNS; ~\citealt{XXX}),
-(SARAS; ~\citealt{patra_et_al2014}),
-(SCIHI; ~\citealt{voytek_et_al2014}),
-(HYPERION; ~\citealt{presley_et_al2015})
+EDGES; ~\citep{baars_et_al1977},
+BIGHORNS; ~\citealt{XXX},
+SARAS; ~\citep{Patra_et_al1999} ,
+SCIHI; ~\citealt{2015PhDT........65V},
+HYPERION; ~\citep{presley_et_al2015}
 % XXX others?
@@
 %
-\subsubsection{Effect of antenna beam pattern and feed return loss on delay spectrum estimation}
-The return loss $\Gamma_{f}$ determines the amount of power coupled to the system via the feed.
+%\subsubsection{Effect of antenna beam pattern and feed return loss on delay spectrum estimation}
+%The return loss $\Gamma_{f}$ determines the amount of power coupled to the system via the feed.
 Additionally, with each reflection, the power coupled to the system reduces by a factor of $\Gamma_{f}^{2}$.
@@
 The complex antenna impedance is shown in Figure \ref{fig:feed_impedance}.
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{plots/Feed_impedance.png}
-\caption{Complex antenna impedance of the HERA feed element.} %Some indication of which line is which on the plot would be really helpful here.
-\label{fig:feed_impedance}
-\end{figure} 
+%\begin{figure}
+%\centering
+%\includegraphics[width=\linewidth]{plots/Feed_impedance.png}
+%\caption{Complex antenna impedance of the HERA feed element.} %Some indication of which line is which on the plot would be really helpful here.
+%\label{fig:feed_impedance}
+%\end{figure} 
 %
-While the antenna beam pattern, $A_{f}$, is a smooth function of frequency and should have its imprint confined to lower delays, the return loss, $\Gamma_{f}$, broadens the delay spectrum.
+%While the antenna beam pattern, $A_{f}$, is a smooth function of frequency and should have its imprint confined to lower delays, the return loss, $\Gamma_{f}$, broadens the delay spectrum.
 However, a smaller return loss will result in a vertical shift of the delay spectrum at lower values and, therefore, can make the higher order reflections insignificant.
@@
 \\
-\subsubsection{Effect of frequency bandwidth on delay spectrum estimation}
-The estimation of the delay spectrum by taking the Fourier transform of the measured return loss is sensitive to the frequency bandwidth of operation.
+%\subsubsection{Effect of frequency bandwidth on delay spectrum estimation}
+%The estimation of the delay spectrum by taking the Fourier transform of the measured return loss is sensitive to the frequency bandwidth of operation.
 Since the measurements are done in the spectral domain, a measurement between two frequencies is analogous to windowing the frequency domain data by a square window function.
@@
 Windowing prior to Fourier transforming the data significantly reduces the system response at higher delays.
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{plots/window.png}
-\caption{The affect of a finite bandwidth on the estimation of the delay spectrum: The blue line shows the delay spectrum of the HERA element computed from the measured data, which is band limited between 100 to 200MHz.
+%\begin{figure}
+%\centering
+%\includegraphics[width=\linewidth]{plots/window.png}
+%\caption{The affect of a finite bandwidth on the estimation of the delay spectrum: The blue line shows the delay spectrum of the HERA element computed from the measured data, which is band limited between 100 to 200MHz.
 The green line shows the delay spectrum estimated from the same data set after multiplying the data by a Blackman Harris window.
 The delay spectrum of the windowed data set shows a significant reduction in the instrument response at higher delays.}
-\label{fig:window}
-\end{figure} 
-\subsubsection{Effect of the dish and feed on the delay spectrum estimation}
-The measurement equations show the effects of multiple reflections of the sky signal between the feed and the dish.
+%\label{fig:window}
+%\end{figure} 
+%\subsubsection{Effect of the dish and feed on the delay spectrum estimation}
+%The measurement equations show the effects of multiple reflections of the sky signal between the feed and the dish.
 Any other reflections off the feed structure and/or any other part of the dish-feed assembly would appear at arbitrary delays.
@@
 The delay spectrum estimated from this measurement provides the lowest limit of the delay spectrum of the instrument, considering there are not multiple reflections between the feed and the dish.
- Any additional reflections also contribute to the measured return loss and, thus, the delay spectrum at various delays.
+ %Any additional reflections also contribute to the measured return loss and, thus, the delay spectrum at various delays.
 Figure \ref{fig:delay_spectrum} shows the delay spectrum of the feed while it is kept upside down on the ground (in green), as well as that of a HERA antenna with the feed suspended at the focal plane (in blue).
@@
 %\subsubsection{Effect of feed height on delay spectrum estimation}
-\subsubsection{Performance Comparison: HERA vs. PAPER}
-While PAPER has established the, to date, most stringent upper limit on the 21cm power spectrum measurement, the need to increase the measurement sensitivity called for increased collecting area per PAPER antenna.
+%\subsubsection{\textbf{Performance Comparison: HERA vs. PAPER}}
+%While PAPER has established the, to date, most stringent upper limit on the 21cm power spectrum measurement, the need to increase the measurement sensitivity called for increased collecting area per PAPER antenna.
 This has driven the parabolic reflector antenna design of the PAPER successor, HERA, where essentially the PAPER antenna, with minor modifications of the ground plane-side plane assembly, works as the feed and, thus, in combination with the dish, yields a larger collecting area per element.
@@
 
-\bibliography{biblio.bib}{}
+%\bibliography{biblio}{}
+\bibliography{Reference}
 \bibliographystyle{apj}

### 2016-06-30 DishReflectometry/Paper1_v2.tex
Second edit with figure 7, 8 replacing fig 4,5

@@
 sky-averaged 21~cm monopole experiments such as
-EDGES; ~\citep{baars_et_al1977},
+EDGES; ~\citep{Bowman_et_al2010},
 BIGHORNS; ~\citealt{XXX},
-SARAS; ~\citep{Patra_et_al1999} ,
-SCIHI; ~\citealt{2015PhDT........65V},
+SARAS; ~\citep{Patra_et_al2015} ,
+SCIHI; ~\citep{2015PhDT........65V},
 HYPERION; ~\citep{presley_et_al2015}
@@
 & = & \frac{ (1+\Gamma_d)(1+\Gamma_{f})}{1+\Gamma_{f}\Gamma_{d}\dfngexp} 
- \label{eq:Sigma}
+\label{corrected_response}
 \end{eqnarray}
@@
 \\
-\indent A VNA is connected to the HERA element via a 50-foot cable.
+\section{\textbf{Reflectometry measurements}}
+
+Reflectometry measurements are carried out at the HERA element prototype in Green
+Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise the performance.  HERA element consists off a $14\,m$ diameter
+parabolic reflector and a crossed-dipole pair as a feed.
+The cross dipole antenna pair is identical to the feed of the PAPER antenna which is suspended at the focal plane of the dish with the support of three vertical poles.
+HERA elements are closely spaced with centre to centre distance between two dishes are equal to the dish diameter.
+Therefore, to reduce the coupling between the adjacent dishes, the crossed dipole feed along with the back plane is encased in a cylindrical cage.
+The feed is raised and
+lowered by a three-pulley system mounted on the three poles. The focal height of the dish is $5m$.  The detail geometry and electromagnetic design of of the feed is presented in deBoer et al 2016. \\
+%A vector network analyser is connected via a 50feet long cable at the feed output of the HERA element and the return loss $(s_{11})$ of the HERA element is measured as a function of frequencies while the feed is suspended at the focal plane of the dish.
+
+ A VNA is connected to the HERA element via a 50-foot cable.
 It then transmits a broadband noise voltage, $\volt_{trans}$, and a factor $(1+\Gamma_f)$ of this voltage is radiated by the feed while the fraction $\Gamma_{f}$ returns to the VNA.
@@
  & = & \bmvolt(\thhat,\nu) \left[(1+\Gamma_f) + \frac{\Gamma_f}{(1+\Gamma_f)}\left(s_{11} - \Gamma_f\right)\right]
+\label{zero_delay_correction}
 \end{eqnarray}
@@
 These will broaden the width of the delay spectrum, which ultimately interferes with the 21cm power spectrum detection.
-% Combining these terms, the expression of visibility will be,
 
-%\begin{eqnarray}\label{eqn:series1}
-%\vis(\vec b, \nu) & = & \int \volt_{1}\volt_{2}^{*} d\Omega \nonumber\\
-%			& = & \int I_{sky}(\vec b, \nu)A(\thhat,\nu) \ifngexp d\Omega
-%\end{eqnarray}
-%%%where we define a combined common instrument parameter, written as, 
-%%% \begin{eqnarray}
-%%%\Sigma(\thhat, \nu) & = & \beam_{f}  [ 1+  \Gamma_{f}\Gamma_{d} \dfngexp \nonumber\\
-%%%&& + (\Gamma_{f}\Gamma_{d})^2(\dfngexp)^{2}+ \nonumber\\
-%%%&&  ....+(\Gamma_{f}\Gamma_{d})^{n}(\dfngexp)^{n}  ]\\
-%%%& = & \beam_{f}+\beam_{f} \displaystyle\sum\limits_{n=1}^{n} [2\Re( \Gamma_{f}\Gamma_{d}\dfngexp)]^{n}
-%%%   \nonumber\\ 
-%%%   \label{eq6}
-%%%\end{eqnarray}
-%%%where, $\beam_{f}=\bmvolt_{f}\bmvolt_{f}^{*}= |a(1-\Gamma_{f})|^{2}$ is the antenna cross power pattern.
-%and the delay spectrum would be, 
-%\begin{eqnarray}
-%\tilde V(\vec b, \tau) & = & \int \left [ \int I_{sky}(\vec b, \nu)\Sigma(\vec b, \nu) \fngexp  d\Omega \right ]  e^{-2\pi i\nu\tau} d\nu \nonumber \\
-%\tilde V(\vec b, \tau) & = & \int \left [ I_{sky}(\vec b, \nu) \ast A(\vec b, \nu) \right]\dfngexp d\Omega
-%\label{eq7}
-%\end{eqnarray}
-
-% Thus, the correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected.
-\\
-
-%In a related series of papers, Thyagarajan et al.
-(2016) have shown the simulated sensitivity calculations of HERA for various antenna element responses (Figure \ref{fig:sim_limit_delay}) using a comprehensive foreground model as well as a model for the EoR power spectrum.
-From these simulations, Figure \ref{fig:sim_limit_delay} (Thyagarajan et al.) shows the level of attenuation required for the multiply reflected sky signal in order to reduce the foreground contaminations at the delay modes significant for power spectrum measurements.
-Ewall-Wice et al.
-(2016) has simulated the time domain response of the HERA element considering multiple reflections between the feed and the dish.
-Figure \ref{fig:sim_limit_delay} shows the simulated cross-power response of a pair of HERA antennas as a function of time (Ewall-wice et al.).
-These simulations set up the performance criterion for the HERA antenna element.
-% \begin{figure*}[ht]
-%\begin{minipage}[b]{0.5\linewidth}
-%\centering
-%\includegraphics[angle=0, width=\linewidth]{plots/sim_limit.jpg}
-%\end{minipage}
-%\hspace{0.1cm}
-%\begin{minipage}[b]{0.5\linewidth}
-%\centering
-%\includegraphics[angle=0, width=\linewidth]{plots/sim_delay.jpg}
-%\end{minipage}
-%\caption{Left: Signal attenuation required for the reflected sky power arriving at the feed at higher delays, as estimated from the simulated antenna beam and foreground models (Thyagarajan et al.).
-The three different contours show three different system performance requirements based on the simulated response of the HERA element for a measurement frequency of 150MHz, corresponding to the redshift of $z=8.47$, and a 14.5m baseline.
-The instrumental requirements become extremely stringent for the detection of the smaller $k_\parallel$ values, corresponding to very large spatial scales.
-Right: The simulated cross power response kernel for HERA.
-The simulation assumes an achromatic beam with the chromaticity attributed entirely to the multiple reflections between the dish and the feed.
-This shows the level to which the multiple reflections at the higher delays is expected to be reduced following the dish and feed designs.} %Some explanation of the left hand axis of the right panel figure would be really nice in here since this is the only mention of R(tau), and it's new notation compared to the rest of the paper.
-%\label{fig:sim_limit_delay}       
-%\end{figure*}
-
-%signal, arriving at the feed at a delay $\Delta \tau$ with respect to the direct incidence, should be
-%at the level of $-60dB$ at a delay of $60ns$ relative to the first incident
-%signal at the feed ~\citep{parsons_deboer_memo}. This specification was
-%approximated based on the power level of the cosmological signal in relation to
-%foreground signals, which is estimated to be six orders of magnitude fainter
-%~\citep{santos_et_al2005,  ali_et_al2008,deoliveira2008, jelic_et_al2008, bernardi_et_al2009,bernardi_et_al2010, ghosh_et_al2011}. Additionally, the $14m$ HERA baselines set a foreground containing
-%Additionally, the $14m$ HERA baselines set a foreground containing
-%horizon-limit (the wedge) that, with some buffer, sets a delay specification of
-%$60ns$
-%~\citep{parsons_et_al2012b,vedantham_et_al2012,nithya_et_al2013,liu_et_al2014a,liu_et_al2014b}.
-Our goal is to measure the instrument response $\Sigma(\nu)$ and its effect on the power spectrum measurements.
-%++++++++++++++++++++++++++++++++++++++++++++++++++++++
-\section{\textbf{Reflectometry measurements}}
 \begin{figure*}
@@
 
-Reflectometry measurements are carried out at the HERA element prototype in Green
-Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise the performance.  HERA element consists off a $14\,m$ diameter
-parabolic reflector and a crossed-dipole pair as a feed.
-The cross dipole antenna pair is identical to the feed of the PAPER antenna which is suspended at the focal plane of the dish with the support of three vertical poles.
-HERA elements are closely spaced with centre to centre distance between two dishes are equal to the dish diameter.
-Therefore, to reduce the coupling between the adjacent dishes, the crossed dipole feed along with the back plane is encased in a cylindrical cage.
-The feed is raised and
-lowered by a three-pulley system mounted on the three poles.
-The focal height of the dish is $5m$.
-The detail geometry and electromagnetic design of of the feed is presented in deBoer et al 2016 (in prep).
-\\
-A vector network analyser is connected via a 50feet long cable at the feed output of the HERA element and the return loss $(s_{11})$ of the HERA element is measured as a function of frequencies while the feed is suspended at the focal plane of the dish.
-This measurement is
-Section 3 laid the mathematical framework of how the delay spectrum is estimated from the return loss measurement.
-The return loss of the feed while  facing up the sky as well as while suspended on the dish and ${I_{rec}\over I_{sky}}$  is shown in figure \ref{fig:all_RL}.
-
-Reflectometry measurements were carried out on the prototype HERA element in Green
-Bank, WV, (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise the performance. The HERA element consists of a $14\,m$ diameter
-parabolic reflector and a crossed-dipole pair -- identical to the feed of the PAPER antenna -- as a feed, which is suspended at the focal plane of the dish, where the focal height is $5m$, with the support of three vertical poles.
-The HERA elements are closely spaced, with the centre-to-centre distance between two dishes equal to the dish diameter.
-Therefore, to reduce the coupling between the adjacent dishes, the crossed-dipole feed and the back plane are encased in a cylindrical cage.
-The feed is raised and lowered by a three-pulley system mounted on the three poles.
-The detailed geometry and electromagnetic design of the feed is presented in deBoer et al.
-2016 (in prep).
-\\
-\indent A VNA is connected via a 50-ft cable at the feed output of the HERA element, and the return loss $(s_{11})$ is measured as a function of frequency while the feed is suspended at the focal plane of the dish.
-Section 3 laid the mathematical framework for how the delay spectrum is estimated from the return loss measurement.
-
-%, if the incident power from the sky signal is $I_{sky}$, the feed
-%reflection coefficient is $\Gamma_{f}$, and the dish reflection
-%coefficient is $\Gamma_{d}$, then the net power entering a feed after
-%$n^{th}$ reflection off the feed and the dish is:
-
-%\begin{eqnarray}
-%\tilde I_{meas}(\vec b, \nu) & = & \int I_{sky}(\vec b, \nu)A(\vec b, \nu) \dfngexp d\Omega
-%\end{eqnarray}
-
 Return loss measurements are similar to auto correlation measurement from a single HERA element.
@@
 
-%
-Return loss measurements are similar to auto correlation measurements from a single HERA element.
-Given our assumption that two adjacent antenna elements have identical design parameters and electrical properties, this power is also a measure of the cross power, or the visibility $\vis (\vec b, \nu)$, between the two antennas with a normalization factor of $2$.
-%
-\section{Results}
+The simultated and measureded return loss of the feed as well as the HERA element is shown in figure \ref{meas_sim_RL_feed} and figure \ref{meas_sim_RL_HERA}.
 \begin{figure}[ht]
@@
 \centering
-\includegraphics[angle=0, width=\linewidth]{plots/RL_mag.png}
+\includegraphics[angle=0, width=\linewidth]{plots/feed_meas_sim_mag.png}
 \end{minipage}
@@
 \centering
-\includegraphics[angle=0, width=\linewidth]{plots/RL_phse.png}
+\includegraphics[angle=0, width=\linewidth]{plots/feed_meas_sim_ph.png}
 \end{minipage}
-\caption{Left: Magnitude of the return loss of power measured in between 100 to 200 MHz using vector network analyser.
-Right panel shows the corresponding phase.
-Return loss of the feed alone is shown in green while the same for the feed+dish assembly is shown in blue.
-Finally, the quantity of interest ${I_{rec}\over I_{sky}}$ is shown in red.
-In ideal condition 100\% of the sky power is to be received and ${I_{rec}\over I_{sky}} = 1$ or 0dB.
-Finite return loss at the antenna input deviate this quantity from its ideal value and ${I_{rec}\over I_{sky}} < 1$.
-Also, frequency dependence of the feed and the dish as well as the multiple reflections introduces the small scale fluctuations as seen in the red curve.
+\caption{Magnitude and phase of the return loss of the feed as simulated and measured.
+While both the measurement and the simulation shows similar resonance around $120~MHz$, the simulation shows a better matching to a 50 Ohm transmission line compared to the measurements.
+The measurement also has some small scale fluctuation due to multiple reflection of the signal at the VNA input.
 }
-% HERA feed design is derived from modified PAPER antenna and therefore the return loss closely relates to the PAPER antenna response with slight frequency shift.
-The return loss measured when the HERA feed is suspended over the dish is, however, show deviation from the feed performance.
+\label{meas_sim_RL_feed}
+\end{figure}
+
+\begin{figure}[ht]
+\begin{minipage}[b]{\linewidth}
+\centering
+\includegraphics[angle=0, width=\linewidth]{plots/HERA_meas_sim_mag.png}
+\end{minipage}
+\vspace{0.1cm}
+\begin{minipage}[b]{\linewidth}
+\centering
+\includegraphics[angle=0, width=\linewidth]{plots/HERA_meas_sim_ph.png}
+\end{minipage}
+\caption{Magnitude and phase of the return loss of the HERA element as simulated and measured.
+In this case, both measurement and simulation shows similar level of return loss across the band with marginally better return loss at the high frequency end of the band.
 }
-\label{fig:all_RL}
+\label{meas_sim_RL_HERA}
 \end{figure}
+
+\section{Results}
 \begin{figure}       
@@
 \includegraphics[width=\linewidth]{plots/H_dish_feed.png}
-\caption{Delay spectrum of the HERA element (blue) the HERA feed (green) estimated by taking the Fourier transform of the measured return loss of power at the feed output.
+\caption{Delay spectrum of the HERA element (green) the HERA feed (blue) estimated by taking the Fourier transform of the measured return loss of power at the feed output.
 The feed, when suspended on the dish results in a more complex return loss and corresponding delay response is shown in the figure.
@@
 
-Figure \ref{fig:all_RL} shows the return loss measured between $100$ to
+Figure \ref{meas_sim_RL_HERA} shows the return loss measured between $100$ to
 $200MHz$ when the feed is suspended at the focal plane of the parabolic dish which is at $5m$ from the dish vertex.
-This measurement is Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{eq3}.
+This measurement is first correc ted to map the response of the antenna from transmitting mode to receiving mode via equation \ref{zero_delay_correction}.
+The corrected measurement is then Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{corrected_response}.
 Measurement bandwidth is kept much larger than the bandwidth of operation to achieve higher delay resolution.
-A number of systematic effects as well as mathematical artefacts that are critical to this measurements and corresponding estimation of the delay spectrum are taken in to account in determination of the delay spectrum and described below.
+A number of systematic effects as well as mathematical artefacts that are critical to this measurements and their effects on the corresponding estimation of the delay spectrum are taken in to account in determination of the delay spectrum and described below.
 
-\subsection{\textbf{Feed effect:zero delay correction}}
+\subsection{\textbf{Zero delay correction}}
 %At first, the frequency domain measurement of s11 is Fourier-transformed to compute the response of the system in the delay domain.
@@
 In delay domain, this appears at the zero delay bin.
-The zero delay response is identical whether or not the feed is suspended on the dish and  Therefore, we measure this response by measuring the feed return loss alone while the feed is kept on the ground facing the sky.
+The zero delay response is identical whether or not the feed is suspended on the dish.
+Therefore, we measure this response by measuring the feed return loss alone while the feed is kept on the ground facing the sky.
 This results in feed return loss alone including the surrounding cage structure but excluding the dish response.
-While $\Gamma_{f}$ fraction of power is reflected off the feed, $1+\Gamma_{f}$ fraction of the power gets transmitted.
+While $\Gamma_{f}$ fraction of incident voltage is reflected off the feed, $1+\Gamma_{f}$ fraction of the voltage is transmitted.
 In receiving mode, upon initial incidence, $\Gamma_{f}$ fraction of voltage is reflected back in to the space while $1+\Gamma_{f}$ voltage enters the feed.
@@
 The using the return loss measurement of the feed $(\Gamma_{f})$, the return loss measurement $s_{11}$ of the dish and feed assembly is corrected via equation \ref{eq:power_ratio} and the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated.
-Magnitude and phase of $\Gamma_{f}$ , $s_{11}$ and ${I_{rec}\over I_{sky}}$ is shown in figure \ref{fig:all_RL}.
 
-Figure \ref{fig:freq} shows the return loss measured between $100$ to
-$200$ MHz when the feed is suspended at the focal plane of the parabolic dish -- $5m$ from the dish vertex.
-This measurement is Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{eq3}.
-The measurement bandwidth is kept much larger than the bandwidth of operation to achieve a higher delay resolution.
-A number of systematic effects, as well as mathematical artifacts critical to these measurements and the corresponding estimation of the delay spectrum, are taken in to account in determining the delay spectrum and are described below.
-
-\subsubsection{\textbf{Effect of antenna beam pattern and feed return loss}}
+\subsection{\textbf{Antenna beam pattern and feed return loss}}
 The return loss $\Gamma_{f}$ determines the amount of power coupled to the system via the feed antenna.
@@
 The return loss of power results from the antenna impedance mismatch with the free space as well as the transmission line.
-The complex feed antenna impedance is shown in the figure \ref{fig:feed_impedance}.
 While antenna beam pattern $A_{f}$ is a smooth function of frequency and should have its imprint confined to lower delays, the return loss $\Gamma_{f}$ broadens the delay spectrum.
@@
 During observation, each HERA element is connected to an active balun similar to the ones used in the PAPER antenna (need reference) which provides greater than 10dB return loss of power at the feed output.These baluns are under further design improvements aiming at 10 to 20dB better imepedance match between the feed and the balun than the measurements presented here.
-Our measurement is done using a vector network analyser for which the active balun has been replaced by a passive balun.Given the antenna impedance and the 50 Ohm transmission line the measurements are done using the passive balun with a 2:1 impedance ratio providing a net return loss of power between the sky, the antenna and the transmission line shown in the figure \ref{fig:all_RL}.
+Our measurement is done using a vector network analyser for which the active balun has been replaced by a passive balun.Given the antenna impedance and the 50 Ohm transmission line the measurements are done using the passive balun with a 2:1 impedance ratio providing a net return loss of power between the sky, the antenna and the transmission line shown in the figure \ref{meas_sim_RL_feed}.
 This measurements are conservative estimate  for both $\Gamma_{f}$ and $s_{11}$.
 
-\subsubsection{\textbf{Effect of measurement bandwidth and window function}}
+\subsection{\textbf{Dish reflections}}
+Measurement equations shows the effects of multiple reflections of the sky signal between the feed and the dish.
+Any other reflections off the feed structure and/or any other part of the dish-feed assembly would appear at arbitrary delays.
+The estimated delay spectrum of the instrument is collectively contributed by all the reflections.
+We measure the return loss of the feed alone keeping it on the ground facing the sky shown in the Figure \ref{meas_sim_RL_feed}.
+Delay spectrum estimated from this measurement provides the lowest limit of the delay spectrum of the instrument considering there is no multiple reflections in between the feed and the dish.
+ Any additional reflections also contributes to the measured return loss and thus contributed to the delay spectrum at various delays.
+Figure \ref{fig:delay_spectrum} shows the delay spectrum of the feed while it is kept upside down on the ground in green, as well as that of a HERA antenna with the feed suspended at the focal plane in blue.
+At lower delays, the reflections are dominated by the feed structure.
+Therefore, the delay spectrum in both the cases follow each other.
+Since the distance between the feed and the dish is 5 m, the roundtrip delay between the dish and the feed as about $30~ns$ around which these two delay spectrum starts to deviate.
+At delays $\> 50nS$ the dish reflections starts to dominate over the reflections from the feed structure and the two delay spectrum deviates from each other.
+
+\subsection{\textbf{Measurement bandwidth and window function}}
 Estimation of the delay spectrum by taking the Fourier transform of the measured return loss is sensitive to the bandwidth of measurements.
@@
 \end{figure}
-%\subsubsection{\textbf{Delay spectrum of subbands}} 
-%The red shifted 21cm power spectrum measurements could be divided into sub-bands around multiple frequencies corresponding to various redshifts.
-Assuming that the power spectrum evolved over the redshift range $\Delta z \>0.5$ (Zaldarriaga 2004, ) corresponding to a $5~MHz$ band width at $150~MHz$.
 
-\subsubsection{\textbf{Effect of dish reflections}}
-Measurement equations shows the effects of multiple reflections of the sky signal between the feed and the dish.
-Any other reflections off the feed structure and/or any other part of the dish-feed assembly would appear at arbitrary delays.
-The estimated delay spectrum of the instrument is collectively contributed by all the reflections.
-We measure the return loss of the feed alone keeping it on the ground facing the sky shown in the Figure \ref{fig:all_RL}.
-Delay spectrum estimated from this measurement provides the lowest limit of the delay spectrum of the instrument considering there is no multiple reflections in between the feed and the dish.
- Any additional reflections also contributes to the measured return loss and thus contributed to the delay spectrum at various delays.
-Figure \ref{fig:delay_spectrum} shows the delay spectrum of the feed while it is kept upside down on the ground in green, as well as that of a HERA antenna with the feed suspended at the focal plane in blue.
-At lower delays, the reflections are dominated by the feed structure.
-Therefore, the delay spectrum in both the cases follow each other.
-Since the distance between the feed and the dish is 5 m, the roundtrip delay between the dish and the feed as about $30~ns$ around which these two delay spectrum starts to deviate.
-At delays $\> 50nS$ the dish reflections starts to dominate over the reflections from the feed structure and the two delay spectrum deviates from each other.
-%\subsubsection{Effect of feed height on delay spectrum estimation}
-\subsubsection{\textbf{Effect of multiple reflection between the feed and the backend.}}
+\subsection{\textbf{Multiple reflection between the feed and the backend.}}
 Multiple reflections of the sky signal between the feed and the dish broadens the delay response of the instrument resulting in spill over of the smooth foreground power sky at higher delays.
@@
 
-%\begin{figure}
-%\centering
-%\includegraphics[width=\linewidth]{plots/VNA_RL.png}
-%\caption{Magnitude and phase of the combined effects of the return loss at the VNA input alone with the cable resistive loss as computed from the return loss measurement of the open load at the feed input of the cable.
-This is consistent with the specifications of the RF connectors which is commonly used at low frequencies }
-%\label{fig:window}
-%\end{figure}
-
 While measuring the return loss of the dish-feed assembly, the signal transmitted by the VNA is reflected first off the feed.
@@
 \end{figure}
-%
-%\subsubsection{Effect of antenna beam pattern and feed return loss on delay spectrum estimation}
-%The return loss $\Gamma_{f}$ determines the amount of power coupled to the system via the feed.
-Additionally, with each reflection, the power coupled to the system reduces by a factor of $\Gamma_{f}^{2}$.
-Since the reflected signal results in a system response at a higher delay, multiple reflections of the signal off the feed and the dish would result in an exponential envelope in the delay spectrum.
-The return loss of power results from the antenna impedance mismatch with free space as well as the transmission line.
-The complex antenna impedance is shown in Figure \ref{fig:feed_impedance}.
-%\begin{figure}
-%\centering
-%\includegraphics[width=\linewidth]{plots/Feed_impedance.png}
-%\caption{Complex antenna impedance of the HERA feed element.} %Some indication of which line is which on the plot would be really helpful here.
-%\label{fig:feed_impedance}
-%\end{figure} 
-%
-%While the antenna beam pattern, $A_{f}$, is a smooth function of frequency and should have its imprint confined to lower delays, the return loss, $\Gamma_{f}$, broadens the delay spectrum.
-However, a smaller return loss will result in a vertical shift of the delay spectrum at lower values and, therefore, can make the higher order reflections insignificant.
-Given the antenna impedance and the 50 Ohm transmission line, the measurements are done using a passive balun with a 2:1 impedance ratio, providing a net return loss of power between the sky, the antenna, and the transmission line shown in Figure \ref{fig:freq}.
-This provides the maximum impedance matching.
-\\
-%\subsubsection{Effect of frequency bandwidth on delay spectrum estimation}
-%The estimation of the delay spectrum by taking the Fourier transform of the measured return loss is sensitive to the frequency bandwidth of operation.
-Since the measurements are done in the spectral domain, a measurement between two frequencies is analogous to windowing the frequency domain data by a square window function.
-In the delay domain, the Fourier transform of this would result in multiple side lobes at higher delays.
-Therefore, appropriate windowing of the data is necessary prior to taking the Fourier transform of the measured data.
-Figure \ref{fig:window} shows the delay spectrum estimated from the measured data using a square window as well as a Blackman Harris window.
-Windowing prior to Fourier transforming the data significantly reduces the system response at higher delays.
-%\begin{figure}
-%\centering
-%\includegraphics[width=\linewidth]{plots/window.png}
-%\caption{The affect of a finite bandwidth on the estimation of the delay spectrum: The blue line shows the delay spectrum of the HERA element computed from the measured data, which is band limited between 100 to 200MHz.
-The green line shows the delay spectrum estimated from the same data set after multiplying the data by a Blackman Harris window.
-The delay spectrum of the windowed data set shows a significant reduction in the instrument response at higher delays.}
-%\label{fig:window}
-%\end{figure} 
-%\subsubsection{Effect of the dish and feed on the delay spectrum estimation}
-%The measurement equations show the effects of multiple reflections of the sky signal between the feed and the dish.
-Any other reflections off the feed structure and/or any other part of the dish-feed assembly would appear at arbitrary delays.
-The estimated delay spectrum of the instrument is collectively contributed to by all the reflections.
-We measure the return loss of the feed alone, keeping it on the ground facing the sky (Figure \ref{fig:freq}).
-The delay spectrum estimated from this measurement provides the lowest limit of the delay spectrum of the instrument, considering there are not multiple reflections between the feed and the dish.
- %Any additional reflections also contribute to the measured return loss and, thus, the delay spectrum at various delays.
-Figure \ref{fig:delay_spectrum} shows the delay spectrum of the feed while it is kept upside down on the ground (in green), as well as that of a HERA antenna with the feed suspended at the focal plane (in blue).
-The red line shows the delay spectrum of the PAPER antenna for comparison with the HERA element.
-%\subsubsection{Effect of feed height on delay spectrum estimation}
-%\subsubsection{\textbf{Performance Comparison: HERA vs. PAPER}}
-%While PAPER has established the, to date, most stringent upper limit on the 21cm power spectrum measurement, the need to increase the measurement sensitivity called for increased collecting area per PAPER antenna.
-This has driven the parabolic reflector antenna design of the PAPER successor, HERA, where essentially the PAPER antenna, with minor modifications of the ground plane-side plane assembly, works as the feed and, thus, in combination with the dish, yields a larger collecting area per element.
-Figure \ref{fig:freq} shows the return loss measurement for the PAPER antenna, and Figure \ref{fig:delay_spectrum} shows the corresponding delay spectrum (red line).
-The HERA feed element shows an improved delay response compared to the PAPER element across all delays $>50~ns$, with marginal improvement at delays $<50~ns$.
-The delay response of the HERA element degrades marginally as the feed is suspended over the dish due to multiple reflections between the feed and the dish.
-The majority of structure in the response at lower delays is due to the feed and its supporting structure, evidenced by those features common to all three measurements.
-At the lower delays, the structures in the delay response remain unaltered even with the variation of the feed height relative to the dish vertex.
-Essentially these structures set lower limits on the $k_{||}$ values that could be probed, and since redshift $z$ maps to frequency (and, thus, $k_{||}$), any redshift above the instrument footprint could likewise be probed.
-%Check for accuracy....
 
-\subsubsection{\textbf{Comparison with simulations}}
+\section{\textbf{Effect of instrument delay spectrum on 21cm power spectrum measurements}}
+
 \begin{itemize}
@@
 \textbf{Comparison with electromagnetic simulation:}\\
-%\begin{figure}
-%\centering
-%\includegraphics[width=\linewidth]{plots/Feed_impedance.png}
-%\caption{Complex antenna impedance of the HERA feed element.}
-%\label{fig:feed_impedance}
-% d\end{figure} 
-The simultated and measureded return loss of the feed as well as the HERA element is shown in figure \ref{meas_sim_RL_feed} and figure \ref{meas_sim_RL_HERA}.
-\begin{figure}[ht]
-\begin{minipage}[b]{\linewidth}
-\centering
-\includegraphics[angle=0, width=\linewidth]{plots/feed_meas_sim_mag.png}
-\end{minipage}
-\vspace{0.1cm}
-\begin{minipage}[b]{\linewidth}
-\centering
-\includegraphics[angle=0, width=\linewidth]{plots/feed_meas_sim_ph.png}
-\end{minipage}
-\caption{Magnitude and phase of the return loss of the feed as simulated and measured.
-While both the measurement and the simulation shows similar resonance around $120~MHz$, the simulation shows a better matching to a 50 Ohm transmission line compared to the measurements.
-The measurement also has some small scale fluctuation due to multiple reflection of the signal at the VNA input.
-}
-\label{meas_sim_RL_feed}
-\end{figure}
-
-\begin{figure}[ht]
-\begin{minipage}[b]{\linewidth}
-\centering
-\includegraphics[angle=0, width=\linewidth]{plots/HERA_meas_sim_mag.png}
-\end{minipage}
-\vspace{0.1cm}
-\begin{minipage}[b]{\linewidth}
-\centering
-\includegraphics[angle=0, width=\linewidth]{plots/HERA_meas_sim_ph.png}
-\end{minipage}
-\caption{Magnitude and phase of the return loss of the HERA element as simulated and measured.
-In this case, both measurement and simulation shows similar level of return loss across the band with marginally better return loss at the high frequency end of the band.
-}
-\label{meas_sim_RL_HERA}
-\end{figure}
 
@@
 %\bibliography{biblio}{}
-\bibliography{Reference}
+\bibliography{Reference}{}
 \bibliographystyle{apj}

### 2016-06-30 DishReflectometry/Paper1_v2.tex
Addend the introduction of OQE formalism.

@@
 
-\begin{itemize}
-\item 
-\textbf{Comparison with electromagnetic simulation:}\\
-
-The delay spectrum estimated from the simulated and measured return loss is shown in the figure \ref{fig:sim_em}.
-The two delay spectrum are in good agreement with each other upto around $60~ns$ up to which the structures in the delay domain are mostly caused due to signal reflections in the feed structure.
+21cm power spectrum measurements are limited by challenges posed by the low frequency radio foreground that is order of magnitude brighter than the expected power spectrum amplitude.
+While PAPER has established the till date the most stringent upper limit on the 21cm power spectrum measurement, the need for increased sensitivity called for increased collecting area per PAPER element.
+This has driven to the parabolic reflector antenna based design of the PAPER successor HERA where essentially the PAPER antenna with minor modification of the ground plane-side plane assembly works as the feed and thus having larger collecting area per element.
+Additional limitations on PAPER and its contemporaries are imposed by the spectral structure of the system response.
+Sky signal is frequency modulated by the system bandpass response.
+In delay spectrum technique of 21cm power spectrum estimation, sky signal is convolved with the system response in the delay domain.
+In this process of convolution, the frequency dependent system response with rapid frequency variation results in spreading of the smooth spectrum foreground of the sky signal to the delays in which EoR power spectrum is to be estimated.
+This essentially limits the capacity of any experiment to probe the smaller spatial scales of fluctuations.
+\\
+	In a related series of papers, the spatial scales of fluctuation $(k_||)$ HERA element delay response has been studied via electromagnetic simulation (deBoer et al 2016) as well as via time domain simulation (Ewall-wice et al 2016).
+Figure \ref{fig:sim_em} and \ref{fig:sim_pk} shows the measurement presented this paper in comparison with the simulations.
+Simulations and measurements are in good agreement with each other upto around $60~ns$ up to which the structures in the delay domain are mostly caused due to signal reflections in the feed structure.
 Since the simulated return loss shows a better match of the antenna to the 50 Ohm transmission line.
@@
 The work is currently under progress to improve the feed return loss at least by  $10dB$ (Eloy et al 2016 in prep?).
-Beyond $60~nS$ other multiple reflections manifests themselves at higher delays and the delay spectrum of the measurement and simulations begin to deviate from each other.
-
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{plots/delay_sim_meas.png}
-\caption{Comparison between delay spectrum of HERA element estimated from the electromagnetic simulation of the feed return loss (dave deBoer 2016) and measurements by a vector network analyser.}
-\label{fig:sim_em}
-\end{figure}
-
-\item
-\textbf{Comparison with time domain simulation: }\\
-In a related series of papers, (Ewall-Wice et al 2016) has shown the simulated power kernel of the HERA element which considers the electromagnetic simulations of the HERA feed and multiple reflection in between the dish and the feed vertex.
-Our measurements, in comparison to the simulations, shows a much complex structure in the delay spectrum.
-This results from various multiple reflections within and around the feed as well as in the cable connecting the feed output to the vector network analyser.
-Once again, keeping all other reflections within the system unchanged, a simple $~10dB$ improvement in the feed impedance match could match the simulations with measurements.
-
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{plots/delay_power.png}
-\caption{Comparison between delay spectrum of HERA element estimated from the simulation of the multiple reflections between the feed and the dish and reflectometry measurements by a vector network analyser.}
-\label{fig:sim_pk}
-\end{figure}
-
-\item
-\textbf{Comparison with foreground simulation}
-In a related series of papers, (Thyagarajan et al 2016) has presented the detailed sensitivity calculations of HERA is using a comprehensive foreground as well as model for EoR power spectrum for various simulated antenna element response.
+Beyond $60~nS$ other multiple reflections manifests themselves at higher delays and the delay spectrum of the measurement and simulations begin to deviate from each other.\\
+Thygarajan et al 2016) has presented the detailed sensitivity calculations of HERA is using a comprehensive foreground model as well as model for EoR power spectrum for various simulated antenna element response.
 The theoretical limits for the level of signal attenuation required in order to reduce the foreground contaminations at the delay modes significant for power spectrum measurements are shown for three different lower limits of $k_\parallel$ values.
@@
 The response is computed for the redshift of $z=8.47$ at frequency $150~MHz$.
-The yellow and cyan curves shows the improvement on the instrument delay spectrum that could be achieved by improving the feed return loss by $20, 30db$ respectively.
-With a $30dB$ improvement in return loss, for power spectrum at $k_{\parallel}>0.15$, the foreground contaminations at higher delays could potentially be limited to only a few delay modes.
-Achieving a $30~dB$ improvement at the feed is extremely challenging.
-However, since multiple reflections results in multiplication of the feed return loss as well as the input return loss at the backend, a $20~dB$ improvement in the feed and another $~20dB$ improvement in the mismatch between the cable and the backend input could establish the same.
-
+\\
 \begin{figure}
@@
 
-\end{itemize}
+In the following section, we further investigate the limits of required instrumental delay response from what is established by Thyagarajan et al 2016.
+Combining with the  inverse covariance weighting formalism of foreground suppression we derive a new limit for the instrument delay response for power spectrum measurements.
+With inverse covariance weighting a foreground suppression of about 30dB could be achieved that results in room for substantial performance degradation and yet a successful measurement of 21~cm power spectrum.
+Our measurements, evaluated in the light of these limits shows that the HERA is not limited by either its systematics.
+With only delay spectrum technique, it is capable of detecting the EoR power spectrum for the $k_{\parallel}$ modes as low as $k_{\parallel}>=0.2$.
+If combined with the inverse covariance weighting formalism of foreground suppression, the instrument performs well below the limits of foreground suppression.
 
-\subsubsection{\textbf{Comparison of performance of HERA with PAPER}}
-While PAPER has established the till date the most stringent upper limit on the 21cm power spectrum measurement, the need to increase the measurement sensitivity called for increased collecting area per PAPER antenna.
-This has driven to the parabolic reflector antenna based design of the PAPER successor HERA where essentially the PAPER antenna with minor modification of the ground plane-side plane assembly works as the feed and thus having larger collecting area per element.
-Figure \ref{fig:freq} shows the return loss measurement of power of the PAPER antenna and figure \ref{fig:delay_spectrum} shows (red line) the corresponding delay spectrum.
-The feed element shows improved delay response compared to the PAPER element across all delays $>50~ns$ with marginal improvement at delays $<50~ns$.
-The delay response of the HERA element degrades marginally as the feed is suspended over the dish due to multiple reflections between the feed and the dish.
-It is evident that majority of the response at lower delays are contributed due to the feed and its supporting structure at lower delays which is somewhat common to all three measurements.
-At the lower delays, the structures in the delay response remains unaltered even with the variation of the feed height relative to the dish vertex.
-It is essentially these structures set lower limits on the $k_{||}$ that could be probed and any redshift $z$ above the instrument footprint.
-
-%\section{\textbf{Effect of instrument delay spectrum on 21cm power spectrum measurements} }
-%The delay response of the instrument is dependent on the band chosen for the Fourier transform.
-%The measurement bandwidth effects the amplitude and phase of the delay spectrum. Fourier transforms taken over wider bandwidth
-%become dominated by the feed sidelobes outside the operating band, making the resultant delay profiles less relevant
-%for the power spectrum performance of the HERA instrument.  Conversely, when performing Fourier transforms over much 
-%narrow bands (the windowed $20MHz$ bands typical of PAPER analysis), the width of the resulting delay profile
-%becomes dominated by sidelobes of low delay emission interacting with the narrow bandwidth kernel.  
-%Although this may appear to be a relevant performance metric for PAPER power spectrum analysis, such an analysis typically pre-filters out low-delay emission using wide bandwidths precisely to avoid sidelobes from low-delay emission.
-Hence, the most relevant delay-spectrum performance profile is that taken using the $100-200MHz$ band.
-\textbf{In the $100-200MHz$ delay profile, we see a delay response of $-25dB$ at $60ns$, which slopes down to $-60dB$ at $\sim120ns$.
-WRITE AGAIN}
-
-%Figure \ref{fig:elevator} is again a delay plot of the return loss at four different feed suspension heights. 
-%We use the PAPER bandwidth and note
-%that the measurements are near identical at low delays, implying that low delay reflections are caused primarily by reflections within the feed cage. 
-%However, at higher delays we notice discrepancies between the different heights.
-%In addition, Figure \ref{fig:outofthedish} presents measurements taken of the feed only.away from the dish. Echosorb is placed under the feed for some of the
-%measurements, with the expectation that it will prevent any reflections off the
-%ground.
-% Measurements are also taken of the feed inside its metal cage in various configurations. It is shown that the feed performs best without the cage and with the absorber. 
-%All these measurements are suggestive of the  fact that the feed-cage assembly itself is responsible for a significant portion of the structure up to $60ns$ and
-%that the cylindrical cage may be contributing up to $20ns$ to the width of the delay profile. 
-%We note that this depends stronglyon its coupling to structures around it. 
-%Structure beyond $60ns$ appears to scale with the height of the feed above the dish.
+would  for power spectrum measurements, especially at smaller spatial scales of fluctuation i.e lower values of $k_{\parallel}$.
 

### 2016-06-30 DishReflectometry/GB_reflectometry_part2/Simulation/plot_simulation.py
dding the directory that has not been added before. This contains all the scripts for comparing the simulations.

@@ -127,8 +127,9 @@ for filename in sys.argv[1:]:
         #plt.show()
         #plt.plot(fq_H,pwr(d2_H),linewidth=2.5,label='return loss feed (measured)' )
         
-        #plt.plot(np.fft.fftshift(tau), 10.0*np.log10(np.fft.fftshift(np.abs(_d))), linewidth=2.5, label= 'Feed Only (Simulation)')
-        plt.plot(np.fft.fftshift(tau1), 10.0*np.log10(np.fft.fftshift(np.abs(_d2H))), linewidth=2.5, color = '#ff8c00' ,  label= 'HERA (EM Simulation)')
+        #plt.plot(np.fft.fftshift(tau), 10.0*np.log10(np.fft.fftshift(np.abs(_d2))), linewidth=2.5, color = '#ff8c00', label= 'EM Simulation')
+        #plt.plot(1000*delay, delay_spectrum, linewidth=2.5, color = 'black', label='Time domain simulation')
+        plt.plot(np.fft.fftshift(tau1), 10.0*np.log10(np.fft.fftshift(np.abs(_d2H))), linewidth=2.5, color = 'blue' ,  label= 'Measurement')
         
         
         #plt.plot(np.fft.fftshift(tau), 0.5*pwr(np.fft.fftshift(np.abs(_d2))), linewidth=2.5, label='HERA feed')
@@ -141,7 +142,7 @@ for filename in sys.argv[1:]:
     	
         
         
-        #plt.plot(1000*delay, delay_spectrum, linewidth=2.5, label='Simulated power kernel of HERA element')
+        #plt.plot(1000*delay, delay_spectrum, linewidth=2.5, label='Time domain simulation')
         
         #_dww_rb = np.fft.ifft((d2_rb)**2*window2) / window2.mean() # compensate for window amplitude
     
@@ -201,11 +202,13 @@ for filename in sys.argv[1:]:
         ddave = npzdata2['dhera']
         #plt.plot(tau3, -ddave,linewidth=1.5 , label='Dave simulation')
         
-        d_t_10 =1+d_feed/30 # Transmission coefficient
-        d1_H = ((d_H/30-d_feed/30)*(d_feed/30)/d_t_H ) # Reflections corrected to produce system bandpass in the receiving mode 
+        d_t_10 =1+d_feed/10 # Transmission coefficient
[…]

### 2016-09-06 DishReflectometry/Paper1_v2.tex
Older changes, all of which are confusing

@@
 
-Since it was first proposed in ~\citep{Shaver_et_al1999} measuring 21~cm
+Since first proposed in ~\citep{Shaver_et_al1999} measuring 21~cm
 emission from neutral hydrogen in our early universe has gained attention as a

### 2016-09-06 DishReflectometry/Paper1_v3.tex
renamed the paper to avoid marging conflict

--- 2016-06-30 DishReflectometry/Paper1_v2.tex
@@
 \begin{equation}
-  P(k_\perp,k_\parallel) = (|\tilde V(\vec b, \tau)|^{2} \left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2 ,
+  P_{21}(k_\perp,k_\parallel) = (|\tilde V(\vec b, \tau)|^{2} \left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2 ,
 \label{eq:delay-power-spectrum}
@@
 \\
+
 \section{\textbf{Reflectometry measurements}}
@@
 \vspace{1.0 em}
-\caption{The HERA feed consists of a pair of crossed-dipoles ove xxx mt diameter backplane made of wire mesh.
-The backplane is surrounded by xxx m wire mesh around the edge resulting in encasing the crossed-dipoles in a cylindrical cage.}
+\caption{The HERA feed consists of a pair of crossed-dipoles over 1.72 mt diameter backplane made of wire mesh.
+The backplane is surrounded by 0.36 m wide wire mesh around the edge resulting in encasing the crossed-dipoles in a cylindrical cage.}
 \label{fig:herafeed}
@@
 
-Return loss measurements are similar to auto correlation measurement from a single HERA element.
+\section{Results}
+Return loss measurements yields the instrument pass band response that would manifest in autocorrelation data of a single HERA element.
 Upon our assumption that two adjacent antenna elements have identical design parameters and electrical properties, this power is also a measure of the cross power or the visibility $\vis (\vec b, \nu)$ between the two antennas with a normalisation factor of $2$.
 
-The simultated and measureded return loss of the feed as well as the HERA element is shown in figure \ref{meas_sim_RL_feed} and figure \ref{meas_sim_RL_HERA}.
+The simultated and measureded return loss of the feed as well as the HERA element is shown in figure \ref{RL_mag_feed} and figure \ref{RL_mag_dish}.
+The measurements deviates from the simulated performance in one major aspect.
+While the return loss of the simulated structure shows two resonant peaks around 120 and $160~MHz$, the feed resonance occur at slightly higher frequencies.
+While the simulated response shows very wide resonant peaks, as expected from these dipole structures, the measured return loss of the feed has a narrow peak around its low frequency resonance.
+This feature somewhat dominates the fall off rate in the delay response of the system bandpass.
+The delay response of the feed alone is shown in figure \ref{ds_feed_on_dish_trans} along with the delay response of a HERA element in transmission mode.
+In the following sections, we compute the response of the HERA element in the receiving mode.
 \begin{figure}[ht]
@@
 \centering
-\includegraphics[angle=0, width=\linewidth]{plots/feed_meas_sim_mag.png}
+\includegraphics[angle=0, width=\linewidth]{/Users/Nipanjana/WORKAREA1/DATA_Area/Project_HERA/DishPapers/DishReflectometry/GB_reflectometry_part3/plot/RL_mag_feed.png}
 \end{minipage}
@@
 }
-\label{meas_sim_RL_feed}
+\label{RL_mag_feed}
 \end{figure}
@@
 \centering
-\includegraphics[angle=0, width=\linewidth]{plots/HERA_meas_sim_mag.png}
+\includegraphics[angle=0, width=\linewidth]{/Users/Nipanjana/WORKAREA1/DATA_Area/Project_HERA/DishPapers/DishReflectometry/GB_reflectometry_part3/plot/RL_mag_dish.png}
 \end{minipage}
@@
 }
-\label{meas_sim_RL_HERA}
+\label{RL_mag_dish}
 \end{figure}
 
-\section{Results}
 \begin{figure}       
 \centering
-\includegraphics[width=\linewidth]{plots/H_dish_feed.png}
-\caption{Delay spectrum of the HERA element (green) the HERA feed (blue) estimated by taking the Fourier transform of the measured return loss of power at the feed output.
-The feed, when suspended on the dish results in a more complex return loss and corresponding delay response is shown in the figure.
-After correcting the measurements from the transmission mode to reception mode by equation \ref{eq:power_ratio} the delay spectrum in the receiving mode is estimated (red).
+\includegraphics[width=\linewidth]{/Users/Nipanjana/WORKAREA1/DATA_Area/Project_HERA/DishPapers/DishReflectometry/GB_reflectometry_part3/plot/ds_feed_on_dish_trans_recp.png}
+\caption{Delay spectrum of the HERA feed (brown) estimated by taking the Fourier transform of the measured return loss of power at the feed output.
+The feed, when suspended on the dish results in a more complex return loss as shown in figure \ref{RL_mag_dish} and corresponding delay response is shown here in black.
+This figure shows the delay spectrum of the instrument in the as estimated from direct measurements of the return loss i.e, in the transmission mode of the antenna.
 }
-\label{fig:delay_spectrum}
+\label{ds_feed_on_dish_trans}
 \end{figure}
 
-Figure \ref{meas_sim_RL_HERA} shows the return loss measured between $100$ to
-$200MHz$ when the feed is suspended at the focal plane of the parabolic dish which is at $5m$ from the dish vertex.
-This measurement is first correc ted to map the response of the antenna from transmitting mode to receiving mode via equation \ref{zero_delay_correction}.
+Figure \ref{RL_mag_dish} shows the measured return loss when the feed is suspended at the focal plane of the parabolic dish which is at $5m$ from the dish vertex.
+The measured return loss is much more complex than what is found from the simulation.
+The delay spectrum in the transmission mode is shown in \ref{ds_feed_on_dish_trans}.
+To estimate the delay spectrum of the dish-feed assembly i.e one single HERA element, this measurement is first corrected to map the response of the antenna from transmitting mode to receiving mode via equation \ref{zero_delay_correction}.
 The corrected measurement is then Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{corrected_response}.
 Measurement bandwidth is kept much larger than the bandwidth of operation to achieve higher delay resolution.
-A number of systematic effects as well as mathematical artefacts that are critical to this measurements and their effects on the corresponding estimation of the delay spectrum are taken in to account in determination of the delay spectrum and described below.
+A number of systematic effects as well as mathematical artfacts that are critical to this measurements and their effects on the corresponding estimation of the delay spectrum are taken in to account in determination of the delay spectrum and described below.
 
@@
 
-\subsection{\textbf{Antenna beam pattern and feed return loss}}
-The return loss $\Gamma_{f}$ determines the amount of power coupled to the system via the feed antenna.
+%\subsection{\textbf{Antenna beam pattern and feed return loss}}
+%The return loss $\Gamma_{f}$ determines the amount of power coupled to the system via the feed antenna.
 Additionally, with each reflections, the power coupled to the system reduces by a factor of $\Gamma_{f}^{2}$.
@@
 During observation, each HERA element is connected to an active balun similar to the ones used in the PAPER antenna (need reference) which provides greater than 10dB return loss of power at the feed output.These baluns are under further design improvements aiming at 10 to 20dB better imepedance match between the feed and the balun than the measurements presented here.
-Our measurement is done using a vector network analyser for which the active balun has been replaced by a passive balun.Given the antenna impedance and the 50 Ohm transmission line the measurements are done using the passive balun with a 2:1 impedance ratio providing a net return loss of power between the sky, the antenna and the transmission line shown in the figure \ref{meas_sim_RL_feed}.
+Our measurement is done using a vector network analyser for which the active balun has been replaced by a passive balun.Given the antenna impedance and the 50 Ohm transmission line the measurements are done using the passive balun with a 4:1 impedance ratio providing a net return loss of power between the sky, the antenna and the transmission line shown in the figure \ref{RL_feed_mag}.
 This measurements are conservative estimate  for both $\Gamma_{f}$ and $s_{11}$.
@@
 The estimated delay spectrum of the instrument is collectively contributed by all the reflections.
-We measure the return loss of the feed alone keeping it on the ground facing the sky shown in the Figure \ref{meas_sim_RL_feed}.
-Delay spectrum estimated from this measurement provides the lowest limit of the delay spectrum of the instrument considering there is no multiple reflections in between the feed and the dish.
- Any additional reflections also contributes to the measured return loss and thus contributed to the delay spectrum at various delays.
-Figure \ref{fig:delay_spectrum} shows the delay spectrum of the feed while it is kept upside down on the ground in green, as well as that of a HERA antenna with the feed suspended at the focal plane in blue.
-At lower delays, the reflections are dominated by the feed structure.
+Delay spectrum estimated from the return loss measurement of the feed alone,  provides the lowest limit of the delay spectrum of the instrument considering there is no multiple reflections in between the feed and the dish.
+From figure \ref{ds_feed_on_dish_trans}, at lower delays, the reflections are dominated by the feed structure.
 Therefore, the delay spectrum in both the cases follow each other.
@@
 \centering
-\includegraphics[width=\linewidth]{plots/window_effect.png}
+\includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/ds_window.png}
 \caption{Effect of finite bandwidth on estimation of delay spectrum: Blue line shows the delay spectrum of the HERA element computed from the measured data which is band limited between 100 to 200MHz.
@@
 
-While measuring the return loss of the dish-feed assembly, the signal transmitted by the VNA is reflected first off the feed.
+%While measuring the return loss of the dish-feed assembly, the signal transmitted by the VNA is reflected first off the feed.
 This is represented by $\Gamma_{f}$ in equation \ref{eq:power_ratio}.
@@
 %
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{plots/delay_spectrum_100_200_BH.png}
-\caption{Delay spectrum of the HERA element, the PAPER element, and the HERA feed estimated by taking the Fourier transform of the measured return loss of power at the feed output.
+%\begin{figure}[ht]
+%\centering
+%\includegraphics[width=\linewidth]{plots/delay_spectrum_100_200_BH.png}
+%\caption{Delay spectrum of the HERA element, the PAPER element, and the HERA feed estimated by taking the Fourier transform of the measured return loss of power at the feed output.
 The HERA feed design is driven by the PAPER element with an improved response at all delays.
@@
 Should be ns not GHz!!!!
-\label{fig:delay_spectrum}
-\end{figure}
+%\label{fig:delay_spectrum}
+%\end{figure}
 
@@
 Beyond $60~nS$ other multiple reflections manifests themselves at higher delays and the delay spectrum of the measurement and simulations begin to deviate from each other.\\
-Thygarajan et al 2016) has presented the detailed sensitivity calculations of HERA is using a comprehensive foreground model as well as model for EoR power spectrum for various simulated antenna element response.
-The theoretical limits for the level of signal attenuation required in order to reduce the foreground contaminations at the delay modes significant for power spectrum measurements are shown for three different lower limits of $k_\parallel$ values.
-The requirements for the reduced instrument response at higher delays are more stringent for the detection of lower $k_\parallel$ modes.
-The response is computed for the redshift of $z=8.47$ at frequency $150~MHz$.
+Thyagarajan et al 2016) has presented the detailed sensitivity calculations of HERA is using a comprehensive foreground model as well as model for EoR power spectrum for various simulated antenna element response.
+The sensitivity is quantified as a ratio of EoR signal power to the foreground power at various $\bold k_{\parallel}$ mode i.e at various delays.
+The theoretical limits for the level of foreground attenuation required relative to the EoR signal in order to reduce the foreground contaminations at the delay modes significant for power spectrum measurements are shown for three different lower limits of $k_\parallel$ values.
+The response is computed for the redshift of $z=8.47$ at frequency $150~MHz$ over a bandwidth of $10~MHz$.
+This simulation shows the effect of chromatic antenna response and how that contaminates the delay modes beyond the horizon limit.
+Thus, this establishes a very stringent limits of required foreground attenuation relative to EoR signal which demands almost an ideal system performance.
 \\
+%As shown in section (), multiple reflection in the antenna system generates multiple copies of the sky signal and thus results in additional foreground contaminations in the delay modes where EOR power spectrum is measurable in case of no reflections.
+Reflectometry measurements shows the relative strength with which the multiple copies of the signal shows up at various delays.
+
 \begin{figure}
 \centering
-\includegraphics[width=\linewidth]{plots/meas_forground.png}
+\includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/HERA_ds_fg_sim.png}
 \caption{Delay spectrum of HERA element estimated from the reflectometry measurements by a vector network analyser compared to the limits of foreground simulation (Thyagarajan et al).}
-\label{fig:sim_fg}
+\label{fig:sim_fg_Nithya}
 \end{figure}
 
-In the following section, we further investigate the limits of required instrumental delay response from what is established by Thyagarajan et al 2016.
-Combining with the  inverse covariance weighting formalism of foreground suppression we derive a new limit for the instrument delay response for power spectrum measurements.
-With inverse covariance weighting a foreground suppression of about 30dB could be achieved that results in room for substantial performance degradation and yet a successful measurement of 21~cm power spectrum.
-Our measurements, evaluated in the light of these limits shows that the HERA is not limited by either its systematics.
-With only delay spectrum technique, it is capable of detecting the EoR power spectrum for the $k_{\parallel}$ modes as low as $k_{\parallel}>=0.2$.
-If combined with the inverse covariance weighting formalism of foreground suppression, the instrument performs well below the limits of foreground suppression.
+The HERA analysis pipeline for power spectrum estimation exploits the inverse covariance weighting technique to reduce the foreground contribution to the measured visibility data.
+In the light of this analysis technique we further investigate the limits of required instrumental delay response from what is established by foreground simulation in Thyagarajan et al 2016.
+In the following section we briefly describe the power spectrum estimation technique used in HERA analysis and the inverse covariance weighting.
+In the next section we evaluate the estimated instrument delay response performance in the context of covariance weighting.
 
-would  for power spectrum measurements, especially at smaller spatial scales of fluctuation i.e lower values of $k_{\parallel}$.
+\subsection{Power spectrum estimation:}
+HERA power spectrum estimation is done using the Optimal Quadratic Estimator (OQE) formalism that has been outlined in extensive detail in (Liu and Tegmark 2011), (Dillon et al 2013), (Liu et al 2014a,2014b), (Trott et al 2016), (Ali et al 2015).
+We briefly  describe the OQE formalism here.\\
+HERA instrument aims at measuring the redshifted 21~cm power spectrum $P_{21}(k_\perp,k_\parallel)$, conventionally written as, 
+\begin{equation}
+\langle  \tilde T_{b}(\bold k) \tilde T_{b}^{*}(\bold k^{'}) \rangle = (2\pi)^{3} \delta (\bold k - \bold k^{'})P_{21}(k_\perp,k_\parallel)
+\end{equation}
+
+where $\langle  \tilde T_{b}(\bold k) \tilde T_{b}^{*}(\bold k^{'}) \rangle $ is the correlation function of the three dimensional spatial Fourier transform of the sky brightness temperature distribution $ \tilde T_{b}(\bold k)$, and $\delta$ is the Dirac delta function.
+While both $P_{21}(k_\perp,k_\parallel), \tilde T_{b}({\bold k})$ is continuous, the power spectrum could only be estimated at discrete values of $\bold k$.
+Observation frequency and bandwidth are so chosen that the power spectrum could e approximated as a constant and a piecewise continuous function of $\bold k$  which correspond to a thin shell in $\bold k$ space.
+This corresponds to the $k_{perp}$, $k_{parallel}$  values $a <k_{\perp} < a+1$, $b <k_{\parallel} < b+1$ where the indices a, b can assume M, N different values.
+We denote the power spectrum as $\hat p_{\alpha}$ where alpha represents a particular $(M,N)$ value.
+Our analysis begins with a data vector $\bold x$.
+$\bold x$ is the list of visibilities measured at a given frequency over a certain bandwidth i.e for a given $k_{\parallel}$ mode for a given $\Delta \bold k $.
+The first estimate of power spectrum is written as,
+
+\begin{equation}
+\hat q_{\alpha} = \bold x^{T} E^{\alpha} \bold x  - b^{\alpha}
+\end{equation}
+
+where $b_{\alpha}$ is a constant that assumes different values for each $\bold k$ and represents any additive noise power spectrum or residual foreground contamination to power spectrum estimate.
+$b_{\alpha}$ could be eliminated from the estimate by cross correlating two visibility data sets at two different times.
+$E^{\alpha}$ is a symmetric matrix operation denoting the Fourier transform of the data, binning, and foreground reduction.
+Various binning and foreground reduction technique would result in various different form of $E^{\alpha}$ resulting in estimates of $\hat p_{\alpha}$ with non identical statistics.
+A possible choice of $E^{\alpha}$ is
+\begin{equation}
+E^{\alpha} =  {1 \over 2} C^{-1} Q_{\alpha} C^{-1}
+\end{equation}
+
+where $C = \langle \bold x \bold x^{t} \rangle$ is the covariance matrix of the data vector $\bold x$.
+$Q_{\alpha} \equiv {\delta C \over \delta p_{\alpha} } $ is a matrix operator that Fourier transforms the visibilities along the frequency axis and maps them into the $\bold k$ space for every M,N values.
+Finally, the normalized estimate of the power spectrum could be written as,
+\begin{equation}
+\hat p_{\alpha} = M \hat q_{\alpha} 
+\end{equation}
+
+Since $\hat p_{\alpha}$ is a discrete estimate of the true power spectrum $p_{\alpha}$, both are related by the window function matrix $W$, 
+\begin{equation}
+\hat p_{\alpha} = W p_{\alpha}
+\end{equation}
+
+Hence, the estimated power spectrum $\hat p_{\alpha}$ for a given $k_{\perp}, k_{\parallel}$ values would have contribution for the nearby $k_{\perp}, k_{\parallel}$ values weighted by the window function.
+The wider the window function, the larger would be the contribution of the adjacent modes to the discrete power spectrum estimate.
+In general, therefore, $W$ is a non-diagonal matrix.
+Also, for a given choice of normalization matrix M, the window function W will be,
+
+\begin{equation}
+ W = MF
+\end{equation}
+
+where , 
+\begin{equation}
+ F_{\alpha\beta} = \frac {1} { 2} [C^{-1}Q_{\alpha}C^{-1}Q_{\beta}]^{T}
+\end{equation} 
+ is the Fisher matrix of the measured data.
+The choice of normalization matrix $M$ is critically important for the analysis.
+If $M = F^{-1}$, $W=I$ resulting in $\hat p_{\alpha} = p_{\alpha}$ i.e, estimated value of the power spectrum equals to the true power spectrum.\\
+ The errors on the power spectrum estimate is given by the covariance of the band power which could be computed from the measured data as,  
+\begin{eqnarray}
+ C_{\alpha} & = & \langle \hat p_{\alpha} \hat p_{\alpha}^{T} \rangle - \langle \hat p_{\alpha} \rangle \langle \hat p_{\alpha}^{T} \rangle \nonumber\\
+ 		& = & MFM^{T}
+ \end{eqnarray}
+
+ For a choice of $M = F^{-1}$, the covariance in the estimated band power is as large as $M$ resulting in highest error in estimation.
+Hence, the choice of the normalization matrix $M$ is critical in the analysis process since its precise form determines the vertical error bars in the estimate of power spectrum.
+
+\subsection{Inverse covariance weighting: revised delay spectrum limit}
+The inverse variance weighting method is a method of aggregating two or more random variable to minimize the variance in their weighted average.
+In our case, the measured visibility is contributed by EoR, foreground and instrumental noise.
+Hence, the estimate of any of the constituent signal would benefit from if the measured data is weighted by the covariance of the individual components.
+This is reflected in our choice of the matrix $E^{\alpha}$.
+$E^{\alpha} = {1 \over 2} C^{-1} Q_{\alpha} C^{-1}$ represents a weighting of the data vector $\bold x$ by inverse of its covariance.
+This results in the smallest vertical error bar in the power spectrum estimate $\hat p_{\alpha}$ (Reference Liu 2011).
+However, there no definite way to know the covariance of individual signal components prior to estimating them.
+In practice, the total covariance matrix $C$ is computed from the measured visibilities.
+It is a sum of covariances of the foreground, instrumental noise and the EoR signals.
+The highest covariance is rendered by the signal which is correlated over various frequency channels at all frequencies such as foreground.
+Hence, weighting the measured visibility by the inverse of the covariance results in order of magnitude reduction of foreground power against the EoR signal \\
+ Combining the inverse covariance weighting formalism with the foreground simulation of Thyagarajan et al 2016, we derive a new limit on required foreground attenuation with respect to the EoR signal, required for power spectrum estimation using HERA measurements.
+The foreground model of Thyagarajan et al (2015a) is adopted wherein the diffused emission is accounted for using de Oliviera-Costa et al.
+2008 and the point sources are modeled using NRAO VLA sky survey at 1.42 GHz(NVSS, Condon et al 1998) and Sydney University Molonglo Sky Survey (SUMSS; Bock et al 199;Mauch et al 2003.) at 843 MHz.
+The EoR signal model is derived from the 21cmFAST (Messinger et al 2011).
+The model parameters are kept same as what is used in Thyagarajan et al 2016 and Ewall-wice et all 2016.
+The EoR model parameters are listed below.\\
+ Virial temperature of minimum mass of dark matter halos that host ionizing sources, $T_{vir}^{min} = 2*10^4 K$, Ionising efficiency $\eta = 20$, Mean Free Path of UV photons $R_{mfp} = 15Mpc.$ For these model parameter values, the redshift of $50\%$ reionization is predicted to be at $z = 8.5$ at 150MHz.\\
+We use the reflectometry measurements, corrected for the antenna response in the receiving mode, to compute the visibilities (eq 13) for the given model of the foreground, the EoR and the system noise.
+These visibilities formed the complex data vector $\bold x$.
+We compute the covariance matrix $C$ from the simulated data.
+$\bold x$ is then multiplied by the inverse of the covariance matrix.
+This step essentially weighs down the foreground contribution to the measured data.
+Once Fourier transformed, the delay spectrum of the simulated data is constituted by linear super position of the delay spectrum of the foreground, the EoR signal.
+We again compute the EoR to foreground power ratio which is now smaller than what is estimated in Thyagarajan et al 2016 as shown in fig:\ref{fig:sim_fg_revised}.
+\begin{figure}[ht]
+\centering
+\includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/HERA_ds_fg_sim_rev.png}
+\caption{Delay spectrum of HERA element estimated from the reflectometry measurements by a vector network analyzer.
+The colored region shows the revised EoR to foreground power ratio in comparison to the measurements and the foreground simulation presented in (Thyagarajan et al 2016).}
+\label{fig:sim_fg_revised}
+\end{figure}
+This demonstrates that the performance of the HERA element performance, in conjunction with the inverse covariance method of foreground suppression, qualifies the system for its the science goal it is designed for, irrespective of its chromatic response generated due to multiple reflections in the system.
+
+%Covariance matrix $C$ is computed from the simulated visibility data.
+Next, the data vector $\bold $ that consists of the complex simulated visibilities, is weighted by the computed covariance of the data.
+%instrument delay response for power spectrum measurements.
+With inverse covariance weighting a %foreground suppression of about 30dB could be achieved that results in room for substantial %performance degradation and yet a successful measurement of 21~cm power spectrum.
+Our %measurements, evaluated in the light of these limits shows that the HERA is not limited by either its %systematics.
+With only delay spectrum technique, it is capable of detecting the EoR power spectrum %for the $k_{\parallel}$ modes as low as $k_{\parallel}>=0.2$.
+If combined with the inverse covariance %weighting formalism of foreground suppression, the instrument performs well below the limits of %foreground suppression.
+We briefly describe the inverse covariance weighting formalism below.
+%\subsection{Inverse covariance weighting}
+%The 21 cm delay spectrum estimate and thus the 21~cm power spectrum, consists of three main components, the foreground power spectrum $\hat p_{FG}$, the EoR power spectrum $\hat p_{EoR}$and the noise power spectrum of the instrument.
+%\begin{equation}
+%\hat p =  \hat p_{FG} + \hat p_{EoR}+ \hat p_{noise}
+%\end{equation}
+%In the inverse-variance weighting, two or more random variables are aggregated to minimize the variance of the weighted average.
+Hence, weighting the estimated delay spectrum with the inverse variance of the foreground reduces the foreground contaminations in the measurements.
+%would  for power spectrum measurements, especially at smaller spatial scales of fluctuation i.e lower values of $k_{\parallel}$.
 

### 2016-09-06 DishReflectometry/Paper1_v1.tex

@@
 A number of systematic effects, as well as mathematical artifacts critical to these measurements and the corresponding estimation of the delay spectrum, are taken in to account in determining the delay spectrum and are described below.
-
-\subsection{Feed effect: zero delay correction}
-%At first, the frequency domain measurement of s11 is Fourier-transformed to compute the response of the system in the delay domain.
 

### 2016-09-06 DishReflectometry/Paper1_v3.tex

@@
 \newcommand{\dfngexp}{{e^{2\pi i\nu \Delta \tau}}}
-\newcommand{\myemail}{skywalker@galaxy.far.far.away}
+%\newcommand{\myemail}{skywalker@galaxy.far.far.away}
 
@@
 
+\def\UCB{\altaffilmark{1}}
+\def\UCBtxt{\affil{\altaffilmark{1}University of California, Berkeley, nipanjana@berkeley.edu}}
+\def\ASU{\altaffilmark{2}}
+\def\ASUtxt{\affil{\altaffilmark{2}Arizona State University, School of Earth and Space Exploration, e-mail: t\_nithyanandan@asu.edu}}
+
+\def\myemail{\altaffilmark{$\dagger$}}
+\def\myemailtxt{\altaffiltext{$\dagger$}{e-mail: nipanjana@berkeley.edu}}
 \begin{document}
@@
 
-\author{Nipanjana Patra\altaffilmark{1} }
-\email{Contact author email: nipanjana@berkeley.edu}
-\author{Aaron Parsons\altaffilmark{1}, Dave DeBoer, Zaki S. Ali\altaffilmark{1}, Cherie Day\altaffilmark{1}, Carina Cheng\altaffilmark{1}}
-\author{Gilbert Hsyu\altaffilmark{2}, Tsz Kuk Leung\altaffilmark{2}}
-\altaffiltext{1}{University of California, Berkeley, nipanjana@berkeley.edu}
-\altaffiltext{2}{To be inserted}
+\author{
+Nipanjana Patra\UCB\myemail,
+Aaron~R.~Parsons\UCB,
+Nithyanandan Thyagarajan\ASU,
+David~R.~DeBoer\UCB,
+Zaki~S.~Ali\UCB,
+Cherie~K.~Day\UCB, 
+Carina Cheng\UCB,
+%Gilbert Hsyu\altaffilmark{2}, 
+%Tsz Kuk Leung\altaffilmark{2}
+}
+%\altaffiltext{2}{To be inserted}}
 
@@
 by sky noise and foregrounds four to five orders of magnitude
-brighter than the signal ~\citep{2015ApJ...801..138P}, 
+brighter than the signal, 
 sky-averaged 21~cm monopole experiments such as
 EDGES; ~\citep{Bowman_et_al2010},
-BIGHORNS; ~\citealt{XXX},
-SARAS; ~\citep{Patra_et_al2015} ,
+BIGHORNS; ~\citealt{2015PhDT........65V},
+SARAS; ~\citep{Patra_et_al2015}, \citep{Patra_et_al2013} ,
 SCIHI; ~\citep{2015PhDT........65V},
@@
 and the future Square Kilometre Array (SKA; ~\citealt{XXX})
-must
-furnish both collecting area and foreground suppression at levels significantly
+must furnish both their foreground suppression limits given their system performance at levels significantly
 beyond anything previously achieved in radio telescopes operating below 1 GHz.
@@
 contaminating spectral modes that might
-otherwise be used to measure reionization ~\citep{XXX}.  Moreover, the chromaticity of
+otherwise be used to measure reionization ~\citep{liu_et_al2014a}.  Moreover, the chromaticity of
 a telescope's response scales linearly with diameter, putting the
@@
 element separation (or telescope diameter), and what it implies for distinguishing
-foreground emission from the cosmological 21~cm signal ~\citep{XXX}.  The ``wedge'', as it is
+foreground emission from the cosmological 21~cm signal~\citep{Thyagarajan_et_al2015}.  The ``wedge'', as it is
 colloquially known, describes a linear relationship between the separation between elements
@@
 wedge pattern.  Outside of the wedge, foreground contamination drops rapidly 
-~\citep{pober_et_al2013,thargarajan_et_al2015}, provided that the spectral responses
+~\citep{pober_et_al2013},\citep{Thyagarajan_et_al2015}, provided that the spectral responses
 of antenna elements and analog electronics are sufficiently smooth\footnote{Here, we distinguish
@@
 element separation in an interferometric baseline.}.  In the promising, avoidance-based
-foreground strategy employed by PAPER ~\citep{parsons_et_al2014,ali_et_al2015}, these modes
+foreground strategy employed by PAPER ~\citep{parsons_et_al2014},\citep{Ali_et_al2015}, these modes
 may be targeted as the lowest risk path for constraining 21~cm reionization in the near term.
@@
 The efficacy of the techniques of foreground removal from the measured data critically limits the 21~cm power spectrum measurements.
-The delay transformation technique of foreground removal, introduced by  ~\cite{ParsonsBacker2009,Parsons2012}, computes the Fourier transform of the visibility measured by an interferometer and produces a spectrum, referred to as the delay spectrum hereafter, which is a function of the geometric time delay corresponding to the physical length of the baseline between two antennas.
+The delay transformation technique of foreground removal, introduced by  ~\citep{Parsons_Backer_2009},\citep{Parsons_et_al_2012}, computes the Fourier transform of the visibility measured by an interferometer and produces a spectrum, referred to as the delay spectrum hereafter, which is a function of the geometric time delay corresponding to the physical length of the baseline between two antennas.
 For the visibilities measured over a wide field across a wide frequency bandwidth, the delay spectrum consists of the instrument response, the foreground signal, and the 21cm power spectrum, hereafter referred to as the EoR signal.
@@
 Such techniques also assume a spectrally smooth instrumental response whose contribution to the measured data, much as the contribution of the smooth spectrum foreground, also has an upper bound in the delay space imposed by the largest geometric delay of the given baseline.
-Beyond this limit, for an ideal system performance, the delay spectrum would be dominated by any wideband signal across the sky with spectral and spatial fluctuations over small scales, such as the EoR signal, and therefore, could be detectable.\\
-\indent The interaction between the sky signal and instrument response can alter the relative contribution of the foreground, instrument response and the EoR signal at a given delay and, thus, influence the detectability of the EoR signal.
+Beyond this limit, for an ideal system performance, the delay spectrum would be dominated by any wideband signal across the sky with spectral and spatial fluctuations over small scales, such as the EoR signal, and therefore, could be detectable.
+The interaction between the sky signal and instrument response can alter the relative contribution of the foreground, instrument response and the EoR signal at a given delay and, thus, influence the detectability of the EoR signal.
 Such interactions may cause the foreground and systematics to spill over into higher delays and, thus, push the upper limit of the foreground and systematics contaminated delay modes to much higher delays.
@@
 \indent The Hydrogen Epoch of Reionization Array (HERA) is a proposed array consisting of 568 14-m dishes in South Africa which will measure the 21~cm power spectrum between 100 to 200~MHz.
-In this paper, we investigate the performance of an individual HERA element and the resulting contribution of the instrument response to the delay spectrum.
- Reflectometry measurements  are carried out across a wide bandwidth on a prototype HERA element in Green Bank, WV (Figure \ref{fig:heradish}), and the results are interpreted in light of the delay spectrum technique.
-Section 2 describes the delay spectrum for the ideal and non-ideal performance of a two element interferometer.
-Reflectometry measurements are described in section 3.
-Section 4 describes the performance of the HERA element as an interferometer for detection of the 21~cm power spectrum.
-In coordination with ~\citet{XXXsisterpapers}, we compare 
-reflectometry measurements with
-a specification for the spectral performance of an element, given models of the relative brightness of
-foreground and 21~cm reionization modes in $k$-space in section 5.
-
+In this paper, we investigate the performance of an individual HERA element and the resulting manifestation of the instrument response to the delay spectrum.
+Reflectometry measurements  are carried out across a wide bandwidth on a prototype HERA element in Green Bank, WV (Figure \ref{fig:heradish}), and the results are interpreted in light of the delay spectrum technique of power spectrum estimation and inverse covariance weighting method of foreground suppression.
+Section 2 briefly describes the delay spectrum for the ideal and non-ideal performance of a two element interferometer.
+Section 3 describes the reflectometry measurements and establishes the connection between visibility measurements and reflectometry.
+Reflectometry results are described in section 5.
+Section 6 evaluates the performance of the HERA element for detection of the 21~cm power spectrum.
+This paper is one in a series of four papers that studies the time and frequency domain simulation of  HERA element~\citep{Ewall-Wice_et_al2016}, ~\citep{ddboer_et_al2016},beam pattern measurements~\citep{Neben_et_al2016}, and foreground limits ~\citep{Thyagarajan_et_al2016}.
+We compare
+reflectometry measurements to the simulated specification for the spectral performance of a HERA element ~\citep{ddboer_et_al2016} and to the limits of EoR to foreground power ratio established by ~\citep{Thyagarajan_et_al2016}.
 \begin{figure*}
@@
 \centering
-\includegraphics[angle=0, width=\linewidth]{/Users/Nipanjana/WORKAREA1/DATA_Area/Project_HERA/DishPapers/DishReflectometry/GB_reflectometry_part3/plot/RL_mag_feed.png}
+\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_mag_feed.png}
 \end{minipage}
@@
 \centering
-\includegraphics[angle=0, width=\linewidth]{/Users/Nipanjana/WORKAREA1/DATA_Area/Project_HERA/DishPapers/DishReflectometry/GB_reflectometry_part3/plot/RL_mag_dish.png}
+\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_mag_dish.png}
 \end{minipage}
@@
 \centering
-\includegraphics[width=\linewidth]{/Users/Nipanjana/WORKAREA1/DATA_Area/Project_HERA/DishPapers/DishReflectometry/GB_reflectometry_part3/plot/ds_feed_on_dish_trans_recp.png}
+\includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/ds_feed_on_dish_trans_recp.png}
 \caption{Delay spectrum of the HERA feed (brown) estimated by taking the Fourier transform of the measured return loss of power at the feed output.
@@
 %\bibliography{biblio}{}
+\bibliographystyle{apj}
 \bibliography{Reference}{}
-\bibliographystyle{apj}
+
 \end{document}

### 2016-09-06 DishReflectometry/Paper1_v3.tex
Corrected references section 2

@@
   P_{21}(k_\perp,k_\parallel) = (|\tilde V(\vec b, \tau)|^{2} \left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2 ,
-\label{eq:delay-power-spectrum}
+\label{eq4}
 \end{equation}
@@
   k_\parallel = \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, 
+ \label{eq5}
 \end{equation}
@@
 The reflected signal illuminates the dish and most of it is reflected back into the space.
-However, a part of it reflects back and forth several times in between the feed and the vertex of the dish which is shadowed by the feed (dashed blue arrows in Figure \ref{fig:cartoon}).
+However, a part of it reflects back and forth several times in between the feed and the vertex of the dish which is shadowed by the feed.
 Such reflections generate multiple copies of the incident sky signal of reduced strength at various delay and phase and thus produces spurious correlations in the visibilities of interferometric data.
@@
 Therefore, it is necessary to measure and understand the instrument delay spectrum in order to qualify the system for the measurement of 21cm power spectrum.
-In this section we compute the visibility of a two element interferometer accounting for the additional reflections of the sky signal in between the feed and the dish vertex and the corresponding effects on the delay spectrum, using the multiple reflection formulation of Sec.
-\ref{sec:multiple}.
-In this section, the effect of reflections on the visibility data and corresponding effect on the delay spectrum is discussed in detail.
+In this section we compute the visibility of a two element interferometer accounting for the additional reflections of the sky signal in between the feed and the dish vertex and the corresponding effects on the delay spectrum in detail.
 We assume two antennas with identical geometry and electrical parameters i.e, $\bmvolt_{1}(\thhat,\nu)=\bmvolt_{2}(\thhat,\nu) = \bmvolt(\thhat,\nu)$.

### 2016-09-07 DishReflectometry/Paper1_v3.tex
Minor bug fixes for equation reference and figure references.
Edited conclusion

@@
 
-\title{THE HYDROGEN EPOCH OF REIONIZATION ARRAY DISH: CHARACTERIZATION OF  THE INSTRUMENTAL RESPONSE WITH REFLECTOMETRY MEASUREMENTS AND ITS IMPLICATIONS ON THE MEASUREMENT OF 21CM POWER SPECTRUM. } 
+\title{THE HERA DISH III : MEASURING ELEMENT CHROMATICITY WITH REFLECTOMETRY. } 
 %\maketitle
@@
 &&  ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}]
+\label{eq6}
 \end{eqnarray}
+
 \begin{figure}
@@
 & = & \frac{ (1+\Gamma_d)(1+\Gamma_{f})}{1+\Gamma_{f}\Gamma_{d}\dfngexp} 
-\label{corrected_response}
+\label{eq7}
 \end{eqnarray}
@@
 &&  ....+ \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp (\Gamma_d\Gamma_f\dfngexp)^n \nonumber \\
+\label{eq8}
 \end{eqnarray}
@@
 {\volt_{rec}\over \volt_{trans} } = \Gamma_f + \frac{(1+\Gamma_f)^2}{\Gamma_{f}} \displaystyle\sum\limits_{n=1}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
-\label{eq:s11}
+\label{eq9}
 \end{equation}
@@
 s_{11} +\frac{(1+\Gamma_f)^2}{\Gamma_f}-\Gamma_f = \frac{(1+\Gamma_f)^2}{\Gamma_{f}} \displaystyle\sum\limits_{n=0}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
+\label{eq10}
 \end{equation}
@@
  & = & \bmvolt(\thhat,\nu) \left[(1+\Gamma_f) + \frac{\Gamma_f}{(1+\Gamma_f)}\left(s_{11} - \Gamma_f\right)\right]
-\label{zero_delay_correction}
+\label{eq11}
 \end{eqnarray}
@@
              &&  \left[ \frac{|\Gamma_f|^2}{|1+\Gamma_{f}|^2}|s_{11} - \Gamma_f|^2  \right]  \nonumber\\
-\label{eq:power_ratio}             
+\label{eq12}             
 \end{eqnarray}
@@
              &&  \left[ \frac{|\Gamma_f|^2}{|1+\Gamma_{f}|^2}|s_{11} - \Gamma_f|^2  \right]  I_{sky} \ifngexp d\Omega
-\label{visibility_mul}
+\label{eq13}
 \end{eqnarray}
@@
 \langle  \tilde T_{b}(\bold k) \tilde T_{b}^{*}(\bold k^{'}) \rangle = (2\pi)^{3} \delta (\bold k - \bold k^{'})P_{21}(k_\perp,k_\parallel)
+\label{eq14}
 \end{equation}
@@
 \hat q_{\alpha} = \bold x^{T} E^{\alpha} \bold x  - b^{\alpha}
+\label{eq15}
 \end{equation}
@@
 E^{\alpha} =  {1 \over 2} C^{-1} Q_{\alpha} C^{-1}
+\label{eq16}
 \end{equation}
@@
 \hat p_{\alpha} = M \hat q_{\alpha} 
+\label{eq17}
 \end{equation}
@@
 \hat p_{\alpha} = W p_{\alpha}
+\label{eq18}
 \end{equation}
@@
  W = MF
+ \label{eq19}
 \end{equation}
@@
  F_{\alpha\beta} = \frac {1} { 2} [C^{-1}Q_{\alpha}C^{-1}Q_{\beta}]^{T}
+ \label{eq20}
 \end{equation} 
@@
  		& = & MFM^{T}
+\label{eq21}
  \end{eqnarray}
@@
 We again compute the EoR to foreground power ratio which is now smaller than what is estimated in Thyagarajan et al 2016 as shown in fig:\ref{fig:sim_fg_revised}.
-\begin{figure}[ht]
+\begin{figure*}[ht]
 \centering
@@
 \label{fig:sim_fg_revised}
-\end{figure}
+\end{figure*}
 This demonstrates that the performance of the HERA element performance, in conjunction with the inverse covariance method of foreground suppression, qualifies the system for its the science goal it is designed for, irrespective of its chromatic response generated due to multiple reflections in the system.
@@
 \section{\textbf{Conclusion}}
-
+The interplay between the extremely bright sky signal with the system response has remained somewhat undermined for the first generation 21cm experiments such as MWA, LOFAR, PAPER.
+With the theory of redshifted 21cm experiments have very well evolved, it is absolute necessity now to quantify the instrumental limits of these measurement in order to produce a believable power spectrum estimates.
+In this paper, we studied the performance of a HERA element in both frequency as well as delay domain.
+The effects of multiple reflections  in a HERA feed-dish assembly is investigated in detail and their effects on the measured visibility as well as delay spectrum is estimated.
 The delay-domain performance of the HERA dish is central to HERA's function as a power spectrum instrument.
-As we have seen, reflectometry measurements can help characterize HERA's performance in this domain, and
-as Equation \ref{eqn:ratio1} shows, these measurements must be adjusted for a difference in transmission/reflection
+Reflectometry measurements characterised HERA's performance in this domain, and as Equation \ref{eq10} shows, these measurements must be adjusted for a difference in transmission/reflection
 at the first feed encounter in order to be interpreted as the delay response of a feed relative to an incident
-plane wave from the sky.  We also see that the choice of windowing function is critical for accurately measuring the
+plane wave from the sky.  It is also shown that the choice of windowing function is critical for accurately measuring the
 antenna delay response at higher delays, where sidelobes from much higher amplitude responses at small delays can easily
-dominate.  We find Hamming, Hanning, and Blackman-Harris windows to be generally adequate while square windowing functions are not.
-Given the critical nature of the windowing function, we recommend that all reflectometry measurements be performed in the
+dominate.  Blackman-Harris window is found to be generally adequate while square windowing functions are not.
+Given the critical nature of the windowing function, it is recommended that all reflectometry measurements be performed in the
 frequency domain, so that the data could be Fourier transformed with the appropriate window.
-
-Taken all together, we summarize that the first version of the HERA dish, with a PAPER-style feed and cylindrical cage, is close to meeting
-specification, but will require additional work to fall below $-60dB$ at $60ns$.  Given that the width of the delay response is a convolution
-of the feed response and the dish reflections, it is not possible to perfectly decouple the response of the feed from that of the dish.
-It may be possible to achieve enough of a reduction to meet specification by modifying the feed.
-Given that previous measurements using a PAPER feed with a simple backplane exhibit structure above $-60dB$ at $60ns$,
-we deduce that these advances will most likely require improving the feed return loss.  We also recommend re-investigating the scattering
-cone for reducing standing waves between the feed and dish.  Finally, given the proximity of our measurements to the rough 
-specification that was adopted for 
-HERA of $-60dB$ attenuation at $60ns$, we recommend reinvestigating this specification to determine more accurately the impact of 
-the element's current delay performance on HERA science.  We suspect that, at the level of $-50dB$ at $60ns$ and $-60dB$ at $120ns$, this
-performance may indeed be adequate for the delay-domain power spectrum analysis for which HERA has been optimized.
+The delay spectrum estimates are then compared with the electromagnetic as well as time domain simulation of the HERA element~\citep{Ewall-Wice_et_al2016}, ~\citep{ddboer_et_al2016}.
+The same is then compared with the foreground simulation of~\cite{Thyagarajan_et_al2015}.
+The performance is also evaluated in the light of HERA power spectrum estimation technique using inverse covariance weighting formalism.
+Taken all together, we summarise that the HERA antenna element, with a PAPER-style crossed dipole feed and cylindrical cage the instrument delay spectrum very well satisfies the criteria necessary to meet its science goal.
 

### 2016-09-13 DishReflectometry/Paper1_v3.tex
Added abstract and completed editing upto section 4

@@
 Aaron~R.~Parsons\UCB,
+David~R.~DeBoer\UCB,
 Nithyanandan Thyagarajan\ASU,
-David~R.~DeBoer\UCB,
-Zaki~S.~Ali\UCB,
-Cherie~K.~Day\UCB, 
-Carina Cheng\UCB,
-%Gilbert Hsyu\altaffilmark{2}, 
-%Tsz Kuk Leung\altaffilmark{2}
+Aaron  Ewall-Wice\altaffilmark{7},
+Gilbert Hsyu\UCB, 
+Tsz Kuk Leung\UCB,
+James E.
+Aguirre\altaffilmark{10}, Paul  Alexander\altaffilmark{5}, Zaki S.
+Ali\altaffilmark{1}, Adam P.
+Beardsley\altaffilmark{2}, Gianni  Bernardi\altaffilmark{11, 13}, Judd D.
+Bowman\altaffilmark{2}, Richard F.
+Bradley\altaffilmark{8}, Chris L.
+Carilli\altaffilmark{9}, Carina  Cheng\altaffilmark{1}, Cherie~K.~Day\UCB, Eloy  de~Lera~Acedo\altaffilmark{5}, Joshua S.
+Dillon\altaffilmark{1}, , Gcobisa  Fadana\altaffilmark{13}, Nicolas  Fagnoni\altaffilmark{5}, Randall  Fritz\altaffilmark{13}, Steve R.
+Furlanetto\altaffilmark{4}, Brian  Glendenning\altaffilmark{9}, Bradley  Greig\altaffilmark{12}, Jasper  Grobbelaar\altaffilmark{13}, Bryna J.
+Hazelton\altaffilmark{14, 15}, Jacqueline N.
+Hewitt\altaffilmark{7}, Jack  Hickish\altaffilmark{1}, Daniel C.
+Jacobs\altaffilmark{2}, Austin  Julius\altaffilmark{13}, MacCalvin  Kariseb\altaffilmark{13}, Saul A.
+Kohn\altaffilmark{10}, Telalo  Lekalake\altaffilmark{13}, Adrian  Liu\altaffilmark{1, 16}, Anita  Loots\altaffilmark{13}, David  MacMahon\altaffilmark{1}, Lourence  Malan\altaffilmark{13}, Cresshim  Malgas\altaffilmark{13}, Matthys  Maree\altaffilmark{13}, Zachary  Martinot\altaffilmark{10}, Nathan  Mathison\altaffilmark{13}, Eunice  Matsetela\altaffilmark{13}, Andrei  Mesinger\altaffilmark{12}, Miguel F.
+Morales\altaffilmark{14}, Abraham R.
+Neben\altaffilmark{7},  Samantha  Pieterse\altaffilmark{13}, Jonathan C.
+Pober\altaffilmark{3}, Nima  Razavi-Ghods\altaffilmark{5}, Jon  Ringuette\altaffilmark{14}, James  Robnett\altaffilmark{9}, Kathryn  Rosie\altaffilmark{13}, Raddwine  Sell\altaffilmark{13}, Craig  Smith\altaffilmark{13}, Angelo  Syce\altaffilmark{13}, Max  Tegmark\altaffilmark{7}, Peter K.~G.
+Williams\altaffilmark{6}, Haoxuan  Zheng\altaffilmark{7}
 }
@@
 
+%\author{ James E.
+Aguirre\altaffilmark{10}, Paul  Alexander\altaffilmark{5}, Zaki S.
+Ali\altaffilmark{1}, Adam P.
+Beardsley\altaffilmark{2}, Gianni  Bernardi\altaffilmark{11, 13}, Judd D.
+Bowman\altaffilmark{2}, Richard F.
+Bradley\altaffilmark{8}, Chris L.
+Carilli\altaffilmark{9}, Carina  Cheng\altaffilmark{1}, Eloy  de~Lera~Acedo\altaffilmark{5}, Joshua S.
+Dillon\altaffilmark{1}, , Gcobisa  Fadana\altaffilmark{13}, Nicolas  Fagnoni\altaffilmark{5}, Randall  Fritz\altaffilmark{13}, Steve R.
+Furlanetto\altaffilmark{4}, Brian  Glendenning\altaffilmark{9}, Bradley  Greig\altaffilmark{12}, Jasper  Grobbelaar\altaffilmark{13}, Bryna J.
+Hazelton\altaffilmark{14, 15}, Jacqueline N.
+Hewitt\altaffilmark{7}, Jack  Hickish\altaffilmark{1}, Daniel C.
+Jacobs\altaffilmark{2}, Austin  Julius\altaffilmark{13}, MacCalvin  Kariseb\altaffilmark{13}, Saul A.
+Kohn\altaffilmark{10}, Telalo  Lekalake\altaffilmark{13}, Adrian  Liu\altaffilmark{1, 16}, Anita  Loots\altaffilmark{13}, David  MacMahon\altaffilmark{1}, Lourence  Malan\altaffilmark{13}, Cresshim  Malgas\altaffilmark{13}, Matthys  Maree\altaffilmark{13}, Zachary  Martinot\altaffilmark{10}, Nathan  Mathison\altaffilmark{13}, Eunice  Matsetela\altaffilmark{13}, Andrei  Mesinger\altaffilmark{12}, Miguel F.
+Morales\altaffilmark{14}, Abraham R.
+Neben\altaffilmark{7},  Samantha  Pieterse\altaffilmark{13}, Jonathan C.
+Pober\altaffilmark{3}, Nima  Razavi-Ghods\altaffilmark{5}, Jon  Ringuette\altaffilmark{14}, James  Robnett\altaffilmark{9}, Kathryn  Rosie\altaffilmark{13}, Raddwine  Sell\altaffilmark{13}, Craig  Smith\altaffilmark{13}, Angelo  Syce\altaffilmark{13}, Max  Tegmark\altaffilmark{7}, Nithyanandan  Thyagarajan\altaffilmark{2}, Peter K.~G.
+Williams\altaffilmark{6}, Haoxuan  Zheng\altaffilmark{7}}
+%\affil{HERA Collaboration}
+\altaffiltext{1}{Department of Astronomy, University of California, Berkeley, CA}
+\altaffiltext{2}{School of Earth and Space Exploration, Arizona State University, Tempe, AZ}
+\altaffiltext{3}{Physics Department, Brown University, Providence, RI}
+\altaffiltext{4}{Department of Physics and Astronomy, University of California, Los Angeles, CA}
+\altaffiltext{5}{Cavendish Astrophysics, University of Cambridge, Cambridge, UK}
+\altaffiltext{6}{Harvard-Smithsonian Center for Astrophysics, Cambridge, MA}
+\altaffiltext{7}{Department of Physics, Massachusetts Institute of Technology, Cambridge, MA}
+\altaffiltext{8}{National Radio Astronomy Observatory, Charlottesville, VA}
+\altaffiltext{9}{National Radio Astronomy Observatory, Socorro, NM}
+\altaffiltext{10}{Department of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA}
+\altaffiltext{11}{Department of Physics and Electronics, Rhodes University, PO Box 94, Grahamstown, 6140, South Africa}
+\altaffiltext{12}{Scuola Normale Superiore, Pisa, Italy}
+\altaffiltext{13}{SKA-SA, Cape Town, South Africa}
+\altaffiltext{14}{Department of Physics, University of Washington, Seattle, WA}
+\altaffiltext{15}{eScience Institute, University of Washington, Seattle, WA}
+\altaffiltext{16}{Hubble Fellow}
+
 \begin{abstract}
+Spectral structure of the systematics has so far been the most dominant limiting factor for the experiments attempting to detect the redshifted 21~cm signal from the Epoch of Reionization (EoR).
+Systematics are specific to instruments and their direct measurement or estimation is not always straightforward.
+The Hydrogen Epoch of Reionization Array (HERA) uses the delay spectrum technique for estimating of 21~cm power spectrum.
+In a unique way, the delay spectrum technique directly translates to reflectometry in case of measuring instrumental response and allows the direct measurement of systematic effects in individual array element.
+This paper presents a detailed investigation of the instrument chromaticity of an antenna element that constitute Hydrogen Epoch of Reionization Array.
+Reflectometry measurements are carried out on a HERA dish-feed assembly between 100 to 200~MHz which studies the multiple reflections in the system that finally results in various spurious spectral response in the measured visibility.
+Reflectometry measurements shows that even without incorporation of any sophisticated analysis method, the instrument is capable of measuring the line of sight component  of the $k$ mode          $k_{\parallel} >0.2 h Mpc^{-1}$ modes of power spectrum with very low foreground contaminations around $k_{\parallel} \approx0.2 h Mpc^{-1}$.
+The performance is significantly better at the high frequency subbands of observation.
+When combined with a powerful foreground suppression method such as inverse covariance weighting, the instrument is capable of measuring the power spectrum for the spatial modes as low as $k_{\parallel} >0.1$.
+The study presented here qualifies HERA as a power spectrum instrument and serves as a fundamental method to design and measure instrument systematics for any future experiment that aims to detect the 21~cm EoR power spectrum.
  \end{abstract}
@@
 and 21~cm reionization power spectrum experiments such as
-the LOw Frequency ARray (LOFAR; ~\citealt{XXX}),
-the Murchison Widefield Array (MWA; ~\citealt{XXX}),
-the Giant Metre-wave Radio Telescope (GMRT; ~\citealt{XXX}),
+the LOw Frequency ARray (LOFAR; ~\citealt{van_Haarlem_2013}),
+the Murchison Widefield Array (MWA; ~\citealt{Tingay_2013}),
+the Giant Metre-wave Radio Telescope (GMRT; ~\citealt{Paciga_et_al2011}),
 the Donald C. Backer Precision Array to Probe the Epoch of Reionization (PAPER; ~\citealt{parsons_et_al2010}),
-the Hydrogen Epoch of Reionization Array (HERA; ~\citealt{XXX}),
+the Hydrogen Epoch of Reionization Array (HERA; ~\citealt{deBoer_2016}),
 and the future Square Kilometre Array (SKA; ~\citealt{XXX})
@@
 We assume two antennas with identical geometry and electrical parameters i.e, $\bmvolt_{1}(\thhat,\nu)=\bmvolt_{2}(\thhat,\nu) = \bmvolt(\thhat,\nu)$.
- \subsection{\textbf{Antenna Reception With Multiple Reflections}}
+ \subsection{Antenna Reception With Multiple Reflections}
 \label{sec:multiple}
@@
 An accurate measurement of this quantity requires receiving $v_{sky}$ from a well calibrated, wideband source in the sky in the far field of the HERA antenna element with significant isotropic emission.
-While this condition is hard to achieve in practice, due to the reciprocity of the antenna performance in the transmission and reception mode, the right hand side of equation \ref{eq:Sigma} could be measured using the return loss measurement technique with a vector network analyzer (VNA).
+While this condition is hard to achieve in practice, due to the reciprocity of the antenna performance in the transmission and reception mode, the right hand side of equation \ref{eq7} could be measured using the return loss measurement technique with a vector network analyzer (VNA).
 \\
@@
 The VNA measures the quantity $\volt_{rec}/\volt_{trans}=s_{11}$ which is the voltage reflection coefficient of the HERA element.
-The fundamental differences between the right hand side of equations \ref{eq:Sigma} and \ref{eq:s11} are the $n=0$ term and the multiplicative factor in front of the convergent series $\displaystyle\sum\limits_{n=1}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}$ that represents the contribution of the delayed voltage components at the VNA input, arising due to multiple signal reflections between the feed and the dish.
-Finally, writing $\volt_{rec}/\volt_{trans}=s_{11}$, equation \ref{eq:s11} can be written as,
+The fundamental differences between the right hand side of equations \ref{eq7} and \ref{eq9} are the $n=0$ term and the multiplicative factor in front of the convergent series $\displaystyle\sum\limits_{n=1}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}$ that represents the contribution of the delayed voltage components at the VNA input, arising due to multiple signal reflections between the feed and the dish.
+Finally, writing $\volt_{rec}/\volt_{trans}=s_{11}$, equation \ref{eq9} can be written as,
 \begin{equation}
@@
 \end{equation}
-Comparing to Eq. \ref{eq:Sigma} and we find that
+Comparing to Eq. \ref{eq7} we find that
 \begin{eqnarray}
@@
 \end{eqnarray}
-When the feed return loss is measured separately, all the higher order terms of equation \ref{eq:s11} do not exist.
+When the feed return loss is measured separately, all the higher order terms of equation \ref{eq9} do not exist.
 In this case, $\Gamma_f = s_{11}^{f}$.
@@
 
-Comparing equations \ref{eq:power_ratio} and \ref{eq2}, the cross power generated by $v_{1}$ and $v_{2}$ would have a spurious visibility response due to the mutual correlation between multiply reflected voltages represented by the second and the third term of the right hand side of equation \ref{eq:power_ratio}.
-In the ideal case, $\Gamma_{f}=0$, in which case equation \ref{eq:power_ratio} results in equation \ref{eq2}.
+Comparing equations \ref{eq13} and \ref{eq2}, the cross power generated by $v_{1}$ and $v_{2}$ would have a spurious visibility response due to the mutual correlation between multiply reflected voltages represented by the second and the third term of the right hand side of equation \ref{eq13}.
+In the ideal case, $\Gamma_{f}=0$, in which case equation \ref{eq13} results in equation \ref{eq2}.
 The Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum.
@@
 
-\section{Results}
-Return loss measurements yields the instrument pass band response that would manifest in autocorrelation data of a single HERA element.
+\section{\textbf{Results}}
+%Return loss measurements yields the instrument pass band response that would manifest in autocorrelation data of a single HERA element.
 Upon our assumption that two adjacent antenna elements have identical design parameters and electrical properties, this power is also a measure of the cross power or the visibility $\vis (\vec b, \nu)$ between the two antennas with a normalisation factor of $2$.
-
-The simultated and measureded return loss of the feed as well as the HERA element is shown in figure \ref{RL_mag_feed} and figure \ref{RL_mag_dish}.
-The measurements deviates from the simulated performance in one major aspect.
-While the return loss of the simulated structure shows two resonant peaks around 120 and $160~MHz$, the feed resonance occur at slightly higher frequencies.
-While the simulated response shows very wide resonant peaks, as expected from these dipole structures, the measured return loss of the feed has a narrow peak around its low frequency resonance.
-This feature somewhat dominates the fall off rate in the delay response of the system bandpass.
-The delay response of the feed alone is shown in figure \ref{ds_feed_on_dish_trans} along with the delay response of a HERA element in transmission mode.
-In the following sections, we compute the response of the HERA element in the receiving mode.
-\begin{figure}[ht]
-\begin{minipage}[b]{\linewidth}
+Performance of the HERA feed and the dish-feed assembly has been simulated by the em solver "High Frequency Structural Simulator(HFSS)" using the finite element method. 
+The simulated and measured return loss of the feed, both magnitude and phase are shown in the upper panel of the figure \ref{RL_mag_dish}.
+While the simulated return loss of the feed structure shows two resonant peaks around 120 and $160~MHz$, the feed resonance occur at slightly higher frequencies.
+Notable are the difference in the shape of the resonant peaks.
+While the simulated response shows very wide resonant peaks, as expected from this dipole structures, the measured return loss of the feed has a narrow peak around its low frequency resonance.
+This feature dominates the fall off rate in the delay response of the system bandpass.
+The delay response of the feed is shown in figure \ref{ds_feed_on_dish_trans}.
+\begin{figure*}[ht]
+\begin{minipage}[b]{0.5\linewidth}
 \centering
@@
 \end{minipage}
+\hspace{0.1cm}
+\begin{minipage}[b]{0.5\linewidth}
+\centering
+\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_ph_feed.png}
+\end{minipage}
 \vspace{0.1cm}  
-\begin{minipage}[b]{\linewidth}
-\centering
-\includegraphics[angle=0, width=\linewidth]{plots/feed_meas_sim_ph.png}
-\end{minipage}
-\caption{Magnitude and phase of the return loss of the feed as simulated and measured.
-While both the measurement and the simulation shows similar resonance around $120~MHz$, the simulation shows a better matching to a 50 Ohm transmission line compared to the measurements.
-The measurement also has some small scale fluctuation due to multiple reflection of the signal at the VNA input.
-}
-\label{RL_mag_feed}
-\end{figure}
-
-\begin{figure}[ht]
-\begin{minipage}[b]{\linewidth}
+\begin{minipage}[b]{0.5\linewidth}
 \centering
@@
 \end{minipage}
-\vspace{0.1cm}
-\begin{minipage}[b]{\linewidth}
+\hspace{0.1cm}
+\begin{minipage}[b]{0.5\linewidth}
 \centering
-\includegraphics[angle=0, width=\linewidth]{plots/HERA_meas_sim_ph.png}
+\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_ph_HERA.png}
 \end{minipage}
-\caption{Magnitude and phase of the return loss of the HERA element as simulated and measured.
-In this case, both measurement and simulation shows similar level of return loss across the band with marginally better return loss at the high frequency end of the band.
-}
+\caption{Upper panel: Magnitude and phase of the return loss of the feed as simulated and measured.
+Both measurement and simulation shows similar level of return loss across the band with marginally better return loss at the high frequency end of the band.
+Lower panel: Magnitude and phase of return loss when the feed is suspended at the focal point of the dish which 5~m above the dish vertex.}
 \label{RL_mag_dish}
-\end{figure}
+\end{figure*}
 
@@
 \centering
-\includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/ds_feed_on_dish_trans_recp.png}
-\caption{Delay spectrum of the HERA feed (brown) estimated by taking the Fourier transform of the measured return loss of power at the feed output.
-The feed, when suspended on the dish results in a more complex return loss as shown in figure \ref{RL_mag_dish} and corresponding delay response is shown here in black.
-This figure shows the delay spectrum of the instrument in the as estimated from direct measurements of the return loss i.e, in the transmission mode of the antenna.
+\includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/ds_feed_dish.png}
+\caption{Delay spectrum of the HERA feed (brown) estimated by taking the Fourier transform of the measured return loss of power at the feed output (upper panel in figure \ref{RL_mag_dish}).
+The feed, when suspended on the dish results in a more complex return loss as shown in the lower panel of figure \ref{RL_mag_dish} and corresponding delay response is shown here in black.
 }
@@
 
-Figure \ref{RL_mag_dish} shows the measured return loss when the feed is suspended at the focal plane of the parabolic dish which is at $5m$ from the dish vertex.
+Lower panel of the figure \ref{RL_mag_dish} shows the measured return loss when the feed is suspended at the focal plane of the parabolic dish which is at $5m$ from the dish vertex.
 The measured return loss is much more complex than what is found from the simulation.
-The delay spectrum in the transmission mode is shown in \ref{ds_feed_on_dish_trans}.
-To estimate the delay spectrum of the dish-feed assembly i.e one single HERA element, this measurement is first corrected to map the response of the antenna from transmitting mode to receiving mode via equation \ref{zero_delay_correction}.
+%To estimate the delay spectrum of the dish-feed assembly i.e one single HERA element, this measurement is first corrected to map the response of the antenna from transmitting mode to receiving mode via equation \ref{zero_delay_correction}.
 The corrected measurement is then Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{corrected_response}.
 Measurement bandwidth is kept much larger than the bandwidth of operation to achieve higher delay resolution.
-A number of systematic effects as well as mathematical artfacts that are critical to this measurements and their effects on the corresponding estimation of the delay spectrum are taken in to account in determination of the delay spectrum and described below.
+A number of systematic effects as well as mathematical artifacts that are critical to this measurement and their effects on the corresponding estimation of the delay spectrum are taken in to account in determination of the delay spectrum and described below.
 
-\subsection{\textbf{Zero delay correction}}
+\subsection{Zero delay response}
 %At first, the frequency domain measurement of s11 is Fourier-transformed to compute the response of the system in the delay domain.
 
+%\subsection{\textbf{Antenna beam pattern and feed return loss}}
+%The return loss $\Gamma_{f}$ determines the amount of power coupled to the system via the feed antenna.
+Additionally, with each reflections, the power coupled to the system reduces by a factor of $\Gamma_{f}^{2}$.
+Since reflected signal results in system response in higher delay, multiple reflections of the signal off the feed and the dish would result in an exponential envelope in the delay spectrum.
+The return loss of power results from the antenna impedance mismatch with the free space as well as the transmission line.
+While antenna beam pattern $A_{f}$ is a smooth function of frequency and should have its imprint confined to lower delays, the return loss $\Gamma_{f}$ broadens the delay spectrum.
+However, a smaller return loss will result in vertical shift of the delay spectrum at lower values and therefore can make the higher order reflections insignificant.
+
+During observation, each HERA element is connected to an active balun similar to the ones used in the PAPER antenna which provides greater than 10dB return loss of power at the feed output as is achieved in the measurement presented here.These baluns are under further design improvements aiming at 10 to 20dB better impedance match between the feed and the balun than the measurements presented here.
+Our measurement is done using a vector network analyzer for which the active balun has been replaced by a passive balun.Given the antenna impedance and the 50 Ohm transmission line the measurements are done using the passive balun with a 4:1 impedance ratio.
+This measurements are conservative estimate  for both $\Gamma_{f}$ and $s_{11}$.\\
 While measuring the return loss of the dish-feed assembly, the signal transmitted by the VNA is reflected first off the feed.
-This is represented by $\Gamma_{f}$ in equation \ref{eq:power_ratio}.
+This is represented by $\Gamma_{f}$ in equation \ref{eq9}.
 This essentially represents a mismatch in between the feed and the 50 Ohm transmission line.
@@
 In receiving mode, in delay domain, this appears at the zero delay bin.
-The using the return loss measurement of the feed $(\Gamma_{f})$, the return loss measurement $s_{11}$ of the dish and feed assembly is corrected via equation \ref{eq:power_ratio} and the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated.
+The using the return loss measurement of the feed $(\Gamma_{f})$, the return loss measurement $s_{11}$ of the dish and feed assembly is corrected via equation \ref{eq11} and the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated.
 
-%\subsection{\textbf{Antenna beam pattern and feed return loss}}
-%The return loss $\Gamma_{f}$ determines the amount of power coupled to the system via the feed antenna.
-Additionally, with each reflections, the power coupled to the system reduces by a factor of $\Gamma_{f}^{2}$.
-Since reflected signal results in system response in higher delay, multiple reflections of the signal off the feed and the dish would result in an exponential envelope in the delay spectrum.
-The return loss of power results from the antenna impedance mismatch with the free space as well as the transmission line.
-While antenna beam pattern $A_{f}$ is a smooth function of frequency and should have its imprint confined to lower delays, the return loss $\Gamma_{f}$ broadens the delay spectrum.
-However, a smaller return loss will result in vertical shift of the delay spectrum at lower values and therefore can make the higher order reflections insignificant.
-During observation, each HERA element is connected to an active balun similar to the ones used in the PAPER antenna (need reference) which provides greater than 10dB return loss of power at the feed output.These baluns are under further design improvements aiming at 10 to 20dB better imepedance match between the feed and the balun than the measurements presented here.
-Our measurement is done using a vector network analyser for which the active balun has been replaced by a passive balun.Given the antenna impedance and the 50 Ohm transmission line the measurements are done using the passive balun with a 4:1 impedance ratio providing a net return loss of power between the sky, the antenna and the transmission line shown in the figure \ref{RL_feed_mag}.
-This measurements are conservative estimate  for both $\Gamma_{f}$ and $s_{11}$.
-
-\subsection{\textbf{Dish reflections}}
+\subsection{Dish reflections}
 Measurement equations shows the effects of multiple reflections of the sky signal between the feed and the dish.
@@
 Therefore, the delay spectrum in both the cases follow each other.
-Since the distance between the feed and the dish is 5 m, the roundtrip delay between the dish and the feed as about $30~ns$ around which these two delay spectrum starts to deviate.
-At delays $\> 50nS$ the dish reflections starts to dominate over the reflections from the feed structure and the two delay spectrum deviates from each other.
+Since the distance between the feed and the dish is 5 m, the roundtrip delay between the dish and the feed as about $30~ns$.
+Hence, the dish reflection is expected to manifest themselves at an integral multiple of $30~ns$.
+The diameter of the feed cavity is $172~cm$  that results in signal reflections every integral multiple of $\approx2.86~ns$.
+The combined effect of feed and the dish dominates the delay spectrum up to $\> 50nS$ after which the dish reflections starts to dominate and the two delay spectrum deviates from each other.
+With some manipulation of the equation \ref{eq10}, we can estimate the dish return loss $\Gamma_{d}$ and corresponding delay spectrum as shown in the figure \ref{dish_delay_spectrum}.
 
-\subsection{\textbf{Measurement bandwidth and window function}}
-Estimation of the delay spectrum by taking the Fourier transform of the measured return loss is sensitive to the bandwidth of measurements.
-Since the measurements are done in the spectral domain, measurement between two frequencies is analogous to windowing the frequency domain data by a square window function.
-In the delay domain, Fourier transform of this would result in multiple side lobes at higher delays.
-Therefore, appropriate windowing of the data is  necessary prior to taking the Fourier transform of the measured data.
-Figure \ref{fig:window} shows the delay spectrum estimated from the measured data using a square window as well as Blackman Harris window.
-Windowing the data prior to Fourier transform significantly reduces the system response higher delays.
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/ds_window.png}
-\caption{Effect of finite bandwidth on estimation of delay spectrum: Blue line shows the delay spectrum of the HERA element computed from the measured data which is band limited between 100 to 200MHz.
-Green line shows the delay spectrum estimated from the same data set after multiplying the data by a Blackman Harris window.
-The delay spectrum of the windowed data set shows significant reduction in the instrument response at higher delays.}
-\label{fig:window}
-\end{figure}
-
-\subsection{\textbf{Multiple reflection between the feed and the backend.}}
-Multiple reflections of the sky signal between the feed and the dish broadens the delay response of the instrument resulting in spill over of the smooth foreground power sky at higher delays.
-Another effect that have exact similar impact on the delay spectrum is the multiple reflection of the received signal between the feed output and the input of the analog backend and correlators.
+\subsection{Multiple reflection between the feed and the backend.}
+Another effect that spill over of the smooth foreground power at higher delays is the multiple reflection of the received signal between the feed output and the input of the analog backend and correlators.
 In our measurements, the feed output is connected to the VNA via a 50 feet long LMR 400 cable.
@@
 The measured return loss is shown in the figure \ref{fig:open_RL}.
-Since the electromagnetic wave travelling through a transmission line undergoes a $100\%$ reflections from an open ended transmission line, we compute the combined effect of the VNA input return loss along with the cable resistive loss from this measurement as shown in fiigure \ref{VNA_RL}.
+Since the electromagnetic wave travelling through a transmission line undergoes a $100\%$ reflections from an open ended transmission line, we compute the combined effect of the VNA input return loss along with the cable resistive loss from this measurement as shown in figure \ref{fig:open_RL}.
 This results an important system design criterion for HERA.
@@
 \centering
-\includegraphics[angle=0, width=\linewidth]{plots/open_delay.png}
+\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/open_delay.png}
 \end{minipage}
@@
 \end{figure*}
+
+\subsection{Measurement bandwidth and window function}
+Estimation of the delay spectrum by taking the Fourier transform of the measured return loss is sensitive to the bandwidth of measurements.
+Since the measurements are done in the spectral domain, measurement between two frequencies is analogous to windowing the frequency domain data by a square window function.
+In the delay domain, Fourier transform of this would result in multiple side lobes at higher delays.
+Therefore, appropriate windowing of the data is  necessary prior to taking the Fourier transform of the measured data.
+Figure \ref{fig:window} shows the delay spectrum estimated from the measured data using a square window as well as Blackman Harris window.
+Windowing the data prior to Fourier transform significantly reduces the system response higher delays.
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/ds_window.png}
+\caption{Effect of finite bandwidth on estimation of delay spectrum: Blue line shows the delay spectrum of the HERA element computed from the measured data which is band limited between 100 to 200MHz.
+Green line shows the delay spectrum estimated from the same data set after multiplying the data by a Blackman Harris window.
+The delay spectrum of the windowed data set shows significant reduction in the instrument response at higher delays.}
+\label{fig:window}
+\end{figure}
 
@@
 %\end{figure}
+\subsection{Delay spectrum of sub bands}
+The dominant term in the expression of  return loss of the HERA element in receiving mode (\ref{eq11}) is the zero delay term $(1+\Gamma_{f})$.
+As mentioned earlier, the feed reflection coefficient $\Gamma_{a}$ shows two resonances in between 100-140~MHz and 160-200~MHz.
+While the one at high frequency is a wider peak, the low frequency resonance shows a sharp feature in frequency.
+This dominates the overall shape of the delay spectrum in figure \ref{ds_feed_on_dish_trans}.\\
+Also, In HERA analysis, the 21~cm power spectrum is estimated by gridding the observed data along the line of sight distance i.e is in frequency or redshift and spatial frequency scale $k$~\citep{liu_et_al2014a}.
+At particular redshift, the bandwidth of observation is so chosen that over the corresponding $\Delta z$, the 21~cm signal does not significantly evolve.
+Typically, the the 21~cm brightness temperature fluctuation evolve over redshift scale $\Delta z>0.5$~\citep{loeb_zaldarriaga2004},~\citep{lidz_et_al2008}.
+Hence, the delay spectrum is estimated over smaller bandwidths.\\
+We estimate the instrument delay spectrum over various sub bands between 100 to 200~MHz as shown in figure \ref{ds_full_sub_band}.
+Each panel of figure \ref{ds_full_sub_band} shows the delay spectrum estimated from the returnloss measurement of the HERA element between 100-200, 100-140, 140-160, 160 to 200~MHz respectively.
+Each panel also compares the estimated delay spectrum with two simulated delay spectra.
+The blue curve is the delay spectrum estimated from the simulated return loss of the feed and the feed-dish assembly that is shown in figure \ref{ds_feed_on_dish_trans}.
+Sub band delay spectra are wider compared to full band delay spectrum.
+Shape of the resonant peaks determines the roll of rate of the delay spectrum in the range of 100-140~MHz and 160~200MHz.
+At higher frequency, our measurements closely follows the em simulations except around 120~ns where the cable reflection between the antenna and the backend manifests itself at all frequencies.
+\\
+The shaded region of each panel shows the EoR to foreground power ratio required for detection of 21~cm power spectrum at those individual delays~\citep{Thyagarajan_et_al2016}.
+This ratio is computed by using the HFSS simulation of chromatic antenna beam as well as return loss (figure \ref{RL_mag_dish}) and the sky models.
+Diffused sky foreground model is incorporated from~\citep{deolivieracosta_et_al2008} whereas the point source contribution is estimated by combining the NRAO VLA Sky Survey (NVSS) at 1.42~GHz~\citep{Condon_1998}, Sydney University Molonglo sky Survey (SUMSS) ~\citep{Bock_et_al_1999}, \citep{Mauch_et_al_2003} at 843~MHz.
+The EoR signal is simulated by using 21cmFAST \citep{Messinger_et_al2011}.
+The model parameters used by~\cite{Thyagarajan_et_al2016} for the EoR signal simulation are : Virial temperature of minimum mass of dark matter halos that host ionizing sources, $T_{vir}^{min} = 2*10^4 K$, Ionising efficiency $\eta = 20$, Mean Free Path of UV photons $R_{mfp} = 15Mpc.$ For these model parameter values, the redshift of $50\%$ reionization is predicted to be at $z = 8.5$ at 150MHz.
+Ideally, the delay response of the smooth foreground is confined at lower delays whereas the same for the EoR signal is spread across the entire delay range.
+However, due to system chromaticity of the simulated response of the HERA element, foreground spills over the higher delays.
+~\cite{Thyagarajan_et_al2016} computes the required attenuation of the foreground with respect to the EoR power available at that delay in order for a detection of the EoR signal at that delay mode.
+It is shown that for a given delay mode, the estimate of a lower $k_{\parallel}$ mode requires a higher  attenuation compared to a higher $k_{\parallel}$ mode.
+(For details ~\cite{Thyagarajan_et_al2016}).
+
+\begin{figure*}[ht]
+\begin{minipage}[b]{0.5\linewidth}
+\centering
+\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/100_200.png}
+\end{minipage}
+\hspace{0.1cm}
+\begin{minipage}[b]{0.5\linewidth}
+\centering
+\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/100_140.png}
+\end{minipage}
+\vspace{0.1cm}
+\begin{minipage}[b]{0.5\linewidth}
+\centering
+\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/140_160.png}
+\end{minipage}
+\hspace{0.1cm}
+\begin{minipage}[b]{0.5\linewidth}
+\centering
+\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/160_200.png}
+\end{minipage}
+\caption{Magnitude and phase of the return loss of the feed as simulated and measured.
+While both the measurement and the simulation shows similar resonance around $120~MHz$, the simulation shows a better matching to a 50 Ohm transmission line compared to the measurements.
+The measurement also has some small scale fluctuation due to multiple reflection of the signal at the VNA input.
+}
+\label{ds_full_sub_band}
+\end{figure*}
 
@@
 \\
-	In a related series of papers, the spatial scales of fluctuation $(k_||)$ HERA element delay response has been studied via electromagnetic simulation (deBoer et al 2016) as well as via time domain simulation (Ewall-wice et al 2016).
  Figure \ref{fig:sim_em} and \ref{fig:sim_pk} shows the measurement presented this paper in comparison with the simulations.
-Simulations and measurements are in good agreement with each other upto around $60~ns$ up to which the structures in the delay domain are mostly caused due to signal reflections in the feed structure.
+Simulations and measurements are in good agreement with each other up to around $60~ns$ up to which the structures in the delay domain are mostly caused due to signal reflections in the feed structure.
 Since the simulated return loss shows a better match of the antenna to the 50 Ohm transmission line.
@@
 \centering
-\includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/HERA_ds_fg_sim.png}
+\includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/simulation_comparison.png}
 \caption{Delay spectrum of HERA element estimated from the reflectometry measurements by a vector network analyser compared to the limits of foreground simulation (Thyagarajan et al).}
@@
 The EoR signal model is derived from the 21cmFAST (Messinger et al 2011).
-The model parameters are kept same as what is used in Thyagarajan et al 2016 and Ewall-wice et all 2016.
-The EoR model parameters are listed below.\\
- Virial temperature of minimum mass of dark matter halos that host ionizing sources, $T_{vir}^{min} = 2*10^4 K$, Ionising efficiency $\eta = 20$, Mean Free Path of UV photons $R_{mfp} = 15Mpc.$ For these model parameter values, the redshift of $50\%$ reionization is predicted to be at $z = 8.5$ at 150MHz.\\
 We use the reflectometry measurements, corrected for the antenna response in the receiving mode, to compute the visibilities (eq 13) for the given model of the foreground, the EoR and the system noise.

### 2016-09-13 DishReflectometry/Paper1_v3.tex

@@
 \begin{abstract}
-Spectral structure of the systematics has so far been the most dominant limiting factor for the experiments attempting to detect the redshifted 21~cm signal from the Epoch of Reionization (EoR).
-Systematics are specific to instruments and their direct measurement or estimation is not always straightforward.
-The Hydrogen Epoch of Reionization Array (HERA) uses the delay spectrum technique for estimating of 21~cm power spectrum.
-In a unique way, the delay spectrum technique directly translates to reflectometry in case of measuring instrumental response and allows the direct measurement of systematic effects in individual array element.
-This paper presents a detailed investigation of the instrument chromaticity of an antenna element that constitute Hydrogen Epoch of Reionization Array.
-Reflectometry measurements are carried out on a HERA dish-feed assembly between 100 to 200~MHz which studies the multiple reflections in the system that finally results in various spurious spectral response in the measured visibility.
-Reflectometry measurements shows that even without incorporation of any sophisticated analysis method, the instrument is capable of measuring the line of sight component  of the $k$ mode          $k_{\parallel} >0.2 h Mpc^{-1}$ modes of power spectrum with very low foreground contaminations around $k_{\parallel} \approx0.2 h Mpc^{-1}$.
-The performance is significantly better at the high frequency subbands of observation.
-When combined with a powerful foreground suppression method such as inverse covariance weighting, the instrument is capable of measuring the power spectrum for the spatial modes as low as $k_{\parallel} >0.1$.
-The study presented here qualifies HERA as a power spectrum instrument and serves as a fundamental method to design and measure instrument systematics for any future experiment that aims to detect the 21~cm EoR power spectrum.
+Spectral structure of the systematics has so far been the most dominant
+limiting factor for the experiments attempting to detect the redshifted 21~cm
+signal from the Epoch of Reionization (EoR). Systematics are specific to
+instruments and their direct measurement or estimation is not always
+straightforward. The Hydrogen Epoch of Reionization Array (HERA) uses the delay
+spectrum technique for estimating of 21~cm power spectrum. In a unique way, the
+delay spectrum technique directly translates to reflectometry in case of
+measuring instrumental response and allows the direct measurement of systematic
+effects in individual array element.  This paper presents a detailed
+investigation of the instrument chromaticity of an antenna element that
+constitute Hydrogen Epoch of Reionization Array. Reflectometry measurements are
+carried out on a HERA dish-feed assembly between 100 to 200~MHz which studies
+the multiple reflections in the system that finally results in various spurious
+spectral response in the measured visibility. Reflectometry measurements shows
+that even without incorporation of any sophisticated analysis method, the
+instrument is capable of measuring the line of sight component  of the $k$ mode
+$k_{\parallel} >0.2 h Mpc^{-1}$ modes of power spectrum with very low
+foreground contaminations around $k_{\parallel} \approx0.2 h Mpc^{-1}$.  The
+performance is significantly better at the high frequency subbands of
+observation. When combined with a powerful foreground suppression method such
+as inverse covariance weighting, the instrument is capable of measuring the
+power spectrum for the spatial modes as low as $k_{\parallel} >0.1$. The study
+presented here qualifies HERA as a power spectrum instrument and serves as a
+fundamental method to design and measure instrument systematics for any future
+experiment that aims to detect the 21~cm EoR power spectrum.  
 \end{abstract}
@@
 % XXX document map
-The efficacy of the techniques of foreground removal from the measured data critically limits the 21~cm power spectrum measurements.
-The delay transformation technique of foreground removal, introduced by  ~\citep{Parsons_Backer_2009},\citep{Parsons_et_al_2012}, computes the Fourier transform of the visibility measured by an interferometer and produces a spectrum, referred to as the delay spectrum hereafter, which is a function of the geometric time delay corresponding to the physical length of the baseline between two antennas.
-For the visibilities measured over a wide field across a wide frequency bandwidth, the delay spectrum consists of the instrument response, the foreground signal, and the 21cm power spectrum, hereafter referred to as the EoR signal.
+The efficacy of the techniques of foreground removal from the measured data
+critically limits the 21~cm power spectrum measurements. The delay
+transformation technique of foreground removal, introduced by
+~\citep{Parsons_Backer_2009},\citep{Parsons_et_al_2012}, computes the Fourier
+transform of the visibility measured by an interferometer and produces a
+spectrum, referred to as the delay spectrum hereafter, which is a function of
+the geometric time delay corresponding to the physical length of the baseline
+between two antennas. For the visibilities measured over a wide field across a
+wide frequency bandwidth, the delay spectrum consists of the instrument
+response, the foreground signal, and the 21cm power spectrum, hereafter
+referred to as the EoR signal.
 %The complex visibility measured by an interferometer is a convolution of the instrument response with the true sky response in the UV plane.
 Therefore, when Fourier transformed, the delay spectrum is the multiplication of the sky response with the instrument response in the delay domain.
-The technique exploits the smooth spectral characteristics of the foreground and for a widefield wide bandwidth visibility measurement by an interferometer with a baseline $b$, confines the foreground contribution to the computed delay spectrum within the largest possible time delay, $\tau = b/c$, corresponding to the given baseline length.
-Such techniques also assume a spectrally smooth instrumental response whose contribution to the measured data, much as the contribution of the smooth spectrum foreground, also has an upper bound in the delay space imposed by the largest geometric delay of the given baseline.
-Beyond this limit, for an ideal system performance, the delay spectrum would be dominated by any wideband signal across the sky with spectral and spatial fluctuations over small scales, such as the EoR signal, and therefore, could be detectable.
-The interaction between the sky signal and instrument response can alter the relative contribution of the foreground, instrument response and the EoR signal at a given delay and, thus, influence the detectability of the EoR signal.
-Such interactions may cause the foreground and systematics to spill over into higher delays and, thus, push the upper limit of the foreground and systematics contaminated delay modes to much higher delays.
-In this process, the EoR signal over large spatial scales will be lost.
-\\
-\indent The Hydrogen Epoch of Reionization Array (HERA) is a proposed array consisting of 568 14-m dishes in South Africa which will measure the 21~cm power spectrum between 100 to 200~MHz.
-In this paper, we investigate the performance of an individual HERA element and the resulting manifestation of the instrument response to the delay spectrum.
-Reflectometry measurements  are carried out across a wide bandwidth on a prototype HERA element in Green Bank, WV (Figure \ref{fig:heradish}), and the results are interpreted in light of the delay spectrum technique of power spectrum estimation and inverse covariance weighting method of foreground suppression.
-Section 2 briefly describes the delay spectrum for the ideal and non-ideal performance of a two element interferometer.
-Section 3 describes the reflectometry measurements and establishes the connection between visibility measurements and reflectometry.
-Reflectometry results are described in section 5.
-Section 6 evaluates the performance of the HERA element for detection of the 21~cm power spectrum.
+The technique exploits the smooth spectral characteristics of the foreground
+and for a widefield wide bandwidth visibility measurement by an interferometer
+with a baseline $b$, confines the foreground contribution to the computed delay
+spectrum within the largest possible time delay, $\tau = b/c$, corresponding to
+the given baseline length. Such techniques also assume a spectrally smooth
+instrumental response whose contribution to the measured data, much as the
+contribution of the smooth spectrum foreground, also has an upper bound in the
+delay space imposed by the largest geometric delay of the given baseline.
+Beyond this limit, for an ideal system performance, the delay spectrum would be
+dominated by any wideband signal across the sky with spectral and spatial
+fluctuations over small scales, such as the EoR signal, and therefore, could be
+detectable. The interaction between the sky signal and instrument response can
+alter the relative contribution of the foreground, instrument response and the
+EoR signal at a given delay and, thus, influence the detectability of the EoR
+signal. Such interactions may cause the foreground and systematics to spill
+over into higher delays and, thus, push the upper limit of the foreground and
+systematics contaminated delay modes to much higher delays. In this process,
+the EoR signal over large spatial scales will be lost. \\
+
+\indent The Hydrogen Epoch of Reionization Array (HERA) is a proposed array
+consisting of 568 14-m dishes in South Africa which will measure the 21~cm
+power spectrum between 100 to 200~MHz.
+In this paper, we investigate the performance of an individual HERA element and
+the resulting manifestation of the instrument response to the delay spectrum.
+Reflectometry measurements  are carried out across a wide bandwidth on a
+prototype HERA element in Green Bank, WV (Figure \ref{fig:heradish}), and the
+results are interpreted in light of the delay spectrum technique of power
+spectrum estimation and inverse covariance weighting method of foreground
+suppression. Section 2 briefly describes the delay spectrum for the ideal and
+non-ideal performance of a two element interferometer. Section 3 describes the
+reflectometry measurements and establishes the connection between visibility
+measurements and reflectometry. Reflectometry results are described in section
+5. Section 6 evaluates the performance of the HERA element for detection of the
+21~cm power spectrum.
+
 This paper is one in a series of four papers that studies the time and frequency domain simulation of  HERA element~\citep{Ewall-Wice_et_al2016}, ~\citep{ddboer_et_al2016},beam pattern measurements~\citep{Neben_et_al2016}, and foreground limits ~\citep{Thyagarajan_et_al2016}.
@@
 
-\indent Since both $k_{\perp}$ and $k_{\parallel}$ are functions of the delay $\tau$, corresponding to the given baseline length, the redshifted 21 cm power spectrum could be estimated from the delay spectrum of the visibility measured by an interferometer.
-The sky delay spectrum from any direction $\thhat$ is convolved with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ %defined this differently earlier
+\indent Since both $k_{\perp}$ and $k_{\parallel}$ are functions of the delay
+$\tau$, corresponding to the given baseline length, the redshifted 21 cm power
+spectrum could be estimated from the delay spectrum of the visibility measured
+by an interferometer. The sky delay spectrum from any direction $\thhat$ is
+convolved with the delay spectrum of the instrument and would be located at the
+delay $\tau = {\vec b \cdot \thhat \over c}$ %defined this differently earlier
  in the delay domain.
@@
 %The phase center is elsewhere defined as being at the center of one of the antennas.
- Hence, the sky contribution from any direction would be confined within $-\tau_{g}<\tau<\tau_{g}$.
-Due to the chromaticity of the sky signal as well as the instrument response, the delay spectrum of the sky spills over into delays with $\tau> \tau_{g}$, with a decaying amplitude [Ref to the Figure Parsons12].
-The foreground, $P_{fg}(\tau)$, which is spectrally smooth, and the 21~cm power spectrum, $P_{21}(\tau)$, which contains spectral signatures, contribute to the sky delay spectrum $P_{sky}(\tau)$.Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground, with respect to the delay spectrum of the $I_{21}$, reduces and the 21cm delay spectrum could be detectable.
+ Hence, the sky contribution from any direction would be confined within
+$-\tau_{g}<\tau<\tau_{g}$. Due to the chromaticity of the sky signal as well as
+the instrument response, the delay spectrum of the sky spills over into delays
+with $\tau> \tau_{g}$, with a decaying amplitude [Ref to the Figure Parsons12].
+The foreground, $P_{fg}(\tau)$, which is spectrally smooth, and the 21~cm power
+spectrum, $P_{21}(\tau)$, which contains spectral signatures, contribute to the
+sky delay spectrum $P_{sky}(\tau)$.Therefore, in the spill over region
+$(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground,
+with respect to the delay spectrum of the $I_{21}$, reduces and the 21cm delay
+spectrum could be detectable.
 
@@
 \section{\textbf{Effects of multiple reflections on visibility and delay spectrum}}
-The Hydrogen Epoch of Reionization Array consists of parabolic dishes which provide increased collecting area per array element compared to its predecessor experiment PAPER.
-Plane waves incident on a parabolic dish are focussed at the feed which is kept at the focal plane of the dish.
-The mismatch between the impedance of free space and the feed and transmission line results in a partial coupling of the sky signal into the feed while the rest is reflected off the feed. 
-The reflected signal illuminates the dish and most of it is reflected back into the space.
-However, a part of it reflects back and forth several times in between the feed and the vertex of the dish which is shadowed by the feed.
-Such reflections generate multiple copies of the incident sky signal of reduced strength at various delay and phase and thus produces spurious correlations in the visibilities of interferometric data.
-Identical spurious visibilities could be resulted due to reflections internal to the system causing delay space distortion.
-Therefore, it is necessary to measure and understand the instrument delay spectrum in order to qualify the system for the measurement of 21cm power spectrum.
-In this section we compute the visibility of a two element interferometer accounting for the additional reflections of the sky signal in between the feed and the dish vertex and the corresponding effects on the delay spectrum in detail.
-We assume two antennas with identical geometry and electrical parameters i.e, $\bmvolt_{1}(\thhat,\nu)=\bmvolt_{2}(\thhat,\nu) = \bmvolt(\thhat,\nu)$.
+
+The Hydrogen Epoch of Reionization Array consists of parabolic dishes which
+provide increased collecting area per array element compared to its predecessor
+experiment PAPER. Plane waves incident on a parabolic dish are focussed at the
+feed which is kept at the focal plane of the dish.  The mismatch between the
+impedance of free space and the feed and transmission line results in a partial
+coupling of the sky signal into the feed while the rest is reflected off the
+feed.  The reflected signal illuminates the dish and most of it is reflected
+back into the space.  However, a part of it reflects back and forth several
+times in between the feed and the vertex of the dish which is shadowed by the
+feed.  Such reflections generate multiple copies of the incident sky signal of
+reduced strength at various delay and phase and thus produces spurious
+correlations in the visibilities of interferometric data.  Identical spurious
+visibilities could be resulted due to reflections internal to the system
+causing delay space distortion. Therefore, it is necessary to measure and
+understand the instrument delay spectrum in order to qualify the system for the
+measurement of 21cm power spectrum.  In this section we compute the visibility
+of a two element interferometer accounting for the additional reflections of
+the sky signal in between the feed and the dish vertex and the corresponding
+effects on the delay spectrum in detail. We assume two antennas with identical
+geometry and electrical parameters i.e,
+$\bmvolt_{1}(\thhat,\nu)=\bmvolt_{2}(\thhat,\nu) = \bmvolt(\thhat,\nu)$.
+
  \subsection{Antenna Reception With Multiple Reflections}
 \label{sec:multiple}
-To examine the performance of an antenna and feed in the presence of multiple reflections, we can think of the system as a screen at a distance $F$ from a feed (see Figure \ref{fig:sys}), noting that this does ignore the sky pattern of the feed itself.
-The screen reflects a factor, $\Gamma_d$, of the voltage and transmits $(1+\Gamma_d)$ (see, {\em e.g.} Pozar).
-Similarly, the feed reflects $\Gamma_f$ and transmits $(1+\Gamma_f)$.
-The voltage pattern $\volt_{sky}$ is incident onto that system and  $(1+\Gamma_{d})(1+\Gamma_{f})$ is coupled into the cable leading from the feed.
-Additionally, however, the voltage pattern is reflected off the feed ($\Gamma_f$), then the dish ($\Gamma_d$) and subsequently $(1+\Gamma_{f})$ of it reenters the feed with a roundtrip time delay $\Delta \tau=2F/c$.
-Hence, if $v_{sky}$ is reflected $n$ times in between the feed and the dish, the net voltage entering the feed after the
-$n^{th}$ reflection may be written as:
+
+To examine the performance of an antenna and feed in the presence of multiple
+reflections, we can think of the system as a screen at a distance $F$ from a
+feed (see Figure \ref{fig:sys}), noting that this does ignore the sky pattern
+of the feed itself.  The screen reflects a factor, $\Gamma_d$, of the voltage
+and transmits $(1+\Gamma_d)$ (see, {\em e.g.} Pozar).  Similarly, the feed
+reflects $\Gamma_f$ and transmits $(1+\Gamma_f)$.  The voltage pattern
+$\volt_{sky}$ is incident onto that system and  $(1+\Gamma_{d})(1+\Gamma_{f})$
+is coupled into the cable leading from the feed.  Additionally, however, the
+voltage pattern is reflected off the feed ($\Gamma_f$), then the dish
+($\Gamma_d$) and subsequently $(1+\Gamma_{f})$ of it reenters the feed with a
+roundtrip time delay $\Delta \tau=2F/c$. Hence, if $v_{sky}$ is reflected $n$
+times in between the feed and the dish, the net voltage entering the feed after
+the $n^{th}$ reflection may be written as:
 \begin{eqnarray}
@@
 
-An accurate measurement of this quantity requires receiving $v_{sky}$ from a well calibrated, wideband source in the sky in the far field of the HERA antenna element with significant isotropic emission.
-While this condition is hard to achieve in practice, due to the reciprocity of the antenna performance in the transmission and reception mode, the right hand side of equation \ref{eq7} could be measured using the return loss measurement technique with a vector network analyzer (VNA).
-\\
+An accurate measurement of this quantity requires receiving $v_{sky}$ from a
+well calibrated, wideband source in the sky in the far field of the HERA
+antenna element with significant isotropic emission. While this condition is
+hard to achieve in practice, due to the reciprocity of the antenna performance
+in the transmission and reception mode, the right hand side of equation
+\ref{eq7} could be measured using the return loss measurement technique with a
+vector network analyzer (VNA). \\
 
@@
 
-Reflectometry measurements are carried out at the HERA element prototype in Green
-Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument response of the feed and dish assembly and characterise the performance.  HERA element consists off a $14\,m$ diameter
-parabolic reflector and a crossed-dipole pair as a feed.
-The cross dipole antenna pair is identical to the feed of the PAPER antenna which is suspended at the focal plane of the dish with the support of three vertical poles.
-HERA elements are closely spaced with centre to centre distance between two dishes are equal to the dish diameter.
-Therefore, to reduce the coupling between the adjacent dishes, the crossed dipole feed along with the back plane is encased in a cylindrical cage.
-The feed is raised and
-lowered by a three-pulley system mounted on the three poles. The focal height of the dish is $5m$.  The detail geometry and electromagnetic design of of the feed is presented in deBoer et al 2016. \\
+Reflectometry measurements are carried out at the HERA element prototype in
+Green Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument
+response of the feed and dish assembly and characterise the performance.  HERA
+element consists off a $14\,m$ diameter parabolic reflector and a
+crossed-dipole pair as a feed. The cross dipole antenna pair is identical to
+the feed of the PAPER antenna which is suspended at the focal plane of the dish
+with the support of three vertical poles. HERA elements are closely spaced with
+centre to centre distance between two dishes are equal to the dish diameter.
+Therefore, to reduce the coupling between the adjacent dishes, the crossed
+dipole feed along with the back plane is encased in a cylindrical cage. The
+feed is raised and lowered by a three-pulley system mounted on the three poles.
+The focal height of the dish is $5m$.  The detail geometry and electromagnetic
+design of of the feed is presented in deBoer et al 2016. \\
+
 %A vector network analyser is connected via a 50feet long cable at the feed output of the HERA element and the return loss $(s_{11})$ of the HERA element is measured as a function of frequencies while the feed is suspended at the focal plane of the dish.
 
- A VNA is connected to the HERA element via a 50-foot cable.
-It then transmits a broadband noise voltage, $\volt_{trans}$, and a factor $(1+\Gamma_f)$ of this voltage is radiated by the feed while the fraction $\Gamma_{f}$ returns to the VNA.
-Although the radiated signal illuminates the dish and most of it is radiated into free space, a fraction $\Gamma_d$ of this signal is reflected back towards the feed, and $(1+\Gamma_f)$ is received by the VNA.
-The received voltage, after $n$ reflections between the dish and the feed (where again $n=0$ is the first reflected signal at the reference plane), is therefore:
+ A VNA is connected to the HERA element via a 50-foot cable. It then transmits
+a broadband noise voltage, $\volt_{trans}$, and a factor $(1+\Gamma_f)$ of this
+voltage is radiated by the feed while the fraction $\Gamma_{f}$ returns to the
+VNA. Although the radiated signal illuminates the dish and most of it is
+radiated into free space, a fraction $\Gamma_d$ of this signal is reflected
+back towards the feed, and $(1+\Gamma_f)$ is received by the VNA.  The received
+voltage, after $n$ reflections between the dish and the feed (where again $n=0$
+is the first reflected signal at the reference plane), is therefore:
 
@@
 
-Comparing equations \ref{eq13} and \ref{eq2}, the cross power generated by $v_{1}$ and $v_{2}$ would have a spurious visibility response due to the mutual correlation between multiply reflected voltages represented by the second and the third term of the right hand side of equation \ref{eq13}.
-In the ideal case, $\Gamma_{f}=0$, in which case equation \ref{eq13} results in equation \ref{eq2}.
-The Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum.
-In the delay domain, visibilities contributed to by any two voltage components from two antennas with no mutual delay will be located at the delay $\tau = 0$ whereas any two voltage components from two antennas having a mutual delay of $n\Delta \tau$ will be centred at $n\Delta \tau$.
-These will broaden the width of the delay spectrum, which ultimately interferes with the 21cm power spectrum detection.
+Comparing equations \ref{eq13} and \ref{eq2}, the cross power generated by
+$v_{1}$ and $v_{2}$ would have a spurious visibility response due to the mutual
+correlation between multiply reflected voltages represented by the second and
+the third term of the right hand side of equation \ref{eq13}. In the ideal
+case, $\Gamma_{f}=0$, in which case equation \ref{eq13} results in equation
+\ref{eq2}. The Fourier transform of this visibility spectrum along the
+frequency axis results in the delay spectrum.  In the delay domain,
+visibilities contributed to by any two voltage components from two antennas
+with no mutual delay will be located at the delay $\tau = 0$ whereas any two
+voltage components from two antennas having a mutual delay of $n\Delta \tau$
+will be centred at $n\Delta \tau$. These will broaden the width of the delay
+spectrum, which ultimately interferes with the 21cm power spectrum detection.
 
@@
 Upon our assumption that two adjacent antenna elements have identical design parameters and electrical properties, this power is also a measure of the cross power or the visibility $\vis (\vec b, \nu)$ between the two antennas with a normalisation factor of $2$.
-Performance of the HERA feed and the dish-feed assembly has been simulated by the em solver "High Frequency Structural Simulator(HFSS)" using the finite element method. 
-The simulated and measured return loss of the feed, both magnitude and phase are shown in the upper panel of the figure \ref{RL_mag_dish}.
-While the simulated return loss of the feed structure shows two resonant peaks around 120 and $160~MHz$, the feed resonance occur at slightly higher frequencies.
-Notable are the difference in the shape of the resonant peaks.
-While the simulated response shows very wide resonant peaks, as expected from this dipole structures, the measured return loss of the feed has a narrow peak around its low frequency resonance.
-This feature dominates the fall off rate in the delay response of the system bandpass.
-The delay response of the feed is shown in figure \ref{ds_feed_on_dish_trans}.
+
+Performance of the HERA feed and the dish-feed assembly has been simulated by
+the em solver "High Frequency Structural Simulator(HFSS)" using the finite
+element method.  The simulated and measured return loss of the feed, both
+magnitude and phase are shown in the upper panel of the figure
+\ref{RL_mag_dish}. While the simulated return loss of the feed structure shows
+two resonant peaks around 120 and $160~MHz$, the feed resonance occur at
+slightly higher frequencies. Notable are the difference in the shape of the
+resonant peaks. While the simulated response shows very wide resonant peaks, as
+expected from this dipole structures, the measured return loss of the feed has
+a narrow peak around its low frequency resonance. This feature dominates the
+fall off rate in the delay response of the system bandpass. The delay response
+of the feed is shown in figure \ref{ds_feed_on_dish_trans}.
+
 \begin{figure*}[ht]
@@
 
-Lower panel of the figure \ref{RL_mag_dish} shows the measured return loss when the feed is suspended at the focal plane of the parabolic dish which is at $5m$ from the dish vertex.
-The measured return loss is much more complex than what is found from the simulation.
+Lower panel of the figure \ref{RL_mag_dish} shows the measured return loss when
+the feed is suspended at the focal plane of the parabolic dish which is at $5m$
+from the dish vertex. The measured return loss is much more complex than what
+is found from the simulation. 
 %To estimate the delay spectrum of the dish-feed assembly i.e one single HERA element, this measurement is first corrected to map the response of the antenna from transmitting mode to receiving mode via equation \ref{zero_delay_correction}.
 The corrected measurement is then Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{corrected_response}.
-Measurement bandwidth is kept much larger than the bandwidth of operation to achieve higher delay resolution.
-A number of systematic effects as well as mathematical artifacts that are critical to this measurement and their effects on the corresponding estimation of the delay spectrum are taken in to account in determination of the delay spectrum and described below.
+Measurement bandwidth is kept much larger than the bandwidth of operation to
+achieve higher delay resolution. A number of systematic effects as well as
+mathematical artifacts that are critical to this measurement and their effects
+on the corresponding estimation of the delay spectrum are taken in to account
+in determination of the delay spectrum and described below.
 
@@
 
-During observation, each HERA element is connected to an active balun similar to the ones used in the PAPER antenna which provides greater than 10dB return loss of power at the feed output as is achieved in the measurement presented here.These baluns are under further design improvements aiming at 10 to 20dB better impedance match between the feed and the balun than the measurements presented here.
-Our measurement is done using a vector network analyzer for which the active balun has been replaced by a passive balun.Given the antenna impedance and the 50 Ohm transmission line the measurements are done using the passive balun with a 4:1 impedance ratio.
-This measurements are conservative estimate  for both $\Gamma_{f}$ and $s_{11}$.\\
-While measuring the return loss of the dish-feed assembly, the signal transmitted by the VNA is reflected first off the feed.
-This is represented by $\Gamma_{f}$ in equation \ref{eq9}.
-This essentially represents a mismatch in between the feed and the 50 Ohm transmission line.
-In delay domain, this appears at the zero delay bin.
-The zero delay response is identical whether or not the feed is suspended on the dish.
-Therefore, we measure this response by measuring the feed return loss alone while the feed is kept on the ground facing the sky.
-This results in feed return loss alone including the surrounding cage structure but excluding the dish response.
-While $\Gamma_{f}$ fraction of incident voltage is reflected off the feed, $1+\Gamma_{f}$ fraction of the voltage is transmitted.
-In receiving mode, upon initial incidence, $\Gamma_{f}$ fraction of voltage is reflected back in to the space while $1+\Gamma_{f}$ voltage enters the feed.
-In receiving mode, in delay domain, this appears at the zero delay bin.
-The using the return loss measurement of the feed $(\Gamma_{f})$, the return loss measurement $s_{11}$ of the dish and feed assembly is corrected via equation \ref{eq11} and the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated.
+During observation, each HERA element is connected to an active balun similar
+to the ones used in the PAPER antenna which provides greater than 10dB return
+loss of power at the feed output as is achieved in the measurement presented
+here.These baluns are under further design improvements aiming at 10 to 20dB
+better impedance match between the feed and the balun than the measurements
+presented here.  Our measurement is done using a vector network analyzer for
+which the active balun has been replaced by a passive balun.Given the antenna
+impedance and the 50 Ohm transmission line the measurements are done using the
+passive balun with a 4:1 impedance ratio. This measurements are conservative
+estimate  for both $\Gamma_{f}$ and $s_{11}$.\\ While measuring the return loss
+of the dish-feed assembly, the signal transmitted by the VNA is reflected first
+off the feed. This is represented by $\Gamma_{f}$ in equation \ref{eq9}. This
+essentially represents a mismatch in between the feed and the 50 Ohm
+transmission line. In delay domain, this appears at the zero delay bin. The
+zero delay response is identical whether or not the feed is suspended on the
+dish. Therefore, we measure this response by measuring the feed return loss
+alone while the feed is kept on the ground facing the sky. This results in feed
+return loss alone including the surrounding cage structure but excluding the
+dish response. While $\Gamma_{f}$ fraction of incident voltage is reflected off
+the feed, $1+\Gamma_{f}$ fraction of the voltage is transmitted. In receiving
+mode, upon initial incidence, $\Gamma_{f}$ fraction of voltage is reflected
+back in to the space while $1+\Gamma_{f}$ voltage enters the feed. In receiving
+mode, in delay domain, this appears at the zero delay bin.  The using the
+return loss measurement of the feed $(\Gamma_{f})$, the return loss measurement
+$s_{11}$ of the dish and feed assembly is corrected via equation \ref{eq11} and
+the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated.
 
 \subsection{Dish reflections}
-Measurement equations shows the effects of multiple reflections of the sky signal between the feed and the dish.
-Any other reflections off the feed structure and/or any other part of the dish-feed assembly would appear at arbitrary delays.
-The estimated delay spectrum of the instrument is collectively contributed by all the reflections.
-Delay spectrum estimated from the return loss measurement of the feed alone,  provides the lowest limit of the delay spectrum of the instrument considering there is no multiple reflections in between the feed and the dish.
-From figure \ref{ds_feed_on_dish_trans}, at lower delays, the reflections are dominated by the feed structure.
-Therefore, the delay spectrum in both the cases follow each other.
-Since the distance between the feed and the dish is 5 m, the roundtrip delay between the dish and the feed as about $30~ns$.
-Hence, the dish reflection is expected to manifest themselves at an integral multiple of $30~ns$.
-The diameter of the feed cavity is $172~cm$  that results in signal reflections every integral multiple of $\approx2.86~ns$.
-The combined effect of feed and the dish dominates the delay spectrum up to $\> 50nS$ after which the dish reflections starts to dominate and the two delay spectrum deviates from each other.
-With some manipulation of the equation \ref{eq10}, we can estimate the dish return loss $\Gamma_{d}$ and corresponding delay spectrum as shown in the figure \ref{dish_delay_spectrum}.
+
+Measurement equations shows the effects of multiple reflections of the sky
+signal between the feed and the dish. Any other reflections off the feed
+structure and/or any other part of the dish-feed assembly would appear at
+arbitrary delays. The estimated delay spectrum of the instrument is
+collectively contributed by all the reflections. Delay spectrum estimated from
+the return loss measurement of the feed alone,  provides the lowest limit of
+the delay spectrum of the instrument considering there is no multiple
+reflections in between the feed and the dish.  From figure
+\ref{ds_feed_on_dish_trans}, at lower delays, the reflections are dominated by
+the feed structure. Therefore, the delay spectrum in both the cases follow each
+other. Since the distance between the feed and the dish is 5 m, the roundtrip
+delay between the dish and the feed as about $30~ns$. Hence, the dish
+reflection is expected to manifest themselves at an integral multiple of
+$30~ns$. The diameter of the feed cavity is $172~cm$  that results in signal
+reflections every integral multiple of $\approx2.86~ns$. The combined effect of
+feed and the dish dominates the delay spectrum up to $\> 50nS$ after which the
+dish reflections starts to dominate and the two delay spectrum deviates from
+each other. With some manipulation of the equation \ref{eq10}, we can estimate
+the dish return loss $\Gamma_{d}$ and corresponding delay spectrum as shown in
+the figure \ref{dish_delay_spectrum}.
 
 \subsection{Multiple reflection between the feed and the backend.}
-Another effect that spill over of the smooth foreground power at higher delays is the multiple reflection of the received signal between the feed output and the input of the analog backend and correlators.
-In our measurements, the feed output is connected to the VNA via a 50 feet long LMR 400 cable.
-This length correspond to a delay of $\approx 120~nS$ for the signals travelling through the cable.
-The delay spectrum of both feed and feed-dish assembly shows an enhanced feature at this delay indicating a reflection from the VNA input.
-We measure the VNA input reflections by disconnecting the feed and connecting an open load at the feed input of the cable.
-The measured return loss is shown in the figure \ref{fig:open_RL}.
-Since the electromagnetic wave travelling through a transmission line undergoes a $100\%$ reflections from an open ended transmission line, we compute the combined effect of the VNA input return loss along with the cable resistive loss from this measurement as shown in figure \ref{fig:open_RL}.
-This results an important system design criterion for HERA.
-The VNA input return loss is found to be at a level of $-14$ to $-30dB$ across the measurement band.
-This is consistent with the matched provided by the commercially available RF connectors that are commonly used.
-This manifests itself in a peak in the delay spectrum which is $50~dB$ above the measurement noise floor.
-The delays at which this effect becomes dominant depends on the length of the cable.
-Due to finite return loss at the input of the backends, this effect will be present in all the observations and thus would impact the instrument delay spectrum.
-However, its effect could be reduced below the level where the foreground  achieving a return loss at the backend input is greater than at least $-30~dB$.
+
+Another effect that spill over of the smooth foreground power at higher delays
+is the multiple reflection of the received signal between the feed output and
+the input of the analog backend and correlators. In our measurements, the feed
+output is connected to the VNA via a 50 feet long LMR 400 cable. This length
+correspond to a delay of $\approx 120~nS$ for the signals travelling through
+the cable. The delay spectrum of both feed and feed-dish assembly shows an
+enhanced feature at this delay indicating a reflection from the VNA input. We
+measure the VNA input reflections by disconnecting the feed and connecting an
+open load at the feed input of the cable. The measured return loss is shown in
+the figure \ref{fig:open_RL}. Since the electromagnetic wave travelling through
+a transmission line undergoes a $100\%$ reflections from an open ended
+transmission line, we compute the combined effect of the VNA input return loss
+along with the cable resistive loss from this measurement as shown in figure
+\ref{fig:open_RL}. This results an important system design criterion for HERA.
+The VNA input return loss is found to be at a level of $-14$ to $-30dB$ across
+the measurement band. This is consistent with the matched provided by the
+commercially available RF connectors that are commonly used. This manifests
+itself in a peak in the delay spectrum which is $50~dB$ above the measurement
+noise floor. The delays at which this effect becomes dominant depends on the
+length of the cable. Due to finite return loss at the input of the backends,
+this effect will be present in all the observations and thus would impact the
+instrument delay spectrum. However, its effect could be reduced below the level
+where the foreground  achieving a return loss at the backend input is greater
+than at least $-30~dB$.
 
@@
 \subsection{Measurement bandwidth and window function}
-Estimation of the delay spectrum by taking the Fourier transform of the measured return loss is sensitive to the bandwidth of measurements.
-Since the measurements are done in the spectral domain, measurement between two frequencies is analogous to windowing the frequency domain data by a square window function.
-In the delay domain, Fourier transform of this would result in multiple side lobes at higher delays.
-Therefore, appropriate windowing of the data is  necessary prior to taking the Fourier transform of the measured data.
-Figure \ref{fig:window} shows the delay spectrum estimated from the measured data using a square window as well as Blackman Harris window.
-Windowing the data prior to Fourier transform significantly reduces the system response higher delays.
+
+Estimation of the delay spectrum by taking the Fourier transform of the
+measured return loss is sensitive to the bandwidth of measurements. Since the
+measurements are done in the spectral domain, measurement between two
+frequencies is analogous to windowing the frequency domain data by a square
+window function. In the delay domain, Fourier transform of this would result in
+multiple side lobes at higher delays. Therefore, appropriate windowing of the
+data is  necessary prior to taking the Fourier transform of the measured data.
+Figure \ref{fig:window} shows the delay spectrum estimated from the measured
+data using a square window as well as Blackman Harris window. Windowing the
+data prior to Fourier transform significantly reduces the system response
+higher delays.
+
 \begin{figure}
@@
 \subsection{Delay spectrum of sub bands}
-The dominant term in the expression of  return loss of the HERA element in receiving mode (\ref{eq11}) is the zero delay term $(1+\Gamma_{f})$.
-As mentioned earlier, the feed reflection coefficient $\Gamma_{a}$ shows two resonances in between 100-140~MHz and 160-200~MHz.
-While the one at high frequency is a wider peak, the low frequency resonance shows a sharp feature in frequency.
-This dominates the overall shape of the delay spectrum in figure \ref{ds_feed_on_dish_trans}.\\
-Also, In HERA analysis, the 21~cm power spectrum is estimated by gridding the observed data along the line of sight distance i.e is in frequency or redshift and spatial frequency scale $k$~\citep{liu_et_al2014a}.
-At particular redshift, the bandwidth of observation is so chosen that over the corresponding $\Delta z$, the 21~cm signal does not significantly evolve.
-Typically, the the 21~cm brightness temperature fluctuation evolve over redshift scale $\Delta z>0.5$~\citep{loeb_zaldarriaga2004},~\citep{lidz_et_al2008}.
-Hence, the delay spectrum is estimated over smaller bandwidths.\\
-We estimate the instrument delay spectrum over various sub bands between 100 to 200~MHz as shown in figure \ref{ds_full_sub_band}.
-Each panel of figure \ref{ds_full_sub_band} shows the delay spectrum estimated from the returnloss measurement of the HERA element between 100-200, 100-140, 140-160, 160 to 200~MHz respectively.
-Each panel also compares the estimated delay spectrum with two simulated delay spectra.
-The blue curve is the delay spectrum estimated from the simulated return loss of the feed and the feed-dish assembly that is shown in figure \ref{ds_feed_on_dish_trans}.
-Sub band delay spectra are wider compared to full band delay spectrum.
-Shape of the resonant peaks determines the roll of rate of the delay spectrum in the range of 100-140~MHz and 160~200MHz.
-At higher frequency, our measurements closely follows the em simulations except around 120~ns where the cable reflection between the antenna and the backend manifests itself at all frequencies.
-\\
-The shaded region of each panel shows the EoR to foreground power ratio required for detection of 21~cm power spectrum at those individual delays~\citep{Thyagarajan_et_al2016}.
-This ratio is computed by using the HFSS simulation of chromatic antenna beam as well as return loss (figure \ref{RL_mag_dish}) and the sky models.
-Diffused sky foreground model is incorporated from~\citep{deolivieracosta_et_al2008} whereas the point source contribution is estimated by combining the NRAO VLA Sky Survey (NVSS) at 1.42~GHz~\citep{Condon_1998}, Sydney University Molonglo sky Survey (SUMSS) ~\citep{Bock_et_al_1999}, \citep{Mauch_et_al_2003} at 843~MHz.
-The EoR signal is simulated by using 21cmFAST \citep{Messinger_et_al2011}.
-The model parameters used by~\cite{Thyagarajan_et_al2016} for the EoR signal simulation are : Virial temperature of minimum mass of dark matter halos that host ionizing sources, $T_{vir}^{min} = 2*10^4 K$, Ionising efficiency $\eta = 20$, Mean Free Path of UV photons $R_{mfp} = 15Mpc.$ For these model parameter values, the redshift of $50\%$ reionization is predicted to be at $z = 8.5$ at 150MHz.
-Ideally, the delay response of the smooth foreground is confined at lower delays whereas the same for the EoR signal is spread across the entire delay range.
-However, due to system chromaticity of the simulated response of the HERA element, foreground spills over the higher delays.
-~\cite{Thyagarajan_et_al2016} computes the required attenuation of the foreground with respect to the EoR power available at that delay in order for a detection of the EoR signal at that delay mode.
-It is shown that for a given delay mode, the estimate of a lower $k_{\parallel}$ mode requires a higher  attenuation compared to a higher $k_{\parallel}$ mode.
-(For details ~\cite{Thyagarajan_et_al2016}).
+
+The dominant term in the expression of  return loss of the HERA element in
+receiving mode (\ref{eq11}) is the zero delay term $(1+\Gamma_{f})$. As
+mentioned earlier, the feed reflection coefficient $\Gamma_{a}$ shows two
+resonances in between 100-140~MHz and 160-200~MHz. While the one at high
+frequency is a wider peak, the low frequency resonance shows a sharp feature in
+frequency. This dominates the overall shape of the delay spectrum in figure
+\ref{ds_feed_on_dish_trans}.\\ Also, In HERA analysis, the 21~cm power spectrum
+is estimated by gridding the observed data along the line of sight distance i.e
+is in frequency or redshift and spatial frequency scale
+$k$~\citep{liu_et_al2014a}. At particular redshift, the bandwidth of
+observation is so chosen that over the corresponding $\Delta z$, the 21~cm
+signal does not significantly evolve. Typically, the the 21~cm brightness
+temperature fluctuation evolve over redshift scale $\Delta
+z>0.5$~\citep{loeb_zaldarriaga2004},~\citep{lidz_et_al2008}. Hence, the delay
+spectrum is estimated over smaller bandwidths.\\ We estimate the instrument
+delay spectrum over various sub bands between 100 to 200~MHz as shown in figure
+\ref{ds_full_sub_band}. Each panel of figure \ref{ds_full_sub_band} shows the
+delay spectrum estimated from the returnloss measurement of the HERA element
+between 100-200, 100-140, 140-160, 160 to 200~MHz respectively. Each panel also
+compares the estimated delay spectrum with two simulated delay spectra. The
+blue curve is the delay spectrum estimated from the simulated return loss of
+the feed and the feed-dish assembly that is shown in figure
+\ref{ds_feed_on_dish_trans}. Sub band delay spectra are wider compared to full
+band delay spectrum.  Shape of the resonant peaks determines the roll of rate
+of the delay spectrum in the range of 100-140~MHz and 160~200MHz. At higher
+frequency, our measurements closely follows the em simulations except around
+120~ns where the cable reflection between the antenna and the backend manifests
+itself at all frequencies. \\ The shaded region of each panel shows the EoR to
+foreground power ratio required for detection of 21~cm power spectrum at those
+individual delays~\citep{Thyagarajan_et_al2016}. This ratio is computed by
+using the HFSS simulation of chromatic antenna beam as well as return loss
+(figure \ref{RL_mag_dish}) and the sky models. Diffused sky foreground model is
+incorporated from~\citep{deolivieracosta_et_al2008} whereas the point source
+contribution is estimated by combining the NRAO VLA Sky Survey (NVSS) at
+1.42~GHz~\citep{Condon_1998}, Sydney University Molonglo sky Survey (SUMSS)
+~\citep{Bock_et_al_1999}, \citep{Mauch_et_al_2003} at 843~MHz. The EoR signal
+is simulated by using 21cmFAST \citep{Messinger_et_al2011}. The model
+parameters used by~\cite{Thyagarajan_et_al2016} for the EoR signal simulation
+are : Virial temperature of minimum mass of dark matter halos that host
+ionizing sources, $T_{vir}^{min} = 2*10^4 K$, Ionising efficiency $\eta = 20$,
+Mean Free Path of UV photons $R_{mfp} = 15Mpc.$ For these model parameter
+values, the redshift of $50\%$ reionization is predicted to be at $z = 8.5$ at
+150MHz.  Ideally, the delay response of the smooth foreground is confined at
+lower delays whereas the same for the EoR signal is spread across the entire
+delay range. However, due to system chromaticity of the simulated response of
+the HERA element, foreground spills over the higher delays.
+~\cite{Thyagarajan_et_al2016} computes the required attenuation of the
+foreground with respect to the EoR power available at that delay in order for a
+detection of the EoR signal at that delay mode. It is shown that for a given
+delay mode, the estimate of a lower $k_{\parallel}$ mode requires a higher
+attenuation compared to a higher $k_{\parallel}$ mode. (For details
+~\cite{Thyagarajan_et_al2016}).
 
@@
 
-21cm power spectrum measurements are limited by challenges posed by the low frequency radio foreground that is order of magnitude brighter than the expected power spectrum amplitude.
-While PAPER has established the till date the most stringent upper limit on the 21cm power spectrum measurement, the need for increased sensitivity called for increased collecting area per PAPER element.
-This has driven to the parabolic reflector antenna based design of the PAPER successor HERA where essentially the PAPER antenna with minor modification of the ground plane-side plane assembly works as the feed and thus having larger collecting area per element.
-Additional limitations on PAPER and its contemporaries are imposed by the spectral structure of the system response.
-Sky signal is frequency modulated by the system bandpass response.
-In delay spectrum technique of 21cm power spectrum estimation, sky signal is convolved with the system response in the delay domain.
-In this process of convolution, the frequency dependent system response with rapid frequency variation results in spreading of the smooth spectrum foreground of the sky signal to the delays in which EoR power spectrum is to be estimated.
-This essentially limits the capacity of any experiment to probe the smaller spatial scales of fluctuations.
-\\
- Figure \ref{fig:sim_em} and \ref{fig:sim_pk} shows the measurement presented this paper in comparison with the simulations.
-Simulations and measurements are in good agreement with each other up to around $60~ns$ up to which the structures in the delay domain are mostly caused due to signal reflections in the feed structure.
-Since the simulated return loss shows a better match of the antenna to the 50 Ohm transmission line.
-At zero delay , in case of simulation, almost $100\%$ of the sky signal is received whereas in case of measurements, this match is found to be less than $5~dB$ resulting in partial coupling of the sky signal to the system.
-Given all the reflections unaltered, if the matching in between the feed and the transmission line is improved by about $10~dB$, which is achievable in reality, the delay spectrum would improve substantially.
-This is plotted in grey.
-The work is currently under progress to improve the feed return loss at least by  $10dB$ (Eloy et al 2016 in prep?).
-Beyond $60~nS$ other multiple reflections manifests themselves at higher delays and the delay spectrum of the measurement and simulations begin to deviate from each other.\\
-Thyagarajan et al 2016) has presented the detailed sensitivity calculations of HERA is using a comprehensive foreground model as well as model for EoR power spectrum for various simulated antenna element response.
-The sensitivity is quantified as a ratio of EoR signal power to the foreground power at various $\bold k_{\parallel}$ mode i.e at various delays.
-The theoretical limits for the level of foreground attenuation required relative to the EoR signal in order to reduce the foreground contaminations at the delay modes significant for power spectrum measurements are shown for three different lower limits of $k_\parallel$ values.
-The response is computed for the redshift of $z=8.47$ at frequency $150~MHz$ over a bandwidth of $10~MHz$.
-This simulation shows the effect of chromatic antenna response and how that contaminates the delay modes beyond the horizon limit.
-Thus, this establishes a very stringent limits of required foreground attenuation relative to EoR signal which demands almost an ideal system performance.
-\\
+21cm power spectrum measurements are limited by challenges posed by the low
+frequency radio foreground that is order of magnitude brighter than the
+expected power spectrum amplitude. While PAPER has established the till date
+the most stringent upper limit on the 21cm power spectrum measurement, the need
+for increased sensitivity called for increased collecting area per PAPER
+element. This has driven to the parabolic reflector antenna based design of the
+PAPER successor HERA where essentially the PAPER antenna with minor
+modification of the ground plane-side plane assembly works as the feed and thus
+having larger collecting area per element. Additional limitations on PAPER and
+its contemporaries are imposed by the spectral structure of the system
+response. Sky signal is frequency modulated by the system bandpass response. In
+delay spectrum technique of 21cm power spectrum estimation, sky signal is
+convolved with the system response in the delay domain. In this process of
+convolution, the frequency dependent system response with rapid frequency
+variation results in spreading of the smooth spectrum foreground of the sky
+signal to the delays in which EoR power spectrum is to be estimated. This
+essentially limits the capacity of any experiment to probe the smaller spatial
+scales of fluctuations. \\ Figure \ref{fig:sim_em} and \ref{fig:sim_pk} shows
+the measurement presented this paper in comparison with the simulations.
+Simulations and measurements are in good agreement with each other up to around
+$60~ns$ up to which the structures in the delay domain are mostly caused due to
+signal reflections in the feed structure. Since the simulated return loss shows
+a better match of the antenna to the 50 Ohm transmission line. At zero delay ,
+in case of simulation, almost $100\%$ of the sky signal is received whereas in
+case of measurements, this match is found to be less than $5~dB$ resulting in
+partial coupling of the sky signal to the system. Given all the reflections
+unaltered, if the matching in between the feed and the transmission line is
+improved by about $10~dB$, which is achievable in reality, the delay spectrum
+would improve substantially. This is plotted in grey. The work is currently
+under progress to improve the feed return loss at least by  $10dB$ (Eloy et al
+2016 in prep?). Beyond $60~nS$ other multiple reflections manifests themselves
+at higher delays and the delay spectrum of the measurement and simulations
+begin to deviate from each other.\\ Thyagarajan et al 2016) has presented the
+detailed sensitivity calculations of HERA is using a comprehensive foreground
+model as well as model for EoR power spectrum for various simulated antenna
+element response. The sensitivity is quantified as a ratio of EoR signal power
+to the foreground power at various $\bold k_{\parallel}$ mode i.e at various
+delays. The theoretical limits for the level of foreground attenuation required
+relative to the EoR signal in order to reduce the foreground contaminations at
+the delay modes significant for power spectrum measurements are shown for three
+different lower limits of $k_\parallel$ values.  The response is computed for
+the redshift of $z=8.47$ at frequency $150~MHz$ over a bandwidth of $10~MHz$.
+This simulation shows the effect of chromatic antenna response and how that
+contaminates the delay modes beyond the horizon limit. Thus, this establishes a
+very stringent limits of required foreground attenuation relative to EoR signal
+which demands almost an ideal system performance. \\
+
 %As shown in section (), multiple reflection in the antenna system generates multiple copies of the sky signal and thus results in additional foreground contaminations in the delay modes where EOR power spectrum is measurable in case of no reflections.
@@
 \subsection{Power spectrum estimation:}
-HERA power spectrum estimation is done using the Optimal Quadratic Estimator (OQE) formalism that has been outlined in extensive detail in (Liu and Tegmark 2011), (Dillon et al 2013), (Liu et al 2014a,2014b), (Trott et al 2016), (Ali et al 2015).
-We briefly  describe the OQE formalism here.\\
-HERA instrument aims at measuring the redshifted 21~cm power spectrum $P_{21}(k_\perp,k_\parallel)$, conventionally written as, 
+
+HERA power spectrum estimation is done using the Optimal Quadratic Estimator
+(OQE) formalism that has been outlined in extensive detail in (Liu and Tegmark
+2011), (Dillon et al 2013), (Liu et al 2014a,2014b), (Trott et al 2016), (Ali
+et al 2015). We briefly  describe the OQE formalism here.\\ HERA instrument
+aims at measuring the redshifted 21~cm power spectrum
+$P_{21}(k_\perp,k_\parallel)$, conventionally written as,
+
 \begin{equation}
@@
 \subsection{Inverse covariance weighting: revised delay spectrum limit}
-The inverse variance weighting method is a method of aggregating two or more random variable to minimize the variance in their weighted average.
-In our case, the measured visibility is contributed by EoR, foreground and instrumental noise.
-Hence, the estimate of any of the constituent signal would benefit from if the measured data is weighted by the covariance of the individual components.
-This is reflected in our choice of the matrix $E^{\alpha}$.
-$E^{\alpha} = {1 \over 2} C^{-1} Q_{\alpha} C^{-1}$ represents a weighting of the data vector $\bold x$ by inverse of its covariance.
-This results in the smallest vertical error bar in the power spectrum estimate $\hat p_{\alpha}$ (Reference Liu 2011).
-However, there no definite way to know the covariance of individual signal components prior to estimating them.
-In practice, the total covariance matrix $C$ is computed from the measured visibilities.
-It is a sum of covariances of the foreground, instrumental noise and the EoR signals.
-The highest covariance is rendered by the signal which is correlated over various frequency channels at all frequencies such as foreground.
-Hence, weighting the measured visibility by the inverse of the covariance results in order of magnitude reduction of foreground power against the EoR signal \\
- Combining the inverse covariance weighting formalism with the foreground simulation of Thyagarajan et al 2016, we derive a new limit on required foreground attenuation with respect to the EoR signal, required for power spectrum estimation using HERA measurements.
-The foreground model of Thyagarajan et al (2015a) is adopted wherein the diffused emission is accounted for using de Oliviera-Costa et al.
-2008 and the point sources are modeled using NRAO VLA sky survey at 1.42 GHz(NVSS, Condon et al 1998) and Sydney University Molonglo Sky Survey (SUMSS; Bock et al 199;Mauch et al 2003.) at 843 MHz.
-The EoR signal model is derived from the 21cmFAST (Messinger et al 2011).
-We use the reflectometry measurements, corrected for the antenna response in the receiving mode, to compute the visibilities (eq 13) for the given model of the foreground, the EoR and the system noise.
-These visibilities formed the complex data vector $\bold x$.
-We compute the covariance matrix $C$ from the simulated data.
-$\bold x$ is then multiplied by the inverse of the covariance matrix.
-This step essentially weighs down the foreground contribution to the measured data.
-Once Fourier transformed, the delay spectrum of the simulated data is constituted by linear super position of the delay spectrum of the foreground, the EoR signal.
-We again compute the EoR to foreground power ratio which is now smaller than what is estimated in Thyagarajan et al 2016 as shown in fig:\ref{fig:sim_fg_revised}.
+
+The inverse variance weighting method is a method of aggregating two or more
+random variable to minimize the variance in their weighted average. In our
+case, the measured visibility is contributed by EoR, foreground and
+instrumental noise. Hence, the estimate of any of the constituent signal would
+benefit from if the measured data is weighted by the covariance of the
+individual components. This is reflected in our choice of the matrix
+$E^{\alpha}$.  $E^{\alpha} = {1 \over 2} C^{-1} Q_{\alpha} C^{-1}$ represents a
+weighting of the data vector $\bold x$ by inverse of its covariance. This
+results in the smallest vertical error bar in the power spectrum estimate $\hat
+p_{\alpha}$ (Reference Liu 2011).  However, there no definite way to know the
+covariance of individual signal components prior to estimating them. In
+practice, the total covariance matrix $C$ is computed from the measured
+visibilities. It is a sum of covariances of the foreground, instrumental noise
+and the EoR signals. The highest covariance is rendered by the signal which is
+correlated over various frequency channels at all frequencies such as
+foreground. Hence, weighting the measured visibility by the inverse of the
+covariance results in order of magnitude reduction of foreground power against
+the EoR signal \\ Combining the inverse covariance weighting formalism with the
+foreground simulation of Thyagarajan et al 2016, we derive a new limit on
+required foreground attenuation with respect to the EoR signal, required for
+power spectrum estimation using HERA measurements. The foreground model of
+Thyagarajan et al (2015a) is adopted wherein the diffused emission is accounted
+for using de Oliviera-Costa et al. 2008 and the point sources are modeled using
+NRAO VLA sky survey at 1.42 GHz(NVSS, Condon et al 1998) and Sydney University
+Molonglo Sky Survey (SUMSS; Bock et al 199;Mauch et al 2003.) at 843 MHz. The
+EoR signal model is derived from the 21cmFAST (Messinger et al 2011). We use
+the reflectometry measurements, corrected for the antenna response in the
+receiving mode, to compute the visibilities (eq 13) for the given model of the
+foreground, the EoR and the system noise. These visibilities formed the complex
+data vector $\bold x$. We compute the covariance matrix $C$ from the simulated
+data. $\bold x$ is then multiplied by the inverse of the covariance matrix.
+This step essentially weighs down the foreground contribution to the measured
+data. Once Fourier transformed, the delay spectrum of the simulated data is
+constituted by linear super position of the delay spectrum of the foreground,
+the EoR signal.  We again compute the EoR to foreground power ratio which is
+now smaller than what is estimated in Thyagarajan et al 2016 as shown in
+fig:\ref{fig:sim_fg_revised}.
+
 \begin{figure*}[ht]
@@
 \section{\textbf{Conclusion}}
-The interplay between the extremely bright sky signal with the system response has remained somewhat undermined for the first generation 21cm experiments such as MWA, LOFAR, PAPER.
-With the theory of redshifted 21cm experiments have very well evolved, it is absolute necessity now to quantify the instrumental limits of these measurement in order to produce a believable power spectrum estimates.
-In this paper, we studied the performance of a HERA element in both frequency as well as delay domain.
-The effects of multiple reflections  in a HERA feed-dish assembly is investigated in detail and their effects on the measured visibility as well as delay spectrum is estimated.
-The delay-domain performance of the HERA dish is central to HERA's function as a power spectrum instrument.
-Reflectometry measurements characterised HERA's performance in this domain, and as Equation \ref{eq10} shows, these measurements must be adjusted for a difference in transmission/reflection
-at the first feed encounter in order to be interpreted as the delay response of a feed relative to an incident
-plane wave from the sky.  It is also shown that the choice of windowing function is critical for accurately measuring the
-antenna delay response at higher delays, where sidelobes from much higher amplitude responses at small delays can easily
-dominate.  Blackman-Harris window is found to be generally adequate while square windowing functions are not.
-Given the critical nature of the windowing function, it is recommended that all reflectometry measurements be performed in the
-frequency domain, so that the data could be Fourier transformed with the appropriate window.
-The delay spectrum estimates are then compared with the electromagnetic as well as time domain simulation of the HERA element~\citep{Ewall-Wice_et_al2016}, ~\citep{ddboer_et_al2016}.
-The same is then compared with the foreground simulation of~\cite{Thyagarajan_et_al2015}.
-The performance is also evaluated in the light of HERA power spectrum estimation technique using inverse covariance weighting formalism.
-Taken all together, we summarise that the HERA antenna element, with a PAPER-style crossed dipole feed and cylindrical cage the instrument delay spectrum very well satisfies the criteria necessary to meet its science goal.
+
+The interplay between the extremely bright sky signal with the system response
+has remained somewhat undermined for the first generation 21cm experiments such
+as MWA, LOFAR, PAPER. With the theory of redshifted 21cm experiments have very
+well evolved, it is absolute necessity now to quantify the instrumental limits
+of these measurement in order to produce a believable power spectrum estimates.
+In this paper, we studied the performance of a HERA element in both frequency
+as well as delay domain. The effects of multiple reflections  in a HERA
+feed-dish assembly is investigated in detail and their effects on the measured
+visibility as well as delay spectrum is estimated.  The delay-domain
+performance of the HERA dish is central to HERA's function as a power spectrum
+instrument. Reflectometry measurements characterised HERA's performance in this
+domain, and as Equation \ref{eq10} shows, these measurements must be adjusted
+for a difference in transmission/reflection at the first feed encounter in
+order to be interpreted as the delay response of a feed relative to an incident
+plane wave from the sky.  It is also shown that the choice of windowing
+function is critical for accurately measuring the antenna delay response at
+higher delays, where sidelobes from much higher amplitude responses at small
+delays can easily dominate.  Blackman-Harris window is found to be generally
+adequate while square windowing functions are not.  Given the critical nature
+of the windowing function, it is recommended that all reflectometry
+measurements be performed in the frequency domain, so that the data could be
+Fourier transformed with the appropriate window.  The delay spectrum estimates
+are then compared with the electromagnetic as well as time domain simulation of
+the HERA element~\citep{Ewall-Wice_et_al2016}, ~\citep{ddboer_et_al2016}. The
+same is then compared with the foreground simulation
+of~\cite{Thyagarajan_et_al2015}. The performance is also evaluated in the light
+of HERA power spectrum estimation technique using inverse covariance weighting
+formalism.  Taken all together, we summarise that the HERA antenna element,
+with a PAPER-style crossed dipole feed and cylindrical cage the instrument
+delay spectrum very well satisfies the criteria necessary to meet its science
+goal.
 

### 2016-09-13 DishReflectometry/Paper1_v3.tex
Edits to abstract

@@
 \begin{abstract}
-Spectral structure of the systematics has so far been the most dominant
+Spectral structure from instrumental systematics is the current
 limiting factor for the experiments attempting to detect the redshifted 21~cm
-signal from the Epoch of Reionization (EoR). Systematics are specific to
-instruments and their direct measurement or estimation is not always
-straightforward. The Hydrogen Epoch of Reionization Array (HERA) uses the delay
-spectrum technique for estimating of 21~cm power spectrum. In a unique way, the
-delay spectrum technique directly translates to reflectometry in case of
-measuring instrumental response and allows the direct measurement of systematic
-effects in individual array element.  This paper presents a detailed
-investigation of the instrument chromaticity of an antenna element that
-constitute Hydrogen Epoch of Reionization Array. Reflectometry measurements are
-carried out on a HERA dish-feed assembly between 100 to 200~MHz which studies
-the multiple reflections in the system that finally results in various spurious
-spectral response in the measured visibility. Reflectometry measurements shows
-that even without incorporation of any sophisticated analysis method, the
-instrument is capable of measuring the line of sight component  of the $k$ mode
-$k_{\parallel} >0.2 h Mpc^{-1}$ modes of power spectrum with very low
-foreground contaminations around $k_{\parallel} \approx0.2 h Mpc^{-1}$.  The
-performance is significantly better at the high frequency subbands of
-observation. When combined with a powerful foreground suppression method such
-as inverse covariance weighting, the instrument is capable of measuring the
-power spectrum for the spatial modes as low as $k_{\parallel} >0.1$. The study
-presented here qualifies HERA as a power spectrum instrument and serves as a
-fundamental method to design and measure instrument systematics for any future
-experiment that aims to detect the 21~cm EoR power spectrum.  
+signal from the Epoch of Reionization (EoR). 
+Recent advances in the delay spectrum methodology for measuring the
+21~cm EoR power spectrum have brought new attention to the impact that
+the frequency performance of antenna elements has on the viability of
+making this challenging measurement.
+%Systematics are specific to
+%instruments and their direct measurement or estimation is not always
+%straightforward. 
+%The Hydrogen Epoch of Reionization Array (HERA) uses the delay
+%spectrum technique for estimating of 21~cm power spectrum. 
+In particular, the delay spectrum formalism provides a relationship
+between time-domain reflectrometry profiles that can be directly
+measured with a vector network analyzer (VNA) and the power spectrum modes accessible
+to a 21~cm EoR experiment.
+%In a unique way, the
+%delay spectrum technique directly translates to reflectometry in case of
+%measuring instrumental response and allows the direct measurement of systematic
+%effects in individual array element.  
+In this paper, we derive the explicit relationship between $S_{11}$ measurements
+made by a VNA and the corresponding convolving kernel in delay space.
+Using this formalism, we examine
+the spectral chromaticity of the prototype antenna elements that
+constitute Hydrogen Epoch of Reionization Array (HERA) 
+between 100 and 200~MHz.
+These reflectometry measurements exhibit spurious chromatic structure relative
+to electromagnetic simulations, but we find 
+that even without compensating for this structure, the antenna element
+will support measuring $k$ modes with line-of-sight components 
+$k_{\parallel} >0.2 h~Mpc^{-1}$.  
+%The performance is significantly better at the high frequency subbands of observation. 
+When combined with the powerful foreground weighting methods used in optimal
+quadratic estimation,
+HERA should be capable of measuring the
+power spectrum at $k_{\parallel} > 0.1$. This study
+qualifies HERA as a power spectrum instrument and serves as an
+important method for designing and measuring instrumental systematics for any future
+experiment aiming to detect the 21~cm EoR power spectrum.  
 \end{abstract}

### 2016-09-13 DishReflectometry/Paper1_v3.tex
Tweaks to abstract

@@
 21~cm EoR power spectrum have brought new attention to the impact that
-the frequency performance of antenna elements has on the viability of
+an antenna's frequency performance has on the viability of
 making this challenging measurement.
@@
 %spectrum technique for estimating of 21~cm power spectrum. 
-In particular, the delay spectrum formalism provides a relationship
+In particular, it provides straightforward relationship
 between time-domain reflectrometry profiles that can be directly
@@
 In this paper, we derive the explicit relationship between $S_{11}$ measurements
-made by a VNA and the corresponding convolving kernel in delay space.
+made by a VNA and the extent of sidelobes of bright foregrounds in delay space.
 Using this formalism, we examine
@@
 between 100 and 200~MHz.
-These reflectometry measurements exhibit spurious chromatic structure relative
+These reflectometry measurements exhibit spurious structure relative
 to electromagnetic simulations, but we find 
 that even without compensating for this structure, the antenna element
-will support measuring $k$ modes with line-of-sight components 
+will support measuring $k$ modes with line-of-sight components of
 $k_{\parallel} >0.2 h~Mpc^{-1}$.  
 %The performance is significantly better at the high frequency subbands of observation. 
-When combined with the powerful foreground weighting methods used in optimal
+We also find that when combined with the powerful foreground weighting methods used in optimal
 quadratic estimation,
 HERA should be capable of measuring the
-power spectrum at $k_{\parallel} > 0.1$. This study
-qualifies HERA as a power spectrum instrument and serves as an
-important method for designing and measuring instrumental systematics for any future
-experiment aiming to detect the 21~cm EoR power spectrum.  
+power spectrum at $k_{\parallel} > 0.1$. This study represents a major step toward
+qualifying HERA as a power spectrum instrument and highlights as an
+important method for characterizing instrumental systematics for future
+experiments aiming to detect the 21~cm EoR power spectrum.  
 \end{abstract}

### 2016-09-15 DishReflectometry/Paper1_v3.tex
Revised section5,6 and added ackknowledgement

@@
 Jacobs\altaffilmark{2}, Austin  Julius\altaffilmark{13}, MacCalvin  Kariseb\altaffilmark{13}, Saul A.
-Kohn\altaffilmark{10}, Telalo  Lekalake\altaffilmark{13}, Adrian  Liu\altaffilmark{1, 16}, Anita  Loots\altaffilmark{13}, David  MacMahon\altaffilmark{1}, Lourence  Malan\altaffilmark{13}, Cresshim  Malgas\altaffilmark{13}, Matthys  Maree\altaffilmark{13}, Zachary  Martinot\altaffilmark{10}, Nathan  Mathison\altaffilmark{13}, Eunice  Matsetela\altaffilmark{13}, Andrei  Mesinger\altaffilmark{12}, Miguel F.
+Kohn\altaffilmark{10}, Anna Lebedeva\UCB, Telalo  Lekalake\altaffilmark{13}, Adrian  Liu\altaffilmark{1, 16}, Anita  Loots\altaffilmark{13}, David  MacMahon\altaffilmark{1}, Lourence  Malan\altaffilmark{13}, Cresshim  Malgas\altaffilmark{13}, Matthys  Maree\altaffilmark{13}, Zachary  Martinot\altaffilmark{10}, Nathan  Mathison\altaffilmark{13}, Eunice  Matsetela\altaffilmark{13}, Andrei  Mesinger\altaffilmark{12}, Miguel F.
 Morales\altaffilmark{14}, Abraham R.
@@
     }
-%\altaffiltext{2}{To be inserted}}
-
-%\author{ James E.
-Aguirre\altaffilmark{10}, Paul  Alexander\altaffilmark{5}, Zaki S.
-Ali\altaffilmark{1}, Adam P.
-Beardsley\altaffilmark{2}, Gianni  Bernardi\altaffilmark{11, 13}, Judd D.
-Bowman\altaffilmark{2}, Richard F.
-Bradley\altaffilmark{8}, Chris L.
-Carilli\altaffilmark{9}, Carina  Cheng\altaffilmark{1}, Eloy  de~Lera~Acedo\altaffilmark{5}, Joshua S.
-Dillon\altaffilmark{1}, , Gcobisa  Fadana\altaffilmark{13}, Nicolas  Fagnoni\altaffilmark{5}, Randall  Fritz\altaffilmark{13}, Steve R.
-Furlanetto\altaffilmark{4}, Brian  Glendenning\altaffilmark{9}, Bradley  Greig\altaffilmark{12}, Jasper  Grobbelaar\altaffilmark{13}, Bryna J.
-Hazelton\altaffilmark{14, 15}, Jacqueline N.
-Hewitt\altaffilmark{7}, Jack  Hickish\altaffilmark{1}, Daniel C.
-Jacobs\altaffilmark{2}, Austin  Julius\altaffilmark{13}, MacCalvin  Kariseb\altaffilmark{13}, Saul A.
-Kohn\altaffilmark{10}, Telalo  Lekalake\altaffilmark{13}, Adrian  Liu\altaffilmark{1, 16}, Anita  Loots\altaffilmark{13}, David  MacMahon\altaffilmark{1}, Lourence  Malan\altaffilmark{13}, Cresshim  Malgas\altaffilmark{13}, Matthys  Maree\altaffilmark{13}, Zachary  Martinot\altaffilmark{10}, Nathan  Mathison\altaffilmark{13}, Eunice  Matsetela\altaffilmark{13}, Andrei  Mesinger\altaffilmark{12}, Miguel F.
-Morales\altaffilmark{14}, Abraham R.
-Neben\altaffilmark{7},  Samantha  Pieterse\altaffilmark{13}, Jonathan C.
-Pober\altaffilmark{3}, Nima  Razavi-Ghods\altaffilmark{5}, Jon  Ringuette\altaffilmark{14}, James  Robnett\altaffilmark{9}, Kathryn  Rosie\altaffilmark{13}, Raddwine  Sell\altaffilmark{13}, Craig  Smith\altaffilmark{13}, Angelo  Syce\altaffilmark{13}, Max  Tegmark\altaffilmark{7}, Nithyanandan  Thyagarajan\altaffilmark{2}, Peter K.~G.
-Williams\altaffilmark{6}, Haoxuan  Zheng\altaffilmark{7}}
-%\affil{HERA Collaboration}
+
     \altaffiltext{1}{Department of Astronomy, University of California, Berkeley, CA}
@@
 
+    Reflectometry is a method of determining the multiple reflection of any signal within a system. 
+    If applied to a radio telescope such as a parabolic dish, this could determine the extent to which 
+    sky signal is reflected back and forth between the reflector and the feed ~\citep{2015arXiv150205862P}.
     Reflectometry measurements are carried out at the HERA element prototype in
@@
     %\end{figure}
-\subsection{Delay spectrum of sub bands}
-
+
+  \subsection{Comparison with simulations:}
+  \begin{figure}{H}
+  \centering
+  \includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/simulation_comparison2.png}
+  \caption{Delay spectrum of HERA element estimated from the reflectometry measurements by a vector network analyser compared to the limits of foreground simulation (Thyagarajan et al).}
+   \label{fig:sim_em}
+   \end{figure}
+ \subsubsection{Electromagnetic simulation:}  
+We compare the delay spectrum estimated from our measurements with the same derived from the return loss obtained from the HFSS simulations of the HERA element (figure \ref{fig:sim_em}).
+The simulation is in good agreement with the measurements up to about 80~ns after which the cable reflection starts to manifests.
 The dominant term in the expression of  return loss of the HERA element in
-receiving mode (\ref{eq11}) is the zero delay term $(1+\Gamma_{f})$. As
+    receiving mode (equation \ref{eq11}) is the zero delay term $(1+\Gamma_{f})$. As
     mentioned earlier, the feed reflection coefficient $\Gamma_{a}$ shows two
@@
     frequency. This dominates the overall shape of the delay spectrum in figure
-\ref{ds_feed_on_dish_trans}.\\ Also, In HERA analysis, the 21~cm power spectrum
-is estimated by gridding the observed data along the line of sight distance i.e
-is in frequency or redshift and spatial frequency scale
-$k$~\citep{liu_et_al2014a}. At particular redshift, the bandwidth of
-observation is so chosen that over the corresponding $\Delta z$, the 21~cm
-signal does not significantly evolve. Typically, the the 21~cm brightness
-temperature fluctuation evolve over redshift scale $\Delta
-z>0.5$~\citep{loeb_zaldarriaga2004},~\citep{lidz_et_al2008}. Hence, the delay
-spectrum is estimated over smaller bandwidths.\\ We estimate the instrument
-delay spectrum over various sub bands between 100 to 200~MHz as shown in figure
-\ref{ds_full_sub_band}. Each panel of figure \ref{ds_full_sub_band} shows the
-delay spectrum estimated from the returnloss measurement of the HERA element
-between 100-200, 100-140, 140-160, 160 to 200~MHz respectively. Each panel also
-compares the estimated delay spectrum with two simulated delay spectra. The
-blue curve is the delay spectrum estimated from the simulated return loss of
-the feed and the feed-dish assembly that is shown in figure
-\ref{ds_feed_on_dish_trans}. Sub band delay spectra are wider compared to full
-band delay spectrum.  Shape of the resonant peaks determines the roll of rate
-of the delay spectrum in the range of 100-140~MHz and 160~200MHz. At higher
-frequency, our measurements closely follows the em simulations except around
-120~ns where the cable reflection between the antenna and the backend manifests
-itself at all frequencies. \\ The shaded region of each panel shows the EoR to
+    \ref{fig:sim_em}.\\
+  \subsubsection{Time domain simulation:}  
+    We also compare our measurements with the time domain simulation presented in ~\cite{Ewall-Wice_et_al2016}.
+In this simulation, electromagnetic response of the HERA element is determined as a function of time using the commercial numerical simulation software Microwave Studio developed by Computer Simulation Technology.
+The simulation assumed a constant $125\Omega$ impedance at the dipole terminals.
+In reality, dipole impedance is function of frequency across the entire band.
+This results in deviation between the simulated delay response and the delay spectrum estimate of our measurements.
+\\
+     \subsubsection{Foreground simulation:}  
+    We also compare our measurement with the foreground simulation of~\citep{Thyagarajan_et_al2016} as shown in the first panel of figure \ref{ds_full_sub_band}.
+The shaded region of each panel shows the EoR to
     foreground power ratio required for detection of 21~cm power spectrum at those
     individual delays~\citep{Thyagarajan_et_al2016}. This ratio is computed by
-using the HFSS simulation of chromatic antenna beam as well as return loss
-(figure \ref{RL_mag_dish}) and the sky models. Diffused sky foreground model is
+    using the HFSS simulation of chromatic antenna beam and the sky models. Diffused sky foreground model is
     incorporated from~\citep{deolivieracosta_et_al2008} whereas the point source
@@
     attenuation compared to a higher $k_{\parallel}$ mode. (For details
-~\cite{Thyagarajan_et_al2016}).
-
+    ~\cite{Thyagarajan_et_al2016}). \\
+     This simulation also, however, does not incorporate the frequency dependent antenna impedance that 
+     results in a frequency dependent return loss of power at the antenna terminal. Hence, the shaded region shows the most      
+     stringent limits of  EoR to foreground power ratio and sets the upper most limit of the required system performance under the assumption of non-chromatic return loss.
+
+    \subsubsection{Delay spectrum of sub bands}
+    In HERA analysis, the 21~cm power spectrum
+    is estimated by gridding the observed data along the line of sight distance i.e
+    is in frequency or redshift and spatial frequency scale
+    $k$~\citep{liu_et_al2014a}. At particular redshift, the bandwidth of
+    observation is so chosen that over corresponding $\Delta z$, the 21~cm
+    signal does not significantly evolve. Typically, the the 21~cm brightness
+    temperature fluctuation evolve over redshift scale $\Delta
+    z>0.5$~\citep{loeb_zaldarriaga2004},~\citep{lidz_et_al2008}. Hence, the delay
+    spectrum is estimated over smaller bandwidths.\\ We estimate the instrument
+    delay spectrum over various sub bands between 100 to 200~MHz as shown in figure
+    \ref{ds_full_sub_band}. Each panel of figure \ref{ds_full_sub_band} shows the
+    delay spectrum estimated from the return loss measurement of the HERA element
+    between 100-200, 100-140, 130-170, 160 to 200~MHz respectively. Each panel also
+    compares the estimated delay spectrum with em simulation of~\cite{deBoer_2016} at various subband.  Sub band delay spectra are wider compared to full
+    band delay spectrum.  Shape of the resonant peaks determines the roll off rate
+    of the delay spectrum at all frequency ranges. At higher
+    frequency, our measurement closely follows the em simulations except around
+    80-120~ns where the cable reflection between the antenna and the backend manifests
+    itself at all frequencies. \\ 
+    The shaded regions are however represents the EoR to Foreground power ratio simulated across the entire band.
+    The HFSS simulation of chromatic antenna beam, as incorporated by \cite{Thyagarajan_et_al2016} varies smoothly  	across frequency resulting in no significant changes in this simulation at various sub bands.
+     HERA system performance conforms directly to the limits as posed by simulations, at frequencies $>160~MHz$.
+With the measured system response including the multiple reflections, the instrument would be able to probe the spatial modes of interest $k_{\parallel}>0.2$ with very little foreground bleeding $k_{\parallel} \approx 0.2$.
+      At other frequencies, it is possible to do a successful measurement by weighting down the
+      foreground contribution in the measured data. This is discussed in the following section.
     \begin{figure*}[ht]
@@
     \centering
-\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/140_160.png}
+    \includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/130_170.png}
     \end{minipage}
@@
     \end{figure*}
-
-\section{\textbf{Effect of instrument delay spectrum on 21cm power spectrum measurements}}
-
-21cm power spectrum measurements are limited by challenges posed by the low
-frequency radio foreground that is order of magnitude brighter than the
-expected power spectrum amplitude. While PAPER has established the till date
-the most stringent upper limit on the 21cm power spectrum measurement, the need
-for increased sensitivity called for increased collecting area per PAPER
-element. This has driven to the parabolic reflector antenna based design of the
-PAPER successor HERA where essentially the PAPER antenna with minor
-modification of the ground plane-side plane assembly works as the feed and thus
-having larger collecting area per element. Additional limitations on PAPER and
-its contemporaries are imposed by the spectral structure of the system
-response. Sky signal is frequency modulated by the system bandpass response. In
-delay spectrum technique of 21cm power spectrum estimation, sky signal is
-convolved with the system response in the delay domain. In this process of
-convolution, the frequency dependent system response with rapid frequency
-variation results in spreading of the smooth spectrum foreground of the sky
-signal to the delays in which EoR power spectrum is to be estimated. This
-essentially limits the capacity of any experiment to probe the smaller spatial
-scales of fluctuations. \\ Figure \ref{fig:sim_em} and \ref{fig:sim_pk} shows
-the measurement presented this paper in comparison with the simulations.
-Simulations and measurements are in good agreement with each other up to around
-$60~ns$ up to which the structures in the delay domain are mostly caused due to
-signal reflections in the feed structure. Since the simulated return loss shows
-a better match of the antenna to the 50 Ohm transmission line. At zero delay ,
-in case of simulation, almost $100\%$ of the sky signal is received whereas in
-case of measurements, this match is found to be less than $5~dB$ resulting in
-partial coupling of the sky signal to the system. Given all the reflections
-unaltered, if the matching in between the feed and the transmission line is
-improved by about $10~dB$, which is achievable in reality, the delay spectrum
-would improve substantially. This is plotted in grey. The work is currently
-under progress to improve the feed return loss at least by  $10dB$ (Eloy et al
-2016 in prep?). Beyond $60~nS$ other multiple reflections manifests themselves
-at higher delays and the delay spectrum of the measurement and simulations
-begin to deviate from each other.\\ Thyagarajan et al 2016) has presented the
-detailed sensitivity calculations of HERA is using a comprehensive foreground
-model as well as model for EoR power spectrum for various simulated antenna
-element response. The sensitivity is quantified as a ratio of EoR signal power
-to the foreground power at various $\bold k_{\parallel}$ mode i.e at various
-delays. The theoretical limits for the level of foreground attenuation required
-relative to the EoR signal in order to reduce the foreground contaminations at
-the delay modes significant for power spectrum measurements are shown for three
-different lower limits of $k_\parallel$ values.  The response is computed for
-the redshift of $z=8.47$ at frequency $150~MHz$ over a bandwidth of $10~MHz$.
-This simulation shows the effect of chromatic antenna response and how that
-contaminates the delay modes beyond the horizon limit. Thus, this establishes a
-very stringent limits of required foreground attenuation relative to EoR signal
-which demands almost an ideal system performance. \\
-
-%As shown in section (), multiple reflection in the antenna system generates multiple copies of the sky signal and thus results in additional foreground contaminations in the delay modes where EOR power spectrum is measurable in case of no reflections.
-Reflectometry measurements shows the relative strength with which the multiple copies of the signal shows up at various delays.
-
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/simulation_comparison.png}
-\caption{Delay spectrum of HERA element estimated from the reflectometry measurements by a vector network analyser compared to the limits of foreground simulation (Thyagarajan et al).}
-\label{fig:sim_fg_Nithya}
-\end{figure}
-
-The HERA analysis pipeline for power spectrum estimation exploits the inverse covariance weighting technique to reduce the foreground contribution to the measured visibility data.
-In the light of this analysis technique we further investigate the limits of required instrumental delay response from what is established by foreground simulation in Thyagarajan et al 2016.
+ The HERA analysis pipeline for power spectrum estimation exploits the inverse covariance weighting to reduce the foreground contribution to the measured visibility data.
+In the light of this analysis technique we further investigate the limits of EoR to foreground power ratio from what is established by foreground simulation in \cite{Thyagarajan_et_al2016}.
 In the following section we briefly describe the power spectrum estimation technique used in HERA analysis and the inverse covariance weighting.
-In the next section we evaluate the estimated instrument delay response performance in the context of covariance weighting.
-
-\subsection{Power spectrum estimation:}
+We evaluate the instrument delay response in the context of covariance weighting.
+
+    \section{\textbf{Power spectrum estimation}}
 
     HERA power spectrum estimation is done using the Optimal Quadratic Estimator
-(OQE) formalism that has been outlined in extensive detail in (Liu and Tegmark
-2011), (Dillon et al 2013), (Liu et al 2014a,2014b), (Trott et al 2016), (Ali
-et al 2015). We briefly  describe the OQE formalism here.\\ HERA instrument
-aims at measuring the redshifted 21~cm power spectrum
-$P_{21}(k_\perp,k_\parallel)$, conventionally written as,
+    (OQE) formalism that has been outlined in extensive detail in  ~\cite{liu_et_al2010}, ~\cite{dillon_et_al2013a}, ~\cite{liu_et_al2014a}, ~\cite{liu_et_al2014b}, ~\cite{trott_et_al2012}, ~\cite{Ali_et_al2015}.
+We briefly  describe the OQE formalism here.
+    Conventionally, the 21~cm power spectrum $P_{21}(k_\perp,k_\parallel)$ is written as,
 
@@
     where $\langle  \tilde T_{b}(\bold k) \tilde T_{b}^{*}(\bold k^{'}) \rangle $ is the correlation function of the three dimensional spatial Fourier transform of the sky brightness temperature distribution $ \tilde T_{b}(\bold k)$, and $\delta$ is the Dirac delta function.
-While both $P_{21}(k_\perp,k_\parallel), \tilde T_{b}({\bold k})$ is continuous, the power spectrum could only be estimated at discrete values of $\bold k$.
-Observation frequency and bandwidth are so chosen that the power spectrum could e approximated as a constant and a piecewise continuous function of $\bold k$  which correspond to a thin shell in $\bold k$ space.
-This corresponds to the $k_{perp}$, $k_{parallel}$  values $a <k_{\perp} < a+1$, $b <k_{\parallel} < b+1$ where the indices a, b can assume M, N different values.
+While both $P_{21}(k_\perp,k_\parallel), \tilde T_{b}({\bold k})$ is continuous, the power spectrum estimate is discrete.
+Observation frequency and bandwidth are so chosen that the power spectrum could be approximated as a constant and a piecewise continuous function of $\bold k$  which correspond to a thin shell in $\bold k$ space.
+This corresponds to the $k_{\perp}$, $k_{\parallel}$  values $a <k_{\perp} < a+1$, $b <k_{\parallel} < b+1$ where the indices a, b can assume M, N different values.
 We denote the power spectrum as $\hat p_{\alpha}$ where alpha represents a particular $(M,N)$ value.
 Our analysis begins with a data vector $\bold x$.
-$\bold x$ is the list of visibilities measured at a given frequency over a certain bandwidth i.e for a given $k_{\parallel}$ mode for a given $\Delta \bold k $.
+$\bold x$ is the list of visibilities measured at a given frequency over a certain bandwidth i.e for a given $k_{\parallel}$ mode for a given $\Delta  k $.
 The first estimate of power spectrum is written as,
@@
     case, the measured visibility is contributed by EoR, foreground and
-instrumental noise. Hence, the estimate of any of the constituent signal would
+    instrumental noise. Hence, the estimate of any of the constituent signals would
     benefit from if the measured data is weighted by the covariance of the
@@
     results in the smallest vertical error bar in the power spectrum estimate $\hat
-p_{\alpha}$ (Reference Liu 2011).  However, there no definite way to know the
+    p_{\alpha}$ \citep{liu_tegmark2011}.  However, there is no definite way to know the
     covariance of individual signal components prior to estimating them. In
@@
     covariance results in order of magnitude reduction of foreground power against
-the EoR signal \\ Combining the inverse covariance weighting formalism with the
-foreground simulation of Thyagarajan et al 2016, we derive a new limit on
-required foreground attenuation with respect to the EoR signal, required for
+    the EoR signal. \\ 
+    Combining the inverse covariance weighting formalism with the
+    foreground simulation of \cite{Thyagarajan_et_al2016}, we derive a new limit on
+    required foreground attenuation with respect to the EoR signal for
     power spectrum estimation using HERA measurements. The foreground model of
-Thyagarajan et al (2015a) is adopted wherein the diffused emission is accounted
-for using de Oliviera-Costa et al. 2008 and the point sources are modeled using
-NRAO VLA sky survey at 1.42 GHz(NVSS, Condon et al 1998) and Sydney University
-Molonglo Sky Survey (SUMSS; Bock et al 199;Mauch et al 2003.) at 843 MHz. The
-EoR signal model is derived from the 21cmFAST (Messinger et al 2011). We use
+    \cite{Thyagarajan_et_al2016} as described in section \ref{subband} is adopted here. We use
     the reflectometry measurements, corrected for the antenna response in the
@@
     the EoR signal.  We again compute the EoR to foreground power ratio which is
-now smaller than what is estimated in Thyagarajan et al 2016 as shown in
-fig:\ref{fig:sim_fg_revised}.
-
-\begin{figure*}[ht]
+    now large due to relatively smaller foreground contribution than what is estimated in \cite{Thyagarajan_et_al2016} as shown       in fig: \ref{fig:sim_fg_revised}.
+
+    \begin{figure*}
     \centering
@@
     \caption{Delay spectrum of HERA element estimated from the reflectometry measurements by a vector network analyzer.
-The colored region shows the revised EoR to foreground power ratio in comparison to the measurements and the foreground simulation presented in (Thyagarajan et al 2016).}
+The colored region shows the revised EoR to foreground power ratio in comparison to the measurements and the foreground simulation presented in \cite{Thyagarajan_et_al2016}.}
     \label{fig:sim_fg_revised}
     \end{figure*}
-This demonstrates that the performance of the HERA element performance, in conjunction with the inverse covariance method of foreground suppression, qualifies the system for its the science goal it is designed for, irrespective of its chromatic response generated due to multiple reflections in the system.
+    This demonstrates that the performance of the HERA element, in conjunction with the inverse covariance method of foreground suppression, qualifies the system for its the science goal it is designed for, irrespective of its chromatic response generated due to multiple reflections in the system.
 
@@
     In this paper, we studied the performance of a HERA element in both frequency
-as well as delay domain. The effects of multiple reflections  in a HERA
+    as well as delay domain. We derived the explicit relationship between the measured return loss
+    of the HERA element using a vector network analyser and the EoR to foreground power ratio.
+    The effects of multiple reflections  in a HERA
     feed-dish assembly is investigated in detail and their effects on the measured
@@
     domain, and as Equation \ref{eq10} shows, these measurements must be adjusted
-for a difference in transmission/reflection at the first feed encounter in
+    for a difference in transmission/reception at the first feed encounter in
     order to be interpreted as the delay response of a feed relative to an incident
@@
     with a PAPER-style crossed dipole feed and cylindrical cage the instrument
-delay spectrum very well satisfies the criteria necessary to meet its science
-goal.
+    delay spectrum satisfies the criteria necessary to meet its science
+    goal. \\
+
+    {\bf Acknowledgements:}  
+This work was supported by the U.S. National Science Foundation (NSF) through awards AST-1440343 and AST-1410719.
+ARP acknowledges support from NSF CAREER award 1352519.
+AL acknowledges support for this work by NASA through Hubble Fellowship grant \#HST-HF2-51363.001-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS5-26555.
+This research was completed as part of the University of California Cosmic Dawn Initiative.
+AL, ARP, and SRF acknowledge support from the University of California Office of the President Multicampus Research Programs and Initiatives through award MR-15-328388
 

### 2016-09-16 DishReflectometry/Paper1_v3.tex
Almost edited everything

@@
 
-    Performance of the HERA feed and the dish-feed assembly has been simulated by
-    the em solver "High Frequency Structural Simulator(HFSS)" using the finite
-    element method.  The simulated and measured return loss of the feed, both
-    magnitude and phase are shown in the upper panel of the figure
-    \ref{RL_mag_dish}. While the simulated return loss of the feed structure shows
-    two resonant peaks around 120 and $160~MHz$, the feed resonance occur at
-    slightly higher frequencies. Notable are the difference in the shape of the
-    resonant peaks. While the simulated response shows very wide resonant peaks, as
-    expected from this dipole structures, the measured return loss of the feed has
-    a narrow peak around its low frequency resonance. This feature dominates the
-    fall off rate in the delay response of the system bandpass. The delay response
-    of the feed is shown in figure \ref{ds_feed_on_dish_trans}.
+    Return loss measurement of the HERA feed as well as dish-feed assembly is shown in figure \ref{RL_mag_dish}. Estimated        
+    delay spectrum is shown in figure \ref{ds_feed_on_dish_trans}. A number of systematic effects as well as
+    mathematical artifacts that are critical to this measurement and their effects
+    on the corresponding estimation of the delay spectrum are discussed next.
 
@@
 
-    Lower panel of the figure \ref{RL_mag_dish} shows the measured return loss when
-    the feed is suspended at the focal plane of the parabolic dish which is at $5m$
-    from the dish vertex. The measured return loss is much more complex than what
-    is found from the simulation. 
        %To estimate the delay spectrum of the dish-feed assembly i.e one single HERA element, this measurement is first corrected to map the response of the antenna from transmitting mode to receiving mode via equation \ref{zero_delay_correction}.
 The corrected measurement is then Fourier transformed to obtain the delay spectrum of the instrument in the receiving mode as given in equation \ref{corrected_response}.
-    Measurement bandwidth is kept much larger than the bandwidth of operation to
-    achieve higher delay resolution. A number of systematic effects as well as
-    mathematical artifacts that are critical to this measurement and their effects
-    on the corresponding estimation of the delay spectrum are taken in to account
-    in determination of the delay spectrum and described below.
+    %Measurement bandwidth is kept much larger than the bandwidth of operation to
+    %achieve higher delay resolution.
 
@@
     to the ones used in the PAPER antenna which provides greater than 10dB return
-    loss of power at the feed output as is achieved in the measurement presented
-    here.These baluns are under further design improvements aiming at 10 to 20dB
-    better impedance match between the feed and the balun than the measurements
-    presented here.  Our measurement is done using a vector network analyzer for
+    loss of power at the feed output. These baluns are currently under further design 
+    improvements aiming at 10 to 20dB
+    better impedance match between the feed and the backend.
+    Measurements presented here is done using a vector network analyzer for
     which the active balun has been replaced by a passive balun.Given the antenna
@@
     the dish return loss $\Gamma_{d}$ and corresponding delay spectrum as shown in
-    the figure \ref{dish_delay_spectrum}.
+    figure \ref{dish_delay_spectrum}.
 
@@
 
-    Another effect that spill over of the smooth foreground power at higher delays
+    Another effect that spills over of the smooth foreground power at higher delays
     is the multiple reflection of the received signal between the feed output and
@@
     output is connected to the VNA via a 50 feet long LMR 400 cable. This length
-    correspond to a delay of $\approx 120~nS$ for the signals travelling through
+    corresponds to a delay of $\approx 120~nS$ for the signals traveling through
     the cable. The delay spectrum of both feed and feed-dish assembly shows an
-    enhanced feature at this delay indicating a reflection from the VNA input. We
+    enhanced feature around this delay indicating a reflection from the VNA input. We
     measure the VNA input reflections by disconnecting the feed and connecting an
     open load at the feed input of the cable. The measured return loss is shown in
-    the figure \ref{fig:open_RL}. Since the electromagnetic wave travelling through
+    figure \ref{fig:open_RL}. Since the electromagnetic wave traveling through
     a transmission line undergoes a $100\%$ reflections from an open ended
@@
     noise floor. The delays at which this effect becomes dominant depends on the
-    length of the cable. Due to finite return loss at the input of the backends,
+    length of the cable. Since our measurement plane is at the open end of the cable
+    first reflection appears at zero delay while the second one appears around 120~ns. 
+    Peak amplitude of the consecutive reflection is reduced by $22~dB$. Third and 
+    consecutive reflections are buried in the noise floor of this measurement.Due to 
+    finite return loss at the input of the backends,
     this effect will be present in all the observations and thus would impact the
@@
     \caption{Left: Magnitude and phase of the return loss measured when the open load is connected at the feed input of the cable.
-Ideally, for an open load, the electromagnetic wave travelling through the transmission cable undergoes a $100\%$ reflections and magnitude of the return loss is $0dB$.
+Ideally, for an open load, the electromagnetic wave traveling through the transmission cable undergoes a $100\%$ reflections and magnitude of the return loss is $0dB$.
 However, due to the resistive loss in the cable, the a small part of the signal is dissipated in the cable resulting a smaller return loss.
@@
     measured return loss is sensitive to the bandwidth of measurements. Since the
-    measurements are done in the spectral domain, measurement between two
-    frequencies is analogous to windowing the frequency domain data by a square
+    measurements are done in the spectral domain over finite bandwidth, it is analogous
+     to windowing the frequency domain data by a square
     window function. In the delay domain, Fourier transform of this would result in
-    multiple side lobes at higher delays. Therefore, appropriate windowing of the
-    data is  necessary prior to taking the Fourier transform of the measured data.
+    multiple side lobes at higher delays. Appropriate windowing of the
+    measured data is necessary prior to taking the Fourier transform reduces
+    the system response at higher delays by few orders of magnitude~\citep{nithya_et_al2013}.
     Figure \ref{fig:window} shows the delay spectrum estimated from the measured
-    data using a square window as well as Blackman Harris window. Windowing the
-    data prior to Fourier transform significantly reduces the system response
-    higher delays.
-
+    data using a square window as well as Blackman Harris window. Even though windowing 
+    results in about $50\%$ loss of spectral sensitivity, it provides an additional $30~dB$ headroom 
+    for the foreground contaminations at higher delays. Spectral sensitivity could be improved by longer integration
+    time.     
     \begin{figure}
@@
  \subsubsection{Electromagnetic simulation:}  
-We compare the delay spectrum estimated from our measurements with the same derived from the return loss obtained from the HFSS simulations of the HERA element (figure \ref{fig:sim_em}).
-The simulation is in good agreement with the measurements up to about 80~ns after which the cable reflection starts to manifests.
-The dominant term in the expression of  return loss of the HERA element in
-    receiving mode (equation \ref{eq11}) is the zero delay term $(1+\Gamma_{f})$. As
-    mentioned earlier, the feed reflection coefficient $\Gamma_{a}$ shows two
-    resonances in between 100-140~MHz and 160-200~MHz. While the one at high
-    frequency is a wider peak, the low frequency resonance shows a sharp feature in
-    frequency. This dominates the overall shape of the delay spectrum in figure
+ Performance of the HERA feed and the dish-feed assembly has been simulated by
+    the em solver "High Frequency Structural Simulator(HFSS)" using the finite
+    element method.  The simulated and measured return loss of the feed, both
+    magnitude and phase are shown in the upper panel of figure
+    \ref{RL_mag_dish}. Bottom panel of figure \ref{RL_mag_dish} shows the measured return loss when
+    feed is suspended at the focal plane of the parabolic dish which is at $5m$
+    from the dish vertex. The measured return loss is much more complex than what
+    is found from simulation. 
+    While the simulated return loss of the feed structure shows
+    two resonant peaks around 120 and $160~MHz$, the feed resonance occur at
+    slightly higher frequencies. Notable are the difference in the shape of the
+    resonant peaks. While the simulated response shows very wide resonant peaks, as
+    expected from these dipole structures, the measured return loss has
+    a narrow peak at its low frequency resonance. The dominant term in the expression of  return loss of the HERA element in
+    receiving mode (equation \ref{eq11}) is the zero delay term $(1+\Gamma_{f})$. Hence the low frequency peak dominates the overall shape of the delay spectrum in figure
     \ref{fig:sim_em}.\\
+
    \subsubsection{Time domain simulation:}  
@@
     foreground power ratio required for detection of 21~cm power spectrum at those
-    individual delays~\citep{Thyagarajan_et_al2016}. This ratio is computed by
+    individual delays. This ratio is computed by
     using the HFSS simulation of chromatic antenna beam and the sky models. Diffused sky foreground model is
@@
     is simulated by using 21cmFAST \citep{Messinger_et_al2011}. The model
-    parameters used by~\cite{Thyagarajan_et_al2016} for the EoR signal simulation
+    parameters used for the EoR signal simulation
     are : Virial temperature of minimum mass of dark matter halos that host
@@
     values, the redshift of $50\%$ reionization is predicted to be at $z = 8.5$ at
-    150MHz.  Ideally, the delay response of the smooth foreground is confined at
-    lower delays whereas the same for the EoR signal is spread across the entire
-    delay range. However, due to system chromaticity of the simulated response of
-    the HERA element, foreground spills over the higher delays.
-    ~\cite{Thyagarajan_et_al2016} computes the required attenuation of the
-    foreground with respect to the EoR power available at that delay in order for a
-    detection of the EoR signal at that delay mode. It is shown that for a given
+    150MHz.  
+    EoR to foreground power ratio shows that for a given
     delay mode, the estimate of a lower $k_{\parallel}$ mode requires a higher
-    attenuation compared to a higher $k_{\parallel}$ mode. (For details
-    ~\cite{Thyagarajan_et_al2016}). \\
+    attenuation compared to a higher $k_{\parallel}$ mode. 
      This simulation also, however, does not incorporate the frequency dependent antenna impedance that 
@@
     \subsubsection{Delay spectrum of sub bands}
+    \label{sub-band}
     In HERA analysis, the 21~cm power spectrum
@@
     between 100-200, 100-140, 130-170, 160 to 200~MHz respectively. Each panel also
-    compares the estimated delay spectrum with em simulation of~\cite{deBoer_2016} at various subband.  Sub band delay spectra are wider compared to full
+    compares the delay spectrum estimate obtained em simulation of~\cite{deBoer_2016} at various subband.  Sub band delay spectra are wider compared to full
     band delay spectrum.  Shape of the resonant peaks determines the roll off rate
@@
     itself at all frequencies. \\ 
-    The shaded regions are however represents the EoR to Foreground power ratio simulated across the entire band.
-    The HFSS simulation of chromatic antenna beam, as incorporated by \cite{Thyagarajan_et_al2016} varies smoothly  	across frequency resulting in no significant changes in this simulation at various sub bands.
+    The shaded regions however represents the EoR to Foreground power ratio simulated across the entire band.
+    The HFSS simulation of chromatic antenna beam varies smoothly across frequency resulting in no significant changes in this simulation at various sub bands.  
      HERA system performance conforms directly to the limits as posed by simulations, at frequencies $>160~MHz$.
-With the measured system response including the multiple reflections, the instrument would be able to probe the spatial modes of interest $k_{\parallel}>0.2$ with very little foreground bleeding $k_{\parallel} \approx 0.2$.
+With the measured system response including the multiple reflections, the instrument would be able to probe the spatial modes of interest $k_{\parallel}>0.2$ with very little foreground bleeding around $k_{\parallel} \approx 0.2$.
       At other frequencies, it is possible to do a successful measurement by weighting down the
@@
     foreground simulation of \cite{Thyagarajan_et_al2016}, we derive a new limit on
-    required foreground attenuation with respect to the EoR signal for
+    foreground attenuation with respect to the EoR signal required for
     power spectrum estimation using HERA measurements. The foreground model of
-    \cite{Thyagarajan_et_al2016} as described in section \ref{subband} is adopted here. We use
+    \cite{Thyagarajan_et_al2016} as described in section \ref{sub-band} is adopted here. We use
     the reflectometry measurements, corrected for the antenna response in the
     receiving mode, to compute the visibilities (eq 13) for the given model of the
-    foreground, the EoR and the system noise. These visibilities formed the complex
+    foreground, the EoR and the system noise. Notable here is, our measurement contains 
+     beam chromaticity as well as chromaticity of the antenna impedance i.e, the effect 
+     of return loss of power at the antenna terminal . These visibilities formed the complex
     data vector $\bold x$. We compute the covariance matrix $C$ from the simulated
@@
     \end{figure*}
-    This demonstrates that the performance of the HERA element, in conjunction with the inverse covariance method of foreground suppression, qualifies the system for its the science goal it is designed for, irrespective of its chromatic response generated due to multiple reflections in the system.
+    This demonstrates that the performance of the HERA element, in conjunction with the inverse covariance method of foreground suppression, qualifies the system for its the science goal it is designed for, irrespective of its intrinsic chromatic response as well as chromaticity generated due to multiple reflections in the system.
 

### 2016-09-20 DishReflectometry/Paper1_v3.tex
Tweaks to intro and S1

@@
     \newcommand{\thhat}{{\hat\theta}}
-    \newcommand{\fngexp}{{e^{\frac{2\pi i\nu\vec{b}\cdot\thhat}{c}}}}
-    \newcommand{\ifngexp}{{e^{-\frac{2\pi i\nu\vec{b}\cdot\thhat}{c}}}}
+    %\newcommand{\fngexp}{{e^{\frac{2\pi i\nu\vec{b}\cdot\thhat}{c}}}}
+    %\newcommand{\ifngexp}{{e^{-\frac{2\pi i\nu\vec{b}\cdot\thhat}{c}}}}
+    \newcommand{\fngexp}{{e^{2\pi i\nu\vec{b}\cdot\thhat/c}}}
+    \newcommand{\ifngexp}{{e^{-2\pi i\nu\vec{b}\cdot\thhat/c}}}
     \newcommand{\dfngexp}{{e^{2\pi i\nu \Delta \tau}}}
@@
 
-    \indent The Hydrogen Epoch of Reionization Array (HERA) is a proposed array
-    consisting of 568 14-m dishes in South Africa which will measure the 21~cm
-    power spectrum between 100 to 200~MHz.
-    In this paper, we investigate the performance of an individual HERA element and
-    the resulting manifestation of the instrument response to the delay spectrum.
-    Reflectometry measurements  are carried out across a wide bandwidth on a
-    prototype HERA element in Green Bank, WV (Figure \ref{fig:heradish}), and the
-    results are interpreted in light of the delay spectrum technique of power
-    spectrum estimation and inverse covariance weighting method of foreground
-    suppression. Section 2 briefly describes the delay spectrum for the ideal and
-    non-ideal performance of a two element interferometer. Section 3 describes the
-    reflectometry measurements and establishes the connection between visibility
-    measurements and reflectometry. Reflectometry results are described in section
-    5. Section 6 evaluates the performance of the HERA element for detection of the
-    21~cm power spectrum.
-
-    This paper is one in a series of four papers that studies the time and frequency domain simulation of  HERA element~\citep{Ewall-Wice_et_al2016}, ~\citep{ddboer_et_al2016},beam pattern measurements~\citep{Neben_et_al2016}, and foreground limits ~\citep{Thyagarajan_et_al2016}.
-We compare
-    reflectometry measurements to the simulated specification for the spectral performance of a HERA element ~\citep{ddboer_et_al2016} and to the limits of EoR to foreground power ratio established by ~\citep{Thyagarajan_et_al2016}.
     \begin{figure*}
@@
 
-    \section{\textbf{Visibility measurements by a two element interferometer and the delay spectrum}}
+    In this paper, we use reflectometry measurements to
+    investigate the delay-domain performance of 
+    the 14-m parabolic dish elements (Figure \ref{fig:heradish}) that are proposed to be used in HERA, operating 
+    from 100 to 200~MHz.
+    %Reflectometry measurements are carried out across a wide bandwidth on a
+    %prototype HERA element in Green Bank, WV (Figure \ref{fig:heradish}), and the
+    %results are interpreted in light of the delay spectrum technique of power
+    %spectrum estimation and inverse covariance weighting method of foreground
+    %suppression. 
+    This paper is one in a series of four papers that studies the time and frequency domain simulation of  HERA element~\citep{Ewall-Wice_et_al2016}, ~\citep{ddboer_et_al2016},beam pattern measurements~\citep{Neben_et_al2016}, and foreground limits ~\citep{Thyagarajan_et_al2016}.
+We compare
+    reflectometry measurements to the simulated specification for the spectral performance of a HERA element ~\citep{ddboer_et_al2016} and to the limits of EoR to foreground power ratio established by ~\citep{Thyagarajan_et_al2016}.
+    In this paper, Section 2 briefly describes the delay spectrum for the ideal and
+    non-ideal performance of a two element interferometer. Section 3 describes the
+    reflectometry measurements and establishes the connection between visibility
+    measurements and reflectometry. Reflectometry results are described in Section
+    5. Section 6 evaluates the performance of the HERA element for detection of the
+    21~cm power spectrum.
+
+    \section{\textbf{Visibility measurements by a two element interferometer in the delay domain}}
+
     Consider a two element interferometer with a baseline $\vec b$.
@@
     \begin{equation}
-    \volt_{1}(\thhat, \nu) = \bmvolt_{1}(\thhat,\nu)\volt_\sky(\thhat,\nu)\nonumber\\
-    \end{equation}
-    \begin{equation}
-    \volt_{2} (\thhat, \nu)= \bmvolt_{2}(\thhat,\nu)\volt_\sky(\thhat,\nu)\fngexp\nonumber\\
+    \volt_{1}(\thhat, \nu) = \bmvolt_{1}(\thhat,\nu)~\volt_\sky(\thhat,\nu)\nonumber\\
+    \end{equation}
+    \begin{equation}
+    \volt_{2} (\thhat, \nu)= \bmvolt_{2}(\thhat,\nu)~\volt_\sky(\thhat,\nu)~\fngexp\nonumber\\
     \end{equation}
@@
     \begin{equation}
-    \vis(\vec b, \nu) =  \int  \volt_{1}(\thhat,\nu)  \volt_{2}^{*} (\thhat, \nu) \ifngexp d\Omega 
+    \vis(\vec b, \nu) =  \int  \volt_{1}(\thhat,\nu)~  \volt_{2}^{*} (\thhat, \nu)~ \ifngexp d\Omega 
     \label{eq1}
@@
 
-    We define the antenna cross power pattern as  $\beam(\thhat,\nu)=\bmvolt_{1}(\thhat,\nu)\bmvolt_{2}^{*}(\thhat,\nu)$ and denote the sky intensity as  $I_\sky(\thhat,\nu)=\volt_\sky(\thhat,\nu)\volt_\sky^{*}(\thhat,\nu)$.
+    We define the antenna cross power pattern as  $\beam(\thhat,\nu)=\bmvolt_{1}(\thhat,\nu)~\bmvolt_{2}^{*}(\thhat,\nu)$ and denote the sky intensity as  $I_\sky(\thhat,\nu)=\volt_\sky(\thhat,\nu)~\volt_\sky^{*}(\thhat,\nu)$.
 Hence,
     \begin{equation}
-    \vis(\vec b,\nu) = \int \beam(\thhat, \nu) I_\sky(\thhat,\nu) \ifngexp d\Omega
+    \vis(\vec b,\nu) = \int \beam(\thhat, \nu)~ I_\sky(\thhat,\nu)~ \ifngexp d\Omega
     	%	& = & \int B(l,m, \nu) I_{sky}(l,m,\nu) exp(-2\pi i \nu \tau_{g} ) dl dm \nonumber\\
@@
     The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. 
-    The redshifted 21 cm spatial power spectrum is defined as
+    It was then shown that the this delay-transformed visibility related to the power spectrum of redshifted
+    21 cm emission as
     \begin{equation}

### 2016-10-04 DishReflectometry/Paper1_v3.tex
Final reading up to section 6

@@
     \begin{eqnarray}
-    \tilde V(\vec b, \tau) & = & \int\!\![{\beam(\vec b,\nu)*I_\sky(\vec b,\nu)] ~e^{-2\pi i\nu\tau}d\nu}%\nonumber\\	                        %& = &   \left [ A(\vec b, \tau)\ast I_{sky}(\vec b, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega
+    %\tilde V(\vec b, \tau) & = & \int\!\![{\beam(\vec b,\nu)*I_\sky(\vec b,\nu)] ~e^{-2\pi i\nu\tau}d\nu}%\nonumber\\	  
+     \tilde V(\vec b, \tau) & = & \beam(\vec b,\tau)*I_\sky(\vec b,\tau)
+                           %& = &   \left [ A(\vec b, \tau)\ast I_{sky}(\vec b, \tau) \ast \delta( \tau - \frac{{\vec {b} \cdot \thhat}}{c} )\right ] d\Omega 
     \label{eq3}
@@
     % XXX define tau_g
-    The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. 
-    It was then shown that the this delay-transformed visibility related to the power spectrum of redshifted
-    21 cm emission as
-    \begin{equation}
-      P_{21}(k_\perp,k_\parallel) = (|\tilde V(\vec b, \tau)|^{2} \left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2 ,
+    The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. Qualitatively, 
+    delay spectrum of the visibility results from the convolution of the delay spectrum of the instrument with the instrument delay response.
+It is, therefore, important to determine the instrument delay response in order to determine sky delay response at a particular delay.
+by de-convolving the delay transformed visibility by the instrument response.
+
+   The delay-transformed visibility is related to the power spectrum of redshifted
+    21 cm emission by the relation, 
+    \begin{equation}
+     %P_{21}(k_\perp,k_\parallel) = (|\tilde V(\vec b, \tau)|^{2} \left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2 ,
+     %\end{equation}
+     %\begin{equation}
+ P_{21}(k_\perp,k_\parallel) = (|\tilde V(\vec b, \tau)|^{2} \left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2 {X^{2}Y \over \Omega \Delta B}
     \label{eq4}
@@
     \end{equation}
-    The power spectrum is a function of cosmological as well as instrumental parameters which are:\\
+    where, \\
+    \begin{itemize}
+    \item
      $f_{21}$:rest frame frequency of the 21~cm radiation.\\
+     \item
     $f$: observation frequency.\\
+    \item
     $z$: cosmological redshift corresponding to the frequency of observation.\\
+    \item
      $\Delta B$: bandwidth centered at the observation frequency.\\
+     \item
      $k_\textrm{B}$: Boltzmann constant.\\
+     \item
      $D\equiv D(z)$ comoving distance along the line of sight\\
+     \item
      $\Delta D$ the comoving distance along the line of sight corresponding to bandwidth of observation $\Delta B$.\\
+     \item
     $E(z)= [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ \\
-    \indent In this paper, we use $\Omega_{M}=0.27$, $\Omega_{\Lambda}=0.73$, $\Omega_{K}=1-\Omega_{M}-\Omega_{\Lambda}$, $H_0=100 h^{-1}\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P(k_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.
-
-    \indent Since both $k_{\perp}$ and $k_{\parallel}$ are functions of the delay
-    $\tau$, corresponding to the given baseline length, the redshifted 21 cm power
-    spectrum could be estimated from the delay spectrum of the visibility measured
-    by an interferometer. The sky delay spectrum from any direction $\thhat$ is
-    convolved with the delay spectrum of the instrument and would be located at the
-    delay $\tau = {\vec b \cdot \thhat \over c}$ %defined this differently earlier
-     in the delay domain.
+    \item
+    X, Y are cosmological scalers that relates the angular dependence with spectral frequency to corresponding comoving distance.
+    \end{itemize}
+   % \indent In this paper, we use $\Omega_{M}=0.27$, $\Omega_{\Lambda}=0.73$, $\Omega_{K}=1-\Omega_{M}-\Omega_{\Lambda}$, $H_0=100 h^{-1}\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P(k_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.
+    %\indent Since both $k_{\perp}$ and $k_{\parallel}$ are functions of the delay
+    %$\tau$, corresponding to the given baseline length, the redshifted 21 cm power
+    %spectrum could be estimated from the delay spectrum of the visibility measured
+    %by an interferometer. 
+    %The sky delay spectrum from any direction $\thhat$ is
+    %convolved with the delay spectrum of the instrument and would be located at the
+    %delay $\tau = {\vec b \cdot \thhat \over c}$ %defined this differently earlier
+     %in the delay domain.
 The maximum geometric delay possible for a given baseline would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$, when the phase centre is halfway in between the two antennas.
 %The phase center is elsewhere defined as being at the center of one of the antennas.
-     Hence, the sky contribution from any direction would be confined within
-    $-\tau_{g}<\tau<\tau_{g}$. Due to the chromaticity of the sky signal as well as
-    the instrument response, the delay spectrum of the sky spills over into delays
-    with $\tau> \tau_{g}$, with a decaying amplitude [Ref to the Figure Parsons12].
-    The foreground, $P_{fg}(\tau)$, which is spectrally smooth, and the 21~cm power
-    spectrum, $P_{21}(\tau)$, which contains spectral signatures, contribute to the
-    sky delay spectrum $P_{sky}(\tau)$.Therefore, in the spill over region
-    $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground,
-    with respect to the delay spectrum of the $I_{21}$, reduces and the 21cm delay
-    spectrum could be detectable.
+     %Hence, the sky contribution from any direction would be confined within
+    %$-\tau_{g}<\tau<\tau_{g}$. Due to the chromaticity of the sky signal as well as
+    %the instrument response, the delay spectrum of the sky spills over into delays
+    %with $\tau> \tau_{g}$, with a decaying amplitude [Ref to the Figure Parsons12].
+    %The foreground, $P_{fg}(\tau)$, which is spectrally smooth, and the 21~cm power
+    %spectrum, $P_{21}(\tau)$, which contains spectral signatures, contribute to the
+    %sky delay spectrum $P_{sky}(\tau)$.Therefore, in the spill over region
+   % $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground,
+    %with respect to the delay spectrum of the $I_{21}$, reduces and the 21cm delay
+    %spectrum could be detectable.
 
@@
 
-    The Hydrogen Epoch of Reionization Array consists of parabolic dishes which
+    HERA consists of parabolic dishes which
     provide increased collecting area per array element compared to its predecessor
@@
 
-    \section{\textbf{Reflectometry measurements}}
-
-    Reflectometry is a method of determining the multiple reflection of any signal within a system. 
-    If applied to a radio telescope such as a parabolic dish, this could determine the extent to which 
+    \section{\textbf{Reflectometry}}
+
+    Reflectometry is a method of determining the multiple reflection of any signal within 
+    a system in either time or frequency domain. If applied to a radio telescope such as
+     a parabolic dish, this could determine the extent to which 
     sky signal is reflected back and forth between the reflector and the feed ~\citep{2015arXiv150205862P}.
-    Reflectometry measurements are carried out at the HERA element prototype in
+    Frequency domain reflectometry measurements are carried out at the HERA element prototype in
     Green Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument
@@
     voltage components from two antennas having a mutual delay of $n\Delta \tau$
-    will be centred at $n\Delta \tau$. These will broaden the width of the delay
-    spectrum, which ultimately interferes with the 21cm power spectrum detection.
+    will be centred at $n\Delta \tau$. These will result in leakage of the foreground 
+    at delays where EoR power spectrum could be measured.
+   % spectrum, which ultimately interferes with the 21cm power spectrum detection.
 
@@
     which the active balun has been replaced by a passive balun.Given the antenna
-    impedance and the 50 Ohm transmission line the measurements are done using the
-    passive balun with a 4:1 impedance ratio. This measurements are conservative
+    impedance and the 50 Ohm transmission line, the measurements are done using the
+    passive balun with a 4:1 impedance ratio. These measurements are conservative
     estimate  for both $\Gamma_{f}$ and $s_{11}$.\\ While measuring the return loss
     of the dish-feed assembly, the signal transmitted by the VNA is reflected first
-    off the feed. This is represented by $\Gamma_{f}$ in equation \ref{eq9}. This
+    from the feed. This is represented by $\Gamma_{f}$ in equation \ref{eq9}. This
     essentially represents a mismatch in between the feed and the 50 Ohm
@@
     dish reflections starts to dominate and the two delay spectrum deviates from
-    each other. With some manipulation of the equation \ref{eq10}, we can estimate
-    the dish return loss $\Gamma_{d}$ and corresponding delay spectrum as shown in
-    figure \ref{dish_delay_spectrum}.
+    each other. 
+    %With some manipulation of the equation \ref{eq10}, we can estimate
+    %the dish return loss $\Gamma_{d}$ and corresponding delay spectrum as shown in
+    %figure \ref{dish_delay_spectrum}.
 
@@
     The VNA input return loss is found to be at a level of $-14$ to $-30dB$ across
-    the measurement band. This is consistent with the matched provided by the
+    the measurement band. This is consistent with the specification provided by the
     commercially available RF connectors that are commonly used. This manifests
@@
     where the foreground  achieving a return loss at the backend input is greater
-    than at least $-30~dB$.
+    than at least $-30~dB$. Moreover, if cable length are sufficiently increased
+    without the loss of signal, these reflections could be made to occur at delays
+    which are not of interest for EoR measurements.
 
@@
 
-  \subsection{Comparison with simulations:}
+  \subsection{Comparison with simulations}
   \begin{figure}{H}
@@
     a narrow peak at its low frequency resonance. The dominant term in the expression of  return loss of the HERA element in
-    receiving mode (equation \ref{eq11}) is the zero delay term $(1+\Gamma_{f})$. Hence the low frequency peak dominates the overall shape of the delay spectrum in figure
+    receiving mode (equation \ref{eq11}) is the zero delay term $(1+\Gamma_{f})$.
+Hence the feed return loss, especially the shape of the low frequency resonant peak dominates the overall shape of the delay spectrum in figure
     \ref{fig:sim_em}.\\

### 2016-11-08 DishReflectometry/Paper1_v4.tex
Revised section 6.

--- 2016-10-04 DishReflectometry/Paper1_v3.tex
@@
 
-    \title{THE HERA DISH III : MEASURING ELEMENT CHROMATICITY WITH REFLECTOMETRY. } 
+    \title{THE HYDROGEN EPOCH OF REIONIZATION ARRAY DISH III : MEASURING CHROMATICITY OF PROTOTYPE ELEMENT WITH REFLECTOMETRY. } 
     %\maketitle
@@
 Carilli\altaffilmark{9}, Carina  Cheng\altaffilmark{1}, Cherie~K.~Day\UCB, Eloy  de~Lera~Acedo\altaffilmark{5}, Joshua S.
-Dillon\altaffilmark{1}, , Gcobisa  Fadana\altaffilmark{13}, Nicolas  Fagnoni\altaffilmark{5}, Randall  Fritz\altaffilmark{13}, Steve R.
+Dillon\altaffilmark{1}, Gcobisa  Fadana\altaffilmark{13}, Nicolas  Fagnoni\altaffilmark{5}, Randall  Fritz\altaffilmark{13}, Steve R.
 Furlanetto\altaffilmark{4}, Brian  Glendenning\altaffilmark{9}, Bradley  Greig\altaffilmark{12}, Jasper  Grobbelaar\altaffilmark{13}, Bryna J.
 Hazelton\altaffilmark{14, 15}, Jacqueline N.
-Hewitt\altaffilmark{7}, Jack  Hickish\altaffilmark{1}, Daniel C.
+Hewitt\altaffilmark{7}, Daniel C.
 Jacobs\altaffilmark{2}, Austin  Julius\altaffilmark{13}, MacCalvin  Kariseb\altaffilmark{13}, Saul A.
@@
     \begin{abstract}
-    Spectral structure from instrumental systematics is the current
+    Spectral structures from instrumental systematic effects is the current
     limiting factor for the experiments attempting to detect the redshifted 21~cm
@@
     Recent advances in the delay spectrum methodology for measuring the
-    21~cm EoR power spectrum have brought new attention to the impact that
-    an antenna's frequency performance has on the viability of
+    21~cm EoR power spectrum have brought new attention to the impact of
+    an antenna's frequency \textbf{response} has on the viability of
     making this challenging measurement.
@@
     %spectrum technique for estimating of 21~cm power spectrum. 
-    In particular, it provides straightforward relationship
-    between time-domain reflectrometry profiles that can be directly
+    In particular, \textbf{this methodology} provides a somewhat straightforward relationship
+    between time-domain reflectometry profiles of an instrument that can be directly
     measured with a vector network analyzer (VNA) and the power spectrum modes accessible
@@
     In this paper, we derive the explicit relationship between $S_{11}$ measurements
-    made by a VNA and the extent of sidelobes of bright foregrounds in delay space.
-    Using this formalism, we examine
-    the spectral chromaticity of the prototype antenna elements that
-    constitute Hydrogen Epoch of Reionization Array (HERA) 
+    made by a VNA and the extent of \textbf{additional foreground contamination in delay space}.
+    \textbf{In the light of this mathematical framework}, we examine
+    the spectral chromaticity of a prototype antenna element which will
+    constitute the Hydrogen Epoch of Reionization Array (HERA) 
     between 100 and 200~MHz.
-    These reflectometry measurements exhibit spurious structure relative
+    These reflectometry measurements exhibit \textbf{additional} structure relative
     to electromagnetic simulations, but we find 
-    that even without compensating for this structure, the antenna element
+    that even without \textbf{any further design improvement}, such an antenna element
     will support measuring $k$ modes with line-of-sight components of
-    $k_{\parallel} >0.2 h~Mpc^{-1}$.  
+    $k_{\parallel} >0.2h$ Mpc$^{-1}$.  
     %The performance is significantly better at the high frequency subbands of observation. 
@@
     quadratic estimation,
-    HERA should be capable of measuring the
-    power spectrum at $k_{\parallel} > 0.1$. This study represents a major step toward
-    qualifying HERA as a power spectrum instrument and highlights as an
-    important method for characterizing instrumental systematics for future
-    experiments aiming to detect the 21~cm EoR power spectrum.  
+    HERA prototype elements \textbf{could successfully measure the
+    power spectrum at spatial modes as low as $k_{\parallel} > 0.1h$~Mpc$^{-1}$. This study represents a major step towards 
+    understanding the HERA antenna element. It also highlights an
+    important method for characterizing instrument response for future
+    experiments designed to detect the 21~cm EoR power spectrum using a reflector-type antenna. } 
     \end{abstract}
@@
 
-    Since it was first proposed in ~\citep{Shaver_et_al1999} measuring 21~cm
+    Since it was first proposed in \cite{1997ApJ...475..429M, Shaver_et_al1999}, \textbf{measurement of redshifted} 21~cm
     emission from neutral hydrogen in our early universe has gained attention as a
@@
     the technical path toward measuring this signal has been extremely challenging.  The
-    weakness of this hyperfine line keeps the 21~cm signal below opacity throughout
+    weakness of \textbf{the} hyperfine line keeps the 21~cm signal below opacity throughout
     cosmological history, but it also creates sensitivity and calibration
@@
     by sky noise and foregrounds four to five orders of magnitude
-    brighter than the signal, 
+    brighter than the signal even in the coldest patches of the sky, 
     sky-averaged 21~cm monopole experiments such as
@@
     BIGHORNS; ~\citealt{2015PhDT........65V},
-    SARAS; ~\citep{Patra_et_al2015}, \citep{Patra_et_al2013} ,
+    SARAS; ~\citep{Patra_et_al2015, Patra_et_al2013} ,
     SCIHI; ~\citep{2015PhDT........65V},
@@
     the Hydrogen Epoch of Reionization Array (HERA; ~\citealt{deBoer_2016}),
-    and the future Square Kilometre Array (SKA; ~\citealt{XXX})
+    and the future Square Kilometre Array (SKA; \footnote{www.skatelescope.org}~\citealt{2013ExA....36..235M})
     must furnish both their foreground suppression limits given their system performance at levels significantly
@@
 
-    One of the most problematic effects facing these experiments is instrument
-    chromaticity.  The spectral dimension of 21~cm reionization experiments is of vital
+    One of the most problematic effects these experiments face is the instrument
+    chromaticity \textbf{that are instrument specific and have unique manifestation in the measured data}.  The spectral dimension of    
+    21~cm reionization experiments is of vital
     importance; for line emission, this coordinate translates to a line-of-sight distance
@@
     as well as probe the evolution of 21~cm emission over cosmological timescales.
-    The evolving response of a radio telescope --- either a single dish
-    or an interferometer --- versus spectral frequency modulates spectrally smooth foregrounds,
+    The response of a radio telescope --- either a single dish
+    or an interferometer --- versus spectral frequency, modulates spectrally smooth foregrounds,
     contaminating spectral modes that might
-    otherwise be used to measure reionization ~\citep{liu_et_al2014a}.  Moreover, the chromaticity of
-    a telescope's response scales linearly with diameter, putting the
+    otherwise be used to measure reionization ~\citep{datta_et_al2010, trott_et_al2012, vedantham_et_al2012, 2012ApJ...752..137M, liu_et_al2014a}.
+\textbf{  Moreover, measurement sensitivity could be increased by increasing the collecting area of the element using reflector structures that  results in increased elementsize.
+However, the chromaticity of
+  a reflector dish scales with its diameter}, putting the
     needs of foreground suppression and signal sensitivity in direct tension with one
-    another. In addition to that, systematic effects are unique to each instrument and their manifestation 
-    is different in each dataset.
+    another. 
+    %In addition to that, systematic effects are unique to each instrument and their manifestation 
+    %is different in each dataset.
 
@@
     element separation (or telescope diameter), and what it implies for distinguishing
-    foreground emission from the cosmological 21~cm signal~\citep{Thyagarajan_et_al2015}.  The ``wedge'', as it is
+    foreground emission from the cosmological 21~cm signal~\textbf{\citep{Parsons_et_al_2012, vedantham_et_al2012, trott_et_al2012, 2014PhRvD..90b3018L, 2014PhRvD..90b3019L, 2015PhRvD..91b3002D,nithya_et_al2013,  Thyagarajan_et_al2015}.}  The ``wedge'', as it is
     colloquially known, describes a linear relationship between the separation between elements
@@
     subtraction.  However, calibration or modeling errors rapidly re-establish the characteristic
-    wedge pattern.  Outside of the wedge, foreground contamination drops rapidly 
-    ~\citep{pober_et_al2013},\citep{Thyagarajan_et_al2015}, provided that the spectral responses
+    wedge pattern~\textbf{\citep{2016MNRAS.461.3135B}.  Outside of the wedge, foreground contamination drops rapidly 
+    ~\citep{pober_et_al2013, 2014PhRvD..89b3002D,  Thyagarajan_et_al2015, Saul_et_al2016}}, provided that the spectral responses
     of antenna elements and analog electronics are sufficiently smooth\footnote{Here, we distinguish
     the chromaticity of the elements in isolation from the chromaticity inherent to
-    element separation in an interferometric baseline.}.  In the promising, avoidance-based
-    foreground strategy employed by PAPER ~\citep{parsons_et_al2014},\citep{Ali_et_al2015}, these modes
+    element separation in an interferometric baseline.}.  In the avoidance-based
+    foreground strategy employed by PAPER ~\citep{parsons_et_al2014, Ali_et_al2015}, these modes
     may be targeted as the lowest risk path for constraining 21~cm reionization in the near term.
@@
     % XXX document map
-    The efficacy of the techniques of foreground removal from the measured data
+    The efficacy of foreground removal from the measured data
     critically limits the 21~cm power spectrum measurements. The delay
     transformation technique of foreground removal, introduced by
-    ~\citep{Parsons_Backer_2009},\citep{Parsons_et_al_2012}, computes the Fourier
+    ~\citep{Parsons_Backer_2009, Parsons_et_al_2012}, computes the Fourier
     transform of the visibility measured by an interferometer and produces a
@@
     between two antennas. For the visibilities measured over a wide field across a
-    wide frequency bandwidth, the delay spectrum consists of the instrument
-    response, the foreground signal, and the 21cm power spectrum, hereafter
+    wide frequency bandwidth, the delay spectrum consists of the convolution of the instrument
+    response with the foreground signal, and the 21cm power spectrum, hereafter
     referred to as the EoR signal.
@@
     The technique exploits the smooth spectral characteristics of the foreground
-    and for a widefield wide bandwidth visibility measurement by an interferometer
+    and for a %widefield wide bandwidth
+     visibility measurement by an interferometer
     with a baseline $b$, confines the foreground contribution to the computed delay
-    spectrum within the largest possible time delay, $\tau = b/c$, corresponding to
-    the given baseline length. Such techniques also assume a spectrally smooth
-    instrumental response whose contribution to the measured data, much as the
-    contribution of the smooth spectrum foreground, also has an upper bound in the
-    delay space imposed by the largest geometric delay of the given baseline.
+    spectrum within the largest possible time delay, $\tau_{g} = b/c$, corresponding to
+    the given baseline length. \textbf{In reality, however, foregrounds show a response beyond the maximum geometric delay    
+    due to broadband spectrum of the foreground sources and chromatic instrument response. For an ideal system, this 
+    is a rapidly diminishing response beyond $\tau_{g}$ spanning the delay range corresponding to the inverse of the  
+    measurement bandwidth. }
     Beyond this limit, for an ideal system performance, the delay spectrum would be
-    dominated by any wideband signal across the sky with spectral and spatial
-    fluctuations over small scales, such as the EoR signal, and therefore, could be
-    detectable. The interaction between the sky signal and instrument response can
-    alter the relative contribution of the foreground, instrument response and the
-    EoR signal at a given delay and, thus, influence the detectability of the EoR
-    signal. Such interactions may cause the foreground and systematics to spill
-    over into higher delays and, thus, push the upper limit of the foreground and
-    systematics contaminated delay modes to much higher delays. In this process,
-    the EoR signal over large spatial scales will be lost. \\
-
+    dominated by any signal with spectral and spatial
+    fluctuations over small scales, such as the EoR signal.  The interaction between the sky signal and instrument response can
+    alter the relative contribution of the foreground, and the
+    EoR signal at a given delay and influence the detectability of the EoR
+    signal. Such interactions may cause the foreground to spill
+    over into higher delays and push the upper limit of the foreground and
+    systematics contaminated delay modes to much higher delays \textbf{contaminating the EoR window .} \\
     \begin{figure*}
@@
     \includegraphics[trim={2cm 20cm 30cm 15cm},clip, totalheight=0.3\textheight]{plots/heradish.jpg}
-    \caption{HERA dish feed at the Green Bank NRAO site.}
+    \caption{A prototype HERA element at the Green Bank NRAO site consisting of a crossed dipole feed and a parabolic reflector dish.}
     \label{fig:heradish}
     \end{figure*}
-
     In this paper, we use reflectometry measurements to
     investigate the delay-domain performance of 
-    the 14-m parabolic dish elements (Figure \ref{fig:heradish}) that are proposed to be used in HERA, operating 
+    \textbf{a prototype 14-m parabolic reflector dish and a crossed dipole feed (figure \ref{fig:heradish}) that are proposed to be used in HERA, operating 
     from 100 to 200~MHz.
+For clarity, the return loss of the feed when measured off of the dish will be referred to as ``feed return loss" hereafter.
+The dish-feed assembly, when the feed is placed at the focal point of the dish is referred to as ``HERA element" hereafter.
+}
     %Reflectometry measurements are carried out across a wide bandwidth on a
@@
     %suppression. 
-    This paper is one in a series of four papers that studies the time and frequency domain simulation of  HERA element~\citep{Ewall-Wice_et_al2016}, ~\citep{ddboer_et_al2016},beam pattern measurements~\citep{Neben_et_al2016}, and foreground limits ~\citep{Thyagarajan_et_al2016}.
+    This paper is one in a series of five papers that studies the time and frequency domain simulation of  HERA element~\citep{Ewall-Wice_et_al2016}, ~\citep{ddboer_et_al2016}, beam pattern measurements~\citep{Neben_et_al2016}, and foreground limits ~\citep{Thyagarajan_et_al2016}.
 We compare
@@
     Consider a two element interferometer with a baseline $\vec b$.
-If we denote the electric field sky signal in the direction $\thhat$ by $\volt_\sky(\vec \theta, \nu)$, then the voltage output of each antenna may be written as,
+If we denote the electric field sky signal in the direction $\thhat$ \textbf{at a frequency $\nu$} by $\volt_\sky(\vec \theta, \nu)$, then the voltage output of each antenna may be written as,
 
@@
     \end{equation}
-    Hence, the time averaged visibility measured by the interferometer may be written as, 
+
+    \textbf{where $\bmvolt_{1}$, $\bmvolt_{2}$ are the voltage gain pattern of the two antennae.}
+    Hence, the visibility measured by the interferometer may be written as, 
     \begin{equation}
@@
     The convolution is carried out along the $\tau$ axis which is Fourier conjugate of the frequency $\nu$. Qualitatively, 
-    delay spectrum of the visibility results from the convolution of the delay spectrum of the instrument with the instrument delay response.
-It is, therefore, important to determine the instrument delay response in order to determine sky delay response at a particular delay.
-by de-convolving the delay transformed visibility by the instrument response.
+    delay spectrum of the visibility results from the convolution of the \textbf{instrument delay response with the delay spectrum of the sky.
+It is, therefore, important to determine the instrument delay response in order to determine sky delay response at a particular delay by de-convolving the delay transformed visibility by the instrument response.
+}
 
@@
     \begin{equation}
-     %P_{21}(k_\perp,k_\parallel) = (|\tilde V(\vec b, \tau)|^{2} \left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2 ,
+     %P_{21}(k_\perp,k_\parallel) = (|\tilde V(\vec b, \tau)|^{2} \left(\frac{1}{$\Omega$\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2 ,
      %\end{equation}
      %\begin{equation}
- P_{21}(k_\perp,k_\parallel) = (|\tilde V(\vec b, \tau)|^{2} \left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2 {X^{2}Y \over \Omega \Delta B}
+ P_{21}(k_\perp,k_\parallel) \approx |(\tilde V(\vec b, \tau)|^{2} \left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2 {X^{2}Y \over \Omega \Delta B}
     \label{eq4}
@@
       k_\perp = \frac{2\pi f}{D}\Bigg({b\over c}\Bigg), \text{ }
-      k_\parallel = \frac{2\pi\tau\,f_{21}H_0\,E(z)}{c(1+z)^2}, 
+      k_\parallel = \frac{2\pi\tau\,f_{21}H(z)}{c(1+z)^2}, 
      \label{eq5}
     \end{equation}
-    where, \\
+
     \begin{itemize}
     \item
-     $f_{21}$:rest frame frequency of the 21~cm radiation.\\
+     $f_{21}$:rest frame frequency of the 21~cm radiation.
      \item
-    $f$: observation frequency.\\
+    $f$: observation frequency.
     \item
-    $z$: cosmological redshift corresponding to the frequency of observation.\\
+    $z$: cosmological redshift corresponding to the frequency of observation.
     \item
-     $\Delta B$: bandwidth centered at the observation frequency.\\
+     $\Delta B$: bandwidth centered at the observation frequency.
      \item
-     $k_\textrm{B}$: Boltzmann constant.\\
+     $k_\textrm{B}$: Boltzmann constant.
      \item
-     $D\equiv D(z)$ comoving distance along the line of sight\\
+     $D\equiv D(z)$ comoving distance along the line of sight
      \item
-     $\Delta D$ the comoving distance along the line of sight corresponding to bandwidth of observation $\Delta B$.\\
+     $\Delta D$ the comoving distance along the line of sight corresponding to bandwidth of observation $\Delta B$.
      \item
-    $E(z)= [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ \\
+    $H(z)= H_{0} [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{R}(1+z)^2+\Omega_\Lambda]^{1/2}$\\
+     where $H(z)$ is the Hubble constant as a function of redshift, $H_{0}= 100 h$~km s$^{-1}$ Mpc$^{-1}$, $\Omega_\textrm{M}=0.27, \Omega_\textrm{R}= 0.73, \Omega_\Lambda=1-\Omega_\textrm{M}-\Omega_\textrm{R}$ are the matter, radiation and dark energy density parameters respectively.
     \item
-    X, Y are cosmological scalers that relates the angular dependence with spectral frequency to corresponding comoving distance.
+    $X, Y$ are cosmological scalars that relates the angular dependence with spectral frequency to corresponding comoving distance.
     \end{itemize}
-   % \indent In this paper, we use $\Omega_{M}=0.27$, $\Omega_{\Lambda}=0.73$, $\Omega_{K}=1-\Omega_{M}-\Omega_{\Lambda}$, $H_0=100 h^{-1}\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P(k_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.
+   % \indent In this paper, we use $$\Omega$_{M}=0.27$, $$\Omega$_{\Lambda}=0.73$, $$\Omega$_{K}=1-$\Omega$_{M}-$\Omega$_{\Lambda}$, $H_0=100 h^{-1}\,$km$\,$s$^{-1}\,$Mpc$^{-1}$, and $P(k_\perp,k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$.
     %\indent Since both $k_{\perp}$ and $k_{\parallel}$ are functions of the delay
@@
 
-    HERA consists of parabolic dishes which
+    HERA consists of \textbf{parabolic reflector antennas} which
     provide increased collecting area per array element compared to its predecessor
-    experiment PAPER. Plane waves incident on a parabolic dish are focussed at the
-    feed which is kept at the focal plane of the dish.  The mismatch between the
+    experiment PAPER. Plane waves incident on a prime focus parabolic dish are focussed at the
+    feed which is at the focal plane of the dish.  The mismatch between the
     impedance of free space and the feed and transmission line results in a partial
@@
     back into the space.  However, a part of it reflects back and forth several
-    times in between the feed and the vertex of the dish which is shadowed by the
+    times between the feed and the vertex of the dish which is shadowed by the
     feed.  Such reflections generate multiple copies of the incident sky signal of
-    reduced strength at various delay and phase and thus produces spurious
-    correlations in the visibilities of interferometric data.  Identical spurious
-    visibilities could be resulted due to reflections internal to the system
-    causing delay space distortion. Therefore, it is necessary to measure and
-    understand the instrument delay spectrum in order to qualify the system for the
-    measurement of 21cm power spectrum.  In this section we compute the visibility
+    reduced strength at various delays and phases producing additional
+    correlations in the visibilities data.  \textbf{Identical
+    visibilities can result from reflections internal to the system,
+    for example between antenna output and backend receiver input causing similar signal contamination in delay space. Therefore, it is necessary to measure and develop the
+    understanding of the instrument delay spectrum.}  In this section we compute the visibility
     of a two element interferometer accounting for the additional reflections of
@@
     reflections, we can think of the system as a screen at a distance $F$ from a
-    feed (see Figure \ref{fig:sys}), noting that this does ignore the sky pattern
-    of the feed itself.  The screen reflects a factor, $\Gamma_d$, of the voltage
-    and transmits $(1+\Gamma_d)$ (see, {\em e.g.} Pozar).  Similarly, the feed
-    reflects $\Gamma_f$ and transmits $(1+\Gamma_f)$.  The voltage pattern
-    $\volt_{sky}$ is incident onto that system and  $(1+\Gamma_{d})(1+\Gamma_{f})$
-    is coupled into the cable leading from the feed.  Additionally, however, the
-    voltage pattern is reflected off the feed ($\Gamma_f$), then the dish
-    ($\Gamma_d$) and subsequently $(1+\Gamma_{f})$ of it reenters the feed with a
+    feed (see figure \ref{fig:sys}).  The screen reflects a factor, $\Gamma_d$, of the voltage
+    and transmits $(1+\Gamma_d)$ where $\Gamma_{d}$ is the voltage reflection coefficient of dish (see, {\em e.g.} Pozar).  Similarly, the feed
+    reflects $\Gamma_f$ and transmits $(1+\Gamma_f)$ where $\Gamma_{f}$ is the voltage reflection coefficient of the feed.  Both $\Gamma_{d}$ and $\Gamma_{f}$ are complex numbers that  
+    are functions of frequencies. Therefore, for a given incidence of the sky voltage
+    $\volt_{sky}$,  $(1+\Gamma_{d})(1+\Gamma_{f})$
+    is coupled into the cable leading to the receiver backend from the feed.  Additionally, the 
+    voltage that is reflected off the feed ($\Gamma_f$), is subsequently reflected off the dish by a factor
+    ($\Gamma_d$) and $(1+\Gamma_{f})$ of it reenters the feed with a
     roundtrip time delay $\Delta \tau=2F/c$. Hence, if $v_{sky}$ is reflected $n$
@@
 
-    \begin{figure}
-    \centering
-    \includegraphics[width=0.5\textwidth]{plots/microsys.pdf}
-    \caption{System}
+    %\begin{figure*}[ht]
+    %\begin{minipage}[b]{0.5\linewidth}
+    %\centering
+    %\includegraphics[width=\linewidth]{plots/microsys.pdf}
+ %   \caption{Schematic diagram of signal propagation  }
+    %\end{minipage}
+    %\hspace{0.1cm}
+    %\begin{minipage}[b]{0.5\linewidth}
+    %\centering
+    %\includegraphics[width=\linewidth]{plots/reflection_cartoon.png}
+    %\caption{Schematic diagram of signal propagation  }
+    %\end{minipage}
+    %\label{fig:sys}
+    %\end{figure*}
+    \begin{figure}[ht]
+    \centering
+    \includegraphics[width=\linewidth]{plots/microsys.pdf}
+    \caption{Schematic diagram of signal propagation through the dish and the feed of during both transmission and reception.
+$V_{sky}$, $V_{in}$ and $V_{rec}$ represents the sky voltage, total reflected voltage from the dish that is incident on the feed and the net received voltage at the receiver input.
+In transmission mode, $V_{trans}$, $V_{out}$ and $V_{rad}$ are the voltage transmitted by the network analyser, the voltage output of the feed and the the net radiated voltage after reflection on the dish.
+$\Gamma_{d}$,  $\Gamma_{f}$ are the voltage return loss of the dish and the feed.
+}
     \label{fig:sys}
@@
     {\volt_{rec}\over \volt_{sky} } & = &   (1+\Gamma_d)(1+\Gamma_{f}) \displaystyle\sum\limits_{n=0}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}\nonumber\\
-    & = & \frac{ (1+\Gamma_d)(1+\Gamma_{f})}{1+\Gamma_{f}\Gamma_{d}\dfngexp} 
+    & = & \frac{ (1+\Gamma_d)(1+\Gamma_{f})}{1-\Gamma_{f}\Gamma_{d}\dfngexp} 
     \label{eq7}
@@
     Note that $n=0$ is when the initial wave enters the cable at the feed (where we assume we have set our reference plane).
-We may identify $(1+\Gamma_d)$ as the voltage reception pattern of the antenna, denoted $\bmvolt(\thhat,\nu)$, which is a function of angle on the sky.
+We identify $(1+\Gamma_d)$ as the voltage reception pattern of the antenna, denoted $\bmvolt(\thhat,\nu)$, which is a function of angle on the sky.
 Additionally, $(1+\Gamma_f$) is the voltage efficiency for the feed (not a function of angle).
@@
     well calibrated, wideband source in the sky in the far field of the HERA
-    antenna element with significant isotropic emission. While this condition is
-    hard to achieve in practice, due to the reciprocity of the antenna performance
-    in the transmission and reception mode, the right hand side of equation
+    antenna element with significant isotropic emission. \textbf{While this condition is
+    hard to achieve in practice, reciprocity of the antenna performance
+    in the transmission and reception mode implies the right hand side of equation
     \ref{eq7} could be measured using the return loss measurement technique with a
-    vector network analyzer (VNA). \\
-
+    vector network analyzer (VNA).} \\
     \section{\textbf{Reflectometry}} 
-
     Reflectometry is a method of determining the multiple reflection of any signal within 
     a system in either time or frequency domain. If applied to a radio telescope such as
-     a parabolic dish, this could determine the extent to which 
+     a parabolic dish, this can determine the extent to which 
     sky signal is reflected back and forth between the reflector and the feed ~\citep{2015arXiv150205862P}.
-    Frequency domain reflectometry measurements are carried out at the HERA element prototype in
-    Green Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument
-    response of the feed and dish assembly and characterise the performance.  HERA
-    element consists off a $14\,m$ diameter parabolic reflector and a
+    Frequency domain reflectometry measurements are carried out on a prototype HERA in
+    Green Bank, WV (figure \ref{fig:heradish}) in order to measure the instrument
+    response of the feed and dish assembly and characterise the performance.  \textbf{The prototype HERA
+    element} consists of a $14.5~m$ diameter parabolic reflector and a
     crossed-dipole pair as a feed. The cross dipole antenna pair is identical to
-    the feed of the PAPER antenna which is suspended at the focal plane of the dish
-    with the support of three vertical poles. HERA elements are closely spaced with
-    centre to centre distance between two dishes are equal to the dish diameter.
+    the feed of the PAPER antenna and suspended at the focal plane of the dish
+    with the support of three vertical poles. HERA elements \textbf{will be} closely spaced with
+    centre to centre distance between two dishes slightly larger than the dish diameter.
     Therefore, to reduce the coupling between the adjacent dishes, the crossed
     dipole feed along with the back plane is encased in a cylindrical cage. The
-    feed is raised and lowered by a three-pulley system mounted on the three poles.
-    The focal height of the dish is $5m$.  The detail geometry and electromagnetic
-    design of of the feed is presented in deBoer et al 2016. \\
+    feed is raised and lowered by a pulley system mounted on the three poles.
+    The focal height of the dish is 5~m.  The detail geometry and electromagnetic
+    design of of the feed is presented in \cite{ddboer_et_al2016}. \\
 
@@
 
-     A VNA is connected to the HERA element via a 50-foot cable. It then transmits
+     A VNA is connected to the HERA element via a $\approx 15$~m cable. It then transmits
     a broadband noise voltage, $\volt_{trans}$, and a factor $(1+\Gamma_f)$ of this
@@
     is the first reflected signal at the reference plane), is therefore:
-
     \begin{eqnarray}
@@
 In this case, $\Gamma_f = s_{11}^{f}$.
-Using this measurement and the VNA measurement of $s11$, the quantity $v_{rec}\over v_{sky}$ is estimated.
+Using this measurement and the VNA measurement of $s_{11}$, the quantity $v_{rec}\over v_{sky}$ is estimated.
 \\
@@
     {I_{rec}\over I_{sky} } & = & \Bigg|{\volt_{rec}\over \volt_{sky} }\Bigg|^2 =  \beam(\thhat,\nu)\times \nonumber\\
-                 && \left[|1+\Gamma_f|^2 +  2\operatorname{Re}\left(\frac{\Gamma_f}{(1+\Gamma_f)}(s_{11} - \Gamma_f)\right)\right] + \nonumber\\ 
-                 &&  \left[ \frac{|\Gamma_f|^2}{|1+\Gamma_{f}|^2}|s_{11} - \Gamma_f|^2  \right]  \nonumber\\
+                 && [ |1+\Gamma_f|^2 +  2\operatorname{Re}\left(\frac{\Gamma_f}{(1+\Gamma_f)}(s_{11} - \Gamma_f)\right)  \nonumber\\ 
+                 &&  + \frac{|\Gamma_f|^2}{|1+\Gamma_{f}|^2}|s_{11} - \Gamma_f|^2]    \nonumber\\
     \label{eq12}             
@@
     \end{eqnarray}
-
     Comparing equations \ref{eq13} and \ref{eq2}, the cross power generated by
-    $v_{1}$ and $v_{2}$ would have a spurious visibility response due to the mutual
+    $v_{1}$ and $v_{2}$ has a spurious visibility response due to the mutual
     correlation between multiply reflected voltages represented by the second and
@@
     will be centred at $n\Delta \tau$. These will result in leakage of the foreground 
-    at delays where EoR power spectrum could be measured.
+    to delays where EoR power spectrum could be measured.
    % spectrum, which ultimately interferes with the 21cm power spectrum detection.
-
      \begin{figure*}
@@
     \vspace{1.0 em}
-    \caption{The HERA feed consists of a pair of crossed-dipoles over 1.72 mt diameter backplane made of wire mesh.
+    \caption{The HERA feed consists of a pair of crossed-dipoles over 1.72 m diameter backplane made of wire mesh.
 The backplane is surrounded by 0.36 m wide wire mesh around the edge resulting in encasing the crossed-dipoles in a cylindrical cage.}
@@
     \end{figure*}
-
      \section{\textbf{Results}}
@@
 Upon our assumption that two adjacent antenna elements have identical design parameters and electrical properties, this power is also a measure of the cross power or the visibility $\vis (\vec b, \nu)$ between the two antennas with a normalisation factor of $2$.
-
-    Return loss measurement of the HERA feed as well as dish-feed assembly is shown in figure \ref{RL_mag_dish}. Estimated        
-    delay spectrum is shown in figure \ref{ds_feed_on_dish_trans}. A number of systematic effects as well as
+    Return loss measurements of the feed as well as HERA element is shown in figure \ref{RL_mag_dish}. Estimated        
+    delay spectra are shown in figure \ref{ds_feed_on_dish_trans}. A number of systematic effects as well as
     mathematical artifacts that are critical to this measurement and their effects
@@
     \centering
-    \includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_mag_feed.png}
+    \includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_feed_mag.png}
     \end{minipage}
@@
     \centering
-    \includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_ph_feed.png}
+    \includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_feed_ph.png}
     \end{minipage}
@@
     \centering
-    \includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_mag_dish.png}
+    \includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_HERA_mag.png}
     \end{minipage}
@@
     \centering
-    \includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_ph_HERA.png}
+    \includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/RL_HERA_ph.png}
     \end{minipage}
@@
 The feed, when suspended on the dish results in a more complex return loss as shown in the lower panel of figure \ref{RL_mag_dish} and corresponding delay response is shown here in black.
+A balun with impedance transformation ratio $4:1$ is used for converting the antenna balanced output to unbalanced output voltage.
+Balun response is embedded in the measurements.
 }
@@
     better impedance match between the feed and the backend.
-    Measurements presented here is done using a vector network analyzer for
-    which the active balun has been replaced by a passive balun.Given the antenna
-    impedance and the 50 Ohm transmission line, the measurements are done using the
-    passive balun with a 4:1 impedance ratio. These measurements are conservative
-    estimate  for both $\Gamma_{f}$ and $s_{11}$.\\ While measuring the return loss
+\textbf{The measurement presented here is done using a vector network analyzer}.
+\textbf{The active balun is replaced by a passive one with 4:1 impedance transformation ratio for achieving a better match to the 50~$\Omega$ transmission line}.
+These measurements, therefore, provide a conservative estimate for $\Gamma_{f}$ and $S_{11}$.
+     %These measurements are conservative
+    %estimate  for both $\Gamma_{f}$ and $s_{11}$}.
+
+     While measuring the return loss
     of the dish-feed assembly, the signal transmitted by the VNA is reflected first
     from the feed. This is represented by $\Gamma_{f}$ in equation \ref{eq9}. This
-    essentially represents a mismatch in between the feed and the 50 Ohm
+    essentially represents a mismatch in between the feed and the 50~$\Omega$
     transmission line. In delay domain, this appears at the zero delay bin. The
@@
     $s_{11}$ of the dish and feed assembly is corrected via equation \ref{eq11} and
-    the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated.
+    the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated. Figure \ref{ds_feed_on_dish_trans}
+    shows the delay response of the feed alone computed from the return loss measurement of the feed alone in 
+    transmission mode(brown). \textbf{Using this return loss measurement of the feed, we compute the quantity $v_{rec}/v_{sky}$. 
+    and the corresponding delay spectrum is shown in black. }
 
@@
 
-    Measurement equations shows the effects of multiple reflections of the sky
+    Measurement equations show the effects of multiple reflections of the sky
     signal between the feed and the dish. Any other reflections off the feed
     structure and/or any other part of the dish-feed assembly would appear at
-    arbitrary delays. The estimated delay spectrum of the instrument is
-    collectively contributed by all the reflections. Delay spectrum estimated from
-    the return loss measurement of the feed alone,  provides the lowest limit of
-    the delay spectrum of the instrument considering there is no multiple
+    \textbf{delays corresponding to particular length scale. The estimated delay spectrum of the instrument is
+    collectively contributed by all the reflections. The delay response of
+    feed alone provides the lowest limit of
+    the delay spectrum of the instrument when there is no multiple
     reflections in between the feed and the dish.  From figure
@@
     other. Since the distance between the feed and the dish is 5 m, the roundtrip
-    delay between the dish and the feed as about $30~ns$. Hence, the dish
-    reflection is expected to manifest themselves at an integral multiple of
-    $30~ns$. The diameter of the feed cavity is $172~cm$  that results in signal
-    reflections every integral multiple of $\approx2.86~ns$. The combined effect of
-    feed and the dish dominates the delay spectrum up to $\> 50nS$ after which the
-    dish reflections starts to dominate and the two delay spectrum deviates from
-    each other. 
+    delay between the dish and the feed is about 30~ns. Hence, the dish
+    reflections are expected to manifest themselves at an integral multiple of
+    30~ns. The diameter of the feed cavity is 172~cm  which results in signal
+    reflections every integral multiple of $\approx$2.86~ns. The combined effect of
+    the feed and the dish dominates the delay spectrum up to $\> $50~ns after which the
+    dish reflections begin to dominate and the two delay spectra deviates. }
     %With some manipulation of the equation \ref{eq10}, we can estimate
@@
 
-    Another effect that spills over of the smooth foreground power at higher delays
-    is the multiple reflection of the received signal between the feed output and
+    Another effect that \textbf{allows smooth foreground power to spill into higher delays}
+    are the multiple reflection of the received signal between the feed output and
     the input of the analog backend and correlators. In our measurements, the feed
-    output is connected to the VNA via a 50 feet long LMR 400 cable. This length
-    corresponds to a delay of $\approx 120~nS$ for the signals traveling through
-    the cable. The delay spectrum of both feed and feed-dish assembly shows an
-    enhanced feature around this delay indicating a reflection from the VNA input. We
+    output is connected to the VNA via a 15~m long LMR 400 cable. This length
+    corresponds to a delay of $\approx$ 120~ns for the signals traveling through
+    the cable. The delay spectra of both feed and feed-dish assembly shows an
+    enhanced feature around this delay indicating a reflection from the VNA input.
+
+     We
     measure the VNA input reflections by disconnecting the feed and connecting an
@@
     figure \ref{fig:open_RL}. Since the electromagnetic wave traveling through
-    a transmission line undergoes a $100\%$ reflections from an open ended
+    a transmission line undergoes a 100$\%$ reflections from an open ended
     transmission line, we compute the combined effect of the VNA input return loss
@@
     \ref{fig:open_RL}. This results an important system design criterion for HERA.
-    The VNA input return loss is found to be at a level of $-14$ to $-30dB$ across
+    The VNA input return loss is found to be at a level of -14 to -30~dB across
     the measurement band. This is consistent with the specification provided by the
     commercially available RF connectors that are commonly used. This manifests
-    itself in a peak in the delay spectrum which is $50~dB$ above the measurement
-    noise floor. The delays at which this effect becomes dominant depends on the
-    length of the cable. Since our measurement plane is at the open end of the cable
+    itself in a peak in the delay spectrum which is 50~dB above the measurement
+    noise floor. The delay at which this effect becomes dominant depends on the
+    length of the cable. Since our measurement plane is at the open end of the cable,
     first reflection appears at zero delay while the second one appears around 120~ns. 
-    Peak amplitude of the consecutive reflection is reduced by $22~dB$. Third and 
-    consecutive reflections are buried in the noise floor of this measurement.Due to 
-    finite return loss at the input of the backends,
-    this effect will be present in all the observations and thus would impact the
+    The peak amplitude of the second reflection is reduced by 22~dB. Third and 
+    consecutive reflections are buried in the noise floor of this measurement. Similar effects
+     will be present in all observations due to  finite return loss at the input of the backends,
+     and would impact the
     instrument delay spectrum. However, its effect could be reduced below the level
-    where the foreground  achieving a return loss at the backend input is greater
-    than at least $-30~dB$. Moreover, if cable length are sufficiently increased
+    where the return loss at the backend input is greater
+    than at least -30~dB. Moreover, if the cable length is sufficiently increased
     without the loss of signal, these reflections could be made to occur at delays
@@
     \end{minipage}
-    \caption{Left: Magnitude and phase of the return loss measured when the open load is connected at the feed input of the cable.
-Ideally, for an open load, the electromagnetic wave traveling through the transmission cable undergoes a $100\%$ reflections and magnitude of the return loss is $0dB$.
+    \caption{Left: Magnitude (blue) and phase (black) of the return loss measured when the open load is connected at the feed input of the cable.
+Ideally, for an open load, the electromagnetic wave traveling through the transmission cable undergoes a $100\%$ reflections and magnitude of the return loss is 0~dB.
 However, due to the resistive loss in the cable, the a small part of the signal is dissipated in the cable resulting a smaller return loss.
@@
      to windowing the frequency domain data by a square
-    window function. In the delay domain, Fourier transform of this would result in
-    multiple side lobes at higher delays. Appropriate windowing of the
-    measured data is necessary prior to taking the Fourier transform reduces
-    the system response at higher delays by few orders of magnitude~\citep{nithya_et_al2013}.
-    Figure \ref{fig:window} shows the delay spectrum estimated from the measured
-    data using a square window as well as Blackman Harris window. Even though windowing 
-    results in about $50\%$ loss of spectral sensitivity, it provides an additional $30~dB$ headroom 
-    for the foreground contaminations at higher delays. Spectral sensitivity could be improved by longer integration
+    window function. In the delay domain, the Fourier transform of this would result in
+    multiple side lobes at higher delays. \textbf{Appropriate windowing of the
+    measured data prior to taking the Fourier transform reduces
+    the system response at higher delays by few orders of magnitude~\citep{nithya_et_al2013, Thyagarajan_et_al2016}.}
+    figure \ref{fig:window} shows the delay spectrum estimated from the measured
+    data using a square window as well as Blackman-Harris window. Even though windowing 
+    results in about 50~$\%$ loss of spectral sensitivity, it may provide an additional 30~dB of headroom 
+    for the foreground contaminations at higher delays. Loss of spectral sensitivity due to windowing could be compensated by longer integration
     time.     
@@
     \includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/ds_window.png}
-    \caption{Effect of finite bandwidth on estimation of delay spectrum: Blue line shows the delay spectrum of the HERA element computed from the measured data which is band limited between 100 to 200MHz.
-Green line shows the delay spectrum estimated from the same data set after multiplying the data by a Blackman Harris window.
+    \caption{Effect of finite bandwidth on estimation of delay spectrum: Blue line shows the delay spectrum of the HERA element computed from the measured data which is band limited between 100 to 200~MHz.
+Black line shows the delay spectrum estimated from the same data set after multiplying the data by a Blackman Harris window.
 The delay spectrum of the windowed data set shows significant reduction in the instrument response at higher delays.}
@@
   \includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/simulation_comparison2.png}
-  \caption{Delay spectrum of HERA element estimated from the reflectometry measurements by a vector network analyser compared to the limits of foreground simulation (Thyagarajan et al).}
+  \caption{Delay spectrum of HERA element estimated from the reflectometry measurements by a vector network analyser compared to the delay spectrum estimated from the EM simulation using HFSS and time domain simulation using CST .}
    \label{fig:sim_em}
    \end{figure}
- \subsubsection{Electromagnetic simulation:}  
- Performance of the HERA feed and the dish-feed assembly has been simulated by
-    the em solver "High Frequency Structural Simulator(HFSS)" using the finite
+
+ \subsubsection{HFSS Electromagnetic simulation:}  
+ Performance of the HERA feed and the HERA element has been simulated by
+    using the EM solver "High Frequency Structural Simulator (HFSS)" using the finite
     element method.  The simulated and measured return loss of the feed, both
@@
     \ref{RL_mag_dish}. Bottom panel of figure \ref{RL_mag_dish} shows the measured return loss when
-    feed is suspended at the focal plane of the parabolic dish which is at $5m$
+    feed is suspended at the focal plane of the parabolic dish which is at $4.5m$
     from the dish vertex. The measured return loss is much more complex than what
@@
     While the simulated return loss of the feed structure shows
-    two resonant peaks around 120 and $160~MHz$, the feed resonance occur at
+    two resonant peaks around 120 and 160~MHz, the feed resonance occur at
     slightly higher frequencies. Notable are the difference in the shape of the
@@
     receiving mode (equation \ref{eq11}) is the zero delay term $(1+\Gamma_{f})$.
-Hence the feed return loss, especially the shape of the low frequency resonant peak dominates the overall shape of the delay spectrum in figure
-    \ref{fig:sim_em}.\\
-
-   \subsubsection{Time domain simulation:}  
-    We also compare our measurements with the time domain simulation presented in ~\cite{Ewall-Wice_et_al2016}.
-In this simulation, electromagnetic response of the HERA element is determined as a function of time using the commercial numerical simulation software Microwave Studio developed by Computer Simulation Technology.
-The simulation assumed a constant $125\Omega$ impedance at the dipole terminals.
-In reality, dipole impedance is function of frequency across the entire band.
+Hence the feed return loss and especially the shape of the low frequency resonant peak dominates the overall shape of the delay spectrum in figure
+    \ref{fig:sim_em}. 
+ \textbf{The simulated return loss of the feed shows smooth variation across the band and wide resonant peaks resulting in a narrow delay spectrum.}
+
+   \subsubsection{CST Time domain simulation:}  
+    We also compare our measurements with the time domain simulation presented in ~\cite{Ewall-Wice_et_al2016} in figure \ref{fig:sim_em}.
+In this simulation, the transient electromagnetic response of the HERA element is determined as a function of time when it is subjected to a plane wavefront.
+The commercial numerical simulation software Microwave Studio, developed by Computer Simulation Technology is used for the simulation.
+The simulation assumed a constant 125~$\Omega$ impedance at the dipole terminal.
+Therefore, delay spectrum estimated from this simulation only has the effects of chromaticity introduced due to the structural reflections.
+In practice, dipole impedance is function of frequency that results in variation of return loss with frequency.
 This results in deviation between the simulated delay response and the delay spectrum estimate of our measurements.
@@
      \subsubsection{Foreground simulation:}  
-    We also compare our measurement with the foreground simulation of~\citep{Thyagarajan_et_al2016} as shown in the first panel of figure \ref{ds_full_sub_band}.
+    We also compare our measurement with the foreground simulation of~\citep{Thyagarajan_et_al2016} as shown by the shaded regions in the first panel of figure \ref{ds_full_sub_band}.
 The shaded region of each panel shows the EoR to
@@
     individual delays. This ratio is computed by
-    using the HFSS simulation of chromatic antenna beam and the sky models. Diffused sky foreground model is
+    using the HFSS simulation of chromatic antenna beam and the sky models. Diffused foreground sky model is
     incorporated from~\citep{deolivieracosta_et_al2008} whereas the point source
@@
     1.42~GHz~\citep{Condon_1998}, Sydney University Molonglo sky Survey (SUMSS)
-    ~\citep{Bock_et_al_1999}, \citep{Mauch_et_al_2003} at 843~MHz. The EoR signal
+    ~\citep{Bock_et_al_1999, Mauch_et_al_2003} at 843~MHz. The EoR signal
     is simulated by using 21cmFAST \citep{Messinger_et_al2011}. The model
@@
     are : Virial temperature of minimum mass of dark matter halos that host
-    ionizing sources, $T_{vir}^{min} = 2*10^4 K$, Ionising efficiency $\eta = 20$,
-    Mean Free Path of UV photons $R_{mfp} = 15Mpc.$ For these model parameter
+    ionizing sources, $T_{vir}^{min} = 2\times10^4$~K, Ionising efficiency $\eta = 20\%$,
+    mean free path of UV photons $R_{mfp} = 15$~Mpc For these model parameter
     values, the redshift of $50\%$ reionization is predicted to be at $z = 8.5$ at
     150MHz.  
-    EoR to foreground power ratio shows that for a given
+    The EoR to foreground power ratio shows that for a given
     delay mode, the estimate of a lower $k_{\parallel}$ mode requires a higher
     attenuation compared to a higher $k_{\parallel}$ mode. 
-     This simulation also, however, does not incorporate the frequency dependent antenna impedance that 
-     results in a frequency dependent return loss of power at the antenna terminal. Hence, the shaded region shows the most      
-     stringent limits of  EoR to foreground power ratio and sets the upper most limit of the required system performance under the assumption of non-chromatic return loss.
+    \textbf{This simulation provides a baseline for the system performance evaluation with a conservative strategy of pure foreground avoidance without any foreground mitigation strategy.
+The measurements differ from the simulation in one aspect.
+Simulation includes the frequency dependent antenna gain which does not include the return loss of of power at the antenna terminal due to frequency dependent antenna impedance.
+This effect is included in the measurements.
+  If included in the model, these limits would provide more conservative estimates of the required instrument response which will be even harder to achieve.}
+     % Hence, the shaded region shows the most      
+   %  stringent limits of EoR to foreground power ratio and sets the upper most limit of the required system performance under    
+     %the assumption of non-chromatic return loss.
 
@@
     \label{sub-band}
-    In HERA analysis, the 21~cm power spectrum
-    is estimated by gridding the observed data along the line of sight distance i.e
-    is in frequency or redshift and spatial frequency scale
+    In the HERA analysis, the 21~cm power spectrum
+    is estimated by discretizing the observed data along the line of sight distance i.e
+    in frequency or redshift and in the plane of the sky
     $k$~\citep{liu_et_al2014a}. At particular redshift, the bandwidth of
-    observation is so chosen that over corresponding $\Delta z$, the 21~cm
+    observation is so chosen that over the corresponding $\Delta z$, the 21~cm
     signal does not significantly evolve. Typically, the the 21~cm brightness
-    temperature fluctuation evolve over redshift scale $\Delta
-    z>0.5$~\citep{loeb_zaldarriaga2004},~\citep{lidz_et_al2008}. Hence, the delay
-    spectrum is estimated over smaller bandwidths.\\ We estimate the instrument
+    temperature fluctuation evolves over redshift scale $\Delta
+    z>0.5$~\citep{loeb_zaldarriaga2004},~\citep{lidz_et_al2008}. Therefore, the delay
+    spectrum is estimated over smaller bandwidths.
+
+    We estimate the instrument
     delay spectrum over various sub bands between 100 to 200~MHz as shown in figure
@@
     between 100-200, 100-140, 130-170, 160 to 200~MHz respectively. Each panel also
-    compares the delay spectrum estimate obtained em simulation of~\cite{deBoer_2016} at various subband.  Sub band delay spectra are wider compared to full
-    band delay spectrum.  Shape of the resonant peaks determines the roll off rate
+    compares the delay spectrum estimate obtained EM simulation of~\cite{deBoer_2016} at various subband. Subband delay spectra are wider compared to full
+    band delay spectrum.  The shape of the resonant peaks determines the roll off rate
     of the delay spectrum at all frequency ranges. At higher
-    frequency, our measurement closely follows the em simulations except around
+    frequency, our measurement closely follows the EM simulations except around
     80-120~ns where the cable reflection between the antenna and the backend manifests
-    itself at all frequencies. \\ 
-    The shaded regions however represents the EoR to Foreground power ratio simulated across the entire band.
+    itself.
+
+    The shaded regions represent the EoR to Foreground power ratio simulated across the entire band.
     The HFSS simulation of chromatic antenna beam varies smoothly across frequency resulting in no significant changes in this simulation at various sub bands.  
-     HERA system performance conforms directly to the limits as posed by simulations, at frequencies $>160~MHz$.
-With the measured system response including the multiple reflections, the instrument would be able to probe the spatial modes of interest $k_{\parallel}>0.2$ with very little foreground bleeding around $k_{\parallel} \approx 0.2$.
+     HERA system performance conforms directly to the limits as posed by simulations, at frequencies $>$160~MHz.
+With the measured system response including the multiple reflections, the instrument would be able to probe the spatial modes of interest $k_{\parallel}>0.2 h$~Mpc$^{-1}$ with very little foreground bleeding around $k_{\parallel} \approx 0.2 h$ Mpc$^{-1}$.
       At other frequencies, it is possible to do a successful measurement by weighting down the
@@
     \end{minipage}
-    \caption{Magnitude and phase of the return loss of the feed as simulated and measured.
-While both the measurement and the simulation shows similar resonance around $120~MHz$, the simulation shows a better matching to a 50 Ohm transmission line compared to the measurements.
-The measurement also has some small scale fluctuation due to multiple reflection of the signal at the VNA input.
+    \caption{Delay response of the instrument estimated from the measurements of the complex return loss of the HERA element and the feed (black).
+The blue curve shows the same estimated from the EM simulation of the feed and the HERA element.
+The shaded gray regions shows the ratio of the EoR to foreground power required to detect the EoR power spectrum at a given delay.
+At a given delay, detection of EoR power spectrum at smaller $k_{\parallel}$ mode requires higher attenuation of the foreground power.
+This is shown by three different shaded region.
+The instrument delay response estimated over the full band is dominated by the sharpest feature present in the observation band.
+At $120~MHz$, the feed impedance is best matched to the 50~$\Omega$ reference impedance providing a very low value of return loss.
+This feature, when Fourier transformed to delay domain results in a wide response.
+At higher frequencies , the measured return loss varies smoothly with frequency resulting in narrow delay response of the instrument.
 }
@@
  The HERA analysis pipeline for power spectrum estimation exploits the inverse covariance weighting to reduce the foreground contribution to the measured visibility data.
-In the light of this analysis technique we further investigate the limits of EoR to foreground power ratio from what is established by foreground simulation in \cite{Thyagarajan_et_al2016}.
-In the following section we briefly describe the power spectrum estimation technique used in HERA analysis and the inverse covariance weighting.
+In the light of this analysis technique we further investigate the limits of EoR to foreground power ratio from what is established by conservative estimates of \cite{Thyagarajan_et_al2016}.
+In the following section we briefly describe the power spectrum estimation technique used in HERA analysis and inverse covariance weighting.
 We evaluate the instrument delay response in the context of covariance weighting.
 
-    \section{\textbf{Power spectrum estimation}}
-
-    HERA power spectrum estimation is done using the Optimal Quadratic Estimator
+   % \section{\textbf{Power spectrum estimation}}  
+   \section{\textbf{Revised delay spectrum limit using inverse covariance weighting}}
+
+    HERA power spectrum estimation is done using the optimal quadratic estimator
     (OQE) formalism that has been outlined in extensive detail in  ~\cite{liu_et_al2010}, ~\cite{dillon_et_al2013a}, ~\cite{liu_et_al2014a}, ~\cite{liu_et_al2014b}, ~\cite{trott_et_al2012}, ~\cite{Ali_et_al2015}.
-We briefly  describe the OQE formalism here.
+We briefly  describe the a few major steps of OQE formalism here and evaluate the prototype HERA element response in the light of this analysis method.
     Conventionally, the 21~cm power spectrum $P_{21}(k_\perp,k_\parallel)$ is written as, 
-
     \begin{equation}
@@
     where $\langle  \tilde T_{b}(\bold k) \tilde T_{b}^{*}(\bold k^{'}) \rangle $ is the correlation function of the three dimensional spatial Fourier transform of the sky brightness temperature distribution $ \tilde T_{b}(\bold k)$, and $\delta$ is the Dirac delta function.
-While both $P_{21}(k_\perp,k_\parallel), \tilde T_{b}({\bold k})$ is continuous, the power spectrum estimate is discrete.
-Observation frequency and bandwidth are so chosen that the power spectrum could be approximated as a constant and a piecewise continuous function of $\bold k$  which correspond to a thin shell in $\bold k$ space.
-This corresponds to the $k_{\perp}$, $k_{\parallel}$  values $a <k_{\perp} < a+1$, $b <k_{\parallel} < b+1$ where the indices a, b can assume M, N different values.
-We denote the power spectrum as $\hat p_{\alpha}$ where alpha represents a particular $(M,N)$ value.
-Our analysis begins with a data vector $\bold x$.
-$\bold x$ is the list of visibilities measured at a given frequency over a certain bandwidth i.e for a given $k_{\parallel}$ mode for a given $\Delta  k $.
-The first estimate of power spectrum is written as,
-
-    \begin{equation}
-    \hat q_{\alpha} = \bold x^{T} E^{\alpha} \bold x  - b^{\alpha}
+%While both $P_{21}(k_\perp,k_\parallel)$ and $\tilde T_{b}({\bold k})$ are continuous, the power spectrum estimate is discrete.
+Observation frequency and bandwidth are so chosen that the power spectrum is approximated as a constant and a piecewise discrete function of $\bold k$  which correspond to a thin shell in $\bold k$ space assuming isotropy perpendicular to the line of sight.
+ %This corresponds to the $k_{\perp}$, $k_{\parallel}$  values $a <k_{\perp} < a+1$, $b <k_{\parallel} < b+1$ where the indices a, b can assume M, N different values.  
+ We denote the power spectrum estimate as $\hat p_{\alpha}$ where $\alpha$ represents a particular value of $k_{\parallel}, k_{\perp}$.
+If $\bold x$ is the list of visibilities measured at a given frequency over a certain bandwidth i.e for a given $k_{\parallel}$ mode for a given $\Delta  k $, the first estimate of power spectrum is,
+    \begin{equation}
+    \hat q_{\alpha} = \bold x^{T} E^{\alpha} \bold x % - b_{\alpha}
     \label{eq15}
     \end{equation}
-
-    where $b_{\alpha}$ is a constant that assumes different values for each $\bold k$ and represents any additive noise power spectrum or residual foreground contamination to power spectrum estimate.
-$b_{\alpha}$ could be eliminated from the estimate by cross correlating two visibility data sets at two different times.
-$E^{\alpha}$ is a symmetric matrix operation denoting the Fourier transform of the data, binning, and foreground reduction.
-Various binning and foreground reduction technique would result in various different form of $E^{\alpha}$ resulting in estimates of $\hat p_{\alpha}$ with non identical statistics.
+ %   where $b_{\alpha}$ is additive noise bias  to the power spectrum estimate.
+In practice, $b_{\alpha}$ can be eliminated from the estimate by cross correlating two visibility data sets with different noise terms.
+ where, $E^{\alpha}$ is a symmetric matrix operation denoting the Fourier transform of the data, binning, and foreground reduction.
+Various binning and foreground reduction techniques result in different forms of $E^{\alpha}$ resulting in estimates of $\hat p_{\alpha}$ with different statistics.
 A possible choice of $E^{\alpha}$ is
@@
     where $C = \langle \bold x \bold x^{t} \rangle$ is the covariance matrix of the data vector $\bold x$.
-$Q_{\alpha} \equiv {\delta C \over \delta p_{\alpha} } $ is a matrix operator that Fourier transforms the visibilities along the frequency axis and maps them into the $\bold k$ space for every M,N values.
+$Q_{\alpha}$ is a matrix operator that Fourier transforms the visibilities along the frequency axis and maps them into the $\bold k$ space.
 Finally, the normalized estimate of the power spectrum could be written as,
@@
     \end{equation} 
-
-    Since $\hat p_{\alpha}$ is a discrete estimate of the true power spectrum $p_{\alpha}$, both are related by the window function matrix $W$, 
+    where $M$ is the normalization matrix.
+ The true power spectrum $p_{\alpha}$ is related to $\hat p_{\alpha}$  by the window function matrix $W$, 
     \begin{equation}
@@
 
-    Hence, the estimated power spectrum $\hat p_{\alpha}$ for a given $k_{\perp}, k_{\parallel}$ values would have contribution for the nearby $k_{\perp}, k_{\parallel}$ values weighted by the window function.
-The wider the window function, the larger would be the contribution of the adjacent modes to the discrete power spectrum estimate.
-In general, therefore, $W$ is a non-diagonal matrix.
-Also, for a given choice of normalization matrix M, the window function W will be,
-
-    \begin{equation}
-     W = MF
-     \label{eq19}
-    \end{equation}
-
-    where , 
-    \begin{equation}
-     F_{\alpha\beta} = \frac {1} { 2} [C^{-1}Q_{\alpha}C^{-1}Q_{\beta}]^{T}
-     \label{eq20}
-    \end{equation} 
-     is the Fisher matrix of the measured data.
+   % Hence, the estimated power spectrum $\hat p_{\alpha}$ for a given $\bold k $ values would have contribution for the nearby $\bold k$ values weighted by the window function.% The wider the window function, the larger would be the contribution of the adjacent modes to the discrete power spectrum estimate.
+%In general, $W$ is a non-diagonal matrix. For a given choice of normalization matrix M, the window function W will be,
+
+   % \begin{equation}
+    % W = MF
+     %\label{eq19}
+    %\end{equation}
+
+   % where , 
+    %\begin{equation}
+     %F_{\alpha\beta} = \frac {1} { 2} [C^{-1}Q_{\alpha}C^{-1}Q_{\beta}]^{T}
+     %\label{eq20}
+    %\end{equation} 
+     %is the Fisher matrix of the measured data.
 The choice of normalization matrix $M$ is critically important for the analysis.
-If $M = F^{-1}$, $W=I$ resulting in $\hat p_{\alpha} = p_{\alpha}$ i.e, estimated value of the power spectrum equals to the true power spectrum.\\
-     The errors on the power spectrum estimate is given by the covariance of the band power which could be computed from the measured data as,  
-    \begin{eqnarray}
-     C_{\alpha} & = & \langle \hat p_{\alpha} \hat p_{\alpha}^{T} \rangle - \langle \hat p_{\alpha} \rangle \langle \hat p_{\alpha}^{T} \rangle \nonumber\\
-     		& = & MFM^{T}
-    \label{eq21}
-     \end{eqnarray}
-
-     For a choice of $M = F^{-1}$, the covariance in the estimated band power is as large as $M$ resulting in highest error in estimation.
+If $M \propto F^{-1}$, $W\propto I$ resulting in $\hat p_{\alpha} = p_{\alpha}$ i.e, estimated value of the power spectrum equals to the true power spectrum.\\
+     %The errors on the power spectrum estimate is given by the covariance of the band power which could be computed from the measured data as,  
+    %\begin{eqnarray}
+     %C_{\alpha, \beta} %& = & \langle \hat p_{\alpha} \hat p_{\beta}^{T} \rangle - \langle \hat p_{\alpha} \rangle \langle \hat p_{\beta}^{T} \rangle \nonumber\\
+     	%	& = & MFM^{T}
+    %\label{eq21}
+     %\end{eqnarray}
+
+     %For a choice of $M \propto F^{-1}$, the covariance in the estimated band power is as large as $M$ resulting in highest error in estimation.
 Hence, the choice of the normalization matrix $M$ is critical in the analysis process since its precise form determines the vertical error bars in the estimate of power spectrum.
 
-    \subsection{Inverse covariance weighting: revised delay spectrum limit}
-
-    The inverse variance weighting method is a method of aggregating two or more
-    random variable to minimize the variance in their weighted average. In our
-    case, the measured visibility is contributed by EoR, foreground and
-    instrumental noise. Hence, the estimate of any of the constituent signals would
-    benefit from if the measured data is weighted by the covariance of the
-    individual components. This is reflected in our choice of the matrix
-    $E^{\alpha}$.  $E^{\alpha} = {1 \over 2} C^{-1} Q_{\alpha} C^{-1}$ represents a
-    weighting of the data vector $\bold x$ by inverse of its covariance. This
-    results in the smallest vertical error bar in the power spectrum estimate $\hat
-    p_{\alpha}$ \citep{liu_tegmark2011}.  However, there is no definite way to know the
-    covariance of individual signal components prior to estimating them. In
-    practice, the total covariance matrix $C$ is computed from the measured
-    visibilities. It is a sum of covariances of the foreground, instrumental noise
-    and the EoR signals. The highest covariance is rendered by the signal which is
-    correlated over various frequency channels at all frequencies such as
-    foreground. Hence, weighting the measured visibility by the inverse of the
-    covariance results in order of magnitude reduction of foreground power against
-    the EoR signal. \\ 
-    Combining the inverse covariance weighting formalism with the
-    foreground simulation of \cite{Thyagarajan_et_al2016}, we derive a new limit on
-    foreground attenuation with respect to the EoR signal required for
-    power spectrum estimation using HERA measurements. The foreground model of
-    \cite{Thyagarajan_et_al2016} as described in section \ref{sub-band} is adopted here. We use
-    the reflectometry measurements, corrected for the antenna response in the
-    receiving mode, to compute the visibilities (eq 13) for the given model of the
-    foreground, the EoR and the system noise. Notable here is, our measurement contains 
-     beam chromaticity as well as chromaticity of the antenna impedance i.e, the effect 
-     of return loss of power at the antenna terminal . These visibilities formed the complex
-    data vector $\bold x$. We compute the covariance matrix $C$ from the simulated
-    data. $\bold x$ is then multiplied by the inverse of the covariance matrix.
-    This step essentially weighs down the foreground contribution to the measured
-    data. Once Fourier transformed, the delay spectrum of the simulated data is
-    constituted by linear super position of the delay spectrum of the foreground,
-    the EoR signal.  We again compute the EoR to foreground power ratio which is
-    now large due to relatively smaller foreground contribution than what is estimated in \cite{Thyagarajan_et_al2016} as shown       in fig: \ref{fig:sim_fg_revised}.
+   % \subsection{Inverse covariance weighting: revised delay spectrum limit}
+  The critical step in the power spectrum estimation formalism is weighting of the data by the inverse of its covariance.
+This results in orders of magnitude reduction in the foreground power relative to the EoR signal.
+We combine the inverse covariance weighting formalism with the
+   simulations of \cite{Thyagarajan_et_al2016} and derive a revised limit on required foreground power reduction with respect to EoR for a successful power spectrum measurement.
+The foreground model of
+    \cite{Thyagarajan_et_al2016} as described in section \ref{sub-band} is adopted here to compute the 
+    data vector $\bold x$ which contains contributions from the EoR, the foreground, and
+   the instrument noise.
+The computed power spectra with and without covariance weighting are shown in figure \ref{fig:cov_weight}.
+The orange curve represents the power spectrum computed from the EoR model for three different baseline orientations for a pair of adjacent HERA elements.
+The blue curves show the power spectrum of the observed sky signal including both foreground and the EoR.
+The contribution from the bright foregrounds dominate the lower delay modes making separation of the EoR from the foreground impossible up to delays $\approx 300$ ~ns.
+   % The matrix $E^{\alpha}$ represents a weighting of the data vector $\bold x$ by inverse of its covariance.
+   Weighting by the covariance matrix which is estimated from the simulated data, results in orders of magnitude reduction in the foreground power relative to the EoR signal at low delays and allow us to estimate the power spectrum at those delays.
+The covariance weighted power spectrum is shown by the purple curve in the plot.
+If any systematic
+    fluctuation is identified by their covariance in frequency, those particular
+    modes can be down-weighted by the inverse covariance weighting. 
+    %Strongsystematics that appear in the covariance of $\bold x$ will appear as eigen modes
+    %of $C$, which will be downweighted in $C^{-1}$ by the square of their corresponding
+    %eigenvalue.
+    \begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/figure_cov_weight.png}
+    \caption{The HERA feed consists of a pair of crossed-dipoles over 1.72 m diameter backplane made of wire mesh.
+The backplane is surrounded by 0.36 m wide wire mesh around the edge resulting in encasing the crossed-dipoles in a cylindrical cage.}
+    \label{fig:cov_weight}
+    \end{figure}
+      %The chromaticity of HERA element introduces a (potentially direction dependent) frequency
+     %covariance in our data. As a result, the
+     %covariance convolves bright foregrounds in $\bold k$-space,
+     %foreground spills into $\bold k$ modes outside the maximum geometric
+     %delay where they contaminate measurements of the EoR power spectrum.
+     %Weighting the measured visibility by the inverse of its
+    %covariance results in orders-of-magnitude reduction in foreground power relative to
+    %the EoR signal.
+    In this sense, using optimal quadratic estimators can dramatically 
+    reduce our reliance on smooth instrumental responses, with a corresponding reduction
+    in the stringency of instrument performance specification.
+
+     We again compute the required attenuation of foreground power relative to the EoR signal at every delay and compare it with the delay response of the instrument.
+\textbf{This ratio now has higher values at each delay in comparison with the conservative estimate provided by \cite{Thyagarajan_et_al2016} as shown in fig: \ref{fig:sim_fg_revised}.
+}
+     %Combining the inverse covariance weighting formalism with the
+    %foreground simulation of \cite{Thyagarajan_et_al2016}, we derive a new specification on
+    %foreground attenuation with respect to the EoR signal required for
+    %power spectrum estimation. The foreground model of
+    %\cite{Thyagarajan_et_al2016} as described in section \ref{sub-band} is adopted here. %We use
+   % the reflectometry measurements, corrected for the antenna response in the
+    %receiving mode (eq \ref{eq11}) to compute the visibilities for the given model of the
+    %foreground, the EoR and the system noise. 
+     \textbf{Our measurement includes chromaticity of the beam as well as antenna impedance as a function of frequency i.e, the effect 
+     of return loss of power at the antenna terminal. Angular response of the antenna beam 
+     can also be a function of frequency and introduce additional modes of fluctuations. This is included in the conservative estimates of \cite{Thyagarajan_et_al2015}. Our
+     measured response is beam integrated and does not take into account this angle dependency.}
+     %These visibilities formed the complex
+    %data vector $\bold x$. We compute the covariance matrix $C$ from the simulated
+    %data. It is hard to know the
+    %covariance of systematics in $\bold x$ prior to estimating them from the data. In
+    %practice, the total covariance matrix $C$ is often estimated from the measured
+    %visibilities themselves~\citep{Ali_et_al2015}. 
+    %$\bold x$ is then multiplied by the inverse of the covariance matrix.
+    %This step essentially weighs down the foreground contribution to the measured
+    %data. Once Fourier transformed, the delay spectrum of the simulated data is
+    %constituted by linear super position of the delay spectrum of the foreground,
+    %and the EoR signal.
 
@@
     \centering
-    \includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/HERA_ds_fg_sim_rev.png}
+    \includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/HERA_ds_fg_sim_revised.png}
     \caption{Delay spectrum of HERA element estimated from the reflectometry measurements by a vector network analyzer.
-The colored region shows the revised EoR to foreground power ratio in comparison to the measurements and the foreground simulation presented in \cite{Thyagarajan_et_al2016}.}
+The colored region shows the revised EoR to foreground power ratio in comparison to our measurements and the conservative estimates presented in \cite{Thyagarajan_et_al2016}.
+Once again it is shown that for a given delay, power spectrum estimate for a small $k_{\parallel}$ value requires higher attenuation of foreground power with respect to EoR.
+However, due to inverse covariance weighting of the visibility, the foreground contribution at each delay is reduced relaxing the limits on the required attenuation by about $30~dB$ at each delay.}
     \label{fig:sim_fg_revised}
     \end{figure*}
-    This demonstrates that the performance of the HERA element, in conjunction with the inverse covariance method of foreground suppression, qualifies the system for its the science goal it is designed for, irrespective of its intrinsic chromatic response as well as chromaticity generated due to multiple reflections in the system.
-
+   \textbf{ This demonstrates that the performance of the HERA element including it intrinsic chromaticity and chromaticity generated due to multiple reflections in the system.
+The prototype HERA element delay response, in conjunction with the inverse covariance method of foreground suppression, indicates that the HERA can make a successful power spectrum measurement for the spatial modes as low as $k_{\parallel} >0.1 h$ Mpc$^{-1}$.}
     %Covariance matrix $C$ is computed from the simulated visibility data.
@@
     %would  for power spectrum measurements, especially at smaller spatial scales of fluctuation i.e lower values of $k_{\parallel}$.
-
     \section{\textbf{Conclusion}}
-
-    The interplay between the extremely bright sky signal with the system response
-    has remained somewhat undermined for the first generation 21cm experiments such
-    as MWA, LOFAR, PAPER. With the theory of redshifted 21cm experiments have very
-    well evolved, it is absolute necessity now to quantify the instrumental limits
-    of these measurement in order to produce a believable power spectrum estimates.
-    In this paper, we studied the performance of a HERA element in both frequency
-    as well as delay domain. We derived the explicit relationship between the measured return loss
-    of the HERA element using a vector network analyser and the EoR to foreground power ratio.
+     \textbf{The interplay between the extremely bright sky signal and the system response
+    has remained somewhat undetermined for the first generation 21cm experiments such
+    as MWA, LOFAR, PAPER. With the theory of redshifted 21cm experiments very
+    well evolved, it is now absolutely necessary to quantify the instrumental limits
+    of these measurements in order to produce accurate power spectrum estimates.}
+
+    In this paper, we studied the performance of a prototype HERA element in both frequency
+    as well as delay domain. \textbf{In this paper, we have introduced a mathematical formalism that explicitly
+    relate the delay response of the HERA element to EoR to foreground power ratio.}
     The effects of multiple reflections  in a HERA
-    feed-dish assembly is investigated in detail and their effects on the measured
+    element is investigated in detail and their effects on the measured
     visibility as well as delay spectrum is estimated.  The delay-domain
     performance of the HERA dish is central to HERA's function as a power spectrum
-    instrument. Reflectometry measurements characterised HERA's performance in this
-    domain, and as Equation \ref{eq10} shows, these measurements must be adjusted
+    instrument.
+
+    Reflectometry measurements characterized HERA's performance in this
+    domain and, as equation \ref{eq10} shows, these measurements must be adjusted
     for a difference in transmission/reception at the first feed encounter in
@@
     higher delays, where sidelobes from much higher amplitude responses at small
-    delays can easily dominate.  Blackman-Harris window is found to be generally
+    delays can easily dominate. The Blackman-Harris window is found to be generally
     adequate while square windowing functions are not.  Given the critical nature
@@
     are then compared with the electromagnetic as well as time domain simulation of
-    the HERA element~\citep{Ewall-Wice_et_al2016}, ~\citep{ddboer_et_al2016}. The
-    same is then compared with the foreground simulation
-    of~\cite{Thyagarajan_et_al2015}. The performance is also evaluated in the light
+    the HERA element~\citep{ddboer_et_al2016, Ewall-Wice_et_al2016}. The
+    same is then compared with the estimates derived from the foreground simulation
+    of~\cite{Thyagarajan_et_al2016}. The performance is also evaluated in the light
     of HERA power spectrum estimation technique using inverse covariance weighting
-    formalism.  Taken all together, we summarise that the HERA antenna element,
-    with a PAPER-style crossed dipole feed and cylindrical cage the instrument
-    delay spectrum satisfies the criteria necessary to meet its science
+    formalism.  Taken all together, we conclude that the HERA antenna element,
+    with a PAPER-style crossed dipole feed and cylindrical cage, satisfies the criteria necessary to meet its science
     goal. \\
@@
 This work was supported by the U.S. National Science Foundation (NSF) through awards AST-1440343 and AST-1410719.
-ARP acknowledges support from NSF CAREER award 1352519.
+ARP acknowledges support from NSF CAREER award 13
+
+52519.
 AL acknowledges support for this work by NASA through Hubble Fellowship grant \#HST-HF2-51363.001-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS5-26555.

### 2016-11-08 DishReflectometry/Paper1_v4.tex
Edits to S6

@@
    % \section{\textbf{Power spectrum estimation}}  
-   \section{\textbf{Revised delay spectrum limit using inverse covariance weighting}}
+   \section{\textbf{Revised delay spectrum specification using inverse covariance weighting}}    
+    The results we presented in the previous section focused on the delay-domain performance of
+the antenna, where it convolves the foreground signal and must fall beneath the amplitude of the 
+21cm EoR signal to avoid a systematic bias.  We used a windowed delay tranformation to make these comparisons.
+This simple analysis lends itself to being easily interpretable, but it omits the 
+suppression of foreground systematics that are a feature of more sophisticated power spectrum estimation techniques.
+In this section, we explore how we might re-evaluate our specification for the delay-domain performance of
+the HERA antenna in light of these techniques.
 
@@
     (OQE) formalism that has been outlined in extensive detail in  ~\cite{liu_et_al2010}, ~\cite{dillon_et_al2013a}, ~\cite{liu_et_al2014a}, ~\cite{liu_et_al2014b}, ~\cite{trott_et_al2012}, ~\cite{Ali_et_al2015}.
-We briefly  describe the a few major steps of OQE formalism here and evaluate the prototype HERA element response in the light of this analysis method.
-    Conventionally, the 21~cm power spectrum $P_{21}(k_\perp,k_\parallel)$ is written as, 
+We briefly  describe the major steps of OQE formalism here and evaluate the prototype HERA element response in the light of this analysis method.
+
+The 21~cm power spectrum $P_{21}(k_\perp,k_\parallel)$ is related to the temperature field as, 
     \begin{equation}
@@
  %This corresponds to the $k_{\perp}$, $k_{\parallel}$  values $a <k_{\perp} < a+1$, $b <k_{\parallel} < b+1$ where the indices a, b can assume M, N different values.  
- We denote the power spectrum estimate as $\hat p_{\alpha}$ where $\alpha$ represents a particular value of $k_{\parallel}, k_{\perp}$.
-If $\bold x$ is the list of visibilities measured at a given frequency over a certain bandwidth i.e for a given $k_{\parallel}$ mode for a given $\Delta  k $, the first estimate of power spectrum is,
-    \begin{equation}
-    \hat q_{\alpha} = \bold x^{T} E^{\alpha} \bold x % - b_{\alpha}
+ We estimate the power spectrum $P(k)$ integrated over a range of $k_\parallel, k_\perp$.  We call this 
+the bandpower $\hat p_{\alpha}$, where $\alpha$ represents a range of $k_{\parallel}, k_{\perp}$. Let us take
+$\bold x$ to be a vector of visibilities measured at range of frequencies.  We can estimate unnormalized
+band powers $\hat q_\alpha$ according to the equation
+    \begin{equation}
+    \hat q_{\alpha} = \bold x^{T} E^{\alpha} \bold x, % - b_{\alpha}
     \label{eq15}
@@
 In practice, $b_{\alpha}$ can be eliminated from the estimate by cross correlating two visibility data sets with different noise terms.
- where, $E^{\alpha}$ is a symmetric matrix operation denoting the Fourier transform of the data, binning, and foreground reduction.
+ where $E^{\alpha}$ is a symmetric matrix operation denoting the Fourier transform of the data, binning, and foreground reduction.
 Various binning and foreground reduction techniques result in different forms of $E^{\alpha}$ resulting in estimates of $\hat p_{\alpha}$ with different statistics.
@@
    % \subsection{Inverse covariance weighting: revised delay spectrum limit}
-  The critical step in the power spectrum estimation formalism is weighting of the data by the inverse of its covariance.
-This results in orders of magnitude reduction in the foreground power relative to the EoR signal.
-We combine the inverse covariance weighting formalism with the
-   simulations of \cite{Thyagarajan_et_al2016} and derive a revised limit on required foreground power reduction with respect to EoR for a successful power spectrum measurement.
-The foreground model of
-    \cite{Thyagarajan_et_al2016} as described in section \ref{sub-band} is adopted here to compute the 
-    data vector $\bold x$ which contains contributions from the EoR, the foreground, and
+  The critical step in the power spectrum estimation formalism is the weighting of the data by the inverse of its covariance.
+This can result in orders-of-magnitude reduction in the foreground power relative to the EoR signal because foregrounds tend to be concentrated into a small number of eigenmodes.
+
+To derive a delay-spectrum specification for an antenna using the inverse covariance weighting, we begin
+with the
+   simulations of \cite{Thyagarajan_et_al2016} and use OQE formalism to estimate the amplitude of the power spectrum
+from a simulated data vector $\bold x$ 
+    which contains contributions from the EoR, the foreground, and
    the instrument noise.
-The computed power spectra with and without covariance weighting are shown in figure \ref{fig:cov_weight}.
-The orange curve represents the power spectrum computed from the EoR model for three different baseline orientations for a pair of adjacent HERA elements.
-The blue curves show the power spectrum of the observed sky signal including both foreground and the EoR.
-The contribution from the bright foregrounds dominate the lower delay modes making separation of the EoR from the foreground impossible up to delays $\approx 300$ ~ns.
+The computed power spectra with and without covariance weighting are shown in figure \ref{fig:cov_weight}, where the strong dependence of the foreground amplitude on the weighting of the data can be clearly seen.
+The orange curve indicates the power spectrum computed from the EoR model averaged over three different baseline orientations for adjacent HERA elements.
+The blue curve indicates the power spectrum of the observed sky signal including both foreground and the EoR using the windowed delay transform analysis.
+Here, the contribution from the bright foregrounds dominate the lower delay modes, making separation of the EoR from the foreground impossible up to delays $\approx 300$ ~ns.
    % The matrix $E^{\alpha}$ represents a weighting of the data vector $\bold x$ by inverse of its covariance.
-   Weighting by the covariance matrix which is estimated from the simulated data, results in orders of magnitude reduction in the foreground power relative to the EoR signal at low delays and allow us to estimate the power spectrum at those delays.
-The covariance weighted power spectrum is shown by the purple curve in the plot.
-If any systematic
-    fluctuation is identified by their covariance in frequency, those particular
-    modes can be down-weighted by the inverse covariance weighting. 
+The covariance weighted power spectrum is illustrated by the purple curve in the plot. 
+   Weighting by the covariance matrix estimated from the simulated data dramatically reduces the foreground power relative to the EoR signal at low delays, opening up the possibility of estimating the EoR power spectrum at those delays.
+
+When using simple delay-transform power spectrum estimation, the chromaticism of the antenna convolves
+the foreground signal in delay domain.  As described in \ref{Thyagarajan_et_al2016}, this 
+enables us to set a specification
+for our antenna reflectometry as a function of delay, as illustrated by the grey shaded regions in
+Figure \ref{fig:sim_fg_revised}.  This relationship is not as simple when using
+optimal quadratic power-spectrum estimation.  For example, a direction-independent bandpass shape 
+that multiplies the foreground signal falls into a single eigenmode that can be downweighted essentially to zero.
+This makes the interpretation of the output power spectrum as a reflectometry constraint problematic.  Without
+knowing in detail the direction dependence of the antenna chromaticism, we cannot know how many eigenmodes
+will be occupied by the systematics arising from the foreground-dish interaction.
+
+To be relatively conservative, we simply use the inverse covariance weighted power spectrum from simulations that
+do not include antenna chromaticism as an effective input foreground amplitude and repeat the translation to
+a reflectometry specification as before.  The result is illustrated by the colored shaded regions
+in Figure \ref{fig:sim_fg_revised}.  This approach ignores the ability of OQE to identify and invert
+instrumental covariances, making it a relatively conservative standard.  On the other hand, should the number
+of direction-dependent spectral eigenmodes of the dish become large, this approach could potentially underestimate
+the impact of dish chromaticism.  Therefore, we present it as a demonstration that our reflectometry specifications
+could be substantially less stringent for HERA's OQE pipeline, but suggest not over-interpreting the exact 
+level of the implied specification without a detailed analysis of the direction dependence of the reflectometry
+results.
+
     %Strongsystematics that appear in the covariance of $\bold x$ will appear as eigen modes
@@
     %the EoR signal.
-    In this sense, using optimal quadratic estimators can dramatically 
-    reduce our reliance on smooth instrumental responses, with a corresponding reduction
-    in the stringency of instrument performance specification.
-
-     We again compute the required attenuation of foreground power relative to the EoR signal at every delay and compare it with the delay response of the instrument.
+    %In this sense, using optimal quadratic estimators can dramatically 
+    %reduce our reliance on smooth instrumental responses, with a corresponding reduction
+    %in the stringency of instrument performance specification.
+
+     %We again compute the required attenuation of foreground power relative to the EoR signal at every delay and compare it with the delay response of the instrument.
 \textbf{This ratio now has higher values at each delay in comparison with the conservative estimate provided by \cite{Thyagarajan_et_al2016} as shown in fig: \ref{fig:sim_fg_revised}.
@@
     %foreground, the EoR and the system noise. 
-     \textbf{Our measurement includes chromaticity of the beam as well as antenna impedance as a function of frequency i.e, the effect 
-     of return loss of power at the antenna terminal. Angular response of the antenna beam 
-     can also be a function of frequency and introduce additional modes of fluctuations. This is included in the conservative estimates of \cite{Thyagarajan_et_al2015}. Our
-     measured response is beam integrated and does not take into account this angle dependency.}
+     %\textbf{Our measurement includes chromaticity of the beam as well as antenna impedance as a function of frequency i.e, the effect 
+     %of return loss of power at the antenna terminal. Angular response of the antenna beam 
+     %can also be a function of frequency and introduce additional modes of fluctuations. This is included in the conservative estimates of \cite{Thyagarajan_et_al2015}. Our
+     %measured response is beam integrated and does not take into account this angle dependency.}
      %These visibilities formed the complex

### 2016-12-07 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev4_submitted.tex
update to published version

--- 2016-02-12 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev4.tex
@@
 Rusty Taylor\altaffilmark{4},
+Max Tegmark\altaffilmark{1,2},
 Butch Wirt\altaffilmark{4},
@@
 
-In detail, we simulate visibilities using PRISim\footnote{https://github.com/nithyanandan/PRISim} for each beam model at various LSTs, modeling the sky as the sum of the Global Sky Model \citep{gsm} and the NVSS \citep{nvss} and SUMSS \citep{sumss,sumss2} point source catalogs.
+In detail, we simulate visibilities using the Precision Radio Interferometry Simulator\footnote{https://github.com/nithyanandan/PRISim} (PRISim) for each beam model at various LSTs, modeling the sky as the sum of the Global Sky Model \citep{gsm} and the NVSS \citep{nvss} and SUMSS \citep{sumss,sumss2} point source catalogs.
 We use a frequency spacing of 781\,kHz, sufficient to characterize delays within and just outside of the horizon limits on both baseline lengths considered, 14.6\,m and 43.8\,m.

### 2016-12-07 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev5.tex
update to published version

--- 2016-12-07 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev4_submitted.tex
@@
 We measure the angular response at 137\,MHz using the ORBCOMM beam mapping system of \citet{neben15}.
-We measure a collecting area of 93\,m$^2$ in the optimal dish/feed configuration, implying HERA-320 should detect the EOR power spectrum at $z\sim9$ with a signal-to-noise ratio of 19.3 using a foreground avoidance approach, and 74.3 using a foreground subtraction approach.
+We measure a collecting area of 93\,m$^2$ in the optimal dish/feed configuration, implying HERA-320 should detect the EOR power spectrum at $z\sim9$ with a signal-to-noise ratio of 12.7 using a foreground avoidance approach with a single season of observations, and 74.3 using a foreground subtraction approach.
 Lastly we study the impact of these beam measurements on the distribution of foregrounds in Fourier space.
@@
 The HERA element (Fig.
-\ref{fig:feeddiagram}) is a 14\,m diameter faceted parabolic dish ($ f/D=0.32$) with a dual-polarized dipole feed suspended at prime focus \citep{dishmemo}.
+\ref{fig:feeddiagram}) is a 14\,m diameter faceted paraboloid ($ f/D=0.32$) with a dual-polarized dipole feed suspended at prime focus \citep{dishmemo}.
 Here $f$ is the focal length of the dish and $D$ is the dish diameter.
 The dish surface is formed by wire mesh sheets (i.e., facets) mounted on PVC tubes which run from the lip of the dish to the hub at the vertex.
-For these tests, the feed consists of a dual linear polarization PAPER sleeved dipole mounted 17'' below a 78'' diameter wire mesh back plane surrounded by a 30'' deep cylinder, suspended from cables attached to each of the three telephone poles around the dish.
+For these tests, the feed consists of a dual linear polarization PAPER sleeved dipole mounted 17'' below a 78'' diameter wire mesh back plane surrounded by a 30'' deep cylinder.
+The feed is suspended from a single point on its back plane from three ropes, each attached to a telephone pole.
+The three telephone poles are equally spaced around the dish.
 The dipole ``sleeves'' are circular disks just above and below the dipole designed to broaden its frequency response.
-The cylinder is offset 0.5'' from the back plane, and is designed to make the beams for both linear polarizations more similar.
+The feed cylinder is offset 0.5'' from the back plane, and is designed to make the dipole beam more azimuthally symmetric and also taper its response near the edges of the dish to reduce spillover into adjacent dishes.
 Fig.
 \ref{fig:feedphoto} shows the feed as deployed on the ground for early testing.
-The nominal dish focus is $f=(f/d)D=4.48$\,m, though given its faceted design, the dish does not have a single focus.
-Our numerical electromagnetic models suggest the best focus is slightly higher due to the feed geometry.
+
+The nominal dish focus is $f=(f/D)D=4.48$\,m, though given its faceted design, the dish does not have a single focus.
+Our numerical electromagnetic models suggest the best focus is slightly higher than that of an perfect paraboloid.
 In this work we study the dish beam pattern at rigging heights of 4.5\,m, 5.0\,m, and 5.3\,m, measured from dish surface to feed plane, the last height being the maximum height we can achieve with the feed suspension system installed on the dish.
@@
 For more details on the dish design and construction see \citet{deboer16}.
-Feed/dish optimization studies are ongoing and the values of these parameters may change in the full HERA array \citep{feedoptimizationmemo}.
+Feed optimization studies are ongoing and the values of these parameters may change in the full HERA array \citep{feedoptimizationmemo}.
 
@@
 \begin{figure}[h]
-\includegraphics[width=3.4in]{feed.jpg}
+\includegraphics[width=3.4in]{feed.pdf}
 \caption{Prototype HERA feed seen here outside the dish and upside-down for preliminary characterization.
@@
 \caption{Simulated dish power patterns (NS polarization) at 137\,MHz (see Sec.
-\ref{sec:dishmodels}) with $h_\text{feed}=5$\,m using HFSS (left) and CST (middle) are shown beside an ideal Airy pattern for a 14\,m diameter dish for comparison.
+\ref{sec:dishmodels}) with $h_\text{feed}=5$\,m using the full-faceted model (left) and the perfect paraboloidal model (middle) are shown beside an ideal Airy pattern for a 14\,m diameter dish for comparison.
 Dased lines mark zenith angles of 20$^\circ$, 40$^\circ$, 60$^\circ$, and 80$^\circ$.}
@@
 
-We numerically model the HERA dish in both ANSYS HFSS\footnote{http://www.ansys.com/Products/Electronics/ANSYS-HFSS} and in CST Microwave Studio\footnote{https://www.cst.com/Products/CSTMWS}, making slightly different assumptions, in order to study the range of realistic beams given modeling inaccuracies and material imperfections.
+We numerically model the HERA dish in two different ways in order to study the range of realistic beams given modeling inaccuracies and material imperfections.
 In particular, the near horizon beam response, which sets the level of horizon brightening in the delay spectrum, is quite sensitive to modeling assumptions.
+We first generate a full-faceted model of the dish using ANSYS HFSS\footnote{http://www.ansys.com/Products/Electronics/ANSYS-HFSS}.
+All mesh surfaces are modeled as solid aluminum and the dipole itself is modeled as copper.
+The 1\,m concrete circle at the vertex is modeled with a dielectric similar to dry soil.
+For comparison, we also model the dish as a perfect paraboloid.
+We simulate this second model using CST Microwave Studio\footnote{https://www.cst.com/Products/CSTMWS}, but the differences are dominated by the dish geometry, not the choice of numerical electromagnetic solver.
 
-The HFSS model uses a realistic faceted dish \citep{deboer16} ($f/D=0.32$) with a 1\,m diameter dielectric similar to dry soil at the vertex.
-In reality a 1\,m diameter circle at the vertex is filled with concrete and supports the PVC pipes which suspend the mesh panels, but we effectively assume here it is perfectly absorbant.
-The feed is modeled as a sleeved dipole with a solid metal back plane and cylinder with the dimensions given above.
-Copper is used for the dipole itself, and aluminum for all reflecting surfaces.
-In the simulations, we excite one of the dipoles using a modal port and measure the total gain response in each direction to 137.5\,MHz radiation.
-
-The CST model assumes a 14\,m diameter perfect paraboloid of solid aluminum with $f/D=0.32$ but neglects the 1\,m hole at the vertex, effectively assuming the concrete and earth ground behind it are perfectly reflective.
-The feed model has the same dimensions and properties as in the HFSS model.
-These simulations are done by exciting one of the dipoles with band-limited noise (100--200\,MHz), then measuring the farfield radiation in each direction after the excitation pulse energy within the structure decays to below -80\,dB.
-
-The simulated HFSS and CST beams for the NS dipole are plotted in Fig.
+The simulated full-faceted and perfect paraboloid beams for the NS dipole are plotted in Fig.
 \ref{fig:modelbeams} (left and center panel) along with an Airy pattern for comparison.
@@
 \begin{figure}[h]
-\includegraphics[width=3.4in]{ref_dipole_and_hera_dish.jpg}
+\includegraphics[width=3.4in]{ref_dipole_and_hera_dish.pdf}
 \caption{The dish with its suspended feed is seen in the back, 50\,m north of one of the reference antennas used in the null experiment to study systematics.
@@
 The measured beams agree with both models in the main lobe out to zenith angles of 15--20$^\circ$ up to slight main lobe tilts, but begin to deviate in the sidelobes where the beam response is 25-30\,dB down from zenith.
-The measured beams typically differ more from both model beams than the models differ from each other, suggesting that real world effects are more significant that the slightly different assumptions used in the CST and HFSS simulations.
+The measured beams typically differ more from both model beams than the models differ from each other, suggesting that real world effects are more significant that the slightly different assumptions used the two beam models.
 In particular, the most likely systematic is mis-centering of the feed over the dish (see Sec.
@@
 
-Figure \ref{fig:measuredbeamslices} shows slices through the E and H planes of these power patterns along with the HFSS and CST numerical models discussed earlier.
+Figure \ref{fig:measuredbeamslices} shows slices through the E and H planes of these power patterns along with the full-faceted and perfect paraboloid numerical models discussed earlier.
 As in the previous plot, the EW and NS beams are shown in the left and right panels, while the different feed heights are shown in the different rows.
@@
 We observe that both models agree with the measured beams in the main lobe but deviate from the data in different ways at the 1--5 dB level in the sidelobes.
-Neither model looks consistently better, suggesting that the as-built HERA dish deviates from both numerical models more significantly than the models deviate from each other due to their slightly different assumptions.
+Neither model agrees consistently better with the data, suggesting that real-world imperfections of the HERA dish dominate over the slightly different modeling assumptions.
 
@@
 The observed dish beam asymmetries, model deviations in sidelobes, and slight shifts of the main lobes all suggest feed centering errors.
-The feed is suspended by rope from three telephone poles spaced around the dish, and is raised by pulling all three ropes to a new length.
+The feed is suspended by three ropes attached from the center of the feed back plane to three telephone poles spaced around the dish, and is raised by pulling all three ropes to a new length.
 Each time this is done the feed centering is slightly disturbed because all three ropes must be pulled to the exact same length to center the feed.
-If feed tilt/rotation errors or dish surface imperfections were significant, then the beam errors at different feed heights would look similar because these errors persist when the feed is raised or lowered.
-All three ropes are tied to a single location on the feed, so rope length errors affect on the feed centering, not its rotation or tilt.
-The fact that the observed model deviations change over the three beam measurements suggests that feed centering errors are most significant because they are the only ones which change when the feed height is changed.
-To mitigate these errors, the feeds in the full HERA array will be tied down to the dish surface at several points.
+Because all three ropes are attached to the same point on the feed, changing their lengths does not affect feed rotation or tilt.
+Thus if rotation or tilt errors, or dish surface imperfections, were significant, then the beam errors at different feed heights would look similar.
+The fact that the observed model deviations change with feed height suggests that feed centering errors are most significant.
+To mitigate all these feed positioning errors, the feeds in the full HERA array will be tied down to the dish surface at several points.
 
@@
 The collecting areas are shown in Table 1 along with the maximal collecting area achieved by the Airy pattern for a 14\,m dish.
-The measured collecting areas are 30--50\% lower than the geometric area.
-This is in line with expectations given that the Airy pattern has the largest possible collecting area, equal to the dish cross section, and the feed's backplane and cylindrical skirt reduce it.
-However we opt for this reduction over added collecting area in order to reduces the azimuthal beam asymmetry.
+The measured collecting areas imply aperture efficiencies of 45--60\%.
+This is in line with expectations given the feed design which tapers the dipole beam towards the edges of the dish to reduce spillover into adjacent dishes.
+The mesh cylinder hanging from the feed back plane around the dipole also reduces the aperture efficiency slightly in order to make the feed beam more azimuthally symmetric.
 
@@
 \hline
-  Airy pattern & 155 & 25.5, 90.8  \\
-    Measured, feed at 5.3\,m & 93.0 & 19.3, 74.3 \\
-    Measured, feed at 5\,m & 77.1 &  16.4, 67.9 \\
-    Measured, feed at 4.5\,m & 68.5 &  15.4, 63.9 \\ 
+  Airy pattern & 155 & 18.7, 90.8  \\
+    Measured, feed at 5.3\,m & 93.0 & 12.7, 74.3 \\
+    Measured, feed at 5\,m & 77.1 &  10.6, 67.9 \\
+    Measured, feed at 4.5\,m & 68.5 &  10.0, 63.9 \\ 
   \hline
@@
 We use a fiducial Epoch of Reionization model generated with 21cmFast \citep{21cmfast}.
-This model assumes $\zeta=31.5$ for the ionizing efficiency, $T_\mathrm{vir}=1.5\times10^4$\,K for the minimum virial temperature of halos producing ionizing photons, and $R_\text{mfp}=30$\,Mpc for the mean free path of ionizing photons, and reaches 50\% ionization at $z \sim 9.5$ and complete ionization at $z \sim 7$, and is consistent with most current observations \citep[e.g.][]{PoberNextGen}.
-We predict SNRs first for a foreground \textit{avoidance} approach where only modes outside of the wedge plus a buffer of $\Delta k_\parallel=0.1\,\mathrm{h}\,\mathrm{Mpc}^{-1}$ are used.
-These modes have frequency dependence larger than that of any source on the sky.
+This model assumes $\zeta=31.5$ for the ionizing efficiency, $T_\mathrm{vir}=1.5\times10^4$\,K for the minimum virial temperature of halos producing ionizing photons, and $R_\text{mfp}=30$\,Mpc for the mean free path of ionizing photons, and reaches 50\% ionization at $z \sim 9.5$ and complete ionization at $z \sim 7$, and is consistent with current observations \citep[e.g.][]{PoberNextGen}.
+
+We predict SNRs first for a foreground \textit{avoidance} approach where only modes outside of the wedge plus a buffer of $\Delta k_\parallel=0.15\,\mathrm{h}\,\mathrm{Mpc}^{-1}$ are used.
+These modes have frequency dependence larger than that of any smooth spectrum source on the sky, and this buffer size is chosen to exclude modes which leak out of the wedge due to beam frequency dependence.
+Due to imperfect impedance matching at the center of the 100-200\,MHz band, the $z\sim8.5$ band requires a slightly larger buffer, though our chosen buffer effectively avoids the leakage in other bands \citep{ewallwice16}.
 We also predict SNRs for a foreground \textit{subtraction} approach using all modes whose instrumental frequency dependence is larger than that of a source at the edge of the main lobe.
 
-The SNRs computed with the measured collecting areas are 15-20 with foreground avoidance compared with 25 for the Airy pattern.
+The SNRs computed with the measured collecting areas are 10-13 with foreground avoidance compared with 19 for the Airy pattern.
 With foreground subtraction, the SNR falls from 90 with the Airy pattern to 60-75 with the measured collecting areas.
-In all cases this reduction is a loss of sensitivity, but a power spectrum detection is still always very significant at the 15$\sigma$ level or better.
+In all cases this reduction is a loss of sensitivity, but a power spectrum detection is still always very significant at the 10$\sigma$ level or better.
 
@@
 The added frequency dependence of the changing overall gain and beam shape with frequency is addressed by the other papers in this series.
-Given that our measured dish power patterns agree well with both numerical models (HFSS and CST) in the main lobe but deviate in the sidelobes, and that these models make somewhat different assumptions about the dish surface, we take them as a representative pair of possible dish models.
+Given that our measured dish power patterns agree well with both numerical models (full-faceted and perfect paraboloid) in the main lobe but deviate in the sidelobes, and that these models make somewhat different assumptions about the dish surface, we take them as a representative pair of possible dish models.
 We use the empirically best feed height of 5.3\,m.
@@
 
-Figure \ref{fig:delayspec} (top panel) shows simulated foreground delay spectra at various LSTs using the nominal HFSS beam.
+Figure \ref{fig:delayspec} (top panel) shows simulated foreground delay spectra at various LSTs using the full-faceted beam.
 As all these LSTs correspond to high galactic latitudes far from the galactic center, the total visibility power (the level of the zero delay mode) varies only by a factor of a few over these LSTs on both baseline lengths (14.6\,m (left panel), 43.8\,m (right panel)).
@@
 \includegraphics[width=6in]{nithya_fg_pspec_lst60deg.pdf}
-\caption{We plot simulated foreground delay spectra using the HFSS beam at various LSTs (top panel).
+\caption{We plot simulated foreground delay spectra using the full-faceted beam at various LSTs (top panel).
 The maximum horizon brightening at the positive horizon occurs close to 0$^\circ$ LST.
@@
 At larger delays, especially near the positive delay horizon limit, all three model delay spectra diverge due to the significant edge brightening which effectively discriminates between these models.
-The CST and HFSS beams reach roughly -32\,dB and -38\,dB at $80^\circ$ zenith angle (Figure \ref{fig:modelbeams}), consistent with the fact that the CST beam has a larger horizon brightening than the HFSS beam.
+The perfect paraboloid and full-faceted beams reach roughly -32\,dB and -38\,dB at $80^\circ$ zenith angle (Figure \ref{fig:modelbeams}), consistent with the fact that the perfect paraboloid beam has a larger horizon brightening than the full-faceted beam.
 This is seen in the delay spectra for both baseline lengths, though the edge brightening is much clearer on the longer baseline where it less diluted by zero delay emission.
@@
 We begun with power pattern measurements made using the beam mapping system of \citet{neben15} which we deployed at the prototype three-element HERA array at the National Radio Astronomy Observatory--Green Bank.
-We measured the dish power pattern with the feed at different heights over the dish surface and found that the best focus is at a feed rigging height of 5.3\,m, though this may change for different feed designs being explored\citep{feedoptimizationmemo}.
+We measured the dish power pattern with the feed at different heights over the dish surface and found that the best focus is at a feed rigging height of 5.3\,m, though this may change for different feed designs being explored \citep{feedoptimizationmemo}.
 The measured beams probe nearly two thirds of the visible sky down to -30\,dB relative to boresight, and agree well with both models in the main lobe out to 10--20$^\circ$ from zenith.
@@
 The most likely culprit is feed mis-centering which shifts and distorts the main lobe sidelobes.
-In the full HERA array, the suspended feeds will be tied to the dish surface at several points to level and center them.
-Characterizing the level of antenna-to-antenna beam variation in the full HERA array and its effects on power spectrum analyses, as Neben et al.
-(in press) do for the MWA, is left as future work.
+In the full HERA array, the suspended feeds will be tied to the dish surface at several points to fine tune the feed centering and leveling, and mitigate wind buffeting.
+Characterizing the level of antenna-to-antenna beam variation in the full HERA array and its effects on power spectrum analyses, as \citet{neben16} do for the MWA, is left as future work.
 
-We quantify HERA's sensitivity to the 21\,cm power spectrum given our beam measurements by first computing the collecting area of the measured beams at the different feed rigging heights, finding 93\,m$^2$ at the best focus.
-We observe a reduction of 30--50\% from the geometric cross section of a 14\,m dish due to feed blockage and under-illumination of the dish.
+We quantify HERA's sensitivity to the 21\,cm power spectrum given our beam measurements by first computing the collecting area of the measured beams at the different feed rigging heights, finding 93\,m$^2$ at the best focus, implying an aperture efficiency of 60\%.
+Feed optimization is ongoing, but the present feed sacrifices aperture efficiency in order to taper the dipole beam towards the edges of the dish and make the X and Y dipole beams as similar as possible using a cylinder hanging from the back plane.
 We convert our measured collecting areas into effective dish sizes, then use 21cmSense to predict the overall power spectrum SNR at $z\sim9.5$ with one season of HERA-320 data.
-We predict SNRs of 19.3 and 74.3 using foreground avoidance and subtraction approaches respectively, compared with SNRs of 25.5 and 90.8 using an ideal unobstructed 14\,m aperture (Airy pattern).
+We predict SNRs of 12.7 and 74.3 using foreground avoidance and subtraction approaches respectively, compared with SNRs of 18.7 and 90.8 using an ideal unobstructed 14\,m aperture (Airy pattern).
 Still, these sensitivities permit a very significant detection of the 21\,cm signal after a single observing season.
@@
 
-We predict the magnitude of this effect for the HERA element as well as its dependence on beam modeling uncertainties.
+We predict the magnitude of this effect for the HERA element and discuss the uncertainties in this estimate due to beam modeling uncertainty.
 As expected, we find that the level of horizon brightening is largest when the galaxy is just above the horizon, and lowest when it is well below.
-When this pitchfork effect is large, we find that the uncertainty in its predicted amplitude is also large, as seen in the differences between the delay spectra calculated using HFSS and CST beam models.
+When this pitchfork effect is large, we find that the uncertainty in its predicted amplitude is also large, as seen in the differences between the delay spectra calculated using full-faceted and perfect paraboloid beam models.
 When the effect is small, the two beam models produce much more similar results, highlighting the delay spectrum as an exquisite probe of the difficult-to-measure beam response at very low elevations.
+Of course the delay spectrum provides only an integrated measure of the beam, but some information can still be extracted.
+By forward modeling foreground delay spectra using different MWA primary beam models, for instance, it was observed that the MWA bowtie dipoles are better modeled as isotropic radiators than hertzian dipoles at these low elevations (N.
+Thyagarajan, private communication).
+Direct measurements using transmitter-equipped drones would be ideal and their development is ongoing \citep{drone1,drone2}.
 
-As discussed by the other papers in this series \citep{ewallwice16,patra16,nithya16}, the frequency dependence of both the beam's angular response and its overall gain widen the delay kernel of a source, leaking power into the EOR window out to $k_\parallel=$0.15-0.23h\,Mpc$^{-1}$.
-This is well inside the wedge plus buffer used in a foreground avoidance analysis.
-Foreground subtraction, however, requires calibrating out the instrument frequency response well enough to begin to access cosmological modes within the wedge.
-This is much more challenging, but the sensitivity gains are enormous as those signal modes are thought to be the strongest.
-Even with only foreground avoidance, though, assuming only previously demonstrated analysis techniques, we project a $19.3\sigma$ detection of the EOR power spectrum with a single observing season which would provide begin to probe reionization models in detail and shed light on our cosmic dawn.
+As discussed by the other papers in this series \citep{ewallwice16,patra16,nithya16}, the frequency dependence of both the beam's angular response and its overall gain widen the delay kernel of a source, leaking power into the EOR window out to $k_\parallel\approx$0.15h\,Mpc$^{-1}$ over much of the 100-200MHz band.
+This leakage falls within the wedge buffer used in a fiducial foreground avoidance analysis, so our SNR projections take into account the sensitivity reduction due to beam chromaticity.
+These sensitivities can be improved using new techniques such as foreground covariance downweighting and fringe rate filtering \citep{ali2015,parsonsoptimalfringeratefiltering}, which mitigate foreground leakage into the EOR window, thereby permitting a smaller buffer.
+Using only these previously demonstrated techniques, we project a $13\sigma$ detection of the EOR power spectrum with a single observing season which would provide begin to probe reionization models in detail and shed light on our cosmic dawn.
 
